### 2015-02-10 papers/data_paper/datapaper.tex
first

\documentclass[preprint2]{emulateapj}

\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{gsavorgn@astro.swin.edu.au}
\newcommand{\fitfigurewidth}{0.8\textwidth}

\shorttitle{Data paper}
\shortauthors{Savorgnan et al.}

\begin{document}

\title{Data paper}

\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
\email{gsavorgn@astro.swin.edu.au}

%\and

%\author{A. W. Graham\altaffilmark{1}}
%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

%\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
%CTIO is operated by AURA, Inc.\ under contract to the National Science
%Foundation.}
%\altaffiltext{2}{Society of Fellows, Harvard University.}
%\altaffiltext{3}{present address: Center for Astrophysics,
%    60 Garden Street, Cambridge, MA 02138}
%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
%\altaffiltext{5}{Patron, Alonso's Bar and Grill}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
abstract % 2d worse than 1d say it!!!
\end{abstract}

\keywords{keywords}

\section{Introduction}
\label{sec:int}
Supermassive black holes and host bulges have very different sizes. 
If the event horizon of the Galactic supermassive black hole was as big as a grain of sand of the Sahara desert, 
then the black hole gravitational sphere-of-influence would be as big as the international airport of Cairo, 
and the Galactic bulge would be as big as the Sahara desert itself.
It is thus surprising that the masses of supermassive black holes ($M_{\rm BH}$) 
scale with a number of properties of their host bulges, 
indicating the non-gravitational origin of these correlations 
(e.g.~\citealt{dressler1989,yee1992,kormendyrichstone1995,magorrian1998,ferraresemerritt2000,gebhardt2000,graham2001,
marconihunt2003,haringrix2004,graham2012bent}). {\bf AL: need to talk to you about Laor's work}\\
The tightness (or small scatter) of the observed black hole mass correlations has led to the idea
that black holes and host galaxies have coevolved with some sort of self-regulated growth.
Exploring the evolution of this growth with cosmic time could help identify
the driving mechanisms of the black hole - galaxy coevolution.
Observations at $z=0$ set the local benchmark from which to measure this evolution.
Any complete theory or model describing the coevolution of galaxies and black holes must incorporate 
all of the observed scaling relations, which also have to be consistent with each other.
%Modern semi-analytic models use the observed black hole mass scaling relations 
%to constrain the black hole accretion rate .
Modern hydrodynamical simulations, such as EAGLE \citep{schaye2015}, calibrate the feedback efficiencies 
to the $z=0$ black hole mass - galaxy mass relation.
Scaling relations can also be employed to predict the masses of black holes in other galaxies, where a direct
measure of $M_{\rm BH}$ would be extremely time consuming or simply impossible due to technological limitations.
Many accurate $M_{\rm BH}$ predictions would help derive 
the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction}) 
and space density (\citealt{grahamdriver2007smbhmassdensity} and references therein; \citealt{comastri2015}). \\
Since the first stellar dynamical detections of black holes were carried out in the '80s 
(see the references in the reviews by \citealt{kormendyrichstone1995} and \citealt{richstone1998}), 
the number of (direct) black hole mass measurements has increased with time 
and it has recently become a statistically meaningful sample -- of the order of 100 objects -- 
with which one can study SMBH demographics. 
It is now generally accepted that supermassive black holes reside at the center of most, if not all, 
massive galaxies, either quiescent or active. \\
Massive, early-type galaxies are often composite systems. 
The knowledge that many elliptical galaxies contain embedded stellar disks can be dated back to 
at least three decades ago 
\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995}. 
After examining long-slit spectroscopic observations of morphologically classified elliptical galaxies in the Fornax cluster, 
\cite{donofrio1995} and \cite{graham1998fornax} concluded that only $\sim$$1/3$ of their galaxies do not harbour any disk-like component.
Surveys with integral field spectrographs of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
have further changed our idea of ``elliptical'' galaxies, 
being all but simple and featureless pressure-supported systems.
More than half of all morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.
\cite{krajnovic2013} showed that ``fast rotators'' as a class are simply disks or at least disk-like objects. 
In their magnitude-limited survey, systems 
without any signature of disk-like components (neither in the kinematics nor in the photometry) 
dominate only the most massive end (beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
Given the prevalence of disks, it is important to perform bulge/disk decompositions, 
if one is to properly explore the black hole-bulge connection. \\
Measuring the photometric and structural properties of a galaxy's spheroidal component requires the ability to 
separate it from the rest of the galaxy. 
Galaxy decomposition is a parametric analysis that allows one to fit the surface brightness distribution
of galaxies using a combination of analytic functions (usually one function per
galaxy component, such as bulges, disks, bars, nuclei, etc.).
The one-dimensional (1D) technique involves fitting isophotes to the galaxy image, extracting the (one-dimensional) surface 
brightness radial profile and modeling it with a combination of analytic functions.
With the two-dimensional (2D) technique one fits analytic functions directly to digital images. \\
Over the past eight years, five independent studies 
\citep{grahamdriver2007,sani2011,vika2012,beifiori2012,lasker2014data,lasker2014anal} have attempted galaxy decomposition
in order to derive the bulge parameters and explore their relation with the black hole masses.
Interestingly, the past studies all %investigated the black hole mass scaling relations using 
used almost the same sample of galaxies, 
but they claimed some contradictory conclusions.
One study \citep{grahamdriver2007} obtained a good $M_{\rm BH}-n_{\rm sph}$ correlation
(the bulge S\'ersic index $n_{\rm sph}$ is a measure of the central radial concentration of stars), 
whereas the remaining four did not.
\cite{lasker2014anal} declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity and the bulge luminosity, 
as opposed to \cite{beifiori2012}, who claimed that the bulge mass is a better tracer of $M_{\rm BH}$ than the galaxy mass.
The past studies did not converge to the same conclusions 
because their best-fit models for the same galaxy were often 
significantly different and not consistent with each other in terms of fitted components. 
Moreover, none of these studies attempted an individual galaxy-by-galaxy 
comparison of their models with the previous literature. 
We have now made this comparison and performed the optimal decompositions,
using $3.6~\rm \mu m$ \emph{Spitzer} satellite imagery, 
which is an excellent proxy for the stellar mass, superior to the $K$-band (\citealt{sheth2010} and references therein).
We will use these to obtain improved black hole mass scaling relations using the largest to date sample of 72 galaxies.

This paper is structured as follows.
Section \ref{sec:data} presents the data-set used to conduct this study. 
Section \ref{sec:anal} describes how we performed the galaxy decompositions, 
i.e.~how we identified and modeled the sub-components that constitute our galaxies. 
In Section \ref{sec:res} we outline the results from our analysis 
and we discuss the error analysis. 
Section \ref{sec:concl} summarizes our main conclusions. 
The individual galaxy decompositions are made available in the electronic version of this manuscript.

\section{Data}
\label{sec:data}
%\subsection{Initial sample}
Our initial galaxy sample (see Table \ref{tab:sample}) consists of 75 objects for which a dynamical detection of the black hole mass 
has been reported in the literature and for which at least one $3.6~\rm \mu m$ \emph{Spitzer}/IRAC observation was made publicy 
available at the time we began our investigation (2013).
Black hole masses were drawn from the catalog of \citet{grahamscott2013} for 70 galaxies,
from \citet{rusli2013bhmassesDM} for 4 galaxies 
and from \citet{greenhill2003} for 1 galaxy.

%\clearpage
\input{table_sample.tex}
%\noindent
\input{table_observations.tex}

\subsection{\emph{Spitzer}/IRAC observations}
\subsubsection{Data acquisition}
For each of our 75 galaxies, we downloaded from the 
Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs), 
listed in Table \ref{tab:obs}.
Each AOR is an individual Spitzer observation sequence, and
includes a number of data frames (the individual exposures) and the calibration data.
The data frames were selected to be %``enhanced Level 1 products'', or
corrected Basic Calibrated Data (cBCD).
Basic Calibrated Data (BCD) are produced by the IRAC Level 1 pipeline. 
This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
and performs dark subtraction, flatfielding correction and flux calibration (into units of $\rm MJy~sr^{-1}$). 
The final product (the BCD) is a flux-calibrated image which has had all the well-understood instrumental signatures removed.
BCD frames are further processed through an ``artifact correction'' pipeline 
that mitigates the commonly found artifacts of stray light, saturation, ``muxbleed'' and column pulldown\footnote{Stray light 
includes scattered light from stars outside the array location as well as filter ghosts from bright stars. 
Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
It looks like a decaying trail of pixels, repeating every fourth column.
Column pulldown is caused by a bright pixel that triggers a bias shift within its respective column, 
creating a lower background value throughout the entire column than in the surrounding columns.}.
After the artifact correction has been applied, the BCD becomes a cBCD.

\subsubsection{Mosaicing}
We performed image mosaicing using the %(command line version of the) 
MOPEX package \citep{makovozmarleau2005mopex}.
Individual cBCD frames with exposure time of $1~\rm sec$ were rejected.
Permanent or semi-permanent bad pixels, contained in a semi-static mask (the ``pmask''), were ignored.
Each AOR is associated to a specific pmask. 
Therefore, when multiple AORs were available for the same galaxy, 
we merged the different pmasks. 
Outlier rejection was performed with the dual outlier and multi-frame techniques.
The pixel size of the mosaic was set to be the same as the input cBCD frames ($1''.22 \times 1''.22$).
For $3.6~\rm \mu m$ observations with this pixel scale, 
the photometric zeropoint magnitude is $m_{\rm zp} = 17.26 \rm~mag$.
The orientation of the mosaic was set to the average rotation angle of the input cBCD frames. 
%{\bf TBD: not n-e oriented or re-sampled because problems with 2d PSF. }
Individual cBCD frames were combined together into a single mosaic with the default linear interpolation algorithm.

\subsubsection{Overlap correction}
Before generating a mosaic, MOPEX can perform background matching among the individual frames
by using the \emph{overlap} module. 
This module calculates and applies an additive correction to the individual frames,
producing a consistent background across the mosaicked image.
According to the \emph{Spitzer Data Cookbook}, the use of the \emph{overlap} module is not particularly recommended for 
$3.6~\rm \mu m$ observations. 
However, after a visual inspection of the mosaics obtained without activating the \emph{overlap} module,
we found that all the mosaics obtained from multiple AORs were affected by patchiness, 
due to bias fluctuations in the CCD array.
For this reason, we re-generated the multiple-AORs mosaics by activating the \emph{overlap} correction,
which successfully removed the ``chessboard'' pattern (see Figure \ref{fig:overlap} for an example).

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/m49nooverlap.eps}
\includegraphics[width=0.49\columnwidth]{images/m49overlap.eps}
\caption{An example of the \emph{overlap} correction. 
The image mosaic of the galaxy M49 was obtained by co-adding frames coming from 8 different AORs.
The evident patchiness (left image) was removed (right image) using the \emph{overlap} module.}
\label{fig:overlap}
\end{center}
\end{figure}

\subsubsection{Sigma mosaics}
For each individual cBCD frame, the IRAC Level 1 pipeline calculates the uncertainty associated to each pixel
and produces an uncertainty frame (or sigma frame).
The initial uncertainty is estimated as the Poisson noise in electrons plus the readout noise added in quadrature
($\sigma^2 = \sigma^2_{\rm readoutnoise} + \sigma^2_{\rm Poisson}$).
This initial sigma frame is carried through the pipeline, and additional uncertainties (e.g.~dark current and flat field uncertainties) 
are added in quadrature when appropriate.
When MOPEX generates an image mosaic, it also produces the associated sigma mosaic 
by interpolating the individual uncertainty frames and co-adding them,
following the standard assumption of additive variances.

\subsubsection{Sky subtraction}
Sky subtraction was performed manually on the image mosaics using the tasks {\tt marksky} and {\tt skyfit} 
of the IRAF\footnote{IRAF is the Image Reduction and Analysis Facility, 
distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} 
package GALPHOT\footnote{GALPHOT was developed in the IRAF - STSDAS environment mainly by 
W. Freudling, J. Salzer, and M. P. Haynes \citep{haynes1999galphot}.}.
The task {\tt skyfit} also provided an estimate of the sky root mean square ($RMS_{\rm sky}$).
%sky value also checked with Galfit

\subsubsection{Additional aestethic corrections}
The image mosaics of 4 galaxies (NGC 0821, NGC 2974, NGC 4291, NGC 4459) were found to be affected 
by bright, highly saturated stars lying close to the target galaxies.
These stars were modeled and subtracted using the software Galfit \citep{peng2010} 
and the extended IRAC Point Response Function (PRF) image at $3.6~\rm \mu m$.
This helped remove the extended wings and spikes of the saturated stars 
(see Figure \ref{fig:aesth} for an example).

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n4459brightstar.eps}
\includegraphics[width=0.49\columnwidth]{images/n4459nobrightstar.eps}
\caption{An example of aestethic correction.
The images show the mosaic of the galaxy NGC 4459 before (left) and after (right) the removal 
of a bright saturated star.}
\label{fig:aesth}
\end{center}
\end{figure}

\subsubsection{Image masking}
Galactic stars and any other objects different from the target galaxy 
were masked through a two-step procedure.
First, we created an initial mask using the IRAF task 
{\tt objmasks}, %\footnote{{\tt objmasks} is part of the {\tt noao.nproto} package.},
that identifies objects by threshold sigma detection.
Then, we refined each mask by hand, using the software 
SAOImage DS9\footnote{SAOImage DS9 development has been made possible by funding 
from the Chandra X-ray Science Center (CXC) 
and the High Energy Astrophysics Science Archive Center (HEASARC).} 
in conjunction with the IRAF task 
{\tt mskregions}. %\footnote{{\tt mskregions} is part of the {\tt proto} package.}.
We identified and carefully masked not only contaminating sources located in the field of the image mosaic,
but also objects overlapping with the target galaxy, such as foreground stars, globular clusters or red giant stars.

\subsubsection{1D PSF}
The one-dimensional Point Spread Function was charachterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected galaxy radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
%We employed both a Gaussian and a Moffat \citep{moffat1969} profile. 
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained %$FWHM = 2''.03$ for the Gaussian function,
$(\alpha, \beta) = (2''.38, 4.39)$ %for the Moffat function
(see Appendix \ref{sec:app1} for the analytical expressions of the Moffat function).

\subsubsection{2D PSF}
The IRAC support team provides the users with a two-dimensional instrument Point Response Function (PRF) at $3.6~\rm \mu m$.
However, we found this PRF to be inadequate for the purposes of our analysis.
In fact, the $FWHM$ of the IRAC instrument PRF ($\sim 1''.8$), as measured by the IRAF task {\tt imexamine}, 
is systematically smaller than the average $FWHM$ of ``real'' stars ($\sim 2''.0$). 
Figure \ref{fig:psf} illustrates this issue.
We also tested the IRAC PRF by providing it as the input Point Spread Function (PSF) for Galfit 
and fitting a number of stars in different image mosaics.
A visual inspection of the fit residuals confirmed that the IRAC instrument PRF is narrower than ``real'' point sources.
For this reason, we constructed our 2D PSF according to the following method 
(as directed by C. Peng, private communication).\\
We provided the IRAC instrument PRF as the input PSF for Galfit 
and simultaneously fit 7 bright stars (belonging to different mosaics), 
modeling the stars with Moffat profiles 
and constraining all the profiles to have the same $(\alpha, \beta)$, position angle and axis ratio.
The 2D PSF image was then obtained by taking the best fit Moffat model -- the same best-fit model for all 7 stars, by construction -- 
and convolving it with the IRAC instrument PRF.
The advantage of this method is to obtain a 2D PSF that is wider than the instrument PRF, 
but maintains the asymmetric features of the instrument PRF (e.g.~wings and spikes).
%This procedure was repeated using a Moffat profile in place of the Gaussian profile.
We then tested this 2D PSF 
on a number of stars (these stars were different from the 7 stars employed to build the 2D PSF image)
and verified that it correctly reproduces the shape of ``real'' point sources.

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth, trim = 220 30 20 20, clip=True]{images/psf.eps}
%\includegraphics[width=1\columnwidth]{images/star1_cut.eps} \\
%\includegraphics[width=1\columnwidth]{images/PRF_IRACch1_129_129_cut.eps}
\caption{Normalized flux versus radial distance 
from the image centroid of an observed point source (top panel) 
and of the IRAC instrument PRF (bottom panel). 
The normalized flux is given in arbitrary units, 
and the radial distance is in units of pixel size of the IRAC detector (1 pixel = $1''.22$).
The blue solid line shows our 1D Moffat PSF model,
which has been normalized to intersect the data point with the largest flux. 
The $FWHM$ of the IRAC PRF is clearly smaller than that of a ``real'' star.
The inserts display the images of the observed point source and the IRAC PRF.}
\label{fig:psf}
\end{center}
\end{figure}

\subsection{Additional data}
\label{sec:adddata}
\subsubsection{Kinematics}
\label{sec:kinem}
A kinematical classification (slow/fast rotator) is available for 34 of our 75 galaxies 
from the ATLAS$^{\rm 3D}$ survey \citep{atlas3dIII-MNRAS} 
and for 3 additional galaxies from \citet{scott2014}.
This classification (Table \ref{tab:sample}, column 7) 
concerns the kinematic properties of galaxies within the instrument field-of-view, % (typically up to one effective radius),
but does not contain additional information -- crucial for our analysis -- about kinematic substructures, 
such as embedded disks or kinematically decoupled components, 
which can require separate modeling.
For this reason, we also visually inspected the velocity fields of our galaxies, 
when available from the literature.
Velocity maps were taken from the ATLAS$^{\rm 3D}$ survey for 34 galaxies 
(observed with SAURON by \citealt{krajnovic2011}),
from \citet{scott2014} for 2 galaxies 
(observed with WiFeS)
and from the SLUGGS survey for 12 galaxies 
(observed with DEIMOS by \citealt{arnold2014}).
While the field-of-views of SAURON ($33'' \times 41''$) and WiFeS ($25'' \times 38''$) 
reach to about one galaxy effective radius (for our local galaxies),
observations taken with DEIMOS can probe the galaxy kinematics well beyond two effective radii.

\subsubsection{AGNs and nuclear dust}
The X-ray, UV and optical radiation 
emitted by the the accretion disks of Active Galactic Nuclei (AGNs) can stimulate infrared thermal emission 
from circumnuclear dust, if present. 
This means that if a galaxy hosts an optical AGN \emph{and} a certain amount of nuclear dust,
we expected to detect some non-stellar nuclear emission at $3.6~\rm \mu m$.
It is therefore important to identify which of our galaxies have both an optical AGN and circumnuclear dust.
To help with this task, we searched NED\footnote{NED is the NASA/IPAC Extragalactic Database.} 
for the individual galaxies and their associated literature.
Unsurprisingly, dusty AGNs were more frequently found in late-type spiral galaxies.

\subsubsection{S\'ersic/core-S\'ersic classification}
\label{sec:corser}
Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or bulges) 
with partially depleted cores, 
i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs.
The majority are thus unresolved in our image mosaics. 
We masked these unresolved cores by excluding the surface brightness profile 
within 3 PSF's $FWHM$ from the galaxy center.
In case of cores with sizes exceeding the PSF's $FWHM$, we excluded the data points within the size of the core 
plus 3 PSF's $FWHM$.
The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
comes from the compilation of \citet{savorgnangraham2014},
who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion, $\sigma$:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
This resulted in us assigning cores to just 2 galaxies when using this alternative method 
if no high resolution image was available.

\section{Analysis}
\label{sec:anal}
\subsection{Isophotal analysis}
We performed an isophotal analysis of our galaxies using the IRAF task {\tt ellipse} \citep{taskellipse}, 
which fits elliptical isophotes to galaxy images.
The center of the isophotes was held fixed, while the ellipticity ($\epsilon$), the position angle ($P.A.$),  
and the amplitude of the fourth harmonic\footnote{The amplitude of the fourth harmonic deviations from perfect ellipses 
($B4$) parameterizes the diskyness ($B4>0$) or boxyness ($B4<0$) of the isophotes.} ($B4$) were allowed to vary with radius.
The step in semi-major axis length between successive ellipses was set to increase linearly, 
and then geometrically in our second run\footnote{In case of linear steps, 
the semi-major axis length for the next ellipse was calculated by adding $1$ pixel to the current length.
In case of geometric steps, the semi-major axis length for the next ellipse 
was calculated as $1.1$ times the current length.}.
As a result, for each galaxy we produced respectively a ``linearly sampled'' and a ``logarithmically sampled'' 
surface brightness profile along the major-axis. 
Major-axis surface brightness profiles were then projected along the equivalent-axis,
i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$), 
also called the circularized radius.
Isophotes corresponding to an intensity less than $3 \times RMS_{\rm sky}$ were rejected.
Some surface brightness profiles were truncated at our discretion before the $3 \times RMS_{\rm sky}$ limit, 
according to specific technical reasons (e.g.~contamination from light of a neighboring galaxy, 
disturbed morphology in the galaxy outskirts, etc.).
Individual cases are discussed in Section \ref{sec:indgal}.

\subsection{Unsharp masking}
Unsharp masking is an image sharpening technique useful to reveal asymmetric structures in galaxies, 
such as bars or (inclined) embedded disks. 
First, the original galaxy image was smoothed with a Gaussian filter.
Then, the original image was divided by the smoothed one. 
The result of such an operation is the ``unsharp mask''. 
The asymmetric features revealed by this technique have sizes 
comparable to the $FWHM$ of the Gaussian kernel used for the smoothing.
Therefore, for each galaxy, we produced a set of different unsharp masks by varying the $FWHM$ of the filter,
to identify all the asymmetric features that could bias the fitting process and may need modeling.
This information was used in combination with kinematic and AGN information discussed in Section \ref{sec:adddata}.

\subsection{1D fitting routine}
The decomposition of surface brightness profiles was performed with software written by G. Savorgnan.
This software can fit an observed surface brightness profile with any linear combination of 
a set of analytical functions (S\'ersic, exponential, Gaussian, Moffat, Ferrer, symmetric Gaussian ring etc. 
see Appendix \ref{sec:app1} for a description of the analytical form of these profiles).
At each iteration, 
the model is numerically convolved with a Moffat filter, to account for PSF effects, 
and then matched to the data.
The minimization routine is based on the Levenberg-Marquardt algorithm.
During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
surface brightness profile.

\subsection{Smoothing technique}
\label{sec:smooth}
Some nearby galaxies in our sample have very large apparent sizes 
and for them we obtained surface brightness profiles more extended than $8~\rm arcmin$.
This means that their outermost (significant) isophote 
corresponds to a projected galactic radius $R$ 
of more than $240$ times the $FWHM$ of the instrumental PSF.
Such level of spatial resolution is unnecessary for the purposes of our analysis 
and, especially in the case of a clumpy star forming galaxy, 
it results in a ``noisy'' surface brightness profile.
Moreover, in the case of a linearly sampled light profile,
it significantly prolongs the computational time of the fitting routine 
(because, at each iteration, the PSF convolution is performed numerically on a large array).
To overcome this problem, we introduced a method to which we refer as the ``smoothing technique''.
This method was applied to the galaxies M31, M81, NGC 4945 and NGC 5128.
For each of these galaxies, we took the image mosaic and we convolved it with a Gaussian filter 
whose $FWHM$ was larger than the $FWHM$ of the instrumental PSF.
We then ran {\tt ellipse} on the convolved image and extracted 
``linearly sampled'' and ``logarithmically sampled'' surface brightness profiles. 
For the ``linearly sampled'' profiles, we set the radial step between contiguous isophotes to be 
comparable to the $FWHM$ of the smoothing Gaussian filter.
Doing so, we reduced the number of fitted isophotes and we also produced smoother surface brightness profiles.
Before the software fit a smoothed light profile, the model to be fit was convolved twice:
the first time to account for PSF effects, 
and the second time to account for the artificial Gaussian smoothing applied to the image mosaic.

\subsection{Identifying and modeling sub-components}
\label{sec:cpts}
In this Section we give a general overview of the guidelines that we followed to identify and model 
the sub-components that constitute our galaxies. 
However, given the level of accuracy and detail to which each galaxy decomposition has been performed in our analysis,
it is hard to encompass all aspects of this matter in a few paragraphs.
The modeling of each galaxy represented a particular and original problem, 
and we remand the reader to Section \ref{sec:indgal},
where we provide individual descriptions of the galaxies that we analyzed. \\
As stressed in Section \ref{sec:int}, our investigation is primarily focused on the spheroidal components 
of galaxies.
%This is naively identified with the whole galaxy in case of an elliptical galaxy,
%and with the bulge of a lenticular or spiral galaxy.
We assumed \emph{a priori} that each of our galaxies has a unique spheroidal component, 
that we modeled with a S\'ersic profile. \\
Disks were normally fit with the exponential model, 
although in the case of highly inclined or edge-on systems we preferred using $n < 1$ S\'ersic functions. 
\citet{pastrav2013a,pastrav2013b} showed that, due to projection effects, their simulated images of inclined galaxy disks 
are better fit by S\'ersic functions with $n < 1$ than pure exponential profiles.
The inclined embedded disks of some ``elliptical'' galaxies were described with Ferrer functions, rather than $n < 1$ S\'ersic functions. 
This choice is motivated by the fact that a S\'ersic + Ferrer model is less degenerate than a S\'ersic + S\'ersic model, 
since the S\'ersic profile can assume any positive ($n > 1$) or negative ($n < 1$) curvature, 
whereas the Ferrer profile can only have a negative curvature as required for an inclined disk. \\
The presence of large-scale disks, such as those of lenticular and spiral galaxies, 
were known \emph{a priori} from the galaxy morphological classification (as listed on NED), 
although some of them were re-classified by us as having intermediate-scale embedded disks.
These were identified in a number of different ways. 
If highly inclined, they can obviously be spotted from the galaxy image or the unsharp mask.
Local maxima in the ellipticity and fourth harmonic profiles 
can provide footprints of less obvious inner disks.
In particular, the ellipticity profile helps distinguish embedded disks from large-scale ones.
Galaxy disks typically have fixed ellipticity, reflecting their inclination to our line of sight.
On the other hand, spheroids can have their ellipticities varying with radius,
but they are usually rounder than inclined disks, thus their average ellipticities are lower than those of inclined disks.
If the ellipticity profile of a galaxy increases with radius, 
this can be ascribed to an inclined disk that becomes progressively more important over the spheroid,
whereas a radial decrease of ellipticity signifies the opposite case.
Therefore, in a situation where a disk is identified from the galaxy image, 
but its extent (large- or intermediate-scale) is ambiguous,
the shape of the ellipticity profile can be decisive. 
Another way to establish the presence of an embedded disk is to look at the velocity map of a galaxy,
following the approach of \citet{arnold2014}. 
A local angular momentum decrease with increasing radius is indicative of an intermediate-scale disk 
that fades toward larger radii. \\
%As an illustration, we consider the galaxy NGC 3377.
%For this galaxy, \citet{arnold2014} reported a strong decline in local specific angular momentum beyond $\sim 35''$, 
%with a disk-to-bulge transition occurring at about $\sim 50''$.
%They did attempt a three-component decomposition (accounting for a bulge, an embedded disk and a central cusp), 
%but unfortunately they fit the spheroidal component with a limited two-parameter $R^{1/4}$ profile {\bf TBD: cite de vaucouleurs} 
%rather than a three-parameter $R^{1/n}$ S\'ersic function.
%Here we used a surface brightness profile twice as extended as that used by \citet{arnold2014} 
%and we identified a nuclear disk and an intermediate-scale disk, both embedded in a larger spheroidal component (see Figure \ref{fig:n3377ex}).
%The presence of an intermediate-scale disk is evident from the unsharp mask of the image mosaic 
%and also from the ellipticity profile, which increases with increasing radius until $R \sim 45''$ (along the major-axis) 
%and dramatically drops at larger radii.
%The nuclear disk can be spotted from the peak at $R \sim 5''$ in the $B4$ profile.
%In our galaxy model for NGC 3377, 
%the difference between the S\'ersic profile of the bulge and the exponential profile of the intermediate-scale disk is minimum in correspondence 
%of the maximum ellipticity, 
%thus our model correctly reproduces the isophotal properties of the galaxy. 
%The residuals of the fit, especially along the major-axis, display some minor structures which indicate that 
%the bulge S\'ersic index might have been slightly overestimated.
%This could be due to the fact that the embedded disk would be better described by a truncated exponential function.
%Alternatively, a contribution from a stellar halo (not included in our model) at large radii could be the reason of a 
%too large S\'ersic index for the bulge. 
%Our equivalent-axis decomposition results in a bulge component that accounts for 94\% of the total luminosity, 
%an intermediate-scale embedded disk contributing to 5\% 
%and a nuclear disk with 1\% of the total light. \\
%A similar situation occurs for the galaxy M59 (see Figure \ref{fig:m59ex}), 
%for which our equivalent-axis model returns a spheroidal component and an embedded disk 
%contributing to 92\% and 8\% of the total light respectively. \\
%The edge-on embedded disk of the S\'ersic galaxy NGC 1332 (see Figure \ref{fig:n1332ex}) was hard to model with an exponential function, 
%leading us to prefer a low-$n$ S\'ersic profile. 
%Our equivalent-axis decomposition returns a spheroidal component accounting for 95\% of the total light,
%and an embedded disk accounting for the remaining 5\%.
%In passing, we note that the bulge-disk decomposition performed by \citet{rusli2011} on NGC 1332 
%is significantly different from our best-fit model.
%\citet{rusli2011} did not identify an intermediate-scale embedded disk, 
%but instead proposed a model featuring a S\'ersic bulge ($n \sim 2.3$, $R_{\rm e} \sim 8''$), accounting for 43\% of the total light, 
%and a large-scale exponential disk. 
%This result led them to the conclusion that NGC 1332 is a disk dominated lenticular galaxy 
%and is displaced from the $M_{\rm BH} - L_{\rm K,sph}$ (black hole mass vs. $K$-band spheroid luminosity) relation of \citet{marconihunt2003} 
%by an order of magnitude along the $M_{\rm BH}$ direction.
%Assuming instead that, as suggested by our model, 
%the galaxy spheroid is a factor of two more luminous than what claimed by \citet{rusli2011}, 
%NGC 1332 would no longer be an outlier in the $M_{\rm BH} - L_{\rm K,sph}$ diagram (see Figure \ref{fig:n1332pl}), 
%perfectly fitting within the $1\sigma$ scatter of the $M_{\rm BH} - L_{\rm K,sph}$ relation for S\'ersic bulges of \citet{grahamscott2013}. \\
Bars are usually recognizable from galaxy images and unsharp masks, 
although local maxima/minima or abrupt changes in the radial profiles of the isophotal parameters 
can provide additional evidence for less obvious bars. 
As noted, we fit bars with Ferrer functions or low-$n$ S\'ersic profiles ($n \sim 0.2$). \\
The presence of a nuclear component -- either resolved or unresolved -- was generally expected in 
(but not restricted to) galaxies that host an optical AGN and circumnuclear dust.
Nuclear stellar disks and nuclear star clusters fall into the category of nuclear components too,
but their identification can be more subtle than for AGNs.
Nuclear clusters have typical sizes of a few parsecs, 
therefore for the majority of our galaxies they are unresolved in \emph{Spitzer}/IRAC $3.6~\rm \mu m$ observations.
If an identification from high-resolution observations was available from the literature, we relied on that, 
otherwise we concluded that a galaxy was nucleated from an excess of nuclear light in the residuals of the 
fit\footnote{This conclusion was drawn after going through the following steps. 
First we identified all the sub-components of a galaxy 
(assuming that the galaxy was not nucleated), built a model accordingly and fit it to the data.
If the residuals of the fit showed a nuclear light excess, 
we repeated the fit by excluding the data points within the nuclear region.
Only after checking that the outcome of the last fit was consistent with the previous one, 
we inferred the presence of a stellar nuclear component, and accounted for it in the final galaxy model.}.
Unresolved nuclear components were fit with PSF-like profiles,
whereas resolved nuclear components were modeled with (PSF-convolved) narrow Gaussian functions. \\
Rings were identified from galaxy images and unsharp masks, and modeled with symmetric Gaussian ring profiles. \\
As an illustration, we consider the galaxy NGC 2974, 
a spiral galaxy which has been misclassified as an elliptical galaxy in the RC3 catalog \citep{RC3}. 
This galaxy hosts a Seyfert AGN \citep{veroncettyveron2006} and filamentary dust in its center \citep{tran2001}.
NGC 2974 is classified as fast rotator by the ATLAS$^{\rm 3D}$ survey, 
and indeed the velocity map obtained by the SLUGGS survey shows that the galaxy kinematics is rotation-dominated 
well beyond three effective radii ($R>150''$), 
as expected from a large-scale disk. 
%\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + Gaussian-AGN 
%($R_{\rm e} = 27''.2$, $n = 3.0$). 
From an inspection of the unsharp mask, we identified a ring at $R \sim 50''$, 
which might be a residual of two tightly wound spiral arms,
and an elongated bar-like component within $R \lesssim 30''$,
that produces a peak in the ellipticity and position angle profiles at $R \sim 20''$.
Our 1D galaxy decomposition for NGC 2974 (see Figure \ref{fig:n2974ex}) consists of a S\'ersic bulge, an exponential large-scale disk,
a Ferrer bar, a Gaussian nuclear component (AGN) and a Gaussian ring.
Although the ring is extremely faint, it is important to account for it in the galaxy decomposition. 
A model without the ring component results in a ``steeper'' exponential profile for the disk 
(i.e.~the exponential model has smaller scale length and more negative central surface brightness) 
and produces bad residual structures within $R \lesssim 40''$.
Our best-fit model returns a bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 8.3\rm~arcsec$, 
a bulge equivalent-axis S\'ersic index $n_{\rm sph}^{\rm eq} = 1.2$ and a $3.6~\rm \mu m$ bulge apparent magnitude $m_{\rm sph} = 8.65~\rm mag$.
\cite{sani2011} modeled NGC 2974 with a S\'ersic bulge and a Gaussian nuclear component (AGN), 
but did not account for the large-scale disk.
From their best-fit 2D model, they obtained a three times larger bulge major-axis effective radius ($R_{\rm e,sph}^{\rm maj} = 27.2\rm~arcsec$), 
a 2.5 times larger bulge S\'ersic index ($n_{\rm sph} = 3$),
and a significantly brighter $3.6~\rm \mu m$ bulge apparent magnitude ($m_{\rm sph} = 7.28~\rm mag$).

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
%\caption{Best-fit model and isophotal parameters for the galaxy NGC 3377. 
%The left panels refer to the major-axis $R_{\rm maj}$, 
%whereas the right panels refer to the equivalent-axis $R_{\rm eq}$.
%The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
%The black points are the observed data.  
%The color lines represent the individual (PSF-convolved) model components:
%red=S\'ersic (bulge), blue=exponential (disk). 
%The best-fit parameters for the S\'ersic profile are included.
%The total (PSF-convolved) model is shown with a black dashed line, 
%but it is hard to distinguish because it almost perfectly matches the data.
%The horizontal grey dashed line indicates the $3~RMS_{\rm sky}$ level.
%$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
%$\Delta \mu$ are the residuals from the fit.
%The six panels below show the ellipticity ($\epsilon$), position angle ($PA$) and $B4$ radial profiles.
%}
%\label{fig:n3377ex}
%\end{center}
%\end{figure*}

\begin{figure*}[h]
\begin{center}
\includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
\caption{Best-fit model and isophotal parameters for the galaxy NGC 2974. 
The left panels refer to the major-axis $R_{\rm maj}$, 
whereas the right panels refer to the equivalent-axis $R_{\rm eq}$.
The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
The black points are the observed data.  
The color lines represent the individual (PSF-convolved) model components:
red=S\'ersic (bulge), blue=exponential (disk), green=Gaussian (AGN), cyan=Ferrer (bar), gray=Gaussian ring (ring). 
The best-fit parameters for the S\'ersic profile are included.
The total (PSF-convolved) model is shown with a black dashed line, 
but it is hard to distinguish because it almost perfectly matches the data.
The horizontal grey dashed line indicates the $3~RMS_{\rm sky}$ level.
$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
$\Delta \mu$ are the residuals from the fit.
The six panels below show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles.}
\label{fig:n2974ex}
\end{center}
\end{figure*}

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
%\caption{Best-fit model and isophotal parameters for the galaxy M59. 
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:m59ex}
%\end{center}
%\end{figure*}
%
%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
%\caption{Best-fit model and isophotal parameters for the galaxy NGC 1332.
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:n1332ex}
%\end{center}
%\end{figure*}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{images/mbhmagk_n1332.pdf}
%\caption{The location of the S\'ersic galaxy NGC 1332 in the black hole mass versus $K$-band spheroid absolute magnitude diagram,
%according to our galaxy decomposition. 
%The red and blue solid lines show the scaling relations for core-S\'ersic and S\'ersic galaxies, respectively, 
%reported by \citet{grahamscott2013}, 
%while the shaded areas mark the $1\sigma$ errors.}
%\label{fig:n1332pl}
%\end{center}
%\end{figure}

\subsection{2D fits}
\label{sec:2d}
Two-dimensional decompositions were carried out using the software \textsc{Imfit} \citep{imfit}.
For each galaxy, we built a 2D model that was consistent with the corresponding 1D model in terms of number and type of components. 
Because the Ferrer profile is not made available in \textsc{Imfit},
bars were fit with a 2D Gaussian function. \\
The 2D decomposition of NGC 2974 is presented in Figure \ref{fig:n29742d}. 
The galaxy was modeled with a S\'ersic bulge, an exponential disk and a Gaussian bar.
The nuclear component was masked and the ring was not 
modeled\footnote{We built the 2D model first including and then omitting a gaussian ring component, 
but both models converged to the same solution, i.e.~the fit ``ignored'' the presence of the faint ring. 
This did not happen in the 1D decomposition because of the different weighting scheme used by the fitting routines.}. 
Our 2D best-fit model returns a bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 10.5~\rm arcsec$, 
a bulge S\'ersic index $n_{\rm sph} = 1.3$ and a $3.6~\rm \mu m$ bulge apparent magnitude $m_{\rm sph} = 8.39~\rm mag$, 
in fairly good agreement with our 1D decomposition.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/n2974_imgmsk.pdf}
\includegraphics[width=\columnwidth]{images/n2974_model.pdf}
\includegraphics[width=\columnwidth]{images/n2974_resid.pdf}
\caption{The image of the galaxy NGC 2974 with its mask (top panel), the best-fit 2D model (middle panel), 
and the residual image after the subtraction of the 2D model (bottom panel).
The ring has not been modeled, and therefore appears in the residual image.}
\label{fig:n29742d}
\end{center}
\end{figure}

\section{Results}
\label{sec:res}
For each galaxy, after we identified its various components and built a model accordingly, 
we simultaneously performed a set of four 1D fits.
All four fits use a Moffat-convolved model.
Two fits use the major-axis surface brightness profile and the remaining two use the equivalent-axis surface brightness profile. 
For each of these pairs, we use a logarithmically sampled surface brightness profile 
and a linearly sampled surface brightness profile. 
Because our fitting routine does not employ any error weighting scheme on the data points that constitute the surface brightness profile, 
a fit to a logarithmically sampled profile puts more weight on the inner region of the galaxy 
and poorly constrains the outskirts.
On the other hand, a fit to a linearly sampled surface brightness profile equally treats inner and outer regions. 
We found that the fits are, in general, more sensitive to the choice of the initial parameters 
when using logarithmically sampled profiles than linearly sampled profiles. 
In addition, a visual examination of the residuals demonstrated that the goodness of the fit within one galaxy effective radius 
is superior when tighter constraints are put on the galaxy outskirts.
In other words, the better quality of the residuals led us to prefer fits that use linearly sampled surface brightness profiles. \\
Among the initial sample of 75, we did not attempt to model 3 galaxies: M32, NGC 4486A and the Circinus Galaxy. 
The first two... {\bf AL: can you write a short sentence about these 2 galaxies, that have uncertain morphology,
because they have been stripped, blah blah, maybe put one reference? please and thank you.}
The Circinus Galaxy lies at only 4 degrees from the Galactic Plane, 
therefore its image mosaic is contaminated by a large number of foreground stars.
Of the remaining 72 galaxies, 
we obtained satisfactory 1D decompositions for 66, 
whereas the models of 6 galaxies were judged not reliable and were thus excluded. 
We also performed 2D decompositions for 31 galaxies. \\
A galaxy-by-galaxy comparison between our best-fit models and those from the previous literature 
helped identify the optimal decompositions and past problems. 
We compared our best-fit models with those of \cite{grahamdriver2007}, \cite{sani2011}, \cite{beifiori2012}, 
\cite{vika2012}, \cite{lasker2014data}. 
These five studies all investigated black hole mass scaling relations.
We also considered the best-fit models of \cite{laurikainen2010} and \cite{rusli2013} because,   
although they did not specifically deal with black hole - galaxy scaling relations, 
their galaxy samples significantly overlap with ours. \\
%In Section \ref{sec:indgal} we discuss individual cases, explaining the discrepancies between different decompositions. \\
Table \ref{tab:fitres} lists the results from the 1D and 2D fits.

\input{table_fitresults.tex}

\subsection{1D versus 2D decompositions}
%In Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}, we compare the bulge best-fit parameters obtained 
%from the 1D decompositions with those obtained from the 2D decompositions.
How do 1D and 2D decompositions compare with each other? 
Although an exhaustive analysis is beyond the scope of the present work, 
we believe that some of the readers might be interested in our practical knowledge, 
having dealt with 1D and 2D techniques of galaxy modeling at the same time. \\
We summarize our experience in the following points:
\begin{itemize}
\item A visual inspection of galaxy images and their unsharp masks is often not sufficient to accurately identify all galaxy components. 
Embedded disks or weak bars can easily be missed, and (inclined) intermediate-scale disks can be confused with large-scale ones.
In this regards, the 1D isophotal analysis is extremely helpful. 
Local minima/maxima or abrupt changes in the ellipticity, position angle and fourth harmonic profiles contain precious information 
about the galaxy constituents.
\item The ellipticity and position angle of bulges can vary with radius.
The analytic functions used by 2D decomposition codes to fit galaxy components have fixed ellipticity and position angle, 
thus they cannot account for their radial gradients. 
This problem is overcome with 1D decomposition techniques.
\item The interpretation of the residuals is often crucial to identify the optimal decomposition for a galaxy. 
In our experience, we found that the reading of 1D residuals was easier than that of 2D residuals.
\end{itemize}
Although we attempted 2D modeling for all galaxies in our sample, 
nearly half of the 2D decompositions were not successful or did not converge.
For the 31 galaxies that had successful 1D and 2D decompositions, 
we compare their 1D and 2D best-fit parameters in Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}.
%The software \textsc{Imfit} returns major-axis measurements of effective radii, 
%which are plotted in Figure \ref{fig:re1d2d} versus the corresponding 1D major-axis measurements.
%2D measurements of S\'ersic indices can be approximated to 1D equivalent-axis measurements, 
%and are therefore compared to them in Figure \ref{fig:n1d2d}.
%Figure \ref{fig:mag1d2d} shows 2D versus 1D measurements of bulge magnitudes. 
The agreement between 1D and 2D effective radii and magnitudes is remarkable, 
whereas a larger amount of scatter in the S\'ersic indices plot might be caused by the fact that 
2D measurements do not exactly correspond to 1D equivalent-axis measurements. 
No systematic effects are observed in any of these three plots, 
which indicates that 1D and 2D techniques of galaxy modeling -- when performed on the same galaxy -- 
give consistent results. \\
In conclusion, since we found that the best-fit parameters do not depend on the decomposition method (1D or 2D) used, 
but we obtained more successful 1D decompositions than 2D, 
we will base our analysis only on the results from 1D fits.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_r_e.eps} 
\caption{2D versus 1D major-axis measurements of effective radii. 
The dashed line displays the 1:1 relation.}
\label{fig:re1d2d}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_n.eps} 
\caption{2D measurements of S\'ersic indices can be approximated to 1D equivalent-axis measurements, 
and are therefore compared to them in this plot. The dashed line displays the 1:1 relation.}
\label{fig:n1d2d}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_mag.eps} 
\caption{2D versus 1D measurements of $3.6~\rm \mu m$ bulge magnitudes. The dashed line displays the 1:1 relation.}
\label{fig:mag1d2d}
\end{center}
\end{figure}

\subsection{Parameter uncertainty}
\label{sec:err}
Estimating the uncertainties associated with the best-fit parameters of our 1D galaxy decompositions is not straightforward.
Monte Carlo simulations could be used for this purpose, 
but they would take into account only random errors and not unknown systematic ones.
Systematic errors include incorrect sky subtraction, 
inaccurate masking of contaminating sources, 
imprecise description of the PSF, 
erroneous choice of model components 
(for example, when failing to identify a galaxy sub-component and thus omitting it in the model, 
or when describing a galaxy sub-component with an inadequate function),
the radial extent of the surface brightness profile and its sampling.
%(if no weighting scheme is applied to the data points during the minimization routine, 
%then, for the same galaxy, the fit of a logarithmically sampled light profile will naturally put more weight on the inner part of the profile 
%than in the case of linear sampling).
When performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well resolved -- galaxies, 
errors are dominated by systematics rather than Poisson noise.
For this reason, we decided to estimate the uncertainties of the bulge best-fit parameters 
with a method that took into account systematic errors.

\subsubsection{Goodness of the bulge modeling}
To do this, we first had to evaluate the goodness of the modeling of the bulge component.
For each of our fits, we calculated the associated $RMS$ scatter\footnote{The $RMS$ scatter of a fit was computed as:
\begin{equation}
\Delta = \sqrt{\frac{\sum_{\rm i=0}^{N} (\mu_{\rm i}^{\rm observed} - \mu_{\rm i}^{\rm model})^2}{N_{\rm DOF}} } ,
\end{equation} 
where %$N$ is the number of data points used in the fit, 
$N_{\rm DOF}$ is the number of degrees-of-freedom, 
$\mu^{\rm observed}$ is the observed surface brightness 
and $\mu^{\rm model}$ is the model surface brightness.}.
Although useful to evaluate the overall quality of a galaxy decomposition, 
the $RMS$ scatter alone cannot be used to assess the goodness of the fit for the spheroidal component only, 
unless the galaxy is a pure spheroid and has consequently been modeled with a single S\'ersic profile.
To illustrate this point with an example, 
one can imagine a situation in which a galaxy is thought to be made of a small bulge and a much more extended disk.
This galaxy is decomposed with a S\'ersic + exponential model.
The exponential function provides an excellent description of the light profile of the disk, 
whereas the S\'ersic function does not do the same for the bulge.
The residuals of the fit will then be flat and close to zero at large radii, 
where the emission of the disk dominates over that of the bulge,
while they will display significant structures at small radii, 
in correspondence of the poorly fit spheroidal component.
In case of linear sampling, 
because the part of the surface brightness profile pertaining to the disk contains more data points 
than the part pertaining to the bulge, 
the global $RMS$ scatter will be relatively small, 
but it obviously will not reflect the accuracy of the fit to the spheroidal component only. \\
A simple but powerful way to get a feeling of how precisely the global model describes the spheroidal component 
is to look at the major- and equivalent-axis fits of each galaxy 
and visually inspect the structures of the residuals within $\sim 1 - 2$ bulge effective radii. 
We did this using a grade from 1 to 3, assigned according to the following criteria.
\begin{itemize}
\item [1)] A grade of 1 was given to the best fits, i.e.~fits that do not exhibit any of the problems listed below.
\item [2)] A grade of 2 was used in the following cases: 
the residuals in correspondence of the bulge component are not randomly distributed around zero, 
being symptomatic of a S\'ersic model having a curvature (regulated by the S\'ersic index $n$) 
that does not match the real ``shape'' of the bulge; 
when we identified, but were not able to accurately model a galaxy sub-component;
in the case of significant inconsistencies between the model and the observed galaxy properties 
(e.g.~an embedded disk modeled with an exponential function, 
whose scale length does not match the size of the disk as expected from the ellipticity profile or the velocity map);
when the S\'ersic profile used to describe the bulge component has a size -- as measured by the effective radius -- 
comparable to a few times the $FWHM$ of the PSF.
\item [3)] A grade of 3 was assigned to the poorer and more anomalous fits, 
or those affected by an obvious degeneracy between the bulge S\'ersic profile and the remaining model components 
(e.g.~when the bulge S\'ersic index varies for more than 50\% {\bf TBD: how often what?} among the four different realizations of the fit, 
or when the output of the fit strongly depends on the choice of the initial parameters).
\end{itemize}
As a result, we classified 27 galaxies (38\% of the 72 galaxies for which we attempted a 1D decomposition) with grade 1, 
29 galaxies (40\%) with grade 2 and 10 galaxies (14\%) with grade 3.
%The absolute values of the uncertainties of the S\'ersic parameters will be estimated in a forthcoming paper, 
%according to the grades assigned here to the fits.

\subsubsection{Uncertainties on $n_{\rm sph}$}
%\label{sec:sigman}
In Figure \ref{fig:compn}, for 58 galaxies, 
we compare the measurements of the bulge S\'ersic index obtained by different authors 
with those obtained by us. 
For each galaxy, we computed the average value $\langle \log(n_{\rm sph}) \rangle$ of all the available measurements, 
and we plot it against the scatter of the individual measurements around $\langle \log(n_{\rm sph}) \rangle$.
The measurements are deliberately heterogeneous, 
in the sense that they were obtained from 1D or 2D decompositions of data in different wavelengths, 
and they refer either to the major-axis or to the equivalent-axis.
In Figure \ref{fig:compn}, the black histogram shows the distribution of the scatter around $\langle \log(n_{\rm sph}) \rangle$ 
only for our measurements. 
38\% of this distribution lie within $-\sigma_1^- = -0.08~\rm dex$ and $+\sigma_1^+ = +0.06~\rm dex$, 
78\% lie within $-\sigma_2^- = -0.21~\rm dex$ and $+\sigma_2^+ = +0.17~\rm dex$,
and 92\% lie within $-\sigma_3^- = -0.25~\rm dex$ and $+\sigma_3^+ = +0.25~\rm dex$. 
We elect to use $\pm \sigma_1^\pm$, $\pm \sigma_2^\pm$ and $\pm \sigma_3^\pm$ as $1\sigma$ uncertainties 
for our measurements of $\log(n_{\rm sph})$ obtained from ``grade 1'', ``grade 2'' and ``grade 3'' fits, respectively. \\

\subsubsection{Uncertainties on $R_{\rm e,sph}$}
The uncertainties on the bulge effective radii were computed with the same method used for the S\'ersic indices. 
However, in Figure \ref{fig:compre} we include only major-axis measurements of $R_{\rm e,sph}$. 
The associated $1\sigma$ uncertainties for our measurements of $\log(R_{\rm e,sph})$ are 
$-\sigma_1^- = -0.11~\rm dex$ and $+\sigma_1^+ = +0.07~\rm dex$, 
$-\sigma_2^- = -0.30~\rm dex$ and $+\sigma_2^+ = +0.32~\rm dex$,
and $-\sigma_3^- = -0.39~\rm dex$ and $+\sigma_3^+ = +0.42~\rm dex$.

\subsubsection{Uncertainties on $m_{\rm sph}$}
To estimate the uncertainties on the bulge magnitudes, 
we compared (see Figure \ref{fig:compmag}) only measurements coming from $K$-band or $3.6~\rm \mu m$ observations.
$3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes by an additive factor of $+0.27\rm~mag$, 
which was estimated using the stellar population models of \cite{worthey1994},
assuming a 13 Gyr old single-burst stellar population with solar metallicity. 
The associated $1\sigma$ uncertainties for our measurements of $m_{\rm sph}$ are 
$-\sigma_1^- = -0.11~\rm mag$ and $+\sigma_1^+ = +0.18~\rm mag$, 
$-\sigma_2^- = -0.58~\rm mag$ and $+\sigma_2^+ = +0.66~\rm mag$,
and $-\sigma_3^- = -0.66~\rm mag$ and $+\sigma_3^+ = +0.88~\rm mag$. \\
{\bf NOTE: When converting from K-band to 3.6, 
Galactic absorption was not taken into account!!!!! But I have the feeling that it's not significant...}

\subsubsection{Uncertainties on $\mu_{\rm e,sph}$}
As for the bulge magnitudes, we estimated the uncertainties on the bulge effective surface brightnesses $\mu_{\rm e,sph}$ 
by comparing only $K$-band or $3.6~\rm \mu m$ measurements (see Figure \ref{fig:compmue}), 
and accounting for the corrective factor. 
Because not explicitly reported by their authors, literature effective surface brightnesses were calculated by us as:
\begin{multline}
\mu_{\rm e,sph} = m_{\rm sph} + 5\log \Bigl(R_{\rm e,sph}^{\rm maj}\sqrt{(b/a)_{\rm sph}} \Bigr) + \\
+ 2.5\log \Bigl[2\pi n_{\rm sph} e^{b_n} b_n^{-2n_{\rm sph}} \Gamma(2n_{\rm sph})\Bigr], 
\end{multline}
where $b_n$ and $\Gamma(2n_{\rm sph})$ are defined in Section \ref{sec:app1}, 
and $(b/a)_{\rm sph}$ is the bulge axis ratio.
While \cite{laurikainen2010} and \cite{sani2011} reported their estimates of $(b/a)_{\rm sph}$, 
\cite{vika2012} and \cite{lasker2014data} did not. 
For the last two studies, we used the values of $(b/a)_{\rm sph}$ reported by \cite{sani2011}.
The associated $1\sigma$ uncertainties for our measurements of $\mu_{\rm e,sph}$ are 
$-\sigma_1^- = -0.33~\rm mag$ and $+\sigma_1^+ = +0.57~\rm mag$, 
$-\sigma_2^- = -0.84~\rm mag$ and $+\sigma_2^+ = +1.59~\rm mag$,
and $-\sigma_3^- = -1.06~\rm mag$ and $+\sigma_3^+ = +1.74~\rm mag$.

\subsubsection{Uncertainties on $\mu_{\rm 0,sph}$}
From the values of $\mu_{\rm e,sph}$, we derived the central surface brightnesses $\mu_{\rm 0,sph}$ as
\begin{equation}
\mu_{\rm 0,sph} = \mu_{\rm e,sph} - \frac{2.5 b_n}{\ln(10)}.
\end{equation}
The associated $1\sigma$ uncertainties for our measurements of $\mu_{\rm 0,sph}$ are 
$-\sigma_1^- = -0.20~\rm mag$ and $+\sigma_1^+ = +0.64~\rm mag$, 
$-\sigma_2^- = -0.70~\rm mag$ and $+\sigma_2^+ = +1.24~\rm mag$,
and $-\sigma_3^- = -1.05~\rm mag$ and $+\sigma_3^+ = +1.57~\rm mag$.

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
\caption{The bottom panel shows 58 galaxies for which at least one measurement of the bulge S\'ersic index $n_{\rm sph}$ is available 
from the literature, in addition to that measured by us.
In ordinate, for each galaxy, we plot the average value $\langle \log(n_{\rm sph}) \rangle$ of (the logarithm of) the individual measurements. 
In abscissa we plot the difference between (the logarithm of) the individual measurements of a galaxy 
and the average value for that same galaxy.
Each data point corresponds to an individual measurement, 
which comes from one of the following studies. 
Red points are from \cite{grahamdriver2007}, 
blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
yellow points are from \cite{vika2012}, gray points are from \cite{beifiori2012},
white points are from \cite{rusli2013}, orange points are from \cite{lasker2014data},
and black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\log(n_{\rm sph}) - \langle \log(n_{\rm sph}) \rangle$ 
for all measurements, 
whereas the black histogram refers only to measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively.}
\label{fig:compn}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_r_e.eps} 
\caption{The bottom panel shows 52 galaxies for which at least one measurement 
of the major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
from the literature, in addition to that measured by us.
In ordinate, for each galaxy, we plot the average value $\langle \log(R_{\rm e}^{\rm maj}) \rangle$ 
of (the logarithm of) the individual measurements. 
In abscissa we plot the difference between (the logarithm of) the individual measurements of a galaxy 
and the average value for that same galaxy.
Each data point corresponds to an individual measurement, 
which comes from one of the following studies. 
Red points are from \cite{grahamdriver2007}, 
blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
yellow points are from \cite{vika2012}, gray points are from \cite{beifiori2012},
orange points are from \cite{lasker2014data},
and black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\log(R_{\rm e}^{\rm maj}) - \langle \log(R_{\rm e}^{\rm maj}) \rangle$ 
for all measurements, 
whereas the black histogram refers only to measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively.}
\label{fig:compre}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mag_sph.eps} 
\caption{The bottom panel shows 51 galaxies for which at least one measurement 
of the bulge apparent magnitude $m_{\rm sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
from the literature, in addition to that measured by us. 
$3.6~\rm \mu m$ magnitudes were converted to $K$-band magnitudes.
In ordinate, for each galaxy, we plot the average value $\langle m_{\rm sph} \rangle$ 
of the individual measurements. 
In abscissa we plot the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
Each data point corresponds to an individual measurement, 
which comes from one of the following studies. 
Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
yellow points are from \cite{vika2012}, 
orange points are from \cite{lasker2014data},
and black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the equivalent-axis).
In the top panel, the white histogram shows the distribution of $m_{\rm sph} - \langle m_{\rm sph} \rangle$ 
for all measurements, 
whereas the black histogram refers only to measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively.}
\label{fig:compmag}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_e.eps} 
\caption{The bottom panel shows 49 galaxies for which at least one measurement 
of the bulge effective surface brightness $\mu_{\rm e,sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
from the literature, in addition to that measured by us. 
$K$-band magnitudes were converted to $3.6~\rm \mu m$ magnitudes.
In ordinate, for each galaxy, we plot the average value $\langle \mu_{\rm e,sph} \rangle$ 
of the individual measurements. 
In abscissa we plot the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
Each data point corresponds to an individual measurement, 
which comes from one of the following studies. 
Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
yellow points are from \cite{vika2012}, 
orange points are from \cite{lasker2014data},
and black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\mu_{\rm e,sph} - \langle \mu_{\rm e,sph} \rangle$ 
for all measurements, 
whereas the black histogram refers only to measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively.}
\label{fig:compmue}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_0.eps} 
\caption{The bottom panel shows 49 galaxies for which at least one measurement 
of the bulge central surface brightness $\mu_{\rm 0,sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
from the literature, in addition to that measured by us. 
$K$-band magnitudes were converted to $3.6~\rm \mu m$ magnitudes.
In ordinate, for each galaxy, we plot the average value $\langle \mu_{\rm 0,sph} \rangle$ 
of the individual measurements. 
In abscissa we plot the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
Each data point corresponds to an individual measurement, 
which comes from one of the following studies. 
Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
yellow points are from \cite{vika2012}, 
orange points are from \cite{lasker2014data},
and black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\mu_{\rm 0,sph} - \langle \mu_{\rm 0,sph} \rangle$ 
for all measurements, 
whereas the black histogram refers only to measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively.}
\label{fig:compmu0}
\end{center}
\end{figure}

\section{Conclusions}
\label{sec:concl}
The widespread presence of embedded components -- such as intermediate-scale disks -- in massive early-type galaxies 
makes galaxy decomposition an essential tool to properly investigate the scaling relations between black hole masses 
and host bulge properties. \\
The bulge best-fit parameters are model-dependent. 
Past studies often used different models for the same galaxy, and obtained significantly discrepant results,  
which led them to draw contrasting conclusions about the black hole-bulge correlations.
These inconsistencies motivated our effort to secure and refine the measure of bulge properties in a sample of 75 galaxies 
with a dynamical estimate of the black hole mass. 
Using $3.6~\rm \mu m$ \emph{Spitzer} satellite imagery, 
we performed state-of-the-art galaxy decompositions. 
We compared our best-fit models with those from the past literature, 
and explained discrepancies when present. 
Table \ref{tab:lit} summarizes the main characteristics of the five past studies that, since 2007, attempted galaxy decomposition 
to derive black hole-bulge scaling relations, 
and highlights why our endeavor represents a substantial improvement over the past literature.
Our sample of galaxies is the largest ever used. 
The $3.6~\rm \mu m$ band is an excellent tracer for the stellar mass, superior to optical bands or the $K$-band. 
\cite{lasker2014data} and this work identified and modeled more galaxy components than any other study, 
and therefore obtained more accurate decompositions,
but we are the first that did it with the assistance of kinematical information.

\begin{table*}%[ht] 
\begin{center}  				      
\caption{{\bf Summary of previous investigations of black hole mass scaling relations.} 
GD07 = \cite{grahamdriver2007}, 
S+11 = \cite{sani2011}, V+12 \cite{vika2012}, B+12 = \cite{beifiori2012}, L+14 = \cite{lasker2014data}.}
\begin{tabular}{lllllll}
\hline
              & {\bf GD07}  & {\bf S+11}   & {\bf V+12} & {\bf B+12}   & {\bf L+14} & {\bf This work}	      \\ %%[0.5ex] 
\hline
{\bf Galaxies with successful fit} & 27		     & 57	       & 25      & 19          & 35      & 66               \\
{\bf Wavelength}        	   & $R$-band	     & $3.6~\rm \mu m$ & $K$-band& $i$-band    & $K$-band& $3.6~\rm \mu m$  \\
{\bf Decomposition}     	   & 1D 	     & 2D	       & 2D	 & 2D	       & 2D	 & 1D \& 2D	    \\
{\bf Nuclear components}       	   & masked	     & modeled         & modeled & not treated & modeled & modeled/masked   \\
{\bf Partially depleted cores} 	   & masked	     & masked	       & masked  & not treated & masked  & masked	    \\ 
{\bf Bars}	        	   & excluded	     & modeled         & modeled & excluded    & modeled & modeled	    \\ 
{\bf Other components}  	   & no 	  & no  	       & no	 & no	       & yes	 & yes  	    \\ 
{\bf Kinematics}        	   & no 	     & no	       & no	 & no	       & no	 & yes  	    \\ %%[0.5ex] 
\hline 
\end{tabular}
\label{tab:lit} 
\end{center}	
\end{table*}

Our principal conclusions are summarized in the following points.
\begin{itemize}
\item One-dimensional and two-dimensional techniques of galaxy decomposition return the same results when applied to the same galaxy.
However, in our practical experience, two-dimensional decompositions {\bf HOW DO YOU WRITE THIS IN ENGLISH?? fail twice as much as one-dimensional ones}, 
either because the fit does not converge or because the result is unphysical. 
A strong limitation of two-dimensional codes is their inability to accommodate the radial gradients of ellipticity and position angle 
often observed in galaxy bulges.
\item We found the interpretation of one-dimensional residuals easier than that of two-dimensional residual images. 
A correct interpretation of the residuals is fundamental to determine the optimal model for a galaxy.
\item A one-dimensional isophotal analysis was extremely helpful and sometimes even necessary to accurately identify galaxy components.
\item Given the level of detail to which each galaxy decomposition was performed, 
we believe that our analysis cannot be reproduced by any current automatic routine. 
\item The uncertainties associated with the bulge best-fit parameters are dominated by systematic errors (e.g.~incorrect sky subtraction, 
inaccurate masking of contaminating sources, erroneous choice of model components), and only marginally affected by random errors. 
For this reason, we developed a method to estimate the uncertainties on the best-fit parameters that takes into account systematic errors.
\end{itemize}

We will use the results from our one-dimensional galaxy decompositions to obtain improved black hole mass scaling relations. 
We will also derive and explore some unpublished correlations. 
These results will be presented in a series of forthcoming papers.

%\clearpage

% \onecolumngrid
% \subsection{individual galaxies}
% \label{sec:indgal}
%
% individual galaxies \\
%
% \clearpage\newpage\noindent
% {\bf IC 1459 \\}
%
% IC 1459 is an elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
% nuclear dust and an indication of a central stellar disk \citep{forbes1994ic1459}.
% The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
% This galaxy has also a partially depleted core ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
%
% %\cite{sani2011} fit this galaxy with a S\'ersic-bulge + Gaussian-AGN model ($R_{\rm e} = 61''.1$, $n=6$).
% %\cite{lasker2014data} used a S\'ersic-bulge + mask-core model ($R_{\rm e} = 62''.4$, $n=8.25$).
% %\cite{rusli2013} adopted a core-S\'ersic model ($R_{\rm e} = 45''.43$, $n=7.6$).
%
% \emph{1D fit -- }
% Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
% We masked the innermost $6''.1$ affected by the partially depleted core 
% and we fit this galaxy with a S\'ersic profile. 
%
% \emph{Other models -- } 
%
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for IC 1459.}
% \end{center}
% \end{figure}
%
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for IC 1459.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
% T.W. 1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
% T.W. 2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
% \hline
% S+11         & S-bul + G-n   & $61.1$  &  $6.0$ \\
% R+13         & core-S\'ersic & $45.4$  &  $7.6$ \\
% L+14         & S-bul + m-c   & $62.4$  &  $8.3$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:ic1459}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf IC 2560 \\}
%
% IC 2560 is a barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
% and dust within the central $2''.5$ \citep{martini2003}.
%
% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model ($R_{\rm e} = 27''.5$, $n=2$).
%
% \emph{1D fit -- }
% A visual inspection of the image of IC 2560 reveals a boxy bulge and
% a large scale bar that extends out to $R \lesssim 43''$.
% The disk appears to be slightly lopsided along the direction of the bar,
% due to two non-symmetric ansae, but it becomes symmetric beyond $R \gtrsim 60''$. 
% This is why the surface brightness profile deviates from a perfect exponential
% in the radial range $42'' \lesssim R \lesssim 60''$, which has been excluded from the fit.
% Motivated by the presence of a strong optical AGN and dust in the nucleus, 
% we accounted for an excess of non-stellar light by adding a central Gaussian component to the model.
% %Our final 1D model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar + Gaussian-AGN.
% %Similarly, our 2D model consists of a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN.\\
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for IC 2560.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for IC 2560.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $6.1$  &  $0.8$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.5$  &  $0.6$ \\
% %T.W. 2D	&  &  & \\
% \hline
% S+11         & S-bul + e-d + G-n & $27.5$  &  $2.0$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:ic2560}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf IC 4296 \\}
%
% IC 4296 is an elliptical galaxy. % with a radio jet \citep{liuxie1992}.
% Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
%
% %\cite{sani2011} fit this galaxy with a S\'ersic-bulge + Gaussian-AGN model ($R_{\rm e} = 33''.6$, $n = 4$).
% %\cite{lasker2014data} employed a S\'ersic-bulge + mask-core model ($R_{\rm e} = 97''.8$, $n=8.2$).
%
% \emph{1D fit -- }
% After masking the innermost $6''.1$, % affected by the (unresolved) partially depleted core,
% we found that a single S\'ersic profile provides a fairly good description of this galaxy.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for IC 4296.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for IC 4296.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
% T.W. 1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
% T.W. 2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
% \hline
% S+11         & S-bul + G-n & $33.6$  &  $4.0$ \\
% L+14         & S-bul + m-c & $97.8$  &  $8.2$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:ic4296}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M31 -- NGC 0224 \\}
%
% M31, the Andromeda galaxy, is a spiral galaxy. 
% Although for decades this galaxy had been classified as an unbarred spiral,
% recent works have unraveled the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}.
% M31 also features a pseudo-ring-like structure at $R \sim 50'$ \citep{athanassoulabeaton2006m31}. 
%
%
% \emph{1D fit -- }
% We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
% The region $2000'' \lesssim R \lesssim 3400''$, where the pseudo-ring is observed, was excluded from the fit.
% A S\'ersic + exponential fit is clearly not adequate to describe the light profile of M31.
% The residuals of such fit display a structure in correspondence of the bar ($R \lesssim 1500''$).
% The bar was thus fit with a Ferrer function.
%
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M31.}
% \end{center}
% \end{figure}
%
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M31.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar & $418.6$  &  $2.2$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar & $173.6$  &  $1.3$ \\
% %T.W. 2D	& $$  & $$  &  $$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m31}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M49 -- NGC 4472 \\}
%
% M49, the brightest member of the Virgo cluster, is a giant elliptical galaxy 
% with a partially depleted core ($R_{\rm break} = 1''.8$, \citealt{rusli2013}).
% %M49 is a slow-rotator \citep{atlas3dIII-MNRAS}.
%
% %\cite{ferrarese2006acsvcs} modeled this galaxy with a core-S\'ersic profile ($R_{\rm e} = 208''$, $n = 5.5$).
% %Also \cite{rusli2013} used a core-S\'ersic model ($R_{\rm e} = 199''$, $n = 5.6$).
%
% \emph{1D fit -- }
% We excluded from the fit the innermost $12''$.
% We found no evidence for embedded components and
% we fit M49 with a single S\'ersic profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M49.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M49.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $190.2$  &  $6.6$ \\
% T.W. 1D eq.  & S-bul + m-c & $135.3$  &  $5.4$ \\
% T.W. 2D      & S-bul + m-c & $151.9$  &  $5.5$ \\
% \hline
% R+13         & core-S\'ersic & $199.0$  &  $5.6$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m49}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M59 -- NGC 4621 \\}
%
% M59 is an elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
% and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}.
% %M59 is a fast-rotator \citep{atlas3dIII-MNRAS}.
%
% %\cite{sani2011} modeled this galaxy with a single S\'ersic-bulge model ($R_{\rm e} = 70''.1$, $n = 5$).
% %\cite{vika2012} used a S\'ersic-bulge + mask-core model ($R_{\rm e} = 54''.7$, $n = 5.7$). 
%
% \emph{1D fit -- }
% The intermediate-scale embedded disk is clearly visible in our unsharp mask image, and 
% the velocity field confirms the presence of a rapidly rotating component. 
% Although faint, it is important to account for the presence of this disk.
% A single S\'ersic fit produces bad residuals.
% The fit notably improves if an embedded exponential disk function 
% is added to the final model.
% We chose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M59.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M59.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c + e-id & $48.0$  &  $5.5$ \\
% T.W. 1D eq.  & S-bul + m-c + e-id & $90.9$  &  $8.8$ \\
% %T.W. 2D	&    & $$  &  $$ \\
% \hline 
% S+11         & S-bul       & $70.1$  &  $5.0$ \\
% V+12         & S-bul + m-c & $54.7$  &  $5.7$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m59}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%
% {\bf M60 -- NGC 4649 \\}
%
% exclude it, doesn't make sense
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M64 -- NGC 4826 \\}
%
% M64 is a dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. 
%
% %B12 model the galaxy image with a 2D S\'ersic function + exponential disk ($n = 1.49$). \\
% \emph{1D fit -- }
% A large-scale bar ($R \lesssim 50''$) can be identified in the unsharp mask 
% and produces corresponding peaks in the ellipticity, PA and B4 profiles.
% We modeled it with a Ferrer function.
% Additional peaks in the ellipticity, PA and B4 profiles at $R \sim 15''$ 
% signal the presence of an embedded disky component, that we described with a low-$n$
% S\'ersic function.
% Although the galaxy is dusty and hosts an AGN, we do not observe any nuclear excess of light 
% in the fit residuals and therefore we consider unnecessary to add a nuclear component to our model.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m64_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M64.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M64.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + S-id  & $3.8$  &  $0.8$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + S-id  & $4.3$  &  $1.4$ \\
% %T.W. 2D	&   & $$  & $$  &  $$ \\
% \hline
% B+12      & S-bul + e-d  & $5.0$  &  $1.5$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m64}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M81 -- NGC 3031 \\}
%
% M81 is an early-type spiral galaxy with a LINER AGN.
% This galaxy features two bars \citep{elmegreen1995m81,gutierrez2011,erwindebattista2013}.
%
% \emph{1D fit -- }
% We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M81.
% The bars are not particularly evident in the galaxy image or in the unsharp mask.
% Any attempt to account for the bars in the fit was unsuccessful. 
% For this reason, we used a simple S\'ersic + exponential model to describe M81.
%
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m81_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M81.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M81.}
% \begin{center}
% \begin{tabular}{llccc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d  & $31.0$  &  $1.7$ \\
% T.W. 1D eq.  & S-bul + e-d  & $33.2$  &  $2.1$ \\
% %T.W. 2D	&   & $$  & $$  &  $$ \\
% \hline
% GD07      & S-bul + e-d	 & $68.1$   &  $3.3$ \\
% S+11      & S-bul + e-d + G-n  & $127.3$  &  $3.0$ \\
% B+12      & S-bul + e-d	 & $50.0$   &  $2.6$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m81}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M84 -- NGC 4374 \\}
%
% M84 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.5$, \citealt{rusli2013}). 
%
% %GD07 model the galaxy light profile with a S\'ersic function ($n = 5.6$).
% %V12 model the galaxy image with a 2D S\'ersic function + core-mask ($n = 3.5$).
% %S11 model the galaxy image with a 2D S\'ersic function + Gaussian ($n = 7.0$).
% %B12 model the galaxy image with a 2D S\'ersic function ($n = 4.10$). \\
%
% \emph{1D fit -- }
% The unsharp mask reveals a faint inner component ($R \lesssim 12''$). 
% Here we excluded the data within $R < 13''.8$ and modeled the galaxy with a S\'ersic profile.
%
% %After masking the innermost $13''.8$, we modeled the galaxy with a S\'ersic profile. 
% %However, we notice that 
% %the 1D and 2D fits are not much affected by the presence of the embedded component.
% %In fact, reducing the size of the central mask to uncover the inner component 
% %(but still masking the region affected by the partially depleted core) does not
% %alter significantly the bulge parameters. 
% %The structures observed in the residuals are caused by the negative ellipticity gradient 
% %(from $\epsilon \sim 0.17$ to $\epsilon \sim 0.03$, over a radial range $10'' < R < 130''$),
% %which cannot be reproduced by the 2D model because of its fixed ellipticity ($\epsilon = 0.10$). 
%   
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m84_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M84.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M84.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c   & $101.6$  &  $7.8$ \\
% T.W. 1D eq.  & S-bul + m-c   & $129.8$  &  $7.9$ \\
% T.W. 2D      & S-bul + m-c   & $181.8$  &  $8.4$ \\
% \hline
% GD07         & S-bul         & $75.1$   &  $5.6$ \\
% S+11         & S-bul + G-n   & $105.9$  &  $7.0$ \\
% V+12         & S-bul + m-c   & $28.7$   &  $3.5$ \\
% B+12         & S-bul         & $63.6$   &  $4.1$ \\
% R+13         & core-S\'ersic & $126.2$  &  $7.1$ \\
% L+14         & S-bul + m-c   & $139.0$  &  $8.3$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m84}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M87 -- NGC 4486 \\}
%
% M87 is a giant elliptical galaxy belonging to the Virgo cluster.
% This galaxy has a large partially depleted core ($R_{\rm break} = 7''.2$, \citealt{ferrarese2006acsvcs}).
%
% \emph{1D fit -- }
% The morphology of M87 is similar to that of M49.
% The innermost $18''.5$ were excluded from the fit.
% We used a single S\'ersic model to characterize M87.
%
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m87_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M87.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M87.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c  & $203.9$  &  $10.0$ \\
% T.W. 1D eq.  & S-bul + m-c  & $87.1$   &  $5.9$ \\
% T.W. 2D      & S-bul + m-c  & $88.3$   &  $4.3$ \\
% \hline
% GD07      & S-bul	    & $-$     &  $6.9$ \\
% S+11      & S-bul + G-n   & $99.5$  &  $4.0$ \\
% V+12      & S-bul + m-c   & $34.6$  &  $2.4$ \\
% R+13      & core-S\'ersic & $180.9$ &  $8.9$ \\
% L+14      & S-bul + m-c   & $122.0$ &  $5.6$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m87}
% \end{table}
%
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%
% {\bf M89 -- NGC 4552 \\}
%
% m87 has ellipticity still increasing, the halo is not prevailing
% m89 instead has a plateau in the ell prof, bcz the halo is predominant
% we need to fit the halo
%
% BTW, if we wanna test the two phase formation scenario, we should care more about the halos...
% at which effective radius does the halo begin?
% what is the ratio of the mass in the galaxy or in the halo?
%
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m89_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M89.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M89.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-halo  & $29.0$  &  $4.6$ \\
% T.W. 1D eq.  & S-bul + e-halo  & $28.2$  &  $5.1$ \\
% %T.W. 2D	&   & $$  & $$  &  $$ \\
% \hline
% &   & $$  &  $$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m89}
% \end{table}
%
%
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M94 -- NGC 4736 \\}
%
% M94 is an almost face-on spiral galaxy, with a Seyfert AGN \citep{veroncettyveron2006} and 
% circumnuclear dust \citep{elmegreen2002m94,peeplesmartini2006m94}.
% This galaxy has a ring-like structure at $R \sim 50''$ \citep{munoztunon1989m94}.
%
% %\cite{fisherdrory2010} fit M94 with a S\'ersic-bulge + exponential-disk model ($R_{\rm e} = 7''.7$, $n = 1.3$). 
%
% \emph{1D fit -- }
% The ellipticity and B4 profiles display a local maximum at $R \sim 10''$, 
% indicating the presence of a disky component embedded in the bulge,
% as already noted by \cite{fisherdrory2010}.
% We modeled this component with a Ferrer function.
% We excluded the data within the innermost $6''.7$, due to the AGN contribution.
% Any attempt to model the ring was unsuccessful, resulting in a degenerate model.
% Therefore we preferred to exclude also the data in the range $20'' \lesssim R \lesssim 80''$, 
% where the ring light dominates over the rest of the galaxy.
% %Our final model for M94 consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m94_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M94.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M94.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar & $11.4$  &  $0.9$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar & $8.4$   &  $1.1$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m94}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M96 -- NGC 3368 \\}
%
% M96 is a spiral galaxy with a large scale bar and no AGN activity \citep{martini2003,nowak2010n3368n3489}. 
%
% %\cite{sani2011} fit this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-bar model 
% %($R_{\rm e} = 45''.6$, $n = 1.0$). 
% \cite{nowak2010n3368n3489} argued for the presence of a large pseudo-bulge and a tiny classical bulge 
% ($R_{\rm e} = 1''.6$, $n = 2.3$). 
%
% \emph{1D fit -- }
% M96 has a complex morphology. 
% The large-scale disk does not exhibit a perfect exponential profile, 
% mainly because of wound spiral arms resembling a ring ($R \sim 185''$),
% which however are too faint and irregular to be described with a Gaussian ring model. 
% The large scale bar extends out to $R \lesssim 80''$ and has been modeled with a Ferrer function.
% A peak at $R \sim 25''$ in the ellipticity profile unravels an inner component embedded in the bulge.
% The isophotal twist observed within $R \lesssim 25''$ suggests that the inner component can be identified 
% with a second bar, as already noted by \cite{erwin2004}.
% We accounted for this embedded component with a low-$n$ S\'ersic profile.
% We built our final model with a S\'ersic-bulge + exponential-disk + Ferrer-bar + S\'ersic-bar.
% The residuals do not display any significant light excess in the nuclear region, 
% in agreement with the lack of AGN activity.
%
% \cite{nowak2010n3368n3489} came to their conclusion by modeling only the innermost $8''.5$ of the 
% light profile of M96 with a S\'ersic-classical-bulge and an exponential-pseudo-bulge, 
% but without subtracting the contribution of the large-scale disk and the large-scale bar.
% In addition, they acknowledged the presence of a secondary inner bar, but did not include it in their fit.
%
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m96_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M96.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M96.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + S-bar  & $7.5$  &  $1.5$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + S-bar  & $5.3$  &  $1.3$ \\
% T.W. 2D      & S-bul + e-d + 2 G-bars       & $8.3$  &  $2.0$ \\
% \hline
% S+11         & S-bul + e-d + G-bar  & $45.6$  &  $1.0$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m96}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%
% {\bf M104 -- NGC 4594 \\} 
%
% OK
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M104.}
% \end{center}
% \end{figure}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M105 -- NGC 3379 \\}
%
% M105 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.1$, \citealt{rusli2013}).
%
% \emph{1D fit -- }
% M105 exhibits a mild isophotal twist and an abrupt change of ellipticity at $R \sim 30''$.
% The velocity map shows rotation at least within $R \lesssim 30''$, 
% but no embedded disk can be recognized in the unsharp mask 
% and the ellipticity profile is quite unusual for a spheroidal system with an inner disk.
% After masking the innermost $6''.1$, we noticed that a single S\'ersic model 
% does not provide a good description of the galaxy light profile.
% However, the addition of a second function (of any analytical form) to the model did not improve the fit.
% We thus employed a single S\'ersic profile for M105.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m105_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M105.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M105.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $57.2$  &  $5.2$ \\
% T.W. 1D eq.  & S-bul + m-c & $50.9$  &  $5.3$ \\
% T.W. 2D      & S-bul + m-c & $73.6$  &  $7.0$ \\
% \hline
% GD07         & S-bul & $58.3$  &  $4.3$ \\
% S+11         & S-bul & $46.0$  &  $5.0$ \\
% R+13         & core-S\'ersic & $55.1$  &  $5.8$ \\
% L+14         & S-bul + m-c & $96.3$  &  $9.3$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m105}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M106 -- NGC 4258 \\} 
%
% M106 is a barred spiral galaxy, harbouring a Seyfert AGN \citep{veroncettyveron2006} 
% with %a radio jet \citep{liuzhang2002} and 
% circumnuclear dust \citep{martini2003}. 
%
% %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 14''.9$, $n = 2.0$). 
% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model 
% %($R_{\rm e} = 111''.7$, $n = 2.0$). 
% %\cite{vika2012} proposed two different fits: the first with a S\'ersic-bulge + exponential-disk + PSF-nucleus
% %($R_{\rm e} = 17''.0$, $n = 3.5$), 
% %and the second with a S\'ersic-bulge + exponential-disk + PSF-nucleus + S\'ersic-bar
% %($R_{\rm e} = 6''.3$, $n = 2.2$).
%
% \emph{1D fit -- }
% We excluded from the fit the innermost $6''.1$ because affected by the AGN emission.
% The boxy bar, responsible for the minimum in the B4 profile at $R \sim 65''$, 
% is faint compared to the large-scale disk and in the light profile is only detectable as a slight swelling
% within $65'' \lesssim R \lesssim 110''$.
% This region has been excluded from the fit.
% A peak in the ellipticity profile at $R \sim 10''$ suggests that a disk-like component might be 
% embedded in the bulge.
% Since the galaxy is barred, this component could be identified with a peanut bulge. 
% However, we found that adding an extra component to the model introduces degeneracies, 
% thus we preferred not to do so.
% While the fit along the major-axis is satisfactory, 
% the equivalent-axis residuals present a sneaky structure within $R \lesssim 20''$,
% due to the unsubtracted embedded component.
% %Our final model consists of a S\'ersic-bulge + exponential-disk.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m106_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M106.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M106.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d & $15.3$  &  $2.0$ \\
% T.W. 1D eq.  & S-bul + e-d & $8.3$   &  $1.2$ \\
% %T.W. 2D	& & $$  & $$  &  $$ \\
% \hline
% GD07     & S-bul + e-d		 & $14.9$   &  $2.0$ \\
% S+11     & S-bul + e-d + G-n  	 & $111.7$  &  $2.0$ \\
% V+12 (1) & S-bul + e-d + PSF-n	 & $17.0$   &  $3.5$ \\
% V+12 (2) & S-bul + e-d + PSF-n + S-bar & $6.3$    &  $2.2$ \\
% L+14     & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $6.3$	 &  $3.3$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m106}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 0524 \\} 
%
% NGC 0524 is an unbarred face-on lenticular galaxy. 
%
% %\cite{laurikainen2010} modeled this galaxy with a S\'ersic-bulge + exponential-disk + 2 Ferrer-lenses 
% %($R_{\rm e} = 8''.9$, $n = 2.7$).
% %\cite{sani2011} opted for a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 26''.8$, $n = 3.0$).
% \emph{1D fit -- }
% The unsharp mask of NGC 0524 unravels a faint multi-ring structure in the galaxy disk,
% with a major ring peaking at $R \sim 20''$.
% We accounted only for this brightest ring using a Gaussian ring profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n0524_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 0524.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 0524.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + G-r & $6.0$  &  $1.1$ \\
% T.W. 1D eq.  & S-bul + e-d + G-r & $5.8$  &  $1.1$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% L+10      & S-bul + e-d + 2 F-l & $8.9$  &  $2.7$ \\
% S+11      & S-bul + e-d	  & $26.8$  &  $3.0$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n0524}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%
% {\bf NGC 0821 \\}
%
% ok
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n0821_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 0821.}
% \end{center}
% \end{figure}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 1023 \\}
%
% NGC 1023 is a barred lenticular galaxy. % with no partially depleted core \cite{faber1997}. \\
%
% %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 17''.7$, $n = 2.0$). 
% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-bar model 
% %($R_{\rm e} = 24''.0$, $n = 3.0$).
% %\cite{lasker2014data} employed a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
% %($R_{\rm e} = 9''.6$, $n = 3.1$).
% \emph{1D fit -- }
% The bar extends out to $R \lesssim 40''$.
% %The light profile of NGC 1023 is well described by a S\'ersic-bulge + exponential-disk + Ferrer-bar model.
% Small deviations of the disk from a perfect exponential profile, 
% within the region $60'' \lesssim R \lesssim 125''$ (that has been excluded from the fit), 
% can be ascribed to some faint residual spiral arms, also noticeable in the 2D residual image. 
% The peak at $R \sim 10''$ in the B4 profile signals the presence of an embedded (and faint) disk.
% The 1D residuals show a structure within $R \lesssim 10''$ caused by this unsubtracted 
% component, also noted by \cite{lasker2014data}.
% Attempts to account for the inner disk by adding a fourth function to the model 
% did not significantly modify the best-fit bulge parameters,
% thus we elected not to model the embedded disk.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n1023_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 1023.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 1023.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar & $9.2$  &  $2.1$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar & $7.4$  &  $2.0$ \\
% T.W. 2D      & S-bul + e-d + G-bar & $6.6$  &  $2.3$ \\
% \hline
% GD07    & S-bul + e-d 	& $17.7$  &  $2.0$ \\
% S+11    & S-bul + e-d + G-bar & $24.0$  &  $3.0$ \\
% L+14    & S-bul + e-d + S-bar & $9.6$   &  $3.1$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n1023}
% \end{table}
%
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 1300 \\}
%
% NGC 1300 is a face-on, barred spiral galaxy. % with no partially depleted core \citep{graham2012MNRAS}. 
%
% %\cite{sani2011} fit NGC 1300 with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 85''.4$, $n = 3.0$).
% %\cite{lasker2014data} built their model with a S\'ersic-bulge + exponential-disk + PSF-nucleus + exponential-inner-disk + 
% %S\'ersic-bar + spiral arms
% %($R_{\rm e} = 10''.4$, $n = 4.3$).
%
% \emph{1D fit -- }
% The morphology of NGC 1300 is quite complex. 
% In addition to a large scale disk and a bulge, the galaxy is composed of 
% a large scale bar that extends up to $R \lesssim 90''$, two prominent spiral arms 
% and an inner disk-like component ($R \lesssim 5''$), disclosed by the peaks in the ellipticity and PA profiles.
% We truncate the light profile at $R \sim 50''$ and we fit the inwards combination of the large-scale bar and the disk 
% as a single component, using an exponential function.
% The embedded component is described with a low-$n$ S\'ersic profile.
% %Our final model consists of a S\'ersic-bulge + exponential-(disk+bar) + S\'ersic-inner disk.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n1300_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 1300.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 1300.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-(d+bar) + S-id & $9.9$  &  $3.8$ \\
% T.W. 1D eq.  & S-bul + e-(d+bar) + S-id & $8.1$  &  $3.6$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% S+11    & S-bul + e-d & $85.4$  &  $3.0$ \\
% L+14    & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $10.4$  &  $4.3$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n1300}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 1316 \\}
%
% ok
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n1316_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 1316.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 1316.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + 2 G-r + G-n & $21.5$  &  $2.0$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + 2 G-r + G-n & $15.9$  &  $1.8$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% S+11      & S-bul + e-d + G-n & $93.0$  &  $5.0$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n1316}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 1332 \\}
%
% ok
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 1332.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 1332.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + S-id + m-c & $34.7$  &  $5.1$ \\
% T.W. 1D eq.  & S-bul + S-id + m-c & $18.0$  &  $3.7$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n1332}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 1374 \\}
%
% ok
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 1399 \\}
%
% NGC 1399, the central galaxy of the Fornax cluster, is an elliptical galaxy with a partially depleted core 
% ($R_{\rm break} \sim 2''.4$, \citealt{rusli2013,dullograham2014cores}).
% The nuclear activity of NGC 1399 is classified as Seyfert \citep{veroncettyveron2006},
% but the galaxy lacks of dust \citep{tran2001}.
%
% %\cite{grahamdriver2007} fit the galaxy light profile with a single S\'ersic-bulge profile 
% %($n = 16.8$).  
% %\cite{rusli2013} modeled NGC 1399 with a core-S\'ersic profile and the sum of a S\'ersic and an exponential
% %function accounting for the galaxy halo 
% %($R_{\rm e} = 36''.2$, $n = 7.38$). 
% %\cite{lasker2014data} used a S\'ersic-bulge + mask-core model 
% %($R_{\rm e} = 154''.0$, $n = 11.1$). 
%
% \emph{1D fit -- }
% The ellipticity and PA profiles display a steep decline within $R \lesssim 60''$,
% suggesting the presence of an embedded disk.
% This inner component is also visible, although very faint, in the unsharp mask.
% TBD!! velocity map, the disk is face on
% We note that, after excluding the innermost $6''.1$ affected by the partially depleted core,
% a single S\'ersic profile is not sufficient to describe the whole galaxy light profile.
% The addition of an inner exponential function to the model 
% notably improves the fit.
% %We build our final model with a S\'ersic-bulge + mask-core + exponential-inner disk.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n1399_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 1399.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 1399.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c + e-id & $405.2$  &  $10.0$ \\
% T.W. 1D eq.  & S-bul + m-c + e-id & $338.1$  &  $10.0$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% GD07         & S-bul  		    & $-$      &  $16.8$ \\
% R+13         & core-S\'ersic + (S+e)-halo & $36.2$   &  $7.4$ \\
% L+14         & S-bul + m-c		    & $154.0$  &  $11.1$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n1399}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 2273 \\}
%
% NGC 2273 is a barred spiral galaxy with a Seyfert AGN \citep{contini1998} 
% and circumnuclear dust \citep{simoeslopes2007}. 
% Its bar is surrounded by two tightly wound star-forming spiral arms that resemble a ring
% \citep{comeron2010}. 
%
% \cite{laurikainen2005} pointed out the presence of an inner disk embedded in the bulge of NGC 2273,
% but they deliberately chose not to model it due to the degeneracy between the functions describing the bulge
% and the inner disk. 
% %Their final model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar 
% %($R_{\rm e} = 2''.6$, $n = 1.8$). 
%
% \emph{1D fit -- }
% The bar of NGC 2273 extends out to $R \lesssim 25''$. 
% The pseudo-ring does not produce any evident swelling in the light profile, 
% therefore we do not account for it in the galaxy model.
% The isophotal parameters confirm the presence of a nuclear disk-like component within $R \lesssim 5''$.
% However, as noted by \cite{laurikainen2005}, any attempt to account for the embedded disk resulted in a 
% degenerate model. 
% This is not surprising if one considers the poor spatial resolution of the galaxy image, 
% the effective radius of the bulge being comparable to the FWHM of the PSF.
% Although NGC 2273 hosts an optical AGN and nuclear dust, no central excess of light is observed in the 1D residuals.
% The addition of a nuclear component to the model does not improve the fit and does not significantly affect
% the bulge parameters.
% %Our final model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n2273_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 2273.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 2273.}
% \begin{center}
% \begin{tabular}{llccc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar & $1.6$  &  $2.1$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar & $1.9$  &  $2.7$ \\
% %T.W. 2D	&  & $$  &  $$ \\
% \hline
% L+05         & S-bul + e-d + F-bar & $2.6$  &  $1.8$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n2273}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 2549 \\}
%
% NGC 2549 is an edge-on barred lenticular galaxy. 
%
% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 11''.6$, $n = 7.0$). 
%
% \emph{1D fit -- }
% Although the edge-on inclination of NGC 2549 complicates the identification of embedded components, 
% a large scale bar ($R \lesssim 45''$) can be recognized in the galaxy image itself and -- more easily -- in the light profile.
% We describe the large scale bar with a Ferrer profile.
% A peak in the ellipticity profile discloses the presence of a disky component
% embedded in the bulge ($R \lesssim 10''$).
% This inner component can be spotted also by looking at the velocity map.
% We fit it with a Ferrer profile.
% %We build our final model with a S\'ersic-bulge + exponential-disk + 2 Ferrer-bars.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n2549_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 2549.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 2549.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + F-id & $6.1$  &  $2.3$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + F-id & $3.1$  &  $1.5$ \\
% T.W. 2D      & S-bul + e-d + G-bar + G-id & $5.6$  &  $2.1$ \\
% \hline
% S+11         & S-bul + e-d & $11.6$  &  $7.0$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n2549}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 2778 \\}
%
% NGC 2778 is an almost face-on lenticular galaxy. 
%
% %\cite{grahamdriver2007} modeled NGC 2778 with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 2''.3$, $n = 1.6$). 
% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk model
% %($R_{\rm e} = 2''.5$, $n = 2.5$). 
% %\cite{vika2012} employed a S\'ersic-bulge + exponential-disk model 
% %($R_{\rm e} = 1''.5$, $n = 2.7$). 
% %\cite{lasker2014data} fit the galaxy with a S\'ersic-bulge + exponential-disk + S\'ersic-bar
% %($R_{\rm e} = 2''.8$, $n = 4.0$). 
%
% \emph{1D fit -- }
% The peak in the ellipticity profile at $R \sim 5''$ unravels the existence of a nuclear component 
% embedded in the galaxy bulge.
% After an inspection of the unsharp mask, we identified this component with a small bar,
% that we modeled with a Ferrer function.
% We also accounted for some nuclear light excess by adding a PSF component to the model.
% %We then fit NGC 2778 with a S\'ersic-bulge + exponential-disk + Ferrer-bar + PSF-nucleus.
% We note that excluding the PSF component from our galaxy model does not significantly affect the 
% bulge effective radius, but it increases the S\'ersic index to $n \sim 2$.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n2778_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 2778.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 2778.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + PSF-n & $2.3$  &  $1.3$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + PSF-n & $2.2$  &  $1.2$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% GD07         & S-bul + e-d	     & $2.3$  &  $1.6$ \\
% S+11         & S-bul + e-d	     & $2.5$  &  $2.5$ \\
% V+12         & S-bul + e-d	     & $1.5$  &  $2.7$ \\
% L+14         & S-bul + e-d + S-bar & $2.8$  &  $4.0$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n2778}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 2787 \\}
%
% NGC 2787 is a barred lenticular galaxy with LINER nuclear activity \citep{veroncettyveron2006}.
% An inner disk is embedded in the bulge of this galaxy \citep{erwin2003n2787}.
% NGC 2787 features a spectacular structure of dust rings at its center \citep{erwinsparke2003}
% and a nuclear stellar disk ($R \lesssim 1''.8$, \citealt{ledo2010}).
%
% %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 4''.6$, $n = 2.0$). 
% %\cite{fisherdrory2008} decomposed NGC 2787 in a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 9''.1$, $n = 1.2$).
% %\cite{laurikainen2010} employed a S\'ersic-bulge + exponential-disk + Ferrer-bar + Ferrer-lens model
% %($R_{\rm e} \sim 4''$, $n = 1.3$).
% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN 
% %($R_{\rm e} = 15''.7$, $n = 3.0$). 
% %\cite{lasker2014data} described NGC 2787 with a S\'ersic-bulge + truncated exponential-disk + 
% %truncated S\'ersic-bar + S\'ersic-inner disk + PSF-nucleus
% %($R_{\rm e} = 14''.3$, $n = 2.8$). 
%
% \emph{1D fit -- }
% NGC 2787 has an undoubtedly complex morphology. 
% This galaxy is made of a bulge, a large scale disk, a bar (see the peaks in the ellipticity, PA and B4 profiles
% at $R \sim 30''$) with two ansae, an inner disk (or bar?) embedded in the bulge (see the peak in the ellipticity profile
% at $R \sim 17''$), and a bright nucleus.
%
% Beyond $R \gtrsim 50''$, where the galaxy large scale disk extends without being affected by the bar ansae,
% the surface brightness profile is not a perfect exponential, being better described by a S\'ersic function
% with $n < 1$.
% Curiously, at optical wavelengths the disk has an exponential decline with no truncation or anti-truncation 
% (see \citealt{erwin2003n2787} their Figure 14, and \citealt{erwin2008}).
% Here we propose two different models for NGC 2787.
% In both cases we used a S\'ersic profile for the bulge, a Ferrer function for the bar, a second Ferrer function for the inner disk (or bar) 
% and a PSF for the nucleus. 
% We then described the large scale disk using a S\'ersic function with $n < 1$ 
% or an exponential function. 
% In the last case we needed to exclude the data within $R \sim 30'' - 50''$ where the ansae produce a hollow.
% The two different decompositions result in the same bulge best-fit parameters ($R_{\rm e} \sim 5''$, $n \sim 1$)
% along the major-axis, whereas the outcome is significantly different along the equivalent-axis 
% ($n = 1.3$ when using the exponential-disk and $n = 2.2$ when using the S\'ersic-disk).
%
% might just pick one TBD!!
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n2787_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 2787.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 2787.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% \multicolumn{4}{c}{\emph{exponential-disk}} \\
% %\hline
% T.W. 1D maj. & S-bul + e-d + F-bar + F-id + PSF-nucleus & $4.8$  &  $1.1$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + F-id + PSF-nucleus & $3.3$  &  $1.3$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% \multicolumn{4}{c}{\emph{S\'ersic-disk}}\\
% %\hline
% T.W. 1D maj. & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.6$  &  $1.1$ \\
% T.W. 1D eq.  & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.4$  &  $2.2$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% GD07         & S-bul + e-d					  & $4.6$   &  $2.0$ \\
% L+10         & S-bul + e-d + F-bar + F-l			  & $4.0$   &  $1.3$ \\
% S+11         & S-bul + e-d + G-bar + G-n			  & $15.7$  &  $3.0$ \\
% L+14         & S-bul + trunc. e-d + trunc. S-bar + S-id + PSF-n & $14.3$  &  $2.8$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n2787}
% \end{table}
%
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 2974 \\}
%
% NGC 2974 is a spiral galaxy which has been misclassified as an elliptical galaxy in the RC3 catalog.
% The galaxy hosts a Seyfert AGN \citep{veroncettyveron2006} and filamentary dust in its center \citep{tran2001}.
%  
% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + Gaussian-AGN 
% %($R_{\rm e} = 27''.2$, $n = 3.0$). 
%
% \emph{1D fit -- }
% From an inspection of the unsharp mask, we identified a ring structure at $R \sim 50''$, 
% probably a residual of two tightly wound spiral arms,
% and an elongated bar-like component within $R \lesssim 30''$, that we fit with a Ferrer function.
% The last one produces a peak in the ellipticity profile at $R \sim 20''$.
% Although the ring is extremely faint, it is important to account for it in the galaxy decomposition. 
% A model without the ring component results in a ``steeper'' exponential-disk (the disk has a smaller scale length 
% and a lower central surface brightness) and produces bad residuals within $R \lesssim 40''$.
% The nuclear component is fit with a Gaussian profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 2974.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 2974.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + G-n + G-r & $8.3$   &  $1.4$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + G-n + G-r & $6.9$   &  $1.2$ \\
% T.W. 2D      & S-bul + e-d + G-bar + m-n	 & $10.6$  &  $1.3$ \\
% \hline
% S+11         & S-bul + G-n & $27.2$  &  $3.0$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n2974}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%   
% {\bf NGC 3079 \\}
%
% inner component?? ok fuck it
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3079_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3079.}
% \end{center}
% \end{figure}
%
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 3091 \\}
%
% NGC 3091 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.62$, \citealt{rusli2013}).
%
% %\cite{rusli2013} modeled NGC 3091 with a single core-S\'ersic profile 
% %($R_{\rm e} = 91''.0$, $n = 9.3$). 
%
% \emph{1D fit -- }
% The data within the innermost $6''.1$ are excluded from the fit.
% A faint embedded component ($R \lesssim 10''$) can be recognized in the unsharp mask and has a corresponding peak in the
% ellipticity profile.
% This extra component is clearly visible in the residual image obtained by subtracting a 2D S\'ersic model from the  
% galaxy image.
% However, any attempt to account for the embedded component resulted in an unsatisfactory fit and did not 
% significantly affect the bulge parameters.
% We thus elected not to model the inner component.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3091_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3091.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 3091.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $100.5$  &  $7.6$ \\
% T.W. 1D eq.  & S-bul + m-c & $51.2$	&  $6.6$ \\
% T.W. 2D      & S-bul + m-c & $67.1$	&  $6.7$ \\
% \hline
% R+13         & core-S\'ersic & $91.0$  &  $9.3$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n3091}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 3115 \\}
%
% NGC 3115 is an edge-on elliptical/lenticular galaxy. 
% Its nuclear activity is classified as passive in the optical wavelengths \citep{gavazzi2013nuclspec}.
% This galaxy features a nuclear stellar disk ($R \sim 1''$, \citealt{scorzabender1995,ledo2010}).
%
% \cite{grahamdriver2007} TBD!!! ask Alister what did they do, not clear from appendix
% ($n = 13.0$). 
% \cite{fisherdrory2008} decomposed the galaxy in a S\'ersic-bulge + exponential disk 
% ($R_{\rm e} = 31''.0$, $n = 3.9$). 
% %\cite{sani2011} modeled NGC 3115 with a S\'ersic-bulge + exponential disk 
% %($R_{\rm e} = 27''.3$, $n = 3.0$). 
% %\cite{lasker2014data} used a S\'ersic-bulge + exponential disk + S\'ersic-envelope 
% %($R_{\rm e} = 3''.9$, $n = 3.0$). 
%
% \emph{1D fit -- }
% NGC 3115 is an example of a galaxy with an intermediate scale disk.
% The surface brightness profile of NGC 3115 does not have an exponential decline at large radii 
% because the disk component does not dominate the outer regions of the galaxy.
% This is immediately evident by looking at the ellipticity and B4 profiles.
% Going from the galaxy center to the outskirts, the ellipticity increases until it reaches its maximum 
% ($\epsilon \sim 0.65$) at $R \sim 90''$. 
% After this point, it starts declining, being as low as $\epsilon \sim 0.55$ at $R \sim 240''$. 
% The galaxy isophotes display a positive diskyness within $R \sim 90''$, but become perfect ellipses 
% ($B4 \sim 0$) beyond that point.
% Now, because galaxy disks typically have fixed ellipticity, reflecting their inclination to our line of sight,
% the previous observations tell us that, going from the galaxy center to the outer regions,
% the disk of NGC 3115 becomes increasingly important relative to the spheroid light, reaching its maximum at $R \sim 90''$.
% Beyond $R \gtrsim 90''$, the contribution from the disk light starts declining more rapidly than the spheroid light.
% This interpretation is supported by the results of \cite{arnold2011n3115},
% who found that within $R \sim 110''$ the bulge of NGC 3115 is flattened and rotates rapidly ($v/\sigma \gtrsim 1.5$),
% whereas at larger radii the rotation declines dramatically (to $v/\sigma \sim 0.7$), 
% but remains well aligned with the inner regions. \\
% From an inspection of the unsharp mask, we identify a faint nuclear edge-on ring ($R \sim 15''$), 
% which produces a corresponding peak in the ellipticity profile. \\
% %We build our model with a S\'ersic-bulge + exponential disk + Gaussian-ring. \\
% We do not observe any nuclear excess of light in the 1D residuals, 
% contrary to what we expected given the presence of a nuclear stellar disk. 
% The addition of a PSF component to the final model does not significantly change the outcome of the fit. 
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3115_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3115.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 3115.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + G-r & $43.6$  &  $4.4$ \\
% T.W. 1D eq.  & S-bul + e-d + G-r & $34.4$  &  $5.1$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% GD07         & ??? TBD	       & $-$	&  $13.0$ \\
% S+11         & S-bul + e-d	       & $27.1$ &  $3.0$ \\
% L+14         & S-bul + e-d + S-halo  & $3.9$  &  $3.0$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n3115}
% \end{table}
%   
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 3227 \\}
%
% NGC 3227 is a spiral galaxy with a large-scale bar. 
% This galaxy hosts a Seyfert AGN \citep{khachikian1974} and circumnuclear dust \citep{martini2003}. 
%
% %\cite{laurikainen2004} decomposed NGC 3227 into a S\'ersic-bulge + exponential-disk + Ferrer-bar 
% %($R_{\rm e} = 1''.8$, $n = 2.2$). 
% %\cite{sani2011} described this galaxy with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 82''.9$, $n = 4.0$). 
% %\cite{lasker2014data} used a S\'ersic-bulge + exponential disk + S\'ersic-bar 
% %($R_{\rm e} = 0''.7$, $n = 4.1$). 
%
% \emph{1D fit -- }
% The large-scale bar produces an evident bump in the major-axis surface brightness profile,
% which is curiously absent in the equivalent-axis profile. \\
% We modeled the bar with a Ferrer function and the nucleus with a Gaussian function. 
% As expected, the Ferrer component is rejected by the equivalent-axis fit.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3227_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3227.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 3227.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + G-n   & $8.1$  &  $1.7$ \\
% T.W. 1D eq.  & S-bul + e-d + [F-bar] + G-n & $4.6$  &  $1.1$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% L+04         & S-bul + e-d + F-bar & $1.8$  &  $2.2$ \\
% S+11         & S-bul + e-d	     & $82.9$ &  $4.0$ \\
% L+14         & S-bul + e-d + S-bar & $0.7$  &  $4.1$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n3227}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 3245 \\}
%
% NGC 3245 is a lenticular galaxy.
%
% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 11''.3$, $n = 4.3$). 
% %\cite{laurikainen2010} described the galaxy with a S\'ersic-bulge + exponential-(disk+lens) + Ferrer-inner disk 
% %($R_{\rm e} \sim 4''$, $n = 2.4$).  
% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 4''.6$, $n = 2.5$). 
% %\cite{vika2012} employed a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 3''.5$, $n = 2.6$). 
% %\cite{beifiori2012} decomposed the galaxy into a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 4''.00$, $n = 1.6$). 
% %\cite{lasker2014data} built their model with a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
% %($R_{\rm e} = 1''.95$, $n = 1.6$). 
%
% \emph{1D fit -- }
% The unsharp mask reveals the presence of an embedded disk ($R \lesssim 15''$), 
% confirmed by the corresponding peaks in the ellipticity and B4 profiles.
% We model this inner component with a Ferrer function.
% %We model the galaxy with a S\'ersic-bulge + exponential-disk + Ferrer-inner disk.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3245_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3245.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 3245.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-id & $4.4$  &  $2.9$ \\
% T.W. 1D eq.  & S-bul + e-d + F-id & $2.4$  &  $1.7$ \\
% T.W. 2D      & S-bul + e-d + G-id & $1.9$  &  $1.8$ \\
% \hline
% GD07         & S-bul + e-d		& $11.3$ &  $4.3$ \\
% L+10         & S-bul + e-(d+l) + F-id & $4.0$  &  $2.4$ \\
% S+11         & S-bul + e-d		& $4.6$  &  $2.5$ \\
% V+12         & S-bul + e-d		& $3.5$  &  $2.6$ \\
% B+12         & S-bul + e-d		& $4.0$  &  $1.6$ \\
% L+14         & S-bul + e-d + S-bar	& $2.0$  &  $1.6$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n3245}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%
% {\bf NGC 3377 \\}
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3377.}
% \end{center}
% \end{figure}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 3384 \\}
%
% NGC 3384 is a barred lenticular galaxy that hosts 
% an embedded disk ($R \lesssim 11''$, \citealt{erwin2004}) and 
% a nuclear stellar disk ($R \lesssim 0''.8$, \citealt{ledo2010}).
%
% %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 2''.5$, $n = 1.7$). 
% %\cite{laurikainen2010} described the galaxy with a S\'ersic-bulge + exponential-disk + 2 Ferrer-bars
% %($R_{\rm e} \sim 4''$, $n = 1.5$).  
% %\cite{sani2011} employed a S\'ersic-bulge + exponential-disk + Gaussian-bar 
% %($R_{\rm e} = 4''.4$, $n = 2.5$). 
% %\cite{beifiori2012} modeled the galaxy with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 8''.3$, $n = 2.3$). 
% %\cite{lasker2014data} decomposed the galaxy into a S\'ersic-bulge + exponential-disk + S\'ersic-inner disk + 
% %S\'ersic-nuclear disk + S\'ersic-bar
% %($R_{\rm e} = 5''.9$, $n = 2.5$). 
%
% \emph{1D fit -- }
% The isophotal parameters clearly show the presence of a boxy bar that extends out to $R \lesssim 18''$.
% We model the bar with a Ferrer function.
% An embedded disk can be seen in the unsharp mask and produces the peak in the ellipticity profile at $R \sim 4''$.
% modeling the embedded disk turned out to be a complicated task, resulting in a degenerate model.
% We elected not to fit the embedded disk (nor the nuclear disk) and we therefore excluded from the fit the innermost $3''.7$,
% where there two components are expected to dominate.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3384_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3384.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 3384.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + m-n & $5.5$  &  $1.6$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + m-n & $5.6$  &  $1.8$ \\
% %T.W. 2D	&  & $$  &  $$ \\
% \hline
% GD07         & S-bul + e-d		      & $2.5$  &  $1.7$ \\
% L+10         & S-bul + e-d + 2 F-bar        & $4.0$  &  $1.5$ \\
% S+11         & S-bul + e-d + G-bar	      & $4.4$  &  $2.5$ \\
% B+12         & S-bul + e-d		      & $8.3$  &  $2.3$ \\
% L+14         & S-bul + e-d + 2 S-id + S-bar & $5.9$  &  $2.5$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n3384}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 3393 \\}
%
% NGC 3393 is an edge-on spiral galaxy hosting a Seyfert AGN \citep{diaz1988n3393} and 
% circumnuclear dust \citep{martini2003}.
% The galaxy has a large-scale bar and a nuclear bar ($R \lesssim 3''$, \citealt{erwin2004}).  
%
% \emph{1D fit -- }
% The large-scale bar ($R \lesssim 20''$) is modeled with a Ferrer function.
% The poor spatial resolution of the data does not allow to fit the nuclear bar and/or the AGN component 
% without incurring degeneracies.
% We thus elected not to fit the nuclear components.
% We note that the addition to the model of a central component would lower the bulge S\'ersic index,
% whereas the the addition of a nuclear bar component would increase the bulge S\'ersic index.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3393_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3393.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 3393.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar & $1.4$  &  $3.4$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar & $1.4$  &  $2.6$ \\
% T.W. 2D      & S-bul + e-d + G-bar & $1.2$  &  $1.9$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n3393}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 3414 \\}
%
% NGC 3414 is a peculiar lenticular/elliptical galaxy. 
% Different interpretations have been proposed about the morphology of this galaxy.
% \cite{whitmore1990} suggested that NGC 3414 is an edge-on galaxy 
% with a large scale polar ring, rather than a face-on barred lenticular.
% \cite{laurikainen2010} decomposed NGC 3414 as a barred lenticular galaxy, but 
% they cautioned against the uncertainty of their solution due to the possible misinterpretation of the 
% galaxy morphology.
%
% \emph{1D fit -- }
% The unsharp mask clearly shows that the edge on component does not extend all the way through the 
% center of the galaxy, but instead it is truncated at $R \sim 20''$.
% However, an elongated structure in the galaxy center resembles a nuclear edge-on disk ($R \lesssim 5''$).
% The velocity map shows rotation within $R \lesssim 5''$ and no rotation within $5'' \lesssim R \lesssim 15''$.
% Beyond $R \gtrsim 15''$ one can recognize a sign of rotation in the opposite direction of the nuclear region.
% The velocity pattern is consistent with the galaxy being a spheroidal system containing a polar ring and a nuclear disk
% both seen edge-on.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3414_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3414.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 3414.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-id + G-r & $28.0$  &  $4.8$ \\
% T.W. 1D eq.  & S-bul + e-id + G-r & $25.5$  &  $4.5$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% L+10         & S-bul + e-d + F-bar	  & $5.0$  &  $2.6$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n3414}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 3489 \\}
%
% NGC 3489 is a barred lenticular galaxy. 
% Its disk has a smooth antitruncation at $R \sim 85''$ \citep{erwin2008}.
%
% \cite{nowak2010n3368n3489} argued for the presence of both a pseudo-bulge and a classical bulge. 
% %\cite{laurikainen2010} fit this galaxy with a S\'ersic-bulge + exponential-disk + Ferrer-bar
% %($R_{\rm e} \sim 2''$, $n = 2.1$). 
% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 4''.6$, $n = 1.5$). 
%
% \emph{1D fit -- }
% We excluded the data beyond $R \gtrsim 38''$ to avoid fitting the antitruncation region.
% The bar is fit with a Ferrer function.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3489_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3489.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 3489.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar & $2.2$  &  $1.5$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar & $1.7$  &  $1.3$ \\
% T.W. 2D      & S-bul + e-d + G-bar & $1.7$  &  $2.1$ \\
% \hline
% L+10         & S-bul + e-d + F-bar & $2.0$  &  $2.1$ \\
% S+11         & S-bul + e-d & $4.6$  &  $1.5$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n3489}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%
% {\bf NGC 3585 \\}
%
% ok
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3585.}
% \end{center}
% \end{figure}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%
% {\bf NGC 3607 \\}
%
% ok
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3607.}
% \end{center}
% \end{figure}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%
% {\bf NGC 3608 \\}
%
% ok
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3608.}
% \end{center}
% \end{figure}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 3842 \\}
%
% NGC 3842 is the brightest member of the Leo Cluster (Abell 1367).
% It is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.7$, 
% \citealt{rusli2013,dullograham2014cores}).
%
% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic model 
% %($R_{\rm e} = 58''.8$, $n = 6.3$). 
%
% \emph{1D fit -- }
% The light profile presents a swelling at $R \sim 20''$ and the ellipticity profile has a peak in the same position.
% One can also glimpse a faint elongated oval in the unsharp mask.
% The innermost $6''.1$ are excluded from the fit due to the presence of a partially depleted core.
% As expected, a single S\'ersic model is not sufficient to provide a good description of the galaxy light profile 
% and we need to add a second component (Ferrer function) to account for the embedded lens.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3842exp_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3842.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 3842.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + F-l + m-c  & $100.7$  &  $8.1$ \\
% T.W. 1D eq.  & S-bul + F-l + m-c  & $73.6$   &  $8.2$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% R+13         & core-S\'ersic & $58.8$  &  $6.3$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n3842}
% \end{table}  
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 3998 \\}
%
% NGC 3998 is a barred lenticular galaxy with a Seyfert AGN and dust in its nucleus \citep{knapp1996n3998}.
% Despite its large stellar velocity dispersion, this galaxy does not have a partially depleted core TBD!! ref??. 
% \cite{gutierrez2011} identified a bar at $R \lesssim 8''$, a ring between $30'' \lesssim R \lesssim 50''$, and  
% an antitruncation in the light profile of the disk at $R \sim 122''$.
% \cite{laurikainen2010} found that NGC 3998 features a weak bar at $R < 8''$,
% a bright lens at $R < 15''$ and a weak bump in the surface brightness profile at $R \sim 40''$ 
% %($R_{\rm e} \sim 5''$, $n = 2.0$).
% %\cite{sani2011} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN 
% %($R_{\rm e} = 4''.7$, $n = 1.5$).
% %\cite{beifiori2012} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 5''.7$, $n = 2.3$).
% %\cite{lasker2014data} used a S\'ersic-bulge + exponential-disk (with inner truncation) + PSF-nucleus + 
% %S\'ersic-inner disk + S\'ersic-bar 
% %($R_{\rm e} = 2''.0$, $n = 1.1$).
%
% \emph{1D fit -- }
% We see three distinct peaks in the ellipticity profile.
% The first two peaks occur at $R \sim 7''$ and $R \sim 15''$, and they correspond to a weak bar and to a faint 
% oval component respectively.
% These components are both fit with a Ferrer function.
% The third peak at $R \sim 35''$ coincides with a bump in the surface brightness profile and is produced by a ring.
% The AGN component is modeled with a Gaussian profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n3998_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 3998.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 3998.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + F-l + G-n + G-r & $5.8$  &  $1.2$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + F-l + G-n + G-r & $4.8$  &  $1.3$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% L+10         &  & $5.0$  &  $2.0$ \\
% S+11         & S-bul + e-d + G-bar + G-n & $4.7$  &  $1.5$ \\
% B+12         & S-bul + e-d & $5.7$  &  $2.3$ \\
% L+14         & S-bul + trunc. e-d + PSF-n + S-bar + S-id & $2.0$  &  $1.1$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n3998}
% \end{table} 
%
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4026 \\}
%
% NGC 4026 is an edge-on lenticular galaxy with a nuclear stellar disk ($R \lesssim 0''.5$, \citealt{ledo2010}).
%
% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 11''.4$, $n = 3.5$).
%
% \emph{1D fit -- }
% The unsharp mask reveals the presence of a bar ($R \lesssim 30''$) and of a disky component 
% embedded in the bulge, that is responsible for the peak at $R \sim 5''$ in the B4 profile.
% The last can be also recognized in the velocity map.
% The bar is fit with a Ferrer function and the inner disk with a low-$n$ S\'ersic profile.
% Due to the poor spatial resolution of our data, we were not able to model the nuclear stellar disk.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4026_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4026.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 4026.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + S-id & $3.4$  &  $2.4$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + S-id & $6.3$  &  $2.1$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% S+11         & S-bul + e-d & $11.4$  &  $3.5$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n4026}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4151 \\}
%
% NGC 4151 is a face-on barred spiral galaxy that hosts a Seyfert AGN \citep{veroncettyveron2006} 
% and circumnuclear dust \citep{pott2010}.
%
% \cite{sani2011} fit this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-AGN model
% ($R_{\rm e} = 5''.4$, $n = 3.5$).
% \cite{gadotti2008} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar + PSF-AGN 
% ($R_{\rm e} = 4''.7$, $n = 3.0$).
%
% \emph{1D fit -- }
% embedded disk in the bulge,
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4151_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4151.}
% \end{center}
% \end{figure}
%
%
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4261 \\}
%
% NGC 4261 is an elliptical galaxy with %a radio jet \citep{liuxie1992}, 
% a LINER nucleus \citep{veroncettyveron2006}
% and a dusty nuclear disk \citep{tran2001}.
% The galaxy features a partially depleted core ($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
%
% %\cite{grahamdriver2007} fit NGC 4261 with a single S\'ersic-bulge 
% %($R_{\rm e} = 88''.6$, $n = 7.3$).
% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model 
% %($R_{\rm e} = 22''.6$, $n = 4.0$).
% %\cite{vika2012} employed a S\'ersic-bulge + mask-core 
% %($R_{\rm e} = 24''.2$, $n = 3.5$).
% %\cite{beifiori2012} adopted a single S\'ersic-bulge model 
% %($R_{\rm e} = 48''.8$, $n = 4.3$).
% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
% %($R_{\rm e} = 77'.1$, $n = 6.3$).
% %\cite{lasker2014data} employed a S\'ersic-bulge + mask-core model 
% %($R_{\rm e} = 68'.4$, $n = 6.5$).
%
% \emph{1D fit -- }
% The ellipticity profile has a peak at $R \sim 10''$, unraveling the presence of an embedded component.
% We identify such component with an inner disk, possibly seen face-on, and we model it with a Ferrer function.
% The innermost $6''.1$ are excluded from the fit due to the presence of a partially depleted core.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4261_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4261.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 4261.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c + F-id & $52.6$  &  $4.7$ \\
% T.W. 1D eq.  & S-bul + m-c + F-id & $47.3$  &  $4.3$ \\
% T.W. 2D      & S-bul + m-c + e-id & $50.4$  &  $4.4$ \\
% \hline
% GD07      & S-bul		& $88.6$  &  $7.3$ \\
% S+11      & S-bul + e-d + G-n & $22.6$  &  $4.0$ \\
% V+12      & S-bul + m-c	& $24.2$  &  $3.5$ \\
% B+12      & S-bul		& $48.8$  &  $4.3$ \\
% R+13      & core-S\'ersic	& $77.1$  &  $6.3$ \\
% L+14      & S-bul + m-c	& $68.4$  &  $6.5$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n4261}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4291 \\}
%
% NGC 4291 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
%
% %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge 
% %($R_{\rm e} = 14'.8$, $n = 4.0$).
% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
% %($R_{\rm e} = 15''.3$, $n = 5.6$).
% %\cite{lasker2014data} adopted a S\'ersic-bulge + mask-core model
% %($R_{\rm e} = 21''.3$, $n = 8.6$).
%
% \emph{1D fit -- }
% After excluding from the fit the innermost $6''.1$, because affected by the partially depleted core,
% we found that NGC 4291 can be modeled with a single S\'ersic profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4291_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4291.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 4291.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $15.0$  &  $4.2$ \\
% T.W. 1D eq.  & S-bul + m-c & $15.4$  &  $5.9$ \\
% T.W. 2D      & S-bul + m-c & $20.8$  &  $7.7$ \\
% \hline
% GD07         & S-bul         & $14.8$  &  $4.0$ \\
% R+13         & core-S\'ersic & $15.3$  &  $5.6$ \\
% L+14         & S-bul + m-c   & $21.3$  &  $8.6$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n4291}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4388 \\}
%
% NGC 4388 is an edge-on spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006} 
% and copious nuclear dust \citep{martini2003}.
%
% \emph{1D fit -- }
% The peaks at $R \sim 30''$ in the ellipticity and B4 profiles signal the presence of a bar.
% The data between $35'' \lesssim R \lesssim 65''$ have been excluded because cannot be accommodated by the Ferrer function 
% used to describe the bar. 
% The AGN component is fit with a Gaussian profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4388_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4388.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 4388.}
% \begin{center}
% \begin{tabular}{llccc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $4.6$  &  $0.6$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.2$  &  $1.3$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n4388}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4459 \\}
%
% NGC 4459 is a lenticular galaxy.
% Its disk profile is reported to have an antitruncation at $R \sim 119''$ \citep{gutierrez2011}.
%
% %\cite{laurikainen2010} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Ferrer-lens 
% %($R_{\rm e} \sim 7'' $, $n = 3.0$).
% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 10''.3$, $n = 2.5$).
% %\cite{vika2012} modeled this galaxy with a S\'ersic-bulge + Moffat-nucleus 
% %($R_{\rm e} = 25''.0$, $n = 3.9$).
% %\cite{beifiori2012} adopted a single S\'ersic-bulge model 
% %($R_{\rm e} = 155''.2$, $n = 7.4$).
%
% \emph{1D fit -- }
% The ellipticity constantly increases across all the observed radial range ($R \lesssim 100''$).
% This is an indication that, going from the galaxy center to the outskirts,
% the disk component becomes increasingly more important than the spheroidal component.
% However, the lack of a plateau in the ellipticity profile at large radii implies that at $R \sim 100''$ 
% the contribution from the bulge is still significant compared to that of the disk.
% In fact, the surface brightness profile does not display an exponential decline at large radii.
% We note that the antitruncation reported by \cite{gutierrez2011} could be an artificial feature 
% produced by the transition between the radial range where the disk becomes increasingly more important 
% over the bulge and the truly exponential decline of the disk beyond $R \gtrsim 119''$.
% We do not find evidence for any embedded components in our data.
% A nuclear light excess is observed in the 1D residuals from a S\'ersic + exponential fit 
% and is consequently modeled with a Gaussian profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4459_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4459.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 4459.}
% \begin{center}
% \begin{tabular}{llccc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + G-n & $18.4$  &  $3.1$ \\
% T.W. 1D eq.  & S-bul + e-d + G-n & $13.0$  &  $2.6$ \\
% %T.W. 2D	&  & $$  &  $$ \\
% \hline
% L+10      & S-bul + e-d + F-l & $7.0$   &  $3.0$ \\
% S+11      & S-bul + e-d	& $10.3$  &  $2.5$ \\
% V+12      & S-bul + M-n	& $25.0$  &  $3.9$ \\
% B+12      & S-bul		& $155.2$ &  $7.4$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n4459}
% \end{table}
%
%
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4473 \\}
%
% NGC 4473 is an elliptical galaxy with an embedded disk \citep{scorzabender1998,ledo2010}.
%
% \cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
% ($R_{\rm e} = 39''.6$, $n = 2.7$). 
% \cite{sani2011} used a S\'ersic-bulge model
% ($R_{\rm e} = 49''.3$, $n = 7.0$). 
% \cite{vika2012} fit this galaxy with a S\'ersic-bulge + mask-core 
% ($R_{\rm e} = 21''.3$, $n = 4.3$). 
% \cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model 
% ($R_{\rm e} = 10''.6$, $n = 2.2$).  
% \cite{lasker2014data} described this galaxy with a single S\'ersic-bulge 
% ($R_{\rm e} = 27''.9$, $n = 5.1$).  
%
%
% \emph{1D fit -- }
% TBD!! explain ellipticity profile...
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4473_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4473.}
% \end{center}
% \end{figure}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4564 \\}
%
% NGC 4564 is an edge-on lenticular galaxy.
%
% %\cite{grahamdriver2007} decomposed this galaxy into a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 4''.3$, $n = 3.2$). 
% \cite{fisherdrory2008} fit this galaxy with a S\'ersic-bulge + exponential-disk 
% ($R_{\rm e} = 8''.7$, $n = 3.7$). 
% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
% %($R_{\rm e} = 25''.0$, $n = 7.0$).
% %\cite{vika2012} used a S\'ersic-bulge + exponential-disk model 
% %($R_{\rm e} = 3''.0$, $n = 3.7$). 
%
% \emph{1D fit -- }
% The isophotal parameters do not show any evidence for embedded components.
% However, fitting NGC 4564 with a S\'ersic + exponential model results in bad residuals.
% In the unsharp mask, one can hardly glimpse an oval structure extending out to $R \lesssim 15''$.
% The addition of a Ferrer function to the model dramatically improves the fit and smoothes the residuals.
% Although the lack of strong evidence for the presence of a (faint) third component, 
% we prefer to model the lens with a Ferrer function 
% because of the notable improvement in the goodness of the global fit.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4564_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4564.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 4564.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-l & $5.0$  &  $2.6$ \\
% T.W. 1D eq.  & S-bul + e-d + F-l & $6.0$  &  $3.0$ \\
% %T.W. 2D	&  & $$  &  $$ \\
% \hline
% GD07      & S-bul + e-d & $4.3$  &  $3.2$ \\
% S+11      & S-bul + e-d & $25.0$ &  $7.0$ \\
% V+12      & S-bul + e-d & $3.0$  &  $3.7$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n4564}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4596 \\}
%
% NGC 4596 is an edge-on barred lenticular galaxy.
%
% %\cite{laurikainen2005} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Ferrer-bar + Ferrer-lens 
% %($R_{\rm e} = 2''.8$, $n = 1.4$). 
% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-bar 
% %($R_{\rm e} = 28''.0$, $n = 3.0$). 
% %\cite{vika2012} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
% %($R_{\rm e} = 13''.2$, $n = 3.6$). 
% %\cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model
% %($R_{\rm e} = 44''.9$, $n = 4.4$).
%
% \emph{1D fit -- }
% The morphology of this galaxy is quite complex. 
% The bar extends out to $R \lesssim 50''$ and concludes in two evident ansae.
% The large-scale disk features a wide ring that is responsible for the curvature in the light profile observed within 
% $60'' \lesssim R \lesssim 130''$ (see also \citealt{comeron2014}).
% An additional embedded disk-like component ($R \lesssim 15''$) can be recognized in the B4 profile and in the velocity map.
% The bump in the light profile within $60'' \lesssim R \lesssim 70''$ corresponds to the ansae of the bar.
% This data range has therefore been excluded from the fit.
% The large scale bar is fit with a Ferrer function and the inner disk with a S\'ersic profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4596_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4596.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 4596.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + G-r + S-id & $6.6$  &  $2.7$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + G-r + S-id & $9.0$  &  $3.0$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% L+05      & S-bul + e-d + F-bar + F-l & $2.8$  &  $1.4$ \\
% S+11      & S-bul + e-d + G-bar & $28.0$  &  $3.0$ \\
% V+12      & S-bul + e-d + S-bar & $13.2$  &  $3.6$ \\
% B+12      & S-bul + e-d & $44.9$  &  $4.4$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n4596}
% \end{table}
%
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4697 \\}
%
% NGC 4697 is an elliptical galaxy with an embedded disk \cite{scorzabender1995}.
%
% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge model
% %($n = 4.0$).
% %\cite{sani2011} described it with a S\'ersic-bulge 
% %($R_{\rm e} = 100'.5$, $n = 5.0$). 
% %\cite{vika2012} proposed a single S\'ersic-bulge model 
% %($R_{\rm e} = 39''.1$, $n = 3.8$) 
% %or a S\'ersic-bulge + exponential-disk model 
% %($R_{\rm e} = 10''.0$, $n = 2.9$).
% %\cite{beifiori2012} chose a single S\'ersic-bulge 
% %($R_{\rm e} = 128''.7$, $n = 5.0$).
% %\cite{lasker2014data} decomposed NGC 4697 into a S\'ersic-bulge + exponential-disk + PSF-nucleus + S\'ersic-envelope 
% %($R_{\rm e} = 6''.3$, $n = 2.1$).
%
% \emph{1D fit -- }
% The velocity map and the unsharp mask of NGC 4697 clearly show 
% the presence of an intermediate-size disk embedded in the main spheroid.
% However, the ellipticity profile presents two peaks. 
% The peak at $R \sim 40''$ corresponds to the embedded disk already mentioned,
% while the peak at $R \sim 10''$ unveils a second inner disk-like component.
% After testing different decomposition models, 
% in which we fit the embedded disks with a set of different functions (exponential, S\'ersic, Ferrer)
% but we always described the main spheroidal component with a S\'ersic profile,
% we noticed that the bulge parameters did not vary significantly among the various decompositions.
% Our preferred model for NGC 4697 consists of a S\'ersic-bulge + 2 S\'ersic-inner disks.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4697_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4697.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 4697.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + 2 S-id & $239.3$  &  $7.2$ \\
% T.W. 1D eq.  & S-bul + 2 S-id & $226.4$  &  $6.7$ \\
% T.W. 2D      & S-bul + e-id	& $121.4$  &  $5.0$ \\
% \hline
% GD07  & S-bul & $-$  &  $4.0$ \\
% S+11  & S-bul & $100.5$  &  $5.0$ \\
% V+12  & S-bul & $39.1$  &  $3.8$ \\
% V+12  & S-bul + e-d & $10.0$  &  $2.9$ \\
% L+14  & S-bul + e-d + PSF-n + S-halo & $6.3$  &  $2.1$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n4697}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4889 \\}
%
% NGC 4889 is the brightest member of the Coma cluster. 
% It is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.6$, \citealt{rusli2013}).
%
% %\cite{rusli2013} modeled NGC 4889 with a core-S\'ersic model 
% %($R_{\rm e} = 169''.2$, $n = 9.8$). 
%
% \emph{1D fit -- }
% We excluded from the fit the innermost $6''.1$ because affected by the partially depleted core and
% we modeled the galaxy with a single S\'ersic profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4889.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 4889.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $119.7$  &  $8.1$ \\
% T.W. 1D eq.  & S-bul + m-c & $60.8$	&  $6.8$ \\
% T.W. 2D      & S-bul + m-c & $104.3$  &  $7.8$ \\
% \hline
% R+13         & core-S\'ersic & $169.2$  &  $9.8$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n4889}
% \end{table}
%   
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 4945 \\}
%
% TBD!!! \\
% NGC 4945 is an edge-on, dusty spiral galaxy that hosts a Seyfert AGN \citep{lin2011}.
%
% \cite{kormendy2010} found that the bulge of NGC 4945 is best modeled with a low-$n$ S\'ersic function
% ($n = 1.3$).
%
% \emph{1D fit -- }
% Given the edge-on inclination of this object, the identification of a possible large-scale bar is complicated.
% The light profile has an obvious bump that could be interpreted in two different ways.
% The bump could be produced by a large-scale bar; 
% in this case, either the disk must have a truncation happening at a radius smaller than the length of the bar,
% or its light profile cannot be exponential (this condition can be caused by the high inclination of the galaxy).
% Alternatively, the bump could be due by the galaxy spiral arms, the disk has an exponential profile with no truncation
% and the galaxy has no bar.
% After checking that both scenarios result in similar best-fit parameters for the bulge, 
% we choose the second and simpler hypothesis.
% We exclude form the fit the data between $R \sim 100''-400''$, where the spiral arm would contribute to the galaxy light,
% and we also exclude the innermost $6''.4$ due to the presence of the AGN.
% Our final model for NGC 4945 consists of a S\'ersic-bulge + exponential-disk.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4945_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 4945.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 4945.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d & $13.9$  &  $1.4$ \\
% T.W. 1D eq.  & S-bul + e-d & $9.5$   &  $1.7$ \\
% T.W. 2D      & S-bul + e-d & $16.2$  &  $0.8$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n4945}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 5077 \\}
%
% ok
%
% \emph{1D fit -- }
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n5077_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 5077.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 5077.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $23.5$  &  $4.2$ \\
% T.W. 1D eq.  & S-bul + m-c & $23.0$  &  $5.7$ \\
% T.W. 2D      & S-bul + m-c & $30.5$  &  $6.8$ \\
% \hline
% S+11         & S-bul + G-n & $29.2$  &  $6.0$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n5077}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%
% {\bf NGC 5128 - Centaurus A \\}
%
% ok
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n5128_1Dfit.eps}
% \caption{}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 5128.}
% \begin{center}
% \begin{tabular}{llccc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & TBD!! & $61.3$  &  $1.2$ \\
% T.W. 1D eq.  &  & $60.8$  &  $2.2$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% S+11         & S-bul + e-d + G-n & $103.6$  &  $3.5$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n5128}
% \end{table}
%
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%
% {\bf NGC 5576 \\}
%
% ok
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
% \caption{}
% \end{center}
% \end{figure}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 5845 \\}
%
% NGC 5845 is an elliptical/lenticular galaxy. 
%
% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
% %($R_{\rm e} = 4''.1$,$n = 3.2$).
% %\cite{sani2011} fit it with a S\'ersic-bulge 
% %($R_{\rm e} = 3''.7$, $n = 3.0$). 
% %\cite{vika2012} used a S\'ersic-bulge model 
% %($R_{\rm e} = 3''.5$, $n = 2.6$).
% %\cite{beifiori2012} chose a single S\'ersic-bulge 
% %($R_{\rm e} = 4''.1$, $n = 3.5$).
% %\cite{lasker2014data} described this galaxy with a S\'ersic-bulge 
% %($R_{\rm e} = 3''.5$, $n = 2.8$).
%
% \emph{1D fit -- }
% The small apparent size of NGC 5845 (compared to the PSF FWHM) implies low resolution for the data 
% and complications for the modeling of this galaxy.
% Here, looking at the unsharp mask and the velocity field, we identify 
% a disk component, either large-scale or embedded.
% To rule out one of the two cases, a good test would be to check whether
% the light profile of NGC 5845 presents an exponential decline in its outer part.
% Unfortunately, the IRAC image is not deep enough and beyond $R \gtrsim 23''$ the galaxy light 
% is fainter than $3 RMS_{\rm SKY}$.
% %Since the too small radial range prevents us from disentangling between an embedded and a large-scale disk,
% %we choose the most statistically significant solution (lowest $\chi^2$), 
% %but we caution that the best fit parameters might be biased by a non adequate choice
% %of the model components. 
% %However, our results are in agreement with those from \cite{jia2012}, 
% %who study the structure and kinematics of NGC5845 with HST/WFPC2 data 
% %and previously published spatially resolved kinematics, and unambiguously identify a 
% %large scale disk in both the photometry and the kinematics. \\
% The ellipticity profile has a peak at $R \sim 13''$ and therefore suggests that the disk is indeed embedded.
% However, when fitting NGC 5845 with a S\'ersic + exponential model, 
% the lowest-$\chi^2$ solution does not reproduce an inner disk, but rather a large-scale one.
% This is because the S\'ersic and the exponential function are degenerate in this decomposition, 
% due to the small number of data points sampling the galaxy light profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n5845_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 5845.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 5845.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d & $3.6$  &  $2.5$ \\
% T.W. 1D eq.  & S-bul + e-d & $3.1$  &  $2.3$ \\
% T.W. 2D      & S-bul + e-d & $2.8$  &  $2.4$ \\
% \hline
% GD07      & S-bul & $4.1$  &  $3.2$ \\
% S+11      & S-bul & $3.7$  &  $3.0$ \\
% V+12      & S-bul & $3.5$  &  $2.6$ \\
% B+12      & S-bul & $4.1$  &  $3.5$ \\
% L+14      & S-bul & $3.5$  &  $2.8$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n5845}
% \end{table}
%
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 5846 \\}
%
% NGC 5846 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
% This galaxy has a LINER nucleus \citep{carrillo1999} and filamentary nuclear dust \citep{tran2001}.
%
% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge
% %($R_{\rm e} = 36''.4$, $n = 3.0$). 
% %\cite{vika2012} used a S\'ersic-bulge + mask-core model 
% %($R_{\rm e} = 46''.3$, $n = 3.7$). 
% %\cite{rusli2013} fit this galaxy with a core-S\'ersic profile 
% %($R_{\rm e} = 113''.2$, $n = 5.3$). 
%
% \emph{1D fit -- }
% This galaxy has a strong isophotal twist between its center and $R \sim 70''$, and
% its light profile presents a slight bump at $R \sim 20''$.
% However, the isophotal parameters, the unsharp mask and the velocity map lack of clear evidence for an embedded component.
% We thus model NGC 5846 with a single S\'ersic profile, after masking the innermost $6''.1$.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n5846_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 5846.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 5846.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $105.1$  &  $6.4$ \\
% T.W. 1D eq.  & S-bul + m-c & $83.4$	&  $5.7$ \\
% T.W. 2D      & S-bul + m-c & $85.1$	&  $5.2$ \\
% \hline
% S+11      & S-bul	    & $36.4$   &  $3.0$ \\
% V+12      & S-bul + m-c   & $46.3$   &  $3.7$ \\
% R+13      & core-S\'ersic & $113.2$  &  $5.3$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n5846}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 6251 \\}
%
% NGC 6251 is an elliptical galaxy with a large stellar velocity dispersion ($\sigma \sim 310~\rm km~s^{-1}$),
% which is a clue for the presence of a partially depleted core.
% The galaxy features a nuclear disk of dust \citep{ferrareseford1999n6251} and a Seyfert AGN \citep{panessabassani2002}.
%
% %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge 
% %($R_{\rm e} = 173''.92$, $n = 11.8$). 
% %\cite{sani2011} adopted a S\'ersic-bulge + Gaussian-AGN model 
% %($R_{\rm e} = 42''.4$, $n = 7.0$). 
% %\cite{lasker2014data} modeled this galaxy with a S\'ersic-bulge 
% %($R_{\rm e} = 20''.6$, $n = 5.0$). 
%
% \emph{1D fit -- }
% We masked the innermost $6''.1$ because possibly affected by the combined contribution of the AGN 
% and the partially depleted core. 
% A single S\'ersic profile provides a good description of NGC 6251.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n6251_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 6251.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 6251.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $41.7$  &  $6.8$ \\
% T.W. 1D eq.  & S-bul + m-c & $30.1$  &  $5.6$ \\
% T.W. 2D      & S-bul + m-c & $39.3$  &  $7.1$ \\
% \hline
% GD07      & S-bul	     & $173.9$  &  $11.8$ \\
% S+11      & S-bul + G-n    & $42.4$	&  $7.0$ \\
% L+14      & S-bul	     & $20.6$	&  $5.0$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n6251}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 7052 \\}
%
% NGC 7052 is an elliptical galaxy reported to have a partially depleted core 
% ($R_{\rm break} = 0''.8$, \citealt{quillen2000}). 
%
% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
% %($R_{\rm e} = 70''.4$, $n = 4.6$). 
% %\cite{sani2011} used a S\'ersic-bulge model 
% %($R_{\rm e} = 39''.3$, $n = 5.0$). 
% %\cite{vika2012} fit this galaxy with a S\'ersic-bulge + exponential-disk
% %($R_{\rm e} = 4''.3$, $n = 1.8$).
% %\cite{lasker2014data} adopted a S\'ersic-bulge model 
% %($R_{\rm e} = 26''.6$, $n = 4.2$). 
%
% \emph{1D fit -- }
% A single S\'ersic function provides a fairly good description of the surface brightness profile of NGC 7052.
% However, the residuals of such fit display a curious behaviour, having a nuclear light excess along the major-axis 
% and a nuclear light deficit along the equivalent-axis. 
% This pattern is still present when the innermost $6''.1$ are excluded and the fit is repeated with a S\'ersic profile.
% The reasons for this are unclear. 
% The best-fit parameters obtained from a single S\'ersic fit, without excluding the innermost data points,
% are not significantly different from those obtained when excluding the core region (see Table \ref{tab:n7052}).
% Given the uncertainty connected to the nuclear region of this galaxy,
% we preferred the model that incorporates the exclusion of the innermost $6''.1$, 
% with the caveat about the ambiguous presence of a partially depleted core.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n7052_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 7052.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 7052.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% \multicolumn{4}{c}{\emph{excluding innermost $6''.1$}} \\
% T.W. 1D maj. & S-bul + m-c & $59.4$  &  $4.2$ \\
% T.W. 1D eq.  & S-bul + m-c & $37.0$  &  $5.6$ \\
% T.W. 2D      & S-bul + m-c & $36.2$  &  $4.0$ \\
% \hline
% \multicolumn{4}{c}{\emph{including innermost $6''.1$}} \\
% T.W. 1D maj. & S-bul & $66.1$  &  $4.8$ \\
% T.W. 1D eq.  & S-bul & $35.0$  &  $5.0$ \\
% %T.W. 2D	&  & $$  & $$  &  $$ \\
% \hline
% GD07      & S-bul & $70.4$  &  $4.6$ \\
% S+11      & S-bul & $39.3$  &  $5.0$ \\
% V+12      & S-bul + e-d & $4.3$  &  $1.8$ \\
% L+14      & S-bul & $26.6$  &  $4.2$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n7052}
% \end{table}
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 7619 \\}
%
% NGC 7619 is an elliptical galaxy reported to have a partially depleted core ($R_{\rm break} = 0''.5$, \citealt{rusli2013}).
%
% %\cite{rusli2013} fit this galaxy with a core-S\'ersic profile 
% %($R_{\rm e} = 100''.1$, $n = 9.3$). 
%
% \emph{1D fit -- }
% We identified an embedded disk signaled by the peak at $R \sim 10''$ in the ellipticity profile.
% The velocity map of this galaxy confirms the presence of a fast rotating component (Falcon-Barroso private comm.).
% We modeled NGC 7619 with a S\'ersic + inner-exponential model.
% We note that the residuals obtained from our best-fit model do not suggest the presence of a partially depleted core,
% whereas they display a nuclear lack of light when the galaxy is modeled with a single S\'ersic-bulge. 
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n7619_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 7619.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 7619.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-id & $63.2$  &  $5.3$ \\
% T.W. 1D eq.  & S-bul + e-id & $58.0$  &  $5.2$ \\
% \hline
% R+13      & core-S\'ersic & $100.1$  &  $9.3$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n7619}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf NGC 7768 \\}
%
% NGC 7768 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
%
% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
% %($R_{\rm e} = 46''.1$, $n = 6.2$). 
%
% \emph{1D fit -- }
% The image of NGC 7768 is corrupted by a saturated star, which lies close to the galaxy.
% The sky background is not constant across the image.
% To be safe, we fit only the innermost $R \lesssim 30''$, where the contribution from the background is negligible.
% The data within $R < 6''.1$ are excluded from the fit due to the presence of a partially depleted core.
% Our best-fit model consists of a single S\'ersic profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/n7768_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for NGC 7768.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for NGC 7768.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $92.9$  &  $8.4$ \\
% T.W. 1D eq.  & S-bul + m-c & $42.1$  &  $6.7$ \\
% \hline
% R+13      & core-S\'ersic & $46.1$  &  $6.2$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:n7768}
% \end{table}
%  
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf UGC 03789 \\}
%
% UGC 03789 is a face-on spiral galaxy.
%
% \emph{1D fit -- }
% This galaxy features a ring ($R \sim 20''$) and a nuclear bar ($R \lesssim 4''$),
% which can be seen in the unsharp mask and produces corresponding peaks in the ellipticity and PA profiles.
% The bar is fit with a Ferrer function.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/ugc03789_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for UGC 03789.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for UGC 03789.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + G-r & $1.8$  &  $1.9$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + G-r & $2.4$  &  $1.4$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:ugc3789}
% \end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgments
GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Elisabete Lima Da Cunha and Gonzalo Diaz 
for useful discussion. \\
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration.

\appendix

\section{1D analytical functions}
\label{sec:app1}
Below we give the mathematical expressions of all the analytical functions used in this work to model 
the observed surface brightness profiles ($\mu$) of galaxies.
We indicate with $R$ the projected galactic radius, 
corresponding to the distance of the isophotes from the galaxy center (along the major- or equivalent-axis). \\

The \emph{S\'ersic profile} \citep{sersic1963,sersic1968} is a three-parameter function with the following form:
\begin{equation}
\mu_{\rm S\acute{e}rsic}(\mu_{\rm e},R_{\rm e},n;R) = \mu_{\rm e} + \frac{2.5~b_{\rm n}}{\ln(10)} 
\Biggl[\biggl(\frac{R}{R_{\rm e}}\biggr)^{1/n}-1\Biggr] ,
\end{equation}
\citep{caon1993,andredakis1995,grahamdriver2005}
where $\mu_{\rm e}$ is the surface brightness at the effective radius $R_{\rm e}$ that encloses 
half of the total light from the model, 
the S\'ersic index $n$ is the parameter that measures the curvature of the radial light profile,
and $b_{\rm n}$ is a scalar value defined in terms of the S\'ersic index $n$.
The value of $b_{\rm n}$ is found by solving numerically the following expression:
\begin{equation}
\Gamma(2n) = 2\gamma(2n,b_{\rm n}),
\end{equation}
where $\Gamma$ is the complete gamma function \citep{ciotti1991} 
and $\gamma$ is the incomplete gamma function defined by 
\begin{equation}
\gamma(2n,x) = \int_{0}^{x} {\rm e}^{-t} t^{2n-1} {\rm d}t .
\end{equation} \\

The \emph{exponential profile} is a special case ($n=1$) of the S\'ersic profile.
It is therefore a two-parameter function, with the following form:
\begin{equation}
\mu_{\rm exponential}(\mu_{\rm 0},h;R) = \mu_{\rm 0} + \frac{2.5}{\ln(10)} \biggl(\frac{R}{h} \biggr) ,
\end{equation}
where $\mu_{\rm 0}$ is the central surface brightness and $h$ is the scale length. \\

The \emph{Gaussian profile} is a two-parameter function with the following form:
\begin{equation}
\mu_{\rm Gaussian}(\mu_{\rm 0},FWHM;R) = \mu_{\rm 0} + \frac{2.5}{\ln(10)} 
\biggl[\frac{R^2}{2(FWHM/2.355)^2} \biggr] ,
\end{equation}
where $\mu_{\rm 0}$ is the central surface brightness 
and $FWHM$ is the full width at half maximum of the Gaussian profile. \\

The \emph{Moffat profile} \citep{moffat1969} is a three-parameter function with the following form:
\begin{equation}
\mu_{\rm Moffat}(\mu_{\rm 0},\alpha,\beta;R) = \mu_{\rm 0} - 2.5 
\log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $\mu_{\rm 0}$ is the central surface brightness,
$\alpha$ is related to the $FWHM$ through 
\begin{equation}
FWHM = 2\alpha \sqrt{2^{1/\beta}-1}
\end{equation}
and $\beta$ regulates the shape of the profile at large radii. \\

The \emph{Ferrer profile} is a four-parameter function with the following form:
\begin{equation}
\mu_{\rm Ferrer}(\mu_{\rm 0},R_{\rm out},\alpha,\beta;R) = \left\{
  \begin{array}{l l}
    \mu_{\rm 0} - 2.5 \log \Biggl[ 1 - \biggl(\frac{R}{R_{\rm out}} \biggr)^{2-\beta} \Biggr]^{\alpha} 
    & \quad \text{for $R<R_{\rm out}$}\\
    +\infty & \quad \text{for $R\geq R_{\rm out}$}
  \end{array} \right. ,
\end{equation}
where $\mu_{\rm 0}$ is the central surface brightness,
$\alpha$ controls the sharpness of the truncation,
$\beta$ is related to the central slope,
and $R_{\rm out}$ is the limit within which the function is defined. \\

The \emph{symmetric Gaussian ring} is a three-parameter function with the following form:
\begin{equation}
\mu_{\rm Gaussian}(\mu_{\rm 0},R_{\rm 0},FWHM;R) = \mu_{\rm 0} + \frac{2.5}{\ln(10)} 
\biggl[\frac{(R-R_{\rm 0})^2}{2(FWHM/2.355)^2} \biggr] ,
\end{equation}
where $\mu_{\rm 0}$ is the central surface brightness,
$R_{\rm 0}$ is the radius at which the Gaussian profile is centered, 
and $FWHM$ is the full width at half maximum of the Gaussian profile. \\

\bibliography{/Users/gsavorgnan/Dropbox/giulia_e_basta/Literature/SMBHbibliography}

\clearpage

\end{document}

### 2015-02-10 papers/data_paper/table_sample.tex
first

\begin{table*}                                        
\begin{center}                                        
\caption{{\bf Galaxy sample.}                        
\emph{Column (1):} Galaxy name.                       
\emph{Column (2):} Distance.                                   
\emph{Column (3):} Black hole mass.                                   
\emph{Column (4):} Reference of the black hole mass reported here (G+03 = \citealt{greenhill2003}, GS13 = \citealt{grahamscott2013}; R+13b = \citealt{rusli2013bhmassesDM}).                                   
\emph{Column (5):} Presence of a partially depleted core. 
The question mark is used when the classification has come from the velocity dispersion criteria mentioned in Section \ref{sec:corser}. 
The value of the core break radius is reported in parenthesis when available.  
\emph{Column (6):} Reference of the identification of a partially depleted core (G+94 = \citealt{grillmair1994}; F+97 = \citealt{forbes1997}; Q+00 = \citealt{quillen2000}, 
T+04 = \citealt{trujillo2004coresersicmodel}; F+06 = \citealt{ferrarese2006acsvcs}; J+11 = \citealt{jardel2011}; R+11 = \citealt{richings2011}; 
DG13 = \citealt{dullograham2013cores}; R+13a = \citealt{rusli2013}).  
\emph{Column (7):} Kinematical classification (fast/slow rotator).
\emph{Column (8):} Availability of velocity map (A = ATLAS$^{\rm 3D}$, S = SLUGGS). 
\emph{Column (9):} Completion of 1D fit. 
\emph{Column (10):} Completion of 2D fit. }                                 
\begin{tabular}{llllllllll}                           
\hline                                                
\multicolumn{1}{l}{{\bf Galaxy}} &                   
\multicolumn{1}{l}{{\bf Distance}} &                 
\multicolumn{1}{l}{{\bf $\bm{M_{\rm BH}}$}} &  
\multicolumn{1}{l}{{\bf Ref.}} &                     
\multicolumn{1}{l}{{\bf Core}} &                     
\multicolumn{1}{l}{{\bf Ref.}} &                     
\multicolumn{1}{l}{{\bf Rot.}} &                     
\multicolumn{1}{l}{{\bf Vel. map}} &                 
\multicolumn{1}{l}{{\bf 1D fit}} &                   
\multicolumn{1}{l}{{\bf 2D fit}} \\                
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{[Mpc]} &                           
\multicolumn{1}{l}{$[10^8~\rm M_{\odot}]$} &         
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{$([\rm arcsec])$} &                                
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{} \\                             
\multicolumn{1}{l}{(1)} &                             
\multicolumn{1}{l}{(2)} &                             
\multicolumn{1}{l}{(3)} &                             
\multicolumn{1}{l}{(4)} &                             
\multicolumn{1}{l}{(5)} &                             
\multicolumn{1}{l}{(6)} &                             
\multicolumn{1}{l}{(7)} &                             
\multicolumn{1}{l}{(8)} &                             
\multicolumn{1}{l}{(9)} &                             
\multicolumn{1}{l}{(10)} \\                         
\hline                                                
Circinus   &  $4.0$  &  $0.017_{-0.003}^{+0.004}$   &  G+03  &  no?  &     &      &     &  no  &  no  \\ 
IC 1459  &  $28.4$  &  $24_{-10}^{+10}$   &  GS13  &  yes  $(0.7)$  &  R+13a  &      &     &  yes  &  yes  \\ 
IC 2560  &  $40.7$  &  $0.044_{-0.022}^{+0.044}$   &  GS13  &  no?  &     &      &     &  yes  &  no  \\ 
IC 4296  &  $40.7$  &  $11_{-2}^{+2}$   &  GS13  &  yes?  &     &      &     &  yes  &  yes  \\ 
M104  &  $9.5$  &  $6.4_{-0.4}^{+0.4}$   &  GS13  &  yes   &  J+11  &      &     &  yes  &  no  \\ 
M105  &  $10.3$  &  $4_{-1}^{+1}$   &  GS13  &  yes  $(1.1)$  &  DG13, R+13a  &  FAST   &  A  &  yes  &  yes  \\ 
M106  &  $7.2$  &  $0.39_{-0.01}^{+0.01}$   &  GS13  &  no   &     &      &     &  yes  &  no  \\ 
M31  &  $0.7$  &  $1.4_{-0.3}^{+0.9}$   &  GS13  &  no   &     &      &     &  yes  &  no  \\ 
M32  &  $0.8$  &  $0.024_{-0.005}^{+0.005}$   &  GS13  &  no   &     &      &     &  no  &  no  \\ 
M49  &  $17.1$  &  $25_{-1}^{+3}$   &  R+13b  &  yes  $(1.5)$  &  DG13, R+13a  &   SLOW  &  A  &  yes  &  yes  \\ 
M59  &  $17.8$  &  $3.9_{-0.4}^{+0.4}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  no  \\ 
M60  &  $16.4$  &  $47_{-10}^{+10}$   &  GS13  &  yes  $(2.7)$  &  DG13, R+13a  &  FAST   &  A, S  &  no  &  no  \\ 
M64  &  $7.3$  &  $0.016_{-0.004}^{+0.004}$   &  GS13  &  no?  &     &      &     &  yes  &  no  \\ 
M77  &  $15.2$  &  $0.084_{-0.003}^{+0.003}$   &  GS13  &  no   &     &      &     &  no  &  no  \\ 
M81  &  $3.8$  &  $0.74_{-0.11}^{+0.21}$   &  GS13  &  no   &     &      &     &  yes  &  no  \\ 
M84  &  $17.9$  &  $9.0_{-0.8}^{+0.9}$   &  GS13  &  yes  $(1.9)$  &  F+06  &   SLOW  &  A, S  &  yes  &  yes  \\ 
M87  &  $15.6$  &  $58.0_{-3.5}^{+3.5}$   &  GS13  &  yes  $(7.2)$  &  F+06  &   SLOW  &  A, S  &  yes  &  yes  \\ 
M89  &  $14.9$  &  $4.7_{-0.5}^{+0.5}$   &  GS13  &  yes  $(0.4)$  &  DG13, R+13a  &   SLOW  &  A  &  yes  &  no  \\ 
M94  &  $4.4$  &  $0.060_{-0.014}^{+0.014}$   &  GS13  &  no?  &     &      &     &  yes  &  no  \\ 
M96  &  $10.1$  &  $0.073_{-0.015}^{+0.015}$   &  GS13  &  no   &     &      &     &  yes  &  yes  \\ 
NGC 0253  &  $3.5$  &  $0.10_{-0.05}^{+0.10}$   &  GS13  &  no   &     &      &     &  no  &  no  \\ 
NGC 0524  &  $23.3$  &  $8.3_{-1.3}^{+2.7}$   &  GS13  &  yes  $(0.2)$  &  R+11  &  FAST   &  A  &  yes  &  no  \\ 
NGC 0821  &  $23.4$  &  $0.39_{-0.09}^{+0.26}$   &  GS13  &  no   &     &  FAST   &  A, S  &  yes  &  yes  \\ 
NGC 1023  &  $11.1$  &  $0.42_{-0.04}^{+0.04}$   &  GS13  &  no   &     &  FAST   &  A, S  &  yes  &  yes  \\ 
NGC 1300  &  $20.7$  &  $0.73_{-0.35}^{+0.69}$   &  GS13  &  no   &     &      &     &  yes  &  no  \\ 
NGC 1316  &  $18.6$  &  $1.50_{-0.80}^{+0.75}$   &  GS13  &  no   &     &  FAST   &     &  yes  &  no  \\ 
NGC 1332  &  $22.3$  &  $14_{-2}^{+2}$   &  GS13  &  no   &     &      &     &  yes  &  no  \\ 
NGC 1374  &  $19.2$  &  $5.8_{-0.5}^{+0.5}$   &  R+13b  &  no?  &     &  FAST   &  A  &  yes  &  yes  \\ 
NGC 1399  &  $19.4$  &  $4.7_{-0.6}^{+0.6}$   &  GS13  &  yes  $(2.4)$  &  DG13, R+13a  &   SLOW  &  A  &  yes  &  no  \\ 
NGC 2273  &  $28.5$  &  $0.083_{-0.004}^{+0.004}$   &  GS13  &  no   &     &      &     &  yes  &  no  \\ 
NGC 2549  &  $12.3$  &  $0.14_{-0.13}^{+0.02}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  yes  \\ 
NGC 2778  &  $22.3$  &  $0.15_{-0.10}^{+0.09}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  no  \\ 
NGC 2787  &  $7.3$  &  $0.40_{-0.05}^{+0.04}$   &  GS13  &  no   &     &      &     &  yes  &  no  \\ 
NGC 2974  &  $20.9$  &  $1.7_{-0.2}^{+0.2}$   &  GS13  &  no   &     &  FAST   &  A, S  &  yes  &  yes  \\ 
NGC 3079  &  $20.7$  &  $0.024_{-0.012}^{+0.024}$   &  GS13  &  no?  &     &      &     &  yes  &  no  \\ 
NGC 3091  &  $51.2$  &  $36_{-2}^{+1}$   &  R+13b  &  yes  $(0.6)$  &  R+13a  &      &     &  yes  &  yes  \\ 
NGC 3115  &  $9.4$  &  $8.8_{-2.7}^{+10.0}$   &  GS13  &  no   &     &      &     &  yes  &  no  \\ 
NGC 3227  &  $20.3$  &  $0.14_{-0.06}^{+0.10}$   &  GS13  &  no   &     &      &     &  yes  &  no  \\ 
NGC 3245  &  $20.3$  &  $2.0_{-0.5}^{+0.5}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  yes  \\ 
NGC 3377  &  $10.9$  &  $0.77_{-0.06}^{+0.04}$   &  GS13  &  no   &     &  FAST   &  A, S  &  yes  &  yes  \\ 
NGC 3384  &  $11.3$  &  $0.17_{-0.02}^{+0.01}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  no  \\ 
NGC 3393  &  $55.2$  &  $0.34_{-0.02}^{+0.02}$   &  GS13  &  no   &     &      &     &  yes  &  yes  \\ 
NGC 3414  &  $24.5$  &  $2.4_{-0.3}^{+0.3}$   &  GS13  &  no   &     &   SLOW  &  A  &  yes  &  no  \\ 
NGC 3489  &  $11.7$  &  $0.058_{-0.008}^{+0.008}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  yes  \\ 
NGC 3585  &  $19.5$  &  $3.1_{-0.6}^{+1.4}$   &  GS13  &  no   &     &      &     &  yes  &  no  \\ 
NGC 3607  &  $22.2$  &  $1.3_{-0.5}^{+0.5}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  yes  \\ 
NGC 3608  &  $22.3$  &  $2.0_{-0.6}^{+1.1}$   &  GS13  &  yes  $(0.2)$  &  DG13, R+13a  &   SLOW  &  A, S  &  yes  &  yes  \\ 
NGC 3842  &  $98.4$  &  $97_{-26}^{+30}$   &  GS13  &  yes  $(0.7)$  &  DG13, R+13a  &      &     &  yes  &  no  \\ 
NGC 3998  &  $13.7$  &  $8.1_{-1.9}^{+2.0}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  no  \\ 
NGC 4026  &  $13.2$  &  $1.8_{-0.3}^{+0.6}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  no  \\ 
NGC 4151  &  $20.0$  &  $0.65_{-0.07}^{+0.07}$   &  GS13  &  no   &     &      &     &  yes  &  no  \\ 
\hline         
\end{tabular}   
\label{tab:sample} 
\end{center}    
\end{table*}

\begin{table*}                                        
\begin{center}                                        
\begin{tabular}{llllllllll}                           
\hline                                                
\multicolumn{1}{l}{{\bf Galaxy}} &                   
\multicolumn{1}{l}{{\bf Distance}} &                 
\multicolumn{1}{l}{{\bf $\mathbf{M_{\rm BH}}$}} &  
\multicolumn{1}{l}{{\bf Ref.}} &                     
\multicolumn{1}{l}{{\bf Core}} &                     
\multicolumn{1}{l}{{\bf Ref.}} &                     
\multicolumn{1}{l}{{\bf Rot.}} &                     
\multicolumn{1}{l}{{\bf Vel. map}} &                 
\multicolumn{1}{l}{{\bf 1D fit}} &                   
\multicolumn{1}{l}{{\bf 2D fit}} \\                
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{[Mpc]} &                           
\multicolumn{1}{l}{$[10^8~\rm M_{\odot}]$} &         
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{$([\rm arcsec])$} &                                
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{} &                                
\multicolumn{1}{l}{} \\                             
\multicolumn{1}{l}{(1)} &                             
\multicolumn{1}{l}{(2)} &                             
\multicolumn{1}{l}{(3)} &                             
\multicolumn{1}{l}{(4)} &                             
\multicolumn{1}{l}{(5)} &                             
\multicolumn{1}{l}{(6)} &                             
\multicolumn{1}{l}{(7)} &                             
\multicolumn{1}{l}{(8)} &                             
\multicolumn{1}{l}{(9)} &                             
\multicolumn{1}{l}{(10)} \\                         
\hline                                                
NGC 4261  &  $30.8$  &  $5_{-1}^{+1}$   &  GS13  &  yes  $(1.6)$  &  R+11  &   SLOW  &  A  &  yes  &  yes  \\ 
NGC 4291  &  $25.5$  &  $3.3_{-2.5}^{+0.9}$   &  GS13  &  yes  $(0.3)$  &  DG13, R+13a  &      &     &  yes  &  yes  \\ 
NGC 4342  &  $23.0$  &  $4.5_{-1.5}^{+2.3}$   &  GS13  &  no   &     &  FAST   &  A  &  no  &  no  \\ 
NGC 4388  &  $17.0$  &  $0.075_{-0.002}^{+0.002}$   &  GS13  &  no?  &     &      &     &  yes  &  no  \\ 
NGC 4459  &  $15.7$  &  $0.68_{-0.13}^{+0.13}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  no  \\ 
NGC 4473  &  $15.3$  &  $1.2_{-0.9}^{+0.4}$   &  GS13  &  no   &     &  FAST   &  A, S  &  yes  &  yes  \\ 
NGC 4486A  &  $17.0$  &  $0.13_{-0.08}^{+0.08}$   &  GS13  &  no   &     &  FAST   &  A  &  no  &  no  \\ 
NGC 4564  &  $14.6$  &  $0.60_{-0.09}^{+0.03}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  no  \\ 
NGC 4596  &  $17.0$  &  $0.79_{-0.33}^{+0.38}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  no  \\ 
NGC 4697  &  $11.4$  &  $1.8_{-0.1}^{+0.2}$   &  GS13  &  no   &     &  FAST   &  A, S  &  yes  &  yes  \\ 
NGC 4889  &  $103.2$  &  $210_{-160}^{+160}$   &  GS13  &  yes  $(1.7)$  &  F+97  &      &     &  yes  &  yes  \\ 
NGC 4945  &  $3.8$  &  $0.014_{-0.007}^{+0.014}$   &  GS13  &  no?  &     &      &     &  yes  &  yes  \\ 
NGC 5077  &  $41.2$  &  $7.4_{-3.0}^{+4.7}$   &  GS13  &  yes  $(0.3)$  &  T+04  &      &     &  yes  &  yes  \\ 
NGC 5128  &  $3.8$  &  $0.45_{-0.10}^{+0.17}$   &  GS13  &  no?  &     &      &     &  yes  &  no  \\ 
NGC 5576  &  $24.8$  &  $1.6_{-0.4}^{+0.3}$   &  GS13  &  no   &     &   SLOW  &  A  &  yes  &  yes  \\ 
NGC 5813  &  $31.3$  &  $6.8_{-0.7}^{+0.7}$   &  GS13  &  yes  $(0.4)$  &  DG13, R+13a  &   SLOW  &  A  &  no  &  no  \\ 
NGC 5845  &  $25.2$  &  $2.6_{-1.5}^{+0.4}$   &  GS13  &  no   &     &  FAST   &  A  &  yes  &  yes  \\ 
NGC 5846  &  $24.2$  &  $11_{-1}^{+1}$   &  GS13  &  yes   &  F+97  &   SLOW  &  A, S  &  yes  &  yes  \\ 
NGC 6251  &  $104.6$  &  $5_{-2}^{+2}$   &  GS13  &  yes?  &     &      &     &  yes  &  yes  \\ 
NGC 7052  &  $66.4$  &  $3.7_{-1.5}^{+2.6}$   &  GS13  &  yes  $(0.8)$  &  Q+00  &      &     &  yes  &  yes  \\ 
NGC 7582  &  $22.0$  &  $0.55_{-0.19}^{+0.26}$   &  GS13  &  no   &     &      &     &  no  &  no  \\ 
NGC 7619  &  $51.5$  &  $25_{-3}^{+8}$   &  R+13b  &  yes  $(0.5)$  &  DG13, R+13a  &      &     &  yes  &  no  \\ 
NGC 7768  &  $112.8$  &  $13_{-4}^{+5}$   &  GS13  &  yes   &  G+94  &      &     &  yes  &  no  \\ 
UGC 03789  &  $48.4$  &  $0.108_{-0.005}^{+0.005}$   &  GS13  &  no?  &     &      &     &  yes  &  no  \\ 
\hline         
\end{tabular}   
\end{center}    
\end{table*}

### 2015-02-10 papers/mbhn/mbhn.tex
first

%%
%% Beginning of file 'sample.tex'
%%
%% Modified 2005 December 5
%%
%% This is a sample manuscript marked up using the
%% AASTeX v5.x LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.x document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the preprint style
%% which will produce a one-column, single-spaced document.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.
%%
%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

%\documentclass[manuscript]{aastex}

%% preprint2 produces a double-column, single-spaced document:

\documentclass[preprint2]{aastex}

\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}
%%\graphicspath{{/Users/gsavorgnan/galaxy_vivisection/results/plots/}}

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.x Author Guide
%% for information.

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{gsavorgn@astro.swin.edu.au}

\newcommand{\fitfigurewidth}{0.8\textwidth}

%% You can insert a short comment on the title page using the command below.

%\slugcomment{Not to appear in Nonlearned J., 45.}

%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.
%% Running heads will not print in the manuscript style.

\shorttitle{Mbh-n paper}
\shortauthors{Savorgnan et al.}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{document}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

\title{Mbh-n paper}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}

%\author{C. D. Biemesderfer\altaffilmark{4,5}}
%\affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
\email{gsavorgn@astro.swin.edu.au}

%\and

%\author{A. W. Graham\altaffilmark{1}}
%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

%\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
%CTIO is operated by AURA, Inc.\ under contract to the National Science
%Foundation.}
%\altaffiltext{2}{Society of Fellows, Harvard University.}
%\altaffiltext{3}{present address: Center for Astrophysics,
%    60 Garden Street, Cambridge, MA 02138}
%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
%\altaffiltext{5}{Patron, Alonso's Bar and Grill}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
blah blah
\end{abstract}

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

\keywords{keywords}

%% From the front matter, we move on to the body of the paper.
%% In the first two sections, notice the use of the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below. We have
%% chosen the first three characters of the first author's name plus
%% the last two numeral of the year of publication as our KEY for
%% each reference.

%% Authors who wish to have the most important objects in their paper
%% linked in the electronic edition to a data center may do so by tagging
%% their objects with \objectname{} or \object{}.  Each macro takes the
%% object name as its required argument. The optional, square-bracket 
%% argument should be used in cases where the data center identification
%% differs from what is to be printed in the paper.  The text appearing 
%% in curly braces is what will appear in print in the published paper. 
%% If the object name is recognized by the data centers, it will be linked
%% in the electronic edition to the object data available at the data centers  
%%
%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
%% the brackets must be escaped with backslashes when used in the first
%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
%%  Otherwise, LaTeX will issue an error.

\section{Introduction}

%%A focal problem today in the dynamics of globular clusters is core collapse.
%%It has been predicted by theory for decades \citep{hen61,lyn68,spi85}, but
%%observation has been less alert to the phenomenon. For many years the
%%central brightness peak in M15 \citep{kin75,new78} seemed a unique anomaly.
%%Then \citet{aur82} suggested a central peak in \object{NGC 6397}, and a
%%limited photographic survey of ours \citep[Paper I]{djo84} found three more
%%cases, \objectname{NGC 6624}, \objectname[M 15]{NGC 7078}, and
%%\object[Cl 1938-341]{Terzan 8}), whose sharp center had often been
%%remarked on \citep{can78}.
%%
%%As an example of how the new AASTeX object tagging macros work, we will
%%cite some of the ``Superlative'' objects mentioned in section 10 of
%%Trimble's (1992) review of astrophysics in the year 1991.  The youngest
%%star yet found was \object[\[JCC87\] IRAS 4]{IRAS 4} in \objectname{NGC 1333}.
%%\object{70 Oph} was found to be the longest period spectroscopic binary.
%%The most massive white dwarf was \object{GD 50}, estimated at 1.2 solar masses.
%%The first neutral hydrogen found in a globular cluster was \object{NGC 2808}
%%while the \objectname[SDSS J093401.92+551427.9]{I Zw 18} retained the
%%record for metal deficiency.  However, another low metallicitity
%%galaxy was \object{UGC 4483} in the \objectname{M 83} group. The
%%largest redshift \object[PC 1247+3406]{source} in 1991 was found at
%%z=4.897.  Lastly, what paper would be complete without a mention of the
%%\object[M1]{Crab nebula}!

\section{Errors}

How do we compute the errors on the measured S\'ersic indices?
Montecarlo, bootstrapping or any other evil statistical method do not take into account the systematics,
which mainly depend on the decomposition model, i.e. the choice of the model components.
But we are lucky, since there are many other decompositions in the literature for our galaxies.
\cite{grahamdriver2007,laurikainen2010,sani2011,vika2012,beifiori2012,rusli2013,lasker2014data} have done this job.
So how about we do something similar to our first paper?
Let's say that I am not better than anybody else at decomposing galaxies 
(this is obviously absurd, given my incredible competence in vivisecting galaxies, but let's assume it for now).
I repeat the same game we did in our first paper.
For each galaxy, I take all the available measurements from the literature, including my own measurement,
and I compute the standard deviation of each set of measurements.
The standard deviation becomes the error of my own measurement.
When my measurement is the only available (nobody other than me ever decomposed that galaxy),
the errors is set to be equal to the median value of the distribution in Figure \ref{fig:hist} 
(almost the same we did in our first paper, see footnote 4).
Figure \ref{fig:hist}: here only galaxies with more than one measurement are contributing.
Take a galaxy, take its set of measurements (more than one!) of the S\'ersic index, 
compute the standard deviation of that set, the standard deviation becomes the error on my own measurement
(BTW, I am using the $n$ derived from the equivalent axis fit).
The distribution of the standard deviations is represented by the histogram.
The median value is $0.13$, which means a median uncertainty of $33\%$ on each individual measurement.
If we take of each set of measurements the average, then the error associated to the average 
and then the median value of all these errors, basically we are doing the same we did in footnote 4 of our first paper,
and the cool thing is that now we get the same number we got then ($20\%$).

\begin{figure}
\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/auxiliary/histo_err_logn.eps}
\caption{}
\label{fig:hist}
\end{figure}

\section{Results}

Figure \ref{fig:mbhn}: Well, we now have the errors on each of OUR measurements of $n$.
We can plot bh mass vs $n$ (in log).

\begin{figure}
\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/mbh_vs_logn.eps}
\caption{}
\label{fig:mbhn}
\end{figure}

Figure \ref{fig:mbhavn}: Almost the same we did in our first paper. We take for each galaxy its set of measurements of $n$,
we reject measurements in disagreement for more than $50\%$,
we compute the median (not the average! this is different from what we did in the past, what do you think?) 
and the error associated to the mean, then we plot the black hole masses vs the median of log(n).
The correlation looks a bit steeper than in Figure \ref{fig:mbhn}, 
with less scatter. I bet you say it looks curved.

PS I will soon step back from the division bulges/ellipticals, 
I seriously believe there is no such division. 
I will explain this soon. ;)

\begin{figure}
\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/mbh_vs_median_logn.eps}
\caption{}
\label{fig:mbhavn}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%

%% In a manner similar to \objectname authors can provide links to dataset
%% hosted at participating data centers via the \dataset{} command.  The
%% second curly bracket argument is printed in the text while the first
%% parentheses argument serves as the valid data set identifier.  Large
%% lists of data set are best provided in a table (see Table 3 for an example).
%% Valid data set identifiers should be obtained from the data center that
%% is currently hosting the data.
%%
%% Note that AASTeX interprets everything between the curly braces in the 
%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
%% compile your manuscript.  Special characters do not 
%% need to be escaped in the optional, square-bracket argument.

%% All our observations were short direct exposures with CCD's.  We also have
%% a random {\it Chandra} data set \dataset{ADS/Sa.ASCA\#X/86008020} and a
%% neat \dataset[ADS/Sa.HST#Y0Q70101T]{HST FOS spectrum} that readers can access
%% via the links in the electronic edition.  Unfortunately this has nothing
%% whatsoever to do with this research.  At Lick Observatory we used a TI 500$\times$500
%% chip and a GEC 575$\times$385, on the 1-m Nickel reflector.  The only
%% filter available at Lick was red.  At CTIO we used a GEC 575$\times$385, with
%% $B, V,$ and $R$ filters, and an RCA 512$\times$320, with $U, B, V, R,$ and $I$
%% filters, on the 1.5-m reflector. In the CTIO observations we tried to
%% concentrate on the shortest practicable wavelengths; but faintness, reddening,
%% and poor short-wavelength sensitivity often kept us from observing in $U$ or
%% even in $B$. All four cameras had scales of the order of 0.4 arcsec/pixel, and
%% our field sizes were around 3 arcmin.
%%
%% The CCD images are unfortunately not always suitable, for very poor
%% clusters or for clusters with large cores.  Since the latter are easily
%% studied by other means, we augmented our own CCD profiles by collecting
%% from the literature a number of star-count profiles
%% \citep{kin68,pet76,har84,ort85}, as well as photoelectric profiles
%% \citep{kin66,kin75} and electronographic profiles \citep{kro84}.
%% In a few cases we judged normality by eye estimates on one of the Sky
%% Surveys.

%% In this section, we use  the \subsection command to set off
%% a subsection.  \footnote is used to insert a footnote to the text.

%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% This section also includes several of the displayed math environments
%% mentioned in the Author Guide.

%%\section{Helicity Amplitudes}
%%
%%It has been realized that helicity amplitudes provide a convenient means
%%for Feynman diagram\footnote{Footnotes can be inserted like this.}
%%evaluations.  These amplitude-level techniques
%%are particularly convenient for calculations involving many Feynman
%%diagrams, where the usual trace techniques for the amplitude
%%squared becomes unwieldy.  Our calculations use the helicity techniques
%%developed by other authors \cite[]{hag86}; we briefly summarize below.
%%
%%\subsection{Formalism} \label{bozomath}
%%
%%%% The equation environment wil produce a numbered display equation.
%%
%%A tree-level amplitude in $e^+e^-$ collisions can be expressed in
%%terms of fermion strings of the form
%%\begin{equation}
%%\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
%%\hat a_nu(p_1,\sigma_1) ,
%%\end{equation}
%%where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
%%and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
%%and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
%%operator $(\tau = \pm1)$.  The $a^\mu_i$ may be formed from particle
%%four-momenta, gauge-boson polarization vectors or fermion strings with
%%an uncontracted Lorentz index associated with final-state fermions.
%%
%%%% The \notetoeditor{TEXT} command allows the author to communicate
%%%% information to the copy editor.  This information will appear as a
%%%% footnote on the printed copy for the manuscript style file.  Nothing will
%%%% appear on the printed copy if the preprint or
%%%% preprint2 style files are used.
%%
%%%% The eqnarray environment produces multi-line display math. The end of
%%%% each line is marked with a \\. Lines will be numbered unless the \\
%%%% is preceded by a \nonumber command.
%%%% Alignment points are marked by ampersands (&). There should be two
%%%% ampersands (&) per line.
%%
%%In the chiral \notetoeditor{Figures 1 and 2 should appear side-by-side in
%%print} representation the $\gamma$ matrices are expressed
%%in terms of $2\times 2$ Pauli matrices $\sigma$ and the unit matrix 1 as
%%\begin{eqnarray}
%%\gamma^\mu  & = &
%% \left(
%%\begin{array}{cc}
%%0 & \sigma^\mu_+ \\
%%\sigma^\mu_- & 0
%%\end{array}	  \right) ,
%% \gamma^5= \left(
%%\begin{array}{cc}
%%-1 &   0\\
%%0 &	1
%%\end{array}	  \right)  , \nonumber \\
%%\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , \nonumber
%%\end{eqnarray}
%%giving
%%\begin{equation}
%%\hat a= \left(
%%\begin{array}{cc}
%%0 & (\hat a)_+\\
%%(\hat a)_- & 0
%%\end{array}\right), (\hat a)_\pm=a_\mu\sigma^\mu_\pm ,
%%\end{equation}
%%The spinors are expressed in terms of two-component Weyl spinors as
%%\begin{equation}
%%u=\left(
%%\begin{array}{c}
%%(u)_-\\
%%(u)_+
%%\end{array}\right), v={\bf (}\vdag_+{\bf ,}	\vdag_-{\bf )} .
%%\end{equation}
%%
%%%% Putting eqnarrays or equations inside the mathletters environment groups
%%%% the enclosed equations by letter. For instance, the eqnarray below, instead
%%%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
%%%% LaTeX the paper and look at the output to see the results.
%%
%%The Weyl spinors are given in terms of helicity eigenstates
%%$\chi_\lambda(p)$ with $\lambda=\pm1$ by
%%\begin{mathletters}
%%\begin{eqnarray}
%%u(p,\lambda)_\pm & = & (E\pm\lambda|{\bf p}|)^{1/2}\chi_\lambda(p) , \\
%%v(p,\lambda)_\pm & = & \pm\lambda(E\mp\lambda|{\bf p}|)^{1/2}\chi
%%_{-\lambda}(p)
%%\end{eqnarray}
%%\end{mathletters}
%%
%%%% This section contains more display math examples, including unnumbered
%%%% equations (displaymath environment). The last paragraph includes some
%%%% examples of in-line math featuring a couple of the AASTeX symbol macros.
%%
%%\section{Floating material and so forth}
%%
%%%% The displaymath environment will produce the same sort of equation as
%%%% the equation environment, except that the equation will not be numbered
%%%% by LaTeX.
%%
%%Consider a task that computes profile parameters for a modified
%%Lorentzian of the form
%%\begin{equation}
%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
%%\end{equation}
%%where
%%\begin{displaymath}
%%d_{1} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{displaymath}
%%d_{2} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{displaymath}
%%x_{1} = (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta
%%\end{displaymath}
%%\begin{displaymath}
%%y_{1} = -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
%%\end{displaymath}
%%
%%In these expressions $x_{0}$,$y_{0}$ is the star center, and $\Theta$ is the
%%angle with the $x$ axis.  Results of this task are shown in table~\ref{tbl-1}.
%%It is not clear how these sorts of analyses may affect determination of
%% $M_{\sun}$, but the assumption is that the alternate results
%%should be less than 90\degr\ out of phase with previous values.
%%We have no observations of \ion{Ca}{2}.
%%Roughly \slantfrac{4}{5} of the electronically submitted abstracts
%%for AAS meetings are error-free.
%%
%%%% If you wish to include an acknowledgments section in your paper,
%%%% separate it off from the body of the text using the \acknowledgments
%%%% command.
%%
%%%% Included in this acknowledgments section are examples of the
%%%% AASTeX hypertext markup commands. Use \url without the optional [HREF]
%%%% argument when you want to print the url directly in the text. Otherwise,
%%%% use either \url or \anchor, with the HREF as the first argument and the
%%%% text to be printed in the second.
%%
\acknowledgments
%chien peng, peter erwin
%%
%%We are grateful to V. Barger, T. Han, and R. J. N. Phillips for
%%doing the math in section~\ref{bozomath}.
%%More information on the AASTeX macros package is available \\ at
%%\url{http://www.aas.org/publications/aastex}.
%%For technical support, please write to
%%\email{aastex-help@aas.org}.
%%
%%%% To help institutions obtain information on the effectiveness of their
%%%% telescopes, the AAS Journals has created a group of keywords for telescope
%%%% facilities. A common set of keywords will make these types of searches
%%%% significantly easier and more accurate. In addition, they will also be
%%%% useful in linking papers together which utilize the same telescopes
%%%% within the framework of the National Virtual Observatory.
%%%% See the AASTeX Web site at http://aastex.aas.org/
%%%% for information on obtaining the facility keywords.
%%
%%%% After the acknowledgments section, use the following syntax and the
%%%% \facility{} macro to list the keywords of facilities used in the research
%%%% for the paper.  Each keyword will be checked against the master list during
%%%% copy editing.  Individual instruments or configurations can be provided 
%%%% in parentheses, after the keyword, but they will not be verified.
%%
%%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
%%
%%%% Appendix material should be preceded with a single \appendix command.
%%%% There should be a \section command for each appendix. Mark appendix
%%%% subsections with the same markup you use in the main body of the paper.
%%
%%%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%%%% The equation counter will reset when it encounters the \appendix
%%%% command and will number appendix equations (A1), (A2), etc.
%%
%%\appendix
%%
%%\section{Appendix material}
%%
%%Consider once again a task that computes profile parameters for a modified
%%Lorentzian of the form
%%\begin{equation}
%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
%%\end{equation}
%%where
%%\begin{mathletters}
%%\begin{displaymath}
%%d_{1} = \frac{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{equation}
%%d_{2} = \case{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
%%\end{equation}
%%\begin{eqnarray}
%%x_{1} & = & (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta \\
%%y_{1} & = & -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
%%\end{eqnarray}
%%\end{mathletters}
%%
%%For completeness, here is one last equation.
%%\begin{equation}
%%e = mc^2
%%\end{equation}

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% AASTeX provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

\bibliography{/Users/gsavorgnan/Dropbox/giulia_e_basta/Literature/SMBHbibliography}

%%\begin{thebibliography}{}
%%\bibitem[Auri\`ere(1982)]{aur82} Auri\`ere, M.  1982, \aap,
%%    109, 301
%%\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
%%    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
%%    McClintock, J. E.  1978, \apj, 224, 39
%%\bibitem[Djorgovski \& King(1984)]{djo84} Djorgovski, S.,
%%    \& King, I. R.  1984, \apjl, 277, L49
%%\bibitem[Hagiwara \& Zeppenfeld(1986)]{hag86} Hagiwara, K., \&
%%    Zeppenfeld, D.  1986, Nucl.Phys., 274, 1
%%\bibitem[Harris \& van den Bergh(1984)]{har84} Harris, W. E.,
%%    \& van den Bergh, S.  1984, \aj, 89, 1816
%%\bibitem[H\`enon(1961)]{hen61} H\'enon, M.  1961, Ann.d'Ap., 24, 369
%%\bibitem[Heiles \& Troland(2003)]{heiles03} Heiles, C. \& Troland, T. H., 2003, \apjs, preprint doi:10.1086/381753
%%\bibitem[Kim, Ostricker, \& Stone(2003)]{kim03} Kim, W.-T.,  Ostriker, E., \& Stone, J. M., 2003, \apj, 599, 1157
%%\bibitem[King(1966)]{kin66}  King, I. R.  1966, \aj, 71, 276
%%\bibitem[King(1975)]{kin75}  King, I. R.  1975, Dynamics of
%%    Stellar Systems, A. Hayli, Dordrecht: Reidel, 1975, 99
%%\bibitem[King et al.(1968)]{kin68}  King, I. R., Hedemann, E.,
%%    Hodge, S. M., \& White, R. E.  1968, \aj, 73, 456
%%\bibitem[Kron et al.(1984)]{kro84} Kron, G. E., Hewitt, A. V.,
%%    \& Wasserman, L. H.  1984, \pasp, 96, 198
%%\bibitem[Lynden-Bell \& Wood(1968)]{lyn68} Lynden-Bell, D.,
%%    \& Wood, R.  1968, \mnras, 138, 495
%%\bibitem[Newell \& O'Neil(1978)]{new78} Newell, E. B.,
%%    \& O'Neil, E. J.  1978, \apjs, 37, 27
%%\bibitem[Ortolani et al.(1985)]{ort85} Ortolani, S., Rosino, L.,
%%    \& Sandage, A.  1985, \aj, 90, 473
%%\bibitem[Peterson(1976)]{pet76} Peterson, C. J.  1976, \aj, 81, 617
%%\bibitem[Rudnick et al.(2003)]{rudnick03} Rudnick, G. et al., 2003, \apj, 599, 847
%%\bibitem[Spitzer(1985)]{spi85} Spitzer, L.  1985, Dynamics of
%%    Star Clusters, J. Goodman \& P. Hut, Dordrecht: Reidel, 109
%%\bibitem[Treu et al.(2003)]{treu03} Treu, T. et al., 2003, \apj, 591, 53
%%\end{thebibliography}

\clearpage

%% Use the figure environment and \plotone or \plottwo to include
%% figures and captions in your electronic submission.
%% To embed the sample graphics in
%% the file, uncomment the \plotone, \plottwo, and
%% \includegraphics commands
%%
%% If you need a layout that cannot be achieved with \plotone or
%% \plottwo, you can invoke the graphicx package directly with the
%% \includegraphics command or use \plotfiddle. For more information,
%% please see the tutorial on "Using Electronic Art with AASTeX" in the
%% documentation section at the AASTeX Web site, http://aastex.aas.org/
%%
%% The examples below also include sample markup for submission of
%% supplemental electronic materials. As always, be sure to check
%% the instructions to authors for the journal you are submitting to
%% for specific submissions guidelines as they vary from
%% journal to journal.

%% This example uses \plotone to include an EPS file scaled to
%% 80% of its natural size with \epsscale. Its caption
%% has been written to indicate that additional figure parts will be
%% available in the electronic journal.

%%\begin{figure}
%%\epsscale{.80}
%%\plotone{f1.eps}
%%\caption{Derived spectra for 3C138 \citep[see][]{heiles03}. Plots for all sources are available
%%in the electronic edition of {\it The Astrophysical Journal}.\label{fig1}}
%%\end{figure}
%%
%%\clearpage
%%
%%%% Here we use \plottwo to present two versions of the same figure,
%%%% one in black and white for print the other in RGB color
%%%% for online presentation. Note that the caption indicates
%%%% that a color version of the figure will be available online.
%%%%
%%
%%\begin{figure}
%%\plottwo{f2.eps}{f2_color.eps}
%%\caption{A panel taken from Figure 2 of \citet{rudnick03}. 
%%See the electronic edition of the Journal for a color version 
%%of this figure.\label{fig2}}
%%\end{figure}
%%
%%%% This figure uses \includegraphics to scale and rotate the still frame
%%%% for an mpeg animation.
%%
%%\begin{figure}
%%\includegraphics[angle=90,scale=.50]{f3.eps}
%%\caption{Animation still frame taken from \citet{kim03}.
%%This figure is also available as an mpeg
%%animation in the electronic edition of the
%%{\it Astrophysical Journal}.}
%%\end{figure}
%%
%%%% If you are not including electonic art with your submission, you may
%%%% mark up your captions using the \figcaption command. See the
%%%% User Guide for details.
%%%%
%%%% No more than seven \figcaption commands are allowed per page,
%%%% so if you have more than seven captions, insert a \clearpage
%%%% after every seventh one.
%%
%%%% Tables should be submitted one per page, so put a \clearpage before
%%%% each one.
%%
%%%% Two options are available to the author for producing tables:  the
%%%% deluxetable environment provided by the AASTeX package or the LaTeX
%%%% table environment.  Use of deluxetable is preferred.
%%%%
%%
%%%% Three table samples follow, two marked up in the deluxetable environment,
%%%% one marked up as a LaTeX table.
%%
%%%% In this first example, note that the \tabletypesize{}
%%%% command has been used to reduce the font size of the table.
%%%% We also use the \rotate command to rotate the table to
%%%% landscape orientation since it is very wide even at the
%%%% reduced font size.
%%%%
%%%% Note also that the \label command needs to be placed
%%%% inside the \tablecaption.
%%
%%%% This table also includes a table comment indicating that the full
%%%% version will be available in machine-readable format in the electronic
%%%% edition.
%%
%%\clearpage
%%
%%\begin{deluxetable}{ccrrrrrrrrcrl}
%%\tabletypesize{\scriptsize}
%%\rotate
%%\tablecaption{Sample table taken from \citet{treu03}\label{tbl-1}}
%%\tablewidth{0pt}
%%\tablehead{
%%\colhead{POS} & \colhead{chip} & \colhead{ID} & \colhead{X} & \colhead{Y} &
%%\colhead{RA} & \colhead{DEC} & \colhead{IAU$\pm$ $\delta$ IAU} &
%%\colhead{IAP1$\pm$ $\delta$ IAP1} & \colhead{IAP2 $\pm$ $\delta$ IAP2} &
%%\colhead{star} & \colhead{E} & \colhead{Comment}
%%}
%%\startdata
%%0 & 2 & 1 & 1370.99 & 57.35	 &   6.651120 &  17.131149 & 21.344$\pm$0.006  & 2
%%4.385$\pm$0.016 & 23.528$\pm$0.013 & 0.0 & 9 & -    \\
%%0 & 2 & 2 & 1476.62 & 8.03	 &   6.651480 &  17.129572 & 21.641$\pm$0.005  & 2
%%3.141$\pm$0.007 & 22.007$\pm$0.004 & 0.0 & 9 & -    \\
%%0 & 2 & 3 & 1079.62 & 28.92	 &   6.652430 &  17.135000 & 23.953$\pm$0.030  & 2
%%4.890$\pm$0.023 & 24.240$\pm$0.023 & 0.0 & - & -    \\
%%0 & 2 & 4 & 114.58  & 21.22	 &   6.655560 &  17.148020 & 23.801$\pm$0.025  & 2
%%5.039$\pm$0.026 & 24.112$\pm$0.021 & 0.0 & - & -    \\
%%0 & 2 & 5 & 46.78   & 19.46	 &   6.655800 &  17.148932 & 23.012$\pm$0.012  & 2
%%3.924$\pm$0.012 & 23.282$\pm$0.011 & 0.0 & - & -    \\
%%0 & 2 & 6 & 1441.84 & 16.16	 &   6.651480 &  17.130072 & 24.393$\pm$0.045  & 2
%%6.099$\pm$0.062 & 25.119$\pm$0.049 & 0.0 & - & -    \\
%%0 & 2 & 7 & 205.43  & 3.96	 &   6.655520 &  17.146742 & 24.424$\pm$0.032  & 2
%%5.028$\pm$0.025 & 24.597$\pm$0.027 & 0.0 & - & -    \\
%%0 & 2 & 8 & 1321.63 & 9.76	 &   6.651950 &  17.131672 & 22.189$\pm$0.011  & 2
%%4.743$\pm$0.021 & 23.298$\pm$0.011 & 0.0 & 4 & edge \\
%%\enddata
%%%% Text for table notes should follow after the \enddata but before
%%%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%%%% in the table for each \tablenotetext.
%%\tablecomments{Table \ref{tbl-1} is published in its entirety in the 
%%electronic edition of the {\it Astrophysical Journal}.  A portion is 
%%shown here for guidance regarding its form and content.}
%%\tablenotetext{a}{Sample footnote for table~\ref{tbl-1} that was generated
%%with the deluxetable environment}
%%\tablenotetext{b}{Another sample footnote for table~\ref{tbl-1}}
%%\end{deluxetable}
%%
%%%% If you use the table environment, please indicate horizontal rules using
%%%% \tableline, not \hline.
%%%% Do not put multiple tabular environments within a single table.
%%%% The optional \label should appear inside the \caption command.
%%
%%\clearpage
%%
%%\begin{table}
%%\begin{center}
%%\caption{More terribly relevant tabular information.\label{tbl-2}}
%%\begin{tabular}{crrrrrrrrrrr}
%%\tableline\tableline
%%Star & Height & $d_{x}$ & $d_{y}$ & $n$ & $\chi^2$ & $R_{maj}$ & $R_{min}$ &
%%\multicolumn{1}{c}{$P$\tablenotemark{a}} & $P R_{maj}$ & $P R_{min}$ &
%%\multicolumn{1}{c}{$\Theta$\tablenotemark{b}} \\
%%\tableline
%%1 &33472.5 &-0.1 &0.4  &53 &27.4 &2.065  &1.940 &3.900 &68.3 &116.2 &-27.639\\
%%2 &27802.4 &-0.3 &-0.2 &60 &3.7  &1.628  &1.510 &2.156 &6.8  &7.5 &-26.764\\
%%3 &29210.6 &0.9  &0.3  &60 &3.4  &1.622  &1.551 &2.159 &6.7  &7.3 &-40.272\\
%%4 &32733.8 &-1.2\tablenotemark{c} &-0.5 &41 &54.8 &2.282  &2.156 &4.313 &117.4 &78.2 &-35.847\\
%%5 & 9607.4 &-0.4 &-0.4 &60 &1.4  &1.669\tablenotemark{c}  &1.574 &2.343 &8.0  &8.9 &-33.417\\
%%6 &31638.6 &1.6  &0.1  &39 &315.2 & 3.433 &3.075 &7.488 &92.1 &25.3 &-12.052\\
%%\tableline
%%\end{tabular}
%%%% Any table notes must follow the \end{tabular} command.
%%\tablenotetext{a}{Sample footnote for table~\ref{tbl-2} that was
%%generated with the \LaTeX\ table environment}
%%\tablenotetext{b}{Yet another sample footnote for table~\ref{tbl-2}}
%%\tablenotetext{c}{Another sample footnote for table~\ref{tbl-2}}
%%\tablecomments{We can also attach a long-ish paragraph of explanatory
%%material to a table.}
%%\end{center}
%%\end{table}
%%
%%%% If the table is more than one page long, the width of the table can vary
%%%% from page to page when the default \tablewidth is used, as below.  The
%%%% individual table widths for each page will be written to the log file; a
%%%% maximum tablewidth for the table can be computed from these values.
%%%% The \tablewidth argument can then be reset and the file reprocessed, so
%%%% that the table is of uniform width throughout. Try getting the widths
%%%% from the log file and changing the \tablewidth parameter to see how
%%%% adjusting this value affects table formatting.
%%
%%%% The \dataset{} macro has also been applied to a few of the objects to
%%%% show how many observations can be tagged in a table.
%%
%%\clearpage
%%
%%\begin{deluxetable}{lrrrrcrrrrr}
%%\tablewidth{0pt}
%%\tablecaption{Literature Data for Program Stars}
%%\tablehead{
%%\colhead{Star}	   & \colhead{V}      &
%%\colhead{b$-$y}	   & \colhead{m$_1$}  &
%%\colhead{c$_1$}	   & \colhead{ref}    &
%%\colhead{T$_{\rm eff}$}  & \colhead{log g}  &
%%\colhead{v$_{\rm turb}$} & \colhead{[Fe/H]} &
%%\colhead{ref}}
%%\startdata
%%HD 97 & 9.7& 0.51& 0.15& 0.35& 2 & \nodata & \nodata & \nodata & $-1.50$ & 2 \\
%%& & & & & & 5015 & \nodata & \nodata & $-1.50$ & 10 \\
%%\dataset[ADS/Sa.HST#O6H04VAXQ]{HD 2665} & 7.7& 0.54& 0.09& 0.34& 2 & \nodata & \nodata & \nodata & $-2.30$ & 2 \\
%%& & & & & & 5000 & 2.50 & 2.4 & $-1.99$ & 5 \\
%%& & & & & & 5120 & 3.00 & 2.0 & $-1.69$ & 7 \\
%%& & & & & & 4980 & \nodata & \nodata & $-2.05$ & 10 \\
%%HD 4306 & 9.0& 0.52& 0.05& 0.35& 20, 2& \nodata & \nodata & \nodata & $-2.70$ & 2 \\
%%& & & & & & 5000 & 1.75 & 2.0 & $-2.70$ & 13 \\
%%& & & & & & 5000 & 1.50 & 1.8 & $-2.65$ & 14 \\
%%& & & & & & 4950 & 2.10 & 2.0 & $-2.92$ & 8 \\
%%& & & & & & 5000 & 2.25 & 2.0 & $-2.83$ & 18 \\
%%& & & & & & \nodata & \nodata & \nodata & $-2.80$ & 21 \\
%%& & & & & & 4930 & \nodata & \nodata & $-2.45$ & 10 \\
%%HD 5426 & 9.6& 0.50& 0.08& 0.34& 2 & \nodata & \nodata & \nodata & $-2.30$ & 2 \\
%%\dataset[ADS/Sa.HST#O5F654010]{HD 6755} & 7.7& 0.49& 0.12& 0.28& 20, 2& \nodata & \nodata & \nodata & $-1.70$ & 2 \\
%%& & & & & & 5200 & 2.50 & 2.4 & $-1.56$ & 5 \\
%%& & & & & & 5260 & 3.00 & 2.7 & $-1.67$ & 7 \\
%%& & & & & & \nodata & \nodata & \nodata & $-1.58$ & 21 \\
%%& & & & & & 5200 & \nodata & \nodata & $-1.80$ & 10 \\
%%& & & & & & 4600 & \nodata & \nodata & $-2.75$ & 10 \\
%%\dataset[ADS/Sa.HST#O56D06010]{HD 94028} & 8.2& 0.34& 0.08& 0.25& 20 & 5795 & 4.00 & \nodata & $-1.70$ & 22 \\
%%& & & & & & 5860 & \nodata & \nodata & $-1.70$ & 4 \\
%%& & & & & & 5910 & 3.80 & \nodata & $-1.76$ & 15 \\
%%& & & & & & 5800 & \nodata & \nodata & $-1.67$ & 17 \\
%%& & & & & & 5902 & \nodata & \nodata & $-1.50$ & 11 \\
%%& & & & & & 5900 & \nodata & \nodata & $-1.57$ & 3 \\
%%& & & & & & \nodata & \nodata & \nodata & $-1.32$ & 21 \\
%%HD 97916 & 9.2& 0.29& 0.10& 0.41& 20 & 6125 & 4.00 & \nodata & $-1.10$ & 22 \\
%%& & & & & & 6160 & \nodata & \nodata & $-1.39$ & 3 \\
%%& & & & & & 6240 & 3.70 & \nodata & $-1.28$ & 15 \\
%%& & & & & & 5950 & \nodata & \nodata & $-1.50$ & 17 \\
%%& & & & & & 6204 & \nodata & \nodata & $-1.36$ & 11 \\
%%\cutinhead{This is a cut-in head}
%%+26\arcdeg2606& 9.7&0.34&0.05&0.28&20,11& 5980 & \nodata & \nodata &$<-2.20$ & 19 \\
%%& & & & & & 5950 & \nodata & \nodata & $-2.89$ & 24 \\
%%+26\arcdeg3578& 9.4&0.31&0.05&0.37&20,11& 5830 & \nodata & \nodata & $-2.60$ & 4 \\
%%& & & & & & 5800 & \nodata & \nodata & $-2.62$ & 17 \\
%%& & & & & & 6177 & \nodata & \nodata & $-2.51$ & 11 \\
%%& & & & & & 6000 & 3.25 & \nodata & $-2.20$ & 22 \\
%%& & & & & & 6140 & 3.50 & \nodata & $-2.57$ & 15 \\
%%+30\arcdeg2611& 9.2&0.82&0.33&0.55& 2 & \nodata & \nodata & \nodata & $-1.70$ & 2 \\
%%& & & & & & 4400 & 1.80 & \nodata & $-1.70$ & 12 \\
%%& & & & & & 4400 & 0.90 & 1.7 & $-1.20$ & 14 \\
%%& & & & & & 4260 & \nodata & \nodata & $-1.55$ & 10 \\
%%+37\arcdeg1458& 8.9&0.44&0.07&0.22&20,11& 5296 & \nodata & \nodata & $-2.39$ & 11 \\
%%& & & & & & 5420 & \nodata & \nodata & $-2.43$ & 3 \\
%%+58\arcdeg1218&10.0&0.51&0.03&0.36& 2 & \nodata & \nodata & \nodata & $-2.80$ & 2 \\
%%& & & & & & 5000 & 1.10 & 2.2 & $-2.71$ & 14 \\
%%& & & & & & 5000 & 2.20 & 1.8 & $-2.46$ & 5 \\
%%& & & & & & 4980 & \nodata & \nodata & $-2.55$ & 10 \\
%%+72\arcdeg0094&10.2&0.31&0.09&0.26&12 & 6160 & \nodata & \nodata & $-1.80$ & 19 \\
%%\sidehead{I'm a side head:}
%%G5--36 & 10.8& 0.40& 0.07& 0.28& 20 & \nodata & \nodata & \nodata & $-1.19$ & 21 \\
%%G18--54 & 10.7& 0.37& 0.08& 0.28& 20 & \nodata & \nodata & \nodata & $-1.34$ & 21 \\
%%G20--08 & 9.9& 0.36& 0.05& 0.25& 20,11& 5849 & \nodata & \nodata & $-2.59$ & 11 \\
%%& & & & & & \nodata & \nodata & \nodata & $-2.03$ & 21 \\
%%G20--15 & 10.6& 0.45& 0.03& 0.27& 20,11& 5657 & \nodata & \nodata & $-2.00$ & 11 \\
%%& & & & & & 6020 & \nodata & \nodata & $-1.56$ & 3 \\
%%& & & & & & \nodata & \nodata & \nodata & $-1.58$ & 21 \\
%%G21--22 & 10.7& 0.38& 0.07& 0.27& 20,11& \nodata & \nodata & \nodata & $-1.23$ & 21 \\
%%G24--03 & 10.5& 0.36& 0.06& 0.27& 20,11& 5866 & \nodata & \nodata & $-1.78$ & 11 \\
%%& & & & & & \nodata & \nodata & \nodata & $-1.70$ & 21 \\
%%G30--52 & 8.6& 0.50& 0.25& 0.27& 11 & 4757 & \nodata & \nodata & $-2.12$ & 11 \\
%%& & & & & & 4880 & \nodata & \nodata & $-2.14$ & 3 \\
%%G33--09 & 10.6& 0.41& 0.10& 0.28& 20 & 5575 & \nodata & \nodata & $-1.48$ & 11 \\
%%G66--22 & 10.5& 0.46& 0.16& 0.28& 11 & 5060 & \nodata & \nodata & $-1.77$ & 3 \\
%%& & & & & & \nodata & \nodata & \nodata & $-1.04$ & 21 \\
%%G90--03 & 10.4& 0.37& 0.04& 0.29& 20 & \nodata & \nodata & \nodata & $-2.01$ & 21 \\
%%LP 608--62\tablenotemark{a} & 10.5& 0.30& 0.07& 0.35& 11 & 6250 & \nodata &
%%\nodata & $-2.70$ & 4 \\
%%\enddata
%%\tablenotetext{a}{Star LP 608--62 is also known as BD+1\arcdeg 2341p.  We will
%%make this footnote extra long so that it extends over two lines.}
%%%% You can append references to a table using the \tablerefs command.
%%\tablerefs{
%%(1) Barbuy, Spite, \& Spite 1985; (2) Bond 1980; (3) Carbon et al. 1987;
%%(4) Hobbs \& Duncan 1987; (5) Gilroy et al. 1988: (6) Gratton \& Ortolani 1986;
%%(7) Gratton \& Sneden 1987; (8) Gratton \& Sneden (1988); (9) Gratton \& Sneden 1991;
%%(10) Kraft et al. 1982; (11) LCL, or Laird, 1990; (12) Leep \& Wallerstein 1981;
%%(13) Luck \& Bond 1981; (14) Luck \& Bond 1985; (15) Magain 1987;
%%(16) Magain 1989; (17) Peterson 1981; (18) Peterson, Kurucz, \& Carney 1990;
%%(19) RMB; (20) Schuster \& Nissen 1988; (21) Schuster \& Nissen 1989b;
%%(22) Spite et al. 1984; (23) Spite \& Spite 1986; (24) Hobbs \& Thorburn 1991;
%%(25) Hobbs et al. 1991; (26) Olsen 1983.}
%%\end{deluxetable}
%%
%%%% Tables may also be prepared as separate files. See the accompanying
%%%% sample file table.tex for an example of an external table file.
%%%% To include an external file in your main document, use the \input
%%%% command. Uncomment the line below to include table.tex in this
%%%% sample file. (Note that you will need to comment out the \documentclass,
%%%% \begin{document}, and \end{document} commands from table.tex if you want
%%%% to include it in this document.)
%%
%%%% \input{table}
%%
%%%% The following command ends your manuscript. LaTeX will ignore any text
%%%% that appears after it.

\end{document}

%%
%% End of file `sample.tex'.

### 2015-02-10 analysis/1D/galaxies/ic1459/temp.sh

@@ -1,0 +1,13 @@
+mv Req_gaussian_linscale.5px_SM.dat	     Req_gaussian_linscale05px_SM.dat
+mv Req_gaussian_linscale.5px_par_SM.dat      Req_gaussian_linscale05px_par_SM.dat
+mv Req_gaussian_linscale.5px_res_SM.dat      Req_gaussian_linscale05px_res_SM.dat
+mv Req_moffat_linscale.5px_SM.dat	     Req_moffat_linscale05px_SM.dat
+mv Req_moffat_linscale.5px_par_SM.dat	     Req_moffat_linscale05px_par_SM.dat
+mv Req_moffat_linscale.5px_res_SM.dat	     Req_moffat_linscale05px_res_SM.dat
+mv Rmaj_gaussian_linscale.5px_SM.dat	     Rmaj_gaussian_linscale05px_SM.dat
+mv Rmaj_gaussian_linscale.5px_par_SM.dat     Rmaj_gaussian_linscale05px_par_SM.dat
+mv Rmaj_gaussian_linscale.5px_res_SM.dat     Rmaj_gaussian_linscale05px_res_SM.dat
+mv Rmaj_moffat_linscale.5px_SM.dat	     Rmaj_moffat_linscale05px_SM.dat
+mv Rmaj_moffat_linscale.5px_par_SM.dat	     Rmaj_moffat_linscale05px_par_SM.dat
+mv Rmaj_moffat_linscale.5px_res_SM.dat	     Rmaj_moffat_linscale05px_res_SM.dat
+mv ic1459_op_mos_galfitsky_linscale.5px.tab  ic1459_op_mos_galfitsky_linscale05px.tab

### 2015-02-10 python_codes/astrolib/mpfit/mpfitexpr.py

@@ -1,0 +1,78 @@
+""" 
+	Copyright (C) 2009 Sergey Koposov
+
+    This program is free software: you can redistribute it and/or modify
+    it under the terms of the GNU General Public License as published by
+    the Free Software Foundation, either version 3 of the License, or
+    (at your option) any later version.
+
+    This program is distributed in the hope that it will be useful,
+    but WITHOUT ANY WARRANTY; without even the implied warranty of
+    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+    GNU General Public License for more details.
+
+    You should have received a copy of the GNU General Public License
+    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+"""
+
+import mpfit 
+import re
+import numpy
+import scipy
+
+def mpfitexpr(func, x, y, err , start_params, check=True, full_output=False,
+						imports=None, **kw):
+	"""Fit the used defined expression to the data
+	Input:
+	- func: string with the function definition 
+	- x: x vector
+	- y: y vector
+	- err: vector with the errors of y
+	- start_params: the starting parameters for the fit
+	Output:
+	- The tuple (params, yfit) with best-fit params and the values of func evaluated at x
+	Keywords:
+	- check: boolean parameter. If true(default) the function will be checked for sanity
+	- full_output: boolean parameter. If True(default is False) then instead of best-fit parameters the mpfit object is returned
+	- imports: list of strings, of optional modules to be imported, required to evaluate the function
+	Example:
+	params,yfit=mpfitexpr('p[0]+p[2]*(x-p[1])',x,y,err,[0,10,1])
+	
+	If you need to use numpy and scipy functions in your function, then
+		you must to use the full names of these functions, e.g.:
+		numpy.sin, numpy.cos etc.
+	
+	This function is motivated by mpfitexpr() from wonderful MPFIT IDL package
+		written by Craig Markwardt	
+	
+	"""
+	
+	hash={}
+	hash['numpy']=numpy
+	hash['scipy']=scipy
+	
+	if imports is not None:
+		for i in imports:
+			#exec '%s=__import__("%s")'%(a,b) in globals(),locals()
+			hash[i]= __import__(i)
+	def myfunc(p,fjac=None,x=None, y=None, err=None):
[…]

### 2015-02-10 python_codes/databases/process_data/process.py

@@ -1,0 +1,128 @@
+import sqlite3 as sql3
+import os
+import numpy as np
+
+from conversions import convert 
+
+
+dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_vivisection.db'
+directoriesFileName = '/Users/gsavorgnan/galaxy_vivisection/analysis/1D/galaxies/directories.list'
+
+axisList = ['maj', 'eq']
+psfsList = ['gaussian', 'moffat']
+scalesList = ['comb', 'log']
+
+
+def process_single_1D(directory, dist_Mpc):
+
+	collection = []
+	collection.append(directory)
+	
+	for axis in axisList:
+		for psf in psfsList:
+			for scale in scalesList:
+				fitResultsFileName = '/Users/gsavorgnan/galaxy_vivisection/analysis/1D/galaxies/' + directory + \
+					'/' + directory + '_' + axis + '_' + psf + '_' + scale + '_par_SM.dat'	
+
+				log_r_e = None
+				mu_e = None
+				log_n = None
+				b = None
+				mag_sph = None
+				mag_tot = None
+				
+				# get distance
+				
+
+				try:
+					fitResultsFile = open(fitResultsFileName)
+					lines = fitResultsFile.readlines()
+					for line in lines:
+						if (line.split()[0] == '1') and (line.split()[1] == 'sersic'):
+							log_r_e = np.log10(convert.arcsecToKpc(float(line.split()[2]),dist_Mpc))
+							mu_e = convert.apparentToAbsoluteMagnitude(float(line.split()[3]),dist_Mpc)
+							log_n = np.log10(float(line.split()[4]))
+							mag_sph = convert.apparentToAbsoluteMagnitude(float(line.split()[6]),dist_Mpc)
+						if (line.split()[0] == 'Total_galaxy_magnitude'):
+							mag_tot = convert.apparentToAbsoluteMagnitude(float(line.split()[1]),dist_Mpc)
+													
+					fitResultsFile.close()
+					
+				except:
+					print 'There was no file named', fitResultsFileName,'.'
+	
+				collection.append(log_r_e)
+				collection.append(mu_e)
+				collection.append(log_n)
+				collection.append(mag_sph)
+				collection.append(mag_tot)
+	
+	return collection
+	
+	
+def process_all_1D():
+	connection = sql3.connect(dbname)
+	cur = connection.cursor()
+	
+	try:
[…]

### 2015-02-10 python_codes/decomposition/ProFitErole1.0.1/collect1DFitResults.py

@@ -1,0 +1,79 @@
+import numpy as np
+import sys
+from scipy.special import gamma
+import os.path
+
+directoriesFileName = '/Users/gsavorgnan/Dropbox/giulia_e_basta/1DfitsReload/directories.list'
+
+directoriesFile = open(directoriesFileName)
+
+directoriesList = []
+
+for line in directoriesFile:
+	if (line[0] != '#'):
+		directoriesList.append(line.split()[0])
+
+directoriesFile.close()
+
+axisList = ['maj', 'eq']
+psfsList = ['gaussian', 'moffat']
+#scalesList = ['logscale', 'linscale1px', 'linscale05px']
+scalesList = ['comb', 'log']
+
+fitResultsFile = open('/Users/gsavorgnan/Dropbox/giulia_e_basta/1DfitsReload/1DfitsReloadResults.dat', 'w')
+
+sys.stdout = fitResultsFile
+
+print '#', 'galaxy', 
+for axis in axisList:
+	for psf in psfsList:    
+		for scale in scalesList:
+			print 're_' + axis + '_' + psf + '_' + scale,
+			print 'mue_' + axis + '_' + psf + '_' + scale,
+			print 'n_' + axis + '_' + psf + '_' + scale,
+			print 'msph_' + axis + '_' + psf + '_' + scale,
+			print 'mtot_' + axis + '_' + psf + '_' + scale,          
+print 
+
+
+for directory in directoriesList:
+
+	print directory,
+	
+	for axis in axisList:
+							
+		for psf in psfsList:
+			
+			for scale in scalesList:
+					
+				outputFileName = '/Users/gsavorgnan/Dropbox/giulia_e_basta/1DfitsReload/' + directory + '/' + directory + '_' + axis + '_' + psf + '_' + scale + '_par_SM.dat'
+				
+				r_e = '""'
+				mu_e = '""'
+				n = '""'
+				b = '""'
+				mag_sph = '""'
+				mag_tot = '""'
+
+				try:
+					outputFile = open(outputFileName)
+					lines = outputFile.readlines()
+					for line in lines:
+						if (line.split()[0] == '1') and (line.split()[1] == 'sersic'):
+							r_e = float(line.split()[2])
+							mu_e = float(line.split()[3])
+							n = float(line.split()[4])
+							mag_sph = float(line.split()[6])
+						if (line.split()[0] == 'Total_galaxy_magnitude'):
+							mag_tot = float(line.split()[1])
+													
[…]

### 2015-02-10 python_codes/decomposition/ProFitErole1.0.1/convolution/psfConvolution.py

@@ -1,0 +1,18 @@
+from convolution import filters
+
+######## PERFORM CONVOLUTION WITH GAUSS O moffat ###
+
+def doPsfConvolution(y_component, psfFunction, x):
+
+	if (psfFunction.name == 'gaussian'):
+		sigma = psfFunction.gaussianFWHM/2.3548
+		#y_component_convolved = filters.gaussFilter(y_component, sigma, filterLength=20, order=0, mode='reflect')
+		y_component_convolved = filters.gaussFilter(x, y_component, sigma)
+		#y_component_convolved = filters.halfGaussFilter(y_component, sigma, filterLength=40, order=0, mode='reflect')
+	elif (psfFunction.name == 'moffat'):
+		alpha = psfFunction.moffatAlpha
+		beta = psfFunction.moffatBeta
+		#y_component_convolved = filters.moffatFilter(y_component, alpha, beta, filterLength=20, mode='reflect')
+		y_component_convolved = filters.moffatFilter(x, y_component, alpha, beta)
+	return y_component_convolved	
+	      

### 2015-02-10 python_codes/decomposition/ProFitErole1.0.1/modelComponents/ferrer.py

@@ -1,0 +1,27 @@
+from convolution.psfConvolution import doPsfConvolution
+import numpy as np
+from scipy import special #.hyp2f1
+
+def buildFerrer(x, params, component, psfFunction, convolve, zeropoint):
+
+	namepar1 = 'par1_' + str(component.number) # r_out
+	namepar2 = 'par2_' + str(component.number) # mu_0
+	namepar3 = 'par3_' + str(component.number) # alpha
+	namepar4 = 'par4_' + str(component.number) # beta
+	
+	x_i = x[x<params[namepar1].value]
+	x_e = x[x>=params[namepar1].value]
+	
+	y_ferrer_i = 10**(zeropoint/2.5) * (10**(-params[namepar2].value/2.5)) * ( 1 - (x_i/params[namepar1].value)**(2 - (params[namepar4].value)) )**(params[namepar3].value)
+	y_ferrer_e = x_e * 0.0
+	y_ferrer = np.concatenate((y_ferrer_i, y_ferrer_e))
+			
+	if (convolve):
+		y_ferrer = doPsfConvolution(y_ferrer, psfFunction, x)
+	return y_ferrer
+
+def computeFerrerParameters(r_out, mu_0, alpha, beta):
+	
+	m_tot = mu_0 - 2.5 * np.log10(2 * np.pi * r_out**2 * (0.5 * special.hyp2f1(-alpha, 2/(2-beta), (2-beta+2)/(2-beta), 1)))
+	
+	return m_tot

### 2015-02-10 python_codes/decomposition/ProFitErole1.0.1/modelComponents/psf.py

@@ -1,0 +1,16 @@
+import numpy as np
+
+def buildPsf(x, params, component, psfFunction, zeropoint):
+
+	if (psfFunction.name == 'gaussian'):
+		namepar2 = 'par2_' + str(component.number) # mu_0
+		fwhm = psfFunction.gaussianFWHM
+		y_psf = 10**(zeropoint/2.5) * (10**(-params[namepar2].value/2.5) * np.exp(-x**2/(2*(fwhm/2.3548)**2)))
+	elif (psfFunction.name == 'moffat'):
+		namepar2 = 'par2_' + str(component.number) # mu_0
+		alpha = psfFunction.moffatAlpha
+		beta = psfFunction.moffatBeta
+		y_psf = 10**(zeropoint/2.5) * (10**(-params[namepar2].value/2.5) * (1 + (x/alpha)**2)**(-beta))
+	
+	return y_psf	
+

### 2015-02-10 python_codes/decomposition/ProFitErole1.0.1/results/initialize1DFitResultsTable.py

@@ -1,0 +1,49 @@
+import numpy as np
+import sys
+from scipy.special import gamma
+import os.path
+
+directoriesFileName = '/Users/gsavorgnan/Dropbox/giulia_e_basta/ProFitErole1.0.1/results/directories.list'
+
+directoriesFile = open(directoriesFileName)
+      
+directoriesList = []
+
+for line in directoriesFile:
+        if (line[0] != '#'):
+                directoriesList.append(line.split()[0])
+
+directoriesFile.close()
+
+axisList = ['Rmaj', 'Req']
+psfsList = ['gaussian', 'moffat']
+scalesList = ['combscale', 'logscale']
+
+fitResultsFile = open('/Users/gsavorgnan/Dropbox/giulia_e_basta/ProFitErole1.0.1/results/1DfitResults.dat', 'w')
+
+sys.stdout = fitResultsFile
+
+print '#', 'galaxy', 
+for axis in axisList:
+        for psf in psfsList:    
+                for scale in scalesList:
+                        print 're_sph_' + axis + '_' + psf + '_' + scale,
+                        print 'mue_sph_' + axis + '_' + psf + '_' + scale,
+                        print 'n_sph_' + axis + '_' + psf + '_' + scale,
+                        print 'b_sph_' + axis + '_' + psf + '_' + scale,
+                        print 'mtot_sph_' + axis + '_' + psf + '_' + scale,
+			print 'h_disc_' + axis + '_' + psf + '_' + scale,
+                        print 'mu0_disc_' + axis + '_' + psf + '_' + scale,
+                        print 'mtot_disc_' + axis + '_' + psf + '_' + scale,
+			print 'Delta_' + axis + '_' + psf + '_' + scale,
+print			
+
+for directory in directoriesList:
+	print directory,
+	for axis in axisList:
+		for psf in psfsList:
+			for scale in scalesList:
+				print '-99  -99  -99  -99  -99  -99  -99  -99  -99 ',
+	print
+	
+        

### 2015-02-10 python_codes/errors/comparison/comparison_sigmaclip.py

@@ -1,0 +1,107 @@
+import sqlite3 as sql3
+import os
+import numpy as np
+
+from instruments import exclusion
+
+dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_vivisection.db'
+
+workslist = ['GrahamDriver2007', 'Laurikainenetal2010', 'Sanietal2011', 'Vikaetal2012',
+	'Beifiorietal2012', 'Ruslietal2013', 'Laskeretal2014']
+	
+parameterslist = ['log_n', 'log_r_e', 'mag_sph']
+threshold_dict = {'log_n' : np.log10(1.5), 'log_r_e' : np.log10(1.66), 'mag_sph' : np.log10(2.)}	
+
+def main():
+	connection = sql3.connect(dbname)
+	cur = connection.cursor()
+	
+	try:
+		cur.execute('DROP TABLE ErrorsComparisonSigmaClip')
+		print 'Table ErrorsComparisonSigmaClip has been erased.'
+	except:
+		print 'Table ErrorsComparisonSigmaClip does not exist.'
+	
+	
+	create_table_string = 'CREATE TABLE ErrorsComparisonSigmaClip (gal_id text, '
+	for parameter in parameterslist:
+		 create_table_string += (parameter + '_median real, ')
+		 create_table_string += (parameter + '_std real, ') 
+		 create_table_string += (parameter + '_num_measurements integer, ')
+	create_table_string = create_table_string[:-2]
+	create_table_string += ')'
+	cur.execute(create_table_string)
+	
+	query = 'select gal_id from OneDFitResultsPhysicalUnits;'
+	cur.execute(query)
+	galaxieslist = cur.fetchall()
+		
+	for gal_id in galaxieslist:
+		collection = []
+		collection.append(gal_id[0])
+		for parameter in parameterslist:
+			measurementslist = getMeasurements(cur, parameter, gal_id[0])
+			#print measurementslist
+			threshold = threshold_dict[parameter]
+			median, stdev, num_measurements = computeStatistics(measurementslist, threshold)
+			
+			collection.append(median)
+			collection.append(stdev)
+			collection.append(num_measurements)
+			
+		question_marks = ''
+		for i in range(len(collection)-1):
+			question_marks += '?,'#
+		question_marks += '?'	
+		
+		#print 'INSERT INTO ErrorsComparisonSigmaClip VALUES (' + question_marks + ')', collection
[…]

### 2015-02-10 python_codes/errors/errors.sh

@@ -1,0 +1,7 @@
+python /Users/gsavorgnan/galaxy_vivisection/python_codes/errors/comparison/comparison.py
+#python /Users/gsavorgnan/galaxy_vivisection/python_codes/errors/comparison/comparison_sigmaclip.py
+python /Users/gsavorgnan/galaxy_vivisection/python_codes/plots/comparison_r_e/comparison.py
+python /Users/gsavorgnan/galaxy_vivisection/python_codes/plots/comparison_n/comparison.py
+python /Users/gsavorgnan/galaxy_vivisection/python_codes/plots/comparison_mu_e/comparison.py
+python /Users/gsavorgnan/galaxy_vivisection/python_codes/plots/comparison_mag_sph/comparison.py
+python /Users/gsavorgnan/galaxy_vivisection/python_codes/errors/vote/vote.py

### 2015-02-10 python_codes/instruments/linear_regression/bces.py

@@ -1,0 +1,325 @@
+import numpy,scipy
+import scipy.stats
+
+
+
+
+# BCES fitting
+# ===============
+
+def bces(y1,y1err,y2,y2err,cerr):
+	"""
+Does the entire regression calculation for 4 slopes:
+OLS(Y|X), OLS(X|Y), bisector, orthogonal.
+Fitting form: Y=AX+B.
+
+Usage:
+
+>>> a,b,aerr,berr,covab=bces(x,xerr,y,yerr,cov)
+
+Output:
+
+- a,b : best-fit parameters a,b of the linear regression 
+- aerr,berr : the standard deviations in a,b
+- covab : the covariance between a and b (e.g. for plotting confidence bands)
+
+Arguments:
+
+- x,y : data
+- xerr,yerr: measurement errors affecting x and y
+- cov : covariance between the measurement errors
+(all are arrays)
+
+v1 Mar 2012: ported from bces_regress.f. Added covariance output.
+Rodrigo Nemmen, http://goo.gl/8S1Oo
+	"""
+	# Arrays holding the code main results for each method:
+	# Elements: 0-Y|X, 1-X|Y, 2-bisector, 3-orthogonal
+	a,b,avar,bvar,covarxiz,covar_ba=numpy.zeros(4),numpy.zeros(4),numpy.zeros(4),numpy.zeros(4),numpy.zeros(4),numpy.zeros(4)
+	# Lists holding the xi and zeta arrays for each method above
+	xi,zeta=[],[]
+	
+	# Calculate sigma's for datapoints using length of conf. intervals
+	sig11var = numpy.mean( y1err**2 )
+	sig22var = numpy.mean( y2err**2 )
+	sig12var = numpy.mean( cerr )
+	
+	# Covariance of Y1 (X) and Y2 (Y)
+	covar_y1y2 = numpy.mean( (y1-y1.mean())*(y2-y2.mean()) )
+
+	# Compute the regression slopes
+	a[0] = (covar_y1y2 - sig12var)/(y1.var() - sig11var)	# Y|X
+	a[1] = (y2.var() - sig22var)/(covar_y1y2 - sig12var)	# X|Y
+	a[2] = ( a[0]*a[1] - 1.0 + numpy.sqrt((1.0 + a[0]**2)*(1.0 + a[1]**2)) ) / (a[0]+a[1])	# bisector
+	if covar_y1y2<0:
[…]

### 2015-02-10 python_codes/instruments/linear_regression/test.py

@@ -1,0 +1,26 @@
+import numpy as np
+import fitexy
+
+#data = open('test.dat')
+data = open('Savorgnan_2014.dat')
+
+xlist = []
+sigxlist = []
+ylist = []
+sigylist = []
+
+for line in data:
+	if line[0] != '#':
+		xlist.append(float(line.split()[0]))
+		sigxlist.append(float(line.split()[1]))	
+		ylist.append(float(line.split()[2]))
+		sigylist.append(float(line.split()[3]))	
+	
+
+x = np.asarray(xlist)
+sigx = np.asarray(sigxlist)
+y = np.asarray(ylist)
+sigy = np.asarray(sigylist)
+
+fitexy.modfitexy(x,sigx,y,sigy,2.,8.,0.,4.,0.0)
+#fitexy.modfitexy(x,sigx,y,sigy,5.,9.,1,10.,0.0)

### 2015-02-10 python_codes/plots/comparison_n/comparison.py

@@ -1,0 +1,127 @@
+import sqlite3 as sql3
+import matplotlib.pyplot as plt
+import matplotlib
+import numpy as np
+import matplotlib.mlab as mlab
+
+from errors.comparison import comparison
+
+from matplotlib import rc
+rc('font',**{'family':'sans-serif','sans-serif':['CenturyGothic']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+rc('text', usetex=True)
+
+matplotlib.rcParams.update({'font.size': 22})
+
+colordict = ['black', 'red', 'blue', 'lightgreen', 'yellow', 'gray', 'white', 'orange']
+
+path_comp_plots = '/Users/gsavorgnan/galaxy_vivisection/results/plots/comparison_n/'
+path_paper_images = '/Users/gsavorgnan/galaxy_vivisection/papers/data_paper/images/'
+
+dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_vivisection.db'
+
+n_grade1 = 27.
+n_grade2 = 29.
+n_grade3 = 10.
+n_tot = 72.
+f_grade1 = n_grade1/n_tot
+f_grade2 = (n_grade1+n_grade2)/n_tot
+f_grade3 = (n_grade1+n_grade2+n_grade3)/n_tot
+#print f_grade1,f_grade2,f_grade3
+
+def comparison_log_n():
+	
+	connection = sql3.connect(dbname)
+	cur = connection.cursor()
+	
+	query = 'select gal_id from OneDFitResults;'
+	cur.execute(query)
+	galaxieslist = cur.fetchall()
+	
+	fig, (ax1, ax2) = plt.subplots(2, sharex=True)
+
+	diff_list = []
+	diff_my_list = []
+	for gal_id in galaxieslist:
+		if gal_id[0] is not None:
+			measurementslist_log_n = comparison.getMeasurements_log_n(cur, gal_id[0])
+			average_log_n, stdev_log_n, num_measurements_log_n = comparison.computeStatistics(measurementslist_log_n)
+			
+			if num_measurements_log_n>1:
+				diff_my = measurementslist_log_n[0] - average_log_n
+				diff_my_list.append(diff_my)
+			
[…]

### 2015-02-10 python_codes/plots/scaling_relations/relations.py

@@ -1,0 +1,525 @@
+import sqlite3 as sql3
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+from scipy import stats
+from instruments.linear_regression import bces
+from instruments.linear_regression import predband
+from instruments import b_n
+
+from matplotlib import rc
+rc('font',**{'family':'sans-serif','sans-serif':['CenturyGothic']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+rc('text', usetex=True)
+
+
+matplotlib.rcParams.update({'font.size': 22})
+
+dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_vivisection.db'
+
+path_auxiliary_plots = '/Users/gsavorgnan/galaxy_vivisection/results/plots/auxiliary/'
+path_scalrel_plots = '/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/'
+
+
+def mag_sph_vs_logn(axis):
+        connection = sql3.connect(dbname)
+        cur = connection.cursor()
+       
+        getdata_query = 'SELECT anc.gal_id, anc.ELLIPTICAL_my, \
+		pysres.mag_sph_eq_moffat_comb, pysres.log_n_' + axis + '_moffat_comb, \
+		errV.perr_mag_sph, errV.merr_mag_sph, errV.perr_log_n, errV.merr_log_n \
+        	FROM Ancillary AS anc \
+        	JOIN OneDFitResultsPhysicalUnits AS pysres ON anc.gal_id = pysres.gal_id \
+		JOIN ErrorsVote as errV ON anc.gal_id = errV.gal_id \
+        	WHERE anc.fit1D_done = 1;'
+       
+        cur.execute(getdata_query)
+        datalist = cur.fetchall()
+        data= np.asarray(datalist).transpose()
+        #print data
+        ELL = data[1].astype(np.int)
+        mag_sph = data[2].astype(np.float)
+        log_n = data[3].astype(np.float)
+	perr_mag_sph = data[4].astype(np.float)
[…]

### 2015-02-10 python_codes/run_codes.sh

@@ -1,0 +1,2 @@
+sh /Users/gsavorgnan/galaxy_vivisection/python_codes/databases/databases.sh
+sh /Users/gsavorgnan/galaxy_vivisection/python_codes/errors/errors.sh

### 2015-02-10 python_codes/tex_tables/tex_tables.py

@@ -1,0 +1,420 @@
+import sqlite3 as sql3
+import os
+import sys
+import numpy as np
+
+terminal = sys.stdout
+dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_vivisection.db'
+sampletableFileName = '/Users/gsavorgnan/galaxy_vivisection/papers/data_paper/table_sample.tex'
+fitresultstableFileName = '/Users/gsavorgnan/galaxy_vivisection/papers/data_paper/table_fitresults.tex'
+
+def putBlankInPlaceOfNone(entry):
+        if entry is None:
+                entry = ' '
+        return entry  
+	
+def header_datapaper_sampletable(caption):
+
+        print '\\begin{table*}                                        '
+        print '\\small                                                '
+        print '\\begin{center}                                        '
+	if caption:
+        	print '\\caption{{\\bf Galaxy sample.}                        '
+        	print '\\emph{Column (1):} Galaxy name.                       '
+        	print '\\emph{Column (2):} Distance.                                   '
+        	print '\\emph{Column (3):} Black hole mass.                                   '
+       		print '\\emph{Column (4):} Reference of the black hole mass reported here \
+			(G+03 = \citealt{greenhill2003}, GS13 = \citealt{grahamscott2013}; R+13b = \citealt{rusli2013bhmassesDM}).                                   '
+        	print '\\emph{Column (5):} Presence of a partially depleted core. \
+			The question mark is used when the classification has come from the velocity dispersion criteria mentioned in Section \\ref{sec:corser}. \
+			The value of the core break radius is reported in parenthesis when available.  '
+        	print '\\emph{Column (6):} Reference of the identification of a partially depleted core \
+			(G+94 = \citealt{grillmair1994}; \
+			F+97 = \citealt{forbes1997}; \
+			Q+00 = \citealt{quillen2000}, \
+			T+04 = \citealt{trujillo2004coresersicmodel}; \
+			F+06 = \citealt{ferrarese2006acsvcs}; \
+			J+11 = \citealt{jardel2011}; \
+			R+11 = \citealt{richings2011}; \
+			R+13a = \citealt{rusli2013}).  '
+		print '\\emph{Column (7):} Kinematical classification (fast/slow rotator).'
+		print '\\emph{Column (8):} Availability of velocity map (A = ATLAS$^{\\rm 3D}$, S = SLUGGS). '
[…]

### 2015-02-10 scripts/initialize/copy_masks.sh

@@ -1,0 +1,109 @@
+cp /Users/gsavorgnan/Dropbox/giulia_e_basta/SPITZER/galfit/circinus/circinus_op_overmos_edgestarmask_extra2.fits                  /Users/gsavorgnan/galaxy_vivisection/data/galaxies/circinus/    
+cp /Users/gsavorgnan/Dropbox/giulia_e_basta/SPITZER/galfit/ic1459/ic1459_op_mos_edgestarmask_extra.fits 			  /Users/gsavorgnan/galaxy_vivisection/data/galaxies/ic1459/	  
+cp /Users/gsavorgnan/Dropbox/giulia_e_basta/SPITZER/galfit/ic1459/ic1459_op_mos_edgestarmask_extra_core.fits			  /Users/gsavorgnan/galaxy_vivisection/data/galaxies/ic1459/	  
+cp /Users/gsavorgnan/Dropbox/giulia_e_basta/SPITZER/galfit/ic2560/ic2560_op_overmos_edgestarmask_extra3.fits			  /Users/gsavorgnan/galaxy_vivisection/data/galaxies/ic2560/	  
+cp /Users/gsavorgnan/Dropbox/giulia_e_basta/SPITZER/galfit/ic4296/ic4296_op_mos_edgestarmask_extra.fits 			  /Users/gsavorgnan/galaxy_vivisection/data/galaxies/ic4296/	  
+cp /Users/gsavorgnan/Dropbox/giulia_e_basta/SPITZER/galfit/ic4296/ic4296_op_mos_edgestarmask_extra_core.fits			  /Users/gsavorgnan/galaxy_vivisection/data/galaxies/ic4296/	  
+cp /Users/gsavorgnan/Dropbox/giulia_e_basta/SPITZER/galfit/m104/m104_op_overmos_edgestarmask_extra.fits 			  /Users/gsavorgnan/galaxy_vivisection/data/galaxies/m104/	  
+cp /Users/gsavorgnan/Dropbox/giulia_e_basta/SPITZER/galfit/m105/m105_op_mos_edgestarmask_extra.fits				  /Users/gsavorgnan/galaxy_vivisection/data/galaxies/m105/	  
+cp /Users/gsavorgnan/Dropbox/giulia_e_basta/SPITZER/galfit/m106/m106_op_overmos_edgestarmask_extra2.fits			  /Users/gsavorgnan/galaxy_vivisection/data/galaxies/m106/	  
[…]

### 2015-02-15 papers/data_paper/datapaper.tex
monday

@@
 indicating the non-gravitational origin of these correlations 
-(e.g.~\citealt{dressler1989,yee1992,kormendyrichstone1995,magorrian1998,ferraresemerritt2000,gebhardt2000,graham2001,
-marconihunt2003,haringrix2004,graham2012bent}). {\bf AL: need to talk to you about Laor's work}\\
-The tightness (or small scatter) of the observed black hole mass correlations has led to the idea
+(e.g.~\citealt{dressler1989,yee1992,kormendyrichstone1995,laor1997,magorrian1998,ferraresemerritt2000,gebhardt2000,graham2001,
+marconihunt2003,haringrix2004,graham2012bent,grahamscott2015}). \\
+The tightness of (i.e.~the small scatter about) the observed black hole mass correlations has led to the idea
 that black holes and host galaxies have coevolved with some sort of self-regulated growth.
 Exploring the evolution of this growth with cosmic time could help identify
-the driving mechanisms of the black hole - galaxy coevolution.
+the driving mechanisms of the black hole -- galaxy coevolution.
 Observations at $z=0$ set the local benchmark from which to measure this evolution.
@@
 Modern hydrodynamical simulations, such as EAGLE \citep{schaye2015}, calibrate the feedback efficiencies 
-to the $z=0$ black hole mass - galaxy mass relation.
-Scaling relations can also be employed to predict the masses of black holes in other galaxies, where a direct
+to match the $z=0$ black hole mass -- galaxy mass relation.
+Such scaling relations can also be employed to predict the masses of black holes in other galaxies, where a direct
 measure of $M_{\rm BH}$ would be extremely time consuming or simply impossible due to technological limitations.
-Many accurate $M_{\rm BH}$ predictions would help derive 
+Moreover, many accurate $M_{\rm BH}$ predictions enable one to derive 
 the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction}) 
-and space density (\citealt{grahamdriver2007smbhmassdensity} and references therein; \citealt{comastri2015}). \\
-Since the first stellar dynamical detections of black holes were carried out in the '80s 
-(see the references in the reviews by \citealt{kormendyrichstone1995} and \citealt{richstone1998}), 
+and space density (e.g.~\citealt{grahamdriver2007smbhmassdensity,comastri2015}). 
+All of these examples depend on the $z=0$ relations, 
+and as such the recalibration of the black hole mass -- bulge stellar mass ratio ($M_{\rm BH}/M_{\rm *,sph}$) in large bulges,
+from $0.1 - 0.2\%$ (e.g.~\citealt{haringrix2004}) to $0.36\%$ \citep{graham2012bent} and then $0.49\%$ \citep{grahamscott2015}, 
+has many substantial implications. \\
+Since the early stellar dynamical detections of black holes were carried out in the '80s 
+(see the references in the reviews by \citealt{kormendyrichstone1995}, \citealt{richstone1998} 
+and \citealt{graham2015bulges} for pioneering papers), 
 the number of (direct) black hole mass measurements has increased with time 
-and it has recently become a statistically meaningful sample -- of the order of 100 objects -- 
+and it has recently become a statistically meaningful sample  
 with which one can study SMBH demographics. 
@@
 Massive, early-type galaxies are often composite systems. 
-The knowledge that many elliptical galaxies contain embedded stellar disks can be dated back to 
-at least three decades ago 
+The knowledge that many ``elliptical'' galaxies actually contain embedded stellar disks dates back  
+at least three decades  
 \citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995}. 
-After examining long-slit spectroscopic observations of morphologically classified elliptical galaxies in the Fornax cluster, 
-\cite{donofrio1995} and \cite{graham1998fornax} concluded that only $\sim$$1/3$ of their galaxies do not harbour any disk-like component.
-Surveys with integral field spectrographs of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
-have further changed our idea of ``elliptical'' galaxies, 
-being all but simple and featureless pressure-supported systems.
+After examining long-slit and integral field unit spectroscopic observations of morphologically classified elliptical galaxies in the Fornax cluster, 
+\cite{donofrio1995}, \cite{graham1998fornax} and \cite{scott2014} concluded that only 3 bright galaxies do not harbour a disk-like component.
+Larger surveys with integral field spectrographs of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
+have further advanced this view of ``elliptical'' galaxies being all but simple and featureless pressure-supported systems.
 More than half of all morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.
-\cite{krajnovic2013} showed that ``fast rotators'' as a class are simply disks or at least disk-like objects. 
+\cite{krajnovic2013} showed that ``fast rotators'' as a class are disk-galaxies or at least disk-like galaxies. 
 In their magnitude-limited survey, systems 
@@
 dominate only the most massive end (beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
-Given the prevalence of disks, it is important to perform bulge/disk decompositions, 
-if one is to properly explore the black hole-bulge connection. \\
+Given the prevalence of disks, it is clearly important to perform bulge/disk decompositions, 
+if one is to properly explore the black hole-bulge connection. 
+Indeed, separating the disk light from that of the bulge has led to the discovery of the missing population of compact, massive spheroids 
+in the local Universe {\bf (Graham, Dullo, Savorgnan 2015)}.
+If we are to properly understand the evolution of galaxies, we need to understand their components.\\
 Measuring the photometric and structural properties of a galaxy's spheroidal component requires the ability to 
 separate it from the rest of the galaxy. 
-Galaxy decomposition is a parametric analysis that allows one to fit the surface brightness distribution
+Such galaxy decomposition involves a parametric analysis that allows one to fit the surface brightness distribution
 of galaxies using a combination of analytic functions (usually one function per
@@
 brightness radial profile and modeling it with a combination of analytic functions.
-With the two-dimensional (2D) technique one fits analytic functions directly to digital images. \\
+With the two-dimensional (2D) technique, one fits analytic functions directly to the 2D images. \\
 Over the past eight years, five independent studies 
@@
 in order to derive the bulge parameters and explore their relation with the black hole masses. 
-Interestingly, the past studies all %investigated the black hole mass scaling relations using 
-used almost the same sample of galaxies, 
-but they claimed some contradictory conclusions.
-One study \citep{grahamdriver2007} obtained a good $M_{\rm BH}-n_{\rm sph}$ correlation
-(the bulge S\'ersic index $n_{\rm sph}$ is a measure of the central radial concentration of stars), 
+{\bf Rusli has explored the black hole - core relation.}
+Interestingly, the past studies used almost the same sample of galaxies, yet they claimed some contradictory conclusions.
+For example, one study \citep{grahamdriver2007} obtained a good $M_{\rm BH}-n_{\rm sph}$ correlation
+(the bulge S\'ersic index $n_{\rm sph}$ is a measure of the central radial concentration of stars, \citealt{trujillo2001}), 
 whereas the remaining four did not.
-\cite{lasker2014anal} declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity and the bulge luminosity, 
+In addition, \cite{lasker2014anal} {\bf who did not work at 3.6um} 
+declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity and the bulge luminosity, 
 as opposed to \cite{beifiori2012}, who claimed that the bulge mass is a better tracer of $M_{\rm BH}$ than the galaxy mass.
@@
 which is an excellent proxy for the stellar mass, superior to the $K$-band (\citealt{sheth2010} and references therein).
-We will use these to obtain improved black hole mass scaling relations using the largest to date sample of 72 galaxies.
+We will use these in a series of forthcoming papers to obtain improved black hole mass scaling relations 
+using the largest sample (66) of galaxies to date.
 
 This paper is structured as follows.
-Section \ref{sec:data} presents the data-set used to conduct this study. 
+Section \ref{sec:data} presents the galaxy sample and imaging data-set used to conduct this study. 
 Section \ref{sec:anal} describes how we performed the galaxy decompositions, 
 i.e.~how we identified and modeled the sub-components that constitute our galaxies. 
-In Section \ref{sec:res} we outline the results from our analysis 
-and we discuss the error analysis. 
+In Section \ref{sec:res} we outline the results from our analysis and discuss the error analysis. 
 Section \ref{sec:concl} summarizes our main conclusions. 
@@
 Our initial galaxy sample (see Table \ref{tab:sample}) consists of 75 objects for which a dynamical detection of the black hole mass 
-has been reported in the literature and for which at least one $3.6~\rm \mu m$ \emph{Spitzer}/IRAC observation was made publicy 
-available at the time we began our investigation (2013).
+had been reported in the literature at the time we started this project, 
+and for which at least one $3.6~\rm \mu m$ \emph{Spitzer}/IRAC\footnote{IRAC is the InfraRed Array Camera onboard the \emph{Spitzer} Space Telescope.} 
+observation was publicy available.
 Black hole masses were drawn from the catalog of \citet{grahamscott2013} for 70 galaxies,
-from \citet{rusli2013bhmassesDM} for 4 galaxies 
-and from \citet{greenhill2003} for 1 galaxy.
+from \citet{rusli2013bhmassesDM} for 4 galaxies and from \citet{greenhill2003} for 1 galaxy. 
+As explained in Section \ref{sec:res}, 
+this initial sample was ultimately reduced to 66 galaxies for which useful bulge parameters could be obtained.
 
@@
 The data frames were selected to be %``enhanced Level 1 products'', or
-corrected Basic Calibrated Data (cBCD).
-Basic Calibrated Data (BCD) are produced by the IRAC Level 1 pipeline. 
+corrected Basic Calibrated Data (cBCD), produced by the IRAC Level 1 pipeline. 
 This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
@@
 Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
-It looks like a decaying trail of pixels, repeating every fourth column.
-Column pulldown is caused by a bright pixel that triggers a bias shift within its respective column, 
+It appears as a decaying trail of pixels, repeating every fourth column.
+``Column pulldown'' is caused by a bright pixel that triggers a bias shift within its respective column, 
 creating a lower background value throughout the entire column than in the surrounding columns.}.
@@
 
-\subsubsection{Mosaicing}
-We performed image mosaicing using the %(command line version of the) 
-MOPEX package \citep{makovozmarleau2005mopex}.
+\subsubsection{Mosaicking}
+We performed image mosaicking using the MOPEX package \citep{makovozmarleau2005mopex}.
+This enabled the production of suitably wide-field-of-view images for accurate sky background subtraction.
 Individual cBCD frames with exposure time of $1~\rm sec$ were rejected.
@@
 we merged the different pmasks. 
-Outlier rejection was performed with the dual outlier and multi-frame techniques.
+Cosmic ray rejection was performed with the dual outlier and multi-frame techniques.
 The pixel size of the mosaic was set to be the same as the input cBCD frames ($1''.22 \times 1''.22$).
@@
 \includegraphics[width=0.49\columnwidth]{images/m49overlap.eps}
-\caption{An example of the \emph{overlap} correction. 
+\caption{Example of the \emph{overlap} correction. 
 The image mosaic of the galaxy M49 was obtained by co-adding frames coming from 8 different AORs.
@@
 \subsubsection{Additional aestethic corrections}
+\label{sec:aesth}
 The image mosaics of 4 galaxies (NGC 0821, NGC 2974, NGC 4291, NGC 4459) were found to be affected 
@@
 \includegraphics[width=0.49\columnwidth]{images/n4459nobrightstar.eps}
-\caption{An example of aestethic correction.
-The images show the mosaic of the galaxy NGC 4459 before (left) and after (right) the removal 
+\caption{Example of aestethic correction.
+The images show the mosaic of the galaxy NGC 4459 before (left) and after (right) the partial removal 
 of a bright saturated star.}
@@
 First, we created an initial mask using the IRAF task 
-{\tt objmasks}, %\footnote{{\tt objmasks} is part of the {\tt noao.nproto} package.},
-that identifies objects by threshold sigma detection.
+{\tt objmasks} that identifies objects by threshold sigma detection.
 Then, we refined each mask by hand, using the software 
@@
 We identified and carefully masked not only contaminating sources located in the field of the image mosaic,
-but also objects overlapping with the target galaxy, such as foreground stars, globular clusters or red giant stars.
+but also objects overlapping with the target galaxy, such as foreground stars, background galaxies, 
+globular clusters or red giant stars.
 
 \subsubsection{1D PSF}
-The one-dimensional Point Spread Function was charachterized using the IRAF task {\tt imexamine}.
+A universal, average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
 A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
@@
 \subsubsection{2D PSF}
-The IRAC support team provides the users with a two-dimensional instrument Point Response Function (PRF) at $3.6~\rm \mu m$.
-However, we found this PRF to be inadequate for the purposes of our analysis.
+The IRAC support team provides users with a two-dimensional instrument Point Response Function (PRF) at $3.6~\rm \mu m$.
+However, while this helped remove the extended wings of saturated stars (see Section \ref{sec:aesth}), 
+we found this PRF to be inadequate for the purposes of our modelling.
 In fact, the $FWHM$ of the IRAC instrument PRF ($\sim 1''.8$), as measured by the IRAF task {\tt imexamine}, 
@@
 \caption{Normalized flux versus radial distance 
-from the image centroid of an observed point source (top panel) 
-and of the IRAC instrument PRF (bottom panel). 
+from the image centroid of an observed point source (bottom panel) 
+and of the IRAC instrument Point Response Function (PRF, top panel). 
 The normalized flux is given in arbitrary units, 
@@
 This classification (Table \ref{tab:sample}, column 7) 
-concerns the kinematic properties of galaxies within the instrument field-of-view, % (typically up to one effective radius),
+concerns the kinematic properties of galaxies within the spectroscopic instrument's field-of-view, 
 but does not contain additional information -- crucial for our analysis -- about kinematic substructures, 
@@
 This means that if a galaxy hosts an optical AGN \emph{and} a certain amount of nuclear dust,
-we expected to detect some non-stellar nuclear emission at $3.6~\rm \mu m$.
+we may detect some non-stellar nuclear emission at $3.6~\rm \mu m$.
 It is therefore important to identify which of our galaxies have both an optical AGN and circumnuclear dust.
@@
 for the individual galaxies and their associated literature.
-Unsurprisingly, dusty AGNs were more frequently found in late-type spiral galaxies.
+Unsurprisingly, dusty AGNs were more frequently found in late-type spiral galaxies, 
+and modelled by us with either a point source or a PSF-convolved Gaussian.
 
@@
 i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
+Such deficits were first noted and researched by \cite{kingminkowski1966}.
 S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
-Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs.
+Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs
+\citep{dullograham2013cores,rusli2013}.
 The majority are thus unresolved in our image mosaics. 
-We masked these unresolved cores by excluding the surface brightness profile 
+We masked these unresolved cores (identified in high-resolution images, see Table \ref{tab:sample}) by excluding the surface brightness profile 
 within 3 PSF's $FWHM$ from the galaxy center.
@@
 or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
-This resulted in us assigning cores to just 2 galaxies when using this alternative method 
-if no high resolution image was available.
+This resulted in us assigning cores to just 2 galaxies using this alternative method when 
+no high resolution image was available.
 
@@
 ($B4$) parameterizes the diskyness ($B4>0$) or boxyness ($B4<0$) of the isophotes.} ($B4$) were allowed to vary with radius.
-The step in semi-major axis length between successive ellipses was set to increase linearly, 
-and then geometrically in our second run\footnote{In case of linear steps, 
+The step in semi-major axis length between successive ellipses was first set to increase linearly, 
+and then geometrically in our second run\footnote{In the case of linear steps, 
 the semi-major axis length for the next ellipse was calculated by adding $1$ pixel to the current length.
-In case of geometric steps, the semi-major axis length for the next ellipse 
+In the case of geometric steps, the semi-major axis length for the next ellipse 
 was calculated as $1.1$ times the current length.}.
@@
 surface brightness profile along the major-axis. 
-Major-axis surface brightness profiles were then projected along the equivalent-axis,
+Major-axis surface brightness profiles were additionally converted into the equivalent-axis,
 i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$), 
-also called the circularized radius.
-Isophotes corresponding to an intensity less than $3 \times RMS_{\rm sky}$ were rejected.
+equivalent to the circularized radius.
+This resulted in 4 profiles per galaxy.
+Isophotes corresponding to an intensity less than 
+three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$) were ignored.
 Some surface brightness profiles were truncated at our discretion before the $3 \times RMS_{\rm sky}$ limit, 
@@
 \subsection{Unsharp masking}
-Unsharp masking is an image sharpening technique useful to reveal asymmetric structures in galaxies, 
+Unsharp masking is an image sharpening technique that is useful to reveal asymmetric structures in galaxies, 
 such as bars or (inclined) embedded disks. 
@@
 Therefore, for each galaxy, we produced a set of different unsharp masks by varying the $FWHM$ of the filter,
-to identify all the asymmetric features that could bias the fitting process and may need modeling.
+to identify all the asymmetric features that could bias the fitting process 
+and may therefore need to be considered during the galaxy modelling phase.
 This information was used in combination with kinematic and AGN information discussed in Section \ref{sec:adddata}.
@@
 \subsection{1D fitting routine}
-The decomposition of surface brightness profiles was performed with software written by G. Savorgnan.
+The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
 This software can fit an observed surface brightness profile with any linear combination of 
@@
 During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
-surface brightness profile.
+surface brightness profile, 
+although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
+The all too often over-looked {\bf ??} with (signal-to-noise)-based weighting schemes 
+is that they immediately become an incorrectly biased weighting schemes when additional components are present but not modelled.
+For example, fitting a S\'ersic model to what is actually a nucleated elliptical galaxy immediately {\bf ??} 
+a (signal-to-noise)-based weighting scheme 
+and results in S\'ersic parameters which describe the bulge less accurately than had no (signal-to-noise)-weighting been used.
+While we have paid careful attention to the components in each galaxy, 
+and more so than the studies upon which our work is building from,
+this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
+What is best in theory is not always best in practice -- in this case, because theory does not allow for unknown additional components
+that are modelled.
 
@@
 where we provide individual descriptions of the galaxies that we analyzed. \\
-As stressed in Section \ref{sec:int}, our investigation is primarily focused on the spheroidal components 
+As stressed in Section \ref{sec:int}, our investigation is primarily focused on the central spheroidal components 
 of galaxies.
-%This is naively identified with the whole galaxy in case of an elliptical galaxy,
-%and with the bulge of a lenticular or spiral galaxy.
 We assumed \emph{a priori} that each of our galaxies has a unique spheroidal component, 
 that we modeled with a S\'ersic profile. \\
-Disks were normally fit with the exponential model, 
-although in the case of highly inclined or edge-on systems we preferred using $n < 1$ S\'ersic functions. 
+Disks were usually fit with the exponential model, 
+although in the case of highly inclined or edge-on systems we preferred using an $n < 1$ S\'ersic function. 
 \citet{pastrav2013a,pastrav2013b} showed that, due to projection effects, their simulated images of inclined galaxy disks 
-are better fit by S\'ersic functions with $n < 1$ than pure exponential profiles.
-The inclined embedded disks of some ``elliptical'' galaxies were described with Ferrer functions, rather than $n < 1$ S\'ersic functions. 
-This choice is motivated by the fact that a S\'ersic + Ferrer model is less degenerate than a S\'ersic + S\'ersic model, 
-since the S\'ersic profile can assume any positive ($n > 1$) or negative ($n < 1$) curvature, 
+are better fit by a S\'ersic function with $n < 1$ than by a pure exponential model.
+The inclined, embedded disks of some ``elliptical'' galaxies were described with Ferrer functions, rather than a $n < 1$ S\'ersic function. 
+This choice was partly motivated by the fact that a S\'ersic + Ferrer model is less degenerate than a S\'ersic + S\'ersic model, 
+since the S\'ersic profile can assume any concave ($n > 1$) or convex ($n < 1$) curvature, 
 whereas the Ferrer profile can only have a negative curvature as required for an inclined disk. \\
@@
 Local maxima in the ellipticity and fourth harmonic profiles 
-can provide footprints of less obvious inner disks.
-In particular, the ellipticity profile helps distinguish embedded disks from large-scale ones.
+can provide footprints of less obvious embedded disks.
+In particular, the ellipticity profile helps distinguish embedded disks from large-scale disks.
 Galaxy disks typically have fixed ellipticity, reflecting their inclination to our line of sight.
@@
 can provide additional evidence for less obvious bars. 
-As noted, we fit bars with Ferrer functions or low-$n$ S\'ersic profiles ($n \sim 0.2$). \\
+As noted, we were able to successfully fit bars with a Ferrer function or a low-$n$ S\'ersic model ($n \sim 0.2$). \\
 The presence of a nuclear component -- either resolved or unresolved -- was generally expected in 
@@
 we repeated the fit by excluding the data points within the nuclear region.
-Only after checking that the outcome of the last fit was consistent with the previous one, 
-we inferred the presence of a stellar nuclear component, and accounted for it in the final galaxy model.}.
-Unresolved nuclear components were fit with PSF-like profiles,
+Only after checking that the outcome of the last fit was consistent with a fit that included a small nuclear component, 
+we inferred the presence of a stellar nuclear component.}.
+Unresolved nuclear components were fit with our optimal Moffat PSF,
 whereas resolved nuclear components were modeled with (PSF-convolved) narrow Gaussian functions. \\
@@
 This galaxy hosts a Seyfert AGN \citep{veroncettyveron2006} and filamentary dust in its center \citep{tran2001}.
-NGC 2974 is classified as fast rotator by the ATLAS$^{\rm 3D}$ survey, 
+NGC 2974 is classified as a fast rotator by the ATLAS$^{\rm 3D}$ survey, 
 and indeed the velocity map obtained by the SLUGGS survey shows that the galaxy kinematics is rotation-dominated 
@@
 and an elongated bar-like component within $R \lesssim 30''$,
-that produces a peak in the ellipticity and position angle profiles at $R \sim 20''$.
-Our 1D galaxy decomposition for NGC 2974 (see Figure \ref{fig:n2974ex}) consists of a S\'ersic bulge, an exponential large-scale disk,
+that is in addition to the more spherical bulge 
+and produces a peak in the ellipticity and position angle profiles at $R \sim 20''$.
+Our 1D galaxy decomposition for NGC 2974 (Figure \ref{fig:n2974ex}) consists of a S\'ersic bulge, an exponential large-scale disk,
 a Ferrer bar, a Gaussian nuclear component (AGN) and a Gaussian ring.
@@
 A model without the ring component results in a ``steeper'' exponential profile for the disk 
-(i.e.~the exponential model has smaller scale length and more negative central surface brightness) 
+(i.e.~the exponential model has a smaller scale length and a brighter central surface brightness) 
 and produces bad residual structures within $R \lesssim 40''$.
-Our best-fit model returns a bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 8.3\rm~arcsec$, 
-a bulge equivalent-axis S\'ersic index $n_{\rm sph}^{\rm eq} = 1.2$ and a $3.6~\rm \mu m$ bulge apparent magnitude $m_{\rm sph} = 8.65~\rm mag$.
+Our best-fit model returns a $3.6~\rm \mu m$ bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 8.3\rm~arcsec$, 
+equivalent-axis S\'ersic index $n_{\rm sph}^{\rm eq} = 1.2$ and apparent magnitude $m_{\rm sph} = 8.65~\rm mag$.
 \cite{sani2011} modeled NGC 2974 with a S\'ersic bulge and a Gaussian nuclear component (AGN), 
 but did not account for the large-scale disk.
-From their best-fit 2D model, they obtained a three times larger bulge major-axis effective radius ($R_{\rm e,sph}^{\rm maj} = 27.2\rm~arcsec$), 
-a 2.5 times larger bulge S\'ersic index ($n_{\rm sph} = 3$),
-and a significantly brighter $3.6~\rm \mu m$ bulge apparent magnitude ($m_{\rm sph} = 7.28~\rm mag$).
+From their best-fit 2D model, they obtained a three times larger 
+$3.6~\rm \mu m$ bulge major-axis effective radius ($R_{\rm e,sph}^{\rm maj} = 27.2\rm~arcsec$), 
+a 2.5 times larger S\'ersic index ($n_{\rm sph} = 3$),
+and a significantly brighter apparent magnitude ($m_{\rm sph} = 7.28~\rm mag$).
 
@@
 This did not happen in the 1D decomposition because of the different weighting scheme used by the fitting routines.}. 
-Our 2D best-fit model returns a bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 10.5~\rm arcsec$, 
+Our best-fit 2D model returns a bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 10.5~\rm arcsec$, 
 a bulge S\'ersic index $n_{\rm sph} = 1.3$ and a $3.6~\rm \mu m$ bulge apparent magnitude $m_{\rm sph} = 8.39~\rm mag$, 
 in fairly good agreement with our 1D decomposition. 
+Fits and descriptions for the other galaxies are available online.
 
@@
 and a linearly sampled surface brightness profile. 
-Because our fitting routine does not employ any error weighting scheme on the data points that constitute the surface brightness profile, 
+Because our fitting routine intentionally does not employ an error weighting scheme on the data points that constitute the surface brightness profile, 
 a fit to a logarithmically sampled profile puts more weight on the inner region of the galaxy 
 and poorly constrains the outskirts.
-On the other hand, a fit to a linearly sampled surface brightness profile equally treats inner and outer regions. 
+On the other hand, a fit to a linearly sampled surface brightness profile equally treats inner and outer regions, 
+but is more susceptible to sky-background subtraction issues. \\ 
 We found that the fits are, in general, more sensitive to the choice of the initial parameters 
 when using logarithmically sampled profiles than linearly sampled profiles. 
-In addition, a visual examination of the residuals demonstrated that the goodness of the fit within one galaxy effective radius 
+In addition, a visual examination of the residuals revealed that the quality of the fit within one galaxy effective radius 
 is superior when tighter constraints are put on the galaxy outskirts.
-In other words, the better quality of the residuals led us to prefer fits that use linearly sampled surface brightness profiles. \\
-Among the initial sample of 75, we did not attempt to model 3 galaxies: M32, NGC 4486A and the Circinus Galaxy. 
+In other words, the better quality of the residuals led us to prefer the fits that use linearly sampled surface brightness profiles,
+although the results were ususally very similar,as might be expected. \\
+Among the initial sample of 75 galaxies, we did not attempt to model 3 galaxies: M32, NGC 4486A and the Circinus Galaxy. 
 The first two... {\bf AL: can you write a short sentence about these 2 galaxies, that have uncertain morphology,
@@
 whereas the models of 6 galaxies were judged not reliable and were thus excluded. 
-We also performed 2D decompositions for 31 galaxies. \\
+We also performed reliable 2D decompositions for 31 galaxies. \\
 A galaxy-by-galaxy comparison between our best-fit models and those from the previous literature 
@@
 We compared our best-fit models with those of \cite{grahamdriver2007}, \cite{sani2011}, \cite{beifiori2012}, 
-\cite{vika2012}, \cite{lasker2014data}. 
-These five studies all investigated black hole mass scaling relations.
+\cite{vika2012} and \cite{lasker2014data}. 
 We also considered the best-fit models of \cite{laurikainen2010} and \cite{rusli2013} because,   
-although they did not specifically deal with black hole - galaxy scaling relations, 
+although they did not specifically deal with black hole -- galaxy scaling relations, 
 their galaxy samples significantly overlap with ours. \\
 %In Section \ref{sec:indgal} we discuss individual cases, explaining the discrepancies between different decompositions. \\
-Table \ref{tab:fitres} lists the results from the 1D and 2D fits.
+Table \ref{tab:fitres} lists the results from both the 1D and 2D fits.
 

### 2015-02-15 python_codes/databases/initialize/init.py

@@ -54,9 +54,9 @@ def ancillary():
 	cur.execute('''CREATE TABLE Ancillary
 		(gal_id text, gal_name text, IRAC_image integer, fit1D_done integer, fit2D_done integer, 
 		ELLIPTICAL_my integer, source text, RA real, DEC real, 
-		z real, distance real, core integer, 
+		z real, bar integer, distance real, core integer, 
 		core_inferred_from_sigma integer, sigma real, mass_BH real, perr_mass_BH real, merr_mass_BH real,
-		size_core real, ref_size_core text)''')
+		size_core real, ref_size_core text, KMAG_sph real)''')
 	
 	for line in data:
 		if line.split()[0] != '#':
@@ -80,6 +80,8 @@ def ancillary():
 			DEC = replaceNull(DEC)
 			z = line.split()[19]
 			z = replaceNull(z)
+			bar = line.split()[22]
+			bar = replaceBoolean(bar)
 			distance = line.split()[23]
 			distance = replaceNull(distance)
 			core = line.split()[24]
@@ -98,10 +100,12 @@ def ancillary():
 			perr_mass_BH = replaceNull(perr_mass_BH)
 			merr_mass_BH = line.split()[32]
 			merr_mass_BH = replaceNull(merr_mass_BH)
+			KMAG_sph = line.split()[47]
+			KMAG_sph = replaceNull(KMAG_sph)
 			
-			collection = [gal_id, gal_name, IRAC_image, fit1D_done, fit2D_done, ELLIPTICAL_my, source, RA, DEC, z, distance, 
-				core, core_inferred_from_sigma, sigma, mass_BH, perr_mass_BH, merr_mass_BH, size_core, ref_size_core]
-			cur.execute('INSERT INTO Ancillary VALUES (?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?)', collection)
+			collection = [gal_id, gal_name, IRAC_image, fit1D_done, fit2D_done, ELLIPTICAL_my, source, RA, DEC, z, bar, distance, 
+				core, core_inferred_from_sigma, sigma, mass_BH, perr_mass_BH, merr_mass_BH, size_core, ref_size_core, KMAG_sph]
+			cur.execute('INSERT INTO Ancillary VALUES (?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?)', collection)
 
 	connection.commit()
 	cur.close()

### 2015-02-15 python_codes/plots/scaling_relations/relations.py

@@ -24,6 +24,175 @@ dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_viv
 path_auxiliary_plots = '/Users/gsavorgnan/galaxy_vivisection/results/plots/auxiliary/'
 path_scalrel_plots = '/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/'
 
+def KMAG_sph_vs_mag_sph():
+	connection = sql3.connect(dbname)
+        cur = connection.cursor()
+       
+        getdata_query = 'SELECT anc.gal_id, anc.KMAG_sph, anc.ELLIPTICAL_my, anc.core, \
+		pysres.mag_sph_eq_moffat_comb \
+		FROM Ancillary AS anc \
+		JOIN OneDFitResultsPhysicalUnits AS pysres ON anc.gal_id = pysres.gal_id \
+		WHERE anc.fit1D_done = 1;'
+	cur.execute(getdata_query)
+        datalist = cur.fetchall()
+        data= np.asarray(datalist).transpose()
+	gal_id = data[0]
+	KMAG_sph = data[1].astype(np.float)
+        ELL = data[2].astype(np.int)
+	core = data[3].astype(np.int)
+	mag_sph = data[4].astype(np.float)
+	
+	fig, ax = plt.subplots()
+	ax.scatter(mag_sph[ELL==1], KMAG_sph[ELL==1], color='red', s=50)	
+	ax.scatter(mag_sph[ELL==0], KMAG_sph[ELL==0], color='blue', s=50)
+	ax.scatter(mag_sph[core==1], KMAG_sph[core==1], color='white', s=20)	
+	
+        full_names = {'n4388' : 'NGC 4388', 'n3585' : 'NGC 3585', 'n3607' : 'NGC 3607', 'n3414' : 'NGC 3414', 'n3115' : 'NGC 3115', 'n3377' : 'NGC 3377'}
+	
+	for g, m, k in zip(gal_id, mag_sph, KMAG_sph):
+		if g in ['n4388']:
+			ax.annotate(full_names[g], xy = (m, k), xytext = (0, 20),
+        			textcoords = 'offset points', ha = 'right', va = 'bottom',
+        			bbox = dict(boxstyle = 'round,pad=0.2', fc = 'blue', alpha = 0.1),
+        			arrowprops = dict(arrowstyle = '-', connectionstyle = 'arc3,rad=0'))
[…]

### 2015-02-19 papers/data_paper/datapaper.tex
hernia

@@
 \includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
-\caption{Best-fit model and isophotal parameters for the galaxy NGC 2974. 
+\caption{Best-fit model, and isophotal parameters, for the galaxy NGC 2974. 
 The left panels refer to the major-axis $R_{\rm maj}$, 
-whereas the right panels refer to the equivalent-axis $R_{\rm eq}$.
+while the right panels refer to the equivalent-axis $R_{\rm eq}$.
 The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
@@
 The color lines represent the individual (PSF-convolved) model components:
-red=S\'ersic (bulge), blue=exponential (disk), green=Gaussian (AGN), cyan=Ferrer (bar), gray=Gaussian ring (ring). 
-The best-fit parameters for the S\'ersic profile are included.
+red=S\'ersic (bulge), dark blue=exponential (disk), green=Gaussian (AGN), cyan=Ferrer (bar), gray=Gaussian ring (ring). 
+The best-fit parameters for the S\'ersic bulge model are inset.
 The total (PSF-convolved) model is shown with a black dashed line, 
-but it is hard to distinguish because it almost perfectly matches the data.
-The horizontal grey dashed line indicates the $3~RMS_{\rm sky}$ level.
+but it is hard to distinguish because it almost perfectly matches the data, 
+hence the residual profile is additionally shown as $\Delta \mu$ in the second row.
+The horizontal grey dashed line corresponds to an intensity 
+equal to three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$).
 $\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
-$\Delta \mu$ are the residuals from the fit.
-The six panels below show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles.}
+The lower six panels show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles. 
+Such profiles are available online for all other galaxies successfully modelled in 1D (see Table \ref{tab:fitres}).}
 \label{fig:n2974ex}
@@
 \includegraphics[width=\columnwidth]{images/n2974_resid.pdf}
-\caption{The image of the galaxy NGC 2974 with its mask (top panel), the best-fit 2D model (middle panel), 
-and the residual image after the subtraction of the 2D model (bottom panel).
+\caption{Image of the galaxy NGC 2974 with its mask (top panel), best-fit 2D model (middle panel), 
+and residual image after the subtraction of the 2D model (bottom panel).
 The ring has not been modeled, and therefore appears in the residual image.}
@@
 \subsection{1D versus 2D decompositions}
-%In Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}, we compare the bulge best-fit parameters obtained 
-%from the 1D decompositions with those obtained from the 2D decompositions.
-How do 1D and 2D decompositions compare with each other? 
-Although an exhaustive analysis is beyond the scope of the present work, 
-we believe that some of the readers might be interested in our practical knowledge, 
-having dealt with 1D and 2D techniques of galaxy modeling at the same time. \\
+Here we explore how 1D and 2D decompositions compare with each other. 
+Readers not interested in our practical knowledge, 
+having dealt with 1D and 2D techniques of galaxy modeling at the same time, can skip to Section \ref{sec:err}. 
 We summarize our experience in the following points:
 \begin{itemize}
-\item A visual inspection of galaxy images and their unsharp masks is often not sufficient to accurately identify all galaxy components. 
-Embedded disks or weak bars can easily be missed, and (inclined) intermediate-scale disks can be confused with large-scale ones.
+\item A visual inspection of galaxy images and their unsharp masks is often not sufficient to accurately identify all of a galaxy's components. 
+Weak bars and some embedded disks can easily be missed. 
+Other (inclined) embedded disks can be confused with large-scale disks.
 In this regards, the 1D isophotal analysis is extremely helpful. 
 Local minima/maxima or abrupt changes in the ellipticity, position angle and fourth harmonic profiles contain precious information 
-about the galaxy constituents.
-\item The ellipticity and position angle of bulges can vary with radius.
+about a galaxy's constituents.
+\item The ellipticity and position angle of triaxial bulges can vary with radius.
 The analytic functions used by 2D decomposition codes to fit galaxy components have fixed ellipticity and position angle, 
-thus they cannot account for their radial gradients. 
+thus they cannot account for these radial gradients. 
 This problem is overcome with 1D decomposition techniques.
-\item The interpretation of the residuals is often crucial to identify the optimal decomposition for a galaxy. 
-In our experience, we found that the reading of 1D residuals was easier than that of 2D residuals.
+\item The interpretation of the residual surface brightness profile is often crucial to identify the optimal decomposition for a galaxy. 
+In our experience, we found that interpreting 1D residuals was easier and more productive than 2D residuals.
 \end{itemize}
-Although we attempted 2D modeling for all galaxies in our sample, 
-nearly half of the 2D decompositions were not successful or did not converge.
-For the 31 galaxies that had successful 1D and 2D decompositions, 
-we compare their 1D and 2D best-fit parameters in Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}.
+Although we attempted 2D modeling for the 72 galaxies in our sample, 
+more than half of the 2D decompositions were not successful or did not converge to a meaningful solution. 
+This should serve as a tip to users of 2D fitting codes. 
+When physically meaningful bulge parameters are required, 
+the output may not be reliable and should be inspected.
+For the 31 galaxies that had successful 2D decompositions, 
+we compare with their 1D parameters in Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}.
 %The software \textsc{Imfit} returns major-axis measurements of effective radii, 
@@
 The agreement between 1D and 2D effective radii and magnitudes is remarkable, 
-whereas a larger amount of scatter in the S\'ersic indices plot might be caused by the fact that 
+whereas a larger amount of scatter in the S\'ersic indices can be caused by the fact that 
 2D measurements do not exactly correspond to 1D equivalent-axis measurements. 
@@
 which indicates that 1D and 2D techniques of galaxy modeling -- when performed on the same galaxy -- 
-give consistent results. \\
+can give consistent results. \\
 In conclusion, since we found that the best-fit parameters do not depend on the decomposition method (1D or 2D) used, 
-but we obtained more successful 1D decompositions than 2D, 
-we will base our analysis only on the results from 1D fits.
+and given that we obtained more successful 1D decompositions than 2D, 
+we will base our analysis on the results from the 1D fits.
 
@@
 \includegraphics[width=\columnwidth]{images/comparison_r_e.eps} 
-\caption{2D versus 1D major-axis measurements of effective radii. 
+\caption{2D versus 1D major-axis measurements of the effective radii. 
 The dashed line displays the 1:1 relation.}
@@
 \includegraphics[width=\columnwidth]{images/comparison_n.eps} 
-\caption{2D measurements of S\'ersic indices can be approximated to 1D equivalent-axis measurements, 
-and are therefore compared to them in this plot. The dashed line displays the 1:1 relation.}
+\caption{2D measurements of the S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
+The dashed line displays the 1:1 relation.}
 \label{fig:n1d2d}
@@
 \includegraphics[width=\columnwidth]{images/comparison_mag.eps} 
-\caption{2D versus 1D measurements of $3.6~\rm \mu m$ bulge magnitudes. The dashed line displays the 1:1 relation.}
+\caption{2D versus 1D measurements of the $3.6~\rm \mu m$ bulge magnitudes. The dashed line displays the 1:1 relation.}
 \label{fig:mag1d2d}
@@
 Monte Carlo simulations could be used for this purpose, 
-but they would take into account only random errors and not unknown systematic ones.
+but they would take into account only random errors and not unknown systematic errors.
 Systematic errors include incorrect sky subtraction, 
@@
 the radial extent of the surface brightness profile and its sampling.
-%(if no weighting scheme is applied to the data points during the minimization routine, 
-%then, for the same galaxy, the fit of a logarithmically sampled light profile will naturally put more weight on the inner part of the profile 
-%than in the case of linear sampling).
-When performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well resolved -- galaxies, 
+These factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters.  
+Moreover, when performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well resolved -- galaxies, 
 errors are dominated by systematics rather than Poisson noise.
@@
 \subsubsection{Goodness of the bulge modeling}
-To do this, we first had to evaluate the goodness of the modeling of the bulge component.
-For each of our fits, we calculated the associated $RMS$ scatter\footnote{The $RMS$ scatter of a fit was computed as:
+For each of our fits, we calculated the associated $RMS$ scatter using:
 \begin{equation}
-\Delta = \sqrt{\frac{\sum_{\rm i=0}^{N} (\mu_{\rm i}^{\rm observed} - \mu_{\rm i}^{\rm model})^2}{N_{\rm DOF}} } ,
+\Delta = \sqrt{\frac{\sum_{\rm i=0}^{N} (\mu_{\rm i}^{\rm obs} - \mu_{\rm i}^{\rm mod})^2}{N_{\rm DOF}} } ,
 \end{equation} 
-where %$N$ is the number of data points used in the fit, 
-$N_{\rm DOF}$ is the number of degrees-of-freedom, 
-$\mu^{\rm observed}$ is the observed surface brightness 
-and $\mu^{\rm model}$ is the model surface brightness.}.
+where $N_{\rm DOF}$ is the number of degrees-of-freedom, 
+$\mu_{\rm i}^{\rm obs}$ is the observed surface brightness 
+and $\mu_{\rm i}^{\rm mod}$ is the model surface brightness at each data point $i$.
 Although useful to evaluate the overall quality of a galaxy decomposition, 
@@
 where the emission of the disk dominates over that of the bulge,
-while they will display significant structures at small radii, 
-in correspondence of the poorly fit spheroidal component.
-In case of linear sampling, 
-because the part of the surface brightness profile pertaining to the disk contains more data points 
+while they will display significant departures at small radii, 
+in correspondence with the poorly fit spheroidal component.
+In the case of linear sampling, 
+because the part of the surface brightness profile pertaining to the disk may contain more data points 
 than the part pertaining to the bulge, 
@@
 but it obviously will not reflect the accuracy of the fit to the spheroidal component only. \\
-A simple but powerful way to get a feeling of how precisely the global model describes the spheroidal component 
+A simple but powerful way to get a feeling of how precisely the global model and its spheroidal component have fared
 is to look at the major- and equivalent-axis fits of each galaxy 
-and visually inspect the structures of the residuals within $\sim 1 - 2$ bulge effective radii. 
+and visually inspect the structures of the residual surface brightness profile 
+(i.e.~the second row in Figure \ref{fig:n2974ex}) within $\sim 1 - 2$ bulge effective radii. 
 We did this using a grade from 1 to 3, assigned according to the following criteria.
@@
 \item [1)] A grade of 1 was given to the best fits, i.e.~fits that do not exhibit any of the problems listed below.
-\item [2)] A grade of 2 was used in the following cases: 
-the residuals in correspondence of the bulge component are not randomly distributed around zero, 
+\item [2)] A grade of 2 was issued in the following cases. 
+The residuals in correspondence with the radial extent of the bulge component are not randomly distributed around zero, 
 being symptomatic of a S\'ersic model having a curvature (regulated by the S\'ersic index $n$) 
-that does not match the real ``shape'' of the bulge; 
-when we identified, but were not able to accurately model a galaxy sub-component;
-in the case of significant inconsistencies between the model and the observed galaxy properties 
+that does not quite match the real ``shape'' of the bulge. 
+When we identified, but were not able to accurately model. a galaxy sub-component.
+In the case of apparent inconsistencies between the model and the observed galaxy properties 
 (e.g.~an embedded disk modeled with an exponential function, 
-whose scale length does not match the size of the disk as expected from the ellipticity profile or the velocity map);
-when the S\'ersic profile used to describe the bulge component has a size -- as measured by the effective radius -- 
+whose scale length does not quite match the size of the disk as expected from the ellipticity profile or the velocity map).
+When the S\'ersic model used to describe the bulge component has a size -- as measured by the effective radius -- 
 comparable to a few times the $FWHM$ of the PSF.
+Galaxies in this category are reasonably well fit despite these issues.
 \item [3)] A grade of 3 was assigned to the poorer and more anomalous fits, 
 or those affected by an obvious degeneracy between the bulge S\'ersic profile and the remaining model components 
-(e.g.~when the bulge S\'ersic index varies for more than 50\% {\bf TBD: how often what?} among the four different realizations of the fit, 
+(e.g.~when the bulge S\'ersic index varies by as much as 50\% among the four different realizations of the fit, 
 or when the output of the fit strongly depends on the choice of the initial parameters).
@@
 29 galaxies (40\%) with grade 2 and 10 galaxies (14\%) with grade 3.
-%The absolute values of the uncertainties of the S\'ersic parameters will be estimated in a forthcoming paper, 
-%according to the grades assigned here to the fits.
+Six galaxies could not be modelled.
+We report the assigned grades in Table \ref{tab:fitres} (column 10).
 
@@
 with those obtained by us. 
-For each galaxy, we computed the average value $\langle \log(n_{\rm sph}) \rangle$ of all the available measurements, 
-and we plot it against the scatter of the individual measurements around $\langle \log(n_{\rm sph}) \rangle$.
-The measurements are deliberately heterogeneous, 
+For each galaxy, we computed the average value $\langle \log(n_{\rm sph}) \rangle$ of the available measurements, 
+and we plot it against the scatter of the individual measurements around each spheroid's $\langle \log(n_{\rm sph}) \rangle$.
+The measurements are heterogeneous, 
 in the sense that they were obtained from 1D or 2D decompositions of data in different wavelengths, 
-and they refer either to the major-axis or to the equivalent-axis.
+and they refer either to the major-axis, the equivalent-axis or some 2D average.
 In Figure \ref{fig:compn}, the black histogram shows the distribution of the scatter around $\langle \log(n_{\rm sph}) \rangle$ 
-only for our measurements. 
+for our measurements. 
 38\% of this distribution lie within $-\sigma_1^- = -0.08~\rm dex$ and $+\sigma_1^+ = +0.06~\rm dex$, 
@@
 \subsubsection{Uncertainties on $R_{\rm e,sph}$}
-The uncertainties on the bulge effective radii were computed with the same method used for the S\'ersic indices. 
+The uncertainties on the bulge effective radii were computed using the same methodology as employed for the S\'ersic indices. 
 However, in Figure \ref{fig:compre} we include only major-axis measurements of $R_{\rm e,sph}$. 
@@
 To estimate the uncertainties on the bulge magnitudes, 
-we compared (see Figure \ref{fig:compmag}) only measurements coming from $K$-band or $3.6~\rm \mu m$ observations.
-$3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes by an additive factor of $+0.27\rm~mag$, 
+we compared (see Figure \ref{fig:compmag}) only those literature measurements coming from $K$-band or $3.6~\rm \mu m$ observations.
+To do this, the $3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes by applying an additive factor of $0.27\rm~mag$, 
 which was estimated using the stellar population models of \cite{worthey1994},
@@
 $-\sigma_2^- = -0.58~\rm mag$ and $+\sigma_2^+ = +0.66~\rm mag$,
-and $-\sigma_3^- = -0.66~\rm mag$ and $+\sigma_3^+ = +0.88~\rm mag$. \\
-{\bf NOTE: When converting from K-band to 3.6, 
-Galactic absorption was not taken into account!!!!! But I have the feeling that it's not significant...}
+and $-\sigma_3^- = -0.66~\rm mag$ and $+\sigma_3^+ = +0.88~\rm mag$.
 
@@
 by comparing only $K$-band or $3.6~\rm \mu m$ measurements (see Figure \ref{fig:compmue}), 
-and accounting for the corrective factor. 
-Because not explicitly reported by their authors, literature effective surface brightnesses were calculated by us as:
+and accounting for the mean color difference of $0.27\rm~mag$. 
+Not explicitly reported in the literature, effective surface brightnesses were calculated by us using:
 \begin{multline}
@@
 \end{multline}
-where $b_n$ and $\Gamma(2n_{\rm sph})$ are defined in Section \ref{sec:app1}, 
+where $b_n$ and $\Gamma(2n_{\rm sph})$ are defined in the Appendix, 
 and $(b/a)_{\rm sph}$ is the bulge axis ratio.
@@
 \subsubsection{Uncertainties on $\mu_{\rm 0,sph}$}
-From the values of $\mu_{\rm e,sph}$, we derived the central surface brightnesses $\mu_{\rm 0,sph}$ as
+From the values of $\mu_{\rm e,sph}$, we derived the central surface brightnesses $\mu_{\rm 0,sph}$ from the equation
 \begin{equation}
@@
 and host bulge properties. \\
-The bulge best-fit parameters are model-dependent. 
 Past studies often used different models for the same galaxy, and obtained significantly discrepant results,  
-which led them to draw contrasting conclusions about the black hole-bulge correlations.
+which led them to draw contrasting conclusions about the black hole--bulge correlations.
 These inconsistencies motivated our effort to secure and refine the measure of bulge properties in a sample of 75 galaxies 
@@
 we performed state-of-the-art galaxy decompositions. 
-We compared our best-fit models with those from the past literature, 
-and explained discrepancies when present. 
+The $3.6~\rm \mu m$ band is an excellent tracer of the stellar mass, superior to optical bands or the $K$-band. 
+Considerable care has been taken in the data reduction, image mosaicking, sky subtraction and component model fitting to the galaxy light.
+We have compared our best-fit models with those from the literature, 
+to identify and explain discrepancies when present. 
+Our analysis additionally benefited from recourse to kinematical information -- not previously used -- to aid the identification of 
+somewhat face-on disks, or the distinction between intermediate-scale disks and large-scale disks, 
+missed in some past investigations and decompositions.
 Table \ref{tab:lit} summarizes the main characteristics of the five past studies that, since 2007, attempted galaxy decomposition 
 to derive black hole-bulge scaling relations, 
-and highlights why our endeavor represents a substantial improvement over the past literature.
-Our sample of galaxies is the largest ever used. 
-The $3.6~\rm \mu m$ band is an excellent tracer for the stellar mass, superior to optical bands or the $K$-band. 
-\cite{lasker2014data} and this work identified and modeled more galaxy components than any other study, 
-and therefore obtained more accurate decompositions,
-but we are the first that did it with the assistance of kinematical information.
+and highlights, in part, why our endeavor represents a substantial improvement over the past literature.
 
@@
 
-Our principal conclusions are summarized in the following points.
 \begin{itemize}
@@
 often observed in galaxy bulges.
-\item We found the interpretation of one-dimensional residuals easier than that of two-dimensional residual images. 
+\item We found the interpretation of one-dimensional residual surface brightness profiles easier than that of two-dimensional residual images. 
 A correct interpretation of the residuals is fundamental to determine the optimal model for a galaxy.
@@
 \item Given the level of detail to which each galaxy decomposition was performed, 
-we believe that our analysis cannot be reproduced by any current automatic routine. 
+we believe that our analysis cannot be reproduced by current automatic routines. 
 \item The uncertainties associated with the bulge best-fit parameters are dominated by systematic errors (e.g.~incorrect sky subtraction, 
@@
 \acknowledgments
+{\bf marconi, sani, hunt...}
 GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Elisabete Lima Da Cunha and Gonzalo Diaz 
@@
 \label{sec:app1}
-Below we give the mathematical expressions of all the analytical functions used in this work to model 
-the observed surface brightness profiles ($\mu$) of galaxies.
-We indicate with $R$ the projected galactic radius, 
-corresponding to the distance of the isophotes from the galaxy center (along the major- or equivalent-axis). \\
-
-The \emph{S\'ersic profile} \citep{sersic1963,sersic1968} is a three-parameter function with the following form:
+Here we provide the mathematical expressions of the analytical functions used to model 
+the observed surface brightness profiles, $\mu(R)$, of galaxies.
+The projected galactic radius, $R$,
+corresponds to the distance of the isophotes from the galaxy center (along either the major- or equivalent-axis). \\
+
+The \citeauthor{sersic1963} (\citeyear{sersic1963,sersic1968}) model is a three-parameter function of the following form:
 \begin{equation}
@@
 where $\mu_{\rm e}$ is the surface brightness at the effective radius $R_{\rm e}$ that encloses 
-half of the total light from the model, 
-the S\'ersic index $n$ is the parameter that measures the curvature of the radial light profile,
-and $b_{\rm n}$ is a scalar value defined in terms of the S\'ersic index $n$.
-The value of $b_{\rm n}$ is found by solving numerically the following expression:
+half of the total light from the model. 
+The S\'ersic index $n$ is the parameter that measures the curvature of the radial light profile,
+and $b_{\rm n}$ is a scalar value defined in terms of the S\'ersic index $n$ such that:
 \begin{equation}
@@
 
-The \emph{exponential profile} is a special case ($n=1$) of the S\'ersic profile.
-It is therefore a two-parameter function, with the following form:
+The exponential model is a special case ($n=1$) of the S\'ersic model.
+It can therefore be written as a two-parameter function such that:
 \begin{equation}
@@
 \end{equation}
-where $\mu_{\rm 0}$ is the central surface brightness and $h$ is the scale length. \\
-
-The \emph{Gaussian profile} is a two-parameter function with the following form:
+where $\mu_{\rm 0}$ is the central surface brightness and $h$ is the scale length equal to $R_{\rm e}/1.678$. \\
+
+The Gaussian model is another special case ($n=0.5$) of the S\'ersic model, and thus also a two-parameter function of the following form:
 \begin{equation}
@@
 \biggl[\frac{R^2}{2(FWHM/2.355)^2} \biggr] ,
+\label{eq:gauss}
 \end{equation}
@@
 
-The \emph{Moffat profile} \citep{moffat1969} is a three-parameter function with the following form:
+The \cite{moffat1969} model is a three-parameter function that can be expressed as:
 \begin{equation}
@@
 \begin{equation}
-FWHM = 2\alpha \sqrt{2^{1/\beta}-1}
+FWHM = 2\alpha \sqrt{2^{1/\beta}-1} ,
 \end{equation}
@@
 
-The \emph{Ferrer profile} is a four-parameter function with the following form:
+The Ferrer model is a four-parameter function defined as:
 \begin{equation}
@@
 $\beta$ is related to the central slope,
-and $R_{\rm out}$ is the limit within which the function is defined. \\
-
-The \emph{symmetric Gaussian ring} is a three-parameter function with the following form:
+and $R_{\rm out}$ is the outer radial limit within which the function is defined. \\
+
+The symmetric Gaussian ring is a three-parameter function of the following form:
 \begin{equation}
@@
 \end{equation}
-where $\mu_{\rm 0}$ is the central surface brightness,
-$R_{\rm 0}$ is the radius at which the Gaussian profile is centered, 
-and $FWHM$ is the full width at half maximum of the Gaussian profile. \\
+where $\mu_{\rm 0}$ and $FWHM$ have the same meaning as in equation \ref{eq:gauss}, 
+and $R_{\rm 0}$ is the radius at which the Gaussian profile is centered. \\
 

### 2015-02-23 papers/data_paper/~datapaper.tex
vittorioiloveu

--- 2015-02-19 papers/data_paper/datapaper.tex
@@
 \begin{center}
-\includegraphics[width=1\columnwidth, trim = 220 30 20 20, clip=True]{images/psf.eps}
+\includegraphics[width=1\columnwidth, trim = 240 40 50 20, clip=True]{images/psf.eps}
 %\includegraphics[width=1\columnwidth]{images/star1_cut.eps} \\
@@
 The left panels refer to the major-axis $R_{\rm maj}$, 
-while the right panels refer to the equivalent-axis $R_{\rm eq}$.
+while the right panels refer to the equivalent-axis $R_{\rm eq}$, 
+i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$).
 The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/n2974_imgmsk.pdf}
-\includegraphics[width=\columnwidth]{images/n2974_model.pdf}
-\includegraphics[width=\columnwidth]{images/n2974_resid.pdf}
-\caption{Image of the galaxy NGC 2974 with its mask (top panel), best-fit 2D model (middle panel), 
+\includegraphics[width=\columnwidth]{images/n2974_imgmsk.jpeg}
+\includegraphics[width=\columnwidth]{images/n2974_unsharp.jpeg}
+\includegraphics[width=\columnwidth]{images/n2974_model.jpeg}
+\includegraphics[width=\columnwidth]{images/n2974_resid.jpeg}
+\caption{Image of the galaxy NGC 2974 with its mask (top panel), unsharp mask (second panel), 
+best-fit 2D model (third panel), 
 and residual image after the subtraction of the 2D model (bottom panel).
-The ring has not been modeled, and therefore appears in the residual image.}
+The lefthand side of the mosaic allowed an accurate determination of the sky background level.}
 \label{fig:n29742d}
@@
 \includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
-\caption{The bottom panel shows 58 galaxies for which at least one measurement of the bulge S\'ersic index $n_{\rm sph}$ is available 
-from the literature, in addition to that measured by us.
+\caption{Bottom panel: 58 galaxies for which at least one measurement of the bulge S\'ersic index $n_{\rm sph}$ is available 
+from the literature (T), in addition to that measured by us.
 In ordinate, for each galaxy, we plot the average value $\langle \log(n_{\rm sph}) \rangle$ of (the logarithm of) the individual measurements. 

### 2015-02-23 python_codes/instruments/linear_regression/test/test.py

@@ -2,8 +2,11 @@ import numpy as np
 from instruments.linear_regression import fitexy
 
 #data = open('test.dat')
-data = open('Savorgnan_2014.dat')
+#data = open('Savorgnan_2014.dat')
 #data = open('msigma.out')
+#data = open('allcoreell.dat')
+#data = open('goodnocoresp.dat')
+data = open('allnocorespi.dat')
 
 xlist = []
 sigxlist = []

### 2015-02-23 python_codes/plots/scaling_relations/relations.py

@@ -563,82 +563,82 @@ def log_mbh_vs_mag_sph():
 	
         fig, ax = plt.subplots()
 
-      ##print 'ELL'
-      ##A,B,Aerr,Berr,covAB=bces.bces(mag_sph[ELL==1]-np.average(mag_sph[ELL==1]),0.5*(perr_mag_sph[ELL==1]+merr_mag_sph[ELL==1]),
-      ##	log_mbh[ELL==1],0.5*(merr_log_mbh[ELL==1] + perr_log_mbh[ELL==1]),mag_sph[ELL==1]*[0.0])
-      ##print '---------------------------------'
-      ##print 'y = A*(x-<x>) + B '
-      ##print '<x> =', np.average(mag_sph[ELL==1])
-      ##print
-      ##print 'OLS(Y|X)    A =', "{0:.4f}".format(A[0]), '+-', "{0:.4f}".format(Aerr[0]), '   B = ', "{0:.4f}".format(B[0]), '+-', "{0:.4f}".format(Berr[0])
-      ##print 'OLS(X|Y)    A =', "{0:.4f}".format(A[1]), '+-', "{0:.4f}".format(Aerr[1]), '   B = ', "{0:.4f}".format(B[1]), '+-', "{0:.4f}".format(Berr[1])
-      ##print 'bisector    A =', "{0:.4f}".format(A[2]), '+-', "{0:.4f}".format(Aerr[2]), '   B = ', "{0:.4f}".format(B[2]), '+-', "{0:.4f}".format(Berr[2])
-      ##print 'orthogonal  A =', "{0:.4f}".format(A[3]), '+-', "{0:.4f}".format(Aerr[3]), '   B = ', "{0:.4f}".format(B[3]), '+-', "{0:.4f}".format(Berr[3])
-      ##print '---------------------------------'
-      ##
-      ##logxx = np.arange(-40,40,0.01)
-      ##yy = (A[2]*(logxx) + B[2])
-      ##ax.plot(logxx+np.average(mag_sph[ELL==1]),10**yy, color='red', linewidth=2.)
-      ##
-      ##print 'BUL'
-      ##A,B,Aerr,Berr,covAB=bces.bces(mag_sph[ELL==0]-np.average(mag_sph[ELL==0]),0.5*(perr_mag_sph[ELL==0]+merr_mag_sph[ELL==0]),
[…]

### 2015-02-27 papers/data_paper/datapaper.tex
fri

@@
 \includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
-\caption{The bottom panel shows 58 galaxies for which at least one measurement of the bulge S\'ersic index $n_{\rm sph}$ is available 
-from the literature, in addition to that measured by us.
-In ordinate, for each galaxy, we plot the average value $\langle \log(n_{\rm sph}) \rangle$ of (the logarithm of) the individual measurements. 
-In abscissa we plot the difference between (the logarithm of) the individual measurements of a galaxy 
-and the average value for that same galaxy.
-Each data point corresponds to an individual measurement, 
-which comes from one of the following studies. 
-Red points are from \cite{grahamdriver2007}, 
-blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
-yellow points are from \cite{vika2012}, gray points are from \cite{beifiori2012},
-white points are from \cite{rusli2013}, orange points are from \cite{lasker2014data},
-and black points are measurements obtained from the 1D fits presented in this work 
+\caption{Bottom panel: 58 galaxies for which at least one measurement of the bulge S\'ersic index $n_{\rm sph}$ is available 
+from the literature (Table \ref{tab:lit}), in addition to that measured by us.
+The average (logarithmic) value $\langle \log(n_{\rm sph}) \rangle$ is plotted against 
+the difference between (the logarithm of) the individual measurements of a galaxy 
+and the average (logarithmic) value for that same galaxy.
+Each data point corresponds to an individual measurement from: 
+\citeauthor{grahamdriver2007}~(\citeyear{grahamdriver2007}, red points);  
+\citeauthor{laurikainen2010}~(\citeyear{laurikainen2010}, blue points); 
+\citeauthor{sani2011}~(\citeyear{sani2011}, green points);  
+\citeauthor{vika2012}~(\citeyear{vika2012}, yellow points);
+\citeauthor{beifiori2012}~(\citeyear{beifiori2012}, gray points); 
+\citeauthor{rusli2013}~(\citeyear{rusli2013}, white points); 
+\citeauthor{lasker2014data}~(\citeyear{lasker2014data}, orange points). 
+Black points are measurements obtained from the 1D fits presented in this work 
 (using linearly sampled surface brightness profiles, along the major-axis).
@@
 for all measurements, 
-whereas the black histogram refers only to measurements obtained by us.
+whereas the black histogram refers only to the measurements obtained by us.
 The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
-of the black histogram, respectively.}
+of the black histogram, respectively, 
+corresponding to our quality flags 1, 2 and 3 given in Table \ref{tab:fitres}.}
 \label{fig:compn}
@@
 \includegraphics[width=1.1\columnwidth]{images/comparison_all_r_e.eps} 
-\caption{The bottom panel shows 52 galaxies for which at least one measurement 
-of the major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
-from the literature, in addition to that measured by us.
-In ordinate, for each galaxy, we plot the average value $\langle \log(R_{\rm e}^{\rm maj}) \rangle$ 
-of (the logarithm of) the individual measurements. 
-In abscissa we plot the difference between (the logarithm of) the individual measurements of a galaxy 
-and the average value for that same galaxy.
-Each data point corresponds to an individual measurement, 
-which comes from one of the following studies. 
-Red points are from \cite{grahamdriver2007}, 
-blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
-yellow points are from \cite{vika2012}, gray points are from \cite{beifiori2012},
-orange points are from \cite{lasker2014data},
-and black points are measurements obtained from the 1D fits presented in this work 
-(using linearly sampled surface brightness profiles, along the major-axis).
-In the top panel, the white histogram shows the distribution of $\log(R_{\rm e}^{\rm maj}) - \langle \log(R_{\rm e}^{\rm maj}) \rangle$ 
-for all measurements, 
-whereas the black histogram refers only to measurements obtained by us.
-The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
-of the black histogram, respectively.}
+\caption{Bottom panel: 52 galaxies for which at least one measurement of the bulge major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
+from the literature (Table \ref{tab:lit}), in addition to that measured by us.
+The average (logarithmic) value $\langle \log(R_{\rm e}^{\rm maj}) \rangle$ is plotted against 
+the difference between (the logarithm of) the individual measurements of a galaxy 
+and the average (logarithmic) value for that same galaxy.
+See Figure \ref{fig:compn} for color description and explanation of the top panel.}
 \label{fig:compre}
@@
 \includegraphics[width=1.1\columnwidth]{images/comparison_all_mag_sph.eps} 
-\caption{The bottom panel shows 51 galaxies for which at least one measurement 
-of the bulge apparent magnitude $m_{\rm sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
-from the literature, in addition to that measured by us. 
-$3.6~\rm \mu m$ magnitudes were converted to $K$-band magnitudes.
-In ordinate, for each galaxy, we plot the average value $\langle m_{\rm sph} \rangle$ 
-of the individual measurements. 
-In abscissa we plot the difference between the individual measurements of a galaxy 
+\caption{Bottom panel: 51 galaxies for which at least one measurement of the bulge apparent magnitude $m_{\rm sph}$ 
+-- either in $K$-band or $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
+$3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes (see Section \ref{sec:err} for details).
+The average value $\langle m_{\rm sph} \rangle$ is plotted against 
+the difference between the individual measurements of a galaxy 
 and the average value for that same galaxy.
-Each data point corresponds to an individual measurement, 
-which comes from one of the following studies. 
-Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
-yellow points are from \cite{vika2012}, 
-orange points are from \cite{lasker2014data},
-and black points are measurements obtained from the 1D fits presented in this work 
-(using linearly sampled surface brightness profiles, along the equivalent-axis).
-In the top panel, the white histogram shows the distribution of $m_{\rm sph} - \langle m_{\rm sph} \rangle$ 
-for all measurements, 
-whereas the black histogram refers only to measurements obtained by us.
-The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
-of the black histogram, respectively.}
+See Figure \ref{fig:compn} for color description and explanation of the top panel.}
 \label{fig:compmag}
@@
 \includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_e.eps} 
-\caption{The bottom panel shows 49 galaxies for which at least one measurement 
-of the bulge effective surface brightness $\mu_{\rm e,sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
-from the literature, in addition to that measured by us. 
-$K$-band magnitudes were converted to $3.6~\rm \mu m$ magnitudes.
-In ordinate, for each galaxy, we plot the average value $\langle \mu_{\rm e,sph} \rangle$ 
-of the individual measurements. 
-In abscissa we plot the difference between the individual measurements of a galaxy 
+\caption{Bottom panel: 49 galaxies for which at least one measurement of the bulge effective surface brightness $\mu_{\rm e,sph}$ 
+-- either in $K$-band or $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
+$K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
+The average value $\langle \mu_{\rm e,sph} \rangle$ is plotted against 
+the difference between the individual measurements of a galaxy 
 and the average value for that same galaxy.
-Each data point corresponds to an individual measurement, 
-which comes from one of the following studies. 
-Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
-yellow points are from \cite{vika2012}, 
-orange points are from \cite{lasker2014data},
-and black points are measurements obtained from the 1D fits presented in this work 
-(using linearly sampled surface brightness profiles, along the major-axis).
-In the top panel, the white histogram shows the distribution of $\mu_{\rm e,sph} - \langle \mu_{\rm e,sph} \rangle$ 
-for all measurements, 
-whereas the black histogram refers only to measurements obtained by us.
-The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
-of the black histogram, respectively.}
+See Figure \ref{fig:compn} for color description and explanation of the top panel.}
 \label{fig:compmue}
@@
 \includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_0.eps} 
-\caption{The bottom panel shows 49 galaxies for which at least one measurement 
-of the bulge central surface brightness $\mu_{\rm 0,sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
-from the literature, in addition to that measured by us. 
-$K$-band magnitudes were converted to $3.6~\rm \mu m$ magnitudes.
-In ordinate, for each galaxy, we plot the average value $\langle \mu_{\rm 0,sph} \rangle$ 
-of the individual measurements. 
-In abscissa we plot the difference between the individual measurements of a galaxy 
+\caption{Bottom panel: 49 galaxies for which at least one measurement of the bulge central surface brightness $\mu_{\rm 0,sph}$ 
+-- either in $K$-band or $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
+$K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
+The average value $\langle \mu_{\rm 0,sph} \rangle$ is plotted against 
+the difference between the individual measurements of a galaxy 
 and the average value for that same galaxy.
-Each data point corresponds to an individual measurement, 
-which comes from one of the following studies. 
-Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
-yellow points are from \cite{vika2012}, 
-orange points are from \cite{lasker2014data},
-and black points are measurements obtained from the 1D fits presented in this work 
-(using linearly sampled surface brightness profiles, along the major-axis).
-In the top panel, the white histogram shows the distribution of $\mu_{\rm 0,sph} - \langle \mu_{\rm 0,sph} \rangle$ 
-for all measurements, 
-whereas the black histogram refers only to measurements obtained by us.
-The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
-of the black histogram, respectively.}
+See Figure \ref{fig:compn} for color description and explanation of the top panel.}
 \label{fig:compmu0}
@@
 These results will be presented in a series of forthcoming papers.
+
+{\bf Lasker's conclusions are: bulge+disk decompositions are not enough, we do better by adding bars, spiral arms and stuff (really?? what a surprising conclusion);
+we modelled the envelope of 5 galaxies; we observed central light deficits in 9 ellipticals; total magnitudes are independent from details of modelling (no, really?)
+and bulge magnitudes are 0.36 mag fainter when additional components (other than bulge and disk) are modelled.  }
 

### 2015-02-27 python_codes/instruments/linear_regression/fitexy.py

@@ -232,16 +232,16 @@ def get_errors_ab(x,sigx,y,sigy,afit,bfit,ainit_err,binit_err,epsilonfit,chisqmi
 	err_afit = (a_range[jright] - a_range[jleft])/2
 	err_bfit = (b_range[kright] - b_range[kleft])/2	
 			
-	fig, ax = plt.subplots()
-	ax.imshow(chisqimg, interpolation='none', cmap=cm.Greys_r)
-	ax.axhline(y=jleft, linewidth=2, color = 'red')
-	ax.axhline(y=jright, linewidth=2, color = 'red')
-	ax.axhline(y=0.5*len(chisqimg_collapsed_a)-1, linewidth=2, color = 'red')
-	ax.axvline(x=kleft, linewidth=2, color = 'red')
-	ax.axvline(x=kright, linewidth=2, color = 'red')
-	ax.axvline(x=0.5*len(chisqimg_collapsed_b)-1, linewidth=2, color = 'red')
-	
-	plt.show()
+       #fig, ax = plt.subplots()
+       #ax.imshow(chisqimg, interpolation='none', cmap=cm.Greys_r)
+       #ax.axhline(y=jleft, linewidth=2, color = 'red')
+       #ax.axhline(y=jright, linewidth=2, color = 'red')
+       #ax.axhline(y=0.5*len(chisqimg_collapsed_a)-1, linewidth=2, color = 'red')
+       #ax.axvline(x=kleft, linewidth=2, color = 'red')
+       #ax.axvline(x=kright, linewidth=2, color = 'red')
+       #ax.axvline(x=0.5*len(chisqimg_collapsed_b)-1, linewidth=2, color = 'red')
+       #
+       #plt.show()
 	#print 'errors', merr_afit,perr_afit,merr_bfit,perr_bfit
 	#print 'errors', err_afit,err_bfit
 	return merr_afit,perr_afit,merr_bfit,perr_bfit

### 2015-02-27 python_codes/plots/comparison_mu_0/comparison.py

@@ -108,10 +108,10 @@ def comparison_mu_0():
 	ax1.text(-msigma_grade3-0.1, 45,   r'$\sigma_3$', fontsize=25)
 	
 	ax2.axis([3.99,-3.99,16.99,10.01])
-	ax2.set_xlabel(r'$\mu_{\rm 0, sph} - <\mu_{\rm 0, sph}>~{\rm [mag~arcsec^{-2}]}$', labelpad=20)
-	ax2.set_ylabel(r'$<\mu_{\rm 0, sph}>~{\rm [mag~arcsec^{-2}]}$', labelpad=20)
+	ax2.set_xlabel(r'$\mu_{\rm 0, sph} - <\mu_{\rm 0, sph}>~{\rm [mag~arcsec^{-2}]}$', labelpad=11)
+	ax2.set_ylabel(r'$<\mu_{\rm 0, sph}>~{\rm [mag~arcsec^{-2}]}$', labelpad=13)
 	
-	plt.subplots_adjust(left=0.15,bottom=0.15)
+	plt.subplots_adjust(left=0.11,bottom=0.15)
 	fig.subplots_adjust(hspace=0)
 	#plt.show()
 	plt.savefig(path_comp_plots + 'comparison_all_mu_0.eps', format='eps', dpi=1000)

### 2015-02-27 python_codes/plots/comparison_n/comparison.py

@@ -103,10 +103,10 @@ def comparison_log_n():
 	ax1.text(psigma_grade3+0.03, 40,   r'$\sigma_3$', fontsize=25)
 	
 	ax2.axis([-0.59,0.59,np.log10(0.7),np.log10(20)])
-	ax2.set_xlabel(r'$\log(n_{\rm sph}) - <\log(n_{\rm sph})>$', labelpad=20)
-	ax2.set_ylabel(r'$<\log(n_{\rm sph})>$', labelpad=20)
+	ax2.set_xlabel(r'$\log(n_{\rm sph}) - <\log(n_{\rm sph})>$', labelpad=15)
+	ax2.set_ylabel(r'$<\log(n_{\rm sph})>$', labelpad=15)
 	
-	plt.subplots_adjust(left=0.15,bottom=0.15)
+	plt.subplots_adjust(left=0.13,bottom=0.15)
 	fig.subplots_adjust(hspace=0)
 	#plt.show()
 	plt.savefig(path_comp_plots + 'comparison_all_n.eps', format='eps', dpi=1000)

### 2015-02-27 python_codes/plots/comparison_r_e/comparison.py

@@ -108,10 +108,10 @@ def comparison_log_r_e():
 	ax1.text(psigma_grade3+0.06, 55,   r'$\sigma_3$', fontsize=25)
 	
 	ax2.axis([-1.29,1.29,np.log10(1.01),np.log10(500)])
-	ax2.set_xlabel(r'$\log(R_{\rm e,sph}^{\rm maj} ~{\rm [arcsec]}) - <\log(R_{\rm e,sph}^{\rm maj}~{\rm [arcsec]})>$', labelpad=20)
-	ax2.set_ylabel(r'$<\log(R_{\rm e,sph}^{\rm maj} ~{\rm [arcsec]})>$', labelpad=20)
+	ax2.set_xlabel(r'$\log(R_{\rm e,sph}^{\rm maj} ~{\rm [arcsec]}) - <\log(R_{\rm e,sph}^{\rm maj}~{\rm [arcsec]})>$', labelpad=10)
+	ax2.set_ylabel(r'$<\log(R_{\rm e,sph}^{\rm maj} ~{\rm [arcsec]})>$', labelpad=10)
 	
-	plt.subplots_adjust(left=0.15,bottom=0.17)
+	plt.subplots_adjust(left=0.12,bottom=0.15)
 	fig.subplots_adjust(hspace=0)
 	#plt.show()
 	plt.savefig(path_comp_plots + 'comparison_all_r_e.eps', format='eps', dpi=1000)

### 2015-03-18 papers/MbhMsph/mm.tex
robi<3u

--- 2015-02-19 papers/data_paper/datapaper.tex
@@
 
-\shorttitle{Data paper}
+\shorttitle{M-M paper}
 \shortauthors{Savorgnan et al.}
@@
 
-\title{Data paper}
+\title{M-M paper, morphological bias }
 
@@
 \begin{abstract}
-abstract % 2d worse than 1d say it!!!
+abstract 
 \end{abstract}
@@
 \label{sec:int}
-Supermassive black holes and host bulges have very different sizes. 
-If the event horizon of the Galactic supermassive black hole was as big as a grain of sand of the Sahara desert, 
-then the black hole gravitational sphere-of-influence would be as big as the international airport of Cairo, 
-and the Galactic bulge would be as big as the Sahara desert itself.
-It is thus surprising that the masses of supermassive black holes ($M_{\rm BH}$) 
-scale with a number of properties of their host bulges, 
-indicating the non-gravitational origin of these correlations 
-(e.g.~\citealt{dressler1989,yee1992,kormendyrichstone1995,laor1997,magorrian1998,ferraresemerritt2000,gebhardt2000,graham2001,
-marconihunt2003,haringrix2004,graham2012bent,grahamscott2015}). \\
-The tightness of (i.e.~the small scatter about) the observed black hole mass correlations has led to the idea
-that black holes and host galaxies have coevolved with some sort of self-regulated growth.
-Exploring the evolution of this growth with cosmic time could help identify
-the driving mechanisms of the black hole -- galaxy coevolution.
-Observations at $z=0$ set the local benchmark from which to measure this evolution.
-Any complete theory or model describing the coevolution of galaxies and black holes must incorporate 
-all of the observed scaling relations, which also have to be consistent with each other.
-%Modern semi-analytic models use the observed black hole mass scaling relations 
-%to constrain the black hole accretion rate .
-Modern hydrodynamical simulations, such as EAGLE \citep{schaye2015}, calibrate the feedback efficiencies 
-to match the $z=0$ black hole mass -- galaxy mass relation.
-Such scaling relations can also be employed to predict the masses of black holes in other galaxies, where a direct
-measure of $M_{\rm BH}$ would be extremely time consuming or simply impossible due to technological limitations.
-Moreover, many accurate $M_{\rm BH}$ predictions enable one to derive 
-the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction}) 
-and space density (e.g.~\citealt{grahamdriver2007smbhmassdensity,comastri2015}). 
-All of these examples depend on the $z=0$ relations, 
-and as such the recalibration of the black hole mass -- bulge stellar mass ratio ($M_{\rm BH}/M_{\rm *,sph}$) in large bulges,
-from $0.1 - 0.2\%$ (e.g.~\citealt{haringrix2004}) to $0.36\%$ \citep{graham2012bent} and then $0.49\%$ \citep{grahamscott2015}, 
-has many substantial implications. \\
-Since the early stellar dynamical detections of black holes were carried out in the '80s 
-(see the references in the reviews by \citealt{kormendyrichstone1995}, \citealt{richstone1998} 
-and \citealt{graham2015bulges} for pioneering papers), 
-the number of (direct) black hole mass measurements has increased with time 
-and it has recently become a statistically meaningful sample  
-with which one can study SMBH demographics. 
-It is now generally accepted that supermassive black holes reside at the center of most, if not all, 
-massive galaxies, either quiescent or active. \\
-Massive, early-type galaxies are often composite systems. 
-The knowledge that many ``elliptical'' galaxies actually contain embedded stellar disks dates back  
-at least three decades  
-\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995}. 
-After examining long-slit and integral field unit spectroscopic observations of morphologically classified elliptical galaxies in the Fornax cluster, 
-\cite{donofrio1995}, \cite{graham1998fornax} and \cite{scott2014} concluded that only 3 bright galaxies do not harbour a disk-like component.
-Larger surveys with integral field spectrographs of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
-have further advanced this view of ``elliptical'' galaxies being all but simple and featureless pressure-supported systems.
-More than half of all morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.
-\cite{krajnovic2013} showed that ``fast rotators'' as a class are disk-galaxies or at least disk-like galaxies. 
-In their magnitude-limited survey, systems 
-without any signature of disk-like components (neither in the kinematics nor in the photometry) 
-dominate only the most massive end (beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
-Given the prevalence of disks, it is clearly important to perform bulge/disk decompositions, 
-if one is to properly explore the black hole-bulge connection. 
-Indeed, separating the disk light from that of the bulge has led to the discovery of the missing population of compact, massive spheroids 
-in the local Universe {\bf (Graham, Dullo, Savorgnan 2015)}.
-If we are to properly understand the evolution of galaxies, we need to understand their components.\\
-Measuring the photometric and structural properties of a galaxy's spheroidal component requires the ability to 
-separate it from the rest of the galaxy. 
-Such galaxy decomposition involves a parametric analysis that allows one to fit the surface brightness distribution
-of galaxies using a combination of analytic functions (usually one function per
-galaxy component, such as bulges, disks, bars, nuclei, etc.).
-The one-dimensional (1D) technique involves fitting isophotes to the galaxy image, extracting the (one-dimensional) surface 
-brightness radial profile and modeling it with a combination of analytic functions.
-With the two-dimensional (2D) technique, one fits analytic functions directly to the 2D images. \\
-Over the past eight years, five independent studies 
-\citep{grahamdriver2007,sani2011,vika2012,beifiori2012,lasker2014data,lasker2014anal} have attempted galaxy decomposition
-in order to derive the bulge parameters and explore their relation with the black hole masses. 
-{\bf Rusli has explored the black hole - core relation.}
-Interestingly, the past studies used almost the same sample of galaxies, yet they claimed some contradictory conclusions.
-For example, one study \citep{grahamdriver2007} obtained a good $M_{\rm BH}-n_{\rm sph}$ correlation
-(the bulge S\'ersic index $n_{\rm sph}$ is a measure of the central radial concentration of stars, \citealt{trujillo2001}), 
-whereas the remaining four did not.
-In addition, \cite{lasker2014anal} {\bf who did not work at 3.6um} 
-declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity and the bulge luminosity, 
-as opposed to \cite{beifiori2012}, who claimed that the bulge mass is a better tracer of $M_{\rm BH}$ than the galaxy mass.
-The past studies did not converge to the same conclusions 
-because their best-fit models for the same galaxy were often 
-significantly different and not consistent with each other in terms of fitted components. 
-Moreover, none of these studies attempted an individual galaxy-by-galaxy 
-comparison of their models with the previous literature. 
-We have now made this comparison and performed the optimal decompositions,
-using $3.6~\rm \mu m$ \emph{Spitzer} satellite imagery, 
-which is an excellent proxy for the stellar mass, superior to the $K$-band (\citealt{sheth2010} and references therein).
-We will use these in a series of forthcoming papers to obtain improved black hole mass scaling relations 
-using the largest sample (66) of galaxies to date.
+More than two and a half decades ago, 
+\cite{dressler1989} foresaw a ``rough scaling of black hole mass with the mass of the spheroidal component'', 
+as suggested by the sequence of five galaxies (M87, M104, M31, M32 and the Milky Way). 
+His ``rough scaling'' was a premature version of the nowadays popular correlation between black hole mass, $M_{\rm BH}$,  
+and host spheroid luminosity, $L_{\rm sph}$, and also host spheroid mass, $M_{\rm sph}$ 
+\citep{yee1992,kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}. 
+These early studies were dominated by high-mass, early-type galaxies, 
+for which they reported a quasi-linear $M_{\rm BH} - M_{\rm sph}$ relation, 
+in agreement with a dry-merging formation scenario. 
+Subsequent studies of the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm sph}$ diagrams 
+(\citealt{ferrareseford2005,lauer2007,graham2007,graham2008bar,gultelkin2009,sani2011,beifiori2012,erwingadotti2012,
+vika2012,vandenbosch2012,mcconnellma2013,kormendyho2013,rusli2013}; 
+see \citealt{graham2015bulges} for an extensive review about the early discovery and successive improvements of these correlations)
+used similar galaxy samples, which remained dominated by high-mass, early-type objects having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 
+and therefore recovered a near-linear relation. 
+However, the consensus about a linear $M_{\rm BH} - M_{\rm sph}$ correlation was not unanimous. 
+Some studies reported a slope steeper than 1,  
+or noticed that low-mass spheroids were downwards offset from the relation traced by their high-mass counterparts 
+\citep{laor1998,wandel1999,laor2001,ryan2007}.
 
-This paper is structured as follows.
-Section \ref{sec:data} presents the galaxy sample and imaging data-set used to conduct this study. 
-Section \ref{sec:anal} describes how we performed the galaxy decompositions, 
-i.e.~how we identified and modeled the sub-components that constitute our galaxies. 
-In Section \ref{sec:res} we outline the results from our analysis and discuss the error analysis. 
-Section \ref{sec:concl} summarizes our main conclusions. 
-The individual galaxy decompositions are made available in the electronic version of this manuscript.
+lasker
 
@@
 \label{sec:data}
-%\subsection{Initial sample}
-Our initial galaxy sample (see Table \ref{tab:sample}) consists of 75 objects for which a dynamical detection of the black hole mass 
-had been reported in the literature at the time we started this project, 
-and for which at least one $3.6~\rm \mu m$ \emph{Spitzer}/IRAC\footnote{IRAC is the InfraRed Array Camera onboard the \emph{Spitzer} Space Telescope.} 
-observation was publicy available.
-Black hole masses were drawn from the catalog of \citet{grahamscott2013} for 70 galaxies,
-from \citet{rusli2013bhmassesDM} for 4 galaxies and from \citet{greenhill2003} for 1 galaxy. 
-As explained in Section \ref{sec:res}, 
-this initial sample was ultimately reduced to 66 galaxies for which useful bulge parameters could be obtained.
-
-%\clearpage
-\input{table_sample.tex}
-%\noindent
-\input{table_observations.tex}
-
-\subsection{\emph{Spitzer}/IRAC observations}
-\subsubsection{Data acquisition}
-For each of our 75 galaxies, we downloaded from the 
-Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
-all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs), 
-listed in Table \ref{tab:obs}.
-Each AOR is an individual Spitzer observation sequence, and
-includes a number of data frames (the individual exposures) and the calibration data.
-The data frames were selected to be %``enhanced Level 1 products'', or
-corrected Basic Calibrated Data (cBCD), produced by the IRAC Level 1 pipeline. 
-This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
-and performs dark subtraction, flatfielding correction and flux calibration (into units of $\rm MJy~sr^{-1}$). 
-The final product (the BCD) is a flux-calibrated image which has had all the well-understood instrumental signatures removed.
-BCD frames are further processed through an ``artifact correction'' pipeline 
-that mitigates the commonly found artifacts of stray light, saturation, ``muxbleed'' and column pulldown\footnote{Stray light 
-includes scattered light from stars outside the array location as well as filter ghosts from bright stars. 
-Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
-It appears as a decaying trail of pixels, repeating every fourth column.
-``Column pulldown'' is caused by a bright pixel that triggers a bias shift within its respective column, 
-creating a lower background value throughout the entire column than in the surrounding columns.}.
-After the artifact correction has been applied, the BCD becomes a cBCD.
-
-\subsubsection{Mosaicking}
-We performed image mosaicking using the MOPEX package \citep{makovozmarleau2005mopex}.
-This enabled the production of suitably wide-field-of-view images for accurate sky background subtraction.
-Individual cBCD frames with exposure time of $1~\rm sec$ were rejected.
-Permanent or semi-permanent bad pixels, contained in a semi-static mask (the ``pmask''), were ignored.
-Each AOR is associated to a specific pmask. 
-Therefore, when multiple AORs were available for the same galaxy, 
-we merged the different pmasks. 
-Cosmic ray rejection was performed with the dual outlier and multi-frame techniques.
-The pixel size of the mosaic was set to be the same as the input cBCD frames ($1''.22 \times 1''.22$).
-For $3.6~\rm \mu m$ observations with this pixel scale, 
-the photometric zeropoint magnitude is $m_{\rm zp} = 17.26 \rm~mag$.
-The orientation of the mosaic was set to the average rotation angle of the input cBCD frames. 
-%{\bf TBD: not n-e oriented or re-sampled because problems with 2d PSF. }
-Individual cBCD frames were combined together into a single mosaic with the default linear interpolation algorithm.
-
-\subsubsection{Overlap correction}
-Before generating a mosaic, MOPEX can perform background matching among the individual frames
-by using the \emph{overlap} module. 
-This module calculates and applies an additive correction to the individual frames,
-producing a consistent background across the mosaicked image.
-According to the \emph{Spitzer Data Cookbook}, the use of the \emph{overlap} module is not particularly recommended for 
-$3.6~\rm \mu m$ observations. 
-However, after a visual inspection of the mosaics obtained without activating the \emph{overlap} module,
-we found that all the mosaics obtained from multiple AORs were affected by patchiness, 
-due to bias fluctuations in the CCD array.
-For this reason, we re-generated the multiple-AORs mosaics by activating the \emph{overlap} correction,
-which successfully removed the ``chessboard'' pattern (see Figure \ref{fig:overlap} for an example).
-
 \begin{figure}[h]
 \begin{center}
-\includegraphics[width=0.49\columnwidth]{images/m49nooverlap.eps}
-\includegraphics[width=0.49\columnwidth]{images/m49overlap.eps}
-\caption{Example of the \emph{overlap} correction. 
-The image mosaic of the galaxy M49 was obtained by co-adding frames coming from 8 different AORs.
-The evident patchiness (left image) was removed (right image) using the \emph{overlap} module.}
-\label{fig:overlap}
+\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
+\caption{}
+\label{fig:}
 \end{center}
@@
 
-\subsubsection{Sigma mosaics}
-For each individual cBCD frame, the IRAC Level 1 pipeline calculates the uncertainty associated to each pixel
-and produces an uncertainty frame (or sigma frame).
-The initial uncertainty is estimated as the Poisson noise in electrons plus the readout noise added in quadrature
-($\sigma^2 = \sigma^2_{\rm readoutnoise} + \sigma^2_{\rm Poisson}$).
-This initial sigma frame is carried through the pipeline, and additional uncertainties (e.g.~dark current and flat field uncertainties) 
-are added in quadrature when appropriate.
-When MOPEX generates an image mosaic, it also produces the associated sigma mosaic 
-by interpolating the individual uncertainty frames and co-adding them,
-following the standard assumption of additive variances.
-
-\subsubsection{Sky subtraction}
-Sky subtraction was performed manually on the image mosaics using the tasks {\tt marksky} and {\tt skyfit} 
-of the IRAF\footnote{IRAF is the Image Reduction and Analysis Facility, 
-distributed by the National Optical Astronomy Observatory, 
-which is operated by the Association of Universities for Research in Astronomy (AURA) 
-under cooperative agreement with the National Science Foundation.} 
-package GALPHOT\footnote{GALPHOT was developed in the IRAF - STSDAS environment mainly by 
-W. Freudling, J. Salzer, and M. P. Haynes \citep{haynes1999galphot}.}.
-The task {\tt skyfit} also provided an estimate of the sky root mean square ($RMS_{\rm sky}$).
-%sky value also checked with Galfit
-
-\subsubsection{Additional aestethic corrections}
-\label{sec:aesth}
-The image mosaics of 4 galaxies (NGC 0821, NGC 2974, NGC 4291, NGC 4459) were found to be affected 
-by bright, highly saturated stars lying close to the target galaxies.
-These stars were modeled and subtracted using the software Galfit \citep{peng2010} 
-and the extended IRAC Point Response Function (PRF) image at $3.6~\rm \mu m$.
-This helped remove the extended wings and spikes of the saturated stars 
-(see Figure \ref{fig:aesth} for an example).
-
+\section{Analysis}
+\label{sec:anal}
 \begin{figure}[h]
 \begin{center}
-\includegraphics[width=0.49\columnwidth]{images/n4459brightstar.eps}
-\includegraphics[width=0.49\columnwidth]{images/n4459nobrightstar.eps}
-\caption{Example of aestethic correction.
-The images show the mosaic of the galaxy NGC 4459 before (left) and after (right) the partial removal 
-of a bright saturated star.}
-\label{fig:aesth}
-\end{center}
-\end{figure}
-
-\subsubsection{Image masking}
-Galactic stars and any other objects different from the target galaxy 
-were masked through a two-step procedure.
-First, we created an initial mask using the IRAF task 
-{\tt objmasks} that identifies objects by threshold sigma detection.
-Then, we refined each mask by hand, using the software 
-SAOImage DS9\footnote{SAOImage DS9 development has been made possible by funding 
-from the Chandra X-ray Science Center (CXC) 
-and the High Energy Astrophysics Science Archive Center (HEASARC).} 
-in conjunction with the IRAF task 
-{\tt mskregions}. %\footnote{{\tt mskregions} is part of the {\tt proto} package.}.
-We identified and carefully masked not only contaminating sources located in the field of the image mosaic,
-but also objects overlapping with the target galaxy, such as foreground stars, background galaxies, 
-globular clusters or red giant stars.
-
-\subsubsection{1D PSF}
-A universal, average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
-A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
-has the following form:
-\begin{equation}
-\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
-\end{equation}
-where $R$ is the projected galaxy radius, $\mu_{\rm 0}$ is the central surface brightness, and 
-$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
-of fixed center and zero background was fit to the 
-(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
-%We employed both a Gaussian and a Moffat \citep{moffat1969} profile. 
-The best-fit parameters of the 20 stars were then averaged together. 
-Doing so, we obtained %$FWHM = 2''.03$ for the Gaussian function,
-$(\alpha, \beta) = (2''.38, 4.39)$ %for the Moffat function
-(see Appendix \ref{sec:app1} for the analytical expressions of the Moffat function).
-
-\subsubsection{2D PSF}
-The IRAC support team provides users with a two-dimensional instrument Point Response Function (PRF) at $3.6~\rm \mu m$.
-However, while this helped remove the extended wings of saturated stars (see Section \ref{sec:aesth}), 
-we found this PRF to be inadequate for the purposes of our modelling.
-In fact, the $FWHM$ of the IRAC instrument PRF ($\sim 1''.8$), as measured by the IRAF task {\tt imexamine}, 
-is systematically smaller than the average $FWHM$ of ``real'' stars ($\sim 2''.0$). 
-Figure \ref{fig:psf} illustrates this issue.
-We also tested the IRAC PRF by providing it as the input Point Spread Function (PSF) for Galfit 
-and fitting a number of stars in different image mosaics.
-A visual inspection of the fit residuals confirmed that the IRAC instrument PRF is narrower than ``real'' point sources.
-For this reason, we constructed our 2D PSF according to the following method 
-(as directed by C. Peng, private communication).\\
-We provided the IRAC instrument PRF as the input PSF for Galfit 
-and simultaneously fit 7 bright stars (belonging to different mosaics), 
-modeling the stars with Moffat profiles 
-and constraining all the profiles to have the same $(\alpha, \beta)$, position angle and axis ratio.
-The 2D PSF image was then obtained by taking the best fit Moffat model -- the same best-fit model for all 7 stars, by construction -- 
-and convolving it with the IRAC instrument PRF.
-The advantage of this method is to obtain a 2D PSF that is wider than the instrument PRF, 
-but maintains the asymmetric features of the instrument PRF (e.g.~wings and spikes).
-%This procedure was repeated using a Moffat profile in place of the Gaussian profile.
-We then tested this 2D PSF 
-on a number of stars (these stars were different from the 7 stars employed to build the 2D PSF image)
-and verified that it correctly reproduces the shape of ``real'' point sources.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=1\columnwidth, trim = 220 30 20 20, clip=True]{images/psf.eps}
-%\includegraphics[width=1\columnwidth]{images/star1_cut.eps} \\
-%\includegraphics[width=1\columnwidth]{images/PRF_IRACch1_129_129_cut.eps}
-\caption{Normalized flux versus radial distance 
-from the image centroid of an observed point source (bottom panel) 
-and of the IRAC instrument Point Response Function (PRF, top panel). 
-The normalized flux is given in arbitrary units, 
-and the radial distance is in units of pixel size of the IRAC detector (1 pixel = $1''.22$).
-The blue solid line shows our 1D Moffat PSF model,
-which has been normalized to intersect the data point with the largest flux. 
-The $FWHM$ of the IRAC PRF is clearly smaller than that of a ``real'' star.
-The inserts display the images of the observed point source and the IRAC PRF.}
-\label{fig:psf}
-\end{center}
-\end{figure}
-
-\subsection{Additional data}
-\label{sec:adddata}
-\subsubsection{Kinematics}
-\label{sec:kinem}
-A kinematical classification (slow/fast rotator) is available for 34 of our 75 galaxies 
-from the ATLAS$^{\rm 3D}$ survey \citep{atlas3dIII-MNRAS} 
-and for 3 additional galaxies from \citet{scott2014}.
-This classification (Table \ref{tab:sample}, column 7) 
-concerns the kinematic properties of galaxies within the spectroscopic instrument's field-of-view, 
-but does not contain additional information -- crucial for our analysis -- about kinematic substructures, 
-such as embedded disks or kinematically decoupled components, 
-which can require separate modeling.
-For this reason, we also visually inspected the velocity fields of our galaxies, 
-when available from the literature.
-Velocity maps were taken from the ATLAS$^{\rm 3D}$ survey for 34 galaxies 
-(observed with SAURON by \citealt{krajnovic2011}),
-from \citet{scott2014} for 2 galaxies 
-(observed with WiFeS)
-and from the SLUGGS survey for 12 galaxies 
-(observed with DEIMOS by \citealt{arnold2014}).
-While the field-of-views of SAURON ($33'' \times 41''$) and WiFeS ($25'' \times 38''$) 
-reach to about one galaxy effective radius (for our local galaxies),
-observations taken with DEIMOS can probe the galaxy kinematics well beyond two effective radii.
-
-\subsubsection{AGNs and nuclear dust}
-The X-ray, UV and optical radiation 
-emitted by the the accretion disks of Active Galactic Nuclei (AGNs) can stimulate infrared thermal emission 
-from circumnuclear dust, if present. 
-This means that if a galaxy hosts an optical AGN \emph{and} a certain amount of nuclear dust,
-we may detect some non-stellar nuclear emission at $3.6~\rm \mu m$.
-It is therefore important to identify which of our galaxies have both an optical AGN and circumnuclear dust.
-To help with this task, we searched NED\footnote{NED is the NASA/IPAC Extragalactic Database.} 
-for the individual galaxies and their associated literature.
-Unsurprisingly, dusty AGNs were more frequently found in late-type spiral galaxies, 
-and modelled by us with either a point source or a PSF-convolved Gaussian.
-
-\subsubsection{S\'ersic/core-S\'ersic classification}
-\label{sec:corser}
-Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or bulges) 
-with partially depleted cores, 
-i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
-Such deficits were first noted and researched by \cite{kingminkowski1966}.
-S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
-Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs
-\citep{dullograham2013cores,rusli2013}.
-The majority are thus unresolved in our image mosaics. 
-We masked these unresolved cores (identified in high-resolution images, see Table \ref{tab:sample}) by excluding the surface brightness profile 
-within 3 PSF's $FWHM$ from the galaxy center.
-In case of cores with sizes exceeding the PSF's $FWHM$, we excluded the data points within the size of the core 
-plus 3 PSF's $FWHM$.
-The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
-comes from the compilation of \citet{savorgnangraham2014},
-who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
-When no high-resolution image analysis was available from the literature, 
-they inferred the presence of a partially depleted core based on the stellar velocity dispersion, $\sigma$:
-a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
-or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
-This resulted in us assigning cores to just 2 galaxies using this alternative method when 
-no high resolution image was available.
-
-\section{Analysis}
-\label{sec:anal}
-\subsection{Isophotal analysis}
-We performed an isophotal analysis of our galaxies using the IRAF task {\tt ellipse} \citep{taskellipse}, 
-which fits elliptical isophotes to galaxy images.
-The center of the isophotes was held fixed, while the ellipticity ($\epsilon$), the position angle ($P.A.$),  
-and the amplitude of the fourth harmonic\footnote{The amplitude of the fourth harmonic deviations from perfect ellipses 
-($B4$) parameterizes the diskyness ($B4>0$) or boxyness ($B4<0$) of the isophotes.} ($B4$) were allowed to vary with radius.
-The step in semi-major axis length between successive ellipses was first set to increase linearly, 
-and then geometrically in our second run\footnote{In the case of linear steps, 
-the semi-major axis length for the next ellipse was calculated by adding $1$ pixel to the current length.
-In the case of geometric steps, the semi-major axis length for the next ellipse 
-was calculated as $1.1$ times the current length.}.
-As a result, for each galaxy we produced respectively a ``linearly sampled'' and a ``logarithmically sampled'' 
-surface brightness profile along the major-axis. 
-Major-axis surface brightness profiles were additionally converted into the equivalent-axis,
-i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$), 
-equivalent to the circularized radius.
-This resulted in 4 profiles per galaxy.
-Isophotes corresponding to an intensity less than 
-three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$) were ignored.
-Some surface brightness profiles were truncated at our discretion before the $3 \times RMS_{\rm sky}$ limit, 
-according to specific technical reasons (e.g.~contamination from light of a neighboring galaxy, 
-disturbed morphology in the galaxy outskirts, etc.).
-Individual cases are discussed in Section \ref{sec:indgal}.
-
-\subsection{Unsharp masking}
-Unsharp masking is an image sharpening technique that is useful to reveal asymmetric structures in galaxies, 
-such as bars or (inclined) embedded disks. 
-First, the original galaxy image was smoothed with a Gaussian filter.
-Then, the original image was divided by the smoothed one. 
-The result of such an operation is the ``unsharp mask''. 
-The asymmetric features revealed by this technique have sizes 
-comparable to the $FWHM$ of the Gaussian kernel used for the smoothing.
-Therefore, for each galaxy, we produced a set of different unsharp masks by varying the $FWHM$ of the filter,
-to identify all the asymmetric features that could bias the fitting process 
-and may therefore need to be considered during the galaxy modelling phase.
-This information was used in combination with kinematic and AGN information discussed in Section \ref{sec:adddata}.
-
-\subsection{1D fitting routine}
-The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
-This software can fit an observed surface brightness profile with any linear combination of 
-a set of analytical functions (S\'ersic, exponential, Gaussian, Moffat, Ferrer, symmetric Gaussian ring etc. 
-see Appendix \ref{sec:app1} for a description of the analytical form of these profiles).
-At each iteration, 
-the model is numerically convolved with a Moffat filter, to account for PSF effects, 
-and then matched to the data.
-The minimization routine is based on the Levenberg-Marquardt algorithm.
-During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
-surface brightness profile, 
-although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
-The all too often over-looked {\bf ??} with (signal-to-noise)-based weighting schemes 
-is that they immediately become an incorrectly biased weighting schemes when additional components are present but not modelled.
-For example, fitting a S\'ersic model to what is actually a nucleated elliptical galaxy immediately {\bf ??} 
-a (signal-to-noise)-based weighting scheme 
-and results in S\'ersic parameters which describe the bulge less accurately than had no (signal-to-noise)-weighting been used.
-While we have paid careful attention to the components in each galaxy, 
-and more so than the studies upon which our work is building from,
-this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
-What is best in theory is not always best in practice -- in this case, because theory does not allow for unknown additional components
-that are modelled.
-
-\subsection{Smoothing technique}
-\label{sec:smooth}
-Some nearby galaxies in our sample have very large apparent sizes 
-and for them we obtained surface brightness profiles more extended than $8~\rm arcmin$.
-This means that their outermost (significant) isophote 
-corresponds to a projected galactic radius $R$ 
-of more than $240$ times the $FWHM$ of the instrumental PSF.
-Such level of spatial resolution is unnecessary for the purposes of our analysis 
-and, especially in the case of a clumpy star forming galaxy, 
-it results in a ``noisy'' surface brightness profile.
-Moreover, in the case of a linearly sampled light profile,
-it significantly prolongs the computational time of the fitting routine 
-(because, at each iteration, the PSF convolution is performed numerically on a large array).
-To overcome this problem, we introduced a method to which we refer as the ``smoothing technique''.
-This method was applied to the galaxies M31, M81, NGC 4945 and NGC 5128.
-For each of these galaxies, we took the image mosaic and we convolved it with a Gaussian filter 
-whose $FWHM$ was larger than the $FWHM$ of the instrumental PSF.
-We then ran {\tt ellipse} on the convolved image and extracted 
-``linearly sampled'' and ``logarithmically sampled'' surface brightness profiles. 
-For the ``linearly sampled'' profiles, we set the radial step between contiguous isophotes to be 
-comparable to the $FWHM$ of the smoothing Gaussian filter.
-Doing so, we reduced the number of fitted isophotes and we also produced smoother surface brightness profiles.
-Before the software fit a smoothed light profile, the model to be fit was convolved twice:
-the first time to account for PSF effects, 
-and the second time to account for the artificial Gaussian smoothing applied to the image mosaic.
-
-\subsection{Identifying and modeling sub-components}
-\label{sec:cpts}
-In this Section we give a general overview of the guidelines that we followed to identify and model 
-the sub-components that constitute our galaxies. 
-However, given the level of accuracy and detail to which each galaxy decomposition has been performed in our analysis,
-it is hard to encompass all aspects of this matter in a few paragraphs.
-The modeling of each galaxy represented a particular and original problem, 
-and we remand the reader to Section \ref{sec:indgal},
-where we provide individual descriptions of the galaxies that we analyzed. \\
-As stressed in Section \ref{sec:int}, our investigation is primarily focused on the central spheroidal components 
-of galaxies.
-We assumed \emph{a priori} that each of our galaxies has a unique spheroidal component, 
-that we modeled with a S\'ersic profile. \\
-Disks were usually fit with the exponential model, 
-although in the case of highly inclined or edge-on systems we preferred using an $n < 1$ S\'ersic function. 
-\citet{pastrav2013a,pastrav2013b} showed that, due to projection effects, their simulated images of inclined galaxy disks 
-are better fit by a S\'ersic function with $n < 1$ than by a pure exponential model.
-The inclined, embedded disks of some ``elliptical'' galaxies were described with Ferrer functions, rather than a $n < 1$ S\'ersic function. 
-This choice was partly motivated by the fact that a S\'ersic + Ferrer model is less degenerate than a S\'ersic + S\'ersic model, 
-since the S\'ersic profile can assume any concave ($n > 1$) or convex ($n < 1$) curvature, 
-whereas the Ferrer profile can only have a negative curvature as required for an inclined disk. \\
-The presence of large-scale disks, such as those of lenticular and spiral galaxies, 
-were known \emph{a priori} from the galaxy morphological classification (as listed on NED), 
-although some of them were re-classified by us as having intermediate-scale embedded disks.
-These were identified in a number of different ways. 
-If highly inclined, they can obviously be spotted from the galaxy image or the unsharp mask.
-Local maxima in the ellipticity and fourth harmonic profiles 
-can provide footprints of less obvious embedded disks.
-In particular, the ellipticity profile helps distinguish embedded disks from large-scale disks.
-Galaxy disks typically have fixed ellipticity, reflecting their inclination to our line of sight.
-On the other hand, spheroids can have their ellipticities varying with radius,
-but they are usually rounder than inclined disks, thus their average ellipticities are lower than those of inclined disks.
-If the ellipticity profile of a galaxy increases with radius, 
-this can be ascribed to an inclined disk that becomes progressively more important over the spheroid,
-whereas a radial decrease of ellipticity signifies the opposite case.
-Therefore, in a situation where a disk is identified from the galaxy image, 
-but its extent (large- or intermediate-scale) is ambiguous,
-the shape of the ellipticity profile can be decisive. 
-Another way to establish the presence of an embedded disk is to look at the velocity map of a galaxy,
-following the approach of \citet{arnold2014}. 
-A local angular momentum decrease with increasing radius is indicative of an intermediate-scale disk 
-that fades toward larger radii. \\
-%As an illustration, we consider the galaxy NGC 3377.
-%For this galaxy, \citet{arnold2014} reported a strong decline in local specific angular momentum beyond $\sim 35''$, 
-%with a disk-to-bulge transition occurring at about $\sim 50''$.
-%They did attempt a three-component decomposition (accounting for a bulge, an embedded disk and a central cusp), 
-%but unfortunately they fit the spheroidal component with a limited two-parameter $R^{1/4}$ profile {\bf TBD: cite de vaucouleurs} 
-%rather than a three-parameter $R^{1/n}$ S\'ersic function.
-%Here we used a surface brightness profile twice as extended as that used by \citet{arnold2014} 
-%and we identified a nuclear disk and an intermediate-scale disk, both embedded in a larger spheroidal component (see Figure \ref{fig:n3377ex}).
-%The presence of an intermediate-scale disk is evident from the unsharp mask of the image mosaic 
-%and also from the ellipticity profile, which increases with increasing radius until $R \sim 45''$ (along the major-axis) 
-%and dramatically drops at larger radii.
-%The nuclear disk can be spotted from the peak at $R \sim 5''$ in the $B4$ profile.
-%In our galaxy model for NGC 3377, 
-%the difference between the S\'ersic profile of the bulge and the exponential profile of the intermediate-scale disk is minimum in correspondence 
-%of the maximum ellipticity, 
-%thus our model correctly reproduces the isophotal properties of the galaxy. 
-%The residuals of the fit, especially along the major-axis, display some minor structures which indicate that 
-%the bulge S\'ersic index might have been slightly overestimated.
-%This could be due to the fact that the embedded disk would be better described by a truncated exponential function.
-%Alternatively, a contribution from a stellar halo (not included in our model) at large radii could be the reason of a 
-%too large S\'ersic index for the bulge. 
-%Our equivalent-axis decomposition results in a bulge component that accounts for 94\% of the total luminosity, 
-%an intermediate-scale embedded disk contributing to 5\% 
-%and a nuclear disk with 1\% of the total light. \\
-%A similar situation occurs for the galaxy M59 (see Figure \ref{fig:m59ex}), 
-%for which our equivalent-axis model returns a spheroidal component and an embedded disk 
-%contributing to 92\% and 8\% of the total light respectively. \\
-%The edge-on embedded disk of the S\'ersic galaxy NGC 1332 (see Figure \ref{fig:n1332ex}) was hard to model with an exponential function, 
-%leading us to prefer a low-$n$ S\'ersic profile. 
-%Our equivalent-axis decomposition returns a spheroidal component accounting for 95\% of the total light,
-%and an embedded disk accounting for the remaining 5\%.
-%In passing, we note that the bulge-disk decomposition performed by \citet{rusli2011} on NGC 1332 
-%is significantly different from our best-fit model.
-%\citet{rusli2011} did not identify an intermediate-scale embedded disk, 
-%but instead proposed a model featuring a S\'ersic bulge ($n \sim 2.3$, $R_{\rm e} \sim 8''$), accounting for 43\% of the total light, 
-%and a large-scale exponential disk. 
-%This result led them to the conclusion that NGC 1332 is a disk dominated lenticular galaxy 
-%and is displaced from the $M_{\rm BH} - L_{\rm K,sph}$ (black hole mass vs. $K$-band spheroid luminosity) relation of \citet{marconihunt2003} 
-%by an order of magnitude along the $M_{\rm BH}$ direction.
-%Assuming instead that, as suggested by our model, 
-%the galaxy spheroid is a factor of two more luminous than what claimed by \citet{rusli2011}, 
-%NGC 1332 would no longer be an outlier in the $M_{\rm BH} - L_{\rm K,sph}$ diagram (see Figure \ref{fig:n1332pl}), 
-%perfectly fitting within the $1\sigma$ scatter of the $M_{\rm BH} - L_{\rm K,sph}$ relation for S\'ersic bulges of \citet{grahamscott2013}. \\
-Bars are usually recognizable from galaxy images and unsharp masks, 
-although local maxima/minima or abrupt changes in the radial profiles of the isophotal parameters 
-can provide additional evidence for less obvious bars. 
-As noted, we were able to successfully fit bars with a Ferrer function or a low-$n$ S\'ersic model ($n \sim 0.2$). \\
-The presence of a nuclear component -- either resolved or unresolved -- was generally expected in 
-(but not restricted to) galaxies that host an optical AGN and circumnuclear dust.
-Nuclear stellar disks and nuclear star clusters fall into the category of nuclear components too,
-but their identification can be more subtle than for AGNs.
-Nuclear clusters have typical sizes of a few parsecs, 
-therefore for the majority of our galaxies they are unresolved in \emph{Spitzer}/IRAC $3.6~\rm \mu m$ observations.
-If an identification from high-resolution observations was available from the literature, we relied on that, 
-otherwise we concluded that a galaxy was nucleated from an excess of nuclear light in the residuals of the 
-fit\footnote{This conclusion was drawn after going through the following steps. 
-First we identified all the sub-components of a galaxy 
-(assuming that the galaxy was not nucleated), built a model accordingly and fit it to the data.
-If the residuals of the fit showed a nuclear light excess, 
-we repeated the fit by excluding the data points within the nuclear region.
-Only after checking that the outcome of the last fit was consistent with a fit that included a small nuclear component, 
-we inferred the presence of a stellar nuclear component.}.
-Unresolved nuclear components were fit with our optimal Moffat PSF,
-whereas resolved nuclear components were modeled with (PSF-convolved) narrow Gaussian functions. \\
-Rings were identified from galaxy images and unsharp masks, and modeled with symmetric Gaussian ring profiles. \\
-As an illustration, we consider the galaxy NGC 2974, 
-a spiral galaxy which has been misclassified as an elliptical galaxy in the RC3 catalog \citep{RC3}. 
-This galaxy hosts a Seyfert AGN \citep{veroncettyveron2006} and filamentary dust in its center \citep{tran2001}.
-NGC 2974 is classified as a fast rotator by the ATLAS$^{\rm 3D}$ survey, 
-and indeed the velocity map obtained by the SLUGGS survey shows that the galaxy kinematics is rotation-dominated 
-well beyond three effective radii ($R>150''$), 
-as expected from a large-scale disk. 
-%\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + Gaussian-AGN 
-%($R_{\rm e} = 27''.2$, $n = 3.0$). 
-From an inspection of the unsharp mask, we identified a ring at $R \sim 50''$, 
-which might be a residual of two tightly wound spiral arms,
-and an elongated bar-like component within $R \lesssim 30''$,
-that is in addition to the more spherical bulge 
-and produces a peak in the ellipticity and position angle profiles at $R \sim 20''$.
-Our 1D galaxy decomposition for NGC 2974 (Figure \ref{fig:n2974ex}) consists of a S\'ersic bulge, an exponential large-scale disk,
-a Ferrer bar, a Gaussian nuclear component (AGN) and a Gaussian ring.
-Although the ring is extremely faint, it is important to account for it in the galaxy decomposition. 
-A model without the ring component results in a ``steeper'' exponential profile for the disk 
-(i.e.~the exponential model has a smaller scale length and a brighter central surface brightness) 
-and produces bad residual structures within $R \lesssim 40''$.
-Our best-fit model returns a $3.6~\rm \mu m$ bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 8.3\rm~arcsec$, 
-equivalent-axis S\'ersic index $n_{\rm sph}^{\rm eq} = 1.2$ and apparent magnitude $m_{\rm sph} = 8.65~\rm mag$.
-\cite{sani2011} modeled NGC 2974 with a S\'ersic bulge and a Gaussian nuclear component (AGN), 
-but did not account for the large-scale disk.
-From their best-fit 2D model, they obtained a three times larger 
-$3.6~\rm \mu m$ bulge major-axis effective radius ($R_{\rm e,sph}^{\rm maj} = 27.2\rm~arcsec$), 
-a 2.5 times larger S\'ersic index ($n_{\rm sph} = 3$),
-and a significantly brighter apparent magnitude ($m_{\rm sph} = 7.28~\rm mag$).
-
-%\begin{figure*}[h]
-%\begin{center}
-%\includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
-%\caption{Best-fit model and isophotal parameters for the galaxy NGC 3377. 
-%The left panels refer to the major-axis $R_{\rm maj}$, 
-%whereas the right panels refer to the equivalent-axis $R_{\rm eq}$.
-%The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
-%The black points are the observed data.  
-%The color lines represent the individual (PSF-convolved) model components:
-%red=S\'ersic (bulge), blue=exponential (disk). 
-%The best-fit parameters for the S\'ersic profile are included.
-%The total (PSF-convolved) model is shown with a black dashed line, 
-%but it is hard to distinguish because it almost perfectly matches the data.
-%The horizontal grey dashed line indicates the $3~RMS_{\rm sky}$ level.
-%$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
-%$\Delta \mu$ are the residuals from the fit.
-%The six panels below show the ellipticity ($\epsilon$), position angle ($PA$) and $B4$ radial profiles.
-%}
-%\label{fig:n3377ex}
-%\end{center}
-%\end{figure*}
-
-\begin{figure*}[h]
-\begin{center}
-\includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
-\caption{Best-fit model, and isophotal parameters, for the galaxy NGC 2974. 
-The left panels refer to the major-axis $R_{\rm maj}$, 
-while the right panels refer to the equivalent-axis $R_{\rm eq}$.
-The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
-The black points are the observed data.  
-The color lines represent the individual (PSF-convolved) model components:
-red=S\'ersic (bulge), dark blue=exponential (disk), green=Gaussian (AGN), cyan=Ferrer (bar), gray=Gaussian ring (ring). 
-The best-fit parameters for the S\'ersic bulge model are inset.
-The total (PSF-convolved) model is shown with a black dashed line, 
-but it is hard to distinguish because it almost perfectly matches the data, 
-hence the residual profile is additionally shown as $\Delta \mu$ in the second row.
-The horizontal grey dashed line corresponds to an intensity 
-equal to three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$).
-$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
-The lower six panels show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles. 
-Such profiles are available online for all other galaxies successfully modelled in 1D (see Table \ref{tab:fitres}).}
-\label{fig:n2974ex}
-\end{center}
-\end{figure*}
-
-%\begin{figure*}[h]
-%\begin{center}
-%\includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
-%\caption{Best-fit model and isophotal parameters for the galaxy M59. 
-%The figure caption is the same as Figure \ref{fig:n3377ex}. 
-%Empty data points represent data excluded from the fit.}
-%\label{fig:m59ex}
-%\end{center}
-%\end{figure*}
-%
-%\begin{figure*}[h]
-%\begin{center}
-%\includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
-%\caption{Best-fit model and isophotal parameters for the galaxy NGC 1332.
-%The figure caption is the same as Figure \ref{fig:n3377ex}. 
-%Empty data points represent data excluded from the fit.}
-%\label{fig:n1332ex}
-%\end{center}
-%\end{figure*}
-%
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width=\columnwidth]{images/mbhmagk_n1332.pdf}
-%\caption{The location of the S\'ersic galaxy NGC 1332 in the black hole mass versus $K$-band spheroid absolute magnitude diagram,
-%according to our galaxy decomposition. 
-%The red and blue solid lines show the scaling relations for core-S\'ersic and S\'ersic galaxies, respectively, 
-%reported by \citet{grahamscott2013}, 
-%while the shaded areas mark the $1\sigma$ errors.}
-%\label{fig:n1332pl}
-%\end{center}
-%\end{figure}
-
-\subsection{2D fits}
-\label{sec:2d}
-Two-dimensional decompositions were carried out using the software \textsc{Imfit} \citep{imfit}.
-For each galaxy, we built a 2D model that was consistent with the corresponding 1D model in terms of number and type of components. 
-Because the Ferrer profile is not made available in \textsc{Imfit},
-bars were fit with a 2D Gaussian function. \\
-The 2D decomposition of NGC 2974 is presented in Figure \ref{fig:n29742d}. 
-The galaxy was modeled with a S\'ersic bulge, an exponential disk and a Gaussian bar.
-The nuclear component was masked and the ring was not 
-modeled\footnote{We built the 2D model first including and then omitting a gaussian ring component, 
-but both models converged to the same solution, i.e.~the fit ``ignored'' the presence of the faint ring. 
-This did not happen in the 1D decomposition because of the different weighting scheme used by the fitting routines.}. 
-Our best-fit 2D model returns a bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 10.5~\rm arcsec$, 
-a bulge S\'ersic index $n_{\rm sph} = 1.3$ and a $3.6~\rm \mu m$ bulge apparent magnitude $m_{\rm sph} = 8.39~\rm mag$, 
-in fairly good agreement with our 1D decomposition. 
-Fits and descriptions for the other galaxies are available online.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{images/n2974_imgmsk.pdf}
-\includegraphics[width=\columnwidth]{images/n2974_model.pdf}
-\includegraphics[width=\columnwidth]{images/n2974_resid.pdf}
-\caption{Image of the galaxy NGC 2974 with its mask (top panel), best-fit 2D model (middle panel), 
-and residual image after the subtraction of the 2D model (bottom panel).
-The ring has not been modeled, and therefore appears in the residual image.}
-\label{fig:n29742d}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_agn.pdf}
+\caption{}
+\label{fig:}
 \end{center}
@@
 \label{sec:res}
-For each galaxy, after we identified its various components and built a model accordingly, 
-we simultaneously performed a set of four 1D fits.
-All four fits use a Moffat-convolved model.
-Two fits use the major-axis surface brightness profile and the remaining two use the equivalent-axis surface brightness profile. 
-For each of these pairs, we use a logarithmically sampled surface brightness profile 
-and a linearly sampled surface brightness profile. 
-Because our fitting routine intentionally does not employ an error weighting scheme on the data points that constitute the surface brightness profile, 
-a fit to a logarithmically sampled profile puts more weight on the inner region of the galaxy 
-and poorly constrains the outskirts.
-On the other hand, a fit to a linearly sampled surface brightness profile equally treats inner and outer regions, 
-but is more susceptible to sky-background subtraction issues. \\ 
-We found that the fits are, in general, more sensitive to the choice of the initial parameters 
-when using logarithmically sampled profiles than linearly sampled profiles. 
-In addition, a visual examination of the residuals revealed that the quality of the fit within one galaxy effective radius 
-is superior when tighter constraints are put on the galaxy outskirts.
-In other words, the better quality of the residuals led us to prefer the fits that use linearly sampled surface brightness profiles,
-although the results were ususally very similar,as might be expected. \\
-Among the initial sample of 75 galaxies, we did not attempt to model 3 galaxies: M32, NGC 4486A and the Circinus Galaxy. 
-The first two... {\bf AL: can you write a short sentence about these 2 galaxies, that have uncertain morphology,
-because they have been stripped, blah blah, maybe put one reference? please and thank you.}
-The Circinus Galaxy lies at only 4 degrees from the Galactic Plane, 
-therefore its image mosaic is contaminated by a large number of foreground stars.
-Of the remaining 72 galaxies, 
-we obtained satisfactory 1D decompositions for 66, 
-whereas the models of 6 galaxies were judged not reliable and were thus excluded. 
-We also performed reliable 2D decompositions for 31 galaxies. \\
-A galaxy-by-galaxy comparison between our best-fit models and those from the previous literature 
-helped identify the optimal decompositions and past problems. 
-We compared our best-fit models with those of \cite{grahamdriver2007}, \cite{sani2011}, \cite{beifiori2012}, 
-\cite{vika2012} and \cite{lasker2014data}. 
-We also considered the best-fit models of \cite{laurikainen2010} and \cite{rusli2013} because,   
-although they did not specifically deal with black hole -- galaxy scaling relations, 
-their galaxy samples significantly overlap with ours. \\
-%In Section \ref{sec:indgal} we discuss individual cases, explaining the discrepancies between different decompositions. \\
-Table \ref{tab:fitres} lists the results from both the 1D and 2D fits.
-
-\input{table_fitresults.tex}
-
-\subsection{1D versus 2D decompositions}
-Here we explore how 1D and 2D decompositions compare with each other. 
-Readers not interested in our practical knowledge, 
-having dealt with 1D and 2D techniques of galaxy modeling at the same time, can skip to Section \ref{sec:err}. 
-We summarize our experience in the following points:
-\begin{itemize}
-\item A visual inspection of galaxy images and their unsharp masks is often not sufficient to accurately identify all of a galaxy's components. 
-Weak bars and some embedded disks can easily be missed. 
-Other (inclined) embedded disks can be confused with large-scale disks.
-In this regards, the 1D isophotal analysis is extremely helpful. 
-Local minima/maxima or abrupt changes in the ellipticity, position angle and fourth harmonic profiles contain precious information 
-about a galaxy's constituents.
-\item The ellipticity and position angle of triaxial bulges can vary with radius.
-The analytic functions used by 2D decomposition codes to fit galaxy components have fixed ellipticity and position angle, 
-thus they cannot account for these radial gradients. 
-This problem is overcome with 1D decomposition techniques.
-\item The interpretation of the residual surface brightness profile is often crucial to identify the optimal decomposition for a galaxy. 
-In our experience, we found that interpreting 1D residuals was easier and more productive than 2D residuals.
-\end{itemize}
-Although we attempted 2D modeling for the 72 galaxies in our sample, 
-more than half of the 2D decompositions were not successful or did not converge to a meaningful solution. 
-This should serve as a tip to users of 2D fitting codes. 
-When physically meaningful bulge parameters are required, 
-the output may not be reliable and should be inspected.
-For the 31 galaxies that had successful 2D decompositions, 
-we compare with their 1D parameters in Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}.
-%The software \textsc{Imfit} returns major-axis measurements of effective radii, 
-%which are plotted in Figure \ref{fig:re1d2d} versus the corresponding 1D major-axis measurements.
-%2D measurements of S\'ersic indices can be approximated to 1D equivalent-axis measurements, 
-%and are therefore compared to them in Figure \ref{fig:n1d2d}.
-%Figure \ref{fig:mag1d2d} shows 2D versus 1D measurements of bulge magnitudes. 
-The agreement between 1D and 2D effective radii and magnitudes is remarkable, 
-whereas a larger amount of scatter in the S\'ersic indices can be caused by the fact that 
-2D measurements do not exactly correspond to 1D equivalent-axis measurements. 
-No systematic effects are observed in any of these three plots, 
-which indicates that 1D and 2D techniques of galaxy modeling -- when performed on the same galaxy -- 
-can give consistent results. \\
-In conclusion, since we found that the best-fit parameters do not depend on the decomposition method (1D or 2D) used, 
-and given that we obtained more successful 1D decompositions than 2D, 
-we will base our analysis on the results from the 1D fits.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{images/comparison_r_e.eps} 
-\caption{2D versus 1D major-axis measurements of the effective radii. 
-The dashed line displays the 1:1 relation.}
-\label{fig:re1d2d}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{images/comparison_n.eps} 
-\caption{2D measurements of the S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
-The dashed line displays the 1:1 relation.}
-\label{fig:n1d2d}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{images/comparison_mag.eps} 
-\caption{2D versus 1D measurements of the $3.6~\rm \mu m$ bulge magnitudes. The dashed line displays the 1:1 relation.}
-\label{fig:mag1d2d}
-\end{center}
-\end{figure}
-
-\subsection{Parameter uncertainty}
-\label{sec:err}
-Estimating the uncertainties associated with the best-fit parameters of our 1D galaxy decompositions is not straightforward.
-Monte Carlo simulations could be used for this purpose, 
-but they would take into account only random errors and not unknown systematic errors.
-Systematic errors include incorrect sky subtraction, 
-inaccurate masking of contaminating sources, 
-imprecise description of the PSF, 
-erroneous choice of model components 
-(for example, when failing to identify a galaxy sub-component and thus omitting it in the model, 
-or when describing a galaxy sub-component with an inadequate function),
-the radial extent of the surface brightness profile and its sampling.
-These factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters.  
-Moreover, when performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well resolved -- galaxies, 
-errors are dominated by systematics rather than Poisson noise.
-For this reason, we decided to estimate the uncertainties of the bulge best-fit parameters 
-with a method that took into account systematic errors.
-
-\subsubsection{Goodness of the bulge modeling}
-For each of our fits, we calculated the associated $RMS$ scatter using:
-\begin{equation}
-\Delta = \sqrt{\frac{\sum_{\rm i=0}^{N} (\mu_{\rm i}^{\rm obs} - \mu_{\rm i}^{\rm mod})^2}{N_{\rm DOF}} } ,
-\end{equation} 
-where $N_{\rm DOF}$ is the number of degrees-of-freedom, 
-$\mu_{\rm i}^{\rm obs}$ is the observed surface brightness 
-and $\mu_{\rm i}^{\rm mod}$ is the model surface brightness at each data point $i$.
-Although useful to evaluate the overall quality of a galaxy decomposition, 
-the $RMS$ scatter alone cannot be used to assess the goodness of the fit for the spheroidal component only, 
-unless the galaxy is a pure spheroid and has consequently been modeled with a single S\'ersic profile.
-To illustrate this point with an example, 
-one can imagine a situation in which a galaxy is thought to be made of a small bulge and a much more extended disk.
-This galaxy is decomposed with a S\'ersic + exponential model.
-The exponential function provides an excellent description of the light profile of the disk, 
-whereas the S\'ersic function does not do the same for the bulge.
-The residuals of the fit will then be flat and close to zero at large radii, 
-where the emission of the disk dominates over that of the bulge,
-while they will display significant departures at small radii, 
-in correspondence with the poorly fit spheroidal component.
-In the case of linear sampling, 
-because the part of the surface brightness profile pertaining to the disk may contain more data points 
-than the part pertaining to the bulge, 
-the global $RMS$ scatter will be relatively small, 
-but it obviously will not reflect the accuracy of the fit to the spheroidal component only. \\
-A simple but powerful way to get a feeling of how precisely the global model and its spheroidal component have fared
-is to look at the major- and equivalent-axis fits of each galaxy 
-and visually inspect the structures of the residual surface brightness profile 
-(i.e.~the second row in Figure \ref{fig:n2974ex}) within $\sim 1 - 2$ bulge effective radii. 
-We did this using a grade from 1 to 3, assigned according to the following criteria.
-\begin{itemize}
-\item [1)] A grade of 1 was given to the best fits, i.e.~fits that do not exhibit any of the problems listed below.
-\item [2)] A grade of 2 was issued in the following cases. 
-The residuals in correspondence with the radial extent of the bulge component are not randomly distributed around zero, 
-being symptomatic of a S\'ersic model having a curvature (regulated by the S\'ersic index $n$) 
-that does not quite match the real ``shape'' of the bulge. 
-When we identified, but were not able to accurately model. a galaxy sub-component.
-In the case of apparent inconsistencies between the model and the observed galaxy properties 
-(e.g.~an embedded disk modeled with an exponential function, 
-whose scale length does not quite match the size of the disk as expected from the ellipticity profile or the velocity map).
-When the S\'ersic model used to describe the bulge component has a size -- as measured by the effective radius -- 
-comparable to a few times the $FWHM$ of the PSF.
-Galaxies in this category are reasonably well fit despite these issues.
-\item [3)] A grade of 3 was assigned to the poorer and more anomalous fits, 
-or those affected by an obvious degeneracy between the bulge S\'ersic profile and the remaining model components 
-(e.g.~when the bulge S\'ersic index varies by as much as 50\% among the four different realizations of the fit, 
-or when the output of the fit strongly depends on the choice of the initial parameters).
-\end{itemize}
-As a result, we classified 27 galaxies (38\% of the 72 galaxies for which we attempted a 1D decomposition) with grade 1, 
-29 galaxies (40\%) with grade 2 and 10 galaxies (14\%) with grade 3.
-Six galaxies could not be modelled.
-We report the assigned grades in Table \ref{tab:fitres} (column 10).
-
-\subsubsection{Uncertainties on $n_{\rm sph}$}
-%\label{sec:sigman}
-In Figure \ref{fig:compn}, for 58 galaxies, 
-we compare the measurements of the bulge S\'ersic index obtained by different authors 
-with those obtained by us. 
-For each galaxy, we computed the average value $\langle \log(n_{\rm sph}) \rangle$ of the available measurements, 
-and we plot it against the scatter of the individual measurements around each spheroid's $\langle \log(n_{\rm sph}) \rangle$.
-The measurements are heterogeneous, 
-in the sense that they were obtained from 1D or 2D decompositions of data in different wavelengths, 
-and they refer either to the major-axis, the equivalent-axis or some 2D average.
-In Figure \ref{fig:compn}, the black histogram shows the distribution of the scatter around $\langle \log(n_{\rm sph}) \rangle$ 
-for our measurements. 
-38\% of this distribution lie within $-\sigma_1^- = -0.08~\rm dex$ and $+\sigma_1^+ = +0.06~\rm dex$, 
-78\% lie within $-\sigma_2^- = -0.21~\rm dex$ and $+\sigma_2^+ = +0.17~\rm dex$,
-and 92\% lie within $-\sigma_3^- = -0.25~\rm dex$ and $+\sigma_3^+ = +0.25~\rm dex$. 
-We elect to use $\pm \sigma_1^\pm$, $\pm \sigma_2^\pm$ and $\pm \sigma_3^\pm$ as $1\sigma$ uncertainties 
-for our measurements of $\log(n_{\rm sph})$ obtained from ``grade 1'', ``grade 2'' and ``grade 3'' fits, respectively. \\
-
-\subsubsection{Uncertainties on $R_{\rm e,sph}$}
-The uncertainties on the bulge effective radii were computed using the same methodology as employed for the S\'ersic indices. 
-However, in Figure \ref{fig:compre} we include only major-axis measurements of $R_{\rm e,sph}$. 
-The associated $1\sigma$ uncertainties for our measurements of $\log(R_{\rm e,sph})$ are 
-$-\sigma_1^- = -0.11~\rm dex$ and $+\sigma_1^+ = +0.07~\rm dex$, 
-$-\sigma_2^- = -0.30~\rm dex$ and $+\sigma_2^+ = +0.32~\rm dex$,
-and $-\sigma_3^- = -0.39~\rm dex$ and $+\sigma_3^+ = +0.42~\rm dex$.
-
-\subsubsection{Uncertainties on $m_{\rm sph}$}
-To estimate the uncertainties on the bulge magnitudes, 
-we compared (see Figure \ref{fig:compmag}) only those literature measurements coming from $K$-band or $3.6~\rm \mu m$ observations.
-To do this, the $3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes by applying an additive factor of $0.27\rm~mag$, 
-which was estimated using the stellar population models of \cite{worthey1994},
-assuming a 13 Gyr old single-burst stellar population with solar metallicity. 
-The associated $1\sigma$ uncertainties for our measurements of $m_{\rm sph}$ are 
-$-\sigma_1^- = -0.11~\rm mag$ and $+\sigma_1^+ = +0.18~\rm mag$, 
-$-\sigma_2^- = -0.58~\rm mag$ and $+\sigma_2^+ = +0.66~\rm mag$,
-and $-\sigma_3^- = -0.66~\rm mag$ and $+\sigma_3^+ = +0.88~\rm mag$.
-
-\subsubsection{Uncertainties on $\mu_{\rm e,sph}$}
-As for the bulge magnitudes, we estimated the uncertainties on the bulge effective surface brightnesses $\mu_{\rm e,sph}$ 
-by comparing only $K$-band or $3.6~\rm \mu m$ measurements (see Figure \ref{fig:compmue}), 
-and accounting for the mean color difference of $0.27\rm~mag$. 
-Not explicitly reported in the literature, effective surface brightnesses were calculated by us using:
-\begin{multline}
-\mu_{\rm e,sph} = m_{\rm sph} + 5\log \Bigl(R_{\rm e,sph}^{\rm maj}\sqrt{(b/a)_{\rm sph}} \Bigr) + \\
-+ 2.5\log \Bigl[2\pi n_{\rm sph} e^{b_n} b_n^{-2n_{\rm sph}} \Gamma(2n_{\rm sph})\Bigr], 
-\end{multline}
-where $b_n$ and $\Gamma(2n_{\rm sph})$ are defined in the Appendix, 
-and $(b/a)_{\rm sph}$ is the bulge axis ratio.
-While \cite{laurikainen2010} and \cite{sani2011} reported their estimates of $(b/a)_{\rm sph}$, 
-\cite{vika2012} and \cite{lasker2014data} did not. 
-For the last two studies, we used the values of $(b/a)_{\rm sph}$ reported by \cite{sani2011}.
-The associated $1\sigma$ uncertainties for our measurements of $\mu_{\rm e,sph}$ are 
-$-\sigma_1^- = -0.33~\rm mag$ and $+\sigma_1^+ = +0.57~\rm mag$, 
-$-\sigma_2^- = -0.84~\rm mag$ and $+\sigma_2^+ = +1.59~\rm mag$,
-and $-\sigma_3^- = -1.06~\rm mag$ and $+\sigma_3^+ = +1.74~\rm mag$.
-
-\subsubsection{Uncertainties on $\mu_{\rm 0,sph}$}
-From the values of $\mu_{\rm e,sph}$, we derived the central surface brightnesses $\mu_{\rm 0,sph}$ from the equation
-\begin{equation}
-\mu_{\rm 0,sph} = \mu_{\rm e,sph} - \frac{2.5 b_n}{\ln(10)}.
-\end{equation}
-The associated $1\sigma$ uncertainties for our measurements of $\mu_{\rm 0,sph}$ are 
-$-\sigma_1^- = -0.20~\rm mag$ and $+\sigma_1^+ = +0.64~\rm mag$, 
-$-\sigma_2^- = -0.70~\rm mag$ and $+\sigma_2^+ = +1.24~\rm mag$,
-and $-\sigma_3^- = -1.05~\rm mag$ and $+\sigma_3^+ = +1.57~\rm mag$.
-
-\begin{figure}%[h]
-\begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
-\caption{The bottom panel shows 58 galaxies for which at least one measurement of the bulge S\'ersic index $n_{\rm sph}$ is available 
-from the literature, in addition to that measured by us.
-In ordinate, for each galaxy, we plot the average value $\langle \log(n_{\rm sph}) \rangle$ of (the logarithm of) the individual measurements. 
-In abscissa we plot the difference between (the logarithm of) the individual measurements of a galaxy 
-and the average value for that same galaxy.
-Each data point corresponds to an individual measurement, 
-which comes from one of the following studies. 
-Red points are from \cite{grahamdriver2007}, 
-blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
-yellow points are from \cite{vika2012}, gray points are from \cite{beifiori2012},
-white points are from \cite{rusli2013}, orange points are from \cite{lasker2014data},
-and black points are measurements obtained from the 1D fits presented in this work 
-(using linearly sampled surface brightness profiles, along the major-axis).
-In the top panel, the white histogram shows the distribution of $\log(n_{\rm sph}) - \langle \log(n_{\rm sph}) \rangle$ 
-for all measurements, 
-whereas the black histogram refers only to measurements obtained by us.
-The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
-of the black histogram, respectively.}
-\label{fig:compn}
-\end{center}
-\end{figure}
-
-\begin{figure}%[h]
-\begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_r_e.eps} 
-\caption{The bottom panel shows 52 galaxies for which at least one measurement 
-of the major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
-from the literature, in addition to that measured by us.
-In ordinate, for each galaxy, we plot the average value $\langle \log(R_{\rm e}^{\rm maj}) \rangle$ 
-of (the logarithm of) the individual measurements. 
-In abscissa we plot the difference between (the logarithm of) the individual measurements of a galaxy 
-and the average value for that same galaxy.
-Each data point corresponds to an individual measurement, 
-which comes from one of the following studies. 
-Red points are from \cite{grahamdriver2007}, 
-blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
-yellow points are from \cite{vika2012}, gray points are from \cite{beifiori2012},
-orange points are from \cite{lasker2014data},
-and black points are measurements obtained from the 1D fits presented in this work 
-(using linearly sampled surface brightness profiles, along the major-axis).
-In the top panel, the white histogram shows the distribution of $\log(R_{\rm e}^{\rm maj}) - \langle \log(R_{\rm e}^{\rm maj}) \rangle$ 
-for all measurements, 
-whereas the black histogram refers only to measurements obtained by us.
-The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
-of the black histogram, respectively.}
-\label{fig:compre}
-\end{center}
-\end{figure}
-
-\begin{figure}%[h]
-\begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_mag_sph.eps} 
-\caption{The bottom panel shows 51 galaxies for which at least one measurement 
-of the bulge apparent magnitude $m_{\rm sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
-from the literature, in addition to that measured by us. 
-$3.6~\rm \mu m$ magnitudes were converted to $K$-band magnitudes.
-In ordinate, for each galaxy, we plot the average value $\langle m_{\rm sph} \rangle$ 
-of the individual measurements. 
-In abscissa we plot the difference between the individual measurements of a galaxy 
-and the average value for that same galaxy.
-Each data point corresponds to an individual measurement, 
-which comes from one of the following studies. 
-Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
-yellow points are from \cite{vika2012}, 
-orange points are from \cite{lasker2014data},
-and black points are measurements obtained from the 1D fits presented in this work 
-(using linearly sampled surface brightness profiles, along the equivalent-axis).
-In the top panel, the white histogram shows the distribution of $m_{\rm sph} - \langle m_{\rm sph} \rangle$ 
-for all measurements, 
-whereas the black histogram refers only to measurements obtained by us.
-The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
-of the black histogram, respectively.}
-\label{fig:compmag}
-\end{center}
-\end{figure}
-
-\begin{figure}%[h]
-\begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_e.eps} 
-\caption{The bottom panel shows 49 galaxies for which at least one measurement 
-of the bulge effective surface brightness $\mu_{\rm e,sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
-from the literature, in addition to that measured by us. 
-$K$-band magnitudes were converted to $3.6~\rm \mu m$ magnitudes.
-In ordinate, for each galaxy, we plot the average value $\langle \mu_{\rm e,sph} \rangle$ 
-of the individual measurements. 
-In abscissa we plot the difference between the individual measurements of a galaxy 
-and the average value for that same galaxy.
-Each data point corresponds to an individual measurement, 
-which comes from one of the following studies. 
-Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
-yellow points are from \cite{vika2012}, 
-orange points are from \cite{lasker2014data},
-and black points are measurements obtained from the 1D fits presented in this work 
-(using linearly sampled surface brightness profiles, along the major-axis).
-In the top panel, the white histogram shows the distribution of $\mu_{\rm e,sph} - \langle \mu_{\rm e,sph} \rangle$ 
-for all measurements, 
-whereas the black histogram refers only to measurements obtained by us.
-The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
-of the black histogram, respectively.}
-\label{fig:compmue}
-\end{center}
-\end{figure}
-
-\begin{figure}%[h]
-\begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_0.eps} 
-\caption{The bottom panel shows 49 galaxies for which at least one measurement 
-of the bulge central surface brightness $\mu_{\rm 0,sph}$ -- either in $K$-band or $3.6~\rm \mu m$ -- is available 
-from the literature, in addition to that measured by us. 
-$K$-band magnitudes were converted to $3.6~\rm \mu m$ magnitudes.
-In ordinate, for each galaxy, we plot the average value $\langle \mu_{\rm 0,sph} \rangle$ 
-of the individual measurements. 
-In abscissa we plot the difference between the individual measurements of a galaxy 
-and the average value for that same galaxy.
-Each data point corresponds to an individual measurement, 
-which comes from one of the following studies. 
-Blue points are from \cite{laurikainen2010}, green points are from \cite{sani2011}, 
-yellow points are from \cite{vika2012}, 
-orange points are from \cite{lasker2014data},
-and black points are measurements obtained from the 1D fits presented in this work 
-(using linearly sampled surface brightness profiles, along the major-axis).
-In the top panel, the white histogram shows the distribution of $\mu_{\rm 0,sph} - \langle \mu_{\rm 0,sph} \rangle$ 
-for all measurements, 
-whereas the black histogram refers only to measurements obtained by us.
-The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
-of the black histogram, respectively.}
-\label{fig:compmu0}
-\end{center}
-\end{figure}
 
@@
 \label{sec:concl}
-The widespread presence of embedded components -- such as intermediate-scale disks -- in massive early-type galaxies 
-makes galaxy decomposition an essential tool to properly investigate the scaling relations between black hole masses 
-and host bulge properties. \\
-Past studies often used different models for the same galaxy, and obtained significantly discrepant results,  
-which led them to draw contrasting conclusions about the black hole--bulge correlations.
-These inconsistencies motivated our effort to secure and refine the measure of bulge properties in a sample of 75 galaxies 
-with a dynamical estimate of the black hole mass. 
-Using $3.6~\rm \mu m$ \emph{Spitzer} satellite imagery, 
-we performed state-of-the-art galaxy decompositions. 
-The $3.6~\rm \mu m$ band is an excellent tracer of the stellar mass, superior to optical bands or the $K$-band. 
-Considerable care has been taken in the data reduction, image mosaicking, sky subtraction and component model fitting to the galaxy light.
-We have compared our best-fit models with those from the literature, 
-to identify and explain discrepancies when present. 
-Our analysis additionally benefited from recourse to kinematical information -- not previously used -- to aid the identification of 
-somewhat face-on disks, or the distinction between intermediate-scale disks and large-scale disks, 
-missed in some past investigations and decompositions.
-Table \ref{tab:lit} summarizes the main characteristics of the five past studies that, since 2007, attempted galaxy decomposition 
-to derive black hole-bulge scaling relations, 
-and highlights, in part, why our endeavor represents a substantial improvement over the past literature.
-
-\begin{table*}%[ht] 
-\begin{center}  				      
-\caption{{\bf Summary of previous investigations of black hole mass scaling relations.} 
-GD07 = \cite{grahamdriver2007}, 
-S+11 = \cite{sani2011}, V+12 \cite{vika2012}, B+12 = \cite{beifiori2012}, L+14 = \cite{lasker2014data}.}
-\begin{tabular}{lllllll}
-\hline
-              & {\bf GD07}  & {\bf S+11}   & {\bf V+12} & {\bf B+12}   & {\bf L+14} & {\bf This work}	      \\ %%[0.5ex] 
-\hline
-{\bf Galaxies with successful fit} & 27		     & 57	       & 25      & 19          & 35      & 66               \\
-{\bf Wavelength}        	   & $R$-band	     & $3.6~\rm \mu m$ & $K$-band& $i$-band    & $K$-band& $3.6~\rm \mu m$  \\
-{\bf Decomposition}     	   & 1D 	     & 2D	       & 2D	 & 2D	       & 2D	 & 1D \& 2D	    \\
-{\bf Nuclear components}       	   & masked	     & modeled         & modeled & not treated & modeled & modeled/masked   \\
-{\bf Partially depleted cores} 	   & masked	     & masked	       & masked  & not treated & masked  & masked	    \\ 
-{\bf Bars}	        	   & excluded	     & modeled         & modeled & excluded    & modeled & modeled	    \\ 
-{\bf Other components}  	   & no 	  & no  	       & no	 & no	       & yes	 & yes  	    \\ 
-{\bf Kinematics}        	   & no 	     & no	       & no	 & no	       & no	 & yes  	    \\ %%[0.5ex] 
-\hline 
-\end{tabular}
-\label{tab:lit} 
-\end{center}	
-\end{table*}
-
-\begin{itemize}
-\item One-dimensional and two-dimensional techniques of galaxy decomposition return the same results when applied to the same galaxy.
-However, in our practical experience, two-dimensional decompositions {\bf HOW DO YOU WRITE THIS IN ENGLISH?? fail twice as much as one-dimensional ones}, 
-either because the fit does not converge or because the result is unphysical. 
-A strong limitation of two-dimensional codes is their inability to accommodate the radial gradients of ellipticity and position angle 
-often observed in galaxy bulges.
-\item We found the interpretation of one-dimensional residual surface brightness profiles easier than that of two-dimensional residual images. 
-A correct interpretation of the residuals is fundamental to determine the optimal model for a galaxy.
-\item A one-dimensional isophotal analysis was extremely helpful and sometimes even necessary to accurately identify galaxy components.
-\item Given the level of detail to which each galaxy decomposition was performed, 
-we believe that our analysis cannot be reproduced by current automatic routines. 
-\item The uncertainties associated with the bulge best-fit parameters are dominated by systematic errors (e.g.~incorrect sky subtraction, 
-inaccurate masking of contaminating sources, erroneous choice of model components), and only marginally affected by random errors. 
-For this reason, we developed a method to estimate the uncertainties on the best-fit parameters that takes into account systematic errors.
-\end{itemize}
-
-We will use the results from our one-dimensional galaxy decompositions to obtain improved black hole mass scaling relations. 
-We will also derive and explore some unpublished correlations. 
-These results will be presented in a series of forthcoming papers.
-
-%\clearpage
-
-% \onecolumngrid
-% \subsection{individual galaxies}
-% \label{sec:indgal}
-%
-% individual galaxies \\
-%
-% \clearpage\newpage\noindent
-% {\bf IC 1459 \\}
-%
-% IC 1459 is an elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
-% nuclear dust and an indication of a central stellar disk \citep{forbes1994ic1459}.
-% The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
-% This galaxy has also a partially depleted core ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
-%
-% %\cite{sani2011} fit this galaxy with a S\'ersic-bulge + Gaussian-AGN model ($R_{\rm e} = 61''.1$, $n=6$).
-% %\cite{lasker2014data} used a S\'ersic-bulge + mask-core model ($R_{\rm e} = 62''.4$, $n=8.25$).
-% %\cite{rusli2013} adopted a core-S\'ersic model ($R_{\rm e} = 45''.43$, $n=7.6$).
-%
-% \emph{1D fit -- }
-% Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
-% We masked the innermost $6''.1$ affected by the partially depleted core 
-% and we fit this galaxy with a S\'ersic profile. 
-%
-% \emph{Other models -- } 
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for IC 1459.}
-% \end{center}
-% \end{figure}
-%
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for IC 1459.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
-% T.W. 1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
-% T.W. 2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
-% \hline
-% S+11         & S-bul + G-n   & $61.1$  &  $6.0$ \\
-% R+13         & core-S\'ersic & $45.4$  &  $7.6$ \\
-% L+14         & S-bul + m-c   & $62.4$  &  $8.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:ic1459}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf IC 2560 \\}
-%
-% IC 2560 is a barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
-% and dust within the central $2''.5$ \citep{martini2003}.
-%
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model ($R_{\rm e} = 27''.5$, $n=2$).
-%
-% \emph{1D fit -- }
-% A visual inspection of the image of IC 2560 reveals a boxy bulge and
-% a large scale bar that extends out to $R \lesssim 43''$.
-% The disk appears to be slightly lopsided along the direction of the bar,
-% due to two non-symmetric ansae, but it becomes symmetric beyond $R \gtrsim 60''$. 
-% This is why the surface brightness profile deviates from a perfect exponential
-% in the radial range $42'' \lesssim R \lesssim 60''$, which has been excluded from the fit.
-% Motivated by the presence of a strong optical AGN and dust in the nucleus, 
-% we accounted for an excess of non-stellar light by adding a central Gaussian component to the model.
-% %Our final 1D model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar + Gaussian-AGN.
-% %Similarly, our 2D model consists of a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN.\\
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for IC 2560.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for IC 2560.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $6.1$  &  $0.8$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.5$  &  $0.6$ \\
-% %T.W. 2D	&  &  & \\
-% \hline
-% S+11         & S-bul + e-d + G-n & $27.5$  &  $2.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:ic2560}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf IC 4296 \\}
-%
-% IC 4296 is an elliptical galaxy. % with a radio jet \citep{liuxie1992}.
-% Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
-%
-% %\cite{sani2011} fit this galaxy with a S\'ersic-bulge + Gaussian-AGN model ($R_{\rm e} = 33''.6$, $n = 4$).
-% %\cite{lasker2014data} employed a S\'ersic-bulge + mask-core model ($R_{\rm e} = 97''.8$, $n=8.2$).
-%
-% \emph{1D fit -- }
-% After masking the innermost $6''.1$, % affected by the (unresolved) partially depleted core,
-% we found that a single S\'ersic profile provides a fairly good description of this galaxy.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for IC 4296.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for IC 4296.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
-% T.W. 1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
-% T.W. 2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
-% \hline
-% S+11         & S-bul + G-n & $33.6$  &  $4.0$ \\
-% L+14         & S-bul + m-c & $97.8$  &  $8.2$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:ic4296}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M31 -- NGC 0224 \\}
-%
-% M31, the Andromeda galaxy, is a spiral galaxy. 
-% Although for decades this galaxy had been classified as an unbarred spiral,
-% recent works have unraveled the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}.
-% M31 also features a pseudo-ring-like structure at $R \sim 50'$ \citep{athanassoulabeaton2006m31}. 
-%
-%
-% \emph{1D fit -- }
-% We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
-% The region $2000'' \lesssim R \lesssim 3400''$, where the pseudo-ring is observed, was excluded from the fit.
-% A S\'ersic + exponential fit is clearly not adequate to describe the light profile of M31.
-% The residuals of such fit display a structure in correspondence of the bar ($R \lesssim 1500''$).
-% The bar was thus fit with a Ferrer function.
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M31.}
-% \end{center}
-% \end{figure}
-%
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M31.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $418.6$  &  $2.2$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $173.6$  &  $1.3$ \\
-% %T.W. 2D	& $$  & $$  &  $$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m31}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M49 -- NGC 4472 \\}
-%
-% M49, the brightest member of the Virgo cluster, is a giant elliptical galaxy 
-% with a partially depleted core ($R_{\rm break} = 1''.8$, \citealt{rusli2013}).
-% %M49 is a slow-rotator \citep{atlas3dIII-MNRAS}.
-%
-% %\cite{ferrarese2006acsvcs} modeled this galaxy with a core-S\'ersic profile ($R_{\rm e} = 208''$, $n = 5.5$).
-% %Also \cite{rusli2013} used a core-S\'ersic model ($R_{\rm e} = 199''$, $n = 5.6$).
-%
-% \emph{1D fit -- }
-% We excluded from the fit the innermost $12''$.
-% We found no evidence for embedded components and
-% we fit M49 with a single S\'ersic profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M49.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M49.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $190.2$  &  $6.6$ \\
-% T.W. 1D eq.  & S-bul + m-c & $135.3$  &  $5.4$ \\
-% T.W. 2D      & S-bul + m-c & $151.9$  &  $5.5$ \\
-% \hline
-% R+13         & core-S\'ersic & $199.0$  &  $5.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m49}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M59 -- NGC 4621 \\}
-%
-% M59 is an elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
-% and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}.
-% %M59 is a fast-rotator \citep{atlas3dIII-MNRAS}.
-%
-% %\cite{sani2011} modeled this galaxy with a single S\'ersic-bulge model ($R_{\rm e} = 70''.1$, $n = 5$).
-% %\cite{vika2012} used a S\'ersic-bulge + mask-core model ($R_{\rm e} = 54''.7$, $n = 5.7$). 
-%
-% \emph{1D fit -- }
-% The intermediate-scale embedded disk is clearly visible in our unsharp mask image, and 
-% the velocity field confirms the presence of a rapidly rotating component. 
-% Although faint, it is important to account for the presence of this disk.
-% A single S\'ersic fit produces bad residuals.
-% The fit notably improves if an embedded exponential disk function 
-% is added to the final model.
-% We chose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M59.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M59.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c + e-id & $48.0$  &  $5.5$ \\
-% T.W. 1D eq.  & S-bul + m-c + e-id & $90.9$  &  $8.8$ \\
-% %T.W. 2D	&    & $$  &  $$ \\
-% \hline 
-% S+11         & S-bul       & $70.1$  &  $5.0$ \\
-% V+12         & S-bul + m-c & $54.7$  &  $5.7$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m59}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf M60 -- NGC 4649 \\}
-%
-% exclude it, doesn't make sense
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M64 -- NGC 4826 \\}
-%
-% M64 is a dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. 
-%
-% %B12 model the galaxy image with a 2D S\'ersic function + exponential disk ($n = 1.49$). \\
-% \emph{1D fit -- }
-% A large-scale bar ($R \lesssim 50''$) can be identified in the unsharp mask 
-% and produces corresponding peaks in the ellipticity, PA and B4 profiles.
-% We modeled it with a Ferrer function.
-% Additional peaks in the ellipticity, PA and B4 profiles at $R \sim 15''$ 
-% signal the presence of an embedded disky component, that we described with a low-$n$
-% S\'ersic function.
-% Although the galaxy is dusty and hosts an AGN, we do not observe any nuclear excess of light 
-% in the fit residuals and therefore we consider unnecessary to add a nuclear component to our model.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m64_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M64.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M64.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + S-id  & $3.8$  &  $0.8$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + S-id  & $4.3$  &  $1.4$ \\
-% %T.W. 2D	&   & $$  & $$  &  $$ \\
-% \hline
-% B+12      & S-bul + e-d  & $5.0$  &  $1.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m64}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M81 -- NGC 3031 \\}
-%
-% M81 is an early-type spiral galaxy with a LINER AGN.
-% This galaxy features two bars \citep{elmegreen1995m81,gutierrez2011,erwindebattista2013}.
-%
-% \emph{1D fit -- }
-% We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M81.
-% The bars are not particularly evident in the galaxy image or in the unsharp mask.
-% Any attempt to account for the bars in the fit was unsuccessful. 
-% For this reason, we used a simple S\'ersic + exponential model to describe M81.
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m81_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M81.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M81.}
-% \begin{center}
-% \begin{tabular}{llccc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d  & $31.0$  &  $1.7$ \\
-% T.W. 1D eq.  & S-bul + e-d  & $33.2$  &  $2.1$ \\
-% %T.W. 2D	&   & $$  & $$  &  $$ \\
-% \hline
-% GD07      & S-bul + e-d	 & $68.1$   &  $3.3$ \\
-% S+11      & S-bul + e-d + G-n  & $127.3$  &  $3.0$ \\
-% B+12      & S-bul + e-d	 & $50.0$   &  $2.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m81}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M84 -- NGC 4374 \\}
-%
-% M84 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.5$, \citealt{rusli2013}). 
-%
-% %GD07 model the galaxy light profile with a S\'ersic function ($n = 5.6$).
-% %V12 model the galaxy image with a 2D S\'ersic function + core-mask ($n = 3.5$).
-% %S11 model the galaxy image with a 2D S\'ersic function + Gaussian ($n = 7.0$).
-% %B12 model the galaxy image with a 2D S\'ersic function ($n = 4.10$). \\
-%
-% \emph{1D fit -- }
-% The unsharp mask reveals a faint inner component ($R \lesssim 12''$). 
-% Here we excluded the data within $R < 13''.8$ and modeled the galaxy with a S\'ersic profile.
-%
-% %After masking the innermost $13''.8$, we modeled the galaxy with a S\'ersic profile. 
-% %However, we notice that 
-% %the 1D and 2D fits are not much affected by the presence of the embedded component.
-% %In fact, reducing the size of the central mask to uncover the inner component 
-% %(but still masking the region affected by the partially depleted core) does not
-% %alter significantly the bulge parameters. 
-% %The structures observed in the residuals are caused by the negative ellipticity gradient 
-% %(from $\epsilon \sim 0.17$ to $\epsilon \sim 0.03$, over a radial range $10'' < R < 130''$),
-% %which cannot be reproduced by the 2D model because of its fixed ellipticity ($\epsilon = 0.10$). 
-%   
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m84_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M84.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M84.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c   & $101.6$  &  $7.8$ \\
-% T.W. 1D eq.  & S-bul + m-c   & $129.8$  &  $7.9$ \\
-% T.W. 2D      & S-bul + m-c   & $181.8$  &  $8.4$ \\
-% \hline
-% GD07         & S-bul         & $75.1$   &  $5.6$ \\
-% S+11         & S-bul + G-n   & $105.9$  &  $7.0$ \\
-% V+12         & S-bul + m-c   & $28.7$   &  $3.5$ \\
-% B+12         & S-bul         & $63.6$   &  $4.1$ \\
-% R+13         & core-S\'ersic & $126.2$  &  $7.1$ \\
-% L+14         & S-bul + m-c   & $139.0$  &  $8.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m84}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M87 -- NGC 4486 \\}
-%
-% M87 is a giant elliptical galaxy belonging to the Virgo cluster.
-% This galaxy has a large partially depleted core ($R_{\rm break} = 7''.2$, \citealt{ferrarese2006acsvcs}).
-%
-% \emph{1D fit -- }
-% The morphology of M87 is similar to that of M49.
-% The innermost $18''.5$ were excluded from the fit.
-% We used a single S\'ersic model to characterize M87.
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m87_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M87.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M87.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c  & $203.9$  &  $10.0$ \\
-% T.W. 1D eq.  & S-bul + m-c  & $87.1$   &  $5.9$ \\
-% T.W. 2D      & S-bul + m-c  & $88.3$   &  $4.3$ \\
-% \hline
-% GD07      & S-bul	    & $-$     &  $6.9$ \\
-% S+11      & S-bul + G-n   & $99.5$  &  $4.0$ \\
-% V+12      & S-bul + m-c   & $34.6$  &  $2.4$ \\
-% R+13      & core-S\'ersic & $180.9$ &  $8.9$ \\
-% L+14      & S-bul + m-c   & $122.0$ &  $5.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m87}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf M89 -- NGC 4552 \\}
-%
-% m87 has ellipticity still increasing, the halo is not prevailing
-% m89 instead has a plateau in the ell prof, bcz the halo is predominant
-% we need to fit the halo
-%
-% BTW, if we wanna test the two phase formation scenario, we should care more about the halos...
-% at which effective radius does the halo begin?
-% what is the ratio of the mass in the galaxy or in the halo?
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m89_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M89.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M89.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-halo  & $29.0$  &  $4.6$ \\
-% T.W. 1D eq.  & S-bul + e-halo  & $28.2$  &  $5.1$ \\
-% %T.W. 2D	&   & $$  & $$  &  $$ \\
-% \hline
-% &   & $$  &  $$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m89}
-% \end{table}
-%
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M94 -- NGC 4736 \\}
-%
-% M94 is an almost face-on spiral galaxy, with a Seyfert AGN \citep{veroncettyveron2006} and 
-% circumnuclear dust \citep{elmegreen2002m94,peeplesmartini2006m94}.
-% This galaxy has a ring-like structure at $R \sim 50''$ \citep{munoztunon1989m94}.
-%
-% %\cite{fisherdrory2010} fit M94 with a S\'ersic-bulge + exponential-disk model ($R_{\rm e} = 7''.7$, $n = 1.3$). 
-%
-% \emph{1D fit -- }
-% The ellipticity and B4 profiles display a local maximum at $R \sim 10''$, 
-% indicating the presence of a disky component embedded in the bulge,
-% as already noted by \cite{fisherdrory2010}.
-% We modeled this component with a Ferrer function.
-% We excluded the data within the innermost $6''.7$, due to the AGN contribution.
-% Any attempt to model the ring was unsuccessful, resulting in a degenerate model.
-% Therefore we preferred to exclude also the data in the range $20'' \lesssim R \lesssim 80''$, 
-% where the ring light dominates over the rest of the galaxy.
-% %Our final model for M94 consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m94_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M94.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M94.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $11.4$  &  $0.9$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $8.4$   &  $1.1$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m94}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M96 -- NGC 3368 \\}
-%
-% M96 is a spiral galaxy with a large scale bar and no AGN activity \citep{martini2003,nowak2010n3368n3489}. 
-%
-% %\cite{sani2011} fit this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-bar model 
-% %($R_{\rm e} = 45''.6$, $n = 1.0$). 
-% \cite{nowak2010n3368n3489} argued for the presence of a large pseudo-bulge and a tiny classical bulge 
-% ($R_{\rm e} = 1''.6$, $n = 2.3$). 
-%
-% \emph{1D fit -- }
-% M96 has a complex morphology. 
-% The large-scale disk does not exhibit a perfect exponential profile, 
-% mainly because of wound spiral arms resembling a ring ($R \sim 185''$),
-% which however are too faint and irregular to be described with a Gaussian ring model. 
-% The large scale bar extends out to $R \lesssim 80''$ and has been modeled with a Ferrer function.
-% A peak at $R \sim 25''$ in the ellipticity profile unravels an inner component embedded in the bulge.
-% The isophotal twist observed within $R \lesssim 25''$ suggests that the inner component can be identified 
-% with a second bar, as already noted by \cite{erwin2004}.
-% We accounted for this embedded component with a low-$n$ S\'ersic profile.
-% We built our final model with a S\'ersic-bulge + exponential-disk + Ferrer-bar + S\'ersic-bar.
-% The residuals do not display any significant light excess in the nuclear region, 
-% in agreement with the lack of AGN activity.
-%
-% \cite{nowak2010n3368n3489} came to their conclusion by modeling only the innermost $8''.5$ of the 
-% light profile of M96 with a S\'ersic-classical-bulge and an exponential-pseudo-bulge, 
-% but without subtracting the contribution of the large-scale disk and the large-scale bar.
-% In addition, they acknowledged the presence of a secondary inner bar, but did not include it in their fit.
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m96_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M96.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M96.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + S-bar  & $7.5$  &  $1.5$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + S-bar  & $5.3$  &  $1.3$ \\
-% T.W. 2D      & S-bul + e-d + 2 G-bars       & $8.3$  &  $2.0$ \\
-% \hline
-% S+11         & S-bul + e-d + G-bar  & $45.6$  &  $1.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m96}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf M104 -- NGC 4594 \\} 
-%
-% OK
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M104.}
-% \end{center}
-% \end{figure}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M105 -- NGC 3379 \\}
-%
-% M105 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.1$, \citealt{rusli2013}).
-%
-% \emph{1D fit -- }
-% M105 exhibits a mild isophotal twist and an abrupt change of ellipticity at $R \sim 30''$.
-% The velocity map shows rotation at least within $R \lesssim 30''$, 
-% but no embedded disk can be recognized in the unsharp mask 
-% and the ellipticity profile is quite unusual for a spheroidal system with an inner disk.
-% After masking the innermost $6''.1$, we noticed that a single S\'ersic model 
-% does not provide a good description of the galaxy light profile.
-% However, the addition of a second function (of any analytical form) to the model did not improve the fit.
-% We thus employed a single S\'ersic profile for M105.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m105_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M105.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M105.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $57.2$  &  $5.2$ \\
-% T.W. 1D eq.  & S-bul + m-c & $50.9$  &  $5.3$ \\
-% T.W. 2D      & S-bul + m-c & $73.6$  &  $7.0$ \\
-% \hline
-% GD07         & S-bul & $58.3$  &  $4.3$ \\
-% S+11         & S-bul & $46.0$  &  $5.0$ \\
-% R+13         & core-S\'ersic & $55.1$  &  $5.8$ \\
-% L+14         & S-bul + m-c & $96.3$  &  $9.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m105}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M106 -- NGC 4258 \\} 
-%
-% M106 is a barred spiral galaxy, harbouring a Seyfert AGN \citep{veroncettyveron2006} 
-% with %a radio jet \citep{liuzhang2002} and 
-% circumnuclear dust \citep{martini2003}. 
-%
-% %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 14''.9$, $n = 2.0$). 
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model 
-% %($R_{\rm e} = 111''.7$, $n = 2.0$). 
-% %\cite{vika2012} proposed two different fits: the first with a S\'ersic-bulge + exponential-disk + PSF-nucleus
-% %($R_{\rm e} = 17''.0$, $n = 3.5$), 
-% %and the second with a S\'ersic-bulge + exponential-disk + PSF-nucleus + S\'ersic-bar
-% %($R_{\rm e} = 6''.3$, $n = 2.2$).
-%
-% \emph{1D fit -- }
-% We excluded from the fit the innermost $6''.1$ because affected by the AGN emission.
-% The boxy bar, responsible for the minimum in the B4 profile at $R \sim 65''$, 
-% is faint compared to the large-scale disk and in the light profile is only detectable as a slight swelling
-% within $65'' \lesssim R \lesssim 110''$.
-% This region has been excluded from the fit.
-% A peak in the ellipticity profile at $R \sim 10''$ suggests that a disk-like component might be 
-% embedded in the bulge.
-% Since the galaxy is barred, this component could be identified with a peanut bulge. 
-% However, we found that adding an extra component to the model introduces degeneracies, 
-% thus we preferred not to do so.
-% While the fit along the major-axis is satisfactory, 
-% the equivalent-axis residuals present a sneaky structure within $R \lesssim 20''$,
-% due to the unsubtracted embedded component.
-% %Our final model consists of a S\'ersic-bulge + exponential-disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m106_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M106.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M106.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d & $15.3$  &  $2.0$ \\
-% T.W. 1D eq.  & S-bul + e-d & $8.3$   &  $1.2$ \\
-% %T.W. 2D	& & $$  & $$  &  $$ \\
-% \hline
-% GD07     & S-bul + e-d		 & $14.9$   &  $2.0$ \\
-% S+11     & S-bul + e-d + G-n  	 & $111.7$  &  $2.0$ \\
-% V+12 (1) & S-bul + e-d + PSF-n	 & $17.0$   &  $3.5$ \\
-% V+12 (2) & S-bul + e-d + PSF-n + S-bar & $6.3$    &  $2.2$ \\
-% L+14     & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $6.3$	 &  $3.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m106}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 0524 \\} 
-%
-% NGC 0524 is an unbarred face-on lenticular galaxy. 
-%
-% %\cite{laurikainen2010} modeled this galaxy with a S\'ersic-bulge + exponential-disk + 2 Ferrer-lenses 
-% %($R_{\rm e} = 8''.9$, $n = 2.7$).
-% %\cite{sani2011} opted for a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 26''.8$, $n = 3.0$).
-% \emph{1D fit -- }
-% The unsharp mask of NGC 0524 unravels a faint multi-ring structure in the galaxy disk,
-% with a major ring peaking at $R \sim 20''$.
-% We accounted only for this brightest ring using a Gaussian ring profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n0524_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 0524.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 0524.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + G-r & $6.0$  &  $1.1$ \\
-% T.W. 1D eq.  & S-bul + e-d + G-r & $5.8$  &  $1.1$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% L+10      & S-bul + e-d + 2 F-l & $8.9$  &  $2.7$ \\
-% S+11      & S-bul + e-d	  & $26.8$  &  $3.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n0524}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 0821 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n0821_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 0821.}
-% \end{center}
-% \end{figure}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1023 \\}
-%
-% NGC 1023 is a barred lenticular galaxy. % with no partially depleted core \cite{faber1997}. \\
-%
-% %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 17''.7$, $n = 2.0$). 
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-bar model 
-% %($R_{\rm e} = 24''.0$, $n = 3.0$).
-% %\cite{lasker2014data} employed a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
-% %($R_{\rm e} = 9''.6$, $n = 3.1$).
-% \emph{1D fit -- }
-% The bar extends out to $R \lesssim 40''$.
-% %The light profile of NGC 1023 is well described by a S\'ersic-bulge + exponential-disk + Ferrer-bar model.
-% Small deviations of the disk from a perfect exponential profile, 
-% within the region $60'' \lesssim R \lesssim 125''$ (that has been excluded from the fit), 
-% can be ascribed to some faint residual spiral arms, also noticeable in the 2D residual image. 
-% The peak at $R \sim 10''$ in the B4 profile signals the presence of an embedded (and faint) disk.
-% The 1D residuals show a structure within $R \lesssim 10''$ caused by this unsubtracted 
-% component, also noted by \cite{lasker2014data}.
-% Attempts to account for the inner disk by adding a fourth function to the model 
-% did not significantly modify the best-fit bulge parameters,
-% thus we elected not to model the embedded disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n1023_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 1023.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 1023.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $9.2$  &  $2.1$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $7.4$  &  $2.0$ \\
-% T.W. 2D      & S-bul + e-d + G-bar & $6.6$  &  $2.3$ \\
-% \hline
-% GD07    & S-bul + e-d 	& $17.7$  &  $2.0$ \\
-% S+11    & S-bul + e-d + G-bar & $24.0$  &  $3.0$ \\
-% L+14    & S-bul + e-d + S-bar & $9.6$   &  $3.1$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n1023}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1300 \\}
-%
-% NGC 1300 is a face-on, barred spiral galaxy. % with no partially depleted core \citep{graham2012MNRAS}. 
-%
-% %\cite{sani2011} fit NGC 1300 with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 85''.4$, $n = 3.0$).
-% %\cite{lasker2014data} built their model with a S\'ersic-bulge + exponential-disk + PSF-nucleus + exponential-inner-disk + 
-% %S\'ersic-bar + spiral arms
-% %($R_{\rm e} = 10''.4$, $n = 4.3$).
-%
-% \emph{1D fit -- }
-% The morphology of NGC 1300 is quite complex. 
-% In addition to a large scale disk and a bulge, the galaxy is composed of 
-% a large scale bar that extends up to $R \lesssim 90''$, two prominent spiral arms 
-% and an inner disk-like component ($R \lesssim 5''$), disclosed by the peaks in the ellipticity and PA profiles.
-% We truncate the light profile at $R \sim 50''$ and we fit the inwards combination of the large-scale bar and the disk 
-% as a single component, using an exponential function.
-% The embedded component is described with a low-$n$ S\'ersic profile.
-% %Our final model consists of a S\'ersic-bulge + exponential-(disk+bar) + S\'ersic-inner disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n1300_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 1300.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 1300.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-(d+bar) + S-id & $9.9$  &  $3.8$ \\
-% T.W. 1D eq.  & S-bul + e-(d+bar) + S-id & $8.1$  &  $3.6$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% S+11    & S-bul + e-d & $85.4$  &  $3.0$ \\
-% L+14    & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $10.4$  &  $4.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n1300}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1316 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n1316_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 1316.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 1316.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + 2 G-r + G-n & $21.5$  &  $2.0$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + 2 G-r + G-n & $15.9$  &  $1.8$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% S+11      & S-bul + e-d + G-n & $93.0$  &  $5.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n1316}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1332 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 1332.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 1332.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + S-id + m-c & $34.7$  &  $5.1$ \\
-% T.W. 1D eq.  & S-bul + S-id + m-c & $18.0$  &  $3.7$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n1332}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1374 \\}
-%
-% ok
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1399 \\}
-%
-% NGC 1399, the central galaxy of the Fornax cluster, is an elliptical galaxy with a partially depleted core 
-% ($R_{\rm break} \sim 2''.4$, \citealt{rusli2013,dullograham2014cores}).
-% The nuclear activity of NGC 1399 is classified as Seyfert \citep{veroncettyveron2006},
-% but the galaxy lacks of dust \citep{tran2001}.
-%
-% %\cite{grahamdriver2007} fit the galaxy light profile with a single S\'ersic-bulge profile 
-% %($n = 16.8$).  
-% %\cite{rusli2013} modeled NGC 1399 with a core-S\'ersic profile and the sum of a S\'ersic and an exponential
-% %function accounting for the galaxy halo 
-% %($R_{\rm e} = 36''.2$, $n = 7.38$). 
-% %\cite{lasker2014data} used a S\'ersic-bulge + mask-core model 
-% %($R_{\rm e} = 154''.0$, $n = 11.1$). 
-%
-% \emph{1D fit -- }
-% The ellipticity and PA profiles display a steep decline within $R \lesssim 60''$,
-% suggesting the presence of an embedded disk.
-% This inner component is also visible, although very faint, in the unsharp mask.
-% TBD!! velocity map, the disk is face on
-% We note that, after excluding the innermost $6''.1$ affected by the partially depleted core,
-% a single S\'ersic profile is not sufficient to describe the whole galaxy light profile.
-% The addition of an inner exponential function to the model 
-% notably improves the fit.
-% %We build our final model with a S\'ersic-bulge + mask-core + exponential-inner disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n1399_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 1399.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 1399.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c + e-id & $405.2$  &  $10.0$ \\
-% T.W. 1D eq.  & S-bul + m-c + e-id & $338.1$  &  $10.0$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% GD07         & S-bul  		    & $-$      &  $16.8$ \\
-% R+13         & core-S\'ersic + (S+e)-halo & $36.2$   &  $7.4$ \\
-% L+14         & S-bul + m-c		    & $154.0$  &  $11.1$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n1399}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 2273 \\}
-%
-% NGC 2273 is a barred spiral galaxy with a Seyfert AGN \citep{contini1998} 
-% and circumnuclear dust \citep{simoeslopes2007}. 
-% Its bar is surrounded by two tightly wound star-forming spiral arms that resemble a ring
-% \citep{comeron2010}. 
-%
-% \cite{laurikainen2005} pointed out the presence of an inner disk embedded in the bulge of NGC 2273,
-% but they deliberately chose not to model it due to the degeneracy between the functions describing the bulge
-% and the inner disk. 
-% %Their final model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar 
-% %($R_{\rm e} = 2''.6$, $n = 1.8$). 
-%
-% \emph{1D fit -- }
-% The bar of NGC 2273 extends out to $R \lesssim 25''$. 
-% The pseudo-ring does not produce any evident swelling in the light profile, 
-% therefore we do not account for it in the galaxy model.
-% The isophotal parameters confirm the presence of a nuclear disk-like component within $R \lesssim 5''$.
-% However, as noted by \cite{laurikainen2005}, any attempt to account for the embedded disk resulted in a 
-% degenerate model. 
-% This is not surprising if one considers the poor spatial resolution of the galaxy image, 
-% the effective radius of the bulge being comparable to the FWHM of the PSF.
-% Although NGC 2273 hosts an optical AGN and nuclear dust, no central excess of light is observed in the 1D residuals.
-% The addition of a nuclear component to the model does not improve the fit and does not significantly affect
-% the bulge parameters.
-% %Our final model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n2273_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 2273.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 2273.}
-% \begin{center}
-% \begin{tabular}{llccc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $1.6$  &  $2.1$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $1.9$  &  $2.7$ \\
-% %T.W. 2D	&  & $$  &  $$ \\
-% \hline
-% L+05         & S-bul + e-d + F-bar & $2.6$  &  $1.8$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n2273}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 2549 \\}
-%
-% NGC 2549 is an edge-on barred lenticular galaxy. 
-%
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 11''.6$, $n = 7.0$). 
-%
-% \emph{1D fit -- }
-% Although the edge-on inclination of NGC 2549 complicates the identification of embedded components, 
-% a large scale bar ($R \lesssim 45''$) can be recognized in the galaxy image itself and -- more easily -- in the light profile.
-% We describe the large scale bar with a Ferrer profile.
-% A peak in the ellipticity profile discloses the presence of a disky component
-% embedded in the bulge ($R \lesssim 10''$).
-% This inner component can be spotted also by looking at the velocity map.
-% We fit it with a Ferrer profile.
-% %We build our final model with a S\'ersic-bulge + exponential-disk + 2 Ferrer-bars.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n2549_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 2549.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 2549.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + F-id & $6.1$  &  $2.3$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + F-id & $3.1$  &  $1.5$ \\
-% T.W. 2D      & S-bul + e-d + G-bar + G-id & $5.6$  &  $2.1$ \\
-% \hline
-% S+11         & S-bul + e-d & $11.6$  &  $7.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n2549}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 2778 \\}
-%
-% NGC 2778 is an almost face-on lenticular galaxy. 
-%
-% %\cite{grahamdriver2007} modeled NGC 2778 with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 2''.3$, $n = 1.6$). 
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk model
-% %($R_{\rm e} = 2''.5$, $n = 2.5$). 
-% %\cite{vika2012} employed a S\'ersic-bulge + exponential-disk model 
-% %($R_{\rm e} = 1''.5$, $n = 2.7$). 
-% %\cite{lasker2014data} fit the galaxy with a S\'ersic-bulge + exponential-disk + S\'ersic-bar
-% %($R_{\rm e} = 2''.8$, $n = 4.0$). 
-%
-% \emph{1D fit -- }
-% The peak in the ellipticity profile at $R \sim 5''$ unravels the existence of a nuclear component 
-% embedded in the galaxy bulge.
-% After an inspection of the unsharp mask, we identified this component with a small bar,
-% that we modeled with a Ferrer function.
-% We also accounted for some nuclear light excess by adding a PSF component to the model.
-% %We then fit NGC 2778 with a S\'ersic-bulge + exponential-disk + Ferrer-bar + PSF-nucleus.
-% We note that excluding the PSF component from our galaxy model does not significantly affect the 
-% bulge effective radius, but it increases the S\'ersic index to $n \sim 2$.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n2778_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 2778.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 2778.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + PSF-n & $2.3$  &  $1.3$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + PSF-n & $2.2$  &  $1.2$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% GD07         & S-bul + e-d	     & $2.3$  &  $1.6$ \\
-% S+11         & S-bul + e-d	     & $2.5$  &  $2.5$ \\
-% V+12         & S-bul + e-d	     & $1.5$  &  $2.7$ \\
-% L+14         & S-bul + e-d + S-bar & $2.8$  &  $4.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n2778}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 2787 \\}
-%
-% NGC 2787 is a barred lenticular galaxy with LINER nuclear activity \citep{veroncettyveron2006}.
-% An inner disk is embedded in the bulge of this galaxy \citep{erwin2003n2787}.
-% NGC 2787 features a spectacular structure of dust rings at its center \citep{erwinsparke2003}
-% and a nuclear stellar disk ($R \lesssim 1''.8$, \citealt{ledo2010}).
-%
-% %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 4''.6$, $n = 2.0$). 
-% %\cite{fisherdrory2008} decomposed NGC 2787 in a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 9''.1$, $n = 1.2$).
-% %\cite{laurikainen2010} employed a S\'ersic-bulge + exponential-disk + Ferrer-bar + Ferrer-lens model
-% %($R_{\rm e} \sim 4''$, $n = 1.3$).
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN 
-% %($R_{\rm e} = 15''.7$, $n = 3.0$). 
-% %\cite{lasker2014data} described NGC 2787 with a S\'ersic-bulge + truncated exponential-disk + 
-% %truncated S\'ersic-bar + S\'ersic-inner disk + PSF-nucleus
-% %($R_{\rm e} = 14''.3$, $n = 2.8$). 
-%
-% \emph{1D fit -- }
-% NGC 2787 has an undoubtedly complex morphology. 
-% This galaxy is made of a bulge, a large scale disk, a bar (see the peaks in the ellipticity, PA and B4 profiles
-% at $R \sim 30''$) with two ansae, an inner disk (or bar?) embedded in the bulge (see the peak in the ellipticity profile
-% at $R \sim 17''$), and a bright nucleus.
-%
-% Beyond $R \gtrsim 50''$, where the galaxy large scale disk extends without being affected by the bar ansae,
-% the surface brightness profile is not a perfect exponential, being better described by a S\'ersic function
-% with $n < 1$.
-% Curiously, at optical wavelengths the disk has an exponential decline with no truncation or anti-truncation 
-% (see \citealt{erwin2003n2787} their Figure 14, and \citealt{erwin2008}).
-% Here we propose two different models for NGC 2787.
-% In both cases we used a S\'ersic profile for the bulge, a Ferrer function for the bar, a second Ferrer function for the inner disk (or bar) 
-% and a PSF for the nucleus. 
-% We then described the large scale disk using a S\'ersic function with $n < 1$ 
-% or an exponential function. 
-% In the last case we needed to exclude the data within $R \sim 30'' - 50''$ where the ansae produce a hollow.
-% The two different decompositions result in the same bulge best-fit parameters ($R_{\rm e} \sim 5''$, $n \sim 1$)
-% along the major-axis, whereas the outcome is significantly different along the equivalent-axis 
-% ($n = 1.3$ when using the exponential-disk and $n = 2.2$ when using the S\'ersic-disk).
-%
-% might just pick one TBD!!
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n2787_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 2787.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 2787.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% \multicolumn{4}{c}{\emph{exponential-disk}} \\
-% %\hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + F-id + PSF-nucleus & $4.8$  &  $1.1$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + F-id + PSF-nucleus & $3.3$  &  $1.3$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% \multicolumn{4}{c}{\emph{S\'ersic-disk}}\\
-% %\hline
-% T.W. 1D maj. & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.6$  &  $1.1$ \\
-% T.W. 1D eq.  & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.4$  &  $2.2$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% GD07         & S-bul + e-d					  & $4.6$   &  $2.0$ \\
-% L+10         & S-bul + e-d + F-bar + F-l			  & $4.0$   &  $1.3$ \\
-% S+11         & S-bul + e-d + G-bar + G-n			  & $15.7$  &  $3.0$ \\
-% L+14         & S-bul + trunc. e-d + trunc. S-bar + S-id + PSF-n & $14.3$  &  $2.8$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n2787}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 2974 \\}
-%
-% NGC 2974 is a spiral galaxy which has been misclassified as an elliptical galaxy in the RC3 catalog.
-% The galaxy hosts a Seyfert AGN \citep{veroncettyveron2006} and filamentary dust in its center \citep{tran2001}.
-%  
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + Gaussian-AGN 
-% %($R_{\rm e} = 27''.2$, $n = 3.0$). 
-%
-% \emph{1D fit -- }
-% From an inspection of the unsharp mask, we identified a ring structure at $R \sim 50''$, 
-% probably a residual of two tightly wound spiral arms,
-% and an elongated bar-like component within $R \lesssim 30''$, that we fit with a Ferrer function.
-% The last one produces a peak in the ellipticity profile at $R \sim 20''$.
-% Although the ring is extremely faint, it is important to account for it in the galaxy decomposition. 
-% A model without the ring component results in a ``steeper'' exponential-disk (the disk has a smaller scale length 
-% and a lower central surface brightness) and produces bad residuals within $R \lesssim 40''$.
-% The nuclear component is fit with a Gaussian profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 2974.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 2974.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-n + G-r & $8.3$   &  $1.4$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + G-n + G-r & $6.9$   &  $1.2$ \\
-% T.W. 2D      & S-bul + e-d + G-bar + m-n	 & $10.6$  &  $1.3$ \\
-% \hline
-% S+11         & S-bul + G-n & $27.2$  &  $3.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n2974}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%   
-% {\bf NGC 3079 \\}
-%
-% inner component?? ok fuck it
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3079_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3079.}
-% \end{center}
-% \end{figure}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3091 \\}
-%
-% NGC 3091 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.62$, \citealt{rusli2013}).
-%
-% %\cite{rusli2013} modeled NGC 3091 with a single core-S\'ersic profile 
-% %($R_{\rm e} = 91''.0$, $n = 9.3$). 
-%
-% \emph{1D fit -- }
-% The data within the innermost $6''.1$ are excluded from the fit.
-% A faint embedded component ($R \lesssim 10''$) can be recognized in the unsharp mask and has a corresponding peak in the
-% ellipticity profile.
-% This extra component is clearly visible in the residual image obtained by subtracting a 2D S\'ersic model from the  
-% galaxy image.
-% However, any attempt to account for the embedded component resulted in an unsatisfactory fit and did not 
-% significantly affect the bulge parameters.
-% We thus elected not to model the inner component.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3091_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3091.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3091.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $100.5$  &  $7.6$ \\
-% T.W. 1D eq.  & S-bul + m-c & $51.2$	&  $6.6$ \\
-% T.W. 2D      & S-bul + m-c & $67.1$	&  $6.7$ \\
-% \hline
-% R+13         & core-S\'ersic & $91.0$  &  $9.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3091}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3115 \\}
-%
-% NGC 3115 is an edge-on elliptical/lenticular galaxy. 
-% Its nuclear activity is classified as passive in the optical wavelengths \citep{gavazzi2013nuclspec}.
-% This galaxy features a nuclear stellar disk ($R \sim 1''$, \citealt{scorzabender1995,ledo2010}).
-%
-% \cite{grahamdriver2007} TBD!!! ask Alister what did they do, not clear from appendix
-% ($n = 13.0$). 
-% \cite{fisherdrory2008} decomposed the galaxy in a S\'ersic-bulge + exponential disk 
-% ($R_{\rm e} = 31''.0$, $n = 3.9$). 
-% %\cite{sani2011} modeled NGC 3115 with a S\'ersic-bulge + exponential disk 
-% %($R_{\rm e} = 27''.3$, $n = 3.0$). 
-% %\cite{lasker2014data} used a S\'ersic-bulge + exponential disk + S\'ersic-envelope 
-% %($R_{\rm e} = 3''.9$, $n = 3.0$). 
-%
-% \emph{1D fit -- }
-% NGC 3115 is an example of a galaxy with an intermediate scale disk.
-% The surface brightness profile of NGC 3115 does not have an exponential decline at large radii 
-% because the disk component does not dominate the outer regions of the galaxy.
-% This is immediately evident by looking at the ellipticity and B4 profiles.
-% Going from the galaxy center to the outskirts, the ellipticity increases until it reaches its maximum 
-% ($\epsilon \sim 0.65$) at $R \sim 90''$. 
-% After this point, it starts declining, being as low as $\epsilon \sim 0.55$ at $R \sim 240''$. 
-% The galaxy isophotes display a positive diskyness within $R \sim 90''$, but become perfect ellipses 
-% ($B4 \sim 0$) beyond that point.
-% Now, because galaxy disks typically have fixed ellipticity, reflecting their inclination to our line of sight,
-% the previous observations tell us that, going from the galaxy center to the outer regions,
-% the disk of NGC 3115 becomes increasingly important relative to the spheroid light, reaching its maximum at $R \sim 90''$.
-% Beyond $R \gtrsim 90''$, the contribution from the disk light starts declining more rapidly than the spheroid light.
-% This interpretation is supported by the results of \cite{arnold2011n3115},
-% who found that within $R \sim 110''$ the bulge of NGC 3115 is flattened and rotates rapidly ($v/\sigma \gtrsim 1.5$),
-% whereas at larger radii the rotation declines dramatically (to $v/\sigma \sim 0.7$), 
-% but remains well aligned with the inner regions. \\
-% From an inspection of the unsharp mask, we identify a faint nuclear edge-on ring ($R \sim 15''$), 
-% which produces a corresponding peak in the ellipticity profile. \\
-% %We build our model with a S\'ersic-bulge + exponential disk + Gaussian-ring. \\
-% We do not observe any nuclear excess of light in the 1D residuals, 
-% contrary to what we expected given the presence of a nuclear stellar disk. 
-% The addition of a PSF component to the final model does not significantly change the outcome of the fit. 
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3115_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3115.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3115.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + G-r & $43.6$  &  $4.4$ \\
-% T.W. 1D eq.  & S-bul + e-d + G-r & $34.4$  &  $5.1$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% GD07         & ??? TBD	       & $-$	&  $13.0$ \\
-% S+11         & S-bul + e-d	       & $27.1$ &  $3.0$ \\
-% L+14         & S-bul + e-d + S-halo  & $3.9$  &  $3.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3115}
-% \end{table}
-%   
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3227 \\}
-%
-% NGC 3227 is a spiral galaxy with a large-scale bar. 
-% This galaxy hosts a Seyfert AGN \citep{khachikian1974} and circumnuclear dust \citep{martini2003}. 
-%
-% %\cite{laurikainen2004} decomposed NGC 3227 into a S\'ersic-bulge + exponential-disk + Ferrer-bar 
-% %($R_{\rm e} = 1''.8$, $n = 2.2$). 
-% %\cite{sani2011} described this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 82''.9$, $n = 4.0$). 
-% %\cite{lasker2014data} used a S\'ersic-bulge + exponential disk + S\'ersic-bar 
-% %($R_{\rm e} = 0''.7$, $n = 4.1$). 
-%
-% \emph{1D fit -- }
-% The large-scale bar produces an evident bump in the major-axis surface brightness profile,
-% which is curiously absent in the equivalent-axis profile. \\
-% We modeled the bar with a Ferrer function and the nucleus with a Gaussian function. 
-% As expected, the Ferrer component is rejected by the equivalent-axis fit.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3227_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3227.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3227.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-n   & $8.1$  &  $1.7$ \\
-% T.W. 1D eq.  & S-bul + e-d + [F-bar] + G-n & $4.6$  &  $1.1$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% L+04         & S-bul + e-d + F-bar & $1.8$  &  $2.2$ \\
-% S+11         & S-bul + e-d	     & $82.9$ &  $4.0$ \\
-% L+14         & S-bul + e-d + S-bar & $0.7$  &  $4.1$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3227}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3245 \\}
-%
-% NGC 3245 is a lenticular galaxy.
-%
-% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 11''.3$, $n = 4.3$). 
-% %\cite{laurikainen2010} described the galaxy with a S\'ersic-bulge + exponential-(disk+lens) + Ferrer-inner disk 
-% %($R_{\rm e} \sim 4''$, $n = 2.4$).  
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 4''.6$, $n = 2.5$). 
-% %\cite{vika2012} employed a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 3''.5$, $n = 2.6$). 
-% %\cite{beifiori2012} decomposed the galaxy into a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 4''.00$, $n = 1.6$). 
-% %\cite{lasker2014data} built their model with a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
-% %($R_{\rm e} = 1''.95$, $n = 1.6$). 
-%
-% \emph{1D fit -- }
-% The unsharp mask reveals the presence of an embedded disk ($R \lesssim 15''$), 
-% confirmed by the corresponding peaks in the ellipticity and B4 profiles.
-% We model this inner component with a Ferrer function.
-% %We model the galaxy with a S\'ersic-bulge + exponential-disk + Ferrer-inner disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3245_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3245.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3245.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-id & $4.4$  &  $2.9$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-id & $2.4$  &  $1.7$ \\
-% T.W. 2D      & S-bul + e-d + G-id & $1.9$  &  $1.8$ \\
-% \hline
-% GD07         & S-bul + e-d		& $11.3$ &  $4.3$ \\
-% L+10         & S-bul + e-(d+l) + F-id & $4.0$  &  $2.4$ \\
-% S+11         & S-bul + e-d		& $4.6$  &  $2.5$ \\
-% V+12         & S-bul + e-d		& $3.5$  &  $2.6$ \\
-% B+12         & S-bul + e-d		& $4.0$  &  $1.6$ \\
-% L+14         & S-bul + e-d + S-bar	& $2.0$  &  $1.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3245}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 3377 \\}
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3377.}
-% \end{center}
-% \end{figure}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3384 \\}
-%
-% NGC 3384 is a barred lenticular galaxy that hosts 
-% an embedded disk ($R \lesssim 11''$, \citealt{erwin2004}) and 
-% a nuclear stellar disk ($R \lesssim 0''.8$, \citealt{ledo2010}).
-%
-% %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 2''.5$, $n = 1.7$). 
-% %\cite{laurikainen2010} described the galaxy with a S\'ersic-bulge + exponential-disk + 2 Ferrer-bars
-% %($R_{\rm e} \sim 4''$, $n = 1.5$).  
-% %\cite{sani2011} employed a S\'ersic-bulge + exponential-disk + Gaussian-bar 
-% %($R_{\rm e} = 4''.4$, $n = 2.5$). 
-% %\cite{beifiori2012} modeled the galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 8''.3$, $n = 2.3$). 
-% %\cite{lasker2014data} decomposed the galaxy into a S\'ersic-bulge + exponential-disk + S\'ersic-inner disk + 
-% %S\'ersic-nuclear disk + S\'ersic-bar
-% %($R_{\rm e} = 5''.9$, $n = 2.5$). 
-%
-% \emph{1D fit -- }
-% The isophotal parameters clearly show the presence of a boxy bar that extends out to $R \lesssim 18''$.
-% We model the bar with a Ferrer function.
-% An embedded disk can be seen in the unsharp mask and produces the peak in the ellipticity profile at $R \sim 4''$.
-% modeling the embedded disk turned out to be a complicated task, resulting in a degenerate model.
-% We elected not to fit the embedded disk (nor the nuclear disk) and we therefore excluded from the fit the innermost $3''.7$,
-% where there two components are expected to dominate.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3384_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3384.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3384.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + m-n & $5.5$  &  $1.6$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + m-n & $5.6$  &  $1.8$ \\
-% %T.W. 2D	&  & $$  &  $$ \\
-% \hline
-% GD07         & S-bul + e-d		      & $2.5$  &  $1.7$ \\
-% L+10         & S-bul + e-d + 2 F-bar        & $4.0$  &  $1.5$ \\
-% S+11         & S-bul + e-d + G-bar	      & $4.4$  &  $2.5$ \\
-% B+12         & S-bul + e-d		      & $8.3$  &  $2.3$ \\
-% L+14         & S-bul + e-d + 2 S-id + S-bar & $5.9$  &  $2.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3384}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3393 \\}
-%
-% NGC 3393 is an edge-on spiral galaxy hosting a Seyfert AGN \citep{diaz1988n3393} and 
-% circumnuclear dust \citep{martini2003}.
-% The galaxy has a large-scale bar and a nuclear bar ($R \lesssim 3''$, \citealt{erwin2004}).  
-%
-% \emph{1D fit -- }
-% The large-scale bar ($R \lesssim 20''$) is modeled with a Ferrer function.
-% The poor spatial resolution of the data does not allow to fit the nuclear bar and/or the AGN component 
-% without incurring degeneracies.
-% We thus elected not to fit the nuclear components.
-% We note that the addition to the model of a central component would lower the bulge S\'ersic index,
-% whereas the the addition of a nuclear bar component would increase the bulge S\'ersic index.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3393_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3393.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3393.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $1.4$  &  $3.4$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $1.4$  &  $2.6$ \\
-% T.W. 2D      & S-bul + e-d + G-bar & $1.2$  &  $1.9$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3393}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3414 \\}
-%
-% NGC 3414 is a peculiar lenticular/elliptical galaxy. 
-% Different interpretations have been proposed about the morphology of this galaxy.
-% \cite{whitmore1990} suggested that NGC 3414 is an edge-on galaxy 
-% with a large scale polar ring, rather than a face-on barred lenticular.
-% \cite{laurikainen2010} decomposed NGC 3414 as a barred lenticular galaxy, but 
-% they cautioned against the uncertainty of their solution due to the possible misinterpretation of the 
-% galaxy morphology.
-%
-% \emph{1D fit -- }
-% The unsharp mask clearly shows that the edge on component does not extend all the way through the 
-% center of the galaxy, but instead it is truncated at $R \sim 20''$.
-% However, an elongated structure in the galaxy center resembles a nuclear edge-on disk ($R \lesssim 5''$).
-% The velocity map shows rotation within $R \lesssim 5''$ and no rotation within $5'' \lesssim R \lesssim 15''$.
-% Beyond $R \gtrsim 15''$ one can recognize a sign of rotation in the opposite direction of the nuclear region.
-% The velocity pattern is consistent with the galaxy being a spheroidal system containing a polar ring and a nuclear disk
-% both seen edge-on.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3414_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3414.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3414.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-id + G-r & $28.0$  &  $4.8$ \\
-% T.W. 1D eq.  & S-bul + e-id + G-r & $25.5$  &  $4.5$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% L+10         & S-bul + e-d + F-bar	  & $5.0$  &  $2.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3414}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3489 \\}
-%
-% NGC 3489 is a barred lenticular galaxy. 
-% Its disk has a smooth antitruncation at $R \sim 85''$ \citep{erwin2008}.
-%
-% \cite{nowak2010n3368n3489} argued for the presence of both a pseudo-bulge and a classical bulge. 
-% %\cite{laurikainen2010} fit this galaxy with a S\'ersic-bulge + exponential-disk + Ferrer-bar
-% %($R_{\rm e} \sim 2''$, $n = 2.1$). 
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 4''.6$, $n = 1.5$). 
-%
-% \emph{1D fit -- }
-% We excluded the data beyond $R \gtrsim 38''$ to avoid fitting the antitruncation region.
-% The bar is fit with a Ferrer function.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3489_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3489.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3489.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $2.2$  &  $1.5$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $1.7$  &  $1.3$ \\
-% T.W. 2D      & S-bul + e-d + G-bar & $1.7$  &  $2.1$ \\
-% \hline
-% L+10         & S-bul + e-d + F-bar & $2.0$  &  $2.1$ \\
-% S+11         & S-bul + e-d & $4.6$  &  $1.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3489}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 3585 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3585.}
-% \end{center}
-% \end{figure}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 3607 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3607.}
-% \end{center}
-% \end{figure}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 3608 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3608.}
-% \end{center}
-% \end{figure}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3842 \\}
-%
-% NGC 3842 is the brightest member of the Leo Cluster (Abell 1367).
-% It is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.7$, 
-% \citealt{rusli2013,dullograham2014cores}).
-%
-% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic model 
-% %($R_{\rm e} = 58''.8$, $n = 6.3$). 
-%
-% \emph{1D fit -- }
-% The light profile presents a swelling at $R \sim 20''$ and the ellipticity profile has a peak in the same position.
-% One can also glimpse a faint elongated oval in the unsharp mask.
-% The innermost $6''.1$ are excluded from the fit due to the presence of a partially depleted core.
-% As expected, a single S\'ersic model is not sufficient to provide a good description of the galaxy light profile 
-% and we need to add a second component (Ferrer function) to account for the embedded lens.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3842exp_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3842.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3842.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + F-l + m-c  & $100.7$  &  $8.1$ \\
-% T.W. 1D eq.  & S-bul + F-l + m-c  & $73.6$   &  $8.2$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% R+13         & core-S\'ersic & $58.8$  &  $6.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3842}
-% \end{table}  
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3998 \\}
-%
-% NGC 3998 is a barred lenticular galaxy with a Seyfert AGN and dust in its nucleus \citep{knapp1996n3998}.
-% Despite its large stellar velocity dispersion, this galaxy does not have a partially depleted core TBD!! ref??. 
-% \cite{gutierrez2011} identified a bar at $R \lesssim 8''$, a ring between $30'' \lesssim R \lesssim 50''$, and  
-% an antitruncation in the light profile of the disk at $R \sim 122''$.
-% \cite{laurikainen2010} found that NGC 3998 features a weak bar at $R < 8''$,
-% a bright lens at $R < 15''$ and a weak bump in the surface brightness profile at $R \sim 40''$ 
-% %($R_{\rm e} \sim 5''$, $n = 2.0$).
-% %\cite{sani2011} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN 
-% %($R_{\rm e} = 4''.7$, $n = 1.5$).
-% %\cite{beifiori2012} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 5''.7$, $n = 2.3$).
-% %\cite{lasker2014data} used a S\'ersic-bulge + exponential-disk (with inner truncation) + PSF-nucleus + 
-% %S\'ersic-inner disk + S\'ersic-bar 
-% %($R_{\rm e} = 2''.0$, $n = 1.1$).
-%
-% \emph{1D fit -- }
-% We see three distinct peaks in the ellipticity profile.
-% The first two peaks occur at $R \sim 7''$ and $R \sim 15''$, and they correspond to a weak bar and to a faint 
-% oval component respectively.
-% These components are both fit with a Ferrer function.
-% The third peak at $R \sim 35''$ coincides with a bump in the surface brightness profile and is produced by a ring.
-% The AGN component is modeled with a Gaussian profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3998_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3998.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3998.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + F-l + G-n + G-r & $5.8$  &  $1.2$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + F-l + G-n + G-r & $4.8$  &  $1.3$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% L+10         &  & $5.0$  &  $2.0$ \\
-% S+11         & S-bul + e-d + G-bar + G-n & $4.7$  &  $1.5$ \\
-% B+12         & S-bul + e-d & $5.7$  &  $2.3$ \\
-% L+14         & S-bul + trunc. e-d + PSF-n + S-bar + S-id & $2.0$  &  $1.1$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3998}
-% \end{table} 
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4026 \\}
-%
-% NGC 4026 is an edge-on lenticular galaxy with a nuclear stellar disk ($R \lesssim 0''.5$, \citealt{ledo2010}).
-%
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 11''.4$, $n = 3.5$).
-%
-% \emph{1D fit -- }
-% The unsharp mask reveals the presence of a bar ($R \lesssim 30''$) and of a disky component 
-% embedded in the bulge, that is responsible for the peak at $R \sim 5''$ in the B4 profile.
-% The last can be also recognized in the velocity map.
-% The bar is fit with a Ferrer function and the inner disk with a low-$n$ S\'ersic profile.
-% Due to the poor spatial resolution of our data, we were not able to model the nuclear stellar disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4026_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4026.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4026.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + S-id & $3.4$  &  $2.4$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + S-id & $6.3$  &  $2.1$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% S+11         & S-bul + e-d & $11.4$  &  $3.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4026}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4151 \\}
-%
-% NGC 4151 is a face-on barred spiral galaxy that hosts a Seyfert AGN \citep{veroncettyveron2006} 
-% and circumnuclear dust \citep{pott2010}.
-%
-% \cite{sani2011} fit this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-AGN model
-% ($R_{\rm e} = 5''.4$, $n = 3.5$).
-% \cite{gadotti2008} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar + PSF-AGN 
-% ($R_{\rm e} = 4''.7$, $n = 3.0$).
-%
-% \emph{1D fit -- }
-% embedded disk in the bulge,
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4151_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4151.}
-% \end{center}
-% \end{figure}
-%
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4261 \\}
-%
-% NGC 4261 is an elliptical galaxy with %a radio jet \citep{liuxie1992}, 
-% a LINER nucleus \citep{veroncettyveron2006}
-% and a dusty nuclear disk \citep{tran2001}.
-% The galaxy features a partially depleted core ($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
-%
-% %\cite{grahamdriver2007} fit NGC 4261 with a single S\'ersic-bulge 
-% %($R_{\rm e} = 88''.6$, $n = 7.3$).
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model 
-% %($R_{\rm e} = 22''.6$, $n = 4.0$).
-% %\cite{vika2012} employed a S\'ersic-bulge + mask-core 
-% %($R_{\rm e} = 24''.2$, $n = 3.5$).
-% %\cite{beifiori2012} adopted a single S\'ersic-bulge model 
-% %($R_{\rm e} = 48''.8$, $n = 4.3$).
-% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
-% %($R_{\rm e} = 77'.1$, $n = 6.3$).
-% %\cite{lasker2014data} employed a S\'ersic-bulge + mask-core model 
-% %($R_{\rm e} = 68'.4$, $n = 6.5$).
-%
-% \emph{1D fit -- }
-% The ellipticity profile has a peak at $R \sim 10''$, unraveling the presence of an embedded component.
-% We identify such component with an inner disk, possibly seen face-on, and we model it with a Ferrer function.
-% The innermost $6''.1$ are excluded from the fit due to the presence of a partially depleted core.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4261_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4261.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4261.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c + F-id & $52.6$  &  $4.7$ \\
-% T.W. 1D eq.  & S-bul + m-c + F-id & $47.3$  &  $4.3$ \\
-% T.W. 2D      & S-bul + m-c + e-id & $50.4$  &  $4.4$ \\
-% \hline
-% GD07      & S-bul		& $88.6$  &  $7.3$ \\
-% S+11      & S-bul + e-d + G-n & $22.6$  &  $4.0$ \\
-% V+12      & S-bul + m-c	& $24.2$  &  $3.5$ \\
-% B+12      & S-bul		& $48.8$  &  $4.3$ \\
-% R+13      & core-S\'ersic	& $77.1$  &  $6.3$ \\
-% L+14      & S-bul + m-c	& $68.4$  &  $6.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4261}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4291 \\}
-%
-% NGC 4291 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
-%
-% %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 14'.8$, $n = 4.0$).
-% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
-% %($R_{\rm e} = 15''.3$, $n = 5.6$).
-% %\cite{lasker2014data} adopted a S\'ersic-bulge + mask-core model
-% %($R_{\rm e} = 21''.3$, $n = 8.6$).
-%
-% \emph{1D fit -- }
-% After excluding from the fit the innermost $6''.1$, because affected by the partially depleted core,
-% we found that NGC 4291 can be modeled with a single S\'ersic profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4291_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4291.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4291.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $15.0$  &  $4.2$ \\
-% T.W. 1D eq.  & S-bul + m-c & $15.4$  &  $5.9$ \\
-% T.W. 2D      & S-bul + m-c & $20.8$  &  $7.7$ \\
-% \hline
-% GD07         & S-bul         & $14.8$  &  $4.0$ \\
-% R+13         & core-S\'ersic & $15.3$  &  $5.6$ \\
-% L+14         & S-bul + m-c   & $21.3$  &  $8.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4291}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4388 \\}
-%
-% NGC 4388 is an edge-on spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006} 
-% and copious nuclear dust \citep{martini2003}.
-%
-% \emph{1D fit -- }
-% The peaks at $R \sim 30''$ in the ellipticity and B4 profiles signal the presence of a bar.
-% The data between $35'' \lesssim R \lesssim 65''$ have been excluded because cannot be accommodated by the Ferrer function 
-% used to describe the bar. 
-% The AGN component is fit with a Gaussian profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4388_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4388.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4388.}
-% \begin{center}
-% \begin{tabular}{llccc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $4.6$  &  $0.6$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.2$  &  $1.3$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4388}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4459 \\}
-%
-% NGC 4459 is a lenticular galaxy.
-% Its disk profile is reported to have an antitruncation at $R \sim 119''$ \citep{gutierrez2011}.
-%
-% %\cite{laurikainen2010} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Ferrer-lens 
-% %($R_{\rm e} \sim 7'' $, $n = 3.0$).
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 10''.3$, $n = 2.5$).
-% %\cite{vika2012} modeled this galaxy with a S\'ersic-bulge + Moffat-nucleus 
-% %($R_{\rm e} = 25''.0$, $n = 3.9$).
-% %\cite{beifiori2012} adopted a single S\'ersic-bulge model 
-% %($R_{\rm e} = 155''.2$, $n = 7.4$).
-%
-% \emph{1D fit -- }
-% The ellipticity constantly increases across all the observed radial range ($R \lesssim 100''$).
-% This is an indication that, going from the galaxy center to the outskirts,
-% the disk component becomes increasingly more important than the spheroidal component.
-% However, the lack of a plateau in the ellipticity profile at large radii implies that at $R \sim 100''$ 
-% the contribution from the bulge is still significant compared to that of the disk.
-% In fact, the surface brightness profile does not display an exponential decline at large radii.
-% We note that the antitruncation reported by \cite{gutierrez2011} could be an artificial feature 
-% produced by the transition between the radial range where the disk becomes increasingly more important 
-% over the bulge and the truly exponential decline of the disk beyond $R \gtrsim 119''$.
-% We do not find evidence for any embedded components in our data.
-% A nuclear light excess is observed in the 1D residuals from a S\'ersic + exponential fit 
-% and is consequently modeled with a Gaussian profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4459_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4459.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4459.}
-% \begin{center}
-% \begin{tabular}{llccc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + G-n & $18.4$  &  $3.1$ \\
-% T.W. 1D eq.  & S-bul + e-d + G-n & $13.0$  &  $2.6$ \\
-% %T.W. 2D	&  & $$  &  $$ \\
-% \hline
-% L+10      & S-bul + e-d + F-l & $7.0$   &  $3.0$ \\
-% S+11      & S-bul + e-d	& $10.3$  &  $2.5$ \\
-% V+12      & S-bul + M-n	& $25.0$  &  $3.9$ \\
-% B+12      & S-bul		& $155.2$ &  $7.4$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4459}
-% \end{table}
-%
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4473 \\}
-%
-% NGC 4473 is an elliptical galaxy with an embedded disk \citep{scorzabender1998,ledo2010}.
-%
-% \cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
-% ($R_{\rm e} = 39''.6$, $n = 2.7$). 
-% \cite{sani2011} used a S\'ersic-bulge model
-% ($R_{\rm e} = 49''.3$, $n = 7.0$). 
-% \cite{vika2012} fit this galaxy with a S\'ersic-bulge + mask-core 
-% ($R_{\rm e} = 21''.3$, $n = 4.3$). 
-% \cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model 
-% ($R_{\rm e} = 10''.6$, $n = 2.2$).  
-% \cite{lasker2014data} described this galaxy with a single S\'ersic-bulge 
-% ($R_{\rm e} = 27''.9$, $n = 5.1$).  
-%
-%
-% \emph{1D fit -- }
-% TBD!! explain ellipticity profile...
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4473_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4473.}
-% \end{center}
-% \end{figure}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4564 \\}
-%
-% NGC 4564 is an edge-on lenticular galaxy.
-%
-% %\cite{grahamdriver2007} decomposed this galaxy into a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 4''.3$, $n = 3.2$). 
-% \cite{fisherdrory2008} fit this galaxy with a S\'ersic-bulge + exponential-disk 
-% ($R_{\rm e} = 8''.7$, $n = 3.7$). 
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 25''.0$, $n = 7.0$).
-% %\cite{vika2012} used a S\'ersic-bulge + exponential-disk model 
-% %($R_{\rm e} = 3''.0$, $n = 3.7$). 
-%
-% \emph{1D fit -- }
-% The isophotal parameters do not show any evidence for embedded components.
-% However, fitting NGC 4564 with a S\'ersic + exponential model results in bad residuals.
-% In the unsharp mask, one can hardly glimpse an oval structure extending out to $R \lesssim 15''$.
-% The addition of a Ferrer function to the model dramatically improves the fit and smoothes the residuals.
-% Although the lack of strong evidence for the presence of a (faint) third component, 
-% we prefer to model the lens with a Ferrer function 
-% because of the notable improvement in the goodness of the global fit.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4564_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4564.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4564.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-l & $5.0$  &  $2.6$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-l & $6.0$  &  $3.0$ \\
-% %T.W. 2D	&  & $$  &  $$ \\
-% \hline
-% GD07      & S-bul + e-d & $4.3$  &  $3.2$ \\
-% S+11      & S-bul + e-d & $25.0$ &  $7.0$ \\
-% V+12      & S-bul + e-d & $3.0$  &  $3.7$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4564}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4596 \\}
-%
-% NGC 4596 is an edge-on barred lenticular galaxy.
-%
-% %\cite{laurikainen2005} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Ferrer-bar + Ferrer-lens 
-% %($R_{\rm e} = 2''.8$, $n = 1.4$). 
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-bar 
-% %($R_{\rm e} = 28''.0$, $n = 3.0$). 
-% %\cite{vika2012} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
-% %($R_{\rm e} = 13''.2$, $n = 3.6$). 
-% %\cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model
-% %($R_{\rm e} = 44''.9$, $n = 4.4$).
-%
-% \emph{1D fit -- }
-% The morphology of this galaxy is quite complex. 
-% The bar extends out to $R \lesssim 50''$ and concludes in two evident ansae.
-% The large-scale disk features a wide ring that is responsible for the curvature in the light profile observed within 
-% $60'' \lesssim R \lesssim 130''$ (see also \citealt{comeron2014}).
-% An additional embedded disk-like component ($R \lesssim 15''$) can be recognized in the B4 profile and in the velocity map.
-% The bump in the light profile within $60'' \lesssim R \lesssim 70''$ corresponds to the ansae of the bar.
-% This data range has therefore been excluded from the fit.
-% The large scale bar is fit with a Ferrer function and the inner disk with a S\'ersic profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4596_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4596.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4596.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-r + S-id & $6.6$  &  $2.7$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + G-r + S-id & $9.0$  &  $3.0$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% L+05      & S-bul + e-d + F-bar + F-l & $2.8$  &  $1.4$ \\
-% S+11      & S-bul + e-d + G-bar & $28.0$  &  $3.0$ \\
-% V+12      & S-bul + e-d + S-bar & $13.2$  &  $3.6$ \\
-% B+12      & S-bul + e-d & $44.9$  &  $4.4$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4596}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4697 \\}
-%
-% NGC 4697 is an elliptical galaxy with an embedded disk \cite{scorzabender1995}.
-%
-% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge model
-% %($n = 4.0$).
-% %\cite{sani2011} described it with a S\'ersic-bulge 
-% %($R_{\rm e} = 100'.5$, $n = 5.0$). 
-% %\cite{vika2012} proposed a single S\'ersic-bulge model 
-% %($R_{\rm e} = 39''.1$, $n = 3.8$) 
-% %or a S\'ersic-bulge + exponential-disk model 
-% %($R_{\rm e} = 10''.0$, $n = 2.9$).
-% %\cite{beifiori2012} chose a single S\'ersic-bulge 
-% %($R_{\rm e} = 128''.7$, $n = 5.0$).
-% %\cite{lasker2014data} decomposed NGC 4697 into a S\'ersic-bulge + exponential-disk + PSF-nucleus + S\'ersic-envelope 
-% %($R_{\rm e} = 6''.3$, $n = 2.1$).
-%
-% \emph{1D fit -- }
-% The velocity map and the unsharp mask of NGC 4697 clearly show 
-% the presence of an intermediate-size disk embedded in the main spheroid.
-% However, the ellipticity profile presents two peaks. 
-% The peak at $R \sim 40''$ corresponds to the embedded disk already mentioned,
-% while the peak at $R \sim 10''$ unveils a second inner disk-like component.
-% After testing different decomposition models, 
-% in which we fit the embedded disks with a set of different functions (exponential, S\'ersic, Ferrer)
-% but we always described the main spheroidal component with a S\'ersic profile,
-% we noticed that the bulge parameters did not vary significantly among the various decompositions.
-% Our preferred model for NGC 4697 consists of a S\'ersic-bulge + 2 S\'ersic-inner disks.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4697_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4697.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4697.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + 2 S-id & $239.3$  &  $7.2$ \\
-% T.W. 1D eq.  & S-bul + 2 S-id & $226.4$  &  $6.7$ \\
-% T.W. 2D      & S-bul + e-id	& $121.4$  &  $5.0$ \\
-% \hline
-% GD07  & S-bul & $-$  &  $4.0$ \\
-% S+11  & S-bul & $100.5$  &  $5.0$ \\
-% V+12  & S-bul & $39.1$  &  $3.8$ \\
-% V+12  & S-bul + e-d & $10.0$  &  $2.9$ \\
-% L+14  & S-bul + e-d + PSF-n + S-halo & $6.3$  &  $2.1$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4697}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4889 \\}
-%
-% NGC 4889 is the brightest member of the Coma cluster. 
-% It is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.6$, \citealt{rusli2013}).
-%
-% %\cite{rusli2013} modeled NGC 4889 with a core-S\'ersic model 
-% %($R_{\rm e} = 169''.2$, $n = 9.8$). 
-%
-% \emph{1D fit -- }
-% We excluded from the fit the innermost $6''.1$ because affected by the partially depleted core and
-% we modeled the galaxy with a single S\'ersic profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4889.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4889.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $119.7$  &  $8.1$ \\
-% T.W. 1D eq.  & S-bul + m-c & $60.8$	&  $6.8$ \\
-% T.W. 2D      & S-bul + m-c & $104.3$  &  $7.8$ \\
-% \hline
-% R+13         & core-S\'ersic & $169.2$  &  $9.8$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4889}
-% \end{table}
-%   
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4945 \\}
-%
-% TBD!!! \\
-% NGC 4945 is an edge-on, dusty spiral galaxy that hosts a Seyfert AGN \citep{lin2011}.
-%
-% \cite{kormendy2010} found that the bulge of NGC 4945 is best modeled with a low-$n$ S\'ersic function
-% ($n = 1.3$).
-%
-% \emph{1D fit -- }
-% Given the edge-on inclination of this object, the identification of a possible large-scale bar is complicated.
-% The light profile has an obvious bump that could be interpreted in two different ways.
-% The bump could be produced by a large-scale bar; 
-% in this case, either the disk must have a truncation happening at a radius smaller than the length of the bar,
-% or its light profile cannot be exponential (this condition can be caused by the high inclination of the galaxy).
-% Alternatively, the bump could be due by the galaxy spiral arms, the disk has an exponential profile with no truncation
-% and the galaxy has no bar.
-% After checking that both scenarios result in similar best-fit parameters for the bulge, 
-% we choose the second and simpler hypothesis.
-% We exclude form the fit the data between $R \sim 100''-400''$, where the spiral arm would contribute to the galaxy light,
-% and we also exclude the innermost $6''.4$ due to the presence of the AGN.
-% Our final model for NGC 4945 consists of a S\'ersic-bulge + exponential-disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4945_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4945.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4945.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d & $13.9$  &  $1.4$ \\
-% T.W. 1D eq.  & S-bul + e-d & $9.5$   &  $1.7$ \\
-% T.W. 2D      & S-bul + e-d & $16.2$  &  $0.8$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4945}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 5077 \\}
-%
-% ok
-%
-% \emph{1D fit -- }
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n5077_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 5077.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 5077.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $23.5$  &  $4.2$ \\
-% T.W. 1D eq.  & S-bul + m-c & $23.0$  &  $5.7$ \\
-% T.W. 2D      & S-bul + m-c & $30.5$  &  $6.8$ \\
-% \hline
-% S+11         & S-bul + G-n & $29.2$  &  $6.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n5077}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 5128 - Centaurus A \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n5128_1Dfit.eps}
-% \caption{}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 5128.}
-% \begin{center}
-% \begin{tabular}{llccc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & TBD!! & $61.3$  &  $1.2$ \\
-% T.W. 1D eq.  &  & $60.8$  &  $2.2$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% S+11         & S-bul + e-d + G-n & $103.6$  &  $3.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n5128}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 5576 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
-% \caption{}
-% \end{center}
-% \end{figure}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 5845 \\}
-%
-% NGC 5845 is an elliptical/lenticular galaxy. 
-%
-% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 4''.1$,$n = 3.2$).
-% %\cite{sani2011} fit it with a S\'ersic-bulge 
-% %($R_{\rm e} = 3''.7$, $n = 3.0$). 
-% %\cite{vika2012} used a S\'ersic-bulge model 
-% %($R_{\rm e} = 3''.5$, $n = 2.6$).
-% %\cite{beifiori2012} chose a single S\'ersic-bulge 
-% %($R_{\rm e} = 4''.1$, $n = 3.5$).
-% %\cite{lasker2014data} described this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 3''.5$, $n = 2.8$).
-%
-% \emph{1D fit -- }
-% The small apparent size of NGC 5845 (compared to the PSF FWHM) implies low resolution for the data 
-% and complications for the modeling of this galaxy.
-% Here, looking at the unsharp mask and the velocity field, we identify 
-% a disk component, either large-scale or embedded.
-% To rule out one of the two cases, a good test would be to check whether
-% the light profile of NGC 5845 presents an exponential decline in its outer part.
-% Unfortunately, the IRAC image is not deep enough and beyond $R \gtrsim 23''$ the galaxy light 
-% is fainter than $3 RMS_{\rm SKY}$.
-% %Since the too small radial range prevents us from disentangling between an embedded and a large-scale disk,
-% %we choose the most statistically significant solution (lowest $\chi^2$), 
-% %but we caution that the best fit parameters might be biased by a non adequate choice
-% %of the model components. 
-% %However, our results are in agreement with those from \cite{jia2012}, 
-% %who study the structure and kinematics of NGC5845 with HST/WFPC2 data 
-% %and previously published spatially resolved kinematics, and unambiguously identify a 
-% %large scale disk in both the photometry and the kinematics. \\
-% The ellipticity profile has a peak at $R \sim 13''$ and therefore suggests that the disk is indeed embedded.
-% However, when fitting NGC 5845 with a S\'ersic + exponential model, 
-% the lowest-$\chi^2$ solution does not reproduce an inner disk, but rather a large-scale one.
-% This is because the S\'ersic and the exponential function are degenerate in this decomposition, 
-% due to the small number of data points sampling the galaxy light profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n5845_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 5845.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 5845.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d & $3.6$  &  $2.5$ \\
-% T.W. 1D eq.  & S-bul + e-d & $3.1$  &  $2.3$ \\
-% T.W. 2D      & S-bul + e-d & $2.8$  &  $2.4$ \\
-% \hline
-% GD07      & S-bul & $4.1$  &  $3.2$ \\
-% S+11      & S-bul & $3.7$  &  $3.0$ \\
-% V+12      & S-bul & $3.5$  &  $2.6$ \\
-% B+12      & S-bul & $4.1$  &  $3.5$ \\
-% L+14      & S-bul & $3.5$  &  $2.8$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n5845}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 5846 \\}
-%
-% NGC 5846 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
-% This galaxy has a LINER nucleus \citep{carrillo1999} and filamentary nuclear dust \citep{tran2001}.
-%
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge
-% %($R_{\rm e} = 36''.4$, $n = 3.0$). 
-% %\cite{vika2012} used a S\'ersic-bulge + mask-core model 
-% %($R_{\rm e} = 46''.3$, $n = 3.7$). 
-% %\cite{rusli2013} fit this galaxy with a core-S\'ersic profile 
-% %($R_{\rm e} = 113''.2$, $n = 5.3$). 
-%
-% \emph{1D fit -- }
-% This galaxy has a strong isophotal twist between its center and $R \sim 70''$, and
-% its light profile presents a slight bump at $R \sim 20''$.
-% However, the isophotal parameters, the unsharp mask and the velocity map lack of clear evidence for an embedded component.
-% We thus model NGC 5846 with a single S\'ersic profile, after masking the innermost $6''.1$.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n5846_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 5846.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 5846.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $105.1$  &  $6.4$ \\
-% T.W. 1D eq.  & S-bul + m-c & $83.4$	&  $5.7$ \\
-% T.W. 2D      & S-bul + m-c & $85.1$	&  $5.2$ \\
-% \hline
-% S+11      & S-bul	    & $36.4$   &  $3.0$ \\
-% V+12      & S-bul + m-c   & $46.3$   &  $3.7$ \\
-% R+13      & core-S\'ersic & $113.2$  &  $5.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n5846}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 6251 \\}
-%
-% NGC 6251 is an elliptical galaxy with a large stellar velocity dispersion ($\sigma \sim 310~\rm km~s^{-1}$),
-% which is a clue for the presence of a partially depleted core.
-% The galaxy features a nuclear disk of dust \citep{ferrareseford1999n6251} and a Seyfert AGN \citep{panessabassani2002}.
-%
-% %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 173''.92$, $n = 11.8$). 
-% %\cite{sani2011} adopted a S\'ersic-bulge + Gaussian-AGN model 
-% %($R_{\rm e} = 42''.4$, $n = 7.0$). 
-% %\cite{lasker2014data} modeled this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 20''.6$, $n = 5.0$). 
-%
-% \emph{1D fit -- }
-% We masked the innermost $6''.1$ because possibly affected by the combined contribution of the AGN 
-% and the partially depleted core. 
-% A single S\'ersic profile provides a good description of NGC 6251.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n6251_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 6251.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 6251.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $41.7$  &  $6.8$ \\
-% T.W. 1D eq.  & S-bul + m-c & $30.1$  &  $5.6$ \\
-% T.W. 2D      & S-bul + m-c & $39.3$  &  $7.1$ \\
-% \hline
-% GD07      & S-bul	     & $173.9$  &  $11.8$ \\
-% S+11      & S-bul + G-n    & $42.4$	&  $7.0$ \\
-% L+14      & S-bul	     & $20.6$	&  $5.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n6251}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 7052 \\}
-%
-% NGC 7052 is an elliptical galaxy reported to have a partially depleted core 
-% ($R_{\rm break} = 0''.8$, \citealt{quillen2000}). 
-%
-% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 70''.4$, $n = 4.6$). 
-% %\cite{sani2011} used a S\'ersic-bulge model 
-% %($R_{\rm e} = 39''.3$, $n = 5.0$). 
-% %\cite{vika2012} fit this galaxy with a S\'ersic-bulge + exponential-disk
-% %($R_{\rm e} = 4''.3$, $n = 1.8$).
-% %\cite{lasker2014data} adopted a S\'ersic-bulge model 
-% %($R_{\rm e} = 26''.6$, $n = 4.2$). 
-%
-% \emph{1D fit -- }
-% A single S\'ersic function provides a fairly good description of the surface brightness profile of NGC 7052.
-% However, the residuals of such fit display a curious behaviour, having a nuclear light excess along the major-axis 
-% and a nuclear light deficit along the equivalent-axis. 
-% This pattern is still present when the innermost $6''.1$ are excluded and the fit is repeated with a S\'ersic profile.
-% The reasons for this are unclear. 
-% The best-fit parameters obtained from a single S\'ersic fit, without excluding the innermost data points,
-% are not significantly different from those obtained when excluding the core region (see Table \ref{tab:n7052}).
-% Given the uncertainty connected to the nuclear region of this galaxy,
-% we preferred the model that incorporates the exclusion of the innermost $6''.1$, 
-% with the caveat about the ambiguous presence of a partially depleted core.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n7052_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 7052.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 7052.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% \multicolumn{4}{c}{\emph{excluding innermost $6''.1$}} \\
-% T.W. 1D maj. & S-bul + m-c & $59.4$  &  $4.2$ \\
-% T.W. 1D eq.  & S-bul + m-c & $37.0$  &  $5.6$ \\
-% T.W. 2D      & S-bul + m-c & $36.2$  &  $4.0$ \\
-% \hline
-% \multicolumn{4}{c}{\emph{including innermost $6''.1$}} \\
-% T.W. 1D maj. & S-bul & $66.1$  &  $4.8$ \\
-% T.W. 1D eq.  & S-bul & $35.0$  &  $5.0$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% GD07      & S-bul & $70.4$  &  $4.6$ \\
-% S+11      & S-bul & $39.3$  &  $5.0$ \\
-% V+12      & S-bul + e-d & $4.3$  &  $1.8$ \\
-% L+14      & S-bul & $26.6$  &  $4.2$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n7052}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 7619 \\}
-%
-% NGC 7619 is an elliptical galaxy reported to have a partially depleted core ($R_{\rm break} = 0''.5$, \citealt{rusli2013}).
-%
-% %\cite{rusli2013} fit this galaxy with a core-S\'ersic profile 
-% %($R_{\rm e} = 100''.1$, $n = 9.3$). 
-%
-% \emph{1D fit -- }
-% We identified an embedded disk signaled by the peak at $R \sim 10''$ in the ellipticity profile.
-% The velocity map of this galaxy confirms the presence of a fast rotating component (Falcon-Barroso private comm.).
-% We modeled NGC 7619 with a S\'ersic + inner-exponential model.
-% We note that the residuals obtained from our best-fit model do not suggest the presence of a partially depleted core,
-% whereas they display a nuclear lack of light when the galaxy is modeled with a single S\'ersic-bulge. 
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n7619_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 7619.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 7619.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-id & $63.2$  &  $5.3$ \\
-% T.W. 1D eq.  & S-bul + e-id & $58.0$  &  $5.2$ \\
-% \hline
-% R+13      & core-S\'ersic & $100.1$  &  $9.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n7619}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 7768 \\}
-%
-% NGC 7768 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
-%
-% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
-% %($R_{\rm e} = 46''.1$, $n = 6.2$). 
-%
-% \emph{1D fit -- }
-% The image of NGC 7768 is corrupted by a saturated star, which lies close to the galaxy.
-% The sky background is not constant across the image.
-% To be safe, we fit only the innermost $R \lesssim 30''$, where the contribution from the background is negligible.
-% The data within $R < 6''.1$ are excluded from the fit due to the presence of a partially depleted core.
-% Our best-fit model consists of a single S\'ersic profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n7768_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 7768.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 7768.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $92.9$  &  $8.4$ \\
-% T.W. 1D eq.  & S-bul + m-c & $42.1$  &  $6.7$ \\
-% \hline
-% R+13      & core-S\'ersic & $46.1$  &  $6.2$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n7768}
-% \end{table}
-%  
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf UGC 03789 \\}
-%
-% UGC 03789 is a face-on spiral galaxy.
-%
-% \emph{1D fit -- }
-% This galaxy features a ring ($R \sim 20''$) and a nuclear bar ($R \lesssim 4''$),
-% which can be seen in the unsharp mask and produces corresponding peaks in the ellipticity and PA profiles.
-% The bar is fit with a Ferrer function.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/ugc03789_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for UGC 03789.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for UGC 03789.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-r & $1.8$  &  $1.9$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + G-r & $2.4$  &  $1.4$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:ugc3789}
-% \end{table}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \acknowledgments
-{\bf marconi, sani, hunt...}
-GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Elisabete Lima Da Cunha and Gonzalo Diaz 
-for useful discussion. \\
+%{\bf marconi, sani, hunt...}
+%GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Elisabete Lima Da Cunha and Gonzalo Diaz 
+%for useful discussion. \\
 This research was supported by Australian Research Council funding through grants
@@
 
-\appendix
-
-\section{1D analytical functions}
-\label{sec:app1}
-Here we provide the mathematical expressions of the analytical functions used to model 
-the observed surface brightness profiles, $\mu(R)$, of galaxies.
-The projected galactic radius, $R$,
-corresponds to the distance of the isophotes from the galaxy center (along either the major- or equivalent-axis). \\
-
-The \citeauthor{sersic1963} (\citeyear{sersic1963,sersic1968}) model is a three-parameter function of the following form:
-\begin{equation}
-\mu_{\rm S\acute{e}rsic}(\mu_{\rm e},R_{\rm e},n;R) = \mu_{\rm e} + \frac{2.5~b_{\rm n}}{\ln(10)} 
-\Biggl[\biggl(\frac{R}{R_{\rm e}}\biggr)^{1/n}-1\Biggr] ,
-\end{equation}
-\citep{caon1993,andredakis1995,grahamdriver2005}
-where $\mu_{\rm e}$ is the surface brightness at the effective radius $R_{\rm e}$ that encloses 
-half of the total light from the model. 
-The S\'ersic index $n$ is the parameter that measures the curvature of the radial light profile,
-and $b_{\rm n}$ is a scalar value defined in terms of the S\'ersic index $n$ such that:
-\begin{equation}
-\Gamma(2n) = 2\gamma(2n,b_{\rm n}),
-\end{equation}
-where $\Gamma$ is the complete gamma function \citep{ciotti1991} 
-and $\gamma$ is the incomplete gamma function defined by 
-\begin{equation}
-\gamma(2n,x) = \int_{0}^{x} {\rm e}^{-t} t^{2n-1} {\rm d}t .
-\end{equation} \\
-
-The exponential model is a special case ($n=1$) of the S\'ersic model.
-It can therefore be written as a two-parameter function such that:
-\begin{equation}
-\mu_{\rm exponential}(\mu_{\rm 0},h;R) = \mu_{\rm 0} + \frac{2.5}{\ln(10)} \biggl(\frac{R}{h} \biggr) ,
-\end{equation}
-where $\mu_{\rm 0}$ is the central surface brightness and $h$ is the scale length equal to $R_{\rm e}/1.678$. \\
-
-The Gaussian model is another special case ($n=0.5$) of the S\'ersic model, and thus also a two-parameter function of the following form:
-\begin{equation}
-\mu_{\rm Gaussian}(\mu_{\rm 0},FWHM;R) = \mu_{\rm 0} + \frac{2.5}{\ln(10)} 
-\biggl[\frac{R^2}{2(FWHM/2.355)^2} \biggr] ,
-\label{eq:gauss}
-\end{equation}
-where $\mu_{\rm 0}$ is the central surface brightness 
-and $FWHM$ is the full width at half maximum of the Gaussian profile. \\
-
-The \cite{moffat1969} model is a three-parameter function that can be expressed as:
-\begin{equation}
-\mu_{\rm Moffat}(\mu_{\rm 0},\alpha,\beta;R) = \mu_{\rm 0} - 2.5 
-\log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
-\end{equation}
-where $\mu_{\rm 0}$ is the central surface brightness,
-$\alpha$ is related to the $FWHM$ through 
-\begin{equation}
-FWHM = 2\alpha \sqrt{2^{1/\beta}-1} ,
-\end{equation}
-and $\beta$ regulates the shape of the profile at large radii. \\
-
-The Ferrer model is a four-parameter function defined as:
-\begin{equation}
-\mu_{\rm Ferrer}(\mu_{\rm 0},R_{\rm out},\alpha,\beta;R) = \left\{
-  \begin{array}{l l}
-    \mu_{\rm 0} - 2.5 \log \Biggl[ 1 - \biggl(\frac{R}{R_{\rm out}} \biggr)^{2-\beta} \Biggr]^{\alpha} 
-    & \quad \text{for $R<R_{\rm out}$}\\
-    +\infty & \quad \text{for $R\geq R_{\rm out}$}
-  \end{array} \right. ,
-\end{equation}
-where $\mu_{\rm 0}$ is the central surface brightness,
-$\alpha$ controls the sharpness of the truncation,
-$\beta$ is related to the central slope,
-and $R_{\rm out}$ is the outer radial limit within which the function is defined. \\
-
-The symmetric Gaussian ring is a three-parameter function of the following form:
-\begin{equation}
-\mu_{\rm Gaussian}(\mu_{\rm 0},R_{\rm 0},FWHM;R) = \mu_{\rm 0} + \frac{2.5}{\ln(10)} 
-\biggl[\frac{(R-R_{\rm 0})^2}{2(FWHM/2.355)^2} \biggr] ,
-\end{equation}
-where $\mu_{\rm 0}$ and $FWHM$ have the same meaning as in equation \ref{eq:gauss}, 
-and $R_{\rm 0}$ is the radius at which the Gaussian profile is centered. \\
-
-\bibliography{/Users/gsavorgnan/Dropbox/giulia_e_basta/Literature/SMBHbibliography}
+\bibliography{/Users/gsavorgnan/Dropbox_notsync/giulia_e_basta/Literature/SMBHbibliography}
 

### 2015-03-18 papers/MbhMsph/~mm.tex
robi<3u

--- 2015-03-18 papers/MbhMsph/mm.tex
@@
 \citep{laor1998,wandel1999,laor2001,ryan2007}.
+Recently, \cite{lasker2014data,lasker2014anal} derived $2.2~\rm \mu m$ bulge luminosities for 35 galaxies 
+(among which only 4 were classified as spiral galaxies), 
+and reported a slope of $0.75 \pm 0.10$ for their $M_{\rm BH} - L_{\rm sph}$ relation. 
+They also claimed that the black hole mass correlates equally well with the total galaxy luminosity (bulge+disk) 
+as it does with the bulge luminosity. \\
+The $M_{\rm BH} - L_{\rm sph}$ relation can be predicted from other two popular correlations involving the bulge velocity dispersion, $\sigma$.
+While the $M_{\rm BH} - \sigma$ relation \citep{ferraresemerritt20}
 
-lasker
+the $M_{\rm BH} - \sigma$ (black hole mass - velocity dispersion) 
+and
 

### 2015-03-18 papers/MbhMsph/mm.sh

@@ -1,0 +1,5 @@
+pdflatex mm
+bibtex mm
+pdflatex mm
+pdflatex mm
+##dvipdfm mm.dvi

### 2015-03-18 python_codes/databases/initialize/init.py

@@ -8,6 +8,9 @@ dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_viv
 ancillaryfilename = '/Users/gsavorgnan/galaxy_vivisection/data/ancillary/SMBHgalaxysample2013.top'
 literaturefilename = '/Users/gsavorgnan/galaxy_vivisection/data/ancillary/literature_decompositions.top'
 mosaicsfilename = '/Users/gsavorgnan/galaxy_vivisection/data/galaxies/mosaics.list'
+sgs2013filename = '/Users/gsavorgnan/galaxy_vivisection/data/Alister-data/SGS13/kmagssph.dat'
+colorfilename = '/Users/gsavorgnan/galaxy_vivisection/data/ancillary/iraccolor.dat'
+
 
 def replaceNull(entry):
 	if entry == '""':
@@ -56,7 +59,7 @@ def ancillary():
 		ELLIPTICAL_my integer, edgeon integer, source text, RA real, DEC real, 
 		z real, morphtype text, simplemorphtype text, bar integer, distance real, core integer, 
 		core_inferred_from_sigma integer, core_my integer, sigma real, mass_BH real, perr_mass_BH real, merr_mass_BH real,
-		size_core real, ref_size_core text, KMAG_sph real, KMAG_tot real)''')
+		size_core real, ref_size_core text, KMAG_sph real, KMAG_tot real, pseudobulge_KH13 integer)''')
 	
 	for line in data:
 		if line.split()[0] != '#':
@@ -112,15 +115,44 @@ def ancillary():
 			KMAG_tot = replaceNull(KMAG_tot)
 			KMAG_sph = line.split()[47]
 			KMAG_sph = replaceNull(KMAG_sph)
+			pseudobulge_KH13 = line.split()[83]
+			pseudobulge_KH13 = replaceBoolean(pseudobulge_KH13)
 			
 			collection = [gal_id, gal_name, IRAC_image, fit1D_done, fit2D_done, ELLIPTICAL_my, edgeon, source, RA, DEC, z, morphtype, simplemorphtype, bar, distance, 
-				core, core_inferred_from_sigma, core_my, sigma, mass_BH, perr_mass_BH, merr_mass_BH, size_core, ref_size_core, KMAG_sph, KMAG_tot]
-			cur.execute('INSERT INTO Ancillary VALUES (?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?)', collection)
[…]

### 2015-03-18 python_codes/instruments/linear_regression/colorline.py

@@ -1,0 +1,119 @@
+# Topics: line, color, LineCollection, cmap, colorline, codex
+'''
+Defines a function colorline that draws a (multi-)colored 2D line with coordinates x and y.
+The color is taken from optional data in z, and creates a LineCollection.
+
+z can be:
+- empty, in which case a default coloring will be used based on the position along the input arrays
+- a single number, for a uniform color [this can also be accomplished with the usual plt.plot]
+- an array of the length of at least the same length as x, to color according to this data
+- an array of a smaller length, in which case the colors are repeated along the curve
+
+The function colorline returns the LineCollection created, which can be modified afterwards.
+
+See also: plt.streamplot
+'''
+
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.collections import LineCollection
+from matplotlib.colors import ListedColormap, BoundaryNorm
+import matplotlib.colors as mcolors
+
+def make_colormap(colors):
+    """
+    Define a new color map based on values specified in the dictionary
+    colors, where colors[z] is the color that value z should be mapped to,
+    with linear interpolation between the given values of z.
+
+    The z values (dictionary keys) are real numbers and the values
+    colors[z] can be either an RGB list, e.g. [1,0,0] for red, or an
+    html hex string, e.g. "#ff0000" for red.
+    """
+
+    from matplotlib.colors import LinearSegmentedColormap, ColorConverter
+    from numpy import sort
+    
+    z = sort(colors.keys())
+    n = len(z)
+    z1 = min(z)
+    zn = max(z)
+    x0 = (z - z1) / (zn - z1)
+    
+    CC = ColorConverter()
+    R = []
+    G = []
+    B = []
+    for i in range(n):
+        #i'th color at level z[i]:
+        Ci = colors[z[i]]      
+        if type(Ci) == str:
+            # a hex string of form '#ff0000' for example (for red)
+            RGB = CC.to_rgb(Ci)
+        else:
+            # assume it's an RGB triple already:
+            RGB = Ci
+        R.append(RGB[0])
+        G.append(RGB[1])
+        B.append(RGB[2])
+
+    cmap_dict = {}
+    cmap_dict['red'] = [(x0[i],R[i],R[i]) for i in range(len(R))]
[…]

### 2015-03-18 python_codes/plots/scaling_relations/relations.py

@@ -3,12 +3,14 @@ import os
 import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib
+import matplotlib.colors as mcolors
 from scipy import stats
 from instruments.linear_regression import bces
 from instruments.linear_regression import predband
 from instruments.linear_regression import fitexy
 from instruments import b_n
-
+from instruments.linear_regression import colorline
+from instruments.linear_regression import akaike
 
 from matplotlib import rc
 rc('font',**{'family':'sans-serif','sans-serif':['CenturyGothic']})
@@ -23,6 +25,58 @@ dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_viv
 
 path_auxiliary_plots = '/Users/gsavorgnan/galaxy_vivisection/results/plots/auxiliary/'
 path_scalrel_plots = '/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/'
+
+
+
+def make_colormap(colors):
+    """
+    Define a new color map based on values specified in the dictionary
+    colors, where colors[z] is the color that value z should be mapped to,
+    with linear interpolation between the given values of z.
+
+    The z values (dictionary keys) are real numbers and the values
+    colors[z] can be either an RGB list, e.g. [1,0,0] for red, or an
+    html hex string, e.g. "#ff0000" for red.
+    """
+
+    from matplotlib.colors import LinearSegmentedColormap, ColorConverter
+    from numpy import sort
+    
+    z = sort(colors.keys())
+    n = len(z)
+    z1 = min(z)
+    zn = max(z)
+    x0 = (z - z1) / (zn - z1)
+    
+    CC = ColorConverter()
+    R = []
+    G = []
+    B = []
+    for i in range(n):
+        #i'th color at level z[i]:
+        Ci = colors[z[i]]      
+        if type(Ci) == str:
+            # a hex string of form '#ff0000' for example (for red)
[…]

### 2015-03-20 papers/MbhMsph/mm.tex
fiday

@@
 for which they reported a quasi-linear $M_{\rm BH} - M_{\rm sph}$ relation, 
-in agreement with a dry-merging formation scenario. 
+consistent with a dry-merging formation scenario. 
 Subsequent studies of the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm sph}$ diagrams 
@@
 used similar galaxy samples, which remained dominated by high-mass, early-type objects having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 
-and therefore recovered a near-linear relation. 
+and recovered a near-linear relation. 
 However, the consensus about a linear $M_{\rm BH} - M_{\rm sph}$ correlation was not unanimous. 
@@
 \citep{laor1998,wandel1999,laor2001,ryan2007}.
+Recently, \cite{lasker2014data,lasker2014anal} derived $2.2~\rm \mu m$ bulge luminosities for 35 galaxies 
+(among which only 4 were classified as spiral galaxies), 
+and reported a slope of $0.75 \pm 0.10$ for their $M_{\rm BH} - L_{\rm sph}$ relation. 
+They also claimed that the black hole mass correlates equally well with the total galaxy luminosity 
+as it does with the bulge luminosity. \\
+The $M_{\rm BH} - L_{\rm sph}$ relation can be predicted from other two correlations involving the bulge velocity dispersion, $\sigma$.
+The first of these two is the $M_{\rm BH} - \sigma$ relation \citep{ferraresemerritt2000,gebhardt2000},
+which can be described by a single power-law $M_{\rm BH} \propto \sigma^5$ 
+over the range in velocity dispersion $70-350~\rm km~s^{-1}$ (e.g.~\citealt{graham2011,mcconnell2011,grahamscott2013}).
+The second is the $L_{\rm sph} - \sigma$ relation, 
+which has long been known to be a ``double power-law'', 
+being $L_{\rm sph} \propto \sigma^5$ at the luminous end \citep{schechter1980,malumuthkrishner1981,vonderlinden2007,liu2008}, 
+and $L_{\rm sph} \propto \sigma^2$ at intermediate and faint luminosities 
+\citep{davies1983,held1992,matkovicguzman2005,derijcke2005,balcells2007screl,chilingarian2008,forbes2008,cody2009,tortora2009,kourkchi2012}. 
+The change in slope of the $L_{\rm sph} - \sigma$ relation occurs at $M_B \approx -20.5\rm~mag$, 
+corresponding to $\sigma \approx 200~\rm km~s^{-1}$. 
+That is, the $M_{\rm BH} - L_{\rm sph}$ relation should be better described by a ``broken'', rather than single, power-law, 
+having $M_{\rm BH} \propto L_{\rm sph}^{2.5}$ at the low-luminosity end, 
+and $M_{\rm BH} \propto L_{\rm sph}^1$ at the high-luminosity end.  
+Due to the scatter in the $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm sph}$) diagram, 
+studies that have not sufficiently probed below $M_{\rm BH} \approx 10^7\rm~M_\odot$ 
+miss the change in slope occuring at $M_{\rm BH} \approx 10^{(8 \pm 1)}\rm~M_\odot$, 
+and erroneously recover a single log-linear relation. \\
+When \cite{graham2012bent} pointed out this overlooked inconsistency, 
+he identified two different populations of galaxies, 
+namely the core-S\'ersic \citep{graham2003coresersicmodel,trujillo2004coresersicmodel} and S\'ersic 
+spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
+whereas S\'ersic spheroids have no central deficit of stars. 
+While core-S\'ersic spheroids are also ``core galaxies'', as given by the Nuker definition \citep{lauer2007lumell},
+it should be noted that $\sim$ $20\%$ of ``core galaxies'' are not core-S\'ersic spheroids 
+(\citealt{dullograham2014cores}, their Appendix A.2), i.e. do not have depleted cores.
+The change in slope of the $L_{\rm sph} - \sigma$ relation corresponds to the division between 
+core-S\'ersic and S\'ersic spheroids (e.g. \citealt{grahamguzman2003}).},
+and attributed the change in slope (from log-quadratic to log-linear) to their different formation mechanisms. 
+In this scenario, core-S\'ersic spheroids are built in additive dry merger events, 
+where the black hole and the bulge grow in lock steps ($M_{\rm BH} \propto L_{\rm sph}^1$), 
+whereas S\'ersic spheroids originate from gas-rich processes, 
+in which the mass of the black hole increases more rapidly than the mass of its host spheroid ($M_{\rm BH} \propto L_{\rm sph}^{2.5}$). 
+\cite{grahamscott2013} and \cite{scott2013} presented double power-law linear regressions 
+for the S\'ersic/core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
+(spheroid stellar mass) diagrams, respectively.
+To obtain their dust-corrected \emph{bulge} magnitudes, they did not perform bulge/disc decompositions, 
+but instead they converted $B-$band and $K_S-$band observed, total \emph{galaxy} magnitudes 
+using a mean statistical correction based on each object's morphological type and disc 
+inclination\footnote{While this resulted in individual bulge magnitudes not being exactly correct, 
+their large sample size allowed them to obtain a reasonably ensemble average correction.}. 
+It should be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
+and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies.
+\\
 
-lasker
+range mbh not to miss the bend
 

### 2015-03-20 papers/MbhMsph/~mm.tex
fiday

--- 2015-03-18 papers/MbhMsph/mm.tex
@@
 \citep{laor1998,wandel1999,laor2001,ryan2007}.
+Recently, \cite{lasker2014data,lasker2014anal} derived $2.2~\rm \mu m$ bulge luminosities for 35 galaxies 
+(among which only 4 were classified as spiral galaxies), 
+and reported a slope of $0.75 \pm 0.10$ for their $M_{\rm BH} - L_{\rm sph}$ relation. 
+They also claimed that the black hole mass correlates equally well with the total galaxy luminosity 
+as it does with the bulge luminosity. \\
+The $M_{\rm BH} - L_{\rm sph}$ relation can be predicted from other two correlations involving the bulge velocity dispersion, $\sigma$.
+The first of these two is the $M_{\rm BH} - \sigma$ relation \citep{ferraresemerritt2000,gebhardt2000},
+which can be described by a single power-law $M_{\rm BH} \propto \sigma^5$ 
+over the range in velocity dispersion $70-350~\rm km~s^{-1}$ (e.g.~\citealt{graham2011,mcconnell2011,grahamscott2013}).
+The second is the $L_{\rm sph} - \sigma$ relation, 
+which has long been known to be a ``double power-law'', 
+being $L_{\rm sph} \propto \sigma^5$ at the luminous end \citep{schechter1980,malumuthkrishner1981,vonderlinden2007,liu2008}, 
+and $L_{\rm sph} \propto \sigma^2$ at intermediate and faint luminosities 
+\citep{davies1983,held1992,matkovicguzman2005,derijcke2005,balcells2007screl,chilingarian2008,forbes2008,cody2009,tortora2009,kourkchi2012}. 
+The change in slope of the $L_{\rm sph} - \sigma$ relation occurs at $M_B \approx -20.5\rm~mag$, 
+corresponding to $\sigma \approx 200~\rm km~s^{-1}$. 
+That is, the $M_{\rm BH} - L_{\rm sph}$ relation should be better described by a ``broken'', rather than single, power-law, 
+having $M_{\rm BH} \propto L_{\rm sph}^{2.5}$ at the low-luminosity end, 
+and $M_{\rm BH} \propto L_{\rm sph}^1$ at the high-luminosity end.  
+Due to the scatter in the $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm sph}$) diagram, 
+studies that have not sufficiently probed below $M_{\rm BH} \approx 10^7\rm~M_\odot$ 
+miss the change in slope occuring at $M_{\rm BH} \approx 10^{(8 \pm 1)}\rm~M_\odot$, 
+and erroneously recover a single log-linear relation. \\
+When \cite{graham2012bent} pointed out this overlooked inconsistency, 
+he identified two different populations of galaxies, 
+namely the core-S\'ersic \citep{graham2003coresersicmodel,trujillo2004coresersicmodel} and S\'ersic 
+spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
+whereas S\'ersic spheroids have no central deficit of stars. 
+While core-S\'ersic spheroids are also ``core galaxies'', as given by the Nuker definition \citep{lauer2007lumell},
+it should be noted that $\sim$ $20\%$ of ``core galaxies'' are not core-S\'ersic spheroids 
+(\citealt{dullograham2014cores}, their Appendix A.2), i.e. do not have depleted cores.
+The change in slope of the $L_{\rm sph} - \sigma$ relation corresponds to the division between 
+core-S\'ersic and S\'ersic spheroids (e.g. \citealt{grahamguzman2003}).},
+and attributed the change in slope (from log-quadratic to log-linear) to their different formation mechanisms. 
+In this scenario, core-S\'ersic spheroids are built in additive dry merger events, 
+where the black hole and the bulge grow in lock steps ($M_{\rm BH} \propto L_{\rm sph}^1$), 
+whereas S\'ersic spheroids originate from gas-rich processes, 
+in which the mass of the black hole increases more rapidly than the mass of its host spheroid ($M_{\rm BH} \propto L_{\rm sph}^{2.5}$). 
+\cite{grahamscott2013} and \cite{scott2013} presented double power-law linear regressions 
+for the S\'ersic/core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
+(spheroid stellar mass) diagrams, respectively.
+To obtain their dust-corrected \emph{bulge} magnitudes, they did not perform bulge/disc decompositions, 
+but instead they converted $B-$band and $K_S-$band observed, total \emph{galaxy} magnitudes 
+using a mean statistical correction based on each object's morphological type and disc 
+inclination\footnote{While this resulted in individual bulge magnitudes not being exactly correct, 
+their large sample size allowed them to obtain a reasonably ensemble average correction.}. 
+It should be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
+and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies. \\
+gs15 add agns
 
-lasker
+range mbh not to miss the bend
 

### 2015-03-23 papers/MbhMsph/mm.tex
mon

@@
 However, the consensus about a linear $M_{\rm BH} - M_{\rm sph}$ correlation was not unanimous. 
-Some studies reported a slope steeper than 1,  
+Some studies reported a slope steeper than one,  
 or noticed that low-mass spheroids were downwards offset from the relation traced by their high-mass counterparts 
@@
 (among which only 4 were classified as spiral galaxies), 
-and reported a slope of $0.75 \pm 0.10$ for their $M_{\rm BH} - L_{\rm sph}$ relation. 
+and reported a slope below unity for their $M_{\rm BH} - M_{\rm sph}$ relation. 
 They also claimed that the black hole mass correlates equally well with the total galaxy luminosity 
@@
 The first of these two is the $M_{\rm BH} - \sigma$ relation \citep{ferraresemerritt2000,gebhardt2000},
-which can be described by a single power-law $M_{\rm BH} \propto \sigma^5$ 
+which can be described by a single power-law ($M_{\rm BH} \propto \sigma^5$) 
 over the range in velocity dispersion $70-350~\rm km~s^{-1}$ (e.g.~\citealt{graham2011,mcconnell2011,grahamscott2013}).
@@
 corresponding to $\sigma \approx 200~\rm km~s^{-1}$. 
-That is, the $M_{\rm BH} - L_{\rm sph}$ relation should be better described by a ``broken'', rather than single, power-law, 
+That is, the $M_{\rm BH} - L_{\rm sph}$ relation should be better described by a ``broken'', rather than a single, power-law, 
 having $M_{\rm BH} \propto L_{\rm sph}^{2.5}$ at the low-luminosity end, 
@@
 studies that have not sufficiently probed below $M_{\rm BH} \approx 10^7\rm~M_\odot$ 
-miss the change in slope occuring at $M_{\rm BH} \approx 10^{(8 \pm 1)}\rm~M_\odot$, 
+can easily miss the change in slope occuring at $M_{\rm BH} \approx 10^{(8 \pm 1)}\rm~M_\odot$, 
 and erroneously recover a single log-linear relation. \\
@@
 While core-S\'ersic spheroids are also ``core galaxies'', as given by the Nuker definition \citep{lauer2007lumell},
-it should be noted that $\sim$ $20\%$ of ``core galaxies'' are not core-S\'ersic spheroids 
+it should be noted that $\sim$20\% of ``core galaxies'' are not core-S\'ersic spheroids 
 (\citealt{dullograham2014cores}, their Appendix A.2), i.e. do not have depleted cores.
@@
 In this scenario, core-S\'ersic spheroids are built in additive dry merger events, 
-where the black hole and the bulge grow in lock steps ($M_{\rm BH} \propto L_{\rm sph}^1$), 
+where the black hole and the bulge grow at the same pace, increasing their mass in lock steps ($M_{\rm BH} \propto L_{\rm sph}^1$), 
 whereas S\'ersic spheroids originate from gas-rich processes, 
@@
 \cite{grahamscott2013} and \cite{scott2013} presented double power-law linear regressions 
-for the S\'ersic/core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
-(spheroid stellar mass) diagrams, respectively.
+for S\'ersic/core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
+(spheroid stellar mass) diagrams, respectively, probing down to $M_{\rm BH} \approx 10^6\rm~M_\odot$. 
 To obtain their dust-corrected \emph{bulge} magnitudes, they did not perform bulge/disc decompositions, 
@@
 It should be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
-and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies.
-\\
-
-range mbh not to miss the bend
+and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies (lenticulars and spirals). \\
+Several recent papers \citep{jiang2011a,jiang2013,mathur2012,reines2013} claimed an offset at the low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ diagram,
+such that the black hole mass is lower than expected from the near-linear correlation traced by the high-mass, early-type spheroids. 
+However, \cite{grahamscott2015} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
+are not randomly offset from the high-mass, near-linear correlation, 
+but lie on the two times steeper relation traced by the S\'ersic spheroids. \\
+here: 66 galaxies, largest dataset to date
+status-of-the-art decomp.
+3.6 um best tracer of stellar mass
+9 systems w $M_{\rm BH} \lesssim 10^7\rm~M_\odot$
+17 spirals
 
@@
 \label{sec:data}
+
 \begin{figure}[h]

### 2015-03-24 papers/MbhMsph/mm.tex
tue

@@
 but lie on the two times steeper relation traced by the S\'ersic spheroids. \\
-here: 66 galaxies, largest dataset to date
-status-of-the-art decomp.
-3.6 um best tracer of stellar mass
-9 systems w $M_{\rm BH} \lesssim 10^7\rm~M_\odot$
-17 spirals
+Here we investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
+using state-of-the-art galaxy decompositions (Savorgnan \& Graham \emph{in preparation}, hereafter \emph{Paper I}) 
+for the largest sample of galaxies with directly measured black hole masses.
+Our decompositions were obtained from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
+which is an excellent proxy for the stellar mass, superior to the $K-$band (\citealt{sheth2010} and references therein).
+Nine of our galaxies have $M_{\rm BH} \lesssim 10^7\rm~M_\odot$, 
+which allows us to accurately constrain the slope of the correlation at the low-mass end.
+In addition to this, our galaxy sample includes 17 spiral galaxies, 
+representing a notable improvement over the past studies dominated by early-type systems.
 
@@
 \label{sec:data}
+Our galaxy sample consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
+at the time we started this project, 
+and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
+Our state-of-the-art galaxy decompositions take into account 
+bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
+We have additionally used kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} 
+to confirm the presence of rotationally supported components in most early-type galaxies, 
+and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
+Details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
+together with the individual 66 galaxy decompositions, will be presented in \emph{Paper I}.
 

### 2015-03-25 papers/MbhMsph/mm.tex
wed

@@
 and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
-Our state-of-the-art galaxy decompositions take into account 
+Bulge luminosities were derived from our state-of-the-art galaxy decompositions, which take into account 
 bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
-We have additionally used kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} 
+Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
 to confirm the presence of rotationally supported components in most early-type galaxies, 
 and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
-Details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
-together with the individual 66 galaxy decompositions, will be presented in \emph{Paper I}.
+\emph{Paper I} will present the dataset used here to investigate the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
+give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
+and illustrate the individual 66 galaxy decompositions.
 
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
+%\caption{}
+%\label{fig:}
+%\end{center}
+%\end{figure}
+
+\section{Analysis}
+\label{sec:anal}
 \begin{figure}[h]
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
 \caption{}

### 2015-03-27 papers/MbhMsph/mm.tex
fri

@@
 Our galaxy sample consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
-at the time we started this project, 
+\citep{grahamscott2013,rusli2013bhmassesDM} at the time we started this project, 
 and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
@@
 give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
-and illustrate the individual 66 galaxy decompositions.
+discuss how we estimated the uncertainties on the bulge parameters, 
+and illustrate the individual 66 galaxy decompositions. \\
+Bulge luminosities\footnote{Absolute luminosities were calculated assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$ \citep{sani2011}.} 
+were converted into stellar masses using the colour-$\Gamma_{3.6}$ relation published by 
+\citeauthor{meidt2014} (\citeyear{meidt2014}, their equation 4), 
+which allows one to estimate the $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6}$, of a galaxy 
+from its $[3.6] - [4.5]$ colour. 
+Individual $[3.6] - [4.5]$ colours\footnote{These are integrated $[3.6] - [4.5]$ colours, measured in a circular aperture 
+within one galaxy's effective radius.} were taken from 
+\citeauthor{peletier2012} (\citeyear{peletier2012}, column 8 of their Table 1) 
+when available for our galaxies, 
+or were estimated from the bulge stellar velocity dispersion, $\sigma$, 
+using the colour-$\sigma$ relation presented by \citeauthor{peletier2012} (\citeyear{peletier2012}, their Figure 6).
+We point out here that using a single $\Gamma_{3.6} = 0.6$, independent of $[3.6] - [4.5]$ colour, 
+does not significantly affect the results of our analysis.
+
+\input{table_sample.tex}
 
@@
 \includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
+\caption{}
+\label{fig:}
+\end{center}
+\end{figure}
+
+\section{Analysis}
+\label{sec:anal}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
 \caption{}

### 2015-03-27 python_codes/instruments/linear_regression/fitexy.py

@@ -75,7 +75,7 @@ def get_ab(x,sigx,y,sigy,ainit,binit,paramsprecision,N,mode):
 	
 		epsilon = epsilon + paramsprecision
 		iteration = iteration + 1
-		print 'Iteration', iteration, '; chisq =', chisqmin, '; N-2 =', (N-2)
+		#print 'Iteration', iteration, '; chisq =', chisqmin, '; N-2 =', (N-2)
 	       #print 'Range for a:', ainit-paramsprecision*6,ainit+paramsprecision*6
 	       #print 'Range for b:', binit-paramsprecision*6,binit+paramsprecision*6
 	       #print 'Epsilon =', epsilon
@@ -152,21 +152,21 @@ def bisect_modfitexy(x,sigx,y,sigy):
 	#print 'epsilon =', epsilon_bisec
 	
 	
-        # plot data and regressions
-        fig, ax = plt.subplots()
-        ax.errorbar(x, y, xerr=sigx, yerr=sigy, ecolor='gray', 
-        	fmt='ko', markersize=12, elinewidth=1.2, capthick=1.2, barsabove=False) 
-        #xxx = np.arange(1.33*min(x)-0.33*max(x),1.33*max(x)-0.33*min(x),(max(x)-min(x))/10.)
-        xxx = np.arange(min(x),max(x),(max(x)-min(x))/10.)
-        y_1 = afit_1 + bfit_1*xxx
-        y_2 = afit_2 + bfit_2*xxx
-        y_test = afit_1 - xxx
-        y_bisec = a_bisec + b_bisec*xxx
-        ax.plot(xxx, y_1, ls='--', color='gray', linewidth=2.)
-        ax.plot(xxx, y_2, ls='--', color='gray', linewidth=2.)
-        #ax.plot(xxx, y_bisec, ls='-', color='black', linewidth=2.)
-        plt.show()
-        #print 'test', [afit_1, afit_2, a_bisec], [bfit_1, bfit_2, b_bisec]
+       ## plot data and regressions
+       #fig, ax = plt.subplots()
+       #ax.errorbar(x, y, xerr=sigx, yerr=sigy, ecolor='gray', 
+       #	fmt='ko', markersize=12, elinewidth=1.2, capthick=1.2, barsabove=False) 
[…]

### 2015-04-01 papers/MbhMsph/mm.tex
wed

@@
 \label{sec:data}
-Our galaxy sample consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
+Our galaxy sample (see Table \ref{tab:sample}) 
+consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
 \citep{grahamscott2013,rusli2013bhmassesDM} at the time we started this project, 
 and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
-Bulge luminosities were derived from our state-of-the-art galaxy decompositions, which take into account 
+Bulge magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 
 bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
@@
 We point out here that using a single $\Gamma_{3.6} = 0.6$, independent of $[3.6] - [4.5]$ colour, 
-does not significantly affect the results of our analysis.
+does not significantly affect the results of our analysis. \\
+The S\'ersic/core-S\'ersic classification presented in this work 
+comes from the compilation of \citet{savorgnangraham2014},
+who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
+When no high-resolution image analysis was available from the literature, 
+they inferred the presence of a partially depleted core based on the stellar velocity dispersion:
+a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
+or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. \\
+For each galaxy, the total luminosity (or galaxy luminosity) is the sum of the luminosities of all its sub-components. 
+Due to the complexity of their modelling, 
+four galaxies (see Table \ref{tab:sample}, column 7) had their galaxy luminosities 
+underestimated\footnote{These four cases will be discussed in \emph{Paper I}.}, 
+which are given here as lower limits.
 
@@
 \label{sec:anal}
+
 \begin{figure}[h]
@@
 \includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
-\caption{}
+\caption{Black hole mass against $3.6\rm~\mu m$ spheroid absolute magnitude. 
+Symbols are coded according to the galaxy morphological type: red circle = elliptical, red star = elliptical/lenticular, 
+red upward triangle = lenticular, blue downward triangle = lenticular/spiral, blue square = spiral, black diamond = merger. 
+Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
+The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
+with the red shaded area denoting its $1\sigma$ uncertainty. 
+The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
+with the blue shaded area denoting its $1\sigma$ uncertainty. 
+The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for core-S\'ersic and S\'ersic spheroids, respectively.}
+\label{fig:mbhmagsph}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
+\caption{Black hole mass against $3.6\rm~\mu m$ galaxy absolute magnitude. 
+Symbols are coded as in Figure \ref{fig:mbhmagsph}.
+Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
+}
 \label{fig:}
@@
 
-\section{Analysis}
-\label{sec:anal}
 \begin{figure}[h]
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
-\caption{}
-\label{fig:}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_agn.pdf}
+\caption{Black hole mass against spheroid stellar mass. 
+Symbols are coded as in Figure \ref{fig:mbhmagsph}, 
+with the addition of the blue dots representing {\bf the AGN sample Jiang}, 
+and the blue crossed circles denoting {\bf the other AGNs}.
+The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
+with the red shaded area denoting its $1\sigma$ uncertainty. 
+The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
+with the blue shaded area denoting its $1\sigma$ uncertainty. }
+\label{fig:mbhmasssph}
 \end{center}
@@
 
-\section{Analysis}
-\label{sec:anal}
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_agn.pdf}
-\caption{}
-\label{fig:}
-\end{center}
-\end{figure}
+\begin{table*}
+\centering
+\caption{Linear regression analysis.}
+\begin{tabular}{llccccc}
+\hline
+\hline
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+\hline 
+\\
+ & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
+Core-S\'ersic (22) & BCES OLS$(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\ 
+                   & BCES OLS$(X|Y)$   & $9.1  \pm 0.1$  & $-0.6  \pm 0.1$  & $-25.73$ & $-$    & $0.61$ \\
+                   & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
+                   & FITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37$ & $0.42$ \\
+                   & FITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.85$ & $0.67$ \\
+                   & FITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
+
+S\'ersic (44) & BCES OLS$(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
+              & BCES OLS$(X|Y)$   & $7.7  \pm 0.1$  & $-0.9  \pm 0.2 $ & $-22.92$ & $-$    & $0.93$ \\
+              & BCES Bisector     & $7.7  \pm 0.1$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
+              & FITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54$ & $0.61$ \\
+              & FITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.89$ & $0.93$ \\
+              & FITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$	& $0.71$ \\
+
+%Ellipticals (E) (30)   & BCES OLS$(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
+% 		       & BCES OLS$(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
+% 		       & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
+% 		       & FITEXY OLS$(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
+% 		       & FITEXY OLS$(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
+% 		       & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
+%
+%Lenticulars (S0) (13)  & BCES OLS$(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
+% 		       & BCES OLS$(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
+% 		       & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
+% 		       & FITEXY OLS$(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
+% 		       & FITEXY OLS$(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
+% 		       & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
+%
+Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
+ 		       & BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
+ 		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.40 \pm 0.04$ & $-24.47$ & $-$    & $0.49$ \\
+ 		       & FITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40$ & $0.46$ \\
+ 		       & FITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $1.00$ & $0.57$\\
+ 		       & FITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
+
+Late-type (S) (17) & BCES OLS$(Y|X)$   & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
+ 		   & BCES OLS$(X|Y)$   & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
+ 		   & BCES Bisector     & $7.2 \pm 0.2$ & $-1.1 \pm 0.3$ & $-22.33$ & $-$    & $0.88$ \\
+ 		   & FITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
+ 		   & FITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
+ 		   & FITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
+\hline 
+\\
+ & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
+Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.06$ & $-0.43 \pm 0.05$ & $$ & $-$ & $0.4487$ \\
+ 		       & BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.63 \pm 0.05$ & $$ & $-$ & $0.5329$ \\
+ 		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $$ & $-$ & $0.4713$ \\
+ 		       & FITEXY OLS$(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
+ 		       & FITEXY OLS$(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
+ 		       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
+
+\hline 
+\hline
+\end{tabular}
+\label{tab:lreg} 
+\end{table*}
 
@@
 \label{sec:res}
+
+compare scatter mbh-msph and mbh-mgal for early types
+
+if 2 overmassive bhs removed, what happens?
 

### 2015-04-01 papers/MbhMsph/~mm.tex
wed

@@
 It should be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
-and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies. \\
-gs15 add agns
-
-range mbh not to miss the bend
+and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies (lenticulars and spirals). \\
+Several recent papers \citep{jiang2011a,jiang2013,mathur2012,reines2013} claimed an offset at the low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ diagram,
+such that the black hole mass is lower than expected from the near-linear correlation traced by the high-mass, early-type spheroids. 
+However, \cite{grahamscott2015} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
+are not randomly offset from the high-mass, near-linear correlation, 
+but lie on the two times steeper relation traced by the S\'ersic spheroids. \\
+Here we investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
+using state-of-the-art galaxy decompositions (Savorgnan \& Graham \emph{in preparation}, hereafter \emph{Paper I}) 
+for the largest sample of galaxies with directly measured black hole masses.
+Our decompositions were obtained from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
+which is an excellent proxy for the stellar mass, superior to the $K-$band (\citealt{sheth2010} and references therein).
+Nine of our galaxies have $M_{\rm BH} \lesssim 10^7\rm~M_\odot$, 
+which allows us to accurately constrain the slope of the correlation at the low-mass end.
+In addition to this, our galaxy sample includes 17 spiral galaxies, 
+representing a notable improvement over the past studies dominated by early-type systems.
 
@@
 \label{sec:data}
+Our galaxy sample (see Table \ref{tab:sample}) 
+consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
+\citep{grahamscott2013,rusli2013bhmassesDM} at the time we started this project, 
+and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
+Bulge magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 
+bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
+Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
+to confirm the presence of rotationally supported components in most early-type galaxies, 
+and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
+\emph{Paper I} will present the dataset used here to investigate the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
+give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
+discuss how we estimated the uncertainties on the bulge parameters, 
+and illustrate the individual 66 galaxy decompositions. \\
+Bulge luminosities\footnote{Absolute luminosities were calculated assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$ \citep{sani2011}.} 
+were converted into stellar masses using the colour-$\Gamma_{3.6}$ relation published by 
+\citeauthor{meidt2014} (\citeyear{meidt2014}, their equation 4), 
+which allows one to estimate the $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6}$, of a galaxy 
+from its $[3.6] - [4.5]$ colour. 
+Individual $[3.6] - [4.5]$ colours\footnote{These are integrated $[3.6] - [4.5]$ colours, measured in a circular aperture 
+within one galaxy's effective radius.} were taken from 
+\citeauthor{peletier2012} (\citeyear{peletier2012}, column 8 of their Table 1) 
+when available for our galaxies, 
+or were estimated from the bulge stellar velocity dispersion, $\sigma$, 
+using the colour-$\sigma$ relation presented by \citeauthor{peletier2012} (\citeyear{peletier2012}, their Figure 6).
+We point out here that using a single $\Gamma_{3.6} = 0.6$, independent of $[3.6] - [4.5]$ colour, 
+does not significantly affect the results of our analysis. \\
+The S\'ersic/core-S\'ersic classification presented in this work 
+comes from the compilation of \citet{savorgnangraham2014},
+who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
+When no high-resolution image analysis was available from the literature, 
+they inferred the presence of a partially depleted core based on the stellar velocity dispersion:
+a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
+or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. \\
+For each galaxy, the total luminosity (or galaxy luminosity) is the sum of the luminosities of all its sub-components. 
+Due to the complexity of their modelling, 
+four galaxies (see Table \ref{tab:sample}, column 7) had their galaxy luminosities 
+underestimated\footnote{These four cases will be discussed in \emph{Paper I}.}, 
+which are given here as lower limits.
+
+\input{table_sample.tex}
+
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
+%\caption{}
+%\label{fig:}
+%\end{center}
+%\end{figure}
+
+\section{Analysis}
+\label{sec:anal}
+
 \begin{figure}[h]
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
-\caption{}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
+\caption{Black hole mass against $3.6\rm~\mu m$ spheroid absolute magnitude. 
+Symbols are coded according to the galaxy morphological type: red circle = elliptical, red star = elliptical/lenticular, 
+red upward triangle = lenticular, blue downward triangle = lenticular/spiral, blue square = spiral, black diamond = merger. 
+Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
+The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
+with the red shaded area denoting its $1\sigma$ uncertainty. 
+The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
+with the blue shaded area denoting its $1\sigma$ uncertainty. 
+The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for core-S\'ersic and S\'ersic spheroids, respectively.}
+\label{fig:mbhmagsph}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
+\caption{Black hole mass against $3.6\rm~\mu m$ galaxy absolute magnitude. 
+Symbols are coded as in Figure \ref{fig:mbhmagsph}.
+Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
+}
 \label{fig:}
@@
 
-\section{Analysis}
-\label{sec:anal}
 \begin{figure}[h]
@@
 \includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_agn.pdf}
-\caption{}
-\label{fig:}
+\caption{Black hole mass against spheroid stellar mass. 
+Symbols are coded as in Figure \ref{fig:mbhmagsph}, 
+with the addition of the blue dots representing {\bf the AGN sample Jiang}, 
+and the blue crossed circles denoting {\bf the other AGNs}.
+The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
+with the red shaded area denoting its $1\sigma$ uncertainty. 
+The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
+with the blue shaded area denoting its $1\sigma$ uncertainty. }
+\label{fig:mbhmasssph}
 \end{center}
@@
 
+\begin{table*}
+\centering
+\caption{Linear regression analysis.}
+\begin{tabular}{llccccc}
+\hline
+\hline
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+\hline 
+\\
+ & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
+Core-S\'ersic (22) & BCES OLS$(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\ 
+                   & BCES OLS$(X|Y)$   & $9.1  \pm 0.1$  & $-0.6  \pm 0.1$  & $-25.73$ & $-$    & $0.61$ \\
+                   & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
+                   & FITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37$ & $0.42$ \\
+                   & FITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.85$ & $0.67$ \\
+                   & FITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
+
+S\'ersic (44) & BCES OLS$(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
+              & BCES OLS$(X|Y)$   & $7.7  \pm 0.1$  & $-0.9  \pm 0.2 $ & $-22.92$ & $-$    & $0.93$ \\
+              & BCES Bisector     & $7.7  \pm 0.1$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
+              & FITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54$ & $0.61$ \\
+              & FITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.89$ & $0.93$ \\
+              & FITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$	& $0.71$ \\
+
+%Ellipticals (E) (30)   & BCES OLS$(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
+% 		       & BCES OLS$(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
+% 		       & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
+% 		       & FITEXY OLS$(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
+% 		       & FITEXY OLS$(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
+% 		       & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
+%
+%Lenticulars (S0) (13)  & BCES OLS$(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
+% 		       & BCES OLS$(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
+% 		       & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
+% 		       & FITEXY OLS$(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
+% 		       & FITEXY OLS$(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
+% 		       & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
+%
+Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
+ 		       & BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
+ 		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.40 \pm 0.04$ & $-24.47$ & $-$    & $0.49$ \\
+ 		       & FITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40$ & $0.46$ \\
+ 		       & FITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $1.00$ & $0.57$\\
+ 		       & FITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
+
+Late-type (S) (17) & BCES OLS$(Y|X)$   & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
+ 		   & BCES OLS$(X|Y)$   & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
+ 		   & BCES Bisector     & $7.2 \pm 0.2$ & $-1.1 \pm 0.3$ & $-22.33$ & $-$    & $0.88$ \\
+ 		   & FITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
+ 		   & FITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
+ 		   & FITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
+\hline 
+\\
+ & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
+Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.06$ & $-0.43 \pm 0.05$ & $-24.88$ & $-$ & $0.4487$ \\
+ 		       & BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.63 \pm 0.05$ & $-24.88$ & $-$ & $0.5329$ \\
+ 		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.4713$ \\
+ 		       & FITEXY OLS$(Y|X)$ & $8.56^{+0.07}_{-0.06}$ & $-0.41^{+0.05}_{-0.05}$ & $-24.88$ & $0.41$ & $0.45$ \\
+ 		       & FITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.0816918911854$ & $-0.661832782075 + 0.0732091327626 - 0.0867908672374$ & $-24.88$ & $0.79$ & $0.55$ \\
+ 		       & FITEXY Bisector   & $$ & $$ & $-24.88$ & $-$    & $$ \\
+
+\hline 
+\hline
+\end{tabular}
+\label{tab:lreg} 
+\end{table*}
+
 \section{Results}
 \label{sec:res}
+
+compare scatter mbh-msph and mbh-mgal for early types
+
+if 2 overmassive bhs removed, what happens?
+
+Mode fit: x|y
+a = 8.55946514403 + 0.0783081088146 - 0.0816918911854
+b = -0.661832782075 + 0.0732091327626 - 0.0867908672374
+epsilon = 0.790044606471
+absolute scatter Delta = 0.553076813686
+--------------------------
+Bisector FITEXY
+y = a + bx
+a = 8.55946514403 + 0.0741309553398 - 0.071795479436
+b = -0.532398339701 + 0.0602832380947 - 0.0668622936876
+absolute scatter Delta = 0.47212846649
+----------------------------
 

### 2015-04-01 python_codes/paper_figures/MbhMsph/figures.py

@@ -11,6 +11,7 @@ from instruments.linear_regression import fitexy
 from instruments import b_n
 from instruments.linear_regression import colorline
 from instruments.linear_regression import akaike
+from instruments.linear_regression import absolutescatter
 
 from matplotlib import rc
 rc('font',**{'family':'sans-serif','sans-serif':['CenturyGothic']})
@@ -726,6 +727,122 @@ def mbh_vs_mag_tot():
 	scatter_kwargs = {"zorder":100}
 	error_kwargs = {"lw":.5, "zorder":0}
 
+		
+	print 'BCES early'
+	print 'n', len(mag_tot[earlytype==1])
+        A,B,Aerr,Berr,covAB=bces.bces(mag_tot[earlytype==1]-np.average(mag_tot[earlytype==1]),
+		err_mag_tot[earlytype==1],
+        	log_mbh[earlytype==1],0.5*(merr_log_mbh[earlytype==1] + perr_log_mbh[earlytype==1]),mag_tot[earlytype==1]*[0.0])
+        absscat_0 = absolutescatter.get_absscatter(mag_tot[earlytype==1]-np.average(mag_tot[earlytype==1]), log_mbh[earlytype==1], B[0], A[0])
+        absscat_1 = absolutescatter.get_absscatter(mag_tot[earlytype==1]-np.average(mag_tot[earlytype==1]), log_mbh[earlytype==1], B[1], A[1])
+        absscat_2 = absolutescatter.get_absscatter(mag_tot[earlytype==1]-np.average(mag_tot[earlytype==1]), log_mbh[earlytype==1], B[2], A[2])
+        absscat_3 = absolutescatter.get_absscatter(mag_tot[earlytype==1]-np.average(mag_tot[earlytype==1]), log_mbh[earlytype==1], B[3], A[3])
+        print '---------------------------------'
+        print 'y = A*(x-<x>) + B '
+        print '<x> =', np.average(mag_tot[earlytype==1])
+        print
[…]

### 2015-04-02 papers/MbhMsph/mm.tex
c

@@
 
-\title{M-M paper, morphological bias }
+\title{M-M paper, morphological dependence }
 
-\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
+\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1} and A. Marconi and E. Sani and L.K. Hunt}
 \affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
@@
 \begin{abstract}
-abstract 
+We have the best latest M-L and M-M diagrams (66 galaxies = biggest sample ever used, IR imaging = minimally affected by dust and star formation, 
+state-of-the-art multicomponent galaxy decompositions = 
+we fit bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores).
+Previous samples were overwhelmingly dominated by early-type galaxies, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7 M_\odot$,
+thus we can explore the low-mass end of the diagrams.
+We provide a table with spheroid luminosities, spheroid stellar masses and galaxy luminosities. 
+We give updated linear regressions for Sersic/core-Sersic galaxies and for different morphological types (E/S0, Sp). 
+Sersic and core-Sersic galaxies have slopes consistent with each other (contrary to what claimed by GS13). 
+In the M-M diagram, bulges of early type galaxies have a slope of $\sim$1, while bulges of spiral galaxies have a slope of 2-3.
+Linear regressions that we provide are symmetrical (to be compared with theoretical expectations) and non-symmetrical (to be used to predict BH masses).
+Contrary to a previous claim, the bulge luminosity appears to be a better indicator of the BH mass than the galaxy luminosity.
+Bulges with $n<2$, claimed by some to be pseudobulges, are not offset to lower BH masses from the correlation defined by bulges with $n>2$.
+
 \end{abstract}
@@
  & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
+All (66)	       & BCES OLS$(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
+		       & BCES OLS$(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
+		       & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
+		       & FITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49$ & $0.56$ \\
+		       & FITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.07}$ & $-0.61^{+0.04}_{-0.05}$ & $-23.86$ & $0.96$ & $0.67$ \\
+		       & FITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
+
 Core-S\'ersic (22) & BCES OLS$(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\ 
@@
  & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
-Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.06$ & $-0.43 \pm 0.05$ & $$ & $-$ & $0.4487$ \\
- 		       & BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.63 \pm 0.05$ & $$ & $-$ & $0.5329$ \\
- 		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $$ & $-$ & $0.4713$ \\
- 		       & FITEXY OLS$(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
- 		       & FITEXY OLS$(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
- 		       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
+All (62)               & BCES OLS$(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
+ 		       & BCES OLS$(X|Y)$   & $8.3 \pm 0.1$   & $-1.0 \pm 0.1$   & $-24.78$ & $-$ & $0.92$ \\
+ 		       & BCES Bisector     & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
+ 		       & FITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.48^{+0.06}_{-0.07}$ & $-24.78$ & $0.62$ & $0.64$ \\
+ 		       & FITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$    & $-24.78$ & $0.87$ & $0.93$ \\
+ 		       & FITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
+
+Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.06$ & $-0.43 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
+ 		       & BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.63 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
+ 		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
+ 		       & FITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.41^{+0.05}_{-0.05}$ & $-24.88$ & $0.41$ & $0.45$ \\
+ 		       & FITEXY OLS$(X|Y)$ & $8.56^{+0.07}_{-0.09}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.79$ & $0.55$ \\
+ 		       & FITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.53^{+0.05}_{-0.07}$ & $-24.88$ & $-$    & $0.47$ \\
+
+%All (62)		& BCES OLS$(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
+%			& BCES OLS$(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
+%			& BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
+%			& FITEXY OLS$(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
+%			& FITEXY OLS$(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
+%			& FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
 

### 2015-04-02 python_codes/instruments/linear_regression/fitexy.py

@@ -176,8 +176,8 @@ def bisect_modfitexy(x,sigx,y,sigy):
 
 def get_errors_ab(x,sigx,y,sigy,afit,bfit,ainit_err,binit_err,epsilonfit,chisqmin,tolerance,N,mode):
 	
-	a_range = np.arange(afit-15*ainit_err,afit+15*ainit_err+tolerance,tolerance)
-	b_range = np.arange(bfit-15*binit_err,bfit+15*binit_err+tolerance,tolerance)
+	a_range = np.arange(afit-3*ainit_err,afit+3*ainit_err+tolerance,tolerance)
+	b_range = np.arange(bfit-3*binit_err,bfit+3*binit_err+tolerance,tolerance)
 	chisqgrid = np.zeros((len(a_range), len(b_range)))
 		
 	for n1 in range(len(a_range)):

### 2015-04-13 papers/MbhMsph/mm.tex
back

@@
 
-\title{M-M paper, morphological dependence }
+\title{M-M paper, morphological dependence, red sequence }
 
@@
 \begin{abstract}
-We have the best latest M-L and M-M diagrams (66 galaxies = biggest sample ever used, IR imaging = minimally affected by dust and star formation, 
+We have the best latest M-L and M-M diagrams (66 galaxies = biggest sample ever used, IR imaging = 
+minimally affected by dust and star formation, 
 state-of-the-art multicomponent galaxy decompositions = 
 we fit bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores).
-Previous samples were overwhelmingly dominated by early-type galaxies, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7 M_\odot$,
+Previous samples were overwhelmingly dominated by early-type galaxies, our sample includes 17 spiral galaxies, 
+half of which have $M_{\rm BH} < 10^7 M_\odot$,
 thus we can explore the low-mass end of the diagrams.
@@
 In the M-M diagram, bulges of early type galaxies have a slope of $\sim$1, while bulges of spiral galaxies have a slope of 2-3.
-Linear regressions that we provide are symmetrical (to be compared with theoretical expectations) and non-symmetrical (to be used to predict BH masses).
-Contrary to a previous claim, the bulge luminosity appears to be a better indicator of the BH mass than the galaxy luminosity.
+Linear regressions that we provide are symmetrical (to be compared with theoretical expectations) 
+and non-symmetrical (to be used to predict BH masses).
+Contrary to a previous claim, 
+the bulge luminosity appears to be a better indicator of the BH mass than the galaxy luminosity.
+only for early type galaxies one can use the tot luminosity as bh mass indicator {\bf check and expand}
 Bulges with $n<2$, claimed by some to be pseudobulges, are not offset to lower BH masses from the correlation defined by bulges with $n>2$.
@@
 their large sample size allowed them to obtain a reasonably ensemble average correction.}. 
-It should be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
+However, this mean statistical correction was obtained from the results of non-modern bulge/disk decompositions, 
+which did not include extra components. 
+It should also be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
 and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies (lenticulars and spirals). \\
@@
 However, \cite{grahamscott2015} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
-are not randomly offset from the high-mass, near-linear correlation, 
-but lie on the two times steeper relation traced by the S\'ersic spheroids. \\
+are not somehow randomly offset from the high-mass, near-linear correlation, 
+but lie on the two times steeper relation traced by the S\'ersic spheroids. 
+{\bf AL: would you like to add a sentence here, mentioning your forthcoming paper with ewan?} \\
 Here we investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
@@
 for the largest sample of galaxies with directly measured black hole masses.
+Our galaxies are large and nearby, which allows us to perform accurate multicomponent decompositions 
+(instead of simple bulge/disk decompositions) without incurring in significant parameter degeneracies. 
 Our decompositions were obtained from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
@@
 representing a notable improvement over the past studies dominated by early-type systems. 
+In a forthcoming paper, we will explore the relation between black hole mass and bulge dynamical mass, 
+$M_{\rm dyn,sph} \propto R_{\rm e} \sigma^2$, and address the issue of a black hole fundamental plane.
+This paper is structured as follows...
 
@@
 and illustrate the individual 66 galaxy decompositions. \\
-Bulge luminosities\footnote{Absolute luminosities were calculated assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$ \citep{sani2011}.} 
-were converted into stellar masses using the colour-$\Gamma_{3.6}$ relation published by 
+Bulge luminosities\footnote{Absolute luminosities were calculated 
+assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$ \citep{sani2011}.} 
+were first converted into stellar masses using a constant $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6} = 0.6$ \citep{meidt2014}.
+We then explored a more sophisticated way to compute mass-to-light ratios, 
+using the color-$\Gamma_{3.6}$ relation published by 
 \citeauthor{meidt2014} (\citeyear{meidt2014}, their equation 4), 
-which allows one to estimate the $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6}$, of a galaxy 
-from its $[3.6] - [4.5]$ colour. 
-Individual $[3.6] - [4.5]$ colours\footnote{These are integrated $[3.6] - [4.5]$ colours, measured in a circular aperture 
+which allows one to estimate $\Gamma_{3.6}$ of a galaxy from its $[3.6] - [4.5]$ color. 
+Individual $[3.6] - [4.5]$ colors\footnote{These are integrated $[3.6] - [4.5]$ colors, measured in a circular aperture 
 within one galaxy's effective radius.} were taken from 
@@
 or were estimated from the bulge stellar velocity dispersion, $\sigma$, 
-using the colour-$\sigma$ relation presented by \citeauthor{peletier2012} (\citeyear{peletier2012}, their Figure 6).
-We point out here that using a single $\Gamma_{3.6} = 0.6$, independent of $[3.6] - [4.5]$ colour, 
-does not significantly affect the results of our analysis. \\
+using the color-$\sigma$ relation presented by \citeauthor{peletier2012} (\citeyear{peletier2012}, their Figure 6).
+We found that the range in $[3.6] - [4.5]$ color is small ($0.06\rm~mag$), 
+and thus the range in $\Gamma_{3.6}$ is also small ($0.04$).
+After checking that using a single $\Gamma_{3.6} = 0.6$, independent of $[3.6] - [4.5]$ color, 
+does not significantly affect the results of our analysis, 
+we decided to use individual, color-dependent mass-to-light ratios. \\
 The S\'ersic/core-S\'ersic classification presented in this work 
@@
 or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. \\
-For each galaxy, the total luminosity (or galaxy luminosity) is the sum of the luminosities of all its sub-components. 
+For each galaxy, the total luminosity (or galaxy luminosity, $L_{\rm gal}$) is the sum of the luminosities of all its sub-components. 
 Due to the complexity of their modelling, 
@@
 %\end{figure}
-
-\section{Analysis}
-\label{sec:anal}
 
@@
 
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
+\caption{Black hole mass against $3.6\rm~\mu m$ spheroid absolute magnitude. 
+Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
+Bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges, are marked with an empty square. 
+The black solid line shows the BCES bisector linear regression for spheroids with $n_{\rm sph} \geq 2$. 
+The inset displays, for all spheroids, the vertical offset 
+from the correlation defined by spheroids with $n_{\rm sph} \geq 2$ only 
+versus the spheroid S\'ersic index. 
+The vertical dashed line corresponds to $n_{\rm sph} = 2$.
+Bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
+from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
+\label{fig:pseudob}
+\end{center}
+\end{figure}
+
 \begin{table*}
 \centering
-\caption{Linear regression analysis.}
+\caption{Linear regression analysis. {\bf X0 is the average X of the subsample...}}
 \begin{tabular}{llccccc}
@@
 \\
- & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
+{\bf Spheroids} & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
 All (66)	       & BCES OLS$(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
@@
 		       & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
-		       & FITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49$ & $0.56$ \\
-		       & FITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.07}$ & $-0.61^{+0.04}_{-0.05}$ & $-23.86$ & $0.96$ & $0.67$ \\
-		       & FITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
+		       & mFITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49$ & $0.56$ \\
+		       & mFITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.07}$ & $-0.61^{+0.04}_{-0.05}$ & $-23.86$ & $0.96$ & $0.67$ \\
+		       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
+
+$n>2$ (43)	       & BCES OLS$(Y|X)$   & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
+		       & BCES OLS$(X|Y)$   & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
+		       & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
+		       & mFITEXY OLS$(Y|X)$ & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38$ & $0.46$ \\
+		       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.78$ & $0.55$ \\
+		       & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
 
@@
                    & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
-                   & FITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37$ & $0.42$ \\
-                   & FITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.85$ & $0.67$ \\
-                   & FITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
+                   & mFITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37$ & $0.42$ \\
+                   & mFITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.85$ & $0.67$ \\
+                   & mFITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
 
@@
               & BCES Bisector     & $7.7  \pm 0.1$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
-              & FITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54$ & $0.61$ \\
-              & FITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.89$ & $0.93$ \\
-              & FITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$	& $0.71$ \\
+              & mFITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54$ & $0.61$ \\
+              & mFITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.89$ & $0.93$ \\
+              & mFITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$	& $0.71$ \\
 
@@
  		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.40 \pm 0.04$ & $-24.47$ & $-$    & $0.49$ \\
- 		       & FITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40$ & $0.46$ \\
- 		       & FITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $1.00$ & $0.57$\\
- 		       & FITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
+ 		       & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40$ & $0.46$ \\
+ 		       & mFITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $1.00$ & $0.57$\\
+ 		       & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
 
@@
  		   & BCES Bisector     & $7.2 \pm 0.2$ & $-1.1 \pm 0.3$ & $-22.33$ & $-$    & $0.88$ \\
- 		   & FITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
- 		   & FITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
- 		   & FITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
+ 		   & mFITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
+ 		   & mFITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
+ 		   & mFITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
 \hline 
 \\
- & \multicolumn{6}{c}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
+{\bf Total galaxies} & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
 All (62)               & BCES OLS$(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
@@
  		       & BCES Bisector     & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
- 		       & FITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.48^{+0.06}_{-0.07}$ & $-24.78$ & $0.62$ & $0.64$ \\
- 		       & FITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$    & $-24.78$ & $0.87$ & $0.93$ \\
- 		       & FITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
+ 		       & mFITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.48^{+0.06}_{-0.07}$ & $-24.78$ & $0.62$ & $0.64$ \\
+ 		       & mFITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$    & $-24.78$ & $0.87$ & $0.93$ \\
+ 		       & mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
 
@@
  		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
- 		       & FITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.41^{+0.05}_{-0.05}$ & $-24.88$ & $0.41$ & $0.45$ \\
- 		       & FITEXY OLS$(X|Y)$ & $8.56^{+0.07}_{-0.09}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.79$ & $0.55$ \\
- 		       & FITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.53^{+0.05}_{-0.07}$ & $-24.88$ & $-$    & $0.47$ \\
+ 		       & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.41^{+0.05}_{-0.05}$ & $-24.88$ & $0.41$ & $0.45$ \\
+ 		       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.07}_{-0.09}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.79$ & $0.55$ \\
+ 		       & mFITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.53^{+0.05}_{-0.07}$ & $-24.88$ & $-$    & $0.47$ \\
 
@@
 
-\section{Results}
+\section{Analysis and results}
 \label{sec:res}
+We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ diagrams 
+using the BCES code from \cite{akritasbershady1996} 
+and also the FITEXY routine \citep{press1992} 
+modified by \cite{tremaine2002} to account for the intrinsic vertical scatter, $\epsilon$. 
+Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
+can give biased results (wrong slope) when the scatter is comparable to the range of the data},
+we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
+In Table \ref{tab:lreg} we report the BCES and modified FITEXY linear regressions for S\'ersic/core-S\'ersic 
+galaxies and for different morphological types (elliptical/lenticular, spiral).
+
+\subsection{Black hole mass -- spheroid luminosity}
+We show the $M_{\rm BH} - L_{\rm sph}$ diagram in Figure \ref{fig:mbhmagsph}. 
+S\'ersic and core-S\'ersic spheroids have slopes consistent with each other (within their $1\sigma$ uncertainties), 
+in disagreement with the findings of \cite{grahamscott2013}. 
+core galaxies have same slope
+sersic gal have shallower slope
+magnitudes of bulges are brighter for the high luminosity sersic galaxies (embedded disks confused with large scale ones)
+and fainter for the low luminosity ones (more components in galaxies)
+
+ELL and S0s separately have both slopes consistent with 1. 
+they define a single sequence.
+vertical scatter along the early type sequence is constant?
+if 2 overmassive bhs removed, what happens?
+In the M-M diagram, bulges of early type galaxies have a slope of $\sim$1, while bulges of spiral galaxies have a slope of 2-3.
+Linear regressions that we provide are symmetrical (to be compared with theoretical expectations) and non-symmetrical (to be used to predict BH masses).
+Contrary to a previous claim, the bulge luminosity appears to be a better indicator of the BH mass than the galaxy luminosity.
 
 compare scatter mbh-msph and mbh-mgal for early types
+intrinsic scatter of early type gals in m-mbul is slightly more than in m-mgal, but this might just depend 
+on the ability of measuring the bulge luminosity, which is model dependent, the gal lum is not.
+only for early type galaxies one can use the tot luminosity as bh mass indicator
 
-if 2 overmassive bhs removed, what happens?
+Bulges with $n<2$, claimed by some to be pseudobulges, are not offset to lower BH masses from the correlation defined by bulges with $n>2$.
+
+\subsection{Black hole mass -- galaxy luminosity}
 

### 2015-04-15 papers/MbhMsph/mm.tex
fanculo il workshop

@@
 in which the mass of the black hole increases more rapidly than the mass of its host spheroid ($M_{\rm BH} \propto L_{\rm sph}^{2.5}$). 
-\cite{grahamscott2013} and \cite{scott2013} presented double power-law linear regressions 
+\citeauthor{grahamscott2013} (\citeyear{grahamscott2013}, hereafter GS13) and \citeauthor{scott2013} (\citeyear{scott2013}, hereafter S+13) 
+presented double power-law linear regressions 
 for S\'ersic/core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
@@
 consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
-\citep{grahamscott2013,rusli2013bhmassesDM} at the time we started this project, 
+(GS13, \citealt{rusli2013bhmassesDM}) at the time we started this project, 
 and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
@@
 comes from the compilation of \citet{savorgnangraham2014},
-who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
+who identified partially depleted cores according to the same criteria used by GS13.
 When no high-resolution image analysis was available from the literature, 
@@
 
-\input{table_sample.tex}
-
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
-%\caption{}
-%\label{fig:}
-%\end{center}
-%\end{figure}
+%\input{table_sample.tex}
 
@@
 \label{fig:mbhmagsph}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
-\caption{Black hole mass against $3.6\rm~\mu m$ galaxy absolute magnitude. 
-Symbols are coded as in Figure \ref{fig:mbhmagsph}.
-Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
-}
-\label{fig:}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_agn.pdf}
-\caption{Black hole mass against spheroid stellar mass. 
-Symbols are coded as in Figure \ref{fig:mbhmagsph}, 
-with the addition of the blue dots representing {\bf the AGN sample Jiang}, 
-and the blue crossed circles denoting {\bf the other AGNs}.
-The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
-with the red shaded area denoting its $1\sigma$ uncertainty. 
-The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
-with the blue shaded area denoting its $1\sigma$ uncertainty. }
-\label{fig:mbhmasssph}
 \end{center}
@@
 
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
+\caption{Black hole mass against $3.6\rm~\mu m$ galaxy absolute magnitude. 
+Symbols are coded as in Figure \ref{fig:mbhmagsph}.
+Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
+}
+\label{fig:mbhmaggal}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+%\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_agn.pdf}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_galsymb_agn.pdf}
+\caption{Black hole mass against spheroid stellar mass. 
+The galaxies from our sample are shown with large symbols (red = E, orange = E/S0 and S0, blue = S0/Sp and Sp, black = merger).
+The 139 small blue dots represent the low-mass AGN sample from \cite{jiang2011a}. 
+The blue crossed circles denote 35 additional galaxies (see \citealt{grahamscott2015}, their Table 2), 
+some of which might have had their bulge stellar masses overestimated.
+The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
+with the red shaded area denoting its $1\sigma$ uncertainty. 
+The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
+with the blue shaded area denoting its $1\sigma$ uncertainty. }
+\label{fig:mbhmasssph}
+\end{center}
+\end{figure}
+
 \begin{table*}
@@
 \\
-{\bf Spheroids} & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
+ & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid luminosity}} \\
+ & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
 All (66)	       & BCES OLS$(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
@@
 %
-Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
+{\bf Early-type (E+S0)} (45) & BCES OLS$(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
  		      	     & BCES OLS$(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
- 		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.40 \pm 0.04$ & $-24.47$ & $-$    & $0.49$ \\
+ 		      	     & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
  		      	     & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40$ & $0.46$ \\
@@
 
-Late-type (S) (17) & BCES OLS$(Y|X)$   & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
+{\bf Late-type (Sp)} (17) & BCES OLS$(Y|X)$    & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
  		   	  & BCES OLS$(X|Y)$    & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
- 		   & BCES Bisector     & $7.2 \pm 0.2$ & $-1.1 \pm 0.3$ & $-22.33$ & $-$    & $0.88$ \\
+ 		   	  & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{-1.1 \pm 0.3}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
  		   	  & mFITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
@@
 \\
-{\bf Total galaxies} & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
+ & \multicolumn{6}{l}{\emph{Black hole mass -- galaxy luminosity}} \\
+  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
 All (62)               & BCES OLS$(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
@@
 %			& FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
+\hline 
+\\
+ & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid stellar mass}} \\
+  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - X_0)/{\rm M_\odot}]$} \\ [0.5em]
+{\bf Early-type (E+S0)} (45)  & BCES OLS$(Y|X)$    & $8.56 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $-$ & $0.48$ \\
+		      	      & BCES OLS$(X|Y)$    & $8.56 \pm 0.08$ & $1.3 \pm 0.1$ & $10.81$ & $-$ & $0.59$ \\
+		      	      & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.0 \pm 0.1}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
+		      	      & FITEXY OLS$(Y|X)$  & $$ & $$ & $10.81$ & $$ & $$ \\
+		      	      & FITEXY OLS$(X|Y)$  & $$ & $$ & $10.81$ & $$ & $$ \\
+		      	      & FITEXY Bisector    & $$ & $$ & $10.81$ & $-$    & $$ \\
+
+{\bf Late-type (Sp)} (17)    & BCES OLS$(Y|X)$    & $7.2 \pm 0.2$ & $1.9 \pm 1.5$ & $10.05$ & $-$ & $0.74$ \\
+		     	     & BCES OLS$(X|Y)$    & $7.2 \pm 0.4$ & $5.9 \pm 3.4$ & $10.05$ & $-$ & $1.70$ \\
+		     	     & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{3.0 \pm 1.3}$ & $\boldsymbol{10.05}$ & $-$ & $\boldsymbol{0.94}$ \\
+		     	     & FITEXY OLS$(Y|X)$  & $$ & $$ & $10.05$ & $$ & $$ \\
+		     	     & FITEXY OLS$(X|Y)$  & $$ & $$ & $10.05$ & $$ & $$ \\
+		     	     & FITEXY Bisector    & $$ & $$ & $10.05$ & $-$    & $$ \\
 
@@
 
-\section{Analysis and results}
-\label{sec:res}
-We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ diagrams 
+\section{Analysis}
+\label{sec:anal}
+We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$, $M_{\rm BH} - M_{\rm *,sph}$ and $M_{\rm BH} - L_{\rm gal}$ diagrams 
 using the BCES code from \cite{akritasbershady1996} 
@@
 we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
-In Table \ref{tab:lreg} we report the BCES and modified FITEXY linear regressions for S\'ersic/core-S\'ersic 
-galaxies and for different morphological types (elliptical/lenticular, spiral).
+In Table \ref{tab:lreg} we report the BCES and modified FITEXY linear regressions, both symmetrical and non-symmetrical, 
+for S\'ersic/core-S\'ersic galaxies and for different galaxy morphological types (elliptical/lenticular, spiral).
+Symmetrical regressions are meant to be compared with theoretical expectations, 
+whereas non-symmetrical Ordinary Least Squares $(Y|X)$ regressions -- 
+since they minimize the scatter in the vertical direction -- 
+can be used to predict black hole masses.
+
+\section{Results and discussion}
+\label{sec:res}
 
 \subsection{Black hole mass -- spheroid luminosity}
-We show the $M_{\rm BH} - L_{\rm sph}$ diagram in Figure \ref{fig:mbhmagsph}. 
+We show the $M_{\rm BH} - L_{\rm sph}$ diagram in Figure \ref{fig:mbhmagsph}. \\
 S\'ersic and core-S\'ersic spheroids have slopes consistent with each other (within their $1\sigma$ uncertainties), 
-in disagreement with the findings of \cite{grahamscott2013}. 
-core galaxies have same slope
-sersic gal have shallower slope
-magnitudes of bulges are brighter for the high luminosity sersic galaxies (embedded disks confused with large scale ones)
-and fainter for the low luminosity ones (more components in galaxies)
+in disagreement with the findings of GS13. 
+The slope that we obtained for core-S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.2 \pm 0.2}$) 
+is consistent with the slope reported by GS13 in the $K_s$-band ($M_{\rm BH} \propto L_{\rm sph}^{1.1 \pm 0.2}$). 
+Instead, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.5 \pm 0.2}$) 
+is significantly shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.7 \pm 0.5}$). 
+Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{which galaxies?} from the classification used here, 
+the main cause of such inconsistency is that the bulge-to-total ratios obtained from our galaxy decompositions 
+are different from those assumed by GS13 to convert galaxy luminosities into bulge luminosities.
+Our bulge-to-total ratios for low-luminosity S\'ersic spheroids ($MAG_{\rm sph} \gtrsim -22 \rm~mag$) 
+are smaller than those used by GS13. 
+The host galaxies of such bulges are late-type, spiral galaxies, 
+which typically present a complex morphology (bars, double bars, embedded disks, nuclear components, etc).
+Our sophisticated galaxy models account for the extra components, 
+while the bulge-to-total ratios of GS13 were derived from simple bulge/disk decompositions 
+which overestimated the bulge luminosity.
+This results in our bulge magnitudes being on average $\sim$$1\rm~mag$ fainter.
+On the other side, our bulge-to-total ratios for high-luminosity S\'ersic spheroids ($MAG_{\rm sph} \lesssim -24 \rm~mag$) 
+are on average larger than those adopted by GS13.
+In this case, the host systems are early-type elliptical/lenticular galaxies that feature intermediate-scale disks\footnote{explain}.
+Past bulge/disk decompositions failed to correctly identify the extent of such disks and treated them as large-scale disks, 
+thus underestimating the bulge luminosity.
+Our bulge magnitudes for such spheroids are on average $\sim$$1\rm~mag$ brighter. \\
+We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 
+which is expected for consistency with other scaling relations 
+(a single power-law $M_{\rm BH} - \sigma$ correlation and a double power-law $L_{\rm sph} - \sigma$ correlation) -- 
+cannot be attributed to the division between the two populations of S\'ersic and core-S\'ersic spheroids.
+We now test a new hypothesis, that is to say the change in slope is to be ascribed to the different formation mechanisms of early- and late-type galaxies. 
+If this hypothesis is correct, 
+the spheroids of early-type (elliptical and lenticular) galaxies will follow $M_{\rm BH} \propto L_{\rm sph}^{\sim 1}$, 
+whereas the spheroids of late-type (spiral) galaxies will have $M_{\rm BH} \propto L_{\rm sph}^{\sim 2.5}$.
+First, we checked that the slopes of the bulges of elliptical and lenticular galaxies, separately, are consistent with each other, 
+and thus, together, they define a single \emph{red sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
+We then fit the bulges of early- and late-type galaxies with two separate log-linear regressions, 
+and obtained $M_{\rm BH} \propto L_{\rm sph}^{1 \pm 0.1}$ and $M_{\rm BH} \propto L_{\rm sph}^{2.75 \pm 0.75}$ respectively, 
+in excellent agreement with the theoretical expectations of our hypothesis.
+{\bf vertical scatter along the early type sequence is constant?
+if 2 overmassive bhs removed, what happens?}
 
-ELL and S0s separately have both slopes consistent with 1. 
-they define a single sequence.
-vertical scatter along the early type sequence is constant?
-if 2 overmassive bhs removed, what happens?
-In the M-M diagram, bulges of early type galaxies have a slope of $\sim$1, while bulges of spiral galaxies have a slope of 2-3.
-Linear regressions that we provide are symmetrical (to be compared with theoretical expectations) and non-symmetrical (to be used to predict BH masses).
+In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
+are taken from our one-dimensional fits of the major-axis surface brightness profiles of galaxies (\emph{Paper I}).}, 
+$n_{\rm sph}$, in the $M_{\rm BH} - L_{\rm sph}$ diagram.
+Our aim is to check whether bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges (e.g.~ cite), 
+are offset to lower black hole masses from the correlation defined by (classical) bulges with $n_{\rm sph}>2$, 
+as reported by \cite{sani2011} {\bf who else?}. 
+To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
+and we compute the vertical offset of all bulges from the regression. 
+In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
+From a visual inspection, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.
+
+\subsection{Black hole mass -- galaxy luminosity}
+Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
+Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
+and thus are not included in the linear regression analysis. 
+\cite{lasker2014anal}
+
 Contrary to a previous claim, the bulge luminosity appears to be a better indicator of the BH mass than the galaxy luminosity.
@@
 
-Bulges with $n<2$, claimed by some to be pseudobulges, are not offset to lower BH masses from the correlation defined by bulges with $n>2$.
+\subsection{Black hole mass -- spheroid stellar mass}
+Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
+where we include our sample of 66 galaxies, 
+plus the 35 + 139 low-mass AGNs taken from the compilation of \cite{grahamscott2015}.
 
-\subsection{Black hole mass -- galaxy luminosity}
+addition of agns
+relations
+agns consistent w spirals, but analysis deferred to other paper
+cubic growth
 
@@
 \acknowledgments
-%{\bf marconi, sani, hunt...}
 %GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Elisabete Lima Da Cunha and Gonzalo Diaz 

### 2015-04-15 python_codes/instruments/markers/markers.py

@@ -1,0 +1,43 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+
+scatter_kwargs = {"zorder":100}
+
+def spiral(ax, color, x0, y0, size):
+	t1 = np.arange(1,4,0.01)
+	t2 = np.arange(1,4,0.01)
+	x1 = size*t1*np.cos(t1)
+	y1 = size*t1*np.sin(t1)
+	x2 = -size*t2*np.cos(t2)
+	y2 = -size*t2*np.sin(t2)
+	
+	t = np.arange(0,2*np.pi,0.01)
+	x = size*1.1*np.cos(t)
+	y = size*1*np.sin(t)
+	
+	ax.plot(10**(x0+x1),10**(y0+y1), color=color, lw=2, **scatter_kwargs)
+	ax.plot(10**(x0+x2),10**(y0+y2), color=color, lw=2, **scatter_kwargs)
+	ax.plot(10**(x0+x),10**(y0+y), color=color, lw=2, **scatter_kwargs)
+	ax.fill_between(10**(x0+x), 10**(y0+0), 10**(y0+y), edgecolor='', facecolor=color, **scatter_kwargs)
+	
+	
+def lenticular(ax, color, x0, y0, size):
+
+	t = np.arange(0,2*np.pi,0.01)
+	x = size*1*np.cos(t)
+	y = size*1.5*np.sin(t)	
+	
+	ax.fill_between(10**(x0+x), 10**(y0+0), 10**(y0+y), edgecolor='', facecolor=color, **scatter_kwargs)
+	ax.plot([10**(x0-2*size),10**(x0+2*size)],[10**(y0),10**(y0)], color=color, lw=3, **scatter_kwargs)
+
+
+def elliptical(ax, color, x0, y0, size):
+
+	t = np.arange(0,2*np.pi,0.01)
+	x = size*1*np.cos(t)
+	y = size*1.5*np.sin(t)	
+	
+	ax.fill_between(10**(x0+x), 10**(y0+0), 10**(y0+y), edgecolor='', facecolor=color, **scatter_kwargs)
+
+

### 2015-04-15 python_codes/paper_figures/MbhMsph/figures.py

@@ -4,6 +4,8 @@ import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib
 import matplotlib.colors as mcolors
+import matplotlib.image as image
+
 from scipy import stats
 from instruments.linear_regression import bces
 from instruments.linear_regression import predband
@@ -12,6 +14,7 @@ from instruments import b_n
 from instruments.linear_regression import colorline
 from instruments.linear_regression import akaike
 from instruments.linear_regression import absolutescatter
+from instruments.markers import markers
 
 from matplotlib import rc
 rc('font',**{'family':'sans-serif','sans-serif':['CenturyGothic']})
@@ -244,6 +247,309 @@ def mbh_vs_mass_sph_agn():
         
         fig, ax = plt.subplots()
 
+        print 'BCES all'
+        print 'n', len(log_mass_sph)
+        A,B,Aerr,Berr,covAB=bces.bces(log_mass_sph-np.average(log_mass_sph),
+        	0.5*(perr_log_mass_sph + merr_log_mass_sph),
+        	log_mbh,0.5*(merr_log_mbh + perr_log_mbh),log_mass_sph*[0.0])
+        absscat_0 = absolutescatter.get_absscatter(log_mass_sph-np.average(log_mass_sph), log_mbh, B[0], A[0])
+        absscat_1 = absolutescatter.get_absscatter(log_mass_sph-np.average(log_mass_sph), log_mbh, B[1], A[1])
+        absscat_2 = absolutescatter.get_absscatter(log_mass_sph-np.average(log_mass_sph), log_mbh, B[2], A[2])
+        absscat_3 = absolutescatter.get_absscatter(log_mass_sph-np.average(log_mass_sph), log_mbh, B[3], A[3])
+        print '---------------------------------'
+        print 'y = A*(x-<x>) + B '
+        print '<x> =', np.average(log_mass_sph)
+        print
[…]

### 2015-04-17 papers/MbhMsph/mm.tex
fanculo

@@
 \begin{abstract}
-We have the best latest M-L and M-M diagrams (66 galaxies = biggest sample ever used, IR imaging = 
-minimally affected by dust and star formation, 
-state-of-the-art multicomponent galaxy decompositions = 
-we fit bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores).
-Previous samples were overwhelmingly dominated by early-type galaxies, our sample includes 17 spiral galaxies, 
-half of which have $M_{\rm BH} < 10^7 M_\odot$,
-thus we can explore the low-mass end of the diagrams.
-We provide a table with spheroid luminosities, spheroid stellar masses and galaxy luminosities. 
-We give updated linear regressions for Sersic/core-Sersic galaxies and for different morphological types (E/S0, Sp). 
-Sersic and core-Sersic galaxies have slopes consistent with each other (contrary to what claimed by GS13). 
-In the M-M diagram, bulges of early type galaxies have a slope of $\sim$1, while bulges of spiral galaxies have a slope of 2-3.
-Linear regressions that we provide are symmetrical (to be compared with theoretical expectations) 
-and non-symmetrical (to be used to predict BH masses).
-Contrary to a previous claim, 
-the bulge luminosity appears to be a better indicator of the BH mass than the galaxy luminosity.
-only for early type galaxies one can use the tot luminosity as bh mass indicator {\bf check and expand}
-Bulges with $n<2$, claimed by some to be pseudobulges, are not offset to lower BH masses from the correlation defined by bulges with $n>2$.
+We present the latest scaling relations between black hole mass, $M_{\rm BH}$, 
+and spheroid luminosity, $L_{\rm sph}$, spheroid stellar mass, $M_{\rm *,sph}$, and galaxy luminosity, $L_{\rm gal}$,
+built upon an unprecedented high-quality data set (provided here in a ready-to-use table).
+Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
+Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
+which is minimally affected by dust and star formation. 
+These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
+that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
+and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
+Previous studies used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
+Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
+and allows us to investigate the poorly studied low-mass end of the correlations.
+We provide updated linear regressions 
+(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
+for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
+The bulges of early-type (E/S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$, 
+as expected from a dry-merging formation scenario,
+and define a tight \emph{red sequence} with intrinsic scatter {\bf ???}.
+On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
+with $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
+indicating that gas-rich processes feed the black hole three times more efficiently than the host bulge. 
+Disproving some previous claims, we also conclude that: 1) S\'ersic and core-S\'ersic galaxies do not define two distinct sequences; 
+2) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
+are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
+3) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$ only for early-type galaxies.
 
@@
 
-%\input{table_sample.tex}
+\input{table_sample.tex}
 
@@
 thus underestimating the bulge luminosity.
-Our bulge magnitudes for such spheroids are on average $\sim$$1\rm~mag$ brighter. \\
+The magnitudes that we obtained for such spheroids are on average $\sim$$1\rm~mag$ brighter. \\
 We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 
@@
 
+{\bf coming now to figure 1: if I look at the blue points it is difficult to believe that they define a linear relation, 
+their magnitude range is too small and it could just be that at low galaxy luminosities the scatter of the MBH-L relation increases. 
+This is what most models predict. Do the galaxies below the correlation have some special property? 
+Could it just be that spiral bulges simple do not follow a tight relation with BH mass?
+
+Giulia, I think you already plan to do this, but can you include the error bars in all places where a relation is presented, so that readers know if there is a relation or not.
+Remember also Ewan's remark about the unsuitability of the Pearson and Spearman correlation coefficients because they do not take into account the error bars on our data - 
+so don't include those simple coefficients.  Actually, it would be worth pointing out to readers that a visual inspection of the plotted data requires 
+the viewer to take into account the error bars when judging-by-eye the strength of a correlation. 
+Maybe then mention in the following sentence that this is why the correlation coefficients are not applicable here. }
+
 In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
-are taken from our one-dimensional fits of the major-axis surface brightness profiles of galaxies (\emph{Paper I}).}, 
+are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).}, 
 $n_{\rm sph}$, in the $M_{\rm BH} - L_{\rm sph}$ diagram.
@@
 From a visual inspection, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.
+
+{\bf As you probably know, and as explained in many of my papers (e.g. http://arxiv.org/abs/1501.02937 ; http://arxiv.org/abs/1108.0997 ; http://arxiv.org/abs/1311.7207 ), 
+pseudobulges are notoriously hard to identify.  It would be a mistake to have a column labelled "pseudobulge".   
+However a galaxy classification column, indicating the presence of a bar, is good to include.  
+While we do not wish to publish the Sersic indices here (that will be kept for a different paper), 
+we could have a column indicating if n is above or below 2 - given that some people mistakingly think that they can use this as a dividing point. 
+Giulia, can you also include a nearby reference to Graham (2013, http://arxiv.org/abs/1108.0997) so that people can read and understand why $n < 2$ 
+does not necessarily equate to a pseudobulge. }
 
@@
 only for early type galaxies one can use the tot luminosity as bh mass indicator
+
+errors on gal mag??????????????? 0.2 constant
 

### 2015-04-17 python_codes/paper_figures/MbhMsph/figures.py

@@ -14,6 +14,7 @@ from instruments import b_n
 from instruments.linear_regression import colorline
 from instruments.linear_regression import akaike
 from instruments.linear_regression import absolutescatter
+from instruments.linear_regression import lnr
 from instruments.markers import markers
 
 from matplotlib import rc
@@ -247,52 +248,52 @@ def mbh_vs_mass_sph_agn():
         
         fig, ax = plt.subplots()
 
-        print 'BCES all'
-        print 'n', len(log_mass_sph)
-        A,B,Aerr,Berr,covAB=bces.bces(log_mass_sph-np.average(log_mass_sph),
-        	0.5*(perr_log_mass_sph + merr_log_mass_sph),
-        	log_mbh,0.5*(merr_log_mbh + perr_log_mbh),log_mass_sph*[0.0])
-        absscat_0 = absolutescatter.get_absscatter(log_mass_sph-np.average(log_mass_sph), log_mbh, B[0], A[0])
-        absscat_1 = absolutescatter.get_absscatter(log_mass_sph-np.average(log_mass_sph), log_mbh, B[1], A[1])
-        absscat_2 = absolutescatter.get_absscatter(log_mass_sph-np.average(log_mass_sph), log_mbh, B[2], A[2])
-        absscat_3 = absolutescatter.get_absscatter(log_mass_sph-np.average(log_mass_sph), log_mbh, B[3], A[3])
-        print '---------------------------------'
-        print 'y = A*(x-<x>) + B '
-        print '<x> =', np.average(log_mass_sph)
-        print
-        print 'OLS(Y|X)    A =', "{0:.4f}".format(A[0]), '+-', "{0:.4f}".format(Aerr[0]), '   B = ', "{0:.4f}".format(B[0]), '+-', "{0:.4f}".format(Berr[0]), 'Delta =', "{0:.4f}".format(absscat_0)
-        print 'OLS(X|Y)    A =', "{0:.4f}".format(A[1]), '+-', "{0:.4f}".format(Aerr[1]), '   B = ', "{0:.4f}".format(B[1]), '+-', "{0:.4f}".format(Berr[1]), 'Delta =', "{0:.4f}".format(absscat_1)
[…]

### 2015-04-19 papers/MbhMsph/mm.tex
monmorn

@@
                        & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
+                       & Kelly OLS$(Y|X)$  & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\
+                       & Kelly OLS$(X|Y)$  & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.6 \pm 0.1$ & $0.67$ \\
+                       & Kelly Bisector    & $$ & $$ & $-23.86$ & $-$    & $$ \\
 
@@
                        & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
+                       & Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.41 \pm 0.06$ & $0.46$ \\
+                       & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.59 \pm 0.08$ & $-24.77$ & $0.5 \pm  0.1$ & $0.56$ \\
+                       & Kelly Bisector    & $$ & $$ & $-24.77$ & $-$    & $$ \\
 
@@
                    & mFITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
+                   & Kelly OLS$(Y|X)$  & $9.0 \pm 0.1$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.41 \pm 0.09$ & $0.42$ \\
+                   & Kelly OLS$(X|Y)$  & $$ & $$ & $-25.73$ & $$ & $$ \\
+                   & Kelly Bisector    & $$ & $$ & $-25.73$ & $-$    & $$ \\
 
@@
               & mFITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$     & $0.71$ \\
+              & Kelly OLS$(Y|X)$  & $7.72 \pm 0.09$ & $-0.41 \pm 0.09$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\
+              & Kelly OLS$(X|Y)$  & $7.7 \pm  0.1$ & $-0.9 \pm  0.2$ & $-22.92$ & $0.8 \pm  0.3$ & $0.98$ \\
+              & Kelly Bisector    & $$ & $$ & $-22.92$ & $-$    & $$ \\
 
@@
                              & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
+                             & Kelly OLS$(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.42 \pm 0.06$ & $ 0.46$ \\
+                             & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.47$ & $0.5 \pm  0.1$ & $0.57$ \\
+                             & Kelly Bisector    & $$ & $$ & $-24.47$ & $-$    & $$ \\
 
@@
                           & mFITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
+                          & Kelly OLS$(Y|X)$  & $7.2 \pm 0.2$ & $-0.5 \pm 0.3$ & $-22.33$ & $0.6 \pm 0.2$ & $0.62$ \\
+                          & Kelly OLS$(X|Y)$  & $$ & $$ & $-22.33$ & $$ & $$ \\
+                          & Kelly Bisector    & $$ & $$ & $-22.33$ & $-$    & $$ \\
+
 \hline 
@@
                        & mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
+                       & Kelly OLS$(Y|X)$  & $8.26 \pm 0.08$ & $-0.48 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.06$ & $0.64$ \\
+                       & Kelly OLS$(X|Y)$  & $8.3 \pm 0.1$ & $-1.0 \pm 0.2$ & $-24.78$ & $0.9 \pm 0.2$ & $0.96$ \\
+                       & Kelly Bisector    & $$ & $$ & $-24.78$ & $-$    & $$ \\
 
@@
                        & mFITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.53^{+0.05}_{-0.07}$ & $-24.88$ & $-$    & $0.47$ \\
+                       & Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.44 \pm 0.06$ & $0.45$ \\
+                       & Kelly OLS$(X|Y)$  & $8.56 \pm 0.09$ & $-0.66 \pm 0.09$ & $-24.88$ & $0.6 \pm 0.1$ & $0.55$ \\
+                       & Kelly Bisector    & $$ & $$ & $-24.88$ & $-$    & $$ \\
 
@@
 %                       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
+%                       & Kelly OLS$(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\
+%                       & Kelly OLS$(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\
+%                       & Kelly Bisector    & $$ & $$ & $$ & $-$    & $$ \\
+
 \hline 
@@
                               & FITEXY Bisector    & $$ & $$ & $10.81$ & $-$    & $$ \\
+                              & Kelly OLS$(Y|X)$  & $8.55 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\
+                              & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $1.3 \pm  0.2$ & $10.81$ & $0.6 \pm  0.1$ & $0.61$ \\
+                              & Kelly Bisector    & $$ & $$ & $10.81$ & $-$    & $$ \\
 
@@
                              & FITEXY Bisector    & $$ & $$ & $10.05$ & $-$    & $$ \\
+                             & Kelly OLS$(Y|X)$  & $7.2 \pm 0.2$ & $0.9 \pm 1.0$ & $10.05$ & $0.7 \pm 0.2$ & $0.65$ \\
+                             & Kelly OLS$(X|Y)$  & $$ & $$ & $10.05$ & $$ & $$ \\
+                             & Kelly Bisector    & $$ & $$ & $10.05$ & $-$    & $$ \\
 

### 2015-04-22 papers/MbhMsph/mm.tex
wed

--- 2015-04-17 papers/MbhMsph/mm.tex
@@
 \usepackage{bm}
+\usepackage{color}
 
@@
 
-\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1} and A. Marconi and E. Sani and L.K. Hunt}
+%\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1} and A. Marconi and E. Sani\altaffilmark{3} and L.K. Hunt}
+%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
+%\email{gsavorgn@astro.swin.edu.au}
+
+\author{G. A. D. Savorgnan and A. W. Graham}
 \affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
 \email{gsavorgn@astro.swin.edu.au}
+\author{A. Marconi}
+\affil{?}
+\author{E. Sani}
+\affil{European Southern Observatory, Alonso de Cordova, Vitacura 3107, Santiago, Chile.}
+\and
+\author{L.K. Hunt}
+\affil{?}
 
@@
 as expected from a dry-merging formation scenario,
-and define a tight \emph{red sequence} with intrinsic scatter {\bf ???}.
+and define a tight \emph{red sequence} with intrinsic scatter $\epsilon = 0.43 \pm 0.06$.
 On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
@@
                        & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
-		       & mFITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49$ & $0.56$ \\
-		       & mFITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.07}$ & $-0.61^{+0.04}_{-0.05}$ & $-23.86$ & $0.96$ & $0.67$ \\
+                       & mFITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
+                       & mFITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.67$ \\
                        & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
+                       & Kelly OLS$(Y|X)$  & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.50 \pm 0.06$ & $0.56$ \\
+                       & Kelly OLS$(X|Y)$  & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.10$ & $0.67$ \\
+                       & Kelly Bisector    & $8.16 \pm 0.08$ & $-0.5 \pm 0.1$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]
 
@@
                        & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
-		       & mFITEXY OLS$(Y|X)$ & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38$ & $0.46$ \\
-		       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.78$ & $0.55$ \\
+                       & mFITEXY OLS$(Y|X)$ & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
+                       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
                        & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
+                       & Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\
+                       & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.48 \pm 0.11$ & $0.55$ \\
+                       & Kelly Bisector    & $8.56 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]
 
@@
                    & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
-                   & mFITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37$ & $0.42$ \\
-                   & mFITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.85$ & $0.67$ \\
+                   & mFITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37^{+0.08}_{-0.06}$ & $0.42$ \\
+                   & mFITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.67$ \\
                    & mFITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
+                   & Kelly OLS$(Y|X)$  & $9.0 \pm 0.1$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.09$ & $0.42$ \\
+                   & \textcolor{red}{Kelly OLS$(X|Y)$}  & $9.0 \pm 1.4$ & $-0.7 \pm 16.1$ & $-25.73$ & $0.7 \pm 19.0$ & $0.64$ \\
+                   & \textcolor{red}{Kelly Bisector}    & $9.0 \pm 1.0$ & $-0.4 \pm 1.1$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]
 
@@
               & BCES Bisector     & $7.7  \pm 0.1$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
-              & mFITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54$ & $0.61$ \\
-              & mFITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.89$ & $0.93$ \\
+              & mFITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54^{+0.09}_{-0.07}$ & $0.61$ \\
+              & mFITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
               & mFITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$     & $0.71$ \\
+              & Kelly OLS$(Y|X)$  & $7.72 \pm 0.09$ & $-0.41 \pm 0.09$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\
+              & Kelly OLS$(X|Y)$  & $7.7 \pm  0.2$ & $-0.9 \pm  0.3$ & $-22.92$ & $0.79 \pm  0.27$ & $0.93$ \\
+              & Kelly Bisector    & $7.7 \pm 0.1$ & $-0.6 \pm 0.2$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
 
@@
                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
- 		      	     & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40$ & $0.46$ \\
- 		      	     & mFITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $1.00$ & $0.57$\\
+                             & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40^{+0.06}_{-0.05}$ & $0.46$ \\
+                             & mFITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $0.49^{+0.08}_{-0.06}$ & $0.57$\\
                              & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
+                             & Kelly OLS$(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.41 \pm 0.06$ & $0.46$ \\
+                             & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.47$ & $0.51 \pm 0.11$ & $0.56$ \\
+                             & Kelly Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.09$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]
 
@@
                           & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{-1.1 \pm 0.3}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
- 		   	  & mFITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
- 		   	  & mFITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
+                          & mFITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.55^{+0.15}_{-0.10}$ & $0.62$ \\
+                          & mFITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.4}$ & $-22.33$ & $1.08^{+0.40}_{-0.24}$ & $1.50$ \\
                           & mFITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
+                          & Kelly OLS$(Y|X)$  & $7.2 \pm 0.2$ & $-0.5 \pm 0.3$ & $-22.33$ & $0.63 \pm 0.16$ & $0.62$ \\
+                          & \textcolor{red}{Kelly OLS$(X|Y)$}  & $7.3 \pm 8919.5$ & $-1.7 \pm 43265.5$ & $-22.33$ & $1.3 \pm 31992.6$ & $1.3$ \\
+                          & \textcolor{red}{Kelly Bisector}    & $7.3 \pm 6307.0$ & $-0.9 \pm 2.9$ & $-22.33$ & $-$    & $0.76$ \\
+
+\hline 
+\hline
+\end{tabular}
+\label{tab:lreg} 
+\end{table*}
+
+\begin{table*}
+\centering
+\caption{Linear regression analysis. {\bf X0 is the average X of the subsample...}}
+\begin{tabular}{llccccc}
+\hline
+\hline
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
 \hline 
@@
   & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
-All (62)               & BCES OLS$(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
+ All (62)		& BCES OLS$(Y|X)$   & $8.26 \pm 0.08$ & $-0.48 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
  			& BCES OLS$(X|Y)$   & $8.3 \pm 0.1$   & $-1.0 \pm 0.1$   & $-24.78$ & $-$ & $0.92$ \\
- 		       & BCES Bisector     & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
- 		       & mFITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.48^{+0.06}_{-0.07}$ & $-24.78$ & $0.62$ & $0.64$ \\
- 		       & mFITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$    & $-24.78$ & $0.87$ & $0.93$ \\
- 		       & mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
+ 			& BCES Bisector     & $8.26 \pm 0.09$ & $-0.71 \pm 0.06$ & $-24.78$ & $-$ & $0.70$ \\
+ 			& mFITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.07}$ & $-0.47^{+0.06}_{-0.06}$ & $-24.78$ & $0.62^{+0.07}_{-0.05}$ & $0.64$ \\
+ 			& mFITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$	& $-24.78$ & $0.91^{+0.10}_{-0.08}$ & $0.93$ \\
+ 			& mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.71^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.70$ \\
+ 			& Kelly OLS$(Y|X)$  & $8.27 \pm 0.08$ & $-0.47 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.06$ & $0.64$ \\
+ 			& Kelly OLS$(X|Y)$  & $8.3 \pm 0.1$ & $-1.0 \pm 0.2$ & $-24.78$ & $0.94 \pm 0.2$ & $0.93$ \\
+ 			& Kelly Bisector    & $8.3 \pm 0.1$ & $-0.7 \pm 0.1$ & $-24.78$ & $-$    & $0.70$ \\ [0.5em]
 
@@
  			& BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
- 		       & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.41^{+0.05}_{-0.05}$ & $-24.88$ & $0.41$ & $0.45$ \\
- 		       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.07}_{-0.09}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.79$ & $0.55$ \\
- 		       & mFITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.53^{+0.05}_{-0.07}$ & $-24.88$ & $-$    & $0.47$ \\
+ 			& mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.41^{+0.05}_{-0.04}$ & $-24.88$ & $0.42^{+0.05}_{-0.05}$ & $0.45$ \\
+ 			& mFITEXY OLS$(X|Y)$ & $8.55^{+0.09}_{-0.07}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.53^{+0.07}_{-0.05}$ & $0.55$ \\
+ 			& mFITEXY Bisector   & $8.55^{+0.08}_{-0.06}$ & $-0.53^{+0.05}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
+ 			& Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $-0.41 \pm 0.05$ & $-24.88$ & $0.44 \pm 0.06$ & $0.45$ \\
+ 			& Kelly OLS$(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.09$ & $-24.88$ & $0.55 \pm 0.11$ & $0.54$ \\
+ 			& Kelly Bisector    & $8.56 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.88$ & $-$    & $0.47$ \\
 
@@
                               & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.0 \pm 0.1}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
-		      	      & FITEXY OLS$(Y|X)$  & $$ & $$ & $10.81$ & $$ & $$ \\
-		      	      & FITEXY OLS$(X|Y)$  & $$ & $$ & $10.81$ & $$ & $$ \\
-		      	      & FITEXY Bisector    & $$ & $$ & $10.81$ & $-$    & $$ \\
+                              & mFITEXY OLS$(Y|X)$  & $8.56^{+0.06}_{-0.07}$ & $0.8^{+0.1}_{-0.1}$ & $10.81$ & $0.42^{+0.06}_{-0.05}$ & $0.48$ \\
+                              & mFITEXY OLS$(X|Y)$  & $8.54^{+0.09}_{-0.08}$ & $1.3^{+0.2}_{-0.1}$ & $10.81$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
+                              & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.0^{+0.1}_{-0.1}$ & $10.81$ & $-$                    & $0.51$ \\
+                              & Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\
+                              & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $1.3 \pm 0.2$ & $10.81$ & $0.54 \pm 0.12$ & $0.59$ \\
+                              & Kelly Bisector    & $8.55 \pm 0.08$ & $1.0 \pm 0.2$ & $10.81$ & $-$    & $0.51$ \\ [0.5em]
 
@@
                              & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{3.0 \pm 1.3}$ & $\boldsymbol{10.05}$ & $-$ & $\boldsymbol{0.94}$ \\
-		     	     & FITEXY OLS$(Y|X)$  & $$ & $$ & $10.05$ & $$ & $$ \\
-		     	     & FITEXY OLS$(X|Y)$  & $$ & $$ & $10.05$ & $$ & $$ \\
-		     	     & FITEXY Bisector    & $$ & $$ & $10.05$ & $-$    & $$ \\
+                             & mFITEXY OLS$(Y|X)$  & $7.2^{+0.1}_{-0.2}$ & $1.2^{+0.7}_{-0.6}$ & $10.05$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
+                             & \textcolor{red}{mFITEXY OLS$(X|Y)$}  & $7.4^{+1.5}_{-0.5}$ & $7.1^{+26.3}_{-3.0}$ & $10.05$ & $1.49^{+0.57}_{-0.35}$ & $2.08$ \\
+                             & \textcolor{red}{mFITEXY Bisector}    & $7.2^{+1.0}_{-0.4}$ & $2.3^{+1.7}_{-1.0}$ & $10.05$ & $-$    & $0.79$ \\
+                             & Kelly OLS$(Y|X)$  & $7.2 \pm 0.2$ & $1.0 \pm 1.0$ & $10.05$ & $0.67 \pm 0.17$ & $0.65$ \\
+                             & \textcolor{red}{Kelly OLS$(X|Y)$}  & $7.3 \pm 25.2$ & $5.2 \pm 740.5$ & $10.05$ & $1.7 \pm 190.7$ & $1.5$ \\
+                             & \textcolor{red}{Kelly Bisector}    & $7.2 \pm 17.8$ & $1.8 \pm 1.8$ & $10.05$ & $-$    & $0.72$ \\
 
@@
 \label{sec:concl}
+ngc0524 outlier, n1332 non outlier
 

### 2015-04-22 python_codes/instruments/linear_regression/fitexy.py

@@ -13,10 +13,11 @@ tolerance = 0.01  # good one
 def modfitexy(x,sigx,y,sigy,mode):
 
 	N = len(x)
-	# compute first guess of slope and intercept with OLS Y|X method ignoring errors
+	# compute first guess of slope and intercept with OLS Y|X method (NON) ignoring errors
 	cov = [0.0]*x
 	# y = A + Bx
-	B,A,Berr,Aerr,covAB=bces.bces(x,sigx*[0.0],y,sigy*[0.0],cov)
+	#B,A,Berr,Aerr,covAB=bces.bces(x,sigx*[0.0],y,sigy*[0.0],cov)
+	B,A,Berr,Aerr,covAB=bces.bces(x,sigx,y,sigy,cov)
 	index = {'y|x' : 0 , 'x|y': 1}
 	
 	ainit = A[index[mode]]
@@ -37,13 +38,19 @@ def modfitexy(x,sigx,y,sigy,mode):
 	print
 	
 	
-	a, b, epsilon, merr_epsilon, perr_epsilon, chisqmin = get_ab(x,sigx,y,sigy,ainit,binit,paramsprecision,N,mode)
+	a, b, epsilon, chisqmin = get_ab(x,sigx,y,sigy,ainit,binit,paramsprecision,N,mode)
 	
 	while paramsprecision > tolerance:
 		paramsprecision = paramsprecision/3
-		a, b, epsilon, merr_epsilon, perr_epsilon, chisqmin = get_ab(x,sigx,y,sigy,a,b,paramsprecision,N,mode)
+		a, b, epsilon, chisqmin = get_ab(x,sigx,y,sigy,a,b,paramsprecision,N,mode)
 		
-	afit, bfit, epsilonfit, merr_epsilonfit, perr_epsilonfit, chisqminfit = a, b, epsilon, merr_epsilon, perr_epsilon, chisqmin 	
+	afit, bfit, epsilonfit, chisqminfit = a, b, epsilon, chisqmin 	
+	
+	epsilonfit_minus, epsilonfit_plus = get_err_epsilon(x,sigx,y,sigy,afit,bfit,epsilonfit,chisqminfit,0.001,N,mode)
+	
+	perr_epsilonfit = epsilonfit_plus - epsilonfit
+	merr_epsilonfit = epsilonfit - epsilonfit_minus
+	
 	print 'get_ab completed'				
 	
[…]

### 2015-04-22 python_codes/tex_tables/tex_tables.py

@@ -490,9 +490,11 @@ def mmpaper_sampletable():
 		physres.mag_sph_eq_moffat_comb, 
 		errV.perr_mag_sph, errV.merr_mag_sph, 
 		physres.mag_tot_eq_moffat_comb, 
-		col.color, anc.bar
+		col.color, anc.bar,
+		res.delta_eq_moffat_comb
 		FROM Ancillary AS anc 
 		JOIN OneDFitResultsPhysicalUnits AS physres ON anc.gal_id = physres.gal_id 
+		JOIN OneDFitResults AS res ON anc.gal_id = res.gal_id \
 		JOIN ErrorsVote as errV ON anc.gal_id = errV.gal_id 
 		JOIN Colors as col ON anc.gal_id = col.gal_id 
 		WHERE anc.fit1D_done = 1
@@ -526,7 +528,14 @@ def mmpaper_sampletable():
 	mag_tot = data[11].astype(np.float)
 	color = data[12].astype(np.float)
 	bar = data[13].astype(np.int)
+	delta = data[14].astype(np.float)
 		
+	## error from 0 to 0.3 mag according to Delta_RMS of profile fit
+	## has mean error = 0.08
+	goodness = delta - min(delta)
+	goodness = goodness/max(goodness)
+	err_mag_tot = 0.3*goodness
+	       
 	log_ML = 3.98*color+0.13 # meidt+2014
 	ML = 10**log_ML
 	
@@ -564,7 +573,7 @@ def mmpaper_sampletable():
                 print '$'+str("{0:.1f}".format(distance[i]))+'$', ' & ', 
                 print_bhmass(mass_BH[i],merr_mass_BH[i],perr_mass_BH[i])
 		print '$' + str("{0:.2f}".format(mag_sph[i])) + '_{-' + str("{0:.2f}".format(merr_mag_sph[i])) + '}^{+' + str("{0:.2f}".format(perr_mag_sph[i])) + '}$ ', ' & ',
-		print '$' + str("{0:.2f}".format(mag_tot[i])) + '$ ', 
+		print '$' + str("{0:.2f}".format(mag_tot[i])) + ' \pm ' + str("{0:.2f}".format(err_mag_tot[i])) + '$ ', 
 		if gal_name[i] in ['M94', 'NGC 3079', 'NGC 4388', 'NGC 4945']:
 			print '*',
 		print ' & ',

### 2015-04-23 papers/MbhMsph/mm.tex
fanc

--- 2015-04-17 papers/MbhMsph/mm.tex
@@
 are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
-3) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$ only for early-type galaxies.
+3) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well, in terms of intrinsic scatter, with $M_{\rm BH}$ only for early-type galaxies.
 
@@
                        & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
-		       & mFITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49$ & $0.56$ \\
-		       & mFITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.07}$ & $-0.61^{+0.04}_{-0.05}$ & $-23.86$ & $0.96$ & $0.67$ \\
+                       & mFITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
+                       & mFITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.67$ \\
                        & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
+                       & Kelly OLS$(Y|X)$  & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\
+                       & Kelly OLS$(X|Y)$  & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\
+                       & Kelly Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.09$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]
 
@@
                        & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
-		       & mFITEXY OLS$(Y|X)$ & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38$ & $0.46$ \\
-		       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.78$ & $0.55$ \\
+                       & mFITEXY OLS$(Y|X)$ & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
+                       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
                        & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
+                       & Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\
+                       & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\
+                       & Kelly Bisector    & $8.55 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]
 
@@
                    & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
-                   & mFITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37$ & $0.42$ \\
-                   & mFITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.85$ & $0.67$ \\
+                   & mFITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37^{+0.08}_{-0.06}$ & $0.42$ \\
+                   & mFITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.67$ \\
                    & mFITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
+                   & Kelly OLS$(Y|X)$  & $9.0 \pm 0.1$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\
+                   & Kelly OLS$(X|Y)$  & $9.0 \pm 0.2$ & $-0.7 \pm 0.3$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\
+                   & Kelly Bisector    & $9.0 \pm 0.1$ & $-0.4 \pm 0.1$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]
 
@@
               & BCES Bisector     & $7.7  \pm 0.1$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
-              & mFITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54$ & $0.61$ \\
-              & mFITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.89$ & $0.93$ \\
+              & mFITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54^{+0.09}_{-0.07}$ & $0.61$ \\
+              & mFITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
               & mFITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$     & $0.71$ \\
+              & Kelly OLS$(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\
+              & Kelly OLS$(X|Y)$  & $7.7 \pm  0.1$ & $-0.9 \pm 0.2$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\
+              & Kelly Bisector    & $7.7 \pm 0.1$ & $-0.6 \pm 0.1$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
 
@@
                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
- 		      	     & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40$ & $0.46$ \\
- 		      	     & mFITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $1.00$ & $0.57$\\
+                             & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40^{+0.06}_{-0.05}$ & $0.46$ \\
+                             & mFITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $0.49^{+0.08}_{-0.06}$ & $0.57$\\
                              & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
+                             & Kelly OLS$(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.41 \pm 0.06$ & $0.46$ \\
+                             & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.48 \pm 0.06$ & $-24.47$ & $0.51 \pm 0.10$ & $0.56$ \\
+                             & Kelly Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.09$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]
 
@@
                           & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{-1.1 \pm 0.3}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
- 		   	  & mFITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
- 		   	  & mFITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
+                          & mFITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.55^{+0.15}_{-0.10}$ & $0.62$ \\
+                          & mFITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.4}$ & $-22.33$ & $1.08^{+0.40}_{-0.24}$ & $1.50$ \\
                           & mFITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
+                          & Kelly OLS$(Y|X)$  & $7.2 \pm 0.2$ & $-0.5 \pm 0.3$ & $-22.33$ & $0.64 \pm 0.16$ & $0.62$ \\
+                          & Kelly OLS$(X|Y)$  & $7.3 \pm 0.4$ & $-1.9 \pm 1.2$ & $-22.33$ & $1.3 \pm 0.9$ & $1.4$ \\
+                          & Kelly Bisector    & $7.3 \pm 0.3$ & $-0.9 \pm 0.5$ & $-22.33$ & $-$    & $0.78$ \\
+
+\hline 
+\hline
+\end{tabular}
+\label{tab:lreg} 
+\end{table*}
+
+\begin{table*}
+\centering
+\caption{Linear regression analysis. {\bf X0 is the average X of the subsample...}}
+\begin{tabular}{llccccc}
+\hline
+\hline
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
 \hline 
@@
  			& BCES Bisector     & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
- 		       & mFITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.48^{+0.06}_{-0.07}$ & $-24.78$ & $0.62$ & $0.64$ \\
- 		       & mFITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$    & $-24.78$ & $0.87$ & $0.93$ \\
- 		       & mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
+ 			& mFITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.05}$ & $0.64$ \\
+ 			& mFITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$	& $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
+ 			& mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
+ 			& Kelly OLS$(Y|X)$  & $8.26 \pm 0.08$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\
+ 			& Kelly OLS$(X|Y)$  & $8.3 \pm 0.1$ & $-1.0 \pm 0.1$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\
+ 			& Kelly Bisector    & $8.3 \pm 0.1$ & $-0.7 \pm 0.1$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]
 
@@
  			& BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
- 		       & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.41^{+0.05}_{-0.05}$ & $-24.88$ & $0.41$ & $0.45$ \\
- 		       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.07}_{-0.09}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.79$ & $0.55$ \\
- 		       & mFITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.53^{+0.05}_{-0.07}$ & $-24.88$ & $-$    & $0.47$ \\
+ 			& mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
+ 			& mFITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
+ 			& mFITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
+ 			& Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\
+ 			& Kelly OLS$(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\
+ 			& Kelly Bisector    & $8.56 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.88$ & $-$    & $0.47$ \\
 
@@
                               & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.0 \pm 0.1}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
-		      	      & FITEXY OLS$(Y|X)$  & $$ & $$ & $10.81$ & $$ & $$ \\
-		      	      & FITEXY OLS$(X|Y)$  & $$ & $$ & $10.81$ & $$ & $$ \\
-		      	      & FITEXY Bisector    & $$ & $$ & $10.81$ & $-$    & $$ \\
+                              & mFITEXY OLS$(Y|X)$  & $8.56^{+0.06}_{-0.07}$ & $0.8^{+0.1}_{-0.1}$ & $10.81$ & $0.42^{+0.06}_{-0.05}$ & $0.48$ \\
+                              & mFITEXY OLS$(X|Y)$  & $8.54^{+0.09}_{-0.08}$ & $1.3^{+0.2}_{-0.1}$ & $10.81$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
+                              & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.0^{+0.1}_{-0.1}$ & $10.81$ & $-$                    & $0.51$ \\
+                              & Kelly OLS$(Y|X)$  & $8.55 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\
+                              & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $1.3 \pm 0.2$ & $10.81$ & $0.54 \pm 0.11$ & $0.59$ \\
+                              & Kelly Bisector    & $8.55 \pm 0.08$ & $1.0 \pm 0.2$ & $10.81$ & $-$    & $0.51$ \\ [0.5em]
 
@@
                              & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{3.0 \pm 1.3}$ & $\boldsymbol{10.05}$ & $-$ & $\boldsymbol{0.94}$ \\
-		     	     & FITEXY OLS$(Y|X)$  & $$ & $$ & $10.05$ & $$ & $$ \\
-		     	     & FITEXY OLS$(X|Y)$  & $$ & $$ & $10.05$ & $$ & $$ \\
-		     	     & FITEXY Bisector    & $$ & $$ & $10.05$ & $-$    & $$ \\
+                             & mFITEXY OLS$(Y|X)$  & $7.2^{+0.1}_{-0.2}$ & $1.2^{+0.7}_{-0.6}$ & $10.05$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
+                             & mFITEXY OLS$(X|Y)$  & $7.4^{+1.5}_{-0.5}$ & $7.1^{+26.3}_{-3.0}$ & $10.05$ & $1.49^{+0.57}_{-0.35}$ & $2.08$ \\
+                             & mFITEXY Bisector    & $7.2^{+1.0}_{-0.4}$ & $2.3^{+1.7}_{-1.0}$ & $10.05$ & $-$    & $0.79$ \\
+                             & Kelly OLS$(Y|X)$  & $7.2 \pm 0.2$ & $0.9 \pm 0.9$ & $10.05$ & $0.67 \pm 0.16$ & $0.65$ \\
+                             & \textcolor{red}{Kelly OLS$(X|Y)$}  & $7.4 \pm 0.6$ & $7.0 \pm 6.6$ & $10.05$ & $1.83 \pm 1.82$ & $2.04$ \\
+                             & \textcolor{red}{Kelly Bisector}    & $7.3 \pm 0.5$ & $1.9 \pm 203.0$ & $10.05$ & $-$    & $0.74$ \\
 

### 2015-04-23 python_codes/paper_figures/MbhMsph/figures.py

@@ -197,8 +197,8 @@ def mbh_vs_mass_sph_agn():
 	
 	bulge = core*[0]
 	bulge[simplemorphtype=='S0'] = 1
-	bulge[simplemorphtype=='S'] = 1
-	bulge[simplemorphtype=='S0/S'] = 1
+	bulge[simplemorphtype=='Sp'] = 1
+	bulge[simplemorphtype=='S0/Sp'] = 1
 	
         for i in range(len(ELL)):
         	if simplemorphtype[i]=='E' and core[i]==1 and gal_id[i] not in outliers:
@@ -303,65 +303,65 @@ def mbh_vs_mass_sph_agn():
        #print '-----------------------------'
        #print '-----------------------------'
        #
-       
+       #
        ############################
-        
-        print 'BCES early'
-        print 'n', len(log_mass_sph[earlytype==1])
-        A,B,Aerr,Berr,covAB=bces.bces(log_mass_sph[earlytype==1]-np.average(log_mass_sph[earlytype==1]),
-        	0.5*(perr_log_mass_sph[earlytype==1] + merr_log_mass_sph[earlytype==1]),
-        	log_mbh[earlytype==1],0.5*(merr_log_mbh[earlytype==1] + perr_log_mbh[earlytype==1]),log_mass_sph[earlytype==1]*[0.0])
-        absscat_0 = absolutescatter.get_absscatter(log_mass_sph[earlytype==1]-np.average(log_mass_sph[earlytype==1]), log_mbh[earlytype==1], B[0], A[0])
-        absscat_1 = absolutescatter.get_absscatter(log_mass_sph[earlytype==1]-np.average(log_mass_sph[earlytype==1]), log_mbh[earlytype==1], B[1], A[1])
-        absscat_2 = absolutescatter.get_absscatter(log_mass_sph[earlytype==1]-np.average(log_mass_sph[earlytype==1]), log_mbh[earlytype==1], B[2], A[2])
-        absscat_3 = absolutescatter.get_absscatter(log_mass_sph[earlytype==1]-np.average(log_mass_sph[earlytype==1]), log_mbh[earlytype==1], B[3], A[3])
-        print '---------------------------------'
-        print 'y = A*(x-<x>) + B '
[…]

### 2015-04-24 papers/MbhMsph/mm.tex
friiiiiiday

@@
 
-\title{M-M paper, morphological dependence, red sequence }
+\title{Supermassive black holes and host bulges affairs -- \\ II. The red and the blue sequences in the mass -- mass diagram.}
 
@@
 Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
-Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
+Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
 which is minimally affected by dust and star formation. 
@@
 as expected from a dry-merging formation scenario,
-and define a tight \emph{red sequence} with intrinsic scatter $\epsilon = 0.43 \pm 0.06$.
+and define a tight \emph{red sequence} with intrinsic scatter $\epsilon = 0.43 \pm 0.06\rm~dex$.
 On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
@@
 are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
-3) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well, in terms of intrinsic scatter, with $M_{\rm BH}$ only for early-type galaxies.
+3) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies.
 
@@
 consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
-(GS13, \citealt{rusli2013bhmassesDM}) at the time we started this project, 
+(by GS13 or \citealt{rusli2013bhmassesDM}) at the time we started this project, 
 and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
@@
 to confirm the presence of rotationally supported components in most early-type galaxies, 
-and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
+and to identify their extent 
+(intermediate-scale disks, that are fully embedded in the bulge, 
+or large-scale disks, that encase the bulge and dominate the light at large radii). 
 \emph{Paper I} will present the dataset used here to investigate the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
 give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
-discuss how we estimated the uncertainties on the bulge parameters, 
-and illustrate the individual 66 galaxy decompositions. \\
+discuss how we estimated the uncertainties\footnote{By comparing, for our galaxies, the measurements of the bulge magnitude 
+obtained by different authors with those obtained by us, we estimated the uncertainties on the bulge magnitudes 
+with a method that takes into account systematic errors. 
+Systematic errors include incorrect sky subtraction, inaccurate masking of contaminating sources, imprecise description of the PSF, 
+erroneous choice of model components (for example, when failing to identify a galaxy subcomponent and thus omitting it in the model, 
+or when describing a galaxy sub-component with an inadequate function), 
+the radial extent of the surface brightness profile and its sampling. 
+These factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters. 
+In fact, when performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well spatially resolved -- galaxies, 
+errors are dominated by systematics rather than Poisson noise.} 
+on the bulge magnitudes, and illustrate the individual 66 galaxy decompositions. \\
 Bulge luminosities\footnote{Absolute luminosities were calculated 
@@
 which are given here as lower limits. 
+Following GS13, we assumed a constant uncertainty of $0.25\rm~mag$ for all galaxy magnitudes.
 
@@
 \begin{center}
-%\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_agn.pdf}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_galsymb_agn.pdf}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
 \caption{Black hole mass against spheroid stellar mass. 
-The galaxies from our sample are shown with large symbols (red = E, orange = E/S0 and S0, blue = S0/Sp and Sp, black = merger).
-The 139 small blue dots represent the low-mass AGN sample from \cite{jiang2011a}. 
-The blue crossed circles denote 35 additional galaxies (see \citealt{grahamscott2015}, their Table 2), 
-some of which might have had their bulge stellar masses overestimated.
+Symbols are coded according to the galaxy morphological type (red = E, orange = E/S0 and S0, blue = S0/Sp and Sp, black = merger).
 The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
@@
 We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$, $M_{\rm BH} - M_{\rm *,sph}$ and $M_{\rm BH} - L_{\rm gal}$ diagrams 
-using the BCES code from \cite{akritasbershady1996} 
-and also the FITEXY routine \citep{press1992} 
-modified by \cite{tremaine2002} to account for the intrinsic vertical scatter, $\epsilon$. 
-Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
-can give biased results (wrong slope) when the scatter is comparable to the range of the data},
-we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
-In Table \ref{tab:lreg} we report the BCES and modified FITEXY linear regressions, both symmetrical and non-symmetrical, 
+using the BCES code from \cite{akritasbershady1996}. 
+We also repeated the analysis with the FITEXY routine \citep{press1992}, modified by \cite{tremaine2002}, 
+and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
+Although all these three linear regression routines account for the intrinsic scatter, 
+only the last two allow to quantify it.
+%Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
+%can give biased results (wrong slope) when the scatter is comparable to the range of the data},
+%we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
+In Table \ref{tab:lreg}, we report the BCES, modified FITEXY and {\tt linmix\_err} linear regressions, both symmetrical and non-symmetrical, 
 for S\'ersic/core-S\'ersic galaxies and for different galaxy morphological types (elliptical/lenticular, spiral).
@@
 whereas the spheroids of late-type (spiral) galaxies will have $M_{\rm BH} \propto L_{\rm sph}^{\sim 2.5}$.
-First, we checked that the slopes of the bulges of elliptical and lenticular galaxies, separately, are consistent with each other, 
-and thus, together, they define a single \emph{red sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
+First, we checked that elliptical and lenticular galaxies, taken separately, have slopes consistent with each other, 
+and thus, taken together, they define a single \emph{red sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
 We then fit the bulges of early- and late-type galaxies with two separate log-linear regressions, 
@@
 in excellent agreement with the theoretical expectations of our hypothesis.
-{\bf vertical scatter along the early type sequence is constant?
-if 2 overmassive bhs removed, what happens?}
-
-{\bf coming now to figure 1: if I look at the blue points it is difficult to believe that they define a linear relation, 
-their magnitude range is too small and it could just be that at low galaxy luminosities the scatter of the MBH-L relation increases. 
-This is what most models predict. Do the galaxies below the correlation have some special property? 
-Could it just be that spiral bulges simple do not follow a tight relation with BH mass?
-
-Giulia, I think you already plan to do this, but can you include the error bars in all places where a relation is presented, so that readers know if there is a relation or not.
-Remember also Ewan's remark about the unsuitability of the Pearson and Spearman correlation coefficients because they do not take into account the error bars on our data - 
-so don't include those simple coefficients.  Actually, it would be worth pointing out to readers that a visual inspection of the plotted data requires 
+%{\bf vertical scatter along the early type sequence is constant? if 2 overmassive bhs removed, what happens?}
+{\bf AL, can you pls write this: 
+Remember also Ewan's remark about the unsuitability of the Pearson and Spearman correlation coefficients because 
+they do not take into account the error bars on our data - 
+so don't include those simple coefficients.  
+Actually, it would be worth pointing out to readers that a visual inspection of the plotted data requires 
 the viewer to take into account the error bars when judging-by-eye the strength of a correlation. 
@@
 
+\subsection{Pseudo- versus classical bulges}
+Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
+formed through violent processes, such as hierarchical clustering via minor mergers, 
+and pseudo-bulges, thought to be disk-like, rotation-supported systems, 
+built from secular evolution processes, such as instabilities of their surrounding disk or bar. 
+Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
+For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
+and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
+thus rotation is not a definitive signature of a pseudobulge. 
+Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
+macarthur2009,dosanjosdasilva2013,seidel2015}). 
+In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
+S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{fisherdrory2010}), 
+although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
+\cite{grahamworley2008} observed no such bimodality in the bulge S\'ersic indices. 
+While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
+being disky components that formed from their surrounding exponential disks 
+(e.g.~\citealt{bardeen1975,hohl1975,combessanders1981,combes1990,pfennigerfriedli1991}), 
+it has been shown that mergers can create bulges with $n_{\rm sph}<2$
+(e.g.~\citealt{elichemoral2011,scannapieco2011,querejeta2015}), 
+just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
+are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994}). \\
+\cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
+with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
+traced by classical bulges. 
 In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
-are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).}, 
-$n_{\rm sph}$, in the $M_{\rm BH} - L_{\rm sph}$ diagram.
-Our aim is to check whether bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges (e.g.~ cite), 
-are offset to lower black hole masses from the correlation defined by (classical) bulges with $n_{\rm sph}>2$, 
-as reported by \cite{sani2011} {\bf who else?}. 
+are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).} 
+in the $M_{\rm BH} - L_{\rm sph}$ diagram.
+Our aim is to check whether $n_{\rm sph}<2$ bulges 
+are offset to lower black hole masses from the correlation defined by $n_{\rm sph}>2$ bulges. 
 To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
@@
 
-{\bf As you probably know, and as explained in many of my papers (e.g. http://arxiv.org/abs/1501.02937 ; http://arxiv.org/abs/1108.0997 ; http://arxiv.org/abs/1311.7207 ), 
-pseudobulges are notoriously hard to identify.  It would be a mistake to have a column labelled "pseudobulge".   
-However a galaxy classification column, indicating the presence of a bar, is good to include.  
-While we do not wish to publish the Sersic indices here (that will be kept for a different paper), 
-we could have a column indicating if n is above or below 2 - given that some people mistakingly think that they can use this as a dividing point. 
-Giulia, can you also include a nearby reference to Graham (2013, http://arxiv.org/abs/1108.0997) so that people can read and understand why $n < 2$ 
-does not necessarily equate to a pseudobulge. }
-
 \subsection{Black hole mass -- galaxy luminosity}
@@
 and thus are not included in the linear regression analysis. 
-\cite{lasker2014anal}
+Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
+\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
+which they fit with a single power-law, have consistent intrinsic scatter.
+Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
+we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
+The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
+has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
+and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
+whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
+and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
+When considering only early-type galaxies, 
+we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter 
+($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
+against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
+{\bf We point out here that this result does not strongly depend on the value that we assumed for the uncertainty of galaxy magnitudes (0.25). 
+In fact, we tested different values and found that we need $error >= 0.7 mag$ to say that gal lum has smaller intrinsic scatter.
 
-Contrary to a previous claim, the bulge luminosity appears to be a better indicator of the BH mass than the galaxy luminosity.
-
-compare scatter mbh-msph and mbh-mgal for early types
-intrinsic scatter of early type gals in m-mbul is slightly more than in m-mgal, but this might just depend 
-on the ability of measuring the bulge luminosity, which is model dependent, the gal lum is not.
-only for early type galaxies one can use the tot luminosity as bh mass indicator
-
-errors on gal mag??????????????? 0.2 constant
+From the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
+than performing galaxy decompositions to obtain bulge luminosities. 
+This, combined with the results from our analysis, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
+to predict black hole masses in a sample of elliptical and lenticular galaxies only.
 
 \subsection{Black hole mass -- spheroid stellar mass}
-Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
-where we include our sample of 66 galaxies, 
-plus the 35 + 139 low-mass AGNs taken from the compilation of \cite{grahamscott2015}.
+Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}.
 
-addition of agns
 relations
@@
 \acknowledgments
-%GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Elisabete Lima Da Cunha and Gonzalo Diaz 
-%for useful discussion. \\
+GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha and Gonzalo Diaz for useful discussion. \\
+% referee thank you!!
 This research was supported by Australian Research Council funding through grants
@@
 under contract with the National Aeronautics and Space Administration. 
+The BCES routine \citep{akritasbershady1996} was run via the python module 
+written by Rodrigo Nemmen \citep{nemmen2012}, which is available at {\url https://github.com/rsnemmen/BCES}.
 

### 2015-04-24 python_codes/paper_figures/MbhMsph/figures.py

@@ -664,6 +664,219 @@ def mbh_vs_mass_sph_agn():
         plt.show()
 	#plt.savefig(path_paper_figures + 'mbh_vs_mass_sph_agn.pdf', format='pdf', dpi=1000)
 
+def mbh_vs_mass_sph():
+	
+	#outliers = [u'n1374', u'n3842exp', u'n4889']
+	outliers = []
+	
+	connection = sql3.connect(dbname)
+	cur = connection.cursor()
+
+	getdata_query = 'SELECT anc.gal_id, anc.mass_BH, anc.perr_mass_BH, anc.merr_mass_BH, anc.core, \
+		pysres.mag_sph_eq_moffat_comb, \
+		errV.perr_mag_sph, errV.merr_mag_sph, \
+		anc.ELLIPTICAL_my, anc.simplemorphtype, \
+		pysres.log_n_eq_moffat_comb, \
+		col.color  \
+		FROM Ancillary AS anc \
+		JOIN OneDFitResultsPhysicalUnits AS pysres ON anc.gal_id = pysres.gal_id \
+		JOIN ErrorsVote as errV ON anc.gal_id = errV.gal_id \
+		JOIN Colors as col ON anc.gal_id = col.gal_id \
+		WHERE anc.fit1D_done = 1;'
+	cur.execute(getdata_query)
+	datalist = cur.fetchall()
+	data= np.asarray(datalist).transpose()
+	#print data
+	gal_id = data[0]
+	mbh = data[1].astype(np.float)
+	log_mbh = np.log10(mbh)
+	perr_mbh = data[2].astype(np.float)
+	perr_log_mbh = np.log10(1 + perr_mbh/mbh)
+	merr_mbh = data[3].astype(np.float)
+	merr_log_mbh = -np.log10(1 - merr_mbh/mbh)
+	core = data[4].astype(np.int)
+	mag_sph = data[5].astype(np.float)
+	perr_mag_sph = data[6].astype(np.float)
+	merr_mag_sph = data[7].astype(np.float)
+	ELL = data[8].astype(np.int)
+	simplemorphtype = data[9]
+	log_n = data[10].astype(np.float)
+	n = 10**log_n
+	color = data[11].astype(np.float)
+	
+	log_ML = 3.98*color+0.13 # meidt+2014
+	ML = 10**log_ML
+	
[…]

### 2015-04-26 papers/MbhMsph/mm.tex
mon morn

@@
 Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
-and thus are not included in the linear regression analysis. 
+and thus are not included in the linear regression analysis. \\
 Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
@@
 and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
-When considering only early-type galaxies, 
-we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter 
-($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
-against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
-{\bf We point out here that this result does not strongly depend on the value that we assumed for the uncertainty of galaxy magnitudes (0.25). 
-In fact, we tested different values and found that we need $error >= 0.7 mag$ to say that gal lum has smaller intrinsic scatter.
-
-From the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
-than performing galaxy decompositions to obtain bulge luminosities. 
-This, combined with the results from our analysis, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
-to predict black hole masses in a sample of elliptical and lenticular galaxies only.
+However, when considering only early-type galaxies, 
+we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
+%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
+%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
+Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
+smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
+we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
+(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
+On the other hand, the uncertainties associated to $L_{\rm sph}$ have been estimated 
+with an advanced method that takes into account the systematic errors related to the galaxy decomposition process. 
+We consider these uncertainties trustworthy and, therefore, we decided to vary only the errors associated to $L_{\rm gal}$.
+We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
+have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
+Because such error is larger than the typical error on $L_{\rm sph}$ used here
+-- and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically used in the literature --, 
+we come to the conclusion that our determination of the intrinsic scatter is reliable, 
+and that, for early-type galaxies, $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$.
+As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
+than performing accurate %galaxy decompositions to obtain bulge luminosities. 
+This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
+to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.
 
@@
 \label{sec:concl}
-ngc0524 outlier, n1332 non outlier
+%ngc0524 outlier, n1332 non outlier
 
@@
 
-\bibliography{/Users/gsavorgnan/Dropbox_notsync/giulia_e_basta/Literature/SMBHbibliography}
+\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
 

### 2015-04-26 python_codes/paper_figures/MbhMsph/figures.py

@@ -1113,7 +1113,7 @@ def mbh_vs_mag_tot():
 	color = data[11].astype(np.float)
 	
 	## constant error on galaxy magnitude
-	err_mag_tot = mag_tot*[0.0] + 0.25
+	err_mag_tot = mag_tot*[0.0] + 0.7
 	
 	## error from 0 to 0.3 mag according to Delta_RMS of profile fit
 	## has mean error = 0.08
@@ -1165,71 +1165,71 @@ def mbh_vs_mag_tot():
 	error_kwargs = {"lw":.5, "zorder":0}
 
         	
-        print 'BCES all'
-        print 'n', len(mag_tot[all==1])
-        A,B,Aerr,Berr,covAB=bces.bces(mag_tot[all==1]-np.average(mag_tot[all==1]),
-        	err_mag_tot[all==1],
-        	log_mbh[all==1],0.5*(merr_log_mbh[all==1] + perr_log_mbh[all==1]),mag_tot[all==1]*[0.0])
-        absscat_0 = absolutescatter.get_absscatter(mag_tot[all==1]-np.average(mag_tot[all==1]), log_mbh[all==1], B[0], A[0])
-        absscat_1 = absolutescatter.get_absscatter(mag_tot[all==1]-np.average(mag_tot[all==1]), log_mbh[all==1], B[1], A[1])
-        absscat_2 = absolutescatter.get_absscatter(mag_tot[all==1]-np.average(mag_tot[all==1]), log_mbh[all==1], B[2], A[2])
-        absscat_3 = absolutescatter.get_absscatter(mag_tot[all==1]-np.average(mag_tot[all==1]), log_mbh[all==1], B[3], A[3])
-        print '---------------------------------'
-        print 'y = A*(x-<x>) + B '
-        print '<x> =', np.average(mag_tot[all==1])
-        print
-        print 'OLS(Y|X)    A =', "{0:.4f}".format(A[0]), '+-', "{0:.4f}".format(Aerr[0]), '   B = ', "{0:.4f}".format(B[0]), '+-', "{0:.4f}".format(Berr[0]), 'Delta =', "{0:.4f}".format(absscat_0)
-        print 'OLS(X|Y)    A =', "{0:.4f}".format(A[1]), '+-', "{0:.4f}".format(Aerr[1]), '   B = ', "{0:.4f}".format(B[1]), '+-', "{0:.4f}".format(Berr[1]), 'Delta =', "{0:.4f}".format(absscat_1)
[…]

### 2015-04-28 papers/MbhMsph/mm.tex
tuesday pill

@@
 \author{A. Marconi}
-\affil{?}
+\affil{Dipartimento di Fisica e Astronomia, Universit\'a di Firenze, via G. Sansone 1, I-50019 Sesto Fiorentino, Firenze, Italy.}
+\and
 \author{E. Sani}
 \affil{European Southern Observatory, Alonso de Cordova, Vitacura 3107, Santiago, Chile.}
-\and
-\author{L.K. Hunt}
-\affil{?}
 
@@
 
-%\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
-%CTIO is operated by AURA, Inc.\ under contract to the National Science
-%Foundation.}
+%\altaffiltext{1}{}
 %\altaffiltext{2}{Society of Fellows, Harvard University.}
@@
 \begin{abstract}
-We present the latest scaling relations between black hole mass, $M_{\rm BH}$, 
-and spheroid luminosity, $L_{\rm sph}$, spheroid stellar mass, $M_{\rm *,sph}$, and galaxy luminosity, $L_{\rm gal}$,
+We present the latest correlations of black hole mass, $M_{\rm BH}$, 
+with spheroid luminosity, $L_{\rm sph}$, spheroid stellar mass, $M_{\rm *,sph}$, and galaxy luminosity, $L_{\rm gal}$,
 built upon an unprecedented high-quality data set (provided here in a ready-to-use table).
 Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
-Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
-which is minimally affected by dust and star formation. 
-These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
-that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
-and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
+%Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
+%which is minimally affected by dust and star formation. 
+%These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
+%that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
+%and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
+Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
+and were derived from our state-of-the-art multicomponent galaxy decompositions 
+that, for the first time, were checked to be consistent with the galaxy kinematics. 
 Previous studies used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
@@
 and allows us to investigate the poorly studied low-mass end of the correlations.
-We provide updated linear regressions 
-(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
-for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
+%We provide updated linear regressions 
+%(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
+%for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
 The bulges of early-type (E/S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$, 
 as expected from a dry-merging formation scenario,
-and define a tight \emph{red sequence} with intrinsic scatter $\epsilon = 0.43 \pm 0.06\rm~dex$.
+and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
 On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
-with $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
-indicating that gas-rich processes feed the black hole three times more efficiently than the host bulge. 
-Disproving some previous claims, we also conclude that: 1) S\'ersic and core-S\'ersic galaxies do not define two distinct sequences; 
-2) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
+with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
+indicating that gas-rich processes feed the black hole from two to three times more efficiently than the host bulge. 
+Disproving some previous claims, we also conclude that: i) S\'ersic and core-S\'ersic galaxies do not define two distinct sequences; 
+ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
 are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
-3) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies.
+iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies.
 
@@
 such that the black hole mass is lower than expected from the near-linear correlation traced by the high-mass, early-type spheroids. 
-However, \cite{grahamscott2015} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
-are not somehow randomly offset from the high-mass, near-linear correlation, 
-but lie on the two times steeper relation traced by the S\'ersic spheroids. 
-{\bf AL: would you like to add a sentence here, mentioning your forthcoming paper with ewan?} \\
+However, \cite{grahamscott2013} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
+are not randomly offset from the high-mass, near-linear correlation, 
+but follow the two times steeper relation traced by the S\'ersic spheroids. 
+Using data from \cite{jiang2011a}, \cite{grahamscott2015} showed that this appears to extend to spheroids with even lower black hole masses 
+($10^{5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 2 \times 10^{6}$), 
+and a more detailed analysis will be presented in Graham et al. (2015, \emph{in preparation}).  \\
 Here we investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
-using state-of-the-art galaxy decompositions (Savorgnan \& Graham \emph{in preparation}, hereafter \emph{Paper I}) 
+using state-of-the-art galaxy decompositions (Savorgnan \& Graham 2015, \emph{in preparation}, hereafter \emph{Paper I}) 
 for the largest sample of galaxies with directly measured black hole masses.
@@
 \includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
-\caption{Black hole mass against $3.6\rm~\mu m$ spheroid absolute magnitude. 
+\caption{Black hole mass versus $3.6\rm~\mu m$ spheroid absolute magnitude. 
 Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
 Bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges, are marked with an empty square. 
-The black solid line shows the BCES bisector linear regression for spheroids with $n_{\rm sph} \geq 2$. 
-The inset displays, for all spheroids, the vertical offset 
-from the correlation defined by spheroids with $n_{\rm sph} \geq 2$ only 
-versus the spheroid S\'ersic index. 
+The black solid line shows the BCES bisector linear regression for spheroids with $n_{\rm sph} \geq 2$. }
+\label{fig:pseudob}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/inset_psb.pdf}
+\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$. 
 The vertical dashed line corresponds to $n_{\rm sph} = 2$.
+The horizontal solid line is equivalent to a zero vertical offset.
 Bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
@@
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
-All (66)               & BCES OLS$(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
-                       & BCES OLS$(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
+All (66)               & BCES $(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
+                       & BCES $(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
                        & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
-                       & mFITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
-                       & mFITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.67$ \\
+                       & mFITEXY $(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
+                       & mFITEXY $(X|Y)$ & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.67$ \\
                        & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
-                       & Kelly OLS$(Y|X)$  & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\
-                       & Kelly OLS$(X|Y)$  & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\
-                       & Kelly Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.09$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]
+                       & {\tt linmix\_err} $(Y|X)$  & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\
+                       & {\tt linmix\_err} $(X|Y)$  & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\
+                       & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.09$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]
 
-$n>2$ (43)             & BCES OLS$(Y|X)$   & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
-                       & BCES OLS$(X|Y)$   & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
+$n>2$ (43)             & BCES $(Y|X)$   & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
+                       & BCES $(X|Y)$   & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
                        & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
-                       & mFITEXY OLS$(Y|X)$ & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
-                       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
+                       & mFITEXY $(Y|X)$ & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
+                       & mFITEXY $(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
                        & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
-                       & Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\
-                       & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\
-                       & Kelly Bisector    & $8.55 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]
+                       & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\
+                       & {\tt linmix\_err} $(X|Y)$  & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\
+                       & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]
 
-Core-S\'ersic (22) & BCES OLS$(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\
-                   & BCES OLS$(X|Y)$   & $9.1  \pm 0.1$  & $-0.6  \pm 0.1$  & $-25.73$ & $-$    & $0.61$ \\
+Core-S\'ersic (22) & BCES $(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\
+                   & BCES $(X|Y)$   & $9.1  \pm 0.1$  & $-0.6  \pm 0.1$  & $-25.73$ & $-$    & $0.61$ \\
                    & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
-                   & mFITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37^{+0.08}_{-0.06}$ & $0.42$ \\
-                   & mFITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.67$ \\
+                   & mFITEXY $(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37^{+0.08}_{-0.06}$ & $0.42$ \\
+                   & mFITEXY $(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.67$ \\
                    & mFITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
-                   & Kelly OLS$(Y|X)$  & $9.0 \pm 0.1$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\
-                   & Kelly OLS$(X|Y)$  & $9.0 \pm 0.2$ & $-0.7 \pm 0.3$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\
-                   & Kelly Bisector    & $9.0 \pm 0.1$ & $-0.4 \pm 0.1$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]
+                   & {\tt linmix\_err} $(Y|X)$  & $9.0 \pm 0.1$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\
+                   & {\tt linmix\_err} $(X|Y)$  & $9.0 \pm 0.2$ & $-0.7 \pm 0.3$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\
+                   & {\tt linmix\_err} Bisector    & $9.0 \pm 0.1$ & $-0.4 \pm 0.1$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]
 
-S\'ersic (44) & BCES OLS$(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
-              & BCES OLS$(X|Y)$   & $7.7  \pm 0.1$  & $-0.9  \pm 0.2 $ & $-22.92$ & $-$    & $0.93$ \\
+S\'ersic (44) & BCES $(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
+              & BCES $(X|Y)$   & $7.7  \pm 0.1$  & $-0.9  \pm 0.2 $ & $-22.92$ & $-$    & $0.93$ \\
               & BCES Bisector     & $7.7  \pm 0.1$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
-              & mFITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54^{+0.09}_{-0.07}$ & $0.61$ \\
-              & mFITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
+              & mFITEXY $(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54^{+0.09}_{-0.07}$ & $0.61$ \\
+              & mFITEXY $(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
               & mFITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$     & $0.71$ \\
-              & Kelly OLS$(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\
-              & Kelly OLS$(X|Y)$  & $7.7 \pm  0.1$ & $-0.9 \pm 0.2$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\
-              & Kelly Bisector    & $7.7 \pm 0.1$ & $-0.6 \pm 0.1$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
+              & {\tt linmix\_err} $(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\
+              & {\tt linmix\_err} $(X|Y)$  & $7.7 \pm  0.1$ & $-0.9 \pm 0.2$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\
+              & {\tt linmix\_err} Bisector    & $7.7 \pm 0.1$ & $-0.6 \pm 0.1$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
 
-%Ellipticals (E) (30)   & BCES OLS$(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
-%                      & BCES OLS$(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
+%Ellipticals (E) (30)   & BCES $(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
+%                      & BCES $(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
 %                      & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
-%                      & FITEXY OLS$(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
-%                      & FITEXY OLS$(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
+%                      & FITEXY $(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
+%                      & FITEXY $(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
 %                      & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
 %
-%Lenticulars (S0) (13)  & BCES OLS$(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
-%                      & BCES OLS$(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
+%Lenticulars (S0) (13)  & BCES $(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
+%                      & BCES $(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
 %                      & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
-%                      & FITEXY OLS$(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
-%                      & FITEXY OLS$(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
+%                      & FITEXY $(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
+%                      & FITEXY $(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
 %                      & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
 %
-{\bf Early-type (E+S0)} (45) & BCES OLS$(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
-                             & BCES OLS$(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
+{\bf Early-type (E+S0)} (45) & BCES $(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
+                             & BCES $(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
-                             & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40^{+0.06}_{-0.05}$ & $0.46$ \\
-                             & mFITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $0.49^{+0.08}_{-0.06}$ & $0.57$\\
+                             & mFITEXY $(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40^{+0.06}_{-0.05}$ & $0.46$ \\
+                             & mFITEXY $(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $0.49^{+0.08}_{-0.06}$ & $0.57$\\
                              & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
-                             & Kelly OLS$(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.41 \pm 0.06$ & $0.46$ \\
-                             & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.48 \pm 0.06$ & $-24.47$ & $0.51 \pm 0.10$ & $0.56$ \\
-                             & Kelly Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.09$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]
+                             & {\tt linmix\_err} $(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.41 \pm 0.06$ & $0.46$ \\
+                             & {\tt linmix\_err} $(X|Y)$  & $8.55 \pm 0.09$ & $-0.48 \pm 0.06$ & $-24.47$ & $0.51 \pm 0.10$ & $0.56$ \\
+                             & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.09$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]
 
-{\bf Late-type (Sp)} (17) & BCES OLS$(Y|X)$    & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
-                          & BCES OLS$(X|Y)$    & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
+{\bf Late-type (Sp)} (17) & BCES $(Y|X)$    & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
+                          & BCES $(X|Y)$    & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
                           & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{-1.1 \pm 0.3}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
-                          & mFITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.55^{+0.15}_{-0.10}$ & $0.62$ \\
-                          & mFITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.4}$ & $-22.33$ & $1.08^{+0.40}_{-0.24}$ & $1.50$ \\
+                          & mFITEXY $(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.55^{+0.15}_{-0.10}$ & $0.62$ \\
+                          & mFITEXY $(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.4}$ & $-22.33$ & $1.08^{+0.40}_{-0.24}$ & $1.50$ \\
                           & mFITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
-                          & Kelly OLS$(Y|X)$  & $7.2 \pm 0.2$ & $-0.5 \pm 0.3$ & $-22.33$ & $0.64 \pm 0.16$ & $0.62$ \\
-                          & Kelly OLS$(X|Y)$  & $7.3 \pm 0.4$ & $-1.9 \pm 1.2$ & $-22.33$ & $1.3 \pm 0.9$ & $1.4$ \\
-                          & Kelly Bisector    & $7.3 \pm 0.3$ & $-0.9 \pm 0.5$ & $-22.33$ & $-$    & $0.78$ \\
+                          & {\tt linmix\_err} $(Y|X)$  & $7.2 \pm 0.2$ & $-0.5 \pm 0.3$ & $-22.33$ & $0.64 \pm 0.16$ & $0.62$ \\
+                          & {\tt linmix\_err} $(X|Y)$  & $7.3 \pm 0.4$ & $-1.9 \pm 1.2$ & $-22.33$ & $1.3 \pm 0.9$ & $1.4$ \\
+                          & {\tt linmix\_err} Bisector    & $7.3 \pm 0.3$ & $-0.9 \pm 0.5$ & $-22.33$ & $-$    & $0.78$ \\
 
@@
   & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
- All (62)		& BCES OLS$(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
- 			& BCES OLS$(X|Y)$   & $8.3 \pm 0.1$   & $-1.0 \pm 0.1$   & $-24.78$ & $-$ & $0.92$ \\
+ All (62)		& BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
+ 			& BCES $(X|Y)$   & $8.3 \pm 0.1$   & $-1.0 \pm 0.1$   & $-24.78$ & $-$ & $0.92$ \\
  			& BCES Bisector     & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
- 			& mFITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.05}$ & $0.64$ \\
- 			& mFITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$	& $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
+ 			& mFITEXY $(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.05}$ & $0.64$ \\
+ 			& mFITEXY $(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$	& $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
  			& mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
- 			& Kelly OLS$(Y|X)$  & $8.26 \pm 0.08$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\
- 			& Kelly OLS$(X|Y)$  & $8.3 \pm 0.1$ & $-1.0 \pm 0.1$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\
- 			& Kelly Bisector    & $8.3 \pm 0.1$ & $-0.7 \pm 0.1$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]
+ 			& {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.08$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\
+ 			& {\tt linmix\_err} $(X|Y)$  & $8.3 \pm 0.1$ & $-1.0 \pm 0.1$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\
+ 			& {\tt linmix\_err} Bisector    & $8.3 \pm 0.1$ & $-0.7 \pm 0.1$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]
 
- Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.06$ & $-0.43 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
- 			& BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.63 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
+ Early-type (E+S0) (45) & BCES $(Y|X)$   & $8.56 \pm 0.06$ & $-0.43 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
+ 			& BCES $(X|Y)$   & $8.56 \pm 0.08$ & $-0.63 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
  			& BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
- 			& mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
- 			& mFITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
+ 			& mFITEXY $(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
+ 			& mFITEXY $(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
  			& mFITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
- 			& Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\
- 			& Kelly OLS$(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\
- 			& Kelly Bisector    & $8.56 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.88$ & $-$    & $0.47$ \\
+ 			& {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\
+ 			& {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\
+ 			& {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.88$ & $-$    & $0.47$ \\
 
-%All (62)               & BCES OLS$(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
-%                       & BCES OLS$(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
+%All (62)               & BCES $(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
+%                       & BCES $(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
 %                       & BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
-%                       & FITEXY OLS$(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
-%                       & FITEXY OLS$(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
+%                       & FITEXY $(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
+%                       & FITEXY $(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
 %                       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
-%                       & Kelly OLS$(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\
-%                       & Kelly OLS$(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\
-%                       & Kelly Bisector    & $$ & $$ & $$ & $-$    & $$ \\
+%                       & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\
+%                       & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\
+%                       & {\tt linmix\_err} Bisector    & $$ & $$ & $$ & $-$    & $$ \\
 
@@
   & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - X_0)/{\rm M_\odot}]$} \\ [0.5em]
-{\bf Early-type (E+S0)} (45)  & BCES OLS$(Y|X)$    & $8.56 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $-$ & $0.48$ \\
-                              & BCES OLS$(X|Y)$    & $8.56 \pm 0.08$ & $1.3 \pm 0.1$ & $10.81$ & $-$ & $0.59$ \\
+{\bf Early-type (E+S0)} (45)  & BCES $(Y|X)$    & $8.56 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $-$ & $0.48$ \\
+                              & BCES $(X|Y)$    & $8.56 \pm 0.08$ & $1.3 \pm 0.1$ & $10.81$ & $-$ & $0.59$ \\
                               & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.0 \pm 0.1}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
-                              & mFITEXY OLS$(Y|X)$  & $8.56^{+0.06}_{-0.07}$ & $0.8^{+0.1}_{-0.1}$ & $10.81$ & $0.42^{+0.06}_{-0.05}$ & $0.48$ \\
-                              & mFITEXY OLS$(X|Y)$  & $8.54^{+0.09}_{-0.08}$ & $1.3^{+0.2}_{-0.1}$ & $10.81$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
+                              & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.07}$ & $0.8^{+0.1}_{-0.1}$ & $10.81$ & $0.42^{+0.06}_{-0.05}$ & $0.48$ \\
+                              & mFITEXY $(X|Y)$  & $8.54^{+0.09}_{-0.08}$ & $1.3^{+0.2}_{-0.1}$ & $10.81$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
                               & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.0^{+0.1}_{-0.1}$ & $10.81$ & $-$                    & $0.51$ \\
-                              & Kelly OLS$(Y|X)$  & $8.55 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\
-                              & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $1.3 \pm 0.2$ & $10.81$ & $0.54 \pm 0.11$ & $0.59$ \\
-                              & Kelly Bisector    & $8.55 \pm 0.08$ & $1.0 \pm 0.2$ & $10.81$ & $-$    & $0.51$ \\ [0.5em]
+                              & {\tt linmix\_err} $(Y|X)$  & $8.55 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\
+                              & {\tt linmix\_err} $(X|Y)$  & $8.55 \pm 0.09$ & $1.3 \pm 0.2$ & $10.81$ & $0.54 \pm 0.11$ & $0.59$ \\
+                              & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $1.0 \pm 0.2$ & $10.81$ & $-$    & $0.51$ \\ [0.5em]
 
-{\bf Late-type (Sp)} (17)    & BCES OLS$(Y|X)$    & $7.2 \pm 0.2$ & $1.9 \pm 1.5$ & $10.05$ & $-$ & $0.74$ \\ 
-                             & BCES OLS$(X|Y)$    & $7.2 \pm 0.4$ & $5.9 \pm 3.4$ & $10.05$ & $-$ & $1.70$ \\
+{\bf Late-type (Sp)} (17)    & BCES $(Y|X)$    & $7.2 \pm 0.2$ & $1.9 \pm 1.5$ & $10.05$ & $-$ & $0.74$ \\ 
+                             & BCES $(X|Y)$    & $7.2 \pm 0.4$ & $5.9 \pm 3.4$ & $10.05$ & $-$ & $1.70$ \\
                              & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{3.0 \pm 1.3}$ & $\boldsymbol{10.05}$ & $-$ & $\boldsymbol{0.94}$ \\
-                             & mFITEXY OLS$(Y|X)$  & $7.2^{+0.1}_{-0.2}$ & $1.2^{+0.7}_{-0.6}$ & $10.05$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
-                             & mFITEXY OLS$(X|Y)$  & $7.4^{+1.5}_{-0.5}$ & $7.1^{+26.3}_{-3.0}$ & $10.05$ & $1.49^{+0.57}_{-0.35}$ & $2.08$ \\
+                             & mFITEXY $(Y|X)$  & $7.2^{+0.1}_{-0.2}$ & $1.2^{+0.7}_{-0.6}$ & $10.05$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
+                             & mFITEXY $(X|Y)$  & $7.4^{+1.5}_{-0.5}$ & $7.1^{+26.3}_{-3.0}$ & $10.05$ & $1.49^{+0.57}_{-0.35}$ & $2.08$ \\
                              & mFITEXY Bisector    & $7.2^{+1.0}_{-0.4}$ & $2.3^{+1.7}_{-1.0}$ & $10.05$ & $-$    & $0.79$ \\
-                             & Kelly OLS$(Y|X)$  & $7.2 \pm 0.2$ & $0.9 \pm 0.9$ & $10.05$ & $0.67 \pm 0.16$ & $0.65$ \\
-                             & \textcolor{red}{Kelly OLS$(X|Y)$}  & $7.4 \pm 0.6$ & $7.0 \pm 6.6$ & $10.05$ & $1.83 \pm 1.82$ & $2.04$ \\
-                             & \textcolor{red}{Kelly Bisector}    & $7.3 \pm 0.5$ & $1.9 \pm 203.0$ & $10.05$ & $-$    & $0.74$ \\
+                             & {\tt linmix\_err} $(Y|X)$  & $7.2 \pm 0.2$ & $0.9 \pm 0.9$ & $10.05$ & $0.67 \pm 0.16$ & $0.65$ \\
+                             & \textcolor{red}{{\tt linmix\_err} $(X|Y)$}  & $7.4 \pm 0.6$ & $7.0 \pm 6.6$ & $10.05$ & $1.83 \pm 1.82$ & $2.04$ \\
+                             & \textcolor{red}{{\tt linmix\_err} Bisector}    & $7.3 \pm 0.5$ & $1.9 \pm 203.0$ & $10.05$ & $-$    & $0.74$ \\
 
@@
 Symmetrical regressions are meant to be compared with theoretical expectations, 
-whereas non-symmetrical Ordinary Least Squares $(Y|X)$ regressions -- 
+whereas non-symmetrical $(Y|X)$ regressions -- 
 since they minimize the scatter in the vertical direction -- 
@@
 Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}. 
+The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$,
+as expected from a dry-merging formation scenario,
+and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
+On the other hand, the bulges of spiral galaxies trace a steeper \emph{blue sequence}, 
+whose slope is not well constrained due to the small size of the subsample and, more importantly, 
+to the small range in $M_{\rm *,sph}$ that the subsample spans.
+For the bulges of spiral galaxies, the BCES code returns a bisector linear regression $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
+while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) slope of $2.3^{+1.7}_{-1.0}$.
+The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
+{\bf which code do we trust more in this case? BCES or FITEXY? is it a quadratic or a cubic growth? }
 
-relations
-agns consistent w spirals, but analysis deferred to other paper
-cubic growth
+\cite{grahamscott2015} collected a sample of $\sim$170 low-redshift ($z \lesssim 0.1$) bulges hosting Active Galactic Nuclei (AGNs) with 
+black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
+and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by predominantly inactive S\'ersic bulges. 
+Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
+we anticipate here that the correlation traced by our bulges of spiral galaxies 
+tracks the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram, 
+i.e. the AGNs appears to be the low-mass continuation of the \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
+We also note that the majority of our spiral galaxies hosts an AGN\footnote{According to the nuclear classification reported on NED 
+(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.\\
+{\bf cite Anne's paper}\\
+{\bf AL: however we analyze the agns in another paper, blah blah}
 
@@
 %ngc0524 outlier, n1332 non outlier
+to be written
 

### 2015-04-28 python_codes/paper_figures/MbhMsph/figures.py

@@ -24,7 +24,7 @@ rc('font',**{'family':'sans-serif','sans-serif':['CenturyGothic']})
 rc('text', usetex=True)
 
 
-matplotlib.rcParams.update({'font.size': 22})
+matplotlib.rcParams.update({'font.size': 26})
 
 dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_vivisection.db'
 
@@ -1029,15 +1029,15 @@ def mbh_vs_mag_sph_psb():
         yy = (A[2]*(logxx) + B[2])
         ax.plot((logxx+np.average(mag_sph[n>2])),10**yy, color='k', ls='-', linewidth=2.)
 	
-        ### fit using FITEXY ###
-        print '-----------------------------'
-        print 'FITEXY n>2'
-        A,perr_A,merr_A,B,perr_B,merr_B = fitexy.bisect_modfitexy(mag_sph[n>2]-np.average(mag_sph[n>2]),
-        	0.5*(perr_mag_sph[n>2] + merr_mag_sph[n>2]),
-        	log_mbh[n>2],0.5*(merr_log_mbh[n>2] + perr_log_mbh[n>2]))
-        print '-----------------------------'
-        print '-----------------------------'
-	
+       #### fit using FITEXY ###
+       #print '-----------------------------'
+       #print 'FITEXY n>2'
+       #A,perr_A,merr_A,B,perr_B,merr_B = fitexy.bisect_modfitexy(mag_sph[n>2]-np.average(mag_sph[n>2]),
+       #	0.5*(perr_mag_sph[n>2] + merr_mag_sph[n>2]),
+       #	log_mbh[n>2],0.5*(merr_log_mbh[n>2] + perr_log_mbh[n>2]))
+       #print '-----------------------------'
+       #print '-----------------------------'
+       #
        #### produce .dat file
        #datfileName = '/Users/gsavorgnan/galaxy_vivisection/data/marconi_fit/mbh_vs_mag_sph_classbul.dat'
        #datfile = open(datfileName, 'w')
@@ -1050,26 +1050,121 @@ def mbh_vs_mag_sph_psb():
 
 	###########################
 
-	# make inset
[…]

### 2015-04-29 papers/MbhMsph/mm.tex
sh

@@
 \begin{abstract}
-We present the latest correlations of black hole mass, $M_{\rm BH}$, 
-with spheroid luminosity, $L_{\rm sph}$, spheroid stellar mass, $M_{\rm *,sph}$, and galaxy luminosity, $L_{\rm gal}$,
-built upon an unprecedented high-quality data set (provided here in a ready-to-use table).
+We present correlations between black hole mass, $M_{\rm BH}$, 
+and both the host galaxy's and spheroid's infrared luminosity, $L_{\rm gal}$ and $L_{\rm sph}$, 
+and the spheroid's stellar mass, $M_{\rm *,sph}$,
+built upon a high-quality data set.
 Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
@@
 that, for the first time, were checked to be consistent with the galaxy kinematics. 
-Previous studies used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
+{\bf limit of 250 words, no room for mentioning the gaalxy components, more appropriate for data paper}
+Previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
 Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
-and allows us to investigate the poorly studied low-mass end of the correlations.
+and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
 %We provide updated linear regressions 
@@
 %for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
-The bulges of early-type (E/S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$, 
-as expected from a dry-merging formation scenario,
+The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
+consistent with a dry-merging formation scenario,
 and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
@@
 with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
-indicating that gas-rich processes feed the black hole from two to three times more efficiently than the host bulge. 
-Disproving some previous claims, we also conclude that: i) S\'ersic and core-S\'ersic galaxies do not define two distinct sequences; 
+indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
+We conclude that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{x \pm x}$, a less steep sequence than previously reported; 
 ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
 are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
-iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies.
+iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
+once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
 
@@
 or large-scale disks, that encase the bulge and dominate the light at large radii). 
-\emph{Paper I} will present the dataset used here to investigate the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
+\emph{Paper I} will present the dataset used here, 
+%to investigate the $M_{\rm BH} - L_{\rm gal}$, $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
 give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
@@
 which are given here as lower limits. 
-Following GS13, we assumed a constant uncertainty of $0.25\rm~mag$ for all galaxy magnitudes.
+Following GS13, we assumed a fixed uncertainty ($0.25\rm~mag$) for $MAG_{\rm gal}$.
 
 \input{table_sample.tex}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
+\caption{Black hole mass against $3.6\rm~\mu m$ galaxy absolute magnitude. 
+Symbols are coded according to the galaxy morphological type: red circle = elliptical, red star = elliptical/lenticular, 
+red upward triangle = lenticular, blue downward triangle = lenticular/spiral, blue square = spiral, black diamond = merger. 
+Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
+The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
+with the red shaded area denoting its $1\sigma$ uncertainty. 
+Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. }
+\label{fig:mbhmaggal}
+\end{center}
+\end{figure}
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
-\caption{Black hole mass against $3.6\rm~\mu m$ galaxy absolute magnitude. 
-Symbols are coded as in Figure \ref{fig:mbhmagsph}.
-Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
-}
-\label{fig:mbhmaggal}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
 \includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
@@
 \centering
-\caption{Linear regression analysis. {\bf X0 is the average X of the subsample...}}
+\caption{Linear regression analysis of the $M_{\rm BH} - MAG_{\rm gal}$ diagram.}
 \begin{tabular}{llccccc}
-\hline
-\hline
-{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
-\hline 
+\tableline\tableline
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm gal} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+\tableline 
 \\
- & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid luminosity}} \\
- & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
+  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - \langle MAG_{\rm gal} \rangle)/{\rm mag}]$} \\ [0.5em]
+ All (62)               & BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
+                        & BCES $(X|Y)$   & $8.26 \pm 0.12$ & $-1.01 \pm 0.15$ & $-24.78$ & $-$ & $0.92$ \\
+                        & BCES Bisector  & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
+                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
+                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
+                        & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
+                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\
+                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\
+                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.15$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]
+
+ Early-type (E+S0) (45) & BCES $(Y|X)$   & $8.56 \pm 0.07$ & $-0.44 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
+                        & BCES $(X|Y)$   & $8.56 \pm 0.08$ & $-0.64 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
+                        & BCES Bisector  & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
+                        & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
+                        & mFITEXY $(X|Y)$  & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.07}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
+                        & mFITEXY Bisector & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
+                        & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\
+                        & {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\
+                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.10$ & $-24.88$ & $-$    & $0.47$ \\
+
+ Late-type (Sp) (17) & BCES $(Y|X)$      & $7.37 \pm 0.17$ & $-0.33 \pm 0.87$   & $-24.39$ & $-$ & $0.65$ \\
+                     & BCES $(X|Y)$      & $7.37 \pm 1.97$ & $-21.66 \pm 53.74$ & $-24.39$ & $-$ & $7.73$ \\                        
+                     & BCES Bisector     & $7.37 \pm 0.20$ & $-1.32 \pm 0.94$   & $-24.39$ & $-$ & $0.77$ \\                     
+                     & FITEXY $(Y|X)$    & $7.38^{+0.17}_{-0.18}$ & $-0.34^{+0.74}_{-0.80}$ & $-24.39$ & $0.63^{+0.19}_{-0.11}$ & $0.65$ \\                         
+                     & FITEXY $(X|Y)$    & $$ & $$ & $-24.39$ & $$ & $$ \\                         
+                     & FITEXY Bisector   & $$ & $$ & $-24.39$ & $-$    & $$ \\                  
+                     & {\tt linmix\_err} $(Y|X)$     & $$ & $$ & $-24.39$ & $$ & $$ \\             
+                     & {\tt linmix\_err} $(X|Y)$     & $$ & $$ & $-24.39$ & $$ & $$ \\             
+                     & {\tt linmix\_err} Bisector    & $$ & $$ & $-24.39$ & $-$    & $$ \\
+
+%All (62)               & BCES $(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
+%                       & BCES $(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
+%                       & BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
+%                       & FITEXY $(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
+%                       & FITEXY $(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
+%                       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
+%                       & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\
+%                       & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\
+%                       & {\tt linmix\_err} Bisector    & $$ & $$ & $$ & $-$    & $$ \\
+
+\tableline 
+\tableline
+\end{tabular}
+\label{tab:lreggal} 
+\end{table*}
+
+\begin{table*}
+\centering
+\caption{Linear regression analysis of the $M_{\rm BH} - MAG_{\rm sph}$ diagram.}
+\begin{tabular}{llccccc}
+\tableline
+\tableline
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+\tableline 
+\\
+ & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
 All (66)               & BCES $(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
@@
                        & BCES Bisector  & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
-                       & mFITEXY $(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
-                       & mFITEXY $(X|Y)$ & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.67$ \\
+                       & mFITEXY $(Y|X)$    & $8.17^{+0.06}_{-0.07}$ & $-0.43^{+0.03}_{-0.04}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
+                       & mFITEXY $(X|Y)$    & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.68$ \\
                        & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
@@
                        & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\
-                       & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]
+                       & {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.48 \pm 0.10$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]
 
-Core-S\'ersic (22) & BCES $(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\
-                   & BCES $(X|Y)$   & $9.1  \pm 0.1$  & $-0.6  \pm 0.1$  & $-25.73$ & $-$    & $0.61$ \\
-                   & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
-                   & mFITEXY $(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37^{+0.08}_{-0.06}$ & $0.42$ \\
-                   & mFITEXY $(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.67$ \\
-                   & mFITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
-                   & {\tt linmix\_err} $(Y|X)$  & $9.0 \pm 0.1$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\
-                   & {\tt linmix\_err} $(X|Y)$  & $9.0 \pm 0.2$ & $-0.7 \pm 0.3$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\
-                   & {\tt linmix\_err} Bisector    & $9.0 \pm 0.1$ & $-0.4 \pm 0.1$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]
+Core-S\'ersic (22) & BCES $(Y|X)$   & $9.06 \pm 0.09$ & $-0.32 \pm 0.11$  & $-25.73$ & $-$    & $0.42$ \\
+                   & BCES $(X|Y)$   & $9.06 \pm 0.12$ & $-0.65 \pm 0.12$  & $-25.73$ & $-$    & $0.61$ \\
+                   & BCES Bisector  & $9.06 \pm 0.10$ & $-0.47 \pm 0.08$  & $-25.73$ & $-$    & $0.48$ \\
+                   & mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.09}$ & $-0.26^{+0.08}_{-0.07}$ & $-25.73$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
+                   & mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $-0.72^{+0.17}_{-0.31}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.68$ \\
+                   & mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $-0.47^{+0.12}_{-0.17}$ & $-25.73$ & $-$    & $0.48$ \\
+                   & {\tt linmix\_err} $(Y|X)$  & $9.04 \pm 0.10$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\
+                   & {\tt linmix\_err} $(X|Y)$  & $9.03 \pm 0.17$ & $-0.69 \pm 0.27$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\
+                   & {\tt linmix\_err} Bisector & $9.04 \pm 0.14$ & $-0.44 \pm 0.16$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]
 
 S\'ersic (44) & BCES $(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
-              & BCES $(X|Y)$   & $7.7  \pm 0.1$  & $-0.9  \pm 0.2 $ & $-22.92$ & $-$    & $0.93$ \\
-              & BCES Bisector     & $7.7  \pm 0.1$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
-              & mFITEXY $(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54^{+0.09}_{-0.07}$ & $0.61$ \\
-              & mFITEXY $(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
-              & mFITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$     & $0.71$ \\
+              & BCES $(X|Y)$   & $7.71 \pm 0.14$ & $-0.86 \pm 0.16$ & $-22.92$ & $-$    & $0.93$ \\
+              & BCES Bisector  & $7.71 \pm 0.10$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
+              & mFITEXY $(Y|X)$   & $7.72^{+0.08}_{-0.09}$ & $-0.41^{+0.07}_{-0.08}$ & $-22.92$ & $0.54^{+0.08}_{-0.07}$ & $0.61$ \\
+              & mFITEXY $(X|Y)$   & $7.72^{+0.14}_{-0.13}$ & $-0.86^{+0.13}_{-0.19}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
+              & mFITEXY Bisector  & $7.72^{+0.11}_{-0.11}$ & $-0.61^{+0.10}_{-0.12}$ & $-22.92$ & $-$                    & $0.71$ \\
               & {\tt linmix\_err} $(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\
-              & {\tt linmix\_err} $(X|Y)$  & $7.7 \pm  0.1$ & $-0.9 \pm 0.2$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\
-              & {\tt linmix\_err} Bisector    & $7.7 \pm 0.1$ & $-0.6 \pm 0.1$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
+              & {\tt linmix\_err} $(X|Y)$  & $7.73 \pm 0.14$ & $-0.86 \pm 0.17$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\
+              & {\tt linmix\_err} Bisector & $7.73 \pm 0.12$ & $-0.62 \pm 0.15$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
 
@@
 %
+
 {\bf Early-type (E+S0)} (45) & BCES $(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
@@
 
-{\bf Late-type (Sp)} (17) & BCES $(Y|X)$    & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
-                          & BCES $(X|Y)$    & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
-                          & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{-1.1 \pm 0.3}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
-                          & mFITEXY $(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.55^{+0.15}_{-0.10}$ & $0.62$ \\
-                          & mFITEXY $(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.4}$ & $-22.33$ & $1.08^{+0.40}_{-0.24}$ & $1.50$ \\
-                          & mFITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
-                          & {\tt linmix\_err} $(Y|X)$  & $7.2 \pm 0.2$ & $-0.5 \pm 0.3$ & $-22.33$ & $0.64 \pm 0.16$ & $0.62$ \\
-                          & {\tt linmix\_err} $(X|Y)$  & $7.3 \pm 0.4$ & $-1.9 \pm 1.2$ & $-22.33$ & $1.3 \pm 0.9$ & $1.4$ \\
-                          & {\tt linmix\_err} Bisector    & $7.3 \pm 0.3$ & $-0.9 \pm 0.5$ & $-22.33$ & $-$    & $0.78$ \\
+{\bf Late-type (Sp)} (17) & BCES $(Y|X)$    & $7.18 \pm 0.16$ & $-0.79 \pm 0.43$ & $-22.33$ & $-$    & $0.70$ \\
+                          & BCES $(X|Y)$    & $7.18 \pm 0.29$ & $-1.71 \pm 0.71$ & $-22.33$ & $-$    & $1.26$ \\
+                          & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.20}$ & $\boldsymbol{-1.15 \pm 0.27}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
+                          & mFITEXY $(Y|X)$    & $7.20^{+0.15}_{-0.15}$ & $-0.53^{+0.22}_{-0.24}$ & $-22.33$ & $0.55^{+0.15}_{-0.10}$ & $0.63$ \\
+                          & mFITEXY $(X|Y)$    & $7.38^{+0.54}_{-0.36}$ & $-2.02^{+0.71}_{-2.13}$ & $-22.33$ & $1.09^{+0.41}_{-0.24}$ & $1.50$ \\
+                          & mFITEXY Bisector   & $7.26^{+0.40}_{-0.28}$ & $-1.03^{+0.33}_{-0.52}$ & $-22.33$ & $-$    & $0.82$ \\
+                          & {\tt linmix\_err} $(Y|X)$  & $7.24 \pm 0.19$ & $-0.46 \pm 0.32$ & $-22.33$ & $0.63 \pm 0.16$ & $0.62$ \\
+                          & {\tt linmix\_err} $(X|Y)$  & $7.34 \pm 0.43$ & $-1.93 \pm 1.30$ & $-22.33$ & $1.31 \pm 0.97$ & $1.43$ \\
+                          & {\tt linmix\_err} Bisector & $7.27 \pm 0.33$ & $-0.96 \pm 0.50$ & $-22.33$ & $-$    & $0.78$ \\
 
-\hline 
-\hline
+\tableline 
+\tableline
 \end{tabular}
-\label{tab:lreg} 
+\label{tab:lregsph} 
 \end{table*}
@@
 \centering
-\caption{Linear regression analysis. {\bf X0 is the average X of the subsample...}}
+\caption{Linear regression analysis of the $M_{\rm BH} - M_{\rm *,sph}$ diagram.}
 \begin{tabular}{llccccc}
-\hline
-\hline
-{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
-\hline 
+\tableline
+\tableline
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle M_{\rm *,sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+\tableline 
 \\
- & \multicolumn{6}{l}{\emph{Black hole mass -- galaxy luminosity}} \\
-  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
- All (62)		& BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
- 			& BCES $(X|Y)$   & $8.3 \pm 0.1$   & $-1.0 \pm 0.1$   & $-24.78$ & $-$ & $0.92$ \\
- 			& BCES Bisector     & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
- 			& mFITEXY $(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.05}$ & $0.64$ \\
- 			& mFITEXY $(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$	& $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
- 			& mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
- 			& {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.08$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\
- 			& {\tt linmix\_err} $(X|Y)$  & $8.3 \pm 0.1$ & $-1.0 \pm 0.1$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\
- 			& {\tt linmix\_err} Bisector    & $8.3 \pm 0.1$ & $-0.7 \pm 0.1$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]
+  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - \langle M_{\rm *,sph} \rangle)/{\rm M_\odot}]$} \\ [0.5em]
+{\bf Early-type (E+S0)} (45)  & BCES $(Y|X)$       & $8.56 \pm 0.07$ & $0.85 \pm 0.12$ & $10.81$ & $-$ & $0.48$ \\
+                              & BCES $(X|Y)$       & $8.56 \pm 0.09$ & $1.27 \pm 0.13$ & $10.81$ & $-$ & $0.59$ \\
+                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.04 \pm 0.10}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
+                              & mFITEXY $(Y|X)$     & $8.56^{+0.06}_{-0.07}$ & $0.83^{+0.11}_{-0.11}$ & $10.81$ & $0.42^{+0.07}_{-0.05}$ & $0.48$ \\
+                              & mFITEXY $(X|Y)$     & $8.54^{+0.08}_{-0.09}$ & $1.32^{+0.18}_{-0.15}$ & $10.81$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
+                              & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.05^{+0.14}_{-0.12}$ & $10.81$ & $-$                    & $0.51$ \\
+                              & {\tt linmix\_err} $(Y|X)$     & $8.55 \pm 0.07$ & $0.82 \pm 0.12$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\
+                              & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $1.29 \pm 0.17$ & $10.81$ & $0.54 \pm 0.11$ & $0.59$ \\
+                              & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $1.03 \pm 0.19$ & $10.81$ & $-$    & $0.51$ \\ [0.5em]
 
- Early-type (E+S0) (45) & BCES $(Y|X)$   & $8.56 \pm 0.06$ & $-0.43 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
- 			& BCES $(X|Y)$   & $8.56 \pm 0.08$ & $-0.63 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
- 			& BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
- 			& mFITEXY $(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
- 			& mFITEXY $(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
- 			& mFITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
- 			& {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\
- 			& {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\
- 			& {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.5 \pm 0.1$ & $-24.88$ & $-$    & $0.47$ \\
+{\bf Late-type (Sp)} (17)    & BCES $(Y|X)$    & $7.18 \pm 0.17$ & $1.95 \pm 1.52$ & $10.05$ & $-$ & $0.74$ \\ 
+                             & BCES $(X|Y)$    & $7.18 \pm 0.39$ & $5.89 \pm 3.40$ & $10.05$ & $-$ & $1.70$ \\
+                             & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.21}$ & $\boldsymbol{3.00 \pm 1.30}$ & $\boldsymbol{10.05}$ & $-$ & $\boldsymbol{0.94}$ \\
+                             & mFITEXY $(Y|X)$     & $7.20^{+0.15}_{-0.16}$ & $1.22^{+0.70}_{-0.62}$  & $10.05$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
+                             & mFITEXY $(X|Y)$     & $7.44^{+1.45}_{-0.52}$ & $7.14^{+26.31}_{-3.01}$ & $10.05$ & $1.49^{+0.56}_{-0.36}$ & $2.08$ \\
+                             & mFITEXY Bisector    & $7.24^{+1.04}_{-0.39}$ & $2.28^{+1.67}_{-1.01}$  & $10.05$ & $-$    & $0.79$ \\
+                             & {\tt linmix\_err} $(Y|X)$  & $7.23 \pm 0.19$ & $0.96 \pm 0.96$ & $10.05$ & $0.67 \pm 0.16$ & $0.65$ \\
+                             & {\tt linmix\_err} $(X|Y)$  & $7.42 \pm 0.64$ & $6.96 \pm 6.73$ & $10.05$ & $1.83 \pm 1.86$ & $2.03$ \\
+                             & {\tt linmix\_err} Bisector & $7.26 \pm 0.47$ & $1.94 \pm 216.38$ & $10.05$ & $-$    & $0.74$ \\
 
-%All (62)               & BCES $(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
-%                       & BCES $(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
-%                       & BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
-%                       & FITEXY $(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
-%                       & FITEXY $(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
-%                       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
-%                       & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\
-%                       & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\
-%                       & {\tt linmix\_err} Bisector    & $$ & $$ & $$ & $-$    & $$ \\
-
-\hline 
-\\
- & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid stellar mass}} \\
-  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - X_0)/{\rm M_\odot}]$} \\ [0.5em]
-{\bf Early-type (E+S0)} (45)  & BCES $(Y|X)$    & $8.56 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $-$ & $0.48$ \\
-                              & BCES $(X|Y)$    & $8.56 \pm 0.08$ & $1.3 \pm 0.1$ & $10.81$ & $-$ & $0.59$ \\
-                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.0 \pm 0.1}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
-                              & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.07}$ & $0.8^{+0.1}_{-0.1}$ & $10.81$ & $0.42^{+0.06}_{-0.05}$ & $0.48$ \\
-                              & mFITEXY $(X|Y)$  & $8.54^{+0.09}_{-0.08}$ & $1.3^{+0.2}_{-0.1}$ & $10.81$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
-                              & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.0^{+0.1}_{-0.1}$ & $10.81$ & $-$                    & $0.51$ \\
-                              & {\tt linmix\_err} $(Y|X)$  & $8.55 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\
-                              & {\tt linmix\_err} $(X|Y)$  & $8.55 \pm 0.09$ & $1.3 \pm 0.2$ & $10.81$ & $0.54 \pm 0.11$ & $0.59$ \\
-                              & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $1.0 \pm 0.2$ & $10.81$ & $-$    & $0.51$ \\ [0.5em]
-
-{\bf Late-type (Sp)} (17)    & BCES $(Y|X)$    & $7.2 \pm 0.2$ & $1.9 \pm 1.5$ & $10.05$ & $-$ & $0.74$ \\ 
-                             & BCES $(X|Y)$    & $7.2 \pm 0.4$ & $5.9 \pm 3.4$ & $10.05$ & $-$ & $1.70$ \\
-                             & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{3.0 \pm 1.3}$ & $\boldsymbol{10.05}$ & $-$ & $\boldsymbol{0.94}$ \\
-                             & mFITEXY $(Y|X)$  & $7.2^{+0.1}_{-0.2}$ & $1.2^{+0.7}_{-0.6}$ & $10.05$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
-                             & mFITEXY $(X|Y)$  & $7.4^{+1.5}_{-0.5}$ & $7.1^{+26.3}_{-3.0}$ & $10.05$ & $1.49^{+0.57}_{-0.35}$ & $2.08$ \\
-                             & mFITEXY Bisector    & $7.2^{+1.0}_{-0.4}$ & $2.3^{+1.7}_{-1.0}$ & $10.05$ & $-$    & $0.79$ \\
-                             & {\tt linmix\_err} $(Y|X)$  & $7.2 \pm 0.2$ & $0.9 \pm 0.9$ & $10.05$ & $0.67 \pm 0.16$ & $0.65$ \\
-                             & \textcolor{red}{{\tt linmix\_err} $(X|Y)$}  & $7.4 \pm 0.6$ & $7.0 \pm 6.6$ & $10.05$ & $1.83 \pm 1.82$ & $2.04$ \\
-                             & \textcolor{red}{{\tt linmix\_err} Bisector}    & $7.3 \pm 0.5$ & $1.9 \pm 203.0$ & $10.05$ & $-$    & $0.74$ \\
-
-\hline 
-\hline
+\tableline 
+\tableline
 \end{tabular}
-\label{tab:lreg} 
+\label{tab:lregmass} 
+\tablecomments{cia}
 \end{table*}
@@
 \label{sec:anal}
-We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$, $M_{\rm BH} - M_{\rm *,sph}$ and $M_{\rm BH} - L_{\rm gal}$ diagrams 
+We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ (see Table \ref{tab:lreggal}), 
+$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}),
 using the BCES code from \cite{akritasbershady1996}. 
-We also repeated the analysis with the FITEXY routine \citep{press1992}, modified by \cite{tremaine2002}, 
+We also repeated the analysis with the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
 and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
-Although all these three linear regression routines account for the intrinsic scatter, 
-only the last two allow to quantify it.
+All these three linear regression routines account for the intrinsic scatter, 
+but only the last two allow to quantify it.
 %Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
@@
 %we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
-In Table \ref{tab:lreg}, we report the BCES, modified FITEXY and {\tt linmix\_err} linear regressions, both symmetrical and non-symmetrical, 
+We report linear regressions, both symmetrical and non-symmetrical, 
 for S\'ersic/core-S\'ersic galaxies and for different galaxy morphological types (elliptical/lenticular, spiral).
@@
 \label{sec:res}
+
+\subsection{Black hole mass -- galaxy luminosity}
+Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
+Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
+and thus are not included in the linear regression analysis. \\
+Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
+\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
+which they fit with a single power-law, have consistent intrinsic scatter.
+Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
+we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
+The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
+has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
+and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
+whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
+and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
+However, when considering only early-type galaxies, 
+we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
+%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
+%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
+Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
+smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
+we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
+(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
+On the other hand, the uncertainties associated to $L_{\rm sph}$ have been estimated 
+with an advanced method that takes into account the systematic errors related to the galaxy decomposition process. 
+We consider these uncertainties trustworthy and, therefore, we decided to vary only the errors associated to $L_{\rm gal}$.
+We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
+have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
+Because such error is larger than the typical error on $L_{\rm sph}$ used here
+-- and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically used in the literature --, 
+we come to the conclusion that our determination of the intrinsic scatter is reliable, 
+and that, for early-type galaxies, $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$.
+As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
+than performing accurate %galaxy decompositions to obtain bulge luminosities. 
+This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
+to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.
 
@@
 
-\subsection{Black hole mass -- galaxy luminosity}
-Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
-Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
-and thus are not included in the linear regression analysis. \\
-Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
-\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
-which they fit with a single power-law, have consistent intrinsic scatter.
-Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
-we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
-The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
-has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
-and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
-whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
-and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
-However, when considering only early-type galaxies, 
-we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
-%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
-%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
-Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
-smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
-we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
-(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
-On the other hand, the uncertainties associated to $L_{\rm sph}$ have been estimated 
-with an advanced method that takes into account the systematic errors related to the galaxy decomposition process. 
-We consider these uncertainties trustworthy and, therefore, we decided to vary only the errors associated to $L_{\rm gal}$.
-We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
-have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
-Because such error is larger than the typical error on $L_{\rm sph}$ used here
--- and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically used in the literature --, 
-we come to the conclusion that our determination of the intrinsic scatter is reliable, 
-and that, for early-type galaxies, $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$.
-As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
-than performing accurate %galaxy decompositions to obtain bulge luminosities. 
-This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
-to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.
-
 \subsection{Black hole mass -- spheroid stellar mass}

### 2015-04-29 python_codes/instruments/linear_regression/fitexy.py

@@ -29,13 +29,13 @@ def modfitexy(x,sigx,y,sigy,mode):
 	bprecision = binit_err/2
 	paramsprecision = min(aprecision,bprecision)
 	print '--------------------------'
-	print 'y = a + bx'
-	print 'Inital guess' 
-	print 'a =', ainit, '+-', ainit_err
-	print 'b =', binit, '+-', binit_err
-	print 'precision = ', paramsprecision
-	print '--------------------------'
-	print
+       #print 'y = a + bx'
+       #print 'Inital guess' 
+       #print 'a =', ainit, '+-', ainit_err
+       #print 'b =', binit, '+-', binit_err
+       #print 'precision = ', paramsprecision
+       #print '--------------------------'
+       #print
 	
 	
 	a, b, epsilon, chisqmin = get_ab(x,sigx,y,sigy,ainit,binit,paramsprecision,N,mode)
@@ -67,10 +67,10 @@ def modfitexy(x,sigx,y,sigy,mode):
 	
 	print 'y = a + bx'
 	print 'Mode fit:', mode
-	print 'a =', afit, '+', perr_afit, '-', merr_afit
-	print 'b =', bfit, '+', perr_bfit, '-', merr_bfit 
-	print 'epsilon =', epsilonfit, '+', perr_epsilonfit, '-', merr_epsilonfit 
-	print 'absolute scatter Delta =', absscat
+	print 'a =', "{0:.2f}".format(afit), '^{+', "{0:.2f}".format(perr_afit), '}_{-', "{0:.2f}".format(merr_afit), '}'
+	print 'b =', "{0:.2f}".format(bfit), '^{+', "{0:.2f}".format(perr_bfit), '}_{-', "{0:.2f}".format(merr_bfit), '}' 
+	print 'epsilon =', "{0:.2f}".format(epsilonfit), '^{+', "{0:.2f}".format(perr_epsilonfit), '}_{-', "{0:.2f}".format(merr_epsilonfit), '}' 
+	print 'absolute scatter Delta =', "{0:.2f}".format(absscat)
 	
 	return afit,merr_afit,perr_afit, bfit,merr_bfit,perr_bfit, epsilonfit,merr_epsilonfit,perr_epsilonfit, absscat					
 
@@ -198,9 +198,9 @@ def bisect_modfitexy(x,sigx,y,sigy):
 	print '--------------------------'
[…]

### 2015-04-29 python_codes/instruments/markers/markers.py

@@ -3,6 +3,8 @@ import matplotlib
 import matplotlib.pyplot as plt
 
 scatter_kwargs = {"zorder":100}
+scatter_kwargs2 = {"zorder":200}
+
 
 def spiral(ax, color, x0, y0, size):
 	t1 = np.arange(1,4,0.01)
@@ -16,10 +18,10 @@ def spiral(ax, color, x0, y0, size):
 	x = size*1.1*np.cos(t)
 	y = size*1*np.sin(t)
 	
-	ax.plot(10**(x0+x1),10**(y0+y1), color=color, lw=2, **scatter_kwargs)
-	ax.plot(10**(x0+x2),10**(y0+y2), color=color, lw=2, **scatter_kwargs)
-	ax.plot(10**(x0+x),10**(y0+y), color=color, lw=2, **scatter_kwargs)
-	ax.fill_between(10**(x0+x), 10**(y0+0), 10**(y0+y), edgecolor='', facecolor=color, **scatter_kwargs)
+	ax.plot(10**(x0+x1),10**(y0+y1), color=color, lw=2, **scatter_kwargs2)
+	ax.plot(10**(x0+x2),10**(y0+y2), color=color, lw=2, **scatter_kwargs2)
+	ax.plot(10**(x0+x),10**(y0+y), color=color, lw=2, **scatter_kwargs2)
+	ax.fill_between(10**(x0+x), 10**(y0+0), 10**(y0+y), edgecolor='', facecolor=color, **scatter_kwargs2)
 	
 	
 def lenticular(ax, color, x0, y0, size):

### 2015-04-29 python_codes/paper_figures/MbhMsph/figures.py

@@ -261,10 +261,10 @@ def mbh_vs_mass_sph_agn():
        #print 'y = A*(x-<x>) + B '
        #print '<x> =', np.average(log_mass_sph)
        #print
-       #print 'OLS(Y|X)    A =', "{0:.4f}".format(A[0]), '+-', "{0:.4f}".format(Aerr[0]), '   B = ', "{0:.4f}".format(B[0]), '+-', "{0:.4f}".format(Berr[0]), 'Delta =', "{0:.4f}".format(absscat_0)
-       #print 'OLS(X|Y)    A =', "{0:.4f}".format(A[1]), '+-', "{0:.4f}".format(Aerr[1]), '   B = ', "{0:.4f}".format(B[1]), '+-', "{0:.4f}".format(Berr[1]), 'Delta =', "{0:.4f}".format(absscat_1)
-       #print 'bisector    A =', "{0:.4f}".format(A[2]), '+-', "{0:.4f}".format(Aerr[2]), '   B = ', "{0:.4f}".format(B[2]), '+-', "{0:.4f}".format(Berr[2]), 'Delta =', "{0:.4f}".format(absscat_2)
-       ##print 'orthogonal  A =', "{0:.4f}".format(A[3]), '+-', "{0:.4f}".format(Aerr[3]), '   B = ', "{0:.4f}".format(B[3]), '+-', "{0:.4f}".format(Berr[3]), 'Delta =', "{0:.4f}".format(absscat_3)
+       #print 'OLS(Y|X)    A =', "{0:.2f}".format(A[0]), '\pm', "{0:.2f}".format(Aerr[0]), '   B = ', "{0:.2f}".format(B[0]), '\pm', "{0:.2f}".format(Berr[0]), 'Delta =', "{0:.2f}".format(absscat_0)
+       #print 'OLS(X|Y)    A =', "{0:.2f}".format(A[1]), '\pm', "{0:.2f}".format(Aerr[1]), '   B = ', "{0:.2f}".format(B[1]), '\pm', "{0:.2f}".format(Berr[1]), 'Delta =', "{0:.2f}".format(absscat_1)
+       #print 'bisector    A =', "{0:.2f}".format(A[2]), '\pm', "{0:.2f}".format(Aerr[2]), '   B = ', "{0:.2f}".format(B[2]), '\pm', "{0:.2f}".format(Berr[2]), 'Delta =', "{0:.2f}".format(absscat_2)
[…]

### 2015-04-30 papers/MbhMsph/mm.tex
thu

@@
 we decided to use individual, color-dependent mass-to-light ratios. \\
+For each galaxy, the total luminosity (or galaxy luminosity, $L_{\rm gal}$) is the sum of the luminosities of all its sub-components. 
+Due to the complexity of their modelling, 
+four galaxies (see Table \ref{tab:sample}, column 7) had their galaxy luminosities 
+underestimated\footnote{These four cases will be discussed in \emph{Paper I}.}, 
+which are given here as lower limits. 
+Following GS13, we assumed a fixed uncertainty ($0.25\rm~mag$) for $MAG_{\rm gal}$. \\
+The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/spiral; Sp = spiral; merger) 
+follows from the galaxy models presented in \emph{Paper I}. 
+Throughout the paper, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
+Galaxies classified as E/S0 are obviously included in the early-type bin, 
+whereas galaxies classified as S0/Sp or as mergers are included in neither the early- nor the late-type bin.\\
 The S\'ersic/core-S\'ersic classification presented in this work 
-comes from the compilation of \citet{savorgnangraham2014},
+comes from the compilation of \citet{savorgnangraham2015},
 who identified partially depleted cores according to the same criteria used by GS13.
@@
 or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. \\
-For each galaxy, the total luminosity (or galaxy luminosity, $L_{\rm gal}$) is the sum of the luminosities of all its sub-components. 
-Due to the complexity of their modelling, 
-four galaxies (see Table \ref{tab:sample}, column 7) had their galaxy luminosities 
-underestimated\footnote{These four cases will be discussed in \emph{Paper I}.}, 
-which are given here as lower limits. 
-Following GS13, we assumed a fixed uncertainty ($0.25\rm~mag$) for $MAG_{\rm gal}$.
 
 \input{table_sample.tex}
+
+\section{Analysis}
+\label{sec:anal}
+We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ (see Table \ref{tab:lreggal}), 
+$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}),
+using the BCES code from \cite{akritasbershady1996}. 
+We also repeated the analysis with the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
+and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
+All these three linear regression routines account for the intrinsic scatter, 
+but only the last two allow to quantify it.
+%Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
+%can give biased results (wrong slope) when the scatter is comparable to the range of the data},
+%we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
+We report linear regressions, both symmetrical and non-symmetrical, 
+for S\'ersic/core-S\'ersic galaxies and for different galaxy morphological types (elliptical/lenticular, spiral).
+Symmetrical regressions are meant to be compared with theoretical expectations, 
+whereas non-symmetrical $(Y|X)$ regressions -- 
+since they minimize the scatter in the vertical direction -- 
+can be used to predict black hole masses.
+
+\section{Results and discussion}
+\label{sec:res}
+
+\subsection{Black hole mass -- galaxy luminosity}
+Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
+Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
+and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
+Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
+\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
+which they fit with a single power-law, have consistent intrinsic scatter.
+Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
+we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
+The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
+has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
+and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
+whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
+and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
+However, when considering only early-type galaxies, 
+we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
+%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
+%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
+Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
+smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
+we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
+(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
+We decided to vary only the errors associated to $L_{\rm gal}$ 
+because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
+that takes into account the systematic errors related to the galaxy decomposition process. 
+We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
+have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
+Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
+and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
+we conclude that our determination of the intrinsic scatter is reliable, 
+and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
+As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
+than performing accurate galaxy decompositions to obtain bulge luminosities. 
+This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
+to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.
 
@@
 \includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
-\caption{Black hole mass against $3.6\rm~\mu m$ galaxy absolute magnitude. 
-Symbols are coded according to the galaxy morphological type: red circle = elliptical, red star = elliptical/lenticular, 
-red upward triangle = lenticular, blue downward triangle = lenticular/spiral, blue square = spiral, black diamond = merger. 
+\caption{Black hole mass plotted against $3.6\rm~\mu m$ galaxy absolute magnitude. 
+Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
+red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
 Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
-The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
+Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
+The red dashed line indicates the BCES bisector linear regression for 45 early-type galaxies (E+S0), 
 with the red shaded area denoting its $1\sigma$ uncertainty. 
-Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. }
+We were not able to obtain any meaningful linear regression for the late-type (Sp) galaxies. }
 \label{fig:mbhmaggal}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
-\caption{Black hole mass against $3.6\rm~\mu m$ spheroid absolute magnitude. 
-Symbols are coded according to the galaxy morphological type: red circle = elliptical, red star = elliptical/lenticular, 
-red upward triangle = lenticular, blue downward triangle = lenticular/spiral, blue square = spiral, black diamond = merger. 
-Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
-The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
-with the red shaded area denoting its $1\sigma$ uncertainty. 
-The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
-with the blue shaded area denoting its $1\sigma$ uncertainty. 
-The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for core-S\'ersic and S\'ersic spheroids, respectively.}
-\label{fig:mbhmagsph}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
-\caption{Black hole mass versus $3.6\rm~\mu m$ spheroid absolute magnitude. 
-Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
-Bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges, are marked with an empty square. 
-The black solid line shows the BCES bisector linear regression for spheroids with $n_{\rm sph} \geq 2$. }
-\label{fig:pseudob}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{images/inset_psb.pdf}
-\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$. 
-The vertical dashed line corresponds to $n_{\rm sph} = 2$.
-The horizontal solid line is equivalent to a zero vertical offset.
-Bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
-from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
-\label{fig:pseudob}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
-\caption{Black hole mass against spheroid stellar mass. 
-Symbols are coded according to the galaxy morphological type (red = E, orange = E/S0 and S0, blue = S0/Sp and Sp, black = merger).
-The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
-with the red shaded area denoting its $1\sigma$ uncertainty. 
-The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
-with the blue shaded area denoting its $1\sigma$ uncertainty. }
-\label{fig:mbhmasssph}
 \end{center}
@@
 
- Late-type (Sp) (17) & BCES $(Y|X)$      & $7.37 \pm 0.17$ & $-0.33 \pm 0.87$   & $-24.39$ & $-$ & $0.65$ \\
-                     & BCES $(X|Y)$      & $7.37 \pm 1.97$ & $-21.66 \pm 53.74$ & $-24.39$ & $-$ & $7.73$ \\                        
-                     & BCES Bisector     & $7.37 \pm 0.20$ & $-1.32 \pm 0.94$   & $-24.39$ & $-$ & $0.77$ \\                     
-                     & FITEXY $(Y|X)$    & $7.38^{+0.17}_{-0.18}$ & $-0.34^{+0.74}_{-0.80}$ & $-24.39$ & $0.63^{+0.19}_{-0.11}$ & $0.65$ \\                         
-                     & FITEXY $(X|Y)$    & $$ & $$ & $-24.39$ & $$ & $$ \\                         
-                     & FITEXY Bisector   & $$ & $$ & $-24.39$ & $-$    & $$ \\                  
-                     & {\tt linmix\_err} $(Y|X)$     & $$ & $$ & $-24.39$ & $$ & $$ \\             
-                     & {\tt linmix\_err} $(X|Y)$     & $$ & $$ & $-24.39$ & $$ & $$ \\             
-                     & {\tt linmix\_err} Bisector    & $$ & $$ & $-24.39$ & $-$    & $$ \\
+%Late-type (Sp) (13) & BCES $(Y|X)$      & $7.37 \pm 0.17$ & $-0.33 \pm 0.87$   & $-24.39$ & $-$ & $0.65$ \\
+%                    & BCES $(X|Y)$      & $7.37 \pm 1.97$ & $-21.66 \pm 53.74$ & $-24.39$ & $-$ & $7.73$ \\
+%                    & BCES Bisector     & $7.37 \pm 0.20$ & $-1.32 \pm 0.94$   & $-24.39$ & $-$ & $0.77$ \\
+%                    & FITEXY $(Y|X)$    & $7.38^{+0.17}_{-0.18}$ & $-0.34^{+0.74}_{-0.80}$ & $-24.39$ & $0.63^{+0.19}_{-0.11}$ & $0.65$ \\
+%                    & FITEXY $(X|Y)$    & $$ & $$ & $-24.39$ & $$ & $$ \\
+%                    & FITEXY Bisector   & $$ & $$ & $-24.39$ & $-$    & $$ \\
+%                    & {\tt linmix\_err} $(Y|X)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
+%                    & {\tt linmix\_err} $(X|Y)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
+%                    & {\tt linmix\_err} Bisector    & $$ & $$ & $-24.39$ & $-$    & $$ \\
 
@@
 \label{tab:lreggal} 
+\tablecomments{For each subsample, we indicate $\langle MAG_{\rm gal} \rangle$, its average value of galaxy magnitudes. 
+In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. 
+Four spiral galaxies had their luminosities underestimated and thus are not included in the linear regression analysis 
+(the sample of all galaxies contains 66-4=62 objects). 
+When considering all galaxies, irrespective of their morphological type, 
+the $M_{\rm BH} - L_{\rm gal}$ correlation is weaker than the $M_{\rm BH} - L_{\rm sph}$ correlation, in terms of intrinsic scatter. 
+However, when considering only early-type galaxies, the $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ correlations 
+have consistent intrinsic scatter. }
 \end{table*}
+
+\subsection{Black hole mass -- spheroid luminosity}
+We now come to the $M_{\rm BH} - L_{\rm sph}$ diagram, which is shown in Figure \ref{fig:mbhmagsph}, 
+and whose linear regression analysis is presented in Table \ref{tab:lregsph}. \\
+S\'ersic and core-S\'ersic spheroids have slopes consistent with each other (within their $1\sigma$ uncertainties), 
+in disagreement with the findings of GS13. 
+The slope that we obtained for core-S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.18 \pm 0.20}$) 
+is consistent with the slope reported by GS13 in the $K_s$-band ($M_{\rm BH} \propto L_{\rm sph}^{1.10 \pm 0.20}$). 
+Instead, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.53 \pm 0.20}$) 
+is shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.73 \pm 0.55}$). 
+Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{which galaxies?} from the classification used here, 
+the main cause of such inconsistency is that the bulge-to-total ratios obtained from our galaxy decompositions 
+are different from those assumed by GS13 to convert galaxy luminosities into bulge luminosities.
+Our bulge-to-total ratios for low-luminosity S\'ersic spheroids ($MAG_{\rm sph} \gtrsim -22 \rm~mag$) 
+are smaller than those used by GS13. 
+The host galaxies of such bulges are late-type, spiral galaxies, 
+which typically present a complex morphology (bars, double bars, embedded disks, nuclear components, etc).
+Our sophisticated galaxy models account for the extra components, 
+while the bulge-to-total ratios of GS13 were derived from simple literature bulge/disk decompositions 
+which overestimated the bulge luminosity.
+This results in our bulge magnitudes being on average $\sim$$1\rm~mag$ fainter than in GS13, after accounting for the different wavelength of the data.
+On the other side, our bulge-to-total ratios for high-luminosity S\'ersic spheroids ($MAG_{\rm sph} \lesssim -24 \rm~mag$) 
+are on average larger than those adopted by GS13.
+In this case, the host systems are early-type galaxies that feature intermediate-scale disks\footnote{explain}.
+Past bulge/disk decompositions failed to correctly identify the extent of such disks and treated them as large-scale disks, 
+thus underestimating the bulge luminosity.
+The magnitudes that we obtained for such spheroids are on average $\sim$$1\rm~mag$ brighter than in GS13. 
+These two effects explain the shallower slope that we obtained for the S\'ersic spheroids. \\
+We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 
+which is expected for consistency with other scaling relations 
+(a single power-law $M_{\rm BH} - \sigma$ correlation and a double power-law $L_{\rm sph} - \sigma$ correlation) -- 
+cannot be attributed to the division between the two populations of S\'ersic and core-S\'ersic spheroids.
+We now test a new hypothesis, that is to say the change in slope is to be ascribed to the different formation mechanisms of early- and late-type galaxies. 
+If this hypothesis is correct, 
+the spheroids of early-type galaxies will follow $M_{\rm BH} \propto L_{\rm sph}^{\sim 1}$, 
+whereas the spheroids of late-type galaxies will have $M_{\rm BH} \propto L_{\rm sph}^{\sim 2.5}$.
+First, we checked that elliptical and lenticular galaxies, taken separately, have slopes consistent with each other, 
+and thus, taken together, they define a single \emph{red sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
+We then fit the bulges of early- and late-type galaxies with two separate log-linear regressions, 
+and obtained $M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ and $M_{\rm BH} \propto L_{\rm sph}^{2.75 \pm 0.75}$ respectively, 
+in excellent agreement with the theoretical expectations of our hypothesis. \\
+%{\bf vertical scatter along the early type sequence is constant? if 2 overmassive bhs removed, what happens?}
+We remark on the unsuitability of the Pearson's and Spearman's correlation coefficients because 
+they do not take into account the error bars on our data.
+Similarly, a visual inspection of the plotted data requires us to take into account the error bars 
+when judging-by-eye the strength of a correlation. 
+We have therefore relied on the quantitative regression analysis rather than subjective approaches.
+
+\subsection{Pseudo- versus classical bulges}
+korm. review \\
+Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
+formed through violent processes, such as hierarchical clustering via minor mergers, 
+and pseudo-bulges, thought to be disk-like, rotation-supported systems, 
+built from secular evolution processes, such as instabilities of their surrounding disk or bar. 
+Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
+For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
+and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
+thus rotation is not a definitive signature of a pseudobulge. 
+Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
+macarthur2009,dosanjosdasilva2013,seidel2015}). 
+In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
+S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{fisherdrory2010}), 
+although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
+\cite{grahamworley2008} observed no such bimodality in the bulge S\'ersic indices. 
+While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
+being disky components that formed from their surrounding exponential disks 
+(e.g.~\citealt{bardeen1975,hohl1975,combessanders1981,combes1990,pfennigerfriedli1991}), 
+it has been shown that mergers can create bulges with $n_{\rm sph}<2$
+(e.g.~\citealt{elichemoral2011,scannapieco2011,querejeta2015}), 
+just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
+are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994}). \\
+\cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
+with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
+traced by classical bulges. 
+In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
+are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).} 
+in the $M_{\rm BH} - L_{\rm sph}$ diagram.
+Our aim is to check whether $n_{\rm sph}<2$ bulges 
+are offset to lower black hole masses from the correlation defined by $n_{\rm sph}>2$ bulges. 
+To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
+and we compute the vertical offset of all bulges from the regression. 
+In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
+From a visual inspection, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
+\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
+Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
+red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
+Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
+The red dashed line indicates the BCES bisector linear regression for the bulges of 45 early-type (E+S0) galaxies, 
+with the red shaded area denoting its $1\sigma$ uncertainty. 
+The blue solid line shows the BCES bisector linear regression for the bulges of 17 late-type (Sp) galaxies, 
+with the blue shaded area denoting its $1\sigma$ uncertainty. 
+The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for core-S\'ersic and S\'ersic spheroids, respectively.}
+\label{fig:mbhmagsph}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
+\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
+Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
+Bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges, are marked with an empty square. 
+The black solid line shows the BCES bisector linear regression for spheroids with $n_{\rm sph} \geq 2$. }
+\label{fig:pseudob}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/inset_psb.pdf}
+\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$, 
+plotted against $n_{\rm sph}$. 
+The vertical dashed line corresponds to $n_{\rm sph} = 2$.
+The horizontal solid line is equivalent to a zero vertical offset.
+Bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
+from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
+\label{fig:pseudob}
+\end{center}
+\end{figure}
 
@@
 \label{tab:lregsph} 
+\tablecomments{For each subsample, we indicate $\langle MAG_{\rm sph} \rangle$, its average value of spheroid magnitudes. 
+In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. 
+Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2). }
 \end{table*}
+
+\subsection{Black hole mass -- spheroid stellar mass}
+Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}. 
+The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$,
+as expected from a dry-merging formation scenario,
+and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
+On the other hand, the bulges of spiral galaxies trace a steeper \emph{blue sequence}, 
+whose slope is less well constrained due to the small size of the subsample and, more importantly, 
+to the small range in $M_{\rm *,sph}$ that the subsample spans.
+For the bulges of spiral galaxies, the BCES code returns a bisector linear regression $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
+while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) slope of $2.3^{+1.7}_{-1.0}$.
+The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
+{\bf which code do we trust more in this case? BCES or FITEXY? is it a quadratic or a cubic growth? }
+
+\cite{grahamscott2015} collected a sample of $\sim$170 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
+bulges hosting Active Galactic Nuclei (AGNs) with 
+black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
+and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by predominantly inactive S\'ersic bulges. 
+%Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
+We anticipate here that the correlation traced by our bulges of spiral galaxies 
+may track the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
+That is, the AGNs appear to be the low-mass continuation of the \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
+We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
+(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.\\
+{\bf cite Anne's paper}\\
+{\bf AL: however we analyze the agns in another paper, blah blah}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
+\caption{Black hole mass plotted against spheroid stellar mass. 
+Symbols are coded according to the galaxy morphological type.
+The red dashed line indicates the BCES bisector linear regression for early-type galaxies (E+S0), 
+with the red shaded area denoting its $1\sigma$ uncertainty. 
+The blue solid line shows the BCES bisector linear regression for late-type (Sp) galaxies, 
+with the blue shaded area denoting its $1\sigma$ uncertainty. {\bf key result}}
+\label{fig:mbhmasssph}
+\end{center}
+\end{figure}
 
@@
 \label{tab:lregmass} 
-\tablecomments{cia}
+\tablecomments{For each subsample, we indicate $\langle M_{\rm *,sph} \rangle$, its average value of spheroid stellar masses. 
+In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. }
 \end{table*}
-
-\section{Analysis}
-\label{sec:anal}
-We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ (see Table \ref{tab:lreggal}), 
-$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}),
-using the BCES code from \cite{akritasbershady1996}. 
-We also repeated the analysis with the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
-and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
-All these three linear regression routines account for the intrinsic scatter, 
-but only the last two allow to quantify it.
-%Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
-%can give biased results (wrong slope) when the scatter is comparable to the range of the data},
-%we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
-We report linear regressions, both symmetrical and non-symmetrical, 
-for S\'ersic/core-S\'ersic galaxies and for different galaxy morphological types (elliptical/lenticular, spiral).
-Symmetrical regressions are meant to be compared with theoretical expectations, 
-whereas non-symmetrical $(Y|X)$ regressions -- 
-since they minimize the scatter in the vertical direction -- 
-can be used to predict black hole masses.
-
-\section{Results and discussion}
-\label{sec:res}
-
-\subsection{Black hole mass -- galaxy luminosity}
-Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
-Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
-and thus are not included in the linear regression analysis. \\
-Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
-\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
-which they fit with a single power-law, have consistent intrinsic scatter.
-Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
-we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
-The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
-has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
-and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
-whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
-and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
-However, when considering only early-type galaxies, 
-we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
-%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
-%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
-Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
-smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
-we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
-(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
-On the other hand, the uncertainties associated to $L_{\rm sph}$ have been estimated 
-with an advanced method that takes into account the systematic errors related to the galaxy decomposition process. 
-We consider these uncertainties trustworthy and, therefore, we decided to vary only the errors associated to $L_{\rm gal}$.
-We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
-have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
-Because such error is larger than the typical error on $L_{\rm sph}$ used here
--- and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically used in the literature --, 
-we come to the conclusion that our determination of the intrinsic scatter is reliable, 
-and that, for early-type galaxies, $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$.
-As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
-than performing accurate %galaxy decompositions to obtain bulge luminosities. 
-This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
-to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.
-
-\subsection{Black hole mass -- spheroid luminosity}
-We show the $M_{\rm BH} - L_{\rm sph}$ diagram in Figure \ref{fig:mbhmagsph}. \\
-S\'ersic and core-S\'ersic spheroids have slopes consistent with each other (within their $1\sigma$ uncertainties), 
-in disagreement with the findings of GS13. 
-The slope that we obtained for core-S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.2 \pm 0.2}$) 
-is consistent with the slope reported by GS13 in the $K_s$-band ($M_{\rm BH} \propto L_{\rm sph}^{1.1 \pm 0.2}$). 
-Instead, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.5 \pm 0.2}$) 
-is significantly shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.7 \pm 0.5}$). 
-Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{which galaxies?} from the classification used here, 
-the main cause of such inconsistency is that the bulge-to-total ratios obtained from our galaxy decompositions 
-are different from those assumed by GS13 to convert galaxy luminosities into bulge luminosities.
-Our bulge-to-total ratios for low-luminosity S\'ersic spheroids ($MAG_{\rm sph} \gtrsim -22 \rm~mag$) 
-are smaller than those used by GS13. 
-The host galaxies of such bulges are late-type, spiral galaxies, 
-which typically present a complex morphology (bars, double bars, embedded disks, nuclear components, etc).
-Our sophisticated galaxy models account for the extra components, 
-while the bulge-to-total ratios of GS13 were derived from simple bulge/disk decompositions 
-which overestimated the bulge luminosity.
-This results in our bulge magnitudes being on average $\sim$$1\rm~mag$ fainter.
-On the other side, our bulge-to-total ratios for high-luminosity S\'ersic spheroids ($MAG_{\rm sph} \lesssim -24 \rm~mag$) 
-are on average larger than those adopted by GS13.
-In this case, the host systems are early-type elliptical/lenticular galaxies that feature intermediate-scale disks\footnote{explain}.
-Past bulge/disk decompositions failed to correctly identify the extent of such disks and treated them as large-scale disks, 
-thus underestimating the bulge luminosity.
-The magnitudes that we obtained for such spheroids are on average $\sim$$1\rm~mag$ brighter. \\
-We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 
-which is expected for consistency with other scaling relations 
-(a single power-law $M_{\rm BH} - \sigma$ correlation and a double power-law $L_{\rm sph} - \sigma$ correlation) -- 
-cannot be attributed to the division between the two populations of S\'ersic and core-S\'ersic spheroids.
-We now test a new hypothesis, that is to say the change in slope is to be ascribed to the different formation mechanisms of early- and late-type galaxies. 
-If this hypothesis is correct, 
-the spheroids of early-type (elliptical and lenticular) galaxies will follow $M_{\rm BH} \propto L_{\rm sph}^{\sim 1}$, 
-whereas the spheroids of late-type (spiral) galaxies will have $M_{\rm BH} \propto L_{\rm sph}^{\sim 2.5}$.
-First, we checked that elliptical and lenticular galaxies, taken separately, have slopes consistent with each other, 
-and thus, taken together, they define a single \emph{red sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
-We then fit the bulges of early- and late-type galaxies with two separate log-linear regressions, 
-and obtained $M_{\rm BH} \propto L_{\rm sph}^{1 \pm 0.1}$ and $M_{\rm BH} \propto L_{\rm sph}^{2.75 \pm 0.75}$ respectively, 
-in excellent agreement with the theoretical expectations of our hypothesis.
-%{\bf vertical scatter along the early type sequence is constant? if 2 overmassive bhs removed, what happens?}
-{\bf AL, can you pls write this: 
-Remember also Ewan's remark about the unsuitability of the Pearson and Spearman correlation coefficients because 
-they do not take into account the error bars on our data - 
-so don't include those simple coefficients.  
-Actually, it would be worth pointing out to readers that a visual inspection of the plotted data requires 
-the viewer to take into account the error bars when judging-by-eye the strength of a correlation. 
-Maybe then mention in the following sentence that this is why the correlation coefficients are not applicable here. }
-
-\subsection{Pseudo- versus classical bulges}
-Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
-formed through violent processes, such as hierarchical clustering via minor mergers, 
-and pseudo-bulges, thought to be disk-like, rotation-supported systems, 
-built from secular evolution processes, such as instabilities of their surrounding disk or bar. 
-Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
-For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
-and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
-thus rotation is not a definitive signature of a pseudobulge. 
-Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
-macarthur2009,dosanjosdasilva2013,seidel2015}). 
-In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
-S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{fisherdrory2010}), 
-although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
-\cite{grahamworley2008} observed no such bimodality in the bulge S\'ersic indices. 
-While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
-being disky components that formed from their surrounding exponential disks 
-(e.g.~\citealt{bardeen1975,hohl1975,combessanders1981,combes1990,pfennigerfriedli1991}), 
-it has been shown that mergers can create bulges with $n_{\rm sph}<2$
-(e.g.~\citealt{elichemoral2011,scannapieco2011,querejeta2015}), 
-just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
-are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994}). \\
-\cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
-with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
-traced by classical bulges. 
-In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
-are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).} 
-in the $M_{\rm BH} - L_{\rm sph}$ diagram.
-Our aim is to check whether $n_{\rm sph}<2$ bulges 
-are offset to lower black hole masses from the correlation defined by $n_{\rm sph}>2$ bulges. 
-To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
-and we compute the vertical offset of all bulges from the regression. 
-In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
-From a visual inspection, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.
-
-\subsection{Black hole mass -- spheroid stellar mass}
-Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}. 
-The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$,
-as expected from a dry-merging formation scenario,
-and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
-On the other hand, the bulges of spiral galaxies trace a steeper \emph{blue sequence}, 
-whose slope is not well constrained due to the small size of the subsample and, more importantly, 
-to the small range in $M_{\rm *,sph}$ that the subsample spans.
-For the bulges of spiral galaxies, the BCES code returns a bisector linear regression $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
-while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) slope of $2.3^{+1.7}_{-1.0}$.
-The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
-{\bf which code do we trust more in this case? BCES or FITEXY? is it a quadratic or a cubic growth? }
-
-\cite{grahamscott2015} collected a sample of $\sim$170 low-redshift ($z \lesssim 0.1$) bulges hosting Active Galactic Nuclei (AGNs) with 
-black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
-and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by predominantly inactive S\'ersic bulges. 
-Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
-we anticipate here that the correlation traced by our bulges of spiral galaxies 
-tracks the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram, 
-i.e. the AGNs appears to be the low-mass continuation of the \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
-We also note that the majority of our spiral galaxies hosts an AGN\footnote{According to the nuclear classification reported on NED 
-(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.\\
-{\bf cite Anne's paper}\\
-{\bf AL: however we analyze the agns in another paper, blah blah}
 

### 2015-04-30 python_codes/paper_figures/MbhMsph/figures.py

@@ -625,13 +625,13 @@ def mbh_vs_mass_sph():
 		markers.elliptical(ax, 'red', np.log10(x0), np.log10(y0), 0.08)
 	
  	for x0,y0 in zip(mass_sph[simplemorphtype=='E/S0'], mbh[simplemorphtype=='E/S0']):
-		markers.lenticular(ax, 'darkorange', np.log10(x0), np.log10(y0), 0.08)
+		markers.lenticular(ax, 'red', np.log10(x0), np.log10(y0), 0.08)
        
 	for x0,y0 in zip(mass_sph[simplemorphtype=='S0'], mbh[simplemorphtype=='S0']):
 		markers.lenticular(ax, 'darkorange', np.log10(x0), np.log10(y0), 0.08)
 	
         for x0,y0 in zip(mass_sph[simplemorphtype=='S0/Sp'], mbh[simplemorphtype=='S0/Sp']):
-		markers.spiral(ax, 'blue', np.log10(x0), np.log10(y0), 0.04)
+		markers.spiral(ax, 'darkorange', np.log10(x0), np.log10(y0), 0.04)
 			
         for x0,y0 in zip(mass_sph[simplemorphtype=='Sp'], mbh[simplemorphtype=='Sp']):
 		markers.spiral(ax, 'blue', np.log10(x0), np.log10(y0), 0.04)
@@ -725,20 +725,21 @@ def mbh_vs_mass_sph():
 				
 	ax.fill_between(10**(logxx+np.average(log_mass_sph[morph_core=='Sp_0'])), 10**yy_lo, 10**yy_up, alpha=0.1, facecolor='b')
 	
+	# legend
+	markers.elliptical(ax, 'red', 8.85, 10.9, 0.08)
+	ax.text(10**9.1, 10**10.75, 'E')
+	markers.lenticular(ax, 'red', 8.85, 10.45, 0.08)
+	ax.text(10**9.1, 10**10.3, 'E/S0')
+	markers.lenticular(ax, 'darkorange', 8.85, 10., 0.08)
+	ax.text(10**9.1, 10**9.85, 'S0')
+	markers.spiral(ax, 'darkorange', 9.8, 10.9, 0.04)
+	ax.text(10**10.05, 10**10.75, 'S0/Sp')
+	markers.spiral(ax, 'blue', 9.8, 10.45, 0.04)
+	ax.text(10**10.05, 10**10.3, 'Sp')
[…]

### 2015-05-01 papers/MbhMsph/mm.tex
friday climb

@@
 
-\title{Supermassive black holes and host bulges affairs -- \\ II. The red and the blue sequences in the mass -- mass diagram.}
+\title{Supermassive black hole and host bulge affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.}
 
@@
 indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
-We conclude that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{x \pm x}$, a less steep sequence than previously reported; 
+We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
 ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
@@
 we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
-The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
+The $M_{\rm BH} - L_{\rm sph}$ log-correlation for all galaxies, irrespective of their morphological type, 
 has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
 and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
-whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
+whereas the $M_{\rm BH} - L_{\rm gal}$ log-correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
 and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
 However, when considering only early-type galaxies, 
-we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
+we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ log-relations have the same level of intrinsic scatter. 
 %($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
@@
 that takes into account the systematic errors related to the galaxy decomposition process. 
-We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
+We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ log-relations for early-type galaxies 
 have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
@@
 is shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.73 \pm 0.55}$). 
-Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{which galaxies?} from the classification used here, 
+Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{The classification has changed for the galaxies 
+NGC 1316, NGC 1332 and NGC 3998.} from the classification used here, 
 the main cause of such inconsistency is that the bulge-to-total ratios obtained from our galaxy decompositions 
@@
 are on average larger than those adopted by GS13.
-In this case, the host systems are early-type galaxies that feature intermediate-scale disks\footnote{explain}.
+In this case, the host systems are early-type galaxies that feature intermediate-scale disks\footnote{Intermediate-scale disks are 
+disks of stars fully embedded in the spheroidal component of their galaxy. 
+They are typical of ``disky'' elliptical galaxies (e.g.~NGC 3377), 
+but they can also be found in other types of host galaxies.
+They can be considered an intermediate class between nuclear disks, with sizes $\sim$$10-100\rm~pc$, %%
+and large-scale disks, that encase the bulge and dominate the light at large radii.}. 
 Past bulge/disk decompositions failed to correctly identify the extent of such disks and treated them as large-scale disks, 
@@
 These two effects explain the shallower slope that we obtained for the S\'ersic spheroids. \\
-We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 
+We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ log-correlation -- 
 which is expected for consistency with other scaling relations 
@@
 \subsection{Pseudo- versus classical bulges}
-korm. review \\
 Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
@@
 In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
-S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{fisherdrory2010}), 
+S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{sani2011,beifiori2012}), 
 although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
@@
 In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
-From a visual inspection, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.
+Among the 23 bulges with $n_{\rm sph}<2$, 12 have positive vertical offset and 11 have negative vertical offset. 
+\cite{kormendy2015review} provides a list of many pseudo-bulges classification criteria, including the divide at $n_{\rm sph}=2$, 
+and cautions that each individual criterion has a failure rate of 0-25\% \citep{fisherdrory2015}. 
+If this is true, we should have that no less than 75\% of $n_{\rm sph}<2$ bulges have negative vertical offset. 
+What we observe, instead, is that there are the same number of $n_{\rm sph}<2$ bulges lying above and below 
+the correlation defined by $n_{\rm sph}>2$ bulges\footnote{One 
+reaches the same conclusion when using the vertical offset from the correlation defined by bulges with $n_{\rm sph}>3$. 
+In this case, there are 13 and 10 bulges with $n_{\rm sph}<2$ that lie above and below, respectively, the correlation of $n_{\rm sph}>3$ bulges.}, 
+and that the amplitude of their offset is the same ($\lesssim 1.5\rm~dex$).
+That is, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.
 
@@
 The horizontal solid line is equivalent to a zero vertical offset.
-Bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
+Among bulges with $n_{\rm sph}<2$, 12 have positive vertical offset and 11 have negative vertical offset.
+Hence, bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
 from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
@@
 \subsection{Black hole mass -- spheroid stellar mass}
-Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}. 
-The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$,
-as expected from a dry-merging formation scenario,
+Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
+and its linear regression analysis in Table \ref{tab:lregmass}. 
+The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
+consistent with a dry-merging formation scenario,
 and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
@@
 to the small range in $M_{\rm *,sph}$ that the subsample spans. 
-For the bulges of spiral galaxies, the BCES code returns a bisector linear regression $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
-while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) slope of $2.3^{+1.7}_{-1.0}$.
+More data would be welcome to better constrain the slope of this \emph{blue sequence}.
+For the bulges of spiral galaxies, the BCES code returns a log-linear relation with slope $3.00 \pm 1.30$, 
+while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) 
+slope $2.28^{+1.67}_{-1.01}$.
 The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies.
-{\bf which code do we trust more in this case? BCES or FITEXY? is it a quadratic or a cubic growth? }
 
@@
 black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
-and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by predominantly inactive S\'ersic bulges. 
+and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges. 
 %Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
@@
 We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
-(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.\\
-{\bf cite Anne's paper}\\
-{\bf AL: however we analyze the agns in another paper, blah blah}
+(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.
+This topic will be investigated in Graham et al. (2015, \emph{in preparation}) with a dedicated careful analysis. \\
 
@@
 Symbols are coded according to the galaxy morphological type.
-The red dashed line indicates the BCES bisector linear regression for early-type galaxies (E+S0), 
+The red dashed line indicates the BCES bisector linear regression for the bulges of early-type galaxies (E+S0), 
 with the red shaded area denoting its $1\sigma$ uncertainty. 
-The blue solid line shows the BCES bisector linear regression for late-type (Sp) galaxies, 
-with the blue shaded area denoting its $1\sigma$ uncertainty. {\bf key result}}
+The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
+a near-linear relation consistent with a dry-merging formation scenario.
+The blue solid line shows the BCES bisector linear regression for the bulges of late-type (Sp) galaxies, 
+with the blue shaded area denoting its $1\sigma$ uncertainty. 
+The bulges of late-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
+indicating that gas-rich processes feed the black hole more efficiently (``quadratically'' or ``cubically'') than the host bulge. }
 \label{fig:mbhmasssph}
@@
   & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - \langle M_{\rm *,sph} \rangle)/{\rm M_\odot}]$} \\ [0.5em]
+ Core-S\'ersic (22)     & BCES $(Y|X)$      & $9.06 \pm 0.09$ & $0.86 \pm 0.28$ & $11.28$ & $-$ & $0.42$ \\
+ 			& BCES $(X|Y)$      & $9.06 \pm 0.12$ & $1.70 \pm 0.32$ & $11.28$ & $-$ & $0.61$ \\
+ 			& BCES Bisector     & $9.06 \pm 0.10$ & $1.19 \pm 0.23$ & $11.28$ & $-$ & $0.47$ \\
+ 			& FITEXY $(Y|X)$    & $9.06^{+0.08}_{-0.08}$ & $0.68^{+0.21}_{-0.20}$ & $11.28$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
+ 			& FITEXY $(X|Y)$    & $9.03^{+0.15}_{-0.16}$ & $1.90^{+0.85}_{-0.46}$ & $11.28$ & $0.62^{+0.13}_{-0.10}$ & $0.68$ \\
+ 			& FITEXY Bisector   & $9.05^{+0.12}_{-0.13}$ & $1.12^{+0.35}_{-0.27}$ & $11.28$ & $-$                    & $0.46$ \\
+ 			& {\tt linmix\_err} $(Y|X)$     & $9.04 \pm 0.10$ & $0.64 \pm 0.25$ & $11.28$ & $0.40 \pm 0.09$ & $0.42$ \\
+ 			& {\tt linmix\_err} $(X|Y)$     & $9.03 \pm 0.17$ & $1.80 \pm 0.70$ & $11.28$ & $0.67 \pm 0.30$ & $0.65$ \\
+ 			& {\tt linmix\_err} Bisector	& $9.04 \pm 0.14$ & $1.06 \pm 0.35$ & $11.28$ & $-$	& $0.45$ \\
+
+ S\'ersic (44)		& BCES $(Y|X)$      & $7.71 \pm 0.09$ & $0.95 \pm 0.21$ & $10.25$ & $-$ & $0.64$ \\
+ 			& BCES $(X|Y)$      & $7.71 \pm 0.16$ & $2.52 \pm 0.54$ & $10.25$ & $-$ & $1.11$ \\
+ 			& BCES Bisector     & $7.71 \pm 0.11$ & $1.48 \pm 0.20$ & $10.25$ & $-$ & $0.74$ \\
+ 			& FITEXY $(Y|X)$    & $7.72^{+0.10}_{-0.09}$ & $0.96^{+0.21}_{-0.21}$ & $10.25$ & $0.58^{+0.09}_{-0.07}$ & $0.64$ \\
+ 			& FITEXY $(X|Y)$    & $7.72^{+0.16}_{-0.16}$ & $2.49^{+0.69}_{-0.45}$ & $10.25$ & $0.93^{+0.15}_{-0.13}$ & $1.10$ \\
+ 			& FITEXY Bisector   & $7.72^{+0.13}_{-0.13}$ & $1.49^{+0.33}_{-0.28}$ & $10.25$ & $-$    & $0.74$ \\
+ 			& {\tt linmix\_err} $(Y|X)$     & $7.73 \pm 0.10$ & $0.98 \pm 0.24$ & $10.25$ & $0.59 \pm 0.08$ & $0.65$ \\
+ 			& {\tt linmix\_err} $(X|Y)$     & $7.73 \pm 0.17$ & $2.48 \pm 0.59$ & $10.25$ & $0.95 \pm 0.27$ & $1.10$ \\
+ 			& {\tt linmix\_err} Bisector	& $7.73 \pm 0.14$ & $1.49 \pm 0.57$ & $10.25$ & $-$	& $0.74$ \\
+
 {\bf Early-type (E+S0)} (45)  & BCES $(Y|X)$       & $8.56 \pm 0.07$ & $0.85 \pm 0.12$ & $10.81$ & $-$ & $0.48$ \\
@@
                              & mFITEXY $(X|Y)$     & $7.44^{+1.45}_{-0.52}$ & $7.14^{+26.31}_{-3.01}$ & $10.05$ & $1.49^{+0.56}_{-0.36}$ & $2.08$ \\
-                             & mFITEXY Bisector    & $7.24^{+1.04}_{-0.39}$ & $2.28^{+1.67}_{-1.01}$  & $10.05$ & $-$    & $0.79$ \\
+                             & {\bf mFITEXY Bisector}    & $\boldsymbol{7.24^{+1.04}_{-0.39}}$ & $\boldsymbol{2.28^{+1.67}_{-1.01}}$  & $\boldsymbol{10.05}$ & $-$    & $\boldsymbol{0.79}$ \\
                              & {\tt linmix\_err} $(Y|X)$  & $7.23 \pm 0.19$ & $0.96 \pm 0.96$ & $10.05$ & $0.67 \pm 0.16$ & $0.65$ \\
@@
 %ngc0524 outlier, n1332 non outlier
-to be written
+to be re-written
+
+\begin{itemize}
+\item The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
+consistent with a dry-merging formation scenario,
+and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
+On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
+with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
+indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
+\item S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{x \pm x}$, a less steep sequence than previously reported; 
+\item bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
+are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
+\item $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
+once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
+\end{itemize}
 

### 2015-05-03 papers/MbhMsph/mm.tex
s

@@
 Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
-and were derived from our state-of-the-art multicomponent galaxy decompositions 
+and were derived from our state-of-the-art {\bf many-component} galaxy decompositions 
 that, for the first time, were checked to be consistent with the galaxy kinematics. 
@@
 see \citealt{graham2015bulges} for an extensive review about the early discovery and successive improvements of these correlations)
-used similar galaxy samples, which remained dominated by high-mass, early-type objects having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 
+used similar galaxy samples, which remained dominated by high-mass, early-type systems having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 
 and recovered a near-linear relation. 
@@
 (among which only 4 were classified as spiral galaxies), 
-and reported a slope below unity for their $M_{\rm BH} - M_{\rm sph}$ relation. 
+and reported a slope below unity for their $M_{\rm BH} - L_{\rm sph}$ relation. 
 They also claimed that the black hole mass correlates equally well with the total galaxy luminosity 
 as it does with the bulge luminosity. \\
-The $M_{\rm BH} - L_{\rm sph}$ relation can be predicted from other two correlations involving the bulge velocity dispersion, $\sigma$.
+The $M_{\rm BH} - L_{\rm sph}$ relation can be predicted from other two correlations that involve 
+the bulge stellar velocity dispersion, $\sigma$.
 The first of these two is the $M_{\rm BH} - \sigma$ relation \citep{ferraresemerritt2000,gebhardt2000},
-which can be described by a single power-law ($M_{\rm BH} \propto \sigma^5$) 
-over the range in velocity dispersion $70-350~\rm km~s^{-1}$ (e.g.~\citealt{graham2011,mcconnell2011,grahamscott2013}).
+which can be described with a single power-law ($M_{\rm BH} \propto \sigma^5$) 
+over a wide range in velocity dispersion ($70-350~\rm km~s^{-1}$, e.g.~\citealt{graham2011,mcconnell2011,grahamscott2013}).
 The second is the $L_{\rm sph} - \sigma$ relation, 
@@
 core-S\'ersic and S\'ersic spheroids (e.g. \citealt{grahamguzman2003}).},
-and attributed the change in slope (from log-quadratic to log-linear) to their different formation mechanisms. 
+and attributed the change in slope (from quadratic to linear) to their different formation mechanisms. 
 In this scenario, core-S\'ersic spheroids are built in additive dry merger events, 
@@
 in which the mass of the black hole increases more rapidly than the mass of its host spheroid ($M_{\rm BH} \propto L_{\rm sph}^{2.5}$). 
-\citeauthor{grahamscott2013} (\citeyear{grahamscott2013}, hereafter GS13) and \citeauthor{scott2013} (\citeyear{scott2013}, hereafter S+13) 
+\citeauthor{grahamscott2013} (\citeyear{grahamscott2013}, hereafter GS13) and \citeauthor{scott2013} (\citeyear{scott2013}) 
 presented double power-law linear regressions 
-for S\'ersic/core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
-(spheroid stellar mass) diagrams, respectively, probing down to $M_{\rm BH} \approx 10^6\rm~M_\odot$. 
+for S\'ersic and core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
+(spheroid stellar mass) diagrams, probing down to $M_{\rm BH} \approx 10^6\rm~M_\odot$. 
 To obtain their dust-corrected \emph{bulge} magnitudes, they did not perform bulge/disc decompositions, 
@@
 their large sample size allowed them to obtain a reasonably ensemble average correction.}. 
-However, this mean statistical correction was obtained from the results of non-modern bulge/disk decompositions, 
-which did not include extra components. 
+However, this mean statistical correction was obtained from the results of non-modern bulge/disk decompositions. 
 It should also be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
@@
 However, \cite{grahamscott2013} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
-are not randomly offset from the high-mass, near-linear correlation, 
+are not randomly offset from such near-linear correlation, 
 but follow the two times steeper relation traced by the S\'ersic spheroids. 
@@
 give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
-discuss how we estimated the uncertainties\footnote{By comparing, for our galaxies, the measurements of the bulge magnitude 
-obtained by different authors with those obtained by us, we estimated the uncertainties on the bulge magnitudes 
+discuss how we estimated the uncertainties\footnote{By comparing, for each of our galaxies, the measurements of the bulge magnitude 
+obtained by different authors with that obtained by us, we estimated the uncertainties on the bulge magnitudes 
 with a method that takes into account systematic errors. 
@@
 We report linear regressions, both symmetrical and non-symmetrical, 
-for S\'ersic/core-S\'ersic galaxies and for different galaxy morphological types (elliptical/lenticular, spiral).
+for S\'ersic/core-S\'ersic and for early/late-type galaxies.
 Symmetrical regressions are meant to be compared with theoretical expectations, 
 whereas non-symmetrical $(Y|X)$ regressions -- 
-since they minimize the scatter in the vertical direction -- 
+since they minimize the scatter in the $\log M_{\rm BH}$ direction -- 
 can be used to predict black hole masses.
@@
 we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
-The $M_{\rm BH} - L_{\rm sph}$ log-correlation for all galaxies, irrespective of their morphological type, 
-has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
+The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
+has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
 and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
-whereas the $M_{\rm BH} - L_{\rm gal}$ log-correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
+whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
 and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
 However, when considering only early-type galaxies, 
-we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ log-relations have the same level of intrinsic scatter. 
+we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
 %($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
 %against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
-Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
+Because the value of the intrinsic scatter depends on the amplitude of the uncertainties associated to the luminosities\footnote{The 
 smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
@@
 that takes into account the systematic errors related to the galaxy decomposition process. 
-We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ log-relations for early-type galaxies 
+We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
 have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
@@
 The slope that we obtained for core-S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.18 \pm 0.20}$) 
-is consistent with the slope reported by GS13 in the $K_s$-band ($M_{\rm BH} \propto L_{\rm sph}^{1.10 \pm 0.20}$). 
+is consistent with the slope reported by GS13 in the $K_s$-band for the same population ($M_{\rm BH} \propto L_{\rm sph}^{1.10 \pm 0.20}$). 
 Instead, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.53 \pm 0.20}$) 
@@
 These two effects explain the shallower slope that we obtained for the S\'ersic spheroids. \\
-We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ log-correlation -- 
+We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 
 which is expected for consistency with other scaling relations 
@@
 traced by classical bulges. 
-In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
-are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).} 
+In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic index 
+is taken from our one-dimensional fit of the galaxy's major-axis surface brightness profile (\emph{Paper I}).} 
 in the $M_{\rm BH} - L_{\rm sph}$ diagram.
@@
 and cautions that each individual criterion has a failure rate of 0-25\% \citep{fisherdrory2015}. 
-If this is true, we should have that no less than 75\% of $n_{\rm sph}<2$ bulges have negative vertical offset. 
+If this is true, we should have that no less than 75\% of $n_{\rm sph}<2$ bulges display negative vertical offset. 
 What we observe, instead, is that there are the same number of $n_{\rm sph}<2$ bulges lying above and below 
@@
 reaches the same conclusion when using the vertical offset from the correlation defined by bulges with $n_{\rm sph}>3$. 
-In this case, there are 13 and 10 bulges with $n_{\rm sph}<2$ that lie above and below, respectively, the correlation of $n_{\rm sph}>3$ bulges.}, 
+In this case, there are 13 and 10 bulges with $n_{\rm sph}<2$ that lie above and below, respectively, the correlation  
+traced by $n_{\rm sph}>3$ bulges.}, 
 and that the amplitude of their offset is the same ($\lesssim 1.5\rm~dex$).
@@
 More data would be welcome to better constrain the slope of this \emph{blue sequence}.
-For the bulges of spiral galaxies, the BCES code returns a log-linear relation with slope $3.00 \pm 1.30$, 
+For the bulges of spiral galaxies, the BCES code returns a log-linear relation with slope $= 3.00 \pm 1.30$, 
 while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) 
-slope $2.28^{+1.67}_{-1.01}$.
+slope $= 2.28^{+1.67}_{-1.01}$.
 The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies.
@@
 black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
-and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges. 
+and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by S\'ersic bulges. 
 %Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 

### 2015-05-04 papers/MbhMsph/mm.tex
mon

@@
 \begin{abstract}
+{\bf limit of 250 words, currently there are 229 words, there's room for 21 words. 
+Things not mentioned: 1) the galaxy components (more appropriate for data paper?????), 
+2) $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, minimally affected by dust and star formation 
+3) updated linear regressions (symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
+for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp)}\\
 We present correlations between black hole mass, $M_{\rm BH}$, 
@@
 Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
-and were derived from our state-of-the-art {\bf many-component} galaxy decompositions 
+and were derived from our state-of-the-art {\bf ``many-component''} galaxy decompositions 
 that, for the first time, were checked to be consistent with the galaxy kinematics. 
-{\bf limit of 250 words, no room for mentioning the gaalxy components, more appropriate for data paper}
 Previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
@@
 with the red shaded area denoting its $1\sigma$ uncertainty. 
-We were not able to obtain any meaningful linear regression for the late-type (Sp) galaxies. }
+We were not able to obtain any meaningful linear regression for the late-type (Sp) galaxies. 
+$M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, 
+but not for all (early+late) galaxies. }
 \label{fig:mbhmaggal}
@@
 \cite{kormendy2015review} provides a list of many pseudo-bulges classification criteria, including the divide at $n_{\rm sph}=2$, 
-and cautions that each individual criterion has a failure rate of 0-25\% \citep{fisherdrory2015}. 
+and cautions that each individual criterion has a failure rate of 0-25\%. 
 If this is true, we should have that no less than 75\% of $n_{\rm sph}<2$ bulges display negative vertical offset. 
@@
 The horizontal solid line is equivalent to a zero vertical offset.
-Among bulges with $n_{\rm sph}<2$, 12 have positive vertical offset and 11 have negative vertical offset.
+Among the bulges with $n_{\rm sph}<2$, 12 have positive vertical offset and 11 have negative vertical offset.
 Hence, bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
@@
 The bulges of late-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
-indicating that gas-rich processes feed the black hole more efficiently (``quadratically'' or ``cubically'') than the host bulge. }
+indicating that gas-rich processes feed the black hole more efficiently (``quadratically'' or ``cubically'') than the host bulge. 
+We note that AGNs with $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ appear to roughly follow the blue line 
+(see Graham et al. 2015, \emph{in preparation}).}
 \label{fig:mbhmasssph}
@@
 \label{sec:concl}
-%ngc0524 outlier, n1332 non outlier
-to be re-written
-
-\begin{itemize}
-\item The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
-consistent with a dry-merging formation scenario,
-and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
-On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
-with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
-indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
-\item S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{x \pm x}$, a less steep sequence than previously reported; 
-\item bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
-are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
-\item $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
-once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
-\end{itemize}
+% %ngc0524 outlier, n1332 non outlier
+% to be re-written
+%
+% \begin{itemize}
+% \item The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
+% consistent with a dry-merging formation scenario,
+% and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
+% On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
+% with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
+% indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
+% \item S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{x \pm x}$, a less steep sequence than previously reported; 
+% \item bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
+% are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
+% \item $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
+% once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
+% \end{itemize}
 

### 2015-05-08 papers/MbhMsph/mm.tex
friday

@@
 \begin{abstract}
-{\bf limit of 250 words, currently there are 229 words, there's room for 21 words. 
-Things not mentioned: 1) the galaxy components (more appropriate for data paper?????), 
-2) $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, minimally affected by dust and star formation 
-3) updated linear regressions (symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
-for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp)}\\
-We present correlations between black hole mass, $M_{\rm BH}$, 
-and both the host galaxy's and spheroid's infrared luminosity, $L_{\rm gal}$ and $L_{\rm sph}$, 
-and the spheroid's stellar mass, $M_{\rm *,sph}$,
-built upon a high-quality data set.
-Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
-%Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
-%which is minimally affected by dust and star formation. 
-%These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
-%that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
-%and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
-Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
-and were derived from our state-of-the-art {\bf ``many-component''} galaxy decompositions 
-that, for the first time, were checked to be consistent with the galaxy kinematics. 
-Previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
+In our first paper, we performed a detailed (i.e.~bulges, disks, bars, spiral arms, rings, haloes, nuclei, cores, etc.) 
+decomposition of 66 galaxies, with directly measured black hole masses, 
+that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
+Our sample is the largest to date and, for the first time, the decompositions were checked to be consistent with the galaxy kinematics.
+Here we present correlations between the black hole mass, $M_{\rm BH}$, 
+and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
+and also stellar mass, $M_{\rm *,sph}$.
+Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
 Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
 and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
-%We provide updated linear regressions 
-%(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
-%for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
 The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
@@
 with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
-indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
+indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they grow. 
 We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
@@
 are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
-iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
-once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
+and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
+once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$. {\bf 241 words}
 
@@
 
-\keywords{keywords}
+\keywords{\bf keywords}
 
@@
 \label{sec:int}
-More than two and a half decades ago, 
-\cite{dressler1989} foresaw a ``rough scaling of black hole mass with the mass of the spheroidal component'', 
+A quarter of a century ago, 
+\cite{dressler1989} foresaw a ``rough scaling of black hole mass with the mass of the spheroidal component'' of galaxies, 
 as suggested by the sequence of five galaxies (M87, M104, M31, M32 and the Milky Way). 
-His ``rough scaling'' was a premature version of the nowadays popular correlation between black hole mass, $M_{\rm BH}$,  
+\cite{yee1992} also announced a relation between what was effectively black hole mass and galaxy mass for bright early-type galaxies.
+This ``rough scaling'' was a premature version of the nowadays popular correlation between black hole mass, $M_{\rm BH}$,  
 and host spheroid luminosity, $L_{\rm sph}$, and also host spheroid mass, $M_{\rm sph}$ 
-\citep{yee1992,kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}. 
+\citep{kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}. 
 These early studies were dominated by high-mass, early-type galaxies, 
 for which they reported a quasi-linear $M_{\rm BH} - M_{\rm sph}$ relation, 
-consistent with a dry-merging formation scenario. 
+consistent with a dry-merging formation scenario which would build and maintain a linear scaling. 
 Subsequent studies of the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm sph}$ diagrams 
-(\citealt{ferrareseford2005,lauer2007,graham2007,graham2008bar,gultelkin2009,sani2011,beifiori2012,erwingadotti2012,
+(\citealt{ferrareseford2005,lauer2007,graham2007,gultelkin2009,sani2011,beifiori2012,erwingadotti2012,
 vika2012,vandenbosch2012,mcconnellma2013,kormendyho2013,rusli2013}; 
 see \citealt{graham2015bulges} for an extensive review about the early discovery and successive improvements of these correlations)
-used similar galaxy samples, which remained dominated by high-mass, early-type systems having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 
+continued to use galaxy samples dominated by high-mass, early-type systems having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 
 and recovered a near-linear relation. 
@@
 Some studies reported a slope steeper than one,  
-or noticed that low-mass spheroids were downwards offset from the relation traced by their high-mass counterparts 
+or noticed that low-mass spheroids were offset to the lower right of the relation traced by their high-mass counterparts 
 \citep{laor1998,wandel1999,laor2001,ryan2007}.
@@
 They also claimed that the black hole mass correlates equally well with the total galaxy luminosity 
-as it does with the bulge luminosity. \\
+as it does with the bulge luminosity. 
+Now we roughly double the sample. \\
 The $M_{\rm BH} - L_{\rm sph}$ relation can be predicted from other two correlations that involve 
@@
 The first of these two is the $M_{\rm BH} - \sigma$ relation \citep{ferraresemerritt2000,gebhardt2000},
-which can be described with a single power-law ($M_{\rm BH} \propto \sigma^5$) 
+which can be described with a single power-law ($M_{\rm BH} \propto \sigma^{5-6}$) 
 over a wide range in velocity dispersion ($70-350~\rm km~s^{-1}$, e.g.~\citealt{graham2011,mcconnell2011,grahamscott2013}).
@@
 which has long been known to be a ``double power-law'', 
-being $L_{\rm sph} \propto \sigma^5$ at the luminous end \citep{schechter1980,malumuthkrishner1981,vonderlinden2007,liu2008}, 
+with $L_{\rm sph} \propto \sigma^{5-6}$ at the luminous end \citep{schechter1980,malumuthkrishner1981,vonderlinden2007,lauer2007lumell,liu2008}, 
 and $L_{\rm sph} \propto \sigma^2$ at intermediate and faint luminosities 
@@
 corresponding to $\sigma \approx 200~\rm km~s^{-1}$. 
-That is, the $M_{\rm BH} - L_{\rm sph}$ relation should be better described by a ``broken'', rather than a single, power-law, 
-having $M_{\rm BH} \propto L_{\rm sph}^{2.5}$ at the low-luminosity end, 
+The $M_{\rm BH} - L_{\rm sph}$ relation should therefore be better described by a ``broken'', rather than a single, power-law, 
+with $M_{\rm BH} \propto L_{\rm sph}^{2.5}$ at the low-luminosity end, 
 and $M_{\rm BH} \propto L_{\rm sph}^1$ at the high-luminosity end.  
@@
 and erroneously recover a single log-linear relation. \\
-When \cite{graham2012bent} pointed out this overlooked inconsistency, 
+When \cite{graham2012bent} pointed out this overlooked inconsistency between these linear and bent relations, 
 he identified two different populations of galaxies, 
@@
 core-S\'ersic and S\'ersic spheroids (e.g. \citealt{grahamguzman2003}).},
-and attributed the change in slope (from quadratic to linear) to their different formation mechanisms. 
+and attributed the change in slope (from super-quadratic to linear) to their different formation mechanisms. 
 In this scenario, core-S\'ersic spheroids are built in additive dry merger events, 
@@
 whereas S\'ersic spheroids originate from gas-rich processes, 
-in which the mass of the black hole increases more rapidly than the mass of its host spheroid ($M_{\rm BH} \propto L_{\rm sph}^{2.5}$). 
+in which the mass of the black hole increases more rapidly than the mass of its host spheroid ($M_{\rm BH} \propto L_{\rm sph}^{2.5}$). \\
 \citeauthor{grahamscott2013} (\citeyear{grahamscott2013}, hereafter GS13) and \citeauthor{scott2013} (\citeyear{scott2013}) 
@@
 but instead they converted $B-$band and $K_S-$band observed, total \emph{galaxy} magnitudes 
-using a mean statistical correction based on each object's morphological type and disc 
+using a mean statistical bulge-to-total ratio based on each object's morphological type and disc 
 inclination\footnote{While this resulted in individual bulge magnitudes not being exactly correct, 
-their large sample size allowed them to obtain a reasonably ensemble average correction.}. 
-However, this mean statistical correction was obtained from the results of non-modern bulge/disk decompositions. 
+their large sample size allowed them to obtain a reasonable $M_{\rm BH} - L_{\rm sph}$ relation for the ensemble.}. 
+This mean statistical correction was obtained from the results of non-modern bulge/disk decompositions. 
 It should also be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
@@
 are not randomly offset from such near-linear correlation, 
-but follow the two times steeper relation traced by the S\'ersic spheroids. 
-Using data from \cite{jiang2011a}, \cite{grahamscott2015} showed that this appears to extend to spheroids with even lower black hole masses 
+but follow the steeper relation traced by the S\'ersic spheroids. 
+Using bulge/disk decomposition data from \cite{jiang2011a}, 
+\cite{grahamscott2015} derived the host spheroid masses 
+and showed that the steeper $M_{\rm BH} - M_{\rm *,sph}$ extends to these spheroids with even lower black hole masses 
 ($10^{5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 2 \times 10^{6}$), 
@@
 Here we investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
-using state-of-the-art galaxy decompositions (Savorgnan \& Graham 2015, \emph{in preparation}, hereafter \emph{Paper I}) 
+using state-of-the-art galaxy decompositions (Savorgnan \& Graham 2015, hereafter \emph{Paper I}) 
 for the largest sample of galaxies with directly measured black hole masses.
 Our galaxies are large and nearby, which allows us to perform accurate multicomponent decompositions 
-(instead of simple bulge/disk decompositions) without incurring in significant parameter degeneracies. 
+(instead of simple bulge/disk decompositions). 
 Our decompositions were obtained from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
-which is an excellent proxy for the stellar mass, superior to the $K-$band (\citealt{sheth2010} and references therein).
+which is an excellent proxy for the stellar mass, superior to the $K-$band (\citealt{sheth2010}, and references therein).
 Nine of our galaxies have $M_{\rm BH} \lesssim 10^7\rm~M_\odot$, 
-which allows us to accurately constrain the slope of the correlation at the low-mass end.
+which allows us to constrain the slope of the correlation at the low-mass end.
 In addition to this, our galaxy sample includes 17 spiral galaxies, 
-representing a notable improvement over the past studies dominated by early-type systems. 
-In a forthcoming paper, we will explore the relation between black hole mass and bulge dynamical mass, 
+representing a notable improvement over past studies dominated by early-type systems. 
+In a forthcoming paper, we will explore the relation between the black hole mass and the bulge dynamical mass, 
 $M_{\rm dyn,sph} \propto R_{\rm e} \sigma^2$, and address the issue of a black hole fundamental plane.
-This paper is structured as follows...
+{\bf This paper is structured as follows... }
 
@@
 consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
-(by GS13 or \citealt{rusli2013bhmassesDM}) at the time we started this project, 
-and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
-Bulge magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 
+(by GS13 or \citealt{rusli2013bhmassesDM}) at the time that we started this project, 
+and for which we were able to obtain useful spheroid parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
+Spheroid magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 
 bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
 Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
-to confirm the presence of rotationally supported components in most early-type galaxies, 
+to confirm the presence of rotationally supported disk components in most early-type galaxies, 
 and to identify their extent 
@@
 or large-scale disks, that encase the bulge and dominate the light at large radii). 
-\emph{Paper I} will present the dataset used here, 
+\emph{Paper I} presents the dataset used here, 
 %to investigate the $M_{\rm BH} - L_{\rm gal}$, $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
-give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
-discuss how we estimated the uncertainties\footnote{By comparing, for each of our galaxies, the measurements of the bulge magnitude 
-obtained by different authors with that obtained by us, we estimated the uncertainties on the bulge magnitudes 
-with a method that takes into account systematic errors. 
+including details about the data reduction process and the galaxy modelling technique that we developed. 
+It also discusses how we estimated the uncertainties\footnote{By comparing, for each of our galaxies, the measurements of the bulge magnitude 
+obtained by different authors with that obtained by us, we estimated the uncertainties on the bulge magnitudes, 
+in effect taking into account systematic errors. 
 Systematic errors include incorrect sky subtraction, inaccurate masking of contaminating sources, imprecise description of the PSF, 
@@
 or when describing a galaxy sub-component with an inadequate function), 
-the radial extent of the surface brightness profile and its sampling. 
-These factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters. 
+the radial extent of the surface brightness profile and one's sampling of this. 
+Most of these factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters. 
 In fact, when performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well spatially resolved -- galaxies, 
 errors are dominated by systematics rather than Poisson noise.} 
-on the bulge magnitudes, and illustrate the individual 66 galaxy decompositions. \\
-Bulge luminosities\footnote{Absolute luminosities were calculated 
-assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$ \citep{sani2011}.} 
-were first converted into stellar masses using a constant $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6} = 0.6$ \citep{meidt2014}.
-We then explored a more sophisticated way to compute mass-to-light ratios, 
+on the bulge magnitudes, and presents the individual 66 galaxy decompositions, 
+along with a comparison and discussion of past decompositions. \\
+Bulge luminosities\footnote{Following \cite{sani2011}, absolute luminosities were calculated 
+assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$.} 
+(Table \ref{tab:sample}) from \emph{Paper I} were converted into stellar masses 
+using a constant $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6} = 0.6$ \citep{meidt2014}.
+We additionally explored a more sophisticated way to compute mass-to-light ratios, 
 using the color-$\Gamma_{3.6}$ relation published by 
@@
 Individual $[3.6] - [4.5]$ colors\footnote{These are integrated $[3.6] - [4.5]$ colors, measured in a circular aperture 
-within one galaxy's effective radius.} were taken from 
+within each galaxy's effective radius.} were taken from 
 \citeauthor{peletier2012} (\citeyear{peletier2012}, column 8 of their Table 1) 
@@
 four galaxies (see Table \ref{tab:sample}, column 7) had their galaxy luminosities 
-underestimated\footnote{These four cases will be discussed in \emph{Paper I}.}, 
+underestimated\footnote{These four cases are discussed in \emph{Paper I}.}, 
 which are given here as lower limits. 
-Following GS13, we assumed a fixed uncertainty ($0.25\rm~mag$) for $MAG_{\rm gal}$. \\
-The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/spiral; Sp = spiral; merger) 
+Following GS13, we assumed a fixed uncertainty ($0.25\rm~mag$) for the absolute galaxy magnitude $MAG_{\rm gal}$. \\
+The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/spiral; Sp = spiral; and merger) 
 follows from the galaxy models presented in \emph{Paper I}. 
-Throughout the paper, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
-Galaxies classified as E/S0 are obviously included in the early-type bin, 
-whereas galaxies classified as S0/Sp or as mergers are included in neither the early- nor the late-type bin.\\
+Throughout this paper, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
+Two galaxies classified as E/S0 are obviously included in the early-type bin, 
+whereas two galaxies classified as S0/Sp or another two classified as mergers are included in neither the early- nor the late-type bin.\\
 The S\'ersic/core-S\'ersic classification presented in this work 
@@
 a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
-or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. \\
+or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. 
+Galaxies with velocity dispersions between these bands had high-resolution images available. \\
 
@@
 We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ (see Table \ref{tab:lreggal}), 
-$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}),
+$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}) data,
 using the BCES code from \cite{akritasbershady1996}. 
-We also repeated the analysis with the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
+We also repeated the analysis using both the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
 and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
-All these three linear regression routines account for the intrinsic scatter, 
-but only the last two allow to quantify it.
+All of these three linear regression routines account for the intrinsic scatter, 
+but only the last two allow one to quantify it.
 %Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
@@
 Symmetrical regressions are meant to be compared with theoretical expectations, 
-whereas non-symmetrical $(Y|X)$ regressions -- 
-since they minimize the scatter in the $\log M_{\rm BH}$ direction -- 
+whereas non-symmetrical direct ($M_{\rm BH}|X$) regressions -- 
+which minimize the scatter in the $\log(M_{\rm BH})$ direction -- 
 can be used to predict black hole masses.
@@
 \subsection{Black hole mass -- galaxy luminosity}
-Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
+The $M_{\rm BH} - L_{\rm gal}$ diagram is shown in Figure \ref{fig:mbhmaggal}.
 Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
 and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
-Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
-\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
+\cite{lasker2014anal} analyzed a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
+and claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
 which they fit with a single power-law, have consistent intrinsic scatter.
-Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
+Here, instead, thanks to our galaxy sample that includes 17 spiral galaxies, 
 we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
-The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
-has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
+Our $M_{\rm BH} - L_{\rm sph}$ relation for 66 galaxies, irrespective of their morphological type, 
+has an intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
 and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
-whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
+whereas our $M_{\rm BH} - L_{\rm gal}$ relation for 62 ($=66-4$) galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
 and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
 However, when considering only early-type galaxies, 
-we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
+we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. \\
 %($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
 %against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
-Because the value of the intrinsic scatter depends on the amplitude of the uncertainties associated to the luminosities\footnote{The 
+Because the value of the intrinsic scatter depends on the size of the uncertainties associated to the absolute magnitudes\footnote{The 
 smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
-we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
-(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
-We decided to vary only the errors associated to $L_{\rm gal}$ 
-because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
-that takes into account the systematic errors related to the galaxy decomposition process. 
+we tested the robustness of our last conclusion by increasing/decreasing the errors associated with $L_{\rm gal}$ 
+(we originally assumed $0.25\rm~mag$). 
+%We decided to vary only the errors associated to $L_{\rm gal}$ 
+%because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
+%that takes into account the systematic errors related to the galaxy decomposition process. 
 We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
@@
 and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
-As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
-than performing accurate galaxy decompositions to obtain bulge luminosities. 
-This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
-to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.
+%As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
+%than performing accurate galaxy decompositions to obtain bulge luminosities. 
+%This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
+%to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.
 
@@
 Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
-The red dashed line indicates the BCES bisector linear regression for 45 early-type galaxies (E+S0), 
+The red dashed line indicates the BCES bisector linear regression for the 45 early-type galaxies (E+S0), 
 with the red shaded area denoting its $1\sigma$ uncertainty. 
-We were not able to obtain any meaningful linear regression for the late-type (Sp) galaxies. 
+We were not able to obtain any meaningful linear regression for the 13 ($=17-4$) late-type (Sp) galaxies. 
 $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, 
@@
 \centering
-\caption{Linear regression analysis of the $M_{\rm BH} - MAG_{\rm gal}$ diagram.}
+\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ diagram.}
 \begin{tabular}{llccccc}
@@
 \subsection{Black hole mass -- spheroid luminosity}
-We now come to the $M_{\rm BH} - L_{\rm sph}$ diagram, which is shown in Figure \ref{fig:mbhmagsph}, 
-and whose linear regression analysis is presented in Table \ref{tab:lregsph}. \\
+The $M_{\rm BH} - L_{\rm sph}$ diagram is shown in Figure \ref{fig:mbhmagsph}, 
+and the linear regression analysis is presented in Table \ref{tab:lregsph}. \\
 S\'ersic and core-S\'ersic spheroids have slopes consistent with each other (within their $1\sigma$ uncertainties), 
@@
 is consistent with the slope reported by GS13 in the $K_s$-band for the same population ($M_{\rm BH} \propto L_{\rm sph}^{1.10 \pm 0.20}$). 
-Instead, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.53 \pm 0.20}$) 
-is shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.73 \pm 0.55}$). 
+However, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.53 \pm 0.20}$) 
+is notably shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.73 \pm 0.55}$). 
 Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{The classification has changed for the galaxies 
@@
 are different from those assumed by GS13 to convert galaxy luminosities into bulge luminosities.
-Our bulge-to-total ratios for low-luminosity S\'ersic spheroids ($MAG_{\rm sph} \gtrsim -22 \rm~mag$) 
+Our bulge-to-total ratios for low-luminosity S\'ersic spheroids ($3.6\rm~\mu m$ $MAG_{\rm sph} \gtrsim -22 \rm~mag$) 
 are smaller than those used by GS13. 
@@
 Our sophisticated galaxy models account for the extra components, 
-while the bulge-to-total ratios of GS13 were derived from simple literature bulge/disk decompositions 
+while the bulge-to-total ratios of GS13 were based on simple literature S\'ersic-bulge/exponential-disk decompositions 
 which overestimated the bulge luminosity.
 This results in our bulge magnitudes being on average $\sim$$1\rm~mag$ fainter than in GS13, after accounting for the different wavelength of the data.
-On the other side, our bulge-to-total ratios for high-luminosity S\'ersic spheroids ($MAG_{\rm sph} \lesssim -24 \rm~mag$) 
+At the same time, our bulge-to-total ratios for the high-luminosity S\'ersic spheroids ($3.6\rm~\mu m$ $MAG_{\rm sph} \lesssim -24 \rm~mag$) 
 are on average larger than those adopted by GS13.
-In this case, the host systems are early-type galaxies that feature intermediate-scale disks\footnote{Intermediate-scale disks are 
+In this regime, the host systems are early-type galaxies that feature intermediate-scale disks\footnote{Intermediate-scale disks are 
 disks of stars fully embedded in the spheroidal component of their galaxy. 
@@
 These two effects explain the shallower slope that we obtained for the S\'ersic spheroids. \\
-We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 
+We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ relation -- 
 which is expected for consistency with other scaling relations 
@@
 cannot be attributed to the division between the two populations of S\'ersic and core-S\'ersic spheroids.
-We now test a new hypothesis, that is to say the change in slope is to be ascribed to the different formation mechanisms of early- and late-type galaxies. 
+We now test a new hypothesis, where the change in slope is ascribed to the different formation mechanisms of early- and late-type galaxies. 
 If this hypothesis is correct, 
@@
 We then fit the bulges of early- and late-type galaxies with two separate log-linear regressions, 
-and obtained $M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ and $M_{\rm BH} \propto L_{\rm sph}^{2.75 \pm 0.75}$ respectively, 
+and obtained $M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$ respectively, 
 in excellent agreement with the theoretical expectations of our hypothesis. \\
 %{\bf vertical scatter along the early type sequence is constant? if 2 overmassive bhs removed, what happens?}
-We remark on the unsuitability of the Pearson's and Spearman's correlation coefficients because 
+We point out the unsuitability of Pearson's and Spearman's correlation coefficients because 
 they do not take into account the error bars on our data.
@@
 
-\subsection{Pseudo- versus classical bulges}
+\subsubsection{Pseudo- versus classical bulges}
 Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
@@
 and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
-thus rotation is not a definitive signature of a pseudobulge. 
+thus rotation is not a definitive signature of a pseudo-bulge. 
 Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
 macarthur2009,dosanjosdasilva2013,seidel2015}). 
-In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
-S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{sani2011,beifiori2012}), 
+In the recent literature, pseudo- and classical bulges have frequently been divided at the 
+S\'ersic index $n_{\rm sph}=2$ (e.g.~\citealt{sani2011,beifiori2012}), 
 although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
-\cite{grahamworley2008} observed no such bimodality in the bulge S\'ersic indices. 
+\cite{grahamworley2008} observed no bimodality in the bulge S\'ersic indices about $n_{\rm sph}=2$ or any other value. 
 While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
@@
 just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
-are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994}). \\
+are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994,jerjen2000}). 
+The use of the S\'ersic index to identify pseudo-bulges is thus a dangerous practice. \\
 \cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
 with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
-traced by classical bulges. 
-In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic index 
-is taken from our one-dimensional fit of the galaxy's major-axis surface brightness profile (\emph{Paper I}).} 
+traced by their (classical) bulges with $n_{\rm sph}>2$. 
+In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
+are taken from our galaxy decompositions (\emph{Paper I}).} 
 in the $M_{\rm BH} - L_{\rm sph}$ diagram.
-Our aim is to check whether $n_{\rm sph}<2$ bulges 
-are offset to lower black hole masses from the correlation defined by $n_{\rm sph}>2$ bulges. 
+Our aim is to check whether bulges with $n_{\rm sph}<2$ 
+are offset to lower black hole masses from the correlation defined by bulges with $n_{\rm sph}>2$. 
 To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
 and we compute the vertical offset of all bulges from the regression. 
-In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
-Among the 23 bulges with $n_{\rm sph}<2$, 12 have positive vertical offset and 11 have negative vertical offset. 
+In Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
+Among the 23 bulges with $n_{\rm sph}<2$, 12 have a positive vertical offset and 11 have a negative vertical offset. 
 \cite{kormendy2015review} provides a list of many pseudo-bulges classification criteria, including the divide at $n_{\rm sph}=2$, 
 and cautions that each individual criterion has a failure rate of 0-25\%. 
-If this is true, we should have that no less than 75\% of $n_{\rm sph}<2$ bulges display negative vertical offset. 
-What we observe, instead, is that there are the same number of $n_{\rm sph}<2$ bulges lying above and below 
-the correlation defined by $n_{\rm sph}>2$ bulges\footnote{One 
-reaches the same conclusion when using the vertical offset from the correlation defined by bulges with $n_{\rm sph}>3$. 
-In this case, there are 13 and 10 bulges with $n_{\rm sph}<2$ that lie above and below, respectively, the correlation  
-traced by $n_{\rm sph}>3$ bulges.}, 
+If this is true, we should have that no less than 75\% of bulges with $n_{\rm sph}<2$ display a negative vertical offset\footnote{One 
+reaches the same conclusion when using the vertical offset from the correlation defined by bulges with $n_{\rm sph}>3$ or even $n_{\rm sph}>4$. 
+There are 13 and 10 bulges with $n_{\rm sph}<2$ that lie above and below, respectively, the correlation traced by bulges with $n_{\rm sph}>3$. 
+Similarly, there are 15 and 8 bulges with $n_{\rm sph}<2$ that lie above and below, respectively, the correlation traced by bulges with $n_{\rm sph}>4$.}. 
+What we observe, instead, is that there are the same number of bulges with $n_{\rm sph}<2$ lying above and below 
+the correlation defined by bulges with $n_{\rm sph}>2$, 
 and that the amplitude of their offset is the same ($\lesssim 1.5\rm~dex$).
@@
 Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
-The red dashed line indicates the BCES bisector linear regression for the bulges of 45 early-type (E+S0) galaxies, 
+The red dashed line indicates the BCES bisector linear regression for the bulges of the 45 early-type (E+S0) galaxies, 
 with the red shaded area denoting its $1\sigma$ uncertainty. 
-The blue solid line shows the BCES bisector linear regression for the bulges of 17 late-type (Sp) galaxies, 
+The blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
 with the blue shaded area denoting its $1\sigma$ uncertainty. 
-The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for core-S\'ersic and S\'ersic spheroids, respectively.}
+The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for the core-S\'ersic and S\'ersic spheroids, respectively.}
 \label{fig:mbhmagsph}
@@
 Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
-Bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges, are marked with an empty square. 
-The black solid line shows the BCES bisector linear regression for spheroids with $n_{\rm sph} \geq 2$. }
+Bulges with $n_{\rm sph}<2$, claimed by some to be pseudo-bulges, are marked with a square. 
+The black solid line shows the BCES bisector linear regression for the spheroids that have $n_{\rm sph} \geq 2$, 
+such that $M_{\rm BH} \propto L_{\rm sph}^{1.25 \pm 0.13}$. }
 \label{fig:pseudob}
@@
 \includegraphics[width=\columnwidth]{images/inset_psb.pdf}
-\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$, 
+\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$ (see Figure \ref{fig:pseudob}), 
 plotted against $n_{\rm sph}$. 
@@
 The horizontal solid line is equivalent to a zero vertical offset.
-Among the bulges with $n_{\rm sph}<2$, 12 have positive vertical offset and 11 have negative vertical offset.
+Among the bulges with $n_{\rm sph}<2$, 12 have a positive vertical offset and 11 have a negative vertical offset.
 Hence, bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
 from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
-\label{fig:pseudob}
+\label{fig:offset}
 \end{center}
@@
 \centering
-\caption{Linear regression analysis of the $M_{\rm BH} - MAG_{\rm sph}$ diagram.}
+\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$ diagram.}
 \begin{tabular}{llccccc}
@@
 
-\cite{grahamscott2015} collected a sample of $\sim$170 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
+Using data from \cite{jiang2011a}, 
+\cite{grahamscott2015} collected a sample of $\sim$140 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
 bulges hosting Active Galactic Nuclei (AGNs) with 
-black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
+black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$, 
 and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by S\'ersic bulges. 
@@
 may track the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
-That is, the AGNs appear to be the low-mass continuation of the \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
+That is, the AGNs appear to be the low-mass continuation of the tentative \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
 We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
 (Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.
-This topic will be investigated in Graham et al. (2015, \emph{in preparation}) with a dedicated careful analysis. \\
+This topic will be investigated in Graham et al. (2015, \emph{in preparation}) with a dedicated analysis. \\
 
@@
 Symbols are coded according to the galaxy morphological type.
-The red dashed line indicates the BCES bisector linear regression for the bulges of early-type galaxies (E+S0), 
+The red dashed line indicates the BCES bisector linear regression for the bulges of the 45 early-type galaxies (E+S0), 
 with the red shaded area denoting its $1\sigma$ uncertainty. 
@@
 a near-linear relation consistent with a dry-merging formation scenario.
-The blue solid line shows the BCES bisector linear regression for the bulges of late-type (Sp) galaxies, 
+The steeper blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
 with the blue shaded area denoting its $1\sigma$ uncertainty. 
 The bulges of late-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
-indicating that gas-rich processes feed the black hole more efficiently (``quadratically'' or ``cubically'') than the host bulge. 
-We note that AGNs with $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ appear to roughly follow the blue line 
+indicating that gas-rich processes feed the black hole more efficiently (``quadratically'' or ``cubically'') than the host bulge grows in stellar mass. 
+We note that AGNs with $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ \citep{jiang2011a} appear to follow the blue line 
 (see Graham et al. 2015, \emph{in preparation}).}

### 2015-05-14 papers/MbhMsph/mm.tex
thu

@@
 as suggested by the sequence of five galaxies (M87, M104, M31, M32 and the Milky Way). 
-\cite{yee1992} also announced a relation between what was effectively black hole mass and galaxy mass for bright early-type galaxies.
+\cite{yee1992} also announced a relation between what was effectively black hole mass and galaxy mass for high-luminosity, bulge-dominated early-type galaxies.
 This ``rough scaling'' was a premature version of the nowadays popular correlation between black hole mass, $M_{\rm BH}$,  
@@
 (\citealt{ferrareseford2005,lauer2007,graham2007,gultelkin2009,sani2011,beifiori2012,erwingadotti2012,
-vika2012,vandenbosch2012,mcconnellma2013,kormendyho2013,rusli2013}; 
-see \citealt{graham2015bulges} for an extensive review about the early discovery and successive improvements of these correlations)
+vika2012,vandenbosch2012,mcconnellma2013,kormendyho2013})
 continued to use galaxy samples dominated by high-mass, early-type systems having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 
@@
 \citep{laor1998,wandel1999,laor2001,ryan2007}.
+\cite{graham2012bent}, \cite{grahamscott2013} and \cite{scott2013} found two distinct trends in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm sph}$ diagrams, 
+i.e. a linear and a quadratic correlation at the high- and low-mass end, respectively.
+Those readers interested in an extensive review about the early discovery and successive improvements of these correlations 
+should consult \cite{graham2015bulges}. \\
 Recently, \cite{lasker2014data,lasker2014anal} derived $2.2~\rm \mu m$ bulge luminosities for 35 galaxies 
@@
 their large sample size allowed them to obtain a reasonable $M_{\rm BH} - L_{\rm sph}$ relation for the ensemble.}. 
-This mean statistical correction was obtained from the results of non-modern bulge/disk decompositions. 
-It should also be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
-and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies (lenticulars and spirals). \\
+These mean statistical bulge-to-total ratios were obtained from the results of literature two-component (S\'ersic-bulge/exponential-disk) decompositions. \\
+%It should also be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
+%and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies (lenticulars and spirals). \\
 Several recent papers \citep{jiang2011a,jiang2013,mathur2012,reines2013} claimed an offset at the low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ diagram,
@@
 %against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
-Because the value of the intrinsic scatter depends on the size of the uncertainties associated to the absolute magnitudes\footnote{The 
+Because the value of the intrinsic scatter depends on the size of the uncertainties associated with the absolute magnitudes\footnote{The 
 smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
-we tested the robustness of our last conclusion by increasing/decreasing the errors associated with $L_{\rm gal}$ 
+we tested the robustness of our last conclusion by increasing the error associated with $L_{\rm gal}$ 
 (we originally assumed $0.25\rm~mag$).
+The intrinsic scatter of the $M_{\rm BH} - L_{\rm gal}$ relation becomes smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation 
+when assuming an error of $L_{\rm gal}$ $\geq 0.7\rm~mag$, 
+which would be oddly larger than the typical error of $L_{\rm sph}$ used here 
+and also significantly larger than the errors of $L_{\rm gal}$ commonly assumed in the literature.
+Hence, we conclude that our determination of the intrinsic scatter is reliable, 
+and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
 %We decided to vary only the errors associated to $L_{\rm gal}$ 
@@
 %that takes into account the systematic errors related to the galaxy decomposition process. 
-We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
-have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
-Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
-and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
-we conclude that our determination of the intrinsic scatter is reliable, 
-and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
+%We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
+%have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
+%Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
+%and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
+%we conclude that our determination of the intrinsic scatter is reliable, 
+%and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
 %As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 

### 2015-05-14 python_codes/paper_figures/MbhMsph/figures.py

@@ -2320,9 +2320,9 @@ def mbh_vs_mass_sph_galsymb_agn():
 def main():
 	#mag_lit_vs_mag_my()
 	#mbh_vs_mass_sph_agn()
-	mbh_vs_mass_sph()
+	#mbh_vs_mass_sph()
 	#mbh_vs_mag_sph_psb()
-	#inset_psb()
+	inset_psb()
 	#mbh_vs_mag_tot()
 	#mbh_vs_mag_sph()
 	#mbh_vs_mass_sph_galsymb_agn()

### 2015-05-14 python_codes/paper_figures/MbhN/figures.py

@@ -1,0 +1,243 @@
+import sqlite3 as sql3
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+import matplotlib.colors as mcolors
+import matplotlib.image as image
+
+from scipy import stats
+from instruments.linear_regression import bces
+from instruments.linear_regression import predband
+from instruments.linear_regression import fitexy
+from instruments import b_n
+from instruments.linear_regression import colorline
+from instruments.linear_regression import akaike
+from instruments.linear_regression import absolutescatter
+#from instruments.linear_regression import lnr
+from instruments.markers import markers
+
+from matplotlib import rc
+rc('font',**{'family':'sans-serif','sans-serif':['CenturyGothic']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+rc('text', usetex=True)
+
+
+matplotlib.rcParams.update({'font.size': 26})
+
+dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_vivisection.db'
+
+path_paper_figures = '/Users/gsavorgnan/galaxy_vivisection/papers/MbhN/images/'
+
+
+
+def mbh_vs_n_sph(axis):
+	
+	#outliers = [u'n1374', u'n3842exp', u'n4889']
+	outliers = []
+	
+	connection = sql3.connect(dbname)
+	cur = connection.cursor()
+
+	getdata_query = 'SELECT anc.gal_id, anc.simplemorphtype, anc.mass_BH, anc.perr_mass_BH, anc.merr_mass_BH, \
+		physres.log_n_' + axis + '_moffat_comb, \
+		errV.perr_log_n, errV.merr_log_n \
+		FROM Ancillary AS anc \
+		JOIN OneDFitResultsPhysicalUnits AS physres ON anc.gal_id = physres.gal_id \
+		JOIN ErrorsVote as errV ON anc.gal_id = errV.gal_id \
+		WHERE anc.fit1D_done = 1;'
+	cur.execute(getdata_query)
[…]

### 2015-05-15 papers/MbhMsph/mm.tex
fri

@@
 
-\shorttitle{M-M paper}
+\shorttitle{Early and late $M_{\rm BH} - M_{\rm *,sph}$ sequence}
 \shortauthors{Savorgnan et al.}
@@
 
-\title{Supermassive black hole and host bulge affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.}
+\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.}
 
@@
 consistent with a dry-merging formation scenario,
-and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
-On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
+and define a tight \emph{early sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
+On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{late sequence}, 
 with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
@@
 
-\keywords{\bf keywords}
+\keywords{galaxies: bulges; galaxies: elliptical and lenticular, cD; galaxies: evolution; galaxies: structure; black hole physics}
 
@@
 \cite{graham2012bent}, \cite{grahamscott2013} and \cite{scott2013} found two distinct trends in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm sph}$ diagrams, 
-i.e. a linear and a quadratic correlation at the high- and low-mass end, respectively.
+i.e. a linear and a super-quadratic correlation at the high- and low-mass end, respectively.
 Those readers interested in an extensive review about the early discovery and successive improvements of these correlations 
@@
 Now we roughly double the sample. \\
-The $M_{\rm BH} - L_{\rm sph}$ relation can be predicted from other two correlations that involve 
+The $M_{\rm BH} - L_{\rm sph}$ relation for early-type (elliptical + lenticular) galaxies can be predicted from other two correlations that involve 
 the bulge stellar velocity dispersion, $\sigma$.
@@
 $M_{\rm dyn,sph} \propto R_{\rm e} \sigma^2$, and address the issue of a black hole fundamental plane.
-{\bf This paper is structured as follows... }
+%{\bf This paper is structured as follows... }
 
@@
 Two galaxies classified as E/S0 are obviously included in the early-type bin, 
-whereas two galaxies classified as S0/Sp or another two classified as mergers are included in neither the early- nor the late-type bin.\\
+whereas two galaxies classified as S0/Sp and another two classified as mergers are included in neither the early- nor the late-type bin.\\
 The S\'ersic/core-S\'ersic classification presented in this work 
@@
 or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. 
-Galaxies with velocity dispersions between these bands had high-resolution images available. \\
+Galaxies with velocity dispersions between these bands had high-resolution images available.
 
@@
 smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
-we tested the robustness of our last conclusion by increasing the error associated with $L_{\rm gal}$ 
+we tested the robustness of our last conclusion by increasing such uncertainties  
 (we originally assumed $0.25\rm~mag$).
 The intrinsic scatter of the $M_{\rm BH} - L_{\rm gal}$ relation becomes smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation 
-when assuming an error of $L_{\rm gal}$ $\geq 0.7\rm~mag$, 
-which would be oddly larger than the typical error of $L_{\rm sph}$ used here 
-and also significantly larger than the errors of $L_{\rm gal}$ commonly assumed in the literature.
+when assuming for $L_{\rm gal}$ an uncertainty larger than $0.7\rm~mag$, 
+which would be significantly larger than the values commonly assumed in the literature, 
+and would also oddly exceed the typical uncertainty that we estimated for $L_{\rm sph}$. 
 Hence, we conclude that our determination of the intrinsic scatter is reliable, 
@@
 with the red shaded area denoting its $1\sigma$ uncertainty. 
-We were not able to obtain any meaningful linear regression for the 13 ($=17-4$) late-type (Sp) galaxies. 
+%%%We were not able to obtain any meaningful linear regression for the 13 ($=17-4$) late-type (Sp) galaxies. 
 $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, 
@@
 which overestimated the bulge luminosity.
-This results in our bulge magnitudes being on average $\sim$$1\rm~mag$ fainter than in GS13, after accounting for the different wavelength of the data.
+This results in our bulge magnitudes being on average $\sim$$0.7\rm~mag$ fainter than in GS13, after accounting for the different wavelength of the data.
 At the same time, our bulge-to-total ratios for the high-luminosity S\'ersic spheroids ($3.6\rm~\mu m$ $MAG_{\rm sph} \lesssim -24 \rm~mag$) 
@@
 thus underestimating the bulge luminosity.
-The magnitudes that we obtained for such spheroids are on average $\sim$$1\rm~mag$ brighter than in GS13. 
+The magnitudes that we obtained for such spheroids are on average $\sim$$0.5\rm~mag$ brighter than in GS13. 
 These two effects explain the shallower slope that we obtained for the S\'ersic spheroids. \\
-We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ relation -- 
-which is expected for consistency with other scaling relations 
-(a single power-law $M_{\rm BH} - \sigma$ correlation and a double power-law $L_{\rm sph} - \sigma$ correlation) -- 
-cannot be attributed to the division between the two populations of S\'ersic and core-S\'ersic spheroids.
-We now test a new hypothesis, where the change in slope is ascribed to the different formation mechanisms of early- and late-type galaxies. 
-If this hypothesis is correct, 
-the spheroids of early-type galaxies will follow $M_{\rm BH} \propto L_{\rm sph}^{\sim 1}$, 
-whereas the spheroids of late-type galaxies will have $M_{\rm BH} \propto L_{\rm sph}^{\sim 2.5}$.
+We have seen that the slope that we obtained for S\'ersic spheroids ($1.53 \pm 0.20$) is not consistent with the $2.5$ 
+expected from $M_{\rm BH} \propto \sigma^5$ and $L_{\rm sph} \propto \sigma^2$, 
+and also that S\'ersic and core-S\'ersic spheroids do not define two distinct $M_{\rm BH} - L_{\rm sph}$ sequences. 
+We now investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ diagram for early- and late-type galaxies.
 First, we checked that elliptical and lenticular galaxies, taken separately, have slopes consistent with each other, 
-and thus, taken together, they define a single \emph{red sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
-We then fit the bulges of early- and late-type galaxies with two separate log-linear regressions, 
-and obtained $M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$ respectively, 
-in excellent agreement with the theoretical expectations of our hypothesis. \\
-%{\bf vertical scatter along the early type sequence is constant? if 2 overmassive bhs removed, what happens?}
+and thus, taken together, they define a single \emph{early sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
+We then fit the bulges of early-type galaxies with a single log-linear regression, 
+and obtained $M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$. 
+We did not find any convincing evidence for the change in slope expected for consistency 
+with the $M_{\rm BH} - \sigma$ and $L_{\rm sph} - \sigma$ correlations. 
+Because the change in slope should occur at $M_{\rm BH} > 10^{8 \pm 1}\rm~M_\odot$, 
+but all the early-type galaxies in our sample have $M_{\rm BH} \gtrsim 10^7\rm~M_\odot$, 
+one possible explanation is that we are still not probing enough low black hole masses for this subsample.
+An alternative possibility is that there is no sharp transition going from $L_{\rm sph} \propto \sigma^2$ at low luminosities 
+to $L_{\rm sph} \propto \sigma^5$ at high luminosities. 
+Although the knowledge that many ``elliptical'' galaxies actually contain embedded stellar disks dates back  
+at least three decades  
+\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995},
+it's mainly thanks to large integral-field-spectrograph surveys of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
+that our view has been further advanced 
+and it's now commonly accepted that most ``elliptical'' galaxies are all but simple and featureless pressure-supported systems. 
+More than half of all morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.
+\cite{krajnovic2013} showed that ``fast rotators'' as a class are disk-galaxies or at least disk-like galaxies. 
+In their magnitude-limited survey, systems 
+without any signature of disk-like components (neither in the kinematics nor in the photometry) 
+dominate only the most massive end (beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
+Past studies that investigated the $L_{\rm sph} - \sigma$ diagram might have failed to identify and consequently model embedded disks 
+in intermediate-luminosity, early-type galaxies, thus overestimating their $L_{\rm sph}$ 
+and mistakenly producing a sharp bent in the $L_{\rm sph} - \sigma$ correlation, rather than a continuously curved relation 
+(with $L_{\rm sph} \propto \sigma^{3-4}$ at intermediate luminosities). \\
+For the bulges of late-type galaxies we obtained $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$. 
+Looking at Figure \ref{fig:mbhmagsph}, one might argue against the statistical significance of this ``tentative'' \emph{late sequence}. 
 We point out the unsuitability of Pearson's and Spearman's correlation coefficients because 
@@
 consistent with a dry-merging formation scenario,
-and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
-On the other hand, the bulges of spiral galaxies trace a steeper \emph{blue sequence}, 
+and define a tight \emph{early sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
+On the other hand, the bulges of spiral galaxies trace a steeper \emph{late sequence}, 
 whose slope is less well constrained due to the small size of the subsample and, more importantly, 
 to the small range in $M_{\rm *,sph}$ that the subsample spans. 
-More data would be welcome to better constrain the slope of this \emph{blue sequence}.
 For the bulges of spiral galaxies, the BCES code returns a log-linear relation with slope $= 3.00 \pm 1.30$, 
@@
 The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
-
-Using data from \cite{jiang2011a}, 
+More data would be welcome to better constrain the slope of this \emph{late sequence}, 
+although we note that direct measurements of black hole masses below $10^6\rm~M_\odot$ are extremely challenging to obtain 
+with the current technological resources. 
+In this regard, using data from \cite{jiang2011a}, 
 \cite{grahamscott2015} collected a sample of $\sim$140 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
-bulges hosting Active Galactic Nuclei (AGNs) with 
+bulges hosting Active Galactic Nuclei (AGNs) with virial
 black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$, 
-and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by S\'ersic bulges. 
+and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges. 
 %Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
@@
 may track the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
-That is, the AGNs appear to be the low-mass continuation of the tentative \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
+That is, the AGNs appear to be the low-mass continuation of the tentative \emph{late sequence} shown in Figure \ref{fig:mbhmasssph}. 
 We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
@@
 \caption{Black hole mass plotted against spheroid stellar mass. 
-Symbols are coded according to the galaxy morphological type.
+Symbols are coded according to the galaxy morphological type (see legend).
 The red dashed line indicates the BCES bisector linear regression for the bulges of the 45 early-type galaxies (E+S0), 
@@
 \acknowledgments
-GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha and Gonzalo Diaz for useful discussion. \\
+GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes, Gonzalo Diaz and Pablo Rosado for useful discussion. \\
 % referee thank you!!

### 2015-05-15 python_codes/paper_figures/MbhMsph/figures.py

@@ -1315,9 +1315,9 @@ def mbh_vs_mag_tot():
        #	log_mbh[all==1],0.5*(merr_log_mbh[all==1] + perr_log_mbh[all==1])):
        #	datfile.write(str(MAGGal) + ' ' + str(err_MAGGal) + ' ' + str(logMassBH) + ' ' + str(err_logMassBH) + ' ' + '\n')
        #datfile.close()
-
-	###########################
-        
+       #
+        ###########################
+       
         print 'BCES early'
         print 'n', len(mag_tot[earlytype==1])
         A,B,Aerr,Berr,covAB=bces.bces(mag_tot[earlytype==1]-np.average(mag_tot[earlytype==1]),
@@ -1334,7 +1334,7 @@ def mbh_vs_mag_tot():
         print 'OLS(Y|X)    A =', "{0:.2f}".format(A[0]), '\pm', "{0:.2f}".format(Aerr[0]), '   B = ', "{0:.2f}".format(B[0]), '\pm', "{0:.2f}".format(Berr[0]), 'Delta =', "{0:.2f}".format(absscat_0)
         print 'OLS(X|Y)    A =', "{0:.2f}".format(A[1]), '\pm', "{0:.2f}".format(Aerr[1]), '   B = ', "{0:.2f}".format(B[1]), '\pm', "{0:.2f}".format(Berr[1]), 'Delta =', "{0:.2f}".format(absscat_1)
         print 'bisector    A =', "{0:.2f}".format(A[2]), '\pm', "{0:.2f}".format(Aerr[2]), '   B = ', "{0:.2f}".format(B[2]), '\pm', "{0:.2f}".format(Berr[2]), 'Delta =', "{0:.2f}".format(absscat_2)
-        #print 'orthogonal  A =', "{0:.2f}".format(A[3]), '\pm', "{0:.2f}".format(Aerr[3]), '   B = ', "{0:.2f}".format(B[3]), '\pm', "{0:.2f}".format(Berr[3]), 'Delta =', "{0:.2f}".format(absscat_3)
+        #print 'orthogonal  A =', "{0:.2f}".format(A[3]), '\pm', "{0:.2f}".format(Aerr[3]), '	B = ', "{0:.2f}".format(B[3]), '\pm', "{0:.2f}".format(Berr[3]), 'Delta =', "{0:.2f}".format(absscat_3)
         print '---------------------------------'
        
         logxx = np.arange(-10,20,0.1)
[…]

### 2015-05-15 python_codes/plots/scaling_relations/relations.py

@@ -251,8 +251,8 @@ def KMAG_sph_vs_mag_sph():
         plt.xlabel(r'$3.6{\rm~\mu m}~MAG_{\rm sph} \rm ~[mag]$', labelpad=20)
         plt.ylabel(r'$K-$band $MAG_{\rm sph} \rm ~[mag]$', labelpad=20)
         plt.subplots_adjust(left=0.15,bottom=0.15)
-	#plt.show()
-	plt.savefig(path_scalrel_plots + 'KMAG_sph_vs_mag_sph.pdf', format='pdf', dpi=1000)
+	plt.show()
+	#plt.savefig(path_scalrel_plots + 'KMAG_sph_vs_mag_sph.pdf', format='pdf', dpi=1000)
 
 def log_mbh_vs_KMAG_sph():
 	connection = sql3.connect(dbname)
@@ -2307,7 +2307,7 @@ def main():
 	#mbh_vs_logr_e()
 	#mag_sph_vs_n('maj')
 	#mag_sph_vs_n('eq')
-	#KMAG_sph_vs_mag_sph()
+	KMAG_sph_vs_mag_sph()
 	#log_mbh_vs_KMAG_sph()
 	#sani_vs_me()
 	#BTratios_GS13_vs_me()
@@ -2317,7 +2317,7 @@ def main():
 	#mu_0_vs_n('maj')
 	#mu_0_vs_n('eq')
 	#mbh_vs_mass_sph()
-	mbh_vs_mass_sph_core()
+	#mbh_vs_mass_sph_core()
 	#table_mbh_vs_mass_sph_core()
 	
 main()

### 2015-05-20 papers/MbhMsph/mm.tex
wed plyo

@@
 
-\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.}
+\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
 
@@
 
-\author{G. A. D. Savorgnan and A. W. Graham}
+\author{Giulia A.~D.~Savorgnan and Alister W.~Graham}
 \affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
 \email{gsavorgn@astro.swin.edu.au}
-\author{A. Marconi}
+\author{Alessandro Marconi}
 \affil{Dipartimento di Fisica e Astronomia, Universit\'a di Firenze, via G. Sansone 1, I-50019 Sesto Fiorentino, Firenze, Italy.}
 \and
-\author{E. Sani}
+\author{Eleonora Sani}
 \affil{European Southern Observatory, Alonso de Cordova, Vitacura 3107, Santiago, Chile.}
@@
 \begin{abstract}
-In our first paper, we performed a detailed (i.e.~bulges, disks, bars, spiral arms, rings, haloes, nuclei, cores, etc.) 
+In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, depleted core, etc.) 
 decomposition of 66 galaxies, with directly measured black hole masses, 
@@
 and also stellar mass, $M_{\rm *,sph}$.
-Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
+Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies.
 Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
@@
 consistent with a dry-merging formation scenario,
-and define a tight \emph{early sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
-On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{late sequence}, 
+and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
+At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper \emph{late-type sequence}, 
 with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
-indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they grow. 
+indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
 We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
@@
 and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
-once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$. {\bf 241 words}
+once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
 
@@
 as suggested by the sequence of five galaxies (M87, M104, M31, M32 and the Milky Way). 
-\cite{yee1992} also announced a relation between what was effectively black hole mass and galaxy mass for high-luminosity, bulge-dominated early-type galaxies.
-This ``rough scaling'' was a premature version of the nowadays popular correlation between black hole mass, $M_{\rm BH}$,  
+\cite{yee1992} then announced a linear relation between what was effectively black hole mass and galaxy mass for high-luminosity, bulge-dominated early-type galaxies 
+radiating near the Eddington limit.
+This ``rough scaling'' was a premature version of the early correlations between black hole mass, $M_{\rm BH}$,  
 and host spheroid luminosity, $L_{\rm sph}$, and also host spheroid mass, $M_{\rm sph}$ 
 \citep{kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}. 
-These early studies were dominated by high-mass, early-type galaxies, 
-for which they reported a quasi-linear $M_{\rm BH} - M_{\rm sph}$ relation, 
-consistent with a dry-merging formation scenario which would build and maintain a linear scaling. 
+These initial studies were dominated by high-mass, early-type galaxies, 
+for which they too reported a quasi-linear $M_{\rm BH} - M_{\rm sph}$ relation. 
 Subsequent studies of the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm sph}$ diagrams 
@@
 vika2012,vandenbosch2012,mcconnellma2013,kormendyho2013})
-continued to use galaxy samples dominated by high-mass, early-type systems having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 
-and recovered a near-linear relation. 
+continued to use galaxy samples dominated by high-mass, early-type systems with $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 
+and they too recovered a near-linear relation. 
 However, the consensus about a linear $M_{\rm BH} - M_{\rm sph}$ correlation was not unanimous. 
-Some studies reported a slope steeper than one,  
-or noticed that low-mass spheroids were offset to the lower right of the relation traced by their high-mass counterparts 
+Some studies had reported a slope steeper than one,  
+or noticed that the low-mass spheroids were offset to the right of (or below) the relation traced by the high-mass spheroids 
 \citep{laor1998,wandel1999,laor2001,ryan2007}.
-\cite{graham2012bent}, \cite{grahamscott2013} and \cite{scott2013} found two distinct trends in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm sph}$ diagrams, 
-i.e. a linear and a super-quadratic correlation at the high- and low-mass end, respectively.
-Those readers interested in an extensive review about the early discovery and successive improvements of these correlations 
-should consult \cite{graham2015bulges}. \\
+\cite{graham2012bent}, \cite{grahamscott2013} and \cite{scott2013} found two distinct trends in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm sph}$ diagrams:  
+a linear and a super-quadratic correlation at the high- and low-mass end, respectively\footnote{Readers 
+interested in an extensive review about the early discovery and successive improvements of these correlations 
+should consult \cite{graham2015bulges}.}. \\
 Recently, \cite{lasker2014data,lasker2014anal} derived $2.2~\rm \mu m$ bulge luminosities for 35 galaxies 
@@
 They also claimed that the black hole mass correlates equally well with the total galaxy luminosity 
-as it does with the bulge luminosity. 
-Now we roughly double the sample. \\
-The $M_{\rm BH} - L_{\rm sph}$ relation for early-type (elliptical + lenticular) galaxies can be predicted from other two correlations that involve 
+as it does with the bulge luminosity.  \\
+The $M_{\rm BH} - L_{\rm sph}$ relation for early-type (elliptical + lenticular) galaxies can be predicted by combining two other correlations that involve 
 the bulge stellar velocity dispersion, $\sigma$.
-The first of these two is the $M_{\rm BH} - \sigma$ relation \citep{ferraresemerritt2000,gebhardt2000},
+One of these is the $M_{\rm BH} - \sigma$ relation \citep{ferraresemerritt2000,gebhardt2000},
 which can be described with a single power-law ($M_{\rm BH} \propto \sigma^{5-6}$) 
 over a wide range in velocity dispersion ($70-350~\rm km~s^{-1}$, e.g.~\citealt{graham2011,mcconnell2011,grahamscott2013}).
-The second is the $L_{\rm sph} - \sigma$ relation, 
+The other is the $L_{\rm sph} - \sigma$ relation, 
 which has long been known to be a ``double power-law'', 
@@
 corresponding to $\sigma \approx 200~\rm km~s^{-1}$. 
-The $M_{\rm BH} - L_{\rm sph}$ relation should therefore be better described by a ``broken'', rather than a single, power-law, 
+The $M_{\rm BH} - L_{\rm sph}$ relation should therefore be better described by a ``broken'', rather than a single power-law: 
 with $M_{\rm BH} \propto L_{\rm sph}^{2.5}$ at the low-luminosity end, 
@@
 he identified two different populations of galaxies, 
-namely the core-S\'ersic \citep{graham2003coresersicmodel,trujillo2004coresersicmodel} and S\'ersic 
+namely the core-S\'ersic spheroids \citep{graham2003coresersicmodel,trujillo2004coresersicmodel} and the S\'ersic 
 spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
-whereas S\'ersic spheroids have no central deficit of stars. 
-While core-S\'ersic spheroids are also ``core galaxies'', as given by the Nuker definition \citep{lauer2007lumell},
-it should be noted that $\sim$20\% of ``core galaxies'' are not core-S\'ersic spheroids 
-(\citealt{dullograham2014cores}, their Appendix A.2), i.e. do not have depleted cores.
-The change in slope of the $L_{\rm sph} - \sigma$ relation corresponds to the division between 
-core-S\'ersic and S\'ersic spheroids (e.g. \citealt{grahamguzman2003}).},
+whereas S\'ersic spheroids have no central deficit of stars.},
 and attributed the change in slope (from super-quadratic to linear) to their different formation mechanisms. 
-In this scenario, core-S\'ersic spheroids are built in additive dry merger events, 
+In this scenario, core-S\'ersic spheroids are built in dry merger events 
 where the black hole and the bulge grow at the same pace, increasing their mass in lock steps ($M_{\rm BH} \propto L_{\rm sph}^1$), 
-whereas S\'ersic spheroids originate from gas-rich processes, 
+whereas S\'ersic spheroids originate from gas-rich processes 
 in which the mass of the black hole increases more rapidly than the mass of its host spheroid ($M_{\rm BH} \propto L_{\rm sph}^{2.5}$). \\
 \citeauthor{grahamscott2013} (\citeyear{grahamscott2013}, hereafter GS13) and \citeauthor{scott2013} (\citeyear{scott2013}) 
-presented double power-law linear regressions 
-for S\'ersic and core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
+presented separate power-law linear regressions 
+for the S\'ersic and core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
 (spheroid stellar mass) diagrams, probing down to $M_{\rm BH} \approx 10^6\rm~M_\odot$. 
 To obtain their dust-corrected \emph{bulge} magnitudes, they did not perform bulge/disc decompositions, 
-but instead they converted $B-$band and $K_S-$band observed, total \emph{galaxy} magnitudes 
+but converted the $B-$band and $K_S-$band observed, total \emph{galaxy} magnitudes into bulge magnitudes 
 using a mean statistical bulge-to-total ratio based on each object's morphological type and disc 
@@
 their large sample size allowed them to obtain a reasonable $M_{\rm BH} - L_{\rm sph}$ relation for the ensemble.}. 
-These mean statistical bulge-to-total ratios were obtained from the results of literature two-component (S\'ersic-bulge/exponential-disk) decompositions. \\
+These mean statistical bulge-to-total ratios were obtained from the results of two-component (S\'ersic-bulge/exponential-disk) decompositions in the literature. \\
 %It should also be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
 %and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies (lenticulars and spirals). \\
-Several recent papers \citep{jiang2011a,jiang2013,mathur2012,reines2013} claimed an offset at the low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ diagram,
-such that the black hole mass is lower than expected from the near-linear correlation traced by the high-mass, early-type spheroids. 
-However, \cite{grahamscott2013} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
-are not randomly offset from such near-linear correlation, 
-but follow the steeper relation traced by the S\'ersic spheroids. 
-Using bulge/disk decomposition data from \cite{jiang2011a}, 
-\cite{grahamscott2015} derived the host spheroid masses 
-and showed that the steeper $M_{\rm BH} - M_{\rm *,sph}$ extends to these spheroids with even lower black hole masses 
-($10^{5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 2 \times 10^{6}$), 
-and a more detailed analysis will be presented in Graham et al. (2015, \emph{in preparation}).  \\
+%Several recent papers \citep{jiang2011a,jiang2013,mathur2012,reines2013} claimed an offset at the low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ diagram,
+%such that the black hole mass is lower than expected from the near-linear correlation traced by the high-mass, early-type spheroids. 
+%However, \cite{grahamscott2013} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
+%are not randomly offset from such near-linear correlation, 
+%but follow the steeper relation traced by the S\'ersic spheroids. 
+%Using bulge/disk decomposition data from \cite{jiang2011a}, 
+%\cite{grahamscott2015} derived the host spheroid masses 
+%and showed that the steeper $M_{\rm BH} - M_{\rm *,sph}$ extends to these spheroids with even lower black hole masses 
+%($10^{5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 2 \times 10^{6}$), 
+%and a more detailed analysis will be presented in Graham et al. (2015, \emph{in preparation}).  \\
 Here we investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
 using state-of-the-art galaxy decompositions (Savorgnan \& Graham 2015, hereafter \emph{Paper I}) 
-for the largest sample of galaxies with directly measured black hole masses.
+for galaxies with directly measured black hole masses.
 Our galaxies are large and nearby, which allows us to perform accurate multicomponent decompositions 
 (instead of simple bulge/disk decompositions). 
-Our decompositions were obtained from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
+Our decompositions were performed on $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
 which is an excellent proxy for the stellar mass, superior to the $K-$band (\citealt{sheth2010}, and references therein).
 Nine of our galaxies have $M_{\rm BH} \lesssim 10^7\rm~M_\odot$, 
-which allows us to constrain the slope of the correlation at the low-mass end.
-In addition to this, our galaxy sample includes 17 spiral galaxies, 
-representing a notable improvement over past studies dominated by early-type systems. 
+which allows us to better constrain the slope of the correlation at the low-mass end.
+Furthermore, our galaxy sample includes 17 spiral galaxies, 
+representing a notable improvement over past studies dominated by early-type galaxies. 
 In a forthcoming paper, we will explore the relation between the black hole mass and the bulge dynamical mass, 
@@
 Our galaxy sample (see Table \ref{tab:sample}) 
-consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
+consists of 66 objects for which a dynamical measurement of the black hole mass had been tabulated in the literature 
 (by GS13 or \citealt{rusli2013bhmassesDM}) at the time that we started this project, 
-and for which we were able to obtain useful spheroid parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
+and for which we were able to obtain useful spheroid parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. \\
 Spheroid magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 
-bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
+bulge, disks, spiral arms, bars, rings, halo, extended or unresolved nuclear source and partially depleted core.
 Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
-to confirm the presence of rotationally supported disk components in most early-type galaxies, 
+to confirm the presence of rotationally supported disk components in most early-type (elliptical + lenticular) galaxies, 
 and to identify their extent 
-(intermediate-scale disks, that are fully embedded in the bulge, 
-or large-scale disks, that encase the bulge and dominate the light at large radii). 
+(intermediate-scale disks that are fully embedded in the bulge, 
+or large-scale disks that encase the bulge and dominate the light at large radii). 
 \emph{Paper I} presents the dataset used here, 
@@
 Following GS13, we assumed a fixed uncertainty ($0.25\rm~mag$) for the absolute galaxy magnitude $MAG_{\rm gal}$. \\
-The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/spiral; Sp = spiral; and merger) 
+The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') 
 follows from the galaxy models presented in \emph{Paper I}. 
-Throughout this paper, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
+Throughout this paper we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
 Two galaxies classified as E/S0 are obviously included in the early-type bin, 
@@
 they inferred the presence of a partially depleted core based on the stellar velocity dispersion:
-a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
+a spheroid is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
 or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. 
-Galaxies with velocity dispersions between these bands had high-resolution images available.
+All of the galaxies with velocity dispersions between these two limits had high-resolution images available.
 
@@
 Symmetrical regressions are meant to be compared with theoretical expectations, 
-whereas non-symmetrical direct ($M_{\rm BH}|X$) regressions -- 
+whereas non-symmetrical forward ($M_{\rm BH}|X$) regressions -- 
 which minimize the scatter in the $\log(M_{\rm BH})$ direction -- 
-can be used to predict black hole masses.
+are best used to predict black hole masses.
 
@@
 The $M_{\rm BH} - L_{\rm gal}$ diagram is shown in Figure \ref{fig:mbhmaggal}.
-Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
+Four spiral galaxies had their total luminosities underestimated (see Table \ref{tab:sample}) 
 and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
@@
 we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
-Our $M_{\rm BH} - L_{\rm sph}$ relation for 66 galaxies, irrespective of their morphological type, 
+That is, when considering only early-type galaxies, 
+we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
+However, our $M_{\rm BH} - L_{\rm sph}$ relation for all 66 galaxies, irrespective of their morphological type, 
 has an intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
@@
 and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
-However, when considering only early-type galaxies, 
-we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. \\
 %($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
@@
 smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
-we tested the robustness of our last conclusion by increasing such uncertainties  
+we tested the robustness of our conclusion by increasing the uncertainties associated with the galaxy absolute magnitudes 
 (we originally assumed $0.25\rm~mag$).
-The intrinsic scatter of the $M_{\rm BH} - L_{\rm gal}$ relation becomes smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation 
-when assuming for $L_{\rm gal}$ an uncertainty larger than $0.7\rm~mag$, 
-which would be significantly larger than the values commonly assumed in the literature, 
+The intrinsic scatter of the $M_{\rm BH} - L_{\rm gal}$ relation only becomes smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation 
+when assuming an uncertainty larger than $0.7\rm~mag$ for $L_{\rm gal}$, 
+which would be significantly larger than the typical value commonly recognized in the literature, 
 and would also oddly exceed the typical uncertainty that we estimated for $L_{\rm sph}$. 
-Hence, we conclude that our determination of the intrinsic scatter is reliable, 
-and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
+Hence, we conclude that our determination of the relative intrinsic scatter is reliable, 
+and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late-type) galaxies.
 %We decided to vary only the errors associated to $L_{\rm gal}$ 
@@
 Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
-Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
+Four spiral galaxies had their magnitudes overestimated (luminosities underestimated) and are shown as upper limits. 
 The red dashed line indicates the BCES bisector linear regression for the 45 early-type galaxies (E+S0), 
 with the red shaded area denoting its $1\sigma$ uncertainty. 
-%%%We were not able to obtain any meaningful linear regression for the 13 ($=17-4$) late-type (Sp) galaxies. 
-$M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, 
-but not for all (early+late) galaxies. }
+$M_{\rm BH}$ correlates equally well with $L_{\rm gal}$ and $L_{\rm sph}$ only for early-type galaxies, 
+but not for all (early+late-type) galaxies. }
 \label{fig:mbhmaggal}
@@
 The $M_{\rm BH} - L_{\rm sph}$ diagram is shown in Figure \ref{fig:mbhmagsph}, 
-and the linear regression analysis is presented in Table \ref{tab:lregsph}. \\
+and the linear regression analysis is presented in Table \ref{tab:lregsph}. 
 S\'ersic and core-S\'ersic spheroids have slopes consistent with each other (within their $1\sigma$ uncertainties), 
@@
 However, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.53 \pm 0.20}$) 
-is notably shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.73 \pm 0.55}$). 
+is notably shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.73 \pm 0.55}$). \\
 Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{The classification has changed for the galaxies 
 NGC 1316, NGC 1332 and NGC 3998.} from the classification used here, 
-the main cause of such inconsistency is that the bulge-to-total ratios obtained from our galaxy decompositions 
+the main cause of the inconsistency is that the bulge-to-total ratios obtained from our galaxy decompositions 
 are different from those assumed by GS13 to convert galaxy luminosities into bulge luminosities.
@@
 which typically present a complex morphology (bars, double bars, embedded disks, nuclear components, etc).
-Our sophisticated galaxy models account for the extra components, 
-while the bulge-to-total ratios of GS13 were based on simple literature S\'ersic-bulge/exponential-disk decompositions 
+Our galaxy models account for the extra components, 
+while the average bulge-to-total ratios of GS13 were based on less sophisticated S\'ersic-bulge/exponential-disk decompositions 
 which overestimated the bulge luminosity.
@@
 These two effects explain the shallower slope that we obtained for the S\'ersic spheroids. \\
-We have seen that the slope that we obtained for S\'ersic spheroids ($1.53 \pm 0.20$) is not consistent with the $2.5$ 
-expected from $M_{\rm BH} \propto \sigma^5$ and $L_{\rm sph} \propto \sigma^2$, 
-and also that S\'ersic and core-S\'ersic spheroids do not define two distinct $M_{\rm BH} - L_{\rm sph}$ sequences. 
-We now investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ diagram for early- and late-type galaxies.
-First, we checked that elliptical and lenticular galaxies, taken separately, have slopes consistent with each other, 
-and thus, taken together, they define a single \emph{early sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
-We then fit the bulges of early-type galaxies with a single log-linear regression, 
+The slope that we obtained for S\'ersic spheroids ($1.53 \pm 0.20$) is not consistent with the value of $2.5$ 
+expected from $M_{\rm BH} \propto \sigma^5$ and $L_{\rm sph} \propto \sigma^2$. 
+In addition, the S\'ersic and core-S\'ersic spheroids appear not to define two distinct $M_{\rm BH} - L_{\rm sph}$ sequences. 
+This leads us to investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ diagram for early- and late-type galaxies.
+First, we checked that the elliptical and lenticular galaxies, taken separately, have slopes consistent with each other, 
+and thus, taken together, they define a single \emph{early-type sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
+We then fit the early-type galaxies with a single log-linear regression, 
 and obtained $M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$. 
-We did not find any convincing evidence for the change in slope expected for consistency 
-with the $M_{\rm BH} - \sigma$ and $L_{\rm sph} - \sigma$ correlations. 
+We did not find any convincing evidence for the change in slope required for consistency 
+with the $M_{\rm BH} - \sigma$ and bent $L_{\rm sph} - \sigma$ correlations. 
 Because the change in slope should occur at $M_{\rm BH} > 10^{8 \pm 1}\rm~M_\odot$, 
@@
 one possible explanation is that we are still not probing enough low black hole masses for this subsample.
-An alternative possibility is that there is no sharp transition going from $L_{\rm sph} \propto \sigma^2$ at low luminosities 
+An additional possibility is that there is no sharp transition going from $L_{\rm sph} \propto \sigma^2$ at low luminosities 
 to $L_{\rm sph} \propto \sigma^5$ at high luminosities. 
@@
 \citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995},
-it's mainly thanks to large integral-field-spectrograph surveys of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
+it is mainly thanks to large integral-field-spectrograph surveys of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
 that our view has been further advanced 
-and it's now commonly accepted that most ``elliptical'' galaxies are all but simple and featureless pressure-supported systems. 
-More than half of all morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.
-\cite{krajnovic2013} showed that ``fast rotators'' as a class are disk-galaxies or at least disk-like galaxies. 
-In their magnitude-limited survey, systems 
-without any signature of disk-like components (neither in the kinematics nor in the photometry) 
-dominate only the most massive end (beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
-Past studies that investigated the $L_{\rm sph} - \sigma$ diagram might have failed to identify and consequently model embedded disks 
-in intermediate-luminosity, early-type galaxies, thus overestimating their $L_{\rm sph}$ 
-and mistakenly producing a sharp bent in the $L_{\rm sph} - \sigma$ correlation, rather than a continuously curved relation 
+and it is now commonly accepted that most ``elliptical'' galaxies contain disks. 
+%More than half of all morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS,krajnovic2013}.
+%\cite{krajnovic2013} showed that ``fast rotators'' as a class are disk-galaxies or at least disk-like galaxies. 
+%In their magnitude-limited survey, systems 
+%without any signature of disk-like components (neither in the kinematics nor in the photometry) 
+%dominate only the most massive end (beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
+Past studies that investigated the $L_{\rm sph} - \sigma$ diagram might have failed to identify and consequently model the disks 
+in intermediate-luminosity, early-type galaxies, thus overestimating $L_{\rm sph}$ 
+and mistakenly producing a sharp bend in the $L_{\rm sph} - \sigma$ correlation, rather than a continuously curved relation 
 (with $L_{\rm sph} \propto \sigma^{3-4}$ at intermediate luminosities). \\
 For the bulges of late-type galaxies we obtained $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$. 
-Looking at Figure \ref{fig:mbhmagsph}, one might argue against the statistical significance of this ``tentative'' \emph{late sequence}. 
-We point out the unsuitability of Pearson's and Spearman's correlation coefficients because 
+From a cursory inspection of Figure \ref{fig:mbhmagsph}, one might be tempted to doubt the statistical significance of this ``tentative'' \emph{late-type sequence}. 
+However, a visual inspection of the plotted data requires one to take into account the error bars 
+when judging-by-eye the strength of a correlation. 
+Similarly, the Pearson's and Spearman's correlation coefficients are not applicable because 
 they do not take into account the error bars on our data.
-Similarly, a visual inspection of the plotted data requires us to take into account the error bars 
-when judging-by-eye the strength of a correlation. 
-We have therefore relied on the quantitative regression analysis rather than subjective approaches.
+We have therefore relied on the quantitative regression analysis.
 
 \subsubsection{Pseudo- versus classical bulges}
-Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
-formed through violent processes, such as hierarchical clustering via minor mergers, 
-and pseudo-bulges, thought to be disk-like, rotation-supported systems, 
-built from secular evolution processes, such as instabilities of their surrounding disk or bar. 
+Current views distinguish between classical bulges (which are considered to be spheroidal, pressure-supported systems, 
+formed through violent processes, such as hierarchical clustering via minor mergers), 
+and pseudo-bulges (thought to be disk-like, rotation-supported systems, 
+built from secular evolution processes, such as instabilities of their surrounding disk or bar). 
 Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
@@
 thus rotation is not a definitive signature of a pseudo-bulge. 
-Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
+Furthermore, many galaxies host both a classical and a pseudo-bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
 macarthur2009,dosanjosdasilva2013,seidel2015}). 
@@
 just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
-are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994,jerjen2000}). 
-The use of the S\'ersic index to identify pseudo-bulges is thus a dangerous practice. \\
+are also well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994,jerjen2000}). 
+The use of the S\'ersic index (in addition to rotation) to identify pseudo-bulges is thus a dangerous practice. \\
 \cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
@@
 To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
-and we compute the vertical offset of all bulges from the regression. 
+and we then compute the vertical offset of all bulges from this regression. 
 In Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
 Among the 23 bulges with $n_{\rm sph}<2$, 12 have a positive vertical offset and 11 have a negative vertical offset. 
-\cite{kormendy2015review} provides a list of many pseudo-bulges classification criteria, including the divide at $n_{\rm sph}=2$, 
+\cite{kormendy2015review} provides a list of many pseudo-bulge classification criteria, including the divide at $n_{\rm sph}=2$, 
 and cautions that each individual criterion has a failure rate of 0-25\%. 
@@
 \caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
-Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
-red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
-Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
-The red dashed line indicates the BCES bisector linear regression for the bulges of the 45 early-type (E+S0) galaxies, 
+Symbols have the same meaning as in Figure \ref{fig:mbhmaggal}.
+The red dashed line indicates the BCES bisector linear regression for the spheroidal component of the 45 early-type (E+S0) galaxies, 
 with the red shaded area denoting its $1\sigma$ uncertainty. 
@@
 Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
-Bulges with $n_{\rm sph}<2$, claimed by some to be pseudo-bulges, are marked with a square. 
+Bulges with $n_{\rm sph}<2$, claimed by some to be pseudo-bulges, are enclosed with a square. 
 The black solid line shows the BCES bisector linear regression for the spheroids that have $n_{\rm sph} \geq 2$, 
@@
 and its linear regression analysis in Table \ref{tab:lregmass}. 
-The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
+The bulges of the early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
 consistent with a dry-merging formation scenario,
-and define a tight \emph{early sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
-On the other hand, the bulges of spiral galaxies trace a steeper \emph{late sequence}, 
-whose slope is less well constrained due to the small size of the subsample and, more importantly, 
-to the small range in $M_{\rm *,sph}$ that the subsample spans. 
-For the bulges of spiral galaxies, the BCES code returns a log-linear relation with slope $= 3.00 \pm 1.30$, 
+and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
+On the other hand, the bulges of the spiral galaxies trace a steeper \emph{late-type sequence}, 
+whose slope is less well constrained due to the smaller size of the subsample and, more importantly, 
+to the smaller range in $M_{\rm *,sph}$ that the subsample spans. 
+For the bulges of spiral galaxies, the BCES code returns a log-linear relation with a slope $= 3.00 \pm 1.30$, 
 while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) 
@@
 The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
-More data would be welcome to better constrain the slope of this \emph{late sequence}, 
+More data would be welcome to better constrain the slope of this \emph{late-type sequence}, 
 although we note that direct measurements of black hole masses below $10^6\rm~M_\odot$ are extremely challenging to obtain 
 with the current technological resources. 
-In this regard, using data from \cite{jiang2011a}, 
-\cite{grahamscott2015} collected a sample of $\sim$140 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
+In this regard, using a sample of $\sim$140 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
 bulges hosting Active Galactic Nuclei (AGNs) with virial
-black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$, 
-and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges. 
-%Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
-We anticipate here that the correlation traced by our bulges of spiral galaxies 
-may track the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
-That is, the AGNs appear to be the low-mass continuation of the tentative \emph{late sequence} shown in Figure \ref{fig:mbhmasssph}. 
-We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
-(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.
-This topic will be investigated in Graham et al. (2015, \emph{in preparation}) with a dedicated analysis. \\
+black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ \citep{jiang2011a}, 
+\cite{grahamscott2015} showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges.
+The majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
+(NASA Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.} and
+we anticipate here that the correlation traced by our spiral galaxy bulges 
+may track the location of these lower mass AGN in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
+That is, the AGNs appear to be the low-mass continuation of our tentative \emph{late-type sequence} shown in Figure \ref{fig:mbhmasssph} 
+and this will be explored with more rigour in a forthcoming paper.
 
@@
 \end{figure}
+
+\section{Conclusions}
+Using $3.6\rm~\mu m$ \emph{Spitzer} imagery, 
+we have performed accurate multicomponent decompositions (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, depleted core, etc.), 
+which were checked to be consistent with the two-dimensional galaxy kinematics, 
+and we have derived galaxy luminosities, spheroid luminosities and spheroid stellar masses for 66 nearby galaxies 
+with a dynamical measurement of their black hole mass. 
+Our galaxy sample, besides being the largest ever used to investigate black hole mass scaling relations, 
+contains 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7 \rm~M_{\odot}$. 
+This constitutes a significant improvement over past studies whose samples were biased towards high-mass, early-type galaxies. \\
+Using our state-of-the-art dataset, we have investigated substructure in the $M_{\rm BH} - L_{\rm gal}$, $M_{\rm BH} - L_{\rm sph}$ 
+and $M_{\rm BH} - M_{\rm *,sph}$ diagrams. 
+Our principal conclusions are: \\
+
+\begin{itemize}
+\item The $M_{\rm BH} - M_{\rm *,sph}$ log-relation for the spheroidal components of early-type (elliptical + lenticular) galaxies 
+      has a slope of $1.04 \pm 0.10$ and intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
+      We call this tight correlation an \emph{early-type sequence}. 
+      The $M_{\rm BH} - M_{\rm *,sph}$ log-relation for the bulges of late-type (spiral) galaxies has a more uncertain slope ($2-3$) 
+      due to the smaller size of the subsample and, more importantly, to the smaller range in stellar mass 
+      ($3 \times 10^9 \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 3 \times 10^{10}$) that the subsample spans. 
+      We refer to this correlation as a ``tentative'' \emph{late-type sequence}. 
+      In (gas-poor) early-type galaxies, the black hole and the stellar content of the spheroidal component grow at the same pace, 
+      following a linear $M_{\rm BH} - M_{\rm *,sph}$ relation. 
+      In (gas-rich) spiral galaxies, the black hole grows faster than its host bulge, 
+      following a quadratic/cubic $M_{\rm BH} - M_{\rm *,sph}$ relation. 
+      For analogy with the color-magnitude diagram, 
+      it would be tempting to refer to our \emph{early-type sequence} as a \emph{red sequence}, 
+      although no bimodality in color has been observed in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
+\item The $M_{\rm BH} - M_{\rm *,sph}$ log-relations for core-S\'ersic and S\'ersic spheroids have slopes consistent with each other 
+      ($1.19 \pm 0.23$ and $1.48 \pm 0.20$, respectively), 
+      thus these two populations do not define two distinct sequences. 
+\item In the $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) diagram, for early-type galaxies, 
+      we did not observe the change in slope required for consistency with the $M_{\rm BH} - \sigma$ and bent $L_{\rm sph} - \sigma$ correlations.
+      This issue of inconsistency remains therefore an open question. 
+      It might be that we are still not probing enough low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) 
+      for the subsample of early-type galaxies, 
+      or that the transition from  $L_{\rm sph} \propto \sigma^2$ at low luminosities to $L_{\rm sph} \propto \sigma^5$ at high luminosities 
+      is less sharp than previously thought.
+\item Spheroids with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
+      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. 
+\item The $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ correlations have the same level of intrinsic scatter 
+      when considering early-type galaxies only. 
+      Once reasonable numbers of spiral galaxies are included, 
+      $M_{\rm BH}$ correlates better with $L_{\rm sph}$ than with $L_{\rm gal}$. 
+\end{itemize}
 
@@
 
-\section{Conclusions}
-\label{sec:concl}
-% %ngc0524 outlier, n1332 non outlier
-% to be re-written
-%
-% \begin{itemize}
-% \item The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
-% consistent with a dry-merging formation scenario,
-% and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
-% On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
-% with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
-% indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
-% \item S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{x \pm x}$, a less steep sequence than previously reported; 
-% \item bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
-% are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
-% \item $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
-% once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
-% \end{itemize}
-
 \acknowledgments

### 2015-05-20 python_codes/instruments/markers/markers_n.py

@@ -1,0 +1,45 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+
+scatter_kwargs = {"zorder":100}
+scatter_kwargs2 = {"zorder":200}
+
+
+def spiral(ax, color, x0, y0, size_x, size_y):
+	t1 = np.arange(1,4,0.01)
+	t2 = np.arange(1,4,0.01)
+	x1 = size_x*t1*np.cos(t1)
+	y1 = size_y*t1*np.sin(t1)
+	x2 = -size_x*t2*np.cos(t2)
+	y2 = -size_y*t2*np.sin(t2)
+	
+	t = np.arange(0,2*np.pi,0.01)
+	x = size_x*1.1*np.cos(t)
+	y = size_y*1*np.sin(t)
+	
+	ax.plot(10**(x0+x1),10**(y0+y1), color=color, lw=2, **scatter_kwargs2)
+	ax.plot(10**(x0+x2),10**(y0+y2), color=color, lw=2, **scatter_kwargs2)
+	ax.plot(10**(x0+x),10**(y0+y), color=color, lw=2, **scatter_kwargs2)
+	ax.fill_between(10**(x0+x), 10**(y0+0), 10**(y0+y), edgecolor='', facecolor=color, **scatter_kwargs2)
+	
+	
+def lenticular(ax, color, x0, y0, size_x, size_y):
+
+	t = np.arange(0,2*np.pi,0.01)
+	x = size_x*1*np.cos(t)
+	y = size_y*1.5*np.sin(t)	
+	
+	ax.fill_between(10**(x0+x), 10**(y0+0), 10**(y0+y), edgecolor='', facecolor=color, **scatter_kwargs)
+	ax.plot([10**(x0-2*size_x),10**(x0+2*size_x)],[10**(y0),10**(y0)], color=color, lw=3, **scatter_kwargs)
+
+
+def elliptical(ax, color, x0, y0, size_x, size_y):
+
+	t = np.arange(0,2*np.pi,0.01)
+	x = size_x*1*np.cos(t)
+	y = size_y*1.5*np.sin(t)	
+	
+	ax.fill_between(10**(x0+x), 10**(y0+0), 10**(y0+y), edgecolor='', facecolor=color, **scatter_kwargs)
+
+

### 2015-05-20 python_codes/paper_figures/MbhMsph/figures.py

@@ -2152,23 +2152,23 @@ def mbh_vs_mass_sph_galsymb_agn():
 	error_kwargs = {"lw":.5, "zorder":0}
 
 	ax.scatter(mass_sph_Jiangagn, mbh_Jiangagn, marker='o', color='b', s=15, alpha=0.5)
-	ax.scatter(mass_sph_lowmassagn, mbh_lowmassagn, marker='o', facecolors='none', edgecolors='b', s=80, alpha=0.5)
-	ax.scatter(mass_sph_lowmassagn, mbh_lowmassagn, marker='+', color='b', s=80, alpha=0.5)
+	#ax.scatter(mass_sph_lowmassagn, mbh_lowmassagn, marker='o', facecolors='none', edgecolors='b', s=80, alpha=0.5)
+	#ax.scatter(mass_sph_lowmassagn, mbh_lowmassagn, marker='+', color='b', s=80, alpha=0.5)
 
 	
 	for x0,y0 in zip(mass_sph[simplemorphtype=='E'], mbh[simplemorphtype=='E']):
 		markers.elliptical(ax, 'red', np.log10(x0), np.log10(y0), 0.08)
 	
  	for x0,y0 in zip(mass_sph[simplemorphtype=='E/S0'], mbh[simplemorphtype=='E/S0']):
-		markers.lenticular(ax, 'darkorange', np.log10(x0), np.log10(y0), 0.08)
+		markers.lenticular(ax, 'red', np.log10(x0), np.log10(y0), 0.08)
        
 	for x0,y0 in zip(mass_sph[simplemorphtype=='S0'], mbh[simplemorphtype=='S0']):
 		markers.lenticular(ax, 'darkorange', np.log10(x0), np.log10(y0), 0.08)
 	
-        for x0,y0 in zip(mass_sph[simplemorphtype=='S0/S'], mbh[simplemorphtype=='S0/S']):
-		markers.spiral(ax, 'blue', np.log10(x0), np.log10(y0), 0.04)
+        for x0,y0 in zip(mass_sph[simplemorphtype=='S0/Sp'], mbh[simplemorphtype=='S0/Sp']):
+		markers.spiral(ax, 'darkorange', np.log10(x0), np.log10(y0), 0.04)
 			
-        for x0,y0 in zip(mass_sph[simplemorphtype=='S'], mbh[simplemorphtype=='S']):
[…]

### 2015-05-25 papers/data_paper/datapaper.tex
thu
ale?

@@
 
-\shorttitle{Data paper}
-\shortauthors{Savorgnan et al.}
+\shorttitle{True-to-life galaxy decomposition}
+\shortauthors{Savorgnan \& Graham}
 
@@
 
-\title{Data paper}
-
-\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
+\title{Supermassive black hole and host bulge affairs \\ I. True to life galaxy decomposition.}
+
+\author{G. A. D. Savorgnan and A. W. Graham}
 \affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
@@
 Indeed, separating the disk light from that of the bulge has led to the discovery of the missing population of compact, massive spheroids 
-in the local Universe {\bf (Graham, Dullo, Savorgnan 2015)}.
+in the local Universe \citep{GDS2015}.
 If we are to properly understand the evolution of galaxies, we need to understand their components.\\
@@
 
-% \onecolumngrid
-% \subsection{individual galaxies}
-% \label{sec:indgal}
-%
-% individual galaxies \\
-%
-% \clearpage\newpage\noindent
-% {\bf IC 1459 \\}
-%
-% IC 1459 is an elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
-% nuclear dust and an indication of a central stellar disk \citep{forbes1994ic1459}.
-% The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
-% This galaxy has also a partially depleted core ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
-%
-% %\cite{sani2011} fit this galaxy with a S\'ersic-bulge + Gaussian-AGN model ($R_{\rm e} = 61''.1$, $n=6$).
-% %\cite{lasker2014data} used a S\'ersic-bulge + mask-core model ($R_{\rm e} = 62''.4$, $n=8.25$).
-% %\cite{rusli2013} adopted a core-S\'ersic model ($R_{\rm e} = 45''.43$, $n=7.6$).
-%
-% \emph{1D fit -- }
-% Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
-% We masked the innermost $6''.1$ affected by the partially depleted core 
-% and we fit this galaxy with a S\'ersic profile. 
-%
-% \emph{Other models -- } 
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for IC 1459.}
-% \end{center}
-% \end{figure}
-%
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for IC 1459.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
-% T.W. 1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
-% T.W. 2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
-% \hline
-% S+11         & S-bul + G-n   & $61.1$  &  $6.0$ \\
-% R+13         & core-S\'ersic & $45.4$  &  $7.6$ \\
-% L+14         & S-bul + m-c   & $62.4$  &  $8.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:ic1459}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf IC 2560 \\}
-%
-% IC 2560 is a barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
-% and dust within the central $2''.5$ \citep{martini2003}.
-%
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model ($R_{\rm e} = 27''.5$, $n=2$).
-%
-% \emph{1D fit -- }
-% A visual inspection of the image of IC 2560 reveals a boxy bulge and
-% a large scale bar that extends out to $R \lesssim 43''$.
-% The disk appears to be slightly lopsided along the direction of the bar,
-% due to two non-symmetric ansae, but it becomes symmetric beyond $R \gtrsim 60''$. 
-% This is why the surface brightness profile deviates from a perfect exponential
-% in the radial range $42'' \lesssim R \lesssim 60''$, which has been excluded from the fit.
-% Motivated by the presence of a strong optical AGN and dust in the nucleus, 
-% we accounted for an excess of non-stellar light by adding a central Gaussian component to the model.
-% %Our final 1D model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar + Gaussian-AGN.
-% %Similarly, our 2D model consists of a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN.\\
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for IC 2560.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for IC 2560.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $6.1$  &  $0.8$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.5$  &  $0.6$ \\
-% %T.W. 2D	&  &  & \\
-% \hline
-% S+11         & S-bul + e-d + G-n & $27.5$  &  $2.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:ic2560}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf IC 4296 \\}
-%
-% IC 4296 is an elliptical galaxy. % with a radio jet \citep{liuxie1992}.
-% Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
-%
-% %\cite{sani2011} fit this galaxy with a S\'ersic-bulge + Gaussian-AGN model ($R_{\rm e} = 33''.6$, $n = 4$).
-% %\cite{lasker2014data} employed a S\'ersic-bulge + mask-core model ($R_{\rm e} = 97''.8$, $n=8.2$).
-%
-% \emph{1D fit -- }
-% After masking the innermost $6''.1$, % affected by the (unresolved) partially depleted core,
-% we found that a single S\'ersic profile provides a fairly good description of this galaxy.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for IC 4296.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for IC 4296.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
-% T.W. 1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
-% T.W. 2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
-% \hline
-% S+11         & S-bul + G-n & $33.6$  &  $4.0$ \\
-% L+14         & S-bul + m-c & $97.8$  &  $8.2$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:ic4296}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M31 -- NGC 0224 \\}
-%
-% M31, the Andromeda galaxy, is a spiral galaxy. 
-% Although for decades this galaxy had been classified as an unbarred spiral,
-% recent works have unraveled the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}.
-% M31 also features a pseudo-ring-like structure at $R \sim 50'$ \citep{athanassoulabeaton2006m31}. 
-%
-%
-% \emph{1D fit -- }
-% We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
-% The region $2000'' \lesssim R \lesssim 3400''$, where the pseudo-ring is observed, was excluded from the fit.
-% A S\'ersic + exponential fit is clearly not adequate to describe the light profile of M31.
-% The residuals of such fit display a structure in correspondence of the bar ($R \lesssim 1500''$).
-% The bar was thus fit with a Ferrer function.
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M31.}
-% \end{center}
-% \end{figure}
-%
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M31.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $418.6$  &  $2.2$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $173.6$  &  $1.3$ \\
-% %T.W. 2D	& $$  & $$  &  $$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m31}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M49 -- NGC 4472 \\}
-%
-% M49, the brightest member of the Virgo cluster, is a giant elliptical galaxy 
-% with a partially depleted core ($R_{\rm break} = 1''.8$, \citealt{rusli2013}).
-% %M49 is a slow-rotator \citep{atlas3dIII-MNRAS}.
-%
-% %\cite{ferrarese2006acsvcs} modeled this galaxy with a core-S\'ersic profile ($R_{\rm e} = 208''$, $n = 5.5$).
-% %Also \cite{rusli2013} used a core-S\'ersic model ($R_{\rm e} = 199''$, $n = 5.6$).
-%
-% \emph{1D fit -- }
-% We excluded from the fit the innermost $12''$.
-% We found no evidence for embedded components and
-% we fit M49 with a single S\'ersic profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M49.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M49.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $190.2$  &  $6.6$ \\
-% T.W. 1D eq.  & S-bul + m-c & $135.3$  &  $5.4$ \\
-% T.W. 2D      & S-bul + m-c & $151.9$  &  $5.5$ \\
-% \hline
-% R+13         & core-S\'ersic & $199.0$  &  $5.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m49}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M59 -- NGC 4621 \\}
-%
-% M59 is an elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
-% and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}.
-% %M59 is a fast-rotator \citep{atlas3dIII-MNRAS}.
-%
-% %\cite{sani2011} modeled this galaxy with a single S\'ersic-bulge model ($R_{\rm e} = 70''.1$, $n = 5$).
-% %\cite{vika2012} used a S\'ersic-bulge + mask-core model ($R_{\rm e} = 54''.7$, $n = 5.7$). 
-%
-% \emph{1D fit -- }
-% The intermediate-scale embedded disk is clearly visible in our unsharp mask image, and 
-% the velocity field confirms the presence of a rapidly rotating component. 
-% Although faint, it is important to account for the presence of this disk.
-% A single S\'ersic fit produces bad residuals.
-% The fit notably improves if an embedded exponential disk function 
-% is added to the final model.
-% We chose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M59.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M59.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c + e-id & $48.0$  &  $5.5$ \\
-% T.W. 1D eq.  & S-bul + m-c + e-id & $90.9$  &  $8.8$ \\
-% %T.W. 2D	&    & $$  &  $$ \\
-% \hline 
-% S+11         & S-bul       & $70.1$  &  $5.0$ \\
-% V+12         & S-bul + m-c & $54.7$  &  $5.7$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m59}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf M60 -- NGC 4649 \\}
-%
-% exclude it, doesn't make sense
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M64 -- NGC 4826 \\}
-%
-% M64 is a dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. 
-%
-% %B12 model the galaxy image with a 2D S\'ersic function + exponential disk ($n = 1.49$). \\
-% \emph{1D fit -- }
-% A large-scale bar ($R \lesssim 50''$) can be identified in the unsharp mask 
-% and produces corresponding peaks in the ellipticity, PA and B4 profiles.
-% We modeled it with a Ferrer function.
-% Additional peaks in the ellipticity, PA and B4 profiles at $R \sim 15''$ 
-% signal the presence of an embedded disky component, that we described with a low-$n$
-% S\'ersic function.
-% Although the galaxy is dusty and hosts an AGN, we do not observe any nuclear excess of light 
-% in the fit residuals and therefore we consider unnecessary to add a nuclear component to our model.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m64_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M64.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M64.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + S-id  & $3.8$  &  $0.8$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + S-id  & $4.3$  &  $1.4$ \\
-% %T.W. 2D	&   & $$  & $$  &  $$ \\
-% \hline
-% B+12      & S-bul + e-d  & $5.0$  &  $1.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m64}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M81 -- NGC 3031 \\}
-%
-% M81 is an early-type spiral galaxy with a LINER AGN.
-% This galaxy features two bars \citep{elmegreen1995m81,gutierrez2011,erwindebattista2013}.
-%
-% \emph{1D fit -- }
-% We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M81.
-% The bars are not particularly evident in the galaxy image or in the unsharp mask.
-% Any attempt to account for the bars in the fit was unsuccessful. 
-% For this reason, we used a simple S\'ersic + exponential model to describe M81.
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m81_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M81.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M81.}
-% \begin{center}
-% \begin{tabular}{llccc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d  & $31.0$  &  $1.7$ \\
-% T.W. 1D eq.  & S-bul + e-d  & $33.2$  &  $2.1$ \\
-% %T.W. 2D	&   & $$  & $$  &  $$ \\
-% \hline
-% GD07      & S-bul + e-d	 & $68.1$   &  $3.3$ \\
-% S+11      & S-bul + e-d + G-n  & $127.3$  &  $3.0$ \\
-% B+12      & S-bul + e-d	 & $50.0$   &  $2.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m81}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M84 -- NGC 4374 \\}
-%
-% M84 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.5$, \citealt{rusli2013}). 
-%
-% %GD07 model the galaxy light profile with a S\'ersic function ($n = 5.6$).
-% %V12 model the galaxy image with a 2D S\'ersic function + core-mask ($n = 3.5$).
-% %S11 model the galaxy image with a 2D S\'ersic function + Gaussian ($n = 7.0$).
-% %B12 model the galaxy image with a 2D S\'ersic function ($n = 4.10$). \\
-%
-% \emph{1D fit -- }
-% The unsharp mask reveals a faint inner component ($R \lesssim 12''$). 
-% Here we excluded the data within $R < 13''.8$ and modeled the galaxy with a S\'ersic profile.
-%
-% %After masking the innermost $13''.8$, we modeled the galaxy with a S\'ersic profile. 
-% %However, we notice that 
-% %the 1D and 2D fits are not much affected by the presence of the embedded component.
-% %In fact, reducing the size of the central mask to uncover the inner component 
-% %(but still masking the region affected by the partially depleted core) does not
-% %alter significantly the bulge parameters. 
-% %The structures observed in the residuals are caused by the negative ellipticity gradient 
-% %(from $\epsilon \sim 0.17$ to $\epsilon \sim 0.03$, over a radial range $10'' < R < 130''$),
-% %which cannot be reproduced by the 2D model because of its fixed ellipticity ($\epsilon = 0.10$). 
-%   
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m84_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M84.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M84.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c   & $101.6$  &  $7.8$ \\
-% T.W. 1D eq.  & S-bul + m-c   & $129.8$  &  $7.9$ \\
-% T.W. 2D      & S-bul + m-c   & $181.8$  &  $8.4$ \\
-% \hline
-% GD07         & S-bul         & $75.1$   &  $5.6$ \\
-% S+11         & S-bul + G-n   & $105.9$  &  $7.0$ \\
-% V+12         & S-bul + m-c   & $28.7$   &  $3.5$ \\
-% B+12         & S-bul         & $63.6$   &  $4.1$ \\
-% R+13         & core-S\'ersic & $126.2$  &  $7.1$ \\
-% L+14         & S-bul + m-c   & $139.0$  &  $8.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m84}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M87 -- NGC 4486 \\}
-%
-% M87 is a giant elliptical galaxy belonging to the Virgo cluster.
-% This galaxy has a large partially depleted core ($R_{\rm break} = 7''.2$, \citealt{ferrarese2006acsvcs}).
-%
-% \emph{1D fit -- }
-% The morphology of M87 is similar to that of M49.
-% The innermost $18''.5$ were excluded from the fit.
-% We used a single S\'ersic model to characterize M87.
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m87_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M87.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M87.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c  & $203.9$  &  $10.0$ \\
-% T.W. 1D eq.  & S-bul + m-c  & $87.1$   &  $5.9$ \\
-% T.W. 2D      & S-bul + m-c  & $88.3$   &  $4.3$ \\
-% \hline
-% GD07      & S-bul	    & $-$     &  $6.9$ \\
-% S+11      & S-bul + G-n   & $99.5$  &  $4.0$ \\
-% V+12      & S-bul + m-c   & $34.6$  &  $2.4$ \\
-% R+13      & core-S\'ersic & $180.9$ &  $8.9$ \\
-% L+14      & S-bul + m-c   & $122.0$ &  $5.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m87}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf M89 -- NGC 4552 \\}
-%
-% m87 has ellipticity still increasing, the halo is not prevailing
-% m89 instead has a plateau in the ell prof, bcz the halo is predominant
-% we need to fit the halo
-%
-% BTW, if we wanna test the two phase formation scenario, we should care more about the halos...
-% at which effective radius does the halo begin?
-% what is the ratio of the mass in the galaxy or in the halo?
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m89_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M89.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M89.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-halo  & $29.0$  &  $4.6$ \\
-% T.W. 1D eq.  & S-bul + e-halo  & $28.2$  &  $5.1$ \\
-% %T.W. 2D	&   & $$  & $$  &  $$ \\
-% \hline
-% &   & $$  &  $$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m89}
-% \end{table}
-%
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M94 -- NGC 4736 \\}
-%
-% M94 is an almost face-on spiral galaxy, with a Seyfert AGN \citep{veroncettyveron2006} and 
-% circumnuclear dust \citep{elmegreen2002m94,peeplesmartini2006m94}.
-% This galaxy has a ring-like structure at $R \sim 50''$ \citep{munoztunon1989m94}.
-%
-% %\cite{fisherdrory2010} fit M94 with a S\'ersic-bulge + exponential-disk model ($R_{\rm e} = 7''.7$, $n = 1.3$). 
-%
-% \emph{1D fit -- }
-% The ellipticity and B4 profiles display a local maximum at $R \sim 10''$, 
-% indicating the presence of a disky component embedded in the bulge,
-% as already noted by \cite{fisherdrory2010}.
-% We modeled this component with a Ferrer function.
-% We excluded the data within the innermost $6''.7$, due to the AGN contribution.
-% Any attempt to model the ring was unsuccessful, resulting in a degenerate model.
-% Therefore we preferred to exclude also the data in the range $20'' \lesssim R \lesssim 80''$, 
-% where the ring light dominates over the rest of the galaxy.
-% %Our final model for M94 consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m94_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M94.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M94.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $11.4$  &  $0.9$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $8.4$   &  $1.1$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m94}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M96 -- NGC 3368 \\}
-%
-% M96 is a spiral galaxy with a large scale bar and no AGN activity \citep{martini2003,nowak2010n3368n3489}. 
-%
-% %\cite{sani2011} fit this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-bar model 
-% %($R_{\rm e} = 45''.6$, $n = 1.0$). 
-% \cite{nowak2010n3368n3489} argued for the presence of a large pseudo-bulge and a tiny classical bulge 
-% ($R_{\rm e} = 1''.6$, $n = 2.3$). 
-%
-% \emph{1D fit -- }
-% M96 has a complex morphology. 
-% The large-scale disk does not exhibit a perfect exponential profile, 
-% mainly because of wound spiral arms resembling a ring ($R \sim 185''$),
-% which however are too faint and irregular to be described with a Gaussian ring model. 
-% The large scale bar extends out to $R \lesssim 80''$ and has been modeled with a Ferrer function.
-% A peak at $R \sim 25''$ in the ellipticity profile unravels an inner component embedded in the bulge.
-% The isophotal twist observed within $R \lesssim 25''$ suggests that the inner component can be identified 
-% with a second bar, as already noted by \cite{erwin2004}.
-% We accounted for this embedded component with a low-$n$ S\'ersic profile.
-% We built our final model with a S\'ersic-bulge + exponential-disk + Ferrer-bar + S\'ersic-bar.
-% The residuals do not display any significant light excess in the nuclear region, 
-% in agreement with the lack of AGN activity.
-%
-% \cite{nowak2010n3368n3489} came to their conclusion by modeling only the innermost $8''.5$ of the 
-% light profile of M96 with a S\'ersic-classical-bulge and an exponential-pseudo-bulge, 
-% but without subtracting the contribution of the large-scale disk and the large-scale bar.
-% In addition, they acknowledged the presence of a secondary inner bar, but did not include it in their fit.
-%
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m96_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M96.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M96.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + S-bar  & $7.5$  &  $1.5$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + S-bar  & $5.3$  &  $1.3$ \\
-% T.W. 2D      & S-bul + e-d + 2 G-bars       & $8.3$  &  $2.0$ \\
-% \hline
-% S+11         & S-bul + e-d + G-bar  & $45.6$  &  $1.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m96}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf M104 -- NGC 4594 \\} 
-%
-% OK
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M104.}
-% \end{center}
-% \end{figure}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M105 -- NGC 3379 \\}
-%
-% M105 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.1$, \citealt{rusli2013}).
-%
-% \emph{1D fit -- }
-% M105 exhibits a mild isophotal twist and an abrupt change of ellipticity at $R \sim 30''$.
-% The velocity map shows rotation at least within $R \lesssim 30''$, 
-% but no embedded disk can be recognized in the unsharp mask 
-% and the ellipticity profile is quite unusual for a spheroidal system with an inner disk.
-% After masking the innermost $6''.1$, we noticed that a single S\'ersic model 
-% does not provide a good description of the galaxy light profile.
-% However, the addition of a second function (of any analytical form) to the model did not improve the fit.
-% We thus employed a single S\'ersic profile for M105.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m105_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M105.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M105.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $57.2$  &  $5.2$ \\
-% T.W. 1D eq.  & S-bul + m-c & $50.9$  &  $5.3$ \\
-% T.W. 2D      & S-bul + m-c & $73.6$  &  $7.0$ \\
-% \hline
-% GD07         & S-bul & $58.3$  &  $4.3$ \\
-% S+11         & S-bul & $46.0$  &  $5.0$ \\
-% R+13         & core-S\'ersic & $55.1$  &  $5.8$ \\
-% L+14         & S-bul + m-c & $96.3$  &  $9.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m105}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf M106 -- NGC 4258 \\} 
-%
-% M106 is a barred spiral galaxy, harbouring a Seyfert AGN \citep{veroncettyveron2006} 
-% with %a radio jet \citep{liuzhang2002} and 
-% circumnuclear dust \citep{martini2003}. 
-%
-% %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 14''.9$, $n = 2.0$). 
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model 
-% %($R_{\rm e} = 111''.7$, $n = 2.0$). 
-% %\cite{vika2012} proposed two different fits: the first with a S\'ersic-bulge + exponential-disk + PSF-nucleus
-% %($R_{\rm e} = 17''.0$, $n = 3.5$), 
-% %and the second with a S\'ersic-bulge + exponential-disk + PSF-nucleus + S\'ersic-bar
-% %($R_{\rm e} = 6''.3$, $n = 2.2$).
-%
-% \emph{1D fit -- }
-% We excluded from the fit the innermost $6''.1$ because affected by the AGN emission.
-% The boxy bar, responsible for the minimum in the B4 profile at $R \sim 65''$, 
-% is faint compared to the large-scale disk and in the light profile is only detectable as a slight swelling
-% within $65'' \lesssim R \lesssim 110''$.
-% This region has been excluded from the fit.
-% A peak in the ellipticity profile at $R \sim 10''$ suggests that a disk-like component might be 
-% embedded in the bulge.
-% Since the galaxy is barred, this component could be identified with a peanut bulge. 
-% However, we found that adding an extra component to the model introduces degeneracies, 
-% thus we preferred not to do so.
-% While the fit along the major-axis is satisfactory, 
-% the equivalent-axis residuals present a sneaky structure within $R \lesssim 20''$,
-% due to the unsubtracted embedded component.
-% %Our final model consists of a S\'ersic-bulge + exponential-disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/m106_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for M106.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for M106.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d & $15.3$  &  $2.0$ \\
-% T.W. 1D eq.  & S-bul + e-d & $8.3$   &  $1.2$ \\
-% %T.W. 2D	& & $$  & $$  &  $$ \\
-% \hline
-% GD07     & S-bul + e-d		 & $14.9$   &  $2.0$ \\
-% S+11     & S-bul + e-d + G-n  	 & $111.7$  &  $2.0$ \\
-% V+12 (1) & S-bul + e-d + PSF-n	 & $17.0$   &  $3.5$ \\
-% V+12 (2) & S-bul + e-d + PSF-n + S-bar & $6.3$    &  $2.2$ \\
-% L+14     & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $6.3$	 &  $3.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:m106}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 0524 \\} 
-%
-% NGC 0524 is an unbarred face-on lenticular galaxy. 
-%
-% %\cite{laurikainen2010} modeled this galaxy with a S\'ersic-bulge + exponential-disk + 2 Ferrer-lenses 
-% %($R_{\rm e} = 8''.9$, $n = 2.7$).
-% %\cite{sani2011} opted for a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 26''.8$, $n = 3.0$).
-% \emph{1D fit -- }
-% The unsharp mask of NGC 0524 unravels a faint multi-ring structure in the galaxy disk,
-% with a major ring peaking at $R \sim 20''$.
-% We accounted only for this brightest ring using a Gaussian ring profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n0524_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 0524.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 0524.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + G-r & $6.0$  &  $1.1$ \\
-% T.W. 1D eq.  & S-bul + e-d + G-r & $5.8$  &  $1.1$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% L+10      & S-bul + e-d + 2 F-l & $8.9$  &  $2.7$ \\
-% S+11      & S-bul + e-d	  & $26.8$  &  $3.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n0524}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 0821 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n0821_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 0821.}
-% \end{center}
-% \end{figure}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1023 \\}
-%
-% NGC 1023 is a barred lenticular galaxy. % with no partially depleted core \cite{faber1997}. \\
-%
-% %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 17''.7$, $n = 2.0$). 
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-bar model 
-% %($R_{\rm e} = 24''.0$, $n = 3.0$).
-% %\cite{lasker2014data} employed a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
-% %($R_{\rm e} = 9''.6$, $n = 3.1$).
-% \emph{1D fit -- }
-% The bar extends out to $R \lesssim 40''$.
-% %The light profile of NGC 1023 is well described by a S\'ersic-bulge + exponential-disk + Ferrer-bar model.
-% Small deviations of the disk from a perfect exponential profile, 
-% within the region $60'' \lesssim R \lesssim 125''$ (that has been excluded from the fit), 
-% can be ascribed to some faint residual spiral arms, also noticeable in the 2D residual image. 
-% The peak at $R \sim 10''$ in the B4 profile signals the presence of an embedded (and faint) disk.
-% The 1D residuals show a structure within $R \lesssim 10''$ caused by this unsubtracted 
-% component, also noted by \cite{lasker2014data}.
-% Attempts to account for the inner disk by adding a fourth function to the model 
-% did not significantly modify the best-fit bulge parameters,
-% thus we elected not to model the embedded disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n1023_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 1023.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 1023.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $9.2$  &  $2.1$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $7.4$  &  $2.0$ \\
-% T.W. 2D      & S-bul + e-d + G-bar & $6.6$  &  $2.3$ \\
-% \hline
-% GD07    & S-bul + e-d 	& $17.7$  &  $2.0$ \\
-% S+11    & S-bul + e-d + G-bar & $24.0$  &  $3.0$ \\
-% L+14    & S-bul + e-d + S-bar & $9.6$   &  $3.1$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n1023}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1300 \\}
-%
-% NGC 1300 is a face-on, barred spiral galaxy. % with no partially depleted core \citep{graham2012MNRAS}. 
-%
-% %\cite{sani2011} fit NGC 1300 with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 85''.4$, $n = 3.0$).
-% %\cite{lasker2014data} built their model with a S\'ersic-bulge + exponential-disk + PSF-nucleus + exponential-inner-disk + 
-% %S\'ersic-bar + spiral arms
-% %($R_{\rm e} = 10''.4$, $n = 4.3$).
-%
-% \emph{1D fit -- }
-% The morphology of NGC 1300 is quite complex. 
-% In addition to a large scale disk and a bulge, the galaxy is composed of 
-% a large scale bar that extends up to $R \lesssim 90''$, two prominent spiral arms 
-% and an inner disk-like component ($R \lesssim 5''$), disclosed by the peaks in the ellipticity and PA profiles.
-% We truncate the light profile at $R \sim 50''$ and we fit the inwards combination of the large-scale bar and the disk 
-% as a single component, using an exponential function.
-% The embedded component is described with a low-$n$ S\'ersic profile.
-% %Our final model consists of a S\'ersic-bulge + exponential-(disk+bar) + S\'ersic-inner disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n1300_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 1300.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 1300.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-(d+bar) + S-id & $9.9$  &  $3.8$ \\
-% T.W. 1D eq.  & S-bul + e-(d+bar) + S-id & $8.1$  &  $3.6$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% S+11    & S-bul + e-d & $85.4$  &  $3.0$ \\
-% L+14    & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $10.4$  &  $4.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n1300}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1316 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n1316_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 1316.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 1316.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + 2 G-r + G-n & $21.5$  &  $2.0$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + 2 G-r + G-n & $15.9$  &  $1.8$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% S+11      & S-bul + e-d + G-n & $93.0$  &  $5.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n1316}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1332 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 1332.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 1332.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + S-id + m-c & $34.7$  &  $5.1$ \\
-% T.W. 1D eq.  & S-bul + S-id + m-c & $18.0$  &  $3.7$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n1332}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1374 \\}
-%
-% ok
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 1399 \\}
-%
-% NGC 1399, the central galaxy of the Fornax cluster, is an elliptical galaxy with a partially depleted core 
-% ($R_{\rm break} \sim 2''.4$, \citealt{rusli2013,dullograham2014cores}).
-% The nuclear activity of NGC 1399 is classified as Seyfert \citep{veroncettyveron2006},
-% but the galaxy lacks of dust \citep{tran2001}.
-%
-% %\cite{grahamdriver2007} fit the galaxy light profile with a single S\'ersic-bulge profile 
-% %($n = 16.8$).  
-% %\cite{rusli2013} modeled NGC 1399 with a core-S\'ersic profile and the sum of a S\'ersic and an exponential
-% %function accounting for the galaxy halo 
-% %($R_{\rm e} = 36''.2$, $n = 7.38$). 
-% %\cite{lasker2014data} used a S\'ersic-bulge + mask-core model 
-% %($R_{\rm e} = 154''.0$, $n = 11.1$). 
-%
-% \emph{1D fit -- }
-% The ellipticity and PA profiles display a steep decline within $R \lesssim 60''$,
-% suggesting the presence of an embedded disk.
-% This inner component is also visible, although very faint, in the unsharp mask.
-% TBD!! velocity map, the disk is face on
-% We note that, after excluding the innermost $6''.1$ affected by the partially depleted core,
-% a single S\'ersic profile is not sufficient to describe the whole galaxy light profile.
-% The addition of an inner exponential function to the model 
-% notably improves the fit.
-% %We build our final model with a S\'ersic-bulge + mask-core + exponential-inner disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n1399_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 1399.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 1399.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c + e-id & $405.2$  &  $10.0$ \\
-% T.W. 1D eq.  & S-bul + m-c + e-id & $338.1$  &  $10.0$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% GD07         & S-bul  		    & $-$      &  $16.8$ \\
-% R+13         & core-S\'ersic + (S+e)-halo & $36.2$   &  $7.4$ \\
-% L+14         & S-bul + m-c		    & $154.0$  &  $11.1$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n1399}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 2273 \\}
-%
-% NGC 2273 is a barred spiral galaxy with a Seyfert AGN \citep{contini1998} 
-% and circumnuclear dust \citep{simoeslopes2007}. 
-% Its bar is surrounded by two tightly wound star-forming spiral arms that resemble a ring
-% \citep{comeron2010}. 
-%
-% \cite{laurikainen2005} pointed out the presence of an inner disk embedded in the bulge of NGC 2273,
-% but they deliberately chose not to model it due to the degeneracy between the functions describing the bulge
-% and the inner disk. 
-% %Their final model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar 
-% %($R_{\rm e} = 2''.6$, $n = 1.8$). 
-%
-% \emph{1D fit -- }
-% The bar of NGC 2273 extends out to $R \lesssim 25''$. 
-% The pseudo-ring does not produce any evident swelling in the light profile, 
-% therefore we do not account for it in the galaxy model.
-% The isophotal parameters confirm the presence of a nuclear disk-like component within $R \lesssim 5''$.
-% However, as noted by \cite{laurikainen2005}, any attempt to account for the embedded disk resulted in a 
-% degenerate model. 
-% This is not surprising if one considers the poor spatial resolution of the galaxy image, 
-% the effective radius of the bulge being comparable to the FWHM of the PSF.
-% Although NGC 2273 hosts an optical AGN and nuclear dust, no central excess of light is observed in the 1D residuals.
-% The addition of a nuclear component to the model does not improve the fit and does not significantly affect
-% the bulge parameters.
-% %Our final model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n2273_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 2273.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 2273.}
-% \begin{center}
-% \begin{tabular}{llccc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $1.6$  &  $2.1$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $1.9$  &  $2.7$ \\
-% %T.W. 2D	&  & $$  &  $$ \\
-% \hline
-% L+05         & S-bul + e-d + F-bar & $2.6$  &  $1.8$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n2273}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 2549 \\}
-%
-% NGC 2549 is an edge-on barred lenticular galaxy. 
-%
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 11''.6$, $n = 7.0$). 
-%
-% \emph{1D fit -- }
-% Although the edge-on inclination of NGC 2549 complicates the identification of embedded components, 
-% a large scale bar ($R \lesssim 45''$) can be recognized in the galaxy image itself and -- more easily -- in the light profile.
-% We describe the large scale bar with a Ferrer profile.
-% A peak in the ellipticity profile discloses the presence of a disky component
-% embedded in the bulge ($R \lesssim 10''$).
-% This inner component can be spotted also by looking at the velocity map.
-% We fit it with a Ferrer profile.
-% %We build our final model with a S\'ersic-bulge + exponential-disk + 2 Ferrer-bars.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n2549_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 2549.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 2549.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + F-id & $6.1$  &  $2.3$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + F-id & $3.1$  &  $1.5$ \\
-% T.W. 2D      & S-bul + e-d + G-bar + G-id & $5.6$  &  $2.1$ \\
-% \hline
-% S+11         & S-bul + e-d & $11.6$  &  $7.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n2549}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 2778 \\}
-%
-% NGC 2778 is an almost face-on lenticular galaxy. 
-%
-% %\cite{grahamdriver2007} modeled NGC 2778 with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 2''.3$, $n = 1.6$). 
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk model
-% %($R_{\rm e} = 2''.5$, $n = 2.5$). 
-% %\cite{vika2012} employed a S\'ersic-bulge + exponential-disk model 
-% %($R_{\rm e} = 1''.5$, $n = 2.7$). 
-% %\cite{lasker2014data} fit the galaxy with a S\'ersic-bulge + exponential-disk + S\'ersic-bar
-% %($R_{\rm e} = 2''.8$, $n = 4.0$). 
-%
-% \emph{1D fit -- }
-% The peak in the ellipticity profile at $R \sim 5''$ unravels the existence of a nuclear component 
-% embedded in the galaxy bulge.
-% After an inspection of the unsharp mask, we identified this component with a small bar,
-% that we modeled with a Ferrer function.
-% We also accounted for some nuclear light excess by adding a PSF component to the model.
-% %We then fit NGC 2778 with a S\'ersic-bulge + exponential-disk + Ferrer-bar + PSF-nucleus.
-% We note that excluding the PSF component from our galaxy model does not significantly affect the 
-% bulge effective radius, but it increases the S\'ersic index to $n \sim 2$.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n2778_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 2778.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 2778.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + PSF-n & $2.3$  &  $1.3$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + PSF-n & $2.2$  &  $1.2$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% GD07         & S-bul + e-d	     & $2.3$  &  $1.6$ \\
-% S+11         & S-bul + e-d	     & $2.5$  &  $2.5$ \\
-% V+12         & S-bul + e-d	     & $1.5$  &  $2.7$ \\
-% L+14         & S-bul + e-d + S-bar & $2.8$  &  $4.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n2778}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 2787 \\}
-%
-% NGC 2787 is a barred lenticular galaxy with LINER nuclear activity \citep{veroncettyveron2006}.
-% An inner disk is embedded in the bulge of this galaxy \citep{erwin2003n2787}.
-% NGC 2787 features a spectacular structure of dust rings at its center \citep{erwinsparke2003}
-% and a nuclear stellar disk ($R \lesssim 1''.8$, \citealt{ledo2010}).
-%
-% %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 4''.6$, $n = 2.0$). 
-% %\cite{fisherdrory2008} decomposed NGC 2787 in a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 9''.1$, $n = 1.2$).
-% %\cite{laurikainen2010} employed a S\'ersic-bulge + exponential-disk + Ferrer-bar + Ferrer-lens model
-% %($R_{\rm e} \sim 4''$, $n = 1.3$).
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN 
-% %($R_{\rm e} = 15''.7$, $n = 3.0$). 
-% %\cite{lasker2014data} described NGC 2787 with a S\'ersic-bulge + truncated exponential-disk + 
-% %truncated S\'ersic-bar + S\'ersic-inner disk + PSF-nucleus
-% %($R_{\rm e} = 14''.3$, $n = 2.8$). 
-%
-% \emph{1D fit -- }
-% NGC 2787 has an undoubtedly complex morphology. 
-% This galaxy is made of a bulge, a large scale disk, a bar (see the peaks in the ellipticity, PA and B4 profiles
-% at $R \sim 30''$) with two ansae, an inner disk (or bar?) embedded in the bulge (see the peak in the ellipticity profile
-% at $R \sim 17''$), and a bright nucleus.
-%
-% Beyond $R \gtrsim 50''$, where the galaxy large scale disk extends without being affected by the bar ansae,
-% the surface brightness profile is not a perfect exponential, being better described by a S\'ersic function
-% with $n < 1$.
-% Curiously, at optical wavelengths the disk has an exponential decline with no truncation or anti-truncation 
-% (see \citealt{erwin2003n2787} their Figure 14, and \citealt{erwin2008}).
-% Here we propose two different models for NGC 2787.
-% In both cases we used a S\'ersic profile for the bulge, a Ferrer function for the bar, a second Ferrer function for the inner disk (or bar) 
-% and a PSF for the nucleus. 
-% We then described the large scale disk using a S\'ersic function with $n < 1$ 
-% or an exponential function. 
-% In the last case we needed to exclude the data within $R \sim 30'' - 50''$ where the ansae produce a hollow.
-% The two different decompositions result in the same bulge best-fit parameters ($R_{\rm e} \sim 5''$, $n \sim 1$)
-% along the major-axis, whereas the outcome is significantly different along the equivalent-axis 
-% ($n = 1.3$ when using the exponential-disk and $n = 2.2$ when using the S\'ersic-disk).
-%
-% might just pick one TBD!!
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n2787_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 2787.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 2787.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% \multicolumn{4}{c}{\emph{exponential-disk}} \\
-% %\hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + F-id + PSF-nucleus & $4.8$  &  $1.1$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + F-id + PSF-nucleus & $3.3$  &  $1.3$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% \multicolumn{4}{c}{\emph{S\'ersic-disk}}\\
-% %\hline
-% T.W. 1D maj. & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.6$  &  $1.1$ \\
-% T.W. 1D eq.  & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.4$  &  $2.2$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% GD07         & S-bul + e-d					  & $4.6$   &  $2.0$ \\
-% L+10         & S-bul + e-d + F-bar + F-l			  & $4.0$   &  $1.3$ \\
-% S+11         & S-bul + e-d + G-bar + G-n			  & $15.7$  &  $3.0$ \\
-% L+14         & S-bul + trunc. e-d + trunc. S-bar + S-id + PSF-n & $14.3$  &  $2.8$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n2787}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 2974 \\}
-%
-% NGC 2974 is a spiral galaxy which has been misclassified as an elliptical galaxy in the RC3 catalog.
-% The galaxy hosts a Seyfert AGN \citep{veroncettyveron2006} and filamentary dust in its center \citep{tran2001}.
-%  
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + Gaussian-AGN 
-% %($R_{\rm e} = 27''.2$, $n = 3.0$). 
-%
-% \emph{1D fit -- }
-% From an inspection of the unsharp mask, we identified a ring structure at $R \sim 50''$, 
-% probably a residual of two tightly wound spiral arms,
-% and an elongated bar-like component within $R \lesssim 30''$, that we fit with a Ferrer function.
-% The last one produces a peak in the ellipticity profile at $R \sim 20''$.
-% Although the ring is extremely faint, it is important to account for it in the galaxy decomposition. 
-% A model without the ring component results in a ``steeper'' exponential-disk (the disk has a smaller scale length 
-% and a lower central surface brightness) and produces bad residuals within $R \lesssim 40''$.
-% The nuclear component is fit with a Gaussian profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 2974.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 2974.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-n + G-r & $8.3$   &  $1.4$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + G-n + G-r & $6.9$   &  $1.2$ \\
-% T.W. 2D      & S-bul + e-d + G-bar + m-n	 & $10.6$  &  $1.3$ \\
-% \hline
-% S+11         & S-bul + G-n & $27.2$  &  $3.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n2974}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%   
-% {\bf NGC 3079 \\}
-%
-% inner component?? ok fuck it
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3079_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3079.}
-% \end{center}
-% \end{figure}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3091 \\}
-%
-% NGC 3091 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.62$, \citealt{rusli2013}).
-%
-% %\cite{rusli2013} modeled NGC 3091 with a single core-S\'ersic profile 
-% %($R_{\rm e} = 91''.0$, $n = 9.3$). 
-%
-% \emph{1D fit -- }
-% The data within the innermost $6''.1$ are excluded from the fit.
-% A faint embedded component ($R \lesssim 10''$) can be recognized in the unsharp mask and has a corresponding peak in the
-% ellipticity profile.
-% This extra component is clearly visible in the residual image obtained by subtracting a 2D S\'ersic model from the  
-% galaxy image.
-% However, any attempt to account for the embedded component resulted in an unsatisfactory fit and did not 
-% significantly affect the bulge parameters.
-% We thus elected not to model the inner component.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3091_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3091.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3091.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $100.5$  &  $7.6$ \\
-% T.W. 1D eq.  & S-bul + m-c & $51.2$	&  $6.6$ \\
-% T.W. 2D      & S-bul + m-c & $67.1$	&  $6.7$ \\
-% \hline
-% R+13         & core-S\'ersic & $91.0$  &  $9.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3091}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3115 \\}
-%
-% NGC 3115 is an edge-on elliptical/lenticular galaxy. 
-% Its nuclear activity is classified as passive in the optical wavelengths \citep{gavazzi2013nuclspec}.
-% This galaxy features a nuclear stellar disk ($R \sim 1''$, \citealt{scorzabender1995,ledo2010}).
-%
-% \cite{grahamdriver2007} TBD!!! ask Alister what did they do, not clear from appendix
-% ($n = 13.0$). 
-% \cite{fisherdrory2008} decomposed the galaxy in a S\'ersic-bulge + exponential disk 
-% ($R_{\rm e} = 31''.0$, $n = 3.9$). 
-% %\cite{sani2011} modeled NGC 3115 with a S\'ersic-bulge + exponential disk 
-% %($R_{\rm e} = 27''.3$, $n = 3.0$). 
-% %\cite{lasker2014data} used a S\'ersic-bulge + exponential disk + S\'ersic-envelope 
-% %($R_{\rm e} = 3''.9$, $n = 3.0$). 
-%
-% \emph{1D fit -- }
-% NGC 3115 is an example of a galaxy with an intermediate scale disk.
-% The surface brightness profile of NGC 3115 does not have an exponential decline at large radii 
-% because the disk component does not dominate the outer regions of the galaxy.
-% This is immediately evident by looking at the ellipticity and B4 profiles.
-% Going from the galaxy center to the outskirts, the ellipticity increases until it reaches its maximum 
-% ($\epsilon \sim 0.65$) at $R \sim 90''$. 
-% After this point, it starts declining, being as low as $\epsilon \sim 0.55$ at $R \sim 240''$. 
-% The galaxy isophotes display a positive diskyness within $R \sim 90''$, but become perfect ellipses 
-% ($B4 \sim 0$) beyond that point.
-% Now, because galaxy disks typically have fixed ellipticity, reflecting their inclination to our line of sight,
-% the previous observations tell us that, going from the galaxy center to the outer regions,
-% the disk of NGC 3115 becomes increasingly important relative to the spheroid light, reaching its maximum at $R \sim 90''$.
-% Beyond $R \gtrsim 90''$, the contribution from the disk light starts declining more rapidly than the spheroid light.
-% This interpretation is supported by the results of \cite{arnold2011n3115},
-% who found that within $R \sim 110''$ the bulge of NGC 3115 is flattened and rotates rapidly ($v/\sigma \gtrsim 1.5$),
-% whereas at larger radii the rotation declines dramatically (to $v/\sigma \sim 0.7$), 
-% but remains well aligned with the inner regions. \\
-% From an inspection of the unsharp mask, we identify a faint nuclear edge-on ring ($R \sim 15''$), 
-% which produces a corresponding peak in the ellipticity profile. \\
-% %We build our model with a S\'ersic-bulge + exponential disk + Gaussian-ring. \\
-% We do not observe any nuclear excess of light in the 1D residuals, 
-% contrary to what we expected given the presence of a nuclear stellar disk. 
-% The addition of a PSF component to the final model does not significantly change the outcome of the fit. 
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3115_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3115.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3115.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + G-r & $43.6$  &  $4.4$ \\
-% T.W. 1D eq.  & S-bul + e-d + G-r & $34.4$  &  $5.1$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% GD07         & ??? TBD	       & $-$	&  $13.0$ \\
-% S+11         & S-bul + e-d	       & $27.1$ &  $3.0$ \\
-% L+14         & S-bul + e-d + S-halo  & $3.9$  &  $3.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3115}
-% \end{table}
-%   
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3227 \\}
-%
-% NGC 3227 is a spiral galaxy with a large-scale bar. 
-% This galaxy hosts a Seyfert AGN \citep{khachikian1974} and circumnuclear dust \citep{martini2003}. 
-%
-% %\cite{laurikainen2004} decomposed NGC 3227 into a S\'ersic-bulge + exponential-disk + Ferrer-bar 
-% %($R_{\rm e} = 1''.8$, $n = 2.2$). 
-% %\cite{sani2011} described this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 82''.9$, $n = 4.0$). 
-% %\cite{lasker2014data} used a S\'ersic-bulge + exponential disk + S\'ersic-bar 
-% %($R_{\rm e} = 0''.7$, $n = 4.1$). 
-%
-% \emph{1D fit -- }
-% The large-scale bar produces an evident bump in the major-axis surface brightness profile,
-% which is curiously absent in the equivalent-axis profile. \\
-% We modeled the bar with a Ferrer function and the nucleus with a Gaussian function. 
-% As expected, the Ferrer component is rejected by the equivalent-axis fit.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3227_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3227.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3227.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-n   & $8.1$  &  $1.7$ \\
-% T.W. 1D eq.  & S-bul + e-d + [F-bar] + G-n & $4.6$  &  $1.1$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% L+04         & S-bul + e-d + F-bar & $1.8$  &  $2.2$ \\
-% S+11         & S-bul + e-d	     & $82.9$ &  $4.0$ \\
-% L+14         & S-bul + e-d + S-bar & $0.7$  &  $4.1$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3227}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3245 \\}
-%
-% NGC 3245 is a lenticular galaxy.
-%
-% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 11''.3$, $n = 4.3$). 
-% %\cite{laurikainen2010} described the galaxy with a S\'ersic-bulge + exponential-(disk+lens) + Ferrer-inner disk 
-% %($R_{\rm e} \sim 4''$, $n = 2.4$).  
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 4''.6$, $n = 2.5$). 
-% %\cite{vika2012} employed a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 3''.5$, $n = 2.6$). 
-% %\cite{beifiori2012} decomposed the galaxy into a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 4''.00$, $n = 1.6$). 
-% %\cite{lasker2014data} built their model with a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
-% %($R_{\rm e} = 1''.95$, $n = 1.6$). 
-%
-% \emph{1D fit -- }
-% The unsharp mask reveals the presence of an embedded disk ($R \lesssim 15''$), 
-% confirmed by the corresponding peaks in the ellipticity and B4 profiles.
-% We model this inner component with a Ferrer function.
-% %We model the galaxy with a S\'ersic-bulge + exponential-disk + Ferrer-inner disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3245_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3245.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3245.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-id & $4.4$  &  $2.9$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-id & $2.4$  &  $1.7$ \\
-% T.W. 2D      & S-bul + e-d + G-id & $1.9$  &  $1.8$ \\
-% \hline
-% GD07         & S-bul + e-d		& $11.3$ &  $4.3$ \\
-% L+10         & S-bul + e-(d+l) + F-id & $4.0$  &  $2.4$ \\
-% S+11         & S-bul + e-d		& $4.6$  &  $2.5$ \\
-% V+12         & S-bul + e-d		& $3.5$  &  $2.6$ \\
-% B+12         & S-bul + e-d		& $4.0$  &  $1.6$ \\
-% L+14         & S-bul + e-d + S-bar	& $2.0$  &  $1.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3245}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 3377 \\}
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3377.}
-% \end{center}
-% \end{figure}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3384 \\}
-%
-% NGC 3384 is a barred lenticular galaxy that hosts 
-% an embedded disk ($R \lesssim 11''$, \citealt{erwin2004}) and 
-% a nuclear stellar disk ($R \lesssim 0''.8$, \citealt{ledo2010}).
-%
-% %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 2''.5$, $n = 1.7$). 
-% %\cite{laurikainen2010} described the galaxy with a S\'ersic-bulge + exponential-disk + 2 Ferrer-bars
-% %($R_{\rm e} \sim 4''$, $n = 1.5$).  
-% %\cite{sani2011} employed a S\'ersic-bulge + exponential-disk + Gaussian-bar 
-% %($R_{\rm e} = 4''.4$, $n = 2.5$). 
-% %\cite{beifiori2012} modeled the galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 8''.3$, $n = 2.3$). 
-% %\cite{lasker2014data} decomposed the galaxy into a S\'ersic-bulge + exponential-disk + S\'ersic-inner disk + 
-% %S\'ersic-nuclear disk + S\'ersic-bar
-% %($R_{\rm e} = 5''.9$, $n = 2.5$). 
-%
-% \emph{1D fit -- }
-% The isophotal parameters clearly show the presence of a boxy bar that extends out to $R \lesssim 18''$.
-% We model the bar with a Ferrer function.
-% An embedded disk can be seen in the unsharp mask and produces the peak in the ellipticity profile at $R \sim 4''$.
-% modeling the embedded disk turned out to be a complicated task, resulting in a degenerate model.
-% We elected not to fit the embedded disk (nor the nuclear disk) and we therefore excluded from the fit the innermost $3''.7$,
-% where there two components are expected to dominate.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3384_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3384.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3384.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + m-n & $5.5$  &  $1.6$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + m-n & $5.6$  &  $1.8$ \\
-% %T.W. 2D	&  & $$  &  $$ \\
-% \hline
-% GD07         & S-bul + e-d		      & $2.5$  &  $1.7$ \\
-% L+10         & S-bul + e-d + 2 F-bar        & $4.0$  &  $1.5$ \\
-% S+11         & S-bul + e-d + G-bar	      & $4.4$  &  $2.5$ \\
-% B+12         & S-bul + e-d		      & $8.3$  &  $2.3$ \\
-% L+14         & S-bul + e-d + 2 S-id + S-bar & $5.9$  &  $2.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3384}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3393 \\}
-%
-% NGC 3393 is an edge-on spiral galaxy hosting a Seyfert AGN \citep{diaz1988n3393} and 
-% circumnuclear dust \citep{martini2003}.
-% The galaxy has a large-scale bar and a nuclear bar ($R \lesssim 3''$, \citealt{erwin2004}).  
-%
-% \emph{1D fit -- }
-% The large-scale bar ($R \lesssim 20''$) is modeled with a Ferrer function.
-% The poor spatial resolution of the data does not allow to fit the nuclear bar and/or the AGN component 
-% without incurring degeneracies.
-% We thus elected not to fit the nuclear components.
-% We note that the addition to the model of a central component would lower the bulge S\'ersic index,
-% whereas the the addition of a nuclear bar component would increase the bulge S\'ersic index.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3393_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3393.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3393.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $1.4$  &  $3.4$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $1.4$  &  $2.6$ \\
-% T.W. 2D      & S-bul + e-d + G-bar & $1.2$  &  $1.9$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3393}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3414 \\}
-%
-% NGC 3414 is a peculiar lenticular/elliptical galaxy. 
-% Different interpretations have been proposed about the morphology of this galaxy.
-% \cite{whitmore1990} suggested that NGC 3414 is an edge-on galaxy 
-% with a large scale polar ring, rather than a face-on barred lenticular.
-% \cite{laurikainen2010} decomposed NGC 3414 as a barred lenticular galaxy, but 
-% they cautioned against the uncertainty of their solution due to the possible misinterpretation of the 
-% galaxy morphology.
-%
-% \emph{1D fit -- }
-% The unsharp mask clearly shows that the edge on component does not extend all the way through the 
-% center of the galaxy, but instead it is truncated at $R \sim 20''$.
-% However, an elongated structure in the galaxy center resembles a nuclear edge-on disk ($R \lesssim 5''$).
-% The velocity map shows rotation within $R \lesssim 5''$ and no rotation within $5'' \lesssim R \lesssim 15''$.
-% Beyond $R \gtrsim 15''$ one can recognize a sign of rotation in the opposite direction of the nuclear region.
-% The velocity pattern is consistent with the galaxy being a spheroidal system containing a polar ring and a nuclear disk
-% both seen edge-on.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3414_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3414.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3414.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-id + G-r & $28.0$  &  $4.8$ \\
-% T.W. 1D eq.  & S-bul + e-id + G-r & $25.5$  &  $4.5$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% L+10         & S-bul + e-d + F-bar	  & $5.0$  &  $2.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3414}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3489 \\}
-%
-% NGC 3489 is a barred lenticular galaxy. 
-% Its disk has a smooth antitruncation at $R \sim 85''$ \citep{erwin2008}.
-%
-% \cite{nowak2010n3368n3489} argued for the presence of both a pseudo-bulge and a classical bulge. 
-% %\cite{laurikainen2010} fit this galaxy with a S\'ersic-bulge + exponential-disk + Ferrer-bar
-% %($R_{\rm e} \sim 2''$, $n = 2.1$). 
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 4''.6$, $n = 1.5$). 
-%
-% \emph{1D fit -- }
-% We excluded the data beyond $R \gtrsim 38''$ to avoid fitting the antitruncation region.
-% The bar is fit with a Ferrer function.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3489_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3489.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3489.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar & $2.2$  &  $1.5$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar & $1.7$  &  $1.3$ \\
-% T.W. 2D      & S-bul + e-d + G-bar & $1.7$  &  $2.1$ \\
-% \hline
-% L+10         & S-bul + e-d + F-bar & $2.0$  &  $2.1$ \\
-% S+11         & S-bul + e-d & $4.6$  &  $1.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3489}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 3585 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3585.}
-% \end{center}
-% \end{figure}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 3607 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3607.}
-% \end{center}
-% \end{figure}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 3608 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3608.}
-% \end{center}
-% \end{figure}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3842 \\}
-%
-% NGC 3842 is the brightest member of the Leo Cluster (Abell 1367).
-% It is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.7$, 
-% \citealt{rusli2013,dullograham2014cores}).
-%
-% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic model 
-% %($R_{\rm e} = 58''.8$, $n = 6.3$). 
-%
-% \emph{1D fit -- }
-% The light profile presents a swelling at $R \sim 20''$ and the ellipticity profile has a peak in the same position.
-% One can also glimpse a faint elongated oval in the unsharp mask.
-% The innermost $6''.1$ are excluded from the fit due to the presence of a partially depleted core.
-% As expected, a single S\'ersic model is not sufficient to provide a good description of the galaxy light profile 
-% and we need to add a second component (Ferrer function) to account for the embedded lens.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3842exp_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3842.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3842.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + F-l + m-c  & $100.7$  &  $8.1$ \\
-% T.W. 1D eq.  & S-bul + F-l + m-c  & $73.6$   &  $8.2$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% R+13         & core-S\'ersic & $58.8$  &  $6.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3842}
-% \end{table}  
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 3998 \\}
-%
-% NGC 3998 is a barred lenticular galaxy with a Seyfert AGN and dust in its nucleus \citep{knapp1996n3998}.
-% Despite its large stellar velocity dispersion, this galaxy does not have a partially depleted core TBD!! ref??. 
-% \cite{gutierrez2011} identified a bar at $R \lesssim 8''$, a ring between $30'' \lesssim R \lesssim 50''$, and  
-% an antitruncation in the light profile of the disk at $R \sim 122''$.
-% \cite{laurikainen2010} found that NGC 3998 features a weak bar at $R < 8''$,
-% a bright lens at $R < 15''$ and a weak bump in the surface brightness profile at $R \sim 40''$ 
-% %($R_{\rm e} \sim 5''$, $n = 2.0$).
-% %\cite{sani2011} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN 
-% %($R_{\rm e} = 4''.7$, $n = 1.5$).
-% %\cite{beifiori2012} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 5''.7$, $n = 2.3$).
-% %\cite{lasker2014data} used a S\'ersic-bulge + exponential-disk (with inner truncation) + PSF-nucleus + 
-% %S\'ersic-inner disk + S\'ersic-bar 
-% %($R_{\rm e} = 2''.0$, $n = 1.1$).
-%
-% \emph{1D fit -- }
-% We see three distinct peaks in the ellipticity profile.
-% The first two peaks occur at $R \sim 7''$ and $R \sim 15''$, and they correspond to a weak bar and to a faint 
-% oval component respectively.
-% These components are both fit with a Ferrer function.
-% The third peak at $R \sim 35''$ coincides with a bump in the surface brightness profile and is produced by a ring.
-% The AGN component is modeled with a Gaussian profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n3998_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 3998.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 3998.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + F-l + G-n + G-r & $5.8$  &  $1.2$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + F-l + G-n + G-r & $4.8$  &  $1.3$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% L+10         &  & $5.0$  &  $2.0$ \\
-% S+11         & S-bul + e-d + G-bar + G-n & $4.7$  &  $1.5$ \\
-% B+12         & S-bul + e-d & $5.7$  &  $2.3$ \\
-% L+14         & S-bul + trunc. e-d + PSF-n + S-bar + S-id & $2.0$  &  $1.1$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n3998}
-% \end{table} 
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4026 \\}
-%
-% NGC 4026 is an edge-on lenticular galaxy with a nuclear stellar disk ($R \lesssim 0''.5$, \citealt{ledo2010}).
-%
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 11''.4$, $n = 3.5$).
-%
-% \emph{1D fit -- }
-% The unsharp mask reveals the presence of a bar ($R \lesssim 30''$) and of a disky component 
-% embedded in the bulge, that is responsible for the peak at $R \sim 5''$ in the B4 profile.
-% The last can be also recognized in the velocity map.
-% The bar is fit with a Ferrer function and the inner disk with a low-$n$ S\'ersic profile.
-% Due to the poor spatial resolution of our data, we were not able to model the nuclear stellar disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4026_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4026.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4026.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + S-id & $3.4$  &  $2.4$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + S-id & $6.3$  &  $2.1$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% S+11         & S-bul + e-d & $11.4$  &  $3.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4026}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4151 \\}
-%
-% NGC 4151 is a face-on barred spiral galaxy that hosts a Seyfert AGN \citep{veroncettyveron2006} 
-% and circumnuclear dust \citep{pott2010}.
-%
-% \cite{sani2011} fit this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-AGN model
-% ($R_{\rm e} = 5''.4$, $n = 3.5$).
-% \cite{gadotti2008} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar + PSF-AGN 
-% ($R_{\rm e} = 4''.7$, $n = 3.0$).
-%
-% \emph{1D fit -- }
-% embedded disk in the bulge,
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4151_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4151.}
-% \end{center}
-% \end{figure}
-%
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4261 \\}
-%
-% NGC 4261 is an elliptical galaxy with %a radio jet \citep{liuxie1992}, 
-% a LINER nucleus \citep{veroncettyveron2006}
-% and a dusty nuclear disk \citep{tran2001}.
-% The galaxy features a partially depleted core ($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
-%
-% %\cite{grahamdriver2007} fit NGC 4261 with a single S\'ersic-bulge 
-% %($R_{\rm e} = 88''.6$, $n = 7.3$).
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model 
-% %($R_{\rm e} = 22''.6$, $n = 4.0$).
-% %\cite{vika2012} employed a S\'ersic-bulge + mask-core 
-% %($R_{\rm e} = 24''.2$, $n = 3.5$).
-% %\cite{beifiori2012} adopted a single S\'ersic-bulge model 
-% %($R_{\rm e} = 48''.8$, $n = 4.3$).
-% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
-% %($R_{\rm e} = 77'.1$, $n = 6.3$).
-% %\cite{lasker2014data} employed a S\'ersic-bulge + mask-core model 
-% %($R_{\rm e} = 68'.4$, $n = 6.5$).
-%
-% \emph{1D fit -- }
-% The ellipticity profile has a peak at $R \sim 10''$, unraveling the presence of an embedded component.
-% We identify such component with an inner disk, possibly seen face-on, and we model it with a Ferrer function.
-% The innermost $6''.1$ are excluded from the fit due to the presence of a partially depleted core.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4261_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4261.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4261.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c + F-id & $52.6$  &  $4.7$ \\
-% T.W. 1D eq.  & S-bul + m-c + F-id & $47.3$  &  $4.3$ \\
-% T.W. 2D      & S-bul + m-c + e-id & $50.4$  &  $4.4$ \\
-% \hline
-% GD07      & S-bul		& $88.6$  &  $7.3$ \\
-% S+11      & S-bul + e-d + G-n & $22.6$  &  $4.0$ \\
-% V+12      & S-bul + m-c	& $24.2$  &  $3.5$ \\
-% B+12      & S-bul		& $48.8$  &  $4.3$ \\
-% R+13      & core-S\'ersic	& $77.1$  &  $6.3$ \\
-% L+14      & S-bul + m-c	& $68.4$  &  $6.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4261}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4291 \\}
-%
-% NGC 4291 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
-%
-% %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 14'.8$, $n = 4.0$).
-% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
-% %($R_{\rm e} = 15''.3$, $n = 5.6$).
-% %\cite{lasker2014data} adopted a S\'ersic-bulge + mask-core model
-% %($R_{\rm e} = 21''.3$, $n = 8.6$).
-%
-% \emph{1D fit -- }
-% After excluding from the fit the innermost $6''.1$, because affected by the partially depleted core,
-% we found that NGC 4291 can be modeled with a single S\'ersic profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4291_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4291.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4291.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $15.0$  &  $4.2$ \\
-% T.W. 1D eq.  & S-bul + m-c & $15.4$  &  $5.9$ \\
-% T.W. 2D      & S-bul + m-c & $20.8$  &  $7.7$ \\
-% \hline
-% GD07         & S-bul         & $14.8$  &  $4.0$ \\
-% R+13         & core-S\'ersic & $15.3$  &  $5.6$ \\
-% L+14         & S-bul + m-c   & $21.3$  &  $8.6$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4291}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4388 \\}
-%
-% NGC 4388 is an edge-on spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006} 
-% and copious nuclear dust \citep{martini2003}.
-%
-% \emph{1D fit -- }
-% The peaks at $R \sim 30''$ in the ellipticity and B4 profiles signal the presence of a bar.
-% The data between $35'' \lesssim R \lesssim 65''$ have been excluded because cannot be accommodated by the Ferrer function 
-% used to describe the bar. 
-% The AGN component is fit with a Gaussian profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4388_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4388.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4388.}
-% \begin{center}
-% \begin{tabular}{llccc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $4.6$  &  $0.6$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.2$  &  $1.3$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4388}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4459 \\}
-%
-% NGC 4459 is a lenticular galaxy.
-% Its disk profile is reported to have an antitruncation at $R \sim 119''$ \citep{gutierrez2011}.
-%
-% %\cite{laurikainen2010} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Ferrer-lens 
-% %($R_{\rm e} \sim 7'' $, $n = 3.0$).
-% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 10''.3$, $n = 2.5$).
-% %\cite{vika2012} modeled this galaxy with a S\'ersic-bulge + Moffat-nucleus 
-% %($R_{\rm e} = 25''.0$, $n = 3.9$).
-% %\cite{beifiori2012} adopted a single S\'ersic-bulge model 
-% %($R_{\rm e} = 155''.2$, $n = 7.4$).
-%
-% \emph{1D fit -- }
-% The ellipticity constantly increases across all the observed radial range ($R \lesssim 100''$).
-% This is an indication that, going from the galaxy center to the outskirts,
-% the disk component becomes increasingly more important than the spheroidal component.
-% However, the lack of a plateau in the ellipticity profile at large radii implies that at $R \sim 100''$ 
-% the contribution from the bulge is still significant compared to that of the disk.
-% In fact, the surface brightness profile does not display an exponential decline at large radii.
-% We note that the antitruncation reported by \cite{gutierrez2011} could be an artificial feature 
-% produced by the transition between the radial range where the disk becomes increasingly more important 
-% over the bulge and the truly exponential decline of the disk beyond $R \gtrsim 119''$.
-% We do not find evidence for any embedded components in our data.
-% A nuclear light excess is observed in the 1D residuals from a S\'ersic + exponential fit 
-% and is consequently modeled with a Gaussian profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4459_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4459.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4459.}
-% \begin{center}
-% \begin{tabular}{llccc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + G-n & $18.4$  &  $3.1$ \\
-% T.W. 1D eq.  & S-bul + e-d + G-n & $13.0$  &  $2.6$ \\
-% %T.W. 2D	&  & $$  &  $$ \\
-% \hline
-% L+10      & S-bul + e-d + F-l & $7.0$   &  $3.0$ \\
-% S+11      & S-bul + e-d	& $10.3$  &  $2.5$ \\
-% V+12      & S-bul + M-n	& $25.0$  &  $3.9$ \\
-% B+12      & S-bul		& $155.2$ &  $7.4$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4459}
-% \end{table}
-%
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4473 \\}
-%
-% NGC 4473 is an elliptical galaxy with an embedded disk \citep{scorzabender1998,ledo2010}.
-%
-% \cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
-% ($R_{\rm e} = 39''.6$, $n = 2.7$). 
-% \cite{sani2011} used a S\'ersic-bulge model
-% ($R_{\rm e} = 49''.3$, $n = 7.0$). 
-% \cite{vika2012} fit this galaxy with a S\'ersic-bulge + mask-core 
-% ($R_{\rm e} = 21''.3$, $n = 4.3$). 
-% \cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model 
-% ($R_{\rm e} = 10''.6$, $n = 2.2$).  
-% \cite{lasker2014data} described this galaxy with a single S\'ersic-bulge 
-% ($R_{\rm e} = 27''.9$, $n = 5.1$).  
-%
-%
-% \emph{1D fit -- }
-% TBD!! explain ellipticity profile...
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4473_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4473.}
-% \end{center}
-% \end{figure}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4564 \\}
-%
-% NGC 4564 is an edge-on lenticular galaxy.
-%
-% %\cite{grahamdriver2007} decomposed this galaxy into a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 4''.3$, $n = 3.2$). 
-% \cite{fisherdrory2008} fit this galaxy with a S\'ersic-bulge + exponential-disk 
-% ($R_{\rm e} = 8''.7$, $n = 3.7$). 
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-% %($R_{\rm e} = 25''.0$, $n = 7.0$).
-% %\cite{vika2012} used a S\'ersic-bulge + exponential-disk model 
-% %($R_{\rm e} = 3''.0$, $n = 3.7$). 
-%
-% \emph{1D fit -- }
-% The isophotal parameters do not show any evidence for embedded components.
-% However, fitting NGC 4564 with a S\'ersic + exponential model results in bad residuals.
-% In the unsharp mask, one can hardly glimpse an oval structure extending out to $R \lesssim 15''$.
-% The addition of a Ferrer function to the model dramatically improves the fit and smoothes the residuals.
-% Although the lack of strong evidence for the presence of a (faint) third component, 
-% we prefer to model the lens with a Ferrer function 
-% because of the notable improvement in the goodness of the global fit.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4564_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4564.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4564.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-l & $5.0$  &  $2.6$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-l & $6.0$  &  $3.0$ \\
-% %T.W. 2D	&  & $$  &  $$ \\
-% \hline
-% GD07      & S-bul + e-d & $4.3$  &  $3.2$ \\
-% S+11      & S-bul + e-d & $25.0$ &  $7.0$ \\
-% V+12      & S-bul + e-d & $3.0$  &  $3.7$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4564}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4596 \\}
-%
-% NGC 4596 is an edge-on barred lenticular galaxy.
-%
-% %\cite{laurikainen2005} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Ferrer-bar + Ferrer-lens 
-% %($R_{\rm e} = 2''.8$, $n = 1.4$). 
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-bar 
-% %($R_{\rm e} = 28''.0$, $n = 3.0$). 
-% %\cite{vika2012} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
-% %($R_{\rm e} = 13''.2$, $n = 3.6$). 
-% %\cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model
-% %($R_{\rm e} = 44''.9$, $n = 4.4$).
-%
-% \emph{1D fit -- }
-% The morphology of this galaxy is quite complex. 
-% The bar extends out to $R \lesssim 50''$ and concludes in two evident ansae.
-% The large-scale disk features a wide ring that is responsible for the curvature in the light profile observed within 
-% $60'' \lesssim R \lesssim 130''$ (see also \citealt{comeron2014}).
-% An additional embedded disk-like component ($R \lesssim 15''$) can be recognized in the B4 profile and in the velocity map.
-% The bump in the light profile within $60'' \lesssim R \lesssim 70''$ corresponds to the ansae of the bar.
-% This data range has therefore been excluded from the fit.
-% The large scale bar is fit with a Ferrer function and the inner disk with a S\'ersic profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4596_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4596.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4596.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-r + S-id & $6.6$  &  $2.7$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + G-r + S-id & $9.0$  &  $3.0$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% L+05      & S-bul + e-d + F-bar + F-l & $2.8$  &  $1.4$ \\
-% S+11      & S-bul + e-d + G-bar & $28.0$  &  $3.0$ \\
-% V+12      & S-bul + e-d + S-bar & $13.2$  &  $3.6$ \\
-% B+12      & S-bul + e-d & $44.9$  &  $4.4$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4596}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4697 \\}
-%
-% NGC 4697 is an elliptical galaxy with an embedded disk \cite{scorzabender1995}.
-%
-% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge model
-% %($n = 4.0$).
-% %\cite{sani2011} described it with a S\'ersic-bulge 
-% %($R_{\rm e} = 100'.5$, $n = 5.0$). 
-% %\cite{vika2012} proposed a single S\'ersic-bulge model 
-% %($R_{\rm e} = 39''.1$, $n = 3.8$) 
-% %or a S\'ersic-bulge + exponential-disk model 
-% %($R_{\rm e} = 10''.0$, $n = 2.9$).
-% %\cite{beifiori2012} chose a single S\'ersic-bulge 
-% %($R_{\rm e} = 128''.7$, $n = 5.0$).
-% %\cite{lasker2014data} decomposed NGC 4697 into a S\'ersic-bulge + exponential-disk + PSF-nucleus + S\'ersic-envelope 
-% %($R_{\rm e} = 6''.3$, $n = 2.1$).
-%
-% \emph{1D fit -- }
-% The velocity map and the unsharp mask of NGC 4697 clearly show 
-% the presence of an intermediate-size disk embedded in the main spheroid.
-% However, the ellipticity profile presents two peaks. 
-% The peak at $R \sim 40''$ corresponds to the embedded disk already mentioned,
-% while the peak at $R \sim 10''$ unveils a second inner disk-like component.
-% After testing different decomposition models, 
-% in which we fit the embedded disks with a set of different functions (exponential, S\'ersic, Ferrer)
-% but we always described the main spheroidal component with a S\'ersic profile,
-% we noticed that the bulge parameters did not vary significantly among the various decompositions.
-% Our preferred model for NGC 4697 consists of a S\'ersic-bulge + 2 S\'ersic-inner disks.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4697_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4697.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4697.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + 2 S-id & $239.3$  &  $7.2$ \\
-% T.W. 1D eq.  & S-bul + 2 S-id & $226.4$  &  $6.7$ \\
-% T.W. 2D      & S-bul + e-id	& $121.4$  &  $5.0$ \\
-% \hline
-% GD07  & S-bul & $-$  &  $4.0$ \\
-% S+11  & S-bul & $100.5$  &  $5.0$ \\
-% V+12  & S-bul & $39.1$  &  $3.8$ \\
-% V+12  & S-bul + e-d & $10.0$  &  $2.9$ \\
-% L+14  & S-bul + e-d + PSF-n + S-halo & $6.3$  &  $2.1$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4697}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4889 \\}
-%
-% NGC 4889 is the brightest member of the Coma cluster. 
-% It is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.6$, \citealt{rusli2013}).
-%
-% %\cite{rusli2013} modeled NGC 4889 with a core-S\'ersic model 
-% %($R_{\rm e} = 169''.2$, $n = 9.8$). 
-%
-% \emph{1D fit -- }
-% We excluded from the fit the innermost $6''.1$ because affected by the partially depleted core and
-% we modeled the galaxy with a single S\'ersic profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4889.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4889.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $119.7$  &  $8.1$ \\
-% T.W. 1D eq.  & S-bul + m-c & $60.8$	&  $6.8$ \\
-% T.W. 2D      & S-bul + m-c & $104.3$  &  $7.8$ \\
-% \hline
-% R+13         & core-S\'ersic & $169.2$  &  $9.8$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4889}
-% \end{table}
-%   
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 4945 \\}
-%
-% TBD!!! \\
-% NGC 4945 is an edge-on, dusty spiral galaxy that hosts a Seyfert AGN \citep{lin2011}.
-%
-% \cite{kormendy2010} found that the bulge of NGC 4945 is best modeled with a low-$n$ S\'ersic function
-% ($n = 1.3$).
-%
-% \emph{1D fit -- }
-% Given the edge-on inclination of this object, the identification of a possible large-scale bar is complicated.
-% The light profile has an obvious bump that could be interpreted in two different ways.
-% The bump could be produced by a large-scale bar; 
-% in this case, either the disk must have a truncation happening at a radius smaller than the length of the bar,
-% or its light profile cannot be exponential (this condition can be caused by the high inclination of the galaxy).
-% Alternatively, the bump could be due by the galaxy spiral arms, the disk has an exponential profile with no truncation
-% and the galaxy has no bar.
-% After checking that both scenarios result in similar best-fit parameters for the bulge, 
-% we choose the second and simpler hypothesis.
-% We exclude form the fit the data between $R \sim 100''-400''$, where the spiral arm would contribute to the galaxy light,
-% and we also exclude the innermost $6''.4$ due to the presence of the AGN.
-% Our final model for NGC 4945 consists of a S\'ersic-bulge + exponential-disk.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4945_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 4945.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 4945.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d & $13.9$  &  $1.4$ \\
-% T.W. 1D eq.  & S-bul + e-d & $9.5$   &  $1.7$ \\
-% T.W. 2D      & S-bul + e-d & $16.2$  &  $0.8$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n4945}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 5077 \\}
-%
-% ok
-%
-% \emph{1D fit -- }
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n5077_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 5077.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 5077.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $23.5$  &  $4.2$ \\
-% T.W. 1D eq.  & S-bul + m-c & $23.0$  &  $5.7$ \\
-% T.W. 2D      & S-bul + m-c & $30.5$  &  $6.8$ \\
-% \hline
-% S+11         & S-bul + G-n & $29.2$  &  $6.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n5077}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 5128 - Centaurus A \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n5128_1Dfit.eps}
-% \caption{}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 5128.}
-% \begin{center}
-% \begin{tabular}{llccc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & TBD!! & $61.3$  &  $1.2$ \\
-% T.W. 1D eq.  &  & $60.8$  &  $2.2$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% S+11         & S-bul + e-d + G-n & $103.6$  &  $3.5$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n5128}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-%
-% {\bf NGC 5576 \\}
-%
-% ok
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
-% \caption{}
-% \end{center}
-% \end{figure}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 5845 \\}
-%
-% NGC 5845 is an elliptical/lenticular galaxy. 
-%
-% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 4''.1$,$n = 3.2$).
-% %\cite{sani2011} fit it with a S\'ersic-bulge 
-% %($R_{\rm e} = 3''.7$, $n = 3.0$). 
-% %\cite{vika2012} used a S\'ersic-bulge model 
-% %($R_{\rm e} = 3''.5$, $n = 2.6$).
-% %\cite{beifiori2012} chose a single S\'ersic-bulge 
-% %($R_{\rm e} = 4''.1$, $n = 3.5$).
-% %\cite{lasker2014data} described this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 3''.5$, $n = 2.8$).
-%
-% \emph{1D fit -- }
-% The small apparent size of NGC 5845 (compared to the PSF FWHM) implies low resolution for the data 
-% and complications for the modeling of this galaxy.
-% Here, looking at the unsharp mask and the velocity field, we identify 
-% a disk component, either large-scale or embedded.
-% To rule out one of the two cases, a good test would be to check whether
-% the light profile of NGC 5845 presents an exponential decline in its outer part.
-% Unfortunately, the IRAC image is not deep enough and beyond $R \gtrsim 23''$ the galaxy light 
-% is fainter than $3 RMS_{\rm SKY}$.
-% %Since the too small radial range prevents us from disentangling between an embedded and a large-scale disk,
-% %we choose the most statistically significant solution (lowest $\chi^2$), 
-% %but we caution that the best fit parameters might be biased by a non adequate choice
-% %of the model components. 
-% %However, our results are in agreement with those from \cite{jia2012}, 
-% %who study the structure and kinematics of NGC5845 with HST/WFPC2 data 
-% %and previously published spatially resolved kinematics, and unambiguously identify a 
-% %large scale disk in both the photometry and the kinematics. \\
-% The ellipticity profile has a peak at $R \sim 13''$ and therefore suggests that the disk is indeed embedded.
-% However, when fitting NGC 5845 with a S\'ersic + exponential model, 
-% the lowest-$\chi^2$ solution does not reproduce an inner disk, but rather a large-scale one.
-% This is because the S\'ersic and the exponential function are degenerate in this decomposition, 
-% due to the small number of data points sampling the galaxy light profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n5845_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 5845.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 5845.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d & $3.6$  &  $2.5$ \\
-% T.W. 1D eq.  & S-bul + e-d & $3.1$  &  $2.3$ \\
-% T.W. 2D      & S-bul + e-d & $2.8$  &  $2.4$ \\
-% \hline
-% GD07      & S-bul & $4.1$  &  $3.2$ \\
-% S+11      & S-bul & $3.7$  &  $3.0$ \\
-% V+12      & S-bul & $3.5$  &  $2.6$ \\
-% B+12      & S-bul & $4.1$  &  $3.5$ \\
-% L+14      & S-bul & $3.5$  &  $2.8$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n5845}
-% \end{table}
-%
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 5846 \\}
-%
-% NGC 5846 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
-% This galaxy has a LINER nucleus \citep{carrillo1999} and filamentary nuclear dust \citep{tran2001}.
-%
-% %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge
-% %($R_{\rm e} = 36''.4$, $n = 3.0$). 
-% %\cite{vika2012} used a S\'ersic-bulge + mask-core model 
-% %($R_{\rm e} = 46''.3$, $n = 3.7$). 
-% %\cite{rusli2013} fit this galaxy with a core-S\'ersic profile 
-% %($R_{\rm e} = 113''.2$, $n = 5.3$). 
-%
-% \emph{1D fit -- }
-% This galaxy has a strong isophotal twist between its center and $R \sim 70''$, and
-% its light profile presents a slight bump at $R \sim 20''$.
-% However, the isophotal parameters, the unsharp mask and the velocity map lack of clear evidence for an embedded component.
-% We thus model NGC 5846 with a single S\'ersic profile, after masking the innermost $6''.1$.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n5846_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 5846.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 5846.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $105.1$  &  $6.4$ \\
-% T.W. 1D eq.  & S-bul + m-c & $83.4$	&  $5.7$ \\
-% T.W. 2D      & S-bul + m-c & $85.1$	&  $5.2$ \\
-% \hline
-% S+11      & S-bul	    & $36.4$   &  $3.0$ \\
-% V+12      & S-bul + m-c   & $46.3$   &  $3.7$ \\
-% R+13      & core-S\'ersic & $113.2$  &  $5.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n5846}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 6251 \\}
-%
-% NGC 6251 is an elliptical galaxy with a large stellar velocity dispersion ($\sigma \sim 310~\rm km~s^{-1}$),
-% which is a clue for the presence of a partially depleted core.
-% The galaxy features a nuclear disk of dust \citep{ferrareseford1999n6251} and a Seyfert AGN \citep{panessabassani2002}.
-%
-% %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 173''.92$, $n = 11.8$). 
-% %\cite{sani2011} adopted a S\'ersic-bulge + Gaussian-AGN model 
-% %($R_{\rm e} = 42''.4$, $n = 7.0$). 
-% %\cite{lasker2014data} modeled this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 20''.6$, $n = 5.0$). 
-%
-% \emph{1D fit -- }
-% We masked the innermost $6''.1$ because possibly affected by the combined contribution of the AGN 
-% and the partially depleted core. 
-% A single S\'ersic profile provides a good description of NGC 6251.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n6251_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 6251.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 6251.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $41.7$  &  $6.8$ \\
-% T.W. 1D eq.  & S-bul + m-c & $30.1$  &  $5.6$ \\
-% T.W. 2D      & S-bul + m-c & $39.3$  &  $7.1$ \\
-% \hline
-% GD07      & S-bul	     & $173.9$  &  $11.8$ \\
-% S+11      & S-bul + G-n    & $42.4$	&  $7.0$ \\
-% L+14      & S-bul	     & $20.6$	&  $5.0$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n6251}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 7052 \\}
-%
-% NGC 7052 is an elliptical galaxy reported to have a partially depleted core 
-% ($R_{\rm break} = 0''.8$, \citealt{quillen2000}). 
-%
-% %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
-% %($R_{\rm e} = 70''.4$, $n = 4.6$). 
-% %\cite{sani2011} used a S\'ersic-bulge model 
-% %($R_{\rm e} = 39''.3$, $n = 5.0$). 
-% %\cite{vika2012} fit this galaxy with a S\'ersic-bulge + exponential-disk
-% %($R_{\rm e} = 4''.3$, $n = 1.8$).
-% %\cite{lasker2014data} adopted a S\'ersic-bulge model 
-% %($R_{\rm e} = 26''.6$, $n = 4.2$). 
-%
-% \emph{1D fit -- }
-% A single S\'ersic function provides a fairly good description of the surface brightness profile of NGC 7052.
-% However, the residuals of such fit display a curious behaviour, having a nuclear light excess along the major-axis 
-% and a nuclear light deficit along the equivalent-axis. 
-% This pattern is still present when the innermost $6''.1$ are excluded and the fit is repeated with a S\'ersic profile.
-% The reasons for this are unclear. 
-% The best-fit parameters obtained from a single S\'ersic fit, without excluding the innermost data points,
-% are not significantly different from those obtained when excluding the core region (see Table \ref{tab:n7052}).
-% Given the uncertainty connected to the nuclear region of this galaxy,
-% we preferred the model that incorporates the exclusion of the innermost $6''.1$, 
-% with the caveat about the ambiguous presence of a partially depleted core.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n7052_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 7052.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 7052.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% \multicolumn{4}{c}{\emph{excluding innermost $6''.1$}} \\
-% T.W. 1D maj. & S-bul + m-c & $59.4$  &  $4.2$ \\
-% T.W. 1D eq.  & S-bul + m-c & $37.0$  &  $5.6$ \\
-% T.W. 2D      & S-bul + m-c & $36.2$  &  $4.0$ \\
-% \hline
-% \multicolumn{4}{c}{\emph{including innermost $6''.1$}} \\
-% T.W. 1D maj. & S-bul & $66.1$  &  $4.8$ \\
-% T.W. 1D eq.  & S-bul & $35.0$  &  $5.0$ \\
-% %T.W. 2D	&  & $$  & $$  &  $$ \\
-% \hline
-% GD07      & S-bul & $70.4$  &  $4.6$ \\
-% S+11      & S-bul & $39.3$  &  $5.0$ \\
-% V+12      & S-bul + e-d & $4.3$  &  $1.8$ \\
-% L+14      & S-bul & $26.6$  &  $4.2$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n7052}
-% \end{table}
-%
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 7619 \\}
-%
-% NGC 7619 is an elliptical galaxy reported to have a partially depleted core ($R_{\rm break} = 0''.5$, \citealt{rusli2013}).
-%
-% %\cite{rusli2013} fit this galaxy with a core-S\'ersic profile 
-% %($R_{\rm e} = 100''.1$, $n = 9.3$). 
-%
-% \emph{1D fit -- }
-% We identified an embedded disk signaled by the peak at $R \sim 10''$ in the ellipticity profile.
-% The velocity map of this galaxy confirms the presence of a fast rotating component (Falcon-Barroso private comm.).
-% We modeled NGC 7619 with a S\'ersic + inner-exponential model.
-% We note that the residuals obtained from our best-fit model do not suggest the presence of a partially depleted core,
-% whereas they display a nuclear lack of light when the galaxy is modeled with a single S\'ersic-bulge. 
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n7619_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 7619.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 7619.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-id & $63.2$  &  $5.3$ \\
-% T.W. 1D eq.  & S-bul + e-id & $58.0$  &  $5.2$ \\
-% \hline
-% R+13      & core-S\'ersic & $100.1$  &  $9.3$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n7619}
-% \end{table}
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf NGC 7768 \\}
-%
-% NGC 7768 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
-%
-% %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
-% %($R_{\rm e} = 46''.1$, $n = 6.2$). 
-%
-% \emph{1D fit -- }
-% The image of NGC 7768 is corrupted by a saturated star, which lies close to the galaxy.
-% The sky background is not constant across the image.
-% To be safe, we fit only the innermost $R \lesssim 30''$, where the contribution from the background is negligible.
-% The data within $R < 6''.1$ are excluded from the fit due to the presence of a partially depleted core.
-% Our best-fit model consists of a single S\'ersic profile.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/n7768_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for NGC 7768.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for NGC 7768.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + m-c & $92.9$  &  $8.4$ \\
-% T.W. 1D eq.  & S-bul + m-c & $42.1$  &  $6.7$ \\
-% \hline
-% R+13      & core-S\'ersic & $46.1$  &  $6.2$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:n7768}
-% \end{table}
-%  
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \clearpage\newpage\noindent
-% {\bf UGC 03789 \\}
-%
-% UGC 03789 is a face-on spiral galaxy.
-%
-% \emph{1D fit -- }
-% This galaxy features a ring ($R \sim 20''$) and a nuclear bar ($R \lesssim 4''$),
-% which can be seen in the unsharp mask and produces corresponding peaks in the ellipticity and PA profiles.
-% The bar is fit with a Ferrer function.
-%
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\fitfigurewidth]{images/ugc03789_1Dfit.eps}
-% \caption{Best-fit model and isophotal parameters for UGC 03789.}
-% \end{center}
-% \end{figure}
-%
-% \begin{table}[h]
-% \small
-% \caption{Best-fit parameters for UGC 03789.}
-% \begin{center}
-% \begin{tabular}{llcc}
-% \hline
-% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
-%   &  &  $[\rm arcsec]$ & \\
-% \hline
-% T.W. 1D maj. & S-bul + e-d + F-bar + G-r & $1.8$  &  $1.9$ \\
-% T.W. 1D eq.  & S-bul + e-d + F-bar + G-r & $2.4$  &  $1.4$ \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \label{tab:ugc3789}
-% \end{table}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \onecolumngrid
+  \subsection{individual galaxies}
+  \label{sec:indgal}
+
+  individual galaxies \\
+
+  \clearpage\newpage\noindent
+  {\bf IC 1459 \\}
+
+  IC 1459 is an elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
+  nuclear dust and an indication of a central stellar disk \citep{forbes1994ic1459}.
+  The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
+  This galaxy has also an unresolved partially depleted core \citep{rusli2013}. \\ % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
+
+  \emph{1D fit -- }
+  Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
+  We masked the innermost $6''.1$ affected by the partially depleted core 
+  and we fit this galaxy with a S\'ersic profile. \\
+
+  \emph{Other models -- } 
+  The best-fit model of L+14 is in reasonable agreement with our results. 
+  S+11 obtained the smallest S\'ersic index because they fit a nuclear component rather than masking the core. 
+  R+13 obtained the smallest effective radius 
+  because they fit a circularized light profile that only extends out to $R_{\rm eq} \lesssim 60''$.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for IC 1459.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of IC 1459.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
+  T.W. 1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
+  T.W. 2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
+  \hline
+  S+11         & S-bul + G-n   & $61.1$  &  $6.0$ \\
+  R+13         & core-S\'ersic & $45.4$  &  $7.6$ \\
+  L+14         & S-bul + m-c   & $62.4$  &  $8.3$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:ic1459}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf IC 2560 \\}
+
+  IC 2560 is a barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
+  and dust within the central $2''.5$ \citep{martini2003}.\\
+
+  \emph{1D fit -- }
+  A visual inspection of the image of IC 2560 reveals a boxy bulge and
+  a large scale bar that extends out to $R_{\rm maj} \lesssim 43''$.
+  The disk appears to be slightly lopsided along the direction of the bar,
+  due to two non-symmetric ansae, but it becomes symmetric beyond $R_{\rm maj} \gtrsim 60''$. 
+  This is why the surface brightness profile deviates from a perfect exponential
+  in the radial range $42'' \lesssim R_{\rm maj} \lesssim 60''$, which has been excluded from the fit.
+  Motivated by the presence of a strong optical AGN and dust in the nucleus, 
+  we accounted for an excess of non-stellar light by adding a central Gaussian component to the model.\\
+
+  \emph{Other models -- } 
+  In their model, S+11 did not account for the bar component and thus overestimated the effective radius and the S\'ersic index of the bulge.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for IC 2560.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of IC 2560.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $6.1$  &  $0.8$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.5$  &  $0.6$ \\
+  \hline
+  S+11         & S-bul + e-d + G-n & $27.5$  &  $2.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:ic2560}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf IC 4296 \\}
+
+  IC 4296 is an elliptical galaxy. 
+  Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core.
+
+  \emph{1D fit -- }
+  After masking the innermost $6''.1$, 
+  we found that a single S\'ersic profile provides a fairly good description of this galaxy.
+
+  \emph{Other models -- } 
+  S+11 obtained the smallest effective radius and S\'ersic index because they fit a nuclear component rather than masking the core. 
+  L+14 obtained the largest effective radius and S\'ersic index, 
+  although the 1D representation of their 2D fit (their Figure 8) shows that their model overestimates the galaxy light at large radii ($R > 100''$), 
+  implying the need for a smaller $R_{\rm e}$ and $n$. 
+  We did not find any conclusing explanation for this, 
+  but we suspect it may be due to the different pixel weighting scheme that they used.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for IC 4296.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of IC 4296.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
+  T.W. 1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
+  T.W. 2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
+  \hline
+  S+11         & S-bul + G-n & $33.6$  &  $4.0$ \\
+  L+14         & S-bul + m-c & $97.8$  &  $8.2$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:ic4296}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf M31 -- NGC 0224 \\}
+
+  M31, the Andromeda galaxy, is a spiral galaxy. 
+  Although for decades this galaxy had been classified as an unbarred spiral,
+  recent works have unraveled the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}.
+  M31 also features a ring-like structure at $R_{\rm maj} \sim 50'$ \citep{athanassoulabeaton2006m31}.
+
+  \emph{1D fit -- }
+  We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
+  The region $2000'' \lesssim R_{\rm maj} \lesssim 3400''$, where the pseudo-ring is observed, was excluded from the fit.
+  A S\'ersic + exponential fit is not adequate to describe the light profile of M31,
+  as the residuals of such fit display a structure in correspondence of the bar ($R_{\rm maj} \lesssim 1500''$).
+  The addition of a Ferrer function to account for the bar notably improved the fit.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M31.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M31.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar & $418.6$  &  $2.2$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar & $173.6$  &  $1.3$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m31}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf M49 -- NGC 4472 \\}
+
+  M49, the brightest member of the Virgo cluster, is a giant elliptical galaxy 
+  with a slightly resolved partially depleted core \citep{rusli2013}. \\ %($R_{\rm break} = 1''.8$, \citealt{rusli2013}).
+
+  \emph{1D fit -- }
+  We excluded from the fit the innermost $12''$.
+  We found no evidence for embedded components and
+  we fit M49 with a single S\'ersic profile. \\
+
+  \emph{Other models -- } 
+  The effective radius estimated by R+13 is larger than that measured by us along the equivalent axis.
+  Since their circularized light profile is almost 3 times more extended than ours, 
+  it is possible that their best-fit model required a larger $R_{\rm e}$ to account for the galaxy intracluster halo light.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M49.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M49.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c   & $190.2$  &  $6.6$ \\
+  T.W. 1D eq.  & S-bul + m-c   & $135.3$  &  $5.4$ \\
+  T.W. 2D      & S-bul + m-c   & $151.9$  &  $5.5$ \\
+  \hline
+  R+13         & core-S\'ersic & $199.0$  &  $5.6$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m49}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf M59 -- NGC 4621 \\}
+
+  M59 is an elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
+  and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}.\\
+
+  \emph{1D fit -- }
+  The intermediate-scale embedded disk is clearly visible in our unsharp mask image, and 
+  the velocity field confirms the presence of a rapidly rotating component. 
+  This has been modeled with an exponential function.
+  We chose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit. \\
+
+  \emph{Other models -- } 
+  We observed no significant discrepancies between our results and the best-fit models of S+11 and V+12.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M59.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M59.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-n + e-id & $48.0$  &  $5.5$ \\
+  T.W. 1D eq.  & S-bul + m-n + e-id & $90.9$  &  $8.8$ \\
+  %T.W. 2D	&    & $$  &  $$ \\
+  \hline 
+  S+11         & S-bul       & $70.1$  &  $5.0$ \\
+  V+12         & S-bul + m-c & $54.7$  &  $5.7$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m59}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%\clearpage\newpage\noindent
+  %%
+  %%{\bf M60 -- NGC 4649 \\}
+  %%
+  %%exclude it, doesn't make sense
+  %%
+  %%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf M64 -- NGC 4826 \\}
+
+  M64 is a dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. \\
+
+  \emph{1D fit -- }
+  A large-scale bar ($R_{\rm maj} \lesssim 50''$) can be identified in the unsharp mask 
+  and produces corresponding peaks in the ellipticity, PA and B4 profiles.
+  We modeled it with a Ferrer function.
+  Additional peaks in the ellipticity, PA and B4 profiles at $R_{\rm maj} \sim 15''$ 
+  signal the presence of an embedded disky component, that we described with a low-$n$
+  S\'ersic function.
+  Although the galaxy is dusty and hosts an AGN, we do not observe any nuclear excess of light 
+  in the fit residuals and therefore we consider unnecessary to add a nuclear component to our model. \\
+
+  \emph{Other models -- } 
+  The best-fit model of B+12 is in reasonable agreement with our results.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m64_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M64.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M64.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + S-id  & $3.8$  &  $0.8$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + S-id  & $4.3$  &  $1.4$ \\
+  %T.W. 2D	&   & $$  & $$  &  $$ \\
+  \hline
+  B+12      & S-bul + e-d  & $5.0$  &  $1.5$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m64}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf M81 -- NGC 3031 \\}
+
+  M81 is an early-type spiral galaxy.
+  This galaxy features two bars \citep{elmegreen1995m81,gutierrez2011,erwindebattista2013}. \\
+
+  \emph{1D fit -- }
+  We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M81.
+  The bars are not particularly evident in the galaxy image or in the unsharp mask.
+  Any attempt to account for the bars in the fit was unsuccessful. 
+  For this reason, we used a simple S\'ersic + exponential model to describe M81. \\
+
+  \emph{Other models -- } 
+  GD07 and B+12 obtained estimates of the effective radius larger than ours by a factor of two. 
+  This is not particularly surprising, given the complicated surface brightness distribution of this galaxy. 
+  The large measurement of the effective radius reported by S+11 is the most discrepant, 
+  but the reasons for this are unclear.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m81_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M81.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M81.}
+  \begin{center}
+  \begin{tabular}{llccc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d  & $31.0$  &  $1.7$ \\
+  T.W. 1D eq.  & S-bul + e-d  & $33.2$  &  $2.1$ \\
+  %T.W. 2D	&   & $$  & $$  &  $$ \\
+  \hline
+  GD07      & S-bul + e-d	 & $68.1$   &  $3.3$ \\
+  S+11      & S-bul + e-d + G-n  & $127.3$  &  $3.0$ \\
+  B+12      & S-bul + e-d	 & $50.0$   &  $2.6$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m81}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf M84 -- NGC 4374 \\}
+
+  M84 is an elliptical galaxy with a slightly resolved partially depleted core \citep{rusli2013}.\\ %($R_{\rm break} = 1''.5$, \citealt{rusli2013}).
+
+  \emph{1D fit -- }
+  The unsharp mask reveals a faint inner component ($R_{\rm maj} \lesssim 12''$). 
+  Here we excluded the data within $R_{\rm maj} < 13''.8$ and modeled the galaxy with a S\'ersic profile.\\
+
+  \emph{Other models -- } 
+  The results obtained by S+11, R+13 and L+14 are in good agreement with those obtained by us. 
+  B+12 did not mask the core and thus underestimated the effective radius and the S\'ersic index. 
+  V+12 used the same model as R+13, L+14 and us, 
+  but the smaller radial extent of their data led them to underestimate the effective radius and the S\'ersic index.
+  It is not clear why GD07 obtained smaller estimates of the effective radius and the S\'ersic index, 
+  since they tipically did not fit the innermost data points of their light profiles.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m84_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M84.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M84.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c   & $101.6$  &  $7.8$ \\
+  T.W. 1D eq.  & S-bul + m-c   & $129.8$  &  $7.9$ \\
+  T.W. 2D      & S-bul + m-c   & $181.8$  &  $8.4$ \\
+  \hline
+  GD07         & S-bul         & $75.1$   &  $5.6$ \\
+  S+11         & S-bul + G-n   & $105.9$  &  $7.0$ \\
+  V+12         & S-bul + m-c   & $28.7$   &  $3.5$ \\
+  B+12         & S-bul         & $63.6$   &  $4.1$ \\
+  R+13         & core-S\'ersic & $126.2$  &  $7.1$ \\
+  L+14         & S-bul + m-c   & $139.0$  &  $8.3$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m84}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf M87 -- NGC 4486 \\}
+
+  M87 is a giant elliptical galaxy belonging to the Virgo cluster.
+  This galaxy has a large ($> 7''$), partially depleted core \citep{ferrarese2006acsvcs}.\\
+
+  \emph{1D fit -- }
+  The morphology of M87 is similar to that of M49.
+  The innermost $18''.5$ were excluded from the fit.
+  We used a single S\'ersic model to fit M87. 
+  We note that the 1D major-axis effective radius obtained from our 1D fit is more than a factor of two larger than that obtained from our 2D fit, 
+  because the last one cannot account for the strong ellipticity gradient of the galaxy.  \\
+
+  \emph{Other models -- } 
+  The 2D fits of S+11 and L+14 produce results which are consistent with our 2D best-fit model. 
+  The 1D fit along the equivalent-axis of R+13 returns the largest values for $R_{\rm e,sph}$ and $n_{\rm sph}$. 
+  As in the case of M49, since their circularized light profile is almost three times more extended than ours, 
+  their best-fit model probably required a larger $R_{\rm e}$ to account for the extra intracluster halo light.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m87_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M87.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M87.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c  & $203.9$  &  $10.0$ \\
+  T.W. 1D eq.  & S-bul + m-c  & $87.1$   &  $5.9$ \\
+  T.W. 2D      & S-bul + m-c  & $88.3$   &  $4.3$ \\
+  \hline
+  GD07      & S-bul	    & $-$     &  $6.9$ \\
+  S+11      & S-bul + G-n   & $99.5$  &  $4.0$ \\
+  V+12      & S-bul + m-c   & $34.6$  &  $2.4$ \\
+  R+13      & core-S\'ersic & $180.9$ &  $8.9$ \\
+  L+14      & S-bul + m-c   & $122.0$ &  $5.6$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m87}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+
+  {\bf M89 -- NGC 4552 \\}
+
+  m87 has ellipticity still increasing, the halo is not prevailing
+  m89 instead has a plateau in the ell prof, bcz the halo is predominant
+  we need to fit the halo
+
+  BTW, if we wanna test the two phase formation scenario, we should care more about the halos...
+  at which effective radius does the halo begin?
+  what is the ratio of the mass in the galaxy or in the halo?
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m89_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M89.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M89.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-halo  & $29.0$  &  $4.6$ \\
+  T.W. 1D eq.  & S-bul + e-halo  & $28.2$  &  $5.1$ \\
+  %T.W. 2D	&   & $$  & $$  &  $$ \\
+  \hline
+  &   & $$  &  $$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m89}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf M94 -- NGC 4736 \\}
+
+  M94 is an almost face-on spiral galaxy, with a Seyfert AGN \citep{veroncettyveron2006} and 
+  circumnuclear dust \citep{elmegreen2002m94,peeplesmartini2006m94}.
+  This galaxy has a ring-like structure at $R_{\rm maj} \sim 50''$ \citep{munoztunon1989m94}.\\
+
+  \emph{1D fit -- }
+  The ellipticity and B4 profiles display a local maximum at $R_{\rm maj} \sim 10''$, 
+  indicating the presence of a disky component embedded in the bulge,
+  as already noted by \cite{fisherdrory2010}.
+  We modeled this component with a Ferrer function.
+  We excluded the data within the innermost $6''.7$, due to the AGN contribution.
+  Any attempt to model the ring was unsuccessful, resulting in a degenerate model, 
+  therefore we preferred to exclude also the data in the range $20'' \lesssim R_{\rm maj} \lesssim 80''$.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m94_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M94.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M94.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar & $11.4$  &  $0.9$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar & $8.4$   &  $1.1$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m94}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf M96 -- NGC 3368 \\}
+
+  M96 is a spiral galaxy with a large scale bar and no AGN activity \citep{martini2003,nowak2010n3368n3489}. 
+  \cite{nowak2010n3368n3489} reported the presence of a large pseudo-bulge and a tiny classical bulge 
+  ($R_{\rm e, sph} = 1''.6$, $n_{\rm sph} = 2.3$). 
+  \cite{erwin2004} observed the presence of two bars in this galaxy. \\
+
+  \emph{1D fit -- }
+  M96 has a complex morphology. 
+  The large-scale disk does not exhibit a perfect exponential profile, 
+  mainly because of wound spiral arms resembling a ring ($R_{\rm maj} \sim 185''$),
+  which however are too faint and irregular to be described with a Gaussian ring model. 
+  The large scale bar extends out to $R_{\rm maj} \lesssim 80''$ and has been modeled with a Ferrer function.
+  A peak at $R_{\rm maj} \sim 25''$ in the ellipticity profile unravels an inner component embedded in the bulge, 
+  that we modelled with a low-$n$ S\'ersic profile.
+  The residuals do not display any significant light excess in the nuclear region, 
+  in agreement with the lack of AGN activity.\\
+
+  \emph{Other models -- } 
+  The bulge effective radius obtained by S+11 largely exceeds our estimates 
+  because their model does not account for the disk or bar embedded in the bulge ($R_{\rm maj} \lesssim 25''$). 
+  \cite{nowak2010n3368n3489} came to their conclusion by modeling only the innermost $8''.5$ of the 
+  light profile of M96 with a S\'ersic-classical-bulge and an exponential-pseudo-bulge, 
+  but without subtracting the contribution of the large-scale disk and the large-scale bar.
+  In addition, they acknowledged the presence of a secondary inner bar, but did not include it in their fit.\\
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m96_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M96.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M96.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + S-bar  & $7.5$  &  $1.5$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + S-bar  & $5.3$  &  $1.3$ \\
+  T.W. 2D      & S-bul + e-d + 2 G-bars       & $8.3$  &  $2.0$ \\
+  \hline
+  S+11         & S-bul + e-d + G-bar  & $45.6$  &  $1.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m96}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+
+  {\bf M104 -- NGC 4594 \\}
+
+  OK
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M104.}
+  \end{center}
+  \end{figure}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf M105 -- NGC 3379 \\}
+
+  M105 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.1$, \citealt{rusli2013}).
+
+  \emph{1D fit -- }
+  M105 exhibits a mild isophotal twist and an abrupt change of ellipticity at $R \sim 30''$.
+  The velocity map shows rotation at least within $R \lesssim 30''$, 
+  but no embedded disk can be recognized in the unsharp mask 
+  and the ellipticity profile is quite unusual for a spheroidal system with an inner disk.
+  After masking the innermost $6''.1$, we noticed that a single S\'ersic model 
+  does not provide a good description of the galaxy light profile.
+  However, the addition of a second function (of any analytical form) to the model did not improve the fit.
+  We thus employed a single S\'ersic profile for M105.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m105_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M105.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M105.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c & $57.2$  &  $5.2$ \\
+  T.W. 1D eq.  & S-bul + m-c & $50.9$  &  $5.3$ \\
+  T.W. 2D      & S-bul + m-c & $73.6$  &  $7.0$ \\
+  \hline
+  GD07         & S-bul & $58.3$  &  $4.3$ \\
+  S+11         & S-bul & $46.0$  &  $5.0$ \\
+  R+13         & core-S\'ersic & $55.1$  &  $5.8$ \\
+  L+14         & S-bul + m-c & $96.3$  &  $9.3$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m105}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf M106 -- NGC 4258 \\}
+
+  M106 is a barred spiral galaxy, harbouring a Seyfert AGN \citep{veroncettyveron2006} 
+  with %a radio jet \citep{liuzhang2002} and 
+  circumnuclear dust \citep{martini2003}.
+
+  %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 14''.9$, $n = 2.0$). 
+  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model 
+  %($R_{\rm e} = 111''.7$, $n = 2.0$). 
+  %\cite{vika2012} proposed two different fits: the first with a S\'ersic-bulge + exponential-disk + PSF-nucleus
+  %($R_{\rm e} = 17''.0$, $n = 3.5$), 
+  %and the second with a S\'ersic-bulge + exponential-disk + PSF-nucleus + S\'ersic-bar
+  %($R_{\rm e} = 6''.3$, $n = 2.2$).
+
+  \emph{1D fit -- }
+  We excluded from the fit the innermost $6''.1$ because affected by the AGN emission.
+  The boxy bar, responsible for the minimum in the B4 profile at $R \sim 65''$, 
+  is faint compared to the large-scale disk and in the light profile is only detectable as a slight swelling
+  within $65'' \lesssim R \lesssim 110''$.
+  This region has been excluded from the fit.
+  A peak in the ellipticity profile at $R \sim 10''$ suggests that a disk-like component might be 
+  embedded in the bulge.
+  Since the galaxy is barred, this component could be identified with a peanut bulge. 
+  However, we found that adding an extra component to the model introduces degeneracies, 
+  thus we preferred not to do so.
+  While the fit along the major-axis is satisfactory, 
+  the equivalent-axis residuals present a sneaky structure within $R \lesssim 20''$,
+  due to the unsubtracted embedded component.
+  %Our final model consists of a S\'ersic-bulge + exponential-disk.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m106_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M106.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M106.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d & $15.3$  &  $2.0$ \\
+  T.W. 1D eq.  & S-bul + e-d & $8.3$   &  $1.2$ \\
+  %T.W. 2D	& & $$  & $$  &  $$ \\
+  \hline
+  GD07     & S-bul + e-d		 & $14.9$   &  $2.0$ \\
+  S+11     & S-bul + e-d + G-n  	 & $111.7$  &  $2.0$ \\
+  V+12 (1) & S-bul + e-d + PSF-n	 & $17.0$   &  $3.5$ \\
+  V+12 (2) & S-bul + e-d + PSF-n + S-bar & $6.3$    &  $2.2$ \\
+  L+14     & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $6.3$	 &  $3.3$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m106}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 0524 \\}
+
+  NGC 0524 is an unbarred face-on lenticular galaxy.
+
+  %\cite{laurikainen2010} modeled this galaxy with a S\'ersic-bulge + exponential-disk + 2 Ferrer-lenses 
+  %($R_{\rm e} = 8''.9$, $n = 2.7$).
+  %\cite{sani2011} opted for a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 26''.8$, $n = 3.0$).
+  \emph{1D fit -- }
+  The unsharp mask of NGC 0524 unravels a faint multi-ring structure in the galaxy disk,
+  with a major ring peaking at $R \sim 20''$.
+  We accounted only for this brightest ring using a Gaussian ring profile.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n0524_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 0524.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 0524.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + G-r & $6.0$  &  $1.1$ \\
+  T.W. 1D eq.  & S-bul + e-d + G-r & $5.8$  &  $1.1$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  L+10      & S-bul + e-d + 2 F-l & $8.9$  &  $2.7$ \\
+  S+11      & S-bul + e-d	  & $26.8$  &  $3.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n0524}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+
+  {\bf NGC 0821 \\}
+
+  ok
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n0821_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 0821.}
+  \end{center}
+  \end{figure}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 1023 \\}
+
+  NGC 1023 is a barred lenticular galaxy. % with no partially depleted core \cite{faber1997}. \\
+
+  %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 17''.7$, $n = 2.0$). 
+  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-bar model 
+  %($R_{\rm e} = 24''.0$, $n = 3.0$).
+  %\cite{lasker2014data} employed a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
+  %($R_{\rm e} = 9''.6$, $n = 3.1$).
+  \emph{1D fit -- }
+  The bar extends out to $R \lesssim 40''$.
+  %The light profile of NGC 1023 is well described by a S\'ersic-bulge + exponential-disk + Ferrer-bar model.
+  Small deviations of the disk from a perfect exponential profile, 
+  within the region $60'' \lesssim R \lesssim 125''$ (that has been excluded from the fit), 
+  can be ascribed to some faint residual spiral arms, also noticeable in the 2D residual image. 
+  The peak at $R \sim 10''$ in the B4 profile signals the presence of an embedded (and faint) disk.
+  The 1D residuals show a structure within $R \lesssim 10''$ caused by this unsubtracted 
+  component, also noted by \cite{lasker2014data}.
+  Attempts to account for the inner disk by adding a fourth function to the model 
+  did not significantly modify the best-fit bulge parameters,
+  thus we elected not to model the embedded disk.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n1023_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 1023.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 1023.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar & $9.2$  &  $2.1$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar & $7.4$  &  $2.0$ \\
+  T.W. 2D      & S-bul + e-d + G-bar & $6.6$  &  $2.3$ \\
+  \hline
+  GD07    & S-bul + e-d 	& $17.7$  &  $2.0$ \\
+  S+11    & S-bul + e-d + G-bar & $24.0$  &  $3.0$ \\
+  L+14    & S-bul + e-d + S-bar & $9.6$   &  $3.1$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n1023}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 1300 \\}
+
+  NGC 1300 is a face-on, barred spiral galaxy. % with no partially depleted core \citep{graham2012MNRAS}.
+
+  %\cite{sani2011} fit NGC 1300 with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 85''.4$, $n = 3.0$).
+  %\cite{lasker2014data} built their model with a S\'ersic-bulge + exponential-disk + PSF-nucleus + exponential-inner-disk + 
+  %S\'ersic-bar + spiral arms
+  %($R_{\rm e} = 10''.4$, $n = 4.3$).
+
+  \emph{1D fit -- }
+  The morphology of NGC 1300 is quite complex. 
+  In addition to a large scale disk and a bulge, the galaxy is composed of 
+  a large scale bar that extends up to $R \lesssim 90''$, two prominent spiral arms 
+  and an inner disk-like component ($R \lesssim 5''$), disclosed by the peaks in the ellipticity and PA profiles.
+  We truncate the light profile at $R \sim 50''$ and we fit the inwards combination of the large-scale bar and the disk 
+  as a single component, using an exponential function.
+  The embedded component is described with a low-$n$ S\'ersic profile.
+  %Our final model consists of a S\'ersic-bulge + exponential-(disk+bar) + S\'ersic-inner disk.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n1300_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 1300.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 1300.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-(d+bar) + S-id & $9.9$  &  $3.8$ \\
+  T.W. 1D eq.  & S-bul + e-(d+bar) + S-id & $8.1$  &  $3.6$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  S+11    & S-bul + e-d & $85.4$  &  $3.0$ \\
+  L+14    & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $10.4$  &  $4.3$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n1300}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 1316 \\}
+
+  ok
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n1316_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 1316.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 1316.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + 2 G-r + G-n & $21.5$  &  $2.0$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + 2 G-r + G-n & $15.9$  &  $1.8$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  S+11      & S-bul + e-d + G-n & $93.0$  &  $5.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n1316}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 1332 \\}
+
+  ok
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 1332.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 1332.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + S-id + m-c & $34.7$  &  $5.1$ \\
+  T.W. 1D eq.  & S-bul + S-id + m-c & $18.0$  &  $3.7$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n1332}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 1374 \\}
+
+  ok
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 1399 \\}
+
+  NGC 1399, the central galaxy of the Fornax cluster, is an elliptical galaxy with a partially depleted core 
+  ($R_{\rm break} \sim 2''.4$, \citealt{rusli2013,dullograham2014cores}).
+  The nuclear activity of NGC 1399 is classified as Seyfert \citep{veroncettyveron2006},
+  but the galaxy lacks of dust \citep{tran2001}.
+
+  %\cite{grahamdriver2007} fit the galaxy light profile with a single S\'ersic-bulge profile 
+  %($n = 16.8$).  
+  %\cite{rusli2013} modeled NGC 1399 with a core-S\'ersic profile and the sum of a S\'ersic and an exponential
+  %function accounting for the galaxy halo 
+  %($R_{\rm e} = 36''.2$, $n = 7.38$). 
+  %\cite{lasker2014data} used a S\'ersic-bulge + mask-core model 
+  %($R_{\rm e} = 154''.0$, $n = 11.1$).
+
+  \emph{1D fit -- }
+  The ellipticity and PA profiles display a steep decline within $R \lesssim 60''$,
+  suggesting the presence of an embedded disk.
+  This inner component is also visible, although very faint, in the unsharp mask.
+  TBD!! velocity map, the disk is face on
+  We note that, after excluding the innermost $6''.1$ affected by the partially depleted core,
+  a single S\'ersic profile is not sufficient to describe the whole galaxy light profile.
+  The addition of an inner exponential function to the model 
+  notably improves the fit.
+  %We build our final model with a S\'ersic-bulge + mask-core + exponential-inner disk.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n1399_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 1399.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 1399.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c + e-id & $405.2$  &  $10.0$ \\
+  T.W. 1D eq.  & S-bul + m-c + e-id & $338.1$  &  $10.0$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  GD07         & S-bul  		    & $-$      &  $16.8$ \\
+  R+13         & core-S\'ersic + (S+e)-halo & $36.2$   &  $7.4$ \\
+  L+14         & S-bul + m-c		    & $154.0$  &  $11.1$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n1399}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 2273 \\}
+
+  NGC 2273 is a barred spiral galaxy with a Seyfert AGN \citep{contini1998} 
+  and circumnuclear dust \citep{simoeslopes2007}. 
+  Its bar is surrounded by two tightly wound star-forming spiral arms that resemble a ring
+  \citep{comeron2010}.
+
+  \cite{laurikainen2005} pointed out the presence of an inner disk embedded in the bulge of NGC 2273,
+  but they deliberately chose not to model it due to the degeneracy between the functions describing the bulge
+  and the inner disk. 
+  %Their final model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar 
+  %($R_{\rm e} = 2''.6$, $n = 1.8$).
+
+  \emph{1D fit -- }
+  The bar of NGC 2273 extends out to $R \lesssim 25''$. 
+  The pseudo-ring does not produce any evident swelling in the light profile, 
+  therefore we do not account for it in the galaxy model.
+  The isophotal parameters confirm the presence of a nuclear disk-like component within $R \lesssim 5''$.
+  However, as noted by \cite{laurikainen2005}, any attempt to account for the embedded disk resulted in a 
+  degenerate model. 
+  This is not surprising if one considers the poor spatial resolution of the galaxy image, 
+  the effective radius of the bulge being comparable to the FWHM of the PSF.
+  Although NGC 2273 hosts an optical AGN and nuclear dust, no central excess of light is observed in the 1D residuals.
+  The addition of a nuclear component to the model does not improve the fit and does not significantly affect
+  the bulge parameters.
+  %Our final model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n2273_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 2273.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 2273.}
+  \begin{center}
+  \begin{tabular}{llccc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar & $1.6$  &  $2.1$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar & $1.9$  &  $2.7$ \\
+  %T.W. 2D	&  & $$  &  $$ \\
+  \hline
+  L+05         & S-bul + e-d + F-bar & $2.6$  &  $1.8$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n2273}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 2549 \\}
+
+  NGC 2549 is an edge-on barred lenticular galaxy.
+
+  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 11''.6$, $n = 7.0$).
+
+  \emph{1D fit -- }
+  Although the edge-on inclination of NGC 2549 complicates the identification of embedded components, 
+  a large scale bar ($R \lesssim 45''$) can be recognized in the galaxy image itself and -- more easily -- in the light profile.
+  We describe the large scale bar with a Ferrer profile.
+  A peak in the ellipticity profile discloses the presence of a disky component
+  embedded in the bulge ($R \lesssim 10''$).
+  This inner component can be spotted also by looking at the velocity map.
+  We fit it with a Ferrer profile.
+  %We build our final model with a S\'ersic-bulge + exponential-disk + 2 Ferrer-bars.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n2549_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 2549.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 2549.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + F-id & $6.1$  &  $2.3$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + F-id & $3.1$  &  $1.5$ \\
+  T.W. 2D      & S-bul + e-d + G-bar + G-id & $5.6$  &  $2.1$ \\
+  \hline
+  S+11         & S-bul + e-d & $11.6$  &  $7.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n2549}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 2778 \\}
+
+  NGC 2778 is an almost face-on lenticular galaxy.
+
+  %\cite{grahamdriver2007} modeled NGC 2778 with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 2''.3$, $n = 1.6$). 
+  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk model
+  %($R_{\rm e} = 2''.5$, $n = 2.5$). 
+  %\cite{vika2012} employed a S\'ersic-bulge + exponential-disk model 
+  %($R_{\rm e} = 1''.5$, $n = 2.7$). 
+  %\cite{lasker2014data} fit the galaxy with a S\'ersic-bulge + exponential-disk + S\'ersic-bar
+  %($R_{\rm e} = 2''.8$, $n = 4.0$).
+
+  \emph{1D fit -- }
+  The peak in the ellipticity profile at $R \sim 5''$ unravels the existence of a nuclear component 
+  embedded in the galaxy bulge.
+  After an inspection of the unsharp mask, we identified this component with a small bar,
+  that we modeled with a Ferrer function.
+  We also accounted for some nuclear light excess by adding a PSF component to the model.
+  %We then fit NGC 2778 with a S\'ersic-bulge + exponential-disk + Ferrer-bar + PSF-nucleus.
+  We note that excluding the PSF component from our galaxy model does not significantly affect the 
+  bulge effective radius, but it increases the S\'ersic index to $n \sim 2$.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n2778_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 2778.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 2778.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + PSF-n & $2.3$  &  $1.3$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + PSF-n & $2.2$  &  $1.2$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  GD07         & S-bul + e-d	     & $2.3$  &  $1.6$ \\
+  S+11         & S-bul + e-d	     & $2.5$  &  $2.5$ \\
+  V+12         & S-bul + e-d	     & $1.5$  &  $2.7$ \\
+  L+14         & S-bul + e-d + S-bar & $2.8$  &  $4.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n2778}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 2787 \\}
+
+  NGC 2787 is a barred lenticular galaxy with LINER nuclear activity \citep{veroncettyveron2006}.
+  An inner disk is embedded in the bulge of this galaxy \citep{erwin2003n2787}.
+  NGC 2787 features a spectacular structure of dust rings at its center \citep{erwinsparke2003}
+  and a nuclear stellar disk ($R \lesssim 1''.8$, \citealt{ledo2010}).
+
+  %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 4''.6$, $n = 2.0$). 
+  %\cite{fisherdrory2008} decomposed NGC 2787 in a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 9''.1$, $n = 1.2$).
+  %\cite{laurikainen2010} employed a S\'ersic-bulge + exponential-disk + Ferrer-bar + Ferrer-lens model
+  %($R_{\rm e} \sim 4''$, $n = 1.3$).
+  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN 
+  %($R_{\rm e} = 15''.7$, $n = 3.0$). 
+  %\cite{lasker2014data} described NGC 2787 with a S\'ersic-bulge + truncated exponential-disk + 
+  %truncated S\'ersic-bar + S\'ersic-inner disk + PSF-nucleus
+  %($R_{\rm e} = 14''.3$, $n = 2.8$).
+
+  \emph{1D fit -- }
+  NGC 2787 has an undoubtedly complex morphology. 
+  This galaxy is made of a bulge, a large scale disk, a bar (see the peaks in the ellipticity, PA and B4 profiles
+  at $R \sim 30''$) with two ansae, an inner disk (or bar?) embedded in the bulge (see the peak in the ellipticity profile
+  at $R \sim 17''$), and a bright nucleus.
+
+  Beyond $R \gtrsim 50''$, where the galaxy large scale disk extends without being affected by the bar ansae,
+  the surface brightness profile is not a perfect exponential, being better described by a S\'ersic function
+  with $n < 1$.
+  Curiously, at optical wavelengths the disk has an exponential decline with no truncation or anti-truncation 
+  (see \citealt{erwin2003n2787} their Figure 14, and \citealt{erwin2008}).
+  Here we propose two different models for NGC 2787.
+  In both cases we used a S\'ersic profile for the bulge, a Ferrer function for the bar, a second Ferrer function for the inner disk (or bar) 
+  and a PSF for the nucleus. 
+  We then described the large scale disk using a S\'ersic function with $n < 1$ 
+  or an exponential function. 
+  In the last case we needed to exclude the data within $R \sim 30'' - 50''$ where the ansae produce a hollow.
+  The two different decompositions result in the same bulge best-fit parameters ($R_{\rm e} \sim 5''$, $n \sim 1$)
+  along the major-axis, whereas the outcome is significantly different along the equivalent-axis 
+  ($n = 1.3$ when using the exponential-disk and $n = 2.2$ when using the S\'ersic-disk).
+
+  might just pick one TBD!!
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n2787_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 2787.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 2787.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  \multicolumn{4}{c}{\emph{exponential-disk}} \\
+  %\hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + F-id + PSF-nucleus & $4.8$  &  $1.1$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + F-id + PSF-nucleus & $3.3$  &  $1.3$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  \multicolumn{4}{c}{\emph{S\'ersic-disk}}\\
+  %\hline
+  T.W. 1D maj. & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.6$  &  $1.1$ \\
+  T.W. 1D eq.  & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.4$  &  $2.2$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  GD07         & S-bul + e-d					  & $4.6$   &  $2.0$ \\
+  L+10         & S-bul + e-d + F-bar + F-l			  & $4.0$   &  $1.3$ \\
+  S+11         & S-bul + e-d + G-bar + G-n			  & $15.7$  &  $3.0$ \\
+  L+14         & S-bul + trunc. e-d + trunc. S-bar + S-id + PSF-n & $14.3$  &  $2.8$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n2787}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 2974 \\}
+
+  NGC 2974 is a spiral galaxy which has been misclassified as an elliptical galaxy in the RC3 catalog.
+  The galaxy hosts a Seyfert AGN \citep{veroncettyveron2006} and filamentary dust in its center \citep{tran2001}.
+
+  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + Gaussian-AGN 
+  %($R_{\rm e} = 27''.2$, $n = 3.0$).
+
+  \emph{1D fit -- }
+  From an inspection of the unsharp mask, we identified a ring structure at $R \sim 50''$, 
+  probably a residual of two tightly wound spiral arms,
+  and an elongated bar-like component within $R \lesssim 30''$, that we fit with a Ferrer function.
+  The last one produces a peak in the ellipticity profile at $R \sim 20''$.
+  Although the ring is extremely faint, it is important to account for it in the galaxy decomposition. 
+  A model without the ring component results in a ``steeper'' exponential-disk (the disk has a smaller scale length 
+  and a lower central surface brightness) and produces bad residuals within $R \lesssim 40''$.
+  The nuclear component is fit with a Gaussian profile.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 2974.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 2974.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + G-n + G-r & $8.3$   &  $1.4$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + G-n + G-r & $6.9$   &  $1.2$ \\
+  T.W. 2D      & S-bul + e-d + G-bar + m-n	 & $10.6$  &  $1.3$ \\
+  \hline
+  S+11         & S-bul + G-n & $27.2$  &  $3.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n2974}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+
+  {\bf NGC 3079 \\}
+
+  inner component?? ok fuck it
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3079_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3079.}
+  \end{center}
+  \end{figure}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 3091 \\}
+
+  NGC 3091 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.62$, \citealt{rusli2013}).
+
+  %\cite{rusli2013} modeled NGC 3091 with a single core-S\'ersic profile 
+  %($R_{\rm e} = 91''.0$, $n = 9.3$).
+
+  \emph{1D fit -- }
+  The data within the innermost $6''.1$ are excluded from the fit.
+  A faint embedded component ($R \lesssim 10''$) can be recognized in the unsharp mask and has a corresponding peak in the
+  ellipticity profile.
+  This extra component is clearly visible in the residual image obtained by subtracting a 2D S\'ersic model from the  
+  galaxy image.
+  However, any attempt to account for the embedded component resulted in an unsatisfactory fit and did not 
+  significantly affect the bulge parameters.
+  We thus elected not to model the inner component.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3091_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3091.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3091.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c & $100.5$  &  $7.6$ \\
+  T.W. 1D eq.  & S-bul + m-c & $51.2$	&  $6.6$ \\
+  T.W. 2D      & S-bul + m-c & $67.1$	&  $6.7$ \\
+  \hline
+  R+13         & core-S\'ersic & $91.0$  &  $9.3$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3091}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 3115 \\}
+
+  NGC 3115 is an edge-on elliptical/lenticular galaxy. 
+  Its nuclear activity is classified as passive in the optical wavelengths \citep{gavazzi2013nuclspec}.
+  This galaxy features a nuclear stellar disk ($R \sim 1''$, \citealt{scorzabender1995,ledo2010}).
+
+  \cite{grahamdriver2007} TBD!!! ask Alister what did they do, not clear from appendix
+  ($n = 13.0$). 
+  \cite{fisherdrory2008} decomposed the galaxy in a S\'ersic-bulge + exponential disk 
+  ($R_{\rm e} = 31''.0$, $n = 3.9$). 
+  %\cite{sani2011} modeled NGC 3115 with a S\'ersic-bulge + exponential disk 
+  %($R_{\rm e} = 27''.3$, $n = 3.0$). 
+  %\cite{lasker2014data} used a S\'ersic-bulge + exponential disk + S\'ersic-envelope 
+  %($R_{\rm e} = 3''.9$, $n = 3.0$).
+
+  \emph{1D fit -- }
+  NGC 3115 is an example of a galaxy with an intermediate scale disk.
+  The surface brightness profile of NGC 3115 does not have an exponential decline at large radii 
+  because the disk component does not dominate the outer regions of the galaxy.
+  This is immediately evident by looking at the ellipticity and B4 profiles.
+  Going from the galaxy center to the outskirts, the ellipticity increases until it reaches its maximum 
+  ($\epsilon \sim 0.65$) at $R \sim 90''$. 
+  After this point, it starts declining, being as low as $\epsilon \sim 0.55$ at $R \sim 240''$. 
+  The galaxy isophotes display a positive diskyness within $R \sim 90''$, but become perfect ellipses 
+  ($B4 \sim 0$) beyond that point.
+  Now, because galaxy disks typically have fixed ellipticity, reflecting their inclination to our line of sight,
+  the previous observations tell us that, going from the galaxy center to the outer regions,
+  the disk of NGC 3115 becomes increasingly important relative to the spheroid light, reaching its maximum at $R \sim 90''$.
+  Beyond $R \gtrsim 90''$, the contribution from the disk light starts declining more rapidly than the spheroid light.
+  This interpretation is supported by the results of \cite{arnold2011n3115},
+  who found that within $R \sim 110''$ the bulge of NGC 3115 is flattened and rotates rapidly ($v/\sigma \gtrsim 1.5$),
+  whereas at larger radii the rotation declines dramatically (to $v/\sigma \sim 0.7$), 
+  but remains well aligned with the inner regions. \\
+  From an inspection of the unsharp mask, we identify a faint nuclear edge-on ring ($R \sim 15''$), 
+  which produces a corresponding peak in the ellipticity profile. \\
+  %We build our model with a S\'ersic-bulge + exponential disk + Gaussian-ring. \\
+  We do not observe any nuclear excess of light in the 1D residuals, 
+  contrary to what we expected given the presence of a nuclear stellar disk. 
+  The addition of a PSF component to the final model does not significantly change the outcome of the fit.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3115_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3115.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3115.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + G-r & $43.6$  &  $4.4$ \\
+  T.W. 1D eq.  & S-bul + e-d + G-r & $34.4$  &  $5.1$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  GD07         & ??? TBD	       & $-$	&  $13.0$ \\
+  S+11         & S-bul + e-d	       & $27.1$ &  $3.0$ \\
+  L+14         & S-bul + e-d + S-halo  & $3.9$  &  $3.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3115}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 3227 \\}
+
+  NGC 3227 is a spiral galaxy with a large-scale bar. 
+  This galaxy hosts a Seyfert AGN \citep{khachikian1974} and circumnuclear dust \citep{martini2003}.
+
+  %\cite{laurikainen2004} decomposed NGC 3227 into a S\'ersic-bulge + exponential-disk + Ferrer-bar 
+  %($R_{\rm e} = 1''.8$, $n = 2.2$). 
+  %\cite{sani2011} described this galaxy with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 82''.9$, $n = 4.0$). 
+  %\cite{lasker2014data} used a S\'ersic-bulge + exponential disk + S\'ersic-bar 
+  %($R_{\rm e} = 0''.7$, $n = 4.1$).
+
+  \emph{1D fit -- }
+  The large-scale bar produces an evident bump in the major-axis surface brightness profile,
+  which is curiously absent in the equivalent-axis profile. \\
+  We modeled the bar with a Ferrer function and the nucleus with a Gaussian function. 
+  As expected, the Ferrer component is rejected by the equivalent-axis fit.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3227_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3227.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3227.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + G-n   & $8.1$  &  $1.7$ \\
+  T.W. 1D eq.  & S-bul + e-d + [F-bar] + G-n & $4.6$  &  $1.1$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  L+04         & S-bul + e-d + F-bar & $1.8$  &  $2.2$ \\
+  S+11         & S-bul + e-d	     & $82.9$ &  $4.0$ \\
+  L+14         & S-bul + e-d + S-bar & $0.7$  &  $4.1$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3227}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 3245 \\}
+
+  NGC 3245 is a lenticular galaxy.
+
+  %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 11''.3$, $n = 4.3$). 
+  %\cite{laurikainen2010} described the galaxy with a S\'ersic-bulge + exponential-(disk+lens) + Ferrer-inner disk 
+  %($R_{\rm e} \sim 4''$, $n = 2.4$).  
+  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 4''.6$, $n = 2.5$). 
+  %\cite{vika2012} employed a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 3''.5$, $n = 2.6$). 
+  %\cite{beifiori2012} decomposed the galaxy into a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 4''.00$, $n = 1.6$). 
+  %\cite{lasker2014data} built their model with a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
+  %($R_{\rm e} = 1''.95$, $n = 1.6$).
+
+  \emph{1D fit -- }
+  The unsharp mask reveals the presence of an embedded disk ($R \lesssim 15''$), 
+  confirmed by the corresponding peaks in the ellipticity and B4 profiles.
+  We model this inner component with a Ferrer function.
+  %We model the galaxy with a S\'ersic-bulge + exponential-disk + Ferrer-inner disk.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3245_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3245.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3245.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-id & $4.4$  &  $2.9$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-id & $2.4$  &  $1.7$ \\
+  T.W. 2D      & S-bul + e-d + G-id & $1.9$  &  $1.8$ \\
+  \hline
+  GD07         & S-bul + e-d		& $11.3$ &  $4.3$ \\
+  L+10         & S-bul + e-(d+l) + F-id & $4.0$  &  $2.4$ \\
+  S+11         & S-bul + e-d		& $4.6$  &  $2.5$ \\
+  V+12         & S-bul + e-d		& $3.5$  &  $2.6$ \\
+  B+12         & S-bul + e-d		& $4.0$  &  $1.6$ \\
+  L+14         & S-bul + e-d + S-bar	& $2.0$  &  $1.6$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3245}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+
+  {\bf NGC 3377 \\}
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3377.}
+  \end{center}
+  \end{figure}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 3384 \\}
+
+  NGC 3384 is a barred lenticular galaxy that hosts 
+  an embedded disk ($R \lesssim 11''$, \citealt{erwin2004}) and 
+  a nuclear stellar disk ($R \lesssim 0''.8$, \citealt{ledo2010}).
+
+  %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 2''.5$, $n = 1.7$). 
+  %\cite{laurikainen2010} described the galaxy with a S\'ersic-bulge + exponential-disk + 2 Ferrer-bars
+  %($R_{\rm e} \sim 4''$, $n = 1.5$).  
+  %\cite{sani2011} employed a S\'ersic-bulge + exponential-disk + Gaussian-bar 
+  %($R_{\rm e} = 4''.4$, $n = 2.5$). 
+  %\cite{beifiori2012} modeled the galaxy with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 8''.3$, $n = 2.3$). 
+  %\cite{lasker2014data} decomposed the galaxy into a S\'ersic-bulge + exponential-disk + S\'ersic-inner disk + 
+  %S\'ersic-nuclear disk + S\'ersic-bar
+  %($R_{\rm e} = 5''.9$, $n = 2.5$).
+
+  \emph{1D fit -- }
+  The isophotal parameters clearly show the presence of a boxy bar that extends out to $R \lesssim 18''$.
+  We model the bar with a Ferrer function.
+  An embedded disk can be seen in the unsharp mask and produces the peak in the ellipticity profile at $R \sim 4''$.
+  modeling the embedded disk turned out to be a complicated task, resulting in a degenerate model.
+  We elected not to fit the embedded disk (nor the nuclear disk) and we therefore excluded from the fit the innermost $3''.7$,
+  where there two components are expected to dominate.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3384_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3384.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3384.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + m-n & $5.5$  &  $1.6$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + m-n & $5.6$  &  $1.8$ \\
+  %T.W. 2D	&  & $$  &  $$ \\
+  \hline
+  GD07         & S-bul + e-d		      & $2.5$  &  $1.7$ \\
+  L+10         & S-bul + e-d + 2 F-bar        & $4.0$  &  $1.5$ \\
+  S+11         & S-bul + e-d + G-bar	      & $4.4$  &  $2.5$ \\
+  B+12         & S-bul + e-d		      & $8.3$  &  $2.3$ \\
+  L+14         & S-bul + e-d + 2 S-id + S-bar & $5.9$  &  $2.5$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3384}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 3393 \\}
+
+  NGC 3393 is an edge-on spiral galaxy hosting a Seyfert AGN \citep{diaz1988n3393} and 
+  circumnuclear dust \citep{martini2003}.
+  The galaxy has a large-scale bar and a nuclear bar ($R \lesssim 3''$, \citealt{erwin2004}).
+
+  \emph{1D fit -- }
+  The large-scale bar ($R \lesssim 20''$) is modeled with a Ferrer function.
+  The poor spatial resolution of the data does not allow to fit the nuclear bar and/or the AGN component 
+  without incurring degeneracies.
+  We thus elected not to fit the nuclear components.
+  We note that the addition to the model of a central component would lower the bulge S\'ersic index,
+  whereas the the addition of a nuclear bar component would increase the bulge S\'ersic index.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3393_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3393.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3393.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar & $1.4$  &  $3.4$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar & $1.4$  &  $2.6$ \\
+  T.W. 2D      & S-bul + e-d + G-bar & $1.2$  &  $1.9$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3393}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 3414 \\}
+
+  NGC 3414 is a peculiar lenticular/elliptical galaxy. 
+  Different interpretations have been proposed about the morphology of this galaxy.
+  \cite{whitmore1990} suggested that NGC 3414 is an edge-on galaxy 
+  with a large scale polar ring, rather than a face-on barred lenticular.
+  \cite{laurikainen2010} decomposed NGC 3414 as a barred lenticular galaxy, but 
+  they cautioned against the uncertainty of their solution due to the possible misinterpretation of the 
+  galaxy morphology.
+
+  \emph{1D fit -- }
+  The unsharp mask clearly shows that the edge on component does not extend all the way through the 
+  center of the galaxy, but instead it is truncated at $R \sim 20''$.
+  However, an elongated structure in the galaxy center resembles a nuclear edge-on disk ($R \lesssim 5''$).
+  The velocity map shows rotation within $R \lesssim 5''$ and no rotation within $5'' \lesssim R \lesssim 15''$.
+  Beyond $R \gtrsim 15''$ one can recognize a sign of rotation in the opposite direction of the nuclear region.
+  The velocity pattern is consistent with the galaxy being a spheroidal system containing a polar ring and a nuclear disk
+  both seen edge-on.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3414_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3414.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3414.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-id + G-r & $28.0$  &  $4.8$ \\
+  T.W. 1D eq.  & S-bul + e-id + G-r & $25.5$  &  $4.5$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  L+10         & S-bul + e-d + F-bar	  & $5.0$  &  $2.6$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3414}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 3489 \\}
+
+  NGC 3489 is a barred lenticular galaxy. 
+  Its disk has a smooth antitruncation at $R \sim 85''$ \citep{erwin2008}.
+
+  \cite{nowak2010n3368n3489} argued for the presence of both a pseudo-bulge and a classical bulge. 
+  %\cite{laurikainen2010} fit this galaxy with a S\'ersic-bulge + exponential-disk + Ferrer-bar
+  %($R_{\rm e} \sim 2''$, $n = 2.1$). 
+  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 4''.6$, $n = 1.5$).
+
+  \emph{1D fit -- }
+  We excluded the data beyond $R \gtrsim 38''$ to avoid fitting the antitruncation region.
+  The bar is fit with a Ferrer function.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3489_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3489.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3489.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar & $2.2$  &  $1.5$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar & $1.7$  &  $1.3$ \\
+  T.W. 2D      & S-bul + e-d + G-bar & $1.7$  &  $2.1$ \\
+  \hline
+  L+10         & S-bul + e-d + F-bar & $2.0$  &  $2.1$ \\
+  S+11         & S-bul + e-d & $4.6$  &  $1.5$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3489}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+
+  {\bf NGC 3585 \\}
+
+  ok
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3585.}
+  \end{center}
+  \end{figure}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+
+  {\bf NGC 3607 \\}
+
+  ok
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3607.}
+  \end{center}
+  \end{figure}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+
+  {\bf NGC 3608 \\}
+
+  ok
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3608.}
+  \end{center}
+  \end{figure}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 3842 \\}
+
+  NGC 3842 is the brightest member of the Leo Cluster (Abell 1367).
+  It is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.7$, 
+  \citealt{rusli2013,dullograham2014cores}).
+
+  %\cite{rusli2013} modeled this galaxy with a core-S\'ersic model 
+  %($R_{\rm e} = 58''.8$, $n = 6.3$).
+
+  \emph{1D fit -- }
+  The light profile presents a swelling at $R \sim 20''$ and the ellipticity profile has a peak in the same position.
+  One can also glimpse a faint elongated oval in the unsharp mask.
+  The innermost $6''.1$ are excluded from the fit due to the presence of a partially depleted core.
+  As expected, a single S\'ersic model is not sufficient to provide a good description of the galaxy light profile 
+  and we need to add a second component (Ferrer function) to account for the embedded lens.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3842exp_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3842.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3842.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + F-l + m-c  & $100.7$  &  $8.1$ \\
+  T.W. 1D eq.  & S-bul + F-l + m-c  & $73.6$   &  $8.2$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  R+13         & core-S\'ersic & $58.8$  &  $6.3$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3842}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 3998 \\}
+
+  NGC 3998 is a barred lenticular galaxy with a Seyfert AGN and dust in its nucleus \citep{knapp1996n3998}.
+  Despite its large stellar velocity dispersion, this galaxy does not have a partially depleted core TBD!! ref??. 
+  \cite{gutierrez2011} identified a bar at $R \lesssim 8''$, a ring between $30'' \lesssim R \lesssim 50''$, and  
+  an antitruncation in the light profile of the disk at $R \sim 122''$.
+  \cite{laurikainen2010} found that NGC 3998 features a weak bar at $R < 8''$,
+  a bright lens at $R < 15''$ and a weak bump in the surface brightness profile at $R \sim 40''$ 
+  %($R_{\rm e} \sim 5''$, $n = 2.0$).
+  %\cite{sani2011} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN 
+  %($R_{\rm e} = 4''.7$, $n = 1.5$).
+  %\cite{beifiori2012} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 5''.7$, $n = 2.3$).
+  %\cite{lasker2014data} used a S\'ersic-bulge + exponential-disk (with inner truncation) + PSF-nucleus + 
+  %S\'ersic-inner disk + S\'ersic-bar 
+  %($R_{\rm e} = 2''.0$, $n = 1.1$).
+
+  \emph{1D fit -- }
+  We see three distinct peaks in the ellipticity profile.
+  The first two peaks occur at $R \sim 7''$ and $R \sim 15''$, and they correspond to a weak bar and to a faint 
+  oval component respectively.
+  These components are both fit with a Ferrer function.
+  The third peak at $R \sim 35''$ coincides with a bump in the surface brightness profile and is produced by a ring.
+  The AGN component is modeled with a Gaussian profile.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3998_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3998.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3998.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + F-l + G-n + G-r & $5.8$  &  $1.2$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + F-l + G-n + G-r & $4.8$  &  $1.3$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  L+10         &  & $5.0$  &  $2.0$ \\
+  S+11         & S-bul + e-d + G-bar + G-n & $4.7$  &  $1.5$ \\
+  B+12         & S-bul + e-d & $5.7$  &  $2.3$ \\
+  L+14         & S-bul + trunc. e-d + PSF-n + S-bar + S-id & $2.0$  &  $1.1$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3998}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4026 \\}
+
+  NGC 4026 is an edge-on lenticular galaxy with a nuclear stellar disk ($R \lesssim 0''.5$, \citealt{ledo2010}).
+
+  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 11''.4$, $n = 3.5$).
+
+  \emph{1D fit -- }
+  The unsharp mask reveals the presence of a bar ($R \lesssim 30''$) and of a disky component 
+  embedded in the bulge, that is responsible for the peak at $R \sim 5''$ in the B4 profile.
+  The last can be also recognized in the velocity map.
+  The bar is fit with a Ferrer function and the inner disk with a low-$n$ S\'ersic profile.
+  Due to the poor spatial resolution of our data, we were not able to model the nuclear stellar disk.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4026_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4026.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4026.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + S-id & $3.4$  &  $2.4$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + S-id & $6.3$  &  $2.1$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  S+11         & S-bul + e-d & $11.4$  &  $3.5$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4026}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4151 \\}
+
+  NGC 4151 is a face-on barred spiral galaxy that hosts a Seyfert AGN \citep{veroncettyveron2006} 
+  and circumnuclear dust \citep{pott2010}.
+
+  \cite{sani2011} fit this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-AGN model
+  ($R_{\rm e} = 5''.4$, $n = 3.5$).
+  \cite{gadotti2008} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar + PSF-AGN 
+  ($R_{\rm e} = 4''.7$, $n = 3.0$).
+
+  \emph{1D fit -- }
+  embedded disk in the bulge,
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4151_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4151.}
+  \end{center}
+  \end{figure}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4261 \\}
+
+  NGC 4261 is an elliptical galaxy with %a radio jet \citep{liuxie1992}, 
+  a LINER nucleus \citep{veroncettyveron2006}
+  and a dusty nuclear disk \citep{tran2001}.
+  The galaxy features a partially depleted core ($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
+
+  %\cite{grahamdriver2007} fit NGC 4261 with a single S\'ersic-bulge 
+  %($R_{\rm e} = 88''.6$, $n = 7.3$).
+  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model 
+  %($R_{\rm e} = 22''.6$, $n = 4.0$).
+  %\cite{vika2012} employed a S\'ersic-bulge + mask-core 
+  %($R_{\rm e} = 24''.2$, $n = 3.5$).
+  %\cite{beifiori2012} adopted a single S\'ersic-bulge model 
+  %($R_{\rm e} = 48''.8$, $n = 4.3$).
+  %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
+  %($R_{\rm e} = 77'.1$, $n = 6.3$).
+  %\cite{lasker2014data} employed a S\'ersic-bulge + mask-core model 
+  %($R_{\rm e} = 68'.4$, $n = 6.5$).
+
+  \emph{1D fit -- }
+  The ellipticity profile has a peak at $R \sim 10''$, unraveling the presence of an embedded component.
+  We identify such component with an inner disk, possibly seen face-on, and we model it with a Ferrer function.
+  The innermost $6''.1$ are excluded from the fit due to the presence of a partially depleted core.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4261_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4261.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4261.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c + F-id & $52.6$  &  $4.7$ \\
+  T.W. 1D eq.  & S-bul + m-c + F-id & $47.3$  &  $4.3$ \\
+  T.W. 2D      & S-bul + m-c + e-id & $50.4$  &  $4.4$ \\
+  \hline
+  GD07      & S-bul		& $88.6$  &  $7.3$ \\
+  S+11      & S-bul + e-d + G-n & $22.6$  &  $4.0$ \\
+  V+12      & S-bul + m-c	& $24.2$  &  $3.5$ \\
+  B+12      & S-bul		& $48.8$  &  $4.3$ \\
+  R+13      & core-S\'ersic	& $77.1$  &  $6.3$ \\
+  L+14      & S-bul + m-c	& $68.4$  &  $6.5$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4261}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4291 \\}
+
+  NGC 4291 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
+
+  %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge 
+  %($R_{\rm e} = 14'.8$, $n = 4.0$).
+  %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
+  %($R_{\rm e} = 15''.3$, $n = 5.6$).
+  %\cite{lasker2014data} adopted a S\'ersic-bulge + mask-core model
+  %($R_{\rm e} = 21''.3$, $n = 8.6$).
+
+  \emph{1D fit -- }
+  After excluding from the fit the innermost $6''.1$, because affected by the partially depleted core,
+  we found that NGC 4291 can be modeled with a single S\'ersic profile.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4291_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4291.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4291.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c & $15.0$  &  $4.2$ \\
+  T.W. 1D eq.  & S-bul + m-c & $15.4$  &  $5.9$ \\
+  T.W. 2D      & S-bul + m-c & $20.8$  &  $7.7$ \\
+  \hline
+  GD07         & S-bul         & $14.8$  &  $4.0$ \\
+  R+13         & core-S\'ersic & $15.3$  &  $5.6$ \\
+  L+14         & S-bul + m-c   & $21.3$  &  $8.6$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4291}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4388 \\}
+
+  NGC 4388 is an edge-on spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006} 
+  and copious nuclear dust \citep{martini2003}.
+
+  \emph{1D fit -- }
+  The peaks at $R \sim 30''$ in the ellipticity and B4 profiles signal the presence of a bar.
+  The data between $35'' \lesssim R \lesssim 65''$ have been excluded because cannot be accommodated by the Ferrer function 
+  used to describe the bar. 
+  The AGN component is fit with a Gaussian profile.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4388_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4388.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4388.}
+  \begin{center}
+  \begin{tabular}{llccc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $4.6$  &  $0.6$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.2$  &  $1.3$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4388}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4459 \\}
+
+  NGC 4459 is a lenticular galaxy.
+  Its disk profile is reported to have an antitruncation at $R \sim 119''$ \citep{gutierrez2011}.
+
+  %\cite{laurikainen2010} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Ferrer-lens 
+  %($R_{\rm e} \sim 7'' $, $n = 3.0$).
+  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 10''.3$, $n = 2.5$).
+  %\cite{vika2012} modeled this galaxy with a S\'ersic-bulge + Moffat-nucleus 
+  %($R_{\rm e} = 25''.0$, $n = 3.9$).
+  %\cite{beifiori2012} adopted a single S\'ersic-bulge model 
+  %($R_{\rm e} = 155''.2$, $n = 7.4$).
+
+  \emph{1D fit -- }
+  The ellipticity constantly increases across all the observed radial range ($R \lesssim 100''$).
+  This is an indication that, going from the galaxy center to the outskirts,
+  the disk component becomes increasingly more important than the spheroidal component.
+  However, the lack of a plateau in the ellipticity profile at large radii implies that at $R \sim 100''$ 
+  the contribution from the bulge is still significant compared to that of the disk.
+  In fact, the surface brightness profile does not display an exponential decline at large radii.
+  We note that the antitruncation reported by \cite{gutierrez2011} could be an artificial feature 
+  produced by the transition between the radial range where the disk becomes increasingly more important 
+  over the bulge and the truly exponential decline of the disk beyond $R \gtrsim 119''$.
+  We do not find evidence for any embedded components in our data.
+  A nuclear light excess is observed in the 1D residuals from a S\'ersic + exponential fit 
+  and is consequently modeled with a Gaussian profile.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4459_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4459.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4459.}
+  \begin{center}
+  \begin{tabular}{llccc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + G-n & $18.4$  &  $3.1$ \\
+  T.W. 1D eq.  & S-bul + e-d + G-n & $13.0$  &  $2.6$ \\
+  %T.W. 2D	&  & $$  &  $$ \\
+  \hline
+  L+10      & S-bul + e-d + F-l & $7.0$   &  $3.0$ \\
+  S+11      & S-bul + e-d	& $10.3$  &  $2.5$ \\
+  V+12      & S-bul + M-n	& $25.0$  &  $3.9$ \\
+  B+12      & S-bul		& $155.2$ &  $7.4$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4459}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4473 \\}
+
+  NGC 4473 is an elliptical galaxy with an embedded disk \citep{scorzabender1998,ledo2010}.
+
+  \cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
+  ($R_{\rm e} = 39''.6$, $n = 2.7$). 
+  \cite{sani2011} used a S\'ersic-bulge model
+  ($R_{\rm e} = 49''.3$, $n = 7.0$). 
+  \cite{vika2012} fit this galaxy with a S\'ersic-bulge + mask-core 
+  ($R_{\rm e} = 21''.3$, $n = 4.3$). 
+  \cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model 
+  ($R_{\rm e} = 10''.6$, $n = 2.2$).  
+  \cite{lasker2014data} described this galaxy with a single S\'ersic-bulge 
+  ($R_{\rm e} = 27''.9$, $n = 5.1$).
+
+  \emph{1D fit -- }
+  TBD!! explain ellipticity profile...
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4473_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4473.}
+  \end{center}
+  \end{figure}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4564 \\}
+
+  NGC 4564 is an edge-on lenticular galaxy.
+
+  %\cite{grahamdriver2007} decomposed this galaxy into a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 4''.3$, $n = 3.2$). 
+  \cite{fisherdrory2008} fit this galaxy with a S\'ersic-bulge + exponential-disk 
+  ($R_{\rm e} = 8''.7$, $n = 3.7$). 
+  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
+  %($R_{\rm e} = 25''.0$, $n = 7.0$).
+  %\cite{vika2012} used a S\'ersic-bulge + exponential-disk model 
+  %($R_{\rm e} = 3''.0$, $n = 3.7$).
+
+  \emph{1D fit -- }
+  The isophotal parameters do not show any evidence for embedded components.
+  However, fitting NGC 4564 with a S\'ersic + exponential model results in bad residuals.
+  In the unsharp mask, one can hardly glimpse an oval structure extending out to $R \lesssim 15''$.
+  The addition of a Ferrer function to the model dramatically improves the fit and smoothes the residuals.
+  Although the lack of strong evidence for the presence of a (faint) third component, 
+  we prefer to model the lens with a Ferrer function 
+  because of the notable improvement in the goodness of the global fit.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4564_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4564.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4564.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-l & $5.0$  &  $2.6$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-l & $6.0$  &  $3.0$ \\
+  %T.W. 2D	&  & $$  &  $$ \\
+  \hline
+  GD07      & S-bul + e-d & $4.3$  &  $3.2$ \\
+  S+11      & S-bul + e-d & $25.0$ &  $7.0$ \\
+  V+12      & S-bul + e-d & $3.0$  &  $3.7$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4564}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4596 \\}
+
+  NGC 4596 is an edge-on barred lenticular galaxy.
+
+  %\cite{laurikainen2005} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Ferrer-bar + Ferrer-lens 
+  %($R_{\rm e} = 2''.8$, $n = 1.4$). 
+  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-bar 
+  %($R_{\rm e} = 28''.0$, $n = 3.0$). 
+  %\cite{vika2012} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
+  %($R_{\rm e} = 13''.2$, $n = 3.6$). 
+  %\cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model
+  %($R_{\rm e} = 44''.9$, $n = 4.4$).
+
+  \emph{1D fit -- }
+  The morphology of this galaxy is quite complex. 
+  The bar extends out to $R \lesssim 50''$ and concludes in two evident ansae.
+  The large-scale disk features a wide ring that is responsible for the curvature in the light profile observed within 
+  $60'' \lesssim R \lesssim 130''$ (see also \citealt{comeron2014}).
+  An additional embedded disk-like component ($R \lesssim 15''$) can be recognized in the B4 profile and in the velocity map.
+  The bump in the light profile within $60'' \lesssim R \lesssim 70''$ corresponds to the ansae of the bar.
+  This data range has therefore been excluded from the fit.
+  The large scale bar is fit with a Ferrer function and the inner disk with a S\'ersic profile.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4596_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4596.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4596.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + G-r + S-id & $6.6$  &  $2.7$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + G-r + S-id & $9.0$  &  $3.0$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  L+05      & S-bul + e-d + F-bar + F-l & $2.8$  &  $1.4$ \\
+  S+11      & S-bul + e-d + G-bar & $28.0$  &  $3.0$ \\
+  V+12      & S-bul + e-d + S-bar & $13.2$  &  $3.6$ \\
+  B+12      & S-bul + e-d & $44.9$  &  $4.4$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4596}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4697 \\}
+
+  NGC 4697 is an elliptical galaxy with an embedded disk \cite{scorzabender1995}.
+
+  %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge model
+  %($n = 4.0$).
+  %\cite{sani2011} described it with a S\'ersic-bulge 
+  %($R_{\rm e} = 100'.5$, $n = 5.0$). 
+  %\cite{vika2012} proposed a single S\'ersic-bulge model 
+  %($R_{\rm e} = 39''.1$, $n = 3.8$) 
+  %or a S\'ersic-bulge + exponential-disk model 
+  %($R_{\rm e} = 10''.0$, $n = 2.9$).
+  %\cite{beifiori2012} chose a single S\'ersic-bulge 
+  %($R_{\rm e} = 128''.7$, $n = 5.0$).
+  %\cite{lasker2014data} decomposed NGC 4697 into a S\'ersic-bulge + exponential-disk + PSF-nucleus + S\'ersic-envelope 
+  %($R_{\rm e} = 6''.3$, $n = 2.1$).
+
+  \emph{1D fit -- }
+  The velocity map and the unsharp mask of NGC 4697 clearly show 
+  the presence of an intermediate-size disk embedded in the main spheroid.
+  However, the ellipticity profile presents two peaks. 
+  The peak at $R \sim 40''$ corresponds to the embedded disk already mentioned,
+  while the peak at $R \sim 10''$ unveils a second inner disk-like component.
+  After testing different decomposition models, 
+  in which we fit the embedded disks with a set of different functions (exponential, S\'ersic, Ferrer)
+  but we always described the main spheroidal component with a S\'ersic profile,
+  we noticed that the bulge parameters did not vary significantly among the various decompositions.
+  Our preferred model for NGC 4697 consists of a S\'ersic-bulge + 2 S\'ersic-inner disks.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4697_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4697.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4697.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + 2 S-id & $239.3$  &  $7.2$ \\
+  T.W. 1D eq.  & S-bul + 2 S-id & $226.4$  &  $6.7$ \\
+  T.W. 2D      & S-bul + e-id	& $121.4$  &  $5.0$ \\
+  \hline
+  GD07  & S-bul & $-$  &  $4.0$ \\
+  S+11  & S-bul & $100.5$  &  $5.0$ \\
+  V+12  & S-bul & $39.1$  &  $3.8$ \\
+  V+12  & S-bul + e-d & $10.0$  &  $2.9$ \\
+  L+14  & S-bul + e-d + PSF-n + S-halo & $6.3$  &  $2.1$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4697}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4889 \\}
+
+  NGC 4889 is the brightest member of the Coma cluster. 
+  It is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.6$, \citealt{rusli2013}).
+
+  %\cite{rusli2013} modeled NGC 4889 with a core-S\'ersic model 
+  %($R_{\rm e} = 169''.2$, $n = 9.8$).
+
+  \emph{1D fit -- }
+  We excluded from the fit the innermost $6''.1$ because affected by the partially depleted core and
+  we modeled the galaxy with a single S\'ersic profile.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4889.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4889.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c & $119.7$  &  $8.1$ \\
+  T.W. 1D eq.  & S-bul + m-c & $60.8$	&  $6.8$ \\
+  T.W. 2D      & S-bul + m-c & $104.3$  &  $7.8$ \\
+  \hline
+  R+13         & core-S\'ersic & $169.2$  &  $9.8$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4889}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 4945 \\}
+
+  TBD!!! \\
+  NGC 4945 is an edge-on, dusty spiral galaxy that hosts a Seyfert AGN \citep{lin2011}.
+
+  \cite{kormendy2010} found that the bulge of NGC 4945 is best modeled with a low-$n$ S\'ersic function
+  ($n = 1.3$).
+
+  \emph{1D fit -- }
+  Given the edge-on inclination of this object, the identification of a possible large-scale bar is complicated.
+  The light profile has an obvious bump that could be interpreted in two different ways.
+  The bump could be produced by a large-scale bar; 
+  in this case, either the disk must have a truncation happening at a radius smaller than the length of the bar,
+  or its light profile cannot be exponential (this condition can be caused by the high inclination of the galaxy).
+  Alternatively, the bump could be due by the galaxy spiral arms, the disk has an exponential profile with no truncation
+  and the galaxy has no bar.
+  After checking that both scenarios result in similar best-fit parameters for the bulge, 
+  we choose the second and simpler hypothesis.
+  We exclude form the fit the data between $R \sim 100''-400''$, where the spiral arm would contribute to the galaxy light,
+  and we also exclude the innermost $6''.4$ due to the presence of the AGN.
+  Our final model for NGC 4945 consists of a S\'ersic-bulge + exponential-disk.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4945_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4945.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4945.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d & $13.9$  &  $1.4$ \\
+  T.W. 1D eq.  & S-bul + e-d & $9.5$   &  $1.7$ \\
+  T.W. 2D      & S-bul + e-d & $16.2$  &  $0.8$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4945}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 5077 \\}
+
+  ok
+
+  \emph{1D fit -- }
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n5077_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 5077.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 5077.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c & $23.5$  &  $4.2$ \\
+  T.W. 1D eq.  & S-bul + m-c & $23.0$  &  $5.7$ \\
+  T.W. 2D      & S-bul + m-c & $30.5$  &  $6.8$ \\
+  \hline
+  S+11         & S-bul + G-n & $29.2$  &  $6.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n5077}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+
+  {\bf NGC 5128 - Centaurus A \\}
+
+  ok
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n5128_1Dfit.eps}
+  \caption{}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 5128.}
+  \begin{center}
+  \begin{tabular}{llccc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & TBD!! & $61.3$  &  $1.2$ \\
+  T.W. 1D eq.  &  & $60.8$  &  $2.2$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  S+11         & S-bul + e-d + G-n & $103.6$  &  $3.5$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n5128}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+
+  {\bf NGC 5576 \\}
+
+  ok
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
+  \caption{}
+  \end{center}
+  \end{figure}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 5845 \\}
+
+  NGC 5845 is an elliptical/lenticular galaxy.
+
+  %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
+  %($R_{\rm e} = 4''.1$,$n = 3.2$).
+  %\cite{sani2011} fit it with a S\'ersic-bulge 
+  %($R_{\rm e} = 3''.7$, $n = 3.0$). 
+  %\cite{vika2012} used a S\'ersic-bulge model 
+  %($R_{\rm e} = 3''.5$, $n = 2.6$).
+  %\cite{beifiori2012} chose a single S\'ersic-bulge 
+  %($R_{\rm e} = 4''.1$, $n = 3.5$).
+  %\cite{lasker2014data} described this galaxy with a S\'ersic-bulge 
+  %($R_{\rm e} = 3''.5$, $n = 2.8$).
+
+  \emph{1D fit -- }
+  The small apparent size of NGC 5845 (compared to the PSF FWHM) implies low resolution for the data 
+  and complications for the modeling of this galaxy.
+  Here, looking at the unsharp mask and the velocity field, we identify 
+  a disk component, either large-scale or embedded.
+  To rule out one of the two cases, a good test would be to check whether
+  the light profile of NGC 5845 presents an exponential decline in its outer part.
+  Unfortunately, the IRAC image is not deep enough and beyond $R \gtrsim 23''$ the galaxy light 
+  is fainter than $3 RMS_{\rm SKY}$.
+  %Since the too small radial range prevents us from disentangling between an embedded and a large-scale disk,
+  %we choose the most statistically significant solution (lowest $\chi^2$), 
+  %but we caution that the best fit parameters might be biased by a non adequate choice
+  %of the model components. 
+  %However, our results are in agreement with those from \cite{jia2012}, 
+  %who study the structure and kinematics of NGC5845 with HST/WFPC2 data 
+  %and previously published spatially resolved kinematics, and unambiguously identify a 
+  %large scale disk in both the photometry and the kinematics. \\
+  The ellipticity profile has a peak at $R \sim 13''$ and therefore suggests that the disk is indeed embedded.
+  However, when fitting NGC 5845 with a S\'ersic + exponential model, 
+  the lowest-$\chi^2$ solution does not reproduce an inner disk, but rather a large-scale one.
+  This is because the S\'ersic and the exponential function are degenerate in this decomposition, 
+  due to the small number of data points sampling the galaxy light profile.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n5845_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 5845.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 5845.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d & $3.6$  &  $2.5$ \\
+  T.W. 1D eq.  & S-bul + e-d & $3.1$  &  $2.3$ \\
+  T.W. 2D      & S-bul + e-d & $2.8$  &  $2.4$ \\
+  \hline
+  GD07      & S-bul & $4.1$  &  $3.2$ \\
+  S+11      & S-bul & $3.7$  &  $3.0$ \\
+  V+12      & S-bul & $3.5$  &  $2.6$ \\
+  B+12      & S-bul & $4.1$  &  $3.5$ \\
+  L+14      & S-bul & $3.5$  &  $2.8$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n5845}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 5846 \\}
+
+  NGC 5846 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
+  This galaxy has a LINER nucleus \citep{carrillo1999} and filamentary nuclear dust \citep{tran2001}.
+
+  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge
+  %($R_{\rm e} = 36''.4$, $n = 3.0$). 
+  %\cite{vika2012} used a S\'ersic-bulge + mask-core model 
+  %($R_{\rm e} = 46''.3$, $n = 3.7$). 
+  %\cite{rusli2013} fit this galaxy with a core-S\'ersic profile 
+  %($R_{\rm e} = 113''.2$, $n = 5.3$).
+
+  \emph{1D fit -- }
+  This galaxy has a strong isophotal twist between its center and $R \sim 70''$, and
+  its light profile presents a slight bump at $R \sim 20''$.
+  However, the isophotal parameters, the unsharp mask and the velocity map lack of clear evidence for an embedded component.
+  We thus model NGC 5846 with a single S\'ersic profile, after masking the innermost $6''.1$.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n5846_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 5846.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 5846.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c & $105.1$  &  $6.4$ \\
+  T.W. 1D eq.  & S-bul + m-c & $83.4$	&  $5.7$ \\
+  T.W. 2D      & S-bul + m-c & $85.1$	&  $5.2$ \\
+  \hline
+  S+11      & S-bul	    & $36.4$   &  $3.0$ \\
+  V+12      & S-bul + m-c   & $46.3$   &  $3.7$ \\
+  R+13      & core-S\'ersic & $113.2$  &  $5.3$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n5846}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 6251 \\}
+
+  NGC 6251 is an elliptical galaxy with a large stellar velocity dispersion ($\sigma \sim 310~\rm km~s^{-1}$),
+  which is a clue for the presence of a partially depleted core.
+  The galaxy features a nuclear disk of dust \citep{ferrareseford1999n6251} and a Seyfert AGN \citep{panessabassani2002}.
+
+  %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge 
+  %($R_{\rm e} = 173''.92$, $n = 11.8$). 
+  %\cite{sani2011} adopted a S\'ersic-bulge + Gaussian-AGN model 
+  %($R_{\rm e} = 42''.4$, $n = 7.0$). 
+  %\cite{lasker2014data} modeled this galaxy with a S\'ersic-bulge 
+  %($R_{\rm e} = 20''.6$, $n = 5.0$).
+
+  \emph{1D fit -- }
+  We masked the innermost $6''.1$ because possibly affected by the combined contribution of the AGN 
+  and the partially depleted core. 
+  A single S\'ersic profile provides a good description of NGC 6251.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n6251_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 6251.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 6251.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c & $41.7$  &  $6.8$ \\
+  T.W. 1D eq.  & S-bul + m-c & $30.1$  &  $5.6$ \\
+  T.W. 2D      & S-bul + m-c & $39.3$  &  $7.1$ \\
+  \hline
+  GD07      & S-bul	     & $173.9$  &  $11.8$ \\
+  S+11      & S-bul + G-n    & $42.4$	&  $7.0$ \\
+  L+14      & S-bul	     & $20.6$	&  $5.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n6251}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 7052 \\}
+
+  NGC 7052 is an elliptical galaxy reported to have a partially depleted core 
+  ($R_{\rm break} = 0''.8$, \citealt{quillen2000}).
+
+  %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
+  %($R_{\rm e} = 70''.4$, $n = 4.6$). 
+  %\cite{sani2011} used a S\'ersic-bulge model 
+  %($R_{\rm e} = 39''.3$, $n = 5.0$). 
+  %\cite{vika2012} fit this galaxy with a S\'ersic-bulge + exponential-disk
+  %($R_{\rm e} = 4''.3$, $n = 1.8$).
+  %\cite{lasker2014data} adopted a S\'ersic-bulge model 
+  %($R_{\rm e} = 26''.6$, $n = 4.2$).
+
+  \emph{1D fit -- }
+  A single S\'ersic function provides a fairly good description of the surface brightness profile of NGC 7052.
+  However, the residuals of such fit display a curious behaviour, having a nuclear light excess along the major-axis 
+  and a nuclear light deficit along the equivalent-axis. 
+  This pattern is still present when the innermost $6''.1$ are excluded and the fit is repeated with a S\'ersic profile.
+  The reasons for this are unclear. 
+  The best-fit parameters obtained from a single S\'ersic fit, without excluding the innermost data points,
+  are not significantly different from those obtained when excluding the core region (see Table \ref{tab:n7052}).
+  Given the uncertainty connected to the nuclear region of this galaxy,
+  we preferred the model that incorporates the exclusion of the innermost $6''.1$, 
+  with the caveat about the ambiguous presence of a partially depleted core.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n7052_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 7052.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 7052.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  \multicolumn{4}{c}{\emph{excluding innermost $6''.1$}} \\
+  T.W. 1D maj. & S-bul + m-c & $59.4$  &  $4.2$ \\
+  T.W. 1D eq.  & S-bul + m-c & $37.0$  &  $5.6$ \\
+  T.W. 2D      & S-bul + m-c & $36.2$  &  $4.0$ \\
+  \hline
+  \multicolumn{4}{c}{\emph{including innermost $6''.1$}} \\
+  T.W. 1D maj. & S-bul & $66.1$  &  $4.8$ \\
+  T.W. 1D eq.  & S-bul & $35.0$  &  $5.0$ \\
+  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  \hline
+  GD07      & S-bul & $70.4$  &  $4.6$ \\
+  S+11      & S-bul & $39.3$  &  $5.0$ \\
+  V+12      & S-bul + e-d & $4.3$  &  $1.8$ \\
+  L+14      & S-bul & $26.6$  &  $4.2$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n7052}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 7619 \\}
+
+  NGC 7619 is an elliptical galaxy reported to have a partially depleted core ($R_{\rm break} = 0''.5$, \citealt{rusli2013}).
+
+  %\cite{rusli2013} fit this galaxy with a core-S\'ersic profile 
+  %($R_{\rm e} = 100''.1$, $n = 9.3$).
+
+  \emph{1D fit -- }
+  We identified an embedded disk signaled by the peak at $R \sim 10''$ in the ellipticity profile.
+  The velocity map of this galaxy confirms the presence of a fast rotating component (Falcon-Barroso private comm.).
+  We modeled NGC 7619 with a S\'ersic + inner-exponential model.
+  We note that the residuals obtained from our best-fit model do not suggest the presence of a partially depleted core,
+  whereas they display a nuclear lack of light when the galaxy is modeled with a single S\'ersic-bulge.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n7619_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 7619.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 7619.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-id & $63.2$  &  $5.3$ \\
+  T.W. 1D eq.  & S-bul + e-id & $58.0$  &  $5.2$ \\
+  \hline
+  R+13      & core-S\'ersic & $100.1$  &  $9.3$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n7619}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf NGC 7768 \\}
+
+  NGC 7768 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
+
+  %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
+  %($R_{\rm e} = 46''.1$, $n = 6.2$).
+
+  \emph{1D fit -- }
+  The image of NGC 7768 is corrupted by a saturated star, which lies close to the galaxy.
+  The sky background is not constant across the image.
+  To be safe, we fit only the innermost $R \lesssim 30''$, where the contribution from the background is negligible.
+  The data within $R < 6''.1$ are excluded from the fit due to the presence of a partially depleted core.
+  Our best-fit model consists of a single S\'ersic profile.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n7768_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 7768.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 7768.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + m-c & $92.9$  &  $8.4$ \\
+  T.W. 1D eq.  & S-bul + m-c & $42.1$  &  $6.7$ \\
+  \hline
+  R+13      & core-S\'ersic & $46.1$  &  $6.2$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n7768}
+  \end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \clearpage\newpage\noindent
+  {\bf UGC 03789 \\}
+
+  UGC 03789 is a face-on spiral galaxy.
+
+  \emph{1D fit -- }
+  This galaxy features a ring ($R \sim 20''$) and a nuclear bar ($R \lesssim 4''$),
+  which can be seen in the unsharp mask and produces corresponding peaks in the ellipticity and PA profiles.
+  The bar is fit with a Ferrer function.
+
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/ugc03789_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for UGC 03789.}
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of UGC 03789.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + G-r & $1.8$  &  $1.9$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + G-r & $2.4$  &  $1.4$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:ugc3789}
+  \end{table}
+
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\bibliography{/Users/gsavorgnan/Dropbox/giulia_e_basta/Literature/SMBHbibliography}
+\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
 

### 2015-05-27 papers/data_paper/datapaper.tex
stancaaa

@@
   individual galaxies \\
+  For each galaxy, we show a figure and a table. 
+  The figure illustrates our 1D best-fit model and the galaxy isophotal parameters. 
+  The left panels refer to the major-axis $R_{\rm maj}$, 
+  while the right panels refer to the equivalent-axis $R_{\rm eq}$, 
+  i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$).
+  The top panels display the galaxy surface brightness ($\mu$) radial profiles obtained with a linear sampling. 
+  The black points are the observed data.  
+  The color lines represent the individual (PSF-convolved) model components:
+  red=S\'ersic, dark blue=exponential, green=Gaussian, cyan=Ferrer, gray=Gaussian ring, pink=PSF. 
+  The best-fit parameters for the S\'ersic bulge model are inset.
+  The total (PSF-convolved) model is shown with a black dashed line. 
+  The residual profile ($data - model$) is shown as $\Delta \mu$ in the second row.
+  The horizontal grey dashed line corresponds to an intensity 
+  equal to three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$).
+  $\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
+  The lower six panels show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles. \\
+  The table reports a comparison between our results (from both our 1D and 2D decompositions) and those obtained by the following authors: 
+  GD07 = \citeauthor{grahamdriver2007} (\citeyear{grahamdriver2007}, who performed 1D fits along the major-axis), 
+  L+10 = \citeauthor{laurikainen2010} (\citeyear{laurikainen2010}, who performed 2D fits), 
+  S+11 = \citeauthor{sani2011} (\citeyear{sani2011}, who performed 2D fits), 
+  B+12 = \citeauthor{beifiori2012} (\citeyear{beifiori2012}, who performed 2D fits), 
+  V+12 = \citeauthor{vika2012} (\citeyear{vika2012}, who performed 2D fits), 
+  R+13 = \citeauthor{rusli2013} (\citeyear{rusli2013}, who performed 1D fits along the equivalent-axis),
+  and L+14 = \citeauthor{lasker2014data} (\citeyear{lasker2014data}, who performed 2D fits).
+  Each galaxy model is the sum of its individual components, which are expressed with the following nomenclature: (analytic function)-(physical component).
+  The analytic functions can be: S=S\'ersic, e=exponential, G=Gaussian, F=Ferrer, M=Moffat and PSF.
+  The physical components can be: bul=bulge or spheroid, d=disk, id=inner disk, bar, n=nucleus, l=lens or oval, r=ring, halo and spiral arms. 
+  When a nuclear component or a partially depleted core have been masked, we signal them as ``m-n'' and ``m-c'', respectively.
+  For example, the model ``S-bul + e-d + e-id + m-n + G-r'' reads ``S\'ersic-bulge + exponential-disk + exponential-inner disk + mask-nucleus + Gaussian-ring''. 
+  The core-S\'ersic model used by \cite{rusli2013} is always implicitly associated with the galaxy spheroidal component. 
+  When fitting their galaxy light profiles, \citeauthor{grahamdriver2007} excluded the innermost data points. 
+  Their models implicitly include ``m-n'' or ``m-c''. 
+  In the table caption, we comment on the most significant discrepancies between our results and those obtained by the other studies.
 
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for IC 1459.
   IC 1459 is an elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
@@
   The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
-  This galaxy has also an unresolved partially depleted core \citep{rusli2013}. \\ % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
-
-  \emph{1D fit -- }
+  This galaxy has also an unresolved partially depleted core \citep{rusli2013}.  % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
   Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
-  We masked the innermost $6''.1$ affected by the partially depleted core 
-  and we fit this galaxy with a S\'ersic profile. \\
-
-  \emph{Other models -- } 
-  The best-fit model of L+14 is in reasonable agreement with our results. 
-  S+11 obtained the smallest S\'ersic index because they fit a nuclear component rather than masking the core. 
-  R+13 obtained the smallest effective radius 
-  because they fit a circularized light profile that only extends out to $R_{\rm eq} \lesssim 60''$.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for IC 1459.}
+  After masking the innermost $6''.1$, we fit this galaxy with a S\'ersic profile.  }
   \end{center}
@@
   \label{tab:ic1459}
+  \tablecomments{S+11 obtained the smallest estimate of the S\'ersic index because they fit a nuclear component rather than masking the core. 
+  R+13 obtained the smallest estimate of the effective radius 
+  because they fit a circularized light profile that only extends out to $R_{\rm eq} \lesssim 60''$. }
   \end{table}
@@
 
-  IC 2560 is a barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
-  and dust within the central $2''.5$ \citep{martini2003}.\\
-
-  \emph{1D fit -- }
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for IC 2560. IC 2560 is a barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
+  and dust within the central $2''.5$ \citep{martini2003}.
   A visual inspection of the image of IC 2560 reveals a boxy bulge and
@@
   This is why the surface brightness profile deviates from a perfect exponential
-  in the radial range $42'' \lesssim R_{\rm maj} \lesssim 60''$, which has been excluded from the fit.
+  in the radial range $42'' \lesssim R_{\rm maj} \lesssim 60''$, which is excluded from the fit.
   Motivated by the presence of a strong optical AGN and dust in the nucleus, 
-  we accounted for an excess of non-stellar light by adding a central Gaussian component to the model.\\
-
-  \emph{Other models -- } 
-  In their model, S+11 did not account for the bar component and thus overestimated the effective radius and the S\'ersic index of the bulge.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for IC 2560.}
+  we account for an excess of non-stellar light by adding a central Gaussian component to the model.}
   \end{center}
@@
   \label{tab:ic2560}
+  \tablecomments{In their model, S+11 did not account for the bar component and thus overestimated the effective radius and the S\'ersic index of the bulge.}
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for IC 4296.
   IC 4296 is an elliptical galaxy. 
   Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
-
-  \emph{1D fit -- }
   After masking the innermost $6''.1$, 
-  we found that a single S\'ersic profile provides a fairly good description of this galaxy.
-
-  \emph{Other models -- } 
-  S+11 obtained the smallest effective radius and S\'ersic index because they fit a nuclear component rather than masking the core. 
-  L+14 obtained the largest effective radius and S\'ersic index, 
-  although the 1D representation of their 2D fit (their Figure 8) shows that their model overestimates the galaxy light at large radii ($R > 100''$), 
-  implying the need for a smaller $R_{\rm e}$ and $n$. 
-  We did not find any conclusing explanation for this, 
-  but we suspect it may be due to the different pixel weighting scheme that they used.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for IC 4296.}
+  we find that a single S\'ersic profile provides a fairly good description of this galaxy.}
   \end{center}
@@
   \label{tab:ic4296}
+  \tablecomments{
+  S+11 obtained the smallest effective radius and S\'ersic index because they fit a nuclear component rather than masking the core. 
+  L+14 obtained the largest effective radius and S\'ersic index, 
+  although the 1D representation of their 2D fit (their Figure 8) shows that their model overestimates the galaxy light at large radii ($R_{\rm maj} > 100''$), 
+  implying the need for a smaller $R_{\rm e}$ and $n$. 
+  We suspect that this could be due to the pixel weighting scheme that they used.
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M31.
   M31, the Andromeda galaxy, is a spiral galaxy. 
@@
   M31 also features a ring-like structure at $R_{\rm maj} \sim 50'$ \citep{athanassoulabeaton2006m31}. 
-
-  \emph{1D fit -- }
   We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
-  The region $2000'' \lesssim R_{\rm maj} \lesssim 3400''$, where the pseudo-ring is observed, was excluded from the fit.
+  The region $2000'' \lesssim R_{\rm maj} \lesssim 3400''$, where the pseudo-ring is observed, is excluded from the fit.
   A S\'ersic + exponential fit is not adequate to describe the light profile of M31,
   as the residuals of such fit display a structure in correspondence of the bar ($R_{\rm maj} \lesssim 1500''$).
-  The addition of a Ferrer function to account for the bar notably improved the fit.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M31.}
+  The addition of a Ferrer function to account for the bar notably improves the fit.
+  }
   \end{center}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M49.
   M49, the brightest member of the Virgo cluster, is a giant elliptical galaxy 
-  with a slightly resolved partially depleted core \citep{rusli2013}. \\ %($R_{\rm break} = 1''.8$, \citealt{rusli2013}).
-
-  \emph{1D fit -- }
-  We excluded from the fit the innermost $12''$.
-  We found no evidence for embedded components and
-  we fit M49 with a single S\'ersic profile. \\
-
-  \emph{Other models -- } 
-  The effective radius estimated by R+13 is larger than that measured by us along the equivalent axis.
-  Since their circularized light profile is almost 3 times more extended than ours, 
-  it is possible that their best-fit model required a larger $R_{\rm e}$ to account for the galaxy intracluster halo light.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M49.}
+  with a slightly resolved partially depleted core \citep{rusli2013}.  %($R_{\rm break} = 1''.8$, \citealt{rusli2013}).
+  The data within the innermost $12''$ are excluded from the fit.
+  We fit M49 with a single S\'ersic profile. 
+  }
   \end{center}
@@
   \label{tab:m49}
+  \tablecomments{
+  The equivalent-axis effective radius estimated by R+13 is larger than that measured by us.
+  Since their circularized light profile is almost 3 times more extended than ours, 
+  it is possible that their best-fit model required a larger $R_{\rm e}$ to account for the galaxy intracluster halo light.
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M59.
   M59 is an elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
-  and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}.\\
-
-  \emph{1D fit -- }
+  and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}. 
   The intermediate-scale embedded disk is clearly visible in our unsharp mask image, and 
-  the velocity field confirms the presence of a rapidly rotating component. 
-  This has been modeled with an exponential function.
-  We chose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit. \\
-
-  \emph{Other models -- } 
-  We observed no significant discrepancies between our results and the best-fit models of S+11 and V+12.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M59.}
+  the velocity map confirms the presence of a rapidly rotating component, which is modeled with an exponential function.
+  We choose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.  
+  }
   \end{center}
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  %%\clearpage\newpage\noindent
-  %%
-  %%{\bf M60 -- NGC 4649 \\}
-  %%
-  %%exclude it, doesn't make sense
-  %%
-  %%
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   \clearpage\newpage\noindent
@@
 
-  M64 is a dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. \\
-
-  \emph{1D fit -- }
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m64_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M64.
+  M64 is a dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. 
   A large-scale bar ($R_{\rm maj} \lesssim 50''$) can be identified in the unsharp mask 
   and produces corresponding peaks in the ellipticity, PA and B4 profiles.
-  We modeled it with a Ferrer function.
+  This is modeled with a Ferrer function.
   Additional peaks in the ellipticity, PA and B4 profiles at $R_{\rm maj} \sim 15''$ 
-  signal the presence of an embedded disky component, that we described with a low-$n$
-  S\'ersic function.
+  signal the presence of an embedded disky component, that we describe with a low-$n$ S\'ersic function.
   Although the galaxy is dusty and hosts an AGN, we do not observe any nuclear excess of light 
-  in the fit residuals and therefore we consider unnecessary to add a nuclear component to our model. \\
-
-  \emph{Other models -- } 
-  The best-fit model of B+12 is in reasonable agreement with our results.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m64_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M64.}
+  in the fit residuals and therefore we consider unnecessary to add a nuclear component to our model. 
+  }
   \end{center}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m81_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M81.
   M81 is an early-type spiral galaxy.
-  This galaxy features two bars \citep{elmegreen1995m81,gutierrez2011,erwindebattista2013}. \\
-
-  \emph{1D fit -- }
+  This galaxy features two bars \citep{elmegreen1995m81,gutierrez2011,erwindebattista2013}. 
   We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M81.
@@
   Any attempt to account for the bars in the fit was unsuccessful. 
-  For this reason, we used a simple S\'ersic + exponential model to describe M81. \\
-
-  \emph{Other models -- } 
+  For this reason, we use a simple S\'ersic + exponential model. 
+  }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M81.}
+  \begin{center}
+  \begin{tabular}{llccc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d  & $31.0$  &  $1.7$ \\
+  T.W. 1D eq.  & S-bul + e-d  & $33.2$  &  $2.1$ \\
+  %T.W. 2D	&   & $$  & $$  &  $$ \\
+  \hline
+  GD07      & S-bul + e-d	 & $68.1$   &  $3.3$ \\
+  S+11      & S-bul + e-d + G-n  & $127.3$  &  $3.0$ \\
+  B+12      & S-bul + e-d	 & $50.0$   &  $2.6$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m81}
+  \tablecomments{
   GD07 and B+12 obtained estimates of the effective radius larger than ours by a factor of two. 
@@
   but the reasons for this are unclear. 
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m81_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M81.}
-  \end{center}
-  \end{figure}
-
-  \begin{table}[h]
-  \small
-  \caption{Best-fit parameters for the spheroidal component of M81.}
-  \begin{center}
-  \begin{tabular}{llccc}
-  \hline
-  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
-    &  &  $[\rm arcsec]$ & \\
-  \hline
-  T.W. 1D maj. & S-bul + e-d  & $31.0$  &  $1.7$ \\
-  T.W. 1D eq.  & S-bul + e-d  & $33.2$  &  $2.1$ \\
-  %T.W. 2D	&   & $$  & $$  &  $$ \\
-  \hline
-  GD07      & S-bul + e-d	 & $68.1$   &  $3.3$ \\
-  S+11      & S-bul + e-d + G-n  & $127.3$  &  $3.0$ \\
-  B+12      & S-bul + e-d	 & $50.0$   &  $2.6$ \\
-  \hline
-  \end{tabular}
-  \end{center}
-  \label{tab:m81}
+  }
   \end{table}
@@
 
-  M84 is an elliptical galaxy with a slightly resolved partially depleted core \citep{rusli2013}.\\ %($R_{\rm break} = 1''.5$, \citealt{rusli2013}).
-
-  \emph{1D fit -- }
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m84_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M84.
+  M84 is an elliptical galaxy with a slightly resolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 1''.5$, \citealt{rusli2013}). 
   The unsharp mask reveals a faint inner component ($R_{\rm maj} \lesssim 12''$). 
-  Here we excluded the data within $R_{\rm maj} < 13''.8$ and modeled the galaxy with a S\'ersic profile.\\
-
-  \emph{Other models -- } 
-  The results obtained by S+11, R+13 and L+14 are in good agreement with those obtained by us. 
-  B+12 did not mask the core and thus underestimated the effective radius and the S\'ersic index. 
-  V+12 used the same model as R+13, L+14 and us, 
-  but the smaller radial extent of their data led them to underestimate the effective radius and the S\'ersic index.
-  It is not clear why GD07 obtained smaller estimates of the effective radius and the S\'ersic index, 
-  since they tipically did not fit the innermost data points of their light profiles.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m84_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M84.}
+  We exclude the data within $R_{\rm maj} < 13''.8$ and model the galaxy with a S\'ersic profile.
+  }
   \end{center}
@@
   \label{tab:m84}
+  \tablecomments{
+  B+12 did not mask the core and thus underestimated the effective radius and the S\'ersic index. 
+  V+12 used the same model as R+13, L+14 and us, 
+  but the smaller radial extent of their data led them to underestimate the effective radius and the S\'ersic index.
+    }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m87_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M87.
   M87 is a giant elliptical galaxy belonging to the Virgo cluster.
-  This galaxy has a large ($> 7''$), partially depleted core \citep{ferrarese2006acsvcs}.\\
-
-  \emph{1D fit -- }
+  This galaxy has a large ($> 7''$), partially depleted core \citep{ferrarese2006acsvcs}.
   The morphology of M87 is similar to that of M49.
-  The innermost $18''.5$ were excluded from the fit.
-  We used a single S\'ersic model to fit M87. 
-  We note that the 1D major-axis effective radius obtained from our 1D fit is more than a factor of two larger than that obtained from our 2D fit, 
-  because the last one cannot account for the strong ellipticity gradient of the galaxy.  \\
-
-  \emph{Other models -- } 
-  The 2D fits of S+11 and L+14 produce results which are consistent with our 2D best-fit model. 
-  The 1D fit along the equivalent-axis of R+13 returns the largest values for $R_{\rm e,sph}$ and $n_{\rm sph}$. 
-  As in the case of M49, since their circularized light profile is almost three times more extended than ours, 
-  their best-fit model probably required a larger $R_{\rm e}$ to account for the extra intracluster halo light.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m87_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M87.}
+  The innermost $18''.5$ are excluded from the fit and
+  a S\'ersic model is used to fit M87. 
+  We note that the effective radius obtained from our 1D major-axis fit is more than a factor of two larger than that obtained from our 2D fit.
+  This is due to the fact that the 2D model has fixed ellipticity and cannot account for the strong ellipticity gradient of the galaxy.  
+  }
   \end{center}
@@
   \label{tab:m87}
+  \tablecomments{
+  The fit of R+13 returns the largest values for $R_{\rm e,sph}$ and $n_{\rm sph}$. 
+  As in the case of M49, since their circularized light profile is almost three times more extended than ours, 
+  it is possible that their best-fit model required a larger $R_{\rm e}$ to account for the extra intracluster halo light.
+  V+12 obtained the smallest estimates of $R_{\rm e,sph}$ and $n_{\rm sph}$ because of the small radial extent of their data.
+  }
   \end{table}
@@
 
-  M94 is an almost face-on spiral galaxy, with a Seyfert AGN \citep{veroncettyveron2006} and 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m94_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M94.
+  M94 is a face-on spiral galaxy, with a Seyfert AGN \citep{veroncettyveron2006} and 
   circumnuclear dust \citep{elmegreen2002m94,peeplesmartini2006m94}.
-  This galaxy has a ring-like structure at $R_{\rm maj} \sim 50''$ \citep{munoztunon1989m94}.\\
-
-  \emph{1D fit -- }
+  This galaxy has a ring-like structure at $R_{\rm maj} \sim 50''$ \citep{munoztunon1989m94}.
   The ellipticity and B4 profiles display a local maximum at $R_{\rm maj} \sim 10''$, 
@@
   as already noted by \cite{fisherdrory2010}.
-  We modeled this component with a Ferrer function.
-  We excluded the data within the innermost $6''.7$, due to the AGN contribution.
+  We model this component with a Ferrer function.
+  We exclude the data within the innermost $6''.7$, due to the AGN contribution.
   Any attempt to model the ring was unsuccessful, resulting in a degenerate model, 
-  therefore we preferred to exclude also the data in the range $20'' \lesssim R_{\rm maj} \lesssim 80''$.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m94_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M94.}
+  therefore we also exclude the data in the range $20'' \lesssim R_{\rm maj} \lesssim 80''$.
+  }
   \end{center}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m96_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M96.
   M96 is a spiral galaxy with a large scale bar and no AGN activity \citep{martini2003,nowak2010n3368n3489}. 
+  \cite{erwin2004} observed the presence of two bars in this galaxy. 
   \cite{nowak2010n3368n3489} reported the presence of a large pseudo-bulge and a tiny classical bulge 
   ($R_{\rm e, sph} = 1''.6$, $n_{\rm sph} = 2.3$). 
-  \cite{erwin2004} observed the presence of two bars in this galaxy. \\
-
-  \emph{1D fit -- }
+  However, they came to this conclusion by modeling only the innermost $8''.5$ of the 
+  light profile of M96 with a S\'ersic-classical bulge and an exponential-pseudobulge, 
+  but without subtracting the contribution of the large-scale disk and the large-scale bar.
+  They also acknowledged the presence of a secondary inner bar, but did not include it in their fit. 
   M96 has a complex morphology. 
@@
   which however are too faint and irregular to be described with a Gaussian ring model. 
-  The large scale bar extends out to $R_{\rm maj} \lesssim 80''$ and has been modeled with a Ferrer function.
-  A peak at $R_{\rm maj} \sim 25''$ in the ellipticity profile unravels an inner component embedded in the bulge, 
-  that we modelled with a low-$n$ S\'ersic profile.
-  The residuals do not display any significant light excess in the nuclear region, 
-  in agreement with the lack of AGN activity.\\
-
-  \emph{Other models -- } 
+  The large scale bar extends out to $R_{\rm maj} \lesssim 80''$ and is modeled with a Ferrer function.
+  A peak at $R_{\rm maj} \sim 25''$ in the ellipticity profile unravels an inner disky component embedded in the bulge, 
+  that we model with a low-$n$ S\'ersic profile.
+  }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M96.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + F-bar + S-id  & $7.5$  &  $1.5$ \\
+  T.W. 1D eq.  & S-bul + e-d + F-bar + S-id  & $5.3$  &  $1.3$ \\
+  T.W. 2D      & S-bul + e-d + G-bar + G-id  & $8.3$  &  $2.0$ \\
+  \hline
+  S+11         & S-bul + e-d + G-bar  & $45.6$  &  $1.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m96}
+  \tablecomments{
   The bulge effective radius obtained by S+11 largely exceeds our estimates 
-  because their model does not account for the disk or bar embedded in the bulge ($R_{\rm maj} \lesssim 25''$). 
-  \cite{nowak2010n3368n3489} came to their conclusion by modeling only the innermost $8''.5$ of the 
-  light profile of M96 with a S\'ersic-classical-bulge and an exponential-pseudo-bulge, 
-  but without subtracting the contribution of the large-scale disk and the large-scale bar.
-  In addition, they acknowledged the presence of a secondary inner bar, but did not include it in their fit.\\
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m96_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M96.}
-  \end{center}
-  \end{figure}
-
-  \begin{table}[h]
-  \small
-  \caption{Best-fit parameters for the spheroidal component of M96.}
-  \begin{center}
-  \begin{tabular}{llcc}
-  \hline
-  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
-    &  &  $[\rm arcsec]$ & \\
-  \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + S-bar  & $7.5$  &  $1.5$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + S-bar  & $5.3$  &  $1.3$ \\
-  T.W. 2D      & S-bul + e-d + 2 G-bars       & $8.3$  &  $2.0$ \\
-  \hline
-  S+11         & S-bul + e-d + G-bar  & $45.6$  &  $1.0$ \\
-  \hline
-  \end{tabular}
-  \end{center}
-  \label{tab:m96}
+  because their model does not account for the inner component embedded in the bulge ($R_{\rm maj} \lesssim 25''$). 
+  }
   \end{table}
@@
 
-  M105 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.1$, \citealt{rusli2013}).
-
-  \emph{1D fit -- }
-  M105 exhibits a mild isophotal twist and an abrupt change of ellipticity at $R \sim 30''$.
-  The velocity map shows rotation at least within $R \lesssim 30''$, 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m105_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M105.
+  M105 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 1''.1$, \citealt{rusli2013}).
+  M105 exhibits a mild isophotal twist and an abrupt change of ellipticity at $R_{\rm maj} \sim 30''$.
+  The velocity map shows rotation at least within $R_{\rm maj} \lesssim 30''$, 
   but no embedded disk can be recognized in the unsharp mask 
   and the ellipticity profile is quite unusual for a spheroidal system with an inner disk.
-  After masking the innermost $6''.1$, we noticed that a single S\'ersic model 
-  does not provide a good description of the galaxy light profile.
-  However, the addition of a second function (of any analytical form) to the model did not improve the fit.
-  We thus employed a single S\'ersic profile for M105.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m105_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M105.}
+  The data within the innermost $6''.1$ are excluded from the fit.
+  A single S\'ersic model does not provide a good description of the galaxy light profile.
+  However, the addition of a second function (of any analytic form) to the model does not improve the fit.
+  We conclude that the galaxy is not fully relaxed yet, and we fit it with a single S\'ersic profile. 
+  }
   \end{center}
@@
   \label{tab:m105}
+  \tablecomments{
+  L+14 obtained the largest values of $R_{\rm e,sph}$ and $n_{\rm sph}$, 
+  possibly due to incorrect sky subtraction (see the ``upturn'' of the three outermost data points in their Figure 21).
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/m106_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for M106.
   M106 is a barred spiral galaxy, harbouring a Seyfert AGN \citep{veroncettyveron2006} 
-  with %a radio jet \citep{liuzhang2002} and 
-  circumnuclear dust \citep{martini2003}.
-
-  %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 14''.9$, $n = 2.0$). 
-  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model 
-  %($R_{\rm e} = 111''.7$, $n = 2.0$). 
-  %\cite{vika2012} proposed two different fits: the first with a S\'ersic-bulge + exponential-disk + PSF-nucleus
-  %($R_{\rm e} = 17''.0$, $n = 3.5$), 
-  %and the second with a S\'ersic-bulge + exponential-disk + PSF-nucleus + S\'ersic-bar
-  %($R_{\rm e} = 6''.3$, $n = 2.2$).
-
-  \emph{1D fit -- }
-  We excluded from the fit the innermost $6''.1$ because affected by the AGN emission.
-  The boxy bar, responsible for the minimum in the B4 profile at $R \sim 65''$, 
-  is faint compared to the large-scale disk and in the light profile is only detectable as a slight swelling
-  within $65'' \lesssim R \lesssim 110''$.
-  This region has been excluded from the fit.
-  A peak in the ellipticity profile at $R \sim 10''$ suggests that a disk-like component might be 
-  embedded in the bulge.
-  Since the galaxy is barred, this component could be identified with a peanut bulge. 
-  However, we found that adding an extra component to the model introduces degeneracies, 
-  thus we preferred not to do so.
-  While the fit along the major-axis is satisfactory, 
-  the equivalent-axis residuals present a sneaky structure within $R \lesssim 20''$,
-  due to the unsubtracted embedded component.
-  %Our final model consists of a S\'ersic-bulge + exponential-disk.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m106_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M106.}
+  with circumnuclear dust \citep{martini2003}. 
+  We exclude from the fit the innermost $6''.1$ because affected by the AGN emission.
+  The boxy bar, responsible for the minimum in the B4 profile at $R_{\rm maj} \sim 65''$, 
+  is fainter than the large-scale disk and in the light profile is only detectable as a slight swelling
+  within $65'' \lesssim R_{\rm maj} \lesssim 110''$.
+  This region is excluded from the fit.
+  A peak in the ellipticity profile at $R_{\rm maj} \sim 10''$ suggests the presence of disky component embedded in the bulge, 
+  but a model that accounts for this component is degenerate.
+  }
   \end{center}
@@
   \label{tab:m106}
+  \tablecomments{
+  The bulge effective radius obtained by S+11 largely exceedes all the other estimates.
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n0524_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 0524.
   NGC 0524 is an unbarred face-on lenticular galaxy. 
-
-  %\cite{laurikainen2010} modeled this galaxy with a S\'ersic-bulge + exponential-disk + 2 Ferrer-lenses 
-  %($R_{\rm e} = 8''.9$, $n = 2.7$).
-  %\cite{sani2011} opted for a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 26''.8$, $n = 3.0$).
-  \emph{1D fit -- }
   The unsharp mask of NGC 0524 unravels a faint multi-ring structure in the galaxy disk,
-  with a major ring peaking at $R \sim 20''$.
-  We accounted only for this brightest ring using a Gaussian ring profile.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n0524_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 0524.}
+  with a major ring peaking at $R_{\rm maj} \sim 20''$.
+  We account only for this brightest ring using a Gaussian ring profile.
+  }
   \end{center}
@@
   \label{tab:n0524}
+  \tablecomments{
+  S+11 obtained the largest value of the effective radius because their two-component model does not account for the ring.
+  Both L+10 and S+11 estimated a S\'ersic index of $\sim$3, 
+  a three times larger value than that obtained by us.
+  }
   \end{table}
@@
 
-  NGC 1023 is a barred lenticular galaxy. % with no partially depleted core \cite{faber1997}. \\
-
-  %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 17''.7$, $n = 2.0$). 
-  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-bar model 
-  %($R_{\rm e} = 24''.0$, $n = 3.0$).
-  %\cite{lasker2014data} employed a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
-  %($R_{\rm e} = 9''.6$, $n = 3.1$).
-  \emph{1D fit -- }
-  The bar extends out to $R \lesssim 40''$.
-  %The light profile of NGC 1023 is well described by a S\'ersic-bulge + exponential-disk + Ferrer-bar model.
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n1023_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 1023.
+  NGC 1023 is a barred lenticular galaxy. 
+  The bar extends out to $R_{\rm maj} \lesssim 40''$.
   Small deviations of the disk from a perfect exponential profile, 
-  within the region $60'' \lesssim R \lesssim 125''$ (that has been excluded from the fit), 
+  within $60'' \lesssim R_{\rm maj} \lesssim 125''$ (the data in this range are excluded from the fit), 
   can be ascribed to some faint residual spiral arms, also noticeable in the 2D residual image. 
-  The peak at $R \sim 10''$ in the B4 profile signals the presence of an embedded (and faint) disk.
-  The 1D residuals show a structure within $R \lesssim 10''$ caused by this unsubtracted 
-  component, also noted by \cite{lasker2014data}.
-  Attempts to account for the inner disk by adding a fourth function to the model 
-  did not significantly modify the best-fit bulge parameters,
-  thus we elected not to model the embedded disk.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n1023_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1023.}
+  The peak at $R_{\rm maj} \sim 10''$ in the B4 profile signals the presence of an embedded (and faint) disk.
+  The 1D residuals show a structure within $R_{\rm maj} \lesssim 10''$ caused by this unsubtracted 
+  component, as also noted by \cite{lasker2014data}.
+  Our attempts to account for the inner disk by adding a fourth function to the model 
+  did not significantly change the bulge best-fit parameters,
+  thus we elect not to model this embedded disk. 
+  }
   \end{center}
@@
   \label{tab:n1023}
+  \tablecomments{
+  S+11 obtained the largest value of the bulge effective radius, although they accounted for the bar in their model.
+  }
   \end{table}
@@
 
-  NGC 1300 is a face-on, barred spiral galaxy. % with no partially depleted core \citep{graham2012MNRAS}.
-
-  %\cite{sani2011} fit NGC 1300 with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 85''.4$, $n = 3.0$).
-  %\cite{lasker2014data} built their model with a S\'ersic-bulge + exponential-disk + PSF-nucleus + exponential-inner-disk + 
-  %S\'ersic-bar + spiral arms
-  %($R_{\rm e} = 10''.4$, $n = 4.3$).
-
-  \emph{1D fit -- }
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n1300_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 1300.
+  NGC 1300 is a face-on, barred spiral galaxy. 
   The morphology of NGC 1300 is quite complex. 
   In addition to a large scale disk and a bulge, the galaxy is composed of 
-  a large scale bar that extends up to $R \lesssim 90''$, two prominent spiral arms 
-  and an inner disk-like component ($R \lesssim 5''$), disclosed by the peaks in the ellipticity and PA profiles.
-  We truncate the light profile at $R \sim 50''$ and we fit the inwards combination of the large-scale bar and the disk 
+  a large scale bar that extends up to $R_{\rm maj} \lesssim 90''$, two prominent spiral arms 
+  and an inner disk-like component ($R_{\rm maj} \lesssim 5''$), disclosed by the peaks in the ellipticity and PA profiles.
+  We truncate the light profile at $R_{\rm maj} \sim 50''$ and we fit the inwards combination of the large-scale bar and the disk 
   as a single component, using an exponential function.
   The embedded component is described with a low-$n$ S\'ersic profile. 
-  %Our final model consists of a S\'ersic-bulge + exponential-(disk+bar) + S\'ersic-inner disk.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n1300_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1300.}
+  }
   \end{center}
@@
   \label{tab:n1300}
+  \tablecomments{
+  S+11 overestimated the bulge effective radius mainly because their model does not account for the large-scale bar.
+  }
   \end{table}
@@
 
-  NGC 1399, the central galaxy of the Fornax cluster, is an elliptical galaxy with a partially depleted core 
-  ($R_{\rm break} \sim 2''.4$, \citealt{rusli2013,dullograham2014cores}).
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n1399_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 1399.
+  NGC 1399, the central galaxy of the Fornax cluster, is an elliptical galaxy with a slightly resolved partially depleted core \citep{rusli2013,dullograham2014cores}. 
+  %($R_{\rm break} \sim 2''.4$, \citealt{rusli2013,dullograham2014cores}).
   The nuclear activity of NGC 1399 is classified as Seyfert \citep{veroncettyveron2006},
   but the galaxy lacks of dust \citep{tran2001}.
-
-  %\cite{grahamdriver2007} fit the galaxy light profile with a single S\'ersic-bulge profile 
-  %($n = 16.8$).  
-  %\cite{rusli2013} modeled NGC 1399 with a core-S\'ersic profile and the sum of a S\'ersic and an exponential
-  %function accounting for the galaxy halo 
-  %($R_{\rm e} = 36''.2$, $n = 7.38$). 
-  %\cite{lasker2014data} used a S\'ersic-bulge + mask-core model 
-  %($R_{\rm e} = 154''.0$, $n = 11.1$).
-
-  \emph{1D fit -- }
-  The ellipticity and PA profiles display a steep decline within $R \lesssim 60''$,
+  The ellipticity and PA profiles display a steep decline within $R_{\rm maj} \lesssim 60''$,
   suggesting the presence of an embedded disk.
   This inner component is also visible, although very faint, in the unsharp mask.
-  TBD!! velocity map, the disk is face on
-  We note that, after excluding the innermost $6''.1$ affected by the partially depleted core,
+  We note that, after excluding the innermost $6''.1$,
   a single S\'ersic profile is not sufficient to describe the whole galaxy light profile.
-  The addition of an inner exponential function to the model 
-  notably improves the fit.
-  %We build our final model with a S\'ersic-bulge + mask-core + exponential-inner disk.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n1399_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1399.}
+  The addition of an inner exponential function to the model notably improves the fit.
+  }
   \end{center}
@@
   \label{tab:n1399}
+  \tablecomments{
+  R+13 used a combination of a S\'ersic + exponential profile to model the halo of this galaxy, 
+  and obtained the smallest estimate of the effective radius, 
+  which is at odds with the fact that central cluster galaxies typically have the largest sizes. 
+  L+14 finds an effective radius which is a factor of two smaller than that obtained by us 
+  because their data have a smaller radial extent ($R_{\rm maj} \lesssim 130'$). 
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n2273_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 2273.
   NGC 2273 is a barred spiral galaxy with a Seyfert AGN \citep{contini1998} 
   and circumnuclear dust \citep{simoeslopes2007}. 
-  Its bar is surrounded by two tightly wound star-forming spiral arms that resemble a ring
-  \citep{comeron2010}.
-
-  \cite{laurikainen2005} pointed out the presence of an inner disk embedded in the bulge of NGC 2273,
-  but they deliberately chose not to model it due to the degeneracy between the functions describing the bulge
-  and the inner disk. 
-  %Their final model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar 
-  %($R_{\rm e} = 2''.6$, $n = 1.8$).
-
-  \emph{1D fit -- }
-  The bar of NGC 2273 extends out to $R \lesssim 25''$. 
+  Its bar is surrounded by two tightly wound star-forming spiral arms that resemble a ring \citep{comeron2010}. 
+  The bar of NGC 2273 extends out to $R_{\rm maj} \lesssim 25''$. 
   The pseudo-ring does not produce any evident swelling in the light profile, 
   therefore we do not account for it in the galaxy model.
-  The isophotal parameters confirm the presence of a nuclear disk-like component within $R \lesssim 5''$.
-  However, as noted by \cite{laurikainen2005}, any attempt to account for the embedded disk resulted in a 
-  degenerate model. 
+  The isophotal parameters confirm the presence of a nuclear disky component within $R_{\rm maj} \lesssim 5''$.
+  However, as noted by \cite{laurikainen2005}, any attempt to account for the embedded disk resulted in a degenerate model. 
   This is not surprising if one considers the poor spatial resolution of the galaxy image, 
-  the effective radius of the bulge being comparable to the FWHM of the PSF.
+  with the effective radius of the bulge comparable to the FWHM of the instrumental PSF.
   Although NGC 2273 hosts an optical AGN and nuclear dust, no central excess of light is observed in the 1D residuals.
-  The addition of a nuclear component to the model does not improve the fit and does not significantly affect
-  the bulge parameters.
-  %Our final model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n2273_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 2273.}
+  The addition of a nuclear component to the model does not significantly improve the fit or change the bulge parameters. 
+  }
   \end{center}
@@
   \hline
-  L+05         & S-bul + e-d + F-bar & $2.6$  &  $1.8$ \\
+  L+10         & S-bul + e-d + F-bar & $2.6$  &  $1.8$ \\
   \hline
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n2549_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 2549.
   NGC 2549 is an edge-on barred lenticular galaxy. 
-
-  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 11''.6$, $n = 7.0$).
-
-  \emph{1D fit -- }
   Although the edge-on inclination of NGC 2549 complicates the identification of embedded components, 
-  a large scale bar ($R \lesssim 45''$) can be recognized in the galaxy image itself and -- more easily -- in the light profile.
+  a large-scale bar ($R_{\rm maj} \lesssim 45''$) can be recognized in the galaxy image and -- more easily -- in the light profile.
   We describe the large scale bar with a Ferrer profile.
   A peak in the ellipticity profile discloses the presence of a disky component
-  embedded in the bulge ($R \lesssim 10''$).
+  embedded in the bulge ($R_{\rm maj} \lesssim 10''$).
   This inner component can be spotted also by looking at the velocity map.
   We fit it with a Ferrer profile.
-  %We build our final model with a S\'ersic-bulge + exponential-disk + 2 Ferrer-bars.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n2549_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 2549.}
+  }
   \end{center}
@@
   \label{tab:n2549}
+  \tablecomments{
+  The model of S+11 does not account for the large-scale bar and largely overestimates the bulge S\'ersic index.
+  }
   \end{table}
@@
 
-  NGC 2778 is an almost face-on lenticular galaxy.
-
-  %\cite{grahamdriver2007} modeled NGC 2778 with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 2''.3$, $n = 1.6$). 
-  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk model
-  %($R_{\rm e} = 2''.5$, $n = 2.5$). 
-  %\cite{vika2012} employed a S\'ersic-bulge + exponential-disk model 
-  %($R_{\rm e} = 1''.5$, $n = 2.7$). 
-  %\cite{lasker2014data} fit the galaxy with a S\'ersic-bulge + exponential-disk + S\'ersic-bar
-  %($R_{\rm e} = 2''.8$, $n = 4.0$).
-
-  \emph{1D fit -- }
-  The peak in the ellipticity profile at $R \sim 5''$ unravels the existence of a nuclear component 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n2778_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 2778.
+  NGC 2778 is a face-on lenticular galaxy. 
+  The peak in the ellipticity profile at $R_{\rm maj} \sim 5''$ unravels the existence of a nuclear component 
   embedded in the galaxy bulge.
   After an inspection of the unsharp mask, we identified this component with a small bar,
-  that we modeled with a Ferrer function.
-  We also accounted for some nuclear light excess by adding a PSF component to the model.
-  %We then fit NGC 2778 with a S\'ersic-bulge + exponential-disk + Ferrer-bar + PSF-nucleus.
-  We note that excluding the PSF component from our galaxy model does not significantly affect the 
-  bulge effective radius, but it increases the S\'ersic index to $n \sim 2$.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n2778_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 2778.}
+  that we model with a Ferrer function.
+  We also account for some nuclear light excess by adding a PSF component to the model.
+  We note that excluding the PSF component from our model does not significantly chiange the 
+  bulge effective radius, but it does increase the bulge S\'ersic index to $n_{\rm sph} \sim 2$.
+  }
   \end{center}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n2787_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 2787.
   NGC 2787 is a barred lenticular galaxy with LINER nuclear activity \citep{veroncettyveron2006}.
@@
   NGC 2787 features a spectacular structure of dust rings at its center \citep{erwinsparke2003}
-  and a nuclear stellar disk ($R \lesssim 1''.8$, \citealt{ledo2010}).
-
-  %\cite{grahamdriver2007} modeled the galaxy light profile with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 4''.6$, $n = 2.0$). 
-  %\cite{fisherdrory2008} decomposed NGC 2787 in a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 9''.1$, $n = 1.2$).
-  %\cite{laurikainen2010} employed a S\'ersic-bulge + exponential-disk + Ferrer-bar + Ferrer-lens model
-  %($R_{\rm e} \sim 4''$, $n = 1.3$).
-  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN 
-  %($R_{\rm e} = 15''.7$, $n = 3.0$). 
-  %\cite{lasker2014data} described NGC 2787 with a S\'ersic-bulge + truncated exponential-disk + 
-  %truncated S\'ersic-bar + S\'ersic-inner disk + PSF-nucleus
-  %($R_{\rm e} = 14''.3$, $n = 2.8$).
-
-  \emph{1D fit -- }
+  and a nuclear stellar disk (with size $\lesssim 1''.8$, \citealt{ledo2010}).
   NGC 2787 has an undoubtedly complex morphology. 
-  This galaxy is made of a bulge, a large scale disk, a bar (see the peaks in the ellipticity, PA and B4 profiles
-  at $R \sim 30''$) with two ansae, an inner disk (or bar?) embedded in the bulge (see the peak in the ellipticity profile
-  at $R \sim 17''$), and a bright nucleus.
-
-  Beyond $R \gtrsim 50''$, where the galaxy large scale disk extends without being affected by the bar ansae,
-  the surface brightness profile is not a perfect exponential, being better described by a S\'ersic function
-  with $n < 1$.
-  Curiously, at optical wavelengths the disk has an exponential decline with no truncation or anti-truncation 
-  (see \citealt{erwin2003n2787} their Figure 14, and \citealt{erwin2008}).
-  Here we propose two different models for NGC 2787.
-  In both cases we used a S\'ersic profile for the bulge, a Ferrer function for the bar, a second Ferrer function for the inner disk (or bar) 
-  and a PSF for the nucleus. 
-  We then described the large scale disk using a S\'ersic function with $n < 1$ 
-  or an exponential function. 
-  In the last case we needed to exclude the data within $R \sim 30'' - 50''$ where the ansae produce a hollow.
-  The two different decompositions result in the same bulge best-fit parameters ($R_{\rm e} \sim 5''$, $n \sim 1$)
-  along the major-axis, whereas the outcome is significantly different along the equivalent-axis 
-  ($n = 1.3$ when using the exponential-disk and $n = 2.2$ when using the S\'ersic-disk).
-
-  might just pick one TBD!!
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n2787_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 2787.}
+  This galaxy is composed of a bulge, a large scale disk, a bar (see the peaks in the ellipticity, PA and B4 profiles
+  at $R_{\rm maj} \sim 30''$) with two ansae, an inner disk (or bar?) embedded in the bulge (see the peak in the ellipticity profile
+  at $R_{\rm maj} \sim 17''$), and a bright nucleus.
+  After masking the data affected by the ansae within $30'' \lesssim R_{\rm maj} \lesssim 50''$,
+  we use a Ferrer function for the bar, a second Ferrer function for the inner disk (or bar) 
+  and a PSF component for the nucleus. 
+  %Beyond $R_{\rm maj} \gtrsim 50''$, where the galaxy large scale disk extends without being affected by the bar ansae,
+  %the surface brightness profile is not a perfect exponential, being better described by a S\'ersic function
+  %with $n < 1$.
+  %Curiously, at optical wavelengths the disk has an exponential decline with no truncation or anti-truncation 
+  %(see \citealt{erwin2003n2787} their Figure 14, and \citealt{erwin2008}).
+  %Here we propose two different models for NGC 2787.
+  %In both cases we used a S\'ersic profile for the bulge, a Ferrer function for the bar, a second Ferrer function for the inner disk (or bar) 
+  %and a PSF for the nucleus. 
+  %We then described the large scale disk using a S\'ersic function with $n < 1$ 
+  %or an exponential function. 
+  %In the last case we needed to exclude the data within $R_{\rm maj} \sim 30'' - 50''$ where the ansae produce a hollow.
+  %The two different decompositions result in the same bulge best-fit parameters ($R_{\rm e} \sim 5''$, $n \sim 1$)
+  %along the major-axis, whereas the outcome is significantly different along the equivalent-axis 
+  %($n = 1.3$ when using the exponential-disk and $n = 2.2$ when using the S\'ersic-disk).
+  }
   \end{center}
@@
   \hline
-  \multicolumn{4}{c}{\emph{exponential-disk}} \\
+  %\multicolumn{4}{c}{\emph{exponential-disk}} \\
   %\hline
@@
   \hline
-  \multicolumn{4}{c}{\emph{S\'ersic-disk}}\\
+  %\multicolumn{4}{c}{\emph{S\'ersic-disk}}\\
+  %%\hline
+  %T.W. 1D maj. & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.6$  &  $1.1$ \\
+  %T.W. 1D eq.  & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.4$  &  $2.2$ \\
+  %%T.W. 2D	&  & $$  & $$  &  $$ \\
   %\hline
-  T.W. 1D maj. & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.6$  &  $1.1$ \\
-  T.W. 1D eq.  & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.4$  &  $2.2$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
   GD07         & S-bul + e-d					  & $4.6$   &  $2.0$ \\
@@
   \label{tab:n2787}
+  \tablecomments{
+  S+11 found larger estimates of the effective radius and S\'ersic index because they did not account for the inner disk. 
+  L+14 also reported a larger effective radius and S\'ersic index because they employed an unusual truncated exponential disk and 
+  truncated S\'ersic bar in their galaxy model. 
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 2974.
   NGC 2974 is a spiral galaxy which has been misclassified as an elliptical galaxy in the RC3 catalog.
   The galaxy hosts a Seyfert AGN \citep{veroncettyveron2006} and filamentary dust in its center \citep{tran2001}.
-
-  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + Gaussian-AGN 
-  %($R_{\rm e} = 27''.2$, $n = 3.0$).
-
-  \emph{1D fit -- }
-  From an inspection of the unsharp mask, we identified a ring structure at $R \sim 50''$, 
+  From an inspection of the unsharp mask, we identified a ring structure at $R_{\rm maj} \sim 50''$, 
   probably a residual of two tightly wound spiral arms,
-  and an elongated bar-like component within $R \lesssim 30''$, that we fit with a Ferrer function.
-  The last one produces a peak in the ellipticity profile at $R \sim 20''$.
+  and an elongated bar-like component within $R_{\rm maj} \lesssim 30''$, that we fit with a Ferrer function.
+  The bar produces a peak in the ellipticity profile at $R_{\rm maj} \sim 20''$.
   Although the ring is extremely faint, it is important to account for it in the galaxy decomposition. 
   A model without the ring component results in a ``steeper'' exponential-disk (the disk has a smaller scale length 
-  and a lower central surface brightness) and produces bad residuals within $R \lesssim 40''$.
+  and a brighter central surface brightness) and produces bad residuals within $R_{\rm maj} \lesssim 40''$.
   The nuclear component is fit with a Gaussian profile.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 2974.}
+  }
   \end{center}
@@
   \label{tab:n2974}
+  \tablecomments{
+  The model of S+11 does not account for the large-scale disk and thus overestimates the bulge effective radius and S\'ersic index.
+  }
   \end{table}
@@
 
-  NGC 3091 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.62$, \citealt{rusli2013}).
-
-  %\cite{rusli2013} modeled NGC 3091 with a single core-S\'ersic profile 
-  %($R_{\rm e} = 91''.0$, $n = 9.3$).
-
-  \emph{1D fit -- }
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3091_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3091.
+  NGC 3091 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 0''.62$, \citealt{rusli2013}).
   The data within the innermost $6''.1$ are excluded from the fit.
-  A faint embedded component ($R \lesssim 10''$) can be recognized in the unsharp mask and has a corresponding peak in the
+  A faint embedded component ($R_{\rm maj} \lesssim 10''$) can be recognized in the unsharp mask and has a corresponding peak in the
   ellipticity profile.
@@
   However, any attempt to account for the embedded component resulted in an unsatisfactory fit and did not 
-  significantly affect the bulge parameters.
-  We thus elected not to model the inner component.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3091_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3091.}
+  significantly change the bulge parameters.
+  We thus elect not to model the inner component. 
+  }
   \end{center}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3115_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3115.
   NGC 3115 is an edge-on elliptical/lenticular galaxy. 
-  Its nuclear activity is classified as passive in the optical wavelengths \citep{gavazzi2013nuclspec}.
-  This galaxy features a nuclear stellar disk ($R \sim 1''$, \citealt{scorzabender1995,ledo2010}).
-
-  \cite{grahamdriver2007} TBD!!! ask Alister what did they do, not clear from appendix
-  ($n = 13.0$). 
-  \cite{fisherdrory2008} decomposed the galaxy in a S\'ersic-bulge + exponential disk 
-  ($R_{\rm e} = 31''.0$, $n = 3.9$). 
-  %\cite{sani2011} modeled NGC 3115 with a S\'ersic-bulge + exponential disk 
-  %($R_{\rm e} = 27''.3$, $n = 3.0$). 
-  %\cite{lasker2014data} used a S\'ersic-bulge + exponential disk + S\'ersic-envelope 
-  %($R_{\rm e} = 3''.9$, $n = 3.0$).
-
-  \emph{1D fit -- }
-  NGC 3115 is an example of a galaxy with an intermediate scale disk.
-  The surface brightness profile of NGC 3115 does not have an exponential decline at large radii 
-  because the disk component does not dominate the outer regions of the galaxy.
+  This galaxy features a nuclear stellar disk (with size $\sim 1''$, \citealt{scorzabender1995,ledo2010}).
+  NGC 3115 has an intermediate scale disk.
   This is immediately evident by looking at the ellipticity and B4 profiles.
-  Going from the galaxy center to the outskirts, the ellipticity increases until it reaches its maximum 
-  ($\epsilon \sim 0.65$) at $R \sim 90''$. 
-  After this point, it starts declining, being as low as $\epsilon \sim 0.55$ at $R \sim 240''$. 
-  The galaxy isophotes display a positive diskyness within $R \sim 90''$, but become perfect ellipses 
+  Going from the galaxy center to the outskirts, the ellipticity increases until it reaches a maximum 
+  ($\epsilon \sim 0.65$) at $R_{\rm maj} \sim 90''$. 
+  After this point, it starts declining, being as low as $\epsilon \sim 0.55$ at $R_{\rm maj} \sim 240''$. 
+  The galaxy isophotes display a positive diskyness within $R_{\rm maj} \sim 90''$, but become perfect ellipses 
   ($B4 \sim 0$) beyond that point.
-  Now, because galaxy disks typically have fixed ellipticity, reflecting their inclination to our line of sight,
+  Because galaxy disks typically have fixed ellipticity, reflecting their inclination to our line of sight,
   the previous observations tell us that, going from the galaxy center to the outer regions,
   the disk of NGC 3115 becomes increasingly important relative to the spheroid light, reaching its maximum at $R \sim 90''$.
-  Beyond $R \gtrsim 90''$, the contribution from the disk light starts declining more rapidly than the spheroid light.
+  Beyond $R_{\rm maj} \gtrsim 90''$, the contribution from the disk light starts declining more rapidly than the spheroid light.
   This interpretation is supported by the results of \cite{arnold2011n3115},
-  who found that within $R \sim 110''$ the bulge of NGC 3115 is flattened and rotates rapidly ($v/\sigma \gtrsim 1.5$),
+  who found that, within $R_{\rm maj} \sim 110''$, the bulge of NGC 3115 is flattened and rotates rapidly ($v/\sigma \gtrsim 1.5$),
   whereas at larger radii the rotation declines dramatically (to $v/\sigma \sim 0.7$), 
-  but remains well aligned with the inner regions. \\
-  From an inspection of the unsharp mask, we identify a faint nuclear edge-on ring ($R \sim 15''$), 
-  which produces a corresponding peak in the ellipticity profile. \\
-  %We build our model with a S\'ersic-bulge + exponential disk + Gaussian-ring. \\
-  We do not observe any nuclear excess of light in the 1D residuals, 
-  contrary to what we expected given the presence of a nuclear stellar disk. 
+  but remains well aligned with the inner regions. 
+  From an inspection of the unsharp mask, we identify a faint nuclear edge-on ring ($R_{\rm maj} \sim 15''$), 
+  which produces a corresponding peak in the ellipticity profile. 
+  %We build our model with a S\'ersic-bulge + exponential disk + Gaussian-ring. 
+  We do not observe any nuclear excess of light in the 1D residuals. 
   The addition of a PSF component to the final model does not significantly change the outcome of the fit. 
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3115_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3115.}
+  }
   \end{center}
@@
   \hline
-  GD07         & ??? TBD	       & $-$	&  $13.0$ \\
+  %GD07         & ??? TBD	       & $-$	&  $13.0$ \\
   S+11         & S-bul + e-d	       & $27.1$ &  $3.0$ \\
@@
   \label{tab:n3115}
+  \tablecomments{
+  S+11 found a smaller effective radius and S\'ersic index for the spheroidal component of this galaxy, 
+  possibly because they modelled the intermediate scale disk as a large-scale disk.
+  L+14 also used a model with a bulge encased in a larger disk, and attributed the excess of light at large radii to a halo. 
+  In doing so, they obviously obtained an even smaller bulge effective radius.
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3227_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3227.
   NGC 3227 is a spiral galaxy with a large-scale bar. 
   This galaxy hosts a Seyfert AGN \citep{khachikian1974} and circumnuclear dust \citep{martini2003}. 
-
-  %\cite{laurikainen2004} decomposed NGC 3227 into a S\'ersic-bulge + exponential-disk + Ferrer-bar 
-  %($R_{\rm e} = 1''.8$, $n = 2.2$). 
-  %\cite{sani2011} described this galaxy with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 82''.9$, $n = 4.0$). 
-  %\cite{lasker2014data} used a S\'ersic-bulge + exponential disk + S\'ersic-bar 
-  %($R_{\rm e} = 0''.7$, $n = 4.1$).
-
-  \emph{1D fit -- }
   The large-scale bar produces an evident bump in the major-axis surface brightness profile,
-  which is curiously absent in the equivalent-axis profile. \\
-  We modeled the bar with a Ferrer function and the nucleus with a Gaussian function. 
+  which is curiously absent in the equivalent-axis profile. 
+  We model the bar with a Ferrer function and the nucleus with a Gaussian function. 
   As expected, the Ferrer component is rejected by the equivalent-axis fit. 
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3227_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3227.}
+  }
   \end{center}
@@
   \label{tab:n3227}
+  \tablecomments{
+  The models of L+10 and L+14 do not account for the bright nulcear component, 
+  and thus underestimate the bulge effective radius and overestimate the bulge S\'ersic index.
+  The bulge effective radius obtained by S+11 is even larger because they did not model the bar. 
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3245_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3245.
   NGC 3245 is a lenticular galaxy.
-
-  %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 11''.3$, $n = 4.3$). 
-  %\cite{laurikainen2010} described the galaxy with a S\'ersic-bulge + exponential-(disk+lens) + Ferrer-inner disk 
-  %($R_{\rm e} \sim 4''$, $n = 2.4$).  
-  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 4''.6$, $n = 2.5$). 
-  %\cite{vika2012} employed a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 3''.5$, $n = 2.6$). 
-  %\cite{beifiori2012} decomposed the galaxy into a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 4''.00$, $n = 1.6$). 
-  %\cite{lasker2014data} built their model with a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
-  %($R_{\rm e} = 1''.95$, $n = 1.6$).
-
-  \emph{1D fit -- }
-  The unsharp mask reveals the presence of an embedded disk ($R \lesssim 15''$), 
+  The unsharp mask reveals the presence of an embedded disk ($R_{\rm maj} \lesssim 15''$), 
   confirmed by the corresponding peaks in the ellipticity and B4 profiles.
   We model this inner component with a Ferrer function. 
-  %We model the galaxy with a S\'ersic-bulge + exponential-disk + Ferrer-inner disk.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3245_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3245.}
+  }
   \end{center}
@@
   \label{tab:n3245}
+  \tablecomments{
+  GD07 found the largest estimates of the bulge effective radius and S\'ersic index.
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3384_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3384.
   NGC 3384 is a barred lenticular galaxy that hosts 
-  an embedded disk ($R \lesssim 11''$, \citealt{erwin2004}) and 
-  a nuclear stellar disk ($R \lesssim 0''.8$, \citealt{ledo2010}).
-
-  %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 2''.5$, $n = 1.7$). 
-  %\cite{laurikainen2010} described the galaxy with a S\'ersic-bulge + exponential-disk + 2 Ferrer-bars
-  %($R_{\rm e} \sim 4''$, $n = 1.5$).  
-  %\cite{sani2011} employed a S\'ersic-bulge + exponential-disk + Gaussian-bar 
-  %($R_{\rm e} = 4''.4$, $n = 2.5$). 
-  %\cite{beifiori2012} modeled the galaxy with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 8''.3$, $n = 2.3$). 
-  %\cite{lasker2014data} decomposed the galaxy into a S\'ersic-bulge + exponential-disk + S\'ersic-inner disk + 
-  %S\'ersic-nuclear disk + S\'ersic-bar
-  %($R_{\rm e} = 5''.9$, $n = 2.5$).
-
-  \emph{1D fit -- }
-  The isophotal parameters clearly show the presence of a boxy bar that extends out to $R \lesssim 18''$.
+  an embedded disk (with size $\lesssim 11''$, \citealt{erwin2004}) and 
+  a nuclear stellar disk (with size $\lesssim 0''.8$, \citealt{ledo2010}).
+  The isophotal parameters clearly show the presence of a boxy bar that extends out to $R_{\rm maj} \lesssim 18''$.
   We model the bar with a Ferrer function.
-  An embedded disk can be seen in the unsharp mask and produces the peak in the ellipticity profile at $R \sim 4''$.
-  modeling the embedded disk turned out to be a complicated task, resulting in a degenerate model.
-  We elected not to fit the embedded disk (nor the nuclear disk) and we therefore excluded from the fit the innermost $3''.7$,
-  where there two components are expected to dominate.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3384_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3384.}
+  An embedded disk can be seen in the unsharp mask and produces the peak in the ellipticity profile at $R_{\rm maj} \sim 4''$.
+  However, any attempt to account for this component resulted in a degenerate model.
+  We elect not to fit neither the embedded disk nor the nuclear disk, by excluding from the fit the data within $R_{\rm maj} < 3''.7$. 
+  }
   \end{center}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3393_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3393.
   NGC 3393 is an edge-on spiral galaxy hosting a Seyfert AGN \citep{diaz1988n3393} and 
   circumnuclear dust \citep{martini2003}.
-  The galaxy has a large-scale bar and a nuclear bar ($R \lesssim 3''$, \citealt{erwin2004}).
-
-  \emph{1D fit -- }
-  The large-scale bar ($R \lesssim 20''$) is modeled with a Ferrer function.
-  The poor spatial resolution of the data does not allow to fit the nuclear bar and/or the AGN component 
-  without incurring degeneracies.
-  We thus elected not to fit the nuclear components.
-  We note that the addition to the model of a central component would lower the bulge S\'ersic index,
-  whereas the the addition of a nuclear bar component would increase the bulge S\'ersic index.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3393_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3393.}
+  The galaxy has a large-scale bar and a nuclear bar (with size $\lesssim 3''$, \citealt{erwin2004}).  
+  The large-scale bar ($R_{\rm maj} \lesssim 20''$) is modeled with a Ferrer function.
+  We do not model the nuclear bar and the AGN component because the poor spatial resolution of the data does not allow to fit them 
+  without incurring into degeneracies.
+  }
   \end{center}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3414_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3414.
   NGC 3414 is a peculiar lenticular/elliptical galaxy. 
   Different interpretations have been proposed about the morphology of this galaxy.
-  \cite{whitmore1990} suggested that NGC 3414 is an edge-on galaxy 
-  with a large scale polar ring, rather than a face-on barred lenticular.
+  \cite{whitmore1990} suggested that NGC 3414 is an spheroidal galaxy 
+  with a large-scale edge-on polar ring, rather than a face-on barred lenticular galaxy.
   \cite{laurikainen2010} decomposed NGC 3414 as a barred lenticular galaxy, but 
-  they cautioned against the uncertainty of their solution due to the possible misinterpretation of the 
-  galaxy morphology.
-
-  \emph{1D fit -- }
-  The unsharp mask clearly shows that the edge on component does not extend all the way through the 
-  center of the galaxy, but instead it is truncated at $R \sim 20''$.
-  However, an elongated structure in the galaxy center resembles a nuclear edge-on disk ($R \lesssim 5''$).
-  The velocity map shows rotation within $R \lesssim 5''$ and no rotation within $5'' \lesssim R \lesssim 15''$.
-  Beyond $R \gtrsim 15''$ one can recognize a sign of rotation in the opposite direction of the nuclear region.
-  The velocity pattern is consistent with the galaxy being a spheroidal system containing a polar ring and a nuclear disk
-  both seen edge-on.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3414_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3414.}
+  they cautioned against the uncertainty of their solution due to the possible misinterpretation of the galaxy morphology.
+  The unsharp mask clearly shows that an embedded component does not extend all the way through the 
+  center of the galaxy, but instead it is truncated at $R_{\rm maj} \sim 20''$.
+  However, an elongated structure in the galaxy center resembles a nuclear edge-on disk ($R_{\rm maj} \lesssim 5''$).
+  The velocity map shows rotation within $R_{\rm maj} \lesssim 5''$, no rotation within $5'' \lesssim R_{\rm maj} \lesssim 15''$,
+  and counterrotation beyond $R_{\rm maj} \gtrsim 15''$.
+  The velocity pattern is consistent with the galaxy being a spheroidal system containing an edge-on polar ring and an edge-on nuclear disk.
+  }
   \end{center}
@@
   \label{tab:n3414}
+  \tablecomments{
+  L+10 used a model with a large-scale exponential disk, thus they obtained a smaller bulge effective radius and S\'ersic index.
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3489_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3489.
   NGC 3489 is a barred lenticular galaxy. 
-  Its disk has a smooth antitruncation at $R \sim 85''$ \citep{erwin2008}.
-
-  \cite{nowak2010n3368n3489} argued for the presence of both a pseudo-bulge and a classical bulge. 
-  %\cite{laurikainen2010} fit this galaxy with a S\'ersic-bulge + exponential-disk + Ferrer-bar
-  %($R_{\rm e} \sim 2''$, $n = 2.1$). 
-  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 4''.6$, $n = 1.5$).
-
-  \emph{1D fit -- }
-  We excluded the data beyond $R \gtrsim 38''$ to avoid fitting the antitruncation region.
+  Its disk has a smooth antitruncation at $R_{\rm maj} \sim 85''$ \citep{erwin2008}.
+  %\cite{nowak2010n3368n3489} argued for the presence of both a pseudo-bulge and a classical bulge. 
   The bar is fit with a Ferrer function.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3489_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3489.}
+  }
   \end{center}
@@
   \label{tab:n3489}
+  \tablecomments{
+  S+11 did not fit the bar and thus obtained a larger estimate of the bulge effective radius.
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3842exp_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3842.
   NGC 3842 is the brightest member of the Leo Cluster (Abell 1367).
-  It is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.7$, 
-  \citealt{rusli2013,dullograham2014cores}).
-
-  %\cite{rusli2013} modeled this galaxy with a core-S\'ersic model 
-  %($R_{\rm e} = 58''.8$, $n = 6.3$).
-
-  \emph{1D fit -- }
-  The light profile presents a swelling at $R \sim 20''$ and the ellipticity profile has a peak in the same position.
+  It is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013,dullograham2014cores}. %($R_{\rm break} = 0''.7$,   \citealt{rusli2013,dullograham2014cores}).
+  The light profile presents a swelling at $R_{\rm maj} \sim 20''$ and the ellipticity profile has a peak in the same position.
   One can also glimpse a faint elongated oval in the unsharp mask.
-  The innermost $6''.1$ are excluded from the fit due to the presence of a partially depleted core.
-  As expected, a single S\'ersic model is not sufficient to provide a good description of the galaxy light profile 
-  and we need to add a second component (Ferrer function) to account for the embedded lens.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3842exp_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3842.}
+  The innermost $6''.1$ are excluded from the fit.
+  A single S\'ersic model is not sufficient to provide a good description of the galaxy light profile, 
+  therefore we add a second component (Ferrer function) to account for the embedded lens.
+  }
   \end{center}
@@
 
-  NGC 3998 is a barred lenticular galaxy with a Seyfert AGN and dust in its nucleus \citep{knapp1996n3998}.
-  Despite its large stellar velocity dispersion, this galaxy does not have a partially depleted core TBD!! ref??. 
-  \cite{gutierrez2011} identified a bar at $R \lesssim 8''$, a ring between $30'' \lesssim R \lesssim 50''$, and  
-  an antitruncation in the light profile of the disk at $R \sim 122''$.
-  \cite{laurikainen2010} found that NGC 3998 features a weak bar at $R < 8''$,
-  a bright lens at $R < 15''$ and a weak bump in the surface brightness profile at $R \sim 40''$ 
-  %($R_{\rm e} \sim 5''$, $n = 2.0$).
-  %\cite{sani2011} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN 
-  %($R_{\rm e} = 4''.7$, $n = 1.5$).
-  %\cite{beifiori2012} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 5''.7$, $n = 2.3$).
-  %\cite{lasker2014data} used a S\'ersic-bulge + exponential-disk (with inner truncation) + PSF-nucleus + 
-  %S\'ersic-inner disk + S\'ersic-bar 
-  %($R_{\rm e} = 2''.0$, $n = 1.1$).
-
-  \emph{1D fit -- }
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n3998_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 3998.
+  NGC 3998 is a barred lenticular galaxy with a Seyfert AGN and nuclear dust \citep{knapp1996n3998}.
+  Despite its large stellar velocity dispersion, this galaxy does not have a partially depleted core. 
+  \cite{gutierrez2011} identified a bar at $R_{\rm maj} \lesssim 8''$, a ring between $30'' \lesssim R_{\rm maj} \lesssim 50''$, and  
+  an antitruncation in the light profile of the disk at $R_{\rm maj} \sim 122''$.
+  \cite{laurikainen2010} found that NGC 3998 features a weak bar at $R_{\rm maj} < 8''$,
+  a bright lens at $R_{\rm maj} < 15''$ and a weak bump in the surface brightness profile at $R_{\rm maj} \sim 40''$.
   We see three distinct peaks in the ellipticity profile.
-  The first two peaks occur at $R \sim 7''$ and $R \sim 15''$, and they correspond to a weak bar and to a faint 
-  oval component respectively.
-  These components are both fit with a Ferrer function.
-  The third peak at $R \sim 35''$ coincides with a bump in the surface brightness profile and is produced by a ring.
+  The first two peaks occur at $R_{\rm maj} \sim 7''$ and $R_{\rm maj} \sim 15''$, and they correspond to a weak bar and to a faint 
+  oval component, respectively.
+  These components are fit with two Ferrer functions.
+  The third peak at $R_{\rm maj} \sim 35''$ coincides with a bump in the surface brightness profile and is produced by a ring.
   The AGN component is modeled with a Gaussian profile.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3998_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3998.}
+  }
   \end{center}
@@
   \hline
-  L+10         &  & $5.0$  &  $2.0$ \\
+  L+10         & S-bul + e-d + F-bar + F-l & $5.0$  &  $2.0$ \\
   S+11         & S-bul + e-d + G-bar + G-n & $4.7$  &  $1.5$ \\
@@
 
-  NGC 4026 is an edge-on lenticular galaxy with a nuclear stellar disk ($R \lesssim 0''.5$, \citealt{ledo2010}).
-
-  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 11''.4$, $n = 3.5$).
-
-  \emph{1D fit -- }
-  The unsharp mask reveals the presence of a bar ($R \lesssim 30''$) and of a disky component 
-  embedded in the bulge, that is responsible for the peak at $R \sim 5''$ in the B4 profile.
-  The last can be also recognized in the velocity map.
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4026_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4026.
+  NGC 4026 is an edge-on lenticular galaxy with a nuclear stellar disk (with size $\lesssim 0''.5$, \citealt{ledo2010}).
+  The unsharp mask reveals the presence of a bar ($R_{\rm maj} \lesssim 30''$) and of a disky component 
+  embedded in the bulge, that is responsible for the peak at $R_{\rm maj} \sim 5''$ in the B4 profile.
+  The disky component can be also recognized in the velocity map.
   The bar is fit with a Ferrer function and the inner disk with a low-$n$ S\'ersic profile.
-  Due to the poor spatial resolution of our data, we were not able to model the nuclear stellar disk.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4026_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4026.}
+  We do not model the nuclear component to avoid degeneracies.
+  }
   \end{center}
@@
   \label{tab:n4026}
+  \tablecomments{S+11 obtained larger estimates of the bulge effective radius and S\'ersic index because they did not model the bar.}
   \end{table}
@@
 
-  NGC 4261 is an elliptical galaxy with %a radio jet \citep{liuxie1992}, 
-  a LINER nucleus \citep{veroncettyveron2006}
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4261_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4261.
+  NGC 4261 is an elliptical galaxy with a LINER nucleus \citep{veroncettyveron2006}
   and a dusty nuclear disk \citep{tran2001}.
-  The galaxy features a partially depleted core ($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
-
-  %\cite{grahamdriver2007} fit NGC 4261 with a single S\'ersic-bulge 
-  %($R_{\rm e} = 88''.6$, $n = 7.3$).
-  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model 
-  %($R_{\rm e} = 22''.6$, $n = 4.0$).
-  %\cite{vika2012} employed a S\'ersic-bulge + mask-core 
-  %($R_{\rm e} = 24''.2$, $n = 3.5$).
-  %\cite{beifiori2012} adopted a single S\'ersic-bulge model 
-  %($R_{\rm e} = 48''.8$, $n = 4.3$).
-  %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
-  %($R_{\rm e} = 77'.1$, $n = 6.3$).
-  %\cite{lasker2014data} employed a S\'ersic-bulge + mask-core model 
-  %($R_{\rm e} = 68'.4$, $n = 6.5$).
-
-  \emph{1D fit -- }
-  The ellipticity profile has a peak at $R \sim 10''$, unraveling the presence of an embedded component.
-  We identify such component with an inner disk, possibly seen face-on, and we model it with a Ferrer function.
-  The innermost $6''.1$ are excluded from the fit due to the presence of a partially depleted core.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4261_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4261.}
+  The galaxy features an unresolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
+  The ellipticity profile has a peak at $R_{\rm maj} \sim 10''$, unraveling the presence of an embedded component, 
+  that we model with a Ferrer function.
+  The data within the innermost $6''.1$ are excluded from the fit.
+  }
   \end{center}
@@
   \label{tab:n4261}
+  \tablecomments{
+  S+11 found the smallest estimate of the effective radius because they added a large-scale disk to their model.
+  Similarly, V+12 obtained a small estimate of the effective radius because of the limited radial extent of their data.
+  }
   \end{table}
@@
 
-  NGC 4291 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
-
-  %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge 
-  %($R_{\rm e} = 14'.8$, $n = 4.0$).
-  %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
-  %($R_{\rm e} = 15''.3$, $n = 5.6$).
-  %\cite{lasker2014data} adopted a S\'ersic-bulge + mask-core model
-  %($R_{\rm e} = 21''.3$, $n = 8.6$).
-
-  \emph{1D fit -- }
-  After excluding from the fit the innermost $6''.1$, because affected by the partially depleted core,
-  we found that NGC 4291 can be modeled with a single S\'ersic profile.
-
   \begin{figure}[h]
@@
   \includegraphics[width=\fitfigurewidth]{images/n4291_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4291.}
+  \caption{Best-fit model and isophotal parameters for NGC 4291.
+  NGC 4291 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
+  After excluding from the fit the data within the innermost $6''.1$, 
+  we observe that NGC 4291 can be well modeled with a S\'ersic profile.
+  }
   \end{center}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4388_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4388.
   NGC 4388 is an edge-on spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006} 
   and copious nuclear dust \citep{martini2003}.
-
-  \emph{1D fit -- }
-  The peaks at $R \sim 30''$ in the ellipticity and B4 profiles signal the presence of a bar.
-  The data between $35'' \lesssim R \lesssim 65''$ have been excluded because cannot be accommodated by the Ferrer function 
-  used to describe the bar. 
+  The peaks at $R_{\rm maj} \sim 30''$ in the ellipticity and B4 profiles signal the presence of a bar.
+  The data between $35'' \lesssim R_{\rm maj} \lesssim 65''$ are excluded from the fit.
   The AGN component is fit with a Gaussian profile.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4388_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4388.}
+  }
   \end{center}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4459_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4459.
   NGC 4459 is a lenticular galaxy.
-  Its disk profile is reported to have an antitruncation at $R \sim 119''$ \citep{gutierrez2011}.
-
-  %\cite{laurikainen2010} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Ferrer-lens 
-  %($R_{\rm e} \sim 7'' $, $n = 3.0$).
-  %\cite{sani2011} used a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 10''.3$, $n = 2.5$).
-  %\cite{vika2012} modeled this galaxy with a S\'ersic-bulge + Moffat-nucleus 
-  %($R_{\rm e} = 25''.0$, $n = 3.9$).
-  %\cite{beifiori2012} adopted a single S\'ersic-bulge model 
-  %($R_{\rm e} = 155''.2$, $n = 7.4$).
-
-  \emph{1D fit -- }
-  The ellipticity constantly increases across all the observed radial range ($R \lesssim 100''$).
+  Its disk profile is reported to have an antitruncation at $R_{\rm maj} \sim 119''$ \citep{gutierrez2011}.
+  The ellipticity constantly increases across all the observed radial range ($R_{\rm maj} \lesssim 100''$).
   This is an indication that, going from the galaxy center to the outskirts,
-  the disk component becomes increasingly more important than the spheroidal component.
-  However, the lack of a plateau in the ellipticity profile at large radii implies that at $R \sim 100''$ 
+  the disk component becomes increasingly more important over the spheroidal component.
+  However, the lack of a plateau in the ellipticity profile at large radii implies that at $R_{\rm maj} \sim 100''$ 
   the contribution from the bulge is still significant compared to that of the disk.
@@
   produced by the transition between the radial range where the disk becomes increasingly more important 
-  over the bulge and the truly exponential decline of the disk beyond $R \gtrsim 119''$.
+  over the bulge and the truly exponential decline of the disk beyond $R_{\rm maj} \gtrsim 119''$.
   We do not find evidence for any embedded components in our data.
-  A nuclear light excess is observed in the 1D residuals from a S\'ersic + exponential fit 
-  and is consequently modeled with a Gaussian profile.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4459_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4459.}
+  A nuclear light excess is modeled with a Gaussian profile.
+  }
   \end{center}
@@
   \label{tab:n4459}
+  \tablecomments{
+  B+12 did not model the large-scale disk and thus overestimated the bulge effective radius and S\'ersic index.
+  }
   \end{table}
@@
   \hline
-  L+05      & S-bul + e-d + F-bar + F-l & $2.8$  &  $1.4$ \\
+  L+10      & S-bul + e-d + F-bar + F-l & $2.8$  &  $1.4$ \\
   S+11      & S-bul + e-d + G-bar & $28.0$  &  $3.0$ \\

### 2015-05-28 papers/data_paper/datapaper.tex
cardioiloveu

@@
 Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs
-\citep{dullograham2013cores,rusli2013}.
+\citep{dullograham2014cores,rusli2013}.
 The majority are thus unresolved in our image mosaics. 
@@
 
-  BTW, if we wanna test the two phase formation scenario, we should care more about the halos...
-  at which effective radius does the halo begin?
-  what is the ratio of the mass in the galaxy or in the halo?
-
   \begin{figure}[h]
@@
   \includegraphics[width=\fitfigurewidth]{images/m89_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M89.}
+  \caption{Best-fit model and isophotal parameters for M89.
+  M89 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. 
+  The galaxy halo dominates the light at large radii, where the isophotes are significantly more elliptical than in the inner part of the galaxy. 
+  The halo is modeled with an exponential function. 
+  }
   \end{center}
@@
   \hline
-  &   & $$  &  $$ \\
+  S+11         & S-bul + e-d     & $24.3$  &  $4.0$ \\
+  V+12         & S-bul           & $16.7$  &  $3.6$ \\
+  B+12         & S-bul           & $45.2$  &  $4.3$ \\
+  R+13         & S-bul + S-halo  & $19.8$  &  $3.8$ \\
   \hline
@@
 
-  ok
-
   \begin{figure}[h]
@@
   \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3585.}
-  \end{center}
-  \end{figure}
+  \caption{Best-fit model and isophotal parameters for NGC 3585. 
+  NGC 3585 is an elliptical galaxy with an embedded disk \cite{scorzabender1995}. 
+  The embedded disk is visible in the unsharp mask and modeled with an exponential function. }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3585.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-id & $105.0$  &  $5.2$ \\
+  T.W. 1D eq.  & S-bul + e-id & $86.3$  &  $6.3$ \\
+  \hline
+  S+11         & S-bul + e-d      & $15.5$   &  $2.5$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3585}
+  \tablecomments{
+  S+11 obtained smaller estimates of the effective radius and S\'ersic index because
+  they oversubtracted a large-scale disk.
+  }
+  \end{table}
 
@@
   \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3607.}
-  \end{center}
-  \end{figure}
+  \caption{Best-fit model and isophotal parameters for NGC 3607. 
+  NGC 3607 is an elliptical galaxy with an embedded disk. 
+  The velocity map shows rotation only within $R_{\rm maj} \lesssim 20''$. 
+   }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3607.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-id & $69.3$  &  $5.5$ \\
+  T.W. 1D eq.  & S-bul + e-id & $65.5$  &  $5.6$ \\
+  T.W. 2D      & S-bul + e-id & $60.0$  &  $5.3$ \\
+  \hline
+  L+10	   & S-bul + e-d      & $6.5$   &  $1.5$ \\
+  S+11	   & S-bul + G-n      & $44.6$  &  $5.0$ \\
+  B+12	   & S-bul	      & $56.3$  &  $4.7$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3607}
+  \tablecomments{L+10 obtained the smallest estimates of the effective radius and S\'ersic index because
+  they oversubtracted a large-scale disk.
+  }
+  \end{table}
 
@@
   \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3608.}
-  \end{center}
-  \end{figure}
+  \caption{Best-fit model and isophotal parameters for NGC 3608.
+  NGC 3608 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013} 
+  and a kinematically decoupled core. 
+  We find unnnecessary masking the nuclear region of this galaxy and we fit the light profile with a single S\'ersic model.
+  }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3608.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul & $47.5$  &  $5.2$ \\
+  T.W. 1D eq.  & S-bul & $43.4$  &  $5.7$ \\
+  T.W. 2D      & S-bul & $62.0$  &  $7.0$ \\
+  \hline
+  S+11         & S-bul            & $56.4$  &  $6.0$ \\
+  B+12         & S-bul            & $182.2$  &  $9.0$ \\
+  R+13         & core-S\'ersic    & $56.9$  &  $6.3$ \\
+  L+14         & S-bul            & $48.9$  &  $6.6$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3608}
+  \tablecomments{B+12 obtained the largest estimates of the effective radius and S\'ersic index, 
+  but the reasons for this are not clear. }
+  \end{table}
 
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4151_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4151.
   NGC 4151 is a face-on barred spiral galaxy that hosts a Seyfert AGN \citep{veroncettyveron2006} 
   and circumnuclear dust \citep{pott2010}.
-
-  \cite{sani2011} fit this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-AGN model
-  ($R_{\rm e} = 5''.4$, $n = 3.5$).
-  \cite{gadotti2008} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar + PSF-AGN 
-  ($R_{\rm e} = 4''.7$, $n = 3.0$).
-
-  \emph{1D fit -- }
-  embedded disk in the bulge,
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4151_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4151.}
-  \end{center}
-  \end{figure}
+  The nucleus of this galaxy is very bright and the IRAf task {\tt ellipse} fails at fitting the isophotes within $R_{\rm maj} < 4''$, 
+  thus our light profile starts at $R_{\rm maj} \sim 4''$. 
+  The bar is fit with a low-$n$ S\'ersic profile.  
+  }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4261.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + S-bar [+ m-n] & $7.6$  &  $1.4$ \\
+  T.W. 1D eq.  & S-bul + e-d + S-bar [+ m-n] & $6.8$  &  $1.9$ \\
+  %T.W. 2D      & S-bul + e-d + S-bar + m-n & $$  &  $$ \\
+  \hline
+  S+11         & S-bul + e-d + G-n         & $5.4$  &  $3.5$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4151}
+  \end{table}
 
@@
 
-  NGC 4473 is an elliptical galaxy with an embedded disk \citep{scorzabender1998,ledo2010}.
-
-  \cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
-  ($R_{\rm e} = 39''.6$, $n = 2.7$). 
-  \cite{sani2011} used a S\'ersic-bulge model
-  ($R_{\rm e} = 49''.3$, $n = 7.0$). 
-  \cite{vika2012} fit this galaxy with a S\'ersic-bulge + mask-core 
-  ($R_{\rm e} = 21''.3$, $n = 4.3$). 
-  \cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model 
-  ($R_{\rm e} = 10''.6$, $n = 2.2$).  
-  \cite{lasker2014data} described this galaxy with a single S\'ersic-bulge 
-  ($R_{\rm e} = 27''.9$, $n = 5.1$).
-
-  \emph{1D fit -- }
-  TBD!! explain ellipticity profile...
-
   \begin{figure}[h]
@@
   \includegraphics[width=\fitfigurewidth]{images/n4473_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4473.}
-  \end{center}
-  \end{figure}
+  \caption{Best-fit model and isophotal parameters for NGC 4473.
+  NGC 4473 is an elliptical galaxy with an embedded disk \citep{ledo2010}.
+  The disk is clearly visible in the velocity map. 
+  We account for a nuclear excess of light by adding a narrow Gaussian function to the model.
+  }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 4473.}
+  \begin{center}
+  \begin{tabular}{llccc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-id + G-n & $45.9$  &  $2.3$ \\
+  T.W. 1D eq.  & S-bul + e-id + G-n & $36.9$  &  $2.9$ \\
+  %T.W. 2D	&  & $$  &  $$ \\
+  \hline
+  GD07      & S-bul                 & $39.6$   &  $2.7$ \\
+  S+11      & S-bul                 & $49.3$   &  $7.0$ \\
+  V+12      & S-bul + m-c           & $21.3$   &  $4.3$ \\
+  B+12      & S-bul + e-d           & $10.6$   &  $2.2$ \\
+  L+14      & S-bul                 & $27.9$   &  $5.1$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n4459}
+  \tablecomments{
+  B+12 obtained the smallest estimates of the effective radius and S\'ersic index because they oversubtracted a large-scale disk. 
+  }
+  \end{table}
 
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4564_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4564.
   NGC 4564 is an edge-on lenticular galaxy.
-
-  %\cite{grahamdriver2007} decomposed this galaxy into a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 4''.3$, $n = 3.2$). 
-  \cite{fisherdrory2008} fit this galaxy with a S\'ersic-bulge + exponential-disk 
-  ($R_{\rm e} = 8''.7$, $n = 3.7$). 
-  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk 
-  %($R_{\rm e} = 25''.0$, $n = 7.0$).
-  %\cite{vika2012} used a S\'ersic-bulge + exponential-disk model 
-  %($R_{\rm e} = 3''.0$, $n = 3.7$).
-
-  \emph{1D fit -- }
-  The isophotal parameters do not show any evidence for embedded components.
-  However, fitting NGC 4564 with a S\'ersic + exponential model results in bad residuals.
-  In the unsharp mask, one can hardly glimpse an oval structure extending out to $R \lesssim 15''$.
+  In the unsharp mask, one can glimpse an oval structure extending out to $R_{\rm maj} \lesssim 15''$ (see the peak in the B4 profile).
+  Fitting NGC 4564 with a S\'ersic + exponential model produces bad residuals.
   The addition of a Ferrer function to the model dramatically improves the fit and smoothes the residuals.
-  Although the lack of strong evidence for the presence of a (faint) third component, 
-  we prefer to model the lens with a Ferrer function 
-  because of the notable improvement in the goodness of the global fit.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4564_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4564.}
+  }
   \end{center}
@@
   \label{tab:n4564}
+  \tablecomments{The most dicrepant results are obtained by S+11, although they used the same model as GD07 and V+12. }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4596_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4596.
   NGC 4596 is an edge-on barred lenticular galaxy.
-
-  %\cite{laurikainen2005} decomposed this galaxy into a S\'ersic-bulge + exponential-disk + Ferrer-bar + Ferrer-lens 
-  %($R_{\rm e} = 2''.8$, $n = 1.4$). 
-  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + exponential-disk + Gaussian-bar 
-  %($R_{\rm e} = 28''.0$, $n = 3.0$). 
-  %\cite{vika2012} decomposed it into a S\'ersic-bulge + exponential-disk + S\'ersic-bar 
-  %($R_{\rm e} = 13''.2$, $n = 3.6$). 
-  %\cite{beifiori2012} adopted a S\'ersic-bulge + exponential-disk model
-  %($R_{\rm e} = 44''.9$, $n = 4.4$).
-
-  \emph{1D fit -- }
   The morphology of this galaxy is quite complex. 
-  The bar extends out to $R \lesssim 50''$ and concludes in two evident ansae.
+  The bar extends out to $R_{\rm maj} \lesssim 50''$ and concludes in two evident ansae.
   The large-scale disk features a wide ring that is responsible for the curvature in the light profile observed within 
-  $60'' \lesssim R \lesssim 130''$ (see also \citealt{comeron2014}).
-  An additional embedded disk-like component ($R \lesssim 15''$) can be recognized in the B4 profile and in the velocity map.
-  The bump in the light profile within $60'' \lesssim R \lesssim 70''$ corresponds to the ansae of the bar.
-  This data range has therefore been excluded from the fit.
-  The large scale bar is fit with a Ferrer function and the inner disk with a S\'ersic profile.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4596_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4596.}
+  $60'' \lesssim R_{\rm maj} \lesssim 130''$ (see also \citealt{comeron2014}).
+  An additional embedded disky component ($R_{\rm maj} \lesssim 15''$) can be recognized in the B4 profile and in the velocity map.
+  The bump in the light profile within $60'' \lesssim R_{\rm maj} \lesssim 70''$ corresponds to the ansae of the bar.
+  This data range is excluded from the fit.
+  The large scale bar is fit with a Ferrer function and the inner disk with a low-$n$ S\'ersic profile.
+  }
   \end{center}
@@
   \label{tab:n4596}
+  \tablecomments{
+  B+12 fit nor the bar neither the inner disk and obtained the largest estimates of the bulge effective radius and S\'ersic index.
+  The models of S+11 and V+12 account for the bar and thus result in lower estimates of the bulge effective radius and S\'ersic index.
+  }
   \end{table}
@@
 
-  NGC 4697 is an elliptical galaxy with an embedded disk \cite{scorzabender1995}.
-
-  %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge model
-  %($n = 4.0$).
-  %\cite{sani2011} described it with a S\'ersic-bulge 
-  %($R_{\rm e} = 100'.5$, $n = 5.0$). 
-  %\cite{vika2012} proposed a single S\'ersic-bulge model 
-  %($R_{\rm e} = 39''.1$, $n = 3.8$) 
-  %or a S\'ersic-bulge + exponential-disk model 
-  %($R_{\rm e} = 10''.0$, $n = 2.9$).
-  %\cite{beifiori2012} chose a single S\'ersic-bulge 
-  %($R_{\rm e} = 128''.7$, $n = 5.0$).
-  %\cite{lasker2014data} decomposed NGC 4697 into a S\'ersic-bulge + exponential-disk + PSF-nucleus + S\'ersic-envelope 
-  %($R_{\rm e} = 6''.3$, $n = 2.1$).
-
-  \emph{1D fit -- }
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4697_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4697.
+  NGC 4697 is an elliptical galaxy with an embedded disk \citep{scorzabender1995}.
   The velocity map and the unsharp mask of NGC 4697 clearly show 
-  the presence of an intermediate-size disk embedded in the main spheroid.
+  the presence of an intermediate-size disk embedded in the galaxy's spheroidal component.
   However, the ellipticity profile presents two peaks. 
-  The peak at $R \sim 40''$ corresponds to the embedded disk already mentioned,
-  while the peak at $R \sim 10''$ unveils a second inner disk-like component.
+  The peak at $R_{\rm maj} \sim 40''$ corresponds to the intermediate-size embedded disk just mentioned,
+  while the peak at $R_{\rm maj} \sim 10''$ unveils a smaller inner disk.
   After testing different decomposition models, 
-  in which we fit the embedded disks with a set of different functions (exponential, S\'ersic, Ferrer)
-  but we always described the main spheroidal component with a S\'ersic profile,
-  we noticed that the bulge parameters did not vary significantly among the various decompositions.
+  in which we fit the two embedded disks with different functions (exponential, S\'ersic, Ferrer),
+  while always describing the main spheroidal component with a S\'ersic profile,
+  we noticed that the spheroid parameters do not significantly vary among the various decompositions.
   Our preferred model for NGC 4697 consists of a S\'ersic-bulge + 2 S\'ersic-inner disks.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4697_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4697.}
+  }
   \end{center}
@@
   \label{tab:n4697}
+  \tablecomments{
+  In both their models, V+12 underestimated the effective radius and the S\'ersic index because of the small radial range of their data. 
+  L+14 oversubtracted a large-scale disk and a halo, and thus underestimated the spheroid effective radius and the S\'ersic index. 
+  }
   \end{table}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4889.
   NGC 4889 is the brightest member of the Coma cluster. 
-  It is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.6$, \citealt{rusli2013}).
-
-  %\cite{rusli2013} modeled NGC 4889 with a core-S\'ersic model 
-  %($R_{\rm e} = 169''.2$, $n = 9.8$).
-
-  \emph{1D fit -- }
-  We excluded from the fit the innermost $6''.1$ because affected by the partially depleted core and
-  we modeled the galaxy with a single S\'ersic profile.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4889.}
+  It is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. % ($R_{\rm break} = 1''.6$, \citealt{rusli2013}).
+  We exclude from the fit the innermost $6''.1$ and
+  we successfully model the galaxy with a single S\'ersic profile.
+  }
   \end{center}
@@
 
-  TBD!!! \\
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n4945_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 4945.
   NGC 4945 is an edge-on, dusty spiral galaxy that hosts a Seyfert AGN \citep{lin2011}.
-
-  \cite{kormendy2010} found that the bulge of NGC 4945 is best modeled with a low-$n$ S\'ersic function
-  ($n = 1.3$).
-
-  \emph{1D fit -- }
-  Given the edge-on inclination of this object, the identification of a possible large-scale bar is complicated.
-  The light profile has an obvious bump that could be interpreted in two different ways.
-  The bump could be produced by a large-scale bar; 
-  in this case, either the disk must have a truncation happening at a radius smaller than the length of the bar,
-  or its light profile cannot be exponential (this condition can be caused by the high inclination of the galaxy).
-  Alternatively, the bump could be due by the galaxy spiral arms, the disk has an exponential profile with no truncation
-  and the galaxy has no bar.
-  After checking that both scenarios result in similar best-fit parameters for the bulge, 
-  we choose the second and simpler hypothesis.
-  We exclude form the fit the data between $R \sim 100''-400''$, where the spiral arm would contribute to the galaxy light,
-  and we also exclude the innermost $6''.4$ due to the presence of the AGN.
-  Our final model for NGC 4945 consists of a S\'ersic-bulge + exponential-disk.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4945_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4945.}
+  The light profile has an obvious bump that can be ascribed to a bar.
+  This bumb cannot be easily modeled with a Ferrer function, thus we exclude form the fit the data in the range $100'' \lesssim R_{\rm maj} \sim 400''$.
+  We also exclude the data within the innermost $6''.4$ due to the contribution from the AGN.
+  }
   \end{center}
@@
 
-  ok
-
-  \emph{1D fit -- }
-
   \begin{figure}[h]
@@
   \includegraphics[width=\fitfigurewidth]{images/n5077_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 5077.}
+  \caption{Best-fit model and isophotal parameters for NGC 5077. 
+  NGC 5077 is an elliptical galaxy with an unresolved partially depleted core \citep{trujillo2004coresersicmodel}. 
+  We mask the data within the innermost $6''.1$ and fit the galaxy with a S\'ersic profile. }
   \end{center}
@@
   \includegraphics[width=\fitfigurewidth]{images/n5128_1Dfit.eps}
-  \caption{}
+  \caption{Best-fit model and isophotal parameters for NGC 5128.
+  NGC 5128 is a merging system. }
   \end{center}
@@
   \hline
-  T.W. 1D maj. & TBD!! & $61.3$  &  $1.2$ \\
-  T.W. 1D eq.  &  & $60.8$  &  $2.2$ \\
+  T.W. 1D maj. & S-bul + e-halo + G-n & $61.3$  &  $1.2$ \\
+  T.W. 1D eq.  & S-bul + e-halo + G-n & $60.8$  &  $2.2$ \\
   %T.W. 2D	&  & $$  & $$  &  $$ \\
@@
   \label{tab:n5128}
+  \tablecomments{}
   \end{table}
@@
 
-  ok
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
-  \caption{}
-  \end{center}
-  \end{figure}
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n5576_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 5576.
+  NGC 5576 is an elliptical galaxy with a disturbed morphology. 
+  The isophotal parameters suggest the presence of an embedded disk ($R_{\rm maj} \lesssim 20''$), 
+  but any attempt to account for such component was unsuccessful. 
+  The data within $R_{\rm maj} \lesssim 36''$ are excluded from the fit 
+  and the galaxy is modeled with a S\'ersic profile.
+  } 
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 5576.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul  & $61.5$  &  $3.3$ \\
+  T.W. 1D eq.  & S-bul  & $49.3$  &  $3.7$ \\
+  T.W. 2D      & S-bul  & $45.9$  &  $8.3$ \\
+  \hline
+  S+11      & S-bul & $34.3$  &  $7.0$ \\
+  V+12      & S-bul & $16.9$  &  $5.1$ \\
+  B+12      & S-bul & $77.6$  &  $8.7$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n5845}
+  \tablecomments{The results obtained by S+11 and B+12 best agree with the results from our 2D model, 
+  in which we did not mask the inner region of the galaxy. 
+  The small radial extent of the data used by V+12 led them to underestimate the effective radius.}
+  \end{table}
 
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n5845_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 5845.
   NGC 5845 is an elliptical/lenticular galaxy. 
-
-  %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
-  %($R_{\rm e} = 4''.1$,$n = 3.2$).
-  %\cite{sani2011} fit it with a S\'ersic-bulge 
-  %($R_{\rm e} = 3''.7$, $n = 3.0$). 
-  %\cite{vika2012} used a S\'ersic-bulge model 
-  %($R_{\rm e} = 3''.5$, $n = 2.6$).
-  %\cite{beifiori2012} chose a single S\'ersic-bulge 
-  %($R_{\rm e} = 4''.1$, $n = 3.5$).
-  %\cite{lasker2014data} described this galaxy with a S\'ersic-bulge 
-  %($R_{\rm e} = 3''.5$, $n = 2.8$).
-
-  \emph{1D fit -- }
   The small apparent size of NGC 5845 (compared to the PSF FWHM) implies low resolution for the data 
   and complications for the modeling of this galaxy.
-  Here, looking at the unsharp mask and the velocity field, we identify 
-  a disk component, either large-scale or embedded.
-  To rule out one of the two cases, a good test would be to check whether
-  the light profile of NGC 5845 presents an exponential decline in its outer part.
-  Unfortunately, the IRAC image is not deep enough and beyond $R \gtrsim 23''$ the galaxy light 
-  is fainter than $3 RMS_{\rm SKY}$.
-  %Since the too small radial range prevents us from disentangling between an embedded and a large-scale disk,
-  %we choose the most statistically significant solution (lowest $\chi^2$), 
-  %but we caution that the best fit parameters might be biased by a non adequate choice
-  %of the model components. 
-  %However, our results are in agreement with those from \cite{jia2012}, 
-  %who study the structure and kinematics of NGC5845 with HST/WFPC2 data 
-  %and previously published spatially resolved kinematics, and unambiguously identify a 
-  %large scale disk in both the photometry and the kinematics. \\
-  The ellipticity profile has a peak at $R \sim 13''$ and therefore suggests that the disk is indeed embedded.
+  Here, looking at the unsharp mask and the velocity field, we identify a disk, but it is not clear whether the disk is large-scale or embedded.
+  The ellipticity profile has a peak at $R_{\rm maj} \sim 13''$ which suggests that the disk is indeed embedded.
   However, when fitting NGC 5845 with a S\'ersic + exponential model, 
-  the lowest-$\chi^2$ solution does not reproduce an inner disk, but rather a large-scale one.
-  This is because the S\'ersic and the exponential function are degenerate in this decomposition, 
-  due to the small number of data points sampling the galaxy light profile.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n5845_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 5845.}
+  the lowest-$\chi^2$ solution does not reproduce an embedded disk.
+  This is because the S\'ersic and the exponential functions are degenerate in this decomposition, 
+  due to the small number of data points in the galaxy light profile.
+  }
   \end{center}
@@
 
-  NGC 5846 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n5846_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 5846.
+  NGC 5846 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
   This galaxy has a LINER nucleus \citep{carrillo1999} and filamentary nuclear dust \citep{tran2001}.
-
-  %\cite{sani2011} modeled this galaxy with a S\'ersic-bulge
-  %($R_{\rm e} = 36''.4$, $n = 3.0$). 
-  %\cite{vika2012} used a S\'ersic-bulge + mask-core model 
-  %($R_{\rm e} = 46''.3$, $n = 3.7$). 
-  %\cite{rusli2013} fit this galaxy with a core-S\'ersic profile 
-  %($R_{\rm e} = 113''.2$, $n = 5.3$).
-
-  \emph{1D fit -- }
-  This galaxy has a strong isophotal twist between its center and $R \sim 70''$, and
-  its light profile presents a slight bump at $R \sim 20''$.
+  It also displays a strong isophotal twist between its center and $R_{\rm maj} \sim 70''$.
+  The light profile presents a slight bump at $R_{\rm maj} \sim 20''$.
   However, the isophotal parameters, the unsharp mask and the velocity map lack of clear evidence for an embedded component.
-  We thus model NGC 5846 with a single S\'ersic profile, after masking the innermost $6''.1$.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n5846_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 5846.}
+  We thus model NGC 5846 with a single S\'ersic profile, after masking the data within innermost $6''.1$.
+  }
   \end{center}
@@
   \label{tab:n5846}
+  \tablecomments{S+11 did not mask the core and thus underestimated the effective radius and S\'ersic index. }
   \end{table}
@@
 
-  NGC 6251 is an elliptical galaxy with a large stellar velocity dispersion ($\sigma \sim 310~\rm km~s^{-1}$),
-  which is a clue for the presence of a partially depleted core.
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n6251_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 6251.
+  NGC 6251 is an elliptical galaxy. Its large stellar velocity dispersion suggests the presence of a partially depleted core.
   The galaxy features a nuclear disk of dust \citep{ferrareseford1999n6251} and a Seyfert AGN \citep{panessabassani2002}.
-
-  %\cite{grahamdriver2007} fit this galaxy with a S\'ersic-bulge 
-  %($R_{\rm e} = 173''.92$, $n = 11.8$). 
-  %\cite{sani2011} adopted a S\'ersic-bulge + Gaussian-AGN model 
-  %($R_{\rm e} = 42''.4$, $n = 7.0$). 
-  %\cite{lasker2014data} modeled this galaxy with a S\'ersic-bulge 
-  %($R_{\rm e} = 20''.6$, $n = 5.0$).
-
-  \emph{1D fit -- }
-  We masked the innermost $6''.1$ because possibly affected by the combined contribution of the AGN 
-  and the partially depleted core. 
-  A single S\'ersic profile provides a good description of NGC 6251.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n6251_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 6251.}
+  We mask the data within the innermost $6''.1$. 
+  A single S\'ersic profile provides a good description of this galaxy.
+  }
   \end{center}
@@
   \label{tab:n6251}
+  \tablecomments{It is not clear why GD07 obtained the largest estimates of the effective radius and S\'ersic index.}
   \end{table}
@@
 
-  NGC 7052 is an elliptical galaxy reported to have a partially depleted core 
-  ($R_{\rm break} = 0''.8$, \citealt{quillen2000}).
-
-  %\cite{grahamdriver2007} modeled this galaxy with a S\'ersic-bulge 
-  %($R_{\rm e} = 70''.4$, $n = 4.6$). 
-  %\cite{sani2011} used a S\'ersic-bulge model 
-  %($R_{\rm e} = 39''.3$, $n = 5.0$). 
-  %\cite{vika2012} fit this galaxy with a S\'ersic-bulge + exponential-disk
-  %($R_{\rm e} = 4''.3$, $n = 1.8$).
-  %\cite{lasker2014data} adopted a S\'ersic-bulge model 
-  %($R_{\rm e} = 26''.6$, $n = 4.2$).
-
-  \emph{1D fit -- }
-  A single S\'ersic function provides a fairly good description of the surface brightness profile of NGC 7052.
-  However, the residuals of such fit display a curious behaviour, having a nuclear light excess along the major-axis 
-  and a nuclear light deficit along the equivalent-axis. 
-  This pattern is still present when the innermost $6''.1$ are excluded and the fit is repeated with a S\'ersic profile.
-  The reasons for this are unclear. 
-  The best-fit parameters obtained from a single S\'ersic fit, without excluding the innermost data points,
-  are not significantly different from those obtained when excluding the core region (see Table \ref{tab:n7052}).
-  Given the uncertainty connected to the nuclear region of this galaxy,
-  we preferred the model that incorporates the exclusion of the innermost $6''.1$, 
-  with the caveat about the ambiguous presence of a partially depleted core.
-
   \begin{figure}[h]
@@
   \includegraphics[width=\fitfigurewidth]{images/n7052_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 7052.}
+  \caption{Best-fit model and isophotal parameters for NGC 7052.
+  NGC 7052 is an elliptical galaxy with an unresolved partially depleted core \citep{quillen2000}. %% ($R_{\rm break} = 0''.8$, \citealt{quillen2000}). 
+  We mask the data within the innermost $6''.1$ and model the galaxy with a single S\'ersic profile.
+  }
   \end{center}
@@
   \hline
-  \multicolumn{4}{c}{\emph{excluding innermost $6''.1$}} \\
+  %\multicolumn{4}{c}{\emph{excluding innermost $6''.1$}} \\
   T.W. 1D maj. & S-bul + m-c & $59.4$  &  $4.2$ \\
@@
   \hline
-  \multicolumn{4}{c}{\emph{including innermost $6''.1$}} \\
-  T.W. 1D maj. & S-bul & $66.1$  &  $4.8$ \\
-  T.W. 1D eq.  & S-bul & $35.0$  &  $5.0$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
+  %\multicolumn{4}{c}{\emph{including innermost $6''.1$}} \\
+  %T.W. 1D maj. & S-bul & $66.1$  &  $4.8$ \\
+  %T.W. 1D eq.  & S-bul & $35.0$  &  $5.0$ \\
+  %%T.W. 2D	&  & $$  & $$  &  $$ \\
+  %\hline
   GD07      & S-bul & $70.4$  &  $4.6$ \\
@@
   \label{tab:n7052}
+  \tablecomments{The model of V+12 subtracts a large-scale disk and thus results in the lowest estimates of the effective radius and S\'ersic index.}
   \end{table}
@@
 
-  NGC 7619 is an elliptical galaxy reported to have a partially depleted core ($R_{\rm break} = 0''.5$, \citealt{rusli2013}).
-
-  %\cite{rusli2013} fit this galaxy with a core-S\'ersic profile 
-  %($R_{\rm e} = 100''.1$, $n = 9.3$).
-
-  \emph{1D fit -- }
-  We identified an embedded disk signaled by the peak at $R \sim 10''$ in the ellipticity profile.
-  The velocity map of this galaxy confirms the presence of a fast rotating component (Falcon-Barroso private comm.).
-  We modeled NGC 7619 with a S\'ersic + inner-exponential model.
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n7619_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 7619.
+  NGC 7619 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %% ($R_{\rm break} = 0''.5$, \citealt{rusli2013}).
+  We identified an embedded disk signaled by the peak at $R_{\rm maj} \sim 10''$ in the ellipticity profile.
+  The velocity map of this galaxy confirms the presence of a fast rotating component (Falcon-Barroso, private comm.).
   We note that the residuals obtained from our best-fit model do not suggest the presence of a partially depleted core,
   whereas they display a nuclear lack of light when the galaxy is modeled with a single S\'ersic-bulge. 
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n7619_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 7619.}
+  }
   \end{center}
@@
 
-  NGC 7768 is an elliptical galaxy with a partially depleted core ($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
-
-  %\cite{rusli2013} modeled this galaxy with a core-S\'ersic profile 
-  %($R_{\rm e} = 46''.1$, $n = 6.2$).
-
-  \emph{1D fit -- }
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n7768_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 7768.
+  NGC 7768 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
   The image of NGC 7768 is corrupted by a saturated star, which lies close to the galaxy.
   The sky background is not constant across the image.
-  To be safe, we fit only the innermost $R \lesssim 30''$, where the contribution from the background is negligible.
-  The data within $R < 6''.1$ are excluded from the fit due to the presence of a partially depleted core.
-  Our best-fit model consists of a single S\'ersic profile.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n7768_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 7768.}
+  To be safe, we fit only the data within the innermost $R_{\rm maj} \lesssim 30''$, where the contribution from the background is negligible.
+  The data within $R_{\rm maj} < 6''.1$ are excluded from the fit.
+  }
   \end{center}
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/ugc03789_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for UGC 03789.
   UGC 03789 is a face-on spiral galaxy.
-
-  \emph{1D fit -- }
-  This galaxy features a ring ($R \sim 20''$) and a nuclear bar ($R \lesssim 4''$),
+  This galaxy features a ring ($R_{\rm maj} \sim 20''$) and a nuclear bar ($R_{\rm maj} \lesssim 4''$),
   which can be seen in the unsharp mask and produces corresponding peaks in the ellipticity and PA profiles.
   The bar is fit with a Ferrer function.
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/ugc03789_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for UGC 03789.}
+  }
   \end{center}

### 2015-05-29 papers/MbhMsph/mm.tex
fri

@@
 that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
-Our sample is the largest to date and, for the first time, the decompositions were checked to be consistent with the galaxy kinematics.
-Here we present correlations between the black hole mass, $M_{\rm BH}$, 
+Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
+We present correlations between the black hole mass, $M_{\rm BH}$, 
 and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
@@
 which has long been known to be a ``double power-law'', 
-with $L_{\rm sph} \propto \sigma^{5-6}$ at the luminous end \citep{schechter1980,malumuthkrishner1981,vonderlinden2007,lauer2007lumell,liu2008}, 
+with $L_{\rm sph} \propto \sigma^{5-6}$ at the luminous end\footnote{Recent 
+work has the $M_{\rm BH} - \sigma$ correlation as steep as $M_{\rm BH} \propto \sigma^{6.5}$ \citep{savorgnangraham2015},
+and the high-luminosity end of the $L_{\rm sph} - \sigma$ correlation as steep as $L_{\rm sph} \propto \sigma^{8}$ \citep{monterodorta2015}.} 
+\citep{schechter1980,malumuthkrishner1981,vonderlinden2007,lauer2007lumell,liu2008}
 and $L_{\rm sph} \propto \sigma^2$ at intermediate and faint luminosities 
@@
 and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
-On the other hand, the bulges of the spiral galaxies trace a steeper \emph{late-type sequence}, 
+\cite{graham2012bent} reported that the $M_{\rm BH}/M_{\rm dyn,sph}$ ratio for core-S\'ersic galaxies was 0.36\% 
+($M_{\rm dyn,sph}$ is the spheroid dynamical mass), 
+and discussed the many implications of this.  
+Using a larger data sample, \cite{grahamscott2013} reported that the $M_{\rm BH}/M_{\rm *,sph}$ ratio was 0.49\% for core-S\'ersic galaxies.   
+Here we find a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.50 \pm 0.04\%$ for the 22 core-S\'ersic galaxies 
+and $0.68 \pm 0.04\%$ for the 45 early-type galaxies.  
+Among other things, this higher value (previously reported to be $0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}), 
+boosts estimates of the black hole mass function and mass density based on galaxy/spheroid luminosity functions. \\
+The bulges of the spiral galaxies trace a steeper \emph{late-type sequence}, 
 whose slope is less well constrained due to the smaller size of the subsample and, more importantly, 
@@
 \section{Conclusions}
-Using $3.6\rm~\mu m$ \emph{Spitzer} imagery, 
+Using $3.6\rm~\mu m$ \emph{Spitzer} images, 
 we have performed accurate multicomponent decompositions (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, depleted core, etc.), 
 which were checked to be consistent with the two-dimensional galaxy kinematics, 
-and we have derived galaxy luminosities, spheroid luminosities and spheroid stellar masses for 66 nearby galaxies 
-with a dynamical measurement of their black hole mass. 
-Our galaxy sample, besides being the largest ever used to investigate black hole mass scaling relations, 
+for 66 nearby galaxies with a dynamical measurement of their black hole mass.
+We have derived galaxy luminosities, spheroid luminosities and spheroid stellar masses. 
+Our galaxy sample, besides being to date the largest sample with reliable bulge masses used to investigate black hole mass scaling relations, 
 contains 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7 \rm~M_{\odot}$. 
@@
       We call this tight correlation an \emph{early-type sequence}. 
-      The $M_{\rm BH} - M_{\rm *,sph}$ log-relation for the bulges of late-type (spiral) galaxies has a more uncertain slope ($2-3$) 
-      due to the smaller size of the subsample and, more importantly, to the smaller range in stellar mass 
+      The $M_{\rm BH} - M_{\rm *,sph}$ log-relation for the bulges of late-type (spiral) galaxies has a slope of $2-3$,
+      which is less well constrained due to
+      the smaller size of the subsample and, more importantly, the smaller range in spheroid stellar mass 
       ($3 \times 10^9 \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 3 \times 10^{10}$) that the subsample spans. 
@@
       For analogy with the color-magnitude diagram, 
-      it would be tempting to refer to our \emph{early-type sequence} as a \emph{red sequence}, 
-      although no bimodality in color has been observed in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
+      it may be tempting to refer to our \emph{early-type sequence} as a \emph{red sequence} 
+      and to our \emph{late-type sequence} as a \emph{blue sequence}.
+      Future work will explore the color of spheroids and galaxies in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.  
+\item The $M_{\rm BH}/M_{\rm *,sph}$ ratio for the early-type galaxies is $0.68 \pm 0.04\%$.
+
+was 0.49\% for core-S\'ersic galaxies.   
+Here we find a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.50 \pm 0.04\%$ for the 22 core-S\'ersic galaxies 
+and $0.68 \pm 0.04\%$ for the 45 early-type galaxies.  
+Among other things, this higher value (previously reported to be $0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}),
+
 \item The $M_{\rm BH} - M_{\rm *,sph}$ log-relations for core-S\'ersic and S\'ersic spheroids have slopes consistent with each other 
       ($1.19 \pm 0.23$ and $1.48 \pm 0.20$, respectively), 
-      thus these two populations do not define two distinct sequences. 
+      thus these two populations do not appear to define two distinct sequences. 
 \item In the $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) diagram, for early-type galaxies, 
-      we did not observe the change in slope required for consistency with the $M_{\rm BH} - \sigma$ and bent $L_{\rm sph} - \sigma$ correlations.
+      we did not observe the change in slope required for consistency with the log-linear $M_{\rm BH} - \sigma$ and bent $L_{\rm sph} - \sigma$ correlations.
       This issue of inconsistency remains therefore an open question. 
-      It might be that we are still not probing enough low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) 
+      It might be that we are still not probing enough low-mass black holes ($M_{\rm BH} < 10^7\rm~M_\odot$) 
       for the subsample of early-type galaxies, 
-      or that the transition from  $L_{\rm sph} \propto \sigma^2$ at low luminosities to $L_{\rm sph} \propto \sigma^5$ at high luminosities 
+      or that the transition from  $L_{\rm sph} \propto \sigma^2$ at low luminosities to $L_{\rm sph} \propto \sigma^{(5-6)}$ at high luminosities 
       is less sharp than previously thought.
+      We intend to investigate this point in our future work. 
 \item Spheroids with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
@@
 \acknowledgments
-GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes, Gonzalo Diaz and Pablo Rosado for useful discussion. \\
+GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. \\
 % referee thank you!!

### 2015-06-01 papers/MbhMsph/mm.tex
endofmm

@@
 consistent with a dry-merging formation scenario,
-and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
+and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
+and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$.
 At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper \emph{late-type sequence}, 
@@
 \item The $M_{\rm BH}/M_{\rm *,sph}$ ratio for the early-type galaxies is $0.68 \pm 0.04\%$. 
-
-was 0.49\% for core-S\'ersic galaxies.   
-Here we find a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.50 \pm 0.04\%$ for the 22 core-S\'ersic galaxies 
-and $0.68 \pm 0.04\%$ for the 45 early-type galaxies.  
-Among other things, this higher value (previously reported to be $0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}),
-
+      This value is dramatically larger than what previously reported ($0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}).
 \item The $M_{\rm BH} - M_{\rm *,sph}$ log-relations for core-S\'ersic and S\'ersic spheroids have slopes consistent with each other 

### 2015-06-02 papers/data_paper/datapaper.tex
onedayleft

@@
 
-  ok
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n1374_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 1374.
+  NGC 1374 is an elliptical galaxy. 
+  A Gaussian function in our model accounts for a relatively faint nuclear component. 
+  }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 1374.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + G-n & $25.6$  &  $3.7$ \\
+  T.W. 1D eq.  & S-bul + G-n & $24.8$  &  $4.1$ \\
+  T.W. 2D      & S-bul + m-n & $25.2$  &  $3.7$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n1374}
+  \end{table}
 
@@
 
-  inner component?? ok fuck it
-
   \begin{figure}[h]
@@
   \includegraphics[width=\fitfigurewidth]{images/n3079_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3079.}
-  \end{center}
-  \end{figure}
+  \caption{Best-fit model and isophotal parameters for NGC 3079.
+  NGC3079 is an edge-on, late-type barred spiral galaxy 
+  with a Seyfert AGN \citep{veroncettyveron2006} and circumnuclear dust \citep{martini2003}. 
+  The bar extends out to $R_{\rm maj} \lesssim 70''$. 
+  We truncate the light profile at $R_{\rm maj} \sim 65''$, before the ``edge'' of the bar, 
+  and we model the combination of the disk and the bar with a Ferrer function. 
+  A Gaussian function accounts for the AGN emission. 
+  }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 2974.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + F-(bar+d) + G-n  & $6.8$  &  $1.3$ \\
+  T.W. 1D eq.  & S-bul + F-(bar+d) + G-n  & $4.3$  &  $1.1$ \\
+  \hline
+  S+11         & S-bul + e-d + G-bar + G-n & $74.1$  &  $2.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n2974}
+  \tablecomments{
+  It is not clear why S+11 obtained a dramatically larger bulge effective radius. 
+  }
+  \end{table}
 
@@
   \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3377.}
-  \end{center}
-  \end{figure}
+  \caption{Best-fit model and isophotal parameters for NGC 3377.
+  NGC 3377 is an elliptical/lenticular galaxy with an intermediate-scale disk and a nuclear stellar disk. 
+  }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3384.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + 2 e-id     & $61.8$  &  $7.7$ \\
+  T.W. 1D eq.  & S-bul + 2 e-id     & $91.7$  &  $9.2$ \\
+  T.W. 2D      & S-bul + e-id + m-n & $71.8$  &  $3.7$ \\
+  \hline
+  GD07         & S-bul     		     & $44.1$  &  $3.0$ \\
+  S+11         & S-bul     		     & $55.2$  &  $6.0$ \\
+  B+12         & S-bul     		     & $43.5$  &  $3.5$ \\
+  L+14         & S-bul + e-id + e-d + S-halo & $10.1$  &  $6.0$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n3384}
+  \end{table}
+
+  The morphology of NGC3377 is similar to NGC0821. 
+  The unsharp mask reveals an embedded disc and the extended velocity field confirms that 
+  it is not a large-scale disc. 
+  The residual image from a 2D single S\'ersic fit diplays the unsubtracted embedded disc
+  and an additional nuclear ($\lesssim 10''$) component.
+  The embedded disc is very close to edge-on.
+  In the 2D fit we adopt a S\'ersic + edge-on disc model, after masking the third nuclear component. 
+  In the 1D fit we are not able to model the embedded disc with an exponential function, 
+  probably because of the orientation of the disc. 
+  The best results are obtained when a Ferrer function is employed. 
+  We tried to model the nuclear cusp with a PSF or a gaussian function. The gaussian function parameters
+  resulted highly degenerate with the Ferrer function parameters, leading us to prefer a PSF profile. \\
 

### 2015-06-03 papers/data_paper/datapaper.tex
final

@@
   \includegraphics[width=\fitfigurewidth]{images/n0821_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 0821.}
-  \end{center}
-  \end{figure}
+  \caption{Best-fit model and isophotal parameters for NGC 0821.
+  NGC 0821 is an edge-on elliptical/lenticular galaxy. 
+  The ellipticity profile and the velocity map show the presence of a faint intermediate-scale disk. 
+  Given its edge-on inclination, the disk is modeled with a low-$n$ S\'ersic function.   
+  }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 0821.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-id + PSF-n & $36.8$  &  $5.4$ \\
+  T.W. 1D eq.  & S-bul + e-id + PSF-n & $20.7$  &  $6.0$ \\
+  T.W. 2D      & S-bul + e-id + m-n   & $33.8$  &  $2.5$ \\
+  \hline
+  GD07    & S-bul 		 & $44.1$   &  $4.0$ \\           
+  S+11    & S-bul 		 & $63.6$   &  $7.0$ \\           
+  B+12    & S-bul 		 & $111.3$  &  $7.7$ \\           
+  L+14    & S-bul + e-d + S-halo & $3.8$    &  $3.1$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:n0821}
+  \tablecomments{
+  L+14 obtained the smallest estimates of the spheroid effective radius and S\'ersic index because they failed to identify the extent 
+  of the intermediate-scale disk. 
+  Inaccurate sky subtraction could be the reason why B+12 obtained a large estimate of the effective radius.
+  }
+  \end{table}
 
@@
 
-  ok
+  Our equivalent-axis decomposition returns a spheroidal component accounting for 95\% of the total light,
+  and an embedded disk accounting for the remaining 5\%.
+  In passing, we note that the bulge-disk decomposition performed by \citet{rusli2011} on NGC 1332 
+  is significantly different from our best-fit model.
+  \citet{rusli2011} did not identify an intermediate-scale embedded disk, 
+  but instead proposed a model featuring a S\'ersic bulge ($n_{\rm sph} \sim 2.3$, $R_{\rm e,sph} \sim 8''$), accounting for 43\% of the total light, 
+  and a large-scale exponential disk. 
+  This result led them to the conclusion that NGC 1332 is a disk dominated lenticular galaxy 
+  and is displaced from the $M_{\rm BH} - L_{\rm K,sph}$ (black hole mass vs. $K$-band spheroid luminosity) relation of \citet{marconihunt2003} 
+  by an order of magnitude along the $M_{\rm BH}$ direction.
+  Assuming instead that, as follows from our model, 
+  the galaxy spheroid is a factor of two more luminous than what claimed by \citet{rusli2011}, 
+  NGC 1332 would no longer be an outlier in our $M_{\rm BH} - L_{\rm sph}$ diagram. \\
 
@@
   \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1332.}
+  \caption{Best-fit model and isophotal parameters for NGC 1332.
+  NGC 1332 is an edge-on elliptical/lenticular galaxy. 
+  Given its large stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
+  The ellipticity profile proves the presence of an intermediate-scale disk. 
+  Given the edge-on inclination of such disk, we model it with a low-$n$ S\'ersic profile. 
+  The data within the innermost $6''.1$ are excluded from the fit.
+  }
   \end{center}

### 2015-06-10 papers/MbhMsph/mm.tex
arcetri wed

@@
 \usepackage{color}
+\usepackage{hyperref}
 
@@
 
-\shorttitle{Early and late $M_{\rm BH} - M_{\rm *,sph}$ sequence}
+%\shorttitle{Early and late $M_{\rm BH} - M_{\rm *,sph}$ sequence}
+\shorttitle{Red and blue $M_{\rm BH} - M_{\rm *,sph}$ sequence}
+
 \shortauthors{Savorgnan et al.}
@@
 
-\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
+%\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
+\title{Supermassive black hole and host bulge affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
 
@@
 consistent with a dry-merging formation scenario,
-and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
+and define a tight %\emph{early-type sequence} 
+\emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
 and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$.
-At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper \emph{late-type sequence}, 
+At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper %\emph{late-type sequence}, 
+\emph{blue sequence}, 
 with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
@@
 are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
-and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
+and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies 
+(most elliptical galaxies contain disks, i.e.~$L_{\rm sph} \neq L_{\rm gal}$) --
 once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
@@
 %and a more detailed analysis will be presented in Graham et al. (2015, \emph{in preparation}).  \\
-Here we investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
+Here we investigate in more detail %substructure in 
+the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
 using state-of-the-art galaxy decompositions (Savorgnan \& Graham 2015, hereafter \emph{Paper I}) 
@@
 or large-scale disks that encase the bulge and dominate the light at large radii). 
+It is worth stressing that, contrary to common knowledge, the majority of ``elliptical'' galaxies contain disks,
+i.e.~they are not single-component spheroidal systems.
 \emph{Paper I} presents the dataset used here, 
@@
 the radial extent of the surface brightness profile and one's sampling of this. 
-Most of these factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters. 
+Most of these factors are not included in popular 2D fitting codes which report only the {\bf statistical} errors associated with their fitted parameters. 
 In fact, when performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well spatially resolved -- galaxies, 
@@
 smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
-we tested the robustness of our conclusion by increasing the uncertainties associated with the galaxy absolute magnitudes 
+we tested the robustness of our conclusion by increasing the uncertainties associated with the galaxy absolute magnitudes\footnote{The 
+value of the intrinsic scatter obviously depends also on the size of the uncertainties associated with the black hole masses. 
+However, black hole masses and their uncertainties have been estimated by various authors using different methods, 
+thus we have limited to no control on their values.}  
 (we originally assumed $0.25\rm~mag$).
@@
 Hence, we conclude that our determination of the relative intrinsic scatter is reliable, 
-and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late-type) galaxies.
+and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies\footnote{The majority 
+of our early-type galaxies are elliptical galaxies, some of which have a bulge-to-total ratio close to 1 ($L_{\rm gal} \simeq L_{\rm sph}$).
+One might wonder whether this constitutes a bias in our analysis.
+However, we checked that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ 
+not only for early-type (elliptical + lenticular) galaxies, 
+but also for lenticular galaxies only. }, 
+but not for all (early+late-type) galaxies.
 %We decided to vary only the errors associated to $L_{\rm gal}$ 
@@
 
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
+\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
+Symbols have the same meaning as in Figure \ref{fig:mbhmaggal}.
+The red dashed line indicates the BCES bisector linear regression for the spheroidal component of the 45 early-type (E+S0) galaxies, 
+with the red shaded area denoting its $1\sigma$ uncertainty. 
+The blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
+with the blue shaded area denoting its $1\sigma$ uncertainty. 
+The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for the core-S\'ersic and S\'ersic spheroids, respectively.}
+\label{fig:mbhmagsph}
+\end{center}
+\end{figure}
+
 \begin{table*}
@@
  All (62)               & BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
+                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
+                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\ [0.5em]
                         & BCES $(X|Y)$   & $8.26 \pm 0.12$ & $-1.01 \pm 0.15$ & $-24.78$ & $-$ & $0.92$ \\
+                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
+                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\ [0.5em]
                         & BCES Bisector  & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
-                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
-                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
                         & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
-                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\
-                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\
                         & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.15$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]
@@
  Early-type (E+S0) (45) & BCES $(Y|X)$   & $8.56 \pm 0.07$ & $-0.44 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
+                        & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
+                        & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\ [0.5em]
                         & BCES $(X|Y)$   & $8.56 \pm 0.08$ & $-0.64 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
+                        & mFITEXY $(X|Y)$  & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.07}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
+                        & {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\ [0.5em]
                         & BCES Bisector  & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
-                        & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
-                        & mFITEXY $(X|Y)$  & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.07}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
                         & mFITEXY Bisector & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
-                        & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\
-                        & {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\
-                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.10$ & $-24.88$ & $-$    & $0.47$ \\
+                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.10$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
-\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
-Symbols have the same meaning as in Figure \ref{fig:mbhmaggal}.
-The red dashed line indicates the BCES bisector linear regression for the spheroidal component of the 45 early-type (E+S0) galaxies, 
-with the red shaded area denoting its $1\sigma$ uncertainty. 
-The blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
-with the blue shaded area denoting its $1\sigma$ uncertainty. 
-The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for the core-S\'ersic and S\'ersic spheroids, respectively.}
-\label{fig:mbhmagsph}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
 \includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
-\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
+\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude (as in Figure \ref{fig:mbhmagsph}). 
 Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
@@
 All (66)               & BCES $(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
+                       & mFITEXY $(Y|X)$    & $8.17^{+0.06}_{-0.07}$ & $-0.43^{+0.03}_{-0.04}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
+                       & {\tt linmix\_err} $(Y|X)$     & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\ [0.5em]
                        & BCES $(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
+                       & mFITEXY $(X|Y)$    & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.68$ \\
+                       & {\tt linmix\_err} $(X|Y)$     & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\ [0.5em]
                        & BCES Bisector  & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
-                       & mFITEXY $(Y|X)$    & $8.17^{+0.06}_{-0.07}$ & $-0.43^{+0.03}_{-0.04}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
-                       & mFITEXY $(X|Y)$    & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.68$ \\
                        & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
-                       & {\tt linmix\_err} $(Y|X)$     & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\
-                       & {\tt linmix\_err} $(X|Y)$     & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\
                        & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.09$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]
@@
 $n>2$ (43)             & BCES $(Y|X)$      & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
+                       & mFITEXY $(Y|X)$    & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
+                       & {\tt linmix\_err} $(Y|X)$     & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\ [0.5em]
                        & BCES $(X|Y)$      & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
+                       & mFITEXY $(X|Y)$    & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
+                       & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\ [0.5em]
                        & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
-                       & mFITEXY $(Y|X)$    & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
-                       & mFITEXY $(X|Y)$    & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
                        & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
-                       & {\tt linmix\_err} $(Y|X)$     & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\
-                       & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\
                        & {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.48 \pm 0.10$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]
@@
 Core-S\'ersic (22) & BCES $(Y|X)$   & $9.06 \pm 0.09$ & $-0.32 \pm 0.11$  & $-25.73$ & $-$    & $0.42$ \\
+                   & mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.09}$ & $-0.26^{+0.08}_{-0.07}$ & $-25.73$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
+                   & {\tt linmix\_err} $(Y|X)$  & $9.04 \pm 0.10$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\ [0.5em]
                    & BCES $(X|Y)$   & $9.06 \pm 0.12$ & $-0.65 \pm 0.12$  & $-25.73$ & $-$    & $0.61$ \\
+                   & mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $-0.72^{+0.17}_{-0.31}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.68$ \\
+                   & {\tt linmix\_err} $(X|Y)$  & $9.03 \pm 0.17$ & $-0.69 \pm 0.27$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\ [0.5em]
                    & BCES Bisector  & $9.06 \pm 0.10$ & $-0.47 \pm 0.08$  & $-25.73$ & $-$    & $0.48$ \\
-                   & mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.09}$ & $-0.26^{+0.08}_{-0.07}$ & $-25.73$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
-                   & mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $-0.72^{+0.17}_{-0.31}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.68$ \\
                    & mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $-0.47^{+0.12}_{-0.17}$ & $-25.73$ & $-$    & $0.48$ \\
-                   & {\tt linmix\_err} $(Y|X)$  & $9.04 \pm 0.10$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\
-                   & {\tt linmix\_err} $(X|Y)$  & $9.03 \pm 0.17$ & $-0.69 \pm 0.27$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\
                    & {\tt linmix\_err} Bisector & $9.04 \pm 0.14$ & $-0.44 \pm 0.16$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]
@@
 S\'ersic (44) & BCES $(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
+              & mFITEXY $(Y|X)$   & $7.72^{+0.08}_{-0.09}$ & $-0.41^{+0.07}_{-0.08}$ & $-22.92$ & $0.54^{+0.08}_{-0.07}$ & $0.61$ \\
+              & {\tt linmix\_err} $(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\ [0.5em]
               & BCES $(X|Y)$   & $7.71 \pm 0.14$ & $-0.86 \pm 0.16$ & $-22.92$ & $-$    & $0.93$ \\
+              & mFITEXY $(X|Y)$   & $7.72^{+0.14}_{-0.13}$ & $-0.86^{+0.13}_{-0.19}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
+              & {\tt linmix\_err} $(X|Y)$  & $7.73 \pm 0.14$ & $-0.86 \pm 0.17$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\ [0.5em]
               & BCES Bisector  & $7.71 \pm 0.10$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
-              & mFITEXY $(Y|X)$   & $7.72^{+0.08}_{-0.09}$ & $-0.41^{+0.07}_{-0.08}$ & $-22.92$ & $0.54^{+0.08}_{-0.07}$ & $0.61$ \\
-              & mFITEXY $(X|Y)$   & $7.72^{+0.14}_{-0.13}$ & $-0.86^{+0.13}_{-0.19}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
               & mFITEXY Bisector  & $7.72^{+0.11}_{-0.11}$ & $-0.61^{+0.10}_{-0.12}$ & $-22.92$ & $-$                    & $0.71$ \\
-              & {\tt linmix\_err} $(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\
-              & {\tt linmix\_err} $(X|Y)$  & $7.73 \pm 0.14$ & $-0.86 \pm 0.17$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\
               & {\tt linmix\_err} Bisector & $7.73 \pm 0.12$ & $-0.62 \pm 0.15$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
@@
 {\bf Early-type (E+S0)} (45) & BCES $(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
+                             & mFITEXY $(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40^{+0.06}_{-0.05}$ & $0.46$ \\
+                             & {\tt linmix\_err} $(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.41 \pm 0.06$ & $0.46$ \\ [0.5em]
                              & BCES $(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
+                             & mFITEXY $(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $0.49^{+0.08}_{-0.06}$ & $0.57$\\
+                             & {\tt linmix\_err} $(X|Y)$  & $8.55 \pm 0.09$ & $-0.48 \pm 0.06$ & $-24.47$ & $0.51 \pm 0.10$ & $0.56$ \\ [0.5em]
                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
-                             & mFITEXY $(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40^{+0.06}_{-0.05}$ & $0.46$ \\
-                             & mFITEXY $(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $0.49^{+0.08}_{-0.06}$ & $0.57$\\
                              & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
-                             & {\tt linmix\_err} $(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.41 \pm 0.06$ & $0.46$ \\
-                             & {\tt linmix\_err} $(X|Y)$  & $8.55 \pm 0.09$ & $-0.48 \pm 0.06$ & $-24.47$ & $0.51 \pm 0.10$ & $0.56$ \\
                              & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.09$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]
@@
 {\bf Late-type (Sp)} (17) & BCES $(Y|X)$    & $7.18 \pm 0.16$ & $-0.79 \pm 0.43$ & $-22.33$ & $-$    & $0.70$ \\
+                          & mFITEXY $(Y|X)$    & $7.20^{+0.15}_{-0.15}$ & $-0.53^{+0.22}_{-0.24}$ & $-22.33$ & $0.55^{+0.15}_{-0.10}$ & $0.63$ \\
+                          & {\tt linmix\_err} $(Y|X)$  & $7.24 \pm 0.19$ & $-0.46 \pm 0.32$ & $-22.33$ & $0.63 \pm 0.16$ & $0.62$ \\ [0.5em]
                           & BCES $(X|Y)$    & $7.18 \pm 0.29$ & $-1.71 \pm 0.71$ & $-22.33$ & $-$    & $1.26$ \\
+                          & mFITEXY $(X|Y)$    & $7.38^{+0.54}_{-0.36}$ & $-2.02^{+0.71}_{-2.13}$ & $-22.33$ & $1.09^{+0.41}_{-0.24}$ & $1.50$ \\
+                          & {\tt linmix\_err} $(X|Y)$  & $7.34 \pm 0.43$ & $-1.93 \pm 1.30$ & $-22.33$ & $1.31 \pm 0.97$ & $1.43$ \\ [0.5em]
                           & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.20}$ & $\boldsymbol{-1.15 \pm 0.27}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
-                          & mFITEXY $(Y|X)$    & $7.20^{+0.15}_{-0.15}$ & $-0.53^{+0.22}_{-0.24}$ & $-22.33$ & $0.55^{+0.15}_{-0.10}$ & $0.63$ \\
-                          & mFITEXY $(X|Y)$    & $7.38^{+0.54}_{-0.36}$ & $-2.02^{+0.71}_{-2.13}$ & $-22.33$ & $1.09^{+0.41}_{-0.24}$ & $1.50$ \\
                           & mFITEXY Bisector   & $7.26^{+0.40}_{-0.28}$ & $-1.03^{+0.33}_{-0.52}$ & $-22.33$ & $-$    & $0.82$ \\
-                          & {\tt linmix\_err} $(Y|X)$  & $7.24 \pm 0.19$ & $-0.46 \pm 0.32$ & $-22.33$ & $0.63 \pm 0.16$ & $0.62$ \\
-                          & {\tt linmix\_err} $(X|Y)$  & $7.34 \pm 0.43$ & $-1.93 \pm 1.30$ & $-22.33$ & $1.31 \pm 0.97$ & $1.43$ \\
-                          & {\tt linmix\_err} Bisector & $7.27 \pm 0.33$ & $-0.96 \pm 0.50$ & $-22.33$ & $-$    & $0.78$ \\
+                          & {\tt linmix\_err} Bisector & $7.27 \pm 0.33$ & $-0.96 \pm 0.50$ & $-22.33$ & $-$    & $0.78$ \\ [0.5em]
 
@@
 slope $= 2.28^{+1.67}_{-1.01}$.
-The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
+%The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
 More data would be welcome to better constrain the slope of this \emph{late-type sequence}, 
@@
       following a quadratic/cubic $M_{\rm BH} - M_{\rm *,sph}$ relation. 
-      For analogy with the color-magnitude diagram, 
-      it may be tempting to refer to our \emph{early-type sequence} as a \emph{red sequence} 
+      Unsurprisingly, in a color-magnitude diagram\footnote{Total $B-V$ colors, 
+      corrected for inclination, Galactic extinction and K-correction, 
+      were taken from the HyperLEDA online database \citep{hyperleda}.}, 
+      our early- and late-type galaxies occupy the two distinct regions of the red sequence and the blue cloud, respectively. 
+      For analogy with this, we refer to our \emph{early-type sequence} as a \emph{red sequence} 
       and to our \emph{late-type sequence} as a \emph{blue sequence}. 
-      Future work will explore the color of spheroids and galaxies in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.  
+      %For analogy with the color-magnitude diagram, 
+      %it may be tempting to refer to our \emph{early-type sequence} as a \emph{red sequence} 
+      %and to our \emph{late-type sequence} as a \emph{blue sequence}.
+      %Future work will explore the color of spheroids and galaxies in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.  
 \item The $M_{\rm BH}/M_{\rm *,sph}$ ratio for the early-type galaxies is $0.68 \pm 0.04\%$. 
@@
  Core-S\'ersic (22)     & BCES $(Y|X)$      & $9.06 \pm 0.09$ & $0.86 \pm 0.28$ & $11.28$ & $-$ & $0.42$ \\
+ 			& mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.08}$ & $0.68^{+0.21}_{-0.20}$ & $11.28$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
+  			& {\tt linmix\_err} $(Y|X)$     & $9.04 \pm 0.10$ & $0.64 \pm 0.25$ & $11.28$ & $0.40 \pm 0.09$ & $0.42$ \\ [0.5em]
 			& BCES $(X|Y)$      & $9.06 \pm 0.12$ & $1.70 \pm 0.32$ & $11.28$ & $-$ & $0.61$ \\
+ 			& mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $1.90^{+0.85}_{-0.46}$ & $11.28$ & $0.62^{+0.13}_{-0.10}$ & $0.68$ \\
+ 			& {\tt linmix\_err} $(X|Y)$     & $9.03 \pm 0.17$ & $1.80 \pm 0.70$ & $11.28$ & $0.67 \pm 0.30$ & $0.65$ \\ [0.5em]
  			& BCES Bisector     & $9.06 \pm 0.10$ & $1.19 \pm 0.23$ & $11.28$ & $-$ & $0.47$ \\
- 			& FITEXY $(Y|X)$    & $9.06^{+0.08}_{-0.08}$ & $0.68^{+0.21}_{-0.20}$ & $11.28$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
- 			& FITEXY $(X|Y)$    & $9.03^{+0.15}_{-0.16}$ & $1.90^{+0.85}_{-0.46}$ & $11.28$ & $0.62^{+0.13}_{-0.10}$ & $0.68$ \\
- 			& FITEXY Bisector   & $9.05^{+0.12}_{-0.13}$ & $1.12^{+0.35}_{-0.27}$ & $11.28$ & $-$                    & $0.46$ \\
- 			& {\tt linmix\_err} $(Y|X)$     & $9.04 \pm 0.10$ & $0.64 \pm 0.25$ & $11.28$ & $0.40 \pm 0.09$ & $0.42$ \\
- 			& {\tt linmix\_err} $(X|Y)$     & $9.03 \pm 0.17$ & $1.80 \pm 0.70$ & $11.28$ & $0.67 \pm 0.30$ & $0.65$ \\
- 			& {\tt linmix\_err} Bisector	& $9.04 \pm 0.14$ & $1.06 \pm 0.35$ & $11.28$ & $-$	& $0.45$ \\
+ 			& mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $1.12^{+0.35}_{-0.27}$ & $11.28$ & $-$                    & $0.46$ \\
+ 			& {\tt linmix\_err} Bisector	& $9.04 \pm 0.14$ & $1.06 \pm 0.35$ & $11.28$ & $-$	& $0.45$ \\ [0.5em]
 
  S\'ersic (44)		& BCES $(Y|X)$      & $7.71 \pm 0.09$ & $0.95 \pm 0.21$ & $10.25$ & $-$ & $0.64$ \\
+ 			& mFITEXY $(Y|X)$   & $7.72^{+0.10}_{-0.09}$ & $0.96^{+0.21}_{-0.21}$ & $10.25$ & $0.58^{+0.09}_{-0.07}$ & $0.64$ \\
+ 			& {\tt linmix\_err} $(Y|X)$     & $7.73 \pm 0.10$ & $0.98 \pm 0.24$ & $10.25$ & $0.59 \pm 0.08$ & $0.65$ \\ [0.5em]
  			& BCES $(X|Y)$      & $7.71 \pm 0.16$ & $2.52 \pm 0.54$ & $10.25$ & $-$ & $1.11$ \\
+ 			& mFITEXY $(X|Y)$   & $7.72^{+0.16}_{-0.16}$ & $2.49^{+0.69}_{-0.45}$ & $10.25$ & $0.93^{+0.15}_{-0.13}$ & $1.10$ \\
+ 			& {\tt linmix\_err} $(X|Y)$     & $7.73 \pm 0.17$ & $2.48 \pm 0.59$ & $10.25$ & $0.95 \pm 0.27$ & $1.10$ \\ [0.5em]
  			& BCES Bisector     & $7.71 \pm 0.11$ & $1.48 \pm 0.20$ & $10.25$ & $-$ & $0.74$ \\
- 			& FITEXY $(Y|X)$    & $7.72^{+0.10}_{-0.09}$ & $0.96^{+0.21}_{-0.21}$ & $10.25$ & $0.58^{+0.09}_{-0.07}$ & $0.64$ \\
- 			& FITEXY $(X|Y)$    & $7.72^{+0.16}_{-0.16}$ & $2.49^{+0.69}_{-0.45}$ & $10.25$ & $0.93^{+0.15}_{-0.13}$ & $1.10$ \\
- 			& FITEXY Bisector   & $7.72^{+0.13}_{-0.13}$ & $1.49^{+0.33}_{-0.28}$ & $10.25$ & $-$    & $0.74$ \\
- 			& {\tt linmix\_err} $(Y|X)$     & $7.73 \pm 0.10$ & $0.98 \pm 0.24$ & $10.25$ & $0.59 \pm 0.08$ & $0.65$ \\
- 			& {\tt linmix\_err} $(X|Y)$     & $7.73 \pm 0.17$ & $2.48 \pm 0.59$ & $10.25$ & $0.95 \pm 0.27$ & $1.10$ \\
- 			& {\tt linmix\_err} Bisector	& $7.73 \pm 0.14$ & $1.49 \pm 0.57$ & $10.25$ & $-$	& $0.74$ \\
+ 			& mFITEXY Bisector  & $7.72^{+0.13}_{-0.13}$ & $1.49^{+0.33}_{-0.28}$ & $10.25$ & $-$    & $0.74$ \\
+ 			& {\tt linmix\_err} Bisector	& $7.73 \pm 0.14$ & $1.49 \pm 0.57$ & $10.25$ & $-$	& $0.74$ \\ [0.5em]
 
 {\bf Early-type (E+S0)} (45)  & BCES $(Y|X)$       & $8.56 \pm 0.07$ & $0.85 \pm 0.12$ & $10.81$ & $-$ & $0.48$ \\
+                              & mFITEXY $(Y|X)$     & $8.56^{+0.06}_{-0.07}$ & $0.83^{+0.11}_{-0.11}$ & $10.81$ & $0.42^{+0.07}_{-0.05}$ & $0.48$ \\
+                              & {\tt linmix\_err} $(Y|X)$     & $8.55 \pm 0.07$ & $0.82 \pm 0.12$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\ [0.5em]
                               & BCES $(X|Y)$       & $8.56 \pm 0.09$ & $1.27 \pm 0.13$ & $10.81$ & $-$ & $0.59$ \\
+                              & mFITEXY $(X|Y)$     & $8.54^{+0.08}_{-0.09}$ & $1.32^{+0.18}_{-0.15}$ & $10.81$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
+                              & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $1.29 \pm 0.17$ & $10.81$ & $0.54 \pm 0.11$ & $0.59$ \\ [0.5em]
                               & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.04 \pm 0.10}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
-                              & mFITEXY $(Y|X)$     & $8.56^{+0.06}_{-0.07}$ & $0.83^{+0.11}_{-0.11}$ & $10.81$ & $0.42^{+0.07}_{-0.05}$ & $0.48$ \\
-                              & mFITEXY $(X|Y)$     & $8.54^{+0.08}_{-0.09}$ & $1.32^{+0.18}_{-0.15}$ & $10.81$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
                               & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.05^{+0.14}_{-0.12}$ & $10.81$ & $-$                    & $0.51$ \\
-                              & {\tt linmix\_err} $(Y|X)$     & $8.55 \pm 0.07$ & $0.82 \pm 0.12$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\
-                              & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $1.29 \pm 0.17$ & $10.81$ & $0.54 \pm 0.11$ & $0.59$ \\
                               & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $1.03 \pm 0.19$ & $10.81$ & $-$    & $0.51$ \\ [0.5em]
@@
 {\bf Late-type (Sp)} (17)    & BCES $(Y|X)$    & $7.18 \pm 0.17$ & $1.95 \pm 1.52$ & $10.05$ & $-$ & $0.74$ \\ 
+                             & mFITEXY $(Y|X)$     & $7.20^{+0.15}_{-0.16}$ & $1.22^{+0.70}_{-0.62}$  & $10.05$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
+                             & {\tt linmix\_err} $(Y|X)$  & $7.23 \pm 0.19$ & $0.96 \pm 0.96$ & $10.05$ & $0.67 \pm 0.16$ & $0.65$ \\ [0.5em]
                              & BCES $(X|Y)$    & $7.18 \pm 0.39$ & $5.89 \pm 3.40$ & $10.05$ & $-$ & $1.70$ \\
+                             & mFITEXY $(X|Y)$     & $7.44^{+1.45}_{-0.52}$ & $7.14^{+26.31}_{-3.01}$ & $10.05$ & $1.49^{+0.56}_{-0.36}$ & $2.08$ \\
+                             & {\tt linmix\_err} $(X|Y)$  & $7.42 \pm 0.64$ & $6.96 \pm 6.73$ & $10.05$ & $1.83 \pm 1.86$ & $2.03$ \\ [0.5em]
                              & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.21}$ & $\boldsymbol{3.00 \pm 1.30}$ & $\boldsymbol{10.05}$ & $-$ & $\boldsymbol{0.94}$ \\
-                             & mFITEXY $(Y|X)$     & $7.20^{+0.15}_{-0.16}$ & $1.22^{+0.70}_{-0.62}$  & $10.05$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
-                             & mFITEXY $(X|Y)$     & $7.44^{+1.45}_{-0.52}$ & $7.14^{+26.31}_{-3.01}$ & $10.05$ & $1.49^{+0.56}_{-0.36}$ & $2.08$ \\
                              & {\bf mFITEXY Bisector}    & $\boldsymbol{7.24^{+1.04}_{-0.39}}$ & $\boldsymbol{2.28^{+1.67}_{-1.01}}$  & $\boldsymbol{10.05}$ & $-$    & $\boldsymbol{0.79}$ \\
-                             & {\tt linmix\_err} $(Y|X)$  & $7.23 \pm 0.19$ & $0.96 \pm 0.96$ & $10.05$ & $0.67 \pm 0.16$ & $0.65$ \\
-                             & {\tt linmix\_err} $(X|Y)$  & $7.42 \pm 0.64$ & $6.96 \pm 6.73$ & $10.05$ & $1.83 \pm 1.86$ & $2.03$ \\
-                             & {\tt linmix\_err} Bisector & $7.26 \pm 0.47$ & $1.94 \pm 216.38$ & $10.05$ & $-$    & $0.74$ \\
+                             & {\tt linmix\_err} Bisector & $7.26 \pm 0.47$ & $1.94 \pm 216.38$ & $10.05$ & $-$    & $0.74$ \\ [0.5em]
 
@@
 under contract with the National Aeronautics and Space Administration. 
+We acknowledge the usage of the HyperLeda database (\url{http://leda.univ-lyon1.fr}).
 The BCES routine \citep{akritasbershady1996} was run via the python module 
-written by Rodrigo Nemmen \citep{nemmen2012}, which is available at {\url https://github.com/rsnemmen/BCES}.
+written by Rodrigo Nemmen \citep{nemmen2012}, which is available at \url{https://github.com/rsnemmen/BCES}.
 

### 2015-06-10 papers/data_paper/datapaper.tex
arcetri wed

@@
   \caption{Best-fit model and isophotal parameters for NGC 3377.
-  NGC 3377 is an elliptical/lenticular galaxy with an intermediate-scale disk and a nuclear stellar disk. 
-  }
-  \end{center}
-  \end{figure}
-
-  \begin{table}[h]
-  \small
-  \caption{Best-fit parameters for the spheroidal component of NGC 3384.}
+  NGC 3377 is an elliptical/lenticular galaxy with an intermediate-scale disk and a nuclear stellar disk \citep{ledo2010}. 
+  For this galaxy, \citet{arnold2014} reported a strong decline in local specific angular momentum beyond $\sim 35''$, 
+  with a disk-to-bulge transition occurring at about $R_{\rm maj} \sim 50''$.
+  \citet{arnold2014} attempted a three-component decomposition (accounting for a bulge, an embedded disk and a central cusp), 
+  but unfortunately they fit the spheroidal component with a limited two-parameter $R^{1/4}$ profile 
+  rather than a three-parameter $R^{1/n}$ S\'ersic function.
+  Here we use a surface brightness profile twice as extended as that used by \citet{arnold2014} 
+  and we identify a nuclear disk and an intermediate-scale disk, both embedded in a larger spheroidal component.
+  The presence of an intermediate-scale disk is evident from the unsharp mask of the image mosaic 
+  and also from the ellipticity profile, which increases with increasing radius until $R_{\rm maj} \sim 45''$ 
+  and then drops at larger radii.
+  The nuclear stellar disk can be spotted from the peak at $R_{\rm maj} \sim 5''$ in the $B4$ profile.
+  Each of the two disks is modelled with an exponential profile. 
+  }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of NGC 3377.}
   \begin{center}
@@
   \end{center}
-  \label{tab:n3384}
-  \end{table}
-
-  The morphology of NGC3377 is similar to NGC0821. 
-  The unsharp mask reveals an embedded disc and the extended velocity field confirms that 
-  it is not a large-scale disc. 
-  The residual image from a 2D single S\'ersic fit diplays the unsubtracted embedded disc
-  and an additional nuclear ($\lesssim 10''$) component.
-  The embedded disc is very close to edge-on.
-  In the 2D fit we adopt a S\'ersic + edge-on disc model, after masking the third nuclear component. 
-  In the 1D fit we are not able to model the embedded disc with an exponential function, 
-  probably because of the orientation of the disc. 
-  The best results are obtained when a Ferrer function is employed. 
-  We tried to model the nuclear cusp with a PSF or a gaussian function. The gaussian function parameters
-  resulted highly degenerate with the Ferrer function parameters, leading us to prefer a PSF profile. \\
+  \label{tab:n3377}
+  \end{table}
 

### 2015-06-10 python_codes/PCA/pca.py

@@ -1,0 +1,98 @@
+import sqlite3 as sql3
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+import matplotlib.colors as mcolors
+from scipy import stats
+#from instruments.linear_regression import bces
+#from instruments.linear_regression import predband
+#from instruments.linear_regression import fitexy
+from instruments import b_n
+#from instruments.linear_regression import colorline
+
+
+from matplotlib import rc
+rc('font',**{'family':'sans-serif','sans-serif':['CenturyGothic']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+rc('text', usetex=True)
+
+
+matplotlib.rcParams.update({'font.size': 12})
+
+dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_vivisection.db'
+
+# get data
+connection = sql3.connect(dbname)
+cur = connection.cursor()
+
+getdata_query = 'SELECT anc.gal_id, anc.simplemorphtype, anc.core, anc.bar, \
+	anc.mass_BH, anc.perr_mass_BH, anc.merr_mass_BH, anc.sigma, \
+	physres.mag_sph_eq_moffat_comb, physres.mag_tot_eq_moffat_comb, \
+	physres.log_n_maj_moffat_comb, physres.log_n_eq_moffat_comb, \
+	physres.mu_e_maj_moffat_comb, physres.mu_e_eq_moffat_comb, \
+	physres.log_r_e_maj_moffat_comb, physres.log_r_e_eq_moffat_comb \
+	FROM Ancillary AS anc \
+	JOIN OneDFitResultsPhysicalUnits AS physres ON anc.gal_id = physres.gal_id \
+	WHERE anc.fit1D_done = 1;'
+
+cur.execute(getdata_query)
+datalist = cur.fetchall()
+data= np.asarray(datalist).transpose()
+#print data
+gal_id = data[0]
+simplemorphtype = data[1]
+core = data[2].astype(np.int)
+bar = data[3].astype(np.int)
+
+mbh = data[4].astype(np.float)
+log_mbh = np.log10(mbh)
+
[…]

### 2015-06-10 python_codes/paper_figures/MbhMsph/figures.py

@@ -2335,8 +2335,8 @@ def mbh_vs_mass_sph_galsymb_agn():
 		
 		
 def main():
-	#mag_lit_vs_mag_my()
-	mbh_vs_mass_sph_agn()
+	mag_lit_vs_mag_my()
+	#mbh_vs_mass_sph_agn()
 	#mbh_vs_mass_sph()
 	#mbh_vs_mag_sph_psb()
 	#inset_psb()

### 2015-06-16 papers/data_paper/datapaper.tex
martedi arcetri

@@
 
-  OK
-
   \begin{figure}[h]
@@
   \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M104.}
-  \end{center}
-  \end{figure}
+  \caption{Best-fit model and isophotal parameters for M104.
+  }
+  \end{center}
+  \end{figure}
+
+  \begin{table}[h]
+  \small
+  \caption{Best-fit parameters for the spheroidal component of M104.}
+  \begin{center}
+  \begin{tabular}{llcc}
+  \hline
+  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
+    &  &  $[\rm arcsec]$ & \\
+  \hline
+  T.W. 1D maj. & S-bul + e-d + G-r + m-c  & $11.1$  &  $5.4$ \\
+  T.W. 1D eq.  & S-bul + e-d + G-r + m-c  & $52.5$  &  $7.1$ \\
+  \hline
+  S+11         & S-bul + e-d + G-bar + G-n  & $66.1$  &  $1.5$ \\
+  \hline
+  \end{tabular}
+  \end{center}
+  \label{tab:m104}
+  \tablecomments{The bulge S\'ersic index obtained by S+11 is smaller than our estimates because 
+  they fit a nuclear component. }
+  \end{table}
 
@@
   \label{tab:n3377}
+  \tablecomments{L+14 obtained the smallest estimate of the effective radius because they oversubtracted a halo.   
+  }
   \end{table}

### 2015-06-16 python_codes/PCA/pca.py

@@ -1,98 +1,0 @@
-import sqlite3 as sql3
-import os
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib
-import matplotlib.colors as mcolors
-from scipy import stats
-#from instruments.linear_regression import bces
-#from instruments.linear_regression import predband
-#from instruments.linear_regression import fitexy
-from instruments import b_n
-#from instruments.linear_regression import colorline
-
-
-from matplotlib import rc
-rc('font',**{'family':'sans-serif','sans-serif':['CenturyGothic']})
-## for Palatino and other serif fonts use:
-#rc('font',**{'family':'serif','serif':['Palatino']})
-rc('text', usetex=True)
-
-
-matplotlib.rcParams.update({'font.size': 12})
-
-dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_vivisection.db'
-
-# get data
-connection = sql3.connect(dbname)
-cur = connection.cursor()
-
-getdata_query = 'SELECT anc.gal_id, anc.simplemorphtype, anc.core, anc.bar, \
-	anc.mass_BH, anc.perr_mass_BH, anc.merr_mass_BH, anc.sigma, \
-	physres.mag_sph_eq_moffat_comb, physres.mag_tot_eq_moffat_comb, \
-	physres.log_n_maj_moffat_comb, physres.log_n_eq_moffat_comb, \
-	physres.mu_e_maj_moffat_comb, physres.mu_e_eq_moffat_comb, \
-	physres.log_r_e_maj_moffat_comb, physres.log_r_e_eq_moffat_comb \
-	FROM Ancillary AS anc \
-	JOIN OneDFitResultsPhysicalUnits AS physres ON anc.gal_id = physres.gal_id \
-	WHERE anc.fit1D_done = 1;'
-
-cur.execute(getdata_query)
-datalist = cur.fetchall()
-data= np.asarray(datalist).transpose()
-#print data
-gal_id = data[0]
-simplemorphtype = data[1]
-core = data[2].astype(np.int)
-bar = data[3].astype(np.int)
-
-mbh = data[4].astype(np.float)
-log_mbh = np.log10(mbh)
-
[…]

### 2015-06-28 papers/data_paper/datapaper.tex
cisiamo

@@
 
-\title{Supermassive black hole and host bulge affairs \\ I. True to life galaxy decomposition.}
+\title{Supermassive black hole and host bulge affairs \\ I. True to life, physically motivated galaxy decomposition.}
 
@@
 %\noindent
-\input{table_observations.tex}
+%\input{table_observations.tex}
 
@@
 Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
-all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs), 
-listed in Table \ref{tab:obs}.
+all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs). 
+%listed in Table \ref{tab:obs}.
 Each AOR is an individual Spitzer observation sequence, and
@@
 The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
-comes from the compilation of \citet{savorgnangraham2014},
+comes from the compilation of \citet{savorgnangraham2015},
 who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
@@
 Among the initial sample of 75 galaxies, we did not attempt to model 3 galaxies: M32, NGC 4486A and the Circinus Galaxy. 
-The first two... {\bf AL: can you write a short sentence about these 2 galaxies, that have uncertain morphology,
-because they have been stripped, blah blah, maybe put one reference? please and thank you.}
+The first two have been stripped by their massive companions, and thus have uncertain morphology. 
 The Circinus Galaxy lies at only 4 degrees from the Galactic Plane, 
@@
 \item One-dimensional and two-dimensional techniques of galaxy decomposition return the same results when applied to the same galaxy.
-However, in our practical experience, two-dimensional decompositions {\bf HOW DO YOU WRITE THIS IN ENGLISH?? fail twice as much as one-dimensional ones}, 
+However, in our practical experience, the failure rate of two-dimensional decompositions 
+is a factor of two higher than the failure rate of one-dimensional decompositions,  
 either because the fit does not converge or because the result is unphysical. 
@@
 
-{\bf Lasker's conclusions are: bulge+disk decompositions are not enough, we do better by adding bars, spiral arms and stuff (really?? what a surprising conclusion);
-we modelled the envelope of 5 galaxies; we observed central light deficits in 9 ellipticals; total magnitudes are independent from details of modelling (no, really?)
-and bulge magnitudes are 0.36 mag fainter when additional components (other than bulge and disk) are modelled.  }
+%{\bf Lasker's conclusions are: bulge+disk decompositions are not enough, we do better by adding bars, spiral arms and stuff (really?? what a surprising conclusion);
+%we modelled the envelope of 5 galaxies; we observed central light deficits in 9 ellipticals; total magnitudes are independent from details of modelling (no, really?)
+%and bulge magnitudes are 0.36 mag fainter when additional components (other than bulge and disk) are modelled.  }
 
@@
   \caption{Best-fit model and isophotal parameters for M104. 
+  M104 is a lenticular/spiral galaxy with a partially depleted core. 
+  The data within the innermost $6''.1$ are excluded from the fit, 
+  and the most obvious ring of the galaxy is modeled.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n1316_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1316.}
+  \caption{Best-fit model and isophotal parameters for NGC 1316. 
+  NGC 1316 is a merger. 
+  The galaxy is composed of a bulge, an elongated structure that can be identified with a bar, 
+  two obvious rings, an outer exponential disk or halo, and a bright nuclear component. }
   \end{center}
@@
   \label{tab:n1316}
+  \tablecomments{
+  S+11 overestimated the bulge effective radius and S\'ersic index because their model does not take into account the bar.
+  }
   \end{table}
@@
   \caption{Best-fit model and isophotal parameters for NGC 5128.
-  NGC 5128 is a merging system. }
+  NGC 5128 is a merging system. 
+  The data within $50'' \lesssim R_{\rm maj} \lesssim 200''$ is excluded from the fit.}
   \end{center}

### 2015-07-08 papers/lentiptical/lentiptical.tex
welcomeback

--- 2015-02-10 papers/mbhn/mbhn.tex
@@
 
-\documentclass[preprint2]{aastex}
+\documentclass[preprint2]{emulateapj}
 
@@
 \usepackage{bm}
-%%\graphicspath{{/Users/gsavorgnan/galaxy_vivisection/results/plots/}}
+\graphicspath{{/Users/gsavorgnan/galaxy_vivisection/papers/lentiptical/images/}}
 
@@
 
-\shorttitle{Mbh-n paper}
-\shortauthors{Savorgnan et al.}
+\shorttitle{Lentiptical galaxies}
+\shortauthors{Savorgnan \& Graham}
 
@@
 
-\title{Mbh-n paper}
+\title{Lentiptical galaxies and their ordinary black holes}
 
@@
 \begin{abstract}
-blah blah
+Lentiptical galaxies are an intermediate class of galaxies between elliptical  
+and lenticular galaxies.
+Lentipticals are early-type, bulge-dominated galaxies that feature a fast-rotating, 
+intermediate-scale disk of stars embedded within a slow-rotating spheroid of stars.
+Such spheroid dominates the light in the central region of the galaxy and also at large radii, 
+unlike lenticular galaxies, whose bulge is encased within a (more extended) large-scale disk. 
+Lentiptical galaxies have often been confused with lenticular galaxies and,
+consequently, their bulge luminosities have been largely underestimated. 
+This surprisingly common mistake has led to some wrong conclusions, 
+such as the claim that a number of lentiptical galaxies are extreme outliers 
+in the $M_{\rm BH} - M_{\rm *,sph}$ diagram, 
+i.e. these galaxies host a central black hole whose mass, $M_{\rm BH}$, is abnormally large 
+compared to expectations from their (underestimated) bulge stellar mass, $M_{\rm *,sph}$.
+
 \end{abstract}
@@
 
-%% From the front matter, we move on to the body of the paper.
-%% In the first two sections, notice the use of the natbib \citep
-%% and \citet commands to identify citations.  The citations are
-%% tied to the reference list via symbolic KEYs. The KEY corresponds
-%% to the KEY in the \bibitem in the reference list below. We have
-%% chosen the first three characters of the first author's name plus
-%% the last two numeral of the year of publication as our KEY for
-%% each reference.
-
-%% Authors who wish to have the most important objects in their paper
-%% linked in the electronic edition to a data center may do so by tagging
-%% their objects with \objectname{} or \object{}.  Each macro takes the
-%% object name as its required argument. The optional, square-bracket 
-%% argument should be used in cases where the data center identification
-%% differs from what is to be printed in the paper.  The text appearing 
-%% in curly braces is what will appear in print in the published paper. 
-%% If the object name is recognized by the data centers, it will be linked
-%% in the electronic edition to the object data available at the data centers  
-%%
-%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
-%% the brackets must be escaped with backslashes when used in the first
-%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
-%%  Otherwise, LaTeX will issue an error.
-
 \section{Introduction}
 
-%%A focal problem today in the dynamics of globular clusters is core collapse.
-%%It has been predicted by theory for decades \citep{hen61,lyn68,spi85}, but
-%%observation has been less alert to the phenomenon. For many years the
-%%central brightness peak in M15 \citep{kin75,new78} seemed a unique anomaly.
-%%Then \citet{aur82} suggested a central peak in \object{NGC 6397}, and a
-%%limited photographic survey of ours \citep[Paper I]{djo84} found three more
-%%cases, \objectname{NGC 6624}, \objectname[M 15]{NGC 7078}, and
-%%\object[Cl 1938-341]{Terzan 8}), whose sharp center had often been
-%%remarked on \citep{can78}.
-%%
-%%As an example of how the new AASTeX object tagging macros work, we will
-%%cite some of the ``Superlative'' objects mentioned in section 10 of
-%%Trimble's (1992) review of astrophysics in the year 1991.  The youngest
-%%star yet found was \object[\[JCC87\] IRAS 4]{IRAS 4} in \objectname{NGC 1333}.
-%%\object{70 Oph} was found to be the longest period spectroscopic binary.
-%%The most massive white dwarf was \object{GD 50}, estimated at 1.2 solar masses.
-%%The first neutral hydrogen found in a globular cluster was \object{NGC 2808}
-%%while the \objectname[SDSS J093401.92+551427.9]{I Zw 18} retained the
-%%record for metal deficiency.  However, another low metallicitity
-%%galaxy was \object{UGC 4483} in the \objectname{M 83} group. The
-%%largest redshift \object[PC 1247+3406]{source} in 1991 was found at
-%%z=4.897.  Lastly, what paper would be complete without a mention of the
-%%\object[M1]{Crab nebula}!
+There are currently two well-known types of stellar disks in galaxies. 
+The first are the large-scale disks (with sizes of a few kpc)  
+that dominate at large radii in spiral and lenticular galaxies; 
+the second are the small (tens to a couple of hundred parsec) nuclear disks 
+observed in both early- and late-type galaxies
+(e.g. \citealt{scorzavandenbosch1998,rest2001,balcells2007,ledo2010}).
+The origin of the nuclear disks has been speculated to arise 
+from the infall of small satellite galaxies or gas clouds {\bf refs}.  
+The origin, or at least the on-going feeding and growth, of the large-scale disks 
+has been attributed to cold gas flows, gas rich mergers and halo accretion events 
+(e.g. \citealt{khochfarsilk2006,dekel2009nat,dekel2009apj,ceverino2010,ceverino2012,conselice2012}).  
+A thorough review can be found in Combes (arXiv:1309.1603 and 1405.6405). \\
 
-\section{Errors}
+A puzzling question, which has been unspoken for decades, 
+is why are there not intermediate-sized disks; 
+why are there not accretion events which create disks larger than the typical nuclear disks 
+but which are not large enough to dominate at large radii? 
+Here we report on the existence of these intermediate-sized stellar disks. \\
 
-How do we compute the errors on the measured S\'ersic indices?
-Montecarlo, bootstrapping or any other evil statistical method do not take into account the systematics,
-which mainly depend on the decomposition model, i.e. the choice of the model components.
-But we are lucky, since there are many other decompositions in the literature for our galaxies.
-\cite{grahamdriver2007,laurikainen2010,sani2011,vika2012,beifiori2012,rusli2013,lasker2014data} have done this job.
-So how about we do something similar to our first paper?
-Let's say that I am not better than anybody else at decomposing galaxies 
-(this is obviously absurd, given my incredible competence in vivisecting galaxies, but let's assume it for now).
-I repeat the same game we did in our first paper.
-For each galaxy, I take all the available measurements from the literature, including my own measurement,
-and I compute the standard deviation of each set of measurements.
-The standard deviation becomes the error of my own measurement.
-When my measurement is the only available (nobody other than me ever decomposed that galaxy),
-the errors is set to be equal to the median value of the distribution in Figure \ref{fig:hist} 
-(almost the same we did in our first paper, see footnote 4).
-Figure \ref{fig:hist}: here only galaxies with more than one measurement are contributing.
-Take a galaxy, take its set of measurements (more than one!) of the S\'ersic index, 
-compute the standard deviation of that set, the standard deviation becomes the error on my own measurement
-(BTW, I am using the $n$ derived from the equivalent axis fit).
-The distribution of the standard deviations is represented by the histogram.
-The median value is $0.13$, which means a median uncertainty of $33\%$ on each individual measurement.
-If we take of each set of measurements the average, then the error associated to the average 
-and then the median value of all these errors, basically we are doing the same we did in footnote 4 of our first paper,
-and the cool thing is that now we get the same number we got then ($20\%$).
+The existence of such disks is not only important for our understanding of disk growth in general, 
+reducing or eliminating an old mystery, 
+but accounting for such structure will impact on our galaxy scaling relations 
+and surely see the reclassification of many ``disky'' elliptical galaxies 
+and lenticular galaxies as \emph{lentiptical} 
+galaxies with intermediate-sized stellar disks that do not dominate at large radii. \\
+
+It is well known to the astronomers that identifying a face-on, featureless stellar disk 
+in an early-type galaxy only by looking at the galaxy image 
+is a very challenging if not even impossible task. 
+Luckily, the majority of such disks are observed by us with some level of inclination, 
+which makes them appear as flat, elliptical components, 
+and helps us distinguishing them from the more spherical galaxy bulges. 
+A more subtle and overlooked issue is the difficulty in identifying the extent of these disks 
+with respect to their bulge.
+
+Kinematic maps, obtained from IFU spectroscopy, constitute an extremely powerful instrument to this purpose. 
+{\bf However, xxxSLUGGS have shown that the limited FOV of the atlas3d maps is not enough to get the full picture,
+and more extended maps are needed to reveal which galaxies display a FR behaviour all the way out 
+and which ones become SR at large radii.}
+Unfortunately, kinematic maps are not yet available for a large sample of galaxies in the local Universe. 
+Notwhithstanding, there is another powerful instrument that can help identify the extent of 
+stellar disks in early-type galaxies, 
+and that has the advantage of requiring only galaxy images (even photometrically uncalibrated), 
+which are cheaper to acquire in terms of telescope time than IFU observations. 
+This instrument is the ellipticity profile of a galaxy's isophotes, 
+that can be easily obtained from a 1D isophotal analysis of the galaxy image, 
+using for example the IRAF task {\tt ellipse}.
+
+The toy model shown in Figure \ref{fig:ellp} illustrates the typical ellipticity profile 
+for a large-scale disk that encases a bulge, as in lenticular (S0) galaxies, 
+for an intermediate-scale disk embedded in a larger spheroid, that we name lentiptical (E/S0) galaxy, 
+and for an elliptical (E) galaxy featuring a nuclear stellar disk. 
+Note that, in the case of an intermediate-scale disk, 
+the maximum of the ellipticity profile corresponds to the minimum difference between the 
+light profile of the bulge and that of the disk (vertical dashed line in Figure \ref{fig:ellp}). 
+Galaxy modellers that attempt to perform bulge/disk decomposition of lentiptical galaxies 
+should always check that their model correctly reproduces this important signature.
+
+The {\bf realization, coscienza, not-knowledge} that many ``elliptical'' galaxies 
+actually contain embedded stellar disks 
+dates back at least three decades 
+\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995,
+donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999} and, 
+more recently, intermediate-scale disks were all but unfamiliar to \cite{krajnovic2013}. 
+However, the class of lentiptical galaxies has been missed out by many galaxy modellers, 
+who labelled as ``unphysical'' the idea that an intermediate-sized stellar disk 
+can exist fully embedded in a larger spheroidal component. 
+This unspoken bias has led them to reject any bulge/disk decomposition with an outcome 
+similar to that illustrated in the middle panel of Figure \ref{fig:ellp}. 
+Unsurprisingly, some studies have found that the b/t ratio of S0s is less than...
+
+Examples of lentiptical galaxies are the galaxies MRK 1216, NGC 1271, NGC 1277, NGC 1332, NGC 3115, NGC 3377 
+(see Figure \ref{fig:n3377ex}) and NGC 4621. 
+All of these galaxies can be easily described and explained with a simple two-component model: 
+an outer S\'ersic bulge plus an embedded, intemediate-sized exponential\footnote{Given 
+its close-to-edge-on inclination,  
+the stellar disk of NGC 1332 is better described by a S\'ersic profile with S\'ersic index $n<1$ 
+\citep{pastrav2013a,pastrav2013b}.} disk. 
+Models that ``forzatamente'' describe the galaxy with an inner S\'ersic bulge 
+encased within a large-scale exponential disk can produce acceptable fits ???? statistically decent??
+only in two cases:
+either the data are shallow, thus they are not probing the re-rise of the bulge, 
+or an outer Sersic halo is added to the model to account for the outer light (n3115 and n3377 lasker).....
+
+show vel map? + ell profile, explain shape
+
+our models are physically motivated and produce bulge luminosities which make these galaxies no longer outliers
+btw they are not outliers on the M-Mgal relation, which suggests poor bulge/disk decomposition
+
+people that do only 2d decompositions, should still perform a 1d isophotal analysis to check extent of disk
 
 \begin{figure}
-\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/auxiliary/histo_err_logn.eps}
-\caption{}
-\label{fig:hist}
+\includegraphics[width=\columnwidth]{diskextent.eps}
+\caption{Illustration of the typical light profile (top plots) and ellipticity profile (bottom plots) of a galaxy 
+featuring a stellar disk with varying size. 
+For simplicity, we show separately the light profile of the bulge (or spheroid) in red 
+and that of the disk in blue. 
+The sum of these two contributions gives the galaxy's light profile (not represented here).
+The left panel shows the case of a large-scale disk, {\bf prototipico} of a barless lenticular galaxy. 
+The right panel displays the case of an elliptical galaxy with a nuclear stellar disk. 
+The middle panel presents the case of a lentiptical galaxy with an inermediate-sized disk. 
+Stellar disks typically have fixed ellipticity, dictated by their inclination to our line of sight.
+Bulges, instead, can have their ellipticities varying with radius,
+but they are usually rounder than inclined disks, 
+thus their average ellipticity is lower than that of an inclined disk.
+If the ellipticity profile of a galaxy increases with radius, 
+this can be ascribed to an inclined disk that becomes progressively more important over the bulge,
+whereas a radial decrease of ellipticity signifies the opposite case. 
+Therefore the ``shape'' of the ellipticity profile can be decisive to distiguish between 
+large- and intermediate-scale disks. 
+}
+\label{fig:ellp}
 \end{figure}
 
-\section{Results}
-
-Figure \ref{fig:mbhn}: Well, we now have the errors on each of OUR measurements of $n$.
-We can plot bh mass vs $n$ (in log).
-
 \begin{figure}
-\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/mbh_vs_logn.eps}
-\caption{}
-\label{fig:mbhn}
+\includegraphics[width=\columnwidth]{n3377ex.eps}
+\caption{
+}
+\label{fig:n3377ex}
 \end{figure}
 
-Figure \ref{fig:mbhavn}: Almost the same we did in our first paper. We take for each galaxy its set of measurements of $n$,
-we reject measurements in disagreement for more than $50\%$,
-we compute the median (not the average! this is different from what we did in the past, what do you think?) 
-and the error associated to the mean, then we plot the black hole masses vs the median of log(n).
-The correlation looks a bit steeper than in Figure \ref{fig:mbhn}, 
-with less scatter. I bet you say it looks curved.
-
-PS I will soon step back from the division bulges/ellipticals, 
-I seriously believe there is no such division. 
-I will explain this soon. ;)
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/mbh_vs_median_logn.eps}
-\caption{}
-\label{fig:mbhavn}
-\end{figure}
+The existence of intermediate-scale stellar discs suggests that a continuum of disc sizes may exist, rather than a dichotomy of nuclear vs. large-scale discs.  
+In a somewhat similar vein, it was previously thought that bulges came in just one of two flavours: 
+classical bulges with n=4 light profiles and pseudobulges with n=1 light profiles (e.g. Carollo et al. 1998-2002?).  
+Although many works still advocate this bulge dichotomy based on their light profiles, Graham \& Worley (2008) have revealed no 
+evidence for a bimodality in the distribution of their Sersic indices from a sample of 400 disc 
+galaxies\footnote{The co-existence of classical and pseudo bulges in the same galaxy (e.g. Erwin et al. 2003, ApJ, 597, 929) 
+further blurs claims for galaxies having either a classical bulge or a pseudobulge.}.   
+The presence of intermediate-scale discs blurs the distinction between elliptical and lenticular galaxies and it may be that our E vs S0 
+classification for galaxies without spiral arms could be better represented by a range of bulge-to-disc (luminosity and size) ratios.
 
@@
 
-%% In a manner similar to \objectname authors can provide links to dataset
-%% hosted at participating data centers via the \dataset{} command.  The
-%% second curly bracket argument is printed in the text while the first
-%% parentheses argument serves as the valid data set identifier.  Large
-%% lists of data set are best provided in a table (see Table 3 for an example).
-%% Valid data set identifiers should be obtained from the data center that
-%% is currently hosting the data.
-%%
-%% Note that AASTeX interprets everything between the curly braces in the 
-%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
-%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
-%% compile your manuscript.  Special characters do not 
-%% need to be escaped in the optional, square-bracket argument.
-
-%% All our observations were short direct exposures with CCD's.  We also have
-%% a random {\it Chandra} data set \dataset{ADS/Sa.ASCA\#X/86008020} and a
-%% neat \dataset[ADS/Sa.HST#Y0Q70101T]{HST FOS spectrum} that readers can access
-%% via the links in the electronic edition.  Unfortunately this has nothing
-%% whatsoever to do with this research.  At Lick Observatory we used a TI 500$\times$500
-%% chip and a GEC 575$\times$385, on the 1-m Nickel reflector.  The only
-%% filter available at Lick was red.  At CTIO we used a GEC 575$\times$385, with
-%% $B, V,$ and $R$ filters, and an RCA 512$\times$320, with $U, B, V, R,$ and $I$
-%% filters, on the 1.5-m reflector. In the CTIO observations we tried to
-%% concentrate on the shortest practicable wavelengths; but faintness, reddening,
-%% and poor short-wavelength sensitivity often kept us from observing in $U$ or
-%% even in $B$. All four cameras had scales of the order of 0.4 arcsec/pixel, and
-%% our field sizes were around 3 arcmin.
-%%
-%% The CCD images are unfortunately not always suitable, for very poor
-%% clusters or for clusters with large cores.  Since the latter are easily
-%% studied by other means, we augmented our own CCD profiles by collecting
-%% from the literature a number of star-count profiles
-%% \citep{kin68,pet76,har84,ort85}, as well as photoelectric profiles
-%% \citep{kin66,kin75} and electronographic profiles \citep{kro84}.
-%% In a few cases we judged normality by eye estimates on one of the Sky
-%% Surveys.
-
-%% In this section, we use  the \subsection command to set off
-%% a subsection.  \footnote is used to insert a footnote to the text.
-
-%% Observe the use of the LaTeX \label
-%% command after the \subsection to give a symbolic KEY to the
-%% subsection for cross-referencing in a \ref command.
-%% You can use LaTeX's \ref and \label commands to keep track of
-%% cross-references to sections, equations, tables, and figures.
-%% That way, if you change the order of any elements, LaTeX will
-%% automatically renumber them.
-
-%% This section also includes several of the displayed math environments
-%% mentioned in the Author Guide.
-
-%%\section{Helicity Amplitudes}
-%%
-%%It has been realized that helicity amplitudes provide a convenient means
-%%for Feynman diagram\footnote{Footnotes can be inserted like this.}
-%%evaluations.  These amplitude-level techniques
-%%are particularly convenient for calculations involving many Feynman
-%%diagrams, where the usual trace techniques for the amplitude
-%%squared becomes unwieldy.  Our calculations use the helicity techniques
-%%developed by other authors \cite[]{hag86}; we briefly summarize below.
-%%
-%%\subsection{Formalism} \label{bozomath}
-%%
-%%%% The equation environment wil produce a numbered display equation.
-%%
-%%A tree-level amplitude in $e^+e^-$ collisions can be expressed in
-%%terms of fermion strings of the form
-%%\begin{equation}
-%%\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
-%%\hat a_nu(p_1,\sigma_1) ,
-%%\end{equation}
-%%where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
-%%and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
-%%and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
-%%operator $(\tau = \pm1)$.  The $a^\mu_i$ may be formed from particle
-%%four-momenta, gauge-boson polarization vectors or fermion strings with
-%%an uncontracted Lorentz index associated with final-state fermions.
-%%
-%%%% The \notetoeditor{TEXT} command allows the author to communicate
-%%%% information to the copy editor.  This information will appear as a
-%%%% footnote on the printed copy for the manuscript style file.  Nothing will
-%%%% appear on the printed copy if the preprint or
-%%%% preprint2 style files are used.
-%%
-%%%% The eqnarray environment produces multi-line display math. The end of
-%%%% each line is marked with a \\. Lines will be numbered unless the \\
-%%%% is preceded by a \nonumber command.
-%%%% Alignment points are marked by ampersands (&). There should be two
-%%%% ampersands (&) per line.
-%%
-%%In the chiral \notetoeditor{Figures 1 and 2 should appear side-by-side in
-%%print} representation the $\gamma$ matrices are expressed
-%%in terms of $2\times 2$ Pauli matrices $\sigma$ and the unit matrix 1 as
-%%\begin{eqnarray}
-%%\gamma^\mu  & = &
-%% \left(
-%%\begin{array}{cc}
-%%0 & \sigma^\mu_+ \\
-%%\sigma^\mu_- & 0
-%%\end{array}	  \right) ,
-%% \gamma^5= \left(
-%%\begin{array}{cc}
-%%-1 &   0\\
-%%0 &	1
-%%\end{array}	  \right)  , \nonumber \\
-%%\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , \nonumber
-%%\end{eqnarray}
-%%giving
-%%\begin{equation}
-%%\hat a= \left(
-%%\begin{array}{cc}
-%%0 & (\hat a)_+\\
-%%(\hat a)_- & 0
-%%\end{array}\right), (\hat a)_\pm=a_\mu\sigma^\mu_\pm ,
-%%\end{equation}
-%%The spinors are expressed in terms of two-component Weyl spinors as
-%%\begin{equation}
-%%u=\left(
-%%\begin{array}{c}
-%%(u)_-\\
-%%(u)_+
-%%\end{array}\right), v={\bf (}\vdag_+{\bf ,}	\vdag_-{\bf )} .
-%%\end{equation}
-%%
-%%%% Putting eqnarrays or equations inside the mathletters environment groups
-%%%% the enclosed equations by letter. For instance, the eqnarray below, instead
-%%%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
-%%%% LaTeX the paper and look at the output to see the results.
-%%
-%%The Weyl spinors are given in terms of helicity eigenstates
-%%$\chi_\lambda(p)$ with $\lambda=\pm1$ by
-%%\begin{mathletters}
-%%\begin{eqnarray}
-%%u(p,\lambda)_\pm & = & (E\pm\lambda|{\bf p}|)^{1/2}\chi_\lambda(p) , \\
-%%v(p,\lambda)_\pm & = & \pm\lambda(E\mp\lambda|{\bf p}|)^{1/2}\chi
-%%_{-\lambda}(p)
-%%\end{eqnarray}
-%%\end{mathletters}
-%%
-%%%% This section contains more display math examples, including unnumbered
-%%%% equations (displaymath environment). The last paragraph includes some
-%%%% examples of in-line math featuring a couple of the AASTeX symbol macros.
-%%
-%%\section{Floating material and so forth}
-%%
-%%%% The displaymath environment will produce the same sort of equation as
-%%%% the equation environment, except that the equation will not be numbered
-%%%% by LaTeX.
-%%
-%%Consider a task that computes profile parameters for a modified
-%%Lorentzian of the form
-%%\begin{equation}
-%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
-%%\end{equation}
-%%where
-%%\begin{displaymath}
-%%d_{1} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
-%%\end{array} \right) ^{2} +
-%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
-%%\end{displaymath}
-%%\begin{displaymath}
-%%d_{2} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
-%%\end{array} \right) ^{2} +
-%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
-%%\end{displaymath}
-%%\begin{displaymath}
-%%x_{1} = (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta
-%%\end{displaymath}
-%%\begin{displaymath}
-%%y_{1} = -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
-%%\end{displaymath}
-%%
-%%In these expressions $x_{0}$,$y_{0}$ is the star center, and $\Theta$ is the
-%%angle with the $x$ axis.  Results of this task are shown in table~\ref{tbl-1}.
-%%It is not clear how these sorts of analyses may affect determination of
-%% $M_{\sun}$, but the assumption is that the alternate results
-%%should be less than 90\degr\ out of phase with previous values.
-%%We have no observations of \ion{Ca}{2}.
-%%Roughly \slantfrac{4}{5} of the electronically submitted abstracts
-%%for AAS meetings are error-free.
-%%
-%%%% If you wish to include an acknowledgments section in your paper,
-%%%% separate it off from the body of the text using the \acknowledgments
-%%%% command.
-%%
-%%%% Included in this acknowledgments section are examples of the
-%%%% AASTeX hypertext markup commands. Use \url without the optional [HREF]
-%%%% argument when you want to print the url directly in the text. Otherwise,
-%%%% use either \url or \anchor, with the HREF as the first argument and the
-%%%% text to be printed in the second.
-%%
 \acknowledgments
-%chien peng, peter erwin
+luca cortese, peppo gavazzi, matteo fossati
 %%
@@
 
-\bibliography{/Users/gsavorgnan/Dropbox/giulia_e_basta/Literature/SMBHbibliography}
-
-%%\begin{thebibliography}{}
-%%\bibitem[Auri\`ere(1982)]{aur82} Auri\`ere, M.  1982, \aap,
-%%    109, 301
-%%\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
-%%    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
-%%    McClintock, J. E.  1978, \apj, 224, 39
-%%\bibitem[Djorgovski \& King(1984)]{djo84} Djorgovski, S.,
-%%    \& King, I. R.  1984, \apjl, 277, L49
-%%\bibitem[Hagiwara \& Zeppenfeld(1986)]{hag86} Hagiwara, K., \&
-%%    Zeppenfeld, D.  1986, Nucl.Phys., 274, 1
-%%\bibitem[Harris \& van den Bergh(1984)]{har84} Harris, W. E.,
-%%    \& van den Bergh, S.  1984, \aj, 89, 1816
-%%\bibitem[H\`enon(1961)]{hen61} H\'enon, M.  1961, Ann.d'Ap., 24, 369
-%%\bibitem[Heiles \& Troland(2003)]{heiles03} Heiles, C. \& Troland, T. H., 2003, \apjs, preprint doi:10.1086/381753
-%%\bibitem[Kim, Ostricker, \& Stone(2003)]{kim03} Kim, W.-T.,  Ostriker, E., \& Stone, J. M., 2003, \apj, 599, 1157
-%%\bibitem[King(1966)]{kin66}  King, I. R.  1966, \aj, 71, 276
-%%\bibitem[King(1975)]{kin75}  King, I. R.  1975, Dynamics of
-%%    Stellar Systems, A. Hayli, Dordrecht: Reidel, 1975, 99
-%%\bibitem[King et al.(1968)]{kin68}  King, I. R., Hedemann, E.,
-%%    Hodge, S. M., \& White, R. E.  1968, \aj, 73, 456
-%%\bibitem[Kron et al.(1984)]{kro84} Kron, G. E., Hewitt, A. V.,
-%%    \& Wasserman, L. H.  1984, \pasp, 96, 198
-%%\bibitem[Lynden-Bell \& Wood(1968)]{lyn68} Lynden-Bell, D.,
-%%    \& Wood, R.  1968, \mnras, 138, 495
-%%\bibitem[Newell \& O'Neil(1978)]{new78} Newell, E. B.,
-%%    \& O'Neil, E. J.  1978, \apjs, 37, 27
-%%\bibitem[Ortolani et al.(1985)]{ort85} Ortolani, S., Rosino, L.,
-%%    \& Sandage, A.  1985, \aj, 90, 473
-%%\bibitem[Peterson(1976)]{pet76} Peterson, C. J.  1976, \aj, 81, 617
-%%\bibitem[Rudnick et al.(2003)]{rudnick03} Rudnick, G. et al., 2003, \apj, 599, 847
-%%\bibitem[Spitzer(1985)]{spi85} Spitzer, L.  1985, Dynamics of
-%%    Star Clusters, J. Goodman \& P. Hut, Dordrecht: Reidel, 109
-%%\bibitem[Treu et al.(2003)]{treu03} Treu, T. et al., 2003, \apj, 591, 53
-%%\end{thebibliography}
+\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
 
 \clearpage
-
-%% Use the figure environment and \plotone or \plottwo to include
-%% figures and captions in your electronic submission.
-%% To embed the sample graphics in
-%% the file, uncomment the \plotone, \plottwo, and
-%% \includegraphics commands
-%%
-%% If you need a layout that cannot be achieved with \plotone or
-%% \plottwo, you can invoke the graphicx package directly with the
-%% \includegraphics command or use \plotfiddle. For more information,
-%% please see the tutorial on "Using Electronic Art with AASTeX" in the
-%% documentation section at the AASTeX Web site, http://aastex.aas.org/
-%%
-%% The examples below also include sample markup for submission of
-%% supplemental electronic materials. As always, be sure to check
-%% the instructions to authors for the journal you are submitting to
-%% for specific submissions guidelines as they vary from
-%% journal to journal.
-
-%% This example uses \plotone to include an EPS file scaled to
-%% 80% of its natural size with \epsscale. Its caption
-%% has been written to indicate that additional figure parts will be
-%% available in the electronic journal.
-
-%%\begin{figure}
-%%\epsscale{.80}
-%%\plotone{f1.eps}
-%%\caption{Derived spectra for 3C138 \citep[see][]{heiles03}. Plots for all sources are available
-%%in the electronic edition of {\it The Astrophysical Journal}.\label{fig1}}
-%%\end{figure}
-%%
-%%\clearpage
-%%
-%%%% Here we use \plottwo to present two versions of the same figure,
-%%%% one in black and white for print the other in RGB color
-%%%% for online presentation. Note that the caption indicates
-%%%% that a color version of the figure will be available online.
-%%%%
-%%
-%%\begin{figure}
-%%\plottwo{f2.eps}{f2_color.eps}
-%%\caption{A panel taken from Figure 2 of \citet{rudnick03}. 
-%%See the electronic edition of the Journal for a color version 
-%%of this figure.\label{fig2}}
-%%\end{figure}
-%%
-%%%% This figure uses \includegraphics to scale and rotate the still frame
-%%%% for an mpeg animation.
-%%
-%%\begin{figure}
-%%\includegraphics[angle=90,scale=.50]{f3.eps}
-%%\caption{Animation still frame taken from \citet{kim03}.
-%%This figure is also available as an mpeg
-%%animation in the electronic edition of the
-%%{\it Astrophysical Journal}.}
-%%\end{figure}
-%%
-%%%% If you are not including electonic art with your submission, you may
-%%%% mark up your captions using the \figcaption command. See the
-%%%% User Guide for details.
-%%%%
-%%%% No more than seven \figcaption commands are allowed per page,
-%%%% so if you have more than seven captions, insert a \clearpage
-%%%% after every seventh one.
-%%
-%%%% Tables should be submitted one per page, so put a \clearpage before
-%%%% each one.
-%%
-%%%% Two options are available to the author for producing tables:  the
-%%%% deluxetable environment provided by the AASTeX package or the LaTeX
-%%%% table environment.  Use of deluxetable is preferred.
-%%%%
-%%
-%%%% Three table samples follow, two marked up in the deluxetable environment,
-%%%% one marked up as a LaTeX table.
-%%
-%%%% In this first example, note that the \tabletypesize{}
-%%%% command has been used to reduce the font size of the table.
-%%%% We also use the \rotate command to rotate the table to
-%%%% landscape orientation since it is very wide even at the
-%%%% reduced font size.
-%%%%
-%%%% Note also that the \label command needs to be placed
-%%%% inside the \tablecaption.
-%%
-%%%% This table also includes a table comment indicating that the full
-%%%% version will be available in machine-readable format in the electronic
-%%%% edition.
-%%
-%%\clearpage
-%%
-%%\begin{deluxetable}{ccrrrrrrrrcrl}
-%%\tabletypesize{\scriptsize}
-%%\rotate
-%%\tablecaption{Sample table taken from \citet{treu03}\label{tbl-1}}
-%%\tablewidth{0pt}
-%%\tablehead{
-%%\colhead{POS} & \colhead{chip} & \colhead{ID} & \colhead{X} & \colhead{Y} &
-%%\colhead{RA} & \colhead{DEC} & \colhead{IAU$\pm$ $\delta$ IAU} &
-%%\colhead{IAP1$\pm$ $\delta$ IAP1} & \colhead{IAP2 $\pm$ $\delta$ IAP2} &
-%%\colhead{star} & \colhead{E} & \colhead{Comment}
-%%}
-%%\startdata
-%%0 & 2 & 1 & 1370.99 & 57.35	 &   6.651120 &  17.131149 & 21.344$\pm$0.006  & 2
-%%4.385$\pm$0.016 & 23.528$\pm$0.013 & 0.0 & 9 & -    \\
-%%0 & 2 & 2 & 1476.62 & 8.03	 &   6.651480 &  17.129572 & 21.641$\pm$0.005  & 2
-%%3.141$\pm$0.007 & 22.007$\pm$0.004 & 0.0 & 9 & -    \\
-%%0 & 2 & 3 & 1079.62 & 28.92	 &   6.652430 &  17.135000 & 23.953$\pm$0.030  & 2
-%%4.890$\pm$0.023 & 24.240$\pm$0.023 & 0.0 & - & -    \\
-%%0 & 2 & 4 & 114.58  & 21.22	 &   6.655560 &  17.148020 & 23.801$\pm$0.025  & 2
-%%5.039$\pm$0.026 & 24.112$\pm$0.021 & 0.0 & - & -    \\
-%%0 & 2 & 5 & 46.78   & 19.46	 &   6.655800 &  17.148932 & 23.012$\pm$0.012  & 2
-%%3.924$\pm$0.012 & 23.282$\pm$0.011 & 0.0 & - & -    \\
-%%0 & 2 & 6 & 1441.84 & 16.16	 &   6.651480 &  17.130072 & 24.393$\pm$0.045  & 2
-%%6.099$\pm$0.062 & 25.119$\pm$0.049 & 0.0 & - & -    \\
-%%0 & 2 & 7 & 205.43  & 3.96	 &   6.655520 &  17.146742 & 24.424$\pm$0.032  & 2
-%%5.028$\pm$0.025 & 24.597$\pm$0.027 & 0.0 & - & -    \\
-%%0 & 2 & 8 & 1321.63 & 9.76	 &   6.651950 &  17.131672 & 22.189$\pm$0.011  & 2
-%%4.743$\pm$0.021 & 23.298$\pm$0.011 & 0.0 & 4 & edge \\
-%%\enddata
-%%%% Text for table notes should follow after the \enddata but before
-%%%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
-%%%% in the table for each \tablenotetext.
-%%\tablecomments{Table \ref{tbl-1} is published in its entirety in the 
-%%electronic edition of the {\it Astrophysical Journal}.  A portion is 
-%%shown here for guidance regarding its form and content.}
-%%\tablenotetext{a}{Sample footnote for table~\ref{tbl-1} that was generated
-%%with the deluxetable environment}
-%%\tablenotetext{b}{Another sample footnote for table~\ref{tbl-1}}
-%%\end{deluxetable}
-%%
-%%%% If you use the table environment, please indicate horizontal rules using
-%%%% \tableline, not \hline.
-%%%% Do not put multiple tabular environments within a single table.
-%%%% The optional \label should appear inside the \caption command.
-%%
-%%\clearpage
-%%
-%%\begin{table}
-%%\begin{center}
-%%\caption{More terribly relevant tabular information.\label{tbl-2}}
-%%\begin{tabular}{crrrrrrrrrrr}
-%%\tableline\tableline
-%%Star & Height & $d_{x}$ & $d_{y}$ & $n$ & $\chi^2$ & $R_{maj}$ & $R_{min}$ &
-%%\multicolumn{1}{c}{$P$\tablenotemark{a}} & $P R_{maj}$ & $P R_{min}$ &
-%%\multicolumn{1}{c}{$\Theta$\tablenotemark{b}} \\
-%%\tableline
-%%1 &33472.5 &-0.1 &0.4  &53 &27.4 &2.065  &1.940 &3.900 &68.3 &116.2 &-27.639\\
-%%2 &27802.4 &-0.3 &-0.2 &60 &3.7  &1.628  &1.510 &2.156 &6.8  &7.5 &-26.764\\
-%%3 &29210.6 &0.9  &0.3  &60 &3.4  &1.622  &1.551 &2.159 &6.7  &7.3 &-40.272\\
-%%4 &32733.8 &-1.2\tablenotemark{c} &-0.5 &41 &54.8 &2.282  &2.156 &4.313 &117.4 &78.2 &-35.847\\
-%%5 & 9607.4 &-0.4 &-0.4 &60 &1.4  &1.669\tablenotemark{c}  &1.574 &2.343 &8.0  &8.9 &-33.417\\
-%%6 &31638.6 &1.6  &0.1  &39 &315.2 & 3.433 &3.075 &7.488 &92.1 &25.3 &-12.052\\
-%%\tableline
-%%\end{tabular}
-%%%% Any table notes must follow the \end{tabular} command.
-%%\tablenotetext{a}{Sample footnote for table~\ref{tbl-2} that was
-%%generated with the \LaTeX\ table environment}
-%%\tablenotetext{b}{Yet another sample footnote for table~\ref{tbl-2}}
-%%\tablenotetext{c}{Another sample footnote for table~\ref{tbl-2}}
-%%\tablecomments{We can also attach a long-ish paragraph of explanatory
-%%material to a table.}
-%%\end{center}
-%%\end{table}
-%%
-%%%% If the table is more than one page long, the width of the table can vary
-%%%% from page to page when the default \tablewidth is used, as below.  The
-%%%% individual table widths for each page will be written to the log file; a
-%%%% maximum tablewidth for the table can be computed from these values.
-%%%% The \tablewidth argument can then be reset and the file reprocessed, so
-%%%% that the table is of uniform width throughout. Try getting the widths
-%%%% from the log file and changing the \tablewidth parameter to see how
-%%%% adjusting this value affects table formatting.
-%%
-%%%% The \dataset{} macro has also been applied to a few of the objects to
-%%%% show how many observations can be tagged in a table.
-%%
-%%\clearpage
-%%
-%%\begin{deluxetable}{lrrrrcrrrrr}
-%%\tablewidth{0pt}
-%%\tablecaption{Literature Data for Program Stars}
-%%\tablehead{
-%%\colhead{Star}	   & \colhead{V}      &
-%%\colhead{b$-$y}	   & \colhead{m$_1$}  &
-%%\colhead{c$_1$}	   & \colhead{ref}    &
-%%\colhead{T$_{\rm eff}$}  & \colhead{log g}  &
-%%\colhead{v$_{\rm turb}$} & \colhead{[Fe/H]} &
-%%\colhead{ref}}
-%%\startdata
-%%HD 97 & 9.7& 0.51& 0.15& 0.35& 2 & \nodata & \nodata & \nodata & $-1.50$ & 2 \\
-%%& & & & & & 5015 & \nodata & \nodata & $-1.50$ & 10 \\
-%%\dataset[ADS/Sa.HST#O6H04VAXQ]{HD 2665} & 7.7& 0.54& 0.09& 0.34& 2 & \nodata & \nodata & \nodata & $-2.30$ & 2 \\
-%%& & & & & & 5000 & 2.50 & 2.4 & $-1.99$ & 5 \\
-%%& & & & & & 5120 & 3.00 & 2.0 & $-1.69$ & 7 \\
-%%& & & & & & 4980 & \nodata & \nodata & $-2.05$ & 10 \\
-%%HD 4306 & 9.0& 0.52& 0.05& 0.35& 20, 2& \nodata & \nodata & \nodata & $-2.70$ & 2 \\
-%%& & & & & & 5000 & 1.75 & 2.0 & $-2.70$ & 13 \\
-%%& & & & & & 5000 & 1.50 & 1.8 & $-2.65$ & 14 \\
-%%& & & & & & 4950 & 2.10 & 2.0 & $-2.92$ & 8 \\
-%%& & & & & & 5000 & 2.25 & 2.0 & $-2.83$ & 18 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-2.80$ & 21 \\
-%%& & & & & & 4930 & \nodata & \nodata & $-2.45$ & 10 \\
-%%HD 5426 & 9.6& 0.50& 0.08& 0.34& 2 & \nodata & \nodata & \nodata & $-2.30$ & 2 \\
-%%\dataset[ADS/Sa.HST#O5F654010]{HD 6755} & 7.7& 0.49& 0.12& 0.28& 20, 2& \nodata & \nodata & \nodata & $-1.70$ & 2 \\
-%%& & & & & & 5200 & 2.50 & 2.4 & $-1.56$ & 5 \\
-%%& & & & & & 5260 & 3.00 & 2.7 & $-1.67$ & 7 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-1.58$ & 21 \\
-%%& & & & & & 5200 & \nodata & \nodata & $-1.80$ & 10 \\
-%%& & & & & & 4600 & \nodata & \nodata & $-2.75$ & 10 \\
-%%\dataset[ADS/Sa.HST#O56D06010]{HD 94028} & 8.2& 0.34& 0.08& 0.25& 20 & 5795 & 4.00 & \nodata & $-1.70$ & 22 \\
-%%& & & & & & 5860 & \nodata & \nodata & $-1.70$ & 4 \\
-%%& & & & & & 5910 & 3.80 & \nodata & $-1.76$ & 15 \\
-%%& & & & & & 5800 & \nodata & \nodata & $-1.67$ & 17 \\
-%%& & & & & & 5902 & \nodata & \nodata & $-1.50$ & 11 \\
-%%& & & & & & 5900 & \nodata & \nodata & $-1.57$ & 3 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-1.32$ & 21 \\
-%%HD 97916 & 9.2& 0.29& 0.10& 0.41& 20 & 6125 & 4.00 & \nodata & $-1.10$ & 22 \\
-%%& & & & & & 6160 & \nodata & \nodata & $-1.39$ & 3 \\
-%%& & & & & & 6240 & 3.70 & \nodata & $-1.28$ & 15 \\
-%%& & & & & & 5950 & \nodata & \nodata & $-1.50$ & 17 \\
-%%& & & & & & 6204 & \nodata & \nodata & $-1.36$ & 11 \\
-%%\cutinhead{This is a cut-in head}
-%%+26\arcdeg2606& 9.7&0.34&0.05&0.28&20,11& 5980 & \nodata & \nodata &$<-2.20$ & 19 \\
-%%& & & & & & 5950 & \nodata & \nodata & $-2.89$ & 24 \\
-%%+26\arcdeg3578& 9.4&0.31&0.05&0.37&20,11& 5830 & \nodata & \nodata & $-2.60$ & 4 \\
-%%& & & & & & 5800 & \nodata & \nodata & $-2.62$ & 17 \\
-%%& & & & & & 6177 & \nodata & \nodata & $-2.51$ & 11 \\
-%%& & & & & & 6000 & 3.25 & \nodata & $-2.20$ & 22 \\
-%%& & & & & & 6140 & 3.50 & \nodata & $-2.57$ & 15 \\
-%%+30\arcdeg2611& 9.2&0.82&0.33&0.55& 2 & \nodata & \nodata & \nodata & $-1.70$ & 2 \\
-%%& & & & & & 4400 & 1.80 & \nodata & $-1.70$ & 12 \\
-%%& & & & & & 4400 & 0.90 & 1.7 & $-1.20$ & 14 \\
-%%& & & & & & 4260 & \nodata & \nodata & $-1.55$ & 10 \\
-%%+37\arcdeg1458& 8.9&0.44&0.07&0.22&20,11& 5296 & \nodata & \nodata & $-2.39$ & 11 \\
-%%& & & & & & 5420 & \nodata & \nodata & $-2.43$ & 3 \\
-%%+58\arcdeg1218&10.0&0.51&0.03&0.36& 2 & \nodata & \nodata & \nodata & $-2.80$ & 2 \\
-%%& & & & & & 5000 & 1.10 & 2.2 & $-2.71$ & 14 \\
-%%& & & & & & 5000 & 2.20 & 1.8 & $-2.46$ & 5 \\
-%%& & & & & & 4980 & \nodata & \nodata & $-2.55$ & 10 \\
-%%+72\arcdeg0094&10.2&0.31&0.09&0.26&12 & 6160 & \nodata & \nodata & $-1.80$ & 19 \\
-%%\sidehead{I'm a side head:}
-%%G5--36 & 10.8& 0.40& 0.07& 0.28& 20 & \nodata & \nodata & \nodata & $-1.19$ & 21 \\
-%%G18--54 & 10.7& 0.37& 0.08& 0.28& 20 & \nodata & \nodata & \nodata & $-1.34$ & 21 \\
-%%G20--08 & 9.9& 0.36& 0.05& 0.25& 20,11& 5849 & \nodata & \nodata & $-2.59$ & 11 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-2.03$ & 21 \\
-%%G20--15 & 10.6& 0.45& 0.03& 0.27& 20,11& 5657 & \nodata & \nodata & $-2.00$ & 11 \\
-%%& & & & & & 6020 & \nodata & \nodata & $-1.56$ & 3 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-1.58$ & 21 \\
-%%G21--22 & 10.7& 0.38& 0.07& 0.27& 20,11& \nodata & \nodata & \nodata & $-1.23$ & 21 \\
-%%G24--03 & 10.5& 0.36& 0.06& 0.27& 20,11& 5866 & \nodata & \nodata & $-1.78$ & 11 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-1.70$ & 21 \\
-%%G30--52 & 8.6& 0.50& 0.25& 0.27& 11 & 4757 & \nodata & \nodata & $-2.12$ & 11 \\
-%%& & & & & & 4880 & \nodata & \nodata & $-2.14$ & 3 \\
-%%G33--09 & 10.6& 0.41& 0.10& 0.28& 20 & 5575 & \nodata & \nodata & $-1.48$ & 11 \\
-%%G66--22 & 10.5& 0.46& 0.16& 0.28& 11 & 5060 & \nodata & \nodata & $-1.77$ & 3 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-1.04$ & 21 \\
-%%G90--03 & 10.4& 0.37& 0.04& 0.29& 20 & \nodata & \nodata & \nodata & $-2.01$ & 21 \\
-%%LP 608--62\tablenotemark{a} & 10.5& 0.30& 0.07& 0.35& 11 & 6250 & \nodata &
-%%\nodata & $-2.70$ & 4 \\
-%%\enddata
-%%\tablenotetext{a}{Star LP 608--62 is also known as BD+1\arcdeg 2341p.  We will
-%%make this footnote extra long so that it extends over two lines.}
-%%%% You can append references to a table using the \tablerefs command.
-%%\tablerefs{
-%%(1) Barbuy, Spite, \& Spite 1985; (2) Bond 1980; (3) Carbon et al. 1987;
-%%(4) Hobbs \& Duncan 1987; (5) Gilroy et al. 1988: (6) Gratton \& Ortolani 1986;
-%%(7) Gratton \& Sneden 1987; (8) Gratton \& Sneden (1988); (9) Gratton \& Sneden 1991;
-%%(10) Kraft et al. 1982; (11) LCL, or Laird, 1990; (12) Leep \& Wallerstein 1981;
-%%(13) Luck \& Bond 1981; (14) Luck \& Bond 1985; (15) Magain 1987;
-%%(16) Magain 1989; (17) Peterson 1981; (18) Peterson, Kurucz, \& Carney 1990;
-%%(19) RMB; (20) Schuster \& Nissen 1988; (21) Schuster \& Nissen 1989b;
-%%(22) Spite et al. 1984; (23) Spite \& Spite 1986; (24) Hobbs \& Thorburn 1991;
-%%(25) Hobbs et al. 1991; (26) Olsen 1983.}
-%%\end{deluxetable}
-%%
-%%%% Tables may also be prepared as separate files. See the accompanying
-%%%% sample file table.tex for an example of an external table file.
-%%%% To include an external file in your main document, use the \input
-%%%% command. Uncomment the line below to include table.tex in this
-%%%% sample file. (Note that you will need to comment out the \documentclass,
-%%%% \begin{document}, and \end{document} commands from table.tex if you want
-%%%% to include it in this document.)
-%%
-%%%% \input{table}
-%%
-%%%% The following command ends your manuscript. LaTeX will ignore any text
-%%%% that appears after it.
 

### 2015-07-08 papers/lentiptical/lentiptical.sh

@@ -1,0 +1,5 @@
+latex lentiptical
+bibtex lentiptical
+latex lentiptical
+latex lentiptical
+dvipdfm lentiptical.dvi

### 2015-07-10 papers/data_paper/datapaper.tex
fri

@@
 
-\title{Supermassive black hole and host bulge affairs \\ I. True to life, physically motivated galaxy decomposition.}
+\title{Supermassive black hole and host bulge affairs \\ I. True to life, physically motivated galaxy decomposition}
 
 \author{G. A. D. Savorgnan and A. W. Graham}
-\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
+\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia}
 \email{gsavorgn@astro.swin.edu.au}
@@
 
-%% Mark off your abstract in the ``abstract'' environment. In the manuscript
-%% style, abstract will output a Received/Accepted line after the
-%% title and affiliation information. No date will appear since the author
-%% does not have this information. The dates will be filled in by the
-%% editorial office after submission.
-
 \begin{abstract}
-abstract % 2d worse than 1d say it!!!
+Several recent studies have performed galaxy decompositions 
+to investigate correlations between the black hole mass and the host spheroid properties, 
+but they have not converged to the same conclusions. 
+This is because their best fit models for the same galaxy were often significantly different 
+and not consistent with each other in terms of fitted components. 
+Using $3.6 \rm ~\mu m$ \emph{Spitzer} imagery, which is a superb tracer of the stellar mass (superior to the $K$-band), 
+we have performed state-of-the-art multicomponent decompositions for 66 galaxies 
+with directly measured black hole masses. 
+Our sample is the largest to date and, 
+unlike previous studies, contains a large number (17) of spiral galaxies with low black hole masses. 
+We paid careful attention to the image mosaicking, sky subtraction and masking of contaminating sources.
+Thanks to a scrupulous inspection of the galaxy photometry (through isophotal analysis and unsharp masking) and -- for the first time -- of the 2D kinematics, 
+we were able to identify and model bulges, large-scale, intermediate-scale or nuclear disks, bars, rings, spiral arms, halos, extended or unresolved nuclear 
+sources and partially depleted cores. 
+For each individual galaxy, we compared our best-fit model with those presented by the previous studies, 
+explained the discrepancies and identified the optimal decomposition.
+We independently performed 1D and 2D decompositions, 
+and concluded that, at least when modelling large, nearby galaxies, 1D techniques have more advantages than 2D techniques. 
+Finally, we developed a method to estimate the uncertainties on the 1D best-fit parameters 
+that takes into account systematic errors, 
+unlike popular 2D codes that only consider statistical errors.
+
 \end{abstract}
 
-\keywords{keywords}
+\keywords{galaxies: bulges; galaxies: elliptical and lenticular, cD; galaxies: evolution; galaxies: structure; black hole physics}
 
@@
 in order to derive the bulge parameters and explore their relation with the black hole masses. 
-{\bf Rusli has explored the black hole - core relation.}
 Interestingly, the past studies used almost the same sample of galaxies, yet they claimed some contradictory conclusions.
@@
 whereas the remaining four did not.
-In addition, \cite{lasker2014anal} {\bf who did not work at 3.6um} 
+In addition, \cite{lasker2014anal} 
 declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity and the bulge luminosity, 
@@
 \end{equation}
-where $R$ is the projected galaxy radius, $\mu_{\rm 0}$ is the central surface brightness, and 
+where $R$ is the projected radius, $\mu_{\rm 0}$ is the central surface brightness, and 
 $\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
@@
 Doing so, we obtained %$FWHM = 2''.03$ for the Gaussian function,
-$(\alpha, \beta) = (2''.38, 4.39)$ %for the Moffat function
-(see Appendix \ref{sec:app1} for the analytical expressions of the Moffat function).
+$(\alpha, \beta) = (2''.38, 4.39)$.
 
@@
 although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
-The all too often over-looked {\bf ??} with (signal-to-noise)-based weighting schemes 
+The all too often over-looked flaw with (signal-to-noise)-based weighting schemes 
 is that they immediately become an incorrectly biased weighting schemes when additional components are present but not modelled.
-For example, fitting a S\'ersic model to what is actually a nucleated elliptical galaxy immediately {\bf ??} 
+For example, fitting a S\'ersic model to what is actually a nucleated elliptical galaxy immediately voids 
 a (signal-to-noise)-based weighting scheme 
@@
 While we have paid careful attention to the components in each galaxy, 
-and more so than the studies upon which our work is building from,
 this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
@@
 
+\acknowledgments
+GS acknowledges the invaluable support received from Alessandro Marconi, Eleonora Sani and Leslie Hunt 
+in the early stages of this research.
+GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Giuseppe Gavazzi, 
+Bililign Dullo, Paolo Bonfini, Elisabete Lima Da Cunha 
+and Gonzalo Diaz 
+for useful discussion. \\
+This research was supported by Australian Research Council funding through grants
+DP110103509 and FT110100263.
+This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
+on-board the Spitzer Space Telescope, 
+which is operated by the Jet Propulsion Laboratory, 
+California Institute of Technology under a contract with NASA.
+This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
+which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
+under contract with the National Aeronautics and Space Administration.
+
+\clearpage
+
   \onecolumngrid
-  \subsection{individual galaxies}
+  \subsection{Individual galaxy decompositions}
   \label{sec:indgal}
 
-  individual galaxies \\
   For each galaxy, we show a figure and a table. 
@@
   The top panels display the galaxy surface brightness ($\mu$) radial profiles obtained with a linear sampling. 
-  The black points are the observed data.  
+  The black points are the observed data used in the fit and the empty points are the observed data excluded from the fit.  
   The color lines represent the individual (PSF-convolved) model components:
@@
   The analytic functions can be: S=S\'ersic, e=exponential, G=Gaussian, F=Ferrer, M=Moffat and PSF.
-  The physical components can be: bul=bulge or spheroid, d=disk, id=inner disk, bar, n=nucleus, l=lens or oval, r=ring, halo and spiral arms. 
+  The physical components can be: bul=bulge (or spheroid), d=disk, id=inner disk, bar, n=nucleus, l=lens or oval, r=ring, halo and spiral arms. 
   When a nuclear component or a partially depleted core have been masked, we signal them as ``m-n'' and ``m-c'', respectively.
@@
   \label{tab:ic1459}
-  \tablecomments{S+11 obtained the smallest estimate of the S\'ersic index because they fit a nuclear component rather than masking the core. 
-  R+13 obtained the smallest estimate of the effective radius 
-  because they fit a circularized light profile that only extends out to $R_{\rm eq} \lesssim 60''$. }
+  %\tablecomments{S+11 obtained the smallest estimate of the S\'ersic index because they fit a nuclear component rather than masking the core. 
+  %R+13 obtained the smallest estimate of the effective radius 
+  %because they fit a circularized light profile that only extends out to $R_{\rm eq} \lesssim 60''$. }
   \end{table}
@@
   S+11 obtained the smallest effective radius and S\'ersic index because they fit a nuclear component rather than masking the core. 
-  L+14 obtained the largest effective radius and S\'ersic index, 
-  although the 1D representation of their 2D fit (their Figure 8) shows that their model overestimates the galaxy light at large radii ($R_{\rm maj} > 100''$), 
-  implying the need for a smaller $R_{\rm e}$ and $n$. 
-  We suspect that this could be due to the pixel weighting scheme that they used.
+  %L+14 obtained the largest effective radius and S\'ersic index, 
+  %although the 1D representation of their 2D fit (their Figure 8) shows that their model overestimates the galaxy light at large radii ($R_{\rm maj} > 100''$), 
+  %implying the need for a smaller $R_{\rm e}$ and $n$. 
+  %We suspect that this could be due to the pixel weighting scheme that they used.
   }
@@
   \tablecomments{
-  The fit of R+13 returns the largest values for $R_{\rm e,sph}$ and $n_{\rm sph}$. 
+  The equivalent-axis fit of R+13 returns the largest values for $R_{\rm e,sph}$ and $n_{\rm sph}$. 
   As in the case of M49, since their circularized light profile is almost three times more extended than ours, 
@@
   {\bf M89 -- NGC 4552 \\}
-
-  m87 has ellipticity still increasing, the halo is not prevailing
-  m89 instead has a plateau in the ell prof, bcz the halo is predominant
-  we need to fit the halo
 
@@
 
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
+  \caption{Best-fit model and isophotal parameters for NGC 1332.
+  NGC 1332 is an edge-on elliptical/lenticular galaxy. 
+  Given its large stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
+  The ellipticity profile proves the presence of an intermediate-scale disk. 
+  Given the edge-on inclination of such disk, we model it with a low-$n$ S\'ersic profile. 
+  The data within the innermost $6''.1$ are excluded from the fit.
   Our equivalent-axis decomposition returns a spheroidal component accounting for 95\% of the total light,
@@
   NGC 1332 would no longer be an outlier in our $M_{\rm BH} - L_{\rm sph}$ diagram. \\
-
-  \begin{figure}[h]
-  \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1332.
-  NGC 1332 is an edge-on elliptical/lenticular galaxy. 
-  Given its large stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
-  The ellipticity profile proves the presence of an intermediate-scale disk. 
-  Given the edge-on inclination of such disk, we model it with a low-$n$ S\'ersic profile. 
-  The data within the innermost $6''.1$ are excluded from the fit.
   }
@@
   and obtained the smallest estimate of the effective radius, 
-  which is at odds with the fact that central cluster galaxies typically have the largest sizes. 
+  which is at odds with the fact that central cluster galaxies typically have very large sizes. 
   L+14 finds an effective radius which is a factor of two smaller than that obtained by us 
@@
   \tablecomments{
-  S+11 found a smaller effective radius and S\'ersic index for the spheroidal component of this galaxy, 
-  possibly because they modelled the intermediate scale disk as a large-scale disk.
-  L+14 also used a model with a bulge encased in a larger disk, and attributed the excess of light at large radii to a halo. 
-  In doing so, they obviously obtained an even smaller bulge effective radius.
+  L+14 used a model with a bulge encased in a larger disk, and attributed the excess of light at large radii to a halo. 
+  In doing so, they obviously obtained a smaller bulge effective radius.
   }
@@
   We model the bar with a Ferrer function and the nucleus with a Gaussian function. 
-  As expected, the Ferrer component is rejected by the equivalent-axis fit. 
+  The Ferrer component is rejected by the equivalent-axis fit. 
   }
@@
   and thus underestimate the bulge effective radius and overestimate the bulge S\'ersic index.
-  The bulge effective radius obtained by S+11 is even larger because they did not model the bar. 
+  The bulge effective radius obtained by S+11 is larger because they did not model the bar. 
   }
@@
   \label{tab:n3245}
-  \tablecomments{
-  GD07 found the largest estimates of the bulge effective radius and S\'ersic index.
-  }
+%  \tablecomments{
+%  GD07 found the largest estimates of the bulge effective radius and S\'ersic index.
+%  }
   \end{table}
@@
   \label{tab:n3489}
-  \tablecomments{
-  S+11 did not fit the bar and thus obtained a larger estimate of the bulge effective radius.
-  }
+  %\tablecomments{
+  %S+11 did not fit the bar and thus obtained a larger estimate of the bulge effective radius.
+  %}
   \end{table}
@@
   \caption{Best-fit model and isophotal parameters for NGC 3585. 
-  NGC 3585 is an elliptical galaxy with an embedded disk \cite{scorzabender1995}. 
+  NGC 3585 is an elliptical galaxy with an embedded disk \citep{scorzabender1995}. 
   The embedded disk is visible in the unsharp mask and modeled with an exponential function. }
@@
   and a kinematically decoupled core. 
-  We find unnnecessary masking the nuclear region of this galaxy and we fit the light profile with a single S\'ersic model.
+  We find that masking the nuclear region of this galaxy is unnnecessary and we fit the light profile with a single S\'ersic model.
   }
@@
   \tablecomments{B+12 obtained the largest estimates of the effective radius and S\'ersic index, 
-  but the reasons for this are not clear. }
+  possibly due to incorrect sky subtraction. }
   \end{table}
@@
   \small
-  \caption{Best-fit parameters for the spheroidal component of NGC 4261.}
+  \caption{Best-fit parameters for the spheroidal component of NGC 4151.}
   \begin{center}
@@
   S+11 found the smallest estimate of the effective radius because they added a large-scale disk to their model.
-  Similarly, V+12 obtained a small estimate of the effective radius because of the limited radial extent of their data.
+  V+12 obtained a small estimate of the effective radius because of the limited radial extent of their data.
   }
@@
   B+12 fit nor the bar neither the inner disk and obtained the largest estimates of the bulge effective radius and S\'ersic index.
-  The models of S+11 and V+12 account for the bar and thus result in lower estimates of the bulge effective radius and S\'ersic index.
+  The models of S+11 and V+12 do not account for the inner disk and thus result in larger estimates of the bulge effective radius.
   }
@@
   NGC 5128 is a merging system. 
-  The data within $50'' \lesssim R_{\rm maj} \lesssim 200''$ is excluded from the fit.}
+  The data within $50'' \lesssim R_{\rm maj} \lesssim 200''$ are excluded from the fit.}
   \end{center}
@@
   \label{tab:n5128}
-  \tablecomments{}
   \end{table}
@@
   \label{tab:n7052}
-  \tablecomments{The model of V+12 subtracts a large-scale disk and thus results in the lowest estimates of the effective radius and S\'ersic index.}
+  \tablecomments{The model of V+12 oversubtracts a large-scale disk and thus results in the lowest estimates of the effective radius and S\'ersic index.}
   \end{table}
@@
 
-\acknowledgments
-{\bf marconi, sani, hunt...}
-GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Elisabete Lima Da Cunha and Gonzalo Diaz 
-for useful discussion. \\
-This research was supported by Australian Research Council funding through grants
-DP110103509 and FT110100263.
-This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
-on-board the Spitzer Space Telescope, 
-which is operated by the Jet Propulsion Laboratory, 
-California Institute of Technology under a contract with NASA.
-This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
-which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
-under contract with the National Aeronautics and Space Administration.
+\clearpage
 

### 2015-07-10 papers/lentiptical/lentiptical.tex
fri

@@
 
-\documentclass[preprint2]{emulateapj}
+\documentclass[12pt,preprint]{nature}
 
@@
 
-\shorttitle{Lentiptical galaxies}
-\shortauthors{Savorgnan \& Graham}
-
 %% This is the end of the preamble.  Indicate the beginning of the
@@
 
-\title{Lentiptical galaxies and their ordinary black holes}
-
-%% Use \author, \affil, and the \and command to format
-%% author and affiliation information.
-%% Note that \email has replaced the old \authoremail command
-%% from AASTeX v4.0. You can use \email to mark an email address
-%% anywhere in the paper, not just in the front matter.
-%% As in the title, use \\ to force line breaks.
-
-\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
-\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
-
-%\author{C. D. Biemesderfer\altaffilmark{4,5}}
-%\affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
-\email{gsavorgn@astro.swin.edu.au}
-
-%\and
-
-%\author{A. W. Graham\altaffilmark{1}}
-%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
-
-%% Notice that each of these authors has alternate affiliations, which
-%% are identified by the \altaffilmark after each name.  Specify alternate
-%% affiliation information with \altaffiltext, with one command per each
-%% affiliation.
-
-%\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
-%CTIO is operated by AURA, Inc.\ under contract to the National Science
-%Foundation.}
-%\altaffiltext{2}{Society of Fellows, Harvard University.}
-%\altaffiltext{3}{present address: Center for Astrophysics,
-%    60 Garden Street, Cambridge, MA 02138}
-%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
-%\altaffiltext{5}{Patron, Alonso's Bar and Grill}
-
-%% Mark off your abstract in the ``abstract'' environment. In the manuscript
-%% style, abstract will output a Received/Accepted line after the
-%% title and affiliation information. No date will appear since the author
-%% does not have this information. The dates will be filled in by the
-%% editorial office after submission.
+Title: Lentiptical galaxies \\
+Authors: G. A. D. Savorgnan and A. W. Graham \\
+Affiliation: Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia. \\
 
 \begin{abstract}
-Lentiptical galaxies are an intermediate class of galaxies between elliptical  
-and lenticular galaxies.
-Lentipticals are early-type, bulge-dominated galaxies that feature a fast-rotating, 
-intermediate-scale disk of stars embedded within a slow-rotating spheroid of stars.
-Such spheroid dominates the light in the central region of the galaxy and also at large radii, 
-unlike lenticular galaxies, whose bulge is encased within a (more extended) large-scale disk. 
+Early-type galaxies are quiescent galaxies, with little or no star formation activity. 
+The majority of early-type galaxies are made of two principal components: 
+a spheroid (or bulge) of stars with random motion and a rapidly rotating stellar disk (1 krajnovic). 
+The relative importance of these two components determines the morphological classification of early-type galaxies into two types: 
+elliptical galaxies are spheroid-dominated systems, 
+whereas lenticular galaxies are composed of a small bulge of stars encased in a larger stellar disk. 
+When perfoming bulge/disk decomposition, 
+the spheroidal component is typically described with a S\'ersic profile (2 sersic), 
+while the disk is fit with an exponential function. 
+Theoretically, the bulge-to-disk ratio, 
+which describes the relative importance of the spheroidal component over the disk component, 
+can assume any positive value. 
+However, several studies have taken into account only bulge/disk decompositions 
+in which the exponential function neatly dominates over the S\'ersic profile at large galaxy radii, 
+and rejected those decompositions in which the exponential function remains ``embedded'' within the S\'ersic profile, 
+considering such decompositions as unphysical.
+Here we show that these rejected models correctly reproduce the kinematics of a class of early-type galaxies, 
+that we name \emph{lentiptical}. 
 Lentiptical galaxies have often been confused with lenticular galaxies and, 
@@
 This surprisingly common mistake has led to some wrong conclusions, 
-such as the claim that a number of lentiptical galaxies are extreme outliers 
-in the $M_{\rm BH} - M_{\rm *,sph}$ diagram, 
-i.e. these galaxies host a central black hole whose mass, $M_{\rm BH}$, is abnormally large 
-compared to expectations from their (underestimated) bulge stellar mass, $M_{\rm *,sph}$.
+such as the claim that a number of lentiptical galaxies host a central black hole whose mass is abnormally large 
+compared to expectations from its (underestimated) bulge luminosity.
 
+Our results demonstrate that there is no bimodality in the distribution of the bulgetodisk
+that the claimed bimodality is artificial
+
+we show that the ell profile is enough to estabilish if the disk is embedded or not
+
+%Lentiptical galaxies are an intermediate class of galaxies between elliptical  
+%and lenticular galaxies.
+%Lentipticals are early-type, bulge-dominated galaxies that feature a fast-rotating, 
+%intermediate-scale disk of stars embedded within a slow-rotating spheroid of stars.
+%Such spheroid dominates the light in the central region of the galaxy and also at large radii, 
+%unlike lenticular galaxies, whose bulge is encased within a (more extended) large-scale disk. 
 \end{abstract}
-
-%% Keywords should appear after the \end{abstract} command. The uncommented
-%% example has been keyed in ApJ style. See the instructions to authors
-%% for the journal to which you are submitting your paper to determine
-%% what keyword punctuation is appropriate.
-
-\keywords{keywords}
 
@@
 
-\acknowledgments
 luca cortese, peppo gavazzi, matteo fossati
@@
 
-\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
+%\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
 

### 2015-07-13 papers/data_paper/datapaper.tex
mon

@@
 
-\title{Supermassive black hole and host bulge affairs \\ I. True to life, physically motivated galaxy decomposition}
+\title{Supermassive black hole and host spheroid affairs \\ I. True to life, physically motivated galaxy decomposition}
 
@@
 Several recent studies have performed galaxy decompositions 
-to investigate correlations between the black hole mass and the host spheroid properties, 
-but they have not converged to the same conclusions. 
-This is because their best fit models for the same galaxy were often significantly different 
+to investigate correlations between the black hole mass and various properties of the host spheroid, 
+but they have not converged on the same conclusions. 
+This is because their models for the same galaxy were often significantly different 
 and not consistent with each other in terms of fitted components. 
@@
 We paid careful attention to the image mosaicking, sky subtraction and masking of contaminating sources.
-Thanks to a scrupulous inspection of the galaxy photometry (through isophotal analysis and unsharp masking) and -- for the first time -- of the 2D kinematics, 
-we were able to identify and model bulges, large-scale, intermediate-scale or nuclear disks, bars, rings, spiral arms, halos, extended or unresolved nuclear 
+After a scrupulous inspection of the galaxy photometry (through isophotal analysis and unsharp masking) and -- for the first time -- 2D kinematics, 
+we were able to account for spheroids, large-scale, intermediate-scale and nuclear disks, bars, rings, spiral arms, halos, extended or unresolved nuclear 
 sources and partially depleted cores. 
-For each individual galaxy, we compared our best-fit model with those presented by the previous studies, 
+For each individual galaxy, we compared our best-fit model with previous studies, 
 explained the discrepancies and identified the optimal decomposition.
-We independently performed 1D and 2D decompositions, 
+Moreover, we have independently performed 1D and 2D decompositions, 
 and concluded that, at least when modelling large, nearby galaxies, 1D techniques have more advantages than 2D techniques. 
-Finally, we developed a method to estimate the uncertainties on the 1D best-fit parameters 
+Finally, we developed a prescription to estimate the uncertainties on the 1D best-fit parameters for the 66 spheroids 
 that takes into account systematic errors, 
@@
 \label{sec:int}
-Supermassive black holes and host bulges have very different sizes. 
-If the event horizon of the Galactic supermassive black hole was as big as a grain of sand of the Sahara desert, 
-then the black hole gravitational sphere-of-influence would be as big as the international airport of Cairo, 
+Supermassive black holes and their host spheroids\footnote{The term ``spheroid'' refers to either an elliptical galaxy or the spheroidal component 
+of a galaxy with a disk. } 
+have very different sizes. 
+If the event horizon of the Galactic supermassive black hole was as big as a grain of sand in the Sahara desert, 
+then the black hole's gravitational sphere-of-influence would be as big as the international airport of Cairo, 
 and the Galactic bulge would be as big as the Sahara desert itself.
 It is thus surprising that the masses of supermassive black holes ($M_{\rm BH}$) 
-scale with a number of properties of their host bulges, 
+scale with a number of properties of their host spheroid, 
 indicating the non-gravitational origin of these correlations 
 (e.g.~\citealt{dressler1989,yee1992,kormendyrichstone1995,laor1997,magorrian1998,ferraresemerritt2000,gebhardt2000,graham2001,
-marconihunt2003,haringrix2004,graham2012bent,grahamscott2015}). \\
-The tightness of (i.e.~the small scatter about) the observed black hole mass correlations has led to the idea
-that black holes and host galaxies have coevolved with some sort of self-regulated growth.
+marconihunt2003,haringrix2004,grahamscott2015}). \\
+The tightness of (i.e.~the small scatter about) the above observed black hole mass correlations has led to the idea
+that black holes and host spheroids have coevolved with some sort of self-regulated growth.
 Exploring the evolution of this growth with cosmic time could help identify
-the driving mechanisms of the black hole -- galaxy coevolution.
+the driving mechanisms of the black hole -- spheroid coevolution.
 Observations at $z=0$ set the local benchmark from which to measure this evolution.
-Any complete theory or model describing the coevolution of galaxies and black holes must incorporate 
+Any complete theory or model describing the coevolution of spheroids and black holes must incorporate 
 all of the observed scaling relations, which also have to be consistent with each other.
@@
 to match the $z=0$ black hole mass -- galaxy mass relation.
-Such scaling relations can also be employed to predict the masses of black holes in other galaxies, where a direct
+The observed scaling relations can also be employed to predict the masses of black holes in other galaxies, where a direct
 measure of $M_{\rm BH}$ would be extremely time consuming or simply impossible due to technological limitations.
 Moreover, many accurate $M_{\rm BH}$ predictions enable one to derive 
-the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction}) 
+the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction}; Fontanot et al. \emph{submitted}) 
 and space density (e.g.~\citealt{grahamdriver2007smbhmassdensity,comastri2015}). 
 All of these examples depend on the $z=0$ relations, 
-and as such the recalibration of the black hole mass -- bulge stellar mass ratio ($M_{\rm BH}/M_{\rm *,sph}$) in large bulges,
-from $0.1 - 0.2\%$ (e.g.~\citealt{haringrix2004}) to $0.36\%$ \citep{graham2012bent} and then $0.49\%$ \citep{grahamscott2015}, 
+and as such the recalibration of the black hole mass -- spheroid stellar mass ratio ($M_{\rm BH}/M_{\rm *,sph}$) in large spheroids,
+from $0.1 - 0.2\%$ (e.g.~\citealt{marconihunt2003,haringrix2004}) to $0.49\%$ \citep{grahamscott2015}, 
 has many substantial implications. \\
@@
 It is now generally accepted that supermassive black holes reside at the center of most, if not all, 
-massive galaxies, either quiescent or active. \\
-Massive, early-type galaxies are often composite systems. 
-The knowledge that many ``elliptical'' galaxies actually contain embedded stellar disks dates back  
+massive spheroids, either quiescent or active. \\
+Massive, early-type (E, E/S0, S0) galaxies are often composite systems. 
+The knowledge that many ``elliptical'' (E) galaxies were misclassified and actually contain embedded stellar disks dates back  
 at least three decades  
-\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995}. 
+\citep{capaccioli1987,carter1987,rixwhite1990,rixwhite1992,bender1990,scorzabender1990,nieto1991,scorzabender1995}. 
 After examining long-slit and integral field unit spectroscopic observations of morphologically classified elliptical galaxies in the Fornax cluster, 
@@
 have further advanced this view of ``elliptical'' galaxies being all but simple and featureless pressure-supported systems.
-More than half of all morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.
+Most of the morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.
 \cite{krajnovic2013} showed that ``fast rotators'' as a class are disk-galaxies or at least disk-like galaxies. 
@@
 without any signature of disk-like components (neither in the kinematics nor in the photometry) 
-dominate only the most massive end (beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
-Given the prevalence of disks, it is clearly important to perform bulge/disk decompositions, 
-if one is to properly explore the black hole-bulge connection. 
+dominate only the most massive end (with stellar masses beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
+Given the prevalence of disks, it is clearly important to perform spheroid/disk decompositions, 
+if one is to properly explore the black hole -- spheroid connection. 
 Indeed, separating the disk light from that of the bulge has led to the discovery of the missing population of compact, massive spheroids 
@@
 of galaxies using a combination of analytic functions (usually one function per
-galaxy component, such as bulges, disks, bars, nuclei, etc.).
+galaxy component, such as spheroids, disks, bars, nuclei, etc.).
 The one-dimensional (1D) technique involves fitting isophotes to the galaxy image, extracting the (one-dimensional) surface 
@@
 \citep{grahamdriver2007,sani2011,vika2012,beifiori2012,lasker2014data,lasker2014anal} have attempted galaxy decomposition
-in order to derive the bulge parameters and explore their relation with the black hole masses. 
+in order to derive the spheroid parameters and explore their relation with the black hole masses. 
 Interestingly, the past studies used almost the same sample of galaxies, yet they claimed some contradictory conclusions.
 For example, one study \citep{grahamdriver2007} obtained a good $M_{\rm BH}-n_{\rm sph}$ correlation 
-(the bulge S\'ersic index $n_{\rm sph}$ is a measure of the central radial concentration of stars, \citealt{trujillo2001}), 
-whereas the remaining four did not.
+(the spheroid S\'ersic index $n_{\rm sph}$ is a measure of the central radial concentration of stars, \citealt{trujillo2001}), 
+whereas the remaining four did not\footnote{\cite{savorgnan2013} showed that, 
+by rejecting the most discrepant S\'ersic index measurements and averaging the remaning ones, 
+a strong $M_{\rm BH}-n_{\rm sph}$ correlation was recovered. 
+The fact that none of the four studies obtained a significant $M_{\rm BH}-n_{\rm sph}$ correlation with their individual measurements 
+is indicative of non accurate galaxy decompositions. }.
 In addition, \cite{lasker2014anal} 
-declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity and the bulge luminosity, 
-as opposed to \cite{beifiori2012}, who claimed that the bulge mass is a better tracer of $M_{\rm BH}$ than the galaxy mass.
+declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity as it does with the spheroid luminosity, 
+as opposed to \cite{beifiori2012} who claimed that the spheroid mass is a better tracer of $M_{\rm BH}$ than the galaxy mass.
 The past studies did not converge to the same conclusions 
@@
 We will use these in a series of forthcoming papers to obtain improved black hole mass scaling relations 
-using the largest sample (66) of galaxies to date.
+using the largest sample (66) of galaxies to date with accurate spheroid properties. \\
 
@@
 As explained in Section \ref{sec:res}, 
-this initial sample was ultimately reduced to 66 galaxies for which useful bulge parameters could be obtained.
+this initial sample was ultimately reduced to 66 galaxies for which useful spheroid parameters could be obtained.
 
@@
 \label{sec:corser}
-Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or bulges) 
+Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or spheroids) 
 with partially depleted cores, 
@@
 a (signal-to-noise)-based weighting scheme 
-and results in S\'ersic parameters which describe the bulge less accurately than had no (signal-to-noise)-weighting been used.
+and results in S\'ersic parameters which describe the spheroid less accurately than had no (signal-to-noise)-weighting been used.
 While we have paid careful attention to the components in each galaxy, 
@@
 %\includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
-%\caption{Best-fit model and isophotal parameters for the galaxy NGC 3377. 
+%\caption{the galaxy NGC 3377. 
 %The left panels refer to the major-axis $R_{\rm maj}$, 
@@
 %\includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
-%\caption{Best-fit model and isophotal parameters for the galaxy M59. 
+%\caption{the galaxy M59. 
 %The figure caption is the same as Figure \ref{fig:n3377ex}. 
@@
 %\includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
-%\caption{Best-fit model and isophotal parameters for the galaxy NGC 1332.
+%\caption{the galaxy NGC 1332.
 %The figure caption is the same as Figure \ref{fig:n3377ex}. 
@@
 about a galaxy's constituents.
-\item The ellipticity and position angle of triaxial bulges can vary with radius.
+\item The ellipticity and position angle of triaxial spheroids can vary with radius.
 The analytic functions used by 2D decomposition codes to fit galaxy components have fixed ellipticity and position angle, 
@@
 This should serve as a tip to users of 2D fitting codes. 
-When physically meaningful bulge parameters are required, 
+When physically meaningful spheroid parameters are required, 
 the output may not be reliable and should be inspected.
@@
 \includegraphics[width=\columnwidth]{images/comparison_r_e.eps} 
-\caption{2D versus 1D major-axis measurements of the effective radii. 
+\caption{2D versus 1D major-axis measurements of the spheroid effective radii. 
 The dashed line displays the 1:1 relation.}
@@
 \includegraphics[width=\columnwidth]{images/comparison_n.eps} 
-\caption{2D measurements of the S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
+\caption{2D measurements of the spheroid S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
 The dashed line displays the 1:1 relation.}
@@
 \includegraphics[width=\columnwidth]{images/comparison_mag.eps} 
-\caption{2D versus 1D measurements of the $3.6~\rm \mu m$ bulge magnitudes. The dashed line displays the 1:1 relation.}
+\caption{2D versus 1D measurements of the $3.6~\rm \mu m$ spheroid magnitudes. The dashed line displays the 1:1 relation.}
 \label{fig:mag1d2d}
@@
 errors are dominated by systematics rather than Poisson noise.
-For this reason, we decided to estimate the uncertainties of the bulge best-fit parameters 
+For this reason, we decided to estimate the uncertainties of the spheroid best-fit parameters 
 with a method that took into account systematic errors.
 
-\subsubsection{Goodness of the bulge modeling}
+\subsubsection{Goodness of the spheroid modeling}
 For each of our fits, we calculated the associated $RMS$ scatter using:
@@
 and visually inspect the structures of the residual surface brightness profile 
-(i.e.~the second row in Figure \ref{fig:n2974ex}) within $\sim 1 - 2$ bulge effective radii. 
+(i.e.~the second row in Figure \ref{fig:n2974ex}) within $\sim 1 - 2$ spheroid effective radii. 
 We did this using a grade from 1 to 3, assigned according to the following criteria.
@@
 \item [2)] A grade of 2 was issued in the following cases. 
-The residuals in correspondence with the radial extent of the bulge component are not randomly distributed around zero, 
+The residuals in correspondence with the radial extent of the spheroidal component are not randomly distributed around zero, 
 being symptomatic of a S\'ersic model having a curvature (regulated by the S\'ersic index $n$) 
-that does not quite match the real ``shape'' of the bulge. 
+that does not quite match the real ``shape'' of the spheroid. 
 When we identified, but were not able to accurately model. a galaxy sub-component.
@@
 whose scale length does not quite match the size of the disk as expected from the ellipticity profile or the velocity map).
-When the S\'ersic model used to describe the bulge component has a size -- as measured by the effective radius -- 
+When the S\'ersic model used to describe the spheroidal component has a size -- as measured by the effective radius -- 
 comparable to a few times the $FWHM$ of the PSF.
@@
 \item [3)] A grade of 3 was assigned to the poorer and more anomalous fits, 
-or those affected by an obvious degeneracy between the bulge S\'ersic profile and the remaining model components 
-(e.g.~when the bulge S\'ersic index varies by as much as 50\% among the four different realizations of the fit, 
+or those affected by an obvious degeneracy between the spheroid S\'ersic profile and the remaining model components 
+(e.g.~when the spheroid S\'ersic index varies by as much as 50\% among the four different realizations of the fit, 
 or when the output of the fit strongly depends on the choice of the initial parameters).
@@
 In Figure \ref{fig:compn}, for 58 galaxies, 
-we compare the measurements of the bulge S\'ersic index obtained by different authors 
+we compare the measurements of the spheroid S\'ersic index obtained by different authors 
 with those obtained by us. 
@@
 \subsubsection{Uncertainties on $R_{\rm e,sph}$}
-The uncertainties on the bulge effective radii were computed using the same methodology as employed for the S\'ersic indices. 
+The uncertainties on the spheroid effective radii were computed using the same methodology as employed for the S\'ersic indices. 
 However, in Figure \ref{fig:compre} we include only major-axis measurements of $R_{\rm e,sph}$. 
@@
 \subsubsection{Uncertainties on $m_{\rm sph}$}
-To estimate the uncertainties on the bulge magnitudes, 
+To estimate the uncertainties on the spheroid magnitudes, 
 we compared (see Figure \ref{fig:compmag}) only those literature measurements coming from $K$-band or $3.6~\rm \mu m$ observations.
@@
 \subsubsection{Uncertainties on $\mu_{\rm e,sph}$}
-As for the bulge magnitudes, we estimated the uncertainties on the bulge effective surface brightnesses $\mu_{\rm e,sph}$ 
+As for the spheroid magnitudes, we estimated the uncertainties on the spheroid effective surface brightnesses $\mu_{\rm e,sph}$ 
 by comparing only $K$-band or $3.6~\rm \mu m$ measurements (see Figure \ref{fig:compmue}), 
@@
 where $b_n$ and $\Gamma(2n_{\rm sph})$ are defined in the Appendix, 
-and $(b/a)_{\rm sph}$ is the bulge axis ratio.
+and $(b/a)_{\rm sph}$ is the spheroid axis ratio.
 While \cite{laurikainen2010} and \cite{sani2011} reported their estimates of $(b/a)_{\rm sph}$, 
@@
 \includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
-\caption{Bottom panel: 58 galaxies for which at least one measurement of the bulge S\'ersic index $n_{\rm sph}$ is available 
+\caption{Bottom panel: 58 galaxies for which at least one measurement of the spheroid S\'ersic index $n_{\rm sph}$ is available 
 from the literature (Table \ref{tab:lit}), in addition to that measured by us.
@@
 of the black histogram, respectively, 
-corresponding to our quality flags 1, 2 and 3 given in Table \ref{tab:fitres}.}
+corresponding to our quality flags 1, 2 and 3 given in Table \ref{tab:fitres} (see Section \ref{sec:err} for details).
+We consider these to be absolute upper limits to the uncertainty on our parameters 
+given the care we have taken to minimise sources of systematic errors. }
 \label{fig:compn}
@@
 \includegraphics[width=1.1\columnwidth]{images/comparison_all_r_e.eps} 
-\caption{Bottom panel: 52 galaxies for which at least one measurement of the bulge major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
+\caption{Bottom panel: 52 galaxies for which at least one measurement of the spheroid major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
 from the literature (Table \ref{tab:lit}), in addition to that measured by us.
@@
 \includegraphics[width=1.1\columnwidth]{images/comparison_all_mag_sph.eps} 
-\caption{Bottom panel: 51 galaxies for which at least one measurement of the bulge apparent magnitude $m_{\rm sph}$ 
--- either in $K$-band or $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
-$3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes (see Section \ref{sec:err} for details).
+\caption{Bottom panel: 51 galaxies for which at least one measurement of the spheroid apparent magnitude $m_{\rm sph}$ 
+-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
+The $3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes (see Section \ref{sec:err} for details).
 The average value $\langle m_{\rm sph} \rangle$ is plotted against 
@@
 \includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_e.eps} 
-\caption{Bottom panel: 49 galaxies for which at least one measurement of the bulge effective surface brightness $\mu_{\rm e,sph}$ 
--- either in $K$-band or $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
-$K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
-The average value $\langle \mu_{\rm e,sph} \rangle$ is plotted against 
+\caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid effective surface brightness $\mu_{\rm e,sph}$ 
+-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
+The $K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
+The average value $\langle \mu_{\rm e,sph} \rangle$ from all fits to a galaxy, 
+not to be confused with the mean effective surface brightness within $R_{\rm e,sph}$, is plotted against 
 the difference between the individual measurements of a galaxy 
@@
 \includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_0.eps} 
-\caption{Bottom panel: 49 galaxies for which at least one measurement of the bulge central surface brightness $\mu_{\rm 0,sph}$ 
--- either in $K$-band or $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
-$K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
+\caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid central surface brightness $\mu_{\rm 0,sph}$ 
+-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
+The $K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
 The average value $\langle \mu_{\rm 0,sph} \rangle$ is plotted against 
@@
 \label{sec:concl}
-The widespread presence of embedded components -- such as intermediate-scale disks -- in massive early-type galaxies 
+The widespread presence of embedded components -- in particular intermediate-scale disks -- in massive early-type galaxies 
 makes galaxy decomposition an essential tool to properly investigate the scaling relations between black hole masses 
-and host bulge properties. \\
-Past studies often used different models for the same galaxy, and obtained significantly discrepant results,  
-which led them to draw contrasting conclusions about the black hole--bulge correlations.
-These inconsistencies motivated our effort to secure and refine the measure of bulge properties in a sample of 75 galaxies 
+and host spheroid properties. \\
+Past studies often used different model components for the same galaxy, and obtained significantly discrepant results,  
+which led them to draw contrasting conclusions about the black hole -- spheroid correlations.
+These inconsistencies motivated our effort to refine and secure the measure of spheroid properties in a sample of 66 galaxies 
 with a dynamical estimate of the black hole mass. 
-Using $3.6~\rm \mu m$ \emph{Spitzer} satellite imagery, 
+Using $3.6~\rm \mu m$ \emph{Spitzer} satellite images, 
 we performed state-of-the-art galaxy decompositions. 
-The $3.6~\rm \mu m$ band is an excellent tracer of the stellar mass, superior to optical bands or the $K$-band. 
+The $3.6~\rm \mu m$ band is an excellent tracer of the stellar mass, superior to optical bands and the $K$-band. 
 Considerable care has been taken in the data reduction, image mosaicking, sky subtraction and component model fitting to the galaxy light.
@@
 to identify and explain discrepancies when present. 
-Our analysis additionally benefited from recourse to kinematical information -- not previously used -- to aid the identification of 
+Our analysis additionally benefited from recourse to kinematical information -- not previously used -- to aid in the identification of 
 somewhat face-on disks, or the distinction between intermediate-scale disks and large-scale disks, 
 missed in some past investigations and decompositions.
-Table \ref{tab:lit} summarizes the main characteristics of the five past studies that, since 2007, attempted galaxy decomposition 
-to derive black hole-bulge scaling relations, 
-and highlights, in part, why our endeavor represents a substantial improvement over the past literature.
+Table \ref{tab:lit} summarizes the main characteristics of the five past studies which, since 2007, attempted galaxy decompositions 
+in order to derive black hole -- spheroid scaling relations, 
+and highlights, in part, why our endeavor represents a substantial improvement over the past literature. \\
 
@@
 \begin{center}  				      
-\caption{{\bf Summary of previous investigations of black hole mass scaling relations.} 
-GD07 = \cite{grahamdriver2007}, 
-S+11 = \cite{sani2011}, V+12 \cite{vika2012}, B+12 = \cite{beifiori2012}, L+14 = \cite{lasker2014data}.}
+\caption{Summary of previous investigations of black hole mass scaling relations} 
 \begin{tabular}{lllllll}
@@
 \label{tab:lit} 
+\tablecomments{GD07 = \cite{grahamdriver2007}, 
+S+11 = \cite{sani2011}, V+12 \cite{vika2012}, B+12 = \cite{beifiori2012}, L+14 = \cite{lasker2014data}.}
 \end{center}	
@@
 
-\begin{itemize}
-\item One-dimensional and two-dimensional techniques of galaxy decomposition return the same results when applied to the same galaxy.
+We reveal that one-dimensional and two-dimensional techniques of galaxy decomposition return the same results when applied to the same galaxy.
 However, in our practical experience, the failure rate of two-dimensional decompositions 
@@
 A strong limitation of two-dimensional codes is their inability to accommodate the radial gradients of ellipticity and position angle 
-often observed in galaxy bulges.
-\item We found the interpretation of one-dimensional residual surface brightness profiles easier than that of two-dimensional residual images. 
-A correct interpretation of the residuals is fundamental to determine the optimal model for a galaxy.
-\item A one-dimensional isophotal analysis was extremely helpful and sometimes even necessary to accurately identify galaxy components.
-\item Given the level of detail to which each galaxy decomposition was performed, 
+often observed in galaxy spheroids.
+The interpretation of one-dimensional residual surface brightness profiles is easier than that of two-dimensional residual images. 
+A one-dimensional isophotal analysis was extremely helpful and sometimes even necessary to accurately identify galaxy components.
+A correct interpretation of the residuals is fundamental to understand and determine the optimal model for a galaxy.
+Given the level of detail to which each galaxy decomposition was performed, 
 we believe that our analysis cannot be reproduced by current automatic routines. 
-\item The uncertainties associated with the bulge best-fit parameters are dominated by systematic errors (e.g.~incorrect sky subtraction, 
+The uncertainties associated with the literatur best-fit parameters of the spheroid are dominated by systematic errors (e.g.~incorrect sky subtraction, 
 inaccurate masking of contaminating sources, erroneous choice of model components), and only marginally affected by random errors. 
-For this reason, we developed a method to estimate the uncertainties on the best-fit parameters that takes into account systematic errors.
-\end{itemize}
+For this reason, we developed a method to estimate the uncertainties on the best-fit parameters that takes into account systematic errors 
+(see Figures \ref{fig:compn} -- \ref{fig:compmu0}).
 
 We will use the results from our one-dimensional galaxy decompositions to obtain improved black hole mass scaling relations. 
-We will also derive and explore some unpublished correlations. 
 These results will be presented in a series of forthcoming papers.
@@
   For each galaxy, we show a figure and a table. 
-  The figure illustrates our 1D best-fit model and the galaxy isophotal parameters. 
+  The figure illustrates our 1D model and the galaxy isophotal parameters. 
   The left panels refer to the major-axis $R_{\rm maj}$, 
   while the right panels refer to the equivalent-axis $R_{\rm eq}$, 
-  i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$).
+  i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$), 
+  equivalent to a circularized profile.
   The top panels display the galaxy surface brightness ($\mu$) radial profiles obtained with a linear sampling. 
@@
   The color lines represent the individual (PSF-convolved) model components:
-  red=S\'ersic, dark blue=exponential, green=Gaussian, cyan=Ferrer, gray=Gaussian ring, pink=PSF. 
-  The best-fit parameters for the S\'ersic bulge model are inset.
+  red=S\'ersic; dark blue=exponential; green=Gaussian; cyan=Ferrer; gray=Gaussian ring; pink=PSF. 
+  The parameters for the S\'ersic spheroid model are inset.
   The total (PSF-convolved) model is shown with a black dashed line. 
@@
   $\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
-  The lower six panels show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles. \\
-  The table reports a comparison between our results (from both our 1D and 2D decompositions) and those obtained by the following authors: 
+  The lower six panels show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles from {\tt ellipse}. \\
+  The Tables report a comparison between our results (from both our 1D and 2D decompositions) and those obtained by the following authors: 
   GD07 = \citeauthor{grahamdriver2007} (\citeyear{grahamdriver2007}, who performed 1D fits along the major-axis), 
@@
   When a nuclear component or a partially depleted core have been masked, we signal them as ``m-n'' and ``m-c'', respectively.
-  For example, the model ``S-bul + e-d + e-id + m-n + G-r'' reads ``S\'ersic-bulge + exponential-disk + exponential-inner disk + mask-nucleus + Gaussian-ring''. 
+  For example, the model ``S-bul + e-d + e-id + m-n + G-r'' reads ``S\'ersic-bulge + exponential-disk + exponential-(inner disk) + mask-nucleus + Gaussian-ring''. 
   The core-S\'ersic model used by \cite{rusli2013} is always implicitly associated with the galaxy spheroidal component. 
-  When fitting their galaxy light profiles, \citeauthor{grahamdriver2007} excluded the innermost data points. 
-  Their models implicitly include ``m-n'' or ``m-c''. 
+  \citeauthor{grahamdriver2007} excluded the innermost data points when fitting their galaxy light profiles,  
+  therefore their models implicitly include ``m-n'' or ``m-c''. 
   In the table caption, we comment on the most significant discrepancies between our results and those obtained by the other studies.
@@
   \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for IC 1459.
-  IC 1459 is an elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
-  nuclear dust and an indication of a central stellar disk \citep{forbes1994ic1459}.
+  \caption{IC 1459: 
+  An elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
+  nuclear dust and indications of a nuclear stellar disk \citep{forbes1994ic1459}.
   The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
-  This galaxy has also an unresolved partially depleted core \citep{rusli2013}.  % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
+  This galaxy also has an unresolved partially depleted core \citep{rusli2013}.  % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
   Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
-  T.W. 1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
-  T.W. 2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
-  \hline
-  S+11         & S-bul + G-n   & $61.1$  &  $6.0$ \\
-  R+13         & core-S\'ersic & $45.4$  &  $7.6$ \\
-  L+14         & S-bul + m-c   & $62.4$  &  $8.3$ \\
+  1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
+  1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
+  2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
+  \hline
+  S+11 2D         & S-bul + G-n   & $61.1$  &  $6.0$ \\
+  R+13 1D eq.         & core-S\'ersic & $45.4$  &  $7.6$ \\
+  L+14 2D         & S-bul + m-c   & $62.4$  &  $8.3$ \\
   \hline
@@
   \label{tab:ic1459}
-  %\tablecomments{S+11 obtained the smallest estimate of the S\'ersic index because they fit a nuclear component rather than masking the core. 
-  %R+13 obtained the smallest estimate of the effective radius 
-  %because they fit a circularized light profile that only extends out to $R_{\rm eq} \lesssim 60''$. }
+  \tablecomments{Our results are shown in the upper portion of the Table. 
+  See Section \ref{sec:indgal} for the legend key to the other authors listed in the lower portion of the Table. 
+  See Table \ref{tab:fitres} for our associated surface brightnesses and magnitudes. }
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for IC 2560. IC 2560 is a barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
+  \caption{IC 2560: A barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
   and dust within the central $2''.5$ \citep{martini2003}.
@@
   in the radial range $42'' \lesssim R_{\rm maj} \lesssim 60''$, which is excluded from the fit.
-  Motivated by the presence of a strong optical AGN and dust in the nucleus, 
+  Motivated by the presence of a strong optical AGN and dust in the nucleus (which adds rather than obscures at $3.6\rm~\mu m$), 
   we account for an excess of non-stellar light by adding a central Gaussian component to the model.}
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $6.1$  &  $0.8$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.5$  &  $0.6$ \\
-  \hline
-  S+11         & S-bul + e-d + G-n & $27.5$  &  $2.0$ \\
+  1D maj. & S-bul + e-d + F-bar + G-n & $6.1$  &  $0.8$ \\
+  1D eq.  & S-bul + e-d + F-bar + G-n & $4.5$  &  $0.6$ \\
+  \hline
+  S+11 2D         & S-bul + e-d + G-n & $27.5$  &  $2.0$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for IC 4296.
-  IC 4296 is an elliptical galaxy. 
+  \caption{IC 4296:
+  An elliptical galaxy. 
   Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
   After masking the innermost $6''.1$, 
-  we find that a single S\'ersic profile provides a fairly good description of this galaxy.}
+  we find that a single S\'ersic profile provides a good description of this galaxy.}
   \end{center}
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
-  T.W. 1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
-  T.W. 2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
-  \hline
-  S+11         & S-bul + G-n & $33.6$  &  $4.0$ \\
-  L+14         & S-bul + m-c & $97.8$  &  $8.2$ \\
+  1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
+  1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
+  2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
+  \hline
+  S+11 2D         & S-bul + G-n & $33.6$  &  $4.0$ \\
+  L+14 2D         & S-bul + m-c & $97.8$  &  $8.2$ \\
   \hline
@@
   \tablecomments{
-  S+11 obtained the smallest effective radius and S\'ersic index because they fit a nuclear component rather than masking the core. 
-  %L+14 obtained the largest effective radius and S\'ersic index, 
-  %although the 1D representation of their 2D fit (their Figure 8) shows that their model overestimates the galaxy light at large radii ($R_{\rm maj} > 100''$), 
-  %implying the need for a smaller $R_{\rm e}$ and $n$. 
-  %We suspect that this could be due to the pixel weighting scheme that they used.
+  S+11 obtained a small effective radius and S\'ersic index because they fit a nuclear component rather than masking the core. 
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M31.
-  M31, the Andromeda galaxy, is a spiral galaxy. 
+  \caption{M31 (Andromeda galaxy):
+  A spiral galaxy. 
   Although for decades this galaxy had been classified as an unbarred spiral,
-  recent works have unraveled the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}.
-  M31 also features a ring-like structure at $R_{\rm maj} \sim 50'$ \citep{athanassoulabeaton2006m31}. 
+  recent works have revealed the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}, 
+  seen as the plateau at $800'' \lesssim R_{\rm maj} \lesssim 1000''$.
+  M31 also features a broad ring-like structure at $R_{\rm maj} \sim 50'$ \citep{athanassoulabeaton2006m31}. 
   We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar & $418.6$  &  $2.2$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar & $173.6$  &  $1.3$ \\
+  1D maj. & S-bul + e-d + F-bar & $418.6$  &  $2.2$ \\
+  1D eq.  & S-bul + e-d + F-bar & $173.6$  &  $1.3$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M49.
-  M49, the brightest member of the Virgo cluster, is a giant elliptical galaxy 
+  \caption{M49:
+  The brightest member of the Virgo cluster, a giant elliptical galaxy 
   with a slightly resolved partially depleted core \citep{rusli2013}.  %($R_{\rm break} = 1''.8$, \citealt{rusli2013}).
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c   & $190.2$  &  $6.6$ \\
-  T.W. 1D eq.  & S-bul + m-c   & $135.3$  &  $5.4$ \\
-  T.W. 2D      & S-bul + m-c   & $151.9$  &  $5.5$ \\
-  \hline
-  R+13         & core-S\'ersic & $199.0$  &  $5.6$ \\
+  1D maj. & S-bul + m-c   & $190.2$  &  $6.6$ \\
+  1D eq.  & S-bul + m-c   & $135.3$  &  $5.4$ \\
+  2D      & S-bul + m-c   & $151.9$  &  $5.5$ \\
+  \hline
+  R+13 1D eq.         & core-S\'ersic & $199.0$  &  $5.6$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M59.
-  M59 is an elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
+  \caption{M59:
+  An elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
   and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}. 
-  The intermediate-scale embedded disk is clearly visible in our unsharp mask image, and 
-  the velocity map confirms the presence of a rapidly rotating component, which is modeled with an exponential function.
+  The intermediate-scale embedded disk is clearly visible in our unsharp mask image (not shown), and 
+  the velocity map confirms the presence of this rapidly rotating component, which is modeled with an exponential function.
   We choose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.  
@@
   \hline
-  T.W. 1D maj. & S-bul + m-n + e-id & $48.0$  &  $5.5$ \\
-  T.W. 1D eq.  & S-bul + m-n + e-id & $90.9$  &  $8.8$ \\
-  %T.W. 2D	&    & $$  &  $$ \\
-  \hline 
-  S+11         & S-bul       & $70.1$  &  $5.0$ \\
-  V+12         & S-bul + m-c & $54.7$  &  $5.7$ \\
+  1D maj. & S-bul + m-n + e-id & $48.0$  &  $5.5$ \\
+  1D eq.  & S-bul + m-n + e-id & $90.9$  &  $8.8$ \\
+  %2D	&    & $$  &  $$ \\
+  \hline 
+  S+11 2D         & S-bul       & $70.1$  &  $5.0$ \\
+  V+12 2D         & S-bul + m-c & $54.7$  &  $5.7$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/m64_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M64.
-  M64 is a dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. 
+  \caption{M64: 
+  A dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. 
   A large-scale bar ($R_{\rm maj} \lesssim 50''$) can be identified in the unsharp mask 
-  and produces corresponding peaks in the ellipticity, PA and B4 profiles.
+  and produces corresponding peaks in the ellipticity, $PA$ and $B4$ profiles.
   This is modeled with a Ferrer function.
-  Additional peaks in the ellipticity, PA and B4 profiles at $R_{\rm maj} \sim 15''$ 
+  Additional peaks in the ellipticity, $PA$ and $B4$ profiles at $R_{\rm maj} \sim 15''$ 
   signal the presence of an embedded disky component, that we describe with a low-$n$ S\'ersic function.
   Although the galaxy is dusty and hosts an AGN, we do not observe any nuclear excess of light 
-  in the fit residuals and therefore we consider unnecessary to add a nuclear component to our model. 
+  in the fit residuals and therefore we found it unnecessary to add a nuclear component to our model. 
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + S-id  & $3.8$  &  $0.8$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + S-id  & $4.3$  &  $1.4$ \\
-  %T.W. 2D	&   & $$  & $$  &  $$ \\
-  \hline
-  B+12      & S-bul + e-d  & $5.0$  &  $1.5$ \\
+  1D maj. & S-bul + e-d + F-bar + S-id  & $3.8$  &  $0.8$ \\
+  1D eq.  & S-bul + e-d + F-bar + S-id  & $4.3$  &  $1.4$ \\
+  %2D	&   & $$  & $$  &  $$ \\
+  \hline
+  B+12 2D      & S-bul + e-d  & $5.0$  &  $1.5$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/m81_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M81.
-  M81 is an early-type spiral galaxy.
-  This galaxy features two bars \citep{elmegreen1995m81,gutierrez2011,erwindebattista2013}. 
+  \caption{M81: 
+  An early-type spiral galaxy.
+  This galaxy features a nuclear bar at $R_{\rm maj} \lesssim 17''$ and a large-scale bar at $R_{\rm maj} \lesssim 130''$ 
+  \citep{elmegreen1995m81,gutierrez2011,erwindebattista2013}. 
   We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M81.
   The bars are not particularly evident in the galaxy image or in the unsharp mask. 
-  Any attempt to account for the bars in the fit was unsuccessful. 
+  The bump at $R_{\rm maj} \lesssim 400''$ is due to spiral arms. 
+  Attempts to account for the bars in the fit were unsuccessful. 
   For this reason, we use a simple S\'ersic + exponential model. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d  & $31.0$  &  $1.7$ \\
-  T.W. 1D eq.  & S-bul + e-d  & $33.2$  &  $2.1$ \\
-  %T.W. 2D	&   & $$  & $$  &  $$ \\
-  \hline
-  GD07      & S-bul + e-d	 & $68.1$   &  $3.3$ \\
-  S+11      & S-bul + e-d + G-n  & $127.3$  &  $3.0$ \\
-  B+12      & S-bul + e-d	 & $50.0$   &  $2.6$ \\
+  1D maj. & S-bul + e-d  & $31.0$  &  $1.7$ \\
+  1D eq.  & S-bul + e-d  & $33.2$  &  $2.1$ \\
+  %2D	&   & $$  & $$  &  $$ \\
+  \hline
+  GD07 1D maj.      & S-bul + e-d	 & $68.1$   &  $3.3$ \\
+  S+11 2D      & S-bul + e-d + G-n  & $127.3$  &  $3.0$ \\
+  B+12 2D      & S-bul + e-d	 & $50.0$   &  $2.6$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/m84_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M84.
-  M84 is an elliptical galaxy with a slightly resolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 1''.5$, \citealt{rusli2013}). 
+  \caption{M84:
+  An elliptical galaxy with a slightly resolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 1''.5$, \citealt{rusli2013}). 
   The unsharp mask reveals a faint inner component ($R_{\rm maj} \lesssim 12''$). 
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c   & $101.6$  &  $7.8$ \\
-  T.W. 1D eq.  & S-bul + m-c   & $129.8$  &  $7.9$ \\
-  T.W. 2D      & S-bul + m-c   & $181.8$  &  $8.4$ \\
-  \hline
-  GD07         & S-bul         & $75.1$   &  $5.6$ \\
-  S+11         & S-bul + G-n   & $105.9$  &  $7.0$ \\
-  V+12         & S-bul + m-c   & $28.7$   &  $3.5$ \\
-  B+12         & S-bul         & $63.6$   &  $4.1$ \\
-  R+13         & core-S\'ersic & $126.2$  &  $7.1$ \\
-  L+14         & S-bul + m-c   & $139.0$  &  $8.3$ \\
+  1D maj. & S-bul + m-c   & $101.6$  &  $7.8$ \\
+  1D eq.  & S-bul + m-c   & $129.8$  &  $7.9$ \\
+  2D      & S-bul + m-c   & $181.8$  &  $8.4$ \\
+  \hline
+  GD07 1D maj.         & S-bul         & $75.1$   &  $5.6$ \\
+  S+11 2D         & S-bul + G-n   & $105.9$  &  $7.0$ \\
+  V+12 2D         & S-bul + m-c   & $28.7$   &  $3.5$ \\
+  B+12 2D         & S-bul         & $63.6$   &  $4.1$ \\
+  R+13 1D eq.         & core-S\'ersic & $126.2$  &  $7.1$ \\
+  L+14 2D         & S-bul + m-c   & $139.0$  &  $8.3$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/m87_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M87.
-  M87 is a giant elliptical galaxy belonging to the Virgo cluster.
+  \caption{M87:
+  A giant elliptical galaxy belonging to the Virgo cluster.
   This galaxy has a large ($> 7''$), partially depleted core \citep{ferrarese2006acsvcs}.
   The morphology of M87 is similar to that of M49.
-  The innermost $18''.5$ are excluded from the fit and
+  The innermost $18''.5$ are excluded and
   a S\'ersic model is used to fit M87. 
   We note that the effective radius obtained from our 1D major-axis fit is more than a factor of two larger than that obtained from our 2D fit.
-  This is due to the fact that the 2D model has fixed ellipticity and cannot account for the strong ellipticity gradient of the galaxy.  
+  This is due to the fact that the 2D model has fixed ellipticity and cannot account for the strong ellipticity gradient of the galaxy, 
+  which serves as a warning to some 2D fits in the literature.  
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c  & $203.9$  &  $10.0$ \\
-  T.W. 1D eq.  & S-bul + m-c  & $87.1$   &  $5.9$ \\
-  T.W. 2D      & S-bul + m-c  & $88.3$   &  $4.3$ \\
-  \hline
-  GD07      & S-bul	    & $-$     &  $6.9$ \\
-  S+11      & S-bul + G-n   & $99.5$  &  $4.0$ \\
-  V+12      & S-bul + m-c   & $34.6$  &  $2.4$ \\
-  R+13      & core-S\'ersic & $180.9$ &  $8.9$ \\
-  L+14      & S-bul + m-c   & $122.0$ &  $5.6$ \\
+  1D maj. & S-bul + m-c  & $203.9$  &  $10.0$ \\
+  1D eq.  & S-bul + m-c  & $87.1$   &  $5.9$ \\
+  2D      & S-bul + m-c  & $88.3$   &  $4.3$ \\
+  \hline
+  GD07 1D maj.      & S-bul	    & $-$     &  $6.9$ \\
+  S+11 2D      & S-bul + G-n   & $99.5$  &  $4.0$ \\
+  V+12 2D      & S-bul + m-c   & $34.6$  &  $2.4$ \\
+  R+13 1D eq.      & core-S\'ersic & $180.9$ &  $8.9$ \\
+  L+14 2D      & S-bul + m-c   & $122.0$ &  $5.6$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/m89_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M89.
-  M89 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. 
+  \caption{M89: 
+  An elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. 
   The galaxy halo dominates the light at large radii, where the isophotes are significantly more elliptical than in the inner part of the galaxy. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-halo  & $29.0$  &  $4.6$ \\
-  T.W. 1D eq.  & S-bul + e-halo  & $28.2$  &  $5.1$ \\
-  %T.W. 2D	&   & $$  & $$  &  $$ \\
-  \hline
-  S+11         & S-bul + e-d     & $24.3$  &  $4.0$ \\
-  V+12         & S-bul           & $16.7$  &  $3.6$ \\
-  B+12         & S-bul           & $45.2$  &  $4.3$ \\
-  R+13         & S-bul + S-halo  & $19.8$  &  $3.8$ \\
+  1D maj. & S-bul + e-halo  & $29.0$  &  $4.6$ \\
+  1D eq.  & S-bul + e-halo  & $28.2$  &  $5.1$ \\
+  %2D	&   & $$  & $$  &  $$ \\
+  \hline
+  S+11 2D         & S-bul + e-d     & $24.3$  &  $4.0$ \\
+  V+12 2D         & S-bul           & $16.7$  &  $3.6$ \\
+  B+12 2D         & S-bul           & $45.2$  &  $4.3$ \\
+  R+13 1D eq.         & S-bul + S-halo  & $19.8$  &  $3.8$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/m94_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M94.
-  M94 is a face-on spiral galaxy, with a Seyfert AGN \citep{veroncettyveron2006} and 
+  \caption{M94: 
+  A face-on spiral galaxy, with a Seyfert AGN \citep{veroncettyveron2006} and 
   circumnuclear dust \citep{elmegreen2002m94,peeplesmartini2006m94}.
   This galaxy has a ring-like structure at $R_{\rm maj} \sim 50''$ \citep{munoztunon1989m94}.
-  The ellipticity and B4 profiles display a local maximum at $R_{\rm maj} \sim 10''$, 
+  The ellipticity and $B4$ profiles display a local maximum at $R_{\rm maj} \sim 10''$, 
   indicating the presence of a disky component embedded in the bulge,
@@
   We exclude the data within the innermost $6''.7$, due to the AGN contribution.
-  Any attempt to model the ring was unsuccessful, resulting in a degenerate model, 
-  therefore we also exclude the data in the range $20'' \lesssim R_{\rm maj} \lesssim 80''$.
+  Attempts to model the ring were unsuccessful, resulting in a degenerate model, 
+  therefore we exclude the data in the range $20'' \lesssim R_{\rm maj} \lesssim 80''$.
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar & $11.4$  &  $0.9$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar & $8.4$   &  $1.1$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  1D maj. & S-bul + e-d + F-bar & $11.4$  &  $0.9$ \\
+  1D eq.  & S-bul + e-d + F-bar & $8.4$   &  $1.1$ \\
+  %2D	&  & $$  & $$  &  $$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/m96_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M96.
-  M96 is a spiral galaxy with a large scale bar and no AGN activity \citep{martini2003,nowak2010n3368n3489}. 
+  \caption{M96:
+  A spiral galaxy with a large scale bar and no AGN activity \citep{martini2003,nowak2010n3368n3489}. 
   \cite{erwin2004} observed the presence of two bars in this galaxy. 
@@
   which however are too faint and irregular to be described with a Gaussian ring model. 
-  The large scale bar extends out to $R_{\rm maj} \lesssim 80''$ and is modeled with a Ferrer function.
-  A peak at $R_{\rm maj} \sim 25''$ in the ellipticity profile unravels an inner disky component embedded in the bulge, 
+  The large-scale bar extends out to $R_{\rm maj} \lesssim 80''$ and is modeled with a Ferrer function.
+  A peak at $R_{\rm maj} \sim 25''$ in the ellipticity profile reveals an inner disky component embedded in the bulge, 
   that we model with a low-$n$ S\'ersic profile.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + S-id  & $7.5$  &  $1.5$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + S-id  & $5.3$  &  $1.3$ \\
-  T.W. 2D      & S-bul + e-d + G-bar + G-id  & $8.3$  &  $2.0$ \\
-  \hline
-  S+11         & S-bul + e-d + G-bar  & $45.6$  &  $1.0$ \\
+  1D maj. & S-bul + e-d + F-bar + S-id  & $7.5$  &  $1.5$ \\
+  1D eq.  & S-bul + e-d + F-bar + S-id  & $5.3$  &  $1.3$ \\
+  2D      & S-bul + e-d + G-bar + G-id  & $8.3$  &  $2.0$ \\
+  \hline
+  S+11 2D         & S-bul + e-d + G-bar  & $45.6$  &  $1.0$ \\
   \hline
@@
   The bulge effective radius obtained by S+11 largely exceeds our estimates 
-  because their model does not account for the inner component embedded in the bulge ($R_{\rm maj} \lesssim 25''$). 
+  because their galaxy decomposition does not account for the inner component embedded in the bulge ($R_{\rm maj} \lesssim 25''$). 
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M104. 
-  M104 is a lenticular/spiral galaxy with a partially depleted core. 
+  \caption{M104: 
+  A lenticular/spiral galaxy with a partially depleted core \citep{jardel2011}. 
   The data within the innermost $6''.1$ are excluded from the fit, 
-  and the most obvious ring of the galaxy is modeled.
+  and the most obvious ring of this galaxy is modeled.
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + G-r + m-c  & $11.1$  &  $5.4$ \\
-  T.W. 1D eq.  & S-bul + e-d + G-r + m-c  & $52.5$  &  $7.1$ \\
-  \hline
-  S+11         & S-bul + e-d + G-bar + G-n  & $66.1$  &  $1.5$ \\
+  1D maj. & S-bul + e-d + G-r + m-c  & $11.1$  &  $5.4$ \\
+  1D eq.  & S-bul + e-d + G-r + m-c  & $52.5$  &  $7.1$ \\
+  \hline
+  S+11 2D         & S-bul + e-d + G-bar + G-n  & $66.1$  &  $1.5$ \\
   \hline
@@
   \tablecomments{The bulge S\'ersic index obtained by S+11 is smaller than our estimates because 
-  they fit a nuclear component. }
+  they fit an additional nuclear component. }
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/m105_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M105.
-  M105 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 1''.1$, \citealt{rusli2013}).
+  \caption{M105: 
+  An elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 1''.1$, \citealt{rusli2013}).
   M105 exhibits a mild isophotal twist and an abrupt change of ellipticity at $R_{\rm maj} \sim 30''$.
@@
   However, the addition of a second function (of any analytic form) to the model does not improve the fit.
-  We conclude that the galaxy is not fully relaxed yet, and we fit it with a single S\'ersic profile. 
+  We conclude that the galaxy may not yet be fully relaxed, and we fit it with a single S\'ersic profile. 
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c & $57.2$  &  $5.2$ \\
-  T.W. 1D eq.  & S-bul + m-c & $50.9$  &  $5.3$ \\
-  T.W. 2D      & S-bul + m-c & $73.6$  &  $7.0$ \\
-  \hline
-  GD07         & S-bul & $58.3$  &  $4.3$ \\
-  S+11         & S-bul & $46.0$  &  $5.0$ \\
-  R+13         & core-S\'ersic & $55.1$  &  $5.8$ \\
-  L+14         & S-bul + m-c & $96.3$  &  $9.3$ \\
+  1D maj. & S-bul + m-c & $57.2$  &  $5.2$ \\
+  1D eq.  & S-bul + m-c & $50.9$  &  $5.3$ \\
+  2D      & S-bul + m-c & $73.6$  &  $7.0$ \\
+  \hline
+  GD07 1D maj.         & S-bul & $58.3$  &  $4.3$ \\
+  S+11 2D         & S-bul & $46.0$  &  $5.0$ \\
+  R+13 1D eq.         & core-S\'ersic & $55.1$  &  $5.8$ \\
+  L+14 2D         & S-bul + m-c & $96.3$  &  $9.3$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/m106_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for M106.
-  M106 is a barred spiral galaxy, harbouring a Seyfert AGN \citep{veroncettyveron2006} 
+  \caption{M106: 
+  A barred spiral galaxy, harbouring a Seyfert AGN \citep{veroncettyveron2006} 
   with circumnuclear dust \citep{martini2003}. 
-  We exclude from the fit the innermost $6''.1$ because affected by the AGN emission.
-  The boxy bar, responsible for the minimum in the B4 profile at $R_{\rm maj} \sim 65''$, 
-  is fainter than the large-scale disk and in the light profile is only detectable as a slight swelling
+  We exclude from the fit the innermost $6''.1$ because it is affected by the AGN emission.
+  The boxy bar, responsible for the minimum in the $B4$ profile at $R_{\rm maj} \sim 65''$, 
+  is fainter than the large-scale disk and in the light profile it is only detectable as a slight swelling
   within $65'' \lesssim R_{\rm maj} \lesssim 110''$.
@@
   A peak in the ellipticity profile at $R_{\rm maj} \sim 10''$ suggests the presence of disky component embedded in the bulge, 
-  but a model that accounts for this component is degenerate.
+  but a model that accounts for this component is degenerate with the other fitted components.
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d & $15.3$  &  $2.0$ \\
-  T.W. 1D eq.  & S-bul + e-d & $8.3$   &  $1.2$ \\
-  %T.W. 2D	& & $$  & $$  &  $$ \\
-  \hline
-  GD07     & S-bul + e-d		 & $14.9$   &  $2.0$ \\
-  S+11     & S-bul + e-d + G-n  	 & $111.7$  &  $2.0$ \\
-  V+12 (1) & S-bul + e-d + PSF-n	 & $17.0$   &  $3.5$ \\
-  V+12 (2) & S-bul + e-d + PSF-n + S-bar & $6.3$    &  $2.2$ \\
-  L+14     & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $6.3$	 &  $3.3$ \\
+  1D maj. & S-bul + e-d & $15.3$  &  $2.0$ \\
+  1D eq.  & S-bul + e-d & $8.3$   &  $1.2$ \\
+  %2D	& & $$  & $$  &  $$ \\
+  \hline
+  GD07 1D maj.     & S-bul + e-d		 & $14.9$   &  $2.0$ \\
+  S+11 2D     & S-bul + e-d + G-n  	 & $111.7$  &  $2.0$ \\
+  V+12 2D (1) & S-bul + e-d + PSF-n	 & $17.0$   &  $3.5$ \\
+  V+12 2D (2) & S-bul + e-d + PSF-n + S-bar & $6.3$    &  $2.2$ \\
+  L+14 2D     & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $6.3$	 &  $3.3$ \\
   \hline
@@
   \tablecomments{
-  The bulge effective radius obtained by S+11 largely exceedes all the other estimates.
+  The bulge effective radius obtained by S+11 largely exceedes all the other estimates, behavior noted also in NGC 3031.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n0524_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 0524.
-  NGC 0524 is an unbarred face-on lenticular galaxy. 
-  The unsharp mask of NGC 0524 unravels a faint multi-ring structure in the galaxy disk,
-  with a major ring peaking at $R_{\rm maj} \sim 20''$.
-  We account only for this brightest ring using a Gaussian ring profile.
+  \caption{NGC 0524: 
+  An unbarred face-on lenticular galaxy. 
+  The unsharp mask of NGC 0524 reveals a faint multi-ring structure in the galaxy disk,
+  with a substantial ring peaking at $R_{\rm maj} \sim 20''$.
+  We account for this brightest ring using a Gaussian ring profile.
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + G-r & $6.0$  &  $1.1$ \\
-  T.W. 1D eq.  & S-bul + e-d + G-r & $5.8$  &  $1.1$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  L+10      & S-bul + e-d + 2 F-l & $8.9$   &  $2.7$ \\
-  S+11      & S-bul + e-d	  & $26.8$  &  $3.0$ \\
+  1D maj. & S-bul + e-d + G-r & $6.0$  &  $1.1$ \\
+  1D eq.  & S-bul + e-d + G-r & $5.8$  &  $1.1$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  L+10 2D      & S-bul + e-d + 2 F-l & $8.9$   &  $2.7$ \\
+  S+11 2D      & S-bul + e-d	  & $26.8$  &  $3.0$ \\
   \hline
@@
   Both L+10 and S+11 estimated a S\'ersic index of $\sim$3, 
-  a three times larger value than that obtained by us.
+  three times larger than the value obtained by us.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n0821_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 0821.
-  NGC 0821 is an edge-on elliptical/lenticular galaxy. 
+  \caption{NGC 0821: 
+  An edge-on elliptical/lenticular galaxy. 
   The ellipticity profile and the velocity map show the presence of a faint intermediate-scale disk. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-id + PSF-n & $36.8$  &  $5.4$ \\
-  T.W. 1D eq.  & S-bul + e-id + PSF-n & $20.7$  &  $6.0$ \\
-  T.W. 2D      & S-bul + e-id + m-n   & $33.8$  &  $2.5$ \\
-  \hline
-  GD07    & S-bul 		 & $44.1$   &  $4.0$ \\           
-  S+11    & S-bul 		 & $63.6$   &  $7.0$ \\           
-  B+12    & S-bul 		 & $111.3$  &  $7.7$ \\           
-  L+14    & S-bul + e-d + S-halo & $3.8$    &  $3.1$ \\
+  1D maj. & S-bul + e-id + PSF-n & $36.8$  &  $5.4$ \\
+  1D eq.  & S-bul + e-id + PSF-n & $20.7$  &  $6.0$ \\
+  2D      & S-bul + e-id + m-n   & $33.8$  &  $2.5$ \\
+  \hline
+  GD07 1D maj.    & S-bul 		 & $44.1$   &  $4.0$ \\           
+  S+11 2D    & S-bul 		 & $63.6$   &  $7.0$ \\           
+  B+12 2D    & S-bul 		 & $111.3$  &  $7.7$ \\           
+  L+14 2D    & S-bul + e-d + S-halo & $3.8$    &  $3.1$ \\
   \hline
@@
   \tablecomments{
-  L+14 obtained the smallest estimates of the spheroid effective radius and S\'ersic index because they failed to identify the extent 
+  L+14 obtained a tiny estimate of the spheroid effective radius and a small S\'ersic index because they failed to identify the extent 
   of the intermediate-scale disk. 
@@
   \includegraphics[width=\fitfigurewidth]{images/n1023_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1023.
-  NGC 1023 is a barred lenticular galaxy. 
+  \caption{NGC 1023:
+  A barred lenticular galaxy. 
   The bar extends out to $R_{\rm maj} \lesssim 40''$.
@@
   within $60'' \lesssim R_{\rm maj} \lesssim 125''$ (the data in this range are excluded from the fit), 
-  can be ascribed to some faint residual spiral arms, also noticeable in the 2D residual image. 
-  The peak at $R_{\rm maj} \sim 10''$ in the B4 profile signals the presence of an embedded (and faint) disk.
+  can be ascribed to faint residual spiral arms, also noticeable in the 2D residual image. 
+  The peak at $R_{\rm maj} \sim 10''$ in the $B4$ profile signals the presence of an embedded (and faint) disk.
   The 1D residuals show a structure within $R_{\rm maj} \lesssim 10''$ caused by this unsubtracted 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar & $9.2$  &  $2.1$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar & $7.4$  &  $2.0$ \\
-  T.W. 2D      & S-bul + e-d + G-bar & $6.6$  &  $2.3$ \\
-  \hline
-  GD07    & S-bul + e-d 	& $17.7$  &  $2.0$ \\
-  S+11    & S-bul + e-d + G-bar & $24.0$  &  $3.0$ \\
-  L+14    & S-bul + e-d + S-bar & $9.6$   &  $3.1$ \\
+  1D maj. & S-bul + e-d + F-bar & $9.2$  &  $2.1$ \\
+  1D eq.  & S-bul + e-d + F-bar & $7.4$  &  $2.0$ \\
+  2D      & S-bul + e-d + G-bar & $6.6$  &  $2.3$ \\
+  \hline
+  GD07 1D maj.    & S-bul + e-d 	& $17.7$  &  $2.0$ \\
+  S+11 2D    & S-bul + e-d + G-bar & $24.0$  &  $3.0$ \\
+  L+14 2D    & S-bul + e-d + S-bar & $9.6$   &  $3.1$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n1300_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1300.
-  NGC 1300 is a face-on, barred spiral galaxy. 
+  \caption{NGC 1300: 
+  A face-on, barred spiral galaxy. 
   The morphology of NGC 1300 is quite complex. 
-  In addition to a large scale disk and a bulge, the galaxy is composed of 
-  a large scale bar that extends up to $R_{\rm maj} \lesssim 90''$, two prominent spiral arms 
-  and an inner disk-like component ($R_{\rm maj} \lesssim 5''$), disclosed by the peaks in the ellipticity and PA profiles.
-  We truncate the light profile at $R_{\rm maj} \sim 50''$ and we fit the inwards combination of the large-scale bar and the disk 
+  In addition to a large-scale disk and a bulge, the galaxy is composed of 
+  a large-scale bar that extends up to $R_{\rm maj} \lesssim 90''$, two prominent spiral arms 
+  and an inner disk-like component ($R_{\rm maj} \lesssim 5''$), disclosed by the peaks in the ellipticity and $PA$ profiles.
+  We truncate the light profile at $R_{\rm maj} \sim 50''$ and we fit the inner combination of the large-scale bar and the disk 
   as a single component, using an exponential function. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-(d+bar) + S-id & $9.9$  &  $3.8$ \\
-  T.W. 1D eq.  & S-bul + e-(d+bar) + S-id & $8.1$  &  $3.6$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  S+11    & S-bul + e-d & $85.4$  &  $3.0$ \\
-  L+14    & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $10.4$  &  $4.3$ \\
+  1D maj. & S-bul + e-(d+bar) + S-id & $9.9$  &  $3.8$ \\
+  1D eq.  & S-bul + e-(d+bar) + S-id & $8.1$  &  $3.6$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  S+11 2D    & S-bul + e-d & $85.4$  &  $3.0$ \\
+  L+14 2D    & S-bul + e-d + PSF-n + e-id + S-bar + spiral arms & $10.4$  &  $4.3$ \\
   \hline
@@
   \tablecomments{
-  S+11 overestimated the bulge effective radius mainly because their model does not account for the large-scale bar.
+  S+11 dramatically overestimated the bulge effective radius mainly because their model does not account for the large-scale bar.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n1316_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1316. 
-  NGC 1316 is a merger. 
+  \caption{NGC 1316:  
+  A merger. 
   The galaxy is composed of a bulge, an elongated structure that can be identified with a bar, 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + 2 G-r + G-n & $21.5$  &  $2.0$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + 2 G-r + G-n & $15.9$  &  $1.8$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  S+11      & S-bul + e-d + G-n & $93.0$  &  $5.0$ \\
+  1D maj. & S-bul + e-d + F-bar + 2 G-r + G-n & $21.5$  &  $2.0$ \\
+  1D eq.  & S-bul + e-d + F-bar + 2 G-r + G-n & $15.9$  &  $1.8$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  S+11 2D      & S-bul + e-d + G-n & $93.0$  &  $5.0$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1332.
-  NGC 1332 is an edge-on elliptical/lenticular galaxy. 
-  Given its large stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
-  The ellipticity profile proves the presence of an intermediate-scale disk. 
-  Given the edge-on inclination of such disk, we model it with a low-$n$ S\'ersic profile. 
+  \caption{NGC 1332: 
+  An edge-on elliptical/lenticular galaxy. 
+  The ellipticity profile broadcasts the presence of an intermediate-scale disk. 
+  Given the edge-on inclination of this disk, we model it with a low-$n$ S\'ersic profile. 
   The data within the innermost $6''.1$ are excluded from the fit.
@@
   is significantly different from our best-fit model.
-  \citet{rusli2011} did not identify an intermediate-scale embedded disk, 
+  \citet{rusli2011} did not identify the intermediate-scale embedded disk, 
   but instead proposed a model featuring a S\'ersic bulge ($n_{\rm sph} \sim 2.3$, $R_{\rm e,sph} \sim 8''$), accounting for 43\% of the total light, 
@@
   by an order of magnitude along the $M_{\rm BH}$ direction.
-  Assuming instead that, as follows from our model, 
-  the galaxy spheroid is a factor of two more luminous than what claimed by \citet{rusli2011}, 
-  NGC 1332 would no longer be an outlier in our $M_{\rm BH} - L_{\rm sph}$ diagram. \\
+  Instead, the galaxy spheroid is a factor of two more luminous than claimed by \citet{rusli2011} and  
+  NGC 1332 is not an outlier in our $M_{\rm BH} - L_{\rm sph}$ diagram. \\
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + S-id + m-c & $34.7$  &  $5.1$ \\
-  T.W. 1D eq.  & S-bul + S-id + m-c & $18.0$  &  $3.7$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  1D maj. & S-bul + S-id + m-c & $34.7$  &  $5.1$ \\
+  1D eq.  & S-bul + S-id + m-c & $18.0$  &  $3.7$ \\
+  %2D	&  & $$  & $$  &  $$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n1374_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1374.
-  NGC 1374 is an elliptical galaxy. 
-  A Gaussian function in our model accounts for a relatively faint nuclear component. 
+  \caption{NGC 1374: 
+  An elliptical galaxy. 
+  A Gaussian function in our model accounts for the relatively faint additional nuclear component. 
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + G-n & $25.6$  &  $3.7$ \\
-  T.W. 1D eq.  & S-bul + G-n & $24.8$  &  $4.1$ \\
-  T.W. 2D      & S-bul + m-n & $25.2$  &  $3.7$ \\
+  1D maj. & S-bul + G-n & $25.6$  &  $3.7$ \\
+  1D eq.  & S-bul + G-n & $24.8$  &  $4.1$ \\
+  2D      & S-bul + m-n & $25.2$  &  $3.7$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n1399_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 1399.
-  NGC 1399, the central galaxy of the Fornax cluster, is an elliptical galaxy with a slightly resolved partially depleted core \citep{rusli2013,dullograham2014cores}. 
+  \caption{NGC 1399: 
+  The central galaxy of the Fornax cluster, an elliptical galaxy with a slightly resolved partially depleted core \citep{rusli2013,dullograham2014cores}. 
   %($R_{\rm break} \sim 2''.4$, \citealt{rusli2013,dullograham2014cores}).
   The nuclear activity of NGC 1399 is classified as Seyfert \citep{veroncettyveron2006},
-  but the galaxy lacks of dust \citep{tran2001}.
-  The ellipticity and PA profiles display a steep decline within $R_{\rm maj} \lesssim 60''$,
+  but the galaxy lacks dust emission \citep{tran2001}.
+  The ellipticity and $PA$ profiles display a steep decline with increasing radius within $R_{\rm maj} \lesssim 60''$,
   suggesting the presence of an embedded disk.
-  This inner component is also visible, although very faint, in the unsharp mask.
+  This inner component is also visible, although faint, in the unsharp mask.
   We note that, after excluding the innermost $6''.1$,
   a single S\'ersic profile is not sufficient to describe the whole galaxy light profile.
-  The addition of an inner exponential function to the model notably improves the fit.
+  The addition of an inner exponential function to model the disk notably improves the fit.
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c + e-id & $405.2$  &  $10.0$ \\
-  T.W. 1D eq.  & S-bul + m-c + e-id & $338.1$  &  $10.0$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  GD07         & S-bul  		    & $-$      &  $16.8$ \\
-  R+13         & core-S\'ersic + (S+e)-halo & $36.2$   &  $7.4$ \\
-  L+14         & S-bul + m-c		    & $154.0$  &  $11.1$ \\
+  1D maj. & S-bul + m-c + e-id & $405.2$  &  $10.0$ \\
+  1D eq.  & S-bul + m-c + e-id & $338.1$  &  $10.0$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  GD07 1D maj.        & S-bul  		    & $-$      &  $16.8$ \\
+  R+13 1D eq.         & core-S\'ersic + (S+e)-halo & $36.2$   &  $7.4$ \\
+  L+14 2D             & S-bul + m-c		    & $154.0$  &  $11.1$ \\
   \hline
@@
   \tablecomments{
-  R+13 used a combination of a S\'ersic + exponential profile to model the halo of this galaxy, 
+  R+13 used a combination of a S\'ersic + exponential profile to model the galaxy's halo, 
   and obtained the smallest estimate of the effective radius, 
-  which is at odds with the fact that central cluster galaxies typically have very large sizes. 
-  L+14 finds an effective radius which is a factor of two smaller than that obtained by us 
-  because their data have a smaller radial extent ($R_{\rm maj} \lesssim 130'$). 
+  and one which is at odds with the fact that central cluster galaxies typically have large sizes. 
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n2273_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 2273.
-  NGC 2273 is a barred spiral galaxy with a Seyfert AGN \citep{contini1998} 
+  \caption{NGC 2273: 
+  A barred spiral galaxy with a Seyfert AGN \citep{contini1998} 
   and circumnuclear dust \citep{simoeslopes2007}. 
@@
   Although NGC 2273 hosts an optical AGN and nuclear dust, no central excess of light is observed in the 1D residuals.
-  The addition of a nuclear component to the model does not significantly improve the fit or change the bulge parameters. 
+  The addition of a nuclear component to the model does not significantly improve the fit nor change the bulge parameters. 
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar & $1.6$  &  $2.1$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar & $1.9$  &  $2.7$ \\
-  %T.W. 2D	&  & $$  &  $$ \\
-  \hline
-  L+10         & S-bul + e-d + F-bar & $2.6$  &  $1.8$ \\
+  1D maj. & S-bul + e-d + F-bar & $1.6$  &  $2.1$ \\
+  1D eq.  & S-bul + e-d + F-bar & $1.9$  &  $2.7$ \\
+  %2D	&  & $$  &  $$ \\
+  \hline
+  L+10 2D         & S-bul + e-d + F-bar & $2.6$  &  $1.8$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n2549_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 2549.
-  NGC 2549 is an edge-on barred lenticular galaxy. 
-  Although the edge-on inclination of NGC 2549 complicates the identification of embedded components, 
+  \caption{NGC 2549: 
+  An edge-on barred lenticular galaxy. 
+  Although the edge-on inclination of NGC 2549 complicates the identification of additional embedded components, 
   a large-scale bar ($R_{\rm maj} \lesssim 45''$) can be recognized in the galaxy image and -- more easily -- in the light profile.
-  We describe the large scale bar with a Ferrer profile.
+  We model the large-scale bar with a Ferrer function.
   A peak in the ellipticity profile discloses the presence of a disky component
   embedded in the bulge ($R_{\rm maj} \lesssim 10''$).
-  This inner component can be spotted also by looking at the velocity map.
-  We fit it with a Ferrer profile.
+  This inner component can be spotted also by looking at the velocity map, and 
+  we fit it with a Ferrer function.
   }
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + F-id & $6.1$  &  $2.3$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + F-id & $3.1$  &  $1.5$ \\
-  T.W. 2D      & S-bul + e-d + G-bar + G-id & $5.6$  &  $2.1$ \\
-  \hline
-  S+11         & S-bul + e-d & $11.6$  &  $7.0$ \\
+  1D maj. & S-bul + e-d + F-bar + F-id & $6.1$  &  $2.3$ \\
+  1D eq.  & S-bul + e-d + F-bar + F-id & $3.1$  &  $1.5$ \\
+  2D      & S-bul + e-d + G-bar + G-id & $5.6$  &  $2.1$ \\
+  \hline
+  S+11 2D         & S-bul + e-d & $11.6$  &  $7.0$ \\
   \hline
@@
   \tablecomments{
-  The model of S+11 does not account for the large-scale bar and largely overestimates the bulge S\'ersic index.
+  The model of S+11 does not account for the large-scale bar and therefore largely overestimates the bulge S\'ersic index.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n2778_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 2778.
-  NGC 2778 is a face-on lenticular galaxy. 
-  The peak in the ellipticity profile at $R_{\rm maj} \sim 5''$ unravels the existence of a nuclear component 
+  \caption{NGC 2778: 
+  A face-on lenticular galaxy. 
+  The peak in the ellipticity profile at $R_{\rm maj} \sim 5''$ reveals the existence of a nuclear component 
   embedded in the galaxy bulge.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + PSF-n & $2.3$  &  $1.3$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + PSF-n & $2.2$  &  $1.2$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  GD07         & S-bul + e-d	     & $2.3$  &  $1.6$ \\
-  S+11         & S-bul + e-d	     & $2.5$  &  $2.5$ \\
-  V+12         & S-bul + e-d	     & $1.5$  &  $2.7$ \\
-  L+14         & S-bul + e-d + S-bar & $2.8$  &  $4.0$ \\
+  1D maj. & S-bul + e-d + F-bar + PSF-n & $2.3$  &  $1.3$ \\
+  1D eq.  & S-bul + e-d + F-bar + PSF-n & $2.2$  &  $1.2$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  GD07 1D maj.         & S-bul + e-d	     & $2.3$  &  $1.6$ \\
+  S+11 2D         & S-bul + e-d	     & $2.5$  &  $2.5$ \\
+  V+12 2D         & S-bul + e-d	     & $1.5$  &  $2.7$ \\
+  L+14 2D         & S-bul + e-d + S-bar & $2.8$  &  $4.0$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n2787_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 2787.
-  NGC 2787 is a barred lenticular galaxy with LINER nuclear activity \citep{veroncettyveron2006}.
+  \caption{NGC 2787: 
+  A barred lenticular galaxy with LINER nuclear activity \citep{veroncettyveron2006}.
   An inner disk is embedded in the bulge of this galaxy \citep{erwin2003n2787}.
@@
   NGC 2787 has an undoubtedly complex morphology. 
-  This galaxy is composed of a bulge, a large scale disk, a bar (see the peaks in the ellipticity, PA and B4 profiles
+  This galaxy is composed of a bulge, a large-scale disk, a bar (see the peaks in the ellipticity, $PA$ and $B4$ profiles
   at $R_{\rm maj} \sim 30''$) with two ansae, an inner disk (or bar?) embedded in the bulge (see the peak in the ellipticity profile
@@
   %\hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + F-id + PSF-nucleus & $4.8$  &  $1.1$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + F-id + PSF-nucleus & $3.3$  &  $1.3$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  1D maj. & S-bul + e-d + F-bar + F-id + PSF-nucleus & $4.8$  &  $1.1$ \\
+  1D eq.  & S-bul + e-d + F-bar + F-id + PSF-nucleus & $3.3$  &  $1.3$ \\
+  %2D	&  & $$  & $$  &  $$ \\
   \hline
@@
   %%\hline
-  %T.W. 1D maj. & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.6$  &  $1.1$ \\
-  %T.W. 1D eq.  & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.4$  &  $2.2$ \\
-  %%T.W. 2D	&  & $$  & $$  &  $$ \\
+  %1D maj. & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.6$  &  $1.1$ \\
+  %1D eq.  & S-bul + S-d + F-bar + F-id + PSF-nucleus & $4.4$  &  $2.2$ \\
+  %%2D	&  & $$  & $$  &  $$ \\
   %\hline
-  GD07         & S-bul + e-d					  & $4.6$   &  $2.0$ \\
-  L+10         & S-bul + e-d + F-bar + F-l			  & $4.0$   &  $1.3$ \\
-  S+11         & S-bul + e-d + G-bar + G-n			  & $15.7$  &  $3.0$ \\
-  L+14         & S-bul + trunc. e-d + trunc. S-bar + S-id + PSF-n & $14.3$  &  $2.8$ \\
+  GD07 1D maj.         & S-bul + e-d					  & $4.6$   &  $2.0$ \\
+  L+10 2D         & S-bul + e-d + F-bar + F-l			  & $4.0$   &  $1.3$ \\
+  S+11 2D         & S-bul + e-d + G-bar + G-n			  & $15.7$  &  $3.0$ \\
+  L+14 2D         & S-bul + trunc. e-d + trunc. S-bar + S-id + PSF-n & $14.3$  &  $2.8$ \\
   \hline
@@
   S+11 found larger estimates of the effective radius and S\'ersic index because they did not account for the inner disk. 
-  L+14 also reported a larger effective radius and S\'ersic index because they employed an unusual truncated exponential disk and 
+  L+14 also reported a larger effective radius and S\'ersic index because they employed a truncated exponential disk and 
   truncated S\'ersic bar in their galaxy model. 
@@
   \includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 2974.
-  NGC 2974 is a spiral galaxy which has been misclassified as an elliptical galaxy in the RC3 catalog.
+  \caption{NGC 2974: 
+  A spiral galaxy which has been misclassified as an elliptical galaxy in the RC3 catalog.
   The galaxy hosts a Seyfert AGN \citep{veroncettyveron2006} and filamentary dust in its center \citep{tran2001}.
@@
   and an elongated bar-like component within $R_{\rm maj} \lesssim 30''$, that we fit with a Ferrer function.
-  The bar produces a peak in the ellipticity profile at $R_{\rm maj} \sim 20''$.
+  The pseudo-ring produces a peak in the $B4$ profile at $R_{\rm maj} \sim 50''$ and 
+  the bar produces a peak in the ellipticity profile at $R_{\rm maj} \sim 20''$.
   Although the ring is extremely faint, it is important to account for it in the galaxy decomposition. 
-  A model without the ring component results in a ``steeper'' exponential-disk (the disk has a smaller scale length 
-  and a brighter central surface brightness) and produces bad residuals within $R_{\rm maj} \lesssim 40''$.
+  A model without the ring component results in a ``steeper'' exponential-disk (i.e. the disk would have a smaller scale length 
+  and a brighter central surface brightness) and produces poor residuals within $R_{\rm maj} \lesssim 40''$.
   The nuclear component is fit with a Gaussian profile.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + G-n + G-r & $8.3$   &  $1.4$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + G-n + G-r & $6.9$   &  $1.2$ \\
-  T.W. 2D      & S-bul + e-d + G-bar + m-n	 & $10.6$  &  $1.3$ \\
-  \hline
-  S+11         & S-bul + G-n & $27.2$  &  $3.0$ \\
+  1D maj. & S-bul + e-d + F-bar + G-n + G-r & $8.3$   &  $1.4$ \\
+  1D eq.  & S-bul + e-d + F-bar + G-n + G-r & $6.9$   &  $1.2$ \\
+  2D      & S-bul + e-d + G-bar + m-n	 & $10.6$  &  $1.3$ \\
+  \hline
+  S+11 2D         & S-bul + G-n & $27.2$  &  $3.0$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n3079_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3079.
-  NGC3079 is an edge-on, late-type barred spiral galaxy 
+  \caption{NGC 3079:
+  An edge-on, late-type barred spiral galaxy 
   with a Seyfert AGN \citep{veroncettyveron2006} and circumnuclear dust \citep{martini2003}. 
@@
   We truncate the light profile at $R_{\rm maj} \sim 65''$, before the ``edge'' of the bar, 
-  and we model the combination of the disk and the bar with a Ferrer function. 
+  and we successfully model the combination of the disk and the bar with a Ferrer function. 
   A Gaussian function accounts for the AGN emission. 
@@
   \hline
-  T.W. 1D maj. & S-bul + F-(bar+d) + G-n  & $6.8$  &  $1.3$ \\
-  T.W. 1D eq.  & S-bul + F-(bar+d) + G-n  & $4.3$  &  $1.1$ \\
-  \hline
-  S+11         & S-bul + e-d + G-bar + G-n & $74.1$  &  $2.0$ \\
+  1D maj. & S-bul + F-(bar+d) + G-n  & $6.8$  &  $1.3$ \\
+  1D eq.  & S-bul + F-(bar+d) + G-n  & $4.3$  &  $1.1$ \\
+  \hline
+  S+11 2D         & S-bul + e-d + G-bar + G-n & $74.1$  &  $2.0$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n3091_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3091.
-  NGC 3091 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 0''.62$, \citealt{rusli2013}).
+  \caption{NGC 3091: 
+  An elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 0''.62$, \citealt{rusli2013}).
   The data within the innermost $6''.1$ are excluded from the fit.
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c & $100.5$  &  $7.6$ \\
-  T.W. 1D eq.  & S-bul + m-c & $51.2$	&  $6.6$ \\
-  T.W. 2D      & S-bul + m-c & $67.1$	&  $6.7$ \\
-  \hline
-  R+13         & core-S\'ersic & $91.0$  &  $9.3$ \\
+  1D maj. & S-bul + m-c & $100.5$  &  $7.6$ \\
+  1D eq.  & S-bul + m-c & $51.2$	&  $6.6$ \\
+  2D      & S-bul + m-c & $67.1$	&  $6.7$ \\
+  \hline
+  R+13 1D eq.         & core-S\'ersic & $91.0$  &  $9.3$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n3115_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3115.
-  NGC 3115 is an edge-on elliptical/lenticular galaxy. 
-  This galaxy features a nuclear stellar disk (with size $\sim 1''$, \citealt{scorzabender1995,ledo2010}).
-  NGC 3115 has an intermediate scale disk.
-  This is immediately evident by looking at the ellipticity and B4 profiles.
-  Going from the galaxy center to the outskirts, the ellipticity increases until it reaches a maximum 
+  \caption{NGC 3115:
+  An edge-on elliptical/lenticular galaxy. 
+  This galaxy features an intermediate-scale disk and a nuclear stellar disk (with size $\sim 1''$, \citealt{scorzabender1995,ledo2010}).
+  The presence of the intermediate-scale disk 
+  is immediately evident by looking at the ellipticity and $B4$ profiles.
+  From the galaxy center to the outskirts, the ellipticity increases until it reaches a maximum 
   ($\epsilon \sim 0.65$) at $R_{\rm maj} \sim 90''$. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + G-r & $43.6$  &  $4.4$ \\
-  T.W. 1D eq.  & S-bul + e-d + G-r & $34.4$  &  $5.1$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  %GD07         & ??? TBD	       & $-$	&  $13.0$ \\
-  S+11         & S-bul + e-d	       & $27.1$ &  $3.0$ \\
-  L+14         & S-bul + e-d + S-halo  & $3.9$  &  $3.0$ \\
+  1D maj. & S-bul + e-d + G-r & $43.6$  &  $4.4$ \\
+  1D eq.  & S-bul + e-d + G-r & $34.4$  &  $5.1$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  %GD07 1D maj.         & ??? TBD	       & $-$	&  $13.0$ \\
+  S+11 2D         & S-bul + e-d	       & $27.1$ &  $3.0$ \\
+  L+14 2D         & S-bul + e-d + S-halo  & $3.9$  &  $3.0$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n3227_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3227.
-  NGC 3227 is a spiral galaxy with a large-scale bar. 
+  \caption{NGC 3227: 
+  A spiral galaxy with a large-scale bar. 
   This galaxy hosts a Seyfert AGN \citep{khachikian1974} and circumnuclear dust \citep{martini2003}. 
   The large-scale bar produces an evident bump in the major-axis surface brightness profile,
-  which is curiously absent in the equivalent-axis profile. 
+  which is absent in the equivalent-axis profile. 
   We model the bar with a Ferrer function and the nucleus with a Gaussian function. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + G-n   & $8.1$  &  $1.7$ \\
-  T.W. 1D eq.  & S-bul + e-d + [F-bar] + G-n & $4.6$  &  $1.1$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  L+04         & S-bul + e-d + F-bar & $1.8$  &  $2.2$ \\
-  S+11         & S-bul + e-d	     & $82.9$ &  $4.0$ \\
-  L+14         & S-bul + e-d + S-bar & $0.7$  &  $4.1$ \\
+  1D maj. & S-bul + e-d + F-bar + G-n   & $8.1$  &  $1.7$ \\
+  1D eq.  & S-bul + e-d + [F-bar] + G-n & $4.6$  &  $1.1$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  L+10 2D         & S-bul + e-d + F-bar & $1.8$  &  $2.2$ \\
+  S+11 2D         & S-bul + e-d	     & $82.9$ &  $4.0$ \\
+  L+14 2D         & S-bul + e-d + S-bar & $0.7$  &  $4.1$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n3245_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3245.
-  NGC 3245 is a lenticular galaxy.
+  \caption{NGC 3245:
+  A lenticular galaxy.
   The unsharp mask reveals the presence of an embedded disk ($R_{\rm maj} \lesssim 15''$), 
-  confirmed by the corresponding peaks in the ellipticity and B4 profiles.
+  confirmed by the corresponding peaks in the ellipticity and $B4$ profiles.
   We model this inner component with a Ferrer function. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-id & $4.4$  &  $2.9$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-id & $2.4$  &  $1.7$ \\
-  T.W. 2D      & S-bul + e-d + G-id & $1.9$  &  $1.8$ \\
-  \hline
-  GD07         & S-bul + e-d		& $11.3$ &  $4.3$ \\
-  L+10         & S-bul + e-(d+l) + F-id & $4.0$  &  $2.4$ \\
-  S+11         & S-bul + e-d		& $4.6$  &  $2.5$ \\
-  V+12         & S-bul + e-d		& $3.5$  &  $2.6$ \\
-  B+12         & S-bul + e-d		& $4.0$  &  $1.6$ \\
-  L+14         & S-bul + e-d + S-bar	& $2.0$  &  $1.6$ \\
+  1D maj. & S-bul + e-d + F-id & $4.4$  &  $2.9$ \\
+  1D eq.  & S-bul + e-d + F-id & $2.4$  &  $1.7$ \\
+  2D      & S-bul + e-d + G-id & $1.9$  &  $1.8$ \\
+  \hline
+  GD07 1D maj.         & S-bul + e-d		& $11.3$ &  $4.3$ \\
+  L+10 2D         & S-bul + e-(d+l) + F-id & $4.0$  &  $2.4$ \\
+  S+11 2D         & S-bul + e-d		& $4.6$  &  $2.5$ \\
+  V+12 2D         & S-bul + e-d		& $3.5$  &  $2.6$ \\
+  B+12 2D         & S-bul + e-d		& $4.0$  &  $1.6$ \\
+  L+14 2D         & S-bul + e-d + S-bar	& $2.0$  &  $1.6$ \\
   \hline
@@
   \label{tab:n3245}
-%  \tablecomments{
-%  GD07 found the largest estimates of the bulge effective radius and S\'ersic index.
-%  }
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3377.
+  \caption{NGC 3377.
   NGC 3377 is an elliptical/lenticular galaxy with an intermediate-scale disk and a nuclear stellar disk \citep{ledo2010}. 
@@
   \hline
-  T.W. 1D maj. & S-bul + 2 e-id     & $61.8$  &  $7.7$ \\
-  T.W. 1D eq.  & S-bul + 2 e-id     & $91.7$  &  $9.2$ \\
-  T.W. 2D      & S-bul + e-id + m-n & $71.8$  &  $3.7$ \\
-  \hline
-  GD07         & S-bul     		     & $44.1$  &  $3.0$ \\
-  S+11         & S-bul     		     & $55.2$  &  $6.0$ \\
-  B+12         & S-bul     		     & $43.5$  &  $3.5$ \\
-  L+14         & S-bul + e-id + e-d + S-halo & $10.1$  &  $6.0$ \\
+  1D maj. & S-bul + 2 e-id     & $61.8$  &  $7.7$ \\
+  1D eq.  & S-bul + 2 e-id     & $91.7$  &  $9.2$ \\
+  2D      & S-bul + e-id + m-n & $71.8$  &  $3.7$ \\
+  \hline
+  GD07 1D maj.         & S-bul     		     & $44.1$  &  $3.0$ \\
+  S+11 2D         & S-bul     		     & $55.2$  &  $6.0$ \\
+  B+12 2D         & S-bul     		     & $43.5$  &  $3.5$ \\
+  L+14 2D         & S-bul + e-id + e-d + S-halo & $10.1$  &  $6.0$ \\
   \hline
@@
   \label{tab:n3377}
-  \tablecomments{L+14 obtained the smallest estimate of the effective radius because they oversubtracted a halo.   
+  \tablecomments{L+14 2D obtained the smallest estimate of the effective radius because they oversubtracted a halo.   
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n3384_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3384.
+  \caption{NGC 3384.
   NGC 3384 is a barred lenticular galaxy that hosts 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + m-n & $5.5$  &  $1.6$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + m-n & $5.6$  &  $1.8$ \\
-  %T.W. 2D	&  & $$  &  $$ \\
-  \hline
-  GD07         & S-bul + e-d		      & $2.5$  &  $1.7$ \\
-  L+10         & S-bul + e-d + 2 F-bar        & $4.0$  &  $1.5$ \\
-  S+11         & S-bul + e-d + G-bar	      & $4.4$  &  $2.5$ \\
-  B+12         & S-bul + e-d		      & $8.3$  &  $2.3$ \\
-  L+14         & S-bul + e-d + 2 S-id + S-bar & $5.9$  &  $2.5$ \\
+  1D maj. & S-bul + e-d + F-bar + m-n & $5.5$  &  $1.6$ \\
+  1D eq.  & S-bul + e-d + F-bar + m-n & $5.6$  &  $1.8$ \\
+  %2D	&  & $$  &  $$ \\
+  \hline
+  GD07 1D maj.         & S-bul + e-d		      & $2.5$  &  $1.7$ \\
+  L+10 2D         & S-bul + e-d + 2 F-bar        & $4.0$  &  $1.5$ \\
+  S+11 2D         & S-bul + e-d + G-bar	      & $4.4$  &  $2.5$ \\
+  B+12 2D         & S-bul + e-d		      & $8.3$  &  $2.3$ \\
+  L+14 2D         & S-bul + e-d + 2 S-id + S-bar & $5.9$  &  $2.5$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n3393_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3393.
+  \caption{NGC 3393.
   NGC 3393 is an edge-on spiral galaxy hosting a Seyfert AGN \citep{diaz1988n3393} and 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar & $1.4$  &  $3.4$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar & $1.4$  &  $2.6$ \\
-  T.W. 2D      & S-bul + e-d + G-bar & $1.2$  &  $1.9$ \\
+  1D maj. & S-bul + e-d + F-bar & $1.4$  &  $3.4$ \\
+  1D eq.  & S-bul + e-d + F-bar & $1.4$  &  $2.6$ \\
+  2D      & S-bul + e-d + G-bar & $1.2$  &  $1.9$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n3414_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3414.
+  \caption{NGC 3414.
   NGC 3414 is a peculiar lenticular/elliptical galaxy. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-id + G-r & $28.0$  &  $4.8$ \\
-  T.W. 1D eq.  & S-bul + e-id + G-r & $25.5$  &  $4.5$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  L+10         & S-bul + e-d + F-bar	  & $5.0$  &  $2.6$ \\
+  1D maj. & S-bul + e-id + G-r & $28.0$  &  $4.8$ \\
+  1D eq.  & S-bul + e-id + G-r & $25.5$  &  $4.5$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  L+10 2D         & S-bul + e-d + F-bar	  & $5.0$  &  $2.6$ \\
   \hline
@@
   \tablecomments{
-  L+10 used a model with a large-scale exponential disk, thus they obtained a smaller bulge effective radius and S\'ersic index.
+  L+10 2D used a model with a large-scale exponential disk, thus they obtained a smaller bulge effective radius and S\'ersic index.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n3489_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3489.
+  \caption{NGC 3489.
   NGC 3489 is a barred lenticular galaxy. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar & $2.2$  &  $1.5$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar & $1.7$  &  $1.3$ \\
-  T.W. 2D      & S-bul + e-d + G-bar & $1.7$  &  $2.1$ \\
-  \hline
-  L+10         & S-bul + e-d + F-bar & $2.0$  &  $2.1$ \\
-  S+11         & S-bul + e-d & $4.6$  &  $1.5$ \\
+  1D maj. & S-bul + e-d + F-bar & $2.2$  &  $1.5$ \\
+  1D eq.  & S-bul + e-d + F-bar & $1.7$  &  $1.3$ \\
+  2D      & S-bul + e-d + G-bar & $1.7$  &  $2.1$ \\
+  \hline
+  L+10 2D         & S-bul + e-d + F-bar & $2.0$  &  $2.1$ \\
+  S+11 2D         & S-bul + e-d & $4.6$  &  $1.5$ \\
   \hline
@@
   %\tablecomments{
-  %S+11 did not fit the bar and thus obtained a larger estimate of the bulge effective radius.
+  %S+11 2D did not fit the bar and thus obtained a larger estimate of the bulge effective radius.
   %}
@@
   \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3585. 
+  \caption{NGC 3585. 
   NGC 3585 is an elliptical galaxy with an embedded disk \citep{scorzabender1995}. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-id & $105.0$  &  $5.2$ \\
-  T.W. 1D eq.  & S-bul + e-id & $86.3$  &  $6.3$ \\
-  \hline
-  S+11         & S-bul + e-d      & $15.5$   &  $2.5$ \\
+  1D maj. & S-bul + e-id & $105.0$  &  $5.2$ \\
+  1D eq.  & S-bul + e-id & $86.3$  &  $6.3$ \\
+  \hline
+  S+11 2D         & S-bul + e-d      & $15.5$   &  $2.5$ \\
   \hline
@@
   \tablecomments{
-  S+11 obtained smaller estimates of the effective radius and S\'ersic index because
+  S+11 2D obtained smaller estimates of the effective radius and S\'ersic index because
   they oversubtracted a large-scale disk.
@@
   \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3607. 
+  \caption{NGC 3607. 
   NGC 3607 is an elliptical galaxy with an embedded disk. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-id & $69.3$  &  $5.5$ \\
-  T.W. 1D eq.  & S-bul + e-id & $65.5$  &  $5.6$ \\
-  T.W. 2D      & S-bul + e-id & $60.0$  &  $5.3$ \\
-  \hline
-  L+10	   & S-bul + e-d      & $6.5$   &  $1.5$ \\
-  S+11	   & S-bul + G-n      & $44.6$  &  $5.0$ \\
-  B+12	   & S-bul	      & $56.3$  &  $4.7$ \\
+  1D maj. & S-bul + e-id & $69.3$  &  $5.5$ \\
+  1D eq.  & S-bul + e-id & $65.5$  &  $5.6$ \\
+  2D      & S-bul + e-id & $60.0$  &  $5.3$ \\
+  \hline
+  L+10 2D	   & S-bul + e-d      & $6.5$   &  $1.5$ \\
+  S+11 2D	   & S-bul + G-n      & $44.6$  &  $5.0$ \\
+  B+12 2D	   & S-bul	      & $56.3$  &  $4.7$ \\
   \hline
@@
   \label{tab:n3607}
-  \tablecomments{L+10 obtained the smallest estimates of the effective radius and S\'ersic index because
+  \tablecomments{L+10 2D obtained the smallest estimates of the effective radius and S\'ersic index because
   they oversubtracted a large-scale disk.
@@
   \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3608.
+  \caption{NGC 3608.
   NGC 3608 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013} 
@@
   \hline
-  T.W. 1D maj. & S-bul & $47.5$  &  $5.2$ \\
-  T.W. 1D eq.  & S-bul & $43.4$  &  $5.7$ \\
-  T.W. 2D      & S-bul & $62.0$  &  $7.0$ \\
-  \hline
-  S+11         & S-bul            & $56.4$  &  $6.0$ \\
-  B+12         & S-bul            & $182.2$  &  $9.0$ \\
-  R+13         & core-S\'ersic    & $56.9$  &  $6.3$ \\
-  L+14         & S-bul            & $48.9$  &  $6.6$ \\
+  1D maj. & S-bul & $47.5$  &  $5.2$ \\
+  1D eq.  & S-bul & $43.4$  &  $5.7$ \\
+  2D      & S-bul & $62.0$  &  $7.0$ \\
+  \hline
+  S+11 2D         & S-bul            & $56.4$  &  $6.0$ \\
+  B+12 2D         & S-bul            & $182.2$  &  $9.0$ \\
+  R+13 1D eq.         & core-S\'ersic    & $56.9$  &  $6.3$ \\
+  L+14 2D         & S-bul            & $48.9$  &  $6.6$ \\
   \hline
@@
   \label{tab:n3608}
-  \tablecomments{B+12 obtained the largest estimates of the effective radius and S\'ersic index, 
+  \tablecomments{B+12 2D obtained the largest estimates of the effective radius and S\'ersic index, 
   possibly due to incorrect sky subtraction. }
@@
   \includegraphics[width=\fitfigurewidth]{images/n3842exp_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3842.
+  \caption{NGC 3842.
   NGC 3842 is the brightest member of the Leo Cluster (Abell 1367).
@@
   \hline
-  T.W. 1D maj. & S-bul + F-l + m-c  & $100.7$  &  $8.1$ \\
-  T.W. 1D eq.  & S-bul + F-l + m-c  & $73.6$   &  $8.2$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  R+13         & core-S\'ersic & $58.8$  &  $6.3$ \\
+  1D maj. & S-bul + F-l + m-c  & $100.7$  &  $8.1$ \\
+  1D eq.  & S-bul + F-l + m-c  & $73.6$   &  $8.2$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  R+13 1D eq.         & core-S\'ersic & $58.8$  &  $6.3$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n3998_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 3998.
+  \caption{NGC 3998.
   NGC 3998 is a barred lenticular galaxy with a Seyfert AGN and nuclear dust \citep{knapp1996n3998}.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + F-l + G-n + G-r & $5.8$  &  $1.2$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + F-l + G-n + G-r & $4.8$  &  $1.3$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  L+10         & S-bul + e-d + F-bar + F-l & $5.0$  &  $2.0$ \\
-  S+11         & S-bul + e-d + G-bar + G-n & $4.7$  &  $1.5$ \\
-  B+12         & S-bul + e-d & $5.7$  &  $2.3$ \\
-  L+14         & S-bul + trunc. e-d + PSF-n + S-bar + S-id & $2.0$  &  $1.1$ \\
+  1D maj. & S-bul + e-d + F-bar + F-l + G-n + G-r & $5.8$  &  $1.2$ \\
+  1D eq.  & S-bul + e-d + F-bar + F-l + G-n + G-r & $4.8$  &  $1.3$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  L+10 2D         & S-bul + e-d + F-bar + F-l & $5.0$  &  $2.0$ \\
+  S+11 2D         & S-bul + e-d + G-bar + G-n & $4.7$  &  $1.5$ \\
+  B+12 2D         & S-bul + e-d & $5.7$  &  $2.3$ \\
+  L+14 2D         & S-bul + trunc. e-d + PSF-n + S-bar + S-id & $2.0$  &  $1.1$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n4026_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4026.
+  \caption{NGC 4026.
   NGC 4026 is an edge-on lenticular galaxy with a nuclear stellar disk (with size $\lesssim 0''.5$, \citealt{ledo2010}).
   The unsharp mask reveals the presence of a bar ($R_{\rm maj} \lesssim 30''$) and of a disky component 
-  embedded in the bulge, that is responsible for the peak at $R_{\rm maj} \sim 5''$ in the B4 profile.
+  embedded in the bulge, that is responsible for the peak at $R_{\rm maj} \sim 5''$ in the $B4$ profile.
   The disky component can be also recognized in the velocity map.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + S-id & $3.4$  &  $2.4$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + S-id & $6.3$  &  $2.1$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  S+11         & S-bul + e-d & $11.4$  &  $3.5$ \\
+  1D maj. & S-bul + e-d + F-bar + S-id & $3.4$  &  $2.4$ \\
+  1D eq.  & S-bul + e-d + F-bar + S-id & $6.3$  &  $2.1$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  S+11 2D         & S-bul + e-d & $11.4$  &  $3.5$ \\
   \hline
@@
   \label{tab:n4026}
-  \tablecomments{S+11 obtained larger estimates of the bulge effective radius and S\'ersic index because they did not model the bar.}
+  \tablecomments{S+11 2D obtained larger estimates of the bulge effective radius and S\'ersic index because they did not model the bar.}
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n4151_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4151.
+  \caption{NGC 4151.
   NGC 4151 is a face-on barred spiral galaxy that hosts a Seyfert AGN \citep{veroncettyveron2006} 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + S-bar [+ m-n] & $7.6$  &  $1.4$ \\
-  T.W. 1D eq.  & S-bul + e-d + S-bar [+ m-n] & $6.8$  &  $1.9$ \\
-  %T.W. 2D      & S-bul + e-d + S-bar + m-n & $$  &  $$ \\
-  \hline
-  S+11         & S-bul + e-d + G-n         & $5.4$  &  $3.5$ \\
+  1D maj. & S-bul + e-d + S-bar [+ m-n] & $7.6$  &  $1.4$ \\
+  1D eq.  & S-bul + e-d + S-bar [+ m-n] & $6.8$  &  $1.9$ \\
+  %2D      & S-bul + e-d + S-bar + m-n & $$  &  $$ \\
+  \hline
+  S+11 2D         & S-bul + e-d + G-n         & $5.4$  &  $3.5$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n4261_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4261.
+  \caption{NGC 4261.
   NGC 4261 is an elliptical galaxy with a LINER nucleus \citep{veroncettyveron2006}
@@
   The galaxy features an unresolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
-  The ellipticity profile has a peak at $R_{\rm maj} \sim 10''$, unraveling the presence of an embedded component, 
+  The ellipticity profile has a peak at $R_{\rm maj} \sim 10''$, revealing the presence of an embedded component, 
   that we model with a Ferrer function.
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c + F-id & $52.6$  &  $4.7$ \\
-  T.W. 1D eq.  & S-bul + m-c + F-id & $47.3$  &  $4.3$ \\
-  T.W. 2D      & S-bul + m-c + e-id & $50.4$  &  $4.4$ \\
-  \hline
-  GD07      & S-bul		& $88.6$  &  $7.3$ \\
-  S+11      & S-bul + e-d + G-n & $22.6$  &  $4.0$ \\
-  V+12      & S-bul + m-c	& $24.2$  &  $3.5$ \\
-  B+12      & S-bul		& $48.8$  &  $4.3$ \\
-  R+13      & core-S\'ersic	& $77.1$  &  $6.3$ \\
-  L+14      & S-bul + m-c	& $68.4$  &  $6.5$ \\
+  1D maj. & S-bul + m-c + F-id & $52.6$  &  $4.7$ \\
+  1D eq.  & S-bul + m-c + F-id & $47.3$  &  $4.3$ \\
+  2D      & S-bul + m-c + e-id & $50.4$  &  $4.4$ \\
+  \hline
+  GD07 1D maj.      & S-bul		& $88.6$  &  $7.3$ \\
+  S+11 2D      & S-bul + e-d + G-n & $22.6$  &  $4.0$ \\
+  V+12 2D      & S-bul + m-c	& $24.2$  &  $3.5$ \\
+  B+12 2D      & S-bul		& $48.8$  &  $4.3$ \\
+  R+13 1D eq.      & core-S\'ersic	& $77.1$  &  $6.3$ \\
+  L+14 2D      & S-bul + m-c	& $68.4$  &  $6.5$ \\
   \hline
@@
   \tablecomments{
-  S+11 found the smallest estimate of the effective radius because they added a large-scale disk to their model.
-  V+12 obtained a small estimate of the effective radius because of the limited radial extent of their data.
+  S+11 2D found the smallest estimate of the effective radius because they added a large-scale disk to their model.
+  V+12 2D obtained a small estimate of the effective radius because of the limited radial extent of their data.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4291_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4291.
+  \caption{NGC 4291.
   NGC 4291 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c & $15.0$  &  $4.2$ \\
-  T.W. 1D eq.  & S-bul + m-c & $15.4$  &  $5.9$ \\
-  T.W. 2D      & S-bul + m-c & $20.8$  &  $7.7$ \\
-  \hline
-  GD07         & S-bul         & $14.8$  &  $4.0$ \\
-  R+13         & core-S\'ersic & $15.3$  &  $5.6$ \\
-  L+14         & S-bul + m-c   & $21.3$  &  $8.6$ \\
+  1D maj. & S-bul + m-c & $15.0$  &  $4.2$ \\
+  1D eq.  & S-bul + m-c & $15.4$  &  $5.9$ \\
+  2D      & S-bul + m-c & $20.8$  &  $7.7$ \\
+  \hline
+  GD07 1D maj.         & S-bul         & $14.8$  &  $4.0$ \\
+  R+13 1D eq.         & core-S\'ersic & $15.3$  &  $5.6$ \\
+  L+14 2D         & S-bul + m-c   & $21.3$  &  $8.6$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n4388_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4388.
+  \caption{NGC 4388.
   NGC 4388 is an edge-on spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006} 
   and copious nuclear dust \citep{martini2003}.
-  The peaks at $R_{\rm maj} \sim 30''$ in the ellipticity and B4 profiles signal the presence of a bar.
+  The peaks at $R_{\rm maj} \sim 30''$ in the ellipticity and $B4$ profiles signal the presence of a bar.
   The data between $35'' \lesssim R_{\rm maj} \lesssim 65''$ are excluded from the fit.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $4.6$  &  $0.6$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.2$  &  $1.3$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
+  1D maj. & S-bul + e-d + F-bar + G-n & $4.6$  &  $0.6$ \\
+  1D eq.  & S-bul + e-d + F-bar + G-n & $4.2$  &  $1.3$ \\
+  %2D	&  & $$  & $$  &  $$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n4459_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4459.
+  \caption{NGC 4459.
   NGC 4459 is a lenticular galaxy.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + G-n & $18.4$  &  $3.1$ \\
-  T.W. 1D eq.  & S-bul + e-d + G-n & $13.0$  &  $2.6$ \\
-  %T.W. 2D	&  & $$  &  $$ \\
-  \hline
-  L+10      & S-bul + e-d + F-l & $7.0$   &  $3.0$ \\
-  S+11      & S-bul + e-d	& $10.3$  &  $2.5$ \\
-  V+12      & S-bul + M-n	& $25.0$  &  $3.9$ \\
-  B+12      & S-bul		& $155.2$ &  $7.4$ \\
+  1D maj. & S-bul + e-d + G-n & $18.4$  &  $3.1$ \\
+  1D eq.  & S-bul + e-d + G-n & $13.0$  &  $2.6$ \\
+  %2D	&  & $$  &  $$ \\
+  \hline
+  L+10 2D      & S-bul + e-d + F-l & $7.0$   &  $3.0$ \\
+  S+11 2D      & S-bul + e-d	& $10.3$  &  $2.5$ \\
+  V+12 2D      & S-bul + M-n	& $25.0$  &  $3.9$ \\
+  B+12 2D      & S-bul		& $155.2$ &  $7.4$ \\
   \hline
@@
   \tablecomments{
-  B+12 did not model the large-scale disk and thus overestimated the bulge effective radius and S\'ersic index.
+  B+12 2D did not model the large-scale disk and thus overestimated the bulge effective radius and S\'ersic index.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4473_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4473.
+  \caption{NGC 4473.
   NGC 4473 is an elliptical galaxy with an embedded disk \citep{ledo2010}.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-id + G-n & $45.9$  &  $2.3$ \\
-  T.W. 1D eq.  & S-bul + e-id + G-n & $36.9$  &  $2.9$ \\
-  %T.W. 2D	&  & $$  &  $$ \\
-  \hline
-  GD07      & S-bul                 & $39.6$   &  $2.7$ \\
-  S+11      & S-bul                 & $49.3$   &  $7.0$ \\
-  V+12      & S-bul + m-c           & $21.3$   &  $4.3$ \\
-  B+12      & S-bul + e-d           & $10.6$   &  $2.2$ \\
-  L+14      & S-bul                 & $27.9$   &  $5.1$ \\
+  1D maj. & S-bul + e-id + G-n & $45.9$  &  $2.3$ \\
+  1D eq.  & S-bul + e-id + G-n & $36.9$  &  $2.9$ \\
+  %2D	&  & $$  &  $$ \\
+  \hline
+  GD07 1D maj.      & S-bul                 & $39.6$   &  $2.7$ \\
+  S+11 2D      & S-bul                 & $49.3$   &  $7.0$ \\
+  V+12 2D      & S-bul + m-c           & $21.3$   &  $4.3$ \\
+  B+12 2D      & S-bul + e-d           & $10.6$   &  $2.2$ \\
+  L+14 2D      & S-bul                 & $27.9$   &  $5.1$ \\
   \hline
@@
   \tablecomments{
-  B+12 obtained the smallest estimates of the effective radius and S\'ersic index because they oversubtracted a large-scale disk. 
+  B+12 2D obtained the smallest estimates of the effective radius and S\'ersic index because they oversubtracted a large-scale disk. 
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4564_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4564.
+  \caption{NGC 4564.
   NGC 4564 is an edge-on lenticular galaxy.
-  In the unsharp mask, one can glimpse an oval structure extending out to $R_{\rm maj} \lesssim 15''$ (see the peak in the B4 profile).
+  In the unsharp mask, one can glimpse an oval structure extending out to $R_{\rm maj} \lesssim 15''$ (see the peak in the $B4$ profile).
   Fitting NGC 4564 with a S\'ersic + exponential model produces bad residuals.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-l & $5.0$  &  $2.6$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-l & $6.0$  &  $3.0$ \\
-  %T.W. 2D	&  & $$  &  $$ \\
-  \hline
-  GD07      & S-bul + e-d & $4.3$  &  $3.2$ \\
-  S+11      & S-bul + e-d & $25.0$ &  $7.0$ \\
-  V+12      & S-bul + e-d & $3.0$  &  $3.7$ \\
+  1D maj. & S-bul + e-d + F-l & $5.0$  &  $2.6$ \\
+  1D eq.  & S-bul + e-d + F-l & $6.0$  &  $3.0$ \\
+  %2D	&  & $$  &  $$ \\
+  \hline
+  GD07 1D maj.      & S-bul + e-d & $4.3$  &  $3.2$ \\
+  S+11 2D      & S-bul + e-d & $25.0$ &  $7.0$ \\
+  V+12 2D      & S-bul + e-d & $3.0$  &  $3.7$ \\
   \hline
@@
   \label{tab:n4564}
-  \tablecomments{The most dicrepant results are obtained by S+11, although they used the same model as GD07 and V+12. }
+  \tablecomments{The most dicrepant results are obtained by S+11 2D, although they used the same model as GD07 1D maj. and V+12 2D. }
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n4596_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4596.
+  \caption{NGC 4596.
   NGC 4596 is an edge-on barred lenticular galaxy.
@@
   $60'' \lesssim R_{\rm maj} \lesssim 130''$ (see also \citealt{comeron2014}).
-  An additional embedded disky component ($R_{\rm maj} \lesssim 15''$) can be recognized in the B4 profile and in the velocity map.
+  An additional embedded disky component ($R_{\rm maj} \lesssim 15''$) can be recognized in the $B4$ profile and in the velocity map.
   The bump in the light profile within $60'' \lesssim R_{\rm maj} \lesssim 70''$ corresponds to the ansae of the bar.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + G-r + S-id & $6.6$  &  $2.7$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + G-r + S-id & $9.0$  &  $3.0$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  L+10      & S-bul + e-d + F-bar + F-l & $2.8$  &  $1.4$ \\
-  S+11      & S-bul + e-d + G-bar & $28.0$  &  $3.0$ \\
-  V+12      & S-bul + e-d + S-bar & $13.2$  &  $3.6$ \\
-  B+12      & S-bul + e-d & $44.9$  &  $4.4$ \\
+  1D maj. & S-bul + e-d + F-bar + G-r + S-id & $6.6$  &  $2.7$ \\
+  1D eq.  & S-bul + e-d + F-bar + G-r + S-id & $9.0$  &  $3.0$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  L+10 2D      & S-bul + e-d + F-bar + F-l & $2.8$  &  $1.4$ \\
+  S+11 2D      & S-bul + e-d + G-bar & $28.0$  &  $3.0$ \\
+  V+12 2D      & S-bul + e-d + S-bar & $13.2$  &  $3.6$ \\
+  B+12 2D      & S-bul + e-d & $44.9$  &  $4.4$ \\
   \hline
@@
   \tablecomments{
-  B+12 fit nor the bar neither the inner disk and obtained the largest estimates of the bulge effective radius and S\'ersic index.
-  The models of S+11 and V+12 do not account for the inner disk and thus result in larger estimates of the bulge effective radius.
+  B+12 2D fit nor the bar neither the inner disk and obtained the largest estimates of the bulge effective radius and S\'ersic index.
+  The models of S+11 2D and V+12 2D do not account for the inner disk and thus result in larger estimates of the bulge effective radius.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4697_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4697.
+  \caption{NGC 4697.
   NGC 4697 is an elliptical galaxy with an embedded disk \citep{scorzabender1995}.
@@
   \hline
-  T.W. 1D maj. & S-bul + 2 S-id & $239.3$  &  $7.2$ \\
-  T.W. 1D eq.  & S-bul + 2 S-id & $226.4$  &  $6.7$ \\
-  T.W. 2D      & S-bul + e-id	& $121.4$  &  $5.0$ \\
-  \hline
-  GD07  & S-bul & $-$  &  $4.0$ \\
-  S+11  & S-bul & $100.5$  &  $5.0$ \\
-  V+12  & S-bul & $39.1$  &  $3.8$ \\
-  V+12  & S-bul + e-d & $10.0$  &  $2.9$ \\
-  L+14  & S-bul + e-d + PSF-n + S-halo & $6.3$  &  $2.1$ \\
+  1D maj. & S-bul + 2 S-id & $239.3$  &  $7.2$ \\
+  1D eq.  & S-bul + 2 S-id & $226.4$  &  $6.7$ \\
+  2D      & S-bul + e-id	& $121.4$  &  $5.0$ \\
+  \hline
+  GD07 1D maj.  & S-bul & $-$  &  $4.0$ \\
+  S+11 2D  & S-bul & $100.5$  &  $5.0$ \\
+  V+12 2D  & S-bul & $39.1$  &  $3.8$ \\
+  V+12 2D  & S-bul + e-d & $10.0$  &  $2.9$ \\
+  L+14 2D  & S-bul + e-d + PSF-n + S-halo & $6.3$  &  $2.1$ \\
   \hline
@@
   \tablecomments{
-  In both their models, V+12 underestimated the effective radius and the S\'ersic index because of the small radial range of their data. 
-  L+14 oversubtracted a large-scale disk and a halo, and thus underestimated the spheroid effective radius and the S\'ersic index. 
+  In both their models, V+12 2D underestimated the effective radius and the S\'ersic index because of the small radial range of their data. 
+  L+14 2D oversubtracted a large-scale disk and a halo, and thus underestimated the spheroid effective radius and the S\'ersic index. 
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4889.
+  \caption{NGC 4889.
   NGC 4889 is the brightest member of the Coma cluster. 
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c & $119.7$  &  $8.1$ \\
-  T.W. 1D eq.  & S-bul + m-c & $60.8$	&  $6.8$ \\
-  T.W. 2D      & S-bul + m-c & $104.3$  &  $7.8$ \\
-  \hline
-  R+13         & core-S\'ersic & $169.2$  &  $9.8$ \\
+  1D maj. & S-bul + m-c & $119.7$  &  $8.1$ \\
+  1D eq.  & S-bul + m-c & $60.8$	&  $6.8$ \\
+  2D      & S-bul + m-c & $104.3$  &  $7.8$ \\
+  \hline
+  R+13 1D eq.         & core-S\'ersic & $169.2$  &  $9.8$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n4945_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 4945.
+  \caption{NGC 4945.
   NGC 4945 is an edge-on, dusty spiral galaxy that hosts a Seyfert AGN \citep{lin2011}.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d & $13.9$  &  $1.4$ \\
-  T.W. 1D eq.  & S-bul + e-d & $9.5$   &  $1.7$ \\
-  T.W. 2D      & S-bul + e-d & $16.2$  &  $0.8$ \\
+  1D maj. & S-bul + e-d & $13.9$  &  $1.4$ \\
+  1D eq.  & S-bul + e-d & $9.5$   &  $1.7$ \\
+  2D      & S-bul + e-d & $16.2$  &  $0.8$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n5077_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 5077. 
+  \caption{NGC 5077. 
   NGC 5077 is an elliptical galaxy with an unresolved partially depleted core \citep{trujillo2004coresersicmodel}. 
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c & $23.5$  &  $4.2$ \\
-  T.W. 1D eq.  & S-bul + m-c & $23.0$  &  $5.7$ \\
-  T.W. 2D      & S-bul + m-c & $30.5$  &  $6.8$ \\
-  \hline
-  S+11         & S-bul + G-n & $29.2$  &  $6.0$ \\
+  1D maj. & S-bul + m-c & $23.5$  &  $4.2$ \\
+  1D eq.  & S-bul + m-c & $23.0$  &  $5.7$ \\
+  2D      & S-bul + m-c & $30.5$  &  $6.8$ \\
+  \hline
+  S+11 2D         & S-bul + G-n & $29.2$  &  $6.0$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n5128_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 5128.
+  \caption{NGC 5128.
   NGC 5128 is a merging system. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-halo + G-n & $61.3$  &  $1.2$ \\
-  T.W. 1D eq.  & S-bul + e-halo + G-n & $60.8$  &  $2.2$ \\
-  %T.W. 2D	&  & $$  & $$  &  $$ \\
-  \hline
-  S+11         & S-bul + e-d + G-n    & $103.6$  &  $3.5$ \\
+  1D maj. & S-bul + e-halo + G-n & $61.3$  &  $1.2$ \\
+  1D eq.  & S-bul + e-halo + G-n & $60.8$  &  $2.2$ \\
+  %2D	&  & $$  & $$  &  $$ \\
+  \hline
+  S+11 2D         & S-bul + e-d + G-n    & $103.6$  &  $3.5$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n5576_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 5576.
+  \caption{NGC 5576.
   NGC 5576 is an elliptical galaxy with a disturbed morphology. 
@@
   \hline
-  T.W. 1D maj. & S-bul  & $61.5$  &  $3.3$ \\
-  T.W. 1D eq.  & S-bul  & $49.3$  &  $3.7$ \\
-  T.W. 2D      & S-bul  & $45.9$  &  $8.3$ \\
-  \hline
-  S+11      & S-bul & $34.3$  &  $7.0$ \\
-  V+12      & S-bul & $16.9$  &  $5.1$ \\
-  B+12      & S-bul & $77.6$  &  $8.7$ \\
+  1D maj. & S-bul  & $61.5$  &  $3.3$ \\
+  1D eq.  & S-bul  & $49.3$  &  $3.7$ \\
+  2D      & S-bul  & $45.9$  &  $8.3$ \\
+  \hline
+  S+11 2D      & S-bul & $34.3$  &  $7.0$ \\
+  V+12 2D      & S-bul & $16.9$  &  $5.1$ \\
+  B+12 2D      & S-bul & $77.6$  &  $8.7$ \\
   \hline
@@
   \label{tab:n5845}
-  \tablecomments{The results obtained by S+11 and B+12 best agree with the results from our 2D model, 
+  \tablecomments{The results obtained by S+11 2D and B+12 2D best agree with the results from our 2D model, 
   in which we did not mask the inner region of the galaxy. 
-  The small radial extent of the data used by V+12 led them to underestimate the effective radius.}
+  The small radial extent of the data used by V+12 2D led them to underestimate the effective radius.}
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n5845_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 5845.
+  \caption{NGC 5845.
   NGC 5845 is an elliptical/lenticular galaxy. 
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d & $3.6$  &  $2.5$ \\
-  T.W. 1D eq.  & S-bul + e-d & $3.1$  &  $2.3$ \\
-  T.W. 2D      & S-bul + e-d & $2.8$  &  $2.4$ \\
-  \hline
-  GD07      & S-bul & $4.1$  &  $3.2$ \\
-  S+11      & S-bul & $3.7$  &  $3.0$ \\
-  V+12      & S-bul & $3.5$  &  $2.6$ \\
-  B+12      & S-bul & $4.1$  &  $3.5$ \\
-  L+14      & S-bul & $3.5$  &  $2.8$ \\
+  1D maj. & S-bul + e-d & $3.6$  &  $2.5$ \\
+  1D eq.  & S-bul + e-d & $3.1$  &  $2.3$ \\
+  2D      & S-bul + e-d & $2.8$  &  $2.4$ \\
+  \hline
+  GD07 1D maj.      & S-bul & $4.1$  &  $3.2$ \\
+  S+11 2D      & S-bul & $3.7$  &  $3.0$ \\
+  V+12 2D      & S-bul & $3.5$  &  $2.6$ \\
+  B+12 2D      & S-bul & $4.1$  &  $3.5$ \\
+  L+14 2D      & S-bul & $3.5$  &  $2.8$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n5846_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 5846.
+  \caption{NGC 5846.
   NGC 5846 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c & $105.1$  &  $6.4$ \\
-  T.W. 1D eq.  & S-bul + m-c & $83.4$	&  $5.7$ \\
-  T.W. 2D      & S-bul + m-c & $85.1$	&  $5.2$ \\
-  \hline
-  S+11      & S-bul	    & $36.4$   &  $3.0$ \\
-  V+12      & S-bul + m-c   & $46.3$   &  $3.7$ \\
-  R+13      & core-S\'ersic & $113.2$  &  $5.3$ \\
+  1D maj. & S-bul + m-c & $105.1$  &  $6.4$ \\
+  1D eq.  & S-bul + m-c & $83.4$	&  $5.7$ \\
+  2D      & S-bul + m-c & $85.1$	&  $5.2$ \\
+  \hline
+  S+11 2D      & S-bul	    & $36.4$   &  $3.0$ \\
+  V+12 2D      & S-bul + m-c   & $46.3$   &  $3.7$ \\
+  R+13 1D eq.      & core-S\'ersic & $113.2$  &  $5.3$ \\
   \hline
@@
   \label{tab:n5846}
-  \tablecomments{S+11 did not mask the core and thus underestimated the effective radius and S\'ersic index. }
+  \tablecomments{S+11 2D did not mask the core and thus underestimated the effective radius and S\'ersic index. }
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n6251_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 6251.
+  \caption{NGC 6251.
   NGC 6251 is an elliptical galaxy. Its large stellar velocity dispersion suggests the presence of a partially depleted core.
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c & $41.7$  &  $6.8$ \\
-  T.W. 1D eq.  & S-bul + m-c & $30.1$  &  $5.6$ \\
-  T.W. 2D      & S-bul + m-c & $39.3$  &  $7.1$ \\
-  \hline
-  GD07      & S-bul	     & $173.9$  &  $11.8$ \\
-  S+11      & S-bul + G-n    & $42.4$	&  $7.0$ \\
-  L+14      & S-bul	     & $20.6$	&  $5.0$ \\
+  1D maj. & S-bul + m-c & $41.7$  &  $6.8$ \\
+  1D eq.  & S-bul + m-c & $30.1$  &  $5.6$ \\
+  2D      & S-bul + m-c & $39.3$  &  $7.1$ \\
+  \hline
+  GD07 1D maj.      & S-bul	     & $173.9$  &  $11.8$ \\
+  S+11 2D      & S-bul + G-n    & $42.4$	&  $7.0$ \\
+  L+14 2D      & S-bul	     & $20.6$	&  $5.0$ \\
   \hline
@@
   \label{tab:n6251}
-  \tablecomments{It is not clear why GD07 obtained the largest estimates of the effective radius and S\'ersic index.}
+  \tablecomments{It is not clear why GD07 1D maj. obtained the largest estimates of the effective radius and S\'ersic index.}
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n7052_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 7052.
+  \caption{NGC 7052.
   NGC 7052 is an elliptical galaxy with an unresolved partially depleted core \citep{quillen2000}. %% ($R_{\rm break} = 0''.8$, \citealt{quillen2000}). 
@@
   %\multicolumn{4}{c}{\emph{excluding innermost $6''.1$}} \\
-  T.W. 1D maj. & S-bul + m-c & $59.4$  &  $4.2$ \\
-  T.W. 1D eq.  & S-bul + m-c & $37.0$  &  $5.6$ \\
-  T.W. 2D      & S-bul + m-c & $36.2$  &  $4.0$ \\
+  1D maj. & S-bul + m-c & $59.4$  &  $4.2$ \\
+  1D eq.  & S-bul + m-c & $37.0$  &  $5.6$ \\
+  2D      & S-bul + m-c & $36.2$  &  $4.0$ \\
   \hline
   %\multicolumn{4}{c}{\emph{including innermost $6''.1$}} \\
-  %T.W. 1D maj. & S-bul & $66.1$  &  $4.8$ \\
-  %T.W. 1D eq.  & S-bul & $35.0$  &  $5.0$ \\
-  %%T.W. 2D	&  & $$  & $$  &  $$ \\
+  %1D maj. & S-bul & $66.1$  &  $4.8$ \\
+  %1D eq.  & S-bul & $35.0$  &  $5.0$ \\
+  %%2D	&  & $$  & $$  &  $$ \\
   %\hline
-  GD07      & S-bul & $70.4$  &  $4.6$ \\
-  S+11      & S-bul & $39.3$  &  $5.0$ \\
-  V+12      & S-bul + e-d & $4.3$  &  $1.8$ \\
-  L+14      & S-bul & $26.6$  &  $4.2$ \\
+  GD07 1D maj.      & S-bul & $70.4$  &  $4.6$ \\
+  S+11 2D      & S-bul & $39.3$  &  $5.0$ \\
+  V+12 2D      & S-bul + e-d & $4.3$  &  $1.8$ \\
+  L+14 2D      & S-bul & $26.6$  &  $4.2$ \\
   \hline
@@
   \label{tab:n7052}
-  \tablecomments{The model of V+12 oversubtracts a large-scale disk and thus results in the lowest estimates of the effective radius and S\'ersic index.}
+  \tablecomments{The model of V+12 2D oversubtracts a large-scale disk and thus results in the lowest estimates of the effective radius and S\'ersic index.}
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n7619_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 7619.
+  \caption{NGC 7619.
   NGC 7619 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %% ($R_{\rm break} = 0''.5$, \citealt{rusli2013}).
@@
   \hline
-  T.W. 1D maj. & S-bul + e-id & $63.2$  &  $5.3$ \\
-  T.W. 1D eq.  & S-bul + e-id & $58.0$  &  $5.2$ \\
-  \hline
-  R+13      & core-S\'ersic & $100.1$  &  $9.3$ \\
+  1D maj. & S-bul + e-id & $63.2$  &  $5.3$ \\
+  1D eq.  & S-bul + e-id & $58.0$  &  $5.2$ \\
+  \hline
+  R+13 1D eq.      & core-S\'ersic & $100.1$  &  $9.3$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n7768_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for NGC 7768.
+  \caption{NGC 7768.
   NGC 7768 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
@@
   \hline
-  T.W. 1D maj. & S-bul + m-c & $92.9$  &  $8.4$ \\
-  T.W. 1D eq.  & S-bul + m-c & $42.1$  &  $6.7$ \\
-  \hline
-  R+13      & core-S\'ersic & $46.1$  &  $6.2$ \\
+  1D maj. & S-bul + m-c & $92.9$  &  $8.4$ \\
+  1D eq.  & S-bul + m-c & $42.1$  &  $6.7$ \\
+  \hline
+  R+13 1D eq.      & core-S\'ersic & $46.1$  &  $6.2$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/ugc03789_1Dfit.eps}
-  \caption{Best-fit model and isophotal parameters for UGC 03789.
+  \caption{UGC 03789.
   UGC 03789 is a face-on spiral galaxy.
   This galaxy features a ring ($R_{\rm maj} \sim 20''$) and a nuclear bar ($R_{\rm maj} \lesssim 4''$),
-  which can be seen in the unsharp mask and produces corresponding peaks in the ellipticity and PA profiles.
+  which can be seen in the unsharp mask and produces corresponding peaks in the ellipticity and $PA$ profiles.
   The bar is fit with a Ferrer function.
@@
   \hline
-  T.W. 1D maj. & S-bul + e-d + F-bar + G-r & $1.8$  &  $1.9$ \\
-  T.W. 1D eq.  & S-bul + e-d + F-bar + G-r & $2.4$  &  $1.4$ \\
+  1D maj. & S-bul + e-d + F-bar + G-r & $1.8$  &  $1.9$ \\
+  1D eq.  & S-bul + e-d + F-bar + G-r & $2.4$  &  $1.4$ \\
   \hline

### 2015-07-15 papers/data_paper/datapaper.tex
finedatap

@@
   The intermediate-scale embedded disk is clearly visible in our unsharp mask image (not shown), and 
-  the velocity map confirms the presence of this rapidly rotating component, which is modeled with an exponential function.
+  the velocity map (ATLAS$^{\rm 3D}$) confirms the presence of this rapidly rotating component, which is modeled with an exponential function.
   We choose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.  
@@
   The data within the innermost $6''.1$ are excluded from the fit, 
-  and the most obvious ring of this galaxy is modeled.
+  and the most obvious elongated feature of this galaxy is modeled with a Ferrer function.
   }
@@
   \hline
-  1D maj. & S-bul + e-d + G-r + m-c  & $11.1$  &  $5.4$ \\
-  1D eq.  & S-bul + e-d + G-r + m-c  & $52.5$  &  $7.1$ \\
+  1D maj. & S-bul + e-d + F-bar + m-c  & $11.0$  &  $5.8$ \\
+  1D eq.  & S-bul + e-d + F-bar + m-c  & $19.6$  &  $3.7$ \\
   \hline
@@
   M105 exhibits a mild isophotal twist and an abrupt change of ellipticity at $R_{\rm maj} \sim 30''$.
-  The velocity map shows rotation at least within $R_{\rm maj} \lesssim 30''$, 
+  The velocity map (ATLAS$^{\rm 3D}$) shows rotation at least within $R_{\rm maj} \lesssim 30''$, 
   but no embedded disk can be recognized in the unsharp mask 
@@
   \caption{NGC 0821: 
-  An edge-on elliptical/lenticular galaxy. 
-  The ellipticity profile and the velocity map show the presence of a faint intermediate-scale disk. 
+  An elliptical galaxy with an edge-on embedded disk. 
+  The ellipticity profile and the velocity map (ATLAS$^{\rm 3D}$, SLUGGS) show the presence of the faint intermediate-scale disk. 
   Given its edge-on inclination, the disk is modeled with a low-$n$ S\'ersic function.   
@@
   embedded in the bulge ($R_{\rm maj} \lesssim 10''$).
-  This inner component can be spotted also by looking at the velocity map, and 
+  This inner component can be spotted also by looking at the velocity map (ATLAS$^{\rm 3D}$), and 
   we fit it with a Ferrer function.
@@
   \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
-  \caption{NGC 3377.
-  NGC 3377 is an elliptical/lenticular galaxy with an intermediate-scale disk and a nuclear stellar disk \citep{ledo2010}. 
+  \caption{NGC 3377: 
+  An elliptical galaxy with an intermediate-scale disk and a nuclear stellar disk \citep{ledo2010}. 
   For this galaxy, \citet{arnold2014} reported a strong decline in local specific angular momentum beyond $\sim 35''$, 
@@
   \citet{arnold2014} attempted a three-component decomposition (accounting for a bulge, an embedded disk and a central cusp), 
-  but unfortunately they fit the spheroidal component with a limited two-parameter $R^{1/4}$ profile 
+  but unfortunately they fit the spheroidal component with a limited two-parameter $R^{1/4}$ function 
   rather than a three-parameter $R^{1/n}$ S\'ersic function.
@@
   and we identify a nuclear disk and an intermediate-scale disk, both embedded in a larger spheroidal component.
-  The presence of an intermediate-scale disk is evident from the unsharp mask of the image mosaic 
-  and also from the ellipticity profile, which increases with increasing radius until $R_{\rm maj} \sim 45''$ 
+  The presence of the intermediate-scale disk is also evident in the unsharp mask of the image mosaic 
+  and also from the ellipticity, which increases with increasing radius until $R_{\rm maj} \sim 45''$ 
   and then drops at larger radii.
@@
   \label{tab:n3377}
-  \tablecomments{L+14 2D obtained the smallest estimate of the effective radius because they oversubtracted a halo.   
+  \tablecomments{L+14 obtained the smallest estimate of the effective radius because they oversubtracted a halo.   
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n3384_1Dfit.eps}
-  \caption{NGC 3384.
-  NGC 3384 is a barred lenticular galaxy that hosts 
+  \caption{NGC 3384: 
+  A barred lenticular galaxy that hosts 
   an embedded disk (with size $\lesssim 11''$, \citealt{erwin2004}) and 
   a nuclear stellar disk (with size $\lesssim 0''.8$, \citealt{ledo2010}).
-  The isophotal parameters clearly show the presence of a boxy bar that extends out to $R_{\rm maj} \lesssim 18''$.
+  The isophotal parameters show clearly the presence of a boxy bar that extends out to $R_{\rm maj} \lesssim 18''$.
   We model the bar with a Ferrer function.
@@
   However, any attempt to account for this component resulted in a degenerate model.
-  We elect not to fit neither the embedded disk nor the nuclear disk, by excluding from the fit the data within $R_{\rm maj} < 3''.7$. 
+  We elect to fit neither the embedded disk nor the nuclear disk, by excluding from the fit the data within $R_{\rm maj} < 3''.7$. 
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n3393_1Dfit.eps}
-  \caption{NGC 3393.
-  NGC 3393 is an edge-on spiral galaxy hosting a Seyfert AGN \citep{diaz1988n3393} and 
+  \caption{NGC 3393: 
+  An edge-on spiral galaxy hosting a Seyfert AGN \citep{diaz1988n3393} and 
   circumnuclear dust \citep{martini2003}.
@@
   The large-scale bar ($R_{\rm maj} \lesssim 20''$) is modeled with a Ferrer function.
-  We do not model the nuclear bar and the AGN component because the poor spatial resolution of the data does not allow to fit them 
-  without incurring into degeneracies.
+  We do not model the nuclear bar and the AGN component because the poor spatial resolution of the data does not allow to fit them.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n3414_1Dfit.eps}
-  \caption{NGC 3414.
-  NGC 3414 is a peculiar lenticular/elliptical galaxy. 
+  \caption{NGC 3414: 
+  A peculiar lenticular/elliptical galaxy. 
   Different interpretations have been proposed about the morphology of this galaxy.
-  \cite{whitmore1990} suggested that NGC 3414 is an spheroidal galaxy 
+  \cite{whitmore1990} suggested that NGC 3414 is a spheroidal galaxy 
   with a large-scale edge-on polar ring, rather than a face-on barred lenticular galaxy.
@@
   However, an elongated structure in the galaxy center resembles a nuclear edge-on disk ($R_{\rm maj} \lesssim 5''$).
-  The velocity map shows rotation within $R_{\rm maj} \lesssim 5''$, no rotation within $5'' \lesssim R_{\rm maj} \lesssim 15''$,
+  The velocity map (ATLAS$^{\rm 3D}$) shows rotation within $R_{\rm maj} \lesssim 5''$, no rotation within $5'' \lesssim R_{\rm maj} \lesssim 15''$,
   and counterrotation beyond $R_{\rm maj} \gtrsim 15''$.
@@
   \tablecomments{
-  L+10 2D used a model with a large-scale exponential disk, thus they obtained a smaller bulge effective radius and S\'ersic index.
+  L+10 used a model with a large-scale exponential disk, thus they obtained a smaller bulge effective radius and S\'ersic index.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n3489_1Dfit.eps}
-  \caption{NGC 3489.
-  NGC 3489 is a barred lenticular galaxy. 
-  Its disk has a smooth antitruncation at $R_{\rm maj} \sim 85''$ \citep{erwin2008}.
+  \caption{NGC 3489: 
+  A barred lenticular galaxy. 
+  Its disk has a smooth anti-truncation at $R_{\rm maj} \sim 85''$ \citep{erwin2008}.
   %\cite{nowak2010n3368n3489} argued for the presence of both a pseudo-bulge and a classical bulge. 
@@
   \label{tab:n3489}
-  %\tablecomments{
-  %S+11 2D did not fit the bar and thus obtained a larger estimate of the bulge effective radius.
-  %}
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
-  \caption{NGC 3585. 
-  NGC 3585 is an elliptical galaxy with an embedded disk \citep{scorzabender1995}. 
+  \caption{NGC 3585: 
+  An elliptical galaxy with an embedded disk \citep{scorzabender1995}. 
   The embedded disk is visible in the unsharp mask and modeled with an exponential function. }
@@
   S+11 2D obtained smaller estimates of the effective radius and S\'ersic index because
-  they oversubtracted a large-scale disk.
+  they included a large-scale disk in their model.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
-  \caption{NGC 3607. 
-  NGC 3607 is an elliptical galaxy with an embedded disk. 
-  The velocity map shows rotation only within $R_{\rm maj} \lesssim 20''$. 
+  \caption{NGC 3607: 
+  An elliptical galaxy with an embedded disk. 
+  The velocity map (ATLAS$^{\rm 3D}$) shows rotation only within $R_{\rm maj} \lesssim 20''$. 
    }
@@
   \label{tab:n3607}
-  \tablecomments{L+10 2D obtained the smallest estimates of the effective radius and S\'ersic index because
-  they oversubtracted a large-scale disk.
+  \tablecomments{L+10 obtained the smallest estimates of the effective radius and S\'ersic index because
+  they included a large-scale disk in their model.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
-  \caption{NGC 3608.
-  NGC 3608 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013} 
-  and a kinematically decoupled core. 
+  \caption{NGC 3608: 
+  An elliptical galaxy with an unresolved partially depleted core \citep{rusli2013} 
+  and a kinematically decoupled core (ATLAS$^{\rm 3D}$, SLUGGS). 
   We find that masking the nuclear region of this galaxy is unnnecessary and we fit the light profile with a single S\'ersic model.
@@
   \label{tab:n3608}
-  \tablecomments{B+12 2D obtained the largest estimates of the effective radius and S\'ersic index, 
+  \tablecomments{B+12 obtained the largest estimates of the effective radius and S\'ersic index, 
   possibly due to incorrect sky subtraction. }
@@
   \includegraphics[width=\fitfigurewidth]{images/n3842exp_1Dfit.eps}
-  \caption{NGC 3842.
-  NGC 3842 is the brightest member of the Leo Cluster (Abell 1367).
-  It is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013,dullograham2014cores}. %($R_{\rm break} = 0''.7$,   \citealt{rusli2013,dullograham2014cores}).
+  \caption{NGC 3842: 
+  The brightest member of the Leo Cluster (Abell 1367), 
+  an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013,dullograham2014cores}. %($R_{\rm break} = 0''.7$,   \citealt{rusli2013,dullograham2014cores}).
   The light profile presents a swelling at $R_{\rm maj} \sim 20''$ and the ellipticity profile has a peak in the same position.
@@
   1D eq.  & S-bul + F-l + m-c  & $73.6$   &  $8.2$ \\
-  %2D	&  & $$  & $$  &  $$ \\
   \hline
@@
   \includegraphics[width=\fitfigurewidth]{images/n3998_1Dfit.eps}
-  \caption{NGC 3998.
-  NGC 3998 is a barred lenticular galaxy with a Seyfert AGN and nuclear dust \citep{knapp1996n3998}.
+  \caption{NGC 3998: 
+  A barred lenticular galaxy with a Seyfert AGN and nuclear dust \citep{knapp1996n3998}.
   Despite its large stellar velocity dispersion, this galaxy does not have a partially depleted core. 
   \cite{gutierrez2011} identified a bar at $R_{\rm maj} \lesssim 8''$, a ring between $30'' \lesssim R_{\rm maj} \lesssim 50''$, and  
-  an antitruncation in the light profile of the disk at $R_{\rm maj} \sim 122''$.
+  an anti-truncation in the light profile of the disk at $R_{\rm maj} \sim 122''$.
   \cite{laurikainen2010} found that NGC 3998 features a weak bar at $R_{\rm maj} < 8''$,
@@
   \includegraphics[width=\fitfigurewidth]{images/n4026_1Dfit.eps}
-  \caption{NGC 4026.
-  NGC 4026 is an edge-on lenticular galaxy with a nuclear stellar disk (with size $\lesssim 0''.5$, \citealt{ledo2010}).
-  The unsharp mask reveals the presence of a bar ($R_{\rm maj} \lesssim 30''$) and of a disky component 
-  embedded in the bulge, that is responsible for the peak at $R_{\rm maj} \sim 5''$ in the $B4$ profile.
-  The disky component can be also recognized in the velocity map.
+  \caption{NGC 4026: 
+  An edge-on lenticular galaxy with a nuclear stellar disk (with size $\lesssim 0''.5$, \citealt{ledo2010}).
+  The unsharp mask reveals the presence of a bar ($R_{\rm maj} \lesssim 30''$) and a disky component 
+  embedded in the bulge that is responsible for the peak at $R_{\rm maj} \sim 5''$ in the $B4$ profile.
+  The disky component can be also recognized in the velocity map (ATLAS$^{\rm 3D}$).
   The bar is fit with a Ferrer function and the inner disk with a low-$n$ S\'ersic profile.
@@
   \label{tab:n4026}
-  \tablecomments{S+11 2D obtained larger estimates of the bulge effective radius and S\'ersic index because they did not model the bar.}
+  \tablecomments{S+11 obtained larger estimates of the bulge effective radius and S\'ersic index because they did not model the bar.}
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n4151_1Dfit.eps}
-  \caption{NGC 4151.
-  NGC 4151 is a face-on barred spiral galaxy that hosts a Seyfert AGN \citep{veroncettyveron2006} 
+  \caption{NGC 4151:
+  A face-on barred spiral galaxy that hosts a Seyfert AGN \citep{veroncettyveron2006} 
   and circumnuclear dust \citep{pott2010}.
@@
   \includegraphics[width=\fitfigurewidth]{images/n4261_1Dfit.eps}
-  \caption{NGC 4261.
-  NGC 4261 is an elliptical galaxy with a LINER nucleus \citep{veroncettyveron2006}
+  \caption{NGC 4261: 
+  An elliptical galaxy with a LINER nucleus \citep{veroncettyveron2006}
   and a dusty nuclear disk \citep{tran2001}.
@@
   \tablecomments{
-  S+11 2D found the smallest estimate of the effective radius because they added a large-scale disk to their model.
-  V+12 2D obtained a small estimate of the effective radius because of the limited radial extent of their data.
+  S+11 found the smallest estimate of the effective radius because they added a large-scale disk to their model.
+  V+12 obtained a small estimate of the effective radius because of the limited radial extent of their data.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4291_1Dfit.eps}
-  \caption{NGC 4291.
-  NGC 4291 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
-  After excluding from the fit the data within the innermost $6''.1$, 
-  we observe that NGC 4291 can be well modeled with a S\'ersic profile.
+  \caption{NGC 4291: 
+  An elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
+  After excluding the data within the innermost $6''.1$ from the fit, 
+  we observe that NGC 4291 can be reasonably well modeled with a S\'ersic profile.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4388_1Dfit.eps}
-  \caption{NGC 4388.
-  NGC 4388 is an edge-on spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006} 
+  \caption{NGC 4388: 
+  An edge-on spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006} 
   and copious nuclear dust \citep{martini2003}.
@@
   \includegraphics[width=\fitfigurewidth]{images/n4459_1Dfit.eps}
-  \caption{NGC 4459.
-  NGC 4459 is a lenticular galaxy.
-  Its disk profile is reported to have an antitruncation at $R_{\rm maj} \sim 119''$ \citep{gutierrez2011}.
+  \caption{NGC 4459: 
+  A lenticular galaxy, 
+  whose disk profile has been reported to have an anti-truncation at $R_{\rm maj} \sim 119''$ \citep{gutierrez2011}.
   The ellipticity constantly increases across all the observed radial range ($R_{\rm maj} \lesssim 100''$).
@@
   We note that the antitruncation reported by \cite{gutierrez2011} could be an artificial feature 
-  produced by the transition between the radial range where the disk becomes increasingly more important 
-  over the bulge and the truly exponential decline of the disk beyond $R_{\rm maj} \gtrsim 119''$.
+  produced by the transition from the S\'ersic bulge to the exponential disk.
   We do not find evidence for any embedded components in our data.
@@
   \tablecomments{
-  B+12 2D did not model the large-scale disk and thus overestimated the bulge effective radius and S\'ersic index.
+  B+12 did not model the large-scale disk and thus overestimated the bulge effective radius and S\'ersic index.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4473_1Dfit.eps}
-  \caption{NGC 4473.
-  NGC 4473 is an elliptical galaxy with an embedded disk \citep{ledo2010}.
-  The disk is clearly visible in the velocity map. 
+  \caption{NGC 4473: 
+  An elliptical galaxy with an embedded disk \citep{ledo2010}.
+  The disk is clearly visible in the velocity map (ATLAS$^{\rm 3D}$, SLUGGS). 
   We account for a nuclear excess of light by adding a narrow Gaussian function to the model.
@@
   \tablecomments{
-  B+12 2D obtained the smallest estimates of the effective radius and S\'ersic index because they oversubtracted a large-scale disk. 
+  B+12 obtained the smallest estimates of the effective radius and S\'ersic index because they included a large-scale disk in their model. 
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4564_1Dfit.eps}
-  \caption{NGC 4564.
-  NGC 4564 is an edge-on lenticular galaxy.
+  \caption{NGC 4564: 
+  An edge-on lenticular galaxy.
   In the unsharp mask, one can glimpse an oval structure extending out to $R_{\rm maj} \lesssim 15''$ (see the peak in the $B4$ profile).
-  Fitting NGC 4564 with a S\'ersic + exponential model produces bad residuals.
-  The addition of a Ferrer function to the model dramatically improves the fit and smoothes the residuals.
+  Fitting NGC 4564 with a S\'ersic + exponential model produces poor residuals.
+  However, the addition of a Ferrer function to the model dramatically improves the fit and smoothes the residuals.
   }
@@
   \label{tab:n4564}
-  \tablecomments{The most dicrepant results are obtained by S+11 2D, although they used the same model as GD07 1D maj. and V+12 2D. }
+  \tablecomments{The most dicrepant results are obtained by S+11, although they used the same model as GD07 and V+12. }
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n4596_1Dfit.eps}
-  \caption{NGC 4596.
-  NGC 4596 is an edge-on barred lenticular galaxy.
+  \caption{NGC 4596: 
+  An edge-on barred lenticular galaxy.
   The morphology of this galaxy is quite complex. 
@@
   An additional embedded disky component ($R_{\rm maj} \lesssim 15''$) can be recognized in the $B4$ profile and in the velocity map.
-  The bump in the light profile within $60'' \lesssim R_{\rm maj} \lesssim 70''$ corresponds to the ansae of the bar.
-  This data range is excluded from the fit.
+  The bump in the light profile within $60'' \lesssim R_{\rm maj} \lesssim 70''$ corresponds to the ansae of the bar and 
+  this data range is therefore excluded from the fit.
   The large scale bar is fit with a Ferrer function and the inner disk with a low-$n$ S\'ersic profile.
@@
   \tablecomments{
-  B+12 2D fit nor the bar neither the inner disk and obtained the largest estimates of the bulge effective radius and S\'ersic index.
-  The models of S+11 2D and V+12 2D do not account for the inner disk and thus result in larger estimates of the bulge effective radius.
+  B+12 fit neither the bar nor the inner disk and obtained the largest estimates of the bulge effective radius and S\'ersic index.
+  The models of S+11 and V+12 do not account for the inner disk and thus result in larger estimates of the bulge effective radius.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4697_1Dfit.eps}
-  \caption{NGC 4697.
-  NGC 4697 is an elliptical galaxy with an embedded disk \citep{scorzabender1995}.
-  The velocity map and the unsharp mask of NGC 4697 clearly show 
+  \caption{NGC 4697: 
+  An elliptical galaxy with an embedded disk \citep{scorzabender1995}.
+  The velocity map (ATLAS$^{\rm 3D}$, SLUGGS) and the unsharp mask of NGC 4697 clearly show 
   the presence of an intermediate-size disk embedded in the galaxy's spheroidal component.
@@
   The peak at $R_{\rm maj} \sim 40''$ corresponds to the intermediate-size embedded disk just mentioned,
-  while the peak at $R_{\rm maj} \sim 10''$ unveils a smaller inner disk.
+  while the peak at $R_{\rm maj} \sim 10''$ pertains to a smaller inner disk.
   After testing different decomposition models, 
@@
   S+11 2D  & S-bul & $100.5$  &  $5.0$ \\
-  V+12 2D  & S-bul & $39.1$  &  $3.8$ \\
-  V+12 2D  & S-bul + e-d & $10.0$  &  $2.9$ \\
+  V+12 (1) 2D  & S-bul & $39.1$  &  $3.8$ \\
+  V+12 (2) 2D  & S-bul + e-d & $10.0$  &  $2.9$ \\
   L+14 2D  & S-bul + e-d + PSF-n + S-halo & $6.3$  &  $2.1$ \\
@@
   \tablecomments{
-  In both their models, V+12 2D underestimated the effective radius and the S\'ersic index because of the small radial range of their data. 
-  L+14 2D oversubtracted a large-scale disk and a halo, and thus underestimated the spheroid effective radius and the S\'ersic index. 
+  In both their models, V+12 underestimated the effective radius and the S\'ersic index because of the small radial range of their data. 
+  In an effort to model the curved light profile, 
+  L+14 included a large-scale disk plus a halo, and thus underestimated the spheroid effective radius and the S\'ersic index. 
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
-  \caption{NGC 4889.
-  NGC 4889 is the brightest member of the Coma cluster. 
-  It is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. % ($R_{\rm break} = 1''.6$, \citealt{rusli2013}).
-  We exclude from the fit the innermost $6''.1$ and
-  we successfully model the galaxy with a single S\'ersic profile.
+  \caption{NGC 4889: 
+  The brightest member of the Coma cluster, 
+  an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. % ($R_{\rm break} = 1''.6$, \citealt{rusli2013}).
+  We exclude the innermost $6''.1$ from the fit and
+  successfully model the galaxy with a single S\'ersic profile.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n4945_1Dfit.eps}
-  \caption{NGC 4945.
-  NGC 4945 is an edge-on, dusty spiral galaxy that hosts a Seyfert AGN \citep{lin2011}.
-  The light profile has an obvious bump that can be ascribed to a bar.
-  This bumb cannot be easily modeled with a Ferrer function, thus we exclude form the fit the data in the range $100'' \lesssim R_{\rm maj} \sim 400''$.
+  \caption{NGC 4945: 
+  An edge-on, dusty spiral galaxy that hosts a Seyfert AGN \citep{lin2011}.
+  The light profile has an obvious bump that can be ascribed to the bar.
+  This bumb cannot be easily modeled with a Ferrer function, thus we exclude the data in the range $100'' \lesssim R_{\rm maj} \sim 400''$ form the fit.
   We also exclude the data within the innermost $6''.4$ due to the contribution from the AGN.
@@
   \includegraphics[width=\fitfigurewidth]{images/n5077_1Dfit.eps}
-  \caption{NGC 5077. 
-  NGC 5077 is an elliptical galaxy with an unresolved partially depleted core \citep{trujillo2004coresersicmodel}. 
+  \caption{NGC 5077:  
+  An elliptical galaxy with an unresolved partially depleted core \citep{trujillo2004coresersicmodel}. 
   We mask the data within the innermost $6''.1$ and fit the galaxy with a S\'ersic profile. }
@@
   \includegraphics[width=\fitfigurewidth]{images/n5128_1Dfit.eps}
-  \caption{NGC 5128.
-  NGC 5128 is a merging system. 
+  \caption{NGC 5128: 
+  A merging system. 
   The data within $50'' \lesssim R_{\rm maj} \lesssim 200''$ are excluded from the fit.}
@@
   \includegraphics[width=\fitfigurewidth]{images/n5576_1Dfit.eps}
-  \caption{NGC 5576.
-  NGC 5576 is an elliptical galaxy with a disturbed morphology. 
+  \caption{NGC 5576: 
+  An elliptical galaxy with a disturbed morphology. 
   The isophotal parameters suggest the presence of an embedded disk ($R_{\rm maj} \lesssim 20''$), 
-  but any attempt to account for such component was unsuccessful. 
+  but attempts to account for such a component were unsuccessful. 
   The data within $R_{\rm maj} \lesssim 36''$ are excluded from the fit 
@@
   \label{tab:n5845}
-  \tablecomments{The results obtained by S+11 2D and B+12 2D best agree with the results from our 2D model, 
+  \tablecomments{The results obtained by S+11 and B+12 agree best with the results from our 2D model, 
   in which we did not mask the inner region of the galaxy. 
-  The small radial extent of the data used by V+12 2D led them to underestimate the effective radius.}
+  The small radial extent of the data used by V+12 led them to underestimate the effective radius.}
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n5845_1Dfit.eps}
-  \caption{NGC 5845.
-  NGC 5845 is an elliptical/lenticular galaxy. 
-  The small apparent size of NGC 5845 (compared to the PSF FWHM) implies low resolution for the data 
-  and complications for the modeling of this galaxy.
-  Here, looking at the unsharp mask and the velocity field, we identify a disk, but it is not clear whether the disk is large-scale or embedded.
-  The ellipticity profile has a peak at $R_{\rm maj} \sim 13''$ which suggests that the disk is indeed embedded.
-  However, when fitting NGC 5845 with a S\'ersic + exponential model, 
-  the lowest-$\chi^2$ solution does not reproduce an embedded disk.
-  This is because the S\'ersic and the exponential functions are degenerate in this decomposition, 
-  due to the small number of data points in the galaxy light profile.
+  \caption{NGC 5845: 
+  A lenticular galaxy. 
+  From the unsharp mask and the velocity map (ATLAS$^{\rm 3D}$), we identify a disk, but it is not clear whether the disk is large-scale or intermediate-scale.
+  The ellipticity profile has a peak at $R_{\rm maj} \sim 13''$ which suggests that the disk is indeed intermediate-scale, 
+  i.e.~it does not dominate at large radii.
   }
@@
   \includegraphics[width=\fitfigurewidth]{images/n5846_1Dfit.eps}
-  \caption{NGC 5846.
-  NGC 5846 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
+  \caption{NGC 5846: 
+  An elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 1''.2$, \citealt{rusli2013}).
   This galaxy has a LINER nucleus \citep{carrillo1999} and filamentary nuclear dust \citep{tran2001}.
@@
   The light profile presents a slight bump at $R_{\rm maj} \sim 20''$.
-  However, the isophotal parameters, the unsharp mask and the velocity map lack of clear evidence for an embedded component.
+  However, the isophotal parameters, the unsharp mask and the velocity map (ATLAS$^{\rm 3D}$) lack of clear evidence for an embedded component.
   We thus model NGC 5846 with a single S\'ersic profile, after masking the data within innermost $6''.1$.
@@
   \label{tab:n5846}
-  \tablecomments{S+11 2D did not mask the core and thus underestimated the effective radius and S\'ersic index. }
+  \tablecomments{S+11 did not mask the core and thus underestimated the effective radius and S\'ersic index. }
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n6251_1Dfit.eps}
-  \caption{NGC 6251.
-  NGC 6251 is an elliptical galaxy. Its large stellar velocity dispersion suggests the presence of a partially depleted core.
+  \caption{NGC 6251: 
+  An elliptical galaxy. 
+  Its large stellar velocity dispersion suggests the presence of a partially depleted core.
   The galaxy features a nuclear disk of dust \citep{ferrareseford1999n6251} and a Seyfert AGN \citep{panessabassani2002}.
@@
   \label{tab:n6251}
-  \tablecomments{It is not clear why GD07 1D maj. obtained the largest estimates of the effective radius and S\'ersic index.}
+  \tablecomments{It is not clear why GD07 obtained the largest estimates of the effective radius and S\'ersic index 
+  (possibly the AGN was bright in their $R$-band image and added to the central cusp). }
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n7052_1Dfit.eps}
-  \caption{NGC 7052.
-  NGC 7052 is an elliptical galaxy with an unresolved partially depleted core \citep{quillen2000}. %% ($R_{\rm break} = 0''.8$, \citealt{quillen2000}). 
+  \caption{NGC 7052: 
+  An elliptical galaxy with an unresolved partially depleted core \citep{quillen2000}. %% ($R_{\rm break} = 0''.8$, \citealt{quillen2000}). 
   We mask the data within the innermost $6''.1$ and model the galaxy with a single S\'ersic profile.
@@
   \label{tab:n7052}
-  \tablecomments{The model of V+12 2D oversubtracts a large-scale disk and thus results in the lowest estimates of the effective radius and S\'ersic index.}
+  \tablecomments{The model of V+12 2D includes an artificial large-scale disk 
+  and thus results in the lowest estimates of the effective radius and S\'ersic index.}
   \end{table}
@@
   \includegraphics[width=\fitfigurewidth]{images/n7619_1Dfit.eps}
-  \caption{NGC 7619.
-  NGC 7619 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %% ($R_{\rm break} = 0''.5$, \citealt{rusli2013}).
+  \caption{NGC 7619: 
+  An elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %% ($R_{\rm break} = 0''.5$, \citealt{rusli2013}).
   We identified an embedded disk signaled by the peak at $R_{\rm maj} \sim 10''$ in the ellipticity profile.
   The velocity map of this galaxy confirms the presence of a fast rotating component (Falcon-Barroso, private comm.).
-  We note that the residuals obtained from our best-fit model do not suggest the presence of a partially depleted core,
-  whereas they display a nuclear lack of light when the galaxy is modeled with a single S\'ersic-bulge. 
-  }
+  We note that the residuals obtained from our bulge + inner-disk model do not suggest the presence of a partially depleted core.
+  }
+  \label{fig:n7619}
   \end{center}
@@
   \includegraphics[width=\fitfigurewidth]{images/n7768_1Dfit.eps}
-  \caption{NGC 7768.
-  NGC 7768 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
+  \caption{NGC 7768: 
+  An elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %%($R_{\rm break} = 0''.3$, \citealt{rusli2013}).
   The image of NGC 7768 is corrupted by a saturated star, which lies close to the galaxy.
@@
   \includegraphics[width=\fitfigurewidth]{images/ugc03789_1Dfit.eps}
-  \caption{UGC 03789.
-  UGC 03789 is a face-on spiral galaxy.
-  This galaxy features a ring ($R_{\rm maj} \sim 20''$) and a nuclear bar ($R_{\rm maj} \lesssim 4''$),
+  \caption{UGC 03789:
+  A face-on spiral galaxy, 
+  featuring a ring ($R_{\rm maj} \sim 20''$) and a nuclear bar ($R_{\rm maj} \lesssim 4''$),
   which can be seen in the unsharp mask and produces corresponding peaks in the ellipticity and $PA$ profiles.

### 2015-07-15 python_codes/decomposition/ProFitErole1.0.1/instruments/plotting.py

@@ -44,6 +44,11 @@ def doFitPanel(fitPanel, rrr, mu, good_rrr, good_mu, bad_rrr, bad_mu, maxsma_arc
 	fitPanel.yaxis.set_major_locator(majorLocator)
 	fitPanel.yaxis.set_minor_locator(minorLocator)
 	
+	start, end = fitPanel.get_ylim()
+	ticks = np.arange(int(start)-1, int(end), -2)
+	fitPanel.yaxis.set_ticks(ticks)
+	fitPanel.yaxis.set_major_formatter(ticker.FormatStrFormatter('%0.0f'))
+	
 	#xxx = np.arange(min(rrr),max(rrr),0.1)
 	xxx = rrr
 	
@@ -286,6 +291,13 @@ def doB4Panel(B4Panel, datatab, Settings, equivalentAxisFit, maxsma_arcsec):
 	B4Panel.yaxis.set_ticks(ticks)
 	B4Panel.yaxis.set_major_formatter(ticker.FormatStrFormatter('%0.3f'))
 	
+        xticks = B4Panel.xaxis.get_major_ticks()   #
+        xticks[0].label1.set_visible(False)	   #
+        xticks[-1].label1.set_visible(False)	   #
+        xticks[-2].label1.set_visible(False)	   #
+     
+        #B4Panel.xaxis.set_ticks(np.arange(0, 800, 200) )
+
 	return B4Panel
 	
 xaxisMinorLocator = 200

### 2015-07-17 papers/MbhMsph/ApJ_submission/mm.tex
submission day

--- 2015-06-10 papers/MbhMsph/mm.tex
@@
 %\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
-\title{Supermassive black hole and host bulge affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
+\title{Supermassive black hole and host spheroid affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
 
@@
 \begin{abstract}
-In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, depleted core, etc.) 
+In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
 decomposition of 66 galaxies, with directly measured black hole masses, 
@@
 and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
-The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
-consistent with a dry-merging formation scenario,
+The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
 and define a tight %\emph{early-type sequence} 
 \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
-and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$.
+and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$, 
+i.e.~a $\pm 2\sigma$ range of 0.1--5\%.
 At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper %\emph{late-type sequence}, 
@@
 ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
-are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
+are not offset to lower $M_{\rm BH}$ from the correlation defined by the current bulge sample with $n_{\rm sph}>2$; 
 and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies 
@@
 
-\keywords{galaxies: bulges; galaxies: elliptical and lenticular, cD; galaxies: evolution; galaxies: structure; black hole physics}
+\keywords{black hole physics; galaxies: bulges; galaxies: elliptical and lenticular, cD; galaxies: evolution; galaxies: structure}
 
@@
 Bulge luminosities\footnote{Following \cite{sani2011}, absolute luminosities were calculated 
-assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$.} 
+assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$. 
+Absolute luminosities were not corrected for cosmological redshift dimming 
+(this correction would be as small as $-0.02\rm~mag$ for galaxies at a distance of $40\rm~Mpc$ 
+or $-0.05\rm~mag$ for galaxies at a distance of $100\rm~Mpc$).} 
 (Table \ref{tab:sample}) from \emph{Paper I} were converted into stellar masses 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
+\includegraphics[width=\columnwidth]{mbh_vs_mag_tot.pdf}
 \caption{Black hole mass plotted against $3.6\rm~\mu m$ galaxy absolute magnitude. 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
+\includegraphics[width=\columnwidth]{mbh_vs_mag_sph.pdf}
 \caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
+\includegraphics[width=\columnwidth]{mbh_vs_mag_sph_psb.pdf}
 \caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude (as in Figure \ref{fig:mbhmagsph}). 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/inset_psb.pdf}
+\includegraphics[width=\columnwidth]{inset_psb.pdf}
 \caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$ (see Figure \ref{fig:pseudob}), 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
+\includegraphics[width=\columnwidth]{mbh_vs_mass_sph.pdf}
 \caption{Black hole mass plotted against spheroid stellar mass. 
@@
 \begin{itemize}
-\item The $M_{\rm BH} - M_{\rm *,sph}$ log-relation for the spheroidal components of early-type (elliptical + lenticular) galaxies 
+\item The logarithmic $M_{\rm BH} - M_{\rm *,sph}$ relation for the spheroidal components of early-type (elliptical + lenticular) galaxies 
       has a slope of $1.04 \pm 0.10$ and intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
@@
       ($3 \times 10^9 \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 3 \times 10^{10}$) that the subsample spans. 
-      We refer to this correlation as a ``tentative'' \emph{late-type sequence}. 
+      We refer to this correlation as a \emph{late-type sequence}. 
       In (gas-poor) early-type galaxies, the black hole and the stellar content of the spheroidal component grow at the same pace, 
@@
       %Future work will explore the color of spheroids and galaxies in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.  
-\item The $M_{\rm BH}/M_{\rm *,sph}$ ratio for the early-type galaxies is $0.68 \pm 0.04\%$. 
-      This value is dramatically larger than what previously reported ($0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}).
-\item The $M_{\rm BH} - M_{\rm *,sph}$ log-relations for core-S\'ersic and S\'ersic spheroids have slopes consistent with each other 
-      ($1.19 \pm 0.23$ and $1.48 \pm 0.20$, respectively), 
-      thus these two populations do not appear to define two distinct sequences. 
+\item The median $M_{\rm BH}/M_{\rm *,sph}$ ratio for the early-type galaxies is $0.68 \pm 0.04\%$. 
+      This value is dramatically larger than what was previously reported ($0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}), 
+      but in close agreement with the value of $0.49\%$ reported by \cite{grahamscott2013} for core-S\'ersic spheroids. 
+\item The logarithmic $M_{\rm BH} - M_{\rm *,sph}$ relations for the core-S\'ersic and S\'ersic spheroids 
+      have slopes with over-lapping uncertainties ($1.19 \pm 0.23$ and $1.48 \pm 0.20$, respectively).  
+      The S\'ersic relation is less steep than, but also has over-lapping uncertainties with, 
+      the slope of $2.22 \pm 0.58$ reported by \cite{scott2013} for S\'ersic spheroids.  
+      The distinction between core-S\'ersic and S\'ersic spheroids found by \cite{scott2013} is thus less pronounced here. 
 \item In the $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) diagram, for early-type galaxies, 
@@
 \end{itemize}
+
+Finally, we note that some of the literature-sourced black hole mass measurements used by \cite{kormendyho2013} are different from those used here.  
+While these differences are smaller than $18\%$ for $78\%$ of the galaxies, 
+in three cases (NGC 0821, NGC 4291, and NGC 3393) they are larger than a factor of $2.3$.  
+We repeated our entire analysis using only the 58 galaxies that are in common between our sample and the sample of \cite{kormendyho2013}, 
+assuming for these galaxies the black hole mass measurements published by \cite{kormendyho2013}. 
+In doing so, we found that none of our conclusions changed.
 
@@
 
-\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
+\bibliography{SMBHbibliography}
 

### 2015-07-17 papers/data_paper/ApJ_submission/datapaper.tex
submission day

--- 2015-07-15 papers/data_paper/datapaper.tex
@@
 
-\author{G. A. D. Savorgnan and A. W. Graham}
+\author{Giulia A. D. Savorgnan and Alister W. Graham}
 \affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia}
@@
 \begin{center}
-\includegraphics[width=0.49\columnwidth]{images/m49nooverlap.eps}
-\includegraphics[width=0.49\columnwidth]{images/m49overlap.eps}
+\includegraphics[width=0.49\columnwidth]{m49nooverlap.eps}
+\includegraphics[width=0.49\columnwidth]{m49overlap.eps}
 \caption{Example of the \emph{overlap} correction. 
@@
 \begin{center}
-\includegraphics[width=0.49\columnwidth]{images/n4459brightstar.eps}
-\includegraphics[width=0.49\columnwidth]{images/n4459nobrightstar.eps}
+\includegraphics[width=0.49\columnwidth]{n4459brightstar.eps}
+\includegraphics[width=0.49\columnwidth]{n4459nobrightstar.eps}
 \caption{Example of aestethic correction.
@@
 \begin{center}
-\includegraphics[width=1\columnwidth, trim = 240 40 50 20, clip=True]{images/psf.eps}
-%\includegraphics[width=1\columnwidth]{images/star1_cut.eps} \\
-%\includegraphics[width=1\columnwidth]{images/PRF_IRACch1_129_129_cut.eps}
+\includegraphics[width=1\columnwidth, trim = 240 40 50 20, clip=True]{psf.eps}
+%\includegraphics[width=1\columnwidth]{star1_cut.eps} \\
+%\includegraphics[width=1\columnwidth]{PRF_IRACch1_129_129_cut.eps}
 \caption{Normalized flux versus radial distance 
@@
 %\begin{center}
-%\includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
+%\includegraphics[width=\fitfigurewidth]{n3377_1Dfit.eps}
 %\caption{the galaxy NGC 3377. 
@@
 \begin{center}
-\includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
+\includegraphics[width=\fitfigurewidth]{n2974_1Dfit.eps}
 \caption{Best-fit model, and isophotal parameters, for the galaxy NGC 2974. 
@@
 %\begin{center}
-%\includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
+%\includegraphics[width=\fitfigurewidth]{m59_1Dfit.eps}
 %\caption{the galaxy M59. 
@@
 %\begin{center}
-%\includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
+%\includegraphics[width=\fitfigurewidth]{n1332_1Dfit.eps}
 %\caption{the galaxy NGC 1332.
@@
 %\begin{center}
-%\includegraphics[width=\columnwidth]{images/mbhmagk_n1332.pdf}
+%\includegraphics[width=\columnwidth]{mbhmagk_n1332.pdf}
 %\caption{The location of the S\'ersic galaxy NGC 1332 in the black hole mass versus $K$-band spheroid absolute magnitude diagram,
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/n2974_imgmsk.jpeg}
-\includegraphics[width=\columnwidth]{images/n2974_unsharp.jpeg}
-\includegraphics[width=\columnwidth]{images/n2974_model.jpeg}
-\includegraphics[width=\columnwidth]{images/n2974_resid.jpeg}
+\includegraphics[width=\columnwidth]{n2974_imgmsk.eps}
+\includegraphics[width=\columnwidth]{n2974_unsharp.eps}
+\includegraphics[width=\columnwidth]{n2974_model.eps}
+\includegraphics[width=\columnwidth]{n2974_resid.eps}
 \caption{Image of the galaxy NGC 2974 with its mask (top panel), unsharp mask (second panel), 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/comparison_r_e.eps} 
+\includegraphics[width=\columnwidth]{comparison_r_e.eps} 
 \caption{2D versus 1D major-axis measurements of the spheroid effective radii. 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/comparison_n.eps} 
+\includegraphics[width=\columnwidth]{comparison_n.eps} 
 \caption{2D measurements of the spheroid S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/comparison_mag.eps} 
+\includegraphics[width=\columnwidth]{comparison_mag.eps} 
 \caption{2D versus 1D measurements of the $3.6~\rm \mu m$ spheroid magnitudes. The dashed line displays the 1:1 relation.}
@@
 \begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
+\includegraphics[width=1.1\columnwidth]{comparison_all_n.eps} 
 \caption{Bottom panel: 58 galaxies for which at least one measurement of the spheroid S\'ersic index $n_{\rm sph}$ is available 
@@
 \begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_r_e.eps} 
+\includegraphics[width=1.1\columnwidth]{comparison_all_r_e.eps} 
 \caption{Bottom panel: 52 galaxies for which at least one measurement of the spheroid major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
@@
 \begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_mag_sph.eps} 
+\includegraphics[width=1.1\columnwidth]{comparison_all_mag_sph.eps} 
 \caption{Bottom panel: 51 galaxies for which at least one measurement of the spheroid apparent magnitude $m_{\rm sph}$ 
@@
 \begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_e.eps} 
+\includegraphics[width=1.1\columnwidth]{comparison_all_mu_e.eps} 
 \caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid effective surface brightness $\mu_{\rm e,sph}$ 
@@
 \begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_0.eps} 
+\includegraphics[width=1.1\columnwidth]{comparison_all_mu_0.eps} 
 \caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid central surface brightness $\mu_{\rm 0,sph}$ 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{ic1459_1Dfit.eps}
   \caption{IC 1459: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{ic2560_1Dfit.eps}
   \caption{IC 2560: A barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{ic4296_1Dfit.eps}
   \caption{IC 4296:
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m31_1Dfit.eps}
   \caption{M31 (Andromeda galaxy):
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m49_1Dfit.eps}
   \caption{M49:
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m59_1Dfit.eps}
   \caption{M59:
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m64_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m64_1Dfit.eps}
   \caption{M64: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m81_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m81_1Dfit.eps}
   \caption{M81: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m84_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m84_1Dfit.eps}
   \caption{M84:
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m87_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m87_1Dfit.eps}
   \caption{M87:
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m89_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m89_1Dfit.eps}
   \caption{M89: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m94_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m94_1Dfit.eps}
   \caption{M94: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m96_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m96_1Dfit.eps}
   \caption{M96:
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m104_1Dfit.eps}
   \caption{M104: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m105_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m105_1Dfit.eps}
   \caption{M105: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/m106_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{m106_1Dfit.eps}
   \caption{M106: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n0524_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n0524_1Dfit.eps}
   \caption{NGC 0524: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n0821_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n0821_1Dfit.eps}
   \caption{NGC 0821: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n1023_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n1023_1Dfit.eps}
   \caption{NGC 1023:
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n1300_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n1300_1Dfit.eps}
   \caption{NGC 1300: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n1316_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n1316_1Dfit.eps}
   \caption{NGC 1316:  
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n1332_1Dfit.eps}
   \caption{NGC 1332: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n1374_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n1374_1Dfit.eps}
   \caption{NGC 1374: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n1399_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n1399_1Dfit.eps}
   \caption{NGC 1399: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n2273_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n2273_1Dfit.eps}
   \caption{NGC 2273: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n2549_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n2549_1Dfit.eps}
   \caption{NGC 2549: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n2778_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n2778_1Dfit.eps}
   \caption{NGC 2778: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n2787_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n2787_1Dfit.eps}
   \caption{NGC 2787: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n2974_1Dfit.eps}
   \caption{NGC 2974: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3079_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3079_1Dfit.eps}
   \caption{NGC 3079:
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3091_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3091_1Dfit.eps}
   \caption{NGC 3091: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3115_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3115_1Dfit.eps}
   \caption{NGC 3115:
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3227_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3227_1Dfit.eps}
   \caption{NGC 3227: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3245_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3245_1Dfit.eps}
   \caption{NGC 3245:
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3377_1Dfit.eps}
   \caption{NGC 3377: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3384_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3384_1Dfit.eps}
   \caption{NGC 3384: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3393_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3393_1Dfit.eps}
   \caption{NGC 3393: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3414_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3414_1Dfit.eps}
   \caption{NGC 3414: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3489_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3489_1Dfit.eps}
   \caption{NGC 3489: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3585_1Dfit.eps}
   \caption{NGC 3585: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3607_1Dfit.eps}
   \caption{NGC 3607: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3608_1Dfit.eps}
   \caption{NGC 3608: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3842exp_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3842exp_1Dfit.eps}
   \caption{NGC 3842: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n3998_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n3998_1Dfit.eps}
   \caption{NGC 3998: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4026_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4026_1Dfit.eps}
   \caption{NGC 4026: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4151_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4151_1Dfit.eps}
   \caption{NGC 4151:
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4261_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4261_1Dfit.eps}
   \caption{NGC 4261: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4291_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4291_1Dfit.eps}
   \caption{NGC 4291: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4388_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4388_1Dfit.eps}
   \caption{NGC 4388: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4459_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4459_1Dfit.eps}
   \caption{NGC 4459: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4473_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4473_1Dfit.eps}
   \caption{NGC 4473: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4564_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4564_1Dfit.eps}
   \caption{NGC 4564: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4596_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4596_1Dfit.eps}
   \caption{NGC 4596: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4697_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4697_1Dfit.eps}
   \caption{NGC 4697: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4889_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4889_1Dfit.eps}
   \caption{NGC 4889: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n4945_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n4945_1Dfit.eps}
   \caption{NGC 4945: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n5077_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n5077_1Dfit.eps}
   \caption{NGC 5077:  
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n5128_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n5128_1Dfit.eps}
   \caption{NGC 5128: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n5576_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n5576_1Dfit.eps}
   \caption{NGC 5576: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n5845_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n5845_1Dfit.eps}
   \caption{NGC 5845: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n5846_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n5846_1Dfit.eps}
   \caption{NGC 5846: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n6251_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n6251_1Dfit.eps}
   \caption{NGC 6251: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n7052_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n7052_1Dfit.eps}
   \caption{NGC 7052: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n7619_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n7619_1Dfit.eps}
   \caption{NGC 7619: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/n7768_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{n7768_1Dfit.eps}
   \caption{NGC 7768: 
@@
   \begin{center}
-  \includegraphics[width=\fitfigurewidth]{images/ugc03789_1Dfit.eps}
+  \includegraphics[width=\fitfigurewidth]{ugc03789_1Dfit.eps}
   \caption{UGC 03789:

### 2015-07-17 papers/data_paper/ApJ_submission/datapaper.sh

@@ -1,0 +1,5 @@
+pdflatex datapaper
+bibtex datapaper
+pdflatex datapaper
+pdflatex datapaper
+##dvipdfm datapaper.dvi

### 2015-07-17 python_codes/databases/initialize/init.py

@@ -10,7 +10,7 @@ literaturefilename = '/Users/gsavorgnan/galaxy_vivisection/data/ancillary/litera
 mosaicsfilename = '/Users/gsavorgnan/galaxy_vivisection/data/galaxies/mosaics.list'
 sgs2013filename = '/Users/gsavorgnan/galaxy_vivisection/data/Alister-data/SGS13/kmagssph.dat'
 colorfilename = '/Users/gsavorgnan/galaxy_vivisection/data/ancillary/iraccolor.dat'
-
+kormendyho2013filename = '/Users/gsavorgnan/galaxy_vivisection/data/KH13/SMBHmasses.top'
 
 def replaceNull(entry):
 	if entry == '""':
@@ -724,6 +724,37 @@ def spitzerdata():
 	connection.close()
 	data.close()
 		
+def kormendyho2013():
+	connection = sql3.connect(dbname)
+	cur = connection.cursor()
+
+	data = open(kormendyho2013filename)
+
+	cur.execute('''CREATE TABLE KormendyHo2013
+		(gal_id text, mass_BH real, perr_mass_BH real, merr_mass_BH real)''')
+	
+	for line in data:
+		if line.split()[0] != '#':
+			gal_id = line.split()[1]	
+			gal_id = replaceNull(gal_id)
+			mass_BH = line.split()[6]
+			mass_BH = replaceNull(mass_BH)
+			min_mass_BH = line.split()[7]
+			min_mass_BH = replaceNull(min_mass_BH)
+			max_mass_BH = line.split()[8]
+			max_mass_BH = replaceNull(max_mass_BH)
+			
+			merr_mass_BH = float(mass_BH) - float(min_mass_BH)
+			perr_mass_BH = -float(mass_BH) + float(max_mass_BH)
+			
+			collection = [gal_id, mass_BH, perr_mass_BH, merr_mass_BH]		
+			cur.execute('INSERT INTO KormendyHo2013 VALUES (?,?,?,?)', collection)
+
+	connection.commit()
+
+	cur.close()
+	connection.close()
+	data.close()
 		
 
 def main():
@@ -763,6 +794,7 @@ def main():
 	#print 'Table SpitzerData has been created.'
 	kmagSGS2013PhysicalUnits()
 	print 'Table KmagSGS2013PhysicalUnits has been created.'
-	
+	kormendyho2013()
+	print 'Table KormendyHo2013 has been created.'
 	
 main()	

### 2015-07-21 papers/lentiptical/lentiptical.tex
tue

@@
 \usepackage{longtable}
-\usepackage[]{graphicx}
+\usepackage{graphicx}
 \usepackage{amsmath}
@@
 \usepackage{bm}
-\graphicspath{{/Users/gsavorgnan/galaxy_vivisection/papers/lentiptical/images/}}
 
@@
 
-Title: Lentiptical galaxies \\
+Title: Lentiptical galaxies and their extraordinarily ordinary black holes \\
 Authors: G. A. D. Savorgnan and A. W. Graham \\
@@
 \begin{abstract}
-Early-type galaxies are quiescent galaxies, with little or no star formation activity. 
-The majority of early-type galaxies are made of two principal components: 
-a spheroid (or bulge) of stars with random motion and a rapidly rotating stellar disk (1 krajnovic). 
-The relative importance of these two components determines the morphological classification of early-type galaxies into two types: 
-elliptical galaxies are spheroid-dominated systems, 
-whereas lenticular galaxies are composed of a small bulge of stars encased in a larger stellar disk. 
+Early-type galaxies include elliptical and lenticular galaxies. 
+%Most early-type galaxies are made of two principal components [ref krajnovic]: 
+%a spheroid (or bulge) of stars, with an approximately ellipsoidal shape, 
+%and a relatively flat stellar disk. 
+%Elliptical galaxies are said to have no stellar disk, 
+%whereas lenticular galaxies are composed of a central bulge of stars encased in a larger stellar disk. 
+Lenticular galaxies are composed of a central spheroid (or bulge) of stars encased in a larger stellar disk. 
 When perfoming bulge/disk decomposition, 
-the spheroidal component is typically described with a S\'ersic profile (2 sersic), 
-while the disk is fit with an exponential function. 
+the spheroidal component is typically described with a S\'ersic profile (ref sersic), 
+while the disk is modelled with an exponential function. 
 Theoretically, the bulge-to-disk ratio, 
@@
 However, several studies have taken into account only bulge/disk decompositions 
-in which the exponential function neatly dominates over the S\'ersic profile at large galaxy radii, 
-and rejected those decompositions in which the exponential function remains ``embedded'' within the S\'ersic profile, 
+in which the exponential-disk function neatly dominates over the S\'ersic-spheroid profile at large galaxy radii, 
+and rejected those decompositions in which the exponential-disk function remains ``embedded'' within the S\'ersic-spheroid profile, 
 considering such decompositions as unphysical.
-Here we show that these rejected models correctly reproduce the kinematics of a class of early-type galaxies, 
-that we name \emph{lentiptical}. 
+Here we show that these ``rejected'' models correctly reproduce the photometric and kinematic properties of a class of early-type galaxies, 
+intermediate between elliptical and lenticular galaxies, that we name \emph{lentiptical}. 
 Lentiptical galaxies have often been confused with lenticular galaxies and, 
 consequently, their bulge luminosities have been largely underestimated. 
-This surprisingly common mistake has led to some wrong conclusions, 
-such as the claim that a number of lentiptical galaxies host a central black hole whose mass is abnormally large 
+This mistake has led to some wrong conclusions, 
+such as the claim that a number of lentiptical galaxies (MRK 1216 [ref yldrim+2015], 
+NGC 1277 [ref vdb+2012], NGC 1271 [ref walsh+2015], and NGC 1332 [ref rusli+2011]) 
+host a central black hole whose mass is abnormally large 
 compared to expectations from its (underestimated) bulge luminosity.
+When lentiptical galaxies are modelled according to our simple prescription, 
+which uses the lowest number of free parameters, 
+they no longer appear as extreme outliers in the (black hole mass) -- (spheroid stellar mass) diagram. 
+Previous ``anomalies'' are explained by one simple ``rule'' 
+and no need di avere nuovi scenari
 
-Our results demonstrate that there is no bimodality in the distribution of the bulgetodisk
-that the claimed bimodality is artificial
+%Our results demonstrate that there is no bimodality in the distribution of the bulgetodisk
+%that the claimed bimodality is artificial
 
-we show that the ell profile is enough to estabilish if the disk is embedded or not
+%we show that the ell profile is enough to estabilish if the disk is embedded or not
 
@@
 
-The existence of such disks is not only important for our understanding of disk growth in general, 
-reducing or eliminating an old mystery, 
-but accounting for such structure will impact on our galaxy scaling relations 
-and surely see the reclassification of many ``disky'' elliptical galaxies 
-and lenticular galaxies as \emph{lentiptical} 
-galaxies with intermediate-sized stellar disks that do not dominate at large radii. \\
-
-It is well known to the astronomers that identifying a face-on, featureless stellar disk 
-in an early-type galaxy only by looking at the galaxy image 
-is a very challenging if not even impossible task. 
-Luckily, the majority of such disks are observed by us with some level of inclination, 
+The majority of stellar disks have some level of inclination with respect to our line-of-sight, 
 which makes them appear as flat, elliptical components, 
 and helps us distinguishing them from the more spherical galaxy bulges. 
-A more subtle and overlooked issue is the difficulty in identifying the extent of these disks 
-with respect to their bulge.
-
-Kinematic maps, obtained from IFU spectroscopy, constitute an extremely powerful instrument to this purpose. 
-{\bf However, xxxSLUGGS have shown that the limited FOV of the atlas3d maps is not enough to get the full picture,
-and more extended maps are needed to reveal which galaxies display a FR behaviour all the way out 
-and which ones become SR at large radii.}
-Unfortunately, kinematic maps are not yet available for a large sample of galaxies in the local Universe. 
-Notwhithstanding, there is another powerful instrument that can help identify the extent of 
+Yet, identifying the extent of these disks with respect to their bulge can be subtle.
+Two-dimensional kinematic maps represent an extremely powerful instrument to this purpose. 
+However, only kinematic maps that extend beyond $\sim$$2$ half-light radii can help distinguish which galaxies, 
+among those classified as central fast rotators (within $\sim$$1$ half-light radius), 
+have increasing or decreasing specific angular momentum profiles at large radii [ref arnold+14]. 
+A specific angular momentum profile that is rapidly increasing at large radii is a signature of a large-scale disk, 
+whereas a profile that declines at large radii is consistent with the presence of an intermediate-scale disk. 
+Unfortunately, such extended kinematic maps are not yet available for a large sample of galaxies in the local Universe. 
+Nevertheless, there is another powerful instrument that can help identify the extent of 
 stellar disks in early-type galaxies, 
-and that has the advantage of requiring only galaxy images (even photometrically uncalibrated), 
-which are cheaper to acquire in terms of telescope time than IFU observations. 
-This instrument is the ellipticity profile of a galaxy's isophotes, 
-that can be easily obtained from a 1D isophotal analysis of the galaxy image, 
-using for example the IRAF task {\tt ellipse}.
+and has the advantage of requiring only galaxy images (even photometrically uncalibrated), 
+which are cheaper to acquire in terms of telescope time than spatially resolved two-dimensional kinematic maps. 
+This instrument is the ellipticity profile of a galaxy's isophotes.
 
@@
 Note that, in the case of an intermediate-scale disk, 
-the maximum of the ellipticity profile corresponds to the minimum difference between the 
+the maximum value of the ellipticity should correspond to the minimum difference between the 
 light profile of the bulge and that of the disk (vertical dashed line in Figure \ref{fig:ellp}). 
-Galaxy modellers that attempt to perform bulge/disk decomposition of lentiptical galaxies 
-should always check that their model correctly reproduces this important signature.
+Galaxy modellers that attempt to perform bulge/disk decomposition of early-type galaxies 
+should always check that their model correctly matches the galaxy's ellipticity profile.
 
-The {\bf realization, coscienza, not-knowledge} that many ``elliptical'' galaxies 
-actually contain embedded stellar disks 
+The awareness that many ``elliptical'' galaxies actually contain embedded stellar disks 
 dates back at least three decades 
@@
 However, the class of lentiptical galaxies has been missed out by many galaxy modellers, 
-who labelled as ``unphysical'' the idea that an intermediate-sized stellar disk 
-can exist fully embedded in a larger spheroidal component. 
+who labelled as ``unphysical'' those bulge/disk decompositions in which 
+the exponential-disk function does not dominate over the S\'ersic-spheroid profile at large radii. 
+%the idea that an intermediate-sized stellar disk 
+%can exist fully embedded in a larger spheroidal component. 
 This unspoken bias has led them to reject any bulge/disk decomposition with an outcome 
 similar to that illustrated in the middle panel of Figure \ref{fig:ellp}. 
-Unsurprisingly, some studies have found that the b/t ratio of S0s is less than...
+%Unsurprisingly, some studies have found that the b/t ratio of S0s is less than...
 
-Examples of lentiptical galaxies are the galaxies MRK 1216, NGC 1271, NGC 1277, NGC 1332, NGC 3115, NGC 3377 
-(see Figure \ref{fig:n3377ex}) and NGC 4621. 
+Examples of lentiptical galaxies are the galaxies MRK 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115. 
 All of these galaxies can be easily described and explained with a simple two-component model: 
-an outer S\'ersic bulge plus an embedded, intemediate-sized exponential\footnote{Given 
-its close-to-edge-on inclination,  
-the stellar disk of NGC 1332 is better described by a S\'ersic profile with S\'ersic index $n<1$ 
-\citep{pastrav2013a,pastrav2013b}.} disk. 
-Models that ``forzatamente'' describe the galaxy with an inner S\'ersic bulge 
-encased within a large-scale exponential disk can produce acceptable fits ???? statistically decent??
-only in two cases:
-either the data are shallow, thus they are not probing the re-rise of the bulge, 
-or an outer Sersic halo is added to the model to account for the outer light (n3115 and n3377 lasker).....
+a S\'ersic-spheroid plus an intemediate-sized exponential-disk. 
+Our bulge/disk decomposition for the galaxy NGC 3115 is presented in Figure \ref{fig:n3115}.
+Light profile extended out to 5 re
+kinematics
 
-show vel map? + ell profile, explain shape
+Models that ``forcedly'' describe the galaxy with an inner S\'ersic-bulge 
+encased within a large-scale exponential-disk can match the surface brightness distribution 
+of the galaxy only in two cases. 
+If the radial extent of the galaxy image is relatively small (less than or similar to one half-light radius), 
+the outer rise of the bulge over the disk is not probed 
+and a model with a large-scale disk can accommodate the observed surface brightness distribution. 
+This problem can affect bulge/disk decompositions that use relatively shallow imagind data, 
+such as 2MASS [ref vika, laurikainen]. 
+When a more extended galaxy image is available, 
+a model featuring a bulge encased in large-scale disk can only work with the addition of an outer S\'ersic-envelope, 
+that accounts for the outer portion of the spheroidal component. 
+These three-component decompositions will typically result in an outer S\'ersic-envelope with a curvature 
+(regulated by the S\'ersic index) similar to that of the inner S\'ersic-bulge, 
+(see the models of [ref lasker+2014] for the galaxies NGC 0821, NGC 3115, NGC 4342, NGC 4697;
+curiously, in these decompositions, the luminosity of the S\'ersic-envelope is comparable or larger than that of the inner S\'ersic-bulge).
 
-our models are physically motivated and produce bulge luminosities which make these galaxies no longer outliers
-btw they are not outliers on the M-Mgal relation, which suggests poor bulge/disk decomposition
+Our two-component models (intermediate-sized disk embedded within a spheroidal component)  
+%require a lower number of galaxy components than three-component models (bulge + disk + envelope), 
+require the lowest number of free parameters, 
+yet they match the kinematic maps (when available) and the ellipticity profiles of lentiptical galaxies. 
+Moreover, when lentiptical galaxies are modeled according to our prescription, 
+they no longer are outlier in the (black hole mass) -- (spheroid stellar mass) diagram, 
+as shown in Figure \ref{fig:mm}. 
+This eliminates the need of invocking a different evolutionary path ... compact relic...
 
-people that do only 2d decompositions, should still perform a 1d isophotal analysis to check extent of disk
+For early-type galaxies, the bulge luminosity and the total galaxy luminosity can be used to predict the black hole mass 
+with the same level of accuracy [cite me].
+The fact that a galaxy hosts a black hole that is over-massive compared to expectations from the bulge luminosity, 
+but is ``normal'' compared to expectations from the total galaxy luminosity, 
+suggests that the bulge luminosity may have been underestimated. 
+Indeed, none of these galaxies is an outlier in the (black hole mass) -- (total galaxy luminosity) diagram [cite me].
 
+%people that do only 2d decompositions, should still perform a 1d isophotal analysis to check extent of disk
+
+The existence of intermediate-scale stellar discs suggests that a continuum of disc sizes may exist, 
+rather than a dichotomy of nuclear vs. large-scale discs.  
+The presence of intermediate-scale disks blurs the distinction between elliptical and lenticular galaxies.
+The existence of such disks is not only important for our understanding of disk growth in general, 
+reducing or eliminating an old mystery, 
+but accounting for such structure will impact on our galaxy scaling relations 
+and surely see the reclassification of many ``disky'' elliptical galaxies 
+and lenticular galaxies as \emph{lentiptical} 
+galaxies with intermediate-sized stellar disks that do not dominate at large radii.
+
+% and it may be that our E vs S0 
+%classification for galaxies without spiral arms could be better represented by a range of bulge-to-disc (luminosity and size) ratios. 
+%In a somewhat similar vein, it was previously thought that bulges came in just one of two flavours: 
+%classical bulges with n=4 light profiles and pseudobulges with n=1 light profiles (e.g. Carollo et al. 1998-2002?).  
+%Although many works still advocate this bulge dichotomy based on their light profiles, Graham \& Worley (2008) have revealed no 
+%evidence for a bimodality in the distribution of their Sersic indices from a sample of 400 disc 
+%galaxies\footnote{The co-existence of classical and pseudo bulges in the same galaxy (e.g. Erwin et al. 2003, ApJ, 597, 929) 
+%further blurs claims for galaxies having either a classical bulge or a pseudobulge.}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%
+
+luca cortese, peppo gavazzi, matteo fossati
+%%
 \begin{figure}
-\includegraphics[width=\columnwidth]{diskextent.eps}
+\includegraphics[width=\columnwidth]{images/diskextent.eps}
 \caption{Illustration of the typical light profile (top plots) and ellipticity profile (bottom plots) of a galaxy 
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{n3377ex.eps}
+\includegraphics[width=\columnwidth]{images/n3115_decomposition.eps}
 \caption{
 }
-\label{fig:n3377ex}
+\label{fig:n3115}
 \end{figure}
 
-The existence of intermediate-scale stellar discs suggests that a continuum of disc sizes may exist, rather than a dichotomy of nuclear vs. large-scale discs.  
-In a somewhat similar vein, it was previously thought that bulges came in just one of two flavours: 
-classical bulges with n=4 light profiles and pseudobulges with n=1 light profiles (e.g. Carollo et al. 1998-2002?).  
-Although many works still advocate this bulge dichotomy based on their light profiles, Graham \& Worley (2008) have revealed no 
-evidence for a bimodality in the distribution of their Sersic indices from a sample of 400 disc 
-galaxies\footnote{The co-existence of classical and pseudo bulges in the same galaxy (e.g. Erwin et al. 2003, ApJ, 597, 929) 
-further blurs claims for galaxies having either a classical bulge or a pseudobulge.}.   
-The presence of intermediate-scale discs blurs the distinction between elliptical and lenticular galaxies and it may be that our E vs S0 
-classification for galaxies without spiral arms could be better represented by a range of bulge-to-disc (luminosity and size) ratios.
+\begin{figure}
+\includegraphics[width=\columnwidth]{images/mm.eps}
+\caption{
+}
+\label{fig:mm}
+\end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%
-
-luca cortese, peppo gavazzi, matteo fossati
-%%
 %%We are grateful to V. Barger, T. Han, and R. J. N. Phillips for

### 2015-07-21 python_codes/paper_figures/lentiptical/n3115/cls/settings.py

@@ -1,0 +1,44 @@
+#### default settings
+
+class Settings:
+    
+    #performFit = False
+    performFit = True
+    
+    #axisFit = 'maj'
+    #axisFit = 'eq'
+    #axisFit = 'min'
+            
+    #fitConvolvedModel = False
+    #plotConvolvedFinalModel = False
+    #plotConvolvedComponent = False
+    fitConvolvedModel = True
+    plotConvolvedFinalModel = True
+    plotConvolvedComponent = True
+    
+    useErrorsInFit = False
+    #useErrorsInFit = True
+    
+    smoothing = False
+    #smoothing = True
+    
+    observation = 'spitzer3.6um'
+    #observation = 'n1271' 
+        
+    if (observation == 'n1277'):
+        pxlToArcsec = 0.05
+        zeropoint = 24.851 # hst for n1277
+    
+    if (observation == 'n1271'):
+        pxlToArcsec = 0.12825
+        zeropoint = 24.6949 # Vega
+    
+    if (observation == 'spitzer3.6um'):
+        pxlToArcsec = 1.2232836
+        zeropoint = 17.25585 #spitzer 3.6 um
+
+    colordict = {'sersic' : 'red', 'tsersic' : 'red', 'disc' : 'blue', 'gaussian' : 'green', 'psf' : 'purple', 'ferrer' : 'lightblue', 'tdisc' : 'blue', 'gring' : 'grey', 'psfwing' : 'purple'}
+    
+    #oversamplingStep = 0.2 # pixels
+    
+#     fitResultsFileName = '/Users/gsavorgnan/Dropbox/giulia_e_basta/ProFitErole1.0.1/results/1DfitResults.dat'

### 2015-07-21 python_codes/paper_figures/lentiptical/n3115/instruments/b_n.py

@@ -1,0 +1,59 @@
+import numpy as np
+from scipy.special import gammainc
+import math
+from decimal import Decimal
+from scipy.optimize import minimize_scalar
+
+######## SETTINGS ##########################
+
+precisionResid = 0.000001
+
+######## COMPUTE b_n #######################
+
+def b_nResid(k, x):
+        
+        out = gammainc(k, x) - 0.50000000000000
+        return out
+
+def computeb_n(n):
+
+        k = 2*n
+		
+	b=2*n - 0.333
+	if (b<0):
+		b=0.000
+		
+	zero  = b_nResid(k, b)	
+	increment = 1.000
+	
+	while (abs(zero) > precisionResid):
+		
+		zero  = b_nResid(k, b)
+		
+		bplus = b + increment
+		bminus = b - increment
+		if (bminus<0):
+			bminus = 0.000
+		
+		zeroplus = b_nResid(k, bplus)	
+		zerominus = b_nResid(k, bminus)
+		
+		if (abs(zeroplus) < precisionResid):
+			b = bplus
+			break
+       		elif (abs(zerominus) < precisionResid):
+			b = bminus
+			break
+       		else:
+			if ( abs(zeroplus) < abs(zero) ):
+				b = bplus
+			elif ( abs(zerominus) < abs(zero) ):
+				b = bminus
+			increment = increment/2.	
+				
+        return b
+	
+
+
+
+

### 2015-07-21 python_codes/paper_figures/lentiptical/n3115/instruments/fitResult.py

@@ -1,0 +1,115 @@
+import numpy as np
+
+from modelComponents.sersic import computeSersicParameters
+from modelComponents.disc import computeDiscParameters
+from modelComponents.gaussian import computeGaussianParameters
+from modelComponents.moffat import computeMoffatParameters
+
+############# PRINT FIT RESULT ##############
+
+def printFitResult(fit, componentslist, psfFunction):
+	
+	print '--------------------------------------------'
+	print 'Results from fit:'
+	print '--------------------------------------------'
+	print 'Number of iterations:', fit.nfev
+	print 'Chisq: ', fit.chisqr
+	print 'Reduced chisq: ', fit.redchi
+	print 'N_free: ', fit.nfree
+	##print 'Delta: ', deltarms   # [sum (residuals**2)/(N-N_dof)]**0.5
+
+	if (fit.success):
+		for component in componentslist:
+			namepar1 = 'par1_' + str(component.number)
+			namepar2 = 'par2_' + str(component.number)
+			namepar3 = 'par3_' + str(component.number)
+			namepar4 = 'par4_' + str(component.number)
+			print 'Component ' + str(component.number) + ': ' + component.name + '.'
+			
+			if (component.name == 'sersic'):
+				r_e = fit.params[namepar1].value
+				mu_e = fit.params[namepar2].value
+				n = fit.params[namepar3].value				
+				b, m_tot = computeSersicParameters(mu_e, r_e, n) 
+				print 'R_e [arcsec] = ', ("{0:.2f}".format(r_e)), '+/-', ("{0:.2f}".format(fit.params[namepar1].stderr)), '	[initial value =', component.parameters[namepar1].value, ']'
+				print 'mu_e [mag/arcsec^2] = ', ("{0:.2f}".format(mu_e)), '+/-', ("{0:.2f}".format(fit.params[namepar2].stderr)), '	 [initial value =', component.parameters[namepar2].value, ']'
+				print 'n = ', ("{0:.2f}".format(n)), '+/-', ("{0:.2f}".format(fit.params[namepar3].stderr)), '       [initial value =', component.parameters[namepar3].value, ']'
+				print 'b_n = ', ("{0:.2f}".format(b))
+				print 'm_tot [mag] = ', ("{0:.2f}".format(m_tot))
+			if (component.name == 'disc'):
[…]

### 2015-07-21 python_codes/paper_figures/lentiptical/n3115/instruments/plotting.py

@@ -1,0 +1,304 @@
+from modelComponents.disc import buildDisc
+from modelComponents.ferrer import buildFerrer
+from modelComponents.gaussian import buildGaussian
+from modelComponents.psf import buildPsf
+from modelComponents.psfWing import buildPsfWing
+from modelComponents.sersic import buildSersic
+from modelComponents.truncDisc import buildTruncDisc
+from modelComponents.truncSersic import buildTruncSersic
+from modelComponents.gaussRing import buildGaussRing
+from instruments.model import buildModel
+
+from convolution.psfConvolution import doPsfConvolution
+
+
+import numpy as np
+import pylab
+from matplotlib.pyplot import fill_between
+import matplotlib.pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib.ticker as ticker
+from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+from matplotlib import rc, font_manager
+
+from textwrap import wrap
+
+
+def doFitPanel(fitPanel, rrr, mu, good_rrr, good_mu, bad_rrr, bad_mu, maxsma_arcsec, minmu, maxmu, componentslist, finalparams, Settings, psfFunction, psfwing_02pxscale_datatab, psfwing_logscale_datatab, goodIndexes, skyRMS, deltarms, sampling, goodIndexes_integer, badIndexes_integer, gaussianSmoothing):
+	
+	sensitivity = Settings.zeropoint - 2.5*np.log10(skyRMS) + 2.5*np.log10(Settings.pxlToArcsec**2)
+	
+	fitPanel.set_xlim([maxsma_arcsec*(-0.1),1.1*maxsma_arcsec])
+	fitPanel.set_ylim([maxmu+1,minmu-1])
+
+	if (sensitivity>maxmu+0.5):
+		fitPanel.set_ylim([sensitivity+0.5,minmu-1])
+	
+	minorLocator   = MultipleLocator(xaxisMinorLocator)
+	fitPanel.xaxis.set_minor_locator(minorLocator)
+#  	majorLocator   = MultipleLocator(xaxisMajorLocator)
+#  	fitPanel.xaxis.set_major_locator(majorLocator)
+
+	majorLocator   = MultipleLocator(2)
+	minorLocator   = MultipleLocator(1)
[…]

### 2015-07-21 python_codes/paper_figures/lentiptical/n3115/reading/ellipseOutput.py

@@ -1,0 +1,16 @@
+import numpy as np
+
+######## READ ELLIPSE OUTPUT IN ARRAYS #############
+
+def readEllipseOutput(data):
+
+      data = open(data)
+      
+      datatab = np.genfromtxt(data, 
+              dtype={'names': ('row', 'sma', 'intens', 'intens_err', 'pix_var', 'rms', 'ellip', 'ellip_err', 'PA', 'PA_err', 'X0', 'X0_ERR', 'Y0', 'Y0_ERR', 'GRAD', 'GRAD_ERR', 'GRAD_R_ERR', 'RSMA', 'MAG', 'MAG_LERR', 'MAG_UERR', 'TFLUX_E', 'TFLUX_C', 'TMAG_E', 'TMAG_C', 'NPIX_E', 'NPIX_C', 'A3', 'A3_ERR', 'B3', 'B3_ERR', 'A4', 'A4_ERR', 'B4', 'B4_ERR'),
+              'formats': ('i4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4', 'f4')}, skiprows=5, missing_values=('INDEF'), filling_values=0.0)      
+      # !!! add missing value control (see genfromtxt function)
+      data.close()
+      
+      return datatab
+

### 2015-07-22 papers/lentiptical/lentiptical.tex
wed

@@
 
-Title: Lentiptical galaxies and their extraordinarily ordinary black holes \\
-Authors: G. A. D. Savorgnan and A. W. Graham \\
+Title: Lentiptical galaxies and their non-extraordinary black holes \\
+Authors: Giulia A. D. Savorgnan and Alister W. Graham \\
 Affiliation: Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia. \\
@@
 can assume any positive value. 
-However, several studies have taken into account only bulge/disk decompositions 
+However, several studies [ref] have taken into account only bulge/disk decompositions 
 in which the exponential-disk function neatly dominates over the S\'ersic-spheroid profile at large galaxy radii, 
@@
 they no longer appear as extreme outliers in the (black hole mass) -- (spheroid stellar mass) diagram. 
-Previous ``anomalies'' are explained by one simple ``rule'' 
-and no need di avere nuovi scenari
+Previous ``anomalies'' are explained and eliminated by one simple ``rule''. 
+This nullifies the need of invoking different evolutionary scenarios 
+for these galaxies and their non-extraordinary black holes.
 
@@
 %that the claimed bimodality is artificial
-
 %we show that the ell profile is enough to estabilish if the disk is embedded or not
-
 %Lentiptical galaxies are an intermediate class of galaxies between elliptical  

### 2015-07-29 papers/MbhMsph/mm.tex
wed

@@
 \\
-  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - \langle M_{\rm *,sph} \rangle)/{\rm M_\odot}]$} \\ [0.5em]
- Core-S\'ersic (22)     & BCES $(Y|X)$      & $9.06 \pm 0.09$ & $0.86 \pm 0.28$ & $11.28$ & $-$ & $0.42$ \\
- 			& mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.08}$ & $0.68^{+0.21}_{-0.20}$ & $11.28$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
-  			& {\tt linmix\_err} $(Y|X)$     & $9.04 \pm 0.10$ & $0.64 \pm 0.25$ & $11.28$ & $0.40 \pm 0.09$ & $0.42$ \\ [0.5em]
-			& BCES $(X|Y)$      & $9.06 \pm 0.12$ & $1.70 \pm 0.32$ & $11.28$ & $-$ & $0.61$ \\
- 			& mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $1.90^{+0.85}_{-0.46}$ & $11.28$ & $0.62^{+0.13}_{-0.10}$ & $0.68$ \\
- 			& {\tt linmix\_err} $(X|Y)$     & $9.03 \pm 0.17$ & $1.80 \pm 0.70$ & $11.28$ & $0.67 \pm 0.30$ & $0.65$ \\ [0.5em]
- 			& BCES Bisector     & $9.06 \pm 0.10$ & $1.19 \pm 0.23$ & $11.28$ & $-$ & $0.47$ \\
- 			& mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $1.12^{+0.35}_{-0.27}$ & $11.28$ & $-$                    & $0.46$ \\
- 			& {\tt linmix\_err} Bisector	& $9.04 \pm 0.14$ & $1.06 \pm 0.35$ & $11.28$ & $-$	& $0.45$ \\ [0.5em]
+  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} / \langle M_{\rm *,sph} \rangle)]$} \\ [0.5em]
+ Core-S\'ersic (22)     & BCES $(Y|X)$      & $9.06 \pm 0.09$ & $0.86 \pm 0.28$ & $10^{11.28}$ & $-$ & $0.42$ \\
+ 			& mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.08}$ & $0.68^{+0.21}_{-0.20}$ & $10^{11.28}$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
+  			& {\tt linmix\_err} $(Y|X)$     & $9.04 \pm 0.10$ & $0.64 \pm 0.25$ & $10^{11.28}$ & $0.40 \pm 0.09$ & $0.42$ \\ [0.5em]
+			& BCES $(X|Y)$      & $9.06 \pm 0.12$ & $1.70 \pm 0.32$ & $10^{11.28}$ & $-$ & $0.61$ \\
+ 			& mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $1.90^{+0.85}_{-0.46}$ & $10^{11.28}$ & $0.62^{+0.13}_{-0.10}$ & $0.68$ \\
+ 			& {\tt linmix\_err} $(X|Y)$     & $9.03 \pm 0.17$ & $1.80 \pm 0.70$ & $10^{11.28}$ & $0.67 \pm 0.30$ & $0.65$ \\ [0.5em]
+ 			& BCES Bisector     & $9.06 \pm 0.10$ & $1.19 \pm 0.23$ & $10^{11.28}$ & $-$ & $0.47$ \\
+ 			& mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $1.12^{+0.35}_{-0.27}$ & $10^{11.28}$ & $-$                    & $0.46$ \\
+ 			& {\tt linmix\_err} Bisector	& $9.04 \pm 0.14$ & $1.06 \pm 0.35$ & $10^{11.28}$ & $-$	& $0.45$ \\ [0.5em]
 
- S\'ersic (44)		& BCES $(Y|X)$      & $7.71 \pm 0.09$ & $0.95 \pm 0.21$ & $10.25$ & $-$ & $0.64$ \\
- 			& mFITEXY $(Y|X)$   & $7.72^{+0.10}_{-0.09}$ & $0.96^{+0.21}_{-0.21}$ & $10.25$ & $0.58^{+0.09}_{-0.07}$ & $0.64$ \\
- 			& {\tt linmix\_err} $(Y|X)$     & $7.73 \pm 0.10$ & $0.98 \pm 0.24$ & $10.25$ & $0.59 \pm 0.08$ & $0.65$ \\ [0.5em]
- 			& BCES $(X|Y)$      & $7.71 \pm 0.16$ & $2.52 \pm 0.54$ & $10.25$ & $-$ & $1.11$ \\
- 			& mFITEXY $(X|Y)$   & $7.72^{+0.16}_{-0.16}$ & $2.49^{+0.69}_{-0.45}$ & $10.25$ & $0.93^{+0.15}_{-0.13}$ & $1.10$ \\
- 			& {\tt linmix\_err} $(X|Y)$     & $7.73 \pm 0.17$ & $2.48 \pm 0.59$ & $10.25$ & $0.95 \pm 0.27$ & $1.10$ \\ [0.5em]
- 			& BCES Bisector     & $7.71 \pm 0.11$ & $1.48 \pm 0.20$ & $10.25$ & $-$ & $0.74$ \\
- 			& mFITEXY Bisector  & $7.72^{+0.13}_{-0.13}$ & $1.49^{+0.33}_{-0.28}$ & $10.25$ & $-$    & $0.74$ \\
- 			& {\tt linmix\_err} Bisector	& $7.73 \pm 0.14$ & $1.49 \pm 0.57$ & $10.25$ & $-$	& $0.74$ \\ [0.5em]
+ S\'ersic (44)		& BCES $(Y|X)$      & $7.71 \pm 0.09$ & $0.95 \pm 0.21$ & $10^{10.25}$ & $-$ & $0.64$ \\
+ 			& mFITEXY $(Y|X)$   & $7.72^{+0.10}_{-0.09}$ & $0.96^{+0.21}_{-0.21}$ & $10^{10.25}$ & $0.58^{+0.09}_{-0.07}$ & $0.64$ \\
+ 			& {\tt linmix\_err} $(Y|X)$     & $7.73 \pm 0.10$ & $0.98 \pm 0.24$ & $10^{10.25}$ & $0.59 \pm 0.08$ & $0.65$ \\ [0.5em]
+ 			& BCES $(X|Y)$      & $7.71 \pm 0.16$ & $2.52 \pm 0.54$ & $10^{10.25}$ & $-$ & $1.11$ \\
+ 			& mFITEXY $(X|Y)$   & $7.72^{+0.16}_{-0.16}$ & $2.49^{+0.69}_{-0.45}$ & $10^{10.25}$ & $0.93^{+0.15}_{-0.13}$ & $1.10$ \\
+ 			& {\tt linmix\_err} $(X|Y)$     & $7.73 \pm 0.17$ & $2.48 \pm 0.59$ & $10^{10.25}$ & $0.95 \pm 0.27$ & $1.10$ \\ [0.5em]
+ 			& BCES Bisector     & $7.71 \pm 0.11$ & $1.48 \pm 0.20$ & $10^{10.25}$ & $-$ & $0.74$ \\
+ 			& mFITEXY Bisector  & $7.72^{+0.13}_{-0.13}$ & $1.49^{+0.33}_{-0.28}$ & $10^{10.25}$ & $-$    & $0.74$ \\
+ 			& {\tt linmix\_err} Bisector	& $7.73 \pm 0.14$ & $1.49 \pm 0.57$ & $10^{10.25}$ & $-$	& $0.74$ \\ [0.5em]
 
-{\bf Early-type (E+S0)} (45)  & BCES $(Y|X)$       & $8.56 \pm 0.07$ & $0.85 \pm 0.12$ & $10.81$ & $-$ & $0.48$ \\
-                              & mFITEXY $(Y|X)$     & $8.56^{+0.06}_{-0.07}$ & $0.83^{+0.11}_{-0.11}$ & $10.81$ & $0.42^{+0.07}_{-0.05}$ & $0.48$ \\
-                              & {\tt linmix\_err} $(Y|X)$     & $8.55 \pm 0.07$ & $0.82 \pm 0.12$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\ [0.5em]
-                              & BCES $(X|Y)$       & $8.56 \pm 0.09$ & $1.27 \pm 0.13$ & $10.81$ & $-$ & $0.59$ \\
-                              & mFITEXY $(X|Y)$     & $8.54^{+0.08}_{-0.09}$ & $1.32^{+0.18}_{-0.15}$ & $10.81$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
-                              & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $1.29 \pm 0.17$ & $10.81$ & $0.54 \pm 0.11$ & $0.59$ \\ [0.5em]
-                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.04 \pm 0.10}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
-                              & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.05^{+0.14}_{-0.12}$ & $10.81$ & $-$                    & $0.51$ \\
-                              & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $1.03 \pm 0.19$ & $10.81$ & $-$    & $0.51$ \\ [0.5em]
+{\bf Early-type (E+S0)} (45)  & BCES $(Y|X)$       & $8.56 \pm 0.07$ & $0.85 \pm 0.12$ & $10^{10.81}$ & $-$ & $0.48$ \\
+                              & mFITEXY $(Y|X)$     & $8.56^{+0.06}_{-0.07}$ & $0.83^{+0.11}_{-0.11}$ & $10^{10.81}$ & $0.42^{+0.07}_{-0.05}$ & $0.48$ \\
+                              & {\tt linmix\_err} $(Y|X)$     & $8.55 \pm 0.07$ & $0.82 \pm 0.12$ & $10^{10.81}$ & $0.43 \pm 0.06$ & $0.48$ \\ [0.5em]
+                              & BCES $(X|Y)$       & $8.56 \pm 0.09$ & $1.27 \pm 0.13$ & $10^{10.81}$ & $-$ & $0.59$ \\
+                              & mFITEXY $(X|Y)$     & $8.54^{+0.08}_{-0.09}$ & $1.32^{+0.18}_{-0.15}$ & $10^{10.81}$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
+                              & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $1.29 \pm 0.17$ & $10^{10.81}$ & $0.54 \pm 0.11$ & $0.59$ \\ [0.5em]
+                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.04 \pm 0.10}$ & $\boldsymbol{10^{10.81}}$ & $-$ & $\boldsymbol{0.51}$ \\
+                              & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.05^{+0.14}_{-0.12}$ & $10^{10.81}$ & $-$                    & $0.51$ \\
+                              & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $1.03 \pm 0.19$ & $10^{10.81}$ & $-$    & $0.51$ \\ [0.5em]
 
-{\bf Late-type (Sp)} (17)    & BCES $(Y|X)$    & $7.18 \pm 0.17$ & $1.95 \pm 1.52$ & $10.05$ & $-$ & $0.74$ \\ 
-                             & mFITEXY $(Y|X)$     & $7.20^{+0.15}_{-0.16}$ & $1.22^{+0.70}_{-0.62}$  & $10.05$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
-                             & {\tt linmix\_err} $(Y|X)$  & $7.23 \pm 0.19$ & $0.96 \pm 0.96$ & $10.05$ & $0.67 \pm 0.16$ & $0.65$ \\ [0.5em]
-                             & BCES $(X|Y)$    & $7.18 \pm 0.39$ & $5.89 \pm 3.40$ & $10.05$ & $-$ & $1.70$ \\
-                             & mFITEXY $(X|Y)$     & $7.44^{+1.45}_{-0.52}$ & $7.14^{+26.31}_{-3.01}$ & $10.05$ & $1.49^{+0.56}_{-0.36}$ & $2.08$ \\
-                             & {\tt linmix\_err} $(X|Y)$  & $7.42 \pm 0.64$ & $6.96 \pm 6.73$ & $10.05$ & $1.83 \pm 1.86$ & $2.03$ \\ [0.5em]
-                             & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.21}$ & $\boldsymbol{3.00 \pm 1.30}$ & $\boldsymbol{10.05}$ & $-$ & $\boldsymbol{0.94}$ \\
-                             & {\bf mFITEXY Bisector}    & $\boldsymbol{7.24^{+1.04}_{-0.39}}$ & $\boldsymbol{2.28^{+1.67}_{-1.01}}$  & $\boldsymbol{10.05}$ & $-$    & $\boldsymbol{0.79}$ \\
-                             & {\tt linmix\_err} Bisector & $7.26 \pm 0.47$ & $1.94 \pm 216.38$ & $10.05$ & $-$    & $0.74$ \\ [0.5em]
+{\bf Late-type (Sp)} (17)    & BCES $(Y|X)$    & $7.18 \pm 0.17$ & $1.95 \pm 1.52$ & $10^{10.05}$ & $-$ & $0.74$ \\ 
+                             & mFITEXY $(Y|X)$     & $7.20^{+0.15}_{-0.16}$ & $1.22^{+0.70}_{-0.62}$  & $10^{10.05}$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
+                             & {\tt linmix\_err} $(Y|X)$  & $7.23 \pm 0.19$ & $0.96 \pm 0.96$ & $10^{10.05}$ & $0.67 \pm 0.16$ & $0.65$ \\ [0.5em]
+                             & BCES $(X|Y)$    & $7.18 \pm 0.39$ & $5.89 \pm 3.40$ & $10^{10.05}$ & $-$ & $1.70$ \\
+                             & mFITEXY $(X|Y)$     & $7.44^{+1.45}_{-0.52}$ & $7.14^{+26.31}_{-3.01}$ & $10^{10.05}$ & $1.49^{+0.56}_{-0.36}$ & $2.08$ \\
+                             & {\tt linmix\_err} $(X|Y)$  & $7.42 \pm 0.64$ & $6.96 \pm 6.73$ & $10^{10.05}$ & $1.83 \pm 1.86$ & $2.03$ \\ [0.5em]
+                             & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.21}$ & $\boldsymbol{3.00 \pm 1.30}$ & $\boldsymbol{10^{10.05}}$ & $-$ & $\boldsymbol{0.94}$ \\
+                             & {\bf mFITEXY Bisector}    & $\boldsymbol{7.24^{+1.04}_{-0.39}}$ & $\boldsymbol{2.28^{+1.67}_{-1.01}}$  & $\boldsymbol{10^{10.05}}$ & $-$    & $\boldsymbol{0.79}$ \\
+                             & {\tt linmix\_err} Bisector & $7.26 \pm 0.47$ & $1.94 \pm 216.38$ & $10^{10.05}$ & $-$    & $0.74$ \\ [0.5em]
 

### 2015-07-29 python_codes/paper_figures/lentiptical/mm.py

@@ -150,7 +150,7 @@ def mbh_vs_mass_sph():
 	mass_sph_m1216 = 2.27*10**11
 	mbh_m1216 = 10**10 ## upper limit
 	#ax.scatter([mass_sph_m1216], [mbh_m1216], marker='.', s=500, color='red', **scatter_kwargs)
-	ax.scatter([mass_sph_m1216], [mbh_m1216/1.5], marker=r'$\uparrow$', s=500, color='red', **scatter_kwargs)
+	ax.scatter([mass_sph_m1216], [mbh_m1216/1.5], marker=r'$\downarrow$', s=500, color='red', **scatter_kwargs)
 	
 	
 	for x0,y0 in zip(mass_sph[simplemorphtype=='S0'], mbh[simplemorphtype=='S0']):
@@ -166,7 +166,7 @@ def mbh_vs_mass_sph():
 	
 	x0 = mass_sph_n1277
 	y0 = mbh_n1277
-	ax.text(x0/1.3, 1.6*y0, 'N1277', size=12, color='red')
+	ax.text(x0/1.7, 1.6*y0, 'N1277', size=12, color='red')
 	
 	x0 = mass_sph_n1271
 	y0 = mbh_n1271
@@ -183,7 +183,7 @@ def mbh_vs_mass_sph():
 	
 	x0 = float(mass_sph[gal_id=='n3998'])
 	y0 = float(mbh[gal_id=='n3998'])
-	ax.text(x0/1.3, 1.3*y0, 'N3998', size=12, color='k')
+	ax.text(x0/0.95, 1.3*y0, 'N3998', size=12, color='k')
 	
         #for x0,y0 in zip(mass_sph[simplemorphtype=='S0/Sp'], mbh[simplemorphtype=='S0/Sp']):
 	#	markers.spiral(ax, 'darkorange', np.log10(x0), np.log10(y0), 0.04)
@@ -231,7 +231,7 @@ def mbh_vs_mass_sph():
 	ax.plot(10**(logxx+np.average(log_mass_sph[earlytype==1])),10**yy_3epsilon_lo, color='k', ls='--', linewidth=2.)
 	ax.fill_between(10**(logxx+np.average(log_mass_sph[earlytype==1])),10**yy_3epsilon_lo,10**yy_3epsilon_up,alpha=0.2, facecolor='gray') 
 	
-	ax.text(10**8.7, 10**6.9, r'$\pm 1 \sigma$', rotation=30, color='k', size=20)
[…]

### 2015-08-21 papers/MbhMsph/mm.tex
vaffanculo e venerdi

--- 2015-07-17 papers/MbhMsph/mm.tex
@@
                         & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
-                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.15$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]
+                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]
 
@@
                         & mFITEXY Bisector & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
-                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.10$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]
+                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.05$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]
 
@@
                        & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
-                       & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.09$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]
+                       & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.03$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]
 
@@
                        & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
-                       & {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.48 \pm 0.10$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]
+                       & {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]
 
@@
                    & mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $-0.47^{+0.12}_{-0.17}$ & $-25.73$ & $-$    & $0.48$ \\
-                   & {\tt linmix\_err} Bisector & $9.04 \pm 0.14$ & $-0.44 \pm 0.16$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]
+                   & {\tt linmix\_err} Bisector & $9.04 \pm 0.14$ & $-0.44 \pm 0.12$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]
 
@@
               & mFITEXY Bisector  & $7.72^{+0.11}_{-0.11}$ & $-0.61^{+0.10}_{-0.12}$ & $-22.92$ & $-$                    & $0.71$ \\
-              & {\tt linmix\_err} Bisector & $7.73 \pm 0.12$ & $-0.62 \pm 0.15$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
+              & {\tt linmix\_err} Bisector & $7.73 \pm 0.12$ & $-0.62 \pm 0.09$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
 
@@
                              & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
-                             & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.09$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]
+                             & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.04$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]
 
@@
                           & mFITEXY Bisector   & $7.26^{+0.40}_{-0.28}$ & $-1.03^{+0.33}_{-0.52}$ & $-22.33$ & $-$    & $0.82$ \\
-                          & {\tt linmix\_err} Bisector & $7.27 \pm 0.33$ & $-0.96 \pm 0.50$ & $-22.33$ & $-$    & $0.78$ \\ [0.5em]
+                          & {\tt linmix\_err} Bisector & $7.27 \pm 0.33$ & $-0.96 \pm 0.37$ & $-22.33$ & $-$    & $0.78$ \\ [0.5em]
 
@@
 \\
-  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - \langle M_{\rm *,sph} \rangle)/{\rm M_\odot}]$} \\ [0.5em]
- Core-S\'ersic (22)     & BCES $(Y|X)$      & $9.06 \pm 0.09$ & $0.86 \pm 0.28$ & $11.28$ & $-$ & $0.42$ \\
- 			& mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.08}$ & $0.68^{+0.21}_{-0.20}$ & $11.28$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
-  			& {\tt linmix\_err} $(Y|X)$     & $9.04 \pm 0.10$ & $0.64 \pm 0.25$ & $11.28$ & $0.40 \pm 0.09$ & $0.42$ \\ [0.5em]
-			& BCES $(X|Y)$      & $9.06 \pm 0.12$ & $1.70 \pm 0.32$ & $11.28$ & $-$ & $0.61$ \\
- 			& mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $1.90^{+0.85}_{-0.46}$ & $11.28$ & $0.62^{+0.13}_{-0.10}$ & $0.68$ \\
- 			& {\tt linmix\_err} $(X|Y)$     & $9.03 \pm 0.17$ & $1.80 \pm 0.70$ & $11.28$ & $0.67 \pm 0.30$ & $0.65$ \\ [0.5em]
- 			& BCES Bisector     & $9.06 \pm 0.10$ & $1.19 \pm 0.23$ & $11.28$ & $-$ & $0.47$ \\
- 			& mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $1.12^{+0.35}_{-0.27}$ & $11.28$ & $-$                    & $0.46$ \\
- 			& {\tt linmix\_err} Bisector	& $9.04 \pm 0.14$ & $1.06 \pm 0.35$ & $11.28$ & $-$	& $0.45$ \\ [0.5em]
+  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} / \langle M_{\rm *,sph} \rangle)]$} \\ [0.5em]
+ Core-S\'ersic (22)     & BCES $(Y|X)$      & $9.06 \pm 0.09$ & $0.86 \pm 0.28$ & $10^{11.28}$ & $-$ & $0.42$ \\
+ 			& mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.08}$ & $0.68^{+0.21}_{-0.20}$ & $10^{11.28}$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
+  			& {\tt linmix\_err} $(Y|X)$     & $9.04 \pm 0.10$ & $0.64 \pm 0.25$ & $10^{11.28}$ & $0.40 \pm 0.09$ & $0.42$ \\ [0.5em]
+			& BCES $(X|Y)$      & $9.06 \pm 0.12$ & $1.70 \pm 0.32$ & $10^{11.28}$ & $-$ & $0.61$ \\
+ 			& mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $1.90^{+0.85}_{-0.46}$ & $10^{11.28}$ & $0.62^{+0.13}_{-0.10}$ & $0.68$ \\
+ 			& {\tt linmix\_err} $(X|Y)$     & $9.03 \pm 0.17$ & $1.80 \pm 0.70$ & $10^{11.28}$ & $0.67 \pm 0.30$ & $0.65$ \\ [0.5em]
+ 			& BCES Bisector     & $9.06 \pm 0.10$ & $1.19 \pm 0.23$ & $10^{11.28}$ & $-$ & $0.47$ \\
+ 			& mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $1.12^{+0.35}_{-0.27}$ & $10^{11.28}$ & $-$                    & $0.46$ \\
+ 			& {\tt linmix\_err} Bisector	& $9.04 \pm 0.14$ & $1.06 \pm 0.26$ & $10^{11.28}$ & $-$	& $0.45$ \\ [0.5em]
 
- S\'ersic (44)		& BCES $(Y|X)$      & $7.71 \pm 0.09$ & $0.95 \pm 0.21$ & $10.25$ & $-$ & $0.64$ \\
- 			& mFITEXY $(Y|X)$   & $7.72^{+0.10}_{-0.09}$ & $0.96^{+0.21}_{-0.21}$ & $10.25$ & $0.58^{+0.09}_{-0.07}$ & $0.64$ \\
- 			& {\tt linmix\_err} $(Y|X)$     & $7.73 \pm 0.10$ & $0.98 \pm 0.24$ & $10.25$ & $0.59 \pm 0.08$ & $0.65$ \\ [0.5em]
- 			& BCES $(X|Y)$      & $7.71 \pm 0.16$ & $2.52 \pm 0.54$ & $10.25$ & $-$ & $1.11$ \\
- 			& mFITEXY $(X|Y)$   & $7.72^{+0.16}_{-0.16}$ & $2.49^{+0.69}_{-0.45}$ & $10.25$ & $0.93^{+0.15}_{-0.13}$ & $1.10$ \\
- 			& {\tt linmix\_err} $(X|Y)$     & $7.73 \pm 0.17$ & $2.48 \pm 0.59$ & $10.25$ & $0.95 \pm 0.27$ & $1.10$ \\ [0.5em]
- 			& BCES Bisector     & $7.71 \pm 0.11$ & $1.48 \pm 0.20$ & $10.25$ & $-$ & $0.74$ \\
- 			& mFITEXY Bisector  & $7.72^{+0.13}_{-0.13}$ & $1.49^{+0.33}_{-0.28}$ & $10.25$ & $-$    & $0.74$ \\
- 			& {\tt linmix\_err} Bisector	& $7.73 \pm 0.14$ & $1.49 \pm 0.57$ & $10.25$ & $-$	& $0.74$ \\ [0.5em]
+ S\'ersic (44)		& BCES $(Y|X)$      & $7.71 \pm 0.09$ & $0.95 \pm 0.21$ & $10^{10.25}$ & $-$ & $0.64$ \\
+ 			& mFITEXY $(Y|X)$   & $7.72^{+0.10}_{-0.09}$ & $0.96^{+0.21}_{-0.21}$ & $10^{10.25}$ & $0.58^{+0.09}_{-0.07}$ & $0.64$ \\
+ 			& {\tt linmix\_err} $(Y|X)$     & $7.73 \pm 0.10$ & $0.98 \pm 0.24$ & $10^{10.25}$ & $0.59 \pm 0.08$ & $0.65$ \\ [0.5em]
+ 			& BCES $(X|Y)$      & $7.71 \pm 0.16$ & $2.52 \pm 0.54$ & $10^{10.25}$ & $-$ & $1.11$ \\
+ 			& mFITEXY $(X|Y)$   & $7.72^{+0.16}_{-0.16}$ & $2.49^{+0.69}_{-0.45}$ & $10^{10.25}$ & $0.93^{+0.15}_{-0.13}$ & $1.10$ \\
+ 			& {\tt linmix\_err} $(X|Y)$     & $7.73 \pm 0.17$ & $2.48 \pm 0.59$ & $10^{10.25}$ & $0.95 \pm 0.27$ & $1.10$ \\ [0.5em]
+ 			& BCES Bisector     & $7.71 \pm 0.11$ & $1.48 \pm 0.20$ & $10^{10.25}$ & $-$ & $0.74$ \\
+ 			& mFITEXY Bisector  & $7.72^{+0.13}_{-0.13}$ & $1.49^{+0.33}_{-0.28}$ & $10^{10.25}$ & $-$    & $0.74$ \\
+ 			& {\tt linmix\_err} Bisector	& $7.73 \pm 0.14$ & $1.49 \pm 0.24$ & $10^{10.25}$ & $-$	& $0.74$ \\ [0.5em]
 
-{\bf Early-type (E+S0)} (45)  & BCES $(Y|X)$       & $8.56 \pm 0.07$ & $0.85 \pm 0.12$ & $10.81$ & $-$ & $0.48$ \\
-                              & mFITEXY $(Y|X)$     & $8.56^{+0.06}_{-0.07}$ & $0.83^{+0.11}_{-0.11}$ & $10.81$ & $0.42^{+0.07}_{-0.05}$ & $0.48$ \\
-                              & {\tt linmix\_err} $(Y|X)$     & $8.55 \pm 0.07$ & $0.82 \pm 0.12$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\ [0.5em]
-                              & BCES $(X|Y)$       & $8.56 \pm 0.09$ & $1.27 \pm 0.13$ & $10.81$ & $-$ & $0.59$ \\
-                              & mFITEXY $(X|Y)$     & $8.54^{+0.08}_{-0.09}$ & $1.32^{+0.18}_{-0.15}$ & $10.81$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
-                              & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $1.29 \pm 0.17$ & $10.81$ & $0.54 \pm 0.11$ & $0.59$ \\ [0.5em]
-                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.04 \pm 0.10}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
-                              & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.05^{+0.14}_{-0.12}$ & $10.81$ & $-$                    & $0.51$ \\
-                              & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $1.03 \pm 0.19$ & $10.81$ & $-$    & $0.51$ \\ [0.5em]
+{\bf Early-type (E+S0)} (45)  & BCES $(Y|X)$       & $8.56 \pm 0.07$ & $0.85 \pm 0.12$ & $10^{10.81}$ & $-$ & $0.48$ \\
+                              & mFITEXY $(Y|X)$     & $8.56^{+0.06}_{-0.07}$ & $0.83^{+0.11}_{-0.11}$ & $10^{10.81}$ & $0.42^{+0.07}_{-0.05}$ & $0.48$ \\
+                              & {\tt linmix\_err} $(Y|X)$     & $8.55 \pm 0.07$ & $0.82 \pm 0.12$ & $10^{10.81}$ & $0.43 \pm 0.06$ & $0.48$ \\ [0.5em]
+                              & BCES $(X|Y)$       & $8.56 \pm 0.09$ & $1.27 \pm 0.13$ & $10^{10.81}$ & $-$ & $0.59$ \\
+                              & mFITEXY $(X|Y)$     & $8.54^{+0.08}_{-0.09}$ & $1.32^{+0.18}_{-0.15}$ & $10^{10.81}$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
+                              & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $1.29 \pm 0.17$ & $10^{10.81}$ & $0.54 \pm 0.11$ & $0.59$ \\ [0.5em]
+                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.04 \pm 0.10}$ & $\boldsymbol{10^{10.81}}$ & $-$ & $\boldsymbol{0.51}$ \\
+                              & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.05^{+0.14}_{-0.12}$ & $10^{10.81}$ & $-$                    & $0.51$ \\
+                              & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $1.03 \pm 0.10$ & $10^{10.81}$ & $-$    & $0.51$ \\ [0.5em]
 
-{\bf Late-type (Sp)} (17)    & BCES $(Y|X)$    & $7.18 \pm 0.17$ & $1.95 \pm 1.52$ & $10.05$ & $-$ & $0.74$ \\ 
-                             & mFITEXY $(Y|X)$     & $7.20^{+0.15}_{-0.16}$ & $1.22^{+0.70}_{-0.62}$  & $10.05$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
-                             & {\tt linmix\_err} $(Y|X)$  & $7.23 \pm 0.19$ & $0.96 \pm 0.96$ & $10.05$ & $0.67 \pm 0.16$ & $0.65$ \\ [0.5em]
-                             & BCES $(X|Y)$    & $7.18 \pm 0.39$ & $5.89 \pm 3.40$ & $10.05$ & $-$ & $1.70$ \\
-                             & mFITEXY $(X|Y)$     & $7.44^{+1.45}_{-0.52}$ & $7.14^{+26.31}_{-3.01}$ & $10.05$ & $1.49^{+0.56}_{-0.36}$ & $2.08$ \\
-                             & {\tt linmix\_err} $(X|Y)$  & $7.42 \pm 0.64$ & $6.96 \pm 6.73$ & $10.05$ & $1.83 \pm 1.86$ & $2.03$ \\ [0.5em]
-                             & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.21}$ & $\boldsymbol{3.00 \pm 1.30}$ & $\boldsymbol{10.05}$ & $-$ & $\boldsymbol{0.94}$ \\
-                             & {\bf mFITEXY Bisector}    & $\boldsymbol{7.24^{+1.04}_{-0.39}}$ & $\boldsymbol{2.28^{+1.67}_{-1.01}}$  & $\boldsymbol{10.05}$ & $-$    & $\boldsymbol{0.79}$ \\
-                             & {\tt linmix\_err} Bisector & $7.26 \pm 0.47$ & $1.94 \pm 216.38$ & $10.05$ & $-$    & $0.74$ \\ [0.5em]
+{\bf Late-type (Sp)} (17)    & BCES $(Y|X)$    & $7.18 \pm 0.17$ & $1.95 \pm 1.52$ & $10^{10.05}$ & $-$ & $0.74$ \\ 
+                             & mFITEXY $(Y|X)$     & $7.20^{+0.15}_{-0.16}$ & $1.22^{+0.70}_{-0.62}$  & $10^{10.05}$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
+                             & {\tt linmix\_err} $(Y|X)$  & $7.23 \pm 0.19$ & $0.96 \pm 0.96$ & $10^{10.05}$ & $0.67 \pm 0.16$ & $0.65$ \\ [0.5em]
+                             & BCES $(X|Y)$    & $7.18 \pm 0.39$ & $5.89 \pm 3.40$ & $10^{10.05}$ & $-$ & $1.70$ \\
+                             & mFITEXY $(X|Y)$     & $7.44^{+1.45}_{-0.52}$ & $7.14^{+26.31}_{-3.01}$ & $10^{10.05}$ & $1.49^{+0.56}_{-0.36}$ & $2.08$ \\
+                             & {\tt linmix\_err} $(X|Y)$  & $7.42 \pm 0.64$ & $6.96 \pm 6.73$ & $10^{10.05}$ & $1.83 \pm 1.86$ & $2.03$ \\ [0.5em]
+                             & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.21}$ & $\boldsymbol{3.00 \pm 1.30}$ & $\boldsymbol{10^{10.05}}$ & $-$ & $\boldsymbol{0.94}$ \\
+                             & {\bf mFITEXY Bisector}    & $\boldsymbol{7.24^{+1.04}_{-0.39}}$ & $\boldsymbol{2.28^{+1.67}_{-1.01}}$  & $\boldsymbol{10^{10.05}}$ & $-$    & $\boldsymbol{0.79}$ \\
+                             & {\tt linmix\_err} Bisector & $7.26 \pm 0.47$ & $1.94 \pm 1.24$ & $10^{10.05}$ & $-$    & $0.74$ \\ [0.5em]
 

### 2015-08-21 papers/mbhn/mbhn.tex
vaffanculo e venerdi

@@
 \usepackage{natbib}
-\bibliographystyle{apj}
+%\bibliographystyle{apj}
 \usepackage{longtable}
@@
 
-%% Keywords should appear after the \end{abstract} command. The uncommented
-%% example has been keyed in ApJ style. See the instructions to authors
-%% for the journal to which you are submitting your paper to determine
-%% what keyword punctuation is appropriate.
-
 \keywords{keywords}
-
-%% From the front matter, we move on to the body of the paper.
-%% In the first two sections, notice the use of the natbib \citep
-%% and \citet commands to identify citations.  The citations are
-%% tied to the reference list via symbolic KEYs. The KEY corresponds
-%% to the KEY in the \bibitem in the reference list below. We have
-%% chosen the first three characters of the first author's name plus
-%% the last two numeral of the year of publication as our KEY for
-%% each reference.
-
-%% Authors who wish to have the most important objects in their paper
-%% linked in the electronic edition to a data center may do so by tagging
-%% their objects with \objectname{} or \object{}.  Each macro takes the
-%% object name as its required argument. The optional, square-bracket 
-%% argument should be used in cases where the data center identification
-%% differs from what is to be printed in the paper.  The text appearing 
-%% in curly braces is what will appear in print in the published paper. 
-%% If the object name is recognized by the data centers, it will be linked
-%% in the electronic edition to the object data available at the data centers  
-%%
-%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
-%% the brackets must be escaped with backslashes when used in the first
-%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
-%%  Otherwise, LaTeX will issue an error.
 
@@
 
-%%A focal problem today in the dynamics of globular clusters is core collapse.
-%%It has been predicted by theory for decades \citep{hen61,lyn68,spi85}, but
-%%observation has been less alert to the phenomenon. For many years the
-%%central brightness peak in M15 \citep{kin75,new78} seemed a unique anomaly.
-%%Then \citet{aur82} suggested a central peak in \object{NGC 6397}, and a
-%%limited photographic survey of ours \citep[Paper I]{djo84} found three more
-%%cases, \objectname{NGC 6624}, \objectname[M 15]{NGC 7078}, and
-%%\object[Cl 1938-341]{Terzan 8}), whose sharp center had often been
-%%remarked on \citep{can78}.
-%%
-%%As an example of how the new AASTeX object tagging macros work, we will
-%%cite some of the ``Superlative'' objects mentioned in section 10 of
-%%Trimble's (1992) review of astrophysics in the year 1991.  The youngest
-%%star yet found was \object[\[JCC87\] IRAS 4]{IRAS 4} in \objectname{NGC 1333}.
-%%\object{70 Oph} was found to be the longest period spectroscopic binary.
-%%The most massive white dwarf was \object{GD 50}, estimated at 1.2 solar masses.
-%%The first neutral hydrogen found in a globular cluster was \object{NGC 2808}
-%%while the \objectname[SDSS J093401.92+551427.9]{I Zw 18} retained the
-%%record for metal deficiency.  However, another low metallicitity
-%%galaxy was \object{UGC 4483} in the \objectname{M 83} group. The
-%%largest redshift \object[PC 1247+3406]{source} in 1991 was found at
-%%z=4.897.  Lastly, what paper would be complete without a mention of the
-%%\object[M1]{Crab nebula}!
-
-\section{Errors}
-
-How do we compute the errors on the measured S\'ersic indices?
-Montecarlo, bootstrapping or any other evil statistical method do not take into account the systematics,
-which mainly depend on the decomposition model, i.e. the choice of the model components.
-But we are lucky, since there are many other decompositions in the literature for our galaxies.
-\cite{grahamdriver2007,laurikainen2010,sani2011,vika2012,beifiori2012,rusli2013,lasker2014data} have done this job.
-So how about we do something similar to our first paper?
-Let's say that I am not better than anybody else at decomposing galaxies 
-(this is obviously absurd, given my incredible competence in vivisecting galaxies, but let's assume it for now).
-I repeat the same game we did in our first paper.
-For each galaxy, I take all the available measurements from the literature, including my own measurement,
-and I compute the standard deviation of each set of measurements.
-The standard deviation becomes the error of my own measurement.
-When my measurement is the only available (nobody other than me ever decomposed that galaxy),
-the errors is set to be equal to the median value of the distribution in Figure \ref{fig:hist} 
-(almost the same we did in our first paper, see footnote 4).
-Figure \ref{fig:hist}: here only galaxies with more than one measurement are contributing.
-Take a galaxy, take its set of measurements (more than one!) of the S\'ersic index, 
-compute the standard deviation of that set, the standard deviation becomes the error on my own measurement
-(BTW, I am using the $n$ derived from the equivalent axis fit).
-The distribution of the standard deviations is represented by the histogram.
-The median value is $0.13$, which means a median uncertainty of $33\%$ on each individual measurement.
-If we take of each set of measurements the average, then the error associated to the average 
-and then the median value of all these errors, basically we are doing the same we did in footnote 4 of our first paper,
-and the cool thing is that now we get the same number we got then ($20\%$).
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/auxiliary/histo_err_logn.eps}
-\caption{}
-\label{fig:hist}
-\end{figure}
-
 \section{Results}
 
-Figure \ref{fig:mbhn}: Well, we now have the errors on each of OUR measurements of $n$.
-We can plot bh mass vs $n$ (in log).
+\begin{table*}
+\centering
+\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
+\begin{tabular}{llccccc}
+\tableline
+\tableline
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+\tableline 
+\\
+ & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
+All (62)               & BCES $(Y|X)$               & $-23.88 \pm 0.15$ & $-7.17 \pm 0.80$ & $0.51$ & $-$ & $1.18$ \\
+                       & mFITEXY $(Y|X)$            & $-23.95 \pm 0.13$ & $-6.70 \pm 0.45$ & $0.51$ & $0.56^{+0.15}_{-0.10}$ & $0.98$ \\
+                       & {\tt linmix\_err} $(Y|X)$  & $-23.92 \pm 0.15$ & $-6.40 \pm 0.57$ & $0.51$ & $0.74 \pm 0.13$ & $1.07$ \\ [0.5em]
+                       & BCES $(X|Y)$               & $-23.88 \pm 0.14$ & $-6.70 \pm 0.51$ & $0.51$ & $-$ & $1.11$ \\
+                       & mFITEXY $(X|Y)$            & $-23.94 \pm 0.14$ & $-7.50 \pm 0.52$ & $0.51$ & $0.59^{+0.17}_{-0.11}$ & $1.23$ \\
+                       & {\tt linmix\_err} $(X|Y)$  & $-23.94 \pm 0.16$ & $-7.51 \pm 0.62$ & $0.51$ & $0.81 \pm 0.16$ & $1.23$ \\ [0.5em]
+                       & BCES Bisector              & $-23.88 \pm 0.14$ & $-6.93 \pm 0.60$ & $0.51$ & $-$ & $1.14$ \\
+                       & mFITEXY Bisector           & $-23.94 \pm 0.13$ & $-7.08 \pm 0.34$ & $0.51$ & $-$ & $1.16$ \\
+                       & {\tt linmix\_err} Bisector & $-23.93 \pm 0.16$ & $-6.91 \pm 0.42$ & $0.51$ & $-$ & $1.14$ \\ [0.5em]
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/mbh_vs_logn.eps}
-\caption{}
-\label{fig:mbhn}
-\end{figure}
+Elliptical (30)	       & BCES $(Y|X)$		    & $-25.46 \pm 1.12$ & $38.47 \pm 114.45$ & $0.76$ & $-$ & $6.37$ \\
+		       & mFITEXY $(Y|X)$	    & $-25.74 \pm 0.18$ & $-9.74 \pm 1.59$ & $0.76$ & $0.24^{+0.32}_{-0.24}$ & $0.94$ \\
+		       & {\tt linmix\_err} $(Y|X)$  & $-25.65 \pm 0.21$ & $-7.87 \pm 2.15$ & $0.76$ & $0.61 \pm 0.22$ & $1.06$ \\ [0.5em]
+		       & BCES $(X|Y)$		    & $-25.46 \pm 0.23$ & $-10.73 \pm 3.21$ & $0.76$ & $-$ & $1.29$ \\
+		       & mFITEXY $(X|Y)$	    & $-25.74 \pm 0.20$ & $-10.42 \pm 1.79$ & $0.76$ & $0.22^{+0.38}_{-0.22}$ & $1.29$ \\
+		       & {\tt linmix\_err} $(X|Y)$  & $-25.72 \pm 0.28$ & $-10.92 \pm 2.70$ & $0.76$ & $0.73 \pm 0.34$ & $1.33$ \\ [0.5em]
+		       & BCES Bisector  	    & $-25.46 \pm 0.20$ & $0.03 \pm 0.05$ & $0.76$ & $-$ & $1.14$ \\
+		       & mFITEXY Bisector	    & $-25.74 \pm 0.19$ & $-10.07 \pm 1.19$ & $0.76$ & $-$ & $1.26$ \\
+		       & {\tt linmix\_err} Bisector & $-25.68 \pm 0.25$ & $-9.15 \pm 1.74$ & $0.76$ & $-$ & $1.16$ \\ [0.5em]
 
-Figure \ref{fig:mbhavn}: Almost the same we did in our first paper. We take for each galaxy its set of measurements of $n$,
-we reject measurements in disagreement for more than $50\%$,
-we compute the median (not the average! this is different from what we did in the past, what do you think?) 
-and the error associated to the mean, then we plot the black hole masses vs the median of log(n).
-The correlation looks a bit steeper than in Figure \ref{fig:mbhn}, 
-with less scatter. I bet you say it looks curved.
+Lenticular (11)	       & BCES $(Y|X)$		    & $-22.08 \pm 1.66$ & $33.52 \pm 98.87$ & $0.33$ & $-$ & $6.09$ \\
+		       & mFITEXY $(Y|X)$	    & $-22.11 \pm 0.24$ & $-6.31 \pm 2.45$ & $0.33$ & $0.42^{+0.28}_{-0.17}$ & $0.71$ \\
+		       & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
+		       & BCES $(X|Y)$		    & $-22.08 \pm 0.19$ & $-6.83 \pm 1.16$ & $0.33$ & $-$ & $0.71$ \\
+		       & mFITEXY $(X|Y)$	    & $-21.94 \pm 0.44$ & $-13.16 \pm 7.91$ & $0.33$ & $0.61^{+0.60}_{-0.56}$ & $1.39$ \\
+		       & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
+		       & BCES Bisector  	    & $-22.08 \pm 0.30$ & $0.06 \pm 0.05$ & $0.33$ & $-$ & $1.09$ \\
+		       & mFITEXY Bisector	    & $-22.05 \pm 0.35$ & $-8.55 \pm 2.79$ & $0.33$ & $-$ & $0.84$ \\
+		       & {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]
 
-PS I will soon step back from the division bulges/ellipticals, 
-I seriously believe there is no such division. 
-I will explain this soon. ;)
+Spiral (17)	       & BCES $(Y|X)$		    & $-22.33 \pm 0.26$ & $-5.31 \pm 5.83$ & $0.18$ & $-$ & $1.15$ \\
+		       & mFITEXY $(Y|X)$	    & $-22.22 \pm 0.19$ & $-2.17 \pm 0.98$ & $0.18$ & $0.53^{+0.24}_{-0.13}$ & $0.72$ \\
+		       & {\tt linmix\_err} $(Y|X)$  & $-22.26 \pm 0.24$ & $-1.53 \pm 1.88$ & $0.18$ & $0.71 \pm      0.22$ & $0.78$ \\ [0.5em]
+		       & BCES $(X|Y)$		    & $-22.33 \pm 0.26$ & $-5.19 \pm 3.77$ & $0.18$ & $-$ & $1.13$ \\
+		       & mFITEXY $(X|Y)$	    & $-22.28 \pm 0.44$ & $-9.08 \pm 5.31$ & $0.51$ & $1.12^{+0.54}_{-0.31}$ & $1.83$ \\
+		       & {\tt linmix\_err} $(X|Y)$  & $-22.24 \pm 0.71$ & $-11.12 \pm 13.59$ & $0.18$ & $1.95 \pm 2.47$ & $2.24$ \\ [0.5em]
+		       & BCES Bisector  	    & $-22.33 \pm 0.26$ & $-5.25 \pm 3.38$ & $0.18$ & $-$ & $1.14$ \\
+		       & mFITEXY Bisector	    & $-22.23 \pm 0.33$ & $-3.60 \pm 1.29$ & $0.18$ & $-$ & $0.92$ \\
+		       & {\tt linmix\_err} Bisector & $-22.25 \pm 0.53$ & $-2.88 \pm 2.66$ & $0.18$ & $-$ & $0.84$ \\ [0.5em]
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{/Users/gsavorgnan/galaxy_vivisection/results/plots/scaling_relations/mbh_vs_median_logn.eps}
-\caption{}
-\label{fig:mbhavn}
-\end{figure}
+\tableline 
+\tableline
+\end{tabular}
+\end{table*}
+
+\begin{table*}
+\centering
+\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
+\begin{tabular}{llccccc}
+\tableline
+\tableline
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+\tableline 
+\\
+Early-type (43)	       & BCES $(Y|X)$		    & $-24.55 \pm 0.22$ & $-11.84 \pm 2.29$ & $0.64$ & $-$ & $1.50$ \\
+		       & mFITEXY $(Y|X)$	    & $-24.74 \pm 0.14$ & $-8.86 \pm 0.66$ & $0.51$ & $0.27^{+0.20}_{-0.27}$ & $0.87$ \\
+		       & {\tt linmix\_err} $(Y|X)$  & $-24.70 \pm 0.17$ & $-8.28 \pm 0.87$ & $0.64$ & $0.58 \pm 0.17$ & $0.98$ \\ [0.5em]
+		       & BCES $(X|Y)$		    & $-24.55 \pm 0.14$ & $-8.25 \pm 0.63$ & $0.64$ & $-$ & $0.96$ \\
+		       & mFITEXY $(X|Y)$	    & $-24.74 \pm 0.14$ & $-9.13 \pm 0.68$ & $0.64$ & $0.23^{+0.25}_{-0.23}$ & $1.08$ \\
+		       & {\tt linmix\_err} $(X|Y)$  & $-24.73 \pm 0.18$ & $-9.08 \pm 0.87$ & $0.64$ & $0.60 \pm 0.21$ & $1.07$ \\ [0.5em]
+		       & BCES Bisector  	    & $-24.55 \pm 0.17$ & $-9.73 \pm 1.05$ & $0.64$ & $-$ & $1.14$ \\
+		       & mFITEXY Bisector	    & $-24.74 \pm 0.14$ & $-8.99 \pm 0.48$ & $0.64$ & $-$ & $1.06$ \\
+		       & {\tt linmix\_err} Bisector & $-24.72 \pm 0.17$ & $-8.66 \pm 0.63$ & $0.64$ & $-$ & $1.02$ \\ [0.5em]
+
+Bulges (30)	       & BCES $(Y|X)$		    & $-22.25 \pm 0.20$ & $-5.88 \pm 3.06$ & $0.26$ & $-$ & $1.16$ \\
+		       & mFITEXY $(Y|X)$	    & $-22.19 \pm 0.14$ & $-2.99 \pm 0.73$ & $0.26$ & $0.52^{+0.18}_{-0.10}$ & $0.75$ \\
+		       & {\tt linmix\_err} $(Y|X)$  & $-22.20 \pm 0.17$ & $-2.48 \pm 1.21$ & $0.26$ & $0.67 \pm 0.15$ & $0.83$ \\ [0.5em]
+		       & BCES $(X|Y)$		    & $-22.25 \pm 0.20$ & $-5.85 \pm 1.83$ & $0.26$ & $-$ & $1.15$ \\
+		       & mFITEXY $(X|Y)$	    & $-22.17 \pm 0.25$ & $-7.65 \pm 2.43$ & $0.26$ & $0.87^{+0.30}_{-0.18}$ & $1.46$ \\
+		       & {\tt linmix\_err} $(X|Y)$  & $-22.16 \pm 0.31$ & $-7.80 \pm 3.89$ & $0.26$ & $1.18 \pm 0.65$ & $1.48$ \\ [0.5em]
+		       & BCES Bisector  	    & $-22.25 \pm 0.20$ & $-5.87 \pm 2.06$ & $0.26$ & $-$ & $1.16$ \\
+		       & mFITEXY Bisector	    & $-22.18 \pm 0.20$ & $-4.34 \pm 0.84$ & $0.26$ & $-$ & $0.96$ \\
+		       & {\tt linmix\_err} Bisector & $-22.19 \pm 0.25$ & $-3.83 \pm 1.39$ & $0.26$ & $-$ & $0.91$ \\ [0.5em]
+
+%All (xx)		& BCES $(Y|X)$  	     & $$ & $$ & $$ & $$ & $$ \\
+%			& mFITEXY $(Y|X)$	     & $$ & $$ & $$ & $$ & $$ \\
+%			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
+%			& BCES $(X|Y)$  	     & $$ & $$ & $$ & $$ & $$ \\
+%			& mFITEXY $(X|Y)$	     & $$ & $$ & $$ & $$ & $$ \\
+%			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
+%			& BCES Bisector 	     & $$ & $$ & $$ & $$ & $$ \\
+%			& mFITEXY Bisector	     & $$ & $$ & $$ & $$ & $$ \\
+%			& {\tt linmix\_err} Bisector & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
+%
+
+\tableline 
+\tableline
+\end{tabular}
+\label{tab:lregsph} 
+\tablecomments{For each subsample, we indicate $\langle MAG_{\rm sph} \rangle$, its average value of spheroid magnitudes. 
+In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. 
+Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2). }
+\end{table*}
 
@@
 
-%% In a manner similar to \objectname authors can provide links to dataset
-%% hosted at participating data centers via the \dataset{} command.  The
-%% second curly bracket argument is printed in the text while the first
-%% parentheses argument serves as the valid data set identifier.  Large
-%% lists of data set are best provided in a table (see Table 3 for an example).
-%% Valid data set identifiers should be obtained from the data center that
-%% is currently hosting the data.
-%%
-%% Note that AASTeX interprets everything between the curly braces in the 
-%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
-%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
-%% compile your manuscript.  Special characters do not 
-%% need to be escaped in the optional, square-bracket argument.
-
-%% All our observations were short direct exposures with CCD's.  We also have
-%% a random {\it Chandra} data set \dataset{ADS/Sa.ASCA\#X/86008020} and a
-%% neat \dataset[ADS/Sa.HST#Y0Q70101T]{HST FOS spectrum} that readers can access
-%% via the links in the electronic edition.  Unfortunately this has nothing
-%% whatsoever to do with this research.  At Lick Observatory we used a TI 500$\times$500
-%% chip and a GEC 575$\times$385, on the 1-m Nickel reflector.  The only
-%% filter available at Lick was red.  At CTIO we used a GEC 575$\times$385, with
-%% $B, V,$ and $R$ filters, and an RCA 512$\times$320, with $U, B, V, R,$ and $I$
-%% filters, on the 1.5-m reflector. In the CTIO observations we tried to
-%% concentrate on the shortest practicable wavelengths; but faintness, reddening,
-%% and poor short-wavelength sensitivity often kept us from observing in $U$ or
-%% even in $B$. All four cameras had scales of the order of 0.4 arcsec/pixel, and
-%% our field sizes were around 3 arcmin.
-%%
-%% The CCD images are unfortunately not always suitable, for very poor
-%% clusters or for clusters with large cores.  Since the latter are easily
-%% studied by other means, we augmented our own CCD profiles by collecting
-%% from the literature a number of star-count profiles
-%% \citep{kin68,pet76,har84,ort85}, as well as photoelectric profiles
-%% \citep{kin66,kin75} and electronographic profiles \citep{kro84}.
-%% In a few cases we judged normality by eye estimates on one of the Sky
-%% Surveys.
-
-%% In this section, we use  the \subsection command to set off
-%% a subsection.  \footnote is used to insert a footnote to the text.
-
-%% Observe the use of the LaTeX \label
-%% command after the \subsection to give a symbolic KEY to the
-%% subsection for cross-referencing in a \ref command.
-%% You can use LaTeX's \ref and \label commands to keep track of
-%% cross-references to sections, equations, tables, and figures.
-%% That way, if you change the order of any elements, LaTeX will
-%% automatically renumber them.
-
-%% This section also includes several of the displayed math environments
-%% mentioned in the Author Guide.
-
-%%\section{Helicity Amplitudes}
-%%
-%%It has been realized that helicity amplitudes provide a convenient means
-%%for Feynman diagram\footnote{Footnotes can be inserted like this.}
-%%evaluations.  These amplitude-level techniques
-%%are particularly convenient for calculations involving many Feynman
-%%diagrams, where the usual trace techniques for the amplitude
-%%squared becomes unwieldy.  Our calculations use the helicity techniques
-%%developed by other authors \cite[]{hag86}; we briefly summarize below.
-%%
-%%\subsection{Formalism} \label{bozomath}
-%%
-%%%% The equation environment wil produce a numbered display equation.
-%%
-%%A tree-level amplitude in $e^+e^-$ collisions can be expressed in
-%%terms of fermion strings of the form
-%%\begin{equation}
-%%\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
-%%\hat a_nu(p_1,\sigma_1) ,
-%%\end{equation}
-%%where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
-%%and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
-%%and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
-%%operator $(\tau = \pm1)$.  The $a^\mu_i$ may be formed from particle
-%%four-momenta, gauge-boson polarization vectors or fermion strings with
-%%an uncontracted Lorentz index associated with final-state fermions.
-%%
-%%%% The \notetoeditor{TEXT} command allows the author to communicate
-%%%% information to the copy editor.  This information will appear as a
-%%%% footnote on the printed copy for the manuscript style file.  Nothing will
-%%%% appear on the printed copy if the preprint or
-%%%% preprint2 style files are used.
-%%
-%%%% The eqnarray environment produces multi-line display math. The end of
-%%%% each line is marked with a \\. Lines will be numbered unless the \\
-%%%% is preceded by a \nonumber command.
-%%%% Alignment points are marked by ampersands (&). There should be two
-%%%% ampersands (&) per line.
-%%
-%%In the chiral \notetoeditor{Figures 1 and 2 should appear side-by-side in
-%%print} representation the $\gamma$ matrices are expressed
-%%in terms of $2\times 2$ Pauli matrices $\sigma$ and the unit matrix 1 as
-%%\begin{eqnarray}
-%%\gamma^\mu  & = &
-%% \left(
-%%\begin{array}{cc}
-%%0 & \sigma^\mu_+ \\
-%%\sigma^\mu_- & 0
-%%\end{array}	  \right) ,
-%% \gamma^5= \left(
-%%\begin{array}{cc}
-%%-1 &   0\\
-%%0 &	1
-%%\end{array}	  \right)  , \nonumber \\
-%%\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , \nonumber
-%%\end{eqnarray}
-%%giving
-%%\begin{equation}
-%%\hat a= \left(
-%%\begin{array}{cc}
-%%0 & (\hat a)_+\\
-%%(\hat a)_- & 0
-%%\end{array}\right), (\hat a)_\pm=a_\mu\sigma^\mu_\pm ,
-%%\end{equation}
-%%The spinors are expressed in terms of two-component Weyl spinors as
-%%\begin{equation}
-%%u=\left(
-%%\begin{array}{c}
-%%(u)_-\\
-%%(u)_+
-%%\end{array}\right), v={\bf (}\vdag_+{\bf ,}	\vdag_-{\bf )} .
-%%\end{equation}
-%%
-%%%% Putting eqnarrays or equations inside the mathletters environment groups
-%%%% the enclosed equations by letter. For instance, the eqnarray below, instead
-%%%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
-%%%% LaTeX the paper and look at the output to see the results.
-%%
-%%The Weyl spinors are given in terms of helicity eigenstates
-%%$\chi_\lambda(p)$ with $\lambda=\pm1$ by
-%%\begin{mathletters}
-%%\begin{eqnarray}
-%%u(p,\lambda)_\pm & = & (E\pm\lambda|{\bf p}|)^{1/2}\chi_\lambda(p) , \\
-%%v(p,\lambda)_\pm & = & \pm\lambda(E\mp\lambda|{\bf p}|)^{1/2}\chi
-%%_{-\lambda}(p)
-%%\end{eqnarray}
-%%\end{mathletters}
-%%
-%%%% This section contains more display math examples, including unnumbered
-%%%% equations (displaymath environment). The last paragraph includes some
-%%%% examples of in-line math featuring a couple of the AASTeX symbol macros.
-%%
-%%\section{Floating material and so forth}
-%%
-%%%% The displaymath environment will produce the same sort of equation as
-%%%% the equation environment, except that the equation will not be numbered
-%%%% by LaTeX.
-%%
-%%Consider a task that computes profile parameters for a modified
-%%Lorentzian of the form
-%%\begin{equation}
-%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
-%%\end{equation}
-%%where
-%%\begin{displaymath}
-%%d_{1} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
-%%\end{array} \right) ^{2} +
-%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
-%%\end{displaymath}
-%%\begin{displaymath}
-%%d_{2} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
-%%\end{array} \right) ^{2} +
-%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
-%%\end{displaymath}
-%%\begin{displaymath}
-%%x_{1} = (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta
-%%\end{displaymath}
-%%\begin{displaymath}
-%%y_{1} = -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
-%%\end{displaymath}
-%%
-%%In these expressions $x_{0}$,$y_{0}$ is the star center, and $\Theta$ is the
-%%angle with the $x$ axis.  Results of this task are shown in table~\ref{tbl-1}.
-%%It is not clear how these sorts of analyses may affect determination of
-%% $M_{\sun}$, but the assumption is that the alternate results
-%%should be less than 90\degr\ out of phase with previous values.
-%%We have no observations of \ion{Ca}{2}.
-%%Roughly \slantfrac{4}{5} of the electronically submitted abstracts
-%%for AAS meetings are error-free.
-%%
-%%%% If you wish to include an acknowledgments section in your paper,
-%%%% separate it off from the body of the text using the \acknowledgments
-%%%% command.
-%%
-%%%% Included in this acknowledgments section are examples of the
-%%%% AASTeX hypertext markup commands. Use \url without the optional [HREF]
-%%%% argument when you want to print the url directly in the text. Otherwise,
-%%%% use either \url or \anchor, with the HREF as the first argument and the
-%%%% text to be printed in the second.
 %%
 \acknowledgments
-%chien peng, peter erwin
-%%
-%%We are grateful to V. Barger, T. Han, and R. J. N. Phillips for
-%%doing the math in section~\ref{bozomath}.
-%%More information on the AASTeX macros package is available \\ at
-%%\url{http://www.aas.org/publications/aastex}.
-%%For technical support, please write to
-%%\email{aastex-help@aas.org}.
-%%
-%%%% To help institutions obtain information on the effectiveness of their
-%%%% telescopes, the AAS Journals has created a group of keywords for telescope
-%%%% facilities. A common set of keywords will make these types of searches
-%%%% significantly easier and more accurate. In addition, they will also be
-%%%% useful in linking papers together which utilize the same telescopes
-%%%% within the framework of the National Virtual Observatory.
-%%%% See the AASTeX Web site at http://aastex.aas.org/
-%%%% for information on obtaining the facility keywords.
-%%
-%%%% After the acknowledgments section, use the following syntax and the
-%%%% \facility{} macro to list the keywords of facilities used in the research
-%%%% for the paper.  Each keyword will be checked against the master list during
-%%%% copy editing.  Individual instruments or configurations can be provided 
-%%%% in parentheses, after the keyword, but they will not be verified.
-%%
-%%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
-%%
-%%%% Appendix material should be preceded with a single \appendix command.
-%%%% There should be a \section command for each appendix. Mark appendix
-%%%% subsections with the same markup you use in the main body of the paper.
-%%
-%%%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
-%%%% The equation counter will reset when it encounters the \appendix
-%%%% command and will number appendix equations (A1), (A2), etc.
-%%
-%%\appendix
-%%
-%%\section{Appendix material}
-%%
-%%Consider once again a task that computes profile parameters for a modified
-%%Lorentzian of the form
-%%\begin{equation}
-%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
-%%\end{equation}
-%%where
-%%\begin{mathletters}
-%%\begin{displaymath}
-%%d_{1} = \frac{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
-%%\end{array} \right) ^{2} +
-%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
-%%\end{displaymath}
-%%\begin{equation}
-%%d_{2} = \case{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
-%%\end{array} \right) ^{2} +
-%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
-%%\end{equation}
-%%\begin{eqnarray}
-%%x_{1} & = & (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta \\
-%%y_{1} & = & -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
-%%\end{eqnarray}
-%%\end{mathletters}
-%%
-%%For completeness, here is one last equation.
-%%\begin{equation}
-%%e = mc^2
-%%\end{equation}
 
-%% The reference list follows the main body and any appendices.
-%% Use LaTeX's thebibliography environment to mark up your reference list.
-%% Note \begin{thebibliography} is followed by an empty set of
-%% curly braces.  If you forget this, LaTeX will generate the error
-%% "Perhaps a missing \item?".
-%%
-%% thebibliography produces citations in the text using \bibitem-\cite
-%% cross-referencing. Each reference is preceded by a
-%% \bibitem command that defines in curly braces the KEY that corresponds
-%% to the KEY in the \cite commands (see the first section above).
-%% Make sure that you provide a unique KEY for every \bibitem or else the
-%% paper will not LaTeX. The square brackets should contain
-%% the citation text that LaTeX will insert in
-%% place of the \cite commands.
-
-%% We have used macros to produce journal name abbreviations.
-%% AASTeX provides a number of these for the more frequently-cited journals.
-%% See the Author Guide for a list of them.
-
-%% Note that the style of the \bibitem labels (in []) is slightly
-%% different from previous examples.  The natbib system solves a host
-%% of citation expression problems, but it is necessary to clearly
-%% delimit the year from the author name used in the citation.
-%% See the natbib documentation for more details and options.
-
-\bibliography{/Users/gsavorgnan/Dropbox/giulia_e_basta/Literature/SMBHbibliography}
-
-%%\begin{thebibliography}{}
-%%\bibitem[Auri\`ere(1982)]{aur82} Auri\`ere, M.  1982, \aap,
-%%    109, 301
-%%\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
-%%    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
-%%    McClintock, J. E.  1978, \apj, 224, 39
-%%\bibitem[Djorgovski \& King(1984)]{djo84} Djorgovski, S.,
-%%    \& King, I. R.  1984, \apjl, 277, L49
-%%\bibitem[Hagiwara \& Zeppenfeld(1986)]{hag86} Hagiwara, K., \&
-%%    Zeppenfeld, D.  1986, Nucl.Phys., 274, 1
-%%\bibitem[Harris \& van den Bergh(1984)]{har84} Harris, W. E.,
-%%    \& van den Bergh, S.  1984, \aj, 89, 1816
-%%\bibitem[H\`enon(1961)]{hen61} H\'enon, M.  1961, Ann.d'Ap., 24, 369
-%%\bibitem[Heiles \& Troland(2003)]{heiles03} Heiles, C. \& Troland, T. H., 2003, \apjs, preprint doi:10.1086/381753
-%%\bibitem[Kim, Ostricker, \& Stone(2003)]{kim03} Kim, W.-T.,  Ostriker, E., \& Stone, J. M., 2003, \apj, 599, 1157
-%%\bibitem[King(1966)]{kin66}  King, I. R.  1966, \aj, 71, 276
-%%\bibitem[King(1975)]{kin75}  King, I. R.  1975, Dynamics of
-%%    Stellar Systems, A. Hayli, Dordrecht: Reidel, 1975, 99
-%%\bibitem[King et al.(1968)]{kin68}  King, I. R., Hedemann, E.,
-%%    Hodge, S. M., \& White, R. E.  1968, \aj, 73, 456
-%%\bibitem[Kron et al.(1984)]{kro84} Kron, G. E., Hewitt, A. V.,
-%%    \& Wasserman, L. H.  1984, \pasp, 96, 198
-%%\bibitem[Lynden-Bell \& Wood(1968)]{lyn68} Lynden-Bell, D.,
-%%    \& Wood, R.  1968, \mnras, 138, 495
-%%\bibitem[Newell \& O'Neil(1978)]{new78} Newell, E. B.,
-%%    \& O'Neil, E. J.  1978, \apjs, 37, 27
-%%\bibitem[Ortolani et al.(1985)]{ort85} Ortolani, S., Rosino, L.,
-%%    \& Sandage, A.  1985, \aj, 90, 473
-%%\bibitem[Peterson(1976)]{pet76} Peterson, C. J.  1976, \aj, 81, 617
-%%\bibitem[Rudnick et al.(2003)]{rudnick03} Rudnick, G. et al., 2003, \apj, 599, 847
-%%\bibitem[Spitzer(1985)]{spi85} Spitzer, L.  1985, Dynamics of
-%%    Star Clusters, J. Goodman \& P. Hut, Dordrecht: Reidel, 109
-%%\bibitem[Treu et al.(2003)]{treu03} Treu, T. et al., 2003, \apj, 591, 53
-%%\end{thebibliography}
+\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
 
@@
 
-%% Use the figure environment and \plotone or \plottwo to include
-%% figures and captions in your electronic submission.
-%% To embed the sample graphics in
-%% the file, uncomment the \plotone, \plottwo, and
-%% \includegraphics commands
-%%
-%% If you need a layout that cannot be achieved with \plotone or
-%% \plottwo, you can invoke the graphicx package directly with the
-%% \includegraphics command or use \plotfiddle. For more information,
-%% please see the tutorial on "Using Electronic Art with AASTeX" in the
-%% documentation section at the AASTeX Web site, http://aastex.aas.org/
-%%
-%% The examples below also include sample markup for submission of
-%% supplemental electronic materials. As always, be sure to check
-%% the instructions to authors for the journal you are submitting to
-%% for specific submissions guidelines as they vary from
-%% journal to journal.
-
-%% This example uses \plotone to include an EPS file scaled to
-%% 80% of its natural size with \epsscale. Its caption
-%% has been written to indicate that additional figure parts will be
-%% available in the electronic journal.
-
-%%\begin{figure}
-%%\epsscale{.80}
-%%\plotone{f1.eps}
-%%\caption{Derived spectra for 3C138 \citep[see][]{heiles03}. Plots for all sources are available
-%%in the electronic edition of {\it The Astrophysical Journal}.\label{fig1}}
-%%\end{figure}
-%%
-%%\clearpage
-%%
-%%%% Here we use \plottwo to present two versions of the same figure,
-%%%% one in black and white for print the other in RGB color
-%%%% for online presentation. Note that the caption indicates
-%%%% that a color version of the figure will be available online.
-%%%%
-%%
-%%\begin{figure}
-%%\plottwo{f2.eps}{f2_color.eps}
-%%\caption{A panel taken from Figure 2 of \citet{rudnick03}. 
-%%See the electronic edition of the Journal for a color version 
-%%of this figure.\label{fig2}}
-%%\end{figure}
-%%
-%%%% This figure uses \includegraphics to scale and rotate the still frame
-%%%% for an mpeg animation.
-%%
-%%\begin{figure}
-%%\includegraphics[angle=90,scale=.50]{f3.eps}
-%%\caption{Animation still frame taken from \citet{kim03}.
-%%This figure is also available as an mpeg
-%%animation in the electronic edition of the
-%%{\it Astrophysical Journal}.}
-%%\end{figure}
-%%
-%%%% If you are not including electonic art with your submission, you may
-%%%% mark up your captions using the \figcaption command. See the
-%%%% User Guide for details.
-%%%%
-%%%% No more than seven \figcaption commands are allowed per page,
-%%%% so if you have more than seven captions, insert a \clearpage
-%%%% after every seventh one.
-%%
-%%%% Tables should be submitted one per page, so put a \clearpage before
-%%%% each one.
-%%
-%%%% Two options are available to the author for producing tables:  the
-%%%% deluxetable environment provided by the AASTeX package or the LaTeX
-%%%% table environment.  Use of deluxetable is preferred.
-%%%%
-%%
-%%%% Three table samples follow, two marked up in the deluxetable environment,
-%%%% one marked up as a LaTeX table.
-%%
-%%%% In this first example, note that the \tabletypesize{}
-%%%% command has been used to reduce the font size of the table.
-%%%% We also use the \rotate command to rotate the table to
-%%%% landscape orientation since it is very wide even at the
-%%%% reduced font size.
-%%%%
-%%%% Note also that the \label command needs to be placed
-%%%% inside the \tablecaption.
-%%
-%%%% This table also includes a table comment indicating that the full
-%%%% version will be available in machine-readable format in the electronic
-%%%% edition.
-%%
-%%\clearpage
-%%
-%%\begin{deluxetable}{ccrrrrrrrrcrl}
-%%\tabletypesize{\scriptsize}
-%%\rotate
-%%\tablecaption{Sample table taken from \citet{treu03}\label{tbl-1}}
-%%\tablewidth{0pt}
-%%\tablehead{
-%%\colhead{POS} & \colhead{chip} & \colhead{ID} & \colhead{X} & \colhead{Y} &
-%%\colhead{RA} & \colhead{DEC} & \colhead{IAU$\pm$ $\delta$ IAU} &
-%%\colhead{IAP1$\pm$ $\delta$ IAP1} & \colhead{IAP2 $\pm$ $\delta$ IAP2} &
-%%\colhead{star} & \colhead{E} & \colhead{Comment}
-%%}
-%%\startdata
-%%0 & 2 & 1 & 1370.99 & 57.35	 &   6.651120 &  17.131149 & 21.344$\pm$0.006  & 2
-%%4.385$\pm$0.016 & 23.528$\pm$0.013 & 0.0 & 9 & -    \\
-%%0 & 2 & 2 & 1476.62 & 8.03	 &   6.651480 &  17.129572 & 21.641$\pm$0.005  & 2
-%%3.141$\pm$0.007 & 22.007$\pm$0.004 & 0.0 & 9 & -    \\
-%%0 & 2 & 3 & 1079.62 & 28.92	 &   6.652430 &  17.135000 & 23.953$\pm$0.030  & 2
-%%4.890$\pm$0.023 & 24.240$\pm$0.023 & 0.0 & - & -    \\
-%%0 & 2 & 4 & 114.58  & 21.22	 &   6.655560 &  17.148020 & 23.801$\pm$0.025  & 2
-%%5.039$\pm$0.026 & 24.112$\pm$0.021 & 0.0 & - & -    \\
-%%0 & 2 & 5 & 46.78   & 19.46	 &   6.655800 &  17.148932 & 23.012$\pm$0.012  & 2
-%%3.924$\pm$0.012 & 23.282$\pm$0.011 & 0.0 & - & -    \\
-%%0 & 2 & 6 & 1441.84 & 16.16	 &   6.651480 &  17.130072 & 24.393$\pm$0.045  & 2
-%%6.099$\pm$0.062 & 25.119$\pm$0.049 & 0.0 & - & -    \\
-%%0 & 2 & 7 & 205.43  & 3.96	 &   6.655520 &  17.146742 & 24.424$\pm$0.032  & 2
-%%5.028$\pm$0.025 & 24.597$\pm$0.027 & 0.0 & - & -    \\
-%%0 & 2 & 8 & 1321.63 & 9.76	 &   6.651950 &  17.131672 & 22.189$\pm$0.011  & 2
-%%4.743$\pm$0.021 & 23.298$\pm$0.011 & 0.0 & 4 & edge \\
-%%\enddata
-%%%% Text for table notes should follow after the \enddata but before
-%%%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
-%%%% in the table for each \tablenotetext.
-%%\tablecomments{Table \ref{tbl-1} is published in its entirety in the 
-%%electronic edition of the {\it Astrophysical Journal}.  A portion is 
-%%shown here for guidance regarding its form and content.}
-%%\tablenotetext{a}{Sample footnote for table~\ref{tbl-1} that was generated
-%%with the deluxetable environment}
-%%\tablenotetext{b}{Another sample footnote for table~\ref{tbl-1}}
-%%\end{deluxetable}
-%%
-%%%% If you use the table environment, please indicate horizontal rules using
-%%%% \tableline, not \hline.
-%%%% Do not put multiple tabular environments within a single table.
-%%%% The optional \label should appear inside the \caption command.
-%%
-%%\clearpage
-%%
-%%\begin{table}
-%%\begin{center}
-%%\caption{More terribly relevant tabular information.\label{tbl-2}}
-%%\begin{tabular}{crrrrrrrrrrr}
-%%\tableline\tableline
-%%Star & Height & $d_{x}$ & $d_{y}$ & $n$ & $\chi^2$ & $R_{maj}$ & $R_{min}$ &
-%%\multicolumn{1}{c}{$P$\tablenotemark{a}} & $P R_{maj}$ & $P R_{min}$ &
-%%\multicolumn{1}{c}{$\Theta$\tablenotemark{b}} \\
-%%\tableline
-%%1 &33472.5 &-0.1 &0.4  &53 &27.4 &2.065  &1.940 &3.900 &68.3 &116.2 &-27.639\\
-%%2 &27802.4 &-0.3 &-0.2 &60 &3.7  &1.628  &1.510 &2.156 &6.8  &7.5 &-26.764\\
-%%3 &29210.6 &0.9  &0.3  &60 &3.4  &1.622  &1.551 &2.159 &6.7  &7.3 &-40.272\\
-%%4 &32733.8 &-1.2\tablenotemark{c} &-0.5 &41 &54.8 &2.282  &2.156 &4.313 &117.4 &78.2 &-35.847\\
-%%5 & 9607.4 &-0.4 &-0.4 &60 &1.4  &1.669\tablenotemark{c}  &1.574 &2.343 &8.0  &8.9 &-33.417\\
-%%6 &31638.6 &1.6  &0.1  &39 &315.2 & 3.433 &3.075 &7.488 &92.1 &25.3 &-12.052\\
-%%\tableline
-%%\end{tabular}
-%%%% Any table notes must follow the \end{tabular} command.
-%%\tablenotetext{a}{Sample footnote for table~\ref{tbl-2} that was
-%%generated with the \LaTeX\ table environment}
-%%\tablenotetext{b}{Yet another sample footnote for table~\ref{tbl-2}}
-%%\tablenotetext{c}{Another sample footnote for table~\ref{tbl-2}}
-%%\tablecomments{We can also attach a long-ish paragraph of explanatory
-%%material to a table.}
-%%\end{center}
-%%\end{table}
-%%
-%%%% If the table is more than one page long, the width of the table can vary
-%%%% from page to page when the default \tablewidth is used, as below.  The
-%%%% individual table widths for each page will be written to the log file; a
-%%%% maximum tablewidth for the table can be computed from these values.
-%%%% The \tablewidth argument can then be reset and the file reprocessed, so
-%%%% that the table is of uniform width throughout. Try getting the widths
-%%%% from the log file and changing the \tablewidth parameter to see how
-%%%% adjusting this value affects table formatting.
-%%
-%%%% The \dataset{} macro has also been applied to a few of the objects to
-%%%% show how many observations can be tagged in a table.
-%%
-%%\clearpage
-%%
-%%\begin{deluxetable}{lrrrrcrrrrr}
-%%\tablewidth{0pt}
-%%\tablecaption{Literature Data for Program Stars}
-%%\tablehead{
-%%\colhead{Star}	   & \colhead{V}      &
-%%\colhead{b$-$y}	   & \colhead{m$_1$}  &
-%%\colhead{c$_1$}	   & \colhead{ref}    &
-%%\colhead{T$_{\rm eff}$}  & \colhead{log g}  &
-%%\colhead{v$_{\rm turb}$} & \colhead{[Fe/H]} &
-%%\colhead{ref}}
-%%\startdata
-%%HD 97 & 9.7& 0.51& 0.15& 0.35& 2 & \nodata & \nodata & \nodata & $-1.50$ & 2 \\
-%%& & & & & & 5015 & \nodata & \nodata & $-1.50$ & 10 \\
-%%\dataset[ADS/Sa.HST#O6H04VAXQ]{HD 2665} & 7.7& 0.54& 0.09& 0.34& 2 & \nodata & \nodata & \nodata & $-2.30$ & 2 \\
-%%& & & & & & 5000 & 2.50 & 2.4 & $-1.99$ & 5 \\
-%%& & & & & & 5120 & 3.00 & 2.0 & $-1.69$ & 7 \\
-%%& & & & & & 4980 & \nodata & \nodata & $-2.05$ & 10 \\
-%%HD 4306 & 9.0& 0.52& 0.05& 0.35& 20, 2& \nodata & \nodata & \nodata & $-2.70$ & 2 \\
-%%& & & & & & 5000 & 1.75 & 2.0 & $-2.70$ & 13 \\
-%%& & & & & & 5000 & 1.50 & 1.8 & $-2.65$ & 14 \\
-%%& & & & & & 4950 & 2.10 & 2.0 & $-2.92$ & 8 \\
-%%& & & & & & 5000 & 2.25 & 2.0 & $-2.83$ & 18 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-2.80$ & 21 \\
-%%& & & & & & 4930 & \nodata & \nodata & $-2.45$ & 10 \\
-%%HD 5426 & 9.6& 0.50& 0.08& 0.34& 2 & \nodata & \nodata & \nodata & $-2.30$ & 2 \\
-%%\dataset[ADS/Sa.HST#O5F654010]{HD 6755} & 7.7& 0.49& 0.12& 0.28& 20, 2& \nodata & \nodata & \nodata & $-1.70$ & 2 \\
-%%& & & & & & 5200 & 2.50 & 2.4 & $-1.56$ & 5 \\
-%%& & & & & & 5260 & 3.00 & 2.7 & $-1.67$ & 7 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-1.58$ & 21 \\
-%%& & & & & & 5200 & \nodata & \nodata & $-1.80$ & 10 \\
-%%& & & & & & 4600 & \nodata & \nodata & $-2.75$ & 10 \\
-%%\dataset[ADS/Sa.HST#O56D06010]{HD 94028} & 8.2& 0.34& 0.08& 0.25& 20 & 5795 & 4.00 & \nodata & $-1.70$ & 22 \\
-%%& & & & & & 5860 & \nodata & \nodata & $-1.70$ & 4 \\
-%%& & & & & & 5910 & 3.80 & \nodata & $-1.76$ & 15 \\
-%%& & & & & & 5800 & \nodata & \nodata & $-1.67$ & 17 \\
-%%& & & & & & 5902 & \nodata & \nodata & $-1.50$ & 11 \\
-%%& & & & & & 5900 & \nodata & \nodata & $-1.57$ & 3 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-1.32$ & 21 \\
-%%HD 97916 & 9.2& 0.29& 0.10& 0.41& 20 & 6125 & 4.00 & \nodata & $-1.10$ & 22 \\
-%%& & & & & & 6160 & \nodata & \nodata & $-1.39$ & 3 \\
-%%& & & & & & 6240 & 3.70 & \nodata & $-1.28$ & 15 \\
-%%& & & & & & 5950 & \nodata & \nodata & $-1.50$ & 17 \\
-%%& & & & & & 6204 & \nodata & \nodata & $-1.36$ & 11 \\
-%%\cutinhead{This is a cut-in head}
-%%+26\arcdeg2606& 9.7&0.34&0.05&0.28&20,11& 5980 & \nodata & \nodata &$<-2.20$ & 19 \\
-%%& & & & & & 5950 & \nodata & \nodata & $-2.89$ & 24 \\
-%%+26\arcdeg3578& 9.4&0.31&0.05&0.37&20,11& 5830 & \nodata & \nodata & $-2.60$ & 4 \\
-%%& & & & & & 5800 & \nodata & \nodata & $-2.62$ & 17 \\
-%%& & & & & & 6177 & \nodata & \nodata & $-2.51$ & 11 \\
-%%& & & & & & 6000 & 3.25 & \nodata & $-2.20$ & 22 \\
-%%& & & & & & 6140 & 3.50 & \nodata & $-2.57$ & 15 \\
-%%+30\arcdeg2611& 9.2&0.82&0.33&0.55& 2 & \nodata & \nodata & \nodata & $-1.70$ & 2 \\
-%%& & & & & & 4400 & 1.80 & \nodata & $-1.70$ & 12 \\
-%%& & & & & & 4400 & 0.90 & 1.7 & $-1.20$ & 14 \\
-%%& & & & & & 4260 & \nodata & \nodata & $-1.55$ & 10 \\
-%%+37\arcdeg1458& 8.9&0.44&0.07&0.22&20,11& 5296 & \nodata & \nodata & $-2.39$ & 11 \\
-%%& & & & & & 5420 & \nodata & \nodata & $-2.43$ & 3 \\
-%%+58\arcdeg1218&10.0&0.51&0.03&0.36& 2 & \nodata & \nodata & \nodata & $-2.80$ & 2 \\
-%%& & & & & & 5000 & 1.10 & 2.2 & $-2.71$ & 14 \\
-%%& & & & & & 5000 & 2.20 & 1.8 & $-2.46$ & 5 \\
-%%& & & & & & 4980 & \nodata & \nodata & $-2.55$ & 10 \\
-%%+72\arcdeg0094&10.2&0.31&0.09&0.26&12 & 6160 & \nodata & \nodata & $-1.80$ & 19 \\
-%%\sidehead{I'm a side head:}
-%%G5--36 & 10.8& 0.40& 0.07& 0.28& 20 & \nodata & \nodata & \nodata & $-1.19$ & 21 \\
-%%G18--54 & 10.7& 0.37& 0.08& 0.28& 20 & \nodata & \nodata & \nodata & $-1.34$ & 21 \\
-%%G20--08 & 9.9& 0.36& 0.05& 0.25& 20,11& 5849 & \nodata & \nodata & $-2.59$ & 11 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-2.03$ & 21 \\
-%%G20--15 & 10.6& 0.45& 0.03& 0.27& 20,11& 5657 & \nodata & \nodata & $-2.00$ & 11 \\
-%%& & & & & & 6020 & \nodata & \nodata & $-1.56$ & 3 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-1.58$ & 21 \\
-%%G21--22 & 10.7& 0.38& 0.07& 0.27& 20,11& \nodata & \nodata & \nodata & $-1.23$ & 21 \\
-%%G24--03 & 10.5& 0.36& 0.06& 0.27& 20,11& 5866 & \nodata & \nodata & $-1.78$ & 11 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-1.70$ & 21 \\
-%%G30--52 & 8.6& 0.50& 0.25& 0.27& 11 & 4757 & \nodata & \nodata & $-2.12$ & 11 \\
-%%& & & & & & 4880 & \nodata & \nodata & $-2.14$ & 3 \\
-%%G33--09 & 10.6& 0.41& 0.10& 0.28& 20 & 5575 & \nodata & \nodata & $-1.48$ & 11 \\
-%%G66--22 & 10.5& 0.46& 0.16& 0.28& 11 & 5060 & \nodata & \nodata & $-1.77$ & 3 \\
-%%& & & & & & \nodata & \nodata & \nodata & $-1.04$ & 21 \\
-%%G90--03 & 10.4& 0.37& 0.04& 0.29& 20 & \nodata & \nodata & \nodata & $-2.01$ & 21 \\
-%%LP 608--62\tablenotemark{a} & 10.5& 0.30& 0.07& 0.35& 11 & 6250 & \nodata &
-%%\nodata & $-2.70$ & 4 \\
-%%\enddata
-%%\tablenotetext{a}{Star LP 608--62 is also known as BD+1\arcdeg 2341p.  We will
-%%make this footnote extra long so that it extends over two lines.}
-%%%% You can append references to a table using the \tablerefs command.
-%%\tablerefs{
-%%(1) Barbuy, Spite, \& Spite 1985; (2) Bond 1980; (3) Carbon et al. 1987;
-%%(4) Hobbs \& Duncan 1987; (5) Gilroy et al. 1988: (6) Gratton \& Ortolani 1986;
-%%(7) Gratton \& Sneden 1987; (8) Gratton \& Sneden (1988); (9) Gratton \& Sneden 1991;
-%%(10) Kraft et al. 1982; (11) LCL, or Laird, 1990; (12) Leep \& Wallerstein 1981;
-%%(13) Luck \& Bond 1981; (14) Luck \& Bond 1985; (15) Magain 1987;
-%%(16) Magain 1989; (17) Peterson 1981; (18) Peterson, Kurucz, \& Carney 1990;
-%%(19) RMB; (20) Schuster \& Nissen 1988; (21) Schuster \& Nissen 1989b;
-%%(22) Spite et al. 1984; (23) Spite \& Spite 1986; (24) Hobbs \& Thorburn 1991;
-%%(25) Hobbs et al. 1991; (26) Olsen 1983.}
-%%\end{deluxetable}
-%%
-%%%% Tables may also be prepared as separate files. See the accompanying
-%%%% sample file table.tex for an example of an external table file.
-%%%% To include an external file in your main document, use the \input
-%%%% command. Uncomment the line below to include table.tex in this
-%%%% sample file. (Note that you will need to comment out the \documentclass,
-%%%% \begin{document}, and \end{document} commands from table.tex if you want
-%%%% to include it in this document.)
-%%
-%%%% \input{table}
-%%
-%%%% The following command ends your manuscript. LaTeX will ignore any text
-%%%% that appears after it.
-
 \end{document}
-
-%%
-%% End of file `sample.tex'.

### 2015-08-21 python_codes/decomposition/ProFitErole1.0.1/makeAllFigures.py

@@ -56,7 +56,7 @@ if (Settings.observation == 'n1271'):
 	print 'n1271'
         gaussianPsf = PsfFunction()
         gaussianPsf.name = 'gaussian'
-        gaussianPsf.gaussianFWHM = 1.8 * Settings.pxlToArcsec 
+        gaussianPsf.gaussianFWHM = 2.3 * Settings.pxlToArcsec 
         
         psfList = [gaussianPsf]
 	

### 2015-08-21 python_codes/paper_figures/lentiptical/n3115/mrk1216.py

@@ -56,13 +56,12 @@ from textwrap import wrap
 
 #################################################### 
 
-moffatPsf = PsfFunction()
-moffatPsf.name = 'moffat'
-moffatPsf.moffatAlpha = (1.61467/(2*np.sqrt(2**(1/4.39)-1)) ) * Settings.pxlToArcsec  # alpha = fwhm / (2 * sqrt(2**(1/beta) - 1) )
-moffatPsf.moffatBeta = 4.39  
-        
-psfList = [moffatPsf]
-	
+gaussianPsf = PsfFunction()
+gaussianPsf.name = 'gaussian'
+gaussianPsf.gaussianFWHM = 2.3 * Settings.pxlToArcsec 
+
+psfList = [gaussianPsf]
+
 gaussianSmoothing = PsfFunction()
 gaussianSmoothing.name = 'gaussian'
 gaussianSmoothing.gaussianFWHM = 5 * 2.3548 * Settings.pxlToArcsec 
@@ -183,8 +182,8 @@ def readFitAndPlot(excludedRangeList, galaxy, axisFit, psfFunction, sampling, be
         rrr = rrr * np.sqrt(1. - ellip) 
     
     
-    #bestFitParamsFileName = galaxy + '_' + axisFit + '_' + gaussianPsf.name + '_comb_par_SM.dat'
-    bestFitParamsFileName = galaxy + '_' + axisFit + '_' + moffatPsf.name + '_comb_par_SM.dat'
+    bestFitParamsFileName = galaxy + '_' + axisFit + '_' + gaussianPsf.name + '_comb_par_SM.dat'
+    #bestFitParamsFileName = galaxy + '_' + axisFit + '_' + moffatPsf.name + '_comb_par_SM.dat'
     
     componentslist, finalparams = readBestFitModel(bestFitParamsFileName)
     
@@ -367,10 +366,7 @@ def createFigure(bestfitFig, psfFunction, equivalentAxisFit, rrr, mu, good_rrr, 
 	fitPanel = doFitPanel(initFitPanel, rrr, mu, good_rrr, good_mu, bad_rrr, bad_mu, maxsma_arcsec, minmu, maxmu, componentslist, finalparams, Settings, psfFunction, psfwing_02pxscale_datatab, psfwing_logscale_datatab, goodIndexes, skyRMS, deltarms, sampling, goodIndexes_integer, badIndexes_integer, gaussianSmoothing)		
[…]

### 2015-08-26 papers/ellicular/ellicular.tex
nature said no

\documentclass[useAMS,usenatbib,article]{mn2e}

\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\bibliographystyle{mn2e}
%\usepackage{tabularx}
%\usepackage{bm}
%\usepackage{color}
%\usepackage{hyperref}

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}
\newcommand\aj{{AJ}}%
\newcommand\actaa{{Acta Astron.}}%
\newcommand\araa{{ARA\&A}}%
\newcommand\apj{{ApJ}}%
\newcommand\apjl{{ApJ}}%
\newcommand\apjs{{ApJS}}%
\newcommand\ao{{Appl.~Opt.}}%
\newcommand\apss{{Ap\&SS}}%
\newcommand\aap{{A\&A}}%
\newcommand\aapr{{A\&A~Rev.}}%
\newcommand\aaps{{A\&AS}}%
\newcommand\azh{{AZh}}%
\newcommand\baas{{BAAS}}%
\newcommand\caa{{Chinese Astron. Astrophys.}}%
\newcommand\cjaa{{Chinese J. Astron. Astrophys.}}%
\newcommand\icarus{{Icarus}}%
\newcommand\jcap{{J. Cosmology Astropart. Phys.}}%
\newcommand\jrasc{{JRASC}}%
\newcommand\memras{{MmRAS}}%
\newcommand\mnras{{MNRAS}}%
\newcommand\na{{New A}}%
\newcommand\nar{{New A Rev.}}%
\newcommand\pra{{Phys.~Rev.~A}}%
\newcommand\prb{{Phys.~Rev.~B}}%
\newcommand\prc{{Phys.~Rev.~C}}%
\newcommand\prd{{Phys.~Rev.~D}}%
\newcommand\pre{{Phys.~Rev.~E}}%
\newcommand\prl{{Phys.~Rev.~Lett.}}%
\newcommand\pasa{{PASA}}%
\newcommand\pasp{{PASP}}%
\newcommand\pasj{{PASJ}}%
\newcommand\qjras{{QJRAS}}%
\newcommand\rmxaa{{Rev. Mexicana Astron. Astrofis.}}%
\newcommand\skytel{{S\&T}}%
\newcommand\solphys{{Sol.~Phys.}}%
\newcommand\sovast{{Soviet~Ast.}}%
\newcommand\ssr{{Space~Sci.~Rev.}}%
\newcommand\zap{{ZAp}}%
\newcommand\nat{{Nature}}%
\newcommand\iaucirc{{IAU~Circ.}}%
\newcommand\aplett{{Astrophys.~Lett.}}%
\newcommand\apspr{{Astrophys.~Space~Phys.~Res.}}%
\newcommand\bain{{Bull.~Astron.~Inst.~Netherlands}}%
\newcommand\fcp{{Fund.~Cosmic~Phys.}}%
\newcommand\gca{{Geochim.~Cosmochim.~Acta}}%
\newcommand\grl{{Geophys.~Res.~Lett.}}%
\newcommand\jcp{{J.~Chem.~Phys.}}%
\newcommand\jgr{{J.~Geophys.~Res.}}%
\newcommand\jqsrt{{J.~Quant.~Spec.~Radiat.~Transf.}}%
\newcommand\memsai{{Mem.~Soc.~Astron.~Italiana}}%
\newcommand\nphysa{{Nucl.~Phys.~A}}%
\newcommand\physrep{{Phys.~Rep.}}%
\newcommand\physscr{{Phys.~Scr}}%
\newcommand\planss{{Planet.~Space~Sci.}}%
\newcommand\procspie{{Proc.~SPIE}}%

%\newcommand{\vdag}{(v)^\dagger}
%\newcommand{\myemail}{gsavorgn@astro.swin.edu.au}
%\newcommand{\fitfigurewidth}{0.8\textwidth}

\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their supermassive black holes}

\author[G.~A.~D. Savorgnan \& A.~W. Graham]
{\parbox{\textwidth}{
Giulia~A.~D. Savorgnan$^{1}$\thanks{E-mail: \texttt{gsavorgn@astro.swin.edu.au}},
Alister W. Graham$^{1}$}\vspace{0.4cm}\\
\parbox{\textwidth}{
$^{1}$Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.\\}}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}

\begin{document}

\maketitle

\label{firstpage}

\begin{abstract}
vjsfkajhda
\end{abstract}

\begin{keywords}
black hole physics -- galaxies: bulges -- galaxies: elliptical and lenticular, cD -- galaxies: evolution -- galaxies: structure
\end{keywords}

\section{Introduction}
\label{sec:int}
There are currently two well-known types of stellar discs in galaxies. 
The first are the large-scale discs (with sizes of a few kiloparsec) that dominate the light at large radii in spiral and lenticular galaxies; 
the second are the small (tens to a couple of hundred parsec) nuclear discs observed in both early- and late-type galaxies 
(e.g.~\citealt{scorzavandenbosch1998,rest2001,balcells2007,ledo2010}). 
The origin of the nuclear discs has been speculated to arise from the infall of small satellite galaxies or gas clouds.  
The origin, or at least the on-going feeding and growth, of the large-scale discs has been attributed to cold gas flows, 
gas rich mergers and halo accretion events (e.g.~\citealt{khochfarsilk2006,dekel2009nat,dekel2009apj,ceverino2010,ceverino2012,conselice2012}). 
A thorough review can be found in Combes (arXiv:1309.1603 and 1405.6405).
On the other hand, intermediate-sized discs have not received the same level of attention as their nuclear and large-scale homologues, 
and, in some cases, they have even been labelled as something ''unphysical''. 
Here we report on the photometric and kinematical signatures of these intermediate-sized stellar discs 
and the impact this has on the important (black hole mass)-to-(spheroid stellar mass) ratio, $M_{\rm BH}/M_{*,sph}$, 
which is used to constrain galaxy evolution models.

%A puzzling question, which has been unspoken for decades, is why are there not intermediate-sized discs: 
%why are there not accretion events which create discs larger than the typical nuclear discs but which are not large enough to dominate at large radii?

\section{Rationale}
\label{sec:rat}
The majority of stellar discs have some level of inclination with respect to our line-of-sight, 
and this makes them appear elliptical (rather than round) when seen in projection on the sky. 
This can help one distinguish them from the more spherically-shaped spheroids. 
Identifying the extent of these discs with respect to their spheroid can however be subtle. 
Two-dimensional kinematic maps represent an important diagnostic tool for this purpose. 
Most early-type galaxies are classified as ``central fast rotators'' \citep{atlas3dIII-MNRAS}, 
that is, they are rapidly rotating within their half-light radius.  
However, more extended kinematic maps \citep{arnold2014} reveal that 
some of the central fast rotators continue to be fast rotating at large radii, 
whereas other central fast rotators become slow rotators in their outer regions.
On the one hand, a specific angular momentum profile that is rapidly increasing beyond $1-2$ half-light radii 
is a signature of a large-scale disc. 
On the other hand, a specific angular momentum profile that increases up to $1-2$ half-light radii and declines beyond that point 
indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 
Unfortunately, such extended kinematic maps are not yet available for large numbers of galaxies in the local Universe. 
Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of stellar discs in early-type galaxies.

The toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 
($\epsilon = 1 - b/a$, where $b/a$ is the ratio of minor-to-major axis length) of 
(i) a lenticular galaxy, comprised of a large-scale disc and a relatively smaller encased bulge, 
(ii) an elliptical galaxy with a nuclear stellar disc, 
and (iii) a galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid. 
%We refer to the last case as an ellicular galaxy. 
In general, stellar discs are intrinsically flat and circular; 
their ellipticity, dictated by their inclination to our line of sight, is fixed. 
Spheroids are often rounder than the observed projection on the sky of their associated discs, 
thus their average ellipticity is often lower than that of their disc. 
An ellipticity profile that increases with radius can be ascribed to an inclined disc that becomes progressively more important at large radii, 
whereas a radial decrease of ellipticity signifies the opposite case.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{images/discmodel.eps}
\caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
the ellipticity profile, $\epsilon$, and the specific angular momentum profile, $\lambda$,
for the three prototype early-type galaxy sub-classes. 
In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
The left panel shows a lenticular galaxy, composed of a bulge encased in a large-scale disc. 
The right panel displays an elliptical galaxy with (an optional) nuclear stellar disc. 
The middle panel presents an early-type galaxy with an intermediate-sized disc embedded in the spheroid. }
\label{fig:model}
\end{center}
\end{figure}

The awareness that many ``elliptical'' galaxies actually contain embedded stellar discs 
dates back at least three decades 
\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995,
donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998} and, 
%more recently, intermediate-scale discs were all but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013}. 
However, the class of early-type galaxies with intermediate-scale discs has been missed by many galaxy modelers, 
who have labeled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
as is observed with spiral galaxies. 
This unspoken bias has led to the rejection of many spheroid/disc decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
Unsurprisingly, studies affected by this bias have not obtained spheroid/disc decompositions with a spheroid-to-total ratio larger than $0.6 - 0.8$ 
(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}).

The existence of intermediate-scale stellar discs reveals a continuum of disc sizes, 
rather than a dichotomy of nuclear versus large-scale discs. 
The presence of intermediate-scale discs also blurs the distinction between elliptical and lenticular galaxies.
%and creates the need for a new subclass to help bridge the divide. 
The existence of such discs is not only important for our understanding of disc growth in general, 
but accounting for such structure will impact our understanding of galaxy structure, 
with important consequences for galaxy scaling relations. 
%It has recently been argued that the classification scheme for elliptical galaxies should not be their apparent axis ratio as seen on the plane of the sky, 
%but instead their spheroid-to-total ratio, with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies \citep{graham2014review}.

\section{Galaxies}
\label{sec:xxx}

\section{Implications}
\label{sec:impl}

\subsection{mm diagram}

\subsection{compact massive sph}

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{images/}
%\caption{}
%\label{fig:}
%\end{center}
%\end{figure}

\section{Acknowledgments}
%GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. \\
% referee thank you!!
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
%This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
%on-board the Spitzer Space Telescope, 
%which is operated by the Jet Propulsion Laboratory, 
%California Institute of Technology under a contract with NASA.
%This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
%which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
%under contract with the National Aeronautics and Space Administration.

\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}

\label{lastpage}

\clearpage

\end{document}

### 2015-08-26 papers/mbhn/mbhn.tex
nature said no

@@
 
-\documentclass[preprint2]{aastex}
+\documentclass[preprint2]{emulateapj}
 
 \usepackage{natbib}
-%\bibliographystyle{apj}
+\bibliographystyle{apj}
 \usepackage{longtable}
@@
 \usepackage{bm}
-%%\graphicspath{{/Users/gsavorgnan/galaxy_vivisection/results/plots/}}
+\usepackage{color}
+\usepackage{hyperref}
 
@@
 
+\section{Data}
+
+\input{table_sample.tex}
+
 \section{Results}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
+\caption{}
+\label{fig:magn}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
+\caption{}
+\label{fig:mbhn}
+\end{center}
+\end{figure}
 
@@
 \\
- & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
+ & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph} - \langle \log n_{\rm sph,maj} \rangle \bigr)$} \\ [0.5em]
 All (62)               & BCES $(Y|X)$               & $-23.88 \pm 0.15$ & $-7.17 \pm 0.80$ & $0.51$ & $-$ & $1.18$ \\
@@
 
-Bulges (30)	       & BCES $(Y|X)$		    & $-22.25 \pm 0.20$ & $-5.88 \pm 3.06$ & $0.26$ & $-$ & $1.16$ \\
+Bulge  (30)	       & BCES $(Y|X)$		    & $-22.25 \pm 0.20$ & $-5.88 \pm 3.06$ & $0.26$ & $-$ & $1.16$ \\
 		       & mFITEXY $(Y|X)$	    & $-22.19 \pm 0.14$ & $-2.99 \pm 0.73$ & $0.26$ & $0.52^{+0.18}_{-0.10}$ & $0.75$ \\
@@
 		       & mFITEXY Bisector	    & $-22.18 \pm 0.20$ & $-4.34 \pm 0.84$ & $0.26$ & $-$ & $0.96$ \\
-		       & {\tt linmix\_err} Bisector & $-22.19 \pm 0.25$ & $-3.83 \pm 1.39$ & $0.26$ & $-$ & $0.91$ \\ [0.5em]
+		       & {\tt linmix\_err} Bisector & $-22.19 \pm 0.25$ & $-3.83 \pm 1.39$ & $0.26$ & $-$ & $0.91$ \\ [1.0em]
+
+% & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph,eq} - \langle \log n_{\rm sph,eq} \rangle \bigr)$} \\ [0.5em]
+%
+% All (62)		 & BCES $(Y|X)$ 	      & $-23.88 \pm 0.15$ & $-7.04 \pm 0.89$ & $0.50$ & $-$ & $1.19$ \\
+%			 & mFITEXY $(Y|X)$	      & $-23.95 \pm 0.12$ & $-6.43 \pm 0.41$ & $0.50$ & $0.55^{+0.16}_{-0.10}$ & $0.96$ \\
+%			 & {\tt linmix\_err} $(Y|X)$  & $-23.91 \pm 0.14$ & $-6.04 \pm 0.54$ & $0.50$ & $0.75 \pm 0.13$ & $1.07$ \\ [0.5em]
+%			 & BCES $(X|Y)$ 	      & $-23.88 \pm 0.14$ & $-6.73 \pm 0.48$ & $0.50$ & $-$ & $1.14$ \\
+%			 & mFITEXY $(X|Y)$	      & $-23.93 \pm 0.13$ & $-7.13 \pm 0.48$ & $0.50$ & $0.58^{+0.17}_{-0.12}$ & $1.21$ \\
+%			 & {\tt linmix\_err} $(X|Y)$  & $-23.93 \pm 0.15$ & $-7.14 \pm 0.57$ & $0.50$ & $0.76 \pm 0.16$ & $1.21$ \\ [0.5em]
+%			 & BCES Bisector	      & $-23.88 \pm 0.15$ & $-6.88 \pm 0.62$ & $0.50$ & $-$ & $1.17$ \\
+%			 & mFITEXY Bisector	      & $-23.94 \pm 0.13$ & $-6.76 \pm 0.31$ & $0.50$ & $-$ & $1.15$ \\
+%			 & {\tt linmix\_err} Bisector & $-23.92 \pm 0.15$ & $-6.55 \pm 0.40$ & $0.50$ & $-$ & $1.12$ \\ [0.5em]
+%
+%
+% Elliptical (30)	 & BCES $(Y|X)$ 	      & $-25.46 \pm 0.26$ & $4.92 \pm 4.72$ & $0.77$ & $-$ & $1.46$ \\
+%			 & mFITEXY $(Y|X)$	      & $-25.66 \pm 0.24$ & $-12.65 \pm 2.78$ & $0.77$ & $0.42^{+0.38}_{-0.42}$ & $1.27$ \\
+%			 & {\tt linmix\_err} $(Y|X)$  & $-25.55 \pm 0.26$ & $-8.54 \pm 4.68$ & $0.77$ & $0.80 \pm 0.24$ & $1.20$ \\ [0.5em]
+%			 & BCES $(X|Y)$ 	      & $-25.46 \pm 0.40$ & $-20.83 \pm 11.31$ & $0.77$ & $-$ & $2.26$ \\
+%			 & mFITEXY $(X|Y)$	      & $-25.63 \pm 0.31$ & $-16.13 \pm 4.37$ & $0.77$ & $0.48^{+0.48}_{-0.48}$ & $1.80$ \\
+%			 & {\tt linmix\_err} $(X|Y)$  & $-25.63 \pm 0.43$ & $-16.66 \pm 6.50$ & $0.77$ & $1.22 \pm 0.65$ & $1.85$ \\ [0.5em]
+%			 & BCES Bisector	      & $-25.46 \pm 0.20$ & $-0.08 \pm 0.10$ & $0.77$ & $-$ & $1.14$ \\
+%			 & mFITEXY Bisector	      & $-25.65 \pm 0.28$ & $-14.18 \pm 2.43$ & $0.77$ & $-$ & $1.63$ \\
+%			 & {\tt linmix\_err} Bisector & $-25.58 \pm 0.35$ & $-11.30 \pm 4.34$ & $0.77$ & $-$ & $1.38$ \\ [0.5em]
+%
+%\tableline 
+%\tableline
+%\end{tabular}
+%\end{table*}
+%
+%\begin{table*}
+%\centering
+%\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
+%\begin{tabular}{llccccc}
+%\tableline
+%\tableline
+%{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+%\tableline 
+%\\
+%
+% Lenticular (11)	 & BCES $(Y|X)$ 	      & $-22.08 \pm 0.89$ & $16.29 \pm 24.44$ & $0.29$ & $-$ & $3.25$ \\
+%			 & mFITEXY $(Y|X)$	      & $-22.16 \pm 0.20$ & $-5.84 \pm 1.83$ & $0.29$ & $0.31^{+0.28}_{-0.20}$ & $0.61$ \\
+%			 & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
+%			 & BCES $(X|Y)$ 	      & $-22.08 \pm 0.20$ & $-7.40 \pm 1.27$ & $0.29$ & $-$ & $0.72$ \\
+%			 & mFITEXY $(X|Y)$	      & $-22.11 \pm 0.28$ & $-8.30 \pm 3.33$ & $0.29$ & $0.40^{+0.33}_{-0.35}$ & $0.77$ \\
+%			 & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
+%			 & BCES Bisector	      & $-22.08 \pm 0.30$ & $0.04 \pm 0.05$ & $0.29$ & $-$ & $1.08$ \\
+%			 & mFITEXY Bisector	      & $-22.14 \pm 0.25$ & $-6.86 \pm 1.70$ & $0.29$ & $-$ & $0.70$ \\
+%			 & {\tt linmix\_err} Bisector & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
+%
+%
+% Spiral (17)		 & BCES $(Y|X)$ 	      & $-22.33 \pm 0.62$ & $-14.53 \pm 71.43$ & $0.17$ & $-$ & $2.71$ \\
+%			 & mFITEXY $(Y|X)$	      & $-22.37 \pm 0.27$ & $-6.53 \pm 2.84$ & $0.17$ & $0.47^{+0.52}_{-0.39}$ & $0.95$ \\
+%			 & {\tt linmix\_err} $(Y|X)$  & $-22.35 \pm 1.23$ & $-3.62 \pm 21.94$ & $0.17$ & $0.63 \pm 0.25$ & $0.93$ \\ [0.5em]
+%			 & BCES $(X|Y)$ 	      & $-22.33 \pm 0.35$ & $-7.91 \pm 5.53$ & $0.17$ & $-$ & $1.54$ \\
+%			 & mFITEXY $(X|Y)$	      & $-22.74 \pm 0.56$ & $-14.91 \pm 10.03$ & $0.17$ & $0.65^{+1.41}_{-0.65}$ & $2.82$ \\
+%			 & {\tt linmix\_err} $(X|Y)$  & $-22.66 \pm 0.88$ & $-16.17 \pm 21.34$ & $0.17$ & $1.47 \pm 2.15$ & $3.04$ \\ [0.5em]
+%			 & BCES Bisector	      & $-22.33 \pm 0.44$ & $-10.25 \pm 18.84$ & $0.17$ & $-$ & $1.94$ \\
+%			 & mFITEXY Bisector	      & $-22.48 \pm 0.44$ & $-9.10 \pm 3.31$ & $0.17$ & $-$ & $1.75$ \\
+%			 & {\tt linmix\_err} Bisector & $-22.41 \pm 1.07$ & $-5.98 \pm 28.65$ & $0.17$ & $-$ & $1.24$ \\ [0.5em]
+%
+%
+% Early-type (43)	 & BCES $(Y|X)$ 	      & $-24.55 \pm 0.22$ & $-10.81 \pm 1.96$ & $0.64$ & $-$ & $1.46$ \\
+%			 & mFITEXY $(Y|X)$	      & $-24.70 \pm 0.14$ & $-7.89 \pm 0.63$ & $0.64$ & $0.46^{+0.18}_{-0.14}$ & $0.93$ \\
+%			 & {\tt linmix\_err} $(Y|X)$  & $-24.63 \pm 0.18$ & $-7.34 \pm 0.83$ & $0.64$ & $0.75 \pm 0.16$ & $1.02$ \\ [0.5em]
+%			 & BCES $(X|Y)$ 	      & $-24.55 \pm 0.16$ & $-8.35 \pm 0.68$ & $0.64$ & $-$ & $1.10$ \\
+%			 & mFITEXY $(X|Y)$	      & $-24.69 \pm 0.16$ & $-8.65 \pm 0.73$ & $0.64$ & $0.48^{+0.20}_{-0.15}$ & $1.14$ \\
+%			 & {\tt linmix\_err} $(X|Y)$  & $-24.68 \pm 0.20$ & $-8.68 \pm 0.91$ & $0.64$ & $0.77 \pm 0.20$ & $1.14$ \\ [0.5em]
+%			 & BCES Bisector	      & $-24.55 \pm 0.18$ & $-9.42 \pm 1.00$ & $0.64$ & $-$ & $1.23$ \\
+%			 & mFITEXY Bisector	      & $-24.69 \pm 0.15$ & $-8.25 \pm 0.48$ & $0.64$ & $-$ & $1.10$ \\
+%			 & {\tt linmix\_err} Bisector & $-24.65 \pm 0.19$ & $-7.96 \pm 0.62$ & $0.64$ & $-$ & $1.07$ \\ [0.5em]
+%
+%
+% Bulge (30)		 & BCES $(Y|X)$ 	      & $-22.25 \pm 0.50$ & $-16.91 \pm 33.45$ & $0.23$ & $-$ & $2.85$ \\
+%			 & mFITEXY $(Y|X)$	      & $-22.21 \pm 0.14$ & $-4.25 \pm 0.94$ & $0.23$ & $0.45^{+0.21}_{-0.13}$ & $0.75$ \\
+%			 & {\tt linmix\_err} $(Y|X)$  & $-22.23 \pm 0.17$ & $-3.36 \pm 1.62$ & $0.23$ & $0.61 \pm 0.17$ & $0.87$ \\ [0.5em]
+%			 & BCES $(X|Y)$ 	      & $-22.25 \pm 0.23$ & $-7.56 \pm 1.94$ & $0.23$ & $-$ & $1.30$ \\
+%			 & mFITEXY $(X|Y)$	      & $-22.23 \pm 0.22$ & $-8.20 \pm 2.44$ & $0.23$ & $0.63^{+0.31}_{-0.19}$ & $1.39$ \\
+%			 & {\tt linmix\_err} $(X|Y)$  & $-22.22 \pm 0.28$ & $-8.42 \pm 4.00$ & $0.23$ & $0.96 \pm 0.54$ & $1.43$ \\ [0.5em]
+%			 & BCES Bisector	      & $-22.25 \pm 0.31$ & $-10.46 \pm 7.05$ & $0.23$ & $-$ & $1.75$ \\
+%			 & mFITEXY Bisector	      & $-22.22 \pm 0.19$ & $-5.62 \pm 0.99$ & $0.23$ & $-$ & $1.05$ \\
+%			 & {\tt linmix\_err} Bisector & $-22.23 \pm 0.23$ & $-4.84 \pm 1.75$ & $0.23$ & $-$ & $0.98$ \\ [0.5em]
 
@@
 \end{tabular}
-\label{tab:lregsph} 
-\tablecomments{For each subsample, we indicate $\langle MAG_{\rm sph} \rangle$, its average value of spheroid magnitudes. 
-In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. 
+\label{tab:lregLn} 
+\tablecomments{For each subsample, we indicate $\langle \log n_{\rm sph} \rangle$, its average value of spheroid S\'ersic index. 
+In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
+all - mergers - outliers
+Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2). }
+\end{table*}
+
+\begin{table*}
+\centering
+\caption{Linear regression analysis of the $M_{\rm BH} - n_{\rm sph}$ diagram.}
+\begin{tabular}{llccccc}
+\tableline
+\tableline
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+\tableline 
+\\
+ & \multicolumn{6}{l}{$\log \bigl( M_{\rm BH}/{\rm [M_\odot]} \bigr) = \alpha + \beta \bigl(\log n_{\rm sph} - \langle \log n_{\rm sph} \rangle \bigr)$} \\ [0.5em]
+ All (62)		& BCES $(Y|X)$  	     & $8.14 \pm 0.08$ & $3.56 \pm 0.38$ & $0.51$ & $-$ & $0.60$ \\
+ 			& mFITEXY $(Y|X)$	     & $8.18 \pm 0.06$ & $3.27 \pm 0.21$ & $0.51$ & $0.22^{+0.10}_{-0.07}$ & $0.45$ \\
+ 			& {\tt linmix\_err} $(Y|X)$  & $8.17 \pm 0.06$ & $3.17 \pm 0.24$ & $0.51$ & $0.29 \pm 0.07$ & $0.56$ \\ [0.5em]
+ 			& BCES $(X|Y)$  	     & $8.14 \pm 0.08$ & $3.56 \pm 0.25$ & $0.51$ & $-$ & $0.60$ \\
+ 			& mFITEXY $(X|Y)$	     & $8.18 \pm 0.06$ & $3.51 \pm 0.23$ & $0.51$ & $0.23^{+0.10}_{-0.07}$ & $0.60$ \\
+ 			& {\tt linmix\_err} $(X|Y)$  & $8.17 \pm 0.07$ & $3.49 \pm 0.26$ & $0.51$ & $0.30 \pm 0.07$ & $0.60$ \\ [0.5em]
+ 			& BCES Bisector 	     & $8.14 \pm 0.08$ & $3.56 \pm 0.29$ & $0.51$ & $-$ & $0.60$ \\
+ 			& mFITEXY Bisector	     & $8.18 \pm 0.06$ & $3.39 \pm 0.15$ & $0.51$ & $-$ & $0.58$ \\
+ 			& {\tt linmix\_err} Bisector & $8.17 \pm 0.07$ & $3.33 \pm 0.18$ & $0.51$ & $-$ & $0.57$ \\ [0.5em]
+
+ Elliptical (30)	& BCES $(Y|X)$  	     & $8.80 \pm 0.53$ & $-18.16 \pm 53.99$ & $0.76$ & $-$ & $3.02$ \\
+ 			& mFITEXY $(Y|X)$	     & $8.90 \pm 0.10$ & $4.47 \pm 0.88$ & $0.76$ & $0.29^{+0.14}_{-0.10}$ & $0.56$ \\
+ 			& {\tt linmix\_err} $(Y|X)$  & $8.84 \pm 0.12$ & $3.56 \pm 1.35$ & $0.76$ & $0.44 \pm 0.12$ & $0.59$ \\ [0.5em]
+ 			& BCES $(X|Y)$  	     & $8.80 \pm 0.18$ & $8.00 \pm 2.55$ & $0.76$ & $-$ & $1.01$ \\
+ 			& mFITEXY $(X|Y)$	     & $8.92 \pm 0.15$ & $6.85 \pm 1.75$ & $0.76$ & $0.36^{+0.20}_{-0.15}$ & $0.89$ \\
+ 			& {\tt linmix\_err} $(X|Y)$  & $8.89 \pm 0.20$ & $6.96 \pm 2.49$ & $0.76$ & $0.63 \pm 0.30$ & $0.89$ \\ [0.5em]
+ 			& BCES Bisector 	     & $8.80 \pm 0.11$ & $-0.03 \pm 0.10$ & $0.76$ & $-$ & $0.64$ \\
+ 			& mFITEXY Bisector	     & $8.91 \pm 0.13$ & $5.42 \pm 0.85$ & $0.76$ & $-$ & $0.73$ \\
+ 			& {\tt linmix\_err} Bisector & $8.85 \pm 0.16$ & $4.73 \pm 1.30$ & $0.76$ & $-$ & $0.67$ \\ [0.5em]
+
+ Lenticular (11)	& BCES $(Y|X)$  	     & $7.75 \pm 0.58$ & $-11.51 \pm 31.78$ & $0.33$ & $-$ & $2.11$ \\
+ 			& mFITEXY $(Y|X)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.26$ \\
+ 			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
+ 			& BCES $(X|Y)$  	     & $7.75 \pm 0.13$ & $3.54 \pm 0.99$ & $0.33$ & $-$ & $0.46$ \\
+ 			& mFITEXY $(X|Y)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.49$ \\
+ 			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
+ 			& BCES Bisector 	     & $7.75 \pm 0.13$ & $-0.09 \pm 0.15$ & $0.33$ & $-$ & $0.48$ \\
+ 			& mFITEXY Bisector	     & $7.65 \pm 0.12$ & $3.78 \pm 0.85$ & $0.33$ & $-$ & $0.49$ \\
+ 			& {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]
+
+ Spiral (17)		& BCES $(Y|X)$  	     & $7.18 \pm 0.28$ & $6.78 \pm 6.62$ & $0.18$ & $-$ & $1.23$ \\
+ 			& mFITEXY $(Y|X)$	     & $7.24 \pm 0.13$ & $4.48 \pm 0.90$ & $0.18$ & $0.13^{+0.42}_{-0.13}$ & $0.52$ \\
+ 			& {\tt linmix\_err} $(Y|X)$  & $7.22 \pm 0.16$ & $3.57 \pm 1.36$ & $0.18$ & $0.39 \pm 0.19$ & $0.70$ \\ [0.5em]
+ 			& BCES $(X|Y)$  	     & $7.18 \pm 0.23$ & $5.48 \pm 1.93$ & $0.18$ & $-$ & $0.99$ \\
+ 			& mFITEXY $(X|Y)$	     & $7.24 \pm 0.14$ & $4.62 \pm 0.96$ & $0.18$ & $0.13^{+0.43}_{-0.13}$ & $0.85$ \\
+ 			& {\tt linmix\_err} $(X|Y)$  & $7.21 \pm 0.21$ & $4.86 \pm 1.64$ & $0.18$ & $0.45 \pm 0.31$ & $0.89$ \\ [0.5em]
+ 			& BCES Bisector 	     & $7.18 \pm 0.25$ & $6.06 \pm 3.66$ & $0.18$ & $-$ & $1.10$ \\
+ 			& mFITEXY Bisector	     & $7.24 \pm 0.14$ & $4.55 \pm 0.66$ & $0.18$ & $-$ & $0.84$ \\
+ 			& {\tt linmix\_err} Bisector & $7.22 \pm 0.19$ & $4.12 \pm 1.07$ & $0.18$ & $-$ & $0.77$ \\ [0.5em]
+
+ Early-type (43)	& BCES $(Y|X)$  	     & $8.54 \pm 0.10$ & $4.07 \pm 0.87$ & $0.64$ & $-$ & $0.65$ \\
+ 			& mFITEXY $(Y|X)$	     & $8.58 \pm 0.07$ & $3.32 \pm 0.34$ & $0.64$ & $0.24^{+0.10}_{-0.07}$ & $0.45$ \\
+ 			& {\tt linmix\_err} $(Y|X)$  & $8.57 \pm 0.08$ & $3.12 \pm 0.43$ & $0.64$ & $0.32 \pm 0.08$ & $0.53$ \\ [0.5em]
+ 			& BCES $(X|Y)$  	     & $8.54 \pm 0.09$ & $3.95 \pm 0.55$ & $0.64$ & $-$ & $0.63$ \\
+ 			& mFITEXY $(X|Y)$	     & $8.59 \pm 0.08$ & $3.88 \pm 0.43$ & $0.64$ & $0.26^{+0.11}_{-0.08}$ & $0.62$ \\
+ 			& {\tt linmix\_err} $(X|Y)$  & $8.59 \pm 0.09$ & $3.82 \pm 0.50$ & $0.64$ & $0.35 \pm 0.10$ & $0.61$ \\ [0.5em]
+ 			& BCES Bisector 	     & $8.54 \pm 0.10$ & $4.01 \pm 0.63$ & $0.64$ & $-$ & $0.64$ \\
+ 			& mFITEXY Bisector	     & $8.59 \pm 0.07$ & $3.58 \pm 0.27$ & $0.64$ & $-$ & $0.58$ \\
+ 			& {\tt linmix\_err} Bisector & $8.58 \pm 0.08$ & $3.44 \pm 0.33$ & $0.64$ & $-$ & $0.56$ \\ [0.5em]
+
+\tableline 
+\tableline
+\end{tabular}
+\label{tab:lregMn} 
+\tablecomments{For each subsample, we indicate $\langle \log n_{\rm sph} \rangle$, its average value of spheroid S\'ersic index. 
+In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
+all - mergers - outliers
 Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2).  }

### 2015-08-26 papers/mbhn/mbhn.sh

@@ -1,5 +1,5 @@
-latex mbhn
-bibtex mbhn
-latex mbhn
-latex mbhn
+latex mbhn.tex
+bibtex mbhn.tex
+latex mbhn.tex
+latex mbhn.tex
 dvipdfm mbhn.dvi

### 2015-08-26 python_codes/paper_figures/MbhN/figures.py

@@ -92,13 +92,13 @@ def mag_sph_vs_n_maj():
 	error_kwargs = {"lw":.5, "zorder":0}
 	
 	for x0,y0 in zip(n[simplemorphtype=='E'], mag_sph[simplemorphtype=='E']):
-		markers_linlog.elliptical(ax, 'red', np.log10(x0), (y0), 0.035, 0.08)
+		markers_linlog.elliptical(ax, 'red', np.log10(x0), (y0), 0.035, 0.12)
 	
         for x0,y0 in zip(n[simplemorphtype=='E/S0'], mag_sph[simplemorphtype=='E/S0']):
-        	markers_linlog.lenticular(ax, 'red', np.log10(x0), (y0), 0.03, 0.1)
+        	markers_linlog.lenticular(ax, 'red', np.log10(x0), (y0), 0.03, 0.12)
        
         for x0,y0 in zip(n[simplemorphtype=='S0'], mag_sph[simplemorphtype=='S0']):
-        	markers_linlog.lenticular(ax, 'darkorange', np.log10(x0), (y0), 0.03, 0.1)
+        	markers_linlog.lenticular(ax, 'darkorange', np.log10(x0), (y0), 0.03, 0.12)
        
         for x0,y0 in zip(n[simplemorphtype=='S0/Sp'], mag_sph[simplemorphtype=='S0/Sp']):
         	markers_linlog.spiral(ax, 'darkorange', np.log10(x0), (y0), 0.02, 0.07)
@@ -510,6 +510,551 @@ def mag_sph_vs_n_maj():
         plt.ylabel(r'$MAG_{\rm sph}~[\rm mag]$', labelpad=13)
         plt.subplots_adjust(left=0.17,bottom=0.15,right=0.97,top=0.9)
         
+	# legend
+        markers_linlog.elliptical(ax, 'red', np.log10(0.52), (-27.9), 0.035, 0.12)
+        ax.text(0.65, -27.6, 'E')
+        markers_linlog.lenticular(ax, 'red', np.log10(0.52), (-27.1), 0.03, 0.12)
+        ax.text(0.65, -26.8, 'E/S0')
+        markers_linlog.lenticular(ax, 'darkorange', np.log10(0.52), (-26.3), 0.03, 0.12)
+        ax.text(0.65, -26, 'S0')
+        markers_linlog.spiral(ax, 'darkorange', np.log10(1.2), (-27.9), 0.02, 0.07)
+        ax.text(1.5, -27.6, 'S0/Sp')
[…]

### 2015-08-26 python_codes/tex_tables/tex_tables.py

@@ -8,6 +8,7 @@ dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_viv
 sampletableFileName = '/Users/gsavorgnan/galaxy_vivisection/papers/data_paper/table_sample.tex'
 fitresultstableFileName = '/Users/gsavorgnan/galaxy_vivisection/papers/data_paper/table_fitresults.tex'
 mmsampletableFileName = '/Users/gsavorgnan/galaxy_vivisection/papers/MbhMsph/table_sample.tex'
+mnsampletableFileName = '/Users/gsavorgnan/galaxy_vivisection/papers/MbhN/table_sample.tex'
 
 def putBlankInPlaceOfNone(entry):
         if entry is None:
@@ -147,6 +148,57 @@ def footer_mmpaper_sampletable(label):
 			Four galaxies had their magnitudes overestimated, which are given here as upper limits. '
 		print '\\emph{Column (8)}: $[3.6]-[4.5]$ colour. '
 		print '\\emph{Column (9)}: Bulge stellar mass. } '	
+        print '\\end{center}    '
+        print '\\end{table*}    '
+
+def header_mnpaper_sampletable(caption):
+
+        print '\\begin{table*}                                        '
+        print '\\small                                                '
+        print '\\begin{center}                                        '
+	if caption:
+        	print '\\caption{Galaxy sample.} '
+        print '\\begin{tabular}{llllllrll}                           '
+        print '\\tableline                                                '
+        print '\\multicolumn{1}{l}{{\\bf Galaxy}} &                   '
+        print '\\multicolumn{1}{l}{{\\bf Type}} &                     '
+        print '\\multicolumn{1}{l}{{\\bf Distance}} &                 '
+        print '\\multicolumn{1}{l}{{\\bf $\\bm{M_{\\rm BH}}$}} &  '
+        print '\\multicolumn{1}{l}{{\\bf $\\bm{MAG_{\\rm sph}}$}} &  '
+        print '\\multicolumn{1}{l}{{\\bf $\\bm{n_{\\rm sph}}$}} \\\\  '
+        print '\\multicolumn{1}{l}{} &                                '
+        print '\\multicolumn{1}{l}{} &                                '
+        print '\\multicolumn{1}{l}{[Mpc]} &                           '
[…]

### 2015-08-27 papers/ellicular/ellicular.tex
burp

@@
 There are currently two well-known types of stellar discs in galaxies. 
-The first are the large-scale discs (with sizes of a few kiloparsec) that dominate the light at large radii in spiral and lenticular galaxies; 
+The first are the large-scale discs (with sizes of a few kiloparsec) 
+that dominate the light at large radii in spiral and lenticular galaxies; 
 the second are the small (tens to a couple of hundred parsec) nuclear discs observed in both early- and late-type galaxies 
@@
 The origin, or at least the on-going feeding and growth, of the large-scale discs has been attributed to cold gas flows, 
-gas rich mergers and halo accretion events (e.g.~\citealt{khochfarsilk2006,dekel2009nat,dekel2009apj,ceverino2010,ceverino2012,conselice2012}). 
-A thorough review can be found in Combes (arXiv:1309.1603 and 1405.6405).
-On the other hand, intermediate-sized discs have not received the same level of attention as their nuclear and large-scale homologues, 
-and, in some cases, they have even been labelled as something ''unphysical''. 
+gas rich mergers and halo accretion events 
+(e.g.~\citealt{khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}). 
+A thorough review can be found in \citet{combes2014arX} and \citet{combes2014pro}.
+On the other hand, intermediate-sized discs have not received the same level of attention 
+as their nuclear and large-scale homologues, 
+or, in some cases, they have even been labelled as something ''unphysical''. 
 Here we report on the photometric and kinematical signatures of these intermediate-sized stellar discs 
-and the impact this has on the important (black hole mass)-to-(spheroid stellar mass) ratio, $M_{\rm BH}/M_{*,sph}$, 
-which is used to constrain galaxy evolution models.
-
+and the impact this has on the important (black hole mass)-to-(spheroid stellar mass) ratio %, $M_{\rm BH}/M_{*,sph}$, 
+which is used to constrain galaxy evolution models. \\
 %A puzzling question, which has been unspoken for decades, is why are there not intermediate-sized discs: 
 %why are there not accretion events which create discs larger than the typical nuclear discs but which are not large enough to dominate at large radii? 
-
-\section{Rationale}
-\label{sec:rat}
 The majority of stellar discs have some level of inclination with respect to our line-of-sight, 
@@
 Unfortunately, such extended kinematic maps are not yet available for large numbers of galaxies in the local Universe. 
-Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of stellar discs in early-type galaxies.
-
+Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of stellar discs in early-type galaxies. \\
 The toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 
@@
 An ellipticity profile that increases with radius can be ascribed to an inclined disc that becomes progressively more important at large radii, 
-whereas a radial decrease of ellipticity signifies the opposite case.
+whereas a radial decrease of ellipticity signifies the opposite case. \\
+The awareness that many ``elliptical'' galaxies actually contain embedded stellar discs 
+dates back at least three decades 
+\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995,
+donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998} and, 
+more recently, intermediate-scale discs were all but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
+However, the class of early-type galaxies with intermediate-scale discs has been missed by many galaxy modelers, 
+who have labeled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
+as is observed with spiral galaxies. 
+This unspoken bias has led to the rejection of many spheroid/disc decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
+Unsurprisingly, studies affected by this bias have not obtained spheroid/disc decompositions with a spheroid-to-total ratio larger than $0.6 - 0.8$ 
+(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}). \\
+The existence of intermediate-scale stellar discs reveals a continuum of disc sizes, 
+rather than a dichotomy of nuclear versus large-scale discs. 
+The presence of intermediate-scale discs also blurs the distinction between elliptical and lenticular galaxies.
+%and creates the need for a new subclass to help bridge the divide. 
+The existence of such discs is not only important for our understanding of disc growth in general, 
+but accounting for such structure will impact our understanding of galaxy structure, 
+with important consequences for galaxy scaling relations. 
+%It has recently been argued that the classification scheme for elliptical galaxies should not be their apparent axis ratio as seen on the plane of the sky, 
+%but instead their spheroid-to-total ratio, with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies \citep{graham2014review}.
 
@@
 
-The awareness that many ``elliptical'' galaxies actually contain embedded stellar discs 
-dates back at least three decades 
-\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995,
-donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998} and, 
-%more recently, intermediate-scale discs were all but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013}. 
-However, the class of early-type galaxies with intermediate-scale discs has been missed by many galaxy modelers, 
-who have labeled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
-as is observed with spiral galaxies. 
-This unspoken bias has led to the rejection of many spheroid/disc decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
-Unsurprisingly, studies affected by this bias have not obtained spheroid/disc decompositions with a spheroid-to-total ratio larger than $0.6 - 0.8$ 
-(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}).
+\section{Galaxies}
+\label{sec:gal}
+Three examples of early-type galaxies with intermediate-scale discs are NGC 3115, Mrk 1216, and NGC 1271. 
+In the following Sections, we present a photometric analysis of these three galaxies, 
+and we compare our results with the kinematical analysis (when) available from the literature. 
+For the galaxy NGC 3115, we used a $3.6~\rm \mu m$ image obtained with the InfraRed Array Camera (IRAC) 
+onboard the \emph{Spitzer Space Telescope}. 
+For the galaxies Mrk 1216 and NGC 1271, we used archived Hubble Space Telescope (\emph{HST}) images 
+taken with the Wide Field Camera 3 (\emph{WFC3}) and the near-infrared \emph{F160W} filter ($H$-band). 
+Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (\emph{submitted}).
+Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
+The one-dimensional Point Spread Function (PSF) was characterized for each individual image 
+using a Gaussian or a \cite{moffat1969} profile.
+We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
+is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
+which is operated
+by the Association of Universities for Research in Astronomy (AURA) 
+under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{isofit...} \citep{taskellipse}. 
+The galaxy isphotes were modelled with a series of concentric ellipses, 
+allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
+The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
+We modelled the light profiles with a combination of PSF-convolved analytic functions, 
+using one function per galaxy component.
 
-The existence of intermediate-scale stellar discs reveals a continuum of disc sizes, 
-rather than a dichotomy of nuclear versus large-scale discs. 
-The presence of intermediate-scale discs also blurs the distinction between elliptical and lenticular galaxies.
-%and creates the need for a new subclass to help bridge the divide. 
-The existence of such discs is not only important for our understanding of disc growth in general, 
-but accounting for such structure will impact our understanding of galaxy structure, 
-with important consequences for galaxy scaling relations. 
-%It has recently been argued that the classification scheme for elliptical galaxies should not be their apparent axis ratio as seen on the plane of the sky, 
-%but instead their spheroid-to-total ratio, with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies \citep{graham2014review}.
+\subsection{NGC 3115}
+The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (see Figure \ref{fig:n3115}). 
+Less obvious is the extent of such disc, if one only relies on a visual inspection of the galaxy image. 
+However, the ellipticity profile is consistent with the presence of an intermediate-scale disc. 
+Moreover, the kinematics of NGC 3115 disprove the presence of a large scale disc, 
+because the galaxy is rapidly rotating only within two effective radii ($\sim 2 \times 50~\rm arcsec$), 
+whereas the rotation significantly drops at larger radii \citep{arnold2011n3115}.  
+The unsharp mask (Figure \ref{fig:n3115}) of NGC 3115 betrays the presence of a fain edge-on nuclear ring, 
+which can also be spotted as a small peak in the ellipticity profile 
+(at semimajor-axis lenght $R_{\rm maj} \sim 15~\rm arcsec$).
 
-\section{Galaxies}
-\label{sec:xxx}
+Two examples of ellicular galaxies are Mrk 1216 and NGC 3115. 
+While the presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure 3), 
+the disc in Mrk 1216 is not immediately apparent from the image 
+-- which is partly why many stellar discs have been over-looked to date. 
+However the radial light profile and the ellipticity profile betray the presence of a disc in both galaxies. 
+The radial light profiles of Mrk 1216 and NGC 3115 extend out to almost four times (4 x 7 arcsec) 
+and five times (5 x 50 arcsec) the galaxy half-light radii, respectively. 
+The main distribution of light in both of these galaxies is well described with a S\'ersic function22 
+for the spheroidal component plus an exponential function for the intermediate-sized disc. 
+Moreover, our photometric analysis enables the recovery of an additional nuclear disc in Mrk 1216 
+and a nuclear ring in NGC 3115. 
+The spheroid/disc decomposition for NGC 3115 is also in excellent agreement with the galaxy's kinematic properties23. 
+This comparison cannot be made for Mrk 1216 because no extended kinematic data are available.  
+Our models with an intermediate-sized disc embedded within a larger spheroidal component, 
+plus an additional nuclear component when one is present, 
+match the observed light distribution, and explain both the kinematic maps15 (when available) 
+and the ellipticity profiles, of three other ellicular galaxies 
+for which a direct measurement of their central supermassive black hole mass is available: 
+NGC 1271; NGC 1277; and NGC 1332.  
+Past models that ``forcedly'' described these ellicular galaxies with an inner bulge 
+encased within a large-scale disc 
+typically required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
+Such three-component models (bulge + disc + envelope) reduce the spheroid luminosity by a factor of 2-3, 
+and underestimate the size of the spheroid by a factor of 10.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.49\columnwidth]{images/n3115_image.jpeg}
+\includegraphics[width=0.49\columnwidth]{images/n3115_unsharp.jpeg} \\
+\includegraphics[width=1.05\columnwidth]{images/n3115_decomposition.pdf}
+\caption{}
+\label{fig:n3115}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.49\columnwidth]{images/mrk1216_image.jpeg}
+\includegraphics[width=0.49\columnwidth]{images/mrk1216_unsharp.jpeg} \\
+\includegraphics[width=1.05\columnwidth]{images/mrk1216_decomposition.pdf}
+\caption{}
+\label{fig:m1216}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.49\columnwidth]{images/n1271_image}
+\includegraphics[width=0.49\columnwidth]{images/n1271_unsharp} \\
+\includegraphics[width=1.05\columnwidth]{images/n1271_decomposition.pdf}
+\caption{}
+\label{fig:m1216}
+\end{center}
+\end{figure}
 
@@
 \subsection{mm diagram}
+Obviously, having both the black hole mass and the spheroid mass correct is important 
+for placing systems in the (black hole mass)-(spheroid stellar mass) diagram. 
+For early-type galaxies, the spheroid luminosity and the total galaxy luminosity 
+can be used to predict the black hole mass with the same level of accuracy \citep{savorgnan2015}. 
+If a galaxy hosts a black hole that is over-massive compared to expectations from the spheroid luminosity, 
+but whose mass is normal compared to expectations from the total galaxy luminosity, 
+one should wonder whether the spheroid luminosity might have been underestimated 
+due to an inaccurate spheroid/disc decomposition. 
+Indeed, none of the five ellicular galaxies mentioned here is a noticeable outlier 
+in the (black hole mass)-(total galaxy luminosity) diagram \citep{savorgnan2015}. 
+For the first time, Figure 4 reveals that when ellicular galaxies are properly modeled, 
+they no longer appear as extreme outliers in the (black hole mass)-(spheroid stellar mass) diagram.
 
 \subsection{compact massive sph}
+Acknowledging the correct structure of ellicular galaxies is also important to properly understand their origin. 
+According to the current paradigm of cosmological structure evolution, 
+the genesis of massive early-type galaxies is characterized by two distinct phases: ''in-situ'' and ''ex-situ''. 
+The first phase takes place in a young Universe (within its first 4 billion years), 
+when cold gas inflows produced short and intense bursts of star formation that created the cores of galaxies. 
+These naked and compact cores, named ''red nuggets''25, have been observed26 at high-redshift with sizes of 1-2 kpc.
+In the second phase (last 10 billion years), stellar discs and stellar envelopes 
+were accreted around these primordial galaxy cores and assembled the external parts of galaxies on scales of 2-20 kpc. 
+Today's Universe is populated by an abundance of compact, massive spheroids27, 
+with the same physical properties -- mass and compactness -- as the high-redshift red nuggets. 
+Some of these local compact massive spheroids are encased within a large-scale disc, 
+that is to say they are the bulges of some lenticular and spiral galaxies. 
+Over the last 10 billion years their spheroids have evolved by growing a relatively flat disc -- 
+rather than a three-dimensional envelope -- 
+which has increased the galaxy size but preserved the bulge compactness. 
+The other compact massive spheroids of today's Universe belong to some ellicular galaxies. 
+Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact ellicular galaxies 
+with purely old (>10 billion years) stellar populations. 
+These galaxies have undergone the lowest degree of disc growth.
+In addition to the observational clues as to the actual physical components in ellicular galaxies, 
+one can reason on other grounds as to why these compact galaxies are not comprised of an inner bulge 
+plus large-scale disc plus outer envelope5,28,6. If they were such three-component systems, 
+then one would have two possibilities. 
+The first possibility is that these galaxies were already fully assembled 10 billion years ago; 
+this would explain their old stellar populations, 
+but it would also imply that their discs and envelopes had already formed during the first 4 billion years of the Universe, 
+in disagreement with the current cosmological picture. 
+The second possibility is that only their inner bulges (with sizes of 0.1-0.2 kpc, 
+according to past decompositions) originated in the first 4 billion years 
+and they subsequently accreted a substantial disc and envelope. 
+If this was correct, then we would observe high-redshift, star-like, naked bulges with stellar masses 
+within a factor of a few times the currently observed red nuggets but sizes which are 10 times smaller. 
+However, a dramatically different expectation is reached 
+if one considers these galaxies as spheroid-dominated systems with an intermediate-scale disc; 
+in this case, both the galaxy size and the spheroid size are compact (1-2 kpc). 
+This implies that, among the local descendants of the high-redshift red nuggets, 
+the compact ellicular galaxies have undergone the lowest degree of disc growth. 
+That is, the bulk of a compact ellicular galaxy quickly assembled ''in-situ'' in a very young Universe 
+and experienced very little evolution over the last 10 billion years.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{images/mm.pdf}
+\caption{Early-type galaxies: black hole mass plotted against spheroid stellar mass for 42 galaxies (black) plus the galaxies Mrk 1216, NGC 1271, NGC 1277, NGC 1332, NGC 3115, and NGC 4291.
+The black solid line is the bisector linear regression for early-type galaxies24.
+The dashed lines mark the 1sigma and 3sigma deviations, where sigma (0.51 dex) is the total rms scatter about the correlation in the black hole mass direction.
+The red color is used for five ellicular galaxies, (Mrk 1216, for which only an upper limit on its black hole mass has been reported) [4], NGC 1271 [6], NGC 1277 [5, 4], NGC 1332 [7], and NGC 4291 [29]), that were claimed to be extreme outliers in this diagram.
+All reside within a 3sigma deviation from the correlation when using their correct spheroid mass.
+For NGC 1277, we show the previously reported spheroid stellar mass [5] in gray.}
+\label{fig:mm}
+\end{center}
+\end{figure}
 

### 2015-08-27 python_codes/paper_figures/ellicular/galaxies/cls/psf.py

@@ -1,0 +1,45 @@
+from cls import PsfFunction
+import numpy as np
+
+def createPsf(Settings):
+    
+    if (Settings.observation == 'spitzer3.6um'): 
+
+        gaussianPsf = PsfFunction()
+        gaussianPsf.name = 'gaussian'
+        gaussianPsf.gaussianFWHM = 1.6648 * Settings.pxlToArcsec 
+        
+        moffatPsf = PsfFunction()
+        moffatPsf.name = 'moffat'
+        moffatPsf.moffatAlpha = (1.61467/(2*np.sqrt(2**(1/4.39)-1)) ) * Settings.pxlToArcsec  # alpha = fwhm / (2 * sqrt(2**(1/beta) - 1) )
+        moffatPsf.moffatBeta = 4.39  
+        
+#        psfList = [gaussianPsf, moffatPsf]
+        psfList = [moffatPsf]
+
+    if (Settings.observation == 'm1216'):
+    
+        gaussianPsf = PsfFunction()
+        gaussianPsf.name = 'gaussian'
+        gaussianPsf.gaussianFWHM = 2.3 * Settings.pxlToArcsec 
+        
+        psfList = [gaussianPsf]
+
+    if (Settings.observation == 'n1271'):
+    
+        gaussianPsf = PsfFunction()
+        gaussianPsf.name = 'gaussian'
+        gaussianPsf.gaussianFWHM = 2.3 * Settings.pxlToArcsec 
+        
+        psfList = [gaussianPsf]
+
+    gaussianSmoothing = PsfFunction()
+    gaussianSmoothing.name = 'gaussian'
+    #gaussianSmoothing.gaussianFWHM = 60 * 2.3548 * Settings.pxlToArcsec  # m31
+    gaussianSmoothing.gaussianFWHM = 5 * 2.3548 * Settings.pxlToArcsec    # m81 n5128
+    #gaussianSmoothing.gaussianFWHM = 3 * 2.3548 * Settings.pxlToArcsec    # n4945
+    
+    return psfList, gaussianSmoothing
+
+
+

### 2015-08-27 python_codes/paper_figures/ellicular/galaxies/cls/settings.py

@@ -1,0 +1,49 @@
+#### default settings
+
+class Settings:
+    
+    #performFit = False
+    performFit = True
+    
+    #axisFit = 'maj'
+    #axisFit = 'eq'
+    #axisFit = 'min'
+            
+    #fitConvolvedModel = False
+    #plotConvolvedFinalModel = False
+    #plotConvolvedComponent = False
+    fitConvolvedModel = True
+    plotConvolvedFinalModel = True
+    plotConvolvedComponent = True
+    
+    useErrorsInFit = False
+    #useErrorsInFit = True
+    
+    smoothing = False
+    #smoothing = True
+    
+    #observation = 'spitzer3.6um'
+    #observation = 'm1216' 
+    observation = 'n1271'
+        
+    if (observation == 'n1277'):
+        pxlToArcsec = 0.05
+        zeropoint = 24.851 # hst for n1277
+    
+    if (observation == 'n1271'):
+        pxlToArcsec = 0.12825
+        zeropoint = 24.6949 # Vega
+    
+    if (observation == 'm1216'):
+        pxlToArcsec = 0.12825
+        zeropoint = 24.6949 # Vega
+    
+    if (observation == 'spitzer3.6um'):
+        pxlToArcsec = 1.2232836
+        zeropoint = 17.25585 #spitzer 3.6 um
+
+    colordict = {'sersic' : 'red', 'tsersic' : 'red', 'disc' : 'blue', 'gaussian' : 'green', 'psf' : 'purple', 'ferrer' : 'lightblue', 'tdisc' : 'blue', 'gring' : 'grey', 'psfwing' : 'purple'}
+    
+    #oversamplingStep = 0.2 # pixels
+    
+#     fitResultsFileName = '/Users/gsavorgnan/Dropbox/giulia_e_basta/ProFitErole1.0.1/results/1DfitResults.dat'

### 2015-08-27 python_codes/paper_figures/ellicular/galaxies/instruments/output.py

@@ -1,0 +1,166 @@
+import numpy as np
+import sys
+from scipy.special import gamma
+import os.path
+
+from modelComponents.sersic import computeSersicParameters
+from modelComponents.disc import computeDiscParameters
+from modelComponents.gaussian import computeGaussianParameters
+from modelComponents.moffat import computeMoffatParameters
+from modelComponents.ferrer import computeFerrerParameters
+from modelComponents.gaussRing import computeGaussRingParameters
+
+def produceOutputFile(Settings, galaxy, axisFit, psfFunction, sampling, componentslist, finalparams, deltarms):
+    
+    outputFileName = galaxy + '_' + axisFit + '_' + psfFunction.name + '_' + sampling + '_par_SM.dat'
+    outputFile = open(outputFileName, 'w')
+    sys.stdout = outputFile
+    
+    flux_total_galaxy = 0
+    
+    for component in componentslist:
+        namepar1 = 'par1_' + str(component.number)
+        namepar2 = 'par2_' + str(component.number)
+        namepar3 = 'par3_' + str(component.number)
+        namepar4 = 'par4_' + str(component.number)
+            
+        if (component.name == 'sersic'):
+            r_e = finalparams[namepar1].value
+            mu_e = finalparams[namepar2].value
+            n = finalparams[namepar3].value
+            b, m_tot = computeSersicParameters(mu_e, r_e, n)
+            print component.number,
+            print component.name,
+            print("{0:.4f}".format(r_e)),
+            print("{0:.4f}".format(mu_e)),
+            print("{0:.4f}".format(n)),
+            print '-99.9999',
+            print("{0:.4f}".format(m_tot))
+        if (component.name == 'disc'):
+            h= finalparams[namepar1].value
+            mu_0 = finalparams[namepar2].value
+            m_tot = computeDiscParameters(mu_0, h) 
+            print component.number,
+            print component.name,
+            print("{0:.4f}".format(h)),
+            print("{0:.4f}".format(mu_0)),
+            print '-99.9999',
+            print '-99.9999',
+            print("{0:.4f}".format(m_tot)) 
+        if (component.name == 'gaussian'):
+            fwhm = finalparams[namepar1].value
+            mu_0 = finalparams[namepar2].value
+            m_tot = computeGaussianParameters(fwhm, mu_0)
+            print component.number,
+            print component.name,
+            print("{0:.4f}".format(fwhm)),
[…]

### 2015-08-27 python_codes/paper_figures/ellicular/galaxies/modelComponents/truncDisc.py

@@ -1,0 +1,25 @@
+from convolution.psfConvolution import doPsfConvolution
+import numpy as np
+
+############# BUILD TRUNCATED DISC MODEL ##########
+
+def buildTruncDisc(x, params, component, psfFunction, convolve, zeropoint):  
+
+	namepar1 = 'par1_' + str(component.number) # h
+	namepar2 = 'par2_' + str(component.number) # mu_0
+	namepar3 = 'par3_' + str(component.number) # r_out
+	
+	x_i = x[x<params[namepar3].value]
+	x_e = x[x>=params[namepar3].value]
+	
+	y_tdisc_sb_i = (params[namepar2].value) + 1.085736*x_i/(params[namepar1].value)
+	y_tdisc_i = 10**(0.4*(zeropoint - y_tdisc_sb_i))
+	y_tdisc_e = x_e * 0.0
+	
+	y_tdisc = np.concatenate((y_tdisc_i, y_tdisc_e))
+	
+	if (convolve):
+		y_tdisc = doPsfConvolution(y_tdisc, psfFunction, x)
+		
+	return y_tdisc
+

### 2015-09-01 papers/ellicular/ellicular.tex
balayage

@@
 
-\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their supermassive black holes}
+\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes}
 
@@
 \begin{abstract}
-vjsfkajhda
+The classification early-type galaxy includes both elliptically-shaped and lenticular galaxies, 
+with the latter composed of a spheroid, or bulge, of stars encased within a larger, but flatter, stellar disc. 
+Theoretically, the spheroid-to-disc flux ratio can assume any positive value. 
+However, several studies only consider spheroid/disc decompositions 
+in which the disc neatly dominates over the spheroid at large galaxy radii -- creating an inner bulge -- 
+and they reject decompositions if the disc remains embedded within the spheroid, labeling them as ``unphysical''. 
+Here we show that these rejected models correctly reproduce the photometric and kinematic properties of a class of early-type galaxy 
+with intermediate-scale disc. 
+Intermediate-scale discs have often been confused with large-scale discs, 
+and as a consequence the disc luminosities have been considerably overestimated 
+and their spheroid luminosities underestimated. 
+%intermediate between that of elliptical and lenticular galaxies, and which we name ellicular galaxies. 
+%Ellicular galaxies have often been confused with lenticular galaxies, and as a consequence their disc luminosities have been considerably overestimated 
+%and their spheroid luminosities underestimated. 
+This has recently led to some surprising conclusions, 
+such as the claim that a number of intermediate-scale disc galaxies (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
+host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
+When intermediate-scale disc galaxies are properly modeled, 
+they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram, 
+thereby resolving previous anomalies. 
+This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
+but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
+and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
+used to describe the coevolution of spheroids and their central supermassive black holes.
+
 \end{abstract}
@@
 (e.g.~\citealt{khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}). 
-A thorough review can be found in \citet{combes2014arX} and \citet{combes2014pro}.
+A thorough review can be found in \citet{combes2014arX,combes2014pro}.
 On the other hand, intermediate-sized discs have not received the same level of attention 
-as their nuclear and large-scale homologues, 
-or, in some cases, they have even been labelled as something ''unphysical''. 
+as their nuclear and large-scale homologues and,  
+in some cases, they have even been labelled as something ''unphysical''. 
 Here we report on the photometric and kinematical signatures of these intermediate-sized stellar discs 
@@
 more recently, intermediate-scale discs were all but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
-However, the class of early-type galaxies with intermediate-scale discs has been missed by many galaxy modelers, 
-who have labeled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
+However, the class of early-type galaxies with intermediate-scale discs has been missed by many galaxy modellers, 
+who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
 as is observed with spiral galaxies. 
@@
 
-\section{Galaxies}
+\section{Intermediate-scale disc galaxies}
 \label{sec:gal}
-Three examples of early-type galaxies with intermediate-scale discs are NGC 3115, Mrk 1216, and NGC 1271. 
+Three examples of early-type galaxies with intermediate-scale discs are Mrk 1216, NGC 1332, and NGC 3115. 
 In the following Sections, we present a photometric analysis of these three galaxies, 
 and we compare our results with the kinematical analysis (when) available from the literature. 
-For the galaxy NGC 3115, we used a $3.6~\rm \mu m$ image obtained with the InfraRed Array Camera (IRAC) 
+For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
 onboard the \emph{Spitzer Space Telescope}. 
-For the galaxies Mrk 1216 and NGC 1271, we used archived Hubble Space Telescope (\emph{HST}) images 
-taken with the Wide Field Camera 3 (\emph{WFC3}) and the near-infrared \emph{F160W} filter ($H$-band). 
+For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
+taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
 Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (\emph{submitted}).
 Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
-The one-dimensional Point Spread Function (PSF) was characterized for each individual image 
-using a Gaussian or a \cite{moffat1969} profile.
+The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
+and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
 We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
 is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
-which is operated
-by the Association of Universities for Research in Astronomy (AURA) 
-under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{isofit...} \citep{taskellipse}. 
-The galaxy isphotes were modelled with a series of concentric ellipses, 
+which is operated by the Association of Universities for Research in Astronomy (AURA) 
+under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
+was performed before {\tt isofit} \citep{ciambur2015} was conceived or available.} \citep{taskellipse}. 
+The galaxy isophotes were modelled with a series of concentric ellipses, 
 allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
@@
 \subsection{NGC 3115}
-The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (see Figure \ref{fig:n3115}). 
+The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
 Less obvious is the extent of such disc, if one only relies on a visual inspection of the galaxy image. 
-However, the ellipticity profile is consistent with the presence of an intermediate-scale disc. 
-Moreover, the kinematics of NGC 3115 disprove the presence of a large scale disc, 
-because the galaxy is rapidly rotating only within two effective radii ($\sim 2 \times 50~\rm arcsec$), 
-whereas the rotation significantly drops at larger radii \citep{arnold2011n3115}.  
-The unsharp mask (Figure \ref{fig:n3115}) of NGC 3115 betrays the presence of a fain edge-on nuclear ring, 
+The ellipticity profile is consistent with the presence of an intermediate-scale disc. 
+Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large scale disc, 
+because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
+whereas the rotation significantly drops at larger radii.  
+The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a fain edge-on nuclear ring, 
 which can also be spotted as a small peak in the ellipticity profile 
 (at semimajor-axis lenght $R_{\rm maj} \sim 15~\rm arcsec$).
+The surface brightness profile (Figure \ref{fig:n3115}) is well described with a S\'ersic-spheroid \citep{sersic1963},  
+an intermediate-sized exponential-disc, and a Gaussian-ring.
 
-Two examples of ellicular galaxies are Mrk 1216 and NGC 3115. 
-While the presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure 3), 
-the disc in Mrk 1216 is not immediately apparent from the image 
--- which is partly why many stellar discs have been over-looked to date. 
-However the radial light profile and the ellipticity profile betray the presence of a disc in both galaxies. 
-The radial light profiles of Mrk 1216 and NGC 3115 extend out to almost four times (4 x 7 arcsec) 
-and five times (5 x 50 arcsec) the galaxy half-light radii, respectively. 
-The main distribution of light in both of these galaxies is well described with a S\'ersic function22 
-for the spheroidal component plus an exponential function for the intermediate-sized disc. 
-Moreover, our photometric analysis enables the recovery of an additional nuclear disc in Mrk 1216 
-and a nuclear ring in NGC 3115. 
-The spheroid/disc decomposition for NGC 3115 is also in excellent agreement with the galaxy's kinematic properties23. 
-This comparison cannot be made for Mrk 1216 because no extended kinematic data are available.  
+\subsection{NGC 1332}
+The morphology of NGC 1332 (Figure \ref{fig:n1332}) is very similar to that of NGC 3115, 
+with the ellipticity profile indicating the presence of an intermediate-scale disc, 
+although in this case no nuclear component was identified from our photometric analysis. 
+The authors of this paper were not able to find any extended kinematic profile or map 
+for this galaxy in the literature. 
+The data within the innermost $6~\rm arcsec$ were excluded from the fit 
+because possibly affected by the presence of a partially depleted core.
+The spheroidal component of NGC 1332 is modelled with a S\'ersic profile. 
+The highly inclined intermediate-scale disc is better described with a $n<1$ S\'ersic profile 
+(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
+rather than with an exponential function \citep{pastrav2013a}. 
+Our galaxy decomposition suggests that NGC 1332 is a spheroid-dominated galaxy, 
+with a spheroid-to-total ratio of $0.95$.
+\cite{rusli2011} did not identify the extent of the intermediate-scale disc, 
+and proposed a model featuring a S\'ersic-bulge and a large-scale exponential-disc, 
+with a spheroid-to-total ratio of $0.43$.
+Based on such bulge-disc decomposition, they concluded that NGC 1332 is a disc dominated lenticular galaxy 
+which is displaced from the (black hole mass)-(spheroid luminosity) correlation of \cite{marconihunt2003} 
+by an order of magnitude along the black hole mass direction. 
+In Section \ref{sec:mm} we show that, according to our decomposition, 
+NGC 1332 lies within the $1\sigma$ scatter about the (black hole mass)-(spheroid stellar mass) correlation 
+for early-type galaxies.
+
+\subsection{Mrk 1216}
+Although the disc in the galaxy Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
+the velocity map \citep{yildirim2015} proves the presence of a fast rotating component 
+at least within three galaxy half-light radii ($\sim 3 \times 5~\rm arcsec$). 
+The ellipticity profile (Figure \ref{fig:m1216}) indicates the presence of an intermediate-scale disc. 
+In addition, a nuclear disc is identified from the change in slope of the ellipticity profile ($R_{\rm maj} \sim 1 - 2 \rm~arcsec$) 
+and from a clear feature in the fourth harmonic profile (not shown here). 
+We modelled the surface brightness profile of Mrk 1216 (Figure \ref{fig:m1216}) with a S\'ersic-spheroid, 
+an intermediate-sized exponential-disc, and a nuclear exponential-disc.
+
+\subsection{Other galaxies}
 Our models with an intermediate-sized disc embedded within a larger spheroidal component, 
 plus an additional nuclear component when one is present, 
-match the observed light distribution, and explain both the kinematic maps15 (when available) 
-and the ellipticity profiles, of three other ellicular galaxies 
-for which a direct measurement of their central supermassive black hole mass is available: 
-NGC 1271; NGC 1277; and NGC 1332.  
-Past models that ``forcedly'' described these ellicular galaxies with an inner bulge 
-encased within a large-scale disc 
-typically required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
-Such three-component models (bulge + disc + envelope) reduce the spheroid luminosity by a factor of 2-3, 
-and underestimate the size of the spheroid by a factor of 10.
+match the observed light distribution, and explain both the extended kinematic maps (when available, \citealt{arnold2014}) and the ellipticity profiles, 
+of other galaxies for which a direct measurement of their central supermassive black hole mass is available: 
+NGC 821; NGC 1271; NGC 1277; NGC 3377; and NGC 4697. 
+Our isophotal analysis and galaxy decompositions for NGC 1271 and NGC 1277 will be presented in 
+Graham, Savorgnan \& Ciambur (\emph{in prep.}) and Graham et al.~(\emph{in prep.}), respectively, 
+while the galaxies NGC 821, NGC 3377 and NGC 4697 have been analysed in Savorgnan \& Graham (\emph{submitted}).
 
@@
 \includegraphics[width=1.05\columnwidth]{images/n3115_decomposition.pdf}
-\caption{}
+\caption{The galaxy NGC 3115. 
+The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
+obtained by dividing the image by a Gaussian-smoothed version of itself. 
+The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
+and the ellipticity profile, $\epsilon$, 
+along the major-axis, $R_{\rm maj}$. 
+The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
+The color lines represent the individual (PSF-convolved) model components: 
+red = S\'ersic (spheroid), blue = exponential (disc), gray = Gaussian ring. 
+The residual profile (data $-$ model) is shown as $\Delta \mu$. 
+The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
+$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
 \label{fig:n3115}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.49\columnwidth]{images/n1332_image}
+\includegraphics[width=0.49\columnwidth]{images/n1332_unsharp} \\
+\includegraphics[width=1.03\columnwidth]{images/n1332_decomposition.pdf}
+\caption{The galaxy NGC 1332. 
+The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
+obtained by dividing the image by a Gaussian-smoothed version of itself. 
+The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
+and the ellipticity profile, $\epsilon$, 
+along the major-axis, $R_{\rm maj}$. 
+The black points are the observed data, which extend out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
+The empty points are data excluded from the fit.   
+The color lines represent the individual (PSF-convolved) model components: 
+red = S\'ersic (spheroid), blue = exponential (disc). 
+The residual profile (data $-$ model) is shown as $\Delta \mu$. 
+The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
+$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
+}
+\label{fig:n1332}
 \end{center}
@@
 \includegraphics[width=1.05\columnwidth]{images/mrk1216_decomposition.pdf}
-\caption{}
-\label{fig:m1216}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.49\columnwidth]{images/n1271_image}
-\includegraphics[width=0.49\columnwidth]{images/n1271_unsharp} \\
-\includegraphics[width=1.05\columnwidth]{images/n1271_decomposition.pdf}
-\caption{}
+\caption{The galaxy Mrk 1216. 
+The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right), 
+obtained by dividing the image by a Gaussian-smoothed version of itself. 
+The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
+and the ellipticity profile, $\epsilon$, 
+along the major-axis, $R_{\rm maj}$. 
+The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$).
+The color lines represent the individual (PSF-convolved) model components: 
+red = S\'ersic (spheroid), blue = exponential (disc). 
+The residual profile (data $-$ model) is shown as $\Delta \mu$. 
+The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
+$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
+}
 \label{fig:m1216}
@@
 \label{sec:impl}
+Past models that ``forcedly'' described intermediate-scale disc galaxies using an inner bulge 
+encased within a large-scale disc 
+commonly required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
+Such three-component models (bulge + disc + envelope) typically reduce the spheroid luminosity by a factor of $3-4$, 
+and underestimate the size of the spheroid by a factor of $6-10$, 
+although more ``extreme'' cases can be found. \\
+\cite{lasker2014data} fit the galaxy NGC 3115 with a bulge + disc + envelope, 
+and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$; 
+we described this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
+and obtained a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. \\
+\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
+which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total ratio of $0.24$; 
+our model consists of a spheroid + intermediate-scale disc + nuclear component, 
+and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
+\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
+and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total ratio of $0.35$; 
+our model with a spheroid + intermediate-scale disc + nuclear disc 
+returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total ratio of $0.94$. \\
+\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
+and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total ratio of $0.19$; 
+our decomposition consists of a spheroid + intermediate-scale disc, 
+with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
+The galaxy NGC 4697 represents an ``extreme'' case. 
+\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
+and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total ratio of $0.08$; 
+we described NGC 4697 using a spheroid + intermediate-scale disc + inner disc model, 
+and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total ratio of $0.89$.
 
-\subsection{mm diagram}
+\subsection{The black hole -- spheroid correlation}
+\label{sec:mm}
+Inaccurate measurements of the spheroid-to-total ratio of galaxies can impact galaxy scaling relations. 
+Recently, a handful of intermediate-scale disc galaxies have been claimed to host \emph{{\"u}ber-massive} black holes, 
+i.e.~their central supermassive black hole has been reported to be 
+over-massive compared to expectations from the spheroid luminosity (or stellar mass).
+This is the case for the galaxies Mrk 1216 (for which only an upper limit on its black hole mass has been published, 
+\citealt{yildirim2015}), NGC 1271 \citep{walsh2015}, 
+NGC 1277 \citep{vandenbosch2012,yildirim2015} and NGC 1332 \citep{rusli2011}.
+In addition to these, also the elliptical galaxy NGC 4291 has been claimed to be a $\sim$$3.6\sigma$ outlier 
+above the (black hole mass)-(spheroid mass) scaling relation \citep{bogdan2012}. 
 Obviously, having both the black hole mass and the spheroid mass correct is important 
-for placing systems in the (black hole mass)-(spheroid stellar mass) diagram. 
-For early-type galaxies, the spheroid luminosity and the total galaxy luminosity 
-can be used to predict the black hole mass with the same level of accuracy \citep{savorgnan2015}. 
+for placing systems in the (black hole mass)-(spheroid mass) diagram. 
+For early-type galaxies, the spheroid luminosity and the galaxy luminosity 
+can be used to predict the black hole mass with the same level of accuracy\footnote{However, 
+when considering all galaxies (early- and late-type) irrespective of their morphological type, 
+the correlation of the black hole mass with the spheroid luminosity is better than that with the galaxy luminosity.} 
+(Savorgnan et al.~\emph{submitted}). 
 If a galaxy hosts a black hole that is over-massive compared to expectations from the spheroid luminosity, 
-but whose mass is normal compared to expectations from the total galaxy luminosity, 
+but whose mass is normal compared to expectations from the galaxy luminosity, 
 one should wonder whether the spheroid luminosity might have been underestimated 
 due to an inaccurate spheroid/disc decomposition. 
-Indeed, none of the five ellicular galaxies mentioned here is a noticeable outlier 
-in the (black hole mass)-(total galaxy luminosity) diagram \citep{savorgnan2015}. 
-For the first time, Figure 4 reveals that when ellicular galaxies are properly modeled, 
-they no longer appear as extreme outliers in the (black hole mass)-(spheroid stellar mass) diagram.
+Indeed, none of the five galaxies mentioned before (Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 4291) is a noticeable outlier 
+in the (black hole mass)-(galaxy luminosity) diagram. 
+In Figure \ref{fig:mm} we show the location of these five galaxies in the (black hole mass)-(spheroid stellar mass) diagram 
+for early-type galaxies of Savorgnan et al.~(\emph{submitted}). 
+Figure 4 was populated using a galaxy decomposition technique extensively described in Savorgnan \& Graham (\emph{submitted}). 
+Briefly, we obtained Spitzer/IRAC $3.6~\rm \mu m$ images for 45 early-type galaxies 
+which already had a dynamical detection of their black hole mass. 
+We modelled their one-dimensional surface brightness profiles with a combination of analytic functions, using one function per galaxy component. 
+Spheroid luminosities were converted into stellar masses using individual, but almost constant mass-to-light ratios ($\sim$$0.6$, \citealt{meidt2014-MNRAS}). 
+In addition, we show the galaxies Mrk 1216, NGC 1271 and NGC 1277, which were not a part of the original sample of 45.
+For the galaxy NGC 1271, we use the black hole mass measurement and the mass-to-light ratio obtained by \cite{walsh2015}. 
+The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition 
+of Graham, Savorgnan \& Ciambur (\emph{in prep.}),  
+who used an archived \emph{HST} image taken with the WFC3 and the near-infrared \emph{F160W} filter. 
+For the galaxy NGC 1277, we use the black hole mass measurement obtained by \cite{vandenbosch2012} 
+and the mass-to-light ratio obtained by \cite{martinnavarro2015}. 
+The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition of Graham et al.~(\emph{in prep.}), 
+who used an archived \emph{HST} image taken with the Advanced Camera for Surveys (\emph{ACS}) and the \emph{F550M} filter. 
+For the galaxy Mrk 1216, we use the upper limit on the black hole mass and the mass-to-light ratio obtained by \cite{yildirim2015}. 
+The luminosity of the spheroidal component of this galaxy comes from our one-dimensional spheroid/disc decomposition (Figure \ref{fig:m1216}).
+For the first time, Figure \ref{fig:mm} reveals that when these five galaxies are properly modeled, 
+they no longer appear as extreme outliers above the (black hole mass)-(spheroid stellar mass) correlation for early-type galaxies, 
+i.e.~they all reside well within a $3\sigma$ deviation from the correlation.
 
-\subsection{compact massive sph}
-Acknowledging the correct structure of ellicular galaxies is also important to properly understand their origin. 
+{\bf change: This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
+but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
+and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
+used to describe the coevolution of spheroids and their central supermassive black holes. }
+
+\subsection{Origin of compact massive galaxies}
+Acknowledging the correct structure of intermediate-scale disc galaxies is also important to properly understand their origin. 
 According to the current paradigm of cosmological structure evolution, 
-the genesis of massive early-type galaxies is characterized by two distinct phases: ''in-situ'' and ''ex-situ''. 
-The first phase takes place in a young Universe (within its first 4 billion years), 
+the genesis of massive early-type galaxies is characterized by two distinct phases: ``in-situ'' and ``ex-situ''. 
+The first phase takes place in a young Universe (within its first $4~\rm Gyr$), 
 when cold gas inflows produced short and intense bursts of star formation that created the cores of galaxies. 
-These naked and compact cores, named ''red nuggets''25, have been observed26 at high-redshift with sizes of 1-2 kpc.
-In the second phase (last 10 billion years), stellar discs and stellar envelopes 
-were accreted around these primordial galaxy cores and assembled the external parts of galaxies on scales of 2-20 kpc. 
-Today's Universe is populated by an abundance of compact, massive spheroids27, 
-with the same physical properties -- mass and compactness -- as the high-redshift red nuggets. 
+These naked and compact cores, named ``red nuggets'' \citep{damjanov2009}, have been observed at high-redshift with sizes of $1-2~\rm kpc$ \citep{vandokkum2008}.
+In the second phase (last $10~\rm Gyr$), stellar discs and stellar envelopes 
+were accreted around these primordial galaxy cores and assembled the external parts of galaxies on scales of $2-20~\rm kpc$. 
+Today's Universe is populated by an abundance of compact, massive spheroids, 
+with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{GDS2015}. 
 Some of these local compact massive spheroids are encased within a large-scale disc, 
 that is to say they are the bulges of some lenticular and spiral galaxies. 
-Over the last 10 billion years their spheroids have evolved by growing a relatively flat disc -- 
+Over the last $10~\rm Gyr$ their spheroids have evolved by growing a relatively flat disc -- 
 rather than a three-dimensional envelope -- 
 which has increased the galaxy size but preserved the bulge compactness. 
-The other compact massive spheroids of today's Universe belong to some ellicular galaxies. 
-Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact ellicular galaxies 
-with purely old (>10 billion years) stellar populations. 
-These galaxies have undergone the lowest degree of disc growth.
+The other compact massive spheroids of today's Universe belong to some intermediate-scale disc galaxies. 
+Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact galaxies 
+with intermediate-scale discs and purely old ($>10~\rm Gyr$) stellar populations. 
+These galaxies have undergone the lowest degree of disc growth. \\
 In addition to the observational clues as to the actual physical components in ellicular galaxies, 
 one can reason on other grounds as to why these compact galaxies are not comprised of an inner bulge 
-plus large-scale disc plus outer envelope5,28,6. If they were such three-component systems, 
-then one would have two possibilities. 
-The first possibility is that these galaxies were already fully assembled 10 billion years ago; 
+plus large-scale disc plus outer envelope. 
+If they were such three-component systems, then one would have two possibilities. 
+The first possibility is that these galaxies were already fully assembled $10~\rm Gyr$ ago; 
 this would explain their old stellar populations, 
-but it would also imply that their discs and envelopes had already formed during the first 4 billion years of the Universe, 
+but it would also imply that their discs and envelopes had already formed during the first $4~\rm Gyr$ of the Universe, 
 in disagreement with the current cosmological picture. 
-The second possibility is that only their inner bulges (with sizes of 0.1-0.2 kpc, 
-according to past decompositions) originated in the first 4 billion years 
+The second possibility is that only their inner bulges (with sizes of $0.1-0.2~\rm kpc$, 
+according to past decompositions) originated in the first $4~\rm Gyr$ 
 and they subsequently accreted a substantial disc and envelope. 
 If this was correct, then we would observe high-redshift, star-like, naked bulges with stellar masses 
-within a factor of a few times the currently observed red nuggets but sizes which are 10 times smaller. 
+within a factor of a few times the currently observed red nuggets but sizes which are $10$ times smaller. 
 However, a dramatically different expectation is reached 
 if one considers these galaxies as spheroid-dominated systems with an intermediate-scale disc; 
-in this case, both the galaxy size and the spheroid size are compact (1-2 kpc). 
+in this case, both the galaxy size and the spheroid size are compact ($1-2~\rm kpc$). 
 This implies that, among the local descendants of the high-redshift red nuggets, 
 the compact ellicular galaxies have undergone the lowest degree of disc growth. 
-That is, the bulk of a compact ellicular galaxy quickly assembled ''in-situ'' in a very young Universe 
-and experienced very little evolution over the last 10 billion years.
+That is, the bulk of a compact ellicular galaxy quickly assembled ``in-situ'' in a very young Universe 
+and experienced very little evolution over the last $10~\rm Gyr$.
 
@@
 \includegraphics[width=\columnwidth]{images/mm.pdf}
-\caption{Early-type galaxies: black hole mass plotted against spheroid stellar mass for 42 galaxies (black) plus the galaxies Mrk 1216, NGC 1271, NGC 1277, NGC 1332, NGC 3115, and NGC 4291.
-The black solid line is the bisector linear regression for early-type galaxies24.
-The dashed lines mark the 1sigma and 3sigma deviations, where sigma (0.51 dex) is the total rms scatter about the correlation in the black hole mass direction.
-The red color is used for five ellicular galaxies, (Mrk 1216, for which only an upper limit on its black hole mass has been reported) [4], NGC 1271 [6], NGC 1277 [5, 4], NGC 1332 [7], and NGC 4291 [29]), that were claimed to be extreme outliers in this diagram.
-All reside within a 3sigma deviation from the correlation when using their correct spheroid mass.
-For NGC 1277, we show the previously reported spheroid stellar mass [5] in gray.}
+\caption{Early-type (elliptical + lenticular) galaxies: 
+black hole mass plotted against spheroid stellar mass for 48 galaxies. 
+The black solid line is the bisector linear regression for all galaxies except Mrk 1216, NGC 1271 and NGC 1277. 
+The dashed lines mark the $1\sigma$ and $3\sigma$ deviations, 
+where $\sigma$ ($0.51$ dex) is the total \emph{rms} scatter about the correlation in the black hole mass direction. 
+The red stars mark four intermediate-scale disc galaxies (Mrk 1216, NGC 1271, NGC 1277 and NGC 1332) and one elliptical galaxy (NGC 4291) 
+that were claimed to be extreme outliers in this diagram. 
+All five reside within a $3\sigma$ deviation from the correlation when using their correct spheroid mass. 
+For NGC 1277, we show the previously reported spheroid stellar mass \citep{vandenbosch2012} in gray. 
+The green color is used to show the location of four other intermediate-scale disc galaxies mentioned in Section \ref{sec:impl}.}
 \label{fig:mm}
@@
 \section{Acknowledgments}
-%GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. \\
 % referee thank you!!
-This research was supported by Australian Research Council funding through grants
-DP110103509 and FT110100263.
-%This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
-%on-board the Spitzer Space Telescope, 
-%which is operated by the Jet Propulsion Laboratory, 
-%California Institute of Technology under a contract with NASA.
-%This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
-%which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
-%under contract with the National Aeronautics and Space Administration.
+This research was supported by Australian Research Council funding through grant FT110100263. 
+GS is grateful to Matteo Fossati, Luca Cortese and Giuseppe Gavazzi for useful comments and discussion. 
+This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC-MNRAS} on-board the Spitzer Space Telescope, 
+which is operated by the Jet Propulsion Laboratory, California Institute of Technology under a contract with NASA, 
+and also on observations made with the NASA/ESA Hubble Space Telescope, 
+and obtained from the Hubble Legacy Archive, 
+which is a collaboration between the Space Telescope Science Institute (STScI/NASA), 
+the Space Telescope European Coordinating Facility (ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).
+This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
+which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
+under contract with the National Aeronautics and Space Administration.
 

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/cls/psf.py

@@ -1,37 +1,0 @@
-from cls import PsfFunction
-import numpy as np
-
-def createPsf(Settings):
-    
-    if (Settings.observation == 'spitzer3.6um'): 
-
-        gaussianPsf = PsfFunction()
-        gaussianPsf.name = 'gaussian'
-        gaussianPsf.gaussianFWHM = 1.6648 * Settings.pxlToArcsec 
-        
-        moffatPsf = PsfFunction()
-        moffatPsf.name = 'moffat'
-        moffatPsf.moffatAlpha = (1.61467/(2*np.sqrt(2**(1/4.39)-1)) ) * Settings.pxlToArcsec  # alpha = fwhm / (2 * sqrt(2**(1/beta) - 1) )
-        moffatPsf.moffatBeta = 4.39  
-        
-#        psfList = [gaussianPsf, moffatPsf]
-        psfList = [moffatPsf]
-
-    if (Settings.observation == 'm1216'):
-    
-        gaussianPsf = PsfFunction()
-        gaussianPsf.name = 'gaussian'
-        gaussianPsf.gaussianFWHM = 2.3 * Settings.pxlToArcsec 
-        
-        psfList = [gaussianPsf]
-
-    gaussianSmoothing = PsfFunction()
-    gaussianSmoothing.name = 'gaussian'
-    #gaussianSmoothing.gaussianFWHM = 60 * 2.3548 * Settings.pxlToArcsec  # m31
-    gaussianSmoothing.gaussianFWHM = 5 * 2.3548 * Settings.pxlToArcsec    # m81 n5128
-    #gaussianSmoothing.gaussianFWHM = 3 * 2.3548 * Settings.pxlToArcsec    # n4945
-    
-    return psfList, gaussianSmoothing
-
-
-

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/cls/settings.py

@@ -1,44 +1,0 @@
-#### default settings
-
-class Settings:
-    
-    #performFit = False
-    performFit = True
-    
-    #axisFit = 'maj'
-    #axisFit = 'eq'
-    #axisFit = 'min'
-            
-    #fitConvolvedModel = False
-    #plotConvolvedFinalModel = False
-    #plotConvolvedComponent = False
-    fitConvolvedModel = True
-    plotConvolvedFinalModel = True
-    plotConvolvedComponent = True
-    
-    useErrorsInFit = False
-    #useErrorsInFit = True
-    
-    smoothing = False
-    #smoothing = True
-    
-    observation = 'spitzer3.6um'
-    #observation = 'm1216' 
-        
-    if (observation == 'n1277'):
-        pxlToArcsec = 0.05
-        zeropoint = 24.851 # hst for n1277
-    
-    if (observation == 'm1216'):
-        pxlToArcsec = 0.12825
-        zeropoint = 24.6949 # Vega
-    
-    if (observation == 'spitzer3.6um'):
-        pxlToArcsec = 1.2232836
-        zeropoint = 17.25585 #spitzer 3.6 um
-
-    colordict = {'sersic' : 'red', 'tsersic' : 'red', 'disc' : 'blue', 'gaussian' : 'green', 'psf' : 'purple', 'ferrer' : 'lightblue', 'tdisc' : 'blue', 'gring' : 'grey', 'psfwing' : 'purple'}
-    
-    #oversamplingStep = 0.2 # pixels
-    
-#     fitResultsFileName = '/Users/gsavorgnan/Dropbox/giulia_e_basta/ProFitErole1.0.1/results/1DfitResults.dat'

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/instruments/b_n.py

@@ -1,59 +1,0 @@
-import numpy as np
-from scipy.special import gammainc
-import math
-from decimal import Decimal
-from scipy.optimize import minimize_scalar
-
-######## SETTINGS ##########################
-
-precisionResid = 0.000001
-
-######## COMPUTE b_n #######################
-
-def b_nResid(k, x):
-        
-        out = gammainc(k, x) - 0.50000000000000
-        return out
-
-def computeb_n(n):
-
-        k = 2*n
-		
-	b=2*n - 0.333
-	if (b<0):
-		b=0.000
-		
-	zero  = b_nResid(k, b)	
-	increment = 1.000
-	
-	while (abs(zero) > precisionResid):
-		
-		zero  = b_nResid(k, b)
-		
-		bplus = b + increment
-		bminus = b - increment
-		if (bminus<0):
-			bminus = 0.000
-		
-		zeroplus = b_nResid(k, bplus)	
-		zerominus = b_nResid(k, bminus)
-		
-		if (abs(zeroplus) < precisionResid):
-			b = bplus
-			break
-       		elif (abs(zerominus) < precisionResid):
-			b = bminus
-			break
-       		else:
-			if ( abs(zeroplus) < abs(zero) ):
-				b = bplus
-			elif ( abs(zerominus) < abs(zero) ):
-				b = bminus
-			increment = increment/2.	
-				
-        return b
-	
-
-
-
-

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/instruments/fitResult.py

@@ -1,115 +1,0 @@
-import numpy as np
-
-from modelComponents.sersic import computeSersicParameters
-from modelComponents.disc import computeDiscParameters
-from modelComponents.gaussian import computeGaussianParameters
-from modelComponents.moffat import computeMoffatParameters
-
-############# PRINT FIT RESULT ##############
-
-def printFitResult(fit, componentslist, psfFunction):
-	
-	print '--------------------------------------------'
-	print 'Results from fit:'
-	print '--------------------------------------------'
-	print 'Number of iterations:', fit.nfev
-	print 'Chisq: ', fit.chisqr
-	print 'Reduced chisq: ', fit.redchi
-	print 'N_free: ', fit.nfree
-	##print 'Delta: ', deltarms   # [sum (residuals**2)/(N-N_dof)]**0.5
-
-	if (fit.success):
-		for component in componentslist:
-			namepar1 = 'par1_' + str(component.number)
-			namepar2 = 'par2_' + str(component.number)
-			namepar3 = 'par3_' + str(component.number)
-			namepar4 = 'par4_' + str(component.number)
-			print 'Component ' + str(component.number) + ': ' + component.name + '.'
-			
-			if (component.name == 'sersic'):
-				r_e = fit.params[namepar1].value
-				mu_e = fit.params[namepar2].value
-				n = fit.params[namepar3].value				
-				b, m_tot = computeSersicParameters(mu_e, r_e, n) 
-				print 'R_e [arcsec] = ', ("{0:.2f}".format(r_e)), '+/-', ("{0:.2f}".format(fit.params[namepar1].stderr)), '	[initial value =', component.parameters[namepar1].value, ']'
-				print 'mu_e [mag/arcsec^2] = ', ("{0:.2f}".format(mu_e)), '+/-', ("{0:.2f}".format(fit.params[namepar2].stderr)), '	 [initial value =', component.parameters[namepar2].value, ']'
-				print 'n = ', ("{0:.2f}".format(n)), '+/-', ("{0:.2f}".format(fit.params[namepar3].stderr)), '       [initial value =', component.parameters[namepar3].value, ']'
-				print 'b_n = ', ("{0:.2f}".format(b))
-				print 'm_tot [mag] = ', ("{0:.2f}".format(m_tot))
-			if (component.name == 'disc'):
[…]

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/instruments/output.py

@@ -1,166 +1,0 @@
-import numpy as np
-import sys
-from scipy.special import gamma
-import os.path
-
-from modelComponents.sersic import computeSersicParameters
-from modelComponents.disc import computeDiscParameters
-from modelComponents.gaussian import computeGaussianParameters
-from modelComponents.moffat import computeMoffatParameters
-from modelComponents.ferrer import computeFerrerParameters
-from modelComponents.gaussRing import computeGaussRingParameters
-
-def produceOutputFile(Settings, galaxy, axisFit, psfFunction, sampling, componentslist, finalparams, deltarms):
-    
-    outputFileName = galaxy + '_' + axisFit + '_' + psfFunction.name + '_' + sampling + '_par_SM.dat'
-    outputFile = open(outputFileName, 'w')
-    sys.stdout = outputFile
-    
-    flux_total_galaxy = 0
-    
-    for component in componentslist:
-        namepar1 = 'par1_' + str(component.number)
-        namepar2 = 'par2_' + str(component.number)
-        namepar3 = 'par3_' + str(component.number)
-        namepar4 = 'par4_' + str(component.number)
-            
-        if (component.name == 'sersic'):
-            r_e = finalparams[namepar1].value
-            mu_e = finalparams[namepar2].value
-            n = finalparams[namepar3].value
-            b, m_tot = computeSersicParameters(mu_e, r_e, n)
-            print component.number,
-            print component.name,
-            print("{0:.4f}".format(r_e)),
-            print("{0:.4f}".format(mu_e)),
-            print("{0:.4f}".format(n)),
-            print '-99.9999',
-            print("{0:.4f}".format(m_tot))
-        if (component.name == 'disc'):
-            h= finalparams[namepar1].value
-            mu_0 = finalparams[namepar2].value
-            m_tot = computeDiscParameters(mu_0, h) 
-            print component.number,
-            print component.name,
-            print("{0:.4f}".format(h)),
-            print("{0:.4f}".format(mu_0)),
-            print '-99.9999',
-            print '-99.9999',
-            print("{0:.4f}".format(m_tot)) 
-        if (component.name == 'gaussian'):
-            fwhm = finalparams[namepar1].value
-            mu_0 = finalparams[namepar2].value
-            m_tot = computeGaussianParameters(fwhm, mu_0)
-            print component.number,
-            print component.name,
-            print("{0:.4f}".format(fwhm)),
[…]

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/instruments/residual.py

@@ -1,17 +1,0 @@
-from instruments.model import buildModel
-
-############# RESIDUAL ##############
-
-def residual(params, x, good_x, y_meas, good_y_meas, good_y_err, goodIndexes, componentslist, psfFunction, fitConvolvedModel, psfwing_02pxscale_datatab, psfwing_logscale_datatab, Settings, sampling, gaussianSmoothing):
-	
-	y_model, good_y_model = buildModel(params, componentslist, x, goodIndexes, psfFunction, fitConvolvedModel, psfwing_02pxscale_datatab, psfwing_logscale_datatab, Settings, sampling, gaussianSmoothing)
-	
-	if Settings.useErrorsInFit:
-		#res = abs(good_y_meas-good_y_model)/good_y_err
-		res = (good_y_meas-good_y_model)**2/good_y_err**2
-	else:
-		#res = abs(good_y_meas-good_y_model)
-		res = (good_y_meas-good_y_model)**2
-	return res	
-	
-	

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/modelComponents/disc.py

@@ -1,26 +1,0 @@
-from convolution.psfConvolution import doPsfConvolution
-import numpy as np
-from instruments import b_n
-from scipy.special import gammainc, gamma
-
-
-def buildDisc(x, params, component, psfFunction, convolve, zeropoint):  
-
-	namepar1 = 'par1_' + str(component.number) # h
-	namepar2 = 'par2_' + str(component.number) # mu_0
-	y_disc_sb = (params[namepar2].value) + 1.085736*x/(params[namepar1].value)
-	y_disc = 10**(0.4*(zeropoint - y_disc_sb))
-	
-	if (convolve):
-		y_disc = doPsfConvolution(y_disc, psfFunction, x)
-		
-	return y_disc
-
-def computeDiscParameters(mu_0, h):
-	r_e = 1.678*h
-	mu_e = mu_0 + 1.821865
-	n = 1
-	b=1.678
-	m_tot = mu_e - 5*np.log10(r_e) - 2.5*np.log10(2*np.pi*n*np.exp(b)*gamma(2*n)/(b**(2*n)))
-	
-	return m_tot

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/modelComponents/ferrer.py

@@ -1,27 +1,0 @@
-from convolution.psfConvolution import doPsfConvolution
-import numpy as np
-from scipy import special #.hyp2f1
-
-def buildFerrer(x, params, component, psfFunction, convolve, zeropoint):
-
-	namepar1 = 'par1_' + str(component.number) # r_out
-	namepar2 = 'par2_' + str(component.number) # mu_0
-	namepar3 = 'par3_' + str(component.number) # alpha
-	namepar4 = 'par4_' + str(component.number) # beta
-	
-	x_i = x[x<params[namepar1].value]
-	x_e = x[x>=params[namepar1].value]
-	
-	y_ferrer_i = 10**(zeropoint/2.5) * (10**(-params[namepar2].value/2.5)) * ( 1 - (x_i/params[namepar1].value)**(2 - (params[namepar4].value)) )**(params[namepar3].value)
-	y_ferrer_e = x_e * 0.0
-	y_ferrer = np.concatenate((y_ferrer_i, y_ferrer_e))
-			
-	if (convolve):
-		y_ferrer = doPsfConvolution(y_ferrer, psfFunction, x)
-	return y_ferrer
-
-def computeFerrerParameters(r_out, mu_0, alpha, beta):
-	
-	m_tot = mu_0 - 2.5 * np.log10(2 * np.pi * r_out**2 * (0.5 * special.hyp2f1(-alpha, 2/(2-beta), (2-beta+2)/(2-beta), 1)))
-	
-	return m_tot

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/modelComponents/gaussian.py

@@ -1,20 +1,0 @@
-from convolution.psfConvolution import doPsfConvolution
-import numpy as np
-
-
-def buildGaussian(x, params, component, psfFunction, convolve, zeropoint):
-
-	namepar1 = 'par1_' + str(component.number) # fwhm
-	namepar2 = 'par2_' + str(component.number) # mag
-	y_gauss = 10**(zeropoint/2.5) * (10**(-params[namepar2].value/2.5) * np.exp(-x**2/(2*(params[namepar1].value/2.3548)**2)))
-	#print y_gauss
-	if (convolve):
-		y_gauss = doPsfConvolution(y_gauss, psfFunction, x)
-	return y_gauss
-
-def computeGaussianParameters(fwhm, mu_0):
-
-	sigma = fwhm/2.3548
-	m_tot = mu_0 - 2.5*np.log10(2*np.pi*(sigma)**2)
-	
-	return m_tot

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/n3115.py

@@ -1,507 +1,0 @@
-# at the moment, works well in pixels
-
-import numpy as np
-from lmfit import minimize, Parameters, report_fit
-import inspect
-from scipy.ndimage.filters import gaussian_filter1d, correlate1d
-from scipy.special import gammainc, gamma
-import sys
-import pylab
-import matplotlib.pyplot as plt
-import shutil
-
-# local folders of project
-
-from reading.dataFileNames import readDataFileNames
-from reading.ellipseOutput import readEllipseOutput
-from reading.inputModel import readInputModel
-from reading.excludeData import readExcludedData
-from reading.bestFitModel import readBestFitModel
-
-from cls.cls import *
-from cls.settings import *
-from cls.psf import *
-
-from instruments.fitResult import printFitResult
-from instruments.model import buildModel
-from instruments.output import *
-
-from instruments.residual import residual
-from instruments import b_n
-#from instruments.plotting import *
-
-from modelComponents.disc import buildDisc
-from modelComponents.ferrer import buildFerrer
-from modelComponents.gaussian import buildGaussian
-from modelComponents.psf import buildPsf
-from modelComponents.psfWing import buildPsfWing
-from modelComponents.sersic import buildSersic
-from modelComponents.truncDisc import buildTruncDisc
-from modelComponents.truncSersic import buildTruncSersic
-from modelComponents.gaussRing import buildGaussRing
-from instruments.model import buildModel
-
-from convolution.psfConvolution import doPsfConvolution
-
-
-from matplotlib.pyplot import fill_between
-from matplotlib.backends.backend_pdf import PdfPages
-import matplotlib.ticker as ticker
-from matplotlib.ticker import MultipleLocator, FormatStrFormatter
-from matplotlib import rc, font_manager
-
-from textwrap import wrap
-
-
-
-#################################################### 
-
-moffatPsf = PsfFunction()
-moffatPsf.name = 'moffat'
-moffatPsf.moffatAlpha = (1.61467/(2*np.sqrt(2**(1/4.39)-1)) ) * Settings.pxlToArcsec  # alpha = fwhm / (2 * sqrt(2**(1/beta) - 1) )
-moffatPsf.moffatBeta = 4.39  
[…]

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/reading/excludeData.py

@@ -1,20 +1,0 @@
-def readExcludedData(txt, Settings):
-    
-    excludedRangeList = None
-    
-    try:
-        
-        excludedRangeList = [] 
-        data = open(txt)
-    
-        for line in data:
-            
-            pt1 = float(line.split()[0]) * Settings.pxlToArcsec
-            pt2 = float(line.split()[1]) * Settings.pxlToArcsec
-            excludedRange = [pt1, pt2]	
-            excludedRangeList.append(excludedRange)
-    except:
-        None
-        
-    return excludedRangeList
-    

### 2015-09-01 python_codes/paper_figures/lentiptical/n3115/reading/inputModel.py

@@ -1,168 +1,0 @@
-from lmfit import Parameters
-import numpy as np
-
-from cls.cls import *
-
-from reading.ellipseOutput import readEllipseOutput
-
-def readInputModel(txt, equivalentAxisFit, Settings):
-
-	psfwing_02pxscale_datatab = None
-	psfwing_logscale_datatab = None
-
-	componentslist = []
-	params = Parameters()
-	
-	data = open(txt)
-	for line in data:
-		if (line[0] != '#'):
-			comp = Component()
-			comp.number = int(line.split()[0])
-			comp.name = str(line.split()[1])
-			
-			#components with 4 parameters
-			if (comp.name == 'ferrer'):
-			
-				par1name = 'par1_' + str(line.split()[0])
-				par2name = 'par2_' + str(line.split()[0])
-				par3name = 'par3_' + str(line.split()[0])
-				par4name = 'par4_' + str(line.split()[0])
-			
-				p1 = (par1name, float(line.split()[2]), True, 0.01, None, None)     # r_out 
-				if (line.split()[3] == 'False'):
-					p1 = (par1name, float(line.split()[2]), False, 0.01, None, None) 
-				p2 = (par2name, float(line.split()[4]), True, None, 35.0, None)     # mu_0 
-				if (line.split()[5] == 'False'):
-					p2 = (par2name, float(line.split()[4]), False, None, 35.0, None)    		
-				p3 = (par3name, float(line.split()[6]), True, 0.01, 4.0, None)     # alpha
-				if (line.split()[7] == 'False'):
-					p3 = (par3name, float(line.split()[6]), False, 0.01, 4.0, None) 	
-				p4 = (par4name, float(line.split()[8]), True, 0.01, 1.999, None)     # beta
-				if (line.split()[9] == 'False'):
-					p4 = (par4name, float(line.split()[8]), False, 0.01, 1.999, None) 	
-						
-				comp.parameters.add_many(p1, p2, p3, p4)  
-				params.add_many(p1, p2, p3, p4)
-	
-				componentslist.append(comp)
-			
-			if (comp.name == 'tsersic'):
-			
-				par1name = 'par1_' + str(line.split()[0])
-				par2name = 'par2_' + str(line.split()[0])
-				par3name = 'par3_' + str(line.split()[0])
-				par4name = 'par4_' + str(line.split()[0])
-			
[…]

### 2015-09-04 papers/ellicular/ellicular.tex
friday

@@
 The color lines represent the individual (PSF-convolved) model components: 
-red = S\'ersic (spheroid), blue = exponential (disc). 
+red = S\'ersic (spheroid), blue = S\'ersic (disc). 
 The residual profile (data $-$ model) is shown as $\Delta \mu$. 
@@
 
-{\bf change: This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
-but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
-and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
-used to describe the coevolution of spheroids and their central supermassive black holes. }
+%{\bf change: This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
+%but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
+%and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
+%used to describe the coevolution of spheroids and their central supermassive black holes. }
 

### 2015-09-17 papers/ellicular/ellicular.tex
nemo

@@
 
-\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes}
+%\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes}
+\title[Ellicular galaxies]{Ellicular galaxies and their (non {\"u}ber-massive) black holes}
 
@@
 Here we show that these rejected models correctly reproduce the photometric and kinematic properties of a class of early-type galaxy 
-with intermediate-scale disc. 
-Intermediate-scale discs have often been confused with large-scale discs, 
-and as a consequence the disc luminosities have been considerably overestimated 
+%with intermediate-scale disc. 
+%Intermediate-scale discs have often been confused with large-scale discs, 
+%and as a consequence the disc luminosities have been considerably overestimated 
+%and their spheroid luminosities underestimated. 
+intermediate between that of elliptical and lenticular galaxies, and which we name ellicular galaxies. 
+Ellicular galaxies have often been confused with lenticular galaxies, and as a consequence their disc luminosities have been considerably overestimated 
 and their spheroid luminosities underestimated. 
-%intermediate between that of elliptical and lenticular galaxies, and which we name ellicular galaxies. 
-%Ellicular galaxies have often been confused with lenticular galaxies, and as a consequence their disc luminosities have been considerably overestimated 
-%and their spheroid luminosities underestimated. 
 This has recently led to some surprising conclusions, 
-such as the claim that a number of intermediate-scale disc galaxies (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
+such as the claim that a number of ellicular galaxies (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
 host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
-When intermediate-scale disc galaxies are properly modeled, 
+When ellicular galaxies are properly modeled, 
 they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram, 
@@
 and (iii) a galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid. 
-%We refer to the last case as an ellicular galaxy. 
+We refer to the last case as an ellicular galaxy. 
 In general, stellar discs are intrinsically flat and circular; 
@@
 more recently, intermediate-scale discs were all but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
-However, the class of early-type galaxies with intermediate-scale discs has been missed by many galaxy modellers, 
+However, the class of ellicular galaxies has been missed by many galaxy modellers, 
 who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
@@
 rather than a dichotomy of nuclear versus large-scale discs. 
-The presence of intermediate-scale discs also blurs the distinction between elliptical and lenticular galaxies.
-%and creates the need for a new subclass to help bridge the divide. 
+The presence of intermediate-scale discs also blurs the distinction between elliptical and lenticular galaxies 
+and creates the need for a new subclass to help bridge the divide. 
 The existence of such discs is not only important for our understanding of disc growth in general, 
@@
 The right panel displays an elliptical galaxy with (an optional) nuclear stellar disc. 
-The middle panel presents an early-type galaxy with an intermediate-sized disc embedded in the spheroid. }
+The middle panel presents an early-type galaxy with an intermediate-sized disc embedded in the spheroid. 
+We refer to the last case as an ellicular galaxy.}
 \label{fig:model}
@@
 \label{sec:gal}
-Three examples of early-type galaxies with intermediate-scale discs are Mrk 1216, NGC 1332, and NGC 3115. 
+Three examples of ellicular galaxies are Mrk 1216, NGC 1332, and NGC 3115. 
 In the following Sections, we present a photometric analysis of these three galaxies, 
@@
 under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
-was performed before {\tt isofit} \citep{ciambur2015} was conceived or available.} \citep{taskellipse}. 
+was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
+After {\tt isofit} was recently developed and implemented in IRAF, 
+we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
+We then repeated the analysis and checked that this change does not significantly alter our results. 
+In fact, although {\tt isofit} provides a more accurate description of the isophotes in presence of an inclined disc, 
+the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
+therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} are small. } 
+\citep{taskellipse}. 
 The galaxy isophotes were modelled with a series of concentric ellipses, 
@@
 (at semimajor-axis lenght $R_{\rm maj} \sim 15~\rm arcsec$).
-The surface brightness profile (Figure \ref{fig:n3115}) is well described with a S\'ersic-spheroid \citep{sersic1963},  
-an intermediate-sized exponential-disc, and a Gaussian-ring.
+The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
+The highly inclined intermediate-scale disc is better fit with a $n<1$ S\'ersic profile 
+(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
+rather than with an exponential function, 
+as explained by \cite{pastrav2013a}. 
+The nuclear ring is modelled with a Gaussian function.
 
@@
 because possibly affected by the presence of a partially depleted core.
-The spheroidal component of NGC 1332 is modelled with a S\'ersic profile. 
-The highly inclined intermediate-scale disc is better described with a $n<1$ S\'ersic profile 
-(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
-rather than with an exponential function \citep{pastrav2013a}. 
+The surface brightness profile of NGC 1332 is well described with a S\'ersic-spheroid plus
+a $n<1$ S\'ersic-disc. 
 Our galaxy decomposition suggests that NGC 1332 is a spheroid-dominated galaxy, 
@@
 by an order of magnitude along the black hole mass direction. 
-In Section \ref{sec:mm} we show that, according to our decomposition, 
+However, in Section \ref{sec:mm} we show that, according to our decomposition, 
 NGC 1332 lies within the $1\sigma$ scatter about the (black hole mass)-(spheroid stellar mass) correlation 
@@
 The color lines represent the individual (PSF-convolved) model components: 
-red = S\'ersic (spheroid), blue = exponential (disc), gray = Gaussian ring. 
+red = S\'ersic (spheroid), blue = S\'ersic (disc), gray = Gaussian ring. 
 The residual profile (data $-$ model) is shown as $\Delta \mu$. 
@@
 \label{sec:impl}
-Past models that ``forcedly'' described intermediate-scale disc galaxies using an inner bulge 
+Past models that ``forcedly'' described ellicular galaxies using an inner bulge 
 encased within a large-scale disc 
@@
 Inaccurate measurements of the spheroid-to-total ratio of galaxies can impact galaxy scaling relations. 
-Recently, a handful of intermediate-scale disc galaxies have been claimed to host \emph{{\"u}ber-massive} black holes, 
+Recently, a handful of ellicular galaxies have been claimed to host \emph{{\"u}ber-massive} black holes, 
 i.e.~their central supermassive black hole has been reported to be 
@@
 for placing systems in the (black hole mass)-(spheroid mass) diagram. 
-For early-type galaxies, the spheroid luminosity and the galaxy luminosity 
-can be used to predict the black hole mass with the same level of accuracy\footnote{However, 
-when considering all galaxies (early- and late-type) irrespective of their morphological type, 
+\emph{For early-type galaxies, the spheroid luminosity and the galaxy luminosity 
+can be used to predict the black hole mass with the same level of accuracy\footnote{Note that 
+\cite{lasker2014anal} reported that the spheroid luminosity and the galaxy luminosity are equally good tracers of the black hole mass 
+irrespective of the galaxy morphological type, but their sample of 35 galaxies contained only 4 spiral galaxies. 
+However, using a sample of 45 early-type and 17 spiral galaxies, 
+Savorgnan et al.~(\emph{submitted}) shows that, when considering all galaxies irrespective of their morphological type, 
 the correlation of the black hole mass with the spheroid luminosity is better than that with the galaxy luminosity.} 
-(Savorgnan et al.~\emph{submitted}). 
+(Savorgnan et al.~submitted). 
 If a galaxy hosts a black hole that is over-massive compared to expectations from the spheroid luminosity, 
@@
 one should wonder whether the spheroid luminosity might have been underestimated 
-due to an inaccurate spheroid/disc decomposition. 
+due to an inaccurate spheroid/disc decomposition. }
 Indeed, none of the five galaxies mentioned before (Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 4291) is a noticeable outlier 
@@
 \subsection{Origin of compact massive galaxies}
-Acknowledging the correct structure of intermediate-scale disc galaxies is also important to properly understand their origin. 
+Acknowledging the correct structure of ellicular galaxies is also important to properly understand their origin. 
 According to the current paradigm of cosmological structure evolution, 
@@
 which has increased the galaxy size but preserved the bulge compactness. 
-The other compact massive spheroids of today's Universe belong to some intermediate-scale disc galaxies. 
-Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact galaxies 
-with intermediate-scale discs and purely old ($>10~\rm Gyr$) stellar populations. 
+The other compact massive spheroids of today's Universe belong to some ellicular galaxies. 
+Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact ellicular galaxies 
+with purely old ($>10~\rm Gyr$) stellar populations. 
 These galaxies have undergone the lowest degree of disc growth. \\
@@
 
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width=\columnwidth]{images/}
-%\caption{}
-%\label{fig:}
-%\end{center}
-%\end{figure}
+\subsection{Ellicular galaxies in the Hubble grid}
+The existence of the oft-overlooked, intermediate-scale discs presented here exposes a likely continuum of disc sizes in early-type galaxies 
+as opposed to a dichotomy of nuclear discs versus large-scale discs. 
+The presence of these intermediate-scale discs also blurs the distinction between elliptical (E) and lenticular (S0) galaxies 
+and arguably creates the need for a new subclass which bridges this divide.  
+While expanding the galaxy nomenclature beyond ellipticals with possible nuclear discs, and lenticulars with large-scale discs, 
+to include something like {\it elliculars} with intermediate-scale discs will be helpful 
+for distinguishing among the different early-type galaxies with different disk scale-lengths, 
+it should be remembered that just as portions of the electromagnetic spectrum are labelled according to their different wavelengths, 
+there is still an underlying continuum.  
+Similarly, binning early-type galaxies as either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact that a continuum exists.  
+Importantly, in the case of early-type galaxies with intermediate scale discs, 
+this particular rotation-classification depends on the galaxy's radial range probed.  
+There is thus a need for more than two bins (E vs.~S0, or SR vs.~FR). \\
+The existence of intermediate-scale discs is not only important for our understanding of disc growth in general, 
+but accounting for such components impacts upon our broader understanding of galaxy structure.  
+It has recently been argued \citep{graham2014review} that the classification scheme for elliptical galaxies 
+should not be their apparent axis ratio as seen on the plane of the sky, 
+but rather early-type galaxies should be quantified by their spheroid-to-total flux ratio, 
+with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies.   
+While spiral galaxies display a range of spheroid-to-total flux ratios from 0 to $\sim$3/4, 
+lenticular galaxies display a range from $\sim$3/4 to $\sim$0.1 (see \citealt{laurikainen2010}).   
+The spheroid-to-total flux ratio is an important quantity, and its broad range observed in lenticular galaxies 
+has led to a resurgence of \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976}) Hubble comb, 
+in which both late-type galaxies (i.e.~spiral galaxies) and lenticular galaxies form the arms of an expanded Hubble tuning fork, 
+with an additional arm for disc galaxies hosting anaemic spiral patterns (see \citealt{cappellari2011kmdr-MNRAS} and \citealt{kormendybender2012}).  
+However because every spiral Hubble type (e.g.~Sa, Sb, Sc) has a broad range of spheroid-to-total ratio 
+(e.g.~\citealt{grahamworley2008}, and references therein), 
+and because this information is not captured by the Hubble comb, 
+a grid of spiral type (predominantly determined by the spiral arms) versus spheroid-to-total ratio is also useful for classifying galaxies.   
+In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale discs in such a Hubble grid \citep{graham2014review}, 
+revealing how they are related to the other galaxies.  
+Aside from the pure elliptical galaxies, each galaxy type displays a range of spheroid-to-total flux ratio.  
+Rather than a scheme in which the spiral morphological type (a, b, c, etc.) changes if the spheroid-to-total ratio changes (as in the Hubble comb), 
+here the galaxy type is linked to the nature and winding of the spiral arms which has been the primary criteria used 
+to classify spiral galaxies over the last half century \citep{sandage1961}.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\columnwidth]{images/Hubble-grid-2/Hubblegrid.pdf}
+\caption{The Hubble grid \citep{graham2014review}, 
+which uses the mean pitch angle of the arms in spiral galaxies to define their morphological type. 
+Ellicular (ES) galaxies are intermediate between elliptical (E) and lenticular (S0) galaxies. }
+\label{fig:grid}
+\end{center}
+\end{figure}
 

### 2015-09-17 python_codes/decomposition/ProFitErole1.0.1/profiterole.py

@@ -249,9 +249,9 @@ def performFitAndPlot(excludedRangeList, galaxy, axisFit, psfFunction, sampling,
 ########## MAIN BODY HERE ############
 
 #samplingList = ['comb', 'log' ]
-samplingList = ['log',  'comb']
+#samplingList = ['log',  'comb']
 #samplingList = ['log' ]
-#samplingList = ['comb']
+samplingList = ['comb']
 #samplingList = ['1lin', 'log']
 
 suffixDict = {'comb' : '_combscale', '02lin' : '_linscale02px', '05lin' : '_linscale05px', 'log' : '_logscale', '1lin' : '_linscale1px', '2lin' : '_linscale2px'}
@@ -259,8 +259,8 @@ suffixDict = {'comb' : '_combscale', '02lin' : '_linscale02px', '05lin' : '_lins
 
 psfList, gaussianSmoothing = createPsf(Settings)
 
-axisFitList = ['maj', 'eq']
-# axisFitList = ['maj']
+#axisFitList = ['maj', 'eq']
+axisFitList = ['maj']
 #axisFitList = ['eq']
 
 prefixEllipseOutput, galaxy, skyRMS = readDataFileNames('init.1dfit')

### 2015-09-18 papers/ellicular/ellicular.tex
fri

@@
 %\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes}
-\title[Ellicular galaxies]{Ellicular galaxies and their (non {\"u}ber-massive) black holes}
+\title[Ellicular galaxies]{Ellicular galaxies and their (non over-massive) black holes}
 
@@
 \begin{abstract}
-The classification early-type galaxy includes both elliptically-shaped and lenticular galaxies, 
-with the latter composed of a spheroid, or bulge, of stars encased within a larger, but flatter, stellar disc. 
-Theoretically, the spheroid-to-disc flux ratio can assume any positive value. 
-However, several studies only consider spheroid/disc decompositions 
-in which the disc neatly dominates over the spheroid at large galaxy radii -- creating an inner bulge -- 
-and they reject decompositions if the disc remains embedded within the spheroid, labeling them as ``unphysical''. 
-Here we show that these rejected models correctly reproduce the photometric and kinematic properties of a class of early-type galaxy 
-%with intermediate-scale disc. 
-%Intermediate-scale discs have often been confused with large-scale discs, 
-%and as a consequence the disc luminosities have been considerably overestimated 
-%and their spheroid luminosities underestimated. 
-intermediate between that of elliptical and lenticular galaxies, and which we name ellicular galaxies. 
-Ellicular galaxies have often been confused with lenticular galaxies, and as a consequence their disc luminosities have been considerably overestimated 
-and their spheroid luminosities underestimated. 
+The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies, 
+with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
+Theoretically, the spheroid-to-disc flux ratio can assume any positive value,  
+but in practice studies often consider only spheroid/disc decompositions 
+in which the disc neatly dominates over the spheroid at large galaxy radii, 
+creating an inner ``bulge'' as observed in most spiral galaxies. 
+Here we reveal that decompositions in which the disc remains embedded within the spheroid, labelled by some as ``unphysical'',  
+correctly reproduce both the photometric and kinematic properties of a class of early-type galaxy 
+intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
+Ellicular galaxies have often been confused with lenticular galaxies, 
+such that %their disc luminosities have been considerably overestimated 
+their spheroid luminosities have been considerably underestimated. 
 This has recently led to some surprising conclusions, 
-such as the claim that a number of ellicular galaxies (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
+such as the claim that a number of ellicular galaxies (e.g.~Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
 host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
-When ellicular galaxies are properly modeled, 
-they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram, 
-thereby resolving previous anomalies. 
+We show that when ellicular galaxies are correctly modeled, 
+they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
 This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
@@
 gas rich mergers and halo accretion events 
-(e.g.~\citealt{khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}). 
-A thorough review can be found in \citet{combes2014arX,combes2014pro}.
+(e.g.~\citealt{whiterees1978,khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}), 
+and a thorough review can be found in \citet{combes2014arX,combes2014pro}.
 On the other hand, intermediate-sized discs have not received the same level of attention 
-as their nuclear and large-scale homologues and,  
-in some cases, they have even been labelled as something ''unphysical''. 
+as their nuclear and large-scale homologues and 
+they have at times been labelled and rejected as ''unphysical'' when detected. 
 Here we report on the photometric and kinematical signatures of these intermediate-sized stellar discs 
-and the impact this has on the important (black hole mass)-to-(spheroid stellar mass) ratio %, $M_{\rm BH}/M_{*,sph}$, 
+and the impact this has on the (black hole mass)-to-(spheroid stellar mass) ratio %, $M_{\rm BH}/M_{*,sph}$, 
 which is used to constrain galaxy evolution models. \\
@@
 This can help one distinguish them from the more spherically-shaped spheroids. 
-Identifying the extent of these discs with respect to their spheroid can however be subtle. 
+Identifying the radial extent of these discs with respect to the spheroid can however be subtle. 
 Two-dimensional kinematic maps represent an important diagnostic tool for this purpose. 
@@
 whereas other central fast rotators become slow rotators in their outer regions.
-On the one hand, a specific angular momentum profile that is rapidly increasing beyond $1-2$ half-light radii 
-is a signature of a large-scale disc. 
-On the other hand, a specific angular momentum profile that increases up to $1-2$ half-light radii and declines beyond that point 
+A specific angular momentum profile that is rapidly increasing beyond $1-2$ half-light radii 
+is a signature of a large-scale disc, 
+while a specific angular momentum profile that increases up to $1-2$ half-light radii and then declines beyond that point 
 indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 
@@
 ($\epsilon = 1 - b/a$, where $b/a$ is the ratio of minor-to-major axis length) of 
-(i) a lenticular galaxy, comprised of a large-scale disc and a relatively smaller encased bulge, 
+(i) a lenticular galaxy comprised of a large-scale disc and a relatively smaller encased bulge, 
 (ii) an elliptical galaxy with a nuclear stellar disc, 
@@
 whereas a radial decrease of ellipticity signifies the opposite case. \\
-The awareness that many ``elliptical'' galaxies actually contain embedded stellar discs 
+The awareness that many so-called ``elliptical'' galaxies actually contain stellar discs 
 dates back at least three decades 
@@
 donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998} and, 
-more recently, intermediate-scale discs were all but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
+more recently, intermediate-scale discs were anything but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
 However, the class of ellicular galaxies has been missed by many galaxy modellers, 
@@
 as is observed with spiral galaxies. 
-This unspoken bias has led to the rejection of many spheroid/disc decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
+This bias has led to the rejection of many spheroid/disc decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
 Unsurprisingly, studies affected by this bias have not obtained spheroid/disc decompositions with a spheroid-to-total ratio larger than $0.6 - 0.8$ 
@@
 In the following Sections, we present a photometric analysis of these three galaxies, 
-and we compare our results with the kinematical analysis (when) available from the literature. 
+and we compare our results with the kinematical analysis available from the literature for Mrk 1216 and NGC 3115. 
 For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
@@
 taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
-Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (\emph{submitted}).
+Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (2015).
 Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
@@
 allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
-The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
+The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan 
+and described in Savorgnan \& Graham (2015).
 We modelled the light profiles with a combination of PSF-convolved analytic functions, 
@@
 The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
-Less obvious is the extent of such disc, if one only relies on a visual inspection of the galaxy image. 
-The ellipticity profile is consistent with the presence of an intermediate-scale disc. 
-Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large scale disc, 
+Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
+The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
+Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
 because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
-whereas the rotation significantly drops at larger radii.  
-The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a fain edge-on nuclear ring, 
+and the rotation significantly drops at larger radii.  
+The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
 which can also be spotted as a small peak in the ellipticity profile 
-(at semimajor-axis lenght $R_{\rm maj} \sim 15~\rm arcsec$).
+(at semimajor-axis length $R_{\rm maj} \sim 15~\rm arcsec$).
 The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
-The highly inclined intermediate-scale disc is better fit with a $n<1$ S\'ersic profile 
+The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
 (the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
@@
 The nuclear ring is modelled with a Gaussian function. 
+In comparison,
 
@@
 Inaccurate measurements of the spheroid-to-total ratio of galaxies can impact galaxy scaling relations. 
-Recently, a handful of ellicular galaxies have been claimed to host \emph{{\"u}ber-massive} black holes, 
+Recently, a handful of ellicular galaxies have been claimed to host \emph{over-massive} black holes, 
 i.e.~their central supermassive black hole has been reported to be 

### 2015-09-18 papers/mbhn/mbhn.tex
fri

@@
 \section{Introduction}
+The empirical \cite{sersic1963,1968} model has been demonstrated to provide adequate description 
+of the light distribution of the stellar spheroidal component of galaxies, 
+yet its physical intepretation has remained unknown for decades.
+
+origin of L-n \\
+M-L + L-n ... M-n \\
+M-C and M-n \\
+s+11 v+12 b+12 \\
+my paper \\
+paper I and II \\
 

### 2015-09-21 papers/ellicular/ellicular.tex
chesonno

@@
 gas rich mergers and halo accretion events 
-(e.g.~\citealt{whiterees1978,khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}), 
+(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}), 
 and a thorough review can be found in \citet{combes2014arX,combes2014pro}.
@@
 (e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}). \\
-The existence of intermediate-scale stellar discs reveals a continuum of disc sizes, 
-rather than a dichotomy of nuclear versus large-scale discs. 
-The presence of intermediate-scale discs also blurs the distinction between elliptical and lenticular galaxies 
-and creates the need for a new subclass to help bridge the divide. 
-The existence of such discs is not only important for our understanding of disc growth in general, 
-but accounting for such structure will impact our understanding of galaxy structure, 
-with important consequences for galaxy scaling relations. 
-%It has recently been argued that the classification scheme for elliptical galaxies should not be their apparent axis ratio as seen on the plane of the sky, 
-%but instead their spheroid-to-total ratio, with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies \citep{graham2014review}.
+{\bf This paper is structured as follows. 
+In Section \ref{sec:gal} we present a detailed photometric analysis of three ellicular galaxies (Mrk 1216, NGC 1332, and NGC 3115) 
+and we briefly describe other five ellicular galaxies (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697). 
+We compare our photometric analysis with the kinematical information available from the literature 
+and explain the differences between our galaxy models and past decompositions. 
+In Section \ref{sec:mm} we explore the important implications this has for the (black hole mass)-(spheroid stellar mass) diagram. 
+In Section \ref{sec:disc} we discuss our results in terms of galaxy evolution 
+and we update the Hubble grid with the inclusion of ellicular galaxies. }
 
@@
 We then repeated the analysis and checked that this change does not significantly alter our results. 
-In fact, although {\tt isofit} provides a more accurate description of the isophotes in presence of an inclined disc, 
+In fact, although {\tt isofit} provides a more accurate description of the isophotes in the presence of an inclined disc, 
 the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
-therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} are small. } 
+therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} 
+are small for these two galaxies. } 
 \citep{taskellipse}. 
@@
 as explained by \cite{pastrav2013a}. 
-The nuclear ring is modelled with a Gaussian function. 
-In comparison,
+The nuclear ring is modelled with a Gaussian function. \\
+In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
+and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
+We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
+and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
+We have used both kinematical information and ellipticity profiles, 
+together with the surface brightness profile, 
+to obtain a physically consistent and meaningful model.
 
@@
 with the ellipticity profile indicating the presence of an intermediate-scale disc, 
-although in this case no nuclear component was identified from our photometric analysis. 
-The authors of this paper were not able to find any extended kinematic profile or map 
+although in this case no nuclear component is evident. 
+We were not able to find any extended kinematic profile or map 
 for this galaxy in the literature. 
 The data within the innermost $6~\rm arcsec$ were excluded from the fit 
-because possibly affected by the presence of a partially depleted core.
+because, according to our galaxy decomposition, they are possibly affected by the presence of a partially depleted core.
 The surface brightness profile of NGC 1332 is well described with a S\'ersic-spheroid plus
-a $n<1$ S\'ersic-disc. 
+an $n<1$ S\'ersic-disc. 
 Our galaxy decomposition suggests that NGC 1332 is a spheroid-dominated galaxy, 
-with a spheroid-to-total ratio of $0.95$.
-\cite{rusli2011} did not identify the extent of the intermediate-scale disc, 
+with a spheroid-to-total ratio of $0.95$. \\
+\cite{rusli2011} did not identify the restricted extent of the intermediate-scale disc, 
+as revealed by the ellipticity profile, 
 and proposed a model featuring a S\'ersic-bulge and a large-scale exponential-disc, 
 with a spheroid-to-total ratio of $0.43$.
-Based on such bulge-disc decomposition, they concluded that NGC 1332 is a disc dominated lenticular galaxy 
+Based on their bulge/disc decomposition, they concluded that NGC 1332 is a disc dominated lenticular galaxy 
 which is displaced from the (black hole mass)-(spheroid luminosity) correlation of \cite{marconihunt2003} 
@@
 for early-type galaxies. 
+{\bf We also note that the majority of galaxies with an elevated stellar velocity dispersion ($\sigma > 270~\rm km~s^{-1}$) 
+are core-S\'ersic galaxies \citep{graham2003coresersicmodel,trujillo2004coresersicmodel,dullograham2014cores}, 
+i.e.~they have a partially depleted core which has been identified from high-resolution photometric data. 
+NGC 1332 has $\sigma = 320~\rm km~s^{-1}$, but, 
+based on their decomposition of \emph{HST} imaging, \cite{rusli2011} did not find a core in this galaxy. 
+However, the identification of a partially depleted core is model dependent, 
+that is, only a correct galaxy decomposition can confirm or rule out the presence of a core. 
+Our galaxy decomposition (Figure \ref{fig:n1332}) suggests that NGC 1332 is in fact a core-S\'ersic galaxy. 
+Since we did not use high-resolution photometric data, 
+we refrain from a firm conclusion, 
+but we caution that a re-analysis of the \emph{HST} data -- by taking into account the correct radial extent of the intermediate-scale disc --
+may indeed reveal the presence of a core.}
 
@@
 Although the disc in the galaxy Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
-the velocity map \citep{yildirim2015} proves the presence of a fast rotating component 
-at least within three galaxy half-light radii ($\sim 3 \times 5~\rm arcsec$). 
-The ellipticity profile (Figure \ref{fig:m1216}) indicates the presence of an intermediate-scale disc. 
-In addition, a nuclear disc is identified from the change in slope of the ellipticity profile ($R_{\rm maj} \sim 1 - 2 \rm~arcsec$) 
-and from a clear feature in the fourth harmonic profile (not shown here). 
+the velocity map \citep{yildirim2015} reveals the presence of a fast rotating component 
+within three galaxy half-light radii ($\sim 3 \times 5~\rm arcsec$). 
+The ellipticity profile (Figure \ref{fig:m1216}), 
+which extends out to five half-light radii, indicates the presence of an intermediate-scale disc. 
+In addition, a nuclear disc is identified from the change in slope of the ellipticity profile ($R_{\rm maj} \sim 1 - 2 \rm~arcsec$), 
+from the unsharp mask, 
+and from a clear feature in the $B4$ fourth harmonic profile (not shown here). 
 We modelled the surface brightness profile of Mrk 1216 (Figure \ref{fig:m1216}) with a S\'ersic-spheroid, 
@@
 match the observed light distribution, and explain both the extended kinematic maps (when available, \citealt{arnold2014}) and the ellipticity profiles, 
-of other galaxies for which a direct measurement of their central supermassive black hole mass is available: 
+of five additional galaxies for which a direct measurement of their central supermassive black hole mass is available: 
 NGC 821; NGC 1271; NGC 1277; NGC 3377; and NGC 4697. 
 Our isophotal analysis and galaxy decompositions for NGC 1271 and NGC 1277 will be presented in 
-Graham, Savorgnan \& Ciambur (\emph{in prep.}) and Graham et al.~(\emph{in prep.}), respectively, 
-while the galaxies NGC 821, NGC 3377 and NGC 4697 have been analysed in Savorgnan \& Graham (\emph{submitted}).
+Graham, Savorgnan \& Ciambur (\emph{in prep.}) and Graham et al.~(2015), respectively, 
+while the galaxies NGC 821, NGC 3377 and NGC 4697 have been analysed in Savorgnan \& Graham (2015).
+
+\subsubsection{NGC 1271}
+{\bf \cite{walsh2015} explored a three-component decomposition for NGC 1271 
+and identified the galaxy bulge with the innermost of the three components, 
+having a half-light radius of $0.61~\rm arcsec$ and a bulge-to-total ratio of $0.23$; 
+our model features a spheroid + intermediate-scale disc, 
+with a spheroid half-light radius of $3.3~\rm arcsec$ and a spheroid-to-total ratio of $0.67$. }
+
+\subsubsection{NGC 1277}
+\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
+which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total ratio of $0.24$; 
+our model consists of a spheroid + intermediate-scale disc + nuclear component, 
+and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total ratio of $0.79$.
+
+\subsubsection{NGC 3377}
+\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
+and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total ratio of $0.35$; 
+our model with a spheroid + intermediate-scale disc + nuclear disc 
+returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total ratio of $0.94$.
+
+\subsubsection{NGC 821}
+\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
+and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total ratio of $0.19$; 
+our decomposition consists of a spheroid + intermediate-scale disc, 
+with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total ratio of $0.79$.
+
+\subsubsection{NGC 4697}
+The galaxy NGC 4697 represents an ``extreme'' case. 
+\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
+and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total ratio of $0.08$; 
+we described NGC 4697 using a spheroid + intermediate-scale disc + nuclear disc model, 
+and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total ratio of $0.89$. \\
+
+Past models that ``forcedly'' described ellicular galaxies using an inner bulge 
+encased within a large-scale disc 
+commonly required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
+Such three-component models (bulge + disc + envelope) typically reduce the spheroid luminosity by a factor of $3-4$, 
+and underestimate the size of the spheroid by a factor of $6-10$, 
+although more ``extreme'' cases can be found.
 
@@
 \includegraphics[width=1.05\columnwidth]{images/n3115_decomposition.pdf}
-\caption{The galaxy NGC 3115. 
+\caption{NGC 3115. 
 The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
@@
 \includegraphics[width=1.03\columnwidth]{images/n1332_decomposition.pdf}
-\caption{The galaxy NGC 1332. 
-The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
-obtained by dividing the image by a Gaussian-smoothed version of itself. 
-The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
-and the ellipticity profile, $\epsilon$, 
-along the major-axis, $R_{\rm maj}$. 
-The black points are the observed data, which extend out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
+\caption{NGC 1332.
+Same as Figure \ref{fig:n3115}, except for the following. 
+The surface brightness profile extends out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
 The empty points are data excluded from the fit. 
-The color lines represent the individual (PSF-convolved) model components: 
-red = S\'ersic (spheroid), blue = S\'ersic (disc). 
-The residual profile (data $-$ model) is shown as $\Delta \mu$. 
-The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
-$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
+%The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
+%obtained by dividing the image by a Gaussian-smoothed version of itself. 
+%The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
+%and the ellipticity profile, $\epsilon$, 
+%along the major-axis, $R_{\rm maj}$. 
+%The black points are the observed data, which extend out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
+%The empty points are data excluded from the fit.   
+%The color lines represent the individual (PSF-convolved) model components: 
+%red = S\'ersic (spheroid), blue = S\'ersic (disc). 
+%The residual profile (data $-$ model) is shown as $\Delta \mu$. 
+%The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
+%$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
 }
@@
 \includegraphics[width=1.05\columnwidth]{images/mrk1216_decomposition.pdf}
-\caption{The galaxy Mrk 1216. 
-The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right), 
-obtained by dividing the image by a Gaussian-smoothed version of itself. 
-The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
-and the ellipticity profile, $\epsilon$, 
-along the major-axis, $R_{\rm maj}$. 
-The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$).
+\caption{Mrk 1216. 
+Same as Figure \ref{fig:n3115}, except for the following. 
+The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right).
+The surface brightness profile extends out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$). 
 The color lines represent the individual (PSF-convolved) model components:
 red = S\'ersic (spheroid), blue = exponential (disc).
-The residual profile (data $-$ model) is shown as $\Delta \mu$. 
-The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
-$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
+%The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right),
+%obtained by dividing the image by a Gaussian-smoothed version of itself.
+%The bottom plots display the best-fit model of the surface brightness profile, $\mu$,
+%and the ellipticity profile, $\epsilon$,
+%along the major-axis, $R_{\rm maj}$.
+%The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$).
+%The color lines represent the individual (PSF-convolved) model components:
+%red = S\'ersic (spheroid), blue = exponential (disc).
+%The residual profile (data $-$ model) is shown as $\Delta \mu$.
+%The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations.
+%$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
 }
@@
 
-\section{Implications}
-\label{sec:impl}
-Past models that ``forcedly'' described ellicular galaxies using an inner bulge 
-encased within a large-scale disc 
-commonly required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
-Such three-component models (bulge + disc + envelope) typically reduce the spheroid luminosity by a factor of $3-4$, 
-and underestimate the size of the spheroid by a factor of $6-10$, 
-although more ``extreme'' cases can be found. \\
-\cite{lasker2014data} fit the galaxy NGC 3115 with a bulge + disc + envelope, 
-and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$; 
-we described this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
-and obtained a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. \\
-\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
-which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total ratio of $0.24$; 
-our model consists of a spheroid + intermediate-scale disc + nuclear component, 
-and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
-\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
-and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total ratio of $0.35$; 
-our model with a spheroid + intermediate-scale disc + nuclear disc 
-returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total ratio of $0.94$. \\
-\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
-and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total ratio of $0.19$; 
-our decomposition consists of a spheroid + intermediate-scale disc, 
-with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
-The galaxy NGC 4697 represents an ``extreme'' case. 
-\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
-and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total ratio of $0.08$; 
-we described NGC 4697 using a spheroid + intermediate-scale disc + inner disc model, 
-and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total ratio of $0.89$.
-
-\subsection{The black hole -- spheroid correlation}
+\section{The black hole -- spheroid correlation}
 \label{sec:mm}
@@
 Recently, a handful of ellicular galaxies have been claimed to host \emph{over-massive} black holes, 
-i.e.~their central supermassive black hole has been reported to be 
-over-massive compared to expectations from the spheroid luminosity (or stellar mass).
+i.e.~the mass of their central supermassive black hole has been reported to be significantly larger 
+than what is expected from the galaxy's spheroid luminosity (or stellar mass).
 This is the case for the galaxies Mrk 1216 (for which only an upper limit on its black hole mass has been published, 
@@
 NGC 1277 \citep{vandenbosch2012,yildirim2015} and NGC 1332 \citep{rusli2011}.
-In addition to these, also the elliptical galaxy NGC 4291 has been claimed to be a $\sim$$3.6\sigma$ outlier 
+In addition to these, the elliptical galaxy NGC 4291 has also been claimed to be a $\sim$$3.6\sigma$ outlier 
 above the (black hole mass)-(spheroid mass) scaling relation \citep{bogdan2012}. 
 Obviously, having both the black hole mass and the spheroid mass correct is important 
-for placing systems in the (black hole mass)-(spheroid mass) diagram. 
-\emph{For early-type galaxies, the spheroid luminosity and the galaxy luminosity 
+for placing systems in the (black hole mass)-(spheroid mass) diagram. \\
+\emph{At present, for early-type galaxies, the spheroid luminosity and the galaxy luminosity 
 can be used to predict the black hole mass with the same level of accuracy\footnote{Note that 
@@
 However, using a sample of 45 early-type and 17 spiral galaxies, 
-Savorgnan et al.~(\emph{submitted}) shows that, when considering all galaxies irrespective of their morphological type, 
+Savorgnan et al.~(2015) shows that, when considering all galaxies irrespective of their morphological type, 
 the correlation of the black hole mass with the spheroid luminosity is better than that with the galaxy luminosity.} 
-(Savorgnan et al.~submitted). 
+(Savorgnan et al.~2015). 
 If a galaxy hosts a black hole that is over-massive compared to expectations from the spheroid luminosity, 
@@
 due to an inaccurate spheroid/disc decomposition. }
-Indeed, none of the five galaxies mentioned before (Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 4291) is a noticeable outlier 
+Indeed, none of the five galaxies just mentioned (Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 4291) is a noticeable outlier 
 in the (black hole mass)-(galaxy luminosity) diagram. 
-In Figure \ref{fig:mm} we show the location of these five galaxies in the (black hole mass)-(spheroid stellar mass) diagram 
-for early-type galaxies of Savorgnan et al.~(\emph{submitted}). 
-Figure 4 was populated using a galaxy decomposition technique extensively described in Savorgnan \& Graham (\emph{submitted}). 
+In Figure \ref{fig:mm} we show the location of these five galaxies in the updated (black hole mass)-(spheroid stellar mass) diagram 
+for early-type galaxies from Savorgnan et al.~(2015). 
+Figure \ref{fig:mm} was populated using the galaxy decomposition technique shown here 
+and extensively described in Savorgnan \& Graham (2015). 
 Briefly, we obtained Spitzer/IRAC $3.6~\rm \mu m$ images for 45 early-type galaxies 
 which already had a dynamical detection of their black hole mass. 
-We modelled their one-dimensional surface brightness profiles with a combination of analytic functions, using one function per galaxy component. 
-Spheroid luminosities were converted into stellar masses using individual, but almost constant mass-to-light ratios ($\sim$$0.6$, \citealt{meidt2014-MNRAS}). 
-In addition, we show the galaxies Mrk 1216, NGC 1271 and NGC 1277, which were not a part of the original sample of 45.
-For the galaxy NGC 1271, we use the black hole mass measurement and the mass-to-light ratio obtained by \cite{walsh2015}. 
-The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition 
-of Graham, Savorgnan \& Ciambur (\emph{in prep.}),  
-who used an archived \emph{HST} image taken with the WFC3 and the near-infrared \emph{F160W} filter. 
+We modelled their one-dimensional surface brightness profiles with a combination of analytic functions, 
+using one function per galaxy component. 
+Spheroid luminosities were converted into stellar masses using individual, 
+but almost constant mass-to-light ratios ($\sim$$0.6$, \citealt{meidt2014-MNRAS}). \\
+In Figure \ref{fig:mm}, we show the galaxies Mrk 1216, NGC 1271 and NGC 1277, 
+which were not a part of the original sample of 45 early-type galaxies.
+For the galaxy NGC 1271, we use the black hole mass measurement 
+and the stellar mass-to-light ratio obtained by \cite{walsh2015}. 
+%The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition 
+%of Graham, Savorgnan \& Ciambur (\emph{in prep.}),  
+%who used an archived \emph{HST} image taken with the WFC3 and the near-infrared \emph{F160W} filter. 
 For the galaxy NGC 1277, we use the black hole mass measurement obtained by \cite{vandenbosch2012} 
-and the mass-to-light ratio obtained by \cite{martinnavarro2015}. 
-The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition of Graham et al.~(\emph{in prep.}), 
-who used an archived \emph{HST} image taken with the Advanced Camera for Surveys (\emph{ACS}) and the \emph{F550M} filter. 
-For the galaxy Mrk 1216, we use the upper limit on the black hole mass and the mass-to-light ratio obtained by \cite{yildirim2015}. 
-The luminosity of the spheroidal component of this galaxy comes from our one-dimensional spheroid/disc decomposition (Figure \ref{fig:m1216}).
-For the first time, Figure \ref{fig:mm} reveals that when these five galaxies are properly modeled, 
+and the stellar mass-to-light ratio obtained by \cite{martinnavarro2015}. 
+%The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition of Graham et al.~(\emph{in prep.}), 
+%who used an archived \emph{HST} image taken with the Advanced Camera for Surveys (\emph{ACS}) and the \emph{F550M} filter. 
+For the galaxy Mrk 1216, we use the upper limit on the black hole mass 
+and the stellar mass-to-light ratio obtained by \cite{yildirim2015}. 
+%The luminosity of the spheroidal component of this galaxy comes from our one-dimensional spheroid/disc decomposition (Figure \ref{fig:m1216}).
+For the first time, Figure \ref{fig:mm} reveals that when the four ellicular galaxies Mrk 1216, NGC 1271, NGC 1277, NGC 1332, 
+and the elliptical galaxy NGC 4291 are properly modeled, 
 they no longer appear as extreme outliers above the (black hole mass)-(spheroid stellar mass) correlation for early-type galaxies, 
@@
 
+\section{Discussion}
+\label{sec:disc}
+
 \subsection{Origin of compact massive galaxies}
-Acknowledging the correct structure of ellicular galaxies is also important to properly understand their origin. 
+Acknowledging the correct structure of ellicular galaxies is important to properly understand their origin. 
 According to the current paradigm of cosmological structure evolution, 
@@
 The first phase takes place in a young Universe (within its first $4~\rm Gyr$), 
-when cold gas inflows produced short and intense bursts of star formation that created the cores of galaxies. 
-These naked and compact cores, named ``red nuggets'' \citep{damjanov2009}, have been observed at high-redshift with sizes of $1-2~\rm kpc$ \citep{vandokkum2008}.
+when cold gas inflows produced short and intense bursts of star formation 
+that created compact and dense conglomerates of stars with high velocity dispersion. 
+These naked and compact conglomerates, named ``red nuggets'' \citep{damjanov2009}, 
+have been observed at high-redshift with half-light sizes of $1-2~\rm kpc$ \citep{daddi2005,trujillo2006,vandokkum2008}.
 In the second phase (last $10~\rm Gyr$), stellar discs and stellar envelopes 
-were accreted around these primordial galaxy cores and assembled the external parts of galaxies on scales of $2-20~\rm kpc$. 
+were accreted around these primordial conglomerates and the external parts of today's galaxies assembled on scales of $2-20~\rm kpc$. \\
 Today's Universe is populated by an abundance of compact, massive spheroids, 
-with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{GDS2015}. 
+with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{graham2013review,GDS2015}. 
 Some of these local compact massive spheroids are encased within a large-scale disc, 
@@
 Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact ellicular galaxies 
-with purely old ($>10~\rm Gyr$) stellar populations. 
+with purely old ($>10~\rm Gyr$) stellar populations. {\bf [these 4 are COMPACT elliculars, the others are non-compact elliculars]}
 These galaxies have undergone the lowest degree of disc growth. \\
@@
 However, a dramatically different expectation is reached 
-if one considers these galaxies as spheroid-dominated systems with an intermediate-scale disc; 
+if one considers these galaxies today as spheroid-dominated systems with an intermediate-scale disc; 
 in this case, both the galaxy size and the spheroid size are compact ($1-2~\rm kpc$). 
@@
 \includegraphics[width=\columnwidth]{images/mm.pdf}
-\caption{Early-type (elliptical + lenticular) galaxies: 
-black hole mass plotted against spheroid stellar mass for 48 galaxies. 
+\caption{Black hole mass plotted against spheroid stellar mass for 45+3 early-type galaxies (from Savorgnan et al.~2015). 
 The black solid line is the bisector linear regression for all galaxies except Mrk 1216, NGC 1271 and NGC 1277. 
@@
 where $\sigma$ ($0.51$ dex) is the total \emph{rms} scatter about the correlation in the black hole mass direction. 
-The red stars mark four intermediate-scale disc galaxies (Mrk 1216, NGC 1271, NGC 1277 and NGC 1332) and one elliptical galaxy (NGC 4291) 
-that were claimed to be extreme outliers in this diagram. 
-All five reside within a $3\sigma$ deviation from the correlation when using their correct spheroid mass. 
+{\bf The red symbols mark five galaxies that were claimed to be extreme outliers in this diagram: 
+four intermediate-scale disc galaxies (Mrk 1216, NGC 1271, NGC 1277 and NGC 1332) and one elliptical galaxy (NGC 4291). }
+All five reside well within a $3\sigma$ deviation from the correlation when using their correct spheroid mass. 
 For NGC 1277, we show the previously reported spheroid stellar mass \citep{vandenbosch2012} in gray. 
-The green color is used to show the location of four other intermediate-scale disc galaxies mentioned in Section \ref{sec:impl}.}
+The green color is used to show the location of four additional intermediate-scale disc galaxies mentioned in Section \ref{sec:gal}.}
 \label{fig:mm}
@@
 \subsection{Ellicular galaxies in the Hubble grid}
-The existence of the oft-overlooked, intermediate-scale discs presented here exposes a likely continuum of disc sizes in early-type galaxies 
-as opposed to a dichotomy of nuclear discs versus large-scale discs. 
-The presence of these intermediate-scale discs also blurs the distinction between elliptical (E) and lenticular (S0) galaxies 
-and arguably creates the need for a new subclass which bridges this divide.  
-While expanding the galaxy nomenclature beyond ellipticals with possible nuclear discs, and lenticulars with large-scale discs, 
-to include something like {\it elliculars} with intermediate-scale discs will be helpful 
-for distinguishing among the different early-type galaxies with different disk scale-lengths, 
-it should be remembered that just as portions of the electromagnetic spectrum are labelled according to their different wavelengths, 
-there is still an underlying continuum.  
-Similarly, binning early-type galaxies as either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact that a continuum exists.  
-Importantly, in the case of early-type galaxies with intermediate scale discs, 
-this particular rotation-classification depends on the galaxy's radial range probed.  
-There is thus a need for more than two bins (E vs.~S0, or SR vs.~FR). \\
-The existence of intermediate-scale discs is not only important for our understanding of disc growth in general, 
-but accounting for such components impacts upon our broader understanding of galaxy structure.  
-It has recently been argued \citep{graham2014review} that the classification scheme for elliptical galaxies 
-should not be their apparent axis ratio as seen on the plane of the sky, 
-but rather early-type galaxies should be quantified by their spheroid-to-total flux ratio, 
-with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies.   
-While spiral galaxies display a range of spheroid-to-total flux ratios from 0 to $\sim$3/4, 
-lenticular galaxies display a range from $\sim$3/4 to $\sim$0.1 (see \citealt{laurikainen2010}).   
-The spheroid-to-total flux ratio is an important quantity, and its broad range observed in lenticular galaxies 
-has led to a resurgence of \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976}) Hubble comb, 
-in which both late-type galaxies (i.e.~spiral galaxies) and lenticular galaxies form the arms of an expanded Hubble tuning fork, 
-with an additional arm for disc galaxies hosting anaemic spiral patterns (see \citealt{cappellari2011kmdr-MNRAS} and \citealt{kormendybender2012}).  
-However because every spiral Hubble type (e.g.~Sa, Sb, Sc) has a broad range of spheroid-to-total ratio 
-(e.g.~\citealt{grahamworley2008}, and references therein), 
-and because this information is not captured by the Hubble comb, 
-a grid of spiral type (predominantly determined by the spiral arms) versus spheroid-to-total ratio is also useful for classifying galaxies.   
-In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale discs in such a Hubble grid \citep{graham2014review}, 
-revealing how they are related to the other galaxies.  
-Aside from the pure elliptical galaxies, each galaxy type displays a range of spheroid-to-total flux ratio.  
-Rather than a scheme in which the spiral morphological type (a, b, c, etc.) changes if the spheroid-to-total ratio changes (as in the Hubble comb), 
-here the galaxy type is linked to the nature and winding of the spiral arms which has been the primary criteria used 
-to classify spiral galaxies over the last half century \citep{sandage1961}.
+The existence of the oft-overlooked, intermediate-scale discs
+exposes a likely continuum of disc sizes in early-type
+galaxies, as opposed to a dichotomy of nuclear discs versus large-scale
+discs. The presence of these intermediate-scale discs also blurs the
+distinction between elliptical (E) and lenticular (S0) galaxies and
+arguably creates the need for a new subclass which bridges this
+divide.  While expanding the galaxy nomenclature beyond ellipticals
+with possible nuclear discs, and lenticulars with large-scale discs,
+to include something like \emph{elliculars} with intermediate-scale
+discs will be helpful for distinguishing among 
+early-type galaxies with different disk scale-lengths, it should be
+remembered that just as portions of the electromagnetic spectrum are
+labelled according to their different wavelengths, there is still an
+underlying continuum.  Similarly, binning early-type galaxies as
+either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact
+that a continuum exists.  Importantly, in the case of early-type
+galaxies with intermediate-scale discs, this particular
+rotation-based classification depends on the galaxy's radial range probed, 
+changing from FR to SR as the radial extent is sufficiently increased. 
+There is thus a need for more the two bins (E vs. S0, or FR vs. SR) 
+and a continuum in the (Hubble-Jeans)-like classification schemes. \\
+It has recently been argued (Graham 2014) that the classification
+scheme for elliptical galaxies should not be their apparent axis ratio
+as seen on the plane of the sky, but rather early-type galaxies should
+be quantified by their spheroid-to-total flux ratio, with a
+continuum from pure elliptical galaxies to disc-dominated lenticular
+galaxies.  While spiral galaxies display a range of spheroid-to-total flux ratios
+from 0 to $\sim$3/4 (e.g.~\citealt{grahamworley2008}, and references
+therein), lenticular galaxies typically display a range from
+$\sim$3/4 to $\sim$0.1 \citep{laurikainen2010}.  This spheroid-to-total flux
+ratio is widely recognised as an important quantity, and its broad range observed in
+lenticular galaxies (see \citealt{cappellari2011kmdr-MNRAS} and \citealt{kormendybender2012}) recently led to a reintroduction of 
+\citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976})
+Hubble comb, in which both late-type galaxies (i.e.~spiral galaxies)
+and lenticular galaxies form separate arms of an expanded Hubble-Jeans tuning
+fork, with an additional arm for disc galaxies hosting anaemic spiral
+patterns.  However because every spiral Hubble type (e.g.~Sa, Sb, Sc), not just the S0 galaxies, 
+has a broad range of spheroid-to-total ratio, and because this information is not captured by the Hubble comb, 
+a grid of spiral morphological type (predominantly determined by the spiral
+arms) versus spheroid-to-total ratio can also be useful for classifying galaxies.  \\
+In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale
+discs in such a ``Hubble grid'', which is effectively the quantitative scheme used by  
+\cite{boroson1981}, \cite{kent1985}, \cite{kodaira1986}, \cite{simiendevaucouleurs1986} 
+in which each galaxy type displays a range of spheroid-to-total flux ratio.
+Rather than a scheme in which the morphological type (a, b, c,
+etc.) changes if the spheroid-to-total ratio changes -- as in the Hubble comb -- here
+the galaxy type is linked to the nature and winding of the spiral arms
+which has been the primary criteria used to classify spiral galaxies
+over the last half century \citep{sandage1961}.  
+Allowing for the varying spheroid-to-total ratio among each galaxy type, 
+the Hubble grid helps to reveal how ellicular galaxies unify the early-type sequence and compare with late-type galaxies.
+
+%The existence of the oft-overlooked, intermediate-scale discs presented here exposes a likely continuum of disc sizes in early-type galaxies 
+%as opposed to a dichotomy of nuclear discs versus large-scale discs. 
+%The presence of these intermediate-scale discs also blurs the distinction between elliptical (E) and lenticular (S0) galaxies 
+%and arguably creates the need for a new subclass which bridges this divide.  
+%While expanding the galaxy nomenclature beyond ellipticals with possible nuclear discs, and lenticulars with large-scale discs, 
+%to include something like {\it elliculars} with intermediate-scale discs will be helpful 
+%for distinguishing among early-type galaxies with different disk scale-lengths, 
+%it should be remembered that just as portions of the electromagnetic spectrum are labelled according to their different wavelengths, 
+%there is still an underlying continuum.  
+%Similarly, binning early-type galaxies as either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact that a continuum exists.  
+%Importantly, in the case of early-type galaxies with intermediate-scale discs, 
+%this particular rotation-classification depends on the galaxy's radial range probed.  
+%There is thus a need for more than two bins (E vs.~S0, or SR vs.~FR). \\
+%%The existence of intermediate-scale discs is not only important for our understanding of disc growth in general, 
+%%but accounting for such components impacts upon our broader understanding of galaxy structure.  
+%It has recently been argued \citep{graham2014review} that the classification scheme for elliptical galaxies 
+%should not be their apparent axis ratio as seen on the plane of the sky, 
+%but rather early-type galaxies should be quantified by their spheroid-to-total flux ratio, 
+%with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies.   
+%While spiral galaxies display a range of spheroid-to-total flux ratios from 0 to $\sim$3/4, 
+%lenticular galaxies display a range from $\sim$3/4 to $\sim$0.1 (see \citealt{laurikainen2010}).   
+%The spheroid-to-total flux ratio is an important quantity, and its broad range observed in lenticular galaxies 
+%has led to a resurgence of \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976}) Hubble comb, 
+%in which both late-type galaxies (i.e.~spiral galaxies) and lenticular galaxies form the arms of an expanded Hubble tuning fork, 
+%with an additional arm for disc galaxies hosting anaemic spiral patterns (see \citealt{cappellari2011kmdr-MNRAS} and \citealt{kormendybender2012}).  
+%However because every spiral Hubble type (e.g.~Sa, Sb, Sc) has a broad range of spheroid-to-total ratio 
+%(e.g.~\citealt{grahamworley2008}, and references therein), 
+%and because this information is not captured by the Hubble comb, 
+%a grid of spiral type (predominantly determined by the spiral arms) versus spheroid-to-total ratio is also useful for classifying galaxies.   
+%In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale discs in such a Hubble grid \citep{graham2014review}, 
+%revealing how they are related to the other galaxies.  
+%Aside from the pure elliptical galaxies, each galaxy type displays a range of spheroid-to-total flux ratio.  
+%Rather than a scheme in which the spiral morphological type (a, b, c, etc.) changes if the spheroid-to-total ratio changes (as in the Hubble comb), 
+%here the galaxy type is linked to the nature and winding of the spiral arms which has been the primary criteria used 
+%to classify spiral galaxies over the last half century \citep{sandage1961}.
 
@@
 \end{figure}
+
+\section{Conclusions}
+{\bf I'll write them after the first ref. rep. :) }
 

### 2015-10-01 papers/data_paper/datapaper.tex
submission day
holidays

@@
 \usepackage{bm}
+\usepackage{hyperref}
 
@@
 
-\shorttitle{True-to-life galaxy decomposition}
+\shorttitle{Galaxy vivisection}
 \shortauthors{Savorgnan \& Graham}
@@
 
-\title{Supermassive black hole and host spheroid affairs \\ I. True to life, physically motivated galaxy decomposition}
+\title{Supermassive black holes and their host spheroids \\ I. Galaxy vivisection}
 
@@
 Moreover, many accurate $M_{\rm BH}$ predictions enable one to derive 
-the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction}; Fontanot et al. \emph{submitted}) 
+the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction,shankar2009,shankar2013,fontanot2015}) 
 and space density (e.g.~\citealt{grahamdriver2007smbhmassdensity,comastri2015}). 
@@
 have further advanced this view of ``elliptical'' galaxies being all but simple and featureless pressure-supported systems.
-Most of the morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.
+Most of the morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII}.
 \cite{krajnovic2013} showed that ``fast rotators'' as a class are disk-galaxies or at least disk-like galaxies. 
@@
 by rejecting the most discrepant S\'ersic index measurements and averaging the remaning ones, 
-a strong $M_{\rm BH}-n_{\rm sph}$ correlation was recovered. 
-The fact that none of the four studies obtained a significant $M_{\rm BH}-n_{\rm sph}$ correlation with their individual measurements 
-is indicative of non accurate galaxy decompositions. }.
+a strong $M_{\rm BH}-n_{\rm sph}$ correlation was recovered. }.
 In addition, \cite{lasker2014anal} 
 declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity as it does with the spheroid luminosity, 
-as opposed to \cite{beifiori2012} who claimed that the spheroid mass is a better tracer of $M_{\rm BH}$ than the galaxy mass.
+as opposed to \cite{beifiori2012} who claimed that the spheroid mass is a better tracer of $M_{\rm BH}$ than the galaxy mass 
+{\bf (see also \citealt{kormendygebhardt2001,erwingadotti2012})}.
 The past studies did not converge to the same conclusions 
@@
 using $3.6~\rm \mu m$ \emph{Spitzer} satellite imagery, 
-which is an excellent proxy for the stellar mass, superior to the $K$-band (\citealt{sheth2010} and references therein).
+which is an excellent proxy for the stellar mass, superior to the $K$-band \citep{junim2008,sheth2010}.
 We will use these in a series of forthcoming papers to obtain improved black hole mass scaling relations 
@@
 all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs). 
-%listed in Table \ref{tab:obs}.
 Each AOR is an individual Spitzer observation sequence, and
@@
 The orientation of the mosaic was set to the average rotation angle of the input cBCD frames. 
-%{\bf TBD: not n-e oriented or re-sampled because problems with 2d PSF. }
 Individual cBCD frames were combined together into a single mosaic with the default linear interpolation algorithm.
@@
 producing a consistent background across the mosaicked image.
-According to the \emph{Spitzer Data Cookbook}, the use of the \emph{overlap} module is not particularly recommended for 
+According to the \emph{Spitzer Data Analysis 
+Cookbook}\footnote{\href{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/cookbook/Spitzer_Data_Cookbook.pdf}
+{\tt http://irsa.ipac.caltech.edu/data/SPITZER/docs/ dataanalysistools/cookbook/Spitzer\_Data\_Cookbook.pdf}}, 
+the use of the \emph{overlap} module is not particularly recommended for 
 $3.6~\rm \mu m$ observations. 
@@
 (background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
-%We employed both a Gaussian and a Moffat \citep{moffat1969} profile. 
 The best-fit parameters of the 20 stars were then averaged together. 
-Doing so, we obtained %$FWHM = 2''.03$ for the Gaussian function,
+Doing so, we obtained 
 $(\alpha, \beta) = (2''.38, 4.39)$.
@@
 but maintains the asymmetric features of the instrument PRF (e.g.~wings and spikes).
-%This procedure was repeated using a Moffat profile in place of the Gaussian profile.
 We then tested this 2D PSF 
@@
 A kinematical classification (slow/fast rotator) is available for 34 of our 75 galaxies 
-from the ATLAS$^{\rm 3D}$ survey \citep{atlas3dIII-MNRAS} 
+from the ATLAS$^{\rm 3D}$ survey \citep{atlas3dIII} 
 and for 3 additional galaxies from \citet{scott2014}.
@@
 disturbed morphology in the galaxy outskirts, etc.). 
+{\bf In particular, we did not attempt to fit down- or up-bendings of large-scale disks 
+(e.g.~\citealt{erwin2005,erwin2008,erwin2012,gutierrez2011,comeron2012,munozmateos2013,kim2014}) 
+by truncating the surface brightness profiles well before the occurrence of these features. }
 Individual cases are discussed in Section \ref{sec:indgal}.
@@
 The all too often over-looked flaw with (signal-to-noise)-based weighting schemes 
-is that they immediately become an incorrectly biased weighting schemes when additional components are present but not modelled.
-For example, fitting a S\'ersic model to what is actually a nucleated elliptical galaxy immediately voids 
+is that they immediately become biased weighting schemes when additional components are present but not modelled.
+For example, fitting only a S\'ersic model to what is actually a nucleated elliptical galaxy immediately voids 
 a (signal-to-noise)-based weighting scheme 
@@
 this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
-What is best in theory is not always best in practice -- in this case, because theory does not allow for unknown additional components
-that are modelled.
+{\bf Over-looked partially depleted cores, or an incorrect PSF, can of course also result in (signal-to-noise)-weighted fitting schemes 
+performing poorly because of the emphasis they place on matching the model to the inner data. }
 
@@
 A local angular momentum decrease with increasing radius is indicative of an intermediate-scale disk 
-that fades toward larger radii. \\
-%As an illustration, we consider the galaxy NGC 3377.
-%For this galaxy, \citet{arnold2014} reported a strong decline in local specific angular momentum beyond $\sim 35''$, 
-%with a disk-to-bulge transition occurring at about $\sim 50''$.
-%They did attempt a three-component decomposition (accounting for a bulge, an embedded disk and a central cusp), 
-%but unfortunately they fit the spheroidal component with a limited two-parameter $R^{1/4}$ profile {\bf TBD: cite de vaucouleurs} 
-%rather than a three-parameter $R^{1/n}$ S\'ersic function.
-%Here we used a surface brightness profile twice as extended as that used by \citet{arnold2014} 
-%and we identified a nuclear disk and an intermediate-scale disk, both embedded in a larger spheroidal component (see Figure \ref{fig:n3377ex}).
-%The presence of an intermediate-scale disk is evident from the unsharp mask of the image mosaic 
-%and also from the ellipticity profile, which increases with increasing radius until $R \sim 45''$ (along the major-axis) 
-%and dramatically drops at larger radii.
-%The nuclear disk can be spotted from the peak at $R \sim 5''$ in the $B4$ profile.
-%In our galaxy model for NGC 3377, 
-%the difference between the S\'ersic profile of the bulge and the exponential profile of the intermediate-scale disk is minimum in correspondence 
-%of the maximum ellipticity, 
-%thus our model correctly reproduces the isophotal properties of the galaxy. 
-%The residuals of the fit, especially along the major-axis, display some minor structures which indicate that 
-%the bulge S\'ersic index might have been slightly overestimated.
-%This could be due to the fact that the embedded disk would be better described by a truncated exponential function.
-%Alternatively, a contribution from a stellar halo (not included in our model) at large radii could be the reason of a 
-%too large S\'ersic index for the bulge. 
-%Our equivalent-axis decomposition results in a bulge component that accounts for 94\% of the total luminosity, 
-%an intermediate-scale embedded disk contributing to 5\% 
-%and a nuclear disk with 1\% of the total light. \\
-%A similar situation occurs for the galaxy M59 (see Figure \ref{fig:m59ex}), 
-%for which our equivalent-axis model returns a spheroidal component and an embedded disk 
-%contributing to 92\% and 8\% of the total light respectively. \\
-%The edge-on embedded disk of the S\'ersic galaxy NGC 1332 (see Figure \ref{fig:n1332ex}) was hard to model with an exponential function, 
-%leading us to prefer a low-$n$ S\'ersic profile. 
-%Our equivalent-axis decomposition returns a spheroidal component accounting for 95\% of the total light,
-%and an embedded disk accounting for the remaining 5\%.
-%In passing, we note that the bulge-disk decomposition performed by \citet{rusli2011} on NGC 1332 
-%is significantly different from our best-fit model.
-%\citet{rusli2011} did not identify an intermediate-scale embedded disk, 
-%but instead proposed a model featuring a S\'ersic bulge ($n \sim 2.3$, $R_{\rm e} \sim 8''$), accounting for 43\% of the total light, 
-%and a large-scale exponential disk. 
-%This result led them to the conclusion that NGC 1332 is a disk dominated lenticular galaxy 
-%and is displaced from the $M_{\rm BH} - L_{\rm K,sph}$ (black hole mass vs. $K$-band spheroid luminosity) relation of \citet{marconihunt2003} 
-%by an order of magnitude along the $M_{\rm BH}$ direction.
-%Assuming instead that, as suggested by our model, 
-%the galaxy spheroid is a factor of two more luminous than what claimed by \citet{rusli2011}, 
-%NGC 1332 would no longer be an outlier in the $M_{\rm BH} - L_{\rm K,sph}$ diagram (see Figure \ref{fig:n1332pl}), 
-%perfectly fitting within the $1\sigma$ scatter of the $M_{\rm BH} - L_{\rm K,sph}$ relation for S\'ersic bulges of \citet{grahamscott2013}. \\
+that fades toward larger radii. 
+{\bf Savorgnan \& Graham (\emph{submitted}) extensively discuss the topic of galaxies with intermediate-scale disks 
+and show that, when these disks are misclassified and modeled as large-scale disks, 
+the luminosity of the spheroidal component is underestimated, 
+which makes these galaxies falsely appear as extreme outliers in the (black hole mass)-(spheroid stellar mass) diagram. } \\
 Bars are usually recognizable from galaxy images and unsharp masks, 
@@
 can provide additional evidence for less obvious bars. 
-As noted, we were able to successfully fit bars with a Ferrer function or a low-$n$ S\'ersic model ($n \sim 0.2$). \\
+{\bf As noted, we were able to successfully fit bars with a Ferrer function 
+(NGC 4151 is the only case for which we described the bar with a $n \sim 0.2$ S\'ersic model). 
+Disk-like components embedded in the bulges of spiral galaxies were described with a $n \lesssim 1$ S\'ersic model or, 
+in a few cases, with a Ferrer function\footnote{\bf The advantage of choosing a Ferrer function over a S\'ersic profile 
+to fit a disk-like component embedded in the bulge 
+is to reduce degeneracies with the S\'ersic profile that describes the bulge.}. 
+This approach is similar to that of \cite{laurikainen2010}, 
+who fit bars with a Ferrer function and inner disks with a S\'ersic model. 
+We did not find evidence of bars with exponential profiles (e.g.~\citealt{elmegreenelmegreen1985,gadotti2008,kim2015}), 
+but this might be due to the low number statistics of barred galaxies in our sample. }\\
 The presence of a nuclear component -- either resolved or unresolved -- was generally expected in 
@@
 Unresolved nuclear components were fit with our optimal Moffat PSF,
-whereas resolved nuclear components were modeled with (PSF-convolved) narrow Gaussian functions. \\
+whereas resolved nuclear components were modeled with (PSF-convolved) narrow Gaussian functions 
+{\bf (\citealt{wadadekar1999,ravindranath2001,peng2002} and \citealt{gadotti2008} discuss the importance of fitting nuclear components)}. \\
 Rings were identified from galaxy images and unsharp masks, and modeled with symmetric Gaussian ring profiles. \\
@@
 as expected from a large-scale disk. 
-%\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + Gaussian-AGN 
-%($R_{\rm e} = 27''.2$, $n = 3.0$). 
 From an inspection of the unsharp mask, we identified a ring at $R \sim 50''$, 
@@
 
-%\begin{figure*}[h]
-%\begin{center}
-%\includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
-%\caption{the galaxy NGC 3377. 
-%The left panels refer to the major-axis $R_{\rm maj}$, 
-%whereas the right panels refer to the equivalent-axis $R_{\rm eq}$.
-%The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
-%The black points are the observed data.  
-%The color lines represent the individual (PSF-convolved) model components:
-%red=S\'ersic (bulge), blue=exponential (disk). 
-%The best-fit parameters for the S\'ersic profile are included.
-%The total (PSF-convolved) model is shown with a black dashed line, 
-%but it is hard to distinguish because it almost perfectly matches the data.
-%The horizontal grey dashed line indicates the $3~RMS_{\rm sky}$ level.
-%$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
-%$\Delta \mu$ are the residuals from the fit.
-%The six panels below show the ellipticity ($\epsilon$), position angle ($PA$) and $B4$ radial profiles.
-%}
-%\label{fig:n3377ex}
-%\end{center}
-%\end{figure*}
-
 \begin{figure*}[h]
@@
 
-%\begin{figure*}[h]
-%\begin{center}
-%\includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
-%\caption{the galaxy M59. 
-%The figure caption is the same as Figure \ref{fig:n3377ex}. 
-%Empty data points represent data excluded from the fit.}
-%\label{fig:m59ex}
-%\end{center}
-%\end{figure*}
-%
-%\begin{figure*}[h]
-%\begin{center}
-%\includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
-%\caption{the galaxy NGC 1332.
-%The figure caption is the same as Figure \ref{fig:n3377ex}. 
-%Empty data points represent data excluded from the fit.}
-%\label{fig:n1332ex}
-%\end{center}
-%\end{figure*}
-%
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width=\columnwidth]{images/mbhmagk_n1332.pdf}
-%\caption{The location of the S\'ersic galaxy NGC 1332 in the black hole mass versus $K$-band spheroid absolute magnitude diagram,
-%according to our galaxy decomposition. 
-%The red and blue solid lines show the scaling relations for core-S\'ersic and S\'ersic galaxies, respectively, 
-%reported by \citet{grahamscott2013}, 
-%while the shaded areas mark the $1\sigma$ errors.}
-%\label{fig:n1332pl}
-%\end{center}
-%\end{figure}
-
 \subsection{2D fits}
@@
 For each galaxy, we built a 2D model that was consistent with the corresponding 1D model in terms of number and type of components. 
-Because the Ferrer profile is not made available in \textsc{Imfit},
-bars were fit with a 2D Gaussian function. \\
+{\bf The only difference between our 1D and 2D models pertains to the description of bars: 
+because the Ferrer profile is not made available in \textsc{Imfit},
+bars were fit with a 2D Gaussian function. } \\
 The 2D decomposition of NGC 2974 is presented in Figure \ref{fig:n29742d}. 
@@
 \includegraphics[width=\columnwidth]{images/n2974_resid.jpeg}
-\caption{Image of the galaxy NGC 2974 with its mask (top panel), unsharp mask (second panel), 
-best-fit 2D model (third panel), 
-and residual image after the subtraction of the 2D model (bottom panel).
+\caption{Image of the galaxy NGC 2974 with its mask (top panel, {\bf on a logarithmic scale}), 
+unsharp mask (second panel, {\bf on a linear scale}), 
+best-fit 2D model (third panel, {\bf on a logarithmic scale}), 
+and residual image after the subtraction of the 2D model (bottom panel, {\bf on a linear scale; 
+the residual patterns correspond to differences between the data and the model of less than 6\%}).
 The lefthand side of the mosaic allowed an accurate determination of the sky background level.}
@@
 \caption{2D measurements of the spheroid S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
-The dashed line displays the 1:1 relation.}
+The dashed line displays the 1:1 relation.
+{\bf The four most obvious outliers are NGC 821, NGC 3377, NGc 4945, and NGC 5576. 
+Their individual cases are discussed in the Appendix. }}
 \label{fig:n1d2d}
@@
 that does not quite match the real ``shape'' of the spheroid. 
-When we identified, but were not able to accurately model. a galaxy sub-component.
+{\bf When we identified, 
+but were not able to model a galaxy sub-component with the same accuracy dedicated to the other components}.
 In the case of apparent inconsistencies between the model and the observed galaxy properties 
@@
 We elect to use $\pm \sigma_1^\pm$, $\pm \sigma_2^\pm$ and $\pm \sigma_3^\pm$ as $1\sigma$ uncertainties 
-for our measurements of $\log(n_{\rm sph})$ obtained from ``grade 1'', ``grade 2'' and ``grade 3'' fits, respectively. \\
+for our measurements of $\log(n_{\rm sph})$ obtained from ``grade 1'', ``grade 2'' and ``grade 3'' fits, respectively. 
+{\bf This means that, if the fit of a galaxy was classified as ``grade 1'', 
+the (logarithmic) value of the spheroid S\'ersic index $\tilde{n}_{\rm sph}$ and associated uncertainties would be 
+$\log(\tilde{n}_{\rm sph})^{+\sigma_1^+}_{-\sigma_1^-} = \log(\tilde{n}_{\rm sph})^{+0.06}_{-0.08}$; 
+if the fit of that galaxy was classified as ``grade 2'', 
+then one would have $\log(\tilde{n}_{\rm sph})^{+\sigma_2^+}_{-\sigma_2^-} = \log(\tilde{n}_{\rm sph})^{+0.17}_{-0.21}$, 
+and so on.  }
 
@@
   Inaccurate sky subtraction could be the reason why B+12 obtained a large estimate of the effective radius.
-  }
+  {\bf We could not obtain a successful 2D model that included a nuclear component, 
+  therefore we opted for masking the nuclear region of the galaxy. 
+  This resulted in a significantly lower S\'ersic index, that we consider underestimated. }}
   \end{table}
@@
   An edge-on elliptical/lenticular galaxy. 
-  The ellipticity profile broadcasts the presence of an intermediate-scale disk. 
+  {\bf The identification of a disk is trivial due to its edge-on orientation, 
+  although a visual inspection of the galaxy image is not enough to estabilish the radial extent of this disk. 
+  The ellipticity profile indicates that the disk is indeed intermediate-sized, i.e.~it does not dominate at large radii. }
   Given the edge-on inclination of this disk, we model it with a low-$n$ S\'ersic profile. 
@@
   \tablecomments{L+14 obtained the smallest estimate of the effective radius because they oversubtracted a halo. 
+  {\bf In our 2D fit, we were not successful in modelling the nuclear disk and opted for masking the nuclear region of the galaxy. 
+  Such 2D model resulted in a significantly lower S\'ersic index, that we trust being underestimated. } 
   }
@@
   the contribution from the bulge is still significant compared to that of the disk.
-  In fact, the surface brightness profile does not display an exponential decline at large radii.
   We note that the antitruncation reported by \cite{gutierrez2011} could be an artificial feature 
   produced by the transition from the S\'ersic bulge to the exponential disk. 
+  {\bf According to their analysis of the surface brightness profile of NGC 4459 (their Figure 14), 
+  the contribution from the disk completely overcomes that of the bulge beyond $R_{\rm maj} \gtrsim 60''$. 
+  In the surface brightness profile, they identified two exponential declines with different scale lengths 
+  (the first between $60'' \lesssim R_{\rm maj} \lesssim 110''$, and the second beyond $R_{\rm maj} \gtrsim 120''$). 
+  However, we checked that in the radial range $60'' \lesssim R_{\rm maj} \lesssim 110''$ 
+  the surface brightness profile is not a perfect exponential, but presents a curvature. 
+  This can be securely assessed only by fitting the data within the mentioned radial range with a single exponential function 
+  and plotting the residuals; 
+  if the residuals betray a curvature, the data cannot be accommodated by a single exponential function. 
+  According to our decomposition, the disk of NGC 4459 starts dominating beyond $R_{\rm maj} \gtrsim 100''$. 
+  The exponential function of our model seems to nicely match the ``second'' exponential decline identified by \cite{gutierrez2011}.  }
   We do not find evidence for any embedded components in our data.
@@
   The light profile has an obvious bump that can be ascribed to the bar.
-  This bumb cannot be easily modeled with a Ferrer function, thus we exclude the data in the range $100'' \lesssim R_{\rm maj} \sim 400''$ form the fit.
+  This bumb cannot be easily modeled with a Ferrer function {\bf nor with a S\'ersic profile}, 
+  thus we exclude the data in the range $100'' \lesssim R_{\rm maj} \sim 400''$ form the fit.
   We also exclude the data within the innermost $6''.4$ due to the contribution from the AGN.

### 2015-10-01 papers/ellicular/ellicular.tex
holidays

@@
-\documentclass[useAMS,usenatbib,article]{mn2e}
+\documentclass[useAMS,usenatbib,article]{mnras}
 
@@
 \usepackage{natbib}
-\bibliographystyle{mn2e}
-%\usepackage{tabularx}
-%\usepackage{bm}
-%\usepackage{color}
-%\usepackage{hyperref}
+\bibliographystyle{mnras}
 
-%% Sometimes a paper's abstract is too long to fit on the
-%% title page in preprint2 mode. When that is the case,
-%% use the longabstract style option.
-
-%% \documentclass[preprint2,longabstract]{aastex}
-\newcommand\aj{{AJ}}%
-\newcommand\actaa{{Acta Astron.}}%
-\newcommand\araa{{ARA\&A}}%
-\newcommand\apj{{ApJ}}%
-\newcommand\apjl{{ApJ}}%
-\newcommand\apjs{{ApJS}}%
-\newcommand\ao{{Appl.~Opt.}}%
-\newcommand\apss{{Ap\&SS}}%
-\newcommand\aap{{A\&A}}%
-\newcommand\aapr{{A\&A~Rev.}}%
-\newcommand\aaps{{A\&AS}}%
-\newcommand\azh{{AZh}}%
-\newcommand\baas{{BAAS}}%
-\newcommand\caa{{Chinese Astron. Astrophys.}}%
-\newcommand\cjaa{{Chinese J. Astron. Astrophys.}}%
-\newcommand\icarus{{Icarus}}%
-\newcommand\jcap{{J. Cosmology Astropart. Phys.}}%
-\newcommand\jrasc{{JRASC}}%
-\newcommand\memras{{MmRAS}}%
-\newcommand\mnras{{MNRAS}}%
-\newcommand\na{{New A}}%
-\newcommand\nar{{New A Rev.}}%
-\newcommand\pra{{Phys.~Rev.~A}}%
-\newcommand\prb{{Phys.~Rev.~B}}%
-\newcommand\prc{{Phys.~Rev.~C}}%
-\newcommand\prd{{Phys.~Rev.~D}}%
-\newcommand\pre{{Phys.~Rev.~E}}%
-\newcommand\prl{{Phys.~Rev.~Lett.}}%
-\newcommand\pasa{{PASA}}%
-\newcommand\pasp{{PASP}}%
-\newcommand\pasj{{PASJ}}%
-\newcommand\qjras{{QJRAS}}%
-\newcommand\rmxaa{{Rev. Mexicana Astron. Astrofis.}}%
-\newcommand\skytel{{S\&T}}%
-\newcommand\solphys{{Sol.~Phys.}}%
-\newcommand\sovast{{Soviet~Ast.}}%
-\newcommand\ssr{{Space~Sci.~Rev.}}%
-\newcommand\zap{{ZAp}}%
-\newcommand\nat{{Nature}}%
-\newcommand\iaucirc{{IAU~Circ.}}%
-\newcommand\aplett{{Astrophys.~Lett.}}%
-\newcommand\apspr{{Astrophys.~Space~Phys.~Res.}}%
-\newcommand\bain{{Bull.~Astron.~Inst.~Netherlands}}%
-\newcommand\fcp{{Fund.~Cosmic~Phys.}}%
-\newcommand\gca{{Geochim.~Cosmochim.~Acta}}%
-\newcommand\grl{{Geophys.~Res.~Lett.}}%
-\newcommand\jcp{{J.~Chem.~Phys.}}%
-\newcommand\jgr{{J.~Geophys.~Res.}}%
-\newcommand\jqsrt{{J.~Quant.~Spec.~Radiat.~Transf.}}%
-\newcommand\memsai{{Mem.~Soc.~Astron.~Italiana}}%
-\newcommand\nphysa{{Nucl.~Phys.~A}}%
-\newcommand\physrep{{Phys.~Rep.}}%
-\newcommand\physscr{{Phys.~Scr}}%
-\newcommand\planss{{Planet.~Space~Sci.}}%
-\newcommand\procspie{{Proc.~SPIE}}%
-
-%\newcommand{\vdag}{(v)^\dagger}
-%\newcommand{\myemail}{gsavorgn@astro.swin.edu.au}
-%\newcommand{\fitfigurewidth}{0.8\textwidth}
-
-%\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes}
 \title[Ellicular galaxies]{Ellicular galaxies and their (non over-massive) black holes}
@@
 Ellicular galaxies have often been confused with lenticular galaxies, 
-such that %their disc luminosities have been considerably overestimated 
-their spheroid luminosities have been considerably underestimated. 
+such that their spheroid luminosities have been considerably underestimated. 
 This has recently led to some surprising conclusions, 
@@
 host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
-We show that when ellicular galaxies are correctly modeled, 
+We show that when ellicular galaxies are correctly modelled, 
 they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
@@
 \begin{keywords}
-black hole physics -- galaxies: bulges -- galaxies: elliptical and lenticular, cD -- galaxies: evolution -- galaxies: structure
+galaxies: classification -- galaxies: bulges -- galaxies: elliptical and lenticular, 
+cD -- galaxies: evolution -- galaxies: structure -- galaxies: individual: Mrk 1216, NGC 1271, NGC 1277, NGC 1332, NGC 4291
 \end{keywords}
@@
 There are currently two well-known types of stellar discs in galaxies. 
-The first are the large-scale discs (with sizes of a few kiloparsec) 
+The first are the large-scale discs (with exponential scale lengths of a few kiloparsec) 
 that dominate the light at large radii in spiral and lenticular galaxies; 
@@
 gas rich mergers and halo accretion events 
-(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}), 
+(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,barneshernquist1992,khochfarsilk2006,dekel2009nat,ceverino2010,
+ceverino2012,conselice2012,rubin2012,martini2013,ueda2014}), 
 and a thorough review can be found in \citet{combes2014arX,combes2014pro}.
@@
 they have at times been labelled and rejected as ''unphysical'' when detected. 
-Here we report on the photometric and kinematical signatures of these intermediate-sized stellar discs 
-and the impact this has on the (black hole mass)-to-(spheroid stellar mass) ratio %, $M_{\rm BH}/M_{*,sph}$, 
+Here we focus on the increasingly overlooked occurence of intermediate-scale discs in galaxies with directly measured black hole masses. 
+We report on the photometric and kinematical signatures of these intermediate-sized stellar discs,  
+and the impact they have on the (black hole mass)-to-(spheroid stellar mass) ratio 
 which is used to constrain galaxy evolution models. \\
-%A puzzling question, which has been unspoken for decades, is why are there not intermediate-sized discs: 
-%why are there not accretion events which create discs larger than the typical nuclear discs but which are not large enough to dominate at large radii? 
 The majority of stellar discs have some level of inclination with respect to our line-of-sight, 
@@
 Two-dimensional kinematic maps represent an important diagnostic tool for this purpose. 
-Most early-type galaxies are classified as ``central fast rotators'' \citep{atlas3dIII-MNRAS}, 
+Most early-type galaxies are classified as ``central fast rotators'' \citep{franx1989,atlas3dIII,scott2014}, 
 that is, they are rapidly rotating within their half-light radius.  
@@
 whereas other central fast rotators become slow rotators in their outer regions.
-A specific angular momentum profile that is rapidly increasing beyond $1-2$ half-light radii 
+A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
 is a signature of a large-scale disc, 
-while a specific angular momentum profile that increases up to $1-2$ half-light radii and then declines beyond that point 
+while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 
 indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 
@@
 Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of stellar discs in early-type galaxies. \\
-The toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 
+Building on the investigation of \cite{rixwhite1990}, 
+the toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 
 ($\epsilon = 1 - b/a$, where $b/a$ is the ratio of minor-to-major axis length) of 
-(i) a lenticular galaxy comprised of a large-scale disc and a relatively smaller encased bulge, 
-(ii) an elliptical galaxy with a nuclear stellar disc, 
-and (iii) a galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid. 
-We refer to the last case as an ellicular galaxy. 
+(i) a ``lenticular'' galaxy comprised of a large-scale disc which dominates the light at large radii over a relatively smaller encased bulge, 
+(ii) an ``elliptical'' galaxy with an additional nuclear stellar disc, 
+and (iii) a galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid 
+which dominates the light at large radii. 
+We refer to the last case as an ``ellicular'' galaxy. 
 In general, stellar discs are intrinsically flat and circular; 
@@
 An ellipticity profile that increases with radius can be ascribed to an inclined disc that becomes progressively more important at large radii, 
-whereas a radial decrease of ellipticity signifies the opposite case. \\
+whereas a radial decrease of ellipticity signifies the opposite case. 
+This approach can be taken to the next level by inspecting the isophotes for discy structures and checking the velocity line profiles for asymmetry 
+(e.g.~\citealt{scorzabender1995} and references therein; \citealt{scorza1998}). \\
 The awareness that many so-called ``elliptical'' galaxies actually contain stellar discs 
-dates back at least three decades 
-\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995,
-donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998} and, 
+dates back many years 
+\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
+vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
+simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999} and, 
 more recently, intermediate-scale discs were anything but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
-However, the class of ellicular galaxies has been missed by many galaxy modellers, 
+However, the class of ellicular galaxies has been missed by many galaxy modellers of late, 
 who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
 as is observed with spiral galaxies. 
-This bias has led to the rejection of many spheroid/disc decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
+Indeed, \citeauthor{graham2011} (\citeyear{graham2011}, his Figure 7) warned about such erroneous fits to spiral galaxies. 
+This bias has led to the rejection of many early-type galaxy decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
 Unsurprisingly, studies affected by this bias have not obtained spheroid/disc decompositions with a spheroid-to-total ratio larger than $0.6 - 0.8$ 
-(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}). \\
-{\bf This paper is structured as follows. 
+(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}). 
+In this paper we investigate the influence this has had on research pertaining to supermassive black hole mass scaling relations involving the host spheroid. \\
+This paper is structured as follows. 
 In Section \ref{sec:gal} we present a detailed photometric analysis of three ellicular galaxies (Mrk 1216, NGC 1332, and NGC 3115) 
-and we briefly describe other five ellicular galaxies (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697). 
-We compare our photometric analysis with the kinematical information available from the literature 
+and we briefly describe another five ellicular galaxies (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697) 
+already modelled by us elsewhere in the literature. 
+We compare our photometric analysis with the kinematical information available from the literature, 
 and explain the differences between our galaxy models and past decompositions. 
@@
 In Section \ref{sec:disc} we discuss our results in terms of galaxy evolution 
-and we update the Hubble grid with the inclusion of ellicular galaxies. }
+and we present the location of ellicular galaxies, relative to other galaxies, in the Hubble grid.
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/discmodel.eps}
+\includegraphics[width=\columnwidth]{discmodel.eps}
 \caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
@@
 which can also be spotted as a small peak in the ellipticity profile 
-(at semimajor-axis length $R_{\rm maj} \sim 15~\rm arcsec$).
+(at semi-major axis length $R_{\rm maj} \sim 15~\rm arcsec$). 
+Such rings are common in early-type galaxies \citep{michardmarchal1993}.
 The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
@@
 with a spheroid-to-total ratio of $0.43$.
-Based on their bulge/disc decomposition, they concluded that NGC 1332 is a disc dominated lenticular galaxy 
+Based on their bulge/disc decomposition, they concluded that NGC 1332 is a disc-dominated lenticular galaxy 
 which is displaced from the (black hole mass)-(spheroid luminosity) correlation of \cite{marconihunt2003} 
@@
 for early-type galaxies. 
-{\bf We also note that the majority of galaxies with an elevated stellar velocity dispersion ($\sigma > 270~\rm km~s^{-1}$) 
-are core-S\'ersic galaxies \citep{graham2003coresersicmodel,trujillo2004coresersicmodel,dullograham2014cores}, 
+We also note that the majority of galaxies with an elevated stellar velocity dispersion ($\sigma > 270~\rm km~s^{-1}$) 
+are core-S\'ersic galaxies \citep{graham2003coresersicmodel,ferrarese2006acsvcs,dullograham2014cores}, 
 i.e.~they have a partially depleted core which has been identified from high-resolution photometric data. 
@@
 based on their decomposition of \emph{HST} imaging, \cite{rusli2011} did not find a core in this galaxy. 
-However, the identification of a partially depleted core is model dependent, 
-that is, only a correct galaxy decomposition can confirm or rule out the presence of a core. 
-Our galaxy decomposition (Figure \ref{fig:n1332}) suggests that NGC 1332 is in fact a core-S\'ersic galaxy. 
+However, our galaxy decomposition (Figure \ref{fig:n1332}) suggests that NGC 1332 is in fact a core-S\'ersic galaxy. 
 Since we did not use high-resolution photometric data, 
@@
 but we caution that a re-analysis of the \emph{HST} data -- by taking into account the correct radial extent of the intermediate-scale disc --
-may indeed reveal the presence of a core.}
+may indeed reveal the presence of a depleted core in this galaxy.
 
@@
 \subsubsection{NGC 1271}
-{\bf \cite{walsh2015} explored a three-component decomposition for NGC 1271 
+\cite{walsh2015} explored a three-component decomposition for NGC 1271 
 and identified the galaxy bulge with the innermost of the three components, 
-having a half-light radius of $0.61~\rm arcsec$ and a bulge-to-total ratio of $0.23$; 
+having a half-light radius of $0.61~\rm arcsec$ and a bulge-to-total flux ratio of $0.23$; 
 our model features a spheroid + intermediate-scale disc, 
-with a spheroid half-light radius of $3.3~\rm arcsec$ and a spheroid-to-total ratio of $0.67$. }
+with a spheroid half-light radius of $3.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.67$.
 
@@
 \cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
-which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total ratio of $0.24$; 
+which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total flux ratio of $0.24$; 
 our model consists of a spheroid + intermediate-scale disc + nuclear component, 
-and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total ratio of $0.79$.
+and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.
 
@@
 \cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
-and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total ratio of $0.35$; 
+and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total flux ratio of $0.35$; 
 our model with a spheroid + intermediate-scale disc + nuclear disc 
-returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total ratio of $0.94$.
+returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total flux ratio of $0.94$.
 
@@
 \cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
-and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total ratio of $0.19$; 
+and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total flux ratio of $0.19$; 
 our decomposition consists of a spheroid + intermediate-scale disc, 
-with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total ratio of $0.79$.
+with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.
 
@@
 \cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
-and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total ratio of $0.08$; 
+and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total flux ratio of $0.08$; 
 we described NGC 4697 using a spheroid + intermediate-scale disc + nuclear disc model, 
-and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total ratio of $0.89$. \\
+and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.89$. \\
 
@@
 \begin{center}
-\includegraphics[width=0.49\columnwidth]{images/n3115_image.jpeg}
-\includegraphics[width=0.49\columnwidth]{images/n3115_unsharp.jpeg} \\
-\includegraphics[width=1.05\columnwidth]{images/n3115_decomposition.pdf}
+\includegraphics[width=0.49\columnwidth]{n3115_image.jpeg}
+\includegraphics[width=0.49\columnwidth]{n3115_unsharp.jpeg} \\
+\includegraphics[width=1.05\columnwidth]{n3115_decomposition.pdf}
 \caption{NGC 3115. 
@@
 \begin{center}
-\includegraphics[width=0.49\columnwidth]{images/n1332_image}
-\includegraphics[width=0.49\columnwidth]{images/n1332_unsharp} \\
-\includegraphics[width=1.03\columnwidth]{images/n1332_decomposition.pdf}
+\includegraphics[width=0.49\columnwidth]{n1332_image}
+\includegraphics[width=0.49\columnwidth]{n1332_unsharp} \\
+\includegraphics[width=1.03\columnwidth]{n1332_decomposition.pdf}
 \caption{NGC 1332.
@@
 The empty points are data excluded from the fit. 
-%The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
-%obtained by dividing the image by a Gaussian-smoothed version of itself. 
-%The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
-%and the ellipticity profile, $\epsilon$, 
-%along the major-axis, $R_{\rm maj}$. 
-%The black points are the observed data, which extend out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
-%The empty points are data excluded from the fit.   
-%The color lines represent the individual (PSF-convolved) model components: 
-%red = S\'ersic (spheroid), blue = S\'ersic (disc). 
-%The residual profile (data $-$ model) is shown as $\Delta \mu$. 
-%The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
-%$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
 }
@@
 \begin{center}
-\includegraphics[width=0.49\columnwidth]{images/mrk1216_image.jpeg}
-\includegraphics[width=0.49\columnwidth]{images/mrk1216_unsharp.jpeg} \\
-\includegraphics[width=1.05\columnwidth]{images/mrk1216_decomposition.pdf}
+\includegraphics[width=0.49\columnwidth]{mrk1216_image.jpeg}
+\includegraphics[width=0.49\columnwidth]{mrk1216_unsharp.jpeg} \\
+\includegraphics[width=1.05\columnwidth]{mrk1216_decomposition.pdf}
 \caption{Mrk 1216. 
@@
 red = S\'ersic (spheroid), blue = exponential (disc).
-%The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right),
-%obtained by dividing the image by a Gaussian-smoothed version of itself.
-%The bottom plots display the best-fit model of the surface brightness profile, $\mu$,
-%and the ellipticity profile, $\epsilon$,
-%along the major-axis, $R_{\rm maj}$.
-%The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$).
-%The color lines represent the individual (PSF-convolved) model components:
-%red = S\'ersic (spheroid), blue = exponential (disc).
-%The residual profile (data $-$ model) is shown as $\Delta \mu$.
-%The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations.
-%$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
 }
@@
 Spheroid luminosities were converted into stellar masses using individual, 
-but almost constant mass-to-light ratios ($\sim$$0.6$, \citealt{meidt2014-MNRAS}). \\
+but almost constant mass-to-light ratios ($\sim$$0.6$, \citealt{meidt2014}). \\
 In Figure \ref{fig:mm}, we show the galaxies Mrk 1216, NGC 1271 and NGC 1277, 
@@
 and the stellar mass-to-light ratio obtained by \cite{walsh2015}. 
-%The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition 
-%of Graham, Savorgnan \& Ciambur (\emph{in prep.}),  
-%who used an archived \emph{HST} image taken with the WFC3 and the near-infrared \emph{F160W} filter. 
 For the galaxy NGC 1277, we use the black hole mass measurement obtained by \cite{vandenbosch2012} 
 and the stellar mass-to-light ratio obtained by \cite{martinnavarro2015}. 
-%The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition of Graham et al.~(\emph{in prep.}), 
-%who used an archived \emph{HST} image taken with the Advanced Camera for Surveys (\emph{ACS}) and the \emph{F550M} filter. 
 For the galaxy Mrk 1216, we use the upper limit on the black hole mass 
 and the stellar mass-to-light ratio obtained by \cite{yildirim2015}. 
-%The luminosity of the spheroidal component of this galaxy comes from our one-dimensional spheroid/disc decomposition (Figure \ref{fig:m1216}).
 For the first time, Figure \ref{fig:mm} reveals that when the four ellicular galaxies Mrk 1216, NGC 1271, NGC 1277, NGC 1332, 
-and the elliptical galaxy NGC 4291 are properly modeled, 
+and the elliptical galaxy NGC 4291 are properly modelled, 
 they no longer appear as extreme outliers above the (black hole mass)-(spheroid stellar mass) correlation for early-type galaxies, 
 i.e.~they all reside well within a $3\sigma$ deviation from the correlation.
-
-%{\bf change: This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
-%but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
-%and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
-%used to describe the coevolution of spheroids and their central supermassive black holes. }
 
@@
 when cold gas inflows produced short and intense bursts of star formation 
-that created compact and dense conglomerates of stars with high velocity dispersion. 
+that created compact and dense conglomerates of stars with high velocity dispersion (e.g.~\citealt{prieto2013}). 
 These naked and compact conglomerates, named ``red nuggets'' \citep{damjanov2009}, 
-have been observed at high-redshift with half-light sizes of $1-2~\rm kpc$ \citep{daddi2005,trujillo2006,vandokkum2008}.
-In the second phase (last $10~\rm Gyr$), stellar discs and stellar envelopes 
-were accreted around these primordial conglomerates and the external parts of today's galaxies assembled on scales of $2-20~\rm kpc$. \\
+have been observed at high-redshift with half-light sizes of 1--2 kpc \citep{daddi2005,trujillo2006,vandokkum2008}.
+In the second phase (last $10~\rm Gyr$), discs and stellar envelopes 
+were accreted around these primordial conglomerates and the external parts of today's galaxies assembled on scales of 2--20 kpc 
+(e.g.~\citealt{driver2013}). \\
 Today's Universe is populated by an abundance of compact, massive spheroids, 
@@
 that is to say they are the bulges of some lenticular and spiral galaxies.  
-Over the last $10~\rm Gyr$ their spheroids have evolved by growing a relatively flat disc -- 
-rather than a three-dimensional envelope -- 
+Over the last $10~\rm Gyr$ their spheroids have evolved by growing a relatively flat disc (e.g.~\citealt{pichon2011,danovich2012,stewart2013})
+-- rather than a three-dimensional envelope -- 
 which has increased the galaxy size but preserved the bulge compactness. 
@@
 Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact ellicular galaxies 
-with purely old ($>10~\rm Gyr$) stellar populations. {\bf [these 4 are COMPACT elliculars, the others are non-compact elliculars]}
+with purely old ($>10~\rm Gyr$) stellar populations. 
 These galaxies have undergone the lowest degree of disc growth. \\
@@
 in disagreement with the current cosmological picture. 
-The second possibility is that only their inner bulges (with sizes of $0.1-0.2~\rm kpc$, 
+The second possibility is that only their inner bulges (with sizes of 0.1--0.2 kpc, 
 according to past decompositions) originated in the first $4~\rm Gyr$ 
@@
 if one considers these galaxies today as spheroid-dominated systems with an intermediate-scale disc; 
-in this case, both the galaxy size and the spheroid size are compact ($1-2~\rm kpc$). 
+in this case, both the galaxy size and the spheroid size are compact (1--2 kpc). 
 This implies that, among the local descendants of the high-redshift red nuggets, 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mm.pdf}
+\includegraphics[width=\columnwidth]{mm.pdf}
 \caption{Black hole mass plotted against spheroid stellar mass for 45+3 early-type galaxies (from Savorgnan et al.~2015). 
@@
 where $\sigma$ ($0.51$ dex) is the total \emph{rms} scatter about the correlation in the black hole mass direction. 
-{\bf The red symbols mark five galaxies that were claimed to be extreme outliers in this diagram: 
-four intermediate-scale disc galaxies (Mrk 1216, NGC 1271, NGC 1277 and NGC 1332) and one elliptical galaxy (NGC 4291). }
+The red symbols mark five galaxies that were claimed to be extreme outliers in this diagram: 
+four intermediate-scale disc galaxies (Mrk 1216, NGC 1271, NGC 1277 and NGC 1332) and one elliptical galaxy (NGC 4291). 
 All five reside well within a $3\sigma$ deviation from the correlation when using their correct spheroid mass. 
@@
 discs. The presence of these intermediate-scale discs also blurs the
-distinction between elliptical (E) and lenticular (S0) galaxies and
+distinction between elliptical (E) and lenticular (S0: $\epsilon = 1-b/a > 0.7$, \citealt{hubble1936,sandage1961}) galaxies and
 arguably creates the need for a new subclass which bridges this
@@
 discs will be helpful for distinguishing among 
-early-type galaxies with different disk scale-lengths, it should be
+early-type galaxies with different disc scale-lengths, it should be
 remembered that just as portions of the electromagnetic spectrum are
@@
 changing from FR to SR as the radial extent is sufficiently increased. 
-There is thus a need for more the two bins (E vs. S0, or FR vs. SR) 
-and a continuum in the (Hubble-Jeans)-like classification schemes. \\
-It has recently been argued (Graham 2014) that the classification
-scheme for elliptical galaxies should not be their apparent axis ratio
-as seen on the plane of the sky, but rather early-type galaxies should
-be quantified by their spheroid-to-total flux ratio, with a
+There is thus a need for more than two bins (E vs. S0, or FR vs. SR) 
+and a continuum in the (Hubble-Jeans)-like classification schemes \citep{vandenbergh1997,sandage2005}. \\
+It has been argued that the classification
+scheme for ``elliptical'' galaxies should not be their apparent axis ratio
+as seen on the plane of the sky (E0--E7), 
+because this depends on the viewing angle rather than being intrinsic to the galaxy. 
+Obviously when dealing with intermediate-scale discs, the boxy/discy shape of the isophotes is a function of both radius and disc inclination, 
+making a single isophote shape parameter problematic and particularly inappropriate for the classification task at hand.
+Section 4 of \cite{kormendybender1996} points out additional complications. 
+Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, with a
 continuum from pure elliptical galaxies to disc-dominated lenticular
-galaxies.  While spiral galaxies display a range of spheroid-to-total flux ratios
+galaxies (Figure \ref{fig:grid}).  \\
+While spiral galaxies display a range of spheroid-to-total flux ratios
 from 0 to $\sim$3/4 (e.g.~\citealt{grahamworley2008}, and references
@@
 ratio is widely recognised as an important quantity, and its broad range observed in
-lenticular galaxies (see \citealt{cappellari2011kmdr-MNRAS} and \citealt{kormendybender2012}) recently led to a reintroduction of 
+lenticular galaxies recently led to a re-introduction of 
 \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976})
@@
 fork, with an additional arm for disc galaxies hosting anaemic spiral
-patterns.  However because every spiral Hubble type (e.g.~Sa, Sb, Sc), not just the S0 galaxies, 
+patterns \citep{cappellari2011kmdr,kormendybender2012}.  
+However because every spiral Hubble type (e.g.~Sa, Sb, Sc), not just the S0 galaxies, 
 has a broad range of spheroid-to-total ratio, and because this information is not captured by the Hubble comb, 
@@
 
-%The existence of the oft-overlooked, intermediate-scale discs presented here exposes a likely continuum of disc sizes in early-type galaxies 
-%as opposed to a dichotomy of nuclear discs versus large-scale discs. 
-%The presence of these intermediate-scale discs also blurs the distinction between elliptical (E) and lenticular (S0) galaxies 
-%and arguably creates the need for a new subclass which bridges this divide.  
-%While expanding the galaxy nomenclature beyond ellipticals with possible nuclear discs, and lenticulars with large-scale discs, 
-%to include something like {\it elliculars} with intermediate-scale discs will be helpful 
-%for distinguishing among early-type galaxies with different disk scale-lengths, 
-%it should be remembered that just as portions of the electromagnetic spectrum are labelled according to their different wavelengths, 
-%there is still an underlying continuum.  
-%Similarly, binning early-type galaxies as either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact that a continuum exists.  
-%Importantly, in the case of early-type galaxies with intermediate-scale discs, 
-%this particular rotation-classification depends on the galaxy's radial range probed.  
-%There is thus a need for more than two bins (E vs.~S0, or SR vs.~FR). \\
-%%The existence of intermediate-scale discs is not only important for our understanding of disc growth in general, 
-%%but accounting for such components impacts upon our broader understanding of galaxy structure.  
-%It has recently been argued \citep{graham2014review} that the classification scheme for elliptical galaxies 
-%should not be their apparent axis ratio as seen on the plane of the sky, 
-%but rather early-type galaxies should be quantified by their spheroid-to-total flux ratio, 
-%with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies.   
-%While spiral galaxies display a range of spheroid-to-total flux ratios from 0 to $\sim$3/4, 
-%lenticular galaxies display a range from $\sim$3/4 to $\sim$0.1 (see \citealt{laurikainen2010}).   
-%The spheroid-to-total flux ratio is an important quantity, and its broad range observed in lenticular galaxies 
-%has led to a resurgence of \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976}) Hubble comb, 
-%in which both late-type galaxies (i.e.~spiral galaxies) and lenticular galaxies form the arms of an expanded Hubble tuning fork, 
-%with an additional arm for disc galaxies hosting anaemic spiral patterns (see \citealt{cappellari2011kmdr-MNRAS} and \citealt{kormendybender2012}).  
-%However because every spiral Hubble type (e.g.~Sa, Sb, Sc) has a broad range of spheroid-to-total ratio 
-%(e.g.~\citealt{grahamworley2008}, and references therein), 
-%and because this information is not captured by the Hubble comb, 
-%a grid of spiral type (predominantly determined by the spiral arms) versus spheroid-to-total ratio is also useful for classifying galaxies.   
-%In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale discs in such a Hubble grid \citep{graham2014review}, 
-%revealing how they are related to the other galaxies.  
-%Aside from the pure elliptical galaxies, each galaxy type displays a range of spheroid-to-total flux ratio.  
-%Rather than a scheme in which the spiral morphological type (a, b, c, etc.) changes if the spheroid-to-total ratio changes (as in the Hubble comb), 
-%here the galaxy type is linked to the nature and winding of the spiral arms which has been the primary criteria used 
-%to classify spiral galaxies over the last half century \citep{sandage1961}.
-
 \begin{figure}[h]
 \begin{center}
-\includegraphics[width=\columnwidth]{images/Hubble-grid-2/Hubblegrid.pdf}
+\includegraphics[width=\columnwidth]{Hubblegrid.pdf}
 \caption{The Hubble grid \citep{graham2014review}, 
@@
 
-\section{Conclusions}
-{\bf I'll write them after the first ref. rep. :) }
+\section{Summary and conclusions}
+Early-type galaxies display a continuous distribution of spheroid-to-total flux ratios, 
+going from disc-less, ``pure'' elliptical galaxies to disc-dominated lenticular galaxies 
+\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
+vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
+simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,
+bendersaglia1999}\footnote{Many past studies were hampered by bulge/disc decompositions which forced an $R^{1/4}$ model for the bulge component 
+and thus obtained spurious bulge-to-disc ratios, and from the \emph{IRAF} task {\tt ellipse} which does not report the correct deviations of isophotes 
+from ellipses \citep{ciambur2015}.}. 
+In between these two extremes lie galaxies with intermediate-scale discs, 
+i.e.~discs of kiloparsec-size that remain ``embedded'' within the spheroidal component of the galaxy 
+and do not dominate the galaxy light at large radii as large-scale discs do. 
+while this is likely known to some readers, 
+the surge of papers presenting galaxy decompositions which are not aware of this reality 
+has created a pressing need for this reminder. 
+For ease of reference, we have introduced the term \emph{ellicular} to designate such early-type galaxies with intermediate-scale discs. 
+We have shown that the light distribution of ellicular galaxies can be accurately described 
+with a simple spheroid + disc (+ optional nuclear component) model, 
+without the need for the addition of a bright envelope-component. \\
+Our decompositions correctly reproduce both the photometric (surface brightness and ellipticity profiles) 
+and kinematic (specific angular momentum profile) properties of nine ellicular galaxies. 
+Four of these nine ellicular galaxies (Mrk 1216, NGC 1271, NGC 1277, NGC 1332) and one additional elliptical galaxy (NGC 4291) 
+had previously been claimed to be extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
+However, here we have demonstrated that, when correctly modelled, 
+these five galaxies all reside well within the scatter of the correlation, 
+i.e. they do not host over-massive black holes. 
+This serves to strengthen the (black hole mass)-(spheroid mass) relation, 
+and rules out the need for exotic formation scenarios.
 
@@
 GS is grateful to Matteo Fossati, Luca Cortese and Giuseppe Gavazzi for useful comments and discussion. 
-This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC-MNRAS} on-board the Spitzer Space Telescope, 
+This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} on-board the Spitzer Space Telescope, 
 which is operated by the Jet Propulsion Laboratory, California Institute of Technology under a contract with NASA, 

### 2015-10-06 papers/MbhMsph/replytoreferee.txt
kry

-

- The referee is correct in saying that the last point in our Conclusion Section is not a new result and,  
  indeed, we didn't mean to deliver this result as a novelty. The Introductions of Papers I and II present 
  some points about black hole mass scaling relations that are currently under debate. One of these points 
  is the level of intrinsic scatter in the black hole mass - spheroid/galaxy luminosity correlation. Some 
  studies (e.g. Erwin & Gadotti 2012, Beifiori et al. 2012, Kormandy & Ho 2013) claimed that the spheroid 
  luminosity is a better tracer of the black hole mass, but the most recent study by Lasker et al. reported 
  that the spheroid luminosity and the galaxy luminosity are equally good proxies of the black hole mass. 
  Our work solves this controversy by showing that the spheroid luminosity and the galaxy luminosity correlate 
  equally well with the black hole mass when only early-type galaxies are considered (Lasker's sample has only 
  4 spiral galaxies). However, when the galaxy sample contains a reasonable number of spiral galaxies, the 
  correlation with the spheroid luminosity has less intrinsic scatter than that with the galaxy luminosity. 
  To our best knowledge, this has never been shown before in the literature. 
  Additional references have been added to the last point in our Conclusion Section.

- The referee is correct, and we are aware of this. Unlike many papers, we believe that we have not under-
  estimated the uncertainties associated to the bulge best-fit parameters. It is possible that some of the 
  results taken from the literature are "grossly wrong", however the exclusion of extreme outliers would 
  affect only the sigma_3 error bars, i.e. the uncertainties associated to the "grade 3" fits, which constitute 
  only 14% of all fits. The exclusion of extreme outliers would have a very small impact on the sigma_1 and 
  sigma_2 errorbars (we learned this from Savorgnan et al. 2013, where we applied a very similar method). 
  In conclusion, the exclusion of extreme outliers would decrease the uncertainties associated to 14% of 
  all galaxies, with little or no effects on the measurement of the intrinsic scatter.

- We prefer not to reference Burstein et al. because they falsely identified many discs due to poor R^(1/4) 
  decompositions.

- A footnote has been added in Section 4.3 to remind the reader why a slope~1 is consistent with a dry-merging 
  formation scenario, although it simply repeats what already stated in the Introduction.

- A (B-V) galaxy color vs. log(galaxy stellar mass) plot is attached. The early-type galaxies are seen to occupy 
  the region of the red sequence, and the spiral galaxies are located in the region of the blue cloud. 
  The correspondence between galaxy morphological type (early vs. late) and position in the color-mass diagram 
  (red sequence vs. blue cloud) is a very well estabilished result and we don't feel the need of showing this 
  (poor) diagram in the paper.

- We fully agree with the referee on this point, as extensively discussed in Section 4.2.1. We don't think that 
  classical and pseudo-bulges can be distinguished based on their Sersic index. However, this has been common 
  practice in the recent literature, and here we are showing that n<2 bulges are not offset from the correlation
  traced by n>2 bulges. The referee might appreciate that we never refereed to our n<2 bulges merely as pseudo-bulges, 
  but we always specified "claimed by some to be pseudo-bulges". In addition, in the text we have questioned the 
  n<2 criterion used by some to identify pseudo-bulges.

- We never claimed that the break of the black hole - bulge mass correlation is due to the bulge mass. 
  In the Introduction, we anticipated that, for consistency with other known scaling relations (Lsph-sigma and 
  Mbh-sigma), a bent Mbh-Lsph correlation is expected, with the bend occurring around Mbh~10^8. 
  In the Mbh-Lsph and Mbh-Msph diagrams, we identified two different sequences (early vs. late) precisely according 
  to the morphology of galaxies. Indeed, the break is caused by the galaxy morphology. 
  We did not identify pseudo-bulges with n<2 bulges. 
  In Figure 5, the red dashed line marks the correlation for ellipticals+lenticulars (as stated in the caption). 
  The correlation for ellipticals only is not shown in this Figure. The spiral galaxies can be seen not following 
  this correlation. 
  Concerns about the lack of a correlation for spiral galaxies are not correct, and have already been addressed in 
  the last paragraph of Section 4.2. The correlation for spiral galaxies has been measured and quantified with 3 
  different linear regression routines. If there was no correlation for spiral galaxies, the uncertainties associated 
  to the slope and intercept of the linear regression would be extremely large.

### 2015-10-06 papers/MbhMsph/mm.tex
holidays
kry

@@
 
-%\shorttitle{Early and late $M_{\rm BH} - M_{\rm *,sph}$ sequence}
 \shorttitle{Red and blue $M_{\rm BH} - M_{\rm *,sph}$ sequence}
@@
 \title{Supermassive black hole and host spheroid affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
-
-%\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1} and A. Marconi and E. Sani\altaffilmark{3} and L.K. Hunt}
-%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
-%\email{gsavorgn@astro.swin.edu.au}
 
@@
 thus rotation is not a definitive signature of a pseudo-bulge. 
-Furthermore, many galaxies host both a classical and a pseudo-bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
-macarthur2009,dosanjosdasilva2013,seidel2015}). 
+Furthermore, many galaxies host both a classical and a pseudo-bulge (e.g.~\citealt{erwin2003,erwin2015,
+athanassoula2005,gadotti2009,macarthur2009,erwin2010,dosanjosdasilva2013,seidel2015}). 
 In the recent literature, pseudo- and classical bulges have frequently been divided at the 
@@
 The bulges of the early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
-consistent with a dry-merging formation scenario,
+consistent with a dry-merging formation scenario\footnote{\bf In dry mergers, the black hole and the bulge grow at the same pace, 
+increasing their mass in lock steps.},
 and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
@@
       Once reasonable numbers of spiral galaxies are included, 
-      $M_{\rm BH}$ correlates better with $L_{\rm sph}$ than with $L_{\rm gal}$. 
+      $M_{\rm BH}$ correlates better with $L_{\rm sph}$ than with $L_{\rm gal}$ {\bf (see also \citealt{erwingadotti2012,beifiori2012})}. 
 \end{itemize}

### 2015-10-06 papers/data_paper/datapaper.tex
kry

@@
 \label{sec:int}
-Supermassive black holes and their host spheroids\footnote{The term ``spheroid'' refers to either an elliptical galaxy or the spheroidal component 
-of a galaxy with a disk. } 
+Supermassive black holes and their host bulges/spheroids\footnote{\bf By the term ``bulge/spheroid'' 
+we mean either an elliptical galaxy or the bulge component of disk galaxies, 
+with no attempt of distinguishing between classical and disk-like pseudo-bulges. } 
 have very different sizes. 
@@
 all of the observed scaling relations, which also have to be consistent with each other.
-%Modern semi-analytic models use the observed black hole mass scaling relations 
-%to constrain the black hole accretion rate .
 Modern hydrodynamical simulations, such as EAGLE \citep{schaye2015}, calibrate the feedback efficiencies 
@@
 If we are to properly understand the evolution of galaxies, we need to understand their components.\\
-Measuring the photometric and structural properties of a galaxy's spheroidal component requires the ability to 
-separate it from the rest of the galaxy. 
+Measuring the photometric and structural properties of a galaxy's spheroidal component 
+requires the ability to separate it from the rest of the galaxy. 
 Such galaxy decomposition involves a parametric analysis that allows one to fit the surface brightness distribution
@@
 where we provide individual descriptions of the galaxies that we analyzed. \\
-As stressed in Section \ref{sec:int}, our investigation is primarily focused on the central spheroidal components 
+{\bf As stressed in Section \ref{sec:int}, our investigation is primarily focused on the central bulge/spheroidal components 
 of galaxies. 
-We assumed \emph{a priori} that each of our galaxies has a unique spheroidal component, 
-that we modeled with a S\'ersic profile. \\
+The objects in our sample are either early-type galaxies (elliptical+lenticular), 
+or ``early-type spiral'' galaxies 
+(i.e.~the morphological classification of our spiral galaxies is within \emph{Sa-Sc}, 
+with the only exception of NGC 4945 which is classified as \emph{Scd}), 
+therefore -- by definition -- they all have a bulge/spheroidal component, 
+unlike ``late-type spiral'' galaxies that can be bulge-less (e.g.~NGC 300).   
+We modeled spheroids/bulges with a S\'ersic profile, without attempting to distinguish between classical and pseudo-bulges. } \\
 Disks were usually fit with the exponential model, 
@@
 who fit bars with a Ferrer function and inner disks with a S\'ersic model. 
-We did not find evidence of bars with exponential profiles (e.g.~\citealt{elmegreenelmegreen1985,gadotti2008,kim2015}), 
-but this might be due to the low number statistics of barred galaxies in our sample. }\\
+Our galaxy sample lacks of ``late-type spiral galaxies''.
+As expected, we did not find evidence of bars with exponential profiles (e.g.~\citealt{elmegreenelmegreen1985,gadotti2008,kim2015}), 
+which are typical of late-type spiral galaxies \citep{gadottidesouza2006}, 
+and we only modeled bars with flat profiles, which are common features of ``early-type spiral'' galaxies \citep{gadottidesouza2006}. }\\
 The presence of a nuclear component -- either resolved or unresolved -- was generally expected in 
@@
 {\bf (\citealt{wadadekar1999,ravindranath2001,peng2002} and \citealt{gadotti2008} discuss the importance of fitting nuclear components)}. \\
-Rings were identified from galaxy images and unsharp masks, and modeled with symmetric Gaussian ring profiles. \\
+Rings were identified from galaxy images and unsharp masks, and modeled with symmetric Gaussian ring profiles 
+(e.g.~\citealt{sheth2010,kim2014}). \\
 As an illustration, we consider the galaxy NGC 2974, 
@@
 The dashed line displays the 1:1 relation.
-{\bf The four most obvious outliers are NGC 821, NGC 3377, NGc 4945, and NGC 5576. 
+{\bf The four most obvious outliers are NGC 821, NGC 3377, NGC 4945, and NGC 5576. 
 Their individual cases are discussed in the Appendix. }}
@@
   This bumb cannot be easily modeled with a Ferrer function {\bf nor with a S\'ersic profile}, 
-  thus we exclude the data in the range $100'' \lesssim R_{\rm maj} \sim 400''$ form the fit.
+  thus we exclude the data in the range $100'' \lesssim R_{\rm maj} \sim 400''$ from the fit.
   We also exclude the data within the innermost $6''.4$ due to the contribution from the AGN.

### 2015-10-09 papers/MbhMsph/replytoreferee_II.txt
friday and i love u kri

--- 2015-10-06 papers/MbhMsph/replytoreferee.txt
@@
--
-
-- The referee is correct in saying that the last point in our Conclusion Section is not a new result and,  
-  indeed, we didn't mean to deliver this result as a novelty. The Introductions of Papers I and II present 
-  some points about black hole mass scaling relations that are currently under debate. One of these points 
-  is the level of intrinsic scatter in the black hole mass - spheroid/galaxy luminosity correlation. Some 
-  studies (e.g. Erwin & Gadotti 2012, Beifiori et al. 2012, Kormandy & Ho 2013) claimed that the spheroid 
-  luminosity is a better tracer of the black hole mass, but the most recent study by Lasker et al. reported 
-  that the spheroid luminosity and the galaxy luminosity are equally good proxies of the black hole mass. 
-  Our work solves this controversy by showing that the spheroid luminosity and the galaxy luminosity correlate 
-  equally well with the black hole mass when only early-type galaxies are considered (Lasker's sample has only 
-  4 spiral galaxies). However, when the galaxy sample contains a reasonable number of spiral galaxies, the 
-  correlation with the spheroid luminosity has less intrinsic scatter than that with the galaxy luminosity. 
-  To our best knowledge, this has never been shown before in the literature. 
-  Additional references have been added to the last point in our Conclusion Section.
-
 - The referee is correct, and we are aware of this. Unlike many papers, we believe that we have not under-
@@
 
-- We prefer not to reference Burstein et al. because they falsely identified many discs due to poor R^(1/4) 
-  decompositions.
+- The referee is correct in saying that the last point in our Conclusion Section is not a new result and,  
+  indeed, we didn't mean to deliver this result as a novelty. The Introductions of Papers I and II present 
+  some points about black hole mass scaling relations that are currently under debate. One of these points 
+  is the level of intrinsic scatter in the black hole mass - spheroid/galaxy luminosity correlation. Some 
+  studies (e.g. Erwin & Gadotti 2012, Beifiori et al. 2012, Kormendy & Ho 2013) claimed that the spheroid 
+  luminosity is a better tracer of the black hole mass, but the most recent study by Lasker et al. reported 
+  that the spheroid luminosity and the galaxy luminosity are equally good proxies for the black hole mass. 
+  Our work solves this controversy by showing that the spheroid luminosity and the galaxy luminosity correlate 
+  equally well with the black hole mass when only early-type galaxies are considered (Lasker's sample has only 
+  4 spiral galaxies). However, when the galaxy sample contains a reasonable number of spiral galaxies, the 
+  correlation with the spheroid luminosity has less intrinsic scatter than that with the galaxy luminosity. 
+  At our best knowledge, this has never been shown before in the literature. 
+  Additional references have been added to the last point in our Conclusion Section.
+
+- We think that the disk of the Sombrero galaxy is an intermediate-scale one. 
+  Our light profile has been truncated at 160'', but we have information about the isophotal parameters out to
+  250'' and the ellipticity profile indicates the presence of an intermediate-scale disk that may be truncated 
+  at 200''. 
+  The bulge/disk decomposition of Gadotti & Sanchez-Janssen (figure 2) uses a more extended light profile 
+  (out to 450'') and is consistent with ours. 
+  Although we did our best at scrutinizing the available literature, we unfortunately missed this work, which
+  has now been referenced in Paper I. 
+  We note that the Sombrero galaxy has been classified as S0/Sp in Paper II, therefore it has not been included 
+  in the early-type nor in the late-type bin. We consider the morphological classification of this galaxy quite 
+  challenging, in the sense that the Sombrero has the structure of a E/S0 galaxy but it also has features typical 
+  of a spiral galaxy (rings and dust at the edge of the disc; note that NED refers to the Sombrero as an Sa spiral
+  galaxy), therefore we feel it's safer to exclude it from the morphological analysis of the Mbh-M diagram.
+
+- We prefer not to reference Burstein et al. because many of their claimed discs were falsely identified 
+  due to poor R^(1/4) decompositions.
 
@@
   The correspondence between galaxy morphological type (early vs. late) and position in the color-mass diagram 
-  (red sequence vs. blue cloud) is a very well estabilished result and we don't feel the need of showing this 
+  (red sequence vs. blue cloud) is a very well established result and we don't feel the need of showing this 
   (poor) diagram in the paper. 
+  TBD ATTACH PLOT
 
@@
   practice in the recent literature, and here we are showing that n<2 bulges are not offset from the correlation
-  traced by n>2 bulges. The referee might appreciate that we never refereed to our n<2 bulges merely as pseudo-bulges, 
+  traced by n>2 bulges. The referee might appreciate that we never referred to our n<2 bulges merely as pseudo-bulges, 
   but we always specified "claimed by some to be pseudo-bulges". In addition, in the text we have questioned the 
@@
   Mbh-sigma), a bent Mbh-Lsph correlation is expected, with the bend occurring around Mbh~10^8. 
-  In the Mbh-Lsph and Mbh-Msph diagrams, we identified two different sequences (early vs. late) precisely according 
+  In the Mbh-Lsph and Mbh-Msph diagrams we identified two different sequences (early vs. late) precisely according 
   to the morphology of galaxies. Indeed, the break is caused by the galaxy morphology. 
@@
   The correlation for ellipticals only is not shown in this Figure. The spiral galaxies can be seen not following 
-  this correlation. 
+  the E+S0 correlation. 
   Concerns about the lack of a correlation for spiral galaxies are not correct, and have already been addressed in 
@@
   to the slope and intercept of the linear regression would be extremely large.  
+  Addressing the gas content of the galaxies in the Mbh-M diagram is definitely a priority for our future research, 
+  and we are planning to tackle this point with a dedicated study.

### 2015-10-09 papers/data_paper/replytoreferee_I.txt
friday and i love u kri

- The tone of the title was not meant to be presumptuous, but we now understand that it is prone to misinterpretation, 
  therefore we have modified it. The new title reads: "Galaxy vivisection".

- We agree that some disk galaxies, like NGC 300, can be bulge-less. However, all galaxies in our sample are either 
  ellipticals/lenticulars or early-type spirals (Sa-Sc), with the only exception of NGC 4945 (Scd). 
  By definition, these galaxies have a spheroid/bulge component, which is what we modelled with a Sersic profile, 
  without attempting to distinguish between classical and pseudo-bulges. The text in Section 3.5 was actually misleading 
  and has been modified.
  Throughout the text, we used the terms "spheroid" and "bulge" as synonims, although we recognize that some bulges are 
  "disk-like" rather than "spheroidal-like". This point has now been clarified in Footnote 1.

- We did not attempt to fit down- or up-bendings of large-scale disks. We scrutinized the 
  available literature for all individual galaxies, and we paid particular attention to the papers that recorded disk breaks. 
  The surface brightness profiles of galaxies that present this feature were truncated well before the occurence of the 
  bending. This was not explicit in the text, and we now added a sentence at the end of Section 3.1.

- The 1D equivalent axis fit does account for the varying ellipticity because the equivalent 
  axis is calculated as Req = Rmaj * (1-ellipticity)^0.5. 
  M87 has a strong ellipticity gradient. The 2D model cannot account for this gradient, and this can be seen in the 2D 
  residual image which looks like a "butterfly pattern". 
  Ideally, galaxies should be fit in 3D, rather than 2D or 1D. 
  However, because the 1D fit tracks the changes in the observed P.A. and ellipticity, the geometric mean axis 
  (equivalent to a circularised axis) enables one to accurately recover the total and component magnitudes 
  in a way that the 2D model cannot.

- The text in Section 3.5 was not accurate, and we have now clarified this point. All bars have been fit with a Ferrer function, 
  except for NGC 4151 where we preferred to use a Sersic model. Disk-like components embedded in the bulges/spheroids have 
  been fit with a low-n Sersic profile and, in a few cases (when the Sersic model was degenerate with the other model-
  components), with a Ferrer function. 
  Gadotti & De Souza (2006) report that flat bars are typical of earlier type spirals, whereas exponential bars are common 
  in later type spirals. This is in agreement with our findings: our galaxy sample lacks of later-type spirals and we did 
  not detect any bar with an exponential profile.

- Sheth et al. (2010, the paper that presents the S4G collaboration) refers to Jun & Im (2008) to point out that the 3.6 um
  band is indeed a better tracer of the stellar mass than the K-band, which still suffers from dust absorption (Driver et al.
  2008, 678, L101).

- In Figure 7 we compared the 2D Sersic indices with the 1D equivalent-axis Sersic indices. These two quantities are not 
  expected to be exactly the same, but they should be approximatively similar. There are four most obvious outliers in this 
  plot: NGC 821, NGC 3377, NGC 4945, and NGC 5576. Their individual cases are discussed in the Appendix. 
  For M87, the 2D Sersic index (4.3) and the 1D equivalent-axis Sersic index (5.9) are in fairly good agreement. 
  The large discrepancy between the M87's 1D major-axis Sersic index and the other two measurements is due to the strong ellipticity
  gradient that this galaxy has. In fact, the 2D model cannot account for such gradient (whereas the 1D equivalent-axis fit can) 
  and the 2D residuals show a significant ``butterfly'' feature caused by this well-understood problem.

- The aim of this work is to investigate scaling relations between the black hole mass, Mbh, and several properties, X, of the host 
  spheroid/bulge. These correlations are commonly expressed as power laws: Mbh \propto X^a, i.e. log(Mbh) = a*log(X) + b. 
  Therefore we are interested in the logarithmic values of the Sersic indices and effective radii, along with their associated 
  uncertainties.

- The point that Footnote 2 was trying to make is the following. Sani et al., Vika et al. and Beifiori et al. did not find a 
  correlation between black hole mass and Sersic index. However, after averaging their Sersic indices together, a strong correlation
  was recovered. This is telling us that the measurements obtained by the individual authors were "noisy", i.e. non accurate. 
  Averaging the Sersic indices together reduces the noise and shows that the black hole mass is indeed correlated to the Sersic 
  index. However, we removed the second sentence of Footnote 2; we will come back to this point in a future paper.

- The claim about the anti-truncation of NGC 4459 has been clarified in the Appendix.

- Thanks for pointing out the missing reference to Erwin & Gadotti (2012), which has now been added.

- The Spitzer cookbook does not explain why the overlap correction is not recommended for 3.6 um images, it just states so. 
  It might be that the cookbook does not consider mosaicking images belonging to different "Astronomical Observation Requests", 
  for which we found that the overlap correction was needed to remove the chessboard effect.

- We did check that the PSF does not significantly vary across the various mosaics. In each mosaic, we selected up to 10 bright 
  non-saturated stars and we characterized them with a Moffat function (using IRAF imexamine). For each mosaic, we averaged 
  together the best-fit parameters of the stars and obtained an average FWHM and beta (the PSF parameters specific of each mosaic). 
  The variation of the Moffat FWHM across all mosaics is +-0''.1; the variation of the Moffat beta is +-2.0.
  The use of a universal PSF is justified for the following reasons: 
  i) the PSF-convolution is way more sensitive to the value of the FWHM than beta, therefore having a 50% variation in beta is 
  not an issue as long as the variation in FWHM is small;
  ii) the use of a non-signal-to-noise-weighted fitting scheme minimizes biases from a non-accurate PSF description;
  iii) not all mosaics have enough stars suitable for PSF characterization; rather than having an individual PSF for each mosaic 
  (which would have been based on only 1-2 stars for some mosaics), we preferred using a universal PSF;
  iv) the IRAC instrument handbook guarantees a pretty stable PSF across time.

- A reference to Gadotti (2008) has been added in Section 3.5.

- Regarding the comment on weighting schemes in Section 3.3, we attach two simple, but hopefully illustrative figures. 
  In both figures, the left hand panel shows a perfect R^(1/4) profile.
  In one figure no weighting scheme is used, while in the other a signal-to-noise-weighting scheme is used. 
  The results of the fit are the same. 
  Now in the right hand-panel, exactly the same partially depleted core has been introduced in both figures.  
  When the R^(1/4) model is fit with the different weighting schemes, the signal-to-noise-weighted scheme can be seen to perform worse.  
  In fact, any central deviation from the assumed model (in this case an R^(1/4) model, but we could have used a Sersic model) 
  results in the signal-to-noise-weighted fitting scheme performing worse.  
  Such deviations arise from: additional star clusters, dust, depleted cores, AGN, non accurate PSF, etc.  
  Unless one correctly accounts for all of these things (which realistically doesn't happen), then the signal-to-noise-weighted scheme 
  performs worse than a scheme with no weighting when it comes to matching the global light profile. 
  ATTACH FIGURES TBD

- References to Sheth et al. and Kim et al. have been added.

- The contrast in Figure 5 was indeed not appropriate and has been adjusted.

- Section 4.2.1, item 2: the typo has been corrected.

- Section 4.2.2: a sentence has been added to explain the different sigma symbols.

- The edge-on disc of NGC 1332 is clearly identified in the galaxy image. The ellipticity profile of the galaxy isophotes indicates 
  that the disc is intermediate-scale. We modified the caption of Figure 35 to better illustrate this point.

- The fourth paragraph of Section 3.5 explains how we decided to include a nuclear component in our models.

- We tried to model the bar of NGC 4945 with a Ferrer function or a Sersic model, but we did not obtain a satisfactory result. 
  We now realize that NGC 4945 is the only later type (Scd) spiral galaxy in our sample, and its bar might might not be well described 
  by a Ferrer function. However, a Sersic model did not provide a good fit of the bar either. It is likely that the edge-on 
  inclination of the galaxy complicated the extraction of the surface brightness profile with ELLIPSE. 
  Our best solution is still to exclude the data in the range where the bar dominates the light and model only the bulge and the 
  large-scale disk. We note that we classified the fit of this galaxy as "grade 2".

- Kormendy & Ho (2013) did not perform bulge/disk decompositions for their galaxies, but they collected results from various sources 
  in the literature. We wanted to compare the results from our decompositions with the results from other systematic studies that 
  performed galaxy modelling in a consistent way.

### 2015-10-09 papers/MbhMsph/mm.tex
friday and i love u kri

@@
 
-%\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
-\title{Supermassive black hole and host spheroid affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
+\title{Supermassive black holes and their host spheroids \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
 
@@
 bulge, disks, spiral arms, bars, rings, halo, extended or unresolved nuclear source and partially depleted core. 
-Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
+Kinematical information \citep{atlas3dIII,scott2014,arnold2014} was used 
 to confirm the presence of rotationally supported disk components in most early-type (elliptical + lenticular) galaxies, 
@@
 In fact, when performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well spatially resolved -- galaxies, 
-errors are dominated by systematics rather than Poisson noise.} 
+errors are dominated by systematics rather than Poisson noise. 
+{\bf Unlike many papers, we believe that we have not under-estimated the uncertainties associated to the bulge best-fit parameters.} } 
 on the bulge magnitudes, and presents the individual 66 galaxy decompositions, 
@@
 and it is now commonly accepted that most ``elliptical'' galaxies contain disks. 
-%More than half of all morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS,krajnovic2013}.
-%\cite{krajnovic2013} showed that ``fast rotators'' as a class are disk-galaxies or at least disk-like galaxies. 
-%In their magnitude-limited survey, systems 
-%without any signature of disk-like components (neither in the kinematics nor in the photometry) 
-%dominate only the most massive end (beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
 Past studies that investigated the $L_{\rm sph} - \sigma$ diagram might have failed to identify and consequently model the disks 
@@
 For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
-and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
+and bars can spin-up classical bulges (e.g.~\citealt{saha2012,saha2015}), 
 thus rotation is not a definitive signature of a pseudo-bulge. 
@@
 consistent with a dry-merging formation scenario\footnote{\bf In dry mergers, the black hole and the bulge grow at the same pace, 
-increasing their mass in lock steps.},
+increasing their mass in lock step.},
 and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 

### 2015-10-09 papers/data_paper/datapaper.tex
friday and i love u kri

@@
 \label{sec:int}
-Supermassive black holes and their host bulges/spheroids\footnote{\bf By the term ``bulge/spheroid'' 
-we mean either an elliptical galaxy or the bulge component of disk galaxies, 
-with no attempt of distinguishing between classical and disk-like pseudo-bulges. } 
+Supermassive black holes and their host spheroids\footnote{\bf By the term ``spheroid'' 
+we mean either an elliptical galaxy or the bulge component of a disk galaxy, 
+with no attempt at distinguishing between classical bulges and disk-like pseudo-bulges. } 
 have very different sizes. 
@@
 disturbed morphology in the galaxy outskirts, etc.). 
-{\bf In particular, we did not attempt to fit down- or up-bendings of large-scale disks 
+{\bf In particular, we did not attempt to fit bends or truncations of large-scale disks 
 (e.g.~\citealt{erwin2005,erwin2008,erwin2012,gutierrez2011,comeron2012,munozmateos2013,kim2014}) 
-by truncating the surface brightness profiles well before the occurrence of these features. }
+but instead truncated the surface brightness profiles before the occurrence of such features. }
 Individual cases are discussed in Section \ref{sec:indgal}.
@@
 where we provide individual descriptions of the galaxies that we analyzed. \\
-{\bf As stressed in Section \ref{sec:int}, our investigation is primarily focused on the central bulge/spheroidal components 
+{\bf As stressed in Section \ref{sec:int}, our investigation is primarily focused on the central spheroidal components 
 of galaxies. 
@@
 therefore -- by definition -- they all have a bulge/spheroidal component, 
-unlike ``late-type spiral'' galaxies that can be bulge-less (e.g.~NGC 300).   
+unlike ``late-type spiral'' galaxies that can be bulgeless (e.g.~NGC 300).   
 We modeled spheroids/bulges with a S\'ersic profile, without attempting to distinguish between classical and pseudo-bulges. } \\
@@
 that fades toward larger radii. 
-{\bf Savorgnan \& Graham (\emph{submitted}) extensively discuss the topic of galaxies with intermediate-scale disks 
+{\bf \cite{savorgnangraham2015ellicular} extensively discuss the topic of galaxies with intermediate-scale disks 
 and show that, when these disks are misclassified and modeled as large-scale disks, 
@@
 {\bf As noted, we were able to successfully fit bars with a Ferrer function 
-(NGC 4151 is the only case for which we described the bar with a $n \sim 0.2$ S\'ersic model). 
-Disk-like components embedded in the bulges of spiral galaxies were described with a $n \lesssim 1$ S\'ersic model or, 
-in a few cases, with a Ferrer function\footnote{\bf The advantage of choosing a Ferrer function over a S\'ersic profile 
+(NGC 4151 is the only case for which we described the bar with an $n \sim 0.2$ S\'ersic model). 
+Disk-like components embedded in the bulges of spiral galaxies were described with an $n \lesssim 1$ S\'ersic model or, 
+in a few cases, with a Ferrer function\footnote{\bf One advantage of choosing a Ferrer function over a S\'ersic profile 
 to fit a disk-like component embedded in the bulge 
@@
 who fit bars with a Ferrer function and inner disks with a S\'ersic model. 
-Our galaxy sample lacks of ``late-type spiral galaxies''.
-As expected, we did not find evidence of bars with exponential profiles (e.g.~\citealt{elmegreenelmegreen1985,gadotti2008,kim2015}), 
-which are typical of late-type spiral galaxies \citep{gadottidesouza2006}, 
-and we only modeled bars with flat profiles, which are common features of ``early-type spiral'' galaxies \citep{gadottidesouza2006}. }\\
+Given that our galaxy sample lacks ``late-type spiral'' galaxies, 
+it is not surprising \citep{gadottidesouza2006} that we did not find bars with exponential profiles 
+(e.g.~\citealt{elmegreenelmegreen1985,gadotti2008,kim2015}).
+The bars in our sample were found to have rather flat inner profiles, 
+as is commonly found for bars in ``early-type spiral'' galaxies \citep{gadottidesouza2006}. } \\
 The presence of a nuclear component -- either resolved or unresolved -- was generally expected in 
@@
 thus they cannot account for these radial gradients. 
-This problem is overcome with 1D decomposition techniques.
+This problem is overcome with 1D decomposition techniques 
+{\bf because the ellipticity, and additionally the deviations from elliptical isophotes, 
+are efficiently included in the equivalent-axis fit (see the Appendix of \citealt{ciambur2015})}.
 \item The interpretation of the residual surface brightness profile is often crucial to identify the optimal decomposition for a galaxy. 
@@
 for our measurements of $\log(n_{\rm sph})$ obtained from ``grade 1'', ``grade 2'' and ``grade 3'' fits, respectively. 
-{\bf This means that, if the fit of a galaxy was classified as ``grade 1'', 
+{\bf This means that, if the fit to a galaxy was classified as ``grade 1'', 
 the (logarithmic) value of the spheroid S\'ersic index $\tilde{n}_{\rm sph}$ and associated uncertainties would be 
 $\log(\tilde{n}_{\rm sph})^{+\sigma_1^+}_{-\sigma_1^-} = \log(\tilde{n}_{\rm sph})^{+0.06}_{-0.08}$; 
-if the fit of that galaxy was classified as ``grade 2'', 
+if the fit to that galaxy was classified as ``grade 2'', 
 then one would have $\log(\tilde{n}_{\rm sph})^{+\sigma_2^+}_{-\sigma_2^-} = \log(\tilde{n}_{\rm sph})^{+0.17}_{-0.21}$, 
@@
   and the most obvious elongated feature of this galaxy is modeled with a Ferrer function. 
+  The ellipticity profile indicates that the disk is of intermediate-scale 
+  {\bf (for a thorough analysis of this galaxy, see \citealt{gadottisanchezjanssen2012})}.
   }

### 2015-10-16 papers/data_paper/ApJ_submission_2/replytoreferee_I.txt
grampians

--- 2015-10-09 papers/data_paper/replytoreferee_I.txt
@@
+Dear Lee,
+
+The referee's comments and suggestions have been very useful and helped improve the quality of the manuscript. 
+We have addressed all the points listed in the reviewer's report. Below are our responses to the report. 
+The title of the paper has been modified, as suggested by the referee, and all changes to the text have been printed 
+in bold face.
+
+Kind regards,
+
+Giulia Savorgnan
+
+RESPONSES TO THE REVIEWER'S REPORT:
+
 - The tone of the title was not meant to be presumptuous, but we now understand that it is prone to misinterpretation, 
@@
   and has been modified.
-  Throughout the text, we used the terms "spheroid" and "bulge" as synonims, although we recognize that some bulges are 
+  Throughout the text, we used the terms "spheroid" and "bulge" as synonyms, although we recognize that some bulges are 
   "disk-like" rather than "spheroidal-like". This point has now been clarified in Footnote 1.
 
-- We did not attempt to fit down- or up-bendings of large-scale disks. We scrutinized the 
-  available literature for all individual galaxies, and we paid particular attention to the papers that recorded disk breaks. 
-  The surface brightness profiles of galaxies that present this feature were truncated well before the occurence of the 
-  bending. This was not explicit in the text, and we now added a sentence at the end of Section 3.1.
+- We did not attempt to fit down- or up-bendings of large-scale disks. We scrutinized the available literature for all 
+  individual galaxies, and we paid particular attention to the papers that recorded disk breaks. 
+  The surface brightness profiles of galaxies that present this feature were truncated well before the occurrence of the 
+  bending. This was not explicit in the text, and we have now added a sentence at the end of Section 3.1.
 
-- The 1D equivalent axis fit does account for the varying ellipticity because the equivalent 
-  axis is calculated as Req = Rmaj * (1-ellipticity)^0.5. 
+- The 1D equivalent axis fit does account for the varying ellipticity because the equivalent axis is calculated as 
+  Req = Rmaj * (1-ellipticity)^0.5. 
   M87 has a strong ellipticity gradient. The 2D model cannot account for this gradient, and this can be seen in the 2D 
   residual image which looks like a "butterfly pattern". 
-  Ideally, galaxies should be fit in 3D, rather than 2D or 1D. 
-  However, because the 1D fit tracks the changes in the observed P.A. and ellipticity, the geometric mean axis 
-  (equivalent to a circularised axis) enables one to accurately recover the total and component magnitudes 
-  in a way that the 2D model cannot.
+  Ideally, galaxies should be fit in 3D, rather than 2D or 1D. However, because the 1D fit tracks the changes in the 
+  observed P.A. and ellipticity, the geometric mean axis (equivalent to a circularized axis) enables one to accurately 
+  recover the total and component magnitudes in a way that the 2D model cannot.
 
@@
   uncertainties. 
+  In addition, the Sersic index is the "exponent" in the Sersic equation, and that one needs to deal with the log of this quantity.  
+  A fixed change in n is very different depending on the value of n, for example 2+/-1 results in a much greater change to the profile 
+  than 10+/-1.
 
@@
   It might be that the cookbook does not consider mosaicking images belonging to different "Astronomical Observation Requests", 
-  for which we found that the overlap correction was needed to remove the chessboard effect.
+  for which we found that the overlap correction was needed to remove the chess-board effect.
 
@@
   performs worse than a scheme with no weighting when it comes to matching the global light profile.
-  ATTACH FIGURES TBD
 
@@
 
-- The fourth paragraph of Section 3.5 explains how we decided to include a nuclear component in our models.
+- The fifth paragraph of Section 3.5 explains how we decided to include a nuclear component in our models.
 
 - We tried to model the bar of NGC 4945 with a Ferrer function or a Sersic model, but we did not obtain a satisfactory result. 
-  We now realize that NGC 4945 is the only later type (Scd) spiral galaxy in our sample, and its bar might might not be well described 
+  We now realize that NGC 4945 is the only later type (Scd) spiral galaxy in our sample, and its bar might not be well described 
   by a Ferrer function. However, a Sersic model did not provide a good fit of the bar either. It is likely that the edge-on 
@@
   performed galaxy modelling in a consistent way.
+
+And finally, I'd like to say thanks for the kind words at the beginning of the report. 
+It is actually "refreshing" for myself to see that our effort is acknowledged by someone that fully understands the problematic 
+involved in galaxy decomposition, so thanks a lot for the encouragement!

### 2015-10-16 papers/MbhMsph/ApJ_submission/mm.tex
grampians

@@
 
-%\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
-\title{Supermassive black hole and host spheroid affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
-
-%\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1} and A. Marconi and E. Sani\altaffilmark{3} and L.K. Hunt}
-%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
-%\email{gsavorgn@astro.swin.edu.au}
+\title{Supermassive black holes and their host spheroids \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
 
@@
 These mean statistical bulge-to-total ratios were obtained from the results of two-component (S\'ersic-bulge/exponential-disk) decompositions in the literature. \\
-%It should also be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
-%and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies (lenticulars and spirals). \\
-%Several recent papers \citep{jiang2011a,jiang2013,mathur2012,reines2013} claimed an offset at the low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ diagram,
-%such that the black hole mass is lower than expected from the near-linear correlation traced by the high-mass, early-type spheroids. 
-%However, \cite{grahamscott2013} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
-%are not randomly offset from such near-linear correlation, 
-%but follow the steeper relation traced by the S\'ersic spheroids. 
-%Using bulge/disk decomposition data from \cite{jiang2011a}, 
-%\cite{grahamscott2015} derived the host spheroid masses 
-%and showed that the steeper $M_{\rm BH} - M_{\rm *,sph}$ extends to these spheroids with even lower black hole masses 
-%($10^{5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 2 \times 10^{6}$), 
-%and a more detailed analysis will be presented in Graham et al. (2015, \emph{in preparation}).  \\
 Here we investigate in more detail %substructure in 
@@
 and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
-%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
-%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
 Because the value of the intrinsic scatter depends on the size of the uncertainties associated with the absolute magnitudes\footnote{The 
@@
 but not for all (early+late-type) galaxies.
-%We decided to vary only the errors associated to $L_{\rm gal}$ 
-%because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
-%that takes into account the systematic errors related to the galaxy decomposition process. 
-%We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
-%have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
-%Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
-%and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
-%we conclude that our determination of the intrinsic scatter is reliable, 
-%and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
-%As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
-%than performing accurate galaxy decompositions to obtain bulge luminosities. 
-%This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
-%to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.
 
@@
                         & mFITEXY Bisector & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
-                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.10$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]
-
-%Late-type (Sp) (13) & BCES $(Y|X)$      & $7.37 \pm 0.17$ & $-0.33 \pm 0.87$   & $-24.39$ & $-$ & $0.65$ \\
-%                    & BCES $(X|Y)$      & $7.37 \pm 1.97$ & $-21.66 \pm 53.74$ & $-24.39$ & $-$ & $7.73$ \\
-%                    & BCES Bisector     & $7.37 \pm 0.20$ & $-1.32 \pm 0.94$   & $-24.39$ & $-$ & $0.77$ \\
-%                    & FITEXY $(Y|X)$    & $7.38^{+0.17}_{-0.18}$ & $-0.34^{+0.74}_{-0.80}$ & $-24.39$ & $0.63^{+0.19}_{-0.11}$ & $0.65$ \\
-%                    & FITEXY $(X|Y)$    & $$ & $$ & $-24.39$ & $$ & $$ \\
-%                    & FITEXY Bisector   & $$ & $$ & $-24.39$ & $-$    & $$ \\
-%                    & {\tt linmix\_err} $(Y|X)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
-%                    & {\tt linmix\_err} $(X|Y)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
-%                    & {\tt linmix\_err} Bisector    & $$ & $$ & $-24.39$ & $-$    & $$ \\
-
-%All (62)               & BCES $(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
-%                       & BCES $(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
-%                       & BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
-%                       & FITEXY $(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
-%                       & FITEXY $(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
-%                       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
-%                       & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\
-%                       & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\
-%                       & {\tt linmix\_err} Bisector    & $$ & $$ & $$ & $-$    & $$ \\
+                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.05$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]
 
@@
 For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
-and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
+and bars can spin-up classical bulges (e.g.~\citealt{saha2012,saha2015}), 
 thus rotation is not a definitive signature of a pseudo-bulge. 
-Furthermore, many galaxies host both a classical and a pseudo-bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
-macarthur2009,dosanjosdasilva2013,seidel2015}). 
+Furthermore, many galaxies host both a classical and a pseudo-bulge (e.g.~\citealt{erwin2003,erwin2015,
+athanassoula2005,gadotti2009,macarthur2009,erwin2010,dosanjosdasilva2013,seidel2015}). 
 In the recent literature, pseudo- and classical bulges have frequently been divided at the 
@@
               & mFITEXY Bisector  & $7.72^{+0.11}_{-0.11}$ & $-0.61^{+0.10}_{-0.12}$ & $-22.92$ & $-$                    & $0.71$ \\
-              & {\tt linmix\_err} Bisector & $7.73 \pm 0.12$ & $-0.62 \pm 0.15$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
-
-%Ellipticals (E) (30)   & BCES $(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
-%                      & BCES $(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
-%                      & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
-%                      & FITEXY $(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
-%                      & FITEXY $(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
-%                      & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
-%
-%Lenticulars (S0) (13)  & BCES $(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
-%                      & BCES $(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
-%                      & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
-%                      & FITEXY $(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
-%                      & FITEXY $(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
-%                      & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
-%
+              & {\tt linmix\_err} Bisector & $7.73 \pm 0.12$ & $-0.62 \pm 0.09$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
 
@@
 The bulges of the early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
-consistent with a dry-merging formation scenario,
+consistent with a dry-merging formation scenario\footnote{\bf In dry mergers, the black hole and the bulge grow at the same pace, 
+increasing their mass in lock step.},
 and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
@@
 slope $= 2.28^{+1.67}_{-1.01}$.
-%The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
 More data would be welcome to better constrain the slope of this \emph{late-type sequence}, 
@@
       and to our \emph{late-type sequence} as a \emph{blue sequence}. 
-      %For analogy with the color-magnitude diagram, 
-      %it may be tempting to refer to our \emph{early-type sequence} as a \emph{red sequence} 
-      %and to our \emph{late-type sequence} as a \emph{blue sequence}.
-      %Future work will explore the color of spheroids and galaxies in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.  
 \item The median $M_{\rm BH}/M_{\rm *,sph}$ ratio for the early-type galaxies is $0.68 \pm 0.04\%$. 
@@
 \acknowledgments
-GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. \\
-% referee thank you!!
+GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. 
+{\bf We thank the anonymous referee for their thorough review and highly appreciate the comments and suggestions, 
+which significantly contributed to improving the quality of the publication. } \\
 This research was supported by Australian Research Council funding through grants

### 2015-10-16 papers/data_paper/ApJ_submission_2/datapaper.tex
grampians

--- 2015-10-09 papers/data_paper/datapaper.tex
@@
 in conjunction with the IRAF task 
-{\tt mskregions}. %\footnote{{\tt mskregions} is part of the {\tt proto} package.}.
+{\tt mskregions}. 
 We identified and carefully masked not only contaminating sources located in the field of the image mosaic,
@@
 \subsubsection{1D PSF}
-A universal, average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
-A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
+A universal\footnote{\bf Across all mosaics, the variation of the Moffat $FWHM$ is $\pm 0''.1$, 
+and the variation of the Moffat $\beta$ is $\pm 2.0$.
+The use of a universal PSF is justified for the following reasons: 
+\emph{i}) the PSF-convolution is more sensitive to the value of the $FWHM$ than $\beta$, 
+i.e. having a 50\% variation in $\beta$ is not an issue as long as the variation in $FWHM$ is small;
+\emph{ii}) the use of a non-signal-to-noise-weighted fitting scheme minimizes biases from a non-accurate PSF description;
+\emph{iii}) not all mosaics have enough stars suitable for the PSF characterization: 
+rather than having an individual PSF for each mosaic (which would have been based on only 1-2 stars for some mosaics), 
+we preferred the use of a universal PSF.}, 
+average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
+A nonlinear least squares \cite{moffat1969} profile\footnote{The \citep{moffat1969} profile 
 has the following form:
@@
 \begin{center}
-\includegraphics[width=1\columnwidth, trim = 240 40 50 20, clip=True]{images/psf.eps}
-%\includegraphics[width=1\columnwidth]{images/star1_cut.eps} \\
-%\includegraphics[width=1\columnwidth]{images/PRF_IRACch1_129_129_cut.eps}
+\includegraphics[width=1\columnwidth, trim = 240 40 50 20, clip=True]{psf.eps}
 \caption{Normalized flux versus radial distance 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/n2974_imgmsk.jpeg}
-\includegraphics[width=\columnwidth]{images/n2974_unsharp.jpeg}
-\includegraphics[width=\columnwidth]{images/n2974_model.jpeg}
-\includegraphics[width=\columnwidth]{images/n2974_resid.jpeg}
+\includegraphics[width=\columnwidth]{n2974_imgmsk.eps}
+\includegraphics[width=\columnwidth]{n2974_unsharp.eps}
+\includegraphics[width=\columnwidth]{n2974_model.eps}
+\includegraphics[width=\columnwidth]{n2974_resid.eps}
 \caption{Image of the galaxy NGC 2974 with its mask (top panel, {\bf on a logarithmic scale}), 
@@
 their galaxy samples significantly overlap with ours. \\
-%In Section \ref{sec:indgal} we discuss individual cases, explaining the discrepancies between different decompositions. \\
 Table \ref{tab:fitres} lists the results from both the 1D and 2D fits.
@@
 we compare with their 1D parameters in Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}.
-%The software \textsc{Imfit} returns major-axis measurements of effective radii, 
-%which are plotted in Figure \ref{fig:re1d2d} versus the corresponding 1D major-axis measurements.
-%2D measurements of S\'ersic indices can be approximated to 1D equivalent-axis measurements, 
-%and are therefore compared to them in Figure \ref{fig:n1d2d}.
-%Figure \ref{fig:mag1d2d} shows 2D versus 1D measurements of bulge magnitudes. 
 The agreement between 1D and 2D effective radii and magnitudes is remarkable, 
@@
 \subsubsection{Uncertainties on $n_{\rm sph}$}
-%\label{sec:sigman}
 In Figure \ref{fig:compn}, for 58 galaxies, 
@@
 
-\begin{figure}%[h]
-\begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
+\begin{figure}
+\begin{center}
+\includegraphics[width=1.1\columnwidth]{comparison_all_n.eps} 
 \caption{Bottom panel: 58 galaxies for which at least one measurement of the spheroid S\'ersic index $n_{\rm sph}$ is available 
@@
 
-\begin{figure}%[h]
-\begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_r_e.eps} 
+\begin{figure}
+\begin{center}
+\includegraphics[width=1.1\columnwidth]{comparison_all_r_e.eps} 
 \caption{Bottom panel: 52 galaxies for which at least one measurement of the spheroid major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
@@
 
-\begin{figure}%[h]
-\begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_mag_sph.eps} 
+\begin{figure}
+\begin{center}
+\includegraphics[width=1.1\columnwidth]{comparison_all_mag_sph.eps} 
 \caption{Bottom panel: 51 galaxies for which at least one measurement of the spheroid apparent magnitude $m_{\rm sph}$ 
@@
 
-\begin{figure}%[h]
-\begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_e.eps} 
+\begin{figure}
+\begin{center}
+\includegraphics[width=1.1\columnwidth]{comparison_all_mu_e.eps} 
 \caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid effective surface brightness $\mu_{\rm e,sph}$ 
@@
 
-\begin{figure}%[h]
-\begin{center}
-\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_0.eps} 
+\begin{figure}
+\begin{center}
+\includegraphics[width=1.1\columnwidth]{comparison_all_mu_0.eps} 
 \caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid central surface brightness $\mu_{\rm 0,sph}$ 
@@
 
-\begin{table*}%[ht] 
+\begin{table*}
 \begin{center}  				      
@@
 \hline
-              & {\bf GD07}  & {\bf S+11}   & {\bf V+12} & {\bf B+12}   & {\bf L+14} & {\bf This work}	      \\ %%[0.5ex] 
+              & {\bf GD07}  & {\bf S+11}   & {\bf V+12} & {\bf B+12}   & {\bf L+14} & {\bf This work}	      \\ 
 \hline
@@
 {\bf Other components}  	   & no 	     & no 	       & no	 & no	       & yes	 & yes  	    \\ 
-{\bf Kinematics}        	   & no 	     & no	       & no	 & no	       & no	 & yes  	    \\ %%[0.5ex] 
+{\bf Kinematics}        	   & no 	     & no	       & no	 & no	       & no	 & yes  	    \\  
 \hline 
@@
 
-%{\bf Lasker's conclusions are: bulge+disk decompositions are not enough, we do better by adding bars, spiral arms and stuff (really?? what a surprising conclusion);
-%we modelled the envelope of 5 galaxies; we observed central light deficits in 9 ellipticals; total magnitudes are independent from details of modelling (no, really?)
-%and bulge magnitudes are 0.36 mag fainter when additional components (other than bulge and disk) are modelled.  }
-
-%\clearpage
-
 \acknowledgments
@@
 and Gonzalo Diaz 
-for useful discussion. \\
+for useful discussion. 
+{\bf We thank the anonymous referee for their thorough review and highly appreciate the comments and suggestions, 
+which significantly contributed to improving the quality of the publication. } \\
 This research was supported by Australian Research Council funding through grants
@@
   The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
-  This galaxy also has an unresolved partially depleted core \citep{rusli2013}.  % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
+  This galaxy also has an unresolved partially depleted core \citep{rusli2013}.  
   Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.

### 2015-10-16 papers/data_paper/datapaper.tex
grampians

@@
 \includegraphics[width=1\columnwidth, trim = 240 40 50 20, clip=True]{images/psf.eps}
-%\includegraphics[width=1\columnwidth]{images/star1_cut.eps} \\
-%\includegraphics[width=1\columnwidth]{images/PRF_IRACch1_129_129_cut.eps}
 \caption{Normalized flux versus radial distance 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/n2974_imgmsk.jpeg}
-\includegraphics[width=\columnwidth]{images/n2974_unsharp.jpeg}
-\includegraphics[width=\columnwidth]{images/n2974_model.jpeg}
-\includegraphics[width=\columnwidth]{images/n2974_resid.jpeg}
+\includegraphics[width=\columnwidth]{images/n2974_imgmsk.eps}
+\includegraphics[width=\columnwidth]{images/n2974_unsharp.eps}
+\includegraphics[width=\columnwidth]{images/n2974_model.eps}
+\includegraphics[width=\columnwidth]{images/n2974_resid.eps}
 \caption{Image of the galaxy NGC 2974 with its mask (top panel, {\bf on a logarithmic scale}), 
@@
 
-\begin{figure}%[h]
+\begin{figure}
 \begin{center}

### 2015-10-16 papers/ellicular/ellicular.tex
grampians

@@
 
-\title[Ellicular galaxies]{Ellicular galaxies and their (non over-massive) black holes}
+%\title[Non over-massive black holes in early-type galaxies]{Early-type galaxies with intermediate-scale discs and their (non over-massive) black holes}
+\title[Non over-massive black holes in early-type galaxies]{Non over-massive black holes in early-type galaxies with intermediate-scale discs}
 
@@
 \begin{abstract}
-The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies, 
-with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
-Theoretically, the spheroid-to-disc flux ratio can assume any positive value,  
+{\bf The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
+%with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
+Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
 but in practice studies often consider only spheroid/disc decompositions 
@@
 creating an inner ``bulge'' as observed in most spiral galaxies. 
-Here we reveal that decompositions in which the disc remains embedded within the spheroid, labelled by some as ``unphysical'',  
-correctly reproduce both the photometric and kinematic properties of a class of early-type galaxy 
-intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
-Ellicular galaxies have often been confused with lenticular galaxies, 
-such that their spheroid luminosities have been considerably underestimated. 
+Here we show that decompositions in which the disc remains embedded within the spheroid, 
+labelled by some as ``unphysical'',  
+correctly reproduce both the photometric and kinematic properties of early-type galaxies 
+%intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
+with intermediate-scale discs. 
+Intermediate-scale discs have often been confused with large-scale discs, and modelled accordingly; 
+when this happens, the spheroid luminosity is considerably underestimated. 
 This has recently led to some surprising conclusions, 
-such as the claim that a number of ellicular galaxies (e.g.~Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
+such as the claim that a number of galaxies with intermediate-scale discs (e.g.~Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
 host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
-We show that when ellicular galaxies are correctly modelled, 
+We show that when galaxies with intermediate-scale discs are correctly modelled, 
 they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
@@
 and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
-used to describe the coevolution of spheroids and their central supermassive black holes.
+used to describe the coevolution of spheroids and their central supermassive black holes. }
 
@@
 \begin{keywords}
-galaxies: classification -- galaxies: bulges -- galaxies: elliptical and lenticular, 
-cD -- galaxies: evolution -- galaxies: structure -- galaxies: individual: Mrk 1216, NGC 1271, NGC 1277, NGC 1332, NGC 4291
+black hole physics -- galaxies: bulges -- galaxies: elliptical and lenticular, cD -- 
+galaxies: evolution -- galaxies: structure -- galaxies: individual: Mrk 1216, NGC 1271, NGC 1277, NGC 1332, NGC 4291
 \end{keywords}
@@
 \label{sec:int}
-There are currently two well-known types of stellar discs in galaxies. 
-The first are the large-scale discs (with exponential scale lengths of a few kiloparsec) 
-that dominate the light at large radii in spiral and lenticular galaxies; 
-the second are the small (tens to a couple of hundred parsec) nuclear discs observed in both early- and late-type galaxies 
-(e.g.~\citealt{scorzavandenbosch1998,rest2001,balcells2007,ledo2010}). 
-The origin of the nuclear discs has been speculated to arise from the infall of small satellite galaxies or gas clouds.  
-The origin, or at least the on-going feeding and growth, of the large-scale discs has been attributed to cold gas flows, 
-gas rich mergers and halo accretion events 
-(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,barneshernquist1992,khochfarsilk2006,dekel2009nat,ceverino2010,
-ceverino2012,conselice2012,rubin2012,martini2013,ueda2014}), 
-and a thorough review can be found in \citet{combes2014arX,combes2014pro}.
-On the other hand, intermediate-sized discs have not received the same level of attention 
-as their nuclear and large-scale homologues and 
-they have at times been labelled and rejected as ''unphysical'' when detected. 
-Here we focus on the increasingly overlooked occurence of intermediate-scale discs in galaxies with directly measured black hole masses. 
-We report on the photometric and kinematical signatures of these intermediate-sized stellar discs,  
-and the impact they have on the (black hole mass)-to-(spheroid stellar mass) ratio 
-which is used to constrain galaxy evolution models. \\
-The majority of stellar discs have some level of inclination with respect to our line-of-sight, 
-and this makes them appear elliptical (rather than round) when seen in projection on the sky. 
-This can help one distinguish them from the more spherically-shaped spheroids. 
-Identifying the radial extent of these discs with respect to the spheroid can however be subtle. 
-Two-dimensional kinematic maps represent an important diagnostic tool for this purpose. 
-Most early-type galaxies are classified as ``central fast rotators'' \citep{franx1989,atlas3dIII,scott2014}, 
+{\bf The awareness that many early-type galaxies contain stellar discs dates back several years 
+\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,bender1988,bender1990,capaccioli1988,franx1989,
+nieto1988,nieto1991,rixwhite1990,rixwhite1992,vandenbergh1990,scorzabender1990,scorzabender1995,
+simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999}. 
+Since then, it has been well known that 
+the identification of a stellar disc in an early-type galaxy based on the galaxy's photometric properties 
+is subjected to inclination effects. 
+This problem has been overcome with kinematic analysis (e.g.~the ATLAS$^{\rm 3D}$ survey, \citealt{cappellari2011}), 
+which allows one to determine the presence of a rotationally-supported component in a galaxy 
+in a way that can be nearly insensitive to projection effects \citep{cappellari2007,emsellem2007}. 
+Yet, identifying the radial extent of an early-type galaxy's disc with respect to the spheroidal component can still be subtle. 
+Most early-type galaxies are classified as ``fast rotators'' \citep{atlas3dIII,scott2014}, 
 that is, they are rapidly rotating within their half-light radius. 
-However, more extended kinematic maps \citep{arnold2014} reveal that 
-some of the central fast rotators continue to be fast rotating at large radii, 
-whereas other central fast rotators become slow rotators in their outer regions.
+The exact definition of a fast rotator can be found in \cite{emsellem2007}, 
+although the most recent literature (e.g.~\citealt{arnold2011n3115,romanowskyfall2012,arnold2014}) 
+prefers the use of the term ``\emph{central} fast rotator'' 
+to emphasize the fact that this classification pertains to the kinematic properties of a galaxy only within its half-light radius.
+Thanks to their more extended kinematic maps, 
+\cite{arnold2014} revealed that some of the central fast rotators continue to be fast rotating at large radii, 
+whereas other central fast rotators become slow rotating in their outer regions.
 A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
@@
 the toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 
-($\epsilon = 1 - b/a$, where $b/a$ is the ratio of minor-to-major axis length) of 
-(i) a ``lenticular'' galaxy comprised of a large-scale disc which dominates the light at large radii over a relatively smaller encased bulge, 
-(ii) an ``elliptical'' galaxy with an additional nuclear stellar disc, 
-and (iii) a galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid 
-which dominates the light at large radii. 
-We refer to the last case as an ``ellicular'' galaxy. 
+($\epsilon = 1 - b/a$, where $b/a$ is the ratio of minor-to-major axis length) 
+and the specific angular momentum profile 
+($\lambda = \langle R |V| \rangle / \langle R \sqrt{V^2 + \sigma^2} \rangle$, 
+where $R$ is the semimajor-axis radius, $V$ is the mean velocity and $\sigma$ is the velocity dispersion, \citealt{emsellem2007}) 
+of 
+(i) a lenticular galaxy, 
+comprised of a large-scale disc which dominates the light at large radii over a relatively smaller encased bulge,  
+i.e.~a disc-dominated central fast rotator that continues to be fast rotating beyond one half-light radius, 
+(ii) a discy elliptical galaxy \citep{kormendybender1996} 
+composed of an intermediate-scale disc embedded in a relatively larger spheroid which dominates the light at large radii,
+i.e.~a spheroid-dominated central fast rotator that becomes slow rotating beyond one half-light radius, and  
+(iii) an elliptical galaxy with an additional nuclear stellar disc, 
+i.e.~a (spheroid-dominated) slow rotator. 
+This is sequence is analogue to that illustrated in Figure 2 of \cite{cappellari2011}, 
+although here we emphasize the correspondence between the spheroid/disc decomposition of the surface brightness profile 
+and the ``shape'' of the ellipticity (assuming that the disc inclination is not close to face-on) and specific angular momentum profiles. 
 In general, stellar discs are intrinsically flat and circular; 
@@
 (e.g.~\citealt{scorzabender1995} and references therein; \citealt{scorza1998}). \\
-The awareness that many so-called ``elliptical'' galaxies actually contain stellar discs 
-dates back many years 
-\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
-vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
-simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999} and, 
-more recently, intermediate-scale discs were anything but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
-However, the class of ellicular galaxies has been missed by many galaxy modellers of late, 
+While some recent studies -- well aware of this problematic -- have correctly distinguished between large- and intermediate-scale discs, 
+and modelled them accordingly (e.g.~\citealt{kormendybender2012,krajnovic2013}), 
+intermediate-scale discs have been missed by many galaxy modellers of late, 
 who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
@@
 Unsurprisingly, studies affected by this bias have not obtained spheroid/disc decompositions with a spheroid-to-total ratio larger than $0.6 - 0.8$ 
-(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}). 
-In this paper we investigate the influence this has had on research pertaining to supermassive black hole mass scaling relations involving the host spheroid. \\
+(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}). \\
+As mentioned before, a photometric analysis allows one to identify the presence and the radial extent of a disc in an early-type galaxy 
+only when the disc has a certain level of inclination. 
+On the other hand, a kinematic analysis has the advantage of being virtually insensitive to inclination effects, 
+but cannot help one determine the radial extent of a disc if the kinematic data are limited within one half-light radius. 
+Therefore, the best results are obtained when photometry and kinematics are combined together. 
+In this paper we focus on the increasingly overlooked occurence of intermediate-scale discs in galaxies with directly measured black hole masses. 
+We report on the photometric and kinematical signatures of these intermediate-sized stellar discs,  
+and the impact they have on the (black hole mass)-to-(spheroid stellar mass) ratio 
+which is used to constrain galaxy evolution models. \\
 This paper is structured as follows. 
-In Section \ref{sec:gal} we present a detailed photometric analysis of three ellicular galaxies (Mrk 1216, NGC 1332, and NGC 3115) 
-and we briefly describe another five ellicular galaxies (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697) 
+In Section \ref{sec:gal} we present a detailed photometric analysis of three galaxies with intermediate-scale discs (Mrk 1216, NGC 1332, and NGC 3115) 
+and we briefly describe another five galaxies with intermediate-scale discs (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697) 
 already modelled by us elsewhere in the literature. 
@@
 In Section \ref{sec:mm} we explore the important implications this has for the (black hole mass)-(spheroid stellar mass) diagram. 
-In Section \ref{sec:disc} we discuss our results in terms of galaxy evolution 
-and we present the location of ellicular galaxies, relative to other galaxies, in the Hubble grid.
+Finally, in Section \ref{sec:disc} we discuss our results in terms of galaxy evolution. }
+
+%There are currently two well-known types of stellar discs in galaxies.
+%The first are the large-scale discs (with exponential scale lengths of a few kiloparsec)
+%that dominate the light at large radii in spiral and lenticular galaxies;
+%the second are the small (tens to a couple of hundred parsec) nuclear discs observed in both early- and late-type galaxies
+%(e.g.~\citealt{scorzavandenbosch1998,rest2001,balcells2007,ledo2010}).
+%The origin of the nuclear discs has been speculated to arise from the infall of small satellite galaxies or gas clouds.
+%The origin, or at least the on-going feeding and growth, of the large-scale discs has been attributed to cold gas flows,
+%gas rich mergers and halo accretion events
+%(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,barneshernquist1992,khochfarsilk2006,dekel2009nat,ceverino2010,
+%ceverino2012,conselice2012,rubin2012,martini2013,ueda2014}),
+%and a thorough review can be found in \citet{combes2014arX,combes2014pro}.
+%On the other hand, intermediate-sized discs have not received the same level of attention
+%as their nuclear and large-scale homologues and
+%they have at times been labelled and rejected as ``unphysical'' when detected.
+%Here we focus on the increasingly overlooked occurence of intermediate-scale discs in galaxies with directly measured black hole masses.
+%We report on the photometric and kinematical signatures of these intermediate-sized stellar discs,
+%and the impact they have on the (black hole mass)-to-(spheroid stellar mass) ratio
+%which is used to constrain galaxy evolution models. \\
+%The majority of stellar discs have some level of inclination with respect to our line-of-sight,
+%and this makes them appear elliptical (rather than round) when seen in projection on the sky.
+%This can help one distinguish them from the more spherically-shaped spheroids.
+%Identifying the radial extent of these discs with respect to the spheroid can however be subtle.
+%Two-dimensional kinematic maps represent an important diagnostic tool for this purpose.
+%Most early-type galaxies are classified as ``central fast rotators'' \citep{franx1989,atlas3dIII,scott2014},
+%that is, they are rapidly rotating within their half-light radius.  
+%However, more extended kinematic maps \citep{arnold2014} reveal that 
+%some of the central fast rotators continue to be fast rotating at large radii, 
+%whereas other central fast rotators become slow rotators in their outer regions.
+%A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
+%is a signature of a large-scale disc, 
+%while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 
+%indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 
+%Unfortunately, such extended kinematic maps are not yet available for large numbers of galaxies in the local Universe. 
+%Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of stellar discs in early-type galaxies. \\
+%Building on the investigation of \cite{rixwhite1990}, 
+%the toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 
+%($\epsilon = 1 - b/a$, where $b/a$ is the ratio of minor-to-major axis length) of 
+%(i) a disc-dominated early-type galaxy, 
+%comprised of a large-scale disc which dominates the light at large radii over a relatively smaller encased bulge, 
+%(ii) a spehroid-dominated early-type galaxy with an additional nuclear stellar disc, 
+%and (iii) an early-type galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid 
+%which dominates the light at large radii. 
+%In general, stellar discs are intrinsically flat and circular; 
+%their ellipticity, dictated by their inclination to our line of sight, is fixed. 
+%Spheroids are often rounder than the observed projection on the sky of their associated discs, 
+%thus their average ellipticity is often lower than that of their disc. 
+%An ellipticity profile that increases with radius can be ascribed to an inclined disc that becomes progressively more important at large radii, 
+%whereas a radial decrease of ellipticity signifies the opposite case. 
+%This approach can be taken to the next level by inspecting the isophotes for discy structures and checking the velocity line profiles for asymmetry 
+%(e.g.~\citealt{scorzabender1995} and references therein; \citealt{scorza1998}). \\
+%The awareness that many so-called ``elliptical'' galaxies actually contain stellar discs 
+%dates back many years 
+%\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
+%vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
+%simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999} and, 
+%more recently, intermediate-scale discs were anything but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
+%However, intermediate-scale discs have been missed by many galaxy modellers of late, 
+%who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
+%as is observed with spiral galaxies. 
+%Indeed, \citeauthor{graham2011} (\citeyear{graham2011}, his Figure 7) warned about such erroneous fits to spiral galaxies. 
+%This bias has led to the rejection of many early-type galaxy decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
+%Unsurprisingly, studies affected by this bias have not obtained spheroid/disc decompositions with a spheroid-to-total ratio larger than $0.6 - 0.8$ 
+%(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}).
+%In this paper we investigate the influence this has had on research pertaining to supermassive black hole mass scaling relations involving the host spheroid. \\
+%This paper is structured as follows.
+%In Section \ref{sec:gal} we present a detailed photometric analysis of three galaxies with intermediate-scale discs (Mrk 1216, NGC 1332, and NGC 3115)
+%and we briefly describe another five galaxies with intermediate-scale discs (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697)
+%already modelled by us elsewhere in the literature.
+%We compare our photometric analysis with the kinematical information available from the literature,
+%and explain the differences between our galaxy models and past decompositions.
+%In Section \ref{sec:mm} we explore the important implications this has for the (black hole mass)-(spheroid stellar mass) diagram.
+%Finally, in Section \ref{sec:disc} we discuss our results in terms of galaxy evolution.
+%%and we present the location of ellicular galaxies, relative to other galaxies, in the Hubble grid.
 
@@
 In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
-The left panel shows a lenticular galaxy, composed of a bulge encased in a large-scale disc. 
-The right panel displays an elliptical galaxy with (an optional) nuclear stellar disc. 
-The middle panel presents an early-type galaxy with an intermediate-sized disc embedded in the spheroid. 
-We refer to the last case as an ellicular galaxy.}
+The left panel shows a disc-dominated central fast rotator (lenticular galaxy), composed of a bulge encased in a large-scale disc. 
+The right panel displays a spheroid-dominated slow rotator (elliptical) with (an optional) nuclear stellar disc. 
+The middle panel presents a spheroid-dominated central fast rotator (discy elliptical) with an intermediate-sized disc embedded in the spheroid. }
 \label{fig:model}
@@
 \label{sec:gal}
-Three examples of ellicular galaxies are Mrk 1216, NGC 1332, and NGC 3115. 
+Three examples of galaxies with intermediate-scale discs are Mrk 1216, NGC 1332, and NGC 3115. 
 In the following Sections, we present a photometric analysis of these three galaxies, 
@@
 \subsection{NGC 3115}
-The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
+The presence of a disc in the {\bf central fast rotator} NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
 Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
@@
 \subsection{Mrk 1216}
-Although the disc in the galaxy Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
+Although the disc in the {\bf central fast rotator} Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
 the velocity map \citep{yildirim2015} reveals the presence of a fast rotating component 
@@
 \subsubsection{NGC 1271}
-\cite{walsh2015} explored a three-component decomposition for NGC 1271 
+\cite{walsh2015} explored a three-component decomposition for the {\bf central fast rotator} NGC 1271 
 and identified the galaxy bulge with the innermost of the three components, 
@@
 \subsubsection{NGC 1277}
-\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
+\cite{vandenbosch2012} proposed a model for the {\bf central fast rotator} NGC 1277 with a bulge + disc + nuclear source + envelope, 
 which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total flux ratio of $0.24$; 
@@
 \subsubsection{NGC 3377}
-\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
+\cite{lasker2014data} modelled the {\bf central fast rotator} NGC 3377 with a bulge + nuclear disc + disc + envelope, 
 and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total flux ratio of $0.35$; 
@@
 \subsubsection{NGC 821}
-\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
+\cite{lasker2014data} decomposed the {\bf central fast rotator} NGC 821 into a bulge + disc + envelope, 
 and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total flux ratio of $0.19$; 
@@
 \subsubsection{NGC 4697}
-The galaxy NGC 4697 represents an ``extreme'' case. 
+The {\bf central fast rotator} NGC 4697 represents an ``extreme'' case. 
 \cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
@@
 
-Past models that ``forcedly'' described ellicular galaxies using an inner bulge 
+Past models that ``forcedly'' described intermediate-scale disc galaxies using an inner bulge 
 encased within a large-scale disc 
@@
 The color lines represent the individual (PSF-convolved) model components: 
-red = S\'ersic (spheroid), blue = S\'ersic (disc), gray = Gaussian ring. 
+{\bf red solid = S\'ersic (spheroid), blue dashed = S\'ersic (disc), green dotted = Gaussian ring. }
 The residual profile (data $-$ model) is shown as $\Delta \mu$. 
@@
 The color lines represent the individual (PSF-convolved) model components:
-red = S\'ersic (spheroid), blue = exponential (disc).
+{\bf red solid = S\'ersic (spheroid), blue dashed = exponential (disc). }
 }
@@
 Inaccurate measurements of the spheroid-to-total ratio of galaxies can impact galaxy scaling relations. 
-Recently, a handful of ellicular galaxies have been claimed to host \emph{over-massive} black holes, 
+Recently, a handful of galaxies with intermediate-scale discs have been claimed to host \emph{over-massive} black holes, 
 i.e.~the mass of their central supermassive black hole has been reported to be significantly larger 
@@
 and the stellar mass-to-light ratio obtained by \cite{yildirim2015}. 
-For the first time, Figure \ref{fig:mm} reveals that when the four ellicular galaxies Mrk 1216, NGC 1271, NGC 1277, NGC 1332, 
+For the first time, Figure \ref{fig:mm} reveals that when the four intermediate-scale disc galaxies Mrk 1216, NGC 1271, NGC 1277, NGC 1332, 
 and the elliptical galaxy NGC 4291 are properly modelled, 
@@
 
-\section{Discussion}
+\section{Origin of compact massive galaxies}
 \label{sec:disc}
 
-\subsection{Origin of compact massive galaxies}
-Acknowledging the correct structure of ellicular galaxies is important to properly understand their origin. 
+Acknowledging the correct structure of galaxies with intermediate-scale discs is important to properly understand their origin. 
 According to the current paradigm of cosmological structure evolution, 
@@
 which has increased the galaxy size but preserved the bulge compactness. 
-The other compact massive spheroids of today's Universe belong to some ellicular galaxies. 
-Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact ellicular galaxies 
+The other compact massive spheroids of today's Universe belong to some galaxies with intermediate-scale discs. 
+Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact intermediate-scale disc galaxies 
 with purely old ($>10~\rm Gyr$) stellar populations. 
 These galaxies have undergone the lowest degree of disc growth. \\
-In addition to the observational clues as to the actual physical components in ellicular galaxies, 
+In addition to the observational clues as to the actual physical components in galaxies with intermediate-scale discs, 
 one can reason on other grounds as to why these compact galaxies are not comprised of an inner bulge 
@@
 This implies that, among the local descendants of the high-redshift red nuggets, 
-the compact ellicular galaxies have undergone the lowest degree of disc growth. 
-That is, the bulk of a compact ellicular galaxy quickly assembled ``in-situ'' in a very young Universe 
+the compact intermediate-scale disc galaxies have undergone the lowest degree of disc growth. 
+That is, the bulk of a compact intermediate-scale disc galaxy quickly assembled ``in-situ'' in a very young Universe 
 and experienced very little evolution over the last $10~\rm Gyr$.
@@
 
-\subsection{Ellicular galaxies in the Hubble grid}
-The existence of the oft-overlooked, intermediate-scale discs
-exposes a likely continuum of disc sizes in early-type
-galaxies, as opposed to a dichotomy of nuclear discs versus large-scale
-discs. The presence of these intermediate-scale discs also blurs the
-distinction between elliptical (E) and lenticular (S0: $\epsilon = 1-b/a > 0.7$, \citealt{hubble1936,sandage1961}) galaxies and
-arguably creates the need for a new subclass which bridges this
-divide.  While expanding the galaxy nomenclature beyond ellipticals
-with possible nuclear discs, and lenticulars with large-scale discs,
-to include something like \emph{elliculars} with intermediate-scale
-discs will be helpful for distinguishing among 
-early-type galaxies with different disc scale-lengths, it should be
-remembered that just as portions of the electromagnetic spectrum are
-labelled according to their different wavelengths, there is still an
-underlying continuum.  Similarly, binning early-type galaxies as
-either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact
-that a continuum exists.  Importantly, in the case of early-type
-galaxies with intermediate-scale discs, this particular
-rotation-based classification depends on the galaxy's radial range probed, 
-changing from FR to SR as the radial extent is sufficiently increased. 
-There is thus a need for more than two bins (E vs. S0, or FR vs. SR) 
-and a continuum in the (Hubble-Jeans)-like classification schemes \citep{vandenbergh1997,sandage2005}. \\
-It has been argued that the classification
-scheme for ``elliptical'' galaxies should not be their apparent axis ratio
-as seen on the plane of the sky (E0--E7), 
-because this depends on the viewing angle rather than being intrinsic to the galaxy. 
-Obviously when dealing with intermediate-scale discs, the boxy/discy shape of the isophotes is a function of both radius and disc inclination, 
-making a single isophote shape parameter problematic and particularly inappropriate for the classification task at hand.
-Section 4 of \cite{kormendybender1996} points out additional complications. 
-Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, with a
-continuum from pure elliptical galaxies to disc-dominated lenticular
-galaxies (Figure \ref{fig:grid}).  \\
-While spiral galaxies display a range of spheroid-to-total flux ratios
-from 0 to $\sim$3/4 (e.g.~\citealt{grahamworley2008}, and references
-therein), lenticular galaxies typically display a range from
-$\sim$3/4 to $\sim$0.1 \citep{laurikainen2010}.  This spheroid-to-total flux
-ratio is widely recognised as an important quantity, and its broad range observed in
-lenticular galaxies recently led to a re-introduction of 
-\citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976})
-Hubble comb, in which both late-type galaxies (i.e.~spiral galaxies)
-and lenticular galaxies form separate arms of an expanded Hubble-Jeans tuning
-fork, with an additional arm for disc galaxies hosting anaemic spiral
-patterns \citep{cappellari2011kmdr,kormendybender2012}.  
-However because every spiral Hubble type (e.g.~Sa, Sb, Sc), not just the S0 galaxies, 
-has a broad range of spheroid-to-total ratio, and because this information is not captured by the Hubble comb, 
-a grid of spiral morphological type (predominantly determined by the spiral
-arms) versus spheroid-to-total ratio can also be useful for classifying galaxies.  \\
-In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale
-discs in such a ``Hubble grid'', which is effectively the quantitative scheme used by  
-\cite{boroson1981}, \cite{kent1985}, \cite{kodaira1986}, \cite{simiendevaucouleurs1986} 
-in which each galaxy type displays a range of spheroid-to-total flux ratio.
-Rather than a scheme in which the morphological type (a, b, c,
-etc.) changes if the spheroid-to-total ratio changes -- as in the Hubble comb -- here
-the galaxy type is linked to the nature and winding of the spiral arms
-which has been the primary criteria used to classify spiral galaxies
-over the last half century \citep{sandage1961}.  
-Allowing for the varying spheroid-to-total ratio among each galaxy type, 
-the Hubble grid helps to reveal how ellicular galaxies unify the early-type sequence and compare with late-type galaxies.
+% \subsection{Ellicular galaxies in the Hubble grid}
+% The existence of the oft-overlooked, intermediate-scale discs
+% exposes a likely continuum of disc sizes in early-type
+% galaxies, as opposed to a dichotomy of nuclear discs versus large-scale
+% discs. The presence of these intermediate-scale discs also blurs the
+% distinction between elliptical (E) and lenticular (S0: $\epsilon = 1-b/a > 0.7$, \citealt{hubble1936,sandage1961}) galaxies and
+% arguably creates the need for a new subclass which bridges this
+% divide.  While expanding the galaxy nomenclature beyond ellipticals
+% with possible nuclear discs, and lenticulars with large-scale discs,
+% to include something like \emph{elliculars} with intermediate-scale
+% discs will be helpful for distinguishing among 
+% early-type galaxies with different disc scale-lengths, it should be
+% remembered that just as portions of the electromagnetic spectrum are
+% labelled according to their different wavelengths, there is still an
+% underlying continuum.  Similarly, binning early-type galaxies as
+% either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact
+% that a continuum exists.  Importantly, in the case of early-type
+% galaxies with intermediate-scale discs, this particular
+% rotation-based classification depends on the galaxy's radial range probed, 
+% changing from FR to SR as the radial extent is sufficiently increased. 
+% There is thus a need for more than two bins (E vs. S0, or FR vs. SR) 
+% and a continuum in the (Hubble-Jeans)-like classification schemes \citep{vandenbergh1997,sandage2005}. \\
+% It has been argued that the classification
+% scheme for ``elliptical'' galaxies should not be their apparent axis ratio
+% as seen on the plane of the sky (E0--E7), 
+% because this depends on the viewing angle rather than being intrinsic to the galaxy. 
+% Obviously when dealing with intermediate-scale discs, the boxy/discy shape of the isophotes is a function of both radius and disc inclination, 
+% making a single isophote shape parameter problematic and particularly inappropriate for the classification task at hand.
+% Section 4 of \cite{kormendybender1996} points out additional complications. 
+% Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, with a
+% continuum from pure elliptical galaxies to disc-dominated lenticular
+% galaxies (Figure \ref{fig:grid}).  \\
+% While spiral galaxies display a range of spheroid-to-total flux ratios
+% from 0 to $\sim$3/4 (e.g.~\citealt{grahamworley2008}, and references
+% therein), lenticular galaxies typically display a range from
+% $\sim$3/4 to $\sim$0.1 \citep{laurikainen2010}.  This spheroid-to-total flux
+% ratio is widely recognised as an important quantity, and its broad range observed in
+% lenticular galaxies recently led to a re-introduction of 
+% \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976})
+% Hubble comb, in which both late-type galaxies (i.e.~spiral galaxies)
+% and lenticular galaxies form separate arms of an expanded Hubble-Jeans tuning
+% fork, with an additional arm for disc galaxies hosting anaemic spiral
+% patterns \citep{cappellari2011kmdr,kormendybender2012}.  
+% However because every spiral Hubble type (e.g.~Sa, Sb, Sc), not just the S0 galaxies, 
+% has a broad range of spheroid-to-total ratio, and because this information is not captured by the Hubble comb, 
+% a grid of spiral morphological type (predominantly determined by the spiral
+% arms) versus spheroid-to-total ratio can also be useful for classifying galaxies.  \\
+% In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale
+% discs in such a ``Hubble grid'', which is effectively the quantitative scheme used by  
+% \cite{boroson1981}, \cite{kent1985}, \cite{kodaira1986}, \cite{simiendevaucouleurs1986} 
+% in which each galaxy type displays a range of spheroid-to-total flux ratio.
+% Rather than a scheme in which the morphological type (a, b, c,
+% etc.) changes if the spheroid-to-total ratio changes -- as in the Hubble comb -- here
+% the galaxy type is linked to the nature and winding of the spiral arms
+% which has been the primary criteria used to classify spiral galaxies
+% over the last half century \citep{sandage1961}.  
+% Allowing for the varying spheroid-to-total ratio among each galaxy type, 
+% the Hubble grid helps to reveal how ellicular galaxies unify the early-type sequence and compare with late-type galaxies.
 
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{Hubblegrid.pdf}
-\caption{The Hubble grid \citep{graham2014review}, 
-which uses the mean pitch angle of the arms in spiral galaxies to define their morphological type. 
-Ellicular (ES) galaxies are intermediate between elliptical (E) and lenticular (S0) galaxies. }
-\label{fig:grid}
-\end{center}
-\end{figure}
+% \begin{figure}[h]
+% \begin{center}
+% \includegraphics[width=\columnwidth]{Hubblegrid.pdf}
+% \caption{The Hubble grid \citep{graham2014review},
+% which uses the mean pitch angle of the arms in spiral galaxies to define their morphological type.
+% Ellicular (ES) galaxies are intermediate between elliptical (E) and lenticular (S0) galaxies. }
+% \label{fig:grid}
+% \end{center}
+% \end{figure}
 
 \section{Summary and conclusions}
-Early-type galaxies display a continuous distribution of spheroid-to-total flux ratios, 
-going from disc-less, ``pure'' elliptical galaxies to disc-dominated lenticular galaxies 
-\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
-vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
-simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,
-bendersaglia1999}\footnote{Many past studies were hampered by bulge/disc decompositions which forced an $R^{1/4}$ model for the bulge component 
-and thus obtained spurious bulge-to-disc ratios, and from the \emph{IRAF} task {\tt ellipse} which does not report the correct deviations of isophotes 
-from ellipses \citep{ciambur2015}.}. 
-In between these two extremes lie galaxies with intermediate-scale discs, 
+{\bf Early-type galaxies display a continuous distribution of spheroid-to-total flux ratios, 
+going from disc-less, ``pure'' elliptical galaxies (slow rotators) 
+to disc-dominated lenticular galaxies (central fast rotators that continue to be fast rotating also beyond one half-light radius) 
+(e.g.~\citealt{cappellari2011}). 
+%\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
+%vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
+%simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,
+%bendersaglia1999}\footnote{Many past studies were hampered by bulge/disc decompositions which forced an $R^{1/4}$ model for the bulge component 
+%and thus obtained spurious bulge-to-disc ratios, and from the \emph{IRAF} task {\tt ellipse} which does not report the correct deviations of isophotes 
+%from ellipses \citep{ciambur2015}.}. 
+In between these two extremes lie galaxies with intermediate-scale discs 
+(spheroid dominated central fast rotators that become slow rotating in their outer regions), 
 i.e.~discs of kiloparsec-size that remain ``embedded'' within the spheroidal component of the galaxy 
-and do not dominate the galaxy light at large radii as large-scale discs do. 
-while this is likely known to some readers, 
+and do not dominate the galaxy light at large radii as large-scale discs do. }
+While this is likely known to some readers, 
 the surge of papers presenting galaxy decompositions which are not aware of this reality 
 has created a pressing need for this reminder. 
-For ease of reference, we have introduced the term \emph{ellicular} to designate such early-type galaxies with intermediate-scale discs. 
-We have shown that the light distribution of ellicular galaxies can be accurately described 
+We have shown that the light distribution of galaxies with intermediate-scale discs can be accurately described 
 with a simple spheroid + disc (+ optional nuclear component) model, 
@@
 Our decompositions correctly reproduce both the photometric (surface brightness and ellipticity profiles) 
-and kinematic (specific angular momentum profile) properties of nine ellicular galaxies. 
-Four of these nine ellicular galaxies (Mrk 1216, NGC 1271, NGC 1277, NGC 1332) and one additional elliptical galaxy (NGC 4291) 
+and kinematic (specific angular momentum profile) properties of nine intermediate-scale disc galaxies. 
+Four of these nine galaxies (Mrk 1216, NGC 1271, NGC 1277, NGC 1332) and one additional elliptical galaxy (NGC 4291) 
 had previously been claimed to be extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
@@
 \section{Acknowledgments}
-% referee thank you!!
 This research was supported by Australian Research Council funding through grant FT110100263. 
 GS is grateful to Matteo Fossati, Luca Cortese and Giuseppe Gavazzi for useful comments and discussion. 
+% referee thank you!!
 This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} on-board the Spitzer Space Telescope, 

### 2015-10-16 python_codes/paper_figures/ellicular/rm.py

@@ -1,0 +1,219 @@
+import sqlite3 as sql3
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+import matplotlib.colors as mcolors
+import matplotlib.image as image
+
+from scipy import stats
+from instruments.linear_regression import bces
+from instruments.linear_regression import predband
+from instruments.linear_regression import fitexy
+from instruments import b_n
+from instruments.linear_regression import colorline
+from instruments.linear_regression import akaike
+from instruments.linear_regression import absolutescatter
+#from instruments.linear_regression import lnr
+from instruments.markers import markers
+
+from matplotlib import rc
+rc('font',**{'family':'sans-serif','sans-serif':['CenturyGothic']})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['Palatino']})
+rc('text', usetex=True)
+
+
+matplotlib.rcParams.update({'font.size': 26})
+
+dbname = '/Users/gsavorgnan/galaxy_vivisection/python_codes/databases/galaxy_vivisection.db'
+
+path_paper_figures = '/Users/gsavorgnan/galaxy_vivisection/papers/ellicular/images/'
+
+def Re_vs_mass_sph():
+	
+	#outliers = [u'n1374', u'n3842exp', u'n4889']
+	outliers = []
+	
+	connection = sql3.connect(dbname)
+	cur = connection.cursor()
+
+	getdata_query = 'SELECT anc.gal_id, \
+		pysres.mag_sph_eq_moffat_comb, \
+		errV.perr_mag_sph, errV.merr_mag_sph, \
+		pysres.log_r_e_maj_moffat_comb, \
+		errV.perr_log_r_e, errV.merr_log_r_e, \
+		col.color  \
+		FROM Ancillary AS anc \
+		JOIN OneDFitResultsPhysicalUnits AS pysres ON anc.gal_id = pysres.gal_id \
+		JOIN ErrorsVote as errV ON anc.gal_id = errV.gal_id \
[…]

### 2015-10-20 papers/ellicular/ellicular.tex
tue

@@
 This has recently led to some surprising conclusions, 
-such as the claim that a number of galaxies with intermediate-scale discs (e.g.~Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
+such as the claim that a number of galaxies with intermediate-scale discs (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
 host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
-We show that when galaxies with intermediate-scale discs are correctly modelled, 
+We show that when these galaxies are correctly modelled, 
 they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
@@
 Unfortunately, such extended kinematic maps are not yet available for large numbers of galaxies in the local Universe. 
-Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of stellar discs in early-type galaxies. \\
+Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of a stellar disc in an early-type galaxy. \\
 Building on the investigation of \cite{rixwhite1990}, 
@@
 composed of an intermediate-scale disc embedded in a relatively larger spheroid which dominates the light at large radii,
-i.e.~a spheroid-dominated central fast rotator that becomes slow rotating beyond one half-light radius, and  
+i.e.~a spheroid-dominated central fast rotator that becomes slow rotating beyond $1-2$ half-light radii, and  
 (iii) an elliptical galaxy with an additional nuclear stellar disc, 
@@
 
-% \subsection{Ellicular galaxies in the Hubble grid}
-% The existence of the oft-overlooked, intermediate-scale discs
-% exposes a likely continuum of disc sizes in early-type
-% galaxies, as opposed to a dichotomy of nuclear discs versus large-scale
-% discs. The presence of these intermediate-scale discs also blurs the
-% distinction between elliptical (E) and lenticular (S0: $\epsilon = 1-b/a > 0.7$, \citealt{hubble1936,sandage1961}) galaxies and
-% arguably creates the need for a new subclass which bridges this
-% divide.  While expanding the galaxy nomenclature beyond ellipticals
-% with possible nuclear discs, and lenticulars with large-scale discs,
-% to include something like \emph{elliculars} with intermediate-scale
-% discs will be helpful for distinguishing among 
-% early-type galaxies with different disc scale-lengths, it should be
-% remembered that just as portions of the electromagnetic spectrum are
-% labelled according to their different wavelengths, there is still an
-% underlying continuum.  Similarly, binning early-type galaxies as
-% either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact
-% that a continuum exists.  Importantly, in the case of early-type
-% galaxies with intermediate-scale discs, this particular
-% rotation-based classification depends on the galaxy's radial range probed, 
-% changing from FR to SR as the radial extent is sufficiently increased. 
-% There is thus a need for more than two bins (E vs. S0, or FR vs. SR) 
-% and a continuum in the (Hubble-Jeans)-like classification schemes \citep{vandenbergh1997,sandage2005}. \\
-% It has been argued that the classification
-% scheme for ``elliptical'' galaxies should not be their apparent axis ratio
-% as seen on the plane of the sky (E0--E7), 
-% because this depends on the viewing angle rather than being intrinsic to the galaxy. 
-% Obviously when dealing with intermediate-scale discs, the boxy/discy shape of the isophotes is a function of both radius and disc inclination, 
-% making a single isophote shape parameter problematic and particularly inappropriate for the classification task at hand.
-% Section 4 of \cite{kormendybender1996} points out additional complications. 
-% Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, with a
-% continuum from pure elliptical galaxies to disc-dominated lenticular
-% galaxies (Figure \ref{fig:grid}).  \\
-% While spiral galaxies display a range of spheroid-to-total flux ratios
-% from 0 to $\sim$3/4 (e.g.~\citealt{grahamworley2008}, and references
-% therein), lenticular galaxies typically display a range from
-% $\sim$3/4 to $\sim$0.1 \citep{laurikainen2010}.  This spheroid-to-total flux
-% ratio is widely recognised as an important quantity, and its broad range observed in
-% lenticular galaxies recently led to a re-introduction of 
-% \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976})
-% Hubble comb, in which both late-type galaxies (i.e.~spiral galaxies)
-% and lenticular galaxies form separate arms of an expanded Hubble-Jeans tuning
-% fork, with an additional arm for disc galaxies hosting anaemic spiral
-% patterns \citep{cappellari2011kmdr,kormendybender2012}.  
-% However because every spiral Hubble type (e.g.~Sa, Sb, Sc), not just the S0 galaxies, 
-% has a broad range of spheroid-to-total ratio, and because this information is not captured by the Hubble comb, 
-% a grid of spiral morphological type (predominantly determined by the spiral
-% arms) versus spheroid-to-total ratio can also be useful for classifying galaxies.  \\
-% In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale
-% discs in such a ``Hubble grid'', which is effectively the quantitative scheme used by  
-% \cite{boroson1981}, \cite{kent1985}, \cite{kodaira1986}, \cite{simiendevaucouleurs1986} 
-% in which each galaxy type displays a range of spheroid-to-total flux ratio.
-% Rather than a scheme in which the morphological type (a, b, c,
-% etc.) changes if the spheroid-to-total ratio changes -- as in the Hubble comb -- here
-% the galaxy type is linked to the nature and winding of the spiral arms
-% which has been the primary criteria used to classify spiral galaxies
-% over the last half century \citep{sandage1961}.  
-% Allowing for the varying spheroid-to-total ratio among each galaxy type, 
-% the Hubble grid helps to reveal how ellicular galaxies unify the early-type sequence and compare with late-type galaxies.
+  \subsection{Ellicular galaxies in the Hubble grid}
+  The existence of the oft-overlooked, intermediate-scale discs
+  exposes a likely continuum of disc sizes in early-type
+  galaxies, as opposed to a dichotomy of nuclear discs versus large-scale
+  discs. The presence of these intermediate-scale discs also blurs the
+  distinction between elliptical (E) and lenticular (S0: $\epsilon = 1-b/a > 0.7$, \citealt{hubble1936,sandage1961}) galaxies and
+  arguably creates the need for a new subclass which bridges this
+  divide.  While expanding the galaxy nomenclature beyond ellipticals
+  with possible nuclear discs, and lenticulars with large-scale discs,
+  to include something like \emph{elliculars} with intermediate-scale
+  discs will be helpful for distinguishing among 
+  early-type galaxies with different disc scale-lengths, it should be
+  remembered that just as portions of the electromagnetic spectrum are
+  labelled according to their different wavelengths, there is still an
+  underlying continuum.  Similarly, binning early-type galaxies as
+  either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact
+  that a continuum exists.  Importantly, in the case of early-type
+  galaxies with intermediate-scale discs, this particular
+  rotation-based classification depends on the galaxy's radial range probed, 
+  changing from FR to SR as the radial extent is sufficiently increased. 
+  There is thus a need for more than two bins (E vs. S0, or FR vs. SR) 
+  and a continuum in the (Hubble-Jeans)-like classification schemes \citep{vandenbergh1997,sandage2005}. \\
+  It has been argued that the classification
+  scheme for ``elliptical'' galaxies should not be their apparent axis ratio
+  as seen on the plane of the sky (E0--E7), 
+  because this depends on the viewing angle rather than being intrinsic to the galaxy. 
+  Obviously when dealing with intermediate-scale discs, the boxy/discy shape of the isophotes is a function of both radius and disc inclination, 
+  making a single isophote shape parameter problematic and particularly inappropriate for the classification task at hand.
+  Section 4 of \cite{kormendybender1996} points out additional complications. 
+  Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, with a
+  continuum from pure elliptical galaxies to disc-dominated lenticular
+  galaxies (Figure \ref{fig:grid}).  \\
+  While spiral galaxies display a range of spheroid-to-total flux ratios
+  from 0 to $\sim$3/4 (e.g.~\citealt{grahamworley2008}, and references
+  therein), lenticular galaxies typically display a range from
+  $\sim$3/4 to $\sim$0.1 \citep{laurikainen2010}.  This spheroid-to-total flux
+  ratio is widely recognised as an important quantity, and its broad range observed in
+  lenticular galaxies recently led to a re-introduction of 
+  \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976})
+  Hubble comb, in which both late-type galaxies (i.e.~spiral galaxies)
+  and lenticular galaxies form separate arms of an expanded Hubble-Jeans tuning
+  fork, with an additional arm for disc galaxies hosting anaemic spiral
+  patterns \citep{cappellari2011kmdr,kormendybender2012}.  
+  However because every spiral Hubble type (e.g.~Sa, Sb, Sc), not just the S0 galaxies, 
+  has a broad range of spheroid-to-total ratio, and because this information is not captured by the Hubble comb, 
+  a grid of spiral morphological type (predominantly determined by the spiral
+  arms) versus spheroid-to-total ratio can also be useful for classifying galaxies.  \\
+  In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale
+  discs in such a ``Hubble grid'', which is effectively the quantitative scheme used by  
+  \cite{boroson1981}, \cite{kent1985}, \cite{kodaira1986}, \cite{simiendevaucouleurs1986} 
+  in which each galaxy type displays a range of spheroid-to-total flux ratio.
+  Rather than a scheme in which the morphological type (a, b, c,
+  etc.) changes if the spheroid-to-total ratio changes -- as in the Hubble comb -- here
+  the galaxy type is linked to the nature and winding of the spiral arms
+  which has been the primary criteria used to classify spiral galaxies
+  over the last half century \citep{sandage1961}.  
+  Allowing for the varying spheroid-to-total ratio among each galaxy type, 
+  the Hubble grid helps to reveal how ellicular galaxies unify the early-type sequence and compare with late-type galaxies.
 
-% \begin{figure}[h]
-% \begin{center}
-% \includegraphics[width=\columnwidth]{Hubblegrid.pdf}
-% \caption{The Hubble grid \citep{graham2014review},
-% which uses the mean pitch angle of the arms in spiral galaxies to define their morphological type.
-% Ellicular (ES) galaxies are intermediate between elliptical (E) and lenticular (S0) galaxies. }
-% \label{fig:grid}
-% \end{center}
-% \end{figure}
+  \begin{figure}[h]
+  \begin{center}
+  \includegraphics[width=\columnwidth]{Hubblegrid.pdf}
+  \caption{The Hubble grid \citep{graham2014review},
+  which uses the mean pitch angle of the arms in spiral galaxies to define their morphological type.
+  Ellicular (ES) galaxies are intermediate between elliptical (E) and lenticular (S0) galaxies. }
+  \label{fig:grid}
+  \end{center}
+  \end{figure}
 
 \section{Summary and conclusions}
-{\bf Early-type galaxies display a continuous distribution of spheroid-to-total flux ratios, 
+{\bf Early-type galaxies display a broad distribution of spheroid-to-total flux ratios (e.g.~\citealt{cappellari2011}), 
 going from disc-less, ``pure'' elliptical galaxies (slow rotators) 
-to disc-dominated lenticular galaxies (central fast rotators that continue to be fast rotating also beyond one half-light radius) 
-(e.g.~\citealt{cappellari2011}). 
+to disc-dominated lenticular galaxies (central fast rotators that continue to be fast rotating also beyond one half-light radius). 
 %\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,

### 2015-10-20 papers/mbhn/mbhn.tex
tue

--- 2015-08-26 papers/mbhn/mbhn.tex
@@
-%%
-%% Beginning of file 'sample.tex'
-%%
-%% Modified 2005 December 5
-%%
-%% This is a sample manuscript marked up using the
-%% AASTeX v5.x LaTeX 2e macros.
-
-%% The first piece of markup in an AASTeX v5.x document
-%% is the \documentclass command. LaTeX will ignore
-%% any data that comes before this command.
-
-%% The command below calls the preprint style
-%% which will produce a one-column, single-spaced document.
-%% Examples of commands for other substyles follow. Use
-%% whichever is most appropriate for your purposes.
-%%
-%%\documentclass[12pt,preprint]{aastex}
-
-%% manuscript produces a one-column, double-spaced document:
-
-%\documentclass[manuscript]{aastex}
-
-%% preprint2 produces a double-column, single-spaced document:
-
 \documentclass[preprint2]{emulateapj}
 
+\bibliographystyle{apj}
 \usepackage{natbib}
-\bibliographystyle{apj}
 \usepackage{longtable}
@@
 \usepackage{amsmath}
-\usepackage{natbib}
 \usepackage{tabularx}
@@
 
-%% Sometimes a paper's abstract is too long to fit on the
-%% title page in preprint2 mode. When that is the case,
-%% use the longabstract style option.
-
-%% \documentclass[preprint2,longabstract]{aastex}
-
-%% If you want to create your own macros, you can do so
-%% using \newcommand. Your macros should appear before
-%% the \begin{document} command.
-%%
-%% If you are submitting to a journal that translates manuscripts
-%% into SGML, you need to follow certain guidelines when preparing
-%% your macros. See the AASTeX v5.x Author Guide
-%% for information.
-
 \newcommand{\vdag}{(v)^\dagger}
 \newcommand{\myemail}{gsavorgn@astro.swin.edu.au}
-
 \newcommand{\fitfigurewidth}{0.8\textwidth}
-
-%% You can insert a short comment on the title page using the command below.
-
-%\slugcomment{Not to appear in Nonlearned J., 45.}
-
-%% If you wish, you may supply running head information, although
-%% this information may be modified by the editorial offices.
-%% The left head contains a list of authors,
-%% usually a maximum of three (otherwise use et al.).  The right
-%% head is a modified title of up to roughly 44 characters.
-%% Running heads will not print in the manuscript style.
 
@@
 
-%% This is the end of the preamble.  Indicate the beginning of the
-%% paper itself with \begin{document}.
-
 \begin{document}
-
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire.
 
@@
 
-%% Use \author, \affil, and the \and command to format
-%% author and affiliation information.
-%% Note that \email has replaced the old \authoremail command
-%% from AASTeX v4.0. You can use \email to mark an email address
-%% anywhere in the paper, not just in the front matter.
-%% As in the title, use \\ to force line breaks.
-
 \author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
 \affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
-
-%\author{C. D. Biemesderfer\altaffilmark{4,5}}
-%\affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
 \email{gsavorgn@astro.swin.edu.au}
-
-%\and
-
-%\author{A. W. Graham\altaffilmark{1}}
-%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
-
-%% Notice that each of these authors has alternate affiliations, which
-%% are identified by the \altaffilmark after each name.  Specify alternate
-%% affiliation information with \altaffiltext, with one command per each
-%% affiliation.
-
-%\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
-%CTIO is operated by AURA, Inc.\ under contract to the National Science
-%Foundation.}
-%\altaffiltext{2}{Society of Fellows, Harvard University.}
-%\altaffiltext{3}{present address: Center for Astrophysics,
-%    60 Garden Street, Cambridge, MA 02138}
-%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
-%\altaffiltext{5}{Patron, Alonso's Bar and Grill}
-
-%% Mark off your abstract in the ``abstract'' environment. In the manuscript
-%% style, abstract will output a Received/Accepted line after the
-%% title and affiliation information. No date will appear since the author
-%% does not have this information. The dates will be filled in by the
-%% editorial office after submission.
 
@@
 \section{Introduction}
+The empirical \cite{sersic1963,sersic1968} $R^{1/n}$ model has been demonstrated to provide adequate description 
+of the light distribution of the stellar spheroidal and disk components of galaxies (add REFS), 
+yet its physical origin has remained unexplained for decades. 
+The S\'ersic model parametrizes the intensity $I$ as a function of the projected galactic radius $R$ such that
+\begin{equation}
+I(R; I_{\rm e},R_{\rm e},n) = I_{\rm e} \exp \biggl \{ -b_{\rm n} \biggl [ \Bigl (\frac{R}{R_{\rm e}} \bigr )^{1/n} -1 \biggr ] \biggr \}, 
+\end{equation}
+where $I_{\rm e}$ indicates the intensity at the effective radius $R_{\rm e}$ that encloses half of the total light from the model, 
+the S\'ersic index $n$ is the parameter that regulates the curvature of the radial light profile, 
+and $b_{\rm n}$ is a constant defined in terms of the S\'ersic index $n$ (see \citealt{grahamdriver2005}, and references therein). 
+A large S\'ersic index corresponds to a steep central profile and a shallow outer profile, 
+whereas a small S\'ersic index corresponds to a shallow central profile and a steep outer profile. 
+This means that, for a stellar spheroidal system whose light distribution is well approximated by the S\'ersic model, 
+the larger the S\'ersic index $n$ is, the more centrally concentrated the stars are and the more extended the outer envelope is. \\
+A compelling physical interpretation for the S\'ersic profile family was recently theorized by \cite{cen2014} 
+and later confirmed by \cite{nipoti2015} by means of $N$-body simulations. 
+\cite{cen2014} conjectured that, when structures form within a standard cold dark matter model seeded by random Gaussian fluctuations, 
+any centrally concentrated stellar structure always possesses an extended stellar envelope, and vice versa. 
+\cite{nipoti2015} quantitatively explored Cen's hypothesis and showed that 
+systems originated from several mergers have a large S\'ersic index ($n \gtrsim 4$), 
+whereas systems with a S\'ersic index as small as $n \simeq 2$ can be produced by coherent dissipationless collapse, 
+and exponential profiles ($n=1$) can only be obtained through dissipative processes.
+This scenario sets the theoretical framework for the well known correlation between the spheroid luminosity, $L_{\rm sph}$,  
+and the spheroid S\'ersic index, $n_{\rm sph}$, (e.g.~\citealt{youngcurrie1994,jerjen2000,grahamguzman2003}), 
+although the numerical results of \cite{nipoti2015} seem to lack of spheroidal systems with $n$ as large as $7 - 10$, 
+which are commonly observed in the local Universe.  \\
+Given the existence of the $L_{\rm sph} - n_{\rm sph}$ correlation 
+and the relation between the central black hole mass, $M_{\rm BH}$, and $L_{\rm sph}$ (e.g.~\citealt{magorrian1998}), 
+an $M_{\rm BH} - n_{\rm sph}$ relation must exist. 
+After \cite{graham2001} showed that the black hole mass is tightly linked to the stellar light concentration of spheroids 
+(measured through a parameter different from but closely related to the S\'ersic index), 
+\cite{grahamdriver2007} presented for the first time the $M_{\rm BH} - n_{\rm sph}$ correlation.
+
+s+11 v+12 b+12  \\
+my paper \\
+paper I and II \\
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
+%\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
 \caption{}
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
+%\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
 \caption{}
@@
 \acknowledgments
+kkkkk
 

### 2015-10-21 papers/mbhn/mbhn.tex
wed

@@
 and $b_{\rm n}$ is a constant defined in terms of the S\'ersic index $n$ (see \citealt{grahamdriver2005}, and references therein). 
-A large S\'ersic index corresponds to a steep central profile and a shallow outer profile, 
-whereas a small S\'ersic index corresponds to a shallow central profile and a steep outer profile. 
+A large S\'ersic index corresponds to a steep inner profile and a shallow outer profile, 
+whereas a small S\'ersic index corresponds to a shallow inner profile and a steep outer profile. 
 This means that, for a stellar spheroidal system whose light distribution is well approximated by the S\'ersic model, 
-the larger the S\'ersic index $n$ is, the more centrally concentrated the stars are and the more extended the outer envelope is. \\
+the larger the S\'ersic index is, the more centrally concentrated the stars are and the more extended the outer envelope is. \\
 A compelling physical interpretation for the S\'ersic profile family was recently theorized by \cite{cen2014} 
@@
 and the spheroid S\'ersic index, $n_{\rm sph}$, (e.g.~\citealt{youngcurrie1994,jerjen2000,grahamguzman2003}), 
-although the numerical results of \cite{nipoti2015} seem to lack of spheroidal systems with $n$ as large as $7 - 10$, 
+although the numerical results of \cite{nipoti2015} seem to lack of spheroidal systems with S\'ersic indices as large as $7 - 10$, 
 which are commonly observed in the local Universe.  \\
 Given the existence of the $L_{\rm sph} - n_{\rm sph}$ correlation 
-and the relation between the central black hole mass, $M_{\rm BH}$, and $L_{\rm sph}$ (e.g.~\citealt{magorrian1998}), 
+and the relation between the central black hole mass, $M_{\rm BH}$, and the spheroid luminosity (e.g.~\citealt{magorrian1998}), 
 an $M_{\rm BH} - n_{\rm sph}$ relation must exist. 
 After \cite{graham2001} showed that the black hole mass is tightly linked to the stellar light concentration of spheroids 
-(measured through a parameter different from but closely related to the S\'ersic index), 
-\cite{grahamdriver2007} presented for the first time the $M_{\rm BH} - n_{\rm sph}$ correlation.
-
-s+11 v+12 b+12  \\
-my paper \\
-paper I and II \\
+(measured through a parameter different from, but closely related to the S\'ersic index), 
+\cite{grahamdriver2007} presented for the first time the $M_{\rm BH} - n_{\rm sph}$ correlation 
+using a sample of 27 elliptical and disk galaxies. 
+\cite{grahamdriver2007} fit their data with a log-quadratic regression, 
+finding that the $M_{\rm BH} - n_{\rm sph}$ log-relation is steeper for spheroids with small S\'ersic indices 
+and shallower for spheroids with large S\'ersic indices, 
+and measured a relatively small level of scatter\footnote{At the time, the $M_{\rm BH} - \sigma$ relation 
+\citep{ferraresemerritt2000,gebhardt2000} was reported to have the same level of scatter as the $M_{\rm BH} - n_{\rm sph}$ 
+relation ($\simeq 0.3~\rm dex$). }.
+A few years later, \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} performed multi-component decompositions 
+for samples of galaxies similar to that used by \cite{grahamdriver2007}, 
+but they surprisingly failed to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation. 
+This issue was tackled by \cite{savorgnan2013}, who collected the S\'ersic index measurements published by 
+\cite{grahamdriver2007}, \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} for a sample of 54 galaxies, 
+and showed that, by rejecting the most discrepant measurements and averaging the remaning ones, 
+a strong $M_{\rm BH} - n_{\rm sph}$ relation was retrieved. 
+Remarkably, \cite{savorgnan2013} repeated their analysis upon excluding the S\'ersic index measurements of \cite{grahamdriver2007} 
+and still regained a significant $M_{\rm BH} - n_{\rm sph}$ relation. 
+This was suggestive that the individual galaxy decompositions of \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} were not accurate, 
+i.e.~each individual study obtained ``noisy'' S\'ersic index measurements 
+which prevented the recovery of a strong $M_{\rm BH} - n_{\rm sph}$ relation. \\
+Motivated by the need of more accurate galaxy decompositions to refine and re-investigate scaling relations 
+between the black hole mass and several galaxy structural parameters, 
+we performed state-of-the-art modelling for the largest sample of galaxies to date (Savorgnan \& Graham 2015, hereafter \emph{Paper I}),  
+for which a dynamical measurement of the black hole mass was available.
+In doing so, we used $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
+given its superb capability to trace the stellar mass (\citealt{sheth2010}, and references therein). 
+In Savorgnan et al.~(2015, hereafter \emph{Paper II}) we examined the correlations between black hole mass and 
+galaxy luminosity, spheroid luminosity and spheroid stellar mass. 
+In this Paper (\emph{Paper III}) we focus on the $M_{\rm BH} - n_{\rm sph}$ relation. \\
+This paper is structured as follows...
 
 \section{Data}
+We populated the $M_{\rm BH} - n_{\rm sph}$ diagram with the same galaxy sample used in \emph{Paper II}, 
+i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
+(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
+and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
+using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
+Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
+extended or unresolved nuclear source and partially depleted core, 
+and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
+\citep{atlas3dIII,scott2014,arnold2014}. 
+Kinematical information was used to confirm the presence of disk components 
+in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
+to estabilish the radial extent of these disks. 
+This enabled us to distinguish between intermediate-scale disks, 
+that are fully embedded in the spheroid,  
+and large-scale disks, that encase the bulge and dominate the light at large radii 
+(see Savorgnan \& Graham 2015 for a discussion on this topic).
+
+%%%
+Spheroid magnitudes were derived from our state-ofthe-
+art galaxy decompositions, which take into account
+%%%
+bulge, disks, spiral arms, bars, rings, halo, extended or
+unresolved nuclear source and partially depleted core.
+%%%
+Kinematical information (Emsellem et al. 2011; Scott
+et al. 2014; Arnold et al. 2014) was used to conrm the
+%%%
+presence of rotationally supported disk components in
+most early-type (elliptical + lenticular) galaxies, and to
+%%%
+identify their extent (intermediate-scale disks that are
+fully embedded in the bulge, or large-scale disks that encase
+%%%
+the bulge and dominate the light at large radii).
+It is worth stressing that, contrary to common knowledge,
+%%%
+the majority of elliptical galaxies contain disks,
+i.e. they are not single-component spheroidal systems.
+%%%
+Paper I presents the dataset used here, including details
+about the data reduction process and the galaxy modelling
+%%%
+technique that we developed. It also discusses how
+we estimated the uncertainties5 on the bulge magnitudes,
+%%%and presents the individual 66 galaxy decompositions,
+along with a comparison and discussion of past decompositions.
+%%%The morphological classication (E = elliptical; E/S0 =
+elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/
+%%%
+spiral; Sp = spiral; and merger") follows from the
+galaxy models presented in Paper I. Throughout this paper
+%%%
+we will refer to early-type galaxies (E+S0) and latetype
+galaxies (Sp). Two galaxies classied as E/S0 are
+%%%
+obviously included in the early-type bin, whereas two
+galaxies classied as S0/Sp and another two classied as
+%%%
+mergers are included in neither the early- nor the latetype
+bin.
 
@@
 \begin{center}
-%\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
+\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
 \caption{}
@@
 \begin{center}
-%\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
+\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
 \caption{}

### 2015-10-23 papers/mbhn/mbhn.tex
friday suzuki

@@
 \section{Data}
-We populated the $M_{\rm BH} - n_{\rm sph}$ diagram with the same galaxy sample used in \emph{Paper II}, 
+We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
+with the same galaxy sample (Table \ref{tab:sample}) used in \emph{Paper II}, 
 i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
@@
 in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
-to estabilish the radial extent of these disks. 
+to estabilish the radial extent of these disks, 
+which in most cases is not obvious from a visual inspection of the galaxy images. 
 This enabled us to distinguish between intermediate-scale disks, 
 that are fully embedded in the spheroid,  
-and large-scale disks, that encase the bulge and dominate the light at large radii 
-(see Savorgnan \& Graham 2015 for a discussion on this topic).
-
-%%%
-Spheroid magnitudes were derived from our state-ofthe-
-art galaxy decompositions, which take into account
-%%%
-bulge, disks, spiral arms, bars, rings, halo, extended or
-unresolved nuclear source and partially depleted core.
-%%%
-Kinematical information (Emsellem et al. 2011; Scott
-et al. 2014; Arnold et al. 2014) was used to conrm the
-%%%
-presence of rotationally supported disk components in
-most early-type (elliptical + lenticular) galaxies, and to
-%%%
-identify their extent (intermediate-scale disks that are
-fully embedded in the bulge, or large-scale disks that encase
-%%%
-the bulge and dominate the light at large radii).
-It is worth stressing that, contrary to common knowledge,
-%%%
-the majority of elliptical galaxies contain disks,
-i.e. they are not single-component spheroidal systems.
-%%%
-Paper I presents the dataset used here, including details
-about the data reduction process and the galaxy modelling
-%%%
-technique that we developed. It also discusses how
-we estimated the uncertainties5 on the bulge magnitudes,
-%%%and presents the individual 66 galaxy decompositions,
-along with a comparison and discussion of past decompositions.
-%%%The morphological classication (E = elliptical; E/S0 =
-elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/
-%%%
-spiral; Sp = spiral; and merger") follows from the
-galaxy models presented in Paper I. Throughout this paper
-%%%
-we will refer to early-type galaxies (E+S0) and latetype
-galaxies (Sp). Two galaxies classied as E/S0 are
-%%%
-obviously included in the early-type bin, whereas two
-galaxies classied as S0/Sp and another two classied as
-%%%
-mergers are included in neither the early- nor the latetype
-bin.
+and large-scale disks, that encase the bulge and dominate the light at large radii.  
+Savorgnan \& Graham (2015) explain that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
+the luminosity of the spheroid is underestimated, 
+hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
+A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
+can be found in \emph{Paper I}, 
+along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
+the spheroid S\'ersic indices have been estimated with a method that takes into account systematic errors. 
+This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by different studies 
+with that obtained by us. 
+Systematic errors are typically not considered by popular 2D fitting codes which report only the statistical errors 
+associated with their fitted parameters. 
+Refer to \emph{Paper I} for a detailed discussion on this. }.  
+The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
+S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
+As in \emph{Paper II}, here we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
+The early-type bin includes two galaxies classified as E/S0, 
+whereas two galaxies classified as S0/Sp and another two classified as mergers are included in neither the early- nor the late-type bin.
 
@@
 
-\section{Results}
+\section{Analysis and results}
+As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
+and $M_{\rm BH} - n_{\rm sph}$ diagrams (see Table \ref{tab:lregLn} and Table \ref{tab:lregMn}, respectively) 
+was performed using three different routines: 
+the BCES code from \cite{akritasbershady1996}, 
+the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
+and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
+All of these three routines take into account the intrinsic scatter, 
+but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
+We report both symmetrical and nonsymmetrical linear regressions.  
+Symmetrical regressions are meant to be compared with theoretical expectations, 
+whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
+allow one to predict values of the ordinate observable ($Y$) with the best possible precision.
+
+%for different morphological types (elliptical/lenticular/spiral)
+
+\subsection{$L_{\rm sph} - n_{\rm sph}$}
 
@@
 \includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
-\caption{}
+\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
+measured along the galaxy major-axis. 
+Symbols are coded according to the galaxy morphological type (see legend). 
+The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
+with the red shaded area denoting its $1\sigma$ uncertainty. 
+The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
+with the blue shaded area denoting its $1\sigma$ uncertainty. 
+The inset panel shows the error bars associated to each data point,  
+where the error bars have the same color coding as the symbols in the main figure. 
+}
 \label{fig:magn}
@@
 
+\subsection{$M_{\rm BH} - n_{\rm sph}$}
+
 \begin{figure}[h]
@@
 \includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
-\caption{}
+\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
+Symbols are coded according to the galaxy morphological type (see legend). 
+The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
+with the red shaded area denoting its $1\sigma$ uncertainty. 
+The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
+with the blue shaded area denoting its $1\sigma$ uncertainty. 
+The inset panel shows the error bars associated to each data point,  
+where the error bars have the same color coding as the symbols in the main figure. 
+}
 \label{fig:mbhn}

### 2015-10-28 papers/ellicular/ellicular.tex
hes crazy

@@
 %\title[Non over-massive black holes in early-type galaxies]{Early-type galaxies with intermediate-scale discs and their (non over-massive) black holes}
-\title[Non over-massive black holes in early-type galaxies]{Non over-massive black holes in early-type galaxies with intermediate-scale discs}
+\title[Explaining the reportedly over-massive black holes]
+{Explaining the reportedly over-massive black holes in early-type galaxies with intermediate-scale discs}
 
@@
 with intermediate-scale discs. 
-Intermediate-scale discs have often been confused with large-scale discs, and modelled accordingly; 
+Intermediate-scale discs have often been confused with large-scale discs and incorrectly modelled as such; 
 when this happens, the spheroid luminosity is considerably underestimated. 
@@
 \label{sec:int}
-{\bf The awareness that many early-type galaxies contain stellar discs dates back several years 
-\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,bender1988,bender1990,capaccioli1988,franx1989,
-nieto1988,nieto1991,rixwhite1990,rixwhite1992,vandenbergh1990,scorzabender1990,scorzabender1995,
-simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999}. 
-Since then, it has been well known that 
-the identification of a stellar disc in an early-type galaxy based on the galaxy's photometric properties 
-is subjected to inclination effects. 
-This problem has been overcome with kinematic analysis (e.g.~the ATLAS$^{\rm 3D}$ survey, \citealt{cappellari2011}), 
-which allows one to determine the presence of a rotationally-supported component in a galaxy 
-in a way that can be nearly insensitive to projection effects \citep{cappellari2007,emsellem2007}. 
+{\bf The awareness that \emph{many} early-type galaxies contain previously over-looked stellar discs dates back half a century 
+\citep{liller1966,michard1984,djorgovski1985,jedrzejewski1987,BenderMoellenhoff1987,
+carter1987,capaccioli1987,capaccioli1988,stromstrom1978,bender1988,bender1990,
+nieto1988,rixwhite1990,vandenbergh1990,scorzabender1990,scorzabender1995,
+simienmichard1990}. 
+Not surprisingly, it is well known that 
+the identification of a stellar disc in an early-type galaxy, particularly when based on the galaxy's photometric properties, 
+is subject to inclination effects. 
+As predicted by \cite{carter1987}, this problem is largely overcome with kinematic analyses 
+(e.g.~\citealt{franx1989,nieto1991,rixwhite1992,cinzanovandermarel1993,donofrio1995,graham1998fornax}, 
+and the ATLAS$^{\rm 3D}$ survey, \citealt{cappellari2011}), 
+which allow one to determine the presence of a rotationally-supported component 
+in a way nearly insensitive to projection effects \citep{mcelroy1983,cappellari2007,emsellem2007}. 
 Yet, identifying the radial extent of an early-type galaxy's disc with respect to the spheroidal component can still be subtle. 
-Most early-type galaxies are classified as ``fast rotators'' \citep{atlas3dIII,scott2014}, 
+Studying both the surface brightness profiles and the ellipticity profiles 
+(a concept pioneered by \citealt{liller1960})\footnote{\cite{liller1960} 
+used ellipticity profiles to help identify elliptical and spiral galaxy type.} 
+of early-type galaxies in the Virgo cluster -- including those with elliptical (E), spindle and lenticular (S0) isophotes -- 
+\cite{liller1966} drew attention to the observation that many of the galaxies displayed 
+``characteristics intermediate between those of type E and type S0'', 
+and she classified them as ``ES'' galaxies\footnote{\cite{strom1977} and \cite{stromstrom1978} 
+classified the intermediate ``ES'' galaxy type as ``E/S0'', see also \cite{thompson1976}.}.  
+Building on this and other investigations of ellipticity profiles (e.g.~\citealt{stromstrom1978,ditullio1979}), 
+\cite{michard1984} used the classification ``S0-like'' for these early-type galaxies with humped ellipticity profiles, 
+dominated by a somewhat edge-on disc at intermediate radii.  
+\cite{nieto1988} identified two dozen such spheroid-dominated early-type galaxies, 
+whose discs do not prevail at large radii, 
+and referred to them as ``disk-ellipticals'' (or ``disky ellipticals'', \citealt{simienmichard1990}) 
+thereby more closely associating them with elliptical galaxies than lenticular galaxies.   
+However, as noted by \cite{nieto1988}, unless the orientation of the disc is favourable 
+(i.e.~somewhat edge-on), it can be missed.  
+The same is true when searching for pointy isophotes that are shaped by the combination of the spheroid and a near edge-on disc 
+(e.g.~\citealt{carter1978,carter1987,jedrzejewski1987,BenderMoellenhoff1987}). 
+Today, most early-type galaxies are classified as ``fast rotators\footnote{The term 
+``fast rotator'' is of course not new for describing certain early-type galaxies (e.g.~\citealt{bertinstiavelli1984,lakedressler1986}).}'' 
+\citep{atlas3dIII,scott2014}, 
 that is, they are rapidly rotating within their half-light radius. 
@@
 where $R$ is the semimajor-axis radius, $V$ is the mean velocity and $\sigma$ is the velocity dispersion, \citealt{emsellem2007}) 
-of 
+of: 
 (i) a lenticular galaxy, 
 comprised of a large-scale disc which dominates the light at large radii over a relatively smaller encased bulge,  
-i.e.~a disc-dominated central fast rotator that continues to be fast rotating beyond one half-light radius, 
-(ii) a discy elliptical galaxy \citep{kormendybender1996} 
+i.e.~a disc-dominated central fast rotator that continues to be fast rotating beyond one half-light radius; 
+(ii) a ``discy elliptical'' galaxy \citep{michard1984,nieto1988} 
 composed of an intermediate-scale disc embedded in a relatively larger spheroid which dominates the light at large radii,
-i.e.~a spheroid-dominated central fast rotator that becomes slow rotating beyond $1-2$ half-light radii, and  
+i.e.~a spheroid-dominated central fast rotator that becomes slow rotating beyond $1-2$ half-light radii; and  
 (iii) an elliptical galaxy with an additional nuclear stellar disc, 
 i.e.~a (spheroid-dominated) slow rotator. 
-This is sequence is analogue to that illustrated in Figure 2 of \cite{cappellari2011}, 
+This sequence is analogue to that illustrated in Figure 2 of \cite{cappellari2011}, 
 although here we emphasize the correspondence between the spheroid/disc decomposition of the surface brightness profile 
-and the ``shape'' of the ellipticity (assuming that the disc inclination is not close to face-on) and specific angular momentum profiles. 
-In general, stellar discs are intrinsically flat and circular; 
-their ellipticity, dictated by their inclination to our line of sight, is fixed. 
+and the ``shape'' of the ellipticity profile (assuming that the disc inclination is not close to face-on) 
+and also the specific angular momentum profiles. \\
+In general, stellar discs are intrinsically flat and close to circular; 
+their apparent ellipticity, dictated by their inclination to our line of sight, is fixed. 
 Spheroids are often rounder than the observed projection on the sky of their associated discs, 
@@
 whereas a radial decrease of ellipticity signifies the opposite case. 
-This approach can be taken to the next level by inspecting the isophotes for discy structures and checking the velocity line profiles for asymmetry 
-(e.g.~\citealt{scorzabender1995} and references therein; \citealt{scorza1998}). \\
-While some recent studies -- well aware of this problematic -- have correctly distinguished between large- and intermediate-scale discs, 
+This approach can be taken to the next level by inspecting the isophotes for discy structures 
+(e.g.~\citealt{carter1978,carter1987,capaccioli1987,jedrzejewski1987,BenderMoellenhoff1987}) 
+and checking the velocity line profiles for asymmetry 
+(e.g.~\citealt{franxillingworth1988ic1459,bender1990,rixwhite1992,scorzabender1995}, and references therein; \citealt{scorza1998}). \\
+While some recent studies have correctly distinguished between large- and intermediate-scale discs, 
 and modelled them accordingly (e.g.~\citealt{kormendybender2012,krajnovic2013}), 
 intermediate-scale discs have been missed by many galaxy modellers of late, 
-who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
+who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions 
+in which the disc does not dominate over the spheroid at large radii 
 as is observed with spiral galaxies. 
-Indeed, \citeauthor{graham2011} (\citeyear{graham2011}, his Figure 7) warned about such erroneous fits to spiral galaxies. 
-This bias has led to the rejection of many early-type galaxy decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
+Indeed, \citeauthor{graham2001} (\citeyear{graham2001}, his Figure 7) warned about such erroneous fits to late-type galaxies. 
+However, this has led to the rejection of many early-type galaxy decompositions 
+similar to that illustrated in the top middle panel of Figure \ref{fig:model}. 
 Unsurprisingly, studies affected by this bias have not obtained spheroid/disc decompositions with a spheroid-to-total ratio larger than $0.6 - 0.8$ 
 (e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}). \\
-As mentioned before, a photometric analysis allows one to identify the presence and the radial extent of a disc in an early-type galaxy 
+As mentioned before, an isophotal analysis allows one to identify the presence and the radial extent of a disc in an early-type galaxy 
 only when the disc has a certain level of inclination. 
@@
 but cannot help one determine the radial extent of a disc if the kinematic data are limited within one half-light radius. 
-Therefore, the best results are obtained when photometry and kinematics are combined together. 
+Therefore, the best results are obtained when photometry and kinematics are combined together. \\
 In this paper we focus on the increasingly overlooked occurence of intermediate-scale discs in galaxies with directly measured black hole masses. 
@@
 and the impact they have on the (black hole mass)-to-(spheroid stellar mass) ratio 
-which is used to constrain galaxy evolution models. \\
-This paper is structured as follows. 
+which is used to constrain galaxy evolution models. 
 In Section \ref{sec:gal} we present a detailed photometric analysis of three galaxies with intermediate-scale discs (Mrk 1216, NGC 1332, and NGC 3115) 
@@
 In Section \ref{sec:mm} we explore the important implications this has for the (black hole mass)-(spheroid stellar mass) diagram. 
-Finally, in Section \ref{sec:disc} we discuss our results in terms of galaxy evolution. }
-
-%There are currently two well-known types of stellar discs in galaxies.
-%The first are the large-scale discs (with exponential scale lengths of a few kiloparsec)
-%that dominate the light at large radii in spiral and lenticular galaxies;
-%the second are the small (tens to a couple of hundred parsec) nuclear discs observed in both early- and late-type galaxies
-%(e.g.~\citealt{scorzavandenbosch1998,rest2001,balcells2007,ledo2010}).
-%The origin of the nuclear discs has been speculated to arise from the infall of small satellite galaxies or gas clouds.
-%The origin, or at least the on-going feeding and growth, of the large-scale discs has been attributed to cold gas flows,
-%gas rich mergers and halo accretion events
-%(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,barneshernquist1992,khochfarsilk2006,dekel2009nat,ceverino2010,
-%ceverino2012,conselice2012,rubin2012,martini2013,ueda2014}),
-%and a thorough review can be found in \citet{combes2014arX,combes2014pro}.
-%On the other hand, intermediate-sized discs have not received the same level of attention
-%as their nuclear and large-scale homologues and
-%they have at times been labelled and rejected as ``unphysical'' when detected.
-%Here we focus on the increasingly overlooked occurence of intermediate-scale discs in galaxies with directly measured black hole masses.
-%We report on the photometric and kinematical signatures of these intermediate-sized stellar discs,
-%and the impact they have on the (black hole mass)-to-(spheroid stellar mass) ratio
-%which is used to constrain galaxy evolution models. \\
-%The majority of stellar discs have some level of inclination with respect to our line-of-sight,
-%and this makes them appear elliptical (rather than round) when seen in projection on the sky.
-%This can help one distinguish them from the more spherically-shaped spheroids.
-%Identifying the radial extent of these discs with respect to the spheroid can however be subtle.
-%Two-dimensional kinematic maps represent an important diagnostic tool for this purpose.
-%Most early-type galaxies are classified as ``central fast rotators'' \citep{franx1989,atlas3dIII,scott2014},
-%that is, they are rapidly rotating within their half-light radius.  
-%However, more extended kinematic maps \citep{arnold2014} reveal that 
-%some of the central fast rotators continue to be fast rotating at large radii, 
-%whereas other central fast rotators become slow rotators in their outer regions.
-%A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
-%is a signature of a large-scale disc, 
-%while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 
-%indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 
-%Unfortunately, such extended kinematic maps are not yet available for large numbers of galaxies in the local Universe. 
-%Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of stellar discs in early-type galaxies. \\
-%Building on the investigation of \cite{rixwhite1990}, 
-%the toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 
-%($\epsilon = 1 - b/a$, where $b/a$ is the ratio of minor-to-major axis length) of 
-%(i) a disc-dominated early-type galaxy, 
-%comprised of a large-scale disc which dominates the light at large radii over a relatively smaller encased bulge, 
-%(ii) a spehroid-dominated early-type galaxy with an additional nuclear stellar disc, 
-%and (iii) an early-type galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid 
-%which dominates the light at large radii. 
-%In general, stellar discs are intrinsically flat and circular; 
-%their ellipticity, dictated by their inclination to our line of sight, is fixed. 
-%Spheroids are often rounder than the observed projection on the sky of their associated discs, 
-%thus their average ellipticity is often lower than that of their disc. 
-%An ellipticity profile that increases with radius can be ascribed to an inclined disc that becomes progressively more important at large radii, 
-%whereas a radial decrease of ellipticity signifies the opposite case. 
-%This approach can be taken to the next level by inspecting the isophotes for discy structures and checking the velocity line profiles for asymmetry 
-%(e.g.~\citealt{scorzabender1995} and references therein; \citealt{scorza1998}). \\
-%The awareness that many so-called ``elliptical'' galaxies actually contain stellar discs 
-%dates back many years 
-%\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
-%vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
-%simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999} and, 
-%more recently, intermediate-scale discs were anything but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
-%However, intermediate-scale discs have been missed by many galaxy modellers of late, 
-%who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
-%as is observed with spiral galaxies. 
-%Indeed, \citeauthor{graham2011} (\citeyear{graham2011}, his Figure 7) warned about such erroneous fits to spiral galaxies. 
-%This bias has led to the rejection of many early-type galaxy decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
-%Unsurprisingly, studies affected by this bias have not obtained spheroid/disc decompositions with a spheroid-to-total ratio larger than $0.6 - 0.8$ 
-%(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}).
-%In this paper we investigate the influence this has had on research pertaining to supermassive black hole mass scaling relations involving the host spheroid. \\
-%This paper is structured as follows.
-%In Section \ref{sec:gal} we present a detailed photometric analysis of three galaxies with intermediate-scale discs (Mrk 1216, NGC 1332, and NGC 3115)
-%and we briefly describe another five galaxies with intermediate-scale discs (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697)
-%already modelled by us elsewhere in the literature.
-%We compare our photometric analysis with the kinematical information available from the literature,
-%and explain the differences between our galaxy models and past decompositions.
-%In Section \ref{sec:mm} we explore the important implications this has for the (black hole mass)-(spheroid stellar mass) diagram.
-%Finally, in Section \ref{sec:disc} we discuss our results in terms of galaxy evolution.
-%%and we present the location of ellicular galaxies, relative to other galaxies, in the Hubble grid.
+Finally, in Section \ref{sec:disc} we briefly discuss our results in terms of galaxy evolution 
+and we present the location of the ES galaxies relative to other disc galaxies 
+in a common classification scheme of Hubble type versus spheroid-to-disc ratio. }
 
@@
 The right panel displays a spheroid-dominated slow rotator (elliptical) with (an optional) nuclear stellar disc. 
-The middle panel presents a spheroid-dominated central fast rotator (discy elliptical) with an intermediate-sized disc embedded in the spheroid. }
+The middle panel presents a spheroid-dominated central fast rotator with an intermediate-sized disc embedded in the spheroid. }
 \label{fig:model}
@@
 \subsection{NGC 3115}
-The presence of a disc in the {\bf central fast rotator} NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
+The presence of a disc in the {\bf central fast rotator} NGC 3115 
+{\bf (e.g.~\citealt{strom1977,nieto1988,scorzabender1995}) }
+is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
 Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
@@
 \subsubsection{NGC 3377}
-\cite{lasker2014data} modelled the {\bf central fast rotator} NGC 3377 with a bulge + nuclear disc + disc + envelope, 
+\cite{lasker2014data} modelled the {\bf central fast rotator} NGC 3377 
+{\bf (e.g.~\citealt{jedrzejewski1987inproceedings,scorzabender1995}) }
+with a bulge + nuclear disc + disc + envelope, 
 and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total flux ratio of $0.35$; 
@@
 \subsubsection{NGC 4697}
-The {\bf central fast rotator} NGC 4697 represents an ``extreme'' case. 
+{\bf While NGC 4697 (e.g.~\citealt{carter1987,Jedrzejewski1987n720n1052n4697,davies1981}) 
+was explicitly referred to as a ``fast rotator'' by \cite{capaccioli1987} and \cite{petrou1981}, 
+it is only a central fast rotator} and it represents an ``extreme'' case. 
 \cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
@@
 \caption{NGC 1332.
-Same as Figure \ref{fig:n3115}, except for the following. 
+Similar to Figure \ref{fig:n3115}. 
 The surface brightness profile extends out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
@@
 \caption{Mrk 1216. 
-Same as Figure \ref{fig:n3115}, except for the following. 
+Similar to Figure \ref{fig:n3115}. 
 The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right).
@@
 The color lines represent the individual (PSF-convolved) model components:
-{\bf red solid = S\'ersic (spheroid), blue dashed = exponential (disc). }
+{\bf red solid = S\'ersic (spheroid), blue dashed = exponential (nuclear and intermediate-scale disc). }
 }
@@
 which has increased the galaxy size but preserved the bulge compactness. 
+{\bf Of course some lenticular/ES galaxies may have been built from mergers (e.g.~\citealt{querejeta2015}, and references therein). }
 The other compact massive spheroids of today's Universe belong to some galaxies with intermediate-scale discs. 
@@
 
-  \subsection{Ellicular galaxies in the Hubble grid}
-  The existence of the oft-overlooked, intermediate-scale discs
-  exposes a likely continuum of disc sizes in early-type
-  galaxies, as opposed to a dichotomy of nuclear discs versus large-scale
-  discs. The presence of these intermediate-scale discs also blurs the
-  distinction between elliptical (E) and lenticular (S0: $\epsilon = 1-b/a > 0.7$, \citealt{hubble1936,sandage1961}) galaxies and
-  arguably creates the need for a new subclass which bridges this
-  divide.  While expanding the galaxy nomenclature beyond ellipticals
-  with possible nuclear discs, and lenticulars with large-scale discs,
-  to include something like \emph{elliculars} with intermediate-scale
-  discs will be helpful for distinguishing among 
-  early-type galaxies with different disc scale-lengths, it should be
-  remembered that just as portions of the electromagnetic spectrum are
-  labelled according to their different wavelengths, there is still an
-  underlying continuum.  Similarly, binning early-type galaxies as
-  either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact
-  that a continuum exists.  Importantly, in the case of early-type
-  galaxies with intermediate-scale discs, this particular
-  rotation-based classification depends on the galaxy's radial range probed, 
-  changing from FR to SR as the radial extent is sufficiently increased. 
-  There is thus a need for more than two bins (E vs. S0, or FR vs. SR) 
-  and a continuum in the (Hubble-Jeans)-like classification schemes \citep{vandenbergh1997,sandage2005}. \\
-  It has been argued that the classification
-  scheme for ``elliptical'' galaxies should not be their apparent axis ratio
-  as seen on the plane of the sky (E0--E7), 
-  because this depends on the viewing angle rather than being intrinsic to the galaxy. 
-  Obviously when dealing with intermediate-scale discs, the boxy/discy shape of the isophotes is a function of both radius and disc inclination, 
-  making a single isophote shape parameter problematic and particularly inappropriate for the classification task at hand.
-  Section 4 of \cite{kormendybender1996} points out additional complications. 
-  Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, with a
-  continuum from pure elliptical galaxies to disc-dominated lenticular
-  galaxies (Figure \ref{fig:grid}).  \\
-  While spiral galaxies display a range of spheroid-to-total flux ratios
-  from 0 to $\sim$3/4 (e.g.~\citealt{grahamworley2008}, and references
-  therein), lenticular galaxies typically display a range from
-  $\sim$3/4 to $\sim$0.1 \citep{laurikainen2010}.  This spheroid-to-total flux
-  ratio is widely recognised as an important quantity, and its broad range observed in
-  lenticular galaxies recently led to a re-introduction of 
-  \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976})
-  Hubble comb, in which both late-type galaxies (i.e.~spiral galaxies)
-  and lenticular galaxies form separate arms of an expanded Hubble-Jeans tuning
-  fork, with an additional arm for disc galaxies hosting anaemic spiral
-  patterns \citep{cappellari2011kmdr,kormendybender2012}.  
-  However because every spiral Hubble type (e.g.~Sa, Sb, Sc), not just the S0 galaxies, 
-  has a broad range of spheroid-to-total ratio, and because this information is not captured by the Hubble comb, 
-  a grid of spiral morphological type (predominantly determined by the spiral
-  arms) versus spheroid-to-total ratio can also be useful for classifying galaxies.  \\
-  In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale
-  discs in such a ``Hubble grid'', which is effectively the quantitative scheme used by  
-  \cite{boroson1981}, \cite{kent1985}, \cite{kodaira1986}, \cite{simiendevaucouleurs1986} 
-  in which each galaxy type displays a range of spheroid-to-total flux ratio.
-  Rather than a scheme in which the morphological type (a, b, c,
-  etc.) changes if the spheroid-to-total ratio changes -- as in the Hubble comb -- here
-  the galaxy type is linked to the nature and winding of the spiral arms
-  which has been the primary criteria used to classify spiral galaxies
-  over the last half century \citep{sandage1961}.  
-  Allowing for the varying spheroid-to-total ratio among each galaxy type, 
-  the Hubble grid helps to reveal how ellicular galaxies unify the early-type sequence and compare with late-type galaxies.
+\subsection{ES galaxies in the Hubble grid}
+{\bf The existence of intermediate-scale discs has led to the suggestion of a likely continuum of disc sizes in early-type galaxies 
+\citep{simiendevaucouleurs1986,capaccioli1988,bender1989,simienmichard1990,scorza1993,scorzavandenBosch1998} 
+as opposed to a dichotomy of say nuclear discs versus large-scale discs.  
+The presence of these intermediate-scale discs blurs the distinction between elliptical (E) and lenticular (S0) galaxies, 
+or central slow-rotators (SR) versus central fast-rotators (FR), see \citeauthor{cappellari2011} (\citeyear{cappellari2011}, their Figure 1 and 2).   
+There is a need for more than two bins (i.e.~nuclear vs.~large-scale disc, E vs.~S0, SR vs.~FR), 
+and a need for a continuum in the (Hubble-Jeans)-like classification 
+schemes\footnote{As noted by \cite{vandenbergh1997} and \cite{sandage2005}, 
+it was Sir James Jeans (1928) who introduced the (tuning fork)-shaped diagram that encapsulated \citeauthor{Hubble1926}'s (\citeyear{Hubble1926}) 
+elliptical-spiral sequence -- itself motivated by the earlier work of \cite{Jeans1919}.}.
+
+It has been argued that the classification scheme for "elliptical" galaxies should not be 
+their apparent axis ratio as seen on the plane of the sky (originally E0--E7, then E0--E4,  see Hubble 1936; Sandage 1961; 
+Liller 1966; Cappellari et al.\ 2011), because this depends on the viewing angle rather than being intrinsic to the galaxy.  
+Obviously when dealing with intermediate-scale discs, 
+the boxy/discy shape of the isophotes is also a function of both radius and disc inclination, 
+making single isophotal shape parameters problematic and particularly inappropriate for the ES class.  
+Section 4 of Kormendy & Bender (1996) points out additional complications in regard to this.  
+Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, 
+with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies (e.g., Capaccioli et al.\ 1988, and references therein).   
+This spheroid-to-total flux (or better mass) ratio is widely recognised as an important quantity, 
+and its broad range observed in the lenticular galaxies led Cappellari et al.\ (2011b) to present the "Hubble comb".   
+Building on van den Bergh's (1976) diagram in which both late-type galaxies (i.e., spiral galaxies) 
+and early-type galaxies form separate prongs of an expanded Hubble-Jeans tuning fork, 
+with an additional prong for disc galaxies hosting anaemic spiral patterns, 
+Cappellari et al. (2011b, see also Kormendy & Bender 2012) presented a scheme in which the morphological type (a, b, c, etc.) 
+changed if the spheroid-to-total ratio changed.  
+However the primary criteria used to assign the spiral galaxy type over the last half century (Sandage 1961) 
+has been the nature of the spiral arms --- the extent to which they are unwound, pitch angle, 
+and the degree of resolution --- rather than the spheroid-to-total ratio.   
+Indeed, in the Hubble Atlas of Galaxies, Sandage (1961) notes that Sa type galaxies exist with both small and large bulges.
+
+The grid seen in Figure~6 and discussed in Graham (2014) was used by Freeman (1970, his Figure~9), 
+Boroson (1981), Kent (1985), Kodaira et al. (1986), Simien & de Vaucouleurs (1986) and others, 
+and allows for the varying spheroid-to-total ratio among each galaxy type.   
+Rather than using the extended classification scheme for early-type galaxies (E - E$^+$ - L$^-$ - L$^o$ - L$^+$-S0, 
+corresponding to the numerical T-type ranging from -5 to 0, e.g., de Vaucouleurs et al.\ 1964, Heidmann et al.\ 1972), 
+we have simply grouped them all together.   While, collectively, spiral galaxies typically display a range of spheroid-to-total flux 
+ratios from 0 to 3/4 (e.g. Graham & Worley 2008, and references therein), 
+lenticular galaxies commonly display a range from 3/4 to 0.1 (Laurikainen et al. 2010), and the ES class have larger ratios.  
+The purpose here is not to provide a complete classification scheme, 
+but to simply show where the early-type galaxies with intermediate-scale discs (ES) reside relative to the other 
+Hubble galaxy types in this familiar diagram which has tended not to include the elliptical galaxies to date.
+
+In Figure 6, can you please move the ES galaxy to a spheroid-to-total ratio of 0.75.  
+Common lenticular galaxies with large-scale discs are known to have ratios up to ~0.75.
+Moving the ES galaxy in Figure 6 will therefore better match with the idea that these are 
+intermediate between S0 and E galaxies. }
 
@@
 \includegraphics[width=\columnwidth]{Hubblegrid.pdf}
-  \caption{The Hubble grid \citep{graham2014review},
-  which uses the mean pitch angle of the arms in spiral galaxies to define their morphological type.
-  Ellicular (ES) galaxies are intermediate between elliptical (E) and lenticular (S0) galaxies. }
+\caption{The Hubble grid showing the location of the ES galaxies, intermediate between
+elliptical (E) and lenticular (S0) galaxies, relative to the spiral galaxies.  }
 \label{fig:grid}

### 2015-10-28 python_codes/paper_figures/MbhMsph/figures.py

@@ -658,8 +658,8 @@ def mbh_vs_mass_sph():
 	ML = 10**log_ML
 	
 	mass_sph = ML*10**(-0.4*(mag_sph-3.25))
+	perr_mass_sph =  ML*10**(-0.4*(mag_sph-merr_mag_sph-3.25)) - mass_sph
 	merr_mass_sph = -ML*10**(-0.4*(mag_sph+perr_mag_sph-3.25)) + mass_sph
-	perr_mass_sph = +ML*10**(-0.4*(mag_sph-merr_mag_sph-3.25)) - mass_sph
 	
 	log_mass_sph = np.log10(mass_sph)
 	perr_log_mass_sph = np.log10(1+perr_mass_sph/mass_sph)
@@ -698,18 +698,27 @@ def mbh_vs_mass_sph():
 			morph_coreList.append('outlier')	
         morph_core = np.asarray(morph_coreList)
 	       
-        ### produce .dat file for paper with Ewan (19 June 2015)
-        datfileName = '/Users/gsavorgnan/galaxy_vivisection/results/tables/mbh_vs_mass_sph.dat'
+       #### produce .dat file for paper with Ewan (19 June 2015)
+       #datfileName = '/Users/gsavorgnan/galaxy_vivisection/results/tables/mbh_vs_mass_sph.dat'
+       #datfile = open(datfileName, 'w')
+       #datfile.write('# galaxy    logMassSph	  +err_logMassSph     -err_logMassSph	  average_err_logMassSph     logMassBH     +err_logMassBH    -err_logMassBH    average_err_logMassBH	 core	type   \n')
+       #for a,b,c,d,e,f,g,h,i,j,k in zip(gal_id, log_mass_sph, perr_log_mass_sph, merr_log_mass_sph, 
+       #	0.5*(perr_log_mass_sph + merr_log_mass_sph),
+       #	log_mbh, perr_log_mbh, merr_log_mbh, 0.5*(merr_log_mbh + perr_log_mbh), 
+       #	core, simplemorphtype):
+       #	datfile.write(str(a) + '    ' + str(b) + '    ' + str(c) + '	' + str(d) + '    ')
+       #	datfile.write(str(e) + '    ' + str(f) + '    ' + str(g) + '	' + str(h) + '    ') 
+       #	datfile.write(str(i) + '    ' + str(j) + '    ' + str(k) + '\n')
+       #datfile.close()
+
+        ### produce .dat file for Francesco (28 October 2015)
[…]

### 2015-10-30 papers/ellicular/ellicular.tex
fanculo

@@
 \usepackage{natbib}
+\usepackage{soul}
 \bibliographystyle{mnras}
@@
 Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of a stellar disc in an early-type galaxy. \\
-Building on the investigation of \cite{rixwhite1990}, 
+Building on the investigations in works such as \cite{liller1966}, \cite{Jedrzejewski1987INPROCEEDINGS} and \cite{rixwhite1990}, 
 the toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 
@@
 i.e.~a (spheroid-dominated) slow rotator. 
-This sequence is analogue to that illustrated in Figure 2 of \cite{cappellari2011}, 
+This sequence is analogue to that illustrated in Figure 2 of \cite{cappellari2011kmdr}, 
 although here we emphasize the correspondence between the spheroid/disc decomposition of the surface brightness profile 
@@
 and also the specific angular momentum profiles. \\
-In general, stellar discs are intrinsically flat and close to circular; 
+In general, stellar discs are intrinsically flat and close to circular \citep{Andersen2001,AndersenBershady2002}; 
 their apparent ellipticity, dictated by their inclination to our line of sight, is fixed. 
@@
 The presence of these intermediate-scale discs blurs the distinction between elliptical (E) and lenticular (S0) galaxies, 
-or central slow-rotators (SR) versus central fast-rotators (FR), see \citeauthor{cappellari2011} (\citeyear{cappellari2011}, their Figure 1 and 2).   
+or slow-rotators (SR) versus fast-rotators (FR), 
+see \citeauthor{cappellari2011kmdr} (\citeyear{cappellari2011kmdr}, their Figure 1 and 2).   
 There is a need for more than two bins (i.e.~nuclear vs.~large-scale disc, E vs.~S0, SR vs.~FR), 
@@
 schemes\footnote{As noted by \cite{vandenbergh1997} and \cite{sandage2005}, 
-it was Sir James Jeans (1928) who introduced the (tuning fork)-shaped diagram that encapsulated \citeauthor{Hubble1926}'s (\citeyear{Hubble1926}) 
-elliptical-spiral sequence -- itself motivated by the earlier work of \cite{Jeans1919}.}.
-
-It has been argued that the classification scheme for "elliptical" galaxies should not be 
-their apparent axis ratio as seen on the plane of the sky (originally E0--E7, then E0--E4,  see Hubble 1936; Sandage 1961; 
-Liller 1966; Cappellari et al.\ 2011), because this depends on the viewing angle rather than being intrinsic to the galaxy.  
+it was Sir James \cite{jeans1928} who introduced the (tuning fork)-shaped diagram that encapsulated \citeauthor{Hubble1926}'s (\citeyear{Hubble1926}) 
+elliptical-spiral sequence -- itself motivated by the earlier work of \cite{Jeans1919}.}.     \\
+It has been argued that the classification scheme for ``elliptical'' galaxies should not be 
+their apparent axis ratio as seen on the plane of the sky (originally E0--E7, see \citealt{hubble1936,sandage1961}, 
+then E0--E4, see \citealt{liller1966} and also \citealt{gorbachev1970}), 
+because this depends on the viewing angle rather than being intrinsic to the galaxy.  
 Obviously when dealing with intermediate-scale discs, 
@@
 making single isophotal shape parameters problematic and particularly inappropriate for the ES class.  
-Section 4 of Kormendy & Bender (1996) points out additional complications in regard to this.  
+Section 4 of \cite{kormendybender1996} points out additional complications in regard to this.  
 Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, 
-with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies (e.g., Capaccioli et al.\ 1988, and references therein).   
+with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies (e.g.~\citealt{capaccioli1988}, and references therein).   
 This spheroid-to-total flux (or better mass) ratio is widely recognised as an important quantity, 
-and its broad range observed in the lenticular galaxies led Cappellari et al.\ (2011b) to present the "Hubble comb".   
-Building on van den Bergh's (1976) diagram in which both late-type galaxies (i.e., spiral galaxies) 
+and its broad range observed in the lenticular galaxies led \cite{cappellari2011kmdr} to present the ``Hubble comb''.   
+Building on \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976}) diagram in which both late-type galaxies (i.e.~spiral galaxies) 
 and early-type galaxies form separate prongs of an expanded Hubble-Jeans tuning fork, 
 with an additional prong for disc galaxies hosting anaemic spiral patterns, 
-Cappellari et al. (2011b, see also Kormendy & Bender 2012) presented a scheme in which the morphological type (a, b, c, etc.) 
+\citeauthor{cappellari2011kmdr} (\citeyear{cappellari2011kmdr}, see also \citealt{kormendybender2012}) 
+presented a scheme in which the morphological type (a, b, c, etc.) 
 changed if the spheroid-to-total ratio changed.  
-However the primary criteria used to assign the spiral galaxy type over the last half century (Sandage 1961) 
-has been the nature of the spiral arms --- the extent to which they are unwound, pitch angle, 
-and the degree of resolution --- rather than the spheroid-to-total ratio.   
-Indeed, in the Hubble Atlas of Galaxies, Sandage (1961) notes that Sa type galaxies exist with both small and large bulges.
-
-The grid seen in Figure~6 and discussed in Graham (2014) was used by Freeman (1970, his Figure~9), 
-Boroson (1981), Kent (1985), Kodaira et al. (1986), Simien & de Vaucouleurs (1986) and others, 
+However the primary criteria used to assign the spiral galaxy type over the last half century \citep{sandage1961} 
+has been the nature of the spiral arms -- the extent to which they are unwound, pitch angle, 
+and the degree of resolution -- rather than the spheroid-to-total ratio.   
+Indeed, in the Hubble Atlas of Galaxies, \cite{sandage1961} notes that Sa type galaxies exist with both small and large bulges 
+(see also \citealt{VorontsovvelYaminovArkhipova1962} and \citealt{Vorontsovvelyaminovnoskova1973}). \\
+The grid seen in Figure \ref{fig:grid} and discussed in \cite{graham2014review} 
+was used by \citeauthor{freeman1970} (\citeyear{freeman1970}, his Figure 9), 
+\cite{boroson1981}, \cite{kent1985}, \cite{kodaira1986}, \cite{simiendevaucouleurs1986} and others, 
 and allows for the varying spheroid-to-total ratio among each galaxy type.   
-Rather than using the extended classification scheme for early-type galaxies (E - E$^+$ - L$^-$ - L$^o$ - L$^+$-S0, 
-corresponding to the numerical T-type ranging from -5 to 0, e.g., de Vaucouleurs et al.\ 1964, Heidmann et al.\ 1972), 
-we have simply grouped them all together.   While, collectively, spiral galaxies typically display a range of spheroid-to-total flux 
-ratios from 0 to 3/4 (e.g. Graham & Worley 2008, and references therein), 
-lenticular galaxies commonly display a range from 3/4 to 0.1 (Laurikainen et al. 2010), and the ES class have larger ratios.  
+Rather than using the extended classification scheme for early-type galaxies (E -- E$^+$ -- L$^-$ -- L$^o$ -- L$^+$ -- S0, 
+corresponding to the numerical T-type ranging from -5 to 0, e.g.~\citealt{devaucouleurs1964,heidmann1972}), 
+we have simply grouped them all together.  
+While, collectively, spiral galaxies typically display a range of spheroid-to-total flux 
+ratios from $0$ to $\approx 3/4$ (e.g.~\citealt{grahamworley2008}, and references therein), 
+lenticular galaxies commonly display a range from $\approx 3/4$ to $\approx 0.1$ \citep{laurikainen2010}, and the ES class have larger ratios.  
 The purpose here is not to provide a complete classification scheme, 
 but to simply show where the early-type galaxies with intermediate-scale discs (ES) reside relative to the other 
-Hubble galaxy types in this familiar diagram which has tended not to include the elliptical galaxies to date.
+Hubble galaxy types in this familiar diagram which has tended not to include the elliptical galaxies to date. }
 
-In Figure 6, can you please move the ES galaxy to a spheroid-to-total ratio of 0.75.  
-Common lenticular galaxies with large-scale discs are known to have ratios up to ~0.75.
-Moving the ES galaxy in Figure 6 will therefore better match with the idea that these are 
-intermediate between S0 and E galaxies. }
-
-\begin{figure}[h]
+\begin{figure}
 \begin{center}
@@
 \section{Summary and conclusions}
-{\bf Early-type galaxies display a broad distribution of spheroid-to-total flux ratios (e.g.~\citealt{cappellari2011}), 
+{\bf Early-type galaxies display a broad distribution of spheroid-to-total flux ratios (e.g.~\citealt{cappellari2011kmdr}), 
 going from disc-less, ``pure'' elliptical galaxies (slow rotators) 
 to disc-dominated lenticular galaxies (central fast rotators that continue to be fast rotating also beyond one half-light radius). 
-%\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
-%vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
-%simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,
-%bendersaglia1999}\footnote{Many past studies were hampered by bulge/disc decompositions which forced an $R^{1/4}$ model for the bulge component 
-%and thus obtained spurious bulge-to-disc ratios, and from the \emph{IRAF} task {\tt ellipse} which does not report the correct deviations of isophotes 
-%from ellipses \citep{ciambur2015}.}. 
 In between these two extremes lie galaxies with intermediate-scale discs 
@@
 GS is grateful to Matteo Fossati, Luca Cortese and Giuseppe Gavazzi for useful comments and discussion. 
-% referee thank you!!
+We are grateful to our anynimous referee for their very careful review of our paper, 
+and for the comments, corrections and suggestions that ensued. 
 This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} on-board the Spitzer Space Telescope, 

### 2015-11-04 papers/ellicular/sabotage/ellicular.tex
wed

--- 2015-10-30 papers/ellicular/ellicular.tex
@@
 {\bf The awareness that \emph{many} early-type galaxies contain previously over-looked stellar discs dates back half a century 
-\citep{liller1966,michard1984,djorgovski1985,jedrzejewski1987,BenderMoellenhoff1987,
-carter1987,capaccioli1987,capaccioli1988,stromstrom1978,bender1988,bender1990,
+\citep{liller1966,stromstrom1978,michard1984,djorgovski1985,jedrzejewski1987,BenderMoellenhoff1987,
+carter1987,capaccioli1987,capaccioli1988,bender1988,bender1990,
 nieto1988,rixwhite1990,vandenbergh1990,scorzabender1990,scorzabender1995,
 simienmichard1990}. 
-Not surprisingly, it is well known that 
+It is well known that 
 the identification of a stellar disc in an early-type galaxy, particularly when based on the galaxy's photometric properties, 
@@
 Studying both the surface brightness profiles and the ellipticity profiles 
-(a concept pioneered by \citealt{liller1960})\footnote{\cite{liller1960} 
-used ellipticity profiles to help identify elliptical and spiral galaxy type.} 
 of early-type galaxies in the Virgo cluster -- including those with elliptical (E), spindle and lenticular (S0) isophotes -- 
@@
 ``characteristics intermediate between those of type E and type S0'', 
-and she classified them as ``ES'' galaxies\footnote{\cite{strom1977} and \cite{stromstrom1978} 
-classified the intermediate ``ES'' galaxy type as ``E/S0'', see also \cite{thompson1976}.}.  
+and she classified them as ``ES'' galaxies.  
 Building on this and other investigations of ellipticity profiles (e.g.~\citealt{stromstrom1978,ditullio1979}), 
@@
 whose discs do not prevail at large radii, 
-and referred to them as ``disk-ellipticals'' (or ``disky ellipticals'', \citealt{simienmichard1990}) 
-thereby more closely associating them with elliptical galaxies than lenticular galaxies.   
+and referred to them as ``disk-ellipticals'' (or ``disky ellipticals'', \citealt{simienmichard1990}).   
 However, as noted by \cite{nieto1988}, unless the orientation of the disc is favourable 
 (i.e.~somewhat edge-on), it can be missed.  
-The same is true when searching for pointy isophotes that are shaped by the combination of the spheroid and a near edge-on disc 
-(e.g.~\citealt{carter1978,carter1987,jedrzejewski1987,BenderMoellenhoff1987}). 
-Today, most early-type galaxies are classified as ``fast rotators\footnote{The term 
-``fast rotator'' is of course not new for describing certain early-type galaxies (e.g.~\citealt{bertinstiavelli1984,lakedressler1986}).}'' 
+Today, most early-type galaxies are classified as ``fast rotators'' 
 \citep{atlas3dIII,scott2014}, 
@@
 and also the specific angular momentum profiles. \\
-In general, stellar discs are intrinsically flat and close to circular \citep{Andersen2001,AndersenBershady2002}; 
+In general, stellar discs are intrinsically flat and close to circular (e.g.~\citealt{Andersen2001,AndersenBershady2002}); 
 their apparent ellipticity, dictated by their inclination to our line of sight, is fixed. 
@@
 as is observed with spiral galaxies. 
-Indeed, \citeauthor{graham2001} (\citeyear{graham2001}, his Figure 7) warned about such erroneous fits to late-type galaxies. 
-However, this has led to the rejection of many early-type galaxy decompositions 
+This has led to the rejection of many early-type galaxy decompositions 
 similar to that illustrated in the top middle panel of Figure \ref{fig:model}. 
@@
 In Section \ref{sec:mm} we explore the important implications this has for the (black hole mass)-(spheroid stellar mass) diagram. 
-Finally, in Section \ref{sec:disc} we briefly discuss our results in terms of galaxy evolution 
-and we present the location of the ES galaxies relative to other disc galaxies 
-in a common classification scheme of Hubble type versus spheroid-to-disc ratio. }
+Finally, in Section \ref{sec:disc} we briefly discuss our results in terms of galaxy evolution. }
 
@@
 Three examples of galaxies with intermediate-scale discs are Mrk 1216, NGC 1332, and NGC 3115. 
-In the following Sections, we present a photometric analysis of these three galaxies, 
+In the following Section, we present a photometric analysis of these three galaxies, 
 and we compare our results with the kinematical analysis available from the literature for Mrk 1216 and NGC 3115. 
@@
 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
-Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
+Less obvious is the radial extent of this disc if one only relies on a visual inspection of the galaxy image. 
 The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
@@
 (at semi-major axis length $R_{\rm maj} \sim 15~\rm arcsec$). 
-Such rings are common in early-type galaxies \citep{michardmarchal1993}.
+Such rings are common in early-type galaxies (e.g.~\citealt{michardmarchal1993}).
 The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
@@
 Today's Universe is populated by an abundance of compact, massive spheroids, 
-with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{graham2013review,GDS2015}. 
+with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{GDS2015}. 
 Some of these local compact massive spheroids are encased within a large-scale disc, 
@@
 \label{fig:mm}
-\end{center}
-\end{figure}
-
-\subsection{ES galaxies in the Hubble grid}
-{\bf The existence of intermediate-scale discs has led to the suggestion of a likely continuum of disc sizes in early-type galaxies 
-\citep{simiendevaucouleurs1986,capaccioli1988,bender1989,simienmichard1990,scorza1993,scorzavandenBosch1998} 
-as opposed to a dichotomy of say nuclear discs versus large-scale discs.  
-The presence of these intermediate-scale discs blurs the distinction between elliptical (E) and lenticular (S0) galaxies, 
-or slow-rotators (SR) versus fast-rotators (FR), 
-see \citeauthor{cappellari2011kmdr} (\citeyear{cappellari2011kmdr}, their Figure 1 and 2).   
-There is a need for more than two bins (i.e.~nuclear vs.~large-scale disc, E vs.~S0, SR vs.~FR), 
-and a need for a continuum in the (Hubble-Jeans)-like classification 
-schemes\footnote{As noted by \cite{vandenbergh1997} and \cite{sandage2005}, 
-it was Sir James \cite{jeans1928} who introduced the (tuning fork)-shaped diagram that encapsulated \citeauthor{Hubble1926}'s (\citeyear{Hubble1926}) 
-elliptical-spiral sequence -- itself motivated by the earlier work of \cite{Jeans1919}.}.     \\
-It has been argued that the classification scheme for ``elliptical'' galaxies should not be 
-their apparent axis ratio as seen on the plane of the sky (originally E0--E7, see \citealt{hubble1936,sandage1961}, 
-then E0--E4, see \citealt{liller1966} and also \citealt{gorbachev1970}), 
-because this depends on the viewing angle rather than being intrinsic to the galaxy.  
-Obviously when dealing with intermediate-scale discs, 
-the boxy/discy shape of the isophotes is also a function of both radius and disc inclination, 
-making single isophotal shape parameters problematic and particularly inappropriate for the ES class.  
-Section 4 of \cite{kormendybender1996} points out additional complications in regard to this.  
-Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, 
-with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies (e.g.~\citealt{capaccioli1988}, and references therein).   
-This spheroid-to-total flux (or better mass) ratio is widely recognised as an important quantity, 
-and its broad range observed in the lenticular galaxies led \cite{cappellari2011kmdr} to present the ``Hubble comb''.   
-Building on \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976}) diagram in which both late-type galaxies (i.e.~spiral galaxies) 
-and early-type galaxies form separate prongs of an expanded Hubble-Jeans tuning fork, 
-with an additional prong for disc galaxies hosting anaemic spiral patterns, 
-\citeauthor{cappellari2011kmdr} (\citeyear{cappellari2011kmdr}, see also \citealt{kormendybender2012}) 
-presented a scheme in which the morphological type (a, b, c, etc.) 
-changed if the spheroid-to-total ratio changed.  
-However the primary criteria used to assign the spiral galaxy type over the last half century \citep{sandage1961} 
-has been the nature of the spiral arms -- the extent to which they are unwound, pitch angle, 
-and the degree of resolution -- rather than the spheroid-to-total ratio.   
-Indeed, in the Hubble Atlas of Galaxies, \cite{sandage1961} notes that Sa type galaxies exist with both small and large bulges 
-(see also \citealt{VorontsovvelYaminovArkhipova1962} and \citealt{Vorontsovvelyaminovnoskova1973}). \\
-The grid seen in Figure \ref{fig:grid} and discussed in \cite{graham2014review} 
-was used by \citeauthor{freeman1970} (\citeyear{freeman1970}, his Figure 9), 
-\cite{boroson1981}, \cite{kent1985}, \cite{kodaira1986}, \cite{simiendevaucouleurs1986} and others, 
-and allows for the varying spheroid-to-total ratio among each galaxy type.   
-Rather than using the extended classification scheme for early-type galaxies (E -- E$^+$ -- L$^-$ -- L$^o$ -- L$^+$ -- S0, 
-corresponding to the numerical T-type ranging from -5 to 0, e.g.~\citealt{devaucouleurs1964,heidmann1972}), 
-we have simply grouped them all together.  
-While, collectively, spiral galaxies typically display a range of spheroid-to-total flux 
-ratios from $0$ to $\approx 3/4$ (e.g.~\citealt{grahamworley2008}, and references therein), 
-lenticular galaxies commonly display a range from $\approx 3/4$ to $\approx 0.1$ \citep{laurikainen2010}, and the ES class have larger ratios.  
-The purpose here is not to provide a complete classification scheme, 
-but to simply show where the early-type galaxies with intermediate-scale discs (ES) reside relative to the other 
-Hubble galaxy types in this familiar diagram which has tended not to include the elliptical galaxies to date. }
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{Hubblegrid.pdf}
-\caption{The Hubble grid showing the location of the ES galaxies, intermediate between
-elliptical (E) and lenticular (S0) galaxies, relative to the spiral galaxies.  }
-\label{fig:grid}
 \end{center}

### 2015-11-04 papers/mbhn/mbhn.tex
wed

@@
 yet its physical origin has remained unexplained for decades. 
-The S\'ersic model parametrizes the intensity $I$ as a function of the projected galactic radius $R$ such that
+The S\'ersic model parametrizes the intensity of light $I$ as a function of the projected galactic radius $R$ such that
 \begin{equation}
@@
 for samples of galaxies similar to that used by \cite{grahamdriver2007}, 
-but they surprisingly failed to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation. 
+but they unexpectedly failed to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation. 
 This issue was tackled by \cite{savorgnan2013}, who collected the S\'ersic index measurements published by 
@@
 and still regained a significant $M_{\rm BH} - n_{\rm sph}$ relation. 
-This was suggestive that the individual galaxy decompositions of \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} were not accurate, 
+This was suggesting that the individual galaxy decompositions of \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} were not accurate, 
 i.e.~each individual study obtained ``noisy'' S\'ersic index measurements 
@@
 galaxy luminosity, spheroid luminosity and spheroid stellar mass. 
-In this Paper (\emph{Paper III}) we focus on the $M_{\rm BH} - n_{\rm sph}$ relation. \\
-This paper is structured as follows...
+Here we focus on the $M_{\rm BH} - n_{\rm sph}$ relation. \\
+This paper (\emph{Paper III}) is structured as follows...
 
@@
 S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
-As in \emph{Paper II}, here we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
-The early-type bin includes two galaxies classified as E/S0, 
-whereas two galaxies classified as S0/Sp and another two classified as mergers are included in neither the early- nor the late-type bin.
+As in \emph{Paper II}, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
+The early-type bin includes the two galaxies classified as E/S0, 
+whereas the two galaxies classified as S0/Sp and the two galaxies classified as mergers are included in neither the early- nor the late-type bin.
 
@@
 As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
-and $M_{\rm BH} - n_{\rm sph}$ diagrams (see Table \ref{tab:lregLn} and Table \ref{tab:lregMn}, respectively) 
+(Table \ref{tab:lregLn} and Figure \ref{fig:magn})
+and $M_{\rm BH} - n_{\rm sph}$ (Table \ref{tab:lregMn} and Figure \ref{fig:mbhn}) diagrams 
 was performed using three different routines: 
@@
 whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
-allow one to predict values of the ordinate observable ($Y$) with the best possible precision.
-
-%for different morphological types (elliptical/lenticular/spiral)
+allow one to predict the value of the observable $Y$ with the best possible precision. \\
+We searched for extreme outliers in both the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams, 
+and found that in our $L_{\rm sph} - n_{\rm sph}$ plot there are no $3\sigma$ outliers, 
+whereas in our $M_{\rm BH} - n_{\rm sph}$ plot 
+the S0 galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
+These two galaxies have therefore been excluded from the rest of the analysis. \\
+{\bf fitexy does better job, we report that} \\
 
 \subsection{$L_{\rm sph} - n_{\rm sph}$}
+Following \cite{graham2001}, 
+who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
+\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013} 
+and obtained two separate $L_{\rm sph} - n_{\rm sph}$ symmetrical linear regressions for elliptical galaxies and the bulges of disk galaxies 
+(in the B- and K-band, respectively). 
+At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013} were of the best quality available 
+to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
+However, these datasets were not the output of a homogeneous analysis, 
+but the collection of the results from various past bulge/disk decomposition studies. 
+It is also worth mentioning that, 
+although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
+{\bf the dust corrections are not precise today refs??, imagine at the time.....}  
+Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our top-quality dataset  
+derived from our state-of-the-art multicomponent galaxy decompositions, 
+that were performed in a consistent manner 
+and using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
+The values of the slope and intercept of the bisector linear regression for the lenticular galaxies 
+are not consistent within the errors with those for the spiral galaxies, 
+but are consistent within the errors with those for the elliptical galaxies.  
+Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
+elliptical and lenticular galaxies form together a single sequence, 
+whereas the combination of lenticular and spiral galaxies do not. 
+{\bf why?? dust? multicomponent? classification?}
+
+ell and s0 have same slope -> early seq \\
+different from late seq \\
 
@@
 \subsection{$M_{\rm BH} - n_{\rm sph}$}
+in sav13 we had m-l from gs13 for core sersic and sersic \\
+however in paper II we say that this is not the case, there are red and blue seq \\
+therefore we look for red and blue seq here \\
+consistent with each other \\
 
@@
 \end{figure}
+
+\section{Discussion}
+intr scatter of correlation for all?\\
+data suggest that m-n more fundamental than l-n ? \\
 
@@
 
-Elliptical (30)	       & BCES $(Y|X)$		    & $-25.46 \pm 1.12$ & $38.47 \pm 114.45$ & $0.76$ & $-$ & $6.37$ \\
+Elliptical (E) (30)    & BCES $(Y|X)$		    & $-25.46 \pm 1.12$ & $38.47 \pm 114.45$ & $0.76$ & $-$ & $6.37$ \\
 		       & mFITEXY $(Y|X)$	    & $-25.74 \pm 0.18$ & $-9.74 \pm 1.59$ & $0.76$ & $0.24^{+0.32}_{-0.24}$ & $0.94$ \\
@@
 
-Lenticular (11)	       & BCES $(Y|X)$		    & $-22.08 \pm 1.66$ & $33.52 \pm 98.87$ & $0.33$ & $-$ & $6.09$ \\
+Lenticular (S0) (11)   & BCES $(Y|X)$		    & $-22.08 \pm 1.66$ & $33.52 \pm 98.87$ & $0.33$ & $-$ & $6.09$ \\
 		       & mFITEXY $(Y|X)$	    & $-22.11 \pm 0.24$ & $-6.31 \pm 2.45$ & $0.33$ & $0.42^{+0.28}_{-0.17}$ & $0.71$ \\
@@
 
-Spiral (17)	       & BCES $(Y|X)$		    & $-22.33 \pm 0.26$ & $-5.31 \pm 5.83$ & $0.18$ & $-$ & $1.15$ \\
+Spiral (Sp) (17)       & BCES $(Y|X)$		    & $-22.33 \pm 0.26$ & $-5.31 \pm 5.83$ & $0.18$ & $-$ & $1.15$ \\
 		       & mFITEXY $(Y|X)$	    & $-22.22 \pm 0.19$ & $-2.17 \pm 0.98$ & $0.18$ & $0.53^{+0.24}_{-0.13}$ & $0.72$ \\
@@
 \\
-Early-type (43)	       & BCES $(Y|X)$		    & $-24.55 \pm 0.22$ & $-11.84 \pm 2.29$ & $0.64$ & $-$ & $1.50$ \\
+Early-type (E+S0) (43) & BCES $(Y|X)$		    & $-24.55 \pm 0.22$ & $-11.84 \pm 2.29$ & $0.64$ & $-$ & $1.50$ \\
 		       & mFITEXY $(Y|X)$	    & $-24.74 \pm 0.14$ & $-8.86 \pm 0.66$ & $0.51$ & $0.27^{+0.20}_{-0.27}$ & $0.87$ \\
@@
 
-Bulge  (30)	       & BCES $(Y|X)$		    & $-22.25 \pm 0.20$ & $-5.88 \pm 3.06$ & $0.26$ & $-$ & $1.16$ \\
+Bulge (S0+Sp) (30)     & BCES $(Y|X)$		    & $-22.25 \pm 0.20$ & $-5.88 \pm 3.06$ & $0.26$ & $-$ & $1.16$ \\
 		       & mFITEXY $(Y|X)$	    & $-22.19 \pm 0.14$ & $-2.99 \pm 0.73$ & $0.26$ & $0.52^{+0.18}_{-0.10}$ & $0.75$ \\
@@
 
- Elliptical (30)	& BCES $(Y|X)$  	     & $8.80 \pm 0.53$ & $-18.16 \pm 53.99$ & $0.76$ & $-$ & $3.02$ \\
+ Elliptical (E) (30)	& BCES $(Y|X)$  	     & $8.80 \pm 0.53$ & $-18.16 \pm 53.99$ & $0.76$ & $-$ & $3.02$ \\
  			& mFITEXY $(Y|X)$	     & $8.90 \pm 0.10$ & $4.47 \pm 0.88$ & $0.76$ & $0.29^{+0.14}_{-0.10}$ & $0.56$ \\
@@
 
- Lenticular (11)	& BCES $(Y|X)$  	     & $7.75 \pm 0.58$ & $-11.51 \pm 31.78$ & $0.33$ & $-$ & $2.11$ \\
+ Lenticular (S0) (11)	& BCES $(Y|X)$  	     & $7.75 \pm 0.58$ & $-11.51 \pm 31.78$ & $0.33$ & $-$ & $2.11$ \\
  			& mFITEXY $(Y|X)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.26$ \\
@@
 
- Spiral (17)		& BCES $(Y|X)$  	     & $7.18 \pm 0.28$ & $6.78 \pm 6.62$ & $0.18$ & $-$ & $1.23$ \\
+ Spiral (Sp) (17)	& BCES $(Y|X)$  	     & $7.18 \pm 0.28$ & $6.78 \pm 6.62$ & $0.18$ & $-$ & $1.23$ \\
  			& mFITEXY $(Y|X)$	     & $7.24 \pm 0.13$ & $4.48 \pm 0.90$ & $0.18$ & $0.13^{+0.42}_{-0.13}$ & $0.52$ \\
@@
 
- Early-type (43)	& BCES $(Y|X)$  	     & $8.54 \pm 0.10$ & $4.07 \pm 0.87$ & $0.64$ & $-$ & $0.65$ \\
+ Early-type (E+S0) (43)	& BCES $(Y|X)$  	     & $8.54 \pm 0.10$ & $4.07 \pm 0.87$ & $0.64$ & $-$ & $0.65$ \\
  			& mFITEXY $(Y|X)$	     & $8.58 \pm 0.07$ & $3.32 \pm 0.34$ & $0.64$ & $0.24^{+0.10}_{-0.07}$ & $0.45$ \\

### 2015-11-05 papers/mbhn/mbhn.tex
thu

@@
 who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
-\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013} 
-and obtained two separate $L_{\rm sph} - n_{\rm sph}$ symmetrical linear regressions for elliptical galaxies and the bulges of disk galaxies 
+\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013review} 
+and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
 (in the B- and K-band, respectively). 
-At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013} were of the best quality available 
+At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013review} were of the best quality available 
 to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
-However, these datasets were not the output of a homogeneous analysis, 
-but the collection of the results from various past bulge/disk decomposition studies. 
+However, these datasets were not obtained from a homogeneous analysis, 
+but they were a collection of results taken from various past bulge/disk decomposition studies. 
 It is also worth mentioning that, 
@@
 {\bf the dust corrections are not precise today refs??, imagine at the time.....}  
-Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our top-quality dataset  
-derived from our state-of-the-art multicomponent galaxy decompositions, 
+Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our high-quality dataset  
+derived from state-of-the-art multicomponent galaxy decompositions, 
 that were performed in a consistent manner 
 and using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
-The values of the slope and intercept of the bisector linear regression for the lenticular galaxies 
+\cite{graham2013review} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
+However, using our dataset, 
+we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
+and found that the values of the slope and intercept for the lenticular galaxies 
 are not consistent within the errors with those for the spiral galaxies, 
@@
 Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
-elliptical and lenticular galaxies form together a single sequence, 
+elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
 whereas the combination of lenticular and spiral galaxies do not. 
 {\bf why?? dust? multicomponent? classification?}
-
-ell and s0 have same slope -> early seq \\
-different from late seq \\
 
@@
 Symbols are coded according to the galaxy morphological type (see legend).
+{\bf crosses outliers!} 
 The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
@@
 \subsection{$M_{\rm BH} - n_{\rm sph}$}
-in sav13 we had m-l from gs13 for core sersic and sersic \\
-however in paper II we say that this is not the case, there are red and blue seq \\
-therefore we look for red and blue seq here \\
-consistent with each other \\
+\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
+spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
+whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
+However, in \emph{Paper II} we found that the slopes of the correlations for S\'ersic and core-S\'ersic spheroids 
+are consistent with each other within their $1\sigma$ uncertainties, 
+which prevents us from considering them as two separate correlations. 
+On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations 
+($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
+and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
+Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
+and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
+we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
+Using the results from the modified FITEXY routine, 
+we report that 
+early-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{3.58 \pm 0.27}$, 
+while late-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{4.55 \pm 0.66}$. 
+The Bayesian estimator {\tt linmix\_err} returns consistent results: 
+a slope of $3.44 \pm 0.33$ for the early-type galaxies 
+and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
+In both cases, the values of the slope and intercept for the early- and late-type galaxies 
+are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
+considering the results of the modified FITEXY routine, 
+the slopes of the relations for early- and late-type galaxies 
+are only marginally consistent with each other within their $1\sigma$ uncertainties. 
+However, the slopes obtained with Bayesian estimator {\tt linmix\_err} 
+are fully consistent with each other within their $1\sigma$ uncertainties. }
+Our analysis shows that the early- and late-type galaxies do not define two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
+i.e.~we do not identify any significant substructure based on the galaxy morphological type. 
+The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
+\begin{equation}
+\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.18 \pm 0.06) + (3.39 \pm 0.15) \bigl(\log n_{\rm sph} - 0.51 \bigr) .
+\end{equation}
 
@@
 Symbols are coded according to the galaxy morphological type (see legend). 
+{\bf crosses outliers!} 
 The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
@@
 with the blue shaded area denoting its $1\sigma$ uncertainty. 
+The linear regressions for early- and late-type galaxies are consistent with each other within their $1\sigma$ uncertainties.  
 The inset panel shows the error bars associated to each data point,  
@@
 
-\section{Discussion}
+\section{Discussion and conclusions}
+
 intr scatter of correlation for all?\\
-data suggest that m-n more fundamental than l-n ? \\
+data suggest that m-n more fundamental than l-n or m-l woooooh? \\
 
@@
 
- Elliptical (E) (30)	& BCES $(Y|X)$  	     & $8.80 \pm 0.53$ & $-18.16 \pm 53.99$ & $0.76$ & $-$ & $3.02$ \\
- 			& mFITEXY $(Y|X)$	     & $8.90 \pm 0.10$ & $4.47 \pm 0.88$ & $0.76$ & $0.29^{+0.14}_{-0.10}$ & $0.56$ \\
- 			& {\tt linmix\_err} $(Y|X)$  & $8.84 \pm 0.12$ & $3.56 \pm 1.35$ & $0.76$ & $0.44 \pm 0.12$ & $0.59$ \\ [0.5em]
- 			& BCES $(X|Y)$  	     & $8.80 \pm 0.18$ & $8.00 \pm 2.55$ & $0.76$ & $-$ & $1.01$ \\
- 			& mFITEXY $(X|Y)$	     & $8.92 \pm 0.15$ & $6.85 \pm 1.75$ & $0.76$ & $0.36^{+0.20}_{-0.15}$ & $0.89$ \\
- 			& {\tt linmix\_err} $(X|Y)$  & $8.89 \pm 0.20$ & $6.96 \pm 2.49$ & $0.76$ & $0.63 \pm 0.30$ & $0.89$ \\ [0.5em]
- 			& BCES Bisector 	     & $8.80 \pm 0.11$ & $-0.03 \pm 0.10$ & $0.76$ & $-$ & $0.64$ \\
- 			& mFITEXY Bisector	     & $8.91 \pm 0.13$ & $5.42 \pm 0.85$ & $0.76$ & $-$ & $0.73$ \\
- 			& {\tt linmix\_err} Bisector & $8.85 \pm 0.16$ & $4.73 \pm 1.30$ & $0.76$ & $-$ & $0.67$ \\ [0.5em]
-
- Lenticular (S0) (11)	& BCES $(Y|X)$  	     & $7.75 \pm 0.58$ & $-11.51 \pm 31.78$ & $0.33$ & $-$ & $2.11$ \\
- 			& mFITEXY $(Y|X)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.26$ \\
- 			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
- 			& BCES $(X|Y)$  	     & $7.75 \pm 0.13$ & $3.54 \pm 0.99$ & $0.33$ & $-$ & $0.46$ \\
- 			& mFITEXY $(X|Y)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.49$ \\
- 			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
- 			& BCES Bisector 	     & $7.75 \pm 0.13$ & $-0.09 \pm 0.15$ & $0.33$ & $-$ & $0.48$ \\
- 			& mFITEXY Bisector	     & $7.65 \pm 0.12$ & $3.78 \pm 0.85$ & $0.33$ & $-$ & $0.49$ \\
- 			& {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]
+%Elliptical (E) (30)	& BCES $(Y|X)$  	     & $8.80 \pm 0.53$ & $-18.16 \pm 53.99$ & $0.76$ & $-$ & $3.02$ \\
+%			& mFITEXY $(Y|X)$	     & $8.90 \pm 0.10$ & $4.47 \pm 0.88$ & $0.76$ & $0.29^{+0.14}_{-0.10}$ & $0.56$ \\
+%			& {\tt linmix\_err} $(Y|X)$  & $8.84 \pm 0.12$ & $3.56 \pm 1.35$ & $0.76$ & $0.44 \pm 0.12$ & $0.59$ \\ [0.5em]
+%			& BCES $(X|Y)$  	     & $8.80 \pm 0.18$ & $8.00 \pm 2.55$ & $0.76$ & $-$ & $1.01$ \\
+%			& mFITEXY $(X|Y)$	     & $8.92 \pm 0.15$ & $6.85 \pm 1.75$ & $0.76$ & $0.36^{+0.20}_{-0.15}$ & $0.89$ \\
+%			& {\tt linmix\_err} $(X|Y)$  & $8.89 \pm 0.20$ & $6.96 \pm 2.49$ & $0.76$ & $0.63 \pm 0.30$ & $0.89$ \\ [0.5em]
+%			& BCES Bisector 	     & $8.80 \pm 0.11$ & $-0.03 \pm 0.10$ & $0.76$ & $-$ & $0.64$ \\
+%			& mFITEXY Bisector	     & $8.91 \pm 0.13$ & $5.42 \pm 0.85$ & $0.76$ & $-$ & $0.73$ \\
+%			& {\tt linmix\_err} Bisector & $8.85 \pm 0.16$ & $4.73 \pm 1.30$ & $0.76$ & $-$ & $0.67$ \\ [0.5em]
+%
+%Lenticular (S0) (11)	& BCES $(Y|X)$  	     & $7.75 \pm 0.58$ & $-11.51 \pm 31.78$ & $0.33$ & $-$ & $2.11$ \\
+%			& mFITEXY $(Y|X)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.26$ \\
+%			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
+%			& BCES $(X|Y)$  	     & $7.75 \pm 0.13$ & $3.54 \pm 0.99$ & $0.33$ & $-$ & $0.46$ \\
+%			& mFITEXY $(X|Y)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.49$ \\
+%			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
+%			& BCES Bisector 	     & $7.75 \pm 0.13$ & $-0.09 \pm 0.15$ & $0.33$ & $-$ & $0.48$ \\
+%			& mFITEXY Bisector	     & $7.65 \pm 0.12$ & $3.78 \pm 0.85$ & $0.33$ & $-$ & $0.49$ \\
+%			& {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]
+%
+ Early-type (E+S0) (43)	& BCES $(Y|X)$  	     & $8.54 \pm 0.10$ & $4.07 \pm 0.87$ & $0.64$ & $-$ & $0.65$ \\
+ 			& mFITEXY $(Y|X)$	     & $8.58 \pm 0.07$ & $3.32 \pm 0.34$ & $0.64$ & $0.24^{+0.10}_{-0.07}$ & $0.45$ \\
+ 			& {\tt linmix\_err} $(Y|X)$  & $8.57 \pm 0.08$ & $3.12 \pm 0.43$ & $0.64$ & $0.32 \pm 0.08$ & $0.53$ \\ [0.5em]
+ 			& BCES $(X|Y)$  	     & $8.54 \pm 0.09$ & $3.95 \pm 0.55$ & $0.64$ & $-$ & $0.63$ \\
+ 			& mFITEXY $(X|Y)$	     & $8.59 \pm 0.08$ & $3.88 \pm 0.43$ & $0.64$ & $0.26^{+0.11}_{-0.08}$ & $0.62$ \\
+ 			& {\tt linmix\_err} $(X|Y)$  & $8.59 \pm 0.09$ & $3.82 \pm 0.50$ & $0.64$ & $0.35 \pm 0.10$ & $0.61$ \\ [0.5em]
+ 			& BCES Bisector 	     & $8.54 \pm 0.10$ & $4.01 \pm 0.63$ & $0.64$ & $-$ & $0.64$ \\
+ 			& mFITEXY Bisector	     & $8.59 \pm 0.07$ & $3.58 \pm 0.27$ & $0.64$ & $-$ & $0.58$ \\
+ 			& {\tt linmix\_err} Bisector & $8.58 \pm 0.08$ & $3.44 \pm 0.33$ & $0.64$ & $-$ & $0.56$ \\ [0.5em]
 
@@
  			& {\tt linmix\_err} Bisector & $7.22 \pm 0.19$ & $4.12 \pm 1.07$ & $0.18$ & $-$ & $0.77$ \\ [0.5em]
-
- Early-type (E+S0) (43)	& BCES $(Y|X)$  	     & $8.54 \pm 0.10$ & $4.07 \pm 0.87$ & $0.64$ & $-$ & $0.65$ \\
- 			& mFITEXY $(Y|X)$	     & $8.58 \pm 0.07$ & $3.32 \pm 0.34$ & $0.64$ & $0.24^{+0.10}_{-0.07}$ & $0.45$ \\
- 			& {\tt linmix\_err} $(Y|X)$  & $8.57 \pm 0.08$ & $3.12 \pm 0.43$ & $0.64$ & $0.32 \pm 0.08$ & $0.53$ \\ [0.5em]
- 			& BCES $(X|Y)$  	     & $8.54 \pm 0.09$ & $3.95 \pm 0.55$ & $0.64$ & $-$ & $0.63$ \\
- 			& mFITEXY $(X|Y)$	     & $8.59 \pm 0.08$ & $3.88 \pm 0.43$ & $0.64$ & $0.26^{+0.11}_{-0.08}$ & $0.62$ \\
- 			& {\tt linmix\_err} $(X|Y)$  & $8.59 \pm 0.09$ & $3.82 \pm 0.50$ & $0.64$ & $0.35 \pm 0.10$ & $0.61$ \\ [0.5em]
- 			& BCES Bisector 	     & $8.54 \pm 0.10$ & $4.01 \pm 0.63$ & $0.64$ & $-$ & $0.64$ \\
- 			& mFITEXY Bisector	     & $8.59 \pm 0.07$ & $3.58 \pm 0.27$ & $0.64$ & $-$ & $0.58$ \\
- 			& {\tt linmix\_err} Bisector & $8.58 \pm 0.08$ & $3.44 \pm 0.33$ & $0.64$ & $-$ & $0.56$ \\ [0.5em]
 

### 2015-11-06 papers/mbhn/mbhn.tex
friday

@@
 \shorttitle{Mbh-n paper}
-\shortauthors{Savorgnan et al.}
+\shortauthors{Savorgnan \& Graham}
 
@@
 
-\title{Mbh-n paper}
+\title{Supermassive black holes and their host spheroids \\ III. Mbh-n paper}
 
@@
 We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
-with the same galaxy sample (Table \ref{tab:sample}) used in \emph{Paper II}, 
+with the same galaxy sample used in \emph{Paper II} (and presented here in Table \ref{tab:sample}), 
 i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
@@
 \section{Analysis and results}
+\label{sec:anal}
 As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
@@
 the S0 galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
-These two galaxies have therefore been excluded from the rest of the analysis. \\
+These two galaxies have therefore been excluded from the rest of the analysis. {\bf mergers are excluded?? 62??} \\
 {\bf fitexy does better job, we report that} \\
@@
 Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our high-quality dataset  
-derived from state-of-the-art multicomponent galaxy decompositions, 
+derived from state-of-the-art multicomponent decompositions, 
 that were performed in a consistent manner 
@@
 Symbols are coded according to the galaxy morphological type (see legend).
-{\bf crosses outliers!} 
+The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
+(see Section \ref{sec:anal}). 
 The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
@@
 whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
-However, in \emph{Paper II} we found that the slopes of the correlations for S\'ersic and core-S\'ersic spheroids 
+However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
 are consistent with each other within their $1\sigma$ uncertainties, 
-which prevents us from considering them as two separate correlations. 
+which prevents us from considering them as two separate sequences. 
 On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations 
@@
 Using the results from the modified FITEXY routine, 
-we report that 
+we find that 
 early-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{3.58 \pm 0.27}$, 
@@
 are only marginally consistent with each other within their $1\sigma$ uncertainties. 
-However, the slopes obtained with Bayesian estimator {\tt linmix\_err} 
-are fully consistent with each other within their $1\sigma$ uncertainties. }
-Our analysis shows that the early- and late-type galaxies do not define two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
-i.e.~we do not identify any significant substructure based on the galaxy morphological type. 
+However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
+are fully consistent with each other within their $1\sigma$ uncertainties. }.
+Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
+i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
 The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
 \begin{equation}
-\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.18 \pm 0.06) + (3.39 \pm 0.15) \bigl(\log n_{\rm sph} - 0.51 \bigr) .
+\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.18 \pm 0.06) + (3.39 \pm 0.15) \bigl(\log n_{\rm sph}^{\rm maj} - 0.51 \bigr) .
 \end{equation}
@@
 Symbols are coded according to the galaxy morphological type (see legend). 
-{\bf crosses outliers!} 
+The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
+(see Section \ref{sec:anal}). 
 The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
@@
 \section{Discussion and conclusions} 
+We have seen that the early- and late-type galaxies in the $M_{\rm BH} - n_{\rm sph}$ diagram can be fit with a single power-law, 
+whereas they follow two separate correlations in the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). 
+We now want to compare the amount of scatter among these two plots. 
+When considering all galaxies, irrespective of their morphological type, 
+the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation. 
+However, because of the different nature of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ correlations 
+(single and double power-law, respectively),  
+we are not comparing apples with apples. 
+One can obtain more informative results by considering early- and late-type galaxies separately. 
+For early-type galaxies only, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent\footnote{Looking 
+at the results obtained with the modified FITEXY routine, 
+the values of the intrisic scatter are only marginally consistent with each other, 
+but looking at the results obtained with the Bayesian estimator {\tt linmix\_err}, 
+the values of the intrisic scatter are fully consistent with each other. } with  
+that of the $M_{\rm BH} - L_{\rm sph}$ relation (within their $1\sigma$ uncertainties). 
+For late-type galaxies only, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent with 
+that of the $M_{\rm BH} - L_{\rm sph}$ relation, 
+{\bf except fitexy xy}.
 
-intr scatter of correlation for all?\\
 data suggest that m-n more fundamental than l-n or m-l woooooh? \\
@@
 \tableline
-{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph}^{\rm maj} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
 \tableline 
 \\
- & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph} - \langle \log n_{\rm sph,maj} \rangle \bigr)$} \\ [0.5em]
+ & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph}^{\rm maj} - \langle \log n_{\rm sph}^{\rm maj} \rangle \bigr)$} \\ [0.5em]
 All (62)               & BCES $(Y|X)$               & $-23.88 \pm 0.15$ & $-7.17 \pm 0.80$ & $0.51$ & $-$ & $1.18$ \\
@@
 \tableline
-{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph}^{\rm maj} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
 \tableline 
@@
 \tableline
-{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph}^{\rm maj} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
 \tableline 
 \\
- & \multicolumn{6}{l}{$\log \bigl( M_{\rm BH}/{\rm [M_\odot]} \bigr) = \alpha + \beta \bigl(\log n_{\rm sph} - \langle \log n_{\rm sph} \rangle \bigr)$} \\ [0.5em]
+ & \multicolumn{6}{l}{$\log \bigl( M_{\rm BH}/{\rm [M_\odot]} \bigr) = \alpha + \beta \bigl(\log n_{\rm sph}^{\rm maj} - \langle \log n_{\rm sph}^{\rm maj} \rangle \bigr)$} \\ [0.5em]
  All (62)		& BCES $(Y|X)$  	     & $8.14 \pm 0.08$ & $3.56 \pm 0.38$ & $0.51$ & $-$ & $0.60$ \\
@@
 
+  \begin{table*}
+  \centering
+  \caption{Intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ relations.}
+  \begin{tabular}{llccr}
+  \tableline
+  \tableline
+  {\bf Subsample} & {\bf Regression} & $\boldsymbol \epsilon$ {\bf for} $\boldsymbol M_{\rm BH} - n_{\rm sph}$ & 
+  $\boldsymbol \epsilon$ {\bf for} $\boldsymbol M_{\rm BH} - L_{\rm sph}$ & \\ 
+  \tableline 
+  \\
+  All		  & mFITEXY $(Y|X)$	      & $0.22^{+0.10}_{-0.07}$ & $0.49^{+0.06}_{-0.05}$ & non consist. \\
+ 		  & {\tt linmix\_err} $(Y|X)$ & $0.29 \pm 0.07$ & $0.51 \pm 0.06$               & non consist. \\
+ 		  & mFITEXY $(X|Y)$	      & $0.23^{+0.10}_{-0.07}$ & $0.58^{+0.07}_{-0.06}$ & non consist. \\
+ 		  & {\tt linmix\_err} $(X|Y)$ & $0.30 \pm 0.07$ & $0.60 \pm 0.09$               & non consist. \\ [0.5em]
+
+  Early-type	  & mFITEXY $(Y|X)$	      & $0.24^{+0.10}_{-0.07}$ & $0.40^{+0.06}_{-0.05}$ & marg. consist. \\
+ 		  & {\tt linmix\_err} $(Y|X)$ & $0.32 \pm 0.08$ & $0.41 \pm 0.06$               & consist. \\
+ 		  & mFITEXY $(X|Y)$	      & $0.26^{+0.11}_{-0.08}$ & $0.49^{+0.08}_{-0.06}$ & marg. consist. \\
+ 		  & {\tt linmix\_err} $(X|Y)$ & $0.35 \pm 0.10$ & $0.51 \pm 0.10$               & consist. \\ [0.5em]
+
+  Late-type	  & mFITEXY $(Y|X)$	      & $0.13^{+0.42}_{-0.13}$ & $0.55^{+0.15}_{-0.10}$ & consist. \\
+ 		  & {\tt linmix\_err} $(Y|X)$ & $0.39 \pm 0.19$ & $0.63 \pm 0.16$               & consist. \\
+ 		  & mFITEXY $(X|Y)$	      & $0.13^{+0.43}_{-0.13}$ & $1.09^{+0.41}_{-0.24}$ & non consist.\\
+ 		  & {\tt linmix\_err} $(X|Y)$ & $0.45 \pm 0.31$ & $1.31 \pm 0.97$               & consist. \\ [0.5em]
+
+  \tableline 
+  \tableline
+  \end{tabular}
+  \label{tab:intsc} 
+  \tablecomments{  }
+  \end{table*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-11-11 papers/ellicular/MNRAS/ellicular.tex
wed

--- 2015-11-04 papers/ellicular/sabotage/ellicular.tex
@@
 \citep{liller1966,stromstrom1978,michard1984,djorgovski1985,jedrzejewski1987,BenderMoellenhoff1987,
-carter1987,capaccioli1987,capaccioli1988,bender1988,bender1990,
-nieto1988,rixwhite1990,vandenbergh1990,scorzabender1990,scorzabender1995,
-simienmichard1990}. 
+carter1987,capaccioli1987,capaccioli1988}. 
 It is well known that 
@@
 (i.e.~somewhat edge-on), it can be missed.  
+The same is true when searching for pointy isophotes that are shaped by the combination of the spheroid and a near edge-on disc 
+(e.g.~\citealt{carter1978,carter1987,jedrzejewski1987,ebneter1987,BenderMoellenhoff1987,bender1988,bijaoui1989}). \\
 Today, most early-type galaxies are classified as ``fast rotators'' 
@@
 \cite{arnold2014} revealed that some of the central fast rotators continue to be fast rotating at large radii, 
-whereas other central fast rotators become slow rotating in their outer regions.
-A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
-is a signature of a large-scale disc, 
-while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 
-indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 
+whereas other central fast rotators become slow rotating in their outer regions\footnote{As pointed out by \cite{cappellari2011}, 
+while all of the disky ellipticals from \cite{Bender1994} are fast rotators, 
+the complement is not true because weak discs only impact the isophotal shape if the discs have orientations close to edge-on, 
+whereas their rotational signature can still be detected when they have a near face-on orientation.  
+Of course if a disc is face-on, then the galaxy will not be classified as a fast rotator. }.
+%A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
+%is a signature of a large-scale disc, 
+%while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 
+%indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 
 Unfortunately, such extended kinematic maps are not yet available for large numbers of galaxies in the local Universe. 
 Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of a stellar disc in an early-type galaxy. \\
+In general, stellar discs are intrinsically flat and close to circular (e.g.~\citealt{Andersen2001,AndersenBershady2002}); 
+their apparent ellipticity, dictated by their inclination to our line of sight, is fixed. 
+Spheroids are often rounder than the observed projection on the sky of their associated discs, 
+thus their average ellipticity is often lower than that of their disc. 
+An ellipticity profile that increases with radius can be ascribed to an inclined disc that becomes progressively more important at large radii, 
+whereas a radial decrease of ellipticity signifies the opposite case. 
+This approach can be taken to the next level by inspecting the isophotes for discy structures 
+(e.g.~\citealt{carter1978,carter1987,capaccioli1987,jedrzejewski1987,BenderMoellenhoff1987}) 
+and checking the velocity line profiles for asymmetry 
+(e.g.~\citealt{franxillingworth1988ic1459,bender1990,rixwhite1992,scorzabender1995}, and references therein; \citealt{scorza1998}). \\
 Building on the investigations in works such as \cite{liller1966}, \cite{Jedrzejewski1987INPROCEEDINGS} and \cite{rixwhite1990}, 
@@
 and also the specific angular momentum profiles. \\
-In general, stellar discs are intrinsically flat and close to circular (e.g.~\citealt{Andersen2001,AndersenBershady2002}); 
-their apparent ellipticity, dictated by their inclination to our line of sight, is fixed. 
-Spheroids are often rounder than the observed projection on the sky of their associated discs, 
-thus their average ellipticity is often lower than that of their disc. 
-An ellipticity profile that increases with radius can be ascribed to an inclined disc that becomes progressively more important at large radii, 
-whereas a radial decrease of ellipticity signifies the opposite case. 
-This approach can be taken to the next level by inspecting the isophotes for discy structures 
-(e.g.~\citealt{carter1978,carter1987,capaccioli1987,jedrzejewski1987,BenderMoellenhoff1987}) 
-and checking the velocity line profiles for asymmetry 
-(e.g.~\citealt{franxillingworth1988ic1459,bender1990,rixwhite1992,scorzabender1995}, and references therein; \citealt{scorza1998}). \\
 While some recent studies have correctly distinguished between large- and intermediate-scale discs, 
@@
 GS is grateful to Matteo Fossati, Luca Cortese and Giuseppe Gavazzi for useful comments and discussion. 
-We are grateful to our anynimous referee for their very careful review of our paper, 
+The publication of this paper would not have been possible without the invaluable support of 
+Chris Blake and Duncan Forbes. 
+We warmly thank our anynimous referee for their very careful review of our paper, 
 and for the comments, corrections and suggestions that ensued. 
@@
 
-\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
+%\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
+\bibliography{SMBHbibliography}
 

### 2015-11-11 papers/ellicular/ellicular.tex
wed

@@
 {\bf The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
-%with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
 Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
@@
 correctly reproduce both the photometric and kinematic properties of early-type galaxies 
-%intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
 with intermediate-scale discs. 
@@
 {\bf The awareness that \emph{many} early-type galaxies contain previously over-looked stellar discs dates back half a century 
-\citep{liller1966,michard1984,djorgovski1985,jedrzejewski1987,BenderMoellenhoff1987,
-carter1987,capaccioli1987,capaccioli1988,stromstrom1978,bender1988,bender1990,
-nieto1988,rixwhite1990,vandenbergh1990,scorzabender1990,scorzabender1995,
-simienmichard1990}. 
-Not surprisingly, it is well known that 
+\citep{liller1966,stromstrom1978,michard1984,djorgovski1985,jedrzejewski1987,BenderMoellenhoff1987,
+carter1987,capaccioli1987,capaccioli1988}. 
+It is well known that 
 the identification of a stellar disc in an early-type galaxy, particularly when based on the galaxy's photometric properties, 
@@
 whose discs do not prevail at large radii, 
-and referred to them as ``disk-ellipticals'' (or ``disky ellipticals'', \citealt{simienmichard1990}) 
-thereby more closely associating them with elliptical galaxies than lenticular galaxies.   
+and referred to them as ``disk-ellipticals'' (or ``disky ellipticals'', \citealt{simienmichard1990}).   
 However, as noted by \cite{nieto1988}, unless the orientation of the disc is favourable 
@@
 The same is true when searching for pointy isophotes that are shaped by the combination of the spheroid and a near edge-on disc 
-(e.g.~\citealt{carter1978,carter1987,jedrzejewski1987,BenderMoellenhoff1987}). 
-Today, most early-type galaxies are classified as ``fast rotators\footnote{The term 
-``fast rotator'' is of course not new for describing certain early-type galaxies (e.g.~\citealt{bertinstiavelli1984,lakedressler1986}).}'' 
+(e.g.~\citealt{carter1978,carter1987,jedrzejewski1987,ebneter1987,BenderMoellenhoff1987,bender1988,bijaoui1989}). \\
+Today, most early-type galaxies are classified as ``fast rotators'' 
 \citep{atlas3dIII,scott2014}, 
@@
 and also the specific angular momentum profiles. \\
-In general, stellar discs are intrinsically flat and close to circular \citep{Andersen2001,AndersenBershady2002}; 
-their apparent ellipticity, dictated by their inclination to our line of sight, is fixed. 
-Spheroids are often rounder than the observed projection on the sky of their associated discs, 
-thus their average ellipticity is often lower than that of their disc. 
-An ellipticity profile that increases with radius can be ascribed to an inclined disc that becomes progressively more important at large radii, 
-whereas a radial decrease of ellipticity signifies the opposite case. 
-This approach can be taken to the next level by inspecting the isophotes for discy structures 
-(e.g.~\citealt{carter1978,carter1987,capaccioli1987,jedrzejewski1987,BenderMoellenhoff1987}) 
-and checking the velocity line profiles for asymmetry 
-(e.g.~\citealt{franxillingworth1988ic1459,bender1990,rixwhite1992,scorzabender1995}, and references therein; \citealt{scorza1998}). \\
 While some recent studies have correctly distinguished between large- and intermediate-scale discs, 
@@
 
-\subsection{ES galaxies in the Hubble grid}
-{\bf The existence of intermediate-scale discs has led to the suggestion of a likely continuum of disc sizes in early-type galaxies 
-\citep{simiendevaucouleurs1986,capaccioli1988,bender1989,simienmichard1990,scorza1993,scorzavandenBosch1998} 
-as opposed to a dichotomy of say nuclear discs versus large-scale discs.  
-The presence of these intermediate-scale discs blurs the distinction between elliptical (E) and lenticular (S0) galaxies, 
-or slow-rotators (SR) versus fast-rotators (FR), 
-see \citeauthor{cappellari2011kmdr} (\citeyear{cappellari2011kmdr}, their Figure 1 and 2).   
-There is a need for more than two bins (i.e.~nuclear vs.~large-scale disc, E vs.~S0, SR vs.~FR), 
-and a need for a continuum in the (Hubble-Jeans)-like classification 
-schemes\footnote{As noted by \cite{vandenbergh1997} and \cite{sandage2005}, 
-it was Sir James \cite{jeans1928} who introduced the (tuning fork)-shaped diagram that encapsulated \citeauthor{Hubble1926}'s (\citeyear{Hubble1926}) 
-elliptical-spiral sequence -- itself motivated by the earlier work of \cite{Jeans1919}.}.     \\
-It has been argued that the classification scheme for ``elliptical'' galaxies should not be 
-their apparent axis ratio as seen on the plane of the sky (originally E0--E7, see \citealt{hubble1936,sandage1961}, 
-then E0--E4, see \citealt{liller1966} and also \citealt{gorbachev1970}), 
-because this depends on the viewing angle rather than being intrinsic to the galaxy.  
-Obviously when dealing with intermediate-scale discs, 
-the boxy/discy shape of the isophotes is also a function of both radius and disc inclination, 
-making single isophotal shape parameters problematic and particularly inappropriate for the ES class.  
-Section 4 of \cite{kormendybender1996} points out additional complications in regard to this.  
-Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, 
-with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies (e.g.~\citealt{capaccioli1988}, and references therein).   
-This spheroid-to-total flux (or better mass) ratio is widely recognised as an important quantity, 
-and its broad range observed in the lenticular galaxies led \cite{cappellari2011kmdr} to present the ``Hubble comb''.   
-Building on \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976}) diagram in which both late-type galaxies (i.e.~spiral galaxies) 
-and early-type galaxies form separate prongs of an expanded Hubble-Jeans tuning fork, 
-with an additional prong for disc galaxies hosting anaemic spiral patterns, 
-\citeauthor{cappellari2011kmdr} (\citeyear{cappellari2011kmdr}, see also \citealt{kormendybender2012}) 
-presented a scheme in which the morphological type (a, b, c, etc.) 
-changed if the spheroid-to-total ratio changed.  
-However the primary criteria used to assign the spiral galaxy type over the last half century \citep{sandage1961} 
-has been the nature of the spiral arms -- the extent to which they are unwound, pitch angle, 
-and the degree of resolution -- rather than the spheroid-to-total ratio.   
-Indeed, in the Hubble Atlas of Galaxies, \cite{sandage1961} notes that Sa type galaxies exist with both small and large bulges 
-(see also \citealt{VorontsovvelYaminovArkhipova1962} and \citealt{Vorontsovvelyaminovnoskova1973}). \\
-The grid seen in Figure \ref{fig:grid} and discussed in \cite{graham2014review} 
-was used by \citeauthor{freeman1970} (\citeyear{freeman1970}, his Figure 9), 
-\cite{boroson1981}, \cite{kent1985}, \cite{kodaira1986}, \cite{simiendevaucouleurs1986} and others, 
-and allows for the varying spheroid-to-total ratio among each galaxy type.   
-Rather than using the extended classification scheme for early-type galaxies (E -- E$^+$ -- L$^-$ -- L$^o$ -- L$^+$ -- S0, 
-corresponding to the numerical T-type ranging from -5 to 0, e.g.~\citealt{devaucouleurs1964,heidmann1972}), 
-we have simply grouped them all together.  
-While, collectively, spiral galaxies typically display a range of spheroid-to-total flux 
-ratios from $0$ to $\approx 3/4$ (e.g.~\citealt{grahamworley2008}, and references therein), 
-lenticular galaxies commonly display a range from $\approx 3/4$ to $\approx 0.1$ \citep{laurikainen2010}, and the ES class have larger ratios.  
-The purpose here is not to provide a complete classification scheme, 
-but to simply show where the early-type galaxies with intermediate-scale discs (ES) reside relative to the other 
-Hubble galaxy types in this familiar diagram which has tended not to include the elliptical galaxies to date. }
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{Hubblegrid.pdf}
-\caption{The Hubble grid showing the location of the ES galaxies, intermediate between
-elliptical (E) and lenticular (S0) galaxies, relative to the spiral galaxies.  }
-\label{fig:grid}
-\end{center}
-\end{figure}
-
 \section{Summary and conclusions}

### 2015-11-11 papers/mbhn/mbhn.tex
wed

@@
 \shorttitle{Mbh-n paper}
-\shortauthors{Savorgnan \& Graham}
+\shortauthors{Savorgnan}
 
@@
 
-\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
+\author{G. A. D. Savorgnan\altaffilmark{1}}
 \affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
@@
 \begin{abstract}
-blah blah
+The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution of stellar spheroidal and disk components, 
+with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
+The S\'ersic index of a galaxy's spheroidal component $n_{\rm sph}$ has been shown to tightly correlate 
+with the mass of the central supermassive black hole $M_{\rm BH}$ by some studies. 
+The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known galaxy scaling relations: 
+the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$ relations, 
+where $L_{\rm sph}$ indicates the galaxy's spheroid luminosity. 
+However, it is widely recognized that obtaining an accurate estimate of the spheroid S\'ersic index is a challenging task, 
+and -- not surprisingly -- other studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
+With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
+and other correlations between the black hole mass and various galaxy properties, 
+we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
+decomposition of 66 galaxies, with directly measured black hole masses, 
+that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
+This sample is the largest to date used to investigate black hole mass scaling relations. 
+In this paper, the third of its series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
+While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
+in the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
+they reunite in a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
+with relatively small intrinsic scatter ($\epsilon_{(Y|X)} \simeq 0.25 \rm~dex$). 
+{\bf to be finished...}
 \end{abstract}
@@
 The S\'ersic model parametrizes the intensity of light $I$ as a function of the projected galactic radius $R$ such that
-\begin{equation}
+\begin{equation*}
 I(R; I_{\rm e},R_{\rm e},n) = I_{\rm e} \exp \biggl \{ -b_{\rm n} \biggl [ \Bigl (\frac{R}{R_{\rm e}} \bigr )^{1/n} -1 \biggr ] \biggr \}, 
-\end{equation}
+\end{equation*}
 where $I_{\rm e}$ indicates the intensity at the effective radius $R_{\rm e}$ that encloses half of the total light from the model, 
@@
 an $M_{\rm BH} - n_{\rm sph}$ relation must exist. 
-After \cite{graham2001} showed that the black hole mass is tightly linked to the stellar light concentration of spheroids 
+After \cite{graham2001bulges} showed that the black hole mass is tightly linked to the stellar light concentration of spheroids 
 (measured through a parameter different from, but closely related to the S\'ersic index), 
@@
 the S0 galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
-These two galaxies have therefore been excluded from the rest of the analysis. {\bf mergers are excluded?? 62??} \\
-{\bf fitexy does better job, we report that} \\
+These two galaxies have therefore been excluded from the rest of the analysis.
 
@@
 although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
-{\bf the dust corrections are not precise today refs??, imagine at the time.....}  
+{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
 Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our high-quality dataset  
@@
 The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
-\begin{equation}
-\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.18 \pm 0.06) + (3.39 \pm 0.15) \bigl(\log n_{\rm sph}^{\rm maj} - 0.51 \bigr) .
-\end{equation}
+\begin{equation*}
+\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph}^{\rm maj} - 0.50 \bigr) . 
+\end{equation*}
+\\
+
+We have seen that the early- and late-type galaxies in the $M_{\rm BH} - n_{\rm sph}$ diagram can be fit with a single power-law, 
+whereas they follow two separate correlations in the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). 
+We now want to compare the amount of scatter among these two plots. 
+In Table \ref{tab:intsc} we summarize the values of the intrinsic scatter 
+in the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams 
+for all, early- and late-type galaxies, 
+obtained with the modified FITEXY routine and the Bayesian estimator {\tt linmix\_err}. 
+When considering all galaxies, irrespective of their morphological type, 
+the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation. 
+However, this is obviously not a fair comparison, 
+because of the different nature of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ correlations 
+(single and double power-law, respectively). 
+One can obtain more informative results by considering early- and late-type galaxies separately. 
+For the early-type galaxies, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent\footnote{Looking 
+at the results obtained with the modified FITEXY routine, 
+the values of the intrisic scatter are only marginally consistent with each other, 
+but looking at the results obtained with the Bayesian estimator {\tt linmix\_err}, 
+the values of the intrisic scatter are fully consistent with each other. } 
+with that of the $M_{\rm BH} - L_{\rm sph}$ relation (within their $1\sigma$ uncertainties). 
+For the late-type galaxies, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent with 
+that of the $M_{\rm BH} - L_{\rm sph}$ relation, 
+except for the inverse ($X|Y$) regression obtained with the modified FITEXY routine. \\
+In passing, we note that the values of the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation 
+are systematically smaller -- although consistent within the errors -- 
+than the corresponding values of the intrinsic scatter of the $M_{\rm BH} - L_{\rm sph}$ relation. 
+In addition, the values of the intrinsic scatter returned by the modified FITEXY routine are systematically smaller than 
+those output by the Bayesian estimator {\tt linmix\_err}.
 
@@
 
-\section{Discussion and conclusions} 
-We have seen that the early- and late-type galaxies in the $M_{\rm BH} - n_{\rm sph}$ diagram can be fit with a single power-law, 
-whereas they follow two separate correlations in the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). 
-We now want to compare the amount of scatter among these two plots. 
-When considering all galaxies, irrespective of their morphological type, 
-the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation. 
-However, because of the different nature of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ correlations 
-(single and double power-law, respectively),  
-we are not comparing apples with apples. 
-One can obtain more informative results by considering early- and late-type galaxies separately. 
-For early-type galaxies only, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent\footnote{Looking 
-at the results obtained with the modified FITEXY routine, 
-the values of the intrisic scatter are only marginally consistent with each other, 
-but looking at the results obtained with the Bayesian estimator {\tt linmix\_err}, 
-the values of the intrisic scatter are fully consistent with each other. } with  
-that of the $M_{\rm BH} - L_{\rm sph}$ relation (within their $1\sigma$ uncertainties). 
-For late-type galaxies only, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent with 
-that of the $M_{\rm BH} - L_{\rm sph}$ relation, 
-{\bf except fitexy xy}.
-
-data suggest that m-n more fundamental than l-n or m-l woooooh? \\
+\section{Conclusions}
 
@@
  & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph}^{\rm maj} - \langle \log n_{\rm sph}^{\rm maj} \rangle \bigr)$} \\ [0.5em]
-All (62)               & BCES $(Y|X)$               & $-23.88 \pm 0.15$ & $-7.17 \pm 0.80$ & $0.51$ & $-$ & $1.18$ \\
-                       & mFITEXY $(Y|X)$            & $-23.95 \pm 0.13$ & $-6.70 \pm 0.45$ & $0.51$ & $0.56^{+0.15}_{-0.10}$ & $0.98$ \\
-                       & {\tt linmix\_err} $(Y|X)$  & $-23.92 \pm 0.15$ & $-6.40 \pm 0.57$ & $0.51$ & $0.74 \pm 0.13$ & $1.07$ \\ [0.5em]
-                       & BCES $(X|Y)$               & $-23.88 \pm 0.14$ & $-6.70 \pm 0.51$ & $0.51$ & $-$ & $1.11$ \\
-                       & mFITEXY $(X|Y)$            & $-23.94 \pm 0.14$ & $-7.50 \pm 0.52$ & $0.51$ & $0.59^{+0.17}_{-0.11}$ & $1.23$ \\
-                       & {\tt linmix\_err} $(X|Y)$  & $-23.94 \pm 0.16$ & $-7.51 \pm 0.62$ & $0.51$ & $0.81 \pm 0.16$ & $1.23$ \\ [0.5em]
-                       & BCES Bisector              & $-23.88 \pm 0.14$ & $-6.93 \pm 0.60$ & $0.51$ & $-$ & $1.14$ \\
-                       & mFITEXY Bisector           & $-23.94 \pm 0.13$ & $-7.08 \pm 0.34$ & $0.51$ & $-$ & $1.16$ \\
-                       & {\tt linmix\_err} Bisector & $-23.93 \pm 0.16$ & $-6.91 \pm 0.42$ & $0.51$ & $-$ & $1.14$ \\ [0.5em]
+All (64)               & BCES $(Y|X)$               & $-23.89 \pm 0.15$ & $-6.90 \pm 0.74$ & $0.50$ & $-$ & $1.22$ \\
+                       & mFITEXY $(Y|X)$            & $-23.91 \pm 0.13$ & $-6.63 \pm 0.45$ & $0.50$ & $0.59^{+0.16}_{-0.11}$ & $1.01$ \\
+                       & {\tt linmix\_err} $(Y|X)$  & $-23.89 \pm 0.14$ & $-6.34 \pm 0.57$ & $0.50$ & $0.74 \pm 0.13$ & $1.14$ \\ [0.5em]
+                       & BCES $(X|Y)$               & $-23.89 \pm 0.15$ & $-6.75 \pm 0.52$ & $0.50$ & $-$ & $1.20$ \\
+                       & mFITEXY $(X|Y)$            & $-23.89 \pm 0.14$ & $-7.49 \pm 0.53$ & $0.50$ & $0.62^{+0.18}_{-0.12}$ & $1.32$ \\
+                       & {\tt linmix\_err} $(X|Y)$  & $-23.90 \pm 0.16$ & $-7.49 \pm 0.62$ & $0.50$ & $0.80 \pm 0.16$ & $1.32$ \\ [0.5em]
+                       & BCES Bisector              & $-23.89 \pm 0.15$ & $-6.83 \pm 0.58$ & $0.50$ & $-$ & $1.21$ \\
+                       & mFITEXY Bisector           & $-23.90 \pm 0.13$ & $-7.04 \pm 0.35$ & $0.50$ & $-$ & $1.24$ \\
+                       & {\tt linmix\_err} Bisector & $-23.89 \pm 0.15$ & $-6.87 \pm 0.42$ & $0.50$ & $-$ & $1.21$ \\ [0.5em]
 
@@
 In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
-all - mergers - outliers
+The lenticular galaxies NGC 0524 and NGC 3998 were excluded from the linear regression analysis (see Section \ref{sec:anal}). 
 Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2). }
@@
  & \multicolumn{6}{l}{$\log \bigl( M_{\rm BH}/{\rm [M_\odot]} \bigr) = \alpha + \beta \bigl(\log n_{\rm sph}^{\rm maj} - \langle \log n_{\rm sph}^{\rm maj} \rangle \bigr)$} \\ [0.5em]
- All (62)		& BCES $(Y|X)$  	     & $8.14 \pm 0.08$ & $3.56 \pm 0.38$ & $0.51$ & $-$ & $0.60$ \\
- 			& mFITEXY $(Y|X)$	     & $8.18 \pm 0.06$ & $3.27 \pm 0.21$ & $0.51$ & $0.22^{+0.10}_{-0.07}$ & $0.45$ \\
- 			& {\tt linmix\_err} $(Y|X)$  & $8.17 \pm 0.06$ & $3.17 \pm 0.24$ & $0.51$ & $0.29 \pm 0.07$ & $0.56$ \\ [0.5em]
- 			& BCES $(X|Y)$  	     & $8.14 \pm 0.08$ & $3.56 \pm 0.25$ & $0.51$ & $-$ & $0.60$ \\
- 			& mFITEXY $(X|Y)$	     & $8.18 \pm 0.06$ & $3.51 \pm 0.23$ & $0.51$ & $0.23^{+0.10}_{-0.07}$ & $0.60$ \\
- 			& {\tt linmix\_err} $(X|Y)$  & $8.17 \pm 0.07$ & $3.49 \pm 0.26$ & $0.51$ & $0.30 \pm 0.07$ & $0.60$ \\ [0.5em]
- 			& BCES Bisector 	     & $8.14 \pm 0.08$ & $3.56 \pm 0.29$ & $0.51$ & $-$ & $0.60$ \\
- 			& mFITEXY Bisector	     & $8.18 \pm 0.06$ & $3.39 \pm 0.15$ & $0.51$ & $-$ & $0.58$ \\
- 			& {\tt linmix\_err} Bisector & $8.17 \pm 0.07$ & $3.33 \pm 0.18$ & $0.51$ & $-$ & $0.57$ \\ [0.5em]
+ All (64)		& BCES $(Y|X)$  	     & $8.14 \pm 0.07$ & $3.49 \pm 0.36$ & $0.50$ & $-$ & $0.61$ \\
+ 			& mFITEXY $(Y|X)$	     & $8.15 \pm 0.06$ & $3.26 \pm 0.21$ & $0.50$ & $0.22^{+0.10}_{-0.07}$ & $0.46$ \\
+ 			& {\tt linmix\_err} $(Y|X)$  & $8.15 \pm 0.06$ & $3.17 \pm 0.24$ & $0.50$ & $0.28 \pm 0.07$ & $0.56$ \\ [0.5em]
+ 			& BCES $(X|Y)$  	     & $8.14 \pm 0.08$ & $3.52 \pm 0.25$ & $0.50$ & $-$ & $0.61$ \\
+ 			& mFITEXY $(X|Y)$	     & $8.15 \pm 0.06$ & $3.49 \pm 0.23$ & $0.50$ & $0.23^{+0.10}_{-0.07}$ & $0.61$ \\
+ 			& {\tt linmix\_err} $(X|Y)$  & $8.15 \pm 0.07$ & $3.49 \pm 0.26$ & $0.50$ & $0.29 \pm 0.08$ & $0.61$ \\ [0.5em]
+ 			& BCES Bisector 	     & $8.14 \pm 0.07$ & $3.51 \pm 0.28$ & $0.50$ & $-$ & $0.61$ \\
+ 			& mFITEXY Bisector	     & $8.15 \pm 0.06$ & $3.37 \pm 0.15$ & $0.50$ & $-$ & $0.59$ \\
+ 			& {\tt linmix\_err} Bisector & $8.15 \pm 0.07$ & $3.32 \pm 0.18$ & $0.50$ & $-$ & $0.58$ \\ [0.5em]
 
@@
 In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
-all - mergers - outliers
+The lenticular galaxies NGC 0524 and NGC 3998 were excluded from the linear regression analysis (see Section \ref{sec:anal}). 
 Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2).  }
@@
   \caption{Intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ relations.}
-  \begin{tabular}{llccr}
+  \begin{tabular}{llcc}
   \tableline
@@
   {\bf Subsample} & {\bf Regression} & $\boldsymbol \epsilon$ {\bf for} $\boldsymbol M_{\rm BH} - n_{\rm sph}$ & 
-  $\boldsymbol \epsilon$ {\bf for} $\boldsymbol M_{\rm BH} - L_{\rm sph}$ & \\ 
+  $\boldsymbol \epsilon$ {\bf for} $\boldsymbol M_{\rm BH} - L_{\rm sph}$ \\ 
   \tableline 
   \\
-  All		  & mFITEXY $(Y|X)$	      & $0.22^{+0.10}_{-0.07}$ & $0.49^{+0.06}_{-0.05}$ & non consist. \\
- 		  & {\tt linmix\_err} $(Y|X)$ & $0.29 \pm 0.07$ & $0.51 \pm 0.06$               & non consist. \\
- 		  & mFITEXY $(X|Y)$	      & $0.23^{+0.10}_{-0.07}$ & $0.58^{+0.07}_{-0.06}$ & non consist. \\
- 		  & {\tt linmix\_err} $(X|Y)$ & $0.30 \pm 0.07$ & $0.60 \pm 0.09$               & non consist. \\ [0.5em]
-
-  Early-type	  & mFITEXY $(Y|X)$	      & $0.24^{+0.10}_{-0.07}$ & $0.40^{+0.06}_{-0.05}$ & marg. consist. \\
- 		  & {\tt linmix\_err} $(Y|X)$ & $0.32 \pm 0.08$ & $0.41 \pm 0.06$               & consist. \\
- 		  & mFITEXY $(X|Y)$	      & $0.26^{+0.11}_{-0.08}$ & $0.49^{+0.08}_{-0.06}$ & marg. consist. \\
- 		  & {\tt linmix\_err} $(X|Y)$ & $0.35 \pm 0.10$ & $0.51 \pm 0.10$               & consist. \\ [0.5em]
-
-  Late-type	  & mFITEXY $(Y|X)$	      & $0.13^{+0.42}_{-0.13}$ & $0.55^{+0.15}_{-0.10}$ & consist. \\
- 		  & {\tt linmix\_err} $(Y|X)$ & $0.39 \pm 0.19$ & $0.63 \pm 0.16$               & consist. \\
- 		  & mFITEXY $(X|Y)$	      & $0.13^{+0.43}_{-0.13}$ & $1.09^{+0.41}_{-0.24}$ & non consist.\\
- 		  & {\tt linmix\_err} $(X|Y)$ & $0.45 \pm 0.31$ & $1.31 \pm 0.97$               & consist. \\ [0.5em]
+  All		  & mFITEXY $(Y|X)$	      & $0.22^{+0.10}_{-0.07}$ & $0.49^{+0.06}_{-0.05}$  \\	     %& non consist.  
+ 		  & {\tt linmix\_err} $(Y|X)$ & $0.29 \pm 0.07$ & $0.51 \pm 0.06$                \\	     %& non consist.  
+ 		  & mFITEXY $(X|Y)$	      & $0.23^{+0.10}_{-0.07}$ & $0.58^{+0.07}_{-0.06}$  \\	     %& non consist.  
+ 		  & {\tt linmix\_err} $(X|Y)$ & $0.30 \pm 0.07$ & $0.60 \pm 0.09$                \\ [0.5em]  %& non consist.  
+ 													     %
+  Early-type	  & mFITEXY $(Y|X)$	      & $0.24^{+0.10}_{-0.07}$ & $0.40^{+0.06}_{-0.05}$  \\	     %& marg. consist.
+ 		  & {\tt linmix\_err} $(Y|X)$ & $0.32 \pm 0.08$ & $0.41 \pm 0.06$                \\	     %& consist.      
+ 		  & mFITEXY $(X|Y)$	      & $0.26^{+0.11}_{-0.08}$ & $0.49^{+0.08}_{-0.06}$  \\	     %& marg. consist.
+ 		  & {\tt linmix\_err} $(X|Y)$ & $0.35 \pm 0.10$ & $0.51 \pm 0.10$                \\ [0.5em]  %& consist.      
+ 													     %
+  Late-type	  & mFITEXY $(Y|X)$	      & $0.13^{+0.42}_{-0.13}$ & $0.55^{+0.15}_{-0.10}$  \\	     %& consist.      
+ 		  & {\tt linmix\_err} $(Y|X)$ & $0.39 \pm 0.19$ & $0.63 \pm 0.16$                \\	     %& consist.      
+ 		  & mFITEXY $(X|Y)$	      & $0.13^{+0.43}_{-0.13}$ & $1.09^{+0.41}_{-0.24}$  \\	     %& non consist.  
+ 		  & {\tt linmix\_err} $(X|Y)$ & $0.45 \pm 0.31$ & $1.31 \pm 0.97$                \\ [0.5em]  %& consist.
 
@@
   \label{tab:intsc} 
-  \tablecomments{  }
+  %\tablecomments{  }
   \end{table*}

### 2015-11-11 python_codes/paper_figures/MbhN/figures.py

@@ -82,7 +82,7 @@ def mag_sph_vs_n_maj():
 	
 	all = mag_sph*[0] + 1
 	all[simplemorphtype=='out'] = 0
-	all[simplemorphtype=='merger'] = 0
+	#all[simplemorphtype=='merger'] = 0
 	
 	# build figure
 	
@@ -617,7 +617,7 @@ def mag_sph_vs_n_eq():
 	
 	all = mag_sph*[0] + 1
 	all[simplemorphtype=='out'] = 0
-	all[simplemorphtype=='merger'] = 0
+	#all[simplemorphtype=='merger'] = 0
 	
 	# build figure
 	
@@ -1145,7 +1145,7 @@ def mbh_vs_n_sph_maj():
         earlytype[simplemorphtype=='E/S0'] = 1
 	
 	all = mbh*[0] + 1
-	all[simplemorphtype=='merger'] = 0
+	#all[simplemorphtype=='merger'] = 0
         all[gal_id=='n0524'] = 0
 	all[gal_id=='n3998'] = 0
 	
@@ -1868,7 +1868,7 @@ def mbh_vs_n_sph_eq():
 def main():
 	mag_sph_vs_n_maj()
 	#mag_sph_vs_n_eq()
-	#mbh_vs_n_sph_maj()
+	mbh_vs_n_sph_maj()
 	#mbh_vs_n_sph_eq()
 	
 main()		

### 2015-11-18 papers/ellicular/arxiv/ellicular.tex
victory

--- 2015-11-11 papers/ellicular/ellicular.tex
@@
 
-%\title[Non over-massive black holes in early-type galaxies]{Early-type galaxies with intermediate-scale discs and their (non over-massive) black holes}
 \title[Explaining the reportedly over-massive black holes]
@@
 {\parbox{\textwidth}{
-Giulia~A.~D. Savorgnan$^{1}$\thanks{E-mail: \texttt{gsavorgn@astro.swin.edu.au}},
-Alister W. Graham$^{1}$}\vspace{0.4cm}\\
+Giulia A.~D.~Savorgnan$^{1}$\thanks{E-mail: \texttt{gsavorgn@astro.swin.edu.au}},
+Alister W.~Graham$^{1}$}\vspace{0.4cm}\\
 \parbox{\textwidth}{
@@
 \begin{abstract}
-{\bf The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
+The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
 Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
@@
 and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
-used to describe the coevolution of spheroids and their central supermassive black holes. }
+used to describe the coevolution of spheroids and their central supermassive black holes.
 
@@
 \label{sec:int}
-{\bf The awareness that \emph{many} early-type galaxies contain previously over-looked stellar discs dates back half a century 
+The awareness that \emph{many} early-type galaxies contain previously over-looked stellar discs dates back half a century 
 \citep{liller1966,stromstrom1978,michard1984,djorgovski1985,jedrzejewski1987,BenderMoellenhoff1987,
@@
 Of course if a disc is face-on, then the galaxy will not be classified as a fast rotator. }.
-%A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
-%is a signature of a large-scale disc, 
-%while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 
-%indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 
 Unfortunately, such extended kinematic maps are not yet available for large numbers of galaxies in the local Universe. 
@@
 In Section \ref{sec:mm} we explore the important implications this has for the (black hole mass)-(spheroid stellar mass) diagram. 
-Finally, in Section \ref{sec:disc} we briefly discuss our results in terms of galaxy evolution. }
+Finally, in Section \ref{sec:disc} we briefly discuss our results in terms of galaxy evolution.
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{discmodel.eps}
+\includegraphics[width=\columnwidth]{discmodel.pdf}
 \caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
@@
 taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
-Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (2015).
+Our galaxy decomposition technique is extensively described in \cite{paperI}.
 Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
@@
 The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan 
-and described in Savorgnan \& Graham (2015).
+and described in \cite{paperI}.
 We modelled the light profiles with a combination of PSF-convolved analytic functions, 
@@
 \subsection{NGC 3115}
-The presence of a disc in the {\bf central fast rotator} NGC 3115 
-{\bf (e.g.~\citealt{strom1977,nieto1988,scorzabender1995}) }
+The presence of a disc in the central fast rotator NGC 3115 
+(e.g.~\citealt{strom1977,nieto1988,scorzabender1995}) 
 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
@@
 \subsection{Mrk 1216}
-Although the disc in the {\bf central fast rotator} Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
+Although the disc in the central fast rotator Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
 the velocity map \citep{yildirim2015} reveals the presence of a fast rotating component 
@@
 Our isophotal analysis and galaxy decompositions for NGC 1271 and NGC 1277 will be presented in 
-Graham, Savorgnan \& Ciambur (\emph{in prep.}) and Graham et al.~(2015), respectively, 
-while the galaxies NGC 821, NGC 3377 and NGC 4697 have been analysed in Savorgnan \& Graham (2015).
+Graham, Savorgnan \& Ciambur (\emph{in prep.}) and \cite{graham2015n1277}, respectively, 
+while the galaxies NGC 821, NGC 3377 and NGC 4697 have been analysed in \cite{paperI}.
 
 \subsubsection{NGC 1271}
-\cite{walsh2015} explored a three-component decomposition for the {\bf central fast rotator} NGC 1271 
+\cite{walsh2015} explored a three-component decomposition for the central fast rotator NGC 1271 
 and identified the galaxy bulge with the innermost of the three components, 
@@
 \subsubsection{NGC 1277}
-\cite{vandenbosch2012} proposed a model for the {\bf central fast rotator} NGC 1277 with a bulge + disc + nuclear source + envelope, 
+\cite{vandenbosch2012} proposed a model for the central fast rotator NGC 1277 with a bulge + disc + nuclear source + envelope, 
 which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total flux ratio of $0.24$; 
@@
 \subsubsection{NGC 3377}
-\cite{lasker2014data} modelled the {\bf central fast rotator} NGC 3377 
-{\bf (e.g.~\citealt{jedrzejewski1987inproceedings,scorzabender1995}) }
+\cite{lasker2014data} modelled the central fast rotator NGC 3377 
+(e.g.~\citealt{Jedrzejewski1987INPROCEEDINGS,scorzabender1995}) 
 with a bulge + nuclear disc + disc + envelope, 
@@
 \subsubsection{NGC 821}
-\cite{lasker2014data} decomposed the {\bf central fast rotator} NGC 821 into a bulge + disc + envelope, 
+\cite{lasker2014data} decomposed the central fast rotator NGC 821 into a bulge + disc + envelope, 
 and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total flux ratio of $0.19$; 
@@
 \subsubsection{NGC 4697}
-{\bf While NGC 4697 (e.g.~\citealt{carter1987,Jedrzejewski1987n720n1052n4697,davies1981}) 
+While NGC 4697 (e.g.~\citealt{carter1987,Jedrzejewski1987n720n1052n4697,davies1981}) 
 was explicitly referred to as a ``fast rotator'' by \cite{capaccioli1987} and \cite{petrou1981}, 
-it is only a central fast rotator} and it represents an ``extreme'' case. 
+it is only a central fast rotator and it represents an ``extreme'' case. 
 \cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
@@
 The color lines represent the individual (PSF-convolved) model components: 
-{\bf red solid = S\'ersic (spheroid), blue dashed = S\'ersic (disc), green dotted = Gaussian ring. }
+red solid = S\'ersic (spheroid), blue dashed = S\'ersic (disc), green dotted = Gaussian ring. 
 The residual profile (data $-$ model) is shown as $\Delta \mu$. 
@@
 The color lines represent the individual (PSF-convolved) model components:
-{\bf red solid = S\'ersic (spheroid), blue dashed = exponential (nuclear and intermediate-scale disc). }
+red solid = S\'ersic (spheroid), blue dashed = exponential (nuclear and intermediate-scale disc). 
 }
@@
 However, using a sample of 45 early-type and 17 spiral galaxies, 
-Savorgnan et al.~(2015) shows that, when considering all galaxies irrespective of their morphological type, 
+\cite{paperII} shows that, when considering all galaxies irrespective of their morphological type, 
 the correlation of the black hole mass with the spheroid luminosity is better than that with the galaxy luminosity.} 
-(Savorgnan et al.~2015). 
+\citep{paperII}. 
 If a galaxy hosts a black hole that is over-massive compared to expectations from the spheroid luminosity, 
@@
 In Figure \ref{fig:mm} we show the location of these five galaxies in the updated (black hole mass)-(spheroid stellar mass) diagram 
-for early-type galaxies from Savorgnan et al.~(2015). 
+for early-type galaxies from \cite{paperII}. 
 Figure \ref{fig:mm} was populated using the galaxy decomposition technique shown here 
-and extensively described in Savorgnan \& Graham (2015). 
+and extensively described in \cite{paperI}. 
 Briefly, we obtained Spitzer/IRAC $3.6~\rm \mu m$ images for 45 early-type galaxies 
@@
 which has increased the galaxy size but preserved the bulge compactness. 
-{\bf Of course some lenticular/ES galaxies may have been built from mergers (e.g.~\citealt{querejeta2015}, and references therein). }
+Of course some lenticular/ES galaxies may have been built from mergers (e.g.~\citealt{querejeta2015}, and references therein). 
 The other compact massive spheroids of today's Universe belong to some galaxies with intermediate-scale discs. 
@@
 \includegraphics[width=\columnwidth]{mm.pdf}
-\caption{Black hole mass plotted against spheroid stellar mass for 45+3 early-type galaxies (from Savorgnan et al.~2015). 
+\caption{Black hole mass plotted against spheroid stellar mass for 45+3 early-type galaxies (from \citealt{paperII}). 
 The black solid line is the bisector linear regression for all galaxies except Mrk 1216, NGC 1271 and NGC 1277. 
@@
 \section{Summary and conclusions}
-{\bf Early-type galaxies display a broad distribution of spheroid-to-total flux ratios (e.g.~\citealt{cappellari2011kmdr}), 
+Early-type galaxies display a broad distribution of spheroid-to-total flux ratios (e.g.~\citealt{cappellari2011kmdr}), 
 going from disc-less, ``pure'' elliptical galaxies (slow rotators) 
@@
 i.e.~discs of kiloparsec-size that remain ``embedded'' within the spheroidal component of the galaxy 
-and do not dominate the galaxy light at large radii as large-scale discs do. }
+and do not dominate the galaxy light at large radii as large-scale discs do. 
 While this is likely known to some readers, 

### 2015-11-18 papers/mbhn/mbhn.tex
victory

@@
 with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
-The S\'ersic index of a galaxy's spheroidal component $n_{\rm sph}$ has been shown to tightly correlate 
-with the mass of the central supermassive black hole $M_{\rm BH}$ by some studies. 
-The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known galaxy scaling relations: 
-the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$ relations, 
+The S\'ersic index of a galaxy's spheroidal component, $n_{\rm sph}$, has been shown to tightly correlate 
+with the mass of the central supermassive black hole, $M_{\rm BH}$. 
+The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known scaling relations: 
+the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$, 
 where $L_{\rm sph}$ indicates the galaxy's spheroid luminosity. 
 However, it is widely recognized that obtaining an accurate estimate of the spheroid S\'ersic index is a challenging task, 
-and -- not surprisingly -- other studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
+and -- not surprisingly -- some studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
 With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
-and other correlations between the black hole mass and various galaxy properties, 
+and other black hole mass scaling relations, 
 we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
@@
 that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
-This sample is the largest to date used to investigate black hole mass scaling relations. 
 In this paper, the third of its series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
@@
 The empirical \cite{sersic1963,sersic1968} $R^{1/n}$ model has been demonstrated to provide adequate description 
-of the light distribution of the stellar spheroidal and disk components of galaxies (add REFS), 
+of the light distribution of the stellar spheroidal\footnote{Throughout the text, we use the term ``spheroid'' to designate 
+either a diskless elliptical galaxy or the bulge component of a disk galaxy, 
+with no attempt at distinguishing between classical bulges and disk-like pseudo-bulges. } and disk components of galaxies 
+(e.g.~\citealt{caon1993,andredakis1995,iodice1997,iodice1999,seigar1998,khosroshahi2000}), 
 yet its physical origin has remained unexplained for decades. 
@@
 between the black hole mass and several galaxy structural parameters, 
-we performed state-of-the-art modelling for the largest sample of galaxies to date (Savorgnan \& Graham 2015, hereafter \emph{Paper I}),  
+we performed state-of-the-art modelling for the largest sample of galaxies to date (Savorgnan \& Graham 2015a, hereafter \emph{Paper I}),  
 for which a dynamical measurement of the black hole mass was available.
@@
 given its superb capability to trace the stellar mass (\citealt{sheth2010}, and references therein). 
-In Savorgnan et al.~(2015, hereafter \emph{Paper II}) we examined the correlations between black hole mass and 
-galaxy luminosity, spheroid luminosity and spheroid stellar mass. 
+In Savorgnan et al.~(2015, hereafter \emph{Paper II}) we examined the correlations between the black hole mass and 
+the total galaxy luminosity, the spheroid luminosity and the spheroid stellar mass. 
 Here we focus on the $M_{\rm BH} - n_{\rm sph}$ relation. \\
@@
 and large-scale disks, that encase the bulge and dominate the light at large radii.  
-Savorgnan \& Graham (2015) explain that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
+Savorgnan \& Graham (2015b) demonstrate that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
 the luminosity of the spheroid is underestimated, 
@@
 along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
-the spheroid S\'ersic indices have been estimated with a method that takes into account systematic errors. 
+the spheroid S\'ersic indices were estimated with a method that takes into account systematic errors. 
 This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by different studies 
 with that obtained by us. 
-Systematic errors are typically not considered by popular 2D fitting codes which report only the statistical errors 
+Systematic errors are typically not considered by popular 2D fitting codes, which report only the statistical errors 
 associated with their fitted parameters. 
-Refer to \emph{Paper I} for a detailed discussion on this. }.  
+Readers should refer to \emph{Paper I} for a more detailed discussion on this topic. }.  
 The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
@@
 whereas in our $M_{\rm BH} - n_{\rm sph}$ plot 
-the S0 galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
+the lenticular galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
 These two galaxies have therefore been excluded from the rest of the analysis. 
+{\bf quote fitexy results bcz more reliable than other 2 }
+%I should have mentioned that the linear regression code, BCES, from Akritas & Bershady (1996) can at times get the slope wrong.  
+%This occurs if the error bars on the velocity dispersion are too big relative to the range of velocity dispersions in one's sample (say >15%), 
+%or if the error bars on the velocity dispersion and black hole masses are not all roughly the same. 
+%That is, if some black hole masses have error bars of 50% while others have error bars of 5%, then we could be in trouble.
 
 \subsection{$L_{\rm sph} - n_{\rm sph}$}
-Following \cite{graham2001}, 
+Following \cite{graham2001bulges}, 
 who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
-\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013review} 
+\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{grahamworley2008} 
 and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
 (in the B- and K-band, respectively). 
-At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013review} were of the best quality available 
+At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{grahamworley2008} were of the best quality available 
 to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
@@
 but they were a collection of results taken from various past bulge/disk decomposition studies. 
-It is also worth mentioning that, 
-although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
-{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
-Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our high-quality dataset  
-derived from state-of-the-art multicomponent decompositions, 
-that were performed in a consistent manner 
-and using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
-\cite{graham2013review} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
+%It is also worth mentioning that, 
+%although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
+%{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
+Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram using only our high-quality dataset. 
+Spheroid luminositites and S\'ersic indices were obtained from accurate multicomponent decompositions,  
+performed in a consistent manner using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
+\cite{grahamworley2008} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
 However, using our dataset, 
@@
 whereas the combination of lenticular and spiral galaxies do not. 
-{\bf why?? dust? multicomponent? classification?}
+Early-type galaxies follow $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$; 
+remarkably, this is exactly the same proportionality obtained by \cite{savorgnan2013} for elliptical galaxies only, 
+upon re-analyzing the dataset from \cite{grahamguzman2003}. 
+Late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence.
 
@@
 are consistent with each other within their $1\sigma$ uncertainties, 
-which prevents us from considering them as two separate sequences. 
+which prevented us from considering them as two separate sequences. 
 On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations 

### 2015-11-18 python_codes/tables/tables.py

@@ -63,6 +63,36 @@ def make_alister_table1():
         f.close()
        
         ############################
+
+def make_shankar_table():
+        connection = sql3.connect(dbname)
+        cur = connection.cursor()
+       
+        getdata_query = 'SELECT anc.gal_id, \
+		physres.log_r_e_maj_moffat_comb, physres.log_r_e_eq_moffat_comb, errV.perr_log_r_e, errV.merr_log_r_e \
+		FROM Ancillary AS anc \
+		JOIN OneDFitResultsPhysicalUnits AS physres ON anc.gal_id = physres.gal_id \
+		JOIN ErrorsVote as errV ON anc.gal_id = errV.gal_id \
+		WHERE anc.fit1D_done = 1;'
+	
+	cur.execute(getdata_query)
+	datalist = cur.fetchall()
+	data= np.asarray(datalist).transpose()
+	#print data
+	gal_id = data[0]
+	log_r_e_maj = data[1].astype(np.float)
+	log_r_e_eq = data[2].astype(np.float)
+	perr_log_r_e = data[3].astype(np.float)
+	merr_log_r_e = data[4].astype(np.float)
+	
+        fName = path_tables + 'r_e_maj-r_e_eq.dat'
+        f = open(fName, 'w')
+        f.write('# galaxy   log_r_e_maj [log(kpc)]   log_r_e_eq [log(kpc)]   perr_log_r_e   merr_log_r_e   \n')
+        for g, a,b,c,d in zip(gal_id, log_r_e_maj, log_r_e_eq, perr_log_r_e, merr_log_r_e):
+        	f.write(str(g) + '     ' + str(a) + '     ' + str(b) + '     ' + str(c) + '     ' + str(d)  + '\n')
+        f.close()
+       
+        ############################
 	
 
 def make_BHFP_data_table():
@@ -215,5 +245,6 @@ def make_BHFP_data_table():
         fi.close()
 
 	
-make_alister_table1()	
-make_BHFP_data_table()	
+#make_alister_table1()	
+#make_BHFP_data_table()	
+make_shankar_table()

### 2015-11-20 papers/MbhMsph/mm.tex
the victory day

@@
 \usepackage{hyperref}
-
-%% Sometimes a paper's abstract is too long to fit on the
-%% title page in preprint2 mode. When that is the case,
-%% use the longabstract style option.
-
-%% \documentclass[preprint2,longabstract]{aastex}
 
@@
 
-%\and
-
-%\author{A. W. Graham\altaffilmark{1}}
-%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
-
-%% Notice that each of these authors has alternate affiliations, which
-%% are identified by the \altaffilmark after each name.  Specify alternate
-%% affiliation information with \altaffiltext, with one command per each
-%% affiliation.
-
-%\altaffiltext{1}{}
-%\altaffiltext{2}{Society of Fellows, Harvard University.}
-%\altaffiltext{3}{present address: Center for Astrophysics,
-%    60 Garden Street, Cambridge, MA 02138}
-%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
-%\altaffiltext{5}{Patron, Alonso's Bar and Grill}
-
-%% Mark off your abstract in the ``abstract'' environment. In the manuscript
-%% style, abstract will output a Received/Accepted line after the
-%% title and affiliation information. No date will appear since the author
-%% does not have this information. The dates will be filled in by the
-%% editorial office after submission.
-
 \begin{abstract}
@@
 The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
-and define a tight %\emph{early-type sequence} 
+and define a tight 
 \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
@@
 i.e.~a $\pm 2\sigma$ range of 0.1--5\%.
-At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper %\emph{late-type sequence}, 
+At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper 
 \emph{blue sequence}, 
@@
 These mean statistical bulge-to-total ratios were obtained from the results of two-component (S\'ersic-bulge/exponential-disk) decompositions in the literature. \\
-%It should also be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
-%and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies (lenticulars and spirals). \\
-%Several recent papers \citep{jiang2011a,jiang2013,mathur2012,reines2013} claimed an offset at the low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ diagram,
-%such that the black hole mass is lower than expected from the near-linear correlation traced by the high-mass, early-type spheroids. 
-%However, \cite{grahamscott2013} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
-%are not randomly offset from such near-linear correlation, 
-%but follow the steeper relation traced by the S\'ersic spheroids. 
-%Using bulge/disk decomposition data from \cite{jiang2011a}, 
-%\cite{grahamscott2015} derived the host spheroid masses 
-%and showed that the steeper $M_{\rm BH} - M_{\rm *,sph}$ extends to these spheroids with even lower black hole masses 
-%($10^{5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 2 \times 10^{6}$), 
-%and a more detailed analysis will be presented in Graham et al. (2015, \emph{in preparation}).  \\
-Here we investigate in more detail %substructure in 
+Here we investigate in more detail 
 the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
@@
 $M_{\rm dyn,sph} \propto R_{\rm e} \sigma^2$, and address the issue of a black hole fundamental plane.
-%{\bf This paper is structured as follows... }
 
@@
 \emph{Paper I} presents the dataset used here, 
-%to investigate the $M_{\rm BH} - L_{\rm gal}$, $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
 including details about the data reduction process and the galaxy modelling technique that we developed. 
@@
 the radial extent of the surface brightness profile and one's sampling of this. 
-Most of these factors are not included in popular 2D fitting codes which report only the {\bf statistical} errors associated with their fitted parameters. 
+Most of these factors are not included in popular 2D fitting codes which report only the statistical errors associated with their fitted parameters. 
 In fact, when performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well spatially resolved -- galaxies, 
 errors are dominated by systematics rather than Poisson noise. 
-{\bf Unlike many papers, we believe that we have not under-estimated the uncertainties associated to the bulge best-fit parameters.} } 
+Unlike many papers, we believe that we have not under-estimated the uncertainties associated to the bulge best-fit parameters. } 
 on the bulge magnitudes, and presents the individual 66 galaxy decompositions, 
@@
 but only the last two allow one to quantify it.
-%Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
-%can give biased results (wrong slope) when the scatter is comparable to the range of the data},
-%we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
 We report linear regressions, both symmetrical and non-symmetrical, 
@@
                         & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.05$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]
-
-%Late-type (Sp) (13) & BCES $(Y|X)$      & $7.37 \pm 0.17$ & $-0.33 \pm 0.87$   & $-24.39$ & $-$ & $0.65$ \\
-%                    & BCES $(X|Y)$      & $7.37 \pm 1.97$ & $-21.66 \pm 53.74$ & $-24.39$ & $-$ & $7.73$ \\
-%                    & BCES Bisector     & $7.37 \pm 0.20$ & $-1.32 \pm 0.94$   & $-24.39$ & $-$ & $0.77$ \\
-%                    & FITEXY $(Y|X)$    & $7.38^{+0.17}_{-0.18}$ & $-0.34^{+0.74}_{-0.80}$ & $-24.39$ & $0.63^{+0.19}_{-0.11}$ & $0.65$ \\
-%                    & FITEXY $(X|Y)$    & $$ & $$ & $-24.39$ & $$ & $$ \\
-%                    & FITEXY Bisector   & $$ & $$ & $-24.39$ & $-$    & $$ \\
-%                    & {\tt linmix\_err} $(Y|X)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
-%                    & {\tt linmix\_err} $(X|Y)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
-%                    & {\tt linmix\_err} Bisector    & $$ & $$ & $-24.39$ & $-$    & $$ \\
-
-%All (62)               & BCES $(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
-%                       & BCES $(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
-%                       & BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
-%                       & FITEXY $(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
-%                       & FITEXY $(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
-%                       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
-%                       & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\
-%                       & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\
-%                       & {\tt linmix\_err} Bisector    & $$ & $$ & $$ & $-$    & $$ \\
 
@@
 are also well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994,jerjen2000}). 
-The use of the S\'ersic index (in addition to rotation) to identify pseudo-bulges is thus a dangerous practice. \\
+The use of the S\'ersic index (in addition to rotation) to identify pseudo-bulges is thus a dangerous practice. 
+{\bf We therefore do not assume that all bulges with $n_{\rm sph}<2$ are built from internal processes in the disk 
+(i.e.~are what some authors call pseudo-bulges). } \\
 \cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
@@
 and that the amplitude of their offset is the same ($\lesssim 1.5\rm~dex$).
-That is, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.
+That is, within the current dataset, 
+bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$. \\
 
@@
 
-%Ellipticals (E) (30)   & BCES $(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
-%                      & BCES $(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
-%                      & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
-%                      & FITEXY $(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
-%                      & FITEXY $(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
-%                      & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
-%
-%Lenticulars (S0) (13)  & BCES $(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
-%                      & BCES $(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
-%                      & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
-%                      & FITEXY $(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
-%                      & FITEXY $(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
-%                      & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
-%
-
 {\bf Early-type (E+S0)} (45) & BCES $(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
@@
 The bulges of the early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
-consistent with a dry-merging formation scenario\footnote{\bf In dry mergers, the black hole and the bulge grow at the same pace, 
+consistent with a dry-merging formation scenario\footnote{In dry mergers, the black hole and the bulge grow at the same pace, 
 increasing their mass in lock step.},
@@
 That is, the AGNs appear to be the low-mass continuation of our tentative \emph{late-type sequence} shown in Figure \ref{fig:mbhmasssph} 
-and this will be explored with more rigour in a forthcoming paper.
+and this will be explored with more rigour in a forthcoming paper. \\
+
+{\bf 
+As a final remark, we comment on the work done by \cite{reinesvolonteri2015}, 
+who investigated the relationship between black hole mass and total galaxy stellar mass, $M_{\rm *,gal}$. 
+Their Figure 8 presents the $M_{\rm BH} - M_{\rm *,gal}$ distribution 
+for a sample of $\approx 260$ local AGNs with virial black hole masses  
+and for $\approx 80$ galaxies with dynamical black hole masses. 
+They concluded that the AGN sample and the early-type galaxies with quiescent black holes define two distinct sequences 
+in their $M_{\rm BH} - M_{\rm *,gal}$ diagram; 
+these two sequences have similar slope, but a normalization factor different by more than one order of magnitude.  
+Since we noted that the \cite{jiang2011a} AGN sample follows the steeper $M_{\rm BH} - M_{\rm *,sph}$ correlation 
+traced by our spiral galaxy bulges (the majority of which host an AGN), 
+it would be interesting to recover the $M_{\rm BH} - M_{\rm *,sph}$ distribution 
+also for the AGN sample of \cite{reinesvolonteri2015}. \\
+However we do note that there is emerging evidence (e.g.~\citealt{busch2015,subramanian2015}) 
+for a population of bulges with black hole masses residing below (or to the right of) the red and blue $M_{\rm BH} - M_{\rm *,sph}$ 
+sequences constructed here using samples with directly measured black hole masses, as speculated by Batcheldor (2010).
+}
 
@@
       We intend to investigate this point in our future work. 
-\item Spheroids with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
-      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. 
+\item {\bf It has been argued that pseuso-bulges (disk-like, rotation-supported systems, built from secular processes) 
+      do not follow the $M_{\rm BH} - L_{\rm sph}$ correlation defined by classical bulges 
+      (spheroidal, pressure-supported systems, formed through violent processes).  
+      The recent literature (e.g.~\citealt{sani2011,beifiori2012}) has distinguished between pseudo- and classical bulges 
+      according to their S\'ersic index, $n_{\rm sph}$. 
+      Although we do not consider the S\'ersic index a good indicator as of the nature of a bulge (e.g.~\citealt{grahamworley2008}), 
+      we investigated this point and found that, within the current dataset,  
+      spheroids with $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
+      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. }
 \item The $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ correlations have the same level of intrinsic scatter 
@@
       Once reasonable numbers of spiral galaxies are included, 
-      $M_{\rm BH}$ correlates better with $L_{\rm sph}$ than with $L_{\rm gal}$ {\bf (see also \citealt{erwingadotti2012,beifiori2012})}. 
+      $M_{\rm BH}$ correlates better with $L_{\rm sph}$ than with $L_{\rm gal}$ (see also \citealt{erwingadotti2012,beifiori2012}). 
 \end{itemize}
@@
 \acknowledgments
-GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. \\
-% referee thank you!!
+GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. 
+We also thank the anonymous referee for useful comments and suggestions. 
 This research was supported by Australian Research Council funding through grants

### 2015-11-20 papers/MbhMsph/ApJ_submission/mm.tex
victory2

@@
 
-%\and
-
-%\author{A. W. Graham\altaffilmark{1}}
-%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
-
-%% Notice that each of these authors has alternate affiliations, which
-%% are identified by the \altaffilmark after each name.  Specify alternate
-%% affiliation information with \altaffiltext, with one command per each
-%% affiliation.
-
-%\altaffiltext{1}{}
-%\altaffiltext{2}{Society of Fellows, Harvard University.}
-%\altaffiltext{3}{present address: Center for Astrophysics,
-%    60 Garden Street, Cambridge, MA 02138}
-%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
-%\altaffiltext{5}{Patron, Alonso's Bar and Grill}
-
-%% Mark off your abstract in the ``abstract'' environment. In the manuscript
-%% style, abstract will output a Received/Accepted line after the
-%% title and affiliation information. No date will appear since the author
-%% does not have this information. The dates will be filled in by the
-%% editorial office after submission.
-
 \begin{abstract}
 In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
-decomposition of 66 galaxies, with directly measured black hole masses, 
+decomposition of 66 galaxies, with directly measured black hole masses, $M_{\rm BH}$, 
 that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
 Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
-We present correlations between the black hole mass, $M_{\rm BH}$, 
+We present correlations between $M_{\rm BH}$ 
 and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
 and also stellar mass, $M_{\rm *,sph}$.
-Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies.
-Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
+While most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies,
+our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
 and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
-The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
-and define a tight %\emph{early-type sequence} 
-\emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
+The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
+and define a tight 
+\emph{red sequence} with intrinsic scatter $\epsilon_{(M_{\rm BH}|M_{\rm *,sph})} = 0.43 \pm 0.06\rm~dex$ 
 and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$, 
 i.e.~a $\pm 2\sigma$ range of 0.1--5\%.
-At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper %\emph{late-type sequence}, 
+At the low-mass end, the bulges of late-type galaxies define a much steeper 
 \emph{blue sequence}, 
-with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
+with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$ and $M_{\rm BH}/M_{\rm *,sph}$ equal to $0.02\%$ at $M_{\rm BH} \approx 10^6~\rm M_\odot$, 
 indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
-We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
+We additionally report that: i) our S\'ersic galaxy sample follows $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, 
+a less steep sequence than previously reported; 
 ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
@@
 and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies 
-(most elliptical galaxies contain disks, i.e.~$L_{\rm sph} \neq L_{\rm gal}$) --
-once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
+-- once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
 
@@
 These mean statistical bulge-to-total ratios were obtained from the results of two-component (S\'ersic-bulge/exponential-disk) decompositions in the literature. \\
-Here we investigate in more detail %substructure in 
+Here we investigate in more detail 
 the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
@@
 That is, the AGNs appear to be the low-mass continuation of our tentative \emph{late-type sequence} shown in Figure \ref{fig:mbhmasssph} 
-and this will be explored with more rigour in a forthcoming paper.
+and this will be explored with more rigour in a forthcoming paper. \\
+
+{\bf 
+As a final remark, we comment on the work by \cite{reinesvolonteri2015}, 
+who investigated the relationship between black hole mass and total galaxy stellar mass, $M_{\rm *,gal}$. 
+Their Figure 8 presents the $M_{\rm BH} - M_{\rm *,gal}$ distribution 
+for a sample of $\approx 260$ local AGNs with virial black hole masses  
+and for $\approx 80$ galaxies with dynamical black hole masses. 
+They concluded that the AGN sample and the early-type galaxies with quiescent black holes define two distinct sequences 
+in their $M_{\rm BH} - M_{\rm *,gal}$ diagram; 
+these two sequences have similar slope, but a normalization factor different by more than one order of magnitude.  
+Since we noted that the \cite{jiang2011a} AGN sample follows the steeper $M_{\rm BH} - M_{\rm *,sph}$ correlation 
+traced by our spiral galaxy bulges (the majority of which host an AGN), 
+it would be interesting to recover the $M_{\rm BH} - M_{\rm *,sph}$ distribution 
+also for the AGN sample of \cite{reinesvolonteri2015}. \\
+However we do note that there is emerging evidence (e.g.~\citealt{busch2015,subramanian2015}) 
+for a population of bulges with black hole masses residing below (or to the right of) the red and blue $M_{\rm BH} - M_{\rm *,sph}$ 
+sequences constructed here using samples with directly measured black hole masses, as speculated by Batcheldor (2010).
+}
 
@@
       We intend to investigate this point in our future work. 
-\item Spheroids with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
-      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. 
+\item {\bf It has been argued that pseuso-bulges (disk-like, rotation-supported systems, built from secular processes) 
+      do not follow the $M_{\rm BH} - L_{\rm sph}$ correlation defined by classical bulges 
+      (spheroidal, pressure-supported systems, formed through violent processes).  
+      The recent literature (e.g.~\citealt{sani2011,beifiori2012}) has distinguished between pseudo- and classical bulges 
+      according to their S\'ersic index, $n_{\rm sph}$. 
+      Although we do not consider the S\'ersic index a good indicator of the nature of a bulge (e.g.~\citealt{grahamworley2008}), 
+      we investigated this point and found that, within the current dataset,  
+      spheroids with $n_{\rm sph}<2$ 
+      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. }
 \item The $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ correlations have the same level of intrinsic scatter 
@@
 GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. 
-{\bf We thank the anonymous referee for their thorough review and highly appreciate the comments and suggestions, 
-which significantly contributed to improving the quality of the publication. } \\
+We also thank the anonymous referee for useful comments and suggestions. 
 This research was supported by Australian Research Council funding through grants

### 2015-11-20 papers/MbhMsph/arxiv/mm.tex
victory2

--- 2015-11-20 papers/MbhMsph/ApJ_submission/mm.tex
@@
 The use of the S\'ersic index (in addition to rotation) to identify pseudo-bulges is thus a dangerous practice. 
-{\bf We therefore do not assume that all bulges with $n_{\rm sph}<2$ are built from internal processes in the disk 
-(i.e.~are what some authors call pseudo-bulges). } \\
+We therefore do not assume that all bulges with $n_{\rm sph}<2$ are built from internal processes in the disk 
+(i.e.~are what some authors call pseudo-bulges).  \\
 \cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
@@
 
-{\bf 
 As a final remark, we comment on the work by \cite{reinesvolonteri2015}, 
@@
 it would be interesting to recover the $M_{\rm BH} - M_{\rm *,sph}$ distribution 
-also for the AGN sample of \cite{reinesvolonteri2015}. \\
+also for the AGN sample of \cite{reinesvolonteri2015}. 
 However we do note that there is emerging evidence (e.g.~\citealt{busch2015,subramanian2015}) 
@@
 sequences constructed here using samples with directly measured black hole masses, as speculated by Batcheldor (2010).
-}
 
@@
       We intend to investigate this point in our future work. 
-\item {\bf It has been argued that pseuso-bulges (disk-like, rotation-supported systems, built from secular processes) 
+\item It has been argued that pseuso-bulges (disk-like, rotation-supported systems, built from secular processes) 
       do not follow the $M_{\rm BH} - L_{\rm sph}$ correlation defined by classical bulges 
@@
       spheroids with $n_{\rm sph}<2$ 
-      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. }
+      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. 
 \item The $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ correlations have the same level of intrinsic scatter 

### 2015-11-20 papers/MbhMsph/mm.tex
victory2

@@
 In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
-decomposition of 66 galaxies, with directly measured black hole masses, 
+decomposition of 66 galaxies, with directly measured black hole masses, $M_{\rm BH}$, 
 that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
 Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
-We present correlations between the black hole mass, $M_{\rm BH}$, 
+We present correlations between $M_{\rm BH}$ 
 and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
 and also stellar mass, $M_{\rm *,sph}$.
-Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies.
-Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
+While most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies,
+our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
 and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
-The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
+The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
 and define a tight 
-\emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
+\emph{red sequence} with intrinsic scatter $\epsilon_{(M_{\rm BH}|M_{\rm *,sph})} = 0.43 \pm 0.06\rm~dex$ 
 and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$, 
 i.e.~a $\pm 2\sigma$ range of 0.1--5\%.
-At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper 
+At the low-mass end, the bulges of late-type galaxies define a much steeper 
 \emph{blue sequence}, 
-with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
+with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$ and $M_{\rm BH}/M_{\rm *,sph}$ equal to $0.02\%$ at $M_{\rm BH} \approx 10^6~\rm M_\odot$, 
 indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
-We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
+We additionally report that: i) our S\'ersic galaxy sample follows $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, 
+a less steep sequence than previously reported; 
 ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
@@
 {\bf 
-As a final remark, we comment on the work done by \cite{reinesvolonteri2015}, 
+As a final remark, we comment on the work by \cite{reinesvolonteri2015}, 
 who investigated the relationship between black hole mass and total galaxy stellar mass, $M_{\rm *,gal}$. 
@@
       according to their S\'ersic index, $n_{\rm sph}$. 
-      Although we do not consider the S\'ersic index a good indicator as of the nature of a bulge (e.g.~\citealt{grahamworley2008}), 
+      Although we do not consider the S\'ersic index a good indicator of the nature of a bulge (e.g.~\citealt{grahamworley2008}), 
       we investigated this point and found that, within the current dataset,  
-      spheroids with $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
+      spheroids with $n_{\rm sph}<2$ 
       are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. }

### 2015-11-20 papers/data_paper/arxiv/datapaper.tex
victory2

--- 2015-10-16 papers/data_paper/ApJ_submission_2/datapaper.tex
@@
 
-%% Sometimes a paper's abstract is too long to fit on the
-%% title page in preprint2 mode. When that is the case,
-%% use the longabstract style option.
-
-%% \documentclass[preprint2,longabstract]{aastex}
-
 \newcommand{\vdag}{(v)^\dagger}
@@
 \email{gsavorgn@astro.swin.edu.au}
-
-%\and
-
-%\author{A. W. Graham\altaffilmark{1}}
-%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
-
-%% Notice that each of these authors has alternate affiliations, which
-%% are identified by the \altaffilmark after each name.  Specify alternate
-%% affiliation information with \altaffiltext, with one command per each
-%% affiliation.
-
-%\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
-%CTIO is operated by AURA, Inc.\ under contract to the National Science
-%Foundation.}
-%\altaffiltext{2}{Society of Fellows, Harvard University.}
-%\altaffiltext{3}{present address: Center for Astrophysics,
-%    60 Garden Street, Cambridge, MA 02138}
-%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
-%\altaffiltext{5}{Patron, Alonso's Bar and Grill}
 
@@
 \label{sec:int}
-Supermassive black holes and their host spheroids\footnote{\bf By the term ``spheroid'' 
+Supermassive black holes and their host spheroids\footnote{By the term ``spheroid'' 
 we mean either an elliptical galaxy or the bulge component of a disk galaxy, 
@@
 as opposed to \cite{beifiori2012} who claimed that the spheroid mass is a better tracer of $M_{\rm BH}$ than the galaxy mass 
-{\bf (see also \citealt{kormendygebhardt2001,erwingadotti2012})}.
+(see also \citealt{kormendygebhardt2001,erwingadotti2012}).
 The past studies did not converge to the same conclusions 
@@
 \label{sec:data}
-%\subsection{Initial sample}
 Our initial galaxy sample (see Table \ref{tab:sample}) consists of 75 objects for which a dynamical detection of the black hole mass 
@@
 
-%\clearpage
 \input{table_sample.tex}
-%\noindent
-%\input{table_observations.tex}
 
@@
 includes a number of data frames (the individual exposures) and the calibration data.
-The data frames were selected to be %``enhanced Level 1 products'', or
+The data frames were selected to be 
 corrected Basic Calibrated Data (cBCD), produced by the IRAC Level 1 pipeline. 
@@
 The task {\tt skyfit} also provided an estimate of the sky root mean square ($RMS_{\rm sky}$).
-%sky value also checked with Galfit
 
@@
 \subsubsection{1D PSF}
-A universal\footnote{\bf Across all mosaics, the variation of the Moffat $FWHM$ is $\pm 0''.1$, 
+A universal\footnote{Across all mosaics, the variation of the Moffat $FWHM$ is $\pm 0''.1$, 
 and the variation of the Moffat $\beta$ is $\pm 2.0$.
@@
 disturbed morphology in the galaxy outskirts, etc.). 
-{\bf In particular, we did not attempt to fit bends or truncations of large-scale disks 
+In particular, we did not attempt to fit bends or truncations of large-scale disks 
 (e.g.~\citealt{erwin2005,erwin2008,erwin2012,gutierrez2011,comeron2012,munozmateos2013,kim2014}) 
-but instead truncated the surface brightness profiles before the occurrence of such features. }
+but instead truncated the surface brightness profiles before the occurrence of such features. 
 Individual cases are discussed in Section \ref{sec:indgal}.
@@
 this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
-{\bf Over-looked partially depleted cores, or an incorrect PSF, can of course also result in (signal-to-noise)-weighted fitting schemes 
-performing poorly because of the emphasis they place on matching the model to the inner data. }
+Over-looked partially depleted cores, or an incorrect PSF, can of course also result in (signal-to-noise)-weighted fitting schemes 
+performing poorly because of the emphasis they place on matching the model to the inner data.
 
@@
 where we provide individual descriptions of the galaxies that we analyzed. \\
-{\bf As stressed in Section \ref{sec:int}, our investigation is primarily focused on the central spheroidal components 
+As stressed in Section \ref{sec:int}, our investigation is primarily focused on the central spheroidal components 
 of galaxies. 
@@
 unlike ``late-type spiral'' galaxies that can be bulgeless (e.g.~NGC 300).   
-We modeled spheroids/bulges with a S\'ersic profile, without attempting to distinguish between classical and pseudo-bulges. } \\
+We modeled spheroids/bulges with a S\'ersic profile, without attempting to distinguish between classical and pseudo-bulges.  \\
 Disks were usually fit with the exponential model, 
@@
 that fades toward larger radii. 
-{\bf \cite{savorgnangraham2015ellicular} extensively discuss the topic of galaxies with intermediate-scale disks 
+\cite{savorgnangraham2015ellicular} extensively discuss the topic of galaxies with intermediate-scale disks 
 and show that, when these disks are misclassified and modeled as large-scale disks, 
 the luminosity of the spheroidal component is underestimated, 
-which makes these galaxies falsely appear as extreme outliers in the (black hole mass)-(spheroid stellar mass) diagram. } \\
+which makes these galaxies falsely appear as extreme outliers in the (black hole mass)-(spheroid stellar mass) diagram.  \\
 Bars are usually recognizable from galaxy images and unsharp masks, 
@@
 can provide additional evidence for less obvious bars. 
-{\bf As noted, we were able to successfully fit bars with a Ferrer function 
+As noted, we were able to successfully fit bars with a Ferrer function 
 (NGC 4151 is the only case for which we described the bar with an $n \sim 0.2$ S\'ersic model). 
 Disk-like components embedded in the bulges of spiral galaxies were described with an $n \lesssim 1$ S\'ersic model or, 
-in a few cases, with a Ferrer function\footnote{\bf One advantage of choosing a Ferrer function over a S\'ersic profile 
+in a few cases, with a Ferrer function\footnote{One advantage of choosing a Ferrer function over a S\'ersic profile 
 to fit a disk-like component embedded in the bulge 
@@
 The bars in our sample were found to have rather flat inner profiles, 
-as is commonly found for bars in ``early-type spiral'' galaxies \citep{gadottidesouza2006}. } \\
+as is commonly found for bars in ``early-type spiral'' galaxies \citep{gadottidesouza2006}.  \\
 The presence of a nuclear component -- either resolved or unresolved -- was generally expected in 
@@
 whereas resolved nuclear components were modeled with (PSF-convolved) narrow Gaussian functions 
-{\bf (\citealt{wadadekar1999,ravindranath2001,peng2002} and \citealt{gadotti2008} discuss the importance of fitting nuclear components)}. \\
+(\citealt{wadadekar1999,ravindranath2001,peng2002} and \citealt{gadotti2008} discuss the importance of fitting nuclear components). \\
 Rings were identified from galaxy images and unsharp masks, and modeled with symmetric Gaussian ring profiles 
@@
 For each galaxy, we built a 2D model that was consistent with the corresponding 1D model in terms of number and type of components. 
-{\bf The only difference between our 1D and 2D models pertains to the description of bars: 
+The only difference between our 1D and 2D models pertains to the description of bars: 
 because the Ferrer profile is not made available in \textsc{Imfit},
-bars were fit with a 2D Gaussian function. } \\
+bars were fit with a 2D Gaussian function.  \\
 The 2D decomposition of NGC 2974 is presented in Figure \ref{fig:n29742d}. 
@@
 \includegraphics[width=\columnwidth]{n2974_resid.eps}
-\caption{Image of the galaxy NGC 2974 with its mask (top panel, {\bf on a logarithmic scale}), 
-unsharp mask (second panel, {\bf on a linear scale}), 
-best-fit 2D model (third panel, {\bf on a logarithmic scale}), 
-and residual image after the subtraction of the 2D model (bottom panel, {\bf on a linear scale; 
-the residual patterns correspond to differences between the data and the model of less than 6\%}).
+\caption{Image of the galaxy NGC 2974 with its mask (top panel, on a logarithmic scale), 
+unsharp mask (second panel, on a linear scale), 
+best-fit 2D model (third panel, on a logarithmic scale), 
+and residual image after the subtraction of the 2D model (bottom panel, on a linear scale; 
+the residual patterns correspond to differences between the data and the model of less than 6\%).
 The lefthand side of the mosaic allowed an accurate determination of the sky background level.}
@@
 This problem is overcome with 1D decomposition techniques 
-{\bf because the ellipticity, and additionally the deviations from elliptical isophotes, 
-are efficiently included in the equivalent-axis fit (see the Appendix of \citealt{ciambur2015})}.
+because the ellipticity, and additionally the deviations from elliptical isophotes, 
+are efficiently included in the equivalent-axis fit (see the Appendix of \citealt{ciambur2015}).
 \item The interpretation of the residual surface brightness profile is often crucial to identify the optimal decomposition for a galaxy. 
@@
 The dashed line displays the 1:1 relation.
-{\bf The four most obvious outliers are NGC 821, NGC 3377, NGC 4945, and NGC 5576. 
-Their individual cases are discussed in the Appendix. }}
+The four most obvious outliers are NGC 821, NGC 3377, NGC 4945, and NGC 5576. 
+Their individual cases are discussed in the Appendix. }
 \label{fig:n1d2d}
@@
 that does not quite match the real ``shape'' of the spheroid. 
-{\bf When we identified, 
-but were not able to model a galaxy sub-component with the same accuracy dedicated to the other components}.
+When we identified, 
+but were not able to model a galaxy sub-component with the same accuracy dedicated to the other components.
 In the case of apparent inconsistencies between the model and the observed galaxy properties 
@@
 for our measurements of $\log(n_{\rm sph})$ obtained from ``grade 1'', ``grade 2'' and ``grade 3'' fits, respectively. 
-{\bf This means that, if the fit to a galaxy was classified as ``grade 1'', 
+This means that, if the fit to a galaxy was classified as ``grade 1'', 
 the (logarithmic) value of the spheroid S\'ersic index $\tilde{n}_{\rm sph}$ and associated uncertainties would be 
@@
 then one would have $\log(\tilde{n}_{\rm sph})^{+\sigma_2^+}_{-\sigma_2^-} = \log(\tilde{n}_{\rm sph})^{+0.17}_{-0.21}$, 
-and so on.  }
+and so on.
 
@@
 for useful discussion. 
-{\bf We thank the anonymous referee for their thorough review and highly appreciate the comments and suggestions, 
-which significantly contributed to improving the quality of the publication. } \\
+We thank the anonymous referee for their thorough review and highly appreciate the comments and suggestions, 
+which significantly contributed to improving the quality of the publication.  \\
 This research was supported by Australian Research Council funding through grants
@@
   The ellipticity profile indicates that the disk is of intermediate-scale 
-  {\bf (for a thorough analysis of this galaxy, see \citealt{gadottisanchezjanssen2012})}.
+  (for a thorough analysis of this galaxy, see \citealt{gadottisanchezjanssen2012}).
   }
@@
   Inaccurate sky subtraction could be the reason why B+12 obtained a large estimate of the effective radius.
-  {\bf We could not obtain a successful 2D model that included a nuclear component, 
+  We could not obtain a successful 2D model that included a nuclear component, 
   therefore we opted for masking the nuclear region of the galaxy. 
-  This resulted in a significantly lower S\'ersic index, that we consider underestimated. }}
+  This resulted in a significantly lower S\'ersic index, that we consider underestimated. }
   \end{table}
@@
   An edge-on elliptical/lenticular galaxy. 
-  {\bf The identification of a disk is trivial due to its edge-on orientation, 
+  The identification of a disk is trivial due to its edge-on orientation, 
   although a visual inspection of the galaxy image is not enough to estabilish the radial extent of this disk. 
-  The ellipticity profile indicates that the disk is indeed intermediate-sized, i.e.~it does not dominate at large radii. }
+  The ellipticity profile indicates that the disk is indeed intermediate-sized, i.e.~it does not dominate at large radii. 
   Given the edge-on inclination of this disk, we model it with a low-$n$ S\'ersic profile. 
@@
   \tablecomments{L+14 obtained the smallest estimate of the effective radius because they oversubtracted a halo. 
-  {\bf In our 2D fit, we were not successful in modelling the nuclear disk and opted for masking the nuclear region of the galaxy. 
-  Such 2D model resulted in a significantly lower S\'ersic index, that we trust being underestimated. } 
+  In our 2D fit, we were not successful in modelling the nuclear disk and opted for masking the nuclear region of the galaxy. 
+  Such 2D model resulted in a significantly lower S\'ersic index, that we trust being underestimated.  
   }
@@
   produced by the transition from the S\'ersic bulge to the exponential disk. 
-  {\bf According to their analysis of the surface brightness profile of NGC 4459 (their Figure 14), 
+  According to their analysis of the surface brightness profile of NGC 4459 (their Figure 14), 
   the contribution from the disk completely overcomes that of the bulge beyond $R_{\rm maj} \gtrsim 60''$. 
@@
   According to our decomposition, the disk of NGC 4459 starts dominating beyond $R_{\rm maj} \gtrsim 100''$. 
-  The exponential function of our model seems to nicely match the ``second'' exponential decline identified by \cite{gutierrez2011}.  }
+  The exponential function of our model seems to nicely match the ``second'' exponential decline identified by \cite{gutierrez2011}.  
   We do not find evidence for any embedded components in our data.

### 2015-11-26 papers/MbhMsph/mm.tex
sex

@@
 In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
-decomposition of 66 galaxies, with directly measured black hole masses, $M_{\rm BH}$, 
-that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
+decomposition of 66 galaxies, with directly measured black hole masses, $M_{BH}$, 
+imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
 Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
-We present correlations between $M_{\rm BH}$ 
-and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
-and also stellar mass, $M_{\rm *,sph}$.
+We present correlations between $M_{BH}$ 
+and the host spheroid (and galaxy) luminosity, $L_{sph}$ (and $L_{gal}$), 
+and also stellar mass, $M_{*,sph}$.
 While most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies,
-our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
-and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
-The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
+our sample includes 17 spiral galaxies, half of which have $M_{BH}<10^7\rm~M_\odot$, 
+and allows us to better investigate the poorly studied low-mass end of the $M_{BH}~-~M_{*,sph}$ correlation.
+The bulges of early-type galaxies follow $M_{BH}~\propto~M_{*,sph}^{1.04~\pm~0.10}$  
 and define a tight 
-\emph{red sequence} with intrinsic scatter $\epsilon_{(M_{\rm BH}|M_{\rm *,sph})} = 0.43 \pm 0.06\rm~dex$ 
-and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$, 
-i.e.~a $\pm 2\sigma$ range of 0.1--5\%.
+\emph{red~sequence} with intrinsic scatter $\epsilon_{(M_{BH}|M_{*,sph})}~=~0.43~\pm~0.06\rm~dex$ 
+and a median $M_{BH}/M_{*,sph}$ ratio of $0.68~\pm~0.04\%$, 
+i.e.~a $\pm~2\sigma$ range of $0.1-5\%$.
 At the low-mass end, the bulges of late-type galaxies define a much steeper 
-\emph{blue sequence}, 
-with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$ and $M_{\rm BH}/M_{\rm *,sph}$ equal to $0.02\%$ at $M_{\rm BH} \approx 10^6~\rm M_\odot$, 
-indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
-We additionally report that: i) our S\'ersic galaxy sample follows $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, 
+\emph{blue~sequence}, 
+with $M_{BH}~\propto~M_{*,sph}^{2-3}$ and $M_{BH}/M_{*,sph}$ equal to $0.02\%$ at $M_{BH}~\approx~10^6\rm~M_\odot$. 
+%indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
+We additionally report that: i)~our S\'ersic galaxy sample follows $M_{BH}~\propto~M_{*,sph}^{1.48~\pm~0.20}$, 
 a less steep sequence than previously reported; 
-ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
-are not offset to lower $M_{\rm BH}$ from the correlation defined by the current bulge sample with $n_{\rm sph}>2$; 
-and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies 
--- once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
+ii)~bulges with S\'ersic index $n_{sph}<2$, argued by some to be pseudo-bulges, 
+are not offset to lower $M_{BH}$ from the correlation defined by the current bulge sample with $n_{sph}>2$; 
+and iii)~$L_{sph}$ and $L_{gal}$ correlate equally well with $M_{BH}$, in terms of intrinsic scatter, only for early-type 
+galaxies~--~once reasonable numbers of spiral galaxies are included, the correlation with $L_{sph}$ is better than that with $L_{gal}$.
 

### 2015-11-26 papers/ellicular/ellicular.tex
sex

@@
 obtained by dividing the image by a Gaussian-smoothed version of itself. 
+In the unsharp mask, the green circles indicate the position of the two brighter spots associated to the edge-on nuclear ring. 
 The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
@@
 \citealt{yildirim2015}), NGC 1271 \citep{walsh2015}, 
-NGC 1277 \citep{vandenbosch2012,yildirim2015} and NGC 1332 \citep{rusli2011}.
+NGC 1277 \citep{vandenbosch2012,yildirim2015,walsh2015n1277} and NGC 1332 \citep{rusli2011}.
 In addition to these, the elliptical galaxy NGC 4291 has also been claimed to be a $\sim$$3.6\sigma$ outlier 
@@
 and the stellar mass-to-light ratio obtained by \cite{walsh2015}. 
-For the galaxy NGC 1277, we use the black hole mass measurement obtained by \cite{vandenbosch2012} 
+For the galaxy NGC 1277, we use the black hole mass measurement obtained by \cite{walsh2015n1277} 
 and the stellar mass-to-light ratio obtained by \cite{martinnavarro2015}. 
+Note that for NGC 1277 we recover a spheroid stellar mass of $2.7 \times 10^{11}~\rm M_\odot$, 
+in agreement with the value of $\approx 1-2 \times 10^{11}~\rm M_\odot$ obtained by \cite{emsellem2013} 
+from his multi-Gaussian expansion models\footnote{In \cite{emsellem2013}, 
+readers will find a clever discussion of the problematics asociated with the definition and the identification 
+of the ``bulge'' component in a galaxy. }.  
 For the galaxy Mrk 1216, we use the upper limit on the black hole mass 

### 2015-11-26 papers/data_paper/arxiv/pdftoeps.sh

@@ -1,0 +1,75 @@
+convert comparison_all_mag_sph.eps    comparison_all_mag_sph.pdf
+convert comparison_all_mu_0.eps       comparison_all_mu_0.pdf
+convert comparison_all_mu_e.eps       comparison_all_mu_e.pdf
+convert comparison_all_n.eps	      comparison_all_n.pdf
+convert comparison_all_r_e.eps	      comparison_all_r_e.pdf
+convert comparison_mag.eps	      comparison_mag.pdf
+convert comparison_n.eps	      comparison_n.pdf
+convert comparison_r_e.eps	      comparison_r_e.pdf
+convert ic1459_1Dfit.eps	      ic1459_1Dfit.pdf
+convert ic2560_1Dfit.eps	      ic2560_1Dfit.pdf
+convert ic4296_1Dfit.eps	      ic4296_1Dfit.pdf
+convert m104_1Dfit.eps		      m104_1Dfit.pdf
+convert m105_1Dfit.eps		      m105_1Dfit.pdf
+convert m106_1Dfit.eps		      m106_1Dfit.pdf
+convert m31_1Dfit.eps		      m31_1Dfit.pdf
+convert m49_1Dfit.eps		      m49_1Dfit.pdf
+convert m59_1Dfit.eps		      m59_1Dfit.pdf
+convert m64_1Dfit.eps		      m64_1Dfit.pdf
+convert m81_1Dfit.eps		      m81_1Dfit.pdf
+convert m84_1Dfit.eps		      m84_1Dfit.pdf
+convert m87_1Dfit.eps		      m87_1Dfit.pdf
+convert m89_1Dfit.eps		      m89_1Dfit.pdf
+convert m94_1Dfit.eps		      m94_1Dfit.pdf
+convert m96_1Dfit.eps		      m96_1Dfit.pdf
+convert n0524_1Dfit.eps 	      n0524_1Dfit.pdf
+convert n0821_1Dfit.eps 	      n0821_1Dfit.pdf
+convert n1023_1Dfit.eps 	      n1023_1Dfit.pdf
+convert n1300_1Dfit.eps 	      n1300_1Dfit.pdf
+convert n1316_1Dfit.eps 	      n1316_1Dfit.pdf
+convert n1332_1Dfit.eps 	      n1332_1Dfit.pdf
[…]

### 2015-11-26 python_codes/paper_figures/ellicular/mm.py

@@ -140,7 +140,8 @@ def mbh_vs_mass_sph():
 	mass_sph_n1277 = 2.69*10**11
 	mass_sph_n1277_b = mass_sph_n1277/11.65*6	
 	mass_sph_n1277_old = 2.88*10**10
-	mbh_n1277 = 1.7*10**10
+	#mbh_n1277 = 1.7*10**10 # van den bosch 2012
+	mbh_n1277 = 4.9*10**9 # walsh+2015
 	ax.scatter([mass_sph_n1277], [mbh_n1277], marker=r'$\star$', s=500, color='red', **scatter_kwargs)
 	#ax.scatter([mass_sph_n1277_b], [mbh_n1277], marker=r'$\star$', s=100, color='red', **scatter_kwargs)
 	ax.scatter([mass_sph_n1277_old], [mbh_n1277], marker=r'$\star$', s=500, color='gray', **scatter_kwargs)
@@ -181,15 +182,15 @@ def mbh_vs_mass_sph():
 	
 	x0 = mass_sph[gal_id=='n1332']
 	y0 = mbh[gal_id=='n1332']
-	ax.text(x0*1.2, y0/1.3, 'N1332', size=12, color='red')
+	ax.text(x0*1.3, y0/1.3, 'N1332', size=12, color='red')
 	
 	x0 = mass_sph_n1277
 	y0 = mbh_n1277
-	ax.text(x0*1.2, y0/1.3, 'N1277', size=12, color='red')
+	ax.text(x0*1.3, y0/1.2, 'N1277', size=12, color='red')
 	
 	x0 = mass_sph_n1271
 	y0 = mbh_n1271
-	ax.text(x0*1.1, y0*1.3, 'N1271', size=12, color='red')
+	ax.text(x0/2.2, y0*1.0, 'N1271', size=12, color='red')
 	
 	x0 = mass_sph_m1216
 	y0 = mbh_m1216

### 2015-12-01 papers/mbhn/mbhn.tex
im in looove

@@
 
-\title{Supermassive black holes and their host spheroids \\ III. Mbh-n paper}
+\title{Supermassive black holes and their host spheroids \\ 
+III. A universal $M_{\rm BH} - n_{\rm sph}$ correlation }
 
-\author{G. A. D. Savorgnan\altaffilmark{1}}
+\author{Giulia A.~D.~Savorgnan\altaffilmark{1}}
 \affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
@@
 between the black hole mass and several galaxy structural parameters, 
-we performed state-of-the-art modelling for the largest sample of galaxies to date (Savorgnan \& Graham 2015a, hereafter \emph{Paper I}),  
+we performed state-of-the-art modelling for the largest sample of galaxies to date (\citealt{paperI}, hereafter \emph{Paper I}),  
 for which a dynamical measurement of the black hole mass was available.
@@
 given its superb capability to trace the stellar mass (\citealt{sheth2010}, and references therein). 
-In Savorgnan et al.~(2015, hereafter \emph{Paper II}) we examined the correlations between the black hole mass and 
+In \citeauthor{paperII} (\citeyear{paperII}, hereafter \emph{Paper II}) we examined the correlations between the black hole mass and 
 the total galaxy luminosity, the spheroid luminosity and the spheroid stellar mass. 
@@
 and large-scale disks, that encase the bulge and dominate the light at large radii.  
-Savorgnan \& Graham (2015b) demonstrate that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
+\cite{ellicular} demonstrate that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
 the luminosity of the spheroid is underestimated, 
@@
 the spheroid S\'ersic indices were estimated with a method that takes into account systematic errors. 
-This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by different studies 
+This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by other studies 
 with that obtained by us. 
@@
 The early-type bin includes the two galaxies classified as E/S0, 
-whereas the two galaxies classified as S0/Sp and the two galaxies classified as mergers are included in neither the early- nor the late-type bin.
+whereas the two galaxies classified as S0/Sp and the two galaxies classified as ``mergers'' are included in neither the early- nor the late-type bin.
 
@@
 but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
+\cite{tremaine2002} cautioned that 
+the BCES estimator becomes ineffective when the dataset contains at least one low-precision measurement -- 
+regardless of how many high-precision measurements are in the sample -- 
+and tends to be biased in case of low number statistics 
+or if the mean square of the uncertainties associated to the independent variable is comparable to 
+the variance of the distribution of the independent variable. 
+According to the results from the Monte Carlo Markov Chain simulations of \cite{tremaine2002} and \cite{novak2006}, 
+these problems can be overcome with the use of the modified FITEXY routine. 
+\cite{park2012} also concluded that the modified FITEXY routine performs better and returns less biased results than the BCES estimator, 
+and noted that the the modified FITEXY routine is computationally less intensive than the Bayesian technique {\tt linmix\_err}. 
+Given that at least one of our subsamples (the lenticular galaxies) has a small size 
+and that the uncertainties associated to $n_{\rm sph}$ are relatively large compared to the range in $n_{\rm sph}$ values for most of our subsamples, 
+we put more trust in the results obtained with the modified FITEXY routine 
+and throughout the text we quote only those. \\ 
 We report both symmetrical and nonsymmetrical linear regressions.  
@@
 the lenticular galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
-These two galaxies have therefore been excluded from the rest of the analysis. 
-{\bf quote fitexy results bcz more reliable than other 2 }
-%I should have mentioned that the linear regression code, BCES, from Akritas & Bershady (1996) can at times get the slope wrong.  
-%This occurs if the error bars on the velocity dispersion are too big relative to the range of velocity dispersions in one's sample (say >15%), 
-%or if the error bars on the velocity dispersion and black hole masses are not all roughly the same. 
-%That is, if some black hole masses have error bars of 50% while others have error bars of 5%, then we could be in trouble.
+These two galaxies have therefore been excluded from the rest of the analysis. \\
 
@@
 whereas the combination of lenticular and spiral galaxies do not. 
-Early-type galaxies follow $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$; 
-remarkably, this is exactly the same proportionality obtained by \cite{savorgnan2013} for elliptical galaxies only, 
-upon re-analyzing the dataset from \cite{grahamguzman2003}. 
-Late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence.
+According to the modified FITEXY routine, 
+early-type galaxies follow\footnote{Using the BCES estimator, 
+\cite{savorgnan2013} re-analyzed the dataset from \cite{grahamguzman2003} 
+and obtained $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$ for the elliptical galaxies only. 
+This result is in excellent agreement with the BCES linear regression obtained here for the early-type galaxies 
+($L_{\rm sph} \propto n_{\rm sph}^{3.89 \pm 0.42}$) 
+and, remarkably, it is exactly the same proportionality obtained here for the early-type galaxies with the modified FITEXY routine. } 
+$L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
+whereas late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence.
 
@@
 which prevented us from considering them as two separate sequences. 
-On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations 
-($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
-and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
+On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations. 
+%($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
+%and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
 Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
@@
 Using the results from the modified FITEXY routine, 
-we find that 
-early-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{3.58 \pm 0.27}$, 
-while late-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{4.55 \pm 0.66}$. 
+we know that the early-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{1.03 \pm 0.11}$ 
+and $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
+therefore we expect to find $M_{\rm BH} \propto n_{\rm sph}^{3.69 \pm 0.44}$; 
+this prediction is in excellent agreement with the observed slope of $3.58 \pm 0.27$ obtained here. 
+On the other hand, late-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{2.58 \pm 1.06}$ 
+and $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$, 
+from which one can predict $M_{\rm BH} \propto n_{\rm sph}^{3.72 \pm 2.03}$; 
+this is consistent with the observed slope of $4.55 \pm 0.66$. 
 The Bayesian estimator {\tt linmix\_err} returns consistent results: 
@@
 \begin{equation*}
-\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph}^{\rm maj} - 0.50 \bigr) . 
+\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph} - 0.50 \bigr) . 
 \end{equation*}
@@
 \tableline
-{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph}^{\rm maj} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
+{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol{\langle \log n_{\rm sph}^{\rm maj} \rangle}$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
 \tableline 
@@
 		       & BCES Bisector  	    & $-22.33 \pm 0.26$ & $-5.25 \pm 3.38$ & $0.18$ & $-$ & $1.14$ \\
-		       & mFITEXY Bisector	    & $-22.23 \pm 0.33$ & $-3.60 \pm 1.29$ & $0.18$ & $-$ & $0.92$ \\
+		       & {\bf mFITEXY Bisector}	    & $\boldsymbol{-22.23 \pm 0.33}$ & $\boldsymbol{-3.60 \pm 1.29}$ & $\boldsymbol{0.18}$ & $-$ & $\boldsymbol{0.92}$ \\
 		       & {\tt linmix\_err} Bisector & $-22.25 \pm 0.53$ & $-2.88 \pm 2.66$ & $0.18$ & $-$ & $0.84$ \\ [0.5em]
@@
 		       & BCES Bisector  	    & $-24.55 \pm 0.17$ & $-9.73 \pm 1.05$ & $0.64$ & $-$ & $1.14$ \\
-		       & mFITEXY Bisector	    & $-24.74 \pm 0.14$ & $-8.99 \pm 0.48$ & $0.64$ & $-$ & $1.06$ \\
+		       & mFITEXY Bisector	    & $\boldsymbol{-24.74 \pm 0.14}$ & $\boldsymbol{-8.99 \pm 0.48}$ & $\boldsymbol{0.64}$ & $-$ & $\boldsymbol{1.06}$ \\
 		       & {\tt linmix\_err} Bisector & $-24.72 \pm 0.17$ & $-8.66 \pm 0.63$ & $0.64$ & $-$ & $1.02$ \\ [0.5em]
@@
  			& BCES Bisector 	     & $8.14 \pm 0.07$ & $3.51 \pm 0.28$ & $0.50$ & $-$ & $0.61$ \\
- 			& mFITEXY Bisector	     & $8.15 \pm 0.06$ & $3.37 \pm 0.15$ & $0.50$ & $-$ & $0.59$ \\
+ 			& {\bf mFITEXY Bisector}     & $\boldsymbol{8.15 \pm 0.06}$ & $\boldsymbol{3.37 \pm 0.15}$ & $\boldsymbol{0.50}$ & $-$ & $\boldsymbol{0.59}$ \\
  			& {\tt linmix\_err} Bisector & $8.15 \pm 0.07$ & $3.32 \pm 0.18$ & $0.50$ & $-$ & $0.58$ \\ [0.5em]

### 2015-12-01 papers/data_paper/arxiv/pdftoeps.sh

@@ -1,75 +1,0 @@
-convert comparison_all_mag_sph.eps    comparison_all_mag_sph.pdf
-convert comparison_all_mu_0.eps       comparison_all_mu_0.pdf
-convert comparison_all_mu_e.eps       comparison_all_mu_e.pdf
-convert comparison_all_n.eps	      comparison_all_n.pdf
-convert comparison_all_r_e.eps	      comparison_all_r_e.pdf
-convert comparison_mag.eps	      comparison_mag.pdf
-convert comparison_n.eps	      comparison_n.pdf
-convert comparison_r_e.eps	      comparison_r_e.pdf
-convert ic1459_1Dfit.eps	      ic1459_1Dfit.pdf
-convert ic2560_1Dfit.eps	      ic2560_1Dfit.pdf
-convert ic4296_1Dfit.eps	      ic4296_1Dfit.pdf
-convert m104_1Dfit.eps		      m104_1Dfit.pdf
-convert m105_1Dfit.eps		      m105_1Dfit.pdf
-convert m106_1Dfit.eps		      m106_1Dfit.pdf
-convert m31_1Dfit.eps		      m31_1Dfit.pdf
-convert m49_1Dfit.eps		      m49_1Dfit.pdf
-convert m59_1Dfit.eps		      m59_1Dfit.pdf
-convert m64_1Dfit.eps		      m64_1Dfit.pdf
-convert m81_1Dfit.eps		      m81_1Dfit.pdf
-convert m84_1Dfit.eps		      m84_1Dfit.pdf
-convert m87_1Dfit.eps		      m87_1Dfit.pdf
-convert m89_1Dfit.eps		      m89_1Dfit.pdf
-convert m94_1Dfit.eps		      m94_1Dfit.pdf
-convert m96_1Dfit.eps		      m96_1Dfit.pdf
-convert n0524_1Dfit.eps 	      n0524_1Dfit.pdf
-convert n0821_1Dfit.eps 	      n0821_1Dfit.pdf
-convert n1023_1Dfit.eps 	      n1023_1Dfit.pdf
-convert n1300_1Dfit.eps 	      n1300_1Dfit.pdf
-convert n1316_1Dfit.eps 	      n1316_1Dfit.pdf
-convert n1332_1Dfit.eps 	      n1332_1Dfit.pdf
[…]

### 2015-12-02 papers/mbhn/mbhn.tex
g

@@
 Readers should refer to \emph{Paper I} for a more detailed discussion on this topic. }. 
+For this analysis, we elected to use the spheroid S\'ersic indices obtained from the decomposition of the one-dimensional 
+major-axis surface brightness profiles of our galaxies.  
 The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
@@
 Given that at least one of our subsamples (the lenticular galaxies) has a small size 
-and that the uncertainties associated to $n_{\rm sph}$ are relatively large compared to the range in $n_{\rm sph}$ values for most of our subsamples, 
+and that the uncertainties associated to $n_{\rm sph}$ are relatively large 
+compared to the range spanned by the $n_{\rm sph}$ values for most of our subsamples, 
 we put more trust in the results obtained with the modified FITEXY routine 
@@
 According to the modified FITEXY routine, 
-early-type galaxies follow\footnote{Using the BCES estimator, 
+early-type galaxies\footnote{Using the BCES estimator, 
 \cite{savorgnan2013} re-analyzed the dataset from \cite{grahamguzman2003} 
@@
 and, remarkably, it is exactly the same proportionality obtained here for the early-type galaxies with the modified FITEXY routine. } 
-$L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
+follow $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
 whereas late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence.
@@
 
-We have seen that the early- and late-type galaxies in the $M_{\rm BH} - n_{\rm sph}$ diagram can be fit with a single power-law, 
-whereas they follow two separate correlations in the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). 
-We now want to compare the amount of scatter among these two plots. 
-In Table \ref{tab:intsc} we summarize the values of the intrinsic scatter 
+We have seen that the early- and late-type galaxies in the $M_{\rm BH} - n_{\rm sph}$ diagram 
+can be fit (together) with a single power-law, 
+whereas they follow two different correlations in the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). 
+We now want to compare the amount of intrinsic scatter in these two plots. 
+In Table \ref{tab:intsc} we report the values of the intrinsic scatter 
 in the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams 

### 2015-12-03 papers/mbhn/mbhn.tex
pum

@@
 
-\shorttitle{Mbh-n paper}
+\shorttitle{A universal $M_{\rm BH} - n_{\rm sph}$ correlation}
 \shortauthors{Savorgnan}
@@
 with the mass of the central supermassive black hole, $M_{\rm BH}$. 
-The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known scaling relations: 
-the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$, 
-where $L_{\rm sph}$ indicates the galaxy's spheroid luminosity. 
-However, it is widely recognized that obtaining an accurate estimate of the spheroid S\'ersic index is a challenging task, 
-and -- not surprisingly -- some studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
+The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known scaling relations 
+involving the spheroid luminosity, $L_{\rm sph}$: 
+the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$ correlations.
+
+However, obtaining an accurate estimate of the spheroid S\'ersic index requires a careful modelling of the galaxy's light distribution 
+and some studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation.
+
 With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
@@
 in the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
-they reunite in a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
-with relatively small intrinsic scatter ($\epsilon_{(Y|X)} \simeq 0.25 \rm~dex$). 
+they reunite into a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
+with relatively small intrinsic scatter ($\epsilon_{(M_{\rm BH} | n_{\rm sph})} \simeq 0.25 \rm~dex$). 
 {\bf to be finished...}
@@
 Given the existence of the $L_{\rm sph} - n_{\rm sph}$ correlation 
-and the relation between the central black hole mass, $M_{\rm BH}$, and the spheroid luminosity (e.g.~\citealt{magorrian1998}), 
+and the relation between the central black hole mass, $M_{\rm BH}$, and the spheroid luminosity 
+(e.g.~\citealt{kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}), 
 an $M_{\rm BH} - n_{\rm sph}$ relation must exist. 
@@
 which prevented the recovery of a strong $M_{\rm BH} - n_{\rm sph}$ relation. \\
-Motivated by the need of more accurate galaxy decompositions to refine and re-investigate scaling relations 
+Motivated by the need for more accurate galaxy decompositions to refine and re-investigate scaling relations 
 between the black hole mass and several galaxy structural parameters, 
@@
 the lenticular galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
-These two galaxies have therefore been excluded from the rest of the analysis. \\
+These two galaxies have therefore been excluded from the rest of the analysis.
 
@@
 \section{Conclusions} 
+The S\'ersic index of a galaxy's spheroidal component, $n_{\rm sph}$, constitutes a direct measure 
+of its central radial concentration of stars. 
+After \cite{graham2001bulges} proved that the central black hole mass, $M_{\rm BH}$, 
+correlates with the stellar light concentration of a galaxy's spheroidal component, 
+\cite{grahamdriver2007} presented and analyzed for the first time a tight $M_{\rm BH} - n_{\rm sph}$ correlation 
+using a sample of 27 elliptical and disk galaxies for which they had performed photometric bulge/disk decomposition. 
+The $M_{\rm BH} - n_{\rm sph}$ correlation can be predicted from the combination of two well known scaling relations 
+involving the spheroid luminosity, $L_{\rm sph}$: 
+the $M_{\rm BH} - L_{\rm sph}$ (e.g.~\citealt{kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}) 
+and the $L_{\rm sph} - n_{\rm sph}$ (e.g.~\citealt{youngcurrie1994,jerjen2000,grahamguzman2003}). 
+However, upon independently attempting photometric multicomponent decompositions 
+for galaxy samples that were similar to that used by \cite{grahamdriver2007}, 
+three subsequent studies \citep{sani2011,vika2012,beifiori2012} failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ relation. 
+\cite{savorgnan2013} collected and compared the S\'ersic index measurements obtained by \cite{grahamdriver2007}, 
+\cite{sani2011}, \cite{vika2012} and \cite{beifiori2012}, 
+and argued that the discrepancies were due to inaccurate galaxy decompositions. \\
+Moved by a urgent need to re-investigate and refine several black hole mass scaling relations, 
+we performed state-of-the-art photometric multicomponent decompositions 
+(i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, depleted core, etc.) 
+for 66 galaxies with a dynamical measurement of their black hole mass (\emph{Paper I}). 
+We carefully measured the S\'ersic index of each galaxy's spheroidal component 
+and estimated its associated uncertainty with a method that takes into account statistical and systematic errors. 
+Our analysis shows that early- (elliptical + lenticular) and late-type (spiral) galaxies define two different correlations 
+in the $L_{\rm sph} - n_{\rm sph}$ diagram, 
+whereas they reunite in a single sequence in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
+With the current dataset, we measured an amount of intrinsic scatter in the $M_{\rm BH} - n_{\rm sph}$ diagram systematically smaller, 
+but still consistent within the errors, with that observed in the the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). \\ 
+%Although we refrain from the conclusion that the $M_{\rm BH} - n_{\rm sph}$ relation is more fundamental than the $M_{\rm BH} - L_{\rm sph}$, 
+Our results suggest that the black hole mass is intimately connected to the spheroid central concentration of stars, 
+which reflects the inner gradient of the spheroid gravitational potential. 
+Besides conferring the spheroid S\'ersic index a predictive power to infer the black hole mass 
+from a galaxy's image only (even photometrically uncalibrated), 
+the $M_{\rm BH} - n_{\rm sph}$ correlation should become a fundamental ingredient in semi-analytic models and simulations of galaxy formation.
 
@@
 \acknowledgments
-kkkkk
+GS warmly thanks Alister Graham and Carlo Nipoti for useful discussion. 
+%We also thank the anonymous referee for useful comments and suggestions. 
+This research was supported by Australian Research Council funding through grants
+DP110103509 and FT110100263.
+This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
+on-board the Spitzer Space Telescope, 
+which is operated by the Jet Propulsion Laboratory, 
+California Institute of Technology under a contract with NASA.
+This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
+which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
+under contract with the National Aeronautics and Space Administration. 
+We acknowledge the usage of the HyperLeda database (\url{http://leda.univ-lyon1.fr}).
+The BCES routine \citep{akritasbershady1996} was run via the python module 
+written by Rodrigo Nemmen \citep{nemmen2012}, which is available at \url{https://github.com/rsnemmen/BCES}.
 

### 2015-12-04 papers/mbhn/mbhn.tex
friday stereosonics

@@
 \title{Supermassive black holes and their host spheroids \\ 
-III. A universal $M_{\rm BH} - n_{\rm sph}$ correlation }
+III. A universal $M_{\rm BH} - \lowercase{n_{\rm sph}}$ correlation }
 
@@
 the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$ correlations. 
-
-However, obtaining an accurate estimate of the spheroid S\'ersic index requires a careful modelling of the galaxy's light distribution 
+Obtaining an accurate estimate of the spheroid S\'ersic index requires a careful modelling of a galaxy's light distribution 
 and some studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
-
 With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
@@
 with relatively small intrinsic scatter ($\epsilon_{(M_{\rm BH} | n_{\rm sph})} \simeq 0.25 \rm~dex$). 
-{\bf to be finished...}
+The black hole mass is therefore closely related to the spheroid central concentration of stars, 
+which mirrors the inner gradient of the spheroid gravitational potential. 
 \end{abstract}
 
-\keywords{keywords}
+\keywords{black hole physics; galaxies: bulges; galaxies: elliptical and lenticular, cD; galaxies: evolution; galaxies: structure}
 
@@
 \begin{equation*}
-I(R; I_{\rm e},R_{\rm e},n) = I_{\rm e} \exp \biggl \{ -b_{\rm n} \biggl [ \Bigl (\frac{R}{R_{\rm e}} \bigr )^{1/n} -1 \biggr ] \biggr \}, 
+I(R; I_{\rm e},R_{\rm e},n) = I_{\rm e} \exp \biggl \{ -b_{\rm n} \biggl [ \biggl (\frac{R}{R_{\rm e}} \biggr )^{1/n} -1 \biggr ] \biggr \}, 
 \end{equation*}
@@
 the S\'ersic index $n$ is the parameter that regulates the curvature of the radial light profile, 
-and $b_{\rm n}$ is a constant defined in terms of the S\'ersic index $n$ (see \citealt{grahamdriver2005}, and references therein). 
+and $b_{\rm n}$ is a constant defined in terms of the S\'ersic index (see \citealt{grahamdriver2005}, and references therein). 
 A large S\'ersic index corresponds to a steep inner profile and a shallow outer profile, 
@@
 Remarkably, \cite{savorgnan2013} repeated their analysis upon excluding the S\'ersic index measurements of \cite{grahamdriver2007} 
-and still regained a significant $M_{\rm BH} - n_{\rm sph}$ relation. 
+and still regained a significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
 This was suggesting that the individual galaxy decompositions of \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} were not accurate, 
@@
 Motivated by the need for more accurate galaxy decompositions to refine and re-investigate scaling relations 
-between the black hole mass and several galaxy structural parameters, 
-we performed state-of-the-art modelling for the largest sample of galaxies to date (\citealt{paperI}, hereafter \emph{Paper I}),  
+between the black hole mass and several host spheroid structural parameters, 
+we performed state-of-the-art modelling for the largest sample of galaxies to date (\citealt{paperI}, hereafter \emph{Paper I})  
 for which a dynamical measurement of the black hole mass was available.
@@
 Readers should refer to \emph{Paper I} for a more detailed discussion on this topic. }. 
-For this analysis, we elected to use the spheroid S\'ersic indices obtained from the decomposition of the one-dimensional 
+For the present analysis, we elected to use the spheroid S\'ersic indices obtained from the decomposition of the one-dimensional 
 major-axis surface brightness profiles of our galaxies.  
@@
 regardless of how many high-precision measurements are in the sample -- 
-and tends to be biased in case of low number statistics 
+and tends to be biased in case of low number statistics, 
 or if the mean square of the uncertainties associated to the independent variable is comparable to 
@@
 therefore we expect to find $M_{\rm BH} \propto n_{\rm sph}^{3.69 \pm 0.44}$; 
-this prediction is in excellent agreement with the observed slope of $3.58 \pm 0.27$ obtained here. 
+this prediction is in excellent agreement with the observed log-slope of $3.58 \pm 0.27$ obtained here. 
 On the other hand, late-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{2.58 \pm 1.06}$ 
@@
 from which one can predict $M_{\rm BH} \propto n_{\rm sph}^{3.72 \pm 2.03}$; 
-this is consistent with the observed slope of $4.55 \pm 0.66$. 
+this is consistent with the observed log-slope of $4.55 \pm 0.66$. 
 The Bayesian estimator {\tt linmix\_err} returns consistent results: 
@@
 \tablecomments{For each subsample, we indicate $\langle \log n_{\rm sph} \rangle$, its average value of spheroid S\'ersic index. 
-In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
+In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $M_{\rm BH}$ direction. 
 The lenticular galaxies NGC 0524 and NGC 3998 were excluded from the linear regression analysis (see Section \ref{sec:anal}). 
@@
 written by Rodrigo Nemmen \citep{nemmen2012}, which is available at \url{https://github.com/rsnemmen/BCES}.
+The modified FITEXY linear regressions were performed using the IDL routine MPFITEXY \citep{williams2010}, 
+which is available at \url{http://purl.org/mike/mpfitexy}. 
+The MPFITEXY routine depends on the MPFIT package \citep{markwardt2009}.
 

### 2015-12-17 papers/mbhn/ApJ_Submission/mbhn.tex
thu

--- 2015-12-04 papers/mbhn/mbhn.tex
@@
 
-\shorttitle{A universal $M_{\rm BH} - n_{\rm sph}$ correlation}
+\shorttitle{The $M_{\rm BH} - n_{\rm sph}$ correlation}
 \shortauthors{Savorgnan}
@@
 \title{Supermassive black holes and their host spheroids \\ 
-III. A universal $M_{\rm BH} - \lowercase{n_{\rm sph}}$ correlation }
+III. The $M_{\rm BH} - \lowercase{n_{\rm sph}}$ correlation }
 
@@
 involving the spheroid luminosity, $L_{\rm sph}$: 
-the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$ correlations. 
+the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$. 
 Obtaining an accurate estimate of the spheroid S\'ersic index requires a careful modelling of a galaxy's light distribution 
@@
 that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
-In this paper, the third of its series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
+In this paper, the third of this series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
 While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
@@
 with relatively small intrinsic scatter ($\epsilon_{(M_{\rm BH} | n_{\rm sph})} \simeq 0.25 \rm~dex$). 
-The black hole mass is therefore closely related to the spheroid central concentration of stars, 
+The black hole mass appears to be closely related to the spheroid central concentration of stars, 
 which mirrors the inner gradient of the spheroid gravitational potential. 
@@
 The empirical \cite{sersic1963,sersic1968} $R^{1/n}$ model has been demonstrated to provide adequate description 
-of the light distribution of the stellar spheroidal\footnote{Throughout the text, we use the term ``spheroid'' to designate 
-either a diskless elliptical galaxy or the bulge component of a disk galaxy, 
-with no attempt at distinguishing between classical bulges and disk-like pseudo-bulges. } and disk components of galaxies 
+of the light distribution of the stellar spheroidal\footnote{Throughout the text, we use the term ``spheroid'' to indicate 
+either a disk-less elliptical galaxy or the bulge component of a disk galaxy;  
+we do not attempt at distinguishing between classical bulges and disk-like pseudo-bulges. } and disk components of galaxies 
 (e.g.~\citealt{caon1993,andredakis1995,iodice1997,iodice1999,seigar1998,khosroshahi2000}), 
 yet its physical origin has remained unexplained for decades. 
-The S\'ersic model parametrizes the intensity of light $I$ as a function of the projected galactic radius $R$ such that
+The S\'ersic model parameterizes the intensity of light $I$ as a function of the projected galactic radius $R$ such that
 \begin{equation*}
@@
 for samples of galaxies similar to that used by \cite{grahamdriver2007}, 
-but they unexpectedly failed to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation. 
+but they failed to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation. 
 This issue was tackled by \cite{savorgnan2013}, who collected the S\'ersic index measurements published by 
 \cite{grahamdriver2007}, \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} for a sample of 54 galaxies, 
-and showed that, by rejecting the most discrepant measurements and averaging the remaning ones, 
+and showed that, by rejecting the most discrepant measurements and averaging the remaining ones, 
 a strong $M_{\rm BH} - n_{\rm sph}$ relation was retrieved. 
@@
 the total galaxy luminosity, the spheroid luminosity and the spheroid stellar mass. 
-Here we focus on the $M_{\rm BH} - n_{\rm sph}$ relation. \\
-This paper (\emph{Paper III}) is structured as follows...
+Here we focus on the $M_{\rm BH} - n_{\rm sph}$ relation.
 
@@
 in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
-to estabilish the radial extent of these disks, 
+to establish the radial extent of these disks, 
 which in most cases is not obvious from a visual inspection of the galaxy images. 
@@
 Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram using only our high-quality dataset. 
-Spheroid luminositites and S\'ersic indices were obtained from accurate multicomponent decompositions,  
+Our spheroid luminosities and S\'ersic indices were obtained from accurate multicomponent decompositions,  
 performed in a consistent manner using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
+\includegraphics[width=\columnwidth]{mag_vs_n_maj.pdf}
 \caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
@@
 The Bayesian estimator {\tt linmix\_err} returns consistent results: 
-a slope of $3.44 \pm 0.33$ for the early-type galaxies 
-and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
-In both cases, the values of the slope and intercept for the early- and late-type galaxies 
+a log-slope of $3.44 \pm 0.33$ for the early-type galaxies 
+and a log-slope of $4.12 \pm 1.07$ for the late-type galaxies. 
+Regardless of the linear regression routine used, 
+the values of the slope and intercept for the early- and late-type galaxies 
 are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
@@
 at the results obtained with the modified FITEXY routine, 
-the values of the intrisic scatter are only marginally consistent with each other, 
+the values of the intrinsic scatter are only marginally consistent with each other, 
 but looking at the results obtained with the Bayesian estimator {\tt linmix\_err}, 
-the values of the intrisic scatter are fully consistent with each other. } 
+the values of the intrinsic scatter are fully consistent with each other. } 
 with that of the $M_{\rm BH} - L_{\rm sph}$ relation (within their $1\sigma$ uncertainties). 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
+\includegraphics[width=\columnwidth]{mbh_vs_n_maj.pdf}
 \caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
@@
   \centering
-  \caption{Intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ relations.}
+  \caption{Intrinsic scatter $\epsilon$ of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ relations.}
   \begin{tabular}{llcc}

### 2016-02-24 papers/mbhn/replytoreferee.txt
referee report mbhn

I thank the referee for a prompt and insightful review that helped improve the quality of the manuscript. 
I have modified the manuscript as suggested by the referee, and highlighted the changes in boldface. 
Below is my response to the referee report.

Figures 1 and 2 have been modified to show the insets with error bars on the same scale as the main plots. 
I wish to maintain the fancy symbols for continuity with Paper II and because they allow to identify 
the two lenticular galaxies excluded from the linear regression analysis (orange crosses) and
the four galaxies classified as E/S0 or S0/Sp. 
If I was to show only the four-colour error bars, these six data points could not be easily located. 
I tried to combine fancy symbols and error bars in a single panel, but the result was a messy and 
too "crowded" plot. 
Hopefully a two-panel figure - with separate symbols and error bars - is a good compromise.

The linear regression for the "all" sample is now shown with a black dotted line in both Figures 1 and 2. 
Indeed, the Figures are now more informative. 
Looking at the bottom panel of Figure 1, one can notice that the blue and orange error bars 
span basically the same range in spheroid magnitude and Sérsic index, but they are offset from each other. 
In effect, the L-n linear regression for all galaxies seems to almost exactly define a separation line 
in between lenticular and spiral galaxies. 
Going beyond a "by eye" assessment, the linear regression analysis, which takes into account the error bars, 
confirms that the slopes of the correlations for early- and late-type galaxies are not consistent with each other
within their 1 sigma uncertainties. 
This is already a quantitative indication that early- and late-type galaxies define two separate L-n sequences, 
which justifies the use of a 4-parameter model, rather than a 2-parameter one, to describe the L-n diagram. 
I've also explored an independent method, drawn from Information Theory, to measure the relative quality of 
a 2-parameter and a 4-parameter model for the given L-n dataset. 
The Akaike Information Criterion rewards the goodness of a fit and penalises the number of parameter used 
in the model, therefore it provides a means for model selection. 
The Akaike Information Criterion test confirms that a 4-parameter model is preferred over a 2-parameter model 
to describe the L-n diagram, whereas a 2-parameter model is preferred over a 4-parameter model to describe 
the Mbh-n dataset. 
Details about the Akaike Information Criterion are given in the manuscript (Section 3.1).

Indeed, I agree with the referee's concern about the uncertain and sometimes misleading definition of "bulge" 
adopted in the literature, which led us to prefer the use of a more general term such as "spheroid" as opposed 
to disk, although we recognise that "spheroid" might not be fully appropriate to describe disk-like pseudobulges. 
In Papers I, II and III, as long as in Savorgnan & Graham (2016, MNRAS, 457, 320), we adopted and tried to be 
consistent with a point of view similar to that of the ATLAS3D team: local galaxies display a continuous distribution 
of spheroid-to-total flux ratios (e.g. Figure 2 of Cappellari et al. 2011), going from disc-less, "pure" 
elliptical galaxies (slow rotators) to disc-dominated lenticular and spiral galaxies (fast rotators). 
In Paper I, we consistently modelled each galaxy's spheroid with a Sérsic profile. Our identification of the spheroidal 
component can be classified as a "photometric" identification: we associated the spheroidal component with the central 
excess of light after the subtraction of discs, bars, nuclei, rings and disc-like components.

Since it was first presented in 2007 by Graham & Driver, the Mbh-n correlation did not receive enough attention 
over the following years. Vika et al. and Beifiori et al. failed to recover the correlation, whereas Sani et al. 
and Lasker et al. didn't even explore the Mbh-n diagram (and we checked that no strong Mbh-n correlation 
could be obtained using their datasets). 
In addition, none of these works explored the L-n diagram, whose more recent analysis was done by us (to our best knowledge) 
in Savorgnan et al. (2013) using the Graham & Guzman (2003) and Graham & Worley (2008) (outdated) datasets. 
For this reason, we felt that joining the analysis of the Mbh-n correlation with that of the more popular Mbh-L 
correlation would not have given enough credit to the former. 
At present, no simulations of black hole-galaxy coevolution take into account the observed Mbh-n correlation. 
A separate analysis and a dedicated manuscript would therefore give more visibility to this relation.
A separate analysis is also motivated by the following fact. The three linear regression routines 
(BCES, mFITEXY and linmix_err) all gave consistent results for the Mbh-L correlation. 
However, as explained in Section 3 of the manuscript, the modified FITEXY routine performs better than the BCES and 
linmix_err codes when it comes to the analysis of our L-n and Mbh-n datasets. 
To avoid confusion, we preferred to keep the analyses of the Mbh-L and Mbh-n relations separate.

### 2016-02-24 papers/mbhn/mbhn.tex
referee report mbhn

@@
 \begin{abstract}
-The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution of stellar spheroidal and disk components, 
+The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution 
+of stellar spheroidal and disk components, 
 with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
-The S\'ersic index of a galaxy's spheroidal component, $n_{\rm sph}$, has been shown to tightly correlate 
-with the mass of the central supermassive black hole, $M_{\rm BH}$. 
-The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known scaling relations 
-involving the spheroid luminosity, $L_{\rm sph}$: 
-the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$. 
+The S\'ersic index of a galaxy's spheroidal component, $n_{sph}$, has been shown to tightly correlate 
+with the mass of the central supermassive black hole, $M_{BH}$. 
+The $M_{BH}-n_{sph}$ correlation is also expected from other two well known scaling relations 
+involving the spheroid luminosity, $L_{sph}$: 
+the $L_{sph}-n_{sph}$ and the $M_{BH}-L_{sph}$. 
 Obtaining an accurate estimate of the spheroid S\'ersic index requires a careful modelling of a galaxy's light distribution 
-and some studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
-With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
+and some studies have failed to recover a statistically significant $M_{BH}-n_{sph}$ correlation. 
+With the aim of re-investigating the $M_{BH}-n_{sph}$ 
 and other black hole mass scaling relations, 
@@
 that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
-In this paper, the third of this series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
+In this paper, the third of this series, we present an analysis of the $L_{sph}-n_{sph}$ 
+and $M_{BH}-n_{sph}$ diagrams. 
 While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
-in the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
-they reunite into a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
-with relatively small intrinsic scatter ($\epsilon_{(M_{\rm BH} | n_{\rm sph})} \simeq 0.25 \rm~dex$). 
+in the $L_{sph}-n_{sph}$ and $M_{BH}-L_{sph}$ diagrams, 
+they reunite into a single $M_{BH} \propto n_{sph}^{3.39 \pm 0.15}$ sequence
+with relatively small intrinsic scatter ($\epsilon \simeq 0.25 \rm~dex$). 
 The black hole mass appears to be closely related to the spheroid central concentration of stars, 
@@
 %{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
-Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram using only our high-quality dataset. 
+Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram (Figure \ref{fig:magn}) using only our high-quality dataset. 
 Our spheroid luminosities and S\'ersic indices were obtained from accurate multicomponent decompositions,  
@@
 follow $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
-whereas late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence.
+whereas late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence. \\
+{\bf Because the log-slopes of the correlations for early- and late-type galaxies are not consistent with each other 
+within their $1\sigma$ uncertainties, 
+our quantitative linear regression analysis suggests that 
+the $L_{\rm sph} - n_{\rm sph}$ diagram is better described with a four-parameter model 
+(two separate power-laws) 
+rather than with a two-parameter model (single power-law). 
+In addition, the relative quality of these two statistical models can be independently assessed 
+using the Akaike Information Criterion ($AIC$, \citealt{akaike1974}). 
+$AIC$ is a trade-off between the statistical significance of a fit and the complexity of the model used. 
+It benefits from the goodness of a fit, 
+but at the same time is also penalized by the number of parameters of the model, 
+hence it discourages overfitting. 
+The $AICc$ is a variation of the $AIC$ that takes into account a correction for finite sample sizes: 
+\begin{equation}
+AICc = 2k - 2 \ln(\mathcal{L}) + \frac{2k (k+1)}{n-k-1} ,
+\end{equation}
+where $k$ is the number of parameter of the model, 
+$n$ is the sample size, 
+and $\mathcal{L}$ is the maximum value of the likelihood function for the model. 
+Within a set of candidate models for a given dataset, 
+the best model has the smallest $AICc$ value. 
+Using our $L_{\rm sph} - n_{\rm sph}$ dataset, 
+the $AICc$ value for a double power-law model is a factor of $3/4$ smaller 
+than the $AICc$ value for a single power-law model. }
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
-\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
+\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mag_vs_n_maj.pdf}
+\caption{\bf Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
 measured along the galaxy major-axis. 
-Symbols are coded according to the galaxy morphological type (see legend).
+The top and bottom panels show the data points and their error bars, respectively.  
+Symbols are coded according to the galaxy morphological type (see legend in the top panel).
 The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
 (see Section \ref{sec:anal}). 
-The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
+The black dotted line is the FITEXY bisector linear regression for all ($64$) galaxies, 
+with the gray shaded area denoting its $1\sigma$ uncertainty. 
+The red dashed line is the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
 with the red shaded area denoting its $1\sigma$ uncertainty. 
-The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
+The shallower blue solid line is the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
 with the blue shaded area denoting its $1\sigma$ uncertainty. 
-The inset panel shows the error bars associated to each data point,  
-where the error bars have the same color coding as the symbols in the main figure. 
+The error bars in the bottom panel have the same color coding as the symbols in the top panel. 
 }
@@
 are fully consistent with each other within their $1\sigma$ uncertainties. }.
-Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
-i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
+Our analysis shows that the early- and late-type galaxies do not follow two separate trends 
+in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
+i.e.~we do not identify any significant substructure based on the galaxy morphological type. 
+{\bf The $AICc$ value for a single power-law model is a factor of $2/3$ smaller 
+than the $AICc$ value for a double power-law model. } \\
 The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
-\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
+\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mbh_vs_n_maj.pdf}
+\caption{\bf Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
+The top and bottom panels show the data points and their error bars, respectively.  
 Symbols are coded according to the galaxy morphological type (see legend). 
@@
 (see Section \ref{sec:anal}). 
-The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
+The black dotted line is the FITEXY bisector linear regression for all ($64$) galaxies, 
+with the gray shaded area denoting its $1\sigma$ uncertainty. 
+The red dashed line is the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
 with the red shaded area denoting its $1\sigma$ uncertainty. 
-The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
+The blue solid line is the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
 with the blue shaded area denoting its $1\sigma$ uncertainty. 
 The linear regressions for early- and late-type galaxies are consistent with each other within their $1\sigma$ uncertainties.  
-The inset panel shows the error bars associated to each data point,  
-where the error bars have the same color coding as the symbols in the main figure. 
+The error bars in the bottom panel have the same color coding as the symbols in the top panel. 
 }
@@
 \acknowledgments
-GS warmly thanks Alister Graham and Carlo Nipoti for useful discussion. 
-%We also thank the anonymous referee for useful comments and suggestions. 
+GS warmly thanks Chris Blake, Alister Graham and Carlo Nipoti for useful discussion. 
+We also thank the anonymous referee for useful comments and suggestions. 
 This research was supported by Australian Research Council funding through grants

### 2016-02-24 python_codes/instruments/markers/markers_linlog.py

@@ -18,9 +18,9 @@ def spiral(ax, color, x0, y0, size_x, size_y):
 	x = size_x*1.1*np.cos(t)
 	y = size_y*1*np.sin(t)
 	
-	ax.plot(10**(x0+x1),(y0+y1), color=color, lw=2, **scatter_kwargs2)
-	ax.plot(10**(x0+x2),(y0+y2), color=color, lw=2, **scatter_kwargs2)
-	ax.plot(10**(x0+x),(y0+y), color=color, lw=2, **scatter_kwargs2)
+	ax.plot(10**(x0+x1),(y0+y1), color=color, lw=1, **scatter_kwargs2)
+	ax.plot(10**(x0+x2),(y0+y2), color=color, lw=1, **scatter_kwargs2)
+	ax.plot(10**(x0+x),(y0+y), color=color, lw=1, **scatter_kwargs2)
 	ax.fill_between(10**(x0+x), (y0+0), (y0+y), edgecolor='', facecolor=color, **scatter_kwargs2)
 	
 	
@@ -31,7 +31,7 @@ def lenticular(ax, color, x0, y0, size_x, size_y):
 	y = size_y*1.5*np.sin(t)	
 	
 	ax.fill_between(10**(x0+x), (y0+0), (y0+y), edgecolor='', facecolor=color, **scatter_kwargs)
-	ax.plot([10**(x0-2*size_x),10**(x0+2*size_x)],[(y0),(y0)], color=color, lw=3, **scatter_kwargs)
+	ax.plot([10**(x0-2*size_x),10**(x0+2*size_x)],[(y0),(y0)], color=color, lw=2, **scatter_kwargs)
 
 
 def elliptical(ax, color, x0, y0, size_x, size_y):

### 2016-02-26 thesis/declaration.tex
added thesis

\chapter*{Declaration}

I herewith declare that this thesis contains no material that has been accepted 
for the award to the candidate of any other degree or diploma. 
To the best of my knowledge, 
this thesis contains no material previously published or written by another author, 
except where due reference is made.
The work presented in this thesis has been carried out 
in the Centre for Astrophysics \& Supercomputing 
at Swinburne University of Technology between September 2012 and April 2016. 
The content of the chapters listed below has appeared in refereed journals.

\begin{itemize}

\item Chapter \ref{ch:recov-mn} has been published as 
``The supermassive black hole mass -- S\'ersic index relations for bulges and elliptical galaxies''
in 2013, MNRAS, 434, 387, by Giulia A.~D.~Savorgnan et al.

\item Chapter \ref{ch:galviv} has been published as 
``Supermassive black holes and their host spheroids I. Disassembling galaxies'' 
in 2016, ApJS, 222, 10, by Giulia A.~D.~Savorgnan \& Alister W.~Graham.

\item Chapter \ref{ch:mm} has been published as 
``Supermassive black holes and their host spheroids 
II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram''
in 2016, ApJ, 817, 21, by Giulia A.~D.~Savorgnan et al.

\item Chapter \ref{ch:msigma} has been published as 
``Overmassive black holes in the $M_{\rm BH} - \sigma$ diagram do not belong to over (dry) merged galaxies''
in 2015, MNRAS, 446, 2330, by Giulia A.~D.~Savorgnan \& Alister W.~Graham.

\item Chapter \ref{ch:ellic} has been published as 
``Explaining the reportedly over-massive black holes in early-type galaxies with intermediate-scale discs'' 
in 2016, MNRAS, 457, 320, by Giulia A.~D.~Savorgnan \& Alister W.~Graham.

\end{itemize}

### 2016-02-26 thesis/ellicular.tex
added thesis

\chapter{Monster black holes in compact massive spheroids with intermediate scale discs}
\label{ch:ellic}

This Chapter brings together three ``hot topics'' of today's astrophysical debate, 
that is, over-massive black holes in the $M_{\rm BH} - L_{\rm sph}$ diagram, 
the variety of intrisic angular momentum radial profiles in local early-type galaxies, 
and the evolution of the mass-size relationship from $z=2$ to $z=0$. 
While an overview about the $M_{\rm BH} - L_{\rm sph}$ outliers was given in Section \ref{sec:monsters}, 
the second topic was only briefly touched in Section \ref{sec:photokin}, 
and no mention of the mass-size relation was made in Chapter \ref{ch:intro} 
because not immediately related to SMBHs. 
Therefore, a more extensive introduction for these last two points is given here. \\

\citet{daddi2005} reported on the observation of seven quiescent early-type galaxies 
at $z=1.4-2.5$ with stellar masses $\gtrsim 10^{11} \rm~M_\odot$ 
and effective radii significantly smaller than those of local couterparts. 
\citet{trujillo2006} analysed ten massive $\approx 5 \times 10^{11} \rm~M_\odot$ galaxies at $z=1.2-1.7$ 
and measured for them sizes a factor of 4 smaller than $z=0$ galaxies with similar stellar masses. 
From this, they concluded that the observed rapid evolution of the structural properties of massive quiescent galaxies 
over the last $\approx 10 \rm~Gyr$ 
cannot be reconciled with a monolithic formation scenario. 
\citet{kriek2008} and \citet{vandokkum2008} found that nearly half of $z \approx 2$ 
massive ($\approx 10^{11} \rm~M_\odot$) galaxies 
have old stellar populations, negligible star formation, and sizes a factor of 5 smaller than 
those of the local descendants.

progenitor bias
intermediate scale disc galaxies (arnold)

compact massive spheroids

n1277 paper

The remainder of this chapter comprises the published version of the paper 
``Explaining the reportedly overmassive black holes in early-type galaxies with intermediate-scale discs'' 
by G.~A.~D.~Savorgnan \& A.~W.~Graham,  
as it appears in Volume 457 of \emph{Monthly Notices of the Royal Astronomical Society}.

\includepdf[pages={1-8}]{MNRAS2016.pdf}

### 2016-02-26 thesis/galaxyvivisection.tex
added thesis

\chapter{Galaxy Vivisection}
\label{ch:galviv}

The preliminary investigation presented in Chapter \ref{ch:recov-mn} \citep{savorgnan2013} 
demonstrated the need for a new, systematic and homogeneous study 
aimed at obtaining more accurate galaxy decompositions 
and refining our knowledge about black hole mass scaling relations. 
In 2013, I visited A.~Marconi, E.~Sani, and L.~K.~Hunt (co-authors of the paper \citealt{sani2011}) 
in Arcetri (Florence) for a short collaboration, 
during which I was shown their 2D galaxy decomposition method using {\tt GALFIT3} \citep{peng2010}. 
This helped set the basis for the development of my own galaxy decomposition strategy. \\

Building on the catalog of \cite{grahamscott2013} 
with the addition of some new black hole mass measurements later published by \cite{rusli2013bhmassesDM}, 
I assembled my initial sample of 75 galaxies. 
For the imaging data, 
I chose to use \emph{Spitzer} archival observations at $3.6~\mu \rm m$ for three main reasons: 
(\emph{i}) the $3.6~\mu \rm m$ passband is currently the best proxy for the stellar mass 
(\citealt{sheth2010}, and references therein); 
(\emph{ii}) archival observations were publicly available for the majority of the galaxies in my initial sample; 
and (\emph{iii}) within a \emph{Spitzer} observation set of a galaxy, 
roughly half of the telescope pointings are dedicated to the imaging of the surrounding sky, 
ensuring a robust background determination during the data reduction process\footnote{These three points put together 
led me to prefer \emph{Spitzer} rather than \emph{HST} observations, 
albeit the lower spatial resolution. }. 
While for each galaxy \cite{sani2011} used only one set of \emph{Spitzer} astronomical observations, 
I downloaded all the publicly available observation sets and merged them into a single mosaic with higher signal-to-noise. 
I paid particular attention to (and invested a consistent amount of time into) the characterisation of the 
2D Point Spread Function (PSF), following the expert advice of C.~Peng. \\

Being aware of the importance of choosing the correct galaxy model 
in order to obtain reliable and meaningful structural parameters, 
I embraced the approach of \cite{laurikainen2005} 
and planned \emph{a priori} identification of the number and nature of the structural components in each galaxy. 
Given the lack of reference literature about advantages and disadvantages 
related to 1D and 2D decomposition techniques, 
I decided to experiment with both. \\

I wrote substantial software to perform 1D decomposition of surface brightness profiles. 
This code is written in {\tt Python} and is based on the Levenberg-Marquardt minimisation routine 
of the {\tt scipy.optimize} module. 
This software allows the user to build a galaxy model with any arbitrary number of analytical functions 
(S\'ersic, exponential, Gaussian, Ferrer, etc.). 
Because the code is written in an object-oriented fashion, 
it is particularly easy to implement any new analytical function into it. \\

For the 2D analysis, I experimented with the codes {\tt GALFIT3} \citep{peng2010} 
and {\tt Imfit} \citep{imfit}. 
After checking that both codes give consistent results, 
I preferred the more script-oriented {\tt Imfit} over {\tt GALFIT3}. \\

The NASA/IPAC Extragalactic Database (NED) has been an invaluable resource 
for the structural analysis of galaxies. 
NED lists all the literature references contained in the SAO/NASA Astrophysics Data System (ADS) 
which mentioned a particular galaxy. 
Thanks to this functionality, 
I was able to search for previous photometric and kinematic analyses, 
structural decompositions, information about the nuclear activity, 
presence of dust or peculiar features, 
and any other detail that could be useful to the analysis of my galaxies. \\

The remainder of this chapter comprises the published version of the paper 
``Supermassive Black Holes and Their Host Spheroids. I. Disassembling Galaxies'' 
by G.~A.~D.~Savorgnan \& A.~W.~Graham,  
as it appears in Volume 222 of the \emph{The Astrophysical Journal Supplement Series}.

\includepdf[pages={1-58}]{ApJS2016.pdf}

### 2016-02-26 thesis/introduction.tex
added thesis

\chapter{Introduction}
\label{ch:intro}
In the 1790s, John Michell of England and Pierre-Simon Laplace of France 
independently imagined an ``invisible star'', 
an object whose escape velocity is greater than the speed of light, 
and they both used Newton's gravitational laws to calculate the mass and size of such object \citep{montgomery2009}.  \\

A century ago, in \citeyear{einstein1915}, Albert Einstein completed his General theory of Relativity 
and submitted to the Prussian Academy of Sciences a seminal paper 
where he published the full treatment of his ``field equations''. 
Einstein's theory finally explained the anomalous precession of the perihelion of Mercury, 
and predicted the deflection of light by means of gravitational fields 
and the gravitational redshift of light. 
Albert Einstein willingly embraced these three implications of his theoretical work, 
and was confident about a timely verification of the last two. 
However, he never accepted nor demonstrated any interest in another conclusion of General Relativity, 
i.e.~the existence of regions of the space-time where the force of gravity is so strong 
that not even light can escape. 
Ironically, while some of his colleagues were fascinated by these exotic, dark objects -- 
first of all the American physicist John Archibald Wheeler, who coined and popularised the term ``black hole'' -- 
Einstein strongly opposed and fought against the idea of those weird mathematical singularities for all his life 
\citep{thorne1994}. 
In his \citeyear{einstein1939} article, 
Einstein derived the relativistic equations that describe a stationary cluster of particles 
orbiting on the surface of a sphere. 
He imagined to gradually reduce the radius of the sphere, 
forcing the particles to move faster and faster, 
and demonstrated that the velocity of the particles was reaching the speed of light 
before the cluster was small enough to become a black hole. 
Einstein interpreted his calculations as a proof of the fact that black holes cannot exist. 
He concluded the article writing ``The essential result of this investigation is a clear understanding as to why 
the Schwarzschild singularities do not exist in physical reality. [...] 
The Schwarzschild singularity does not appear for the reason that matter cannot be concentrated arbitrarily''.  \\

Today, not only their existence is unanimously taken for granted by the scientific community, 
but black holes are at the centre of some of the most active research fields of astronomy. 
We know that they come in different flavours and they occupy a wide range of masses, 
going from the hypothetical, minuscule, primordial black holes (e.g.~\citealt{carrhawking1974}), 
generated by density fluctuations of matter during the very first moments of the Universe's expansion 
after the Big Bang, 
through the well understood stellar black holes (e.g.~\citealt{shahbaz1999}), 
remnant products left behind after the death of a massive star, 
to the so called ``massive black holes'', 
occupying the centre of nuclear star clusters and galaxies. 
Massive black holes are further differentiated into two classes according to their mass: 
Intermediate Mass Black Holes (within the mass range $100 - 10^5~\rm M_\odot$, e.g.~\citealt{millercolbert2004,vandermarel2004}), 
still lacking many incontrovertible direct detections 
(but for which we might accumulate evidence over the next years, e.g.~\citealt{pasham2014}), 
and Supermassive Black Holes (e.g.~\citealt{ferrarese2006book}), 
which are the focus of this thesis.

\section{Supermassive black holes} 
An astrophysical black hole is a region of the space-time whose escape velocity is greater than the speed of light.
Black holes are the simplest objects in the Universe. 
They are completely characterised by three properties: mass, spin (or angular momentum) and electric charge. \\

Supermassive black holes (SMBHs) are the most massive black holes known, with typical masses  
$M_{\rm BH} \approx 10^6 - 10^9~\rm M_{\odot}$.
This class of black holes was first theorised \citep{lynden-bell1969,wolfeburbidge1970} after the discovery of quasars.
Quasars can be as luminous as galaxies ($\approx 10^{46}~\rm erg~s^{-1}$).
However, their rapid variability ($\approx$ minutes) at high energies implies tiny sizes for these objects 
($\approx 10^{-6}~\rm pc$), even smaller than the Solar System.
Small sizes and powerful energy outputs led to the conclusion that accreting SMBHs are the engine of quasars
\citep{salpeter1964,zeldovichnovikov1964,lynden-bell1978}. \\

Because quasars were numerous at high redshift, the Universe should be populated with relic black holes \citep{soltan1982}. 
Assuming that the luminosity of quasars is produced by accretion of mass onto the central black hole, 
Andrzej Soltan calculated a lower limit for the integrated energy density due to quasar light, 
derived the corresponding value of mass density of accreted material, 
and showed that, because this mass must be discretely distributed in today's Universe, 
then most, if not all, nearby galaxies host quiescent black holes in their nuclei, 
each black hole having a mass in the $10^8 - 10^9~\rm M_{\odot}$ range. 
This realisation motivated the search of SMBHs at the centre of galaxies, 
i.e.~at the bottom of the potential well, 
where dynamical friction is expected to drag compact massive objects. \\

The gravitational potential of a SMBH dominates over the gravitational potential of the host galaxy within the 
sphere-of-influence radius 
\begin{equation}
r_{\rm h} = \frac{G M_{\rm BH}}{\sigma_*^2} \approx 0.45 \biggl ( \frac{M_{\rm BH}}{10^6 \rm~M_{\odot}} \biggr ) 
\biggl ( \frac{100 \rm~km~s^{-1}}{\sigma_*} \biggr ) \rm~pc ,
\end{equation}
where $G$ is the gravitational constant and $\sigma_*$ is the velocity dispersion of the stars in the 
host galaxy's bulge.
A dynamical detection of a black hole requires the ability to resolve its sphere-of-influence.
For local galaxies ($\lesssim 20~\rm Mpc$), it demands a subarcsecond spatial resolution.
It is only after the introduction of CCD on spectrographs ('80s) that stellar dynamical 
detections of black holes became possible (see the references in the reviews by 
\citealt{kormendyrichstone1995} and \citealt{richstone1998}).
The number of dynamical black hole mass measurements has increased with time and it has recently become a 
statistically meaningful sample with which one can study SMBH demographics. 
It is now generally accepted that SMBHs reside at the centre of most, if not all, 
massive galaxies, either quiescent or active.

\subsection{Measuring black hole masses}
Techniques to measure the mass of SMBHs can be divided into two main categories: direct and indirect methods 
(see \citealt{ferrareseford2005} for a thorough review). 
In direct methods, the mass of a black hole is determined from its gravitational imprint 
in the motion of the surrounding stars or gas. 
The spatial resolution of the observing instrument has to be smaller than the size of the black hole sphere-of-influence, 
which implies challenging technology and time-consuming observations. 
In indirect methods, one adopts approximations to the direct methods 
or uses a parameter of the host galaxy as a proxy to infer the black hole mass 
on the basis of observed scaling relations. \\

Sgr A$^*$, the radio source associated with the Galactic black hole, represents a special case study. 
Thanks to its proximity ($8.28 \pm 0.33 \rm~kpc$, \citealt{genzel2010}), 
near infrared techniques have made possible to resolve and follow each individual star 
orbiting around Sgr A$^*$. 
From the analysis of these orbits, 
\citet{ghez2008} derived a best-fit central mass of $(4.5 \pm 0.4) \times 10^6 \rm~M_\odot$. \\

When measuring black hole masses in gas-poor early-type galaxies, 
the primary method of choice is based on modelling the integrated kinematics of stars 
acquired through high spatial resolution spectroscopy. 
Because to a good approximation the stars in a local galaxy constitute a collisionless system, 
it is possible to describe their motion analytically and constrain the central gravitational potential. 
The best-fit model to the observed integrated stellar kinematics 
returns an estimate of the black hole mass and the stellar mass-to-light ratio, 
which are treated as free parameters. 
Although modelling the integrated stellar kinematics can in principle return robust black hole mass estimates, 
this method is not exempted from systematics and degeneracies, 
which are mainly caused by our poor ability to resolve the tiny black hole sphere-of-influence even in the most nearby galaxies 
\citep{valluri2004}. 
\citet{gebhardtthomas2009} first explored the effects of including the additional contribution from a dark matter halo 
when modelling the central stellar kinematics of the galaxy M87.
Their measurement of the black hole mass was over a factor of two larger than previous stellar dynamical measurements 
which did not account for dark matter.  
Upon deriving 10 new black hole mass measurements from the analysis of two-dimensional stellar kinematics, 
\citet{rusli2013bhmassesDM} concluded that the omission of dark matter systematically overestimates the stellar mass-to-light ratio 
and underestimates the black hole mass; 
this bias does not significantly affect the estimate of the black hole mass 
only if the spatial resolution of the observations is at least a factor of 10 smaller 
than the size of the black hole sphere-of-influence.
\citet{merritt2013book} reminds that, 
among all current black hole mass measurements based on stellar-dynamics, 
only three cases were carried out with enough spatial resolution to detect 
a convincing Keplerian rise in the central stellar velocities, 
as expected from the presence of a central massive object. 
From this consideration, he raises doubts about the majority of such black hole mass detections, 
and pessimistically cautions that they should be interpreted as upper limits only. \\

When water maser clouds are present in an Active Galactic Nucleus (AGN) 
in the form of a thin disc (with sub-parsec size) rotating around the central engine 
and heated by the X-ray photons emitted by the AGN accretion disc, 
the gas dynamics can be studied with radio interferometric techniques (e.g.~with the Very Long Baseline Array)
and the central gravitational potential constrained, 
benefiting from a spatial resolution that can be up to $\approx 200$ times higher than that allowed by the Hubble Space Telescope 
(e.g.~the black hole mass measurement in the galaxy NGC 4258, \citealt{miyoshi1995}). 
Water masers allow the most accurate mass measurements for SMBHs in galaxies other than the Milky Way. \\

More than half of massive early-type (elliptical + lenticular) galaxies and virtually all spiral galaxies have 
detectable warm ionised gas in their nuclei \citep{ho1997}, 
whose emission lines are easier to measure than stellar absorption lines. 
In principle, under the assumption that the ionised gas is distributed in a rotationally-supported Keplerian disc, 
where the effects of stellar orbital anisotropy, triaxiality or dark matter are negligible, 
modelling the gas dynamics is conceptually simpler than modelling the integrated stellar kinematics. 
However, as \citet{kormendyho2013} pointed out, unlike stars, gas is subject to non-gravitational perturbations 
(turbulence, shocks, radiation pressure, magnetic fields, etc.), 
hence its dynamics could be much more complicated than the ordered motion assumed within a Keplerian disc model.
\citet{kormendyho2013} compared the common black hole mass measurements obtained from gas and stellar dynamics for eight galaxies 
and concluded that the gas-based measurements are systematically underestimated 
when the modelling of the gas dynamics does not include corrections for large emission-line widths, 
which are speculated to imply significant random motions of gas perturbed by non-gravitational fenomena, such as radio jets. \\

Other black hole mass determination methods can be applied to some AGNs and quasars. 
These techniques rely on fitting accretion disc models to multiwavelength continua spectra \citep{shields1978,malkan1983}
or studying the emission line due to iron fluorescence (e.g.~\citealt{fabian2000,reynoldsnowak2003}).
Reverberation mapping (e.g.~\citealt{peterson1993}) consists of 
modelling the structure of the broad emission-line region of an AGN, 
as probed by the short-term variability of the ionising continuum,
and estimating the black hole mass by assuming a calibration factor that depends on an observed correlation 
between the black hole mass and some host galaxy parameter\footnote{Typically, this scaling factor is calibrated 
on the $M_{\rm BH} - \sigma_*$ relation, i.e.~the observed correlation between black hole mass and host spheroid 
stellar velocity dispersion (e.g.~\citealt{ferraresemerritt2000,gebhardt2000}). }. \\

Building on past catalogs of direct black hole mass measurements 
obtained with stellar-kinematics, gas-dynamics, or water maser techniques, 
\cite{grahamscott2013} compiled a sample of $\approx 80$ galaxies with a reliable measure of $M_{\rm BH}$. 
The galaxy sample used in this work is based on that published by \cite{grahamscott2013}.

\subsection{Scaling relations}
Over the last three decades, observations have demonstrated that 
the black hole mass scales with a number of properties of its host spheroid 
(see Section \ref{sec:spheroid} for the meaning of the term ``spheroid''), 
on scales much larger than the black hole sphere-of-influence.
The black hole mass has been shown to correlate with 
the spheroid luminosity $L_{\rm sph}$ \citep{dressler1989,kormendyrichstone1995}, 
the spheroid stellar velocity dispersion $\sigma_*$ \citep{ferraresemerritt2000,gebhardt2000}, 
the spheroid central radial concentration of stars \citep{graham2001,grahamdriver2007}, 
the spheroid dynamical mass $M_{\rm dyn,sph}$ \citep{magorrian1998,marconihunt2003,haringrix2004}, 
the spheroid gravitational binding energy \citep{allerrichstone2007}, 
the spheroid kinetic energy of random motion \citep{feolimele2005,feolimancini2009},
the spheroid effective radius \citep{sani2011}, 
and the spheroid stellar mass (e.g.~\citealt{magorrian1998,sani2011,beifiori2012,scott2013}).
Other correlations with host galaxy parameters  -- as opposed to spheroid parameters -- have been proposed, such as with
the spiral arm pitch angle \citep{seigar2008,berrier2013}, 
the number of globular clusters \citep{burkerttremaine2010,snyder2011},
the dark matter halo \citep{ferrarese2002}
and the velocity dispersion of the globular clusters \citep{sadouncolin2012,pota2013}. 
Very recently, \cite{lasker2014anal} claimed that the black hole mass correlates equally well with the spheroid and 
the total galaxy luminosity. \\

The astrophysical interest in black hole mass scaling relations can be summarised in three points.
First, the correlations probe a strong connection between SMBHs and their host spheroids.
Exploring how scaling relations have changed throughout the cosmic time could help identify
the driving mechanisms of the black hole -- galaxy co-evolution.
Observations at $z=0$ are the most accurate and therefore the most important.
Second, \emph{all} of the observed scaling relations must be taken into account by any complete theory or model describing 
the co-evolution of galaxies and SMBHs\footnote{Modern semi-analytic models 
use the observed black hole mass scaling relations 
to constrain the black hole accretion rate ($\dot{M}_{\rm BH}$).}.
A fundamental, but non-trivial, requirement is that all the correlations have to be consistent with each other.
Third, scaling relations can be employed to predict the masses of SMBHs in other galaxies, where a direct
measure of $M_{\rm BH}$ would be extremely time consuming or simply impossible due to technological 
limitations.
Many accurate $M_{\rm BH}$ predictions would help derive 
the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction}) 
and space density (\citealt{grahamdriver2007smbhmassdensity} and references therein),
and aid study of SMBH demographics. \\

\subsection{Spheroid}
\label{sec:spheroid}
Throughout the text, the term ``spheroid'' will be used to indicate either a pure elliptical galaxy  
or the bulge component of a disc galaxy. 
Obviously, if a galaxy is composed of a relatively flat stellar disc 
embedded in a triaxial, elliptically-shaped stellar system which dominates the light at large radii 
(a ``discy elliptical'', \citealt{michard1984,nieto1988}), 
the term ``spheroid'' designates the latter component. 
Providing a self-sufficient definition of a galaxy's ``bulge'' is not trivial. 
In \cite{laurikainen2016review}, B.~Madore retraces the history of the origin of this term, 
from its first legitimation as ``Galactic bulge'', 
to the modern, ordinary acceptation that all extragalactic astronomers embrace 
when they think about lenticular or early-type spiral galaxies. 
A bulge can be identified photometrically, 
as the central component rising above the inward extrapolation of the disc's surface brightness profile, 
or morphologically, 
as a 3-dimensional rounded swelling which emerges from the disc plane 
(best visible in the vast majority of massive, edge-on galaxies, e.g.~\citealt{kautsch2006}), 
or also kinematically, 
by distinguishing a structure with low-angular momentum and higher vertical dispersion
at the centre of a high-angular momentum thin disc (e.g.~\citealt{fabricius2014}). 
It is common practice to make a distinction between \emph{classical bulges} and \emph{pseudobulges}. 
Classical bulges are merger-built, pressure-supported systems, 
whereas pseudobulges are disc-like, rotation-supported systems, 
originated from secular evolution processes such as disc or bar instabilities 
\citep{kormendy1982,kormendykennicutt2004}.

\subsection{Co-evolution and AGN feedback}
The tightness (or small scatter) of the observed black hole mass correlations led to the idea
that SMBHs and host galaxies have co-evolved with some sort of self-regulated growth.
AGN feedback has been proposed as the process by which this occurs
(e.g.~\citealt{silkrees1998,fabian1999,ostrikerciotti2005}; see \citealt{fabian2012} for a review). 
The AGN is believed to emit intense flux of photons and particles 
which can sweep the gas from the host spheroid 
and terminate both star formation and gas accretion onto the black hole. 
This idea is motivated by the fact that the black hole binding energy ($\propto M_{\rm BH} c^2$) 
is much larger than the bulge binding energy ($\propto M_{\rm dyn,sph} \sigma_*^2$). 
Therefore, if just a very small percentage of the AGN energy output couples to the gas, 
all of the gas reservoir can be blown away from the host galaxy. 
The current picture distinguishes between ``quasar mode AGN feedback'', 
which takes place when the AGN energy output is close to the Eddington limit\footnote{The Eddington 
limit is the maximum luminosity at which an object can emit 
owing to balance between the outward radiation pressure and the inward gravitational force. } 
and whose main effect is to blow gas away from the spheroid, 
and ``radio mode AGN feedback'', also known as ``maintenance mode'', 
which injects energy into the interstellar gas and prevents it from cooling. \\

Although observational evidence is not always clear, 
the AGN feedback scenario is consistent with some direct observations,
such as the X-ray cavities of giant ellipticals, galaxy groups and clusters, 
thought to be inflated by AGN jets (e.g.~\citealt{mcnamaranulsen2012}), 
or the blue-shifted quasar absorption lines, signature of high-velocity winds (e.g.~\citealt{tombesi2012}),
or the ionised gas outflows seen in radio galaxies (e.g.~\citealt{nesvadba2006}). 
Many mechanisms, either radiative (through photons) or mechanical (through high-energy
particles, winds or jets), can be responsible for AGN feedback, 
but it has not yet been established which ones are dominating. 
For each AGN feedback mechanism, 
theoretical models predict how the black hole mass scales with the host spheroid properties. 
These predictions can be compared with the observed scalings of the empirical black hole mass correlations 
to constrain the models and understand which mechanisms are prevailing. 
Part of the popularity of the AGN feedback scenario resides in its ability to resolve some 
open questions in galaxy formation.
For instance, AGN feedback is invoked to explain the ``cooling flow problem'', which states
that, in the absence of an energy input, the X-ray halos of the most massive galaxies known, Brightest
Cluster Galaxies (BCGs), and galaxy clusters
would cool quickly, producing cold gas and associated giant bursts of star formation activity that are
not observed in the predicted large amounts (e.g.~\citealt{ostrikerciotti2005}).
AGN activity is also believed to quench star formation in high-mass galaxies,
explaining why the galaxy mass function (at high masses) drops more quickly than expected from our
standard cosmology (e.g.~\citealt{croton2006}). \\

An alternative idea to explain the empirical black hole mass correlations 
without calling into play AGN feedback
was explicitly proposed for the first time by \citet{peng2007}, 
and similar conclusions were reached later by \citet{gaskell2010}, 
\citet{hirschmann2010} and \citet{jahnkemaccio2011}. 
These studies showed that, starting from a distribution of small progenitor \{galaxy -- black hole\} pairs, 
regardless of whether or not the initial black hole masses correlate with the initial galaxy masses, 
and building bigger galaxies through a succession of dry mergers 
(where galaxy masses and black hole masses add separately), 
as a consequence of the central limit theorem, 
after several mergers one obtains a near-linear correlation between black hole mass and galaxy mass, 
whose scatter decreases with increasing mass. 
In addition to this, the central limit theorem guarantees that, 
regardless of the nature of the initial distributions of galaxy and black hole masses, 
the final distributions converge to Gaussians. 
However, this scenario does not fit in with the non-linear $M_{\rm BH} - L_{\rm sph}$ correlation 
found by \cite{grahamscott2013}, 
as explained in Section \ref{sec:bent}.  \\

\subsection{The S\'ersic/core-S\'ersic paradigm}  
\label{sec:bent}
For many years, the samples of galaxies with a direct measurement of their black hole mass 
had been dominated by early-type, high-luminosity galaxies, hosting the most massive black holes known. 
From these samples, the $M_{\rm BH} - M_{\rm dyn,sph}$ and $M_{\rm BH} - L_{\rm sph}$ log-linear relations 
had been reported to have an exponent $\beta$ close to 1 (i.e.~$M_{\rm BH} \propto M_{\rm dyn,sph}^{\beta \simeq 1}$). 
However, \cite{graham2012bent} addressed a crucial inconsistency, 
that becomes clear when one considers the following points.

\begin{itemize} 
\item[1)] The $L_{\rm sph} - \sigma_*$ log-linear relation is not described by a single power law. %\cite{matkovicguzman2005}
	  In fact, this correlation has a different slope if one considers only the bright \emph{core-S\'ersic} spheroids
	  ($L_{\rm sph} \propto \sigma_*^5$) rather than the fainter \emph{S\'ersic} spheroids ($L_{\rm sph} \propto \sigma_*^2$).
	  %\cite{davies1983}
	  Core-S\'ersic spheroids display a central deficit of light relative to the inward extrapolation of their 
	  outer S\'ersic light profile, whereas S\'ersic spheroids do not. 
	  The different behaviour of their central light profile is thought to be indicative of distinct formation scenarios 
	  (see Section \ref{sec:corser} for a digression on this topic).
	  \cite{davies1983} and \cite{matkovicguzman2005} showed that the change in slope of the $L_{\rm sph} - \sigma_*$ relation 
	  occurs at the B-band absolute magnitude $M_{\rm B} \approx -20.5~\rm mag$ ($\sigma_* \approx 200~\rm km~s^{-1}$) and corresponds to 
	  the division between core-S\'ersic and S\'ersic spheroids (e.g.~\citealt{grahamguzman2003}).
\item[2)] The $M_{\rm BH} - \sigma_*$ relation, instead, does not have a bent nature, 
          being well described by a single power law \citep{graham2012bent}.
\item[3)] The dynamical mass-to-light ratio scales with the luminosity as $(M/L)_{\rm dyn} \propto L^{1/4}$ (e.g.~\citealt{faber1987}).
\end{itemize}

These three points put together led to the conclusion that 
the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm dyn,sph}$ log-linear
relations could not be fit with a single power law. 
Core-S\'ersic spheroids were expected to follow $M_{\rm BH} \propto L_{\rm sph}^{1.0}$ and 
$M_{\rm BH} \propto M_{\rm dyn,sph}^{1.0}$.
S\'ersic spheroids, instead, were predicted to define a much steeper sequence, having $M_{\rm BH} \propto L_{\rm sph}^{2.5}$ and 
$M_{\rm BH} \propto M_{\rm dyn,sph}^{2.0}$.
Therefore, the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm dyn,sph}$ log-linear
relations should be better described by a broken (or \emph{bent}) power law. \\

Upon re-analysing the sample of $\approx 30$ galaxies presented by \cite{haringrix2004}, 
\cite{graham2012bent} derived linear regressions for S\'ersic and core-S\'ersic spheroids, separately, 
in the $M_{\rm BH} - M_{\rm dyn,sph}$ diagram, 
and reported on the bent nature of this correlation. 
The findings of \cite{graham2012bent} were later confirmed by \cite{grahamscott2013}, 
who expanded the galaxy sample with $\approx 40$ additional objects and  
converted B- and K-band observed, total galaxy magnitudes of disc galaxies into dust-corrected, bulge magnitudes. 
Rather than do this galaxy by galaxy, which would require careful bulge/disc decompositions, 
they employed a mean statistical correction based on each object's morphological type and disc inclination. 
These mean statistical bulge-to-total ratios were derived from the results of two-component 
(S\'ersic-bulge/exponential-disc) models 
taken from \citeauthor{grahamworley2008} (\citeyear{grahamworley2008}, and references therein).  
\cite{grahamscott2013} found $M_{\rm BH} \propto L_{\rm sph}^{1.10 \pm 0.20}$ for their core-S\'ersic subsample
and $M_{\rm BH} \propto L_{\rm sph}^{2.73 \pm 0.55}$ for their S\'ersic subsample (using K-band luminosities). 
Following \cite{grahamscott2013}, 
\cite{scott2013} converted luminosities into stellar masses and 
found $M_{\rm BH} \propto M_{\rm *,sph}^{0.97 \pm 0.14}$ for core-S\'ersic spheroids,
and $M_{\rm BH} \propto M_{\rm *,sph}^{2.22 \pm 0.58}$ for S\'ersic spheroids. 
More recently, \cite{grahamscott2015} compiled a sample of $\approx 140$ low-redshift ($z \leq 0.35$, 
with a median redshift $\langle z \rangle = 0.085$) 
bulges hosting AGNs with virial black hole masses 
$10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ \citep{jiang2011a}, 
and showed that they roughly follow the near-quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges. \\

The physical interpretation that \cite{grahamscott2013} and \cite{scott2013} attributed 
to the bent nature of the $M_{\rm BH} - M_{\rm *,sph}$ relation is the following. 
Core-S\'ersic spheroids follow a near-linear $M_{\rm BH} - M_{\rm *,sph}$ relation 
because these high-mass systems grow mainly through non-dissipative (gas-poor) major merger events, 
where the progenitor black holes and galaxies are summed together in lock steps.
Instead, the (two times) steeper relation for S\'ersic galaxies implies that 
their central black hole must grow more rapidly than their host spheroid. 
S\'ersic galaxies are intermediate-mass galaxies, thought to be built through wet-wet or wet-dry mergers as well as
via gas accretion processes which enhance both star formation and AGN activity. \\

Many of the concepts treated in this and the previous Sections 
are extensively reviewed in \cite{graham2016bulges}.

\subsection{S\'ersic and core-S\'ersic spheroids} 
\label{sec:corser}
The nomenclature \emph{S\'ersic}/\emph{core-S\'ersic} was introduced as a consequence of an observed dichotomy 
in the nature of the central surface brightness profile of stellar spheroids (elliptical galaxies or the bulges of disc galaxies). 
The surface brightness profile of S\'ersic spheroids is well described by the S\'ersic (\citeyear{sersic1963}, \citeyear{sersic1968}) model 
all over its radial extent, including the innermost central parsecs. 
Occasionally, the surface brightness profile of S\'ersic spheroids can exhibit a nuclear light excess, 
due to the contribution of an additional stellar component (e.g.~a nuclear star cluster) on top of the stellar spheroid itself. 
The surface brightness profile of core-S\'ersic spheroids is characterised by the presence of a partially depleted core, 
i.e.~a central deficit of stellar light not caused by dust obscuration. 
Beyond the region affected by the partially depleted core, 
the surface brightness profile of core-S\'ersic spheroids is well approximated by the S\'ersic (\citeyear{sersic1963}, \citeyear{sersic1968}) model. 
The core-S\'ersic model \citep{graham2003coresersicmodel,trujillo2004coresersicmodel} provides an excellent description 
of the overall surface brightness profile of core-S\'ersic spheroids. 
Core-S\'ersic spheroids fall also into the category of ``core galaxies'', as given by the Nuker definition \citep{lauer2007}, 
although $\approx 20\%$ of ``core galaxies'' are not core-S\'ersic galaxies \citep{dullograham2014cores}, 
i.e.~they do not have depleted cores.
Figure \ref{fig:corser} illustrates the dichotomy between a S\'ersic and a core-S\'ersic spheroid. 
The presence of a partially depleted core is detected in the surface brightness profile of NGC 3348, 
whereas the best-fit model for NGC 5831 is essentially a pure S\'ersic model. \\

\begin{figure}[htb] 
\begin{center}
\includegraphics[width=0.9\textwidth]{images/sersiccoresersic.eps}
\end{center}
\caption{
The observed major-axis surface brightness radial profiles ($\mu$, in units of $\rm mag~arcsec^{-2}$) 
of the elliptical galaxies NGC 3348 and NGC 5831 
are shown with the black points in the top left and right panels, respectively. 
The solid lines are fits using the empirical core-S\'ersic model, 
and the dotted extensions are their inner and outer extrapolations. 
The long dashed lines indicate extrapolations of the outer S\'ersic-like part of the core-S\'ersic model. 
The residuals from the fits ($\Delta \mu = data - model$) are shown with black squares in the bottom panels, 
and the rms scatter $\Delta$ is given for each fit. 
This Figure was extracted from \cite{graham2003coresersicmodel}. }
\label{fig:corser}
\end{figure}

Partially depleted cores are believed to form during dissipationless (``dry'', i.e.~gas-poor) mergers \citep{begelman1980}, 
where the progenitor black holes sink towards the centre of the remnant galaxy due to dynamical friction against stars, 
form a bound pair and further reduce their orbital separation by transferring their binding energy to the surrounding stars 
via a three-body scattering process also known as ``gravitational slingshot'' 
(\citealt{milosavljevicmerritt2001,merritt2013CQG}, and references therein). 
The scouring action of the black hole binary has the effect of lowering the galaxy's stellar central density, 
in fact producing a partially depleted core 
(e.g.~\citealt{merritt2006RPP,dotti2012,colpi2014}). 
The lack of a significant amount of gas during the merger is a necessary condition 
to guarantee the formation of a partially depleted core. 
\cite{mayer2009} and \cite{colpi2009} followed the simulations of two merging Milky Way-like galaxies 
and reported that the time-scale for the formation of a close black hole binary system due to dynamical friction against gas 
is $\approx$100 times shorter than that due to dynamical friction against stars. 
Therefore, a black hole binary coalesces more quickly in a gas-rich (``wet'') merger than in a gas-poor (``dry'') merger, 
i.e.~when gas is in play, the binary does not have enough time to form a partially depleted core. 
In addition, gas is likely to be funnelled towards the centre of the galaxy remnant, shock and induce star formation, 
which would act against the formation of a core by increasing the central stellar density.

\subsection{Origin of SMBHs}
As of today, the formation of SMBHs is still an unsolved puzzle. 
The key astrophysical questions that pertain to this open debate are: 
(\emph{i}) what are the initial seeds of SMBHs and when did they form? 
(\emph{ii}) how were these seeds distributed in the early universe 
(i.e.~what is their mass distribution function and space density)? 
and (\emph{iii}) what is their accretion history throughout the Universe's first few billion years? 
\cite{volonteribellovary2012} review three possible pathways -- not mutually exclusive -- 
that have been proposed as viable mechanisms to SMBH seeds formation. \\

The first of these three theoretical scenarios states that SMBHs originated from the remnants of Population III stars. 
Population III stars are the (hypothetical) first generation of stars, which formed out of zero-metallicity pristine gas. 
The lack of metals implies inefficient cooling and inefficient fragmentation of the gas, 
making possible to produce very massive stars (with initial masses $\gtrsim 100~\rm M_\odot$). 
The fate of Population III stars mainly depends on their initial mass \citep{heger2003}. 
A low-metallicity star that initially weights $\approx 25 - 140~\rm M_\odot$ is predicted to directly collapse into a black hole 
with about half of the mass of its progenitor star. 
Such black hole would not be heavy enough to be dragged by dynamical friction towards the host galaxy centre, 
therefore it would hardly contribute to the formation of a central SMBH. 
Between $\approx 140 - 260~\rm M_\odot$, low-metallicity stars lie within the pair instability supernova regime, 
where the final nuclear-powered explosion completely disrupts the star and leaves no remnant. 
Above $\approx 260~\rm M_\odot$, the nucleus of a low-metallicity star is highly unstable 
and quickly ($\approx 2~\rm Myr$) collapses into a black hole that retains at least half of the initial stellar mass. 
For many years, these high-mass stellar black holes have been considered the most promising SMBH seeds candidates. 
However, as recent numerical simulations were improved 
thanks to the achievement of better resolution and the inclusion of more complex physics 
(e.g.~\citealt{turk2009,greif2011,clark2011,stacy2012}), 
it became clear that fragmentation played a more important role in the formation of Population III stars, 
which turned into less attractive candidates for the origin of SMBHs. \\

A second possibility for the genesis of SMBH seeds is the formation of a supermassive star (up to $\approx 10^6~\rm M_\odot$) 
at the centre of a primordial galaxy. 
In this scenario, low-metallicity, low-angular momentum gas infalls towards the bottom of the potential well of a dark matter halo and, 
due to gravitational instabilities, does not settle into a rotationally supported disc, 
but accumulates into a very massive star, 
whose core rapidly ($\approx 1~\rm Myr$) collapses into a black hole and swallows the surrounding gas envelope, 
giving birth to a $\approx 10^3 - 10^6~\rm M_\odot$ SMBH seed. \\

According to the third theoretical scenario, gas infalls towards the centre of a dark matter halo and fragments into several stars
that form a dense stellar cluster. 
Before the first supernova explosions can occur, small stars collide with each other within the cluster 
and merge into a massive ($\approx 10^3~\rm M_\odot$) star which eventually collapses into a black hole with similar mass. \\

The discovery of ultraluminous quasars at $z>6$ has accentuated the urge to create very massive black hole seeds in a relatively short time 
(e.g.~\citealt{alexandernatarajan2014,madau2014,lupi2015}). 
To date, there have been nearly 50 claims of $z>6$ quasars hosting $\gtrsim 10^9~\rm M_\odot$ black holes 
(e.g.~\citealt{fan2003,jiang2007,mortlock2011,banados2014,trakhtenbrot2015,wu2015}). 
Within a $\Lambda$CDM cosmology, such early giant monsters could not have formed so quickly 
without the creation of anomalously massive seeds 
or incredibly high accretion rates, i.e.~exceeding the Eddington limit 
(but see \citealt{meliamcclintock2015} for an alternative explanation). 
However, it is worth noting that these black hole masses are calculated with the reverberation mapping method, 
assuming that $M_{\rm BH}$ is directly proportional to the virial factor $f$, 
which is calibrated on the normalisation of the $z=0$ observed $M_{\rm BH} - \sigma_*$ correlation. 
The existence of (unknown) selection biases in the local sample of directly measured black hole masses 
would imply a systematic overestimation of the virial factor and, consequently, 
of the black hole masses estimated with the reverberation mapping technique. \\

%\subsection{bhfp}
%\cite{marconihunt2003} pointed out a significant correlation between the residuals of the $M_{\rm BH} - \sigma_*$
%relation and the effective radii of the spheroids in their sample. 
%Motivated by this observation, many studies have explored the possibility that the different black hole mass 
%scaling relations were projections of the same black hole ``fundamental plane'' (BHFP), in analogy to the
%well known fundamental plane of spheroids ($R_{\rm e,sph} \propto \sigma_{*}^{\alpha} \langle \mu_{\rm e,sph}\rangle^{\beta}$,
%with $\langle \mu_{\rm e,sph}\rangle$ the mean bulge surface brightness within $R_{\rm e,sph}$, \citealt{djorgovskidavis1987}).
%Various three-parameter correlations have been investigated, in the form of $M_{\rm BH} - R_{\rm e,sph} - \langle \mu_{\rm e,sph}\rangle$ 
%\citep{barwaykembhavi2007}, 
%$M_{\rm BH} - R_{\rm e,sph} - \sigma_{*}$ \citep{marconihunt2003,defrancesco2006,allerrichstone2007,
%hopkins2007} and $M_{\rm BH} - R_{\rm e,sph} - n_{\rm sph}$ \citep{graham2008}.
%However, \cite{graham2008} revisited all the three versions of the BHFP and showed that none of them is defined by the population
%of barless spheroids. 
%In fact, the bulges of barred spiral galaxies systematically deviate from the $M_{\rm BH} - \sigma_*$ relation, 
%producing the apparent black hole plane. 
%\cite{graham2008} nevertheless pointed out that more and better quality data would be welcome in fully resolving this issue.
%
%
%This observation motivated \cite{hopkins2007} to search for a black hole ``fundamental plane'' (BHFP), in analogy to the
%well known fundamental plane of spheroids ($R_{\rm e} \propto \sigma_{*}^{\alpha} I_{\rm e}^{\beta}$).
%They found that the systems in their sample lie on a BHFP of the form $M_{\rm BH} \propto \sigma_{*}^{3.0} R_{\rm e}^{0.5}$ 
%or $M_{\rm BH} \propto M_{*}^{0.5 - 0.7} \sigma_{*}^{1.5 - 2.0 }$.

%\subsection{fundamental corr}

\subsection{Monster black holes}
\label{sec:monsters}
Over the last five years, several claims of detections of \emph{over-massive} black holes accumulated in the literature. 
Over-massive black holes are black holes whose mass is significantly larger 
than what is expected from the galaxy's spheroid stellar velocity dispersion or stellar mass, 
i.e.~they are positive outliers in the $M_{\rm BH} - \sigma_*$ or $M_{\rm BH} - M_{\rm *,sph}$ diagrams. \\

Using integral-field spectrographs at the Gemini North and Keck 2 telescopes, 
\cite{mcconnell2011} targeted the BCGs (NGC 3842 and NGC 4889) of two massive galaxy clusters, 
the Leo and Coma clusters (Abell 1367 and Abell 1656, respectively), 
and reported the direct detection of the two most massive black holes ever found at that time. 
They claimed that these two black holes are significantly more massive 
than predicted by the popular $M_{\rm BH} - \sigma_*$ and $M_{\rm BH} - L_{\rm sph}$ correlations, 
and speculated that the growth of the largest galaxies and their black holes happens by means of evolutionary processes 
different from what is commonly assumed for less massive elliptical galaxies. \\

\cite{rusli2011} obtained SINFONI integral-field unit observations of the nuclear region of the galaxy NGC 1332 
and measured a one billion solar masses black hole, 
consistent with the galaxy's stellar velocity dispersion, 
but offset from the $M_{\rm BH} - L_{\rm sph}$ relation by a full order of magnitude. \\

\cite{vandenbosch2012} combined archival Hubble Space Telescope (\emph{HST}) high-resolution imaging 
and long-slit spectroscopy (obtained with the Marcario Low Resolution Spectrograph on the Hobby-Eberly Telescope, Texas) 
of the nuclear region of the galaxy NGC 1277, 
and directly measured the central black hole mass by fitting self-consistent Schwarzschild models 
to the integrated stellar kinematics. 
They found a twenty billion solar masses black hole, 
which they estimated to weight 59\% of the host spheroid's mass (or 14\% of the galaxy's total stellar mass). 
According to their measurement, 
the black hole of NGC 1277 was an order of magnitude more massive than what expected from the host spheroid's stellar velocity dispersion 
and two orders of magnitude more massive than what expected from the host spheroid's stellar mass.
\cite{emsellem2013} re-analysed \citeauthor{vandenbosch2012}'s data 
and showed that their observations were consistent with a black hole mass up to an order of magnitude smaller 
than the extraordinary value previously reported. 
However, \cite{yildirim2015} and \cite{scharwachter2015} confirmed \citeauthor{vandenbosch2012}'s measurement. \\

\cite{bogdan2012} reported on the unusually high $M_{\rm BH}/M_{*,sph}$ ratio for the galaxies NGC 4342 and NGC 4291 
and concluded that no co-evolution subsisted between these two galaxies and their black holes. 
Other reportedly over-massive black holes belong to the galaxies NGC 1271 \citep{walsh2015} and Mrk 1216 \citep{yildirim2015}. \\

On the basis of these claims, \cite{ferremateu2015} theorised that, 
while most today's massive early-type galaxies have completed their two-phase growth path (``in-situ'' and ``ex-situ''), 
the over-massive black holes hosts skipped the second (``ex-situ'') phase and therefore represent an exception.

\section{Galaxy decomposition}
Galaxy decomposition is a parametric analysis that allows one to fit the surface brightness distribution
of galaxies using a combination of analytic functions (usually one function per
galaxy component, such as spheroid, disc, bar, nucleus, etc.). 
The 1D (one-dimensional) technique begins with fitting isophotes to the galaxy image.
Isophotes are curves along which the intensity of light is constant 
and they are typically described with concentric ellipses.  
The 1D surface brightness radial profile is then extracted and modelled with a combination of 1D analytic functions. 
With the 2D (two-dimensional) technique one fits 2D analytic functions directly to digital images. 
Galaxy decomposition is useful to perform structural analysis of galaxies and obtain the best-fit 
parameters of the spheroidal component, such as the luminosity, the half-light radius 
and the central radial concentration of stars. \\

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\textwidth]{images/galaxyvivisection.eps}
\end{center}
\caption{Schematic representation of one-dimensional galaxy decomposition. 
The mock galaxy at the top is composed of a spheroid (orange), a large-scale disc (blue), 
a bar (green), and a nuclear source (red). 
The observed surface brightness profile of the galaxy (intensity of light as a function of galactocentric radius) 
is the white curve. 
The contribution of each galaxy component to the total surface brightness profile is modelled with one analytic function, 
illustrated with a solid line of the same colour as the corresponding component. 
The sum of all analytic functions gives the total galaxy model, 
which is matched to the observed surface brightness profile. }
\end{figure}

Pioneer studies that performed 1D bulge/disc decompositions of galaxies (e.g.~\citealt{simiendevaucouleurs1986}) 
described the bulge component with a \cite{devaucouleurs1948} $R^{1/4}$ profile:
\begin{equation}
\mu_{\rm de Vaucouleurs}(\mu_{\rm e},R_{\rm e};R) = \mu_{\rm e} + 8.32678
\Biggl[\biggl(\frac{R}{R_{\rm e}}\biggr)^{1/4}-1\Biggr] ,
\end{equation} 
and the disc component with an exponential profile:
\begin{equation}
\mu_{\rm exponential}(\mu_{\rm 0},h;R) = \mu_{\rm 0} + \frac{2.5}{\ln(10)} \biggl(\frac{R}{h} \biggr) .
\end{equation} 
Here $\mu$ is the surface brightness profile, 
$R$ is the projected galactic radius, i.e.~the distance of the isophotes from the galaxy centre, 
$R_{\rm e}$ is the bulge effective radius (or half-light radius) that encloses half of the total light from the model, 
$\mu_{\rm e}$ is the bulge surface brightness at the effective radius, 
$\mu_{\rm 0}$ is the disc central surface brightness, 
and $h$ is the disc scale length. \\

However, it soon became clear to some that the fixed curvature of the two-parameter de Vaucouleurs $R^{1/4}$ law 
was not adequate to accommodate the variety of shapes observed in the light profiles of stellar spheroidal systems. 
A more ductile mathematical function was needed 
such as the three-parameter \cite{sersic1963,sersic1968} $R^{1/n}$ model: 
\begin{equation}
\mu_{\rm S\acute{e}rsic}(\mu_{\rm e},R_{\rm e},n;R) = \mu_{\rm e} + \frac{2.5~b_{\rm n}}{\ln(10)} 
\Biggl[\biggl(\frac{R}{R_{\rm e}}\biggr)^{1/n}-1\Biggr] ,
\end{equation}
where the S\'ersic index $n$ is the parameter that measures the curvature of the radial light profile,
and $b_{\rm n}$ is a scalar value defined in terms of the S\'ersic index 
(see \citealt{grahamdriver2005} for a valuable compendium). 
After \cite{caon1993} and \cite{donofrio1994} demonstrated the superiority of the S\'ersic model 
over the de Vaucouleurs law in describing the spatial distribution of light of early-type galaxies, 
the varying curvature of the S\'ersic model became a necessity also for rendering 
the light profiles of the bulges of spiral galaxies 
\citep{andredakis1995,moriondo1998,grahamprieto1999,khosroshahi2000,graham2001}. \\

Thanks to the improved computational speed of machines, 
2D fitting algorithms have become more and more popular over the last two decades. 
\cite{dejong1996} presented a 2D decomposition technique 
which allowed one to model the surface photometry of a galaxy 
using an exponential light profile for both the bulge and the disc. 
\cite{simard1998} developed the IRAF\footnote{IRAF is the Image Reduction and Analysis Facility, 
distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} package {\tt GIM2D}, 
a 2D decomposition code aimed at distant galaxies. 
{\tt GIM2D} takes an input image and simultaneously decomposes all the objects 
as the sum of a S\'ersic and an exponential profile. \\

A major breakthrough came with {\tt GALFIT}, 
a 2D fitting algorithm released by \citeauthor{peng2002} (\citeyear{peng2002}; 
the nowadays popular {\tt GALFIT3}, an improved version of the original algorithm, was presented by \citealt{peng2010}), 
which marked an important turning point for the quantitative morphological analysis of galaxies. 
Thanks to its capability of fitting a galaxy with an arbitrary number of components 
-- chosen from a wide variety of analytical functions such as the S\'ersic and the ``Nuker'' models, 
or the exponential, Gaussian, and Moffat profiles -- 
and to its optimisation in computational speed, 
{\tt GALFIT} was specifically conceived for modelling large images of spatially well-resolved, 
nearby galaxies observed with the Hubble Space Telescope. \\

\cite{desouza2004} developed {\tt BUDDA} (Bulge/disc Decomposition Analysis), 
a code to perform 2D decomposition of galaxies using a two-component S\'ersic+exponential model. 
The number of fitted components was intentionally limited to two (bulge+disc), 
with the purpose of using the residual images 
to study the additional substructures such as bars, lenses, rings, and inner discs. \\

\cite{laurikainen2005} opted for a hybrid approach, 
combining the advantages of a 2D decomposition technique 
with the insight gained from a 1D isophotal analysis. 
In this exemplary study, the authors modelled the images of 24 early-type disc galaxies (S0/S0a) 
accounting for bulge, disc, bars, ovals/lenses\footnote{According to their nomenclature, 
an egg-shaped structure (with axis ratio $b/a \gtrsim 0.85$) 
embedded within the large-scale disc of a galaxy 
is dubbed lens or oval in case of a lenticular or spiral galaxy, respectively. 
Lenses/ovals and pseudobulges might have similar ellipticities, 
but the former typically have lower surface brightness and sharper outer edges than the latter 
\citep{kormendykennicutt2004}. }, and inner discs. 
Their decomposition method was assessed on synthetic images of galaxies composed of a bulge, 
a large-scale disc, and a bar. 
They tested the effects of the omission of the bar component from the galaxy model. 
While a three-component (bulge+disc+bar) model was correctly recovering the real bulge parameters, 
a two-component (bulge+disc) model was overestimating the bulge luminosity by up to 40\% 
because the S\'ersic model for the bulge was somehow ``forced'' to account also for the bar. 
They also experimented with a large number of different weighting maps, 
and concluded that the results from the fit were not significantly dependent on the choice of the weighting function,
unless the signal-to-noise of the galaxy image was extremely low, 
or a prominent component was not included in the model. 
In addition, they pointed out that a fit lacking seeing correction resulted in notably biased bulge parameters. 
\cite{laurikainen2005} stressed an important point about galaxy decomposition: 
in order to have control of the physical meaning of the different components in a galaxy, 
\emph{a priori} evaluation of the existence of such components is required. 
This concept is opposed to the (nowadays popular) approach of repeating the fit of a galaxy 
by continuously increasing the number of model components 
until all residual structures are eliminated from the residual image.  
\cite{laurikainen2005} used three different methods to identify the structural components of a galaxy:
they inspected (\emph{i}) the radial profiles of ellipticity and position angle of the galaxy's isophotes, 
whose bumps often correspond to bars, ovals/lenses, and inner discs 
when these components are sufficiently bright compared to the large-scale disc, 
(\emph{ii}) the radial profiles of low azimuthal wavenumber Fourier amplitudes and phases, 
sensitive to weak bars and ovals/lenses, 
and (\emph{iii}) the unsharp masks\footnote{Unsharp masks are obtained from the original images 
with a mathematical operation of convolution. By suppressing large-scale, low-frequency variations 
in the images, they act as a filter and reveal faint asymmetric structures within the galaxies 
\citep{malinzealey1979,erwinsparke2003}.}, useful to reveal the innermost structures. 
Upon comparing the results from their three-component decompositions 
with those obtained from the two-component decompositions of \cite{simiendevaucouleurs1986} in the B-band 
and \cite{desouza2004} in the K$_S$-band, 
\cite{laurikainen2005} noted that their bulge-to-total ratios were considerably smaller for all Hubble types. 
This large discrepancy was not due to the wavelength used, 
but to the fact that, when a galaxy model does not account for a bar, 
a large fraction of the bar light erroneously goes into the bulge model, 
artificially increasing the bulge-to-total ratio. 
This sophisticated decomposition method was applied to the analysis of 175 early-type disc galaxies 
using deep near-infrared imaging \citep{laurikainen2007,laurikainen2010},  
and the results from these decompositions were used for a detailed study of bars, ovals/lenses and bulges. 
They found ovals/lenses in 70\% of the S0/S0a galaxy sample, 
and nuclear components (bars/rings/discs) in 50\% of them.

\subsection{Photometry and kinematics}
\label{sec:photokin}
Early-type galaxies can exhibit a wide variety of kinematic features, 
going from the fainter rotationally-supported systems to the brighter dispersion-dominated ones (e.g.~\citealt{davies1983}). 
While the identification of stellar discs in images of spiral galaxies is generally trivial thanks to the presence of spiral arms, 
featureless discs in bright, early-type galaxies can be particularly hard to recognise 
by looking at the photometry alone, due to well-known inclination effects (e.g.\citealt{rixwhite1990,gerhardbinney1996}). 
However, this problem can be alleviated with the use of kinematic information
(e.g.~\citealt{carter1987,franx1989,nieto1991,rixwhite1992,cinzanovandermarel1993,donofrio1995,graham1998fornax}).
In particular, our understanding of the internal structure of early-type galaxies has undoubtedly improved over the past decade 
thanks to the introduction of integral-field spectrographs and the analysis of two-dimensional kinematic maps 
(e.g.~the ATLAS$^{\rm 3D}$ survey, \citealt{cappellari2011}). \\

\cite{emsellem2007} used the specific angular momentum within one effective radius 
($\lambda_{\rm R} = \langle R |V| \rangle / \langle R \sqrt{V^2 + \sigma^2} \rangle $, 
where $R$ is the semimajor-axis radius, $V$ is the mean velocity and $\sigma$ is the velocity dispersion)  
and the ellipticity at one effective radius 
($\epsilon = 1 - (b/a)$, 
where $(b/a)$ is the ratio of minor-to-major axis length) 
to classify early-type galaxies into fast rotators and slow rotators, 
based on the empirical divide $\lambda_{\rm R} = 0.31 \sqrt{\epsilon}$. \\

\cite{krajnovic2006} developed ``kinemetry'', 
a method that combines surface photometry and kinematics 
to recognise less obvious structures in galaxies, such as embedded discs and kinematic subcomponents. 
Using kinemetry, \cite{krajnovic2011} measured the regularity of velocity maps 
and demonstrated that fast rotators are typically nearly axisymmetric systems, 
whereas most slow rotators are triaxial systems. 
At present, the joint effort of imaging and integral-field spectroscopy is undeniably our best chance 
to disclose the internal structure of galaxies (e.g.~\citealt{krajnovic2015IAUS}).  \\

Putting this paradigm into practice, 
\cite{krajnovic2013} compared photometric signatures and kinematic properties of stellar discs 
for the 180 unbarred early-type galaxies of the ATLAS$^{\rm 3D}$ sample. 
For each galaxy, they fit the light distribution using a single bulge \citep{sersic1963,sersic1968} 
and a bulge+disc (S\'ersic+exponential) model, 
preferring the latter when the improvement over the single bulge model was substantial 
and no correlation within the residuals was observed. 
They found that exponential sub-components in fast rotators correspond 
to a genuine family of rotationally-supported discs or disc-like structures, 
which were identified in 83\% of the unbarred early-type subsample,
contributing to 40\% of the total stellar mass and  
covering a full range of disc-to-total flux ratios. 
From their analysis, \cite{krajnovic2013} concluded that, when using photometry only, 
inclination effects do not particularly affect the identification of dominant discs, 
but they become much more disruptive when dealing with low-inclination, medium size discs. 
The use of kinematics is therefore the best approach to mitigate inclination effects. 
One of the key results obtained by the ATLAS$^{\rm 3D}$ Collaboration is that 
the majority of early-type galaxies contain stellar discs 
with an essentially continuous distribution of disc-to-total flux ratios, 
which led \cite{cappellari2011} to the introduction of a new classification scheme 
aimed at replacing the classical Hubble diagram. \\

\subsection{A compendium of the previous literature }
Over the past nine years, five independent studies 
\citep{grahamdriver2007,sani2011,vika2012,beifiori2012,lasker2014data,lasker2014anal}
have attempted galaxy decomposition 
for samples of galaxies with a direct measure of the black hole mass. 
The main aim of each study was to derive the parameters of the spheroidal components of their galaxies 
and explore correlation with the black hole mass.
Table \ref{tab:lit} summarises the main characteristics and findings of each work. 
%The last column refers to the study presented in this thesis 
%and highlights its improvements over the past literature.

\begin{table}[ht] 
\footnotesize
%\small
\centering 
\begin{tabular}{llllll}
\hline\hline 
		       & {\bf GD07}	 & {\bf S+11}	   & {\bf V+12} & {\bf B+12}  & {\bf L+14} \\ 	      %& {\bf This work}   \\ 
\hline \\ [-1.5ex]
{\bf Galaxies }        & 27		 & 57		   & 25 	& 19	      & 35	   \\	      %& 66		  \\
{\bf Wavelength }      & R-band 	 & $3.6~\mu \rm m$ & K-band	& $i$-band    & K-band     \\	      %& $3.6~\mu \rm m$   \\
{\bf Decomposition}    & 1D		 & 2D		   & 2D 	& 2D	      & 2D	   \\	      %& 1D \& 2D	  \\
{\bf Nuclei }	       & masked 	 & modelled	   & modelled	& not treated & modelled    \\	      %& modelled/masked    \\
{\bf Cores }	       & masked 	 & masked	   & masked	& not treated & masked     \\ 	      %& masked  	  \\ 
{\bf Bars }	       & excluded	 & modelled	   & modelled	& excluded    & modelled    \\ 	      %& modelled 	  \\ 
{\bf Other components} & no		 & no		   & no 	& no	      & yes	   \\ 	      %& yes		  \\ 
{\bf Kinematics}       & no		 & no		   & no 	& no	      & no	   \\ [0.5ex] %& yes		  \\ [0.5ex] 
\hline
\multicolumn{6}{c}{\emph{Conclusions}} \\ 
\hline \\ [-1.5ex]
$\boldsymbol{ M_{\rm BH}-n_{\rm sph}}$  		& yes	& no	     & no  & no        & -	     \\ 	%& -   \\
$\boldsymbol{ M_{\rm BH}-L_{\rm sph}}$  		& -	& yes	     & yes & yes       & fundamental \\ 	%& -   \\
$\boldsymbol{ M_{\rm BH}-M_{\rm sph,dyn}}$		& -	& yes	     & -   & yes       & -	     \\ 	%& -   \\
$\boldsymbol{ M_{\rm BH}-M_{\rm sph,*}}$		& -	& yes	     & -   & -         & -	     \\ 	%& -   \\
$\boldsymbol{ M_{\rm BH}-R_{\rm e}}$			& -	& secondary  & -   & -         & -	     \\ 	%& -   \\
$\boldsymbol{ M_{\rm BH}-\langle \mu_{\rm e} \rangle}$  & -	& -	     & -   & no        & -	     \\ 	%& -   \\
$\boldsymbol{ M_{\rm BH}-L_{\rm gal}}$  		& -	& -	     & -   & secondary & fundamental \\ [0.5ex] %& -   \\ [0.5ex] 
\hline 
\hline 
\end{tabular}
\caption{ Main characteristics and findings of the latest five studies that have attempted galaxy decomposition 
to derive and explore black hole mass scaling relations. 
The number of galaxies accounts only for those with a direct measurement of the black hole mass 
(no upper limits are considered here). 
GD07 = \cite{grahamdriver2007}; S+11 = \cite{sani2011}; V+12 = \cite{vika2012}; B+12 = \cite{beifiori2012}; 
L+14 = \cite{lasker2014data,lasker2014anal}.}
\label{tab:lit} 
\end{table}

\cite{sani2011} used galaxy images 
obtained with the \emph{Spitzer} satellite in the $3.6~\mu \rm m$ wavelength-band, 
which currently represents the best proxy for the stellar mass, 
even superior to the K-band (\citealt{sheth2010}, and references therein). \\

%Besides using the largest sample of galaxies to date, 
%this work is based on observations in the $3.6~\mu \rm m$ wavelength-band, obtained with the \emph{Spitzer} satellite,
%which currently represents the best proxy for the stellar mass (\citealt{sheth2010}, and references therein). 
There has been an ongoing debate as to whether 2D galaxy decomposition techniques should be preferred over 1D techniques. 
The performance of each method can vary according to different technical factors 
(such as the signal-to-noise of the galaxy images, the accuracy of the description of the Point Spread Function, 
the gradient of ellipticity and position angle of the galaxy isophotes, 
the fitting weighting scheme, etc.), 
therefore advantages and disadvantages are not absolute and depend on the individual science case. 
To our best knowledge, 
no published study has ever been conducted on a systematic comparison between 1D and 2D galaxy decomposition techniques. \\

%we chose to experiment with both methods and compare the results. 
Previous works have demonstrated that, when studying galaxies with a complex morphology, 
the accuracy of the recovery of the bulge parameters increases 
when all galaxy components are taken into account by the model  
\citep{laurikainen2005,gadotti2008,salo2015}. 
\cite{lasker2014data} identified and modelled more galaxy components than any other study,
but no work did it with the assistance of kinematical information. \\

Interestingly, the past studies all used almost the same sample of galaxies 
(the number of directly measured black hole masses increased with time), 
but they claimed some contradictory conclusions. 
One study obtained a good $M_{\rm BH}-n_{\rm sph}$ correlation, whereas three did not.
\cite{lasker2014anal} elected the $M_{\rm BH}-L_{\rm gal}$ relation as the fundamental one
(likewise the $M_{\rm BH}-L_{\rm sph}$), 
as opposed to \cite{beifiori2012}, who presented it as a secondary correlation.
The past studies did not converge to the same conclusions 
because their best-fit models for the same galaxy were often 
significantly different and not consistent with each other in terms 
of fitted components. 
Moreover, none of these studies attempted an individual galaxy-by-galaxy 
comparison of their models with the previous literature. 
%We have now made this comparison, identified the optimal decomposition, 
%and obtained improved black hole mass scaling relations using a large sample of galaxies.
%Our work will also present a comparison between 1D and 2D galaxy decompositions.

\section{Thesis outline}
The aim of this thesis is to refine and re-investigate several black hole mass scaling relations 
through the careful modelling of the spatial light distribution 
of a selected sample of 66 nearby galaxies. 
After obtaining robust structural parameters for the galaxies under study, 
I will explore substructure in the correlations between these parameters and the black hole mass, 
and explain discrepancies in the results presented in the past literature. \\

In Chapter \ref{ch:recov-mn} \citep{savorgnan2013}, 
we tackle the issue of the $M_{\rm BH} - n_{\rm sph}$ correlation using literature data. 
Four studies independently carried out photometric decompositions for similar samples of galaxies, 
but only one of them obtained a statistically significant $M_{\rm BH} - n_{\rm sph}$ relation. 
For each galaxy analysed by two or more studies, 
we compared the models used to fit the galaxy's spatial distribution of light, 
and found that the same galaxy was often described with remarkably different models 
in terms of number and type of sub-components. 
This was obviously resulting in significantly different best-fit parameters. 
We then collected the S\'ersic index measurements obtained by the four studies for 54 common galaxies 
with a direct measure of their black hole mass, 
rejected the most discrepant values, 
and used the remaining measurements to populate the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Besides recovering a statistically significant $M_{\rm BH} - n_{\rm sph}$ relation for all galaxies, 
we also explored substructure for different galaxy morphological types 
(elliptical galaxies versus bulges of disc galaxies)
and nature of the nuclear light profile (S\'ersic versus core-S\'ersic). \\

In Chapter \ref{ch:galviv} \citep{paperI}, 
we present the 1D decompositions carried out by us for 66 local galaxies 
with a direct measure of their black hole mass. 
We describe the careful data reduction process through which 
we created the image-mosaics for these galaxies, 
using archival observations at $3.6~\mu \rm m$ obtained with \emph{Spitzer}. 
We detail our 1D galaxy decomposition technique and our method to estimate the uncertainties 
associated with the spheroid's best-fit parameters. 
Upon comparing the results obtained from our 1D and 2D galaxy models, 
we comment on the advantages and disadvantages connected with 1D and 2D decomposition techniques. 
The individual 1D galaxy decompositions are illustrated, 
along with a thorough analysis of each galaxy's structure 
and a scrupulous comparison with several past decompositions. \\

In Chapter \ref{ch:mm} \citep{paperII}, 
we use the results from our 1D galaxy decompositions 
to explore substructure in the $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ 
(or $M_{\rm BH} - M_{\rm *,sph}$) diagrams 
for different galaxy morphological types and nature of the nuclear light profile. 
Upon performing a detailed linear regression analysis using three different routines, 
we concluded that early-type (elliptical+lenticular) and late-type (spiral) galaxies 
follow two separate correlations in the $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) diagram. 
In addition, we compared the level of intrinsic scatter 
in the $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams 
to address the question of whether or not the $M_{\rm BH} - L_{\rm sph}$ correlation 
is more fundamental than the $M_{\rm BH} - L_{\rm gal}$ correlation. \\

In Chapter \ref{ch:mn} \citep{paperIII}, 
we use the results from our 1D galaxy decompositions to populate 
the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
The analysis that we performed here is essentially analogous to that presented in Chapter \ref{ch:mm}.  
We did not observe any significant substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
where all galaxies, irrespective of their morphological type, define a single tight correlation. 
Consistency between the $M_{\rm BH} - n_{\rm sph}$ and other galaxy scaling relations 
is dicussed here.  \\

In Chapter \ref{ch:msigma} \citep{savorgnangraham2015}, 
we concentrate on the $M_{\rm BH} - \sigma_*$ scaling relation 
and the presence of some outlying, ``overmassive'' black holes at the high-mass end of this correlation. 
\cite{volontericiotti2013} proposed a theoretical interpretation 
to explain why central cluster galaxies tend to appear as positive outliers 
in the $M_{\rm BH} - \sigma_*$ diagram, lying above the observed $z=0$ correlation. 
According to the results from their semi-analytical models, 
central cluster galaxies experienced more dry mergers 
than the ``average'' population of massive early-type galaxies. 
Dry mergers are expected to increase the black hole mass, 
while leaving almost unchanged the stellar velocity dispersion. 
We tested the interpretation offered by \cite{volontericiotti2013} 
using the latest observational data. 
First, we updated the $M_{\rm BH} - \sigma_*$ diagram with a total of 89 galaxies 
and performed a linear regression analysis of it. 
Then, for each galaxy with a parially depleted core 
we measured the extent of dry mergers experienced by the galaxy 
by means of the ratio between the central stellar mass deficit and the black hole mass. 
We showed that no positive trend is observed between the number of dry mergers 
and the positive vertical offset from the $M_{\rm BH} - \sigma_*$ correlation. 
A similar test using the kinematics of galaxies gave consistent results, 
disproving the scenario advocated by \cite{volontericiotti2013}. \\

In Chapter \ref{ch:ellic} \citep{ellicular}, 
we tackle the issue of the ``overmassive'' black holes 
in the $M_{\rm BH} - M_{\rm *,sph}$ diagram. 
Due to inaccurate decompositions that failed to take into account the correct size of the main disc component, 
a number of galaxies (Mrk 1216, NGC 1271, NGC 1277, and NGC 1332) had their spheroid luminosity underestimated, 
which made them appear as positive outliers above the $M_{\rm BH} - M_{\rm *,sph}$ correlation. 
With the aid of photometric and kinematic information, 
we identified the radial extent of the main disc component, 
and built a galaxy model accordingly. 
We showed that when these galaxies are correctly modelled, 
they lie well within the scatter of the observed $M_{\rm BH} - M_{\rm *,sph}$ correlation. \\

Finally, Chapter \ref{ch:concl} contains a summary of my principal findings, conclusions, 
and some promising directions for future research.

### 2016-02-26 thesis/mm.tex
added thesis

\chapter{$M_{\rm BH} - L_{\rm gal}$, $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ }
\label{ch:mm}

In Chapter \ref{ch:galviv}, reliable and accurate multicomponent decompositions were presented 
for 66 galaxies out of the 75 belonging to the initial sample. 
These 66 galaxies constitute our final sample, 
which is currently the largest sample to date used to investigate correlations between 
directly measured black hole masses and host galaxy parameters. \\

This Chapter is dedicated to the analysis of three black hole mass correlations: 
the $M_{\rm BH} - L_{\rm gal}$, $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ relations. 
Four principal questions will be addressed.

\begin{enumerate}

\item Is the $M_{\rm BH} - L_{\rm sph}$ relation more fundamental than the $M_{\rm BH} - L_{\rm gal}$ relation 
      (e.g.~\citealt{kormendyho2013}), 
      or are they equally important (e.g.~\citealt{lasker2014anal})?

\item \cite{grahamscott2013} identified two different sequences of spheroids in the $M_{\rm BH} - L_{\rm sph}$ 
      diagram, namely S\'ersic and core-S\'ersic. 
      However, their bulge luminosities were not derived from individual galaxy decompositions, 
      but they were inferred from observed, total galaxy magnitudes 
      through a mean statistical correction. 
      Do we recover their result here, using the present dataset?

\item Does the quality of the present dataset allow us to identify any (additional) substructure 
      in the three diagrams under study?

\item Some studies have distinguished pseudobulges and classical bulges according to their S\'ersic index, 
      and claimed that in the $M_{\rm BH} - L_{\rm sph}$ diagram 
      pseudobulges are offset from the correlation defined by classical bulges. 
      Here we test this result with our data.

\end{enumerate}

A robust linear regression analysis is crucial for the study of black hole mass correlations.
In particular, more emphasis is typically given to the slope rather than the intercept of scaling relations, 
because the slope is the parameter that theoretical models (currently) predict. 
Several studies (e.g.~\citealt{tremaine2002,graham2007,tundo2007,graham2016review}) 
have pointed out inconsistencies between the values of the slope
measured by different groups for the same correlation. 
These discrepancies can arise from the use of different galaxy samples, 
selection biases, or the statistical techniques used to perform the linear regression analysis. \\

In the following analysis, we will make use of three linear regression routines: 
the {\tt BCES} code from \cite{akritasbershady1996}, 
the {\tt FITEXY} routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
Albeit its remarkable computational speed, 
the {\tt BCES} estimator is not reliable in case of poor number statistics of the galaxy sample analysed, 
or when at least one low-precision measurement is included in the dataset, 
or if the mean square of the uncertainties associated with the independent variable is comparable to 
the variance of the distribution of the independent variable \citep{tremaine2002}. 
When any of these circumstances occur, 
the modified {\tt FITEXY} routine and the Bayesian estimator {\tt linmix\_err} 
perform better than the {\tt BCES} routine \citep{tremaine2002,novak2006,park2012}. 
All of these three estimators take into account the intrinsic scatter of a correlation, 
but only the {\tt FITEXY} and the {\tt linmix\_err} codes allow one to measure it. 
The interest in measuring the intrinsic scatter of black hole mass scaling relations 
relies on the assumption that 
the galaxy parameter associated with the smallest intrinsic residual variance 
has the best chance of being causally correlated to the black hole mass. \\

The remainder of this chapter comprises the published version of the paper 
``Supermassive Black Holes and Their Host Spheroids. 
II. The Red and Blue Sequence in the $M_{\rm BH} - M_{\rm *,sph}$ Diagram'' 
by G.~A.~D.~Savorgnan et al.,  
as it appears in Volume 817 of the \emph{The Astrophysical Journal}.

\includepdf[pages={1-12}]{ApJ2016.pdf}

### 2016-02-26 thesis/mn.tex
added thesis

\chapter{$M_{\rm BH} - n_{\rm sph}$}
\label{ch:mn}

chapter x was dedicated to recovery of mn correlation with literature data

now we can do better with high quality data set

consistency with other correlations

good uncertainties -> robust estimate of intr scatter -> comparison with m-l

The remainder of this chapter comprises the published version of the paper 
``Supermassive Black Holes and Their Host Spheroids. 
III. The $M_{\rm BH} - n_{\rm sph}$ correlation'' 
by G.~A.~D.~Savorgnan,  
as it appears in Volume xxx of the \emph{The Astrophysical Journal}.

\includepdf[pages={1-10}]{mbhn.pdf}

### 2016-02-26 thesis/recovery-mn.tex
added thesis

\chapter{The recovery of the $M_{\rm BH} - n_{\rm sph}$ relation}
\label{ch:recov-mn}

\cite{graham2001} demonstrated that the mass of SMBHs is correlated 
to the stellar light concentration of their host spheroid. 
Six years later, \cite{grahamdriver2007} expanded the galaxy sample of \cite{graham2001} 
and carried out 1D bulge/disc decompositions. 
They described the 1D surface brightness profile of spheroids with the S\'ersic model, 
and obtained a direct measure of the central radial concentration of stars 
by means of the S\'ersic index. 
\cite{grahamdriver2007} confirmed the early findings of \cite{graham2001}, 
presenting a strong correlation between the black hole mass and the spheroid S\'ersic index ($M_{\rm BH} - n_{\rm sph}$). 
They measured a small level of scatter, 
which made the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - \sigma_*$ correlations 
evenly competing for the title of fundamental black hole mass scaling relation. \\

As the number of directly measured black hole masses increased with time and
the constantly improving technology of machines allowed shorter computational times for 2D decomposition codes, 
more studies were dedicated to the analysis of various black hole mass scaling relations. 
\cite{sani2011}, \cite{vika2012}, and \cite{beifiori2012} attempted 2D decompositions 
of their samples of galaxies with a direct measure of the black hole mass. 
\citeauthor{sani2011} and \citeauthor{vika2012} included more than two components in their galaxy models 
-- such as bars and nuclear sources -- 
whereas \citeauthor{beifiori2012} excluded barred galaxies from their analysis. 
From these decompositions, they derived and analysed several correlations. 
However, none of these three studies was able to obtain a strong $M_{\rm BH} - n_{\rm sph}$ relation from their data. 
This raised an obvious question: 
what prevented \citeauthor{sani2011}, \citeauthor{vika2012}, and \citeauthor{beifiori2012} 
from the recovery of a tight $M_{\rm BH} - n_{\rm sph}$ correlation? 
Imputable factors could be the decomposition technique (1D versus 2D), 
the use of more sophisticated models featuring a larger number of components, 
the use of different wavelengths, 
or possibly the accuracy of the decompositions. \\

These circumstances motivated us to engage a preliminary study in 2012, 
aiming at explaining the lack of an $M_{\rm BH} - n_{\rm sph}$ correlation 
in the data of \citeauthor{sani2011}, \citeauthor{vika2012}, and \citeauthor{beifiori2012} 
After collecting and comparing the results from the galaxy decompositions 
of the aforementioned four studies (\citeauthor{grahamdriver2007}, \citeauthor{sani2011}, 
\citeauthor{vika2012}, and \citeauthor{beifiori2012}), 
we immediately noticed that some galaxies had been described with significantly different models 
(e.g.~the galaxy M60, treated as a discless elliptical galaxy by two studies, 
and as a lenticular galaxy by the other two studies). 
Different galaxy models (for the same galaxy) evidently resulted in different best-fit parameters. 
Not only this, but some studies obtained largely discrepant best-fit parameters 
for the same galaxy even though they used the same choice of decomposition 
(e.g.~two studies described the galaxy NGC 3115 with a S\'ersic-bulge + exponential-disc model, 
but obtained a bulge S\'ersic index of $3$ and $13$, respectively). 
This confirmed doubts about the accuracy of some decompositions. \\

For each galaxy, we averaged the available S\'ersic index measurements 
and used these average values to populate the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Immediately, we noticed that a clear correlation was emerging from the data, 
although with a significant amount of scatter. 
We attributed the large amount of scatter to ``bad'' decompositions, 
and decided to develop a method for an impartial identification of the ``bad'' S\'ersic index measurements. 
After estimating a maximum tolerable disagreement between the S\'ersic index measurements of the same galaxy 
by taking into account the use of different decomposition methods and wavelengths, 
we excluded the most discrepant measurements and averaged the remaining ones. 
This resulted in a dramatic reduction of scatter 
and the recovery of a strong $M_{\rm BH} - n_{\rm sph}$ correlation. 
Finally, we explored substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram 
expected for consistency with other known scaling relations. \\

The remainder of this chapter comprises the published version of the paper 
``The supermassive black hole mass -- S\'ersic index relations for bulges and elliptical galaxies''
by G.~A.~D.~Savorgnan et al., 
as it appears in Volume 434 of \emph{Monthly Notices of the Royal Astronomical Society}.

\includepdf[pages={1-11}]{MNRAS2013.pdf}

### 2016-02-26 thesis/ubermassive-msigma.tex
added thesis

\chapter{m-sigma}
\label{ch:msigma}

A precise measurement of the log-slope of the $M_{\rm BH} - \sigma$ correlation is important 
to constrain theoretical models of AGN feedback. 
For example, energy driven outflows are expected to produce a scaling of $M_{\rm BH} \propto \sigma^5$, 
whereas momentum driven outflows should result into a shallower $M_{\rm BH} \propto \sigma^4$ relation 
\citep{silkrees1998,fabian1999}. 
Since the $M_{\rm BH} - \sigma$ correlation was presented for the first time by \citet{ferraresemerritt2000}
and \citet{gebhardt2000}, 
there has been an ongoing, lively debate about its log-slope, 
whose estimates differed by up to a few standard deviations 
depending on the choice of galaxy sample, the method used to measure the velocity dispersion,
the assumed uncertainty associated with the velocity dispersion, 
and the linear regression algorithm (e.g.~\citealt{tremaine2002}). \\

Recent measurements of SMBH masses in Central Cluster Galaxies (CCGs)
have added new data points at the high-mass end of the 
$M_{\rm BH} - \sigma$ diagram \citep{mcconnell2011,mcconnell2012}, 
which appear to be outlying (``over-massive'') with respect to the observed correlation. 
\citet{volontericiotti2013} explained the presence of over-massive black holes in CCGs 
(they included in this definition either central dominant galaxies or brightest cluster galaxies) 
as a natural consequence of the fact that these galaxies have experienced more dry mergers 
than any other early-type galaxy. 
Their semi-analytical models are based on the idea that parabolic dissipationless dry mergers 
increase a galaxy's mass, luminosity and effective radius, 
but do not significantly change its velocity dispersion (e.g.~\citealt{ciotti2007}). 
Let an elliptical galaxy be a non rotating, isotropic and virialized spheroidal system 
with stellar mass $M_{*}$ and gas mass $M_{\rm g} = \alpha M_{*}$. 
The total energy $E$ of this galaxy is the sum of its total kinetic energy $K$ and its total gravitational energy $W$. 
The total kinetic energy is given by the sum of the stellar kinetic energy $K_*$ and the gas internal energy $K_{\rm g}$, 
therefore the total energy can be expressed as:
\begin{equation}
E = K_* + K_{\rm g} + W \ .
\end{equation}
The stellar kinetic energy is 
\begin{equation}
K_* = \frac{3}{2} M_* \sigma_*^2 \ ,
\end{equation}
where $\sigma_*$ is the stellar velocity dispersion. \\
The gas internal energy is defined as 
\begin{equation}
K_{\rm g} = \frac{3}{2} \frac{k_{\rm B}}{\bar{m} } \int_{\mathcal{V}} \rho_{\rm g} T d\mathcal{V} \ ,
\end{equation}
where $k_{\rm B}$ is the Boltzmann constant, $\bar{m}$ is the gas mean molecular mass, and 
$\rho_{\rm g}$ and $T$ are the density spatial distribution and the temperature of the gas, respectively, 
within the galaxy's volume $\mathcal{V}$. \\
The total gravitational energy is defined as 
\begin{equation}
W = \frac{1}{2} \int_{\mathcal{V}} (\rho_* + \rho_{\rm g}) (\phi_* + \phi_{\rm g}) d\mathcal{V} \ , 
\end{equation}
where $\rho_*$ is the density spatial distribution of stars, 
and $\phi_*$ and $\phi_{\rm g}$ indicate the gravitational potential of stars and gas, respectively. \\
Under the assumption of gas in equilibrium in the total gravitational field, 
from the Jeans and hydrostatic equations one has that $T = \bar{m} \sigma_*^2 / k_{\rm B}$ and thus 
\begin{equation}
K_{\rm g} = \alpha K_* \ .
\end{equation}
Assuming also that the spatial distribution of gas is proportional to that of stars (i.e.~$\rho_{\rm g} = \alpha \rho_*$ 
and $\phi_{\rm g} = \alpha \phi_*$), 
the total gravitational energy can be written as 
\begin{equation}
W = \frac{1}{2} (1+\alpha)^2 \int_{\mathcal{V}} \rho_* \phi_* d\mathcal{V} = (1+\alpha)^2 W_* \ ,
\end{equation}
where $W_*$ is the gravitational energy of the stellar component only. \\
From the virial theorem (i.e.~$E = K+W = W/2 = -2K$), the galaxy's total energy can be expressed as 
\begin{equation}
E = \frac{1}{2} (1+\alpha)^2 W_* = - (1+\alpha) K_* \ .
\end{equation}
We now consider the parabolic dissipationless merger of two galaxies (with stellar masses $M_{*1}$ and $M_{*2}$,
and total energies $E_1$ and $E_2$), 
i.e.~a merger where both the total energy and the total mass are conserved, 
and no gas is converted into stars. \\
The gas fraction $\alpha$ of the merger remnant is by definition
\begin{equation}
\alpha = \frac{M_{\rm g}}{M_*} = \frac{M_{\rm g1} + M_{\rm g2}}{M_{*1}+M_{*2}} \ ,
\end{equation}
where the nomenclature is self-esplicative. \\
By imposing the conservation of total energy, we get 
\begin{equation*}
E = E_1 + E_2 
\end{equation*}
\begin{equation*}
-(1+\alpha) \frac{3}{2} M_* \sigma_*^2 = -(1+\alpha_1) \frac{3}{2} M_{*1} \sigma_{*1}^2 -(1+\alpha_2) \frac{3}{2} M_{*2} \sigma_{*2}^2 \\
\end{equation*}
\begin{equation*}
\bigl[ (1+\alpha_1)M_{*1} + (1+\alpha_2)M_{*2} \bigr ] \sigma_*^2 = (1+\alpha_1)M_{*1}\sigma_{*1}^2 + (1+\alpha_2)M_{*2}\sigma_{*2}^2
\end{equation*}
\begin{equation}
\sigma_*^2 = \frac{(1+\alpha_1)M_{*1}\sigma_{*1}^2 + (1+\alpha_2)M_{*2}\sigma_{*2}^2}{\bigl[ (1+\alpha_1)M_{*1} + (1+\alpha_2)M_{*2} \bigr ]} \ .
\label{eq:sigma*2}
\end{equation}
By defining $c_1 = (1+\alpha_1)M_{*1}/\bigl[ (1+\alpha_1)M_{*1} + (1+\alpha_2)M_{*2} \bigr ]$ 
and $c_2 = (1+\alpha_2)M_{*2}/\bigl[ (1+\alpha_1)M_{*1} + (1+\alpha_2)M_{*2} \bigr ]$, 
Equation \ref{eq:sigma*2} can be simplified as 
\begin{equation}
\sigma_*^2 = c_1 \sigma_{*1}^2 + c_2 \sigma_{*2}^2 \ .
\end{equation}
Finally, since $c_1 + c_2 = 1$, we have that 
\begin{equation}
\min(\sigma_{*1}^2, \sigma_{*2}^2) \leq \sigma_*^2 \leq \max(\sigma_{*1}^2, \sigma_{*2}^2) \ ,
\end{equation}
that is, the velocity dispersion of the merger remnant cannot be larger 
than the maximum velocity dispersion of the progenitor galaxies. 
This conclusion is not true in case of a wet merger or non-parabolic (i.e.~bound) orbits of the progenitors. \\

Whether or not considering the over-massive black holes as an ``exception to the rule'', 
or in other words legitimately excluding them from the linear regression analysis of the $M_{\rm BH} - \sigma$ diagram, 
obviously has an impact on the estimate of the log-slope of the correlation. 
Therefore, it is important to test the scenario proposed by \citet{volontericiotti2013} 
with empirical data. \\

The remainder of this chapter comprises the published version of the paper 
``Overmassive black holes in the $M_{\rm BH} - \sigma$ diagram 
do not belong to over (dry) merged galaxies'' 
by G.~A.~D.~Savorgnan \& A.~W.~Graham,  
as it appears in Volume 446 of \emph{Monthly Notices of the Royal Astronomical Society}.

\includepdf[pages={1-7}]{MNRAS2015.pdf}

### 2016-02-26 thesis/thesis.sh

@@ -1,0 +1,5 @@
+pdflatex thesis
+bibtex thesis
+pdflatex thesis
+bibtex thesis
+pdflatex thesis

### 2016-03-01 thesis/conclusions.tex
finished ellicular, started conclusions

\chapter{concl}
\label{ch:concl}

In this thesis, we explored several scaling relations between the supermassive black hole mass 
and various properties of the host spheroid, 
aiming at gaining a more profound understanding of the co-evolution between SMBHs and galaxies. 
A summary of our principal findings and some additional brief considerations about them are presented here. 
The end of this Chapter incorporates some promising future research directions. \\

In Chapter \ref{ch:recov-mn} \citep{savorgnan2013}, we compared the results obtained by four independent studies 
\citep{grahamdriver2007,sani2011,vika2012,beifiori2012}
that attempted photometric decompositions for similar samples of galaxies with a direct measurement 
of the black hole mass. 
In many cases, we found a large discrepancy between the S\'ersic index measurements 
obtained by different studies for the spheroidal component of the same galaxy, 
either due to a significantly different choice of model components 
or to various systematic effects that led to inaccurate decompositions. 
By rejecting the most discrepant S\'ersic index measurements and averaging the remaining ones, 
we were able to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation, 
which was not found in the individual datasets of three of the four studies.

### 2016-03-01 thesis/ellicular.tex
finished ellicular, started conclusions

@@
 that is, over-massive black holes in the $M_{\rm BH} - L_{\rm sph}$ diagram, 
-the variety of intrisic angular momentum radial profiles in local early-type galaxies, 
+the variety of bulge-to-disc ratios in local early-type galaxies, 
 and the evolution of the mass-size relationship from $z=2$ to $z=0$. 
-While an overview about the $M_{\rm BH} - L_{\rm sph}$ outliers was given in Section \ref{sec:monsters}, 
-the second topic was only briefly touched in Section \ref{sec:photokin}, 
-and no mention of the mass-size relation was made in Chapter \ref{ch:intro} 
+While an overview about the first two topics was given in Sections \ref{sec:monsters} and \ref{sec:photokin}, 
+no mention of the mass-size relation was made in Chapter \ref{ch:intro} 
 because not immediately related to SMBHs. 
-Therefore, a more extensive introduction for these last two points is given here. \\
+Therefore, a more extensive introduction of this last point is given here. \\
 
+It has been claimed that high-redshift passive galaxies were significanly more compact 
+than their local counterparts. 
 \citet{daddi2005} reported on the observation of seven quiescent early-type galaxies 
@@
 have old stellar populations, negligible star formation, and sizes a factor of 5 smaller than 
-those of the local descendants.
-
-progenitor bias
-intermediate scale disc galaxies (arnold)
-
-compact massive spheroids
-
-n1277 paper
+those of local descendants, 
+and silimilar conclusions were reached by several other studies 
+(e.g.\citealt{toft2007,trujillo2007,zirm2007,buitrago2008,damjanov2009}). 
+While some studies have pointed out that ``progenitor bias''\footnote{``Progenitor bias'' refers to sample confusion 
+of the local descendants of high-redhift massive quiescent galaxies. 
+While some of the $z=0$ red-sequence galaxies might have had a passive evolution since $z \approx 2$, 
+other $z=0$ red-sequence galaxies might descend from $z \approx 2$ star-forming galaxies. } 
+(e.g.~\citealt{carollo2014}) might play an important role 
+when tracking the evolution of massive quiescent galaxies, 
+minor dry mergers have been commonly advocated to explain the size growth of these galaxies 
+(e.g.~\citealt{hopkins2009,carrasco2010,cimatti2012,fan2013,de2014}).
+However, not enough satellites have been found around massive galaxies 
+to support the minor dry mergers scenario 
+(e.g.~\citealt{khochfarburkert2006,maller2006,hopkins2009,naab2009,mclure2013}). 
+A fascinating solution to the problem was proposed by \citet{graham2013review}, 
+who suggested that the high-redshift compact massive spheroids have evolved into the bulges 
+of today's massive early-type disc galaxies (see also \citealt{dullograham2013cores} and \citealt{driver2013}). 
+This view was confirmed by \citet{gds2015}, 
+who used bulge/disc decomposition 
+to unveil a large number of previously unnoticed local stellar spheroidal systems 
+with the same structural properties, old stellar populations, 
+and similar number density as the high-redshift compact massive spheroids. 
+\citet{gds2015} advocated the growth of two-dimensional stellar disks around the compact massive spheroids 
+to explain the evolution of these objects. \\
 

### 2016-03-02 thesis/conclusions.tex
conclusions

@@
-\chapter{concl}
+\chapter{Final remarks}
 \label{ch:concl}
 
-In this thesis, we explored several scaling relations between the supermassive black hole mass 
+In this thesis, we explored scaling relations between the supermassive black hole mass 
 and various properties of the host spheroid, 
@@
 \citep{grahamdriver2007,sani2011,vika2012,beifiori2012}
-that attempted photometric decompositions for similar samples of galaxies with a direct measurement 
+that attempted photometric decompositions of similar samples of galaxies with a direct measurement 
 of the black hole mass. 
-In many cases, we found a large discrepancy between the S\'ersic index measurements 
+In many cases we found a large discrepancy between the S\'ersic index measurements 
 obtained by different studies for the spheroidal component of the same galaxy, 
 either due to a significantly different choice of model components 
-or to various systematic effects that led to inaccurate decompositions. 
+or to other various systematic effects. 
 By rejecting the most discrepant S\'ersic index measurements and averaging the remaining ones, 
-we were able to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation, 
-which was not found in the individual datasets of three of the four studies.
+we were able to recover a strong $M_{\rm BH} - n_{\rm sph}$ correlation, 
+which was not found using the individual datasets of three of the four studies. 
+From this we concluded that some of the galaxy decompositions were not accurate. 
+Chapter \ref{ch:recov-mn} emphasises the importance of a correct, physically motivated selection of model components 
+and cautions against the several systematics that can affect galaxy decomposition. \\
+
+Chapter \ref{ch:galviv} was dedicated to the careful multicomponent decomposition of 66 galaxies 
+with a direct measurement of the black hole mass. 
+We followed the same approach as \citet{laurikainen2005} in selecting the components for each galaxy model.  
+\emph{A priori} identification of the galaxy components was done on the basis of several different indicators 
+such as the analysis of the isophotal parameters, 
+the inspection of unsharp masks, 
+complementary information extracted from the literature, 
+and -- most importantly -- from the galaxy kinematics. 
+A joint photometric-kinematic approach (e.g.~\citealt{krajnovic2013,arnold2014}) 
+turned out to play a decisive role for the robustness of our galaxy modelling. 
+Upon examining central \citep{atlas3dIII,scott2014} and more extended \citep{arnold2014} velocity maps 
+and comparing kinematic and photometric signatures of stellar discs, 
+we were able to securely identify the presence and the radial extent of such discs. 
+We observed a wide range of spheroid-to-disc ratios in early-type galaxies, 
+going from parsec-sized nuclear discs, to kiloparsec-sized intermediate- and large-scale discs, 
+in agreement with the findings of \citet{krajnovic2013}. 
+Comparison of our results with those obtained by previous studies indicates that 
+multicomponent models (as opposed to simple bulge/disc models) are necessary 
+to derive reliable structural parameters, confirming previous results 
+(e.g.~\citealt{laurikainen2005,laurikainen2007,laurikainen2010,lasker2014data,salo2015}). 
+In general, the best-fit parameters obtained with 1D and 2D decomposition techniques for the same galaxy 
+are consistent with each other, 
+i.e.~no systematic effects were noticed between 1D and 2D modelling. 
+However, our practical experience led us to prefer the 1D decomposition technique. 
+Advantages associated with the 1D technique are a higher convergence rate for the fits, 
+the wealth of information contained in the 1D isophotal analysis, 
+and the easier interpretation of the 1D residuals. 
+We caution against the dangerous practice of identifying unsubtracted galaxy components 
+from the residual image of a 2D fit. 
+As an additional warning, 
+given the level of detail to which our galaxy decompositions were carried out, 
+we do not consider possible for current automatic routines to reproduce our analysis. \\
+
+In Chapter \ref{ch:mm}, we used our dataset to derive and explore 
+the $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) relations. 
+We identified two distinct trends in the $M_{\rm BH} - M_{\rm *,sph}$ diagram, 
+that is, a \emph{red sequence} of early-type galaxies (E+S0) 
+following $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$ 
+and a dramatically steeper \emph{blue sequence} of late-type galaxies (Sp) 
+following $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$.

### 2016-03-03 thesis/conclusions.tex
conclusions chapter 4

@@
 In Chapter \ref{ch:mm}, we used our dataset to derive and explore 
-the $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) relations. 
+the $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) diagrams. 
+When considering all galaxies, irrespective of their morphological type, 
+the $M_{\rm BH} - L_{\rm sph}$ correlation has a lower level of intrinsic scatter 
+than the $M_{\rm BH} - L_{\rm gal}$ correlation. 
+However, when considering only early-type galaxies (elliptical+lenticular), 
+$L_{\rm gal}$ and $L_{\rm sph}$ correlate equally well with $M_{\rm BH}$. 
+\citet{lasker2014anal} found the same level of intrinsic scatter in their 
+$M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams for all galaxies
+because their sample was highly biased towards early-type objects 
+(among their 35 galaxies, only four are spirals). 
+Our subsample of S\'ersic spheroids defines a less steep $M_{\rm BH} - L_{\rm sph}$ 
+sequence than previously reported by \citet{grahamscott2013}. 
+We do not observe any offset of spheroids with S\'ersic index $n_{\rm sph} < 2$ 
+from the $M_{\rm BH} - L_{\rm sph}$ correlation traced by spheroids with $n_{\rm sph} > 2$, 
+in disagreement with the claims of \citet{sani2011}. 
 We identified two distinct trends in the $M_{\rm BH} - M_{\rm *,sph}$ diagram, 
-that is, a \emph{red sequence} of early-type galaxies (E+S0) 
+that is, a \emph{red sequence} of early-type galaxies (elliptical+lenticular) 
 following $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$ 
-and a dramatically steeper \emph{blue sequence} of late-type galaxies (Sp) 
+and a dramatically steeper \emph{blue sequence} of late-type galaxies (spiral) 
 following $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$. 
+This is in agreement with the near-linear $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) correlation 
+measured by previous studies that used galaxy samples dominated by high-mass early type objects 
+(e.g.~\citealt{magorrian1998,marconihunt2003,haringrix2004,gultelkin2009,sani2011,beifiori2012,
+erwingadotti2012,vika2012}),  
+and it gives reason as to why other studies, 
+whose galaxy samples gave a better representation of the late-type population 
+with low-mass ($M_{\rm BH} \lesssim 10^8 \rm~M_\odot$) black holes, 
+obtained a correlation steeper than linear 
+or noticed super-linear deviations at the low-luminosity end of the diagram 
+(e.g.~\citealt{laor1998,laor2001,wandel1999,salucci2000,ryan2007}). 
+An interesting exception has been the under-linear $M_{\rm BH} \propto L_{\rm sph}^{0.75 \pm 0.10}$ 
+measured by \citet{lasker2014anal}, 
+who attributed the smaller log-slope of the correlation 
+to the reduction of bulge luminosities derived from their multicomponents fits 
+and to the type of linear regression algorithm used. 
+It is worth mentioning that, among our 17 spiral galaxies, at least 12 host a Seyfert nucleus. 
+\citet{wandel1999} and \citet{ryan2007} had previously noted that a linear $M_{\rm BH} - M_{\rm *,sph}$ relation 
+systematically overestimates the $M_{\rm BH}/M_{\rm *,sph}$ ratio in Seyfert galaxies. 
+In effect, the sample of $\approx 140$ low-redshift AGNs with virial black hole masses 
+$10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ collected by \citet{grahamscott2015} 
+appear to be the low-mass continuation of the $M_{\rm BH} - M_{\rm *,sph}$ sequence traced by our spiral galaxies. 
+Finally, we note that our estimate of the normalization of the $M_{\rm BH} - M_{\rm *,sph}$ relation for early-type galaxies 
+is the largest ever reported: $M_{\rm BH}/M_{\rm *,sph}$ is $\approx 0.7\%$ using our dataset, 
+whereas it is as low as $\approx 0.5\%$ in \citet{scott2013} and \citet{kormendyho2013}, 
+and even lower in previous studies. 
+A recalibration of the $M_{\rm BH} - M_{\rm *,sph}$ normalization has important consequences 
+for semi-analytical models and simulations of galaxy evolution that include black hole growth, 
+and it also affects calculations of gravitational waves background from SMBH binary coalescence 
+(but see Shankar et al.~\emph{submitted to MNRAS}). \\
+
+m-n? \\
+
+In Chapter \ref{ch:msigma}, we focused on the $M_{\rm BH} - \sigma$ diagram 
+and in particular on the over-massive black holes that have been reported to exist 
+at the high-mass end of the correlation. 
+\citet{volontericiotti2013} explained the presence of the outlying black holes 
+as a natural consequence of the fact that their host galaxies have experienced more dry mergers 
+than any other galaxy, 
+since dry mergers are expected to increase the black hole mass 
+and ``conserve'' the stellar velocity dispersion. 
+We tested and disproved this scenario for xx core-S\'ersic galaxies, 
+using the ratio between black hole mass and stellar mass deficit as a proxy 
+for the number of dry mergers experienced by the galaxy \citep{xxx}. 
+This was confirmed by a second test using the central kinematic classification of xx galaxies. 
+The slope of the m-sigma is this... 
+comparison

### 2016-03-07 papers/mbhn/mbhn.tex
conclusions ellicular

@@
 but they were a collection of results taken from various past bulge/disk decomposition studies. 
-%It is also worth mentioning that, 
-%although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
-%{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
 Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram (Figure \ref{fig:magn}) using only our high-quality dataset. 
@@
 whereas late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence. \\
-{\bf Because the log-slopes of the correlations for early- and late-type galaxies are not consistent with each other 
+Because the log-slopes of the correlations for early- and late-type galaxies are not consistent with each other 
 within their $1\sigma$ uncertainties, 
@@
 the $AICc$ value for a double power-law model is a factor of $3/4$ smaller 
-than the $AICc$ value for a single power-law model. }
+than the $AICc$ value for a single power-law model.
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mag_vs_n_maj.pdf}
-\caption{\bf Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
+%\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mag_vs_n_maj.pdf}
+\includegraphics[width=\columnwidth, trim = 20 0 220 0]{mag_vs_n_maj.pdf}
+\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
 measured along the galaxy major-axis. 
@@
 On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations. 
-%($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
-%and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
 Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
@@
 i.e.~we do not identify any significant substructure based on the galaxy morphological type. 
-{\bf The $AICc$ value for a single power-law model is a factor of $2/3$ smaller 
-than the $AICc$ value for a double power-law model. } \\
+The $AICc$ value for a single power-law model is a factor of $2/3$ smaller 
+than the $AICc$ value for a double power-law model.  \\
 The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
@@
 \begin{center}
-\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mbh_vs_n_maj.pdf}
-\caption{\bf Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
+%\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mbh_vs_n_maj.pdf}
+\includegraphics[width=\columnwidth, trim = 20 0 220 0]{mbh_vs_n_maj.pdf}
+\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
 The top and bottom panels show the data points and their error bars, respectively.  
@@
 but still consistent within the errors, with that observed in the the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). \\ 
-%Although we refrain from the conclusion that the $M_{\rm BH} - n_{\rm sph}$ relation is more fundamental than the $M_{\rm BH} - L_{\rm sph}$, 
 Our results suggest that the black hole mass is intimately connected to the spheroid central concentration of stars, 
@@
 
-% & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph,eq} - \langle \log n_{\rm sph,eq} \rangle \bigr)$} \\ [0.5em]
-%
-% All (62)		 & BCES $(Y|X)$ 	      & $-23.88 \pm 0.15$ & $-7.04 \pm 0.89$ & $0.50$ & $-$ & $1.19$ \\
-%			 & mFITEXY $(Y|X)$	      & $-23.95 \pm 0.12$ & $-6.43 \pm 0.41$ & $0.50$ & $0.55^{+0.16}_{-0.10}$ & $0.96$ \\
-%			 & {\tt linmix\_err} $(Y|X)$  & $-23.91 \pm 0.14$ & $-6.04 \pm 0.54$ & $0.50$ & $0.75 \pm 0.13$ & $1.07$ \\ [0.5em]
-%			 & BCES $(X|Y)$ 	      & $-23.88 \pm 0.14$ & $-6.73 \pm 0.48$ & $0.50$ & $-$ & $1.14$ \\
-%			 & mFITEXY $(X|Y)$	      & $-23.93 \pm 0.13$ & $-7.13 \pm 0.48$ & $0.50$ & $0.58^{+0.17}_{-0.12}$ & $1.21$ \\
-%			 & {\tt linmix\_err} $(X|Y)$  & $-23.93 \pm 0.15$ & $-7.14 \pm 0.57$ & $0.50$ & $0.76 \pm 0.16$ & $1.21$ \\ [0.5em]
-%			 & BCES Bisector	      & $-23.88 \pm 0.15$ & $-6.88 \pm 0.62$ & $0.50$ & $-$ & $1.17$ \\
-%			 & mFITEXY Bisector	      & $-23.94 \pm 0.13$ & $-6.76 \pm 0.31$ & $0.50$ & $-$ & $1.15$ \\
-%			 & {\tt linmix\_err} Bisector & $-23.92 \pm 0.15$ & $-6.55 \pm 0.40$ & $0.50$ & $-$ & $1.12$ \\ [0.5em]
-%
-%
-% Elliptical (30)	 & BCES $(Y|X)$ 	      & $-25.46 \pm 0.26$ & $4.92 \pm 4.72$ & $0.77$ & $-$ & $1.46$ \\
-%			 & mFITEXY $(Y|X)$	      & $-25.66 \pm 0.24$ & $-12.65 \pm 2.78$ & $0.77$ & $0.42^{+0.38}_{-0.42}$ & $1.27$ \\
-%			 & {\tt linmix\_err} $(Y|X)$  & $-25.55 \pm 0.26$ & $-8.54 \pm 4.68$ & $0.77$ & $0.80 \pm 0.24$ & $1.20$ \\ [0.5em]
-%			 & BCES $(X|Y)$ 	      & $-25.46 \pm 0.40$ & $-20.83 \pm 11.31$ & $0.77$ & $-$ & $2.26$ \\
-%			 & mFITEXY $(X|Y)$	      & $-25.63 \pm 0.31$ & $-16.13 \pm 4.37$ & $0.77$ & $0.48^{+0.48}_{-0.48}$ & $1.80$ \\
-%			 & {\tt linmix\_err} $(X|Y)$  & $-25.63 \pm 0.43$ & $-16.66 \pm 6.50$ & $0.77$ & $1.22 \pm 0.65$ & $1.85$ \\ [0.5em]
-%			 & BCES Bisector	      & $-25.46 \pm 0.20$ & $-0.08 \pm 0.10$ & $0.77$ & $-$ & $1.14$ \\
-%			 & mFITEXY Bisector	      & $-25.65 \pm 0.28$ & $-14.18 \pm 2.43$ & $0.77$ & $-$ & $1.63$ \\
-%			 & {\tt linmix\_err} Bisector & $-25.58 \pm 0.35$ & $-11.30 \pm 4.34$ & $0.77$ & $-$ & $1.38$ \\ [0.5em]
-%
-%\tableline 
-%\tableline
-%\end{tabular}
-%\end{table*}
-%
-%\begin{table*}
-%\centering
-%\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
-%\begin{tabular}{llccccc}
-%\tableline
-%\tableline
-%{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
-%\tableline 
-%\\
-%
-% Lenticular (11)	 & BCES $(Y|X)$ 	      & $-22.08 \pm 0.89$ & $16.29 \pm 24.44$ & $0.29$ & $-$ & $3.25$ \\
-%			 & mFITEXY $(Y|X)$	      & $-22.16 \pm 0.20$ & $-5.84 \pm 1.83$ & $0.29$ & $0.31^{+0.28}_{-0.20}$ & $0.61$ \\
-%			 & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
-%			 & BCES $(X|Y)$ 	      & $-22.08 \pm 0.20$ & $-7.40 \pm 1.27$ & $0.29$ & $-$ & $0.72$ \\
-%			 & mFITEXY $(X|Y)$	      & $-22.11 \pm 0.28$ & $-8.30 \pm 3.33$ & $0.29$ & $0.40^{+0.33}_{-0.35}$ & $0.77$ \\
-%			 & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
-%			 & BCES Bisector	      & $-22.08 \pm 0.30$ & $0.04 \pm 0.05$ & $0.29$ & $-$ & $1.08$ \\
-%			 & mFITEXY Bisector	      & $-22.14 \pm 0.25$ & $-6.86 \pm 1.70$ & $0.29$ & $-$ & $0.70$ \\
-%			 & {\tt linmix\_err} Bisector & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
-%
-%
-% Spiral (17)		 & BCES $(Y|X)$ 	      & $-22.33 \pm 0.62$ & $-14.53 \pm 71.43$ & $0.17$ & $-$ & $2.71$ \\
-%			 & mFITEXY $(Y|X)$	      & $-22.37 \pm 0.27$ & $-6.53 \pm 2.84$ & $0.17$ & $0.47^{+0.52}_{-0.39}$ & $0.95$ \\
-%			 & {\tt linmix\_err} $(Y|X)$  & $-22.35 \pm 1.23$ & $-3.62 \pm 21.94$ & $0.17$ & $0.63 \pm 0.25$ & $0.93$ \\ [0.5em]
-%			 & BCES $(X|Y)$ 	      & $-22.33 \pm 0.35$ & $-7.91 \pm 5.53$ & $0.17$ & $-$ & $1.54$ \\
-%			 & mFITEXY $(X|Y)$	      & $-22.74 \pm 0.56$ & $-14.91 \pm 10.03$ & $0.17$ & $0.65^{+1.41}_{-0.65}$ & $2.82$ \\
-%			 & {\tt linmix\_err} $(X|Y)$  & $-22.66 \pm 0.88$ & $-16.17 \pm 21.34$ & $0.17$ & $1.47 \pm 2.15$ & $3.04$ \\ [0.5em]
-%			 & BCES Bisector	      & $-22.33 \pm 0.44$ & $-10.25 \pm 18.84$ & $0.17$ & $-$ & $1.94$ \\
-%			 & mFITEXY Bisector	      & $-22.48 \pm 0.44$ & $-9.10 \pm 3.31$ & $0.17$ & $-$ & $1.75$ \\
-%			 & {\tt linmix\_err} Bisector & $-22.41 \pm 1.07$ & $-5.98 \pm 28.65$ & $0.17$ & $-$ & $1.24$ \\ [0.5em]
-%
-%
-% Early-type (43)	 & BCES $(Y|X)$ 	      & $-24.55 \pm 0.22$ & $-10.81 \pm 1.96$ & $0.64$ & $-$ & $1.46$ \\
-%			 & mFITEXY $(Y|X)$	      & $-24.70 \pm 0.14$ & $-7.89 \pm 0.63$ & $0.64$ & $0.46^{+0.18}_{-0.14}$ & $0.93$ \\
-%			 & {\tt linmix\_err} $(Y|X)$  & $-24.63 \pm 0.18$ & $-7.34 \pm 0.83$ & $0.64$ & $0.75 \pm 0.16$ & $1.02$ \\ [0.5em]
-%			 & BCES $(X|Y)$ 	      & $-24.55 \pm 0.16$ & $-8.35 \pm 0.68$ & $0.64$ & $-$ & $1.10$ \\
-%			 & mFITEXY $(X|Y)$	      & $-24.69 \pm 0.16$ & $-8.65 \pm 0.73$ & $0.64$ & $0.48^{+0.20}_{-0.15}$ & $1.14$ \\
-%			 & {\tt linmix\_err} $(X|Y)$  & $-24.68 \pm 0.20$ & $-8.68 \pm 0.91$ & $0.64$ & $0.77 \pm 0.20$ & $1.14$ \\ [0.5em]
-%			 & BCES Bisector	      & $-24.55 \pm 0.18$ & $-9.42 \pm 1.00$ & $0.64$ & $-$ & $1.23$ \\
-%			 & mFITEXY Bisector	      & $-24.69 \pm 0.15$ & $-8.25 \pm 0.48$ & $0.64$ & $-$ & $1.10$ \\
-%			 & {\tt linmix\_err} Bisector & $-24.65 \pm 0.19$ & $-7.96 \pm 0.62$ & $0.64$ & $-$ & $1.07$ \\ [0.5em]
-%
-%
-% Bulge (30)		 & BCES $(Y|X)$ 	      & $-22.25 \pm 0.50$ & $-16.91 \pm 33.45$ & $0.23$ & $-$ & $2.85$ \\
-%			 & mFITEXY $(Y|X)$	      & $-22.21 \pm 0.14$ & $-4.25 \pm 0.94$ & $0.23$ & $0.45^{+0.21}_{-0.13}$ & $0.75$ \\
-%			 & {\tt linmix\_err} $(Y|X)$  & $-22.23 \pm 0.17$ & $-3.36 \pm 1.62$ & $0.23$ & $0.61 \pm 0.17$ & $0.87$ \\ [0.5em]
-%			 & BCES $(X|Y)$ 	      & $-22.25 \pm 0.23$ & $-7.56 \pm 1.94$ & $0.23$ & $-$ & $1.30$ \\
-%			 & mFITEXY $(X|Y)$	      & $-22.23 \pm 0.22$ & $-8.20 \pm 2.44$ & $0.23$ & $0.63^{+0.31}_{-0.19}$ & $1.39$ \\
-%			 & {\tt linmix\_err} $(X|Y)$  & $-22.22 \pm 0.28$ & $-8.42 \pm 4.00$ & $0.23$ & $0.96 \pm 0.54$ & $1.43$ \\ [0.5em]
-%			 & BCES Bisector	      & $-22.25 \pm 0.31$ & $-10.46 \pm 7.05$ & $0.23$ & $-$ & $1.75$ \\
-%			 & mFITEXY Bisector	      & $-22.22 \pm 0.19$ & $-5.62 \pm 0.99$ & $0.23$ & $-$ & $1.05$ \\
-%			 & {\tt linmix\_err} Bisector & $-22.23 \pm 0.23$ & $-4.84 \pm 1.75$ & $0.23$ & $-$ & $0.98$ \\ [0.5em]
-
-%All (xx)		& BCES $(Y|X)$  	     & $$ & $$ & $$ & $$ & $$ \\
-%			& mFITEXY $(Y|X)$	     & $$ & $$ & $$ & $$ & $$ \\
-%			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
-%			& BCES $(X|Y)$  	     & $$ & $$ & $$ & $$ & $$ \\
-%			& mFITEXY $(X|Y)$	     & $$ & $$ & $$ & $$ & $$ \\
-%			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
-%			& BCES Bisector 	     & $$ & $$ & $$ & $$ & $$ \\
-%			& mFITEXY Bisector	     & $$ & $$ & $$ & $$ & $$ \\
-%			& {\tt linmix\_err} Bisector & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
-%
-
 \tableline 
@@
 
-%Elliptical (E) (30)	& BCES $(Y|X)$  	     & $8.80 \pm 0.53$ & $-18.16 \pm 53.99$ & $0.76$ & $-$ & $3.02$ \\
-%			& mFITEXY $(Y|X)$	     & $8.90 \pm 0.10$ & $4.47 \pm 0.88$ & $0.76$ & $0.29^{+0.14}_{-0.10}$ & $0.56$ \\
-%			& {\tt linmix\_err} $(Y|X)$  & $8.84 \pm 0.12$ & $3.56 \pm 1.35$ & $0.76$ & $0.44 \pm 0.12$ & $0.59$ \\ [0.5em]
-%			& BCES $(X|Y)$  	     & $8.80 \pm 0.18$ & $8.00 \pm 2.55$ & $0.76$ & $-$ & $1.01$ \\
-%			& mFITEXY $(X|Y)$	     & $8.92 \pm 0.15$ & $6.85 \pm 1.75$ & $0.76$ & $0.36^{+0.20}_{-0.15}$ & $0.89$ \\
-%			& {\tt linmix\_err} $(X|Y)$  & $8.89 \pm 0.20$ & $6.96 \pm 2.49$ & $0.76$ & $0.63 \pm 0.30$ & $0.89$ \\ [0.5em]
-%			& BCES Bisector 	     & $8.80 \pm 0.11$ & $-0.03 \pm 0.10$ & $0.76$ & $-$ & $0.64$ \\
-%			& mFITEXY Bisector	     & $8.91 \pm 0.13$ & $5.42 \pm 0.85$ & $0.76$ & $-$ & $0.73$ \\
-%			& {\tt linmix\_err} Bisector & $8.85 \pm 0.16$ & $4.73 \pm 1.30$ & $0.76$ & $-$ & $0.67$ \\ [0.5em]
-%
-%Lenticular (S0) (11)	& BCES $(Y|X)$  	     & $7.75 \pm 0.58$ & $-11.51 \pm 31.78$ & $0.33$ & $-$ & $2.11$ \\
-%			& mFITEXY $(Y|X)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.26$ \\
-%			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
-%			& BCES $(X|Y)$  	     & $7.75 \pm 0.13$ & $3.54 \pm 0.99$ & $0.33$ & $-$ & $0.46$ \\
-%			& mFITEXY $(X|Y)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.49$ \\
-%			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
-%			& BCES Bisector 	     & $7.75 \pm 0.13$ & $-0.09 \pm 0.15$ & $0.33$ & $-$ & $0.48$ \\
-%			& mFITEXY Bisector	     & $7.65 \pm 0.12$ & $3.78 \pm 0.85$ & $0.33$ & $-$ & $0.49$ \\
-%			& {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]
-%
  Early-type (E+S0) (43)	& BCES $(Y|X)$  	     & $8.54 \pm 0.10$ & $4.07 \pm 0.87$ & $0.64$ & $-$ & $0.65$ \\
@@
   \label{tab:intsc} 
-  %\tablecomments{  }
   \end{table*}

### 2016-03-07 thesis/conclusions.tex
conclusions ellicular

@@
-\chapter{Final remarks}
+\chapter{Final remarks and future perspectives}
 \label{ch:concl}
@@
 A summary of our principal findings and some additional brief considerations about them are presented here. 
-The end of this Chapter incorporates some promising future research directions. \\
+This Chapter incorporates also some promising future research directions. \\
 
@@
 we do not consider possible for current automatic routines to reproduce our analysis. \\
+future: bayes analysis to estimate max number of components, comparison with "physical" components; 
+improving kin-phot approach, large kin maps are needed, 
+combining hst + wide field obs to map galaxy outskirts, 
+use bayes analysis to estimate uncertainties on params so that we don't need other decompositions, 
+use of isofit and boggy's code for decomp, \\
 
@@
 and it also affects calculations of gravitational waves background from SMBH binary coalescence 
-(but see Shankar et al.~\emph{submitted to MNRAS}). \\
+(but see Shankar et al.~\emph{submitted to MNRAS} TBD). \\
 
@@
 \citet{volontericiotti2013} explained the presence of the outlying black holes 
-as a natural consequence of the fact that their host galaxies have experienced more dry mergers 
+as a natural consequence of the fact that their host Central Cluster Galaxies (CCGs) have experienced more dry mergers 
 than any other galaxy, 
@@
 and ``conserve'' the stellar velocity dispersion. 
-We tested and disproved this scenario for xx core-S\'ersic galaxies, 
+We tested and disproved this scenario for 23 core-S\'ersic galaxies, 
 using the ratio between black hole mass and stellar mass deficit as a proxy 
-for the number of dry mergers experienced by the galaxy \citep{xxx}. 
-This was confirmed by a second test using the central kinematic classification of xx galaxies. 
-The slope of the m-sigma is this... 
-comparison
+for the number of dry mergers experienced by a galaxy \citep{merritt2006}. 
+This was confirmed by a second test using the central kinematic classification of 37 galaxies. 
+Our analysis suggests that 
+the merger history of the CCGs hosting over-massive black holes in the $M_{\rm BH} - \sigma$ diagram 
+is not exceptional, 
+therefore these galaxies should be considered as legitimate members of the $M_{\rm BH} - \sigma$ correlation. 
+An alternative possibility for the CCGs is that their partially depleted core 
+has been replenished by stars, globular clusters and nuclear star clusters 
+acquired from minor dry mergers, 
+where the accreted satellite galaxies do not host a massive black hole. 
+However, high-resolution cosmological simulations seem to favour an ``inside-out'' formation scenario 
+for early-type galaxies, 
+where minor mergers only contribute to the build-up of the external envelope of high-mass galaxies 
+(e.g.~\citealt{wellons2016}). 
+It should also be noted that evidence is accumulating against the ``naive'' assumption 
+that low-mass galaxies do not host any central massive black hole 
+(e.g.~\citealt{Baldassare2015,Graham2016LEDA}). \\
+
+Finally, in Chapter \ref{ch:ellicular}, 
+we tackled the issue of the over-massive black holes in the $M_{\rm BH} - M_{\rm *,sph}$ diagram. 
+We showed that the intermediate-scale discs of the galaxies Mrk 1216 \citep{yildirim2015}, NGC 1271 \citep{walsh2015}, 
+NGC 1277 \citep{vandenbosch2012}, and NGC 1332 \citep{rusli2011} 
+had been confused with large-scale discs and incorrectly modelled as such. 
+This led to the considerable underestimation of their spheroid luminosity, 
+which caused them to appear as extreme outliers above the $M_{\rm BH} - M_{\rm *,sph}$ correlation 
+of local early-type galaxies. 
+Furthermore, at least one of these galaxies had its black hole mass overestimated by one order of magnitude 
+(NGC 1277, \citealt{Graham2016n1277}). 
+The spheroidal components of these four galaxies, plus the galaxy NGC 3115, 
+have the same structural properties (compactness) and purely old stellar population 
+as the $z \approx 2$ compact massive spheroids (e.g.~\citealt{daddi2005,trujillo2006,vandokkum2008,damjanov2009}), 
+i.e.~they experienced no evolution over the last $10 \rm~Gyr$. 
+Assuming that the $M_{\rm BH} - M_{\rm *,sph}$ correlation was already in place at $z=2$, 
+their spheroids are a follis record of that correlation
+the fact that these galaxies reside $\lesssim 1\sigma$ above the $M_{\rm BH} - M_{\rm *,sph}$ correlation 
+of $z=0$ early-type galaxies 
+implies that 
+if they trace the z=2 correlation
+
+\cite{gds2015} showed that, while the majority of the high-redshift compact massive spheroids 
+have evolved into today's bulges of lenticular and early-type spiral galaxies, 
+i.e.~they have accreted a large-scale stellar disc, 
+a few of them (such as Mrk 1216, NGC 1271, NGC 1277, NGC 1332 and NGC 3115) 
+have only accreted an intermediate-scale stellar disc.
+
+no evolution of correlation  sph
+
+if the disc is small, they were on correlation at z=2, no evolution of correlation gal
+
+(but see Shankar et al.~\emph{submitted to MNRAS} TBD). \\

### 2016-03-08 thesis/conclusions.tex
conclusions chapter 7

@@
 and various properties of the host spheroid, 
-aiming at gaining a more profound understanding of the co-evolution between SMBHs and galaxies. 
-A summary of our principal findings and some additional brief considerations about them are presented here. 
+aiming at a more profound understanding of the co-evolution between SMBHs and galaxies. 
+A summary of our principal findings and some additional considerations are presented here. 
 This Chapter incorporates also some promising future research directions. \\
@@
 of the black hole mass. 
-In many cases we found a large discrepancy between the S\'ersic index measurements 
-obtained by different studies for the spheroidal component of the same galaxy, 
+In many cases we found a large discrepancy between the spheroid S\'ersic index measurements 
+obtained by different studies for the same galaxy, 
 either due to a significantly different choice of model components 
@@
 we were able to recover a strong $M_{\rm BH} - n_{\rm sph}$ correlation, 
-which was not found using the individual datasets of three of the four studies. 
+which was not found using the individual datasets of three of the four aforementioned studies. 
 From this we concluded that some of the galaxy decompositions were not accurate. 
@@
 
-Chapter \ref{ch:galviv} was dedicated to the careful multicomponent decomposition of 66 galaxies 
+Chapter \ref{ch:galviv} \citep{paperI} was dedicated to the careful multicomponent decomposition of 66 galaxies 
 with a direct measurement of the black hole mass. 
@@
 
-In Chapter \ref{ch:mm}, we used our dataset to derive and explore 
+In Chapter \ref{ch:mm} \citep{paperII}, we used our dataset to derive and explore 
 the $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) diagrams. 
@@
 sequence than previously reported by \citet{grahamscott2013}. 
-We do not observe any offset of spheroids with S\'ersic index $n_{\rm sph} < 2$ 
+We did not observe any offset of spheroids with S\'ersic index $n_{\rm sph} < 2$ 
 from the $M_{\rm BH} - L_{\rm sph}$ correlation traced by spheroids with $n_{\rm sph} > 2$, 
@@
 This is in agreement with the near-linear $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) correlation 
-measured by previous studies that used galaxy samples dominated by high-mass early type objects 
+measured by previous studies that used galaxy samples dominated by high-mass early-type objects 
 (e.g.~\citealt{magorrian1998,marconihunt2003,haringrix2004,gultelkin2009,sani2011,beifiori2012,
@@
 (e.g.~\citealt{laor1998,laor2001,wandel1999,salucci2000,ryan2007}). 
-An interesting exception has been the under-linear $M_{\rm BH} \propto L_{\rm sph}^{0.75 \pm 0.10}$ 
+An interesting exception has been the under-linear $M_{\rm BH} \propto L_{\rm sph}^{0.75 \pm 0.10}$ relation 
 measured by \citet{lasker2014anal}, 
@@
 and it also affects calculations of gravitational waves background from SMBH binary coalescence 
-(but see Shankar et al.~\emph{submitted to MNRAS} TBD). \\
+(but see \citealt{shankar2016}). \\
 
@@
 (e.g.~\citealt{Baldassare2015,Graham2016LEDA}). \\
+shankar tbd
 
-Finally, in Chapter \ref{ch:ellicular}, 
+Finally, in Chapter \ref{ch:ellic}, 
 we tackled the issue of the over-massive black holes in the $M_{\rm BH} - M_{\rm *,sph}$ diagram. 
@@
 had been confused with large-scale discs and incorrectly modelled as such. 
-This led to the considerable underestimation of their spheroid luminosity, 
+This led to a considerable underestimation of their spheroid luminosity, 
 which caused them to appear as extreme outliers above the $M_{\rm BH} - M_{\rm *,sph}$ correlation 
@@
 Furthermore, at least one of these galaxies had its black hole mass overestimated by one order of magnitude 
-(NGC 1277, \citealt{Graham2016n1277}). 
-The spheroidal components of these four galaxies, plus the galaxy NGC 3115, 
-have the same structural properties (compactness) and purely old stellar population 
-as the $z \approx 2$ compact massive spheroids (e.g.~\citealt{daddi2005,trujillo2006,vandokkum2008,damjanov2009}), 
-i.e.~they experienced no evolution over the last $10 \rm~Gyr$. 
-Assuming that the $M_{\rm BH} - M_{\rm *,sph}$ correlation was already in place at $z=2$, 
-their spheroids are a follis record of that correlation
-the fact that these galaxies reside $\lesssim 1\sigma$ above the $M_{\rm BH} - M_{\rm *,sph}$ correlation 
-of $z=0$ early-type galaxies 
-implies that 
-if they trace the z=2 correlation
-
+(NGC 1277, e.g.~\citealt{Graham2016n1277}). 
 \cite{gds2015} showed that, while the majority of the high-redshift compact massive spheroids 
@@
 i.e.~they have accreted a large-scale stellar disc, 
-a few of them (such as Mrk 1216, NGC 1271, NGC 1277, NGC 1332 and NGC 3115) 
+a few of them (such as Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115) 
 have only accreted an intermediate-scale stellar disc. 
-
-no evolution of correlation  sph
-
-if the disc is small, they were on correlation at z=2, no evolution of correlation gal
+The spheroidal components of the galaxies Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 
+have the same structural properties (compactness), stellar mass ($\approx 10^{11} \rm~M_\odot$), 
+high stellar velocity dispersion ($\approx 300 \rm~km~s^{-1}$) and purely old stellar population 
+as the $z \approx 2$ compact massive spheroids (e.g.~\citealt{daddi2005,trujillo2006,vandokkum2008,damjanov2009}), 
+i.e.~they experienced negligible evolution over the last $10 \rm~Gyr$. 
+If also their black holes has had little or no mass accretion since $z = 2$, 
+assuming that the $M_{\rm BH} - M_{\rm *,sph}$ relation was already in place $10 \rm~Gyr$ ago, 
+these five spheroids provides us with a fossil record of the correlation at $z=2$. 
+The fact that the five spheroids lie within $\lesssim 1\sigma$ above the $z=0$ correlation 
+can be used as a constraint for the evolution with redshift of the $M_{\rm BH} - M_{\rm *,sph}$ normalization 
+(assuming no evolution with redshift of the log-slope of the correlation). 
+Furthermore, knowing that their intermediate-scale discs have been accreted over the last $10 \rm~Gyr$ 
+and that their disc-to-total ratios are typically small ($\lesssim 20\%$), 
+one can deduce that the location of these five galaxies in the $M_{\rm BH} - M_{\rm *,gal}$ diagram 
+(where $M_{\rm *,gal}$ is the galaxy stellar mass) 
+is roughly the same as that at $z=2$. 
+Therefore, finding a larger number of local galaxies with the same charachteristics of the aforementioned five 
+would be helpful to study the redshift evolution of the $M_{\rm BH} - M_{\rm *,sph}$ 
+and $M_{\rm BH} - M_{\rm *,gal}$ relations. 
+The Hobby-Eberly Telescope Massive Galaxy Survey (HETMGS, \citealt{vandenBosch2015}) 
+has identified a few of these rare objects 
+such as Mrk 1216, NGC 1271, NGC 1277, and NGC 1281 \citep{yildirim2016}, 
+although the last galaxy still lacks an accurate photometric decomposition; 
+more of them might be yet to be found in the HETMGS database. 
+\citet{saulder2015} selected 76 compact massive galaxies with high stellar velocity dispersion within $0.05 < z < 0.2$ 
+from the Sloan Digital Sky Survey (SDSS, \citealt{abazajian2009}) 
+and proposed them as candidate survivors of the $z=2$ compact massive spheroids. 
+However, it should be noted that their criterion of high mass and compactness relies on the \emph{galaxy} properties 
+rather than on the \emph{spheroid} properties, 
+therefore a number of these candidates might not be real descendant of the $z=2$ population\footnote{Some 
+candidates might be lenticular galaxies with compact \emph{galaxy} sizes and large disc-to-total ratios, 
+therefore their spheroids would be significantly less massive than the $z=2$ red nuggets. }. 
+The same holds for the simulated compact massive galaxies of \citet{wellons2016}. 
+It would be interesting to perform photometric decompositions for these 76 candidates 
+and select only those with compact massive \emph{spheroids}.
 

### 2016-03-09 papers/mbhn/mbhn.tex
sleep

@@
 either a disk-less elliptical galaxy or the bulge component of a disk galaxy;  
-we do not attempt at distinguishing between classical bulges and disk-like pseudo-bulges. } and disk components of galaxies 
+we do not attempt at distinguishing between classical bulges and disk-like pseudo-bulges 
+(see \citealt{graham2015review} or \citealt{Graham2015pseudobulges}). } and disk components of galaxies 
 (e.g.~\citealt{caon1993,andredakis1995,iodice1997,iodice1999,seigar1998,khosroshahi2000}), 

### 2016-03-09 thesis/conclusions.tex
sleep

@@
 we do not consider possible for current automatic routines to reproduce our analysis. \\
-future: bayes analysis to estimate max number of components, comparison with "physical" components; 
+In our 1D galaxy decomposition code, the minimisation routine is based on the Levenberg-Marquardt algorithm, 
+which is known to be one of the fastest algorithms available, 
+but is also prone to ``get trapped'' into local minima of the chi-squared distribution. 
+As a future project, it would be interesting to implement in the code different minimisation algorithms, 
+such as those available in {\tt Imfit} \citep{imfit},  
+and test their performance. 
+It would also be beneficial to create a procedure to estimate the systematic uncertainties 
+associated with the best-fit parameters from the fit itself, 
+without the need to resort to decompositions performed by other authors as we did in this work. 
+One of the issues associated with multicomponent decomposition is the risk of ``overfitting'', 
+i.e.~having a model with more components (or parameters) than what is actually needed. 
+Information theory and Bayes analysis provide us with a number of methods 
+to estimate the maximum number of parameters required by a model 
+to fit a given dataset, 
+such as the \citep{akaike1974} Information Criterion that we used in Chapter \ref{ch:mn}. 
+One could check whether or not these methods agree with our human-supervised selection 
+of ``physically motivated'' model components.
+
 improving kin-phot approach, large kin maps are needed, 
 combining hst + wide field obs to map galaxy outskirts, 
-use bayes analysis to estimate uncertainties on params so that we don't need other decompositions, 
 use of isofit and boggy's code for decomp, \\

### 2016-03-10 thesis/acknowledgement.tex
all chapters but concl

\chapter*{Acknowledgements}

alister, duncan, c blake, greg

karl,

gonzalo, rob, piero, glenn, anna, angela,

elisa, shaun, silvia, james

gym friends, rock climbing friends

### 2016-03-10 thesis/conclusions.tex
all chapters but concl

--- 2016-03-08 thesis/conclusions.tex
@@
 we do not consider possible for current automatic routines to reproduce our analysis. \\
-future: bayes analysis to estimate max number of components, comparison with "physical" components; 
-improving kin-phot approach, large kin maps are needed, 
-combining hst + wide field obs to map galaxy outskirts, 
-use bayes analysis to estimate uncertainties on params so that we don't need other decompositions, 
-use of isofit and boggy's code for decomp, \\
+In our 1D galaxy decomposition code, the minimisation routine is based on the Levenberg-Marquardt algorithm, 
+which is known to be one of the fastest algorithms available, 
+but is also prone to ``get trapped'' into local minima of the chi-squared distribution. 
+As a future project, it would be interesting to implement in the code different minimisation algorithms, 
+such as those available in {\tt Imfit} \citep{imfit},  
+and test their performance. 
+It would also be beneficial to create a procedure to estimate the systematic uncertainties 
+associated with the best-fit parameters from the fit itself, 
+without the need to resort to decompositions performed by other authors as we did in this work. 
+One of the issues associated with multicomponent decomposition is the risk of ``overfitting'', 
+i.e.~having a model with more components (or parameters) than what is actually needed. 
+Information theory and Bayes analysis provide us with a number of methods 
+to estimate the maximum number of parameters required by a model 
+to fit a given dataset, 
+such as the \citet{akaike1974} Information Criterion that was used in Chapter \ref{ch:mn}. 
+One could check whether or not these methods agree with our human-supervised selection 
+of ``physically motivated'' model components. 
+Our structural analysis of galaxies confirmed the usefulness of a joint photometric-kinematic approach, 
+especially when extended (i.e.~$> 1 R_{\rm e}$, \citealt{arnold2014}) kinematic maps are available. 
+Future galaxy decomposition studies will be able to take advantage from the large datasets 
+of on-going Integral Field Spectroscopy surveys (e.g.~SAMI, \citealt{croom2012}, and MaNGA, \citealt{law2014}). 
+Finally, we note that \citet{ciambur2015} recently developed the IRAF task {\tt isofit}, 
+which allows the user to perform a more sophisticated isophotal analysis of galaxies than the task {\tt ellipse} 
+in the presence of an inclined disc. 
+Our isophotal analysis was carried out before {\tt isofit} was conceived or available, 
+but future studies will be able to use it. \\
 
@@
 (e.g.~\citealt{Baldassare2015,Graham2016LEDA}). \\
-shankar tbd
 
@@
 
-(but see Shankar et al.~\emph{submitted to MNRAS} TBD). \\
+%(but see Shankar et al.~\emph{submitted to MNRAS} TBD). \\

### 2016-03-10 thesis/mn.tex
conclusions ellicular
all chapters but concl

@@
 
-chapter x was dedicated to recovery of mn correlation with literature data
+While the previous Chapter was dedicated to the study of the relations between 
+black hole mass and galaxy or spheroid luminosity, 
+in this Chapter we will perform an analogous analysis 
+to explore the relation between black hole mass and spheroid S\'ersic index ($M_{\rm BH} - n_{\rm sph}$). 
+To address the issue of consistency between galaxy scaling relations 
+that was outlined in Chapter \ref{ch:intro}, 
+it is mandatory to include also an analysis of the relation between spheroid luminosity 
+and spheroid S\'ersic index ($L_{\rm sph} - n_{\rm sph}$). 
+The reliability of the uncertainties associated with the S\'ersic index measurements 
+obtained from our 1D decompositions 
+ensures a robust estimate of the intrinsic scatter in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
+which can be compared with that in the $M_{\rm BH} - L_{\rm sph}$ diagram. \\
 
-now we can do better with high quality data set
-
-consistency with other correlations
-
-good uncertainties -> robust estimate of intr scatter -> comparison with m-l
-
-The remainder of this chapter comprises the published version of the paper 
+The remainder of this chapter comprises the peer-reviewed version of the paper 
 ``Supermassive Black Holes and Their Host Spheroids. 
@@
 by G.~A.~D.~Savorgnan,  
-as it appears in Volume xxx of the \emph{The Astrophysical Journal}.
+accepted for publication in the \emph{The Astrophysical Journal}.
 
-\includepdf[pages={1-10}]{mbhn.pdf}
+\includepdf[pages={1-10}]{ApJ2016b.pdf}

### 2016-03-10 thesis/recovery-mn.tex
all chapters but concl

@@
 \cite{graham2001} demonstrated that the mass of SMBHs is correlated 
-to the stellar light concentration of their host spheroid. 
+with the stellar light concentration of their host spheroid. 
 Six years later, \cite{grahamdriver2007} expanded the galaxy sample of \cite{graham2001} 
@@
 \citeauthor{sani2011} and \citeauthor{vika2012} included more than two components in their galaxy models 
--- such as bars and nuclear sources -- 
-whereas \citeauthor{beifiori2012} excluded barred galaxies from their analysis. 
+such as bars and nuclear sources, 
+whereas \citeauthor{beifiori2012} excluded barred galaxies from their analysis 
+and used simple bulge+disc models. 
 From these decompositions, they derived and analysed several correlations. 
@@
 \citeauthor{vika2012}, and \citeauthor{beifiori2012}), 
-we immediately noticed that some galaxies had been described with significantly different models 
+we immediately noticed that some galaxies had been described by these authors with significantly different models 
 (e.g.~the galaxy M60, treated as a discless elliptical galaxy by two studies, 
@@
 Not only this, but some studies obtained largely discrepant best-fit parameters 
-for the same galaxy even though they used the same choice of decomposition 
+for the same galaxy even when they used the same choice of decomposition 
 (e.g.~two studies described the galaxy NGC 3115 with a S\'ersic-bulge + exponential-disc model, 
 but obtained a bulge S\'ersic index of $3$ and $13$, respectively). 
-This confirmed doubts about the accuracy of some decompositions. \\
+This confirmed our doubts about the accuracy of some decompositions. \\
 
@@
 and used these average values to populate the $M_{\rm BH} - n_{\rm sph}$ diagram. 
-Immediately, we noticed that a clear correlation was emerging from the data, 
+We noticed that a clear correlation was emerging from the data, 
 although with a significant amount of scatter. 

### 2016-03-10 thesis/ubermassive-msigma.tex
conclusions ellicular
all chapters but concl

@@
-\chapter{m-sigma}
+\chapter{Monster black holes in Central Cluster Galaxies}
 \label{ch:msigma}
 
-A precise measurement of the log-slope of the $M_{\rm BH} - \sigma$ correlation is important 
+A precise measurement of the log-slope of the $M_{\rm BH} - \sigma_*$ correlation is important 
 to constrain theoretical models of AGN feedback. 
-For example, energy driven outflows are expected to produce a scaling of $M_{\rm BH} \propto \sigma^5$, 
-whereas momentum driven outflows should result into a shallower $M_{\rm BH} \propto \sigma^4$ relation 
+For example, energy driven outflows are expected to produce a scaling of $M_{\rm BH} \propto \sigma_*^5$, 
+whereas momentum driven outflows should result into a shallower $M_{\rm BH} \propto \sigma_*^4$ relation 
 \citep{silkrees1998,fabian1999}. 
-Since the $M_{\rm BH} - \sigma$ correlation was presented for the first time by \citet{ferraresemerritt2000}
+Since the $M_{\rm BH} - \sigma_*$ correlation was presented for the first time by \citet{ferraresemerritt2000}
 and \citet{gebhardt2000}, 
@@
 have added new data points at the high-mass end of the 
-$M_{\rm BH} - \sigma$ diagram \citep{mcconnell2011,mcconnell2012}, 
+$M_{\rm BH} - \sigma_*$ diagram \citep{mcconnell2011,mcconnell2012}, 
 which appear to be outlying (``over-massive'') with respect to the observed correlation. 
@@
 Whether or not considering the over-massive black holes as an ``exception to the rule'', 
-or in other words legitimately excluding them from the linear regression analysis of the $M_{\rm BH} - \sigma$ diagram, 
+or in other words legitimately excluding them from the linear regression analysis of the $M_{\rm BH} - \sigma_*$ diagram, 
 obviously has an impact on the estimate of the log-slope of the correlation. 

### 2016-03-10 python_codes/paper_figures/MbhN/figures.py

@@ -186,6 +186,14 @@ def mag_sph_vs_n_maj():
         	datfile.write(str(logNmaj) + ' ' + str(err_logNmaj) + ' ' + str(MAGsph) + ' ' + str(err_MAGsph) + ' ' + '\n')
         datfile.close()
 	
+        ### produce .dat file for Shankar
+        datfileName = '/Users/gsavorgnan/galaxy_vivisection/results/n_maj_sph_Francesco.dat'
+        datfile = open(datfileName, 'w')
+        datfile.write('# galaxy lognmaj err_logn \n')
+        for galaxy, logNmaj, err_logNmaj in zip(gal_id, log_n, 0.5*(perr_log_n + merr_log_n) ):
+        	datfile.write(galaxy + ' ' + str(logNmaj) + ' ' + str(err_logNmaj) + ' ' + '\n')
+        datfile.close()
+	
 	
 	#######################################
 	
@@ -610,7 +618,7 @@ def mag_sph_vs_n_maj():
 	
 	#plt.show()
 	#plt.savefig('test.pdf', format='pdf', dpi=100)
-	plt.savefig(path_paper_figures + 'mag_vs_n_maj.pdf', format='pdf', dpi=1000)
+	#plt.savefig(path_paper_figures + 'mag_vs_n_maj.pdf', format='pdf', dpi=1000)
 
 
 def mbh_vs_n_sph_maj():

### 2016-03-11 papers/MbhMsph/erratum/mm.tex
erratum

--- 2015-10-16 papers/MbhMsph/ApJ_submission/mm.tex
@@
-\documentclass[preprint2]{emulateapj}
-
-\usepackage{natbib}
-\bibliographystyle{apj}
-\usepackage{longtable}
-\usepackage[]{graphicx}
-\usepackage{amsmath}
-\usepackage{natbib}
-\usepackage{tabularx}
-\usepackage{bm}
-\usepackage{color}
-\usepackage{hyperref}
-
-%% Sometimes a paper's abstract is too long to fit on the
-%% title page in preprint2 mode. When that is the case,
-%% use the longabstract style option.
-
-%% \documentclass[preprint2,longabstract]{aastex}
+\documentclass{aastex6}
 
 \newcommand{\vdag}{(v)^\dagger}
-\newcommand{\myemail}{gsavorgn@astro.swin.edu.au}
-\newcommand{\fitfigurewidth}{0.8\textwidth}
-
-\shorttitle{Red and blue $M_{\rm BH} - M_{\rm *,sph}$ sequence}
-
-\shortauthors{Savorgnan et al.}
+\newcommand\aastex{AAS\TeX}
+\newcommand\latex{La\TeX}
 
@@
 
-\title{Supermassive black holes and their host spheroids \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
+\title{Erratum: ``Supermassive black holes and their host spheroids \\ 
+II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram'' (2016, ApJ, 817, 21)}
 
@@
 
-%\and
+\keywords{}
 
-%\author{A. W. Graham\altaffilmark{1}}
-%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
+\section*{}
 
-%% Notice that each of these authors has alternate affiliations, which
-%% are identified by the \altaffilmark after each name.  Specify alternate
-%% affiliation information with \altaffiltext, with one command per each
-%% affiliation.
-
-%\altaffiltext{1}{}
-%\altaffiltext{2}{Society of Fellows, Harvard University.}
-%\altaffiltext{3}{present address: Center for Astrophysics,
-%    60 Garden Street, Cambridge, MA 02138}
-%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
-%\altaffiltext{5}{Patron, Alonso's Bar and Grill}
-
-%% Mark off your abstract in the ``abstract'' environment. In the manuscript
-%% style, abstract will output a Received/Accepted line after the
-%% title and affiliation information. No date will appear since the author
-%% does not have this information. The dates will be filled in by the
-%% editorial office after submission.
-
-\begin{abstract}
-In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
-decomposition of 66 galaxies, with directly measured black hole masses, 
-that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
-Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
-We present correlations between the black hole mass, $M_{\rm BH}$, 
-and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
-and also stellar mass, $M_{\rm *,sph}$.
-Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies.
-Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
-and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
-The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
-and define a tight %\emph{early-type sequence} 
-\emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
-and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$, 
-i.e.~a $\pm 2\sigma$ range of 0.1--5\%.
-At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper %\emph{late-type sequence}, 
-\emph{blue sequence}, 
-with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
-indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
-We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
-ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
-are not offset to lower $M_{\rm BH}$ from the correlation defined by the current bulge sample with $n_{\rm sph}>2$; 
-and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies 
-(most elliptical galaxies contain disks, i.e.~$L_{\rm sph} \neq L_{\rm gal}$) --
-once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.
-
-\end{abstract}
-
-\keywords{black hole physics; galaxies: bulges; galaxies: elliptical and lenticular, cD; galaxies: evolution; galaxies: structure}
-
-\section{Introduction}
-\label{sec:int}
-A quarter of a century ago, 
-\cite{dressler1989} foresaw a ``rough scaling of black hole mass with the mass of the spheroidal component'' of galaxies, 
-as suggested by the sequence of five galaxies (M87, M104, M31, M32 and the Milky Way). 
-\cite{yee1992} then announced a linear relation between what was effectively black hole mass and galaxy mass for high-luminosity, bulge-dominated early-type galaxies 
-radiating near the Eddington limit.
-This ``rough scaling'' was a premature version of the early correlations between black hole mass, $M_{\rm BH}$,  
-and host spheroid luminosity, $L_{\rm sph}$, and also host spheroid mass, $M_{\rm sph}$ 
-\citep{kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}. 
-These initial studies were dominated by high-mass, early-type galaxies, 
-for which they too reported a quasi-linear $M_{\rm BH} - M_{\rm sph}$ relation. 
-Subsequent studies of the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm sph}$ diagrams 
-(\citealt{ferrareseford2005,lauer2007,graham2007,gultelkin2009,sani2011,beifiori2012,erwingadotti2012,
-vika2012,vandenbosch2012,mcconnellma2013,kormendyho2013})
-continued to use galaxy samples dominated by high-mass, early-type systems with $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 
-and they too recovered a near-linear relation. 
-However, the consensus about a linear $M_{\rm BH} - M_{\rm sph}$ correlation was not unanimous. 
-Some studies had reported a slope steeper than one,  
-or noticed that the low-mass spheroids were offset to the right of (or below) the relation traced by the high-mass spheroids 
-\citep{laor1998,wandel1999,laor2001,ryan2007}.
-\cite{graham2012bent}, \cite{grahamscott2013} and \cite{scott2013} found two distinct trends in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm sph}$ diagrams:  
-a linear and a super-quadratic correlation at the high- and low-mass end, respectively\footnote{Readers 
-interested in an extensive review about the early discovery and successive improvements of these correlations 
-should consult \cite{graham2015bulges}.}. \\
-Recently, \cite{lasker2014data,lasker2014anal} derived $2.2~\rm \mu m$ bulge luminosities for 35 galaxies 
-(among which only 4 were classified as spiral galaxies), 
-and reported a slope below unity for their $M_{\rm BH} - L_{\rm sph}$ relation. 
-They also claimed that the black hole mass correlates equally well with the total galaxy luminosity 
-as it does with the bulge luminosity.  \\
-The $M_{\rm BH} - L_{\rm sph}$ relation for early-type (elliptical + lenticular) galaxies can be predicted by combining two other correlations that involve 
-the bulge stellar velocity dispersion, $\sigma$.
-One of these is the $M_{\rm BH} - \sigma$ relation \citep{ferraresemerritt2000,gebhardt2000},
-which can be described with a single power-law ($M_{\rm BH} \propto \sigma^{5-6}$) 
-over a wide range in velocity dispersion ($70-350~\rm km~s^{-1}$, e.g.~\citealt{graham2011,mcconnell2011,grahamscott2013}).
-The other is the $L_{\rm sph} - \sigma$ relation, 
-which has long been known to be a ``double power-law'', 
-with $L_{\rm sph} \propto \sigma^{5-6}$ at the luminous end\footnote{Recent 
-work has the $M_{\rm BH} - \sigma$ correlation as steep as $M_{\rm BH} \propto \sigma^{6.5}$ \citep{savorgnangraham2015},
-and the high-luminosity end of the $L_{\rm sph} - \sigma$ correlation as steep as $L_{\rm sph} \propto \sigma^{8}$ \citep{monterodorta2015}.} 
-\citep{schechter1980,malumuthkrishner1981,vonderlinden2007,lauer2007lumell,liu2008}
-and $L_{\rm sph} \propto \sigma^2$ at intermediate and faint luminosities 
-\citep{davies1983,held1992,matkovicguzman2005,derijcke2005,balcells2007screl,chilingarian2008,forbes2008,cody2009,tortora2009,kourkchi2012}. 
-The change in slope of the $L_{\rm sph} - \sigma$ relation occurs at $M_B \approx -20.5\rm~mag$, 
-corresponding to $\sigma \approx 200~\rm km~s^{-1}$. 
-The $M_{\rm BH} - L_{\rm sph}$ relation should therefore be better described by a ``broken'', rather than a single power-law: 
-with $M_{\rm BH} \propto L_{\rm sph}^{2.5}$ at the low-luminosity end, 
-and $M_{\rm BH} \propto L_{\rm sph}^1$ at the high-luminosity end.  
-Due to the scatter in the $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm sph}$) diagram, 
-studies that have not sufficiently probed below $M_{\rm BH} \approx 10^7\rm~M_\odot$ 
-can easily miss the change in slope occuring at $M_{\rm BH} \approx 10^{(8 \pm 1)}\rm~M_\odot$, 
-and erroneously recover a single log-linear relation. \\
-When \cite{graham2012bent} pointed out this overlooked inconsistency between these linear and bent relations, 
-he identified two different populations of galaxies, 
-namely the core-S\'ersic spheroids \citep{graham2003coresersicmodel,trujillo2004coresersicmodel} and the S\'ersic 
-spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
-whereas S\'ersic spheroids have no central deficit of stars.},
-and attributed the change in slope (from super-quadratic to linear) to their different formation mechanisms. 
-In this scenario, core-S\'ersic spheroids are built in dry merger events 
-where the black hole and the bulge grow at the same pace, increasing their mass in lock steps ($M_{\rm BH} \propto L_{\rm sph}^1$), 
-whereas S\'ersic spheroids originate from gas-rich processes 
-in which the mass of the black hole increases more rapidly than the mass of its host spheroid ($M_{\rm BH} \propto L_{\rm sph}^{2.5}$). \\
-\citeauthor{grahamscott2013} (\citeyear{grahamscott2013}, hereafter GS13) and \citeauthor{scott2013} (\citeyear{scott2013}) 
-presented separate power-law linear regressions 
-for the S\'ersic and core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
-(spheroid stellar mass) diagrams, probing down to $M_{\rm BH} \approx 10^6\rm~M_\odot$. 
-To obtain their dust-corrected \emph{bulge} magnitudes, they did not perform bulge/disc decompositions, 
-but converted the $B-$band and $K_S-$band observed, total \emph{galaxy} magnitudes into bulge magnitudes 
-using a mean statistical bulge-to-total ratio based on each object's morphological type and disc 
-inclination\footnote{While this resulted in individual bulge magnitudes not being exactly correct, 
-their large sample size allowed them to obtain a reasonable $M_{\rm BH} - L_{\rm sph}$ relation for the ensemble.}. 
-These mean statistical bulge-to-total ratios were obtained from the results of two-component (S\'ersic-bulge/exponential-disk) decompositions in the literature. \\
-Here we investigate in more detail %substructure in 
-the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams 
-using state-of-the-art galaxy decompositions (Savorgnan \& Graham 2015, hereafter \emph{Paper I}) 
-for galaxies with directly measured black hole masses.
-Our galaxies are large and nearby, which allows us to perform accurate multicomponent decompositions 
-(instead of simple bulge/disk decompositions). 
-Our decompositions were performed on $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
-which is an excellent proxy for the stellar mass, superior to the $K-$band (\citealt{sheth2010}, and references therein).
-Nine of our galaxies have $M_{\rm BH} \lesssim 10^7\rm~M_\odot$, 
-which allows us to better constrain the slope of the correlation at the low-mass end.
-Furthermore, our galaxy sample includes 17 spiral galaxies, 
-representing a notable improvement over past studies dominated by early-type galaxies. 
-In a forthcoming paper, we will explore the relation between the black hole mass and the bulge dynamical mass, 
-$M_{\rm dyn,sph} \propto R_{\rm e} \sigma^2$, and address the issue of a black hole fundamental plane.
-%{\bf This paper is structured as follows... }
-
-\section{Data}
-\label{sec:data}
-Our galaxy sample (see Table \ref{tab:sample}) 
-consists of 66 objects for which a dynamical measurement of the black hole mass had been tabulated in the literature 
-(by GS13 or \citealt{rusli2013bhmassesDM}) at the time that we started this project, 
-and for which we were able to obtain useful spheroid parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. \\
-Spheroid magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 
-bulge, disks, spiral arms, bars, rings, halo, extended or unresolved nuclear source and partially depleted core. 
-Kinematical information \citep{atlas3dIII,scott2014,arnold2014} was used 
-to confirm the presence of rotationally supported disk components in most early-type (elliptical + lenticular) galaxies, 
-and to identify their extent 
-(intermediate-scale disks that are fully embedded in the bulge, 
-or large-scale disks that encase the bulge and dominate the light at large radii). 
-It is worth stressing that, contrary to common knowledge, the majority of ``elliptical'' galaxies contain disks,
-i.e.~they are not single-component spheroidal systems.
-\emph{Paper I} presents the dataset used here, 
-%to investigate the $M_{\rm BH} - L_{\rm gal}$, $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
-including details about the data reduction process and the galaxy modelling technique that we developed. 
-It also discusses how we estimated the uncertainties\footnote{By comparing, for each of our galaxies, the measurements of the bulge magnitude 
-obtained by different authors with that obtained by us, we estimated the uncertainties on the bulge magnitudes, 
-in effect taking into account systematic errors. 
-Systematic errors include incorrect sky subtraction, inaccurate masking of contaminating sources, imprecise description of the PSF, 
-erroneous choice of model components (for example, when failing to identify a galaxy subcomponent and thus omitting it in the model, 
-or when describing a galaxy sub-component with an inadequate function), 
-the radial extent of the surface brightness profile and one's sampling of this. 
-Most of these factors are not included in popular 2D fitting codes which report only the {\bf statistical} errors associated with their fitted parameters. 
-In fact, when performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well spatially resolved -- galaxies, 
-errors are dominated by systematics rather than Poisson noise. 
-{\bf Unlike many papers, we believe that we have not under-estimated the uncertainties associated to the bulge best-fit parameters.} } 
-on the bulge magnitudes, and presents the individual 66 galaxy decompositions, 
-along with a comparison and discussion of past decompositions. \\
-Bulge luminosities\footnote{Following \cite{sani2011}, absolute luminosities were calculated 
-assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$. 
-Absolute luminosities were not corrected for cosmological redshift dimming 
-(this correction would be as small as $-0.02\rm~mag$ for galaxies at a distance of $40\rm~Mpc$ 
-or $-0.05\rm~mag$ for galaxies at a distance of $100\rm~Mpc$).} 
-(Table \ref{tab:sample}) from \emph{Paper I} were converted into stellar masses 
-using a constant $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6} = 0.6$ \citep{meidt2014}.
-We additionally explored a more sophisticated way to compute mass-to-light ratios, 
-using the color-$\Gamma_{3.6}$ relation published by 
-\citeauthor{meidt2014} (\citeyear{meidt2014}, their equation 4), 
-which allows one to estimate $\Gamma_{3.6}$ of a galaxy from its $[3.6] - [4.5]$ color. 
-Individual $[3.6] - [4.5]$ colors\footnote{These are integrated $[3.6] - [4.5]$ colors, measured in a circular aperture 
-within each galaxy's effective radius.} were taken from 
-\citeauthor{peletier2012} (\citeyear{peletier2012}, column 8 of their Table 1) 
-when available for our galaxies, 
-or were estimated from the bulge stellar velocity dispersion, $\sigma$, 
-using the color-$\sigma$ relation presented by \citeauthor{peletier2012} (\citeyear{peletier2012}, their Figure 6).
-We found that the range in $[3.6] - [4.5]$ color is small ($0.06\rm~mag$), 
-and thus the range in $\Gamma_{3.6}$ is also small ($0.04$).
-After checking that using a single $\Gamma_{3.6} = 0.6$, independent of $[3.6] - [4.5]$ color, 
-does not significantly affect the results of our analysis, 
-we decided to use individual, color-dependent mass-to-light ratios. \\
-For each galaxy, the total luminosity (or galaxy luminosity, $L_{\rm gal}$) is the sum of the luminosities of all its sub-components. 
-Due to the complexity of their modelling, 
-four galaxies (see Table \ref{tab:sample}, column 7) had their galaxy luminosities 
-underestimated\footnote{These four cases are discussed in \emph{Paper I}.}, 
-which are given here as lower limits. 
-Following GS13, we assumed a fixed uncertainty ($0.25\rm~mag$) for the absolute galaxy magnitude $MAG_{\rm gal}$. \\
-The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') 
-follows from the galaxy models presented in \emph{Paper I}. 
-Throughout this paper we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
-Two galaxies classified as E/S0 are obviously included in the early-type bin, 
-whereas two galaxies classified as S0/Sp and another two classified as mergers are included in neither the early- nor the late-type bin.\\
-The S\'ersic/core-S\'ersic classification presented in this work 
-comes from the compilation of \citet{savorgnangraham2015},
-who identified partially depleted cores according to the same criteria used by GS13.
-When no high-resolution image analysis was available from the literature, 
-they inferred the presence of a partially depleted core based on the stellar velocity dispersion:
-a spheroid is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
-or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. 
-All of the galaxies with velocity dispersions between these two limits had high-resolution images available.
-
-\input{table_sample.tex}
-
-\section{Analysis}
-\label{sec:anal}
-We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ (see Table \ref{tab:lreggal}), 
-$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}) data,
-using the BCES code from \cite{akritasbershady1996}. 
-We also repeated the analysis using both the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
-and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
-All of these three linear regression routines account for the intrinsic scatter, 
-but only the last two allow one to quantify it.
-%Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
-%can give biased results (wrong slope) when the scatter is comparable to the range of the data},
-%we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
-We report linear regressions, both symmetrical and non-symmetrical, 
-for S\'ersic/core-S\'ersic and for early/late-type galaxies.
-Symmetrical regressions are meant to be compared with theoretical expectations, 
-whereas non-symmetrical forward ($M_{\rm BH}|X$) regressions -- 
-which minimize the scatter in the $\log(M_{\rm BH})$ direction -- 
-are best used to predict black hole masses.
-
-\section{Results and discussion}
-\label{sec:res}
-
-\subsection{Black hole mass -- galaxy luminosity}
-The $M_{\rm BH} - L_{\rm gal}$ diagram is shown in Figure \ref{fig:mbhmaggal}.
-Four spiral galaxies had their total luminosities underestimated (see Table \ref{tab:sample}) 
-and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
-\cite{lasker2014anal} analyzed a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
-and claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
-which they fit with a single power-law, have consistent intrinsic scatter.
-Here, instead, thanks to our galaxy sample that includes 17 spiral galaxies, 
-we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
-That is, when considering only early-type galaxies, 
-we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
-However, our $M_{\rm BH} - L_{\rm sph}$ relation for all 66 galaxies, irrespective of their morphological type, 
-has an intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
-and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
-whereas our $M_{\rm BH} - L_{\rm gal}$ relation for 62 ($=66-4$) galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
-and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
-Because the value of the intrinsic scatter depends on the size of the uncertainties associated with the absolute magnitudes\footnote{The 
-smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
-we tested the robustness of our conclusion by increasing the uncertainties associated with the galaxy absolute magnitudes\footnote{The 
-value of the intrinsic scatter obviously depends also on the size of the uncertainties associated with the black hole masses. 
-However, black hole masses and their uncertainties have been estimated by various authors using different methods, 
-thus we have limited to no control on their values.}  
-(we originally assumed $0.25\rm~mag$).
-The intrinsic scatter of the $M_{\rm BH} - L_{\rm gal}$ relation only becomes smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation 
-when assuming an uncertainty larger than $0.7\rm~mag$ for $L_{\rm gal}$, 
-which would be significantly larger than the typical value commonly recognized in the literature, 
-and would also oddly exceed the typical uncertainty that we estimated for $L_{\rm sph}$. 
-Hence, we conclude that our determination of the relative intrinsic scatter is reliable, 
-and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies\footnote{The majority 
-of our early-type galaxies are elliptical galaxies, some of which have a bulge-to-total ratio close to 1 ($L_{\rm gal} \simeq L_{\rm sph}$).
-One might wonder whether this constitutes a bias in our analysis.
-However, we checked that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ 
-not only for early-type (elliptical + lenticular) galaxies, 
-but also for lenticular galaxies only. }, 
-but not for all (early+late-type) galaxies.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{mbh_vs_mag_tot.pdf}
-\caption{Black hole mass plotted against $3.6\rm~\mu m$ galaxy absolute magnitude. 
-Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
-red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
-Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
-Four spiral galaxies had their magnitudes overestimated (luminosities underestimated) and are shown as upper limits. 
-The red dashed line indicates the BCES bisector linear regression for the 45 early-type galaxies (E+S0), 
-with the red shaded area denoting its $1\sigma$ uncertainty. 
-$M_{\rm BH}$ correlates equally well with $L_{\rm gal}$ and $L_{\rm sph}$ only for early-type galaxies, 
-but not for all (early+late-type) galaxies. }
-\label{fig:mbhmaggal}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{mbh_vs_mag_sph.pdf}
-\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
-Symbols have the same meaning as in Figure \ref{fig:mbhmaggal}.
-The red dashed line indicates the BCES bisector linear regression for the spheroidal component of the 45 early-type (E+S0) galaxies, 
-with the red shaded area denoting its $1\sigma$ uncertainty. 
-The blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
-with the blue shaded area denoting its $1\sigma$ uncertainty. 
-The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for the core-S\'ersic and S\'ersic spheroids, respectively.}
-\label{fig:mbhmagsph}
-\end{center}
-\end{figure}
-
-\begin{table*}
-\centering
-\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ diagram.}
-\begin{tabular}{llccccc}
-\tableline\tableline
-{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm gal} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
-\tableline 
-\\
-  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - \langle MAG_{\rm gal} \rangle)/{\rm mag}]$} \\ [0.5em]
- All (62)               & BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
-                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
-                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\ [0.5em]
-                        & BCES $(X|Y)$   & $8.26 \pm 0.12$ & $-1.01 \pm 0.15$ & $-24.78$ & $-$ & $0.92$ \\
-                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
-                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\ [0.5em]
-                        & BCES Bisector  & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
-                        & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
-                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]
-
- Early-type (E+S0) (45) & BCES $(Y|X)$   & $8.56 \pm 0.07$ & $-0.44 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
-                        & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
-                        & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\ [0.5em]
-                        & BCES $(X|Y)$   & $8.56 \pm 0.08$ & $-0.64 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
-                        & mFITEXY $(X|Y)$  & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.07}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
-                        & {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\ [0.5em]
-                        & BCES Bisector  & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
-                        & mFITEXY Bisector & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
-                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.05$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]
-
-\tableline 
-\tableline
-\end{tabular}
-\label{tab:lreggal} 
-\tablecomments{For each subsample, we indicate $\langle MAG_{\rm gal} \rangle$, its average value of galaxy magnitudes. 
-In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. 
-Four spiral galaxies had their luminosities underestimated and thus are not included in the linear regression analysis 
-(the sample of all galaxies contains 66-4=62 objects). 
-When considering all galaxies, irrespective of their morphological type, 
-the $M_{\rm BH} - L_{\rm gal}$ correlation is weaker than the $M_{\rm BH} - L_{\rm sph}$ correlation, in terms of intrinsic scatter. 
-However, when considering only early-type galaxies, the $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ correlations 
-have consistent intrinsic scatter. }
-\end{table*}
-
-\subsection{Black hole mass -- spheroid luminosity}
-The $M_{\rm BH} - L_{\rm sph}$ diagram is shown in Figure \ref{fig:mbhmagsph}, 
-and the linear regression analysis is presented in Table \ref{tab:lregsph}. 
-S\'ersic and core-S\'ersic spheroids have slopes consistent with each other (within their $1\sigma$ uncertainties), 
-in disagreement with the findings of GS13. 
-The slope that we obtained for core-S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.18 \pm 0.20}$) 
-is consistent with the slope reported by GS13 in the $K_s$-band for the same population ($M_{\rm BH} \propto L_{\rm sph}^{1.10 \pm 0.20}$). 
-However, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.53 \pm 0.20}$) 
-is notably shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.73 \pm 0.55}$). \\
-Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{The classification has changed for the galaxies 
-NGC 1316, NGC 1332 and NGC 3998.} from the classification used here, 
-the main cause of the inconsistency is that the bulge-to-total ratios obtained from our galaxy decompositions 
-are different from those assumed by GS13 to convert galaxy luminosities into bulge luminosities.
-Our bulge-to-total ratios for low-luminosity S\'ersic spheroids ($3.6\rm~\mu m$ $MAG_{\rm sph} \gtrsim -22 \rm~mag$) 
-are smaller than those used by GS13. 
-The host galaxies of such bulges are late-type, spiral galaxies, 
-which typically present a complex morphology (bars, double bars, embedded disks, nuclear components, etc).
-Our galaxy models account for the extra components, 
-while the average bulge-to-total ratios of GS13 were based on less sophisticated S\'ersic-bulge/exponential-disk decompositions 
-which overestimated the bulge luminosity.
-This results in our bulge magnitudes being on average $\sim$$0.7\rm~mag$ fainter than in GS13, after accounting for the different wavelength of the data.
-At the same time, our bulge-to-total ratios for the high-luminosity S\'ersic spheroids ($3.6\rm~\mu m$ $MAG_{\rm sph} \lesssim -24 \rm~mag$) 
-are on average larger than those adopted by GS13.
-In this regime, the host systems are early-type galaxies that feature intermediate-scale disks\footnote{Intermediate-scale disks are 
-disks of stars fully embedded in the spheroidal component of their galaxy. 
-They are typical of ``disky'' elliptical galaxies (e.g.~NGC 3377), 
-but they can also be found in other types of host galaxies.
-They can be considered an intermediate class between nuclear disks, with sizes $\sim$$10-100\rm~pc$, %%
-and large-scale disks, that encase the bulge and dominate the light at large radii.}. 
-Past bulge/disk decompositions failed to correctly identify the extent of such disks and treated them as large-scale disks, 
-thus underestimating the bulge luminosity.
-The magnitudes that we obtained for such spheroids are on average $\sim$$0.5\rm~mag$ brighter than in GS13. 
-These two effects explain the shallower slope that we obtained for the S\'ersic spheroids. \\
-The slope that we obtained for S\'ersic spheroids ($1.53 \pm 0.20$) is not consistent with the value of $2.5$ 
-expected from $M_{\rm BH} \propto \sigma^5$ and $L_{\rm sph} \propto \sigma^2$. 
-In addition, the S\'ersic and core-S\'ersic spheroids appear not to define two distinct $M_{\rm BH} - L_{\rm sph}$ sequences. 
-This leads us to investigate substructure in the $M_{\rm BH} - L_{\rm sph}$ diagram for early- and late-type galaxies.
-First, we checked that the elliptical and lenticular galaxies, taken separately, have slopes consistent with each other, 
-and thus, taken together, they define a single \emph{early-type sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
-We then fit the early-type galaxies with a single log-linear regression, 
-and obtained $M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$. 
-We did not find any convincing evidence for the change in slope required for consistency 
-with the $M_{\rm BH} - \sigma$ and bent $L_{\rm sph} - \sigma$ correlations. 
-Because the change in slope should occur at $M_{\rm BH} > 10^{8 \pm 1}\rm~M_\odot$, 
-but all the early-type galaxies in our sample have $M_{\rm BH} \gtrsim 10^7\rm~M_\odot$, 
-one possible explanation is that we are still not probing enough low black hole masses for this subsample.
-An additional possibility is that there is no sharp transition going from $L_{\rm sph} \propto \sigma^2$ at low luminosities 
-to $L_{\rm sph} \propto \sigma^5$ at high luminosities. 
-Although the knowledge that many ``elliptical'' galaxies actually contain embedded stellar disks dates back  
-at least three decades  
-\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995},
-it is mainly thanks to large integral-field-spectrograph surveys of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
-that our view has been further advanced 
-and it is now commonly accepted that most ``elliptical'' galaxies contain disks. 
-Past studies that investigated the $L_{\rm sph} - \sigma$ diagram might have failed to identify and consequently model the disks 
-in intermediate-luminosity, early-type galaxies, thus overestimating $L_{\rm sph}$ 
-and mistakenly producing a sharp bend in the $L_{\rm sph} - \sigma$ correlation, rather than a continuously curved relation 
-(with $L_{\rm sph} \propto \sigma^{3-4}$ at intermediate luminosities). \\
-For the bulges of late-type galaxies we obtained $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$. 
-From a cursory inspection of Figure \ref{fig:mbhmagsph}, one might be tempted to doubt the statistical significance of this ``tentative'' \emph{late-type sequence}. 
-However, a visual inspection of the plotted data requires one to take into account the error bars 
-when judging-by-eye the strength of a correlation. 
-Similarly, the Pearson's and Spearman's correlation coefficients are not applicable because 
-they do not take into account the error bars on our data.
-We have therefore relied on the quantitative regression analysis.
-
-\subsubsection{Pseudo- versus classical bulges}
-Current views distinguish between classical bulges (which are considered to be spheroidal, pressure-supported systems, 
-formed through violent processes, such as hierarchical clustering via minor mergers), 
-and pseudo-bulges (thought to be disk-like, rotation-supported systems, 
-built from secular evolution processes, such as instabilities of their surrounding disk or bar). 
-Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
-For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
-and bars can spin-up classical bulges (e.g.~\citealt{saha2012,saha2015}), 
-thus rotation is not a definitive signature of a pseudo-bulge. 
-Furthermore, many galaxies host both a classical and a pseudo-bulge (e.g.~\citealt{erwin2003,erwin2015,
-athanassoula2005,gadotti2009,macarthur2009,erwin2010,dosanjosdasilva2013,seidel2015}). 
-In the recent literature, pseudo- and classical bulges have frequently been divided at the 
-S\'ersic index $n_{\rm sph}=2$ (e.g.~\citealt{sani2011,beifiori2012}), 
-although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
-\cite{grahamworley2008} observed no bimodality in the bulge S\'ersic indices about $n_{\rm sph}=2$ or any other value. 
-While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
-being disky components that formed from their surrounding exponential disks 
-(e.g.~\citealt{bardeen1975,hohl1975,combessanders1981,combes1990,pfennigerfriedli1991}), 
-it has been shown that mergers can create bulges with $n_{\rm sph}<2$
-(e.g.~\citealt{elichemoral2011,scannapieco2011,querejeta2015}), 
-just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
-are also well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994,jerjen2000}). 
-The use of the S\'ersic index (in addition to rotation) to identify pseudo-bulges is thus a dangerous practice. \\
-\cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
-with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
-traced by their (classical) bulges with $n_{\rm sph}>2$. 
-In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
-are taken from our galaxy decompositions (\emph{Paper I}).} 
-in the $M_{\rm BH} - L_{\rm sph}$ diagram.
-Our aim is to check whether bulges with $n_{\rm sph}<2$ 
-are offset to lower black hole masses from the correlation defined by bulges with $n_{\rm sph}>2$. 
-To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
-and we then compute the vertical offset of all bulges from this regression. 
-In Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
-Among the 23 bulges with $n_{\rm sph}<2$, 12 have a positive vertical offset and 11 have a negative vertical offset. 
-\cite{kormendy2015review} provides a list of many pseudo-bulge classification criteria, including the divide at $n_{\rm sph}=2$, 
-and cautions that each individual criterion has a failure rate of 0-25\%. 
-If this is true, we should have that no less than 75\% of bulges with $n_{\rm sph}<2$ display a negative vertical offset\footnote{One 
-reaches the same conclusion when using the vertical offset from the correlation defined by bulges with $n_{\rm sph}>3$ or even $n_{\rm sph}>4$. 
-There are 13 and 10 bulges with $n_{\rm sph}<2$ that lie above and below, respectively, the correlation traced by bulges with $n_{\rm sph}>3$. 
-Similarly, there are 15 and 8 bulges with $n_{\rm sph}<2$ that lie above and below, respectively, the correlation traced by bulges with $n_{\rm sph}>4$.}. 
-What we observe, instead, is that there are the same number of bulges with $n_{\rm sph}<2$ lying above and below 
-the correlation defined by bulges with $n_{\rm sph}>2$, 
-and that the amplitude of their offset is the same ($\lesssim 1.5\rm~dex$).
-That is, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{mbh_vs_mag_sph_psb.pdf}
-\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude (as in Figure \ref{fig:mbhmagsph}). 
-Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
-Bulges with $n_{\rm sph}<2$, claimed by some to be pseudo-bulges, are enclosed with a square. 
-The black solid line shows the BCES bisector linear regression for the spheroids that have $n_{\rm sph} \geq 2$, 
-such that $M_{\rm BH} \propto L_{\rm sph}^{1.25 \pm 0.13}$. }
-\label{fig:pseudob}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{inset_psb.pdf}
-\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$ (see Figure \ref{fig:pseudob}), 
-plotted against $n_{\rm sph}$. 
-The vertical dashed line corresponds to $n_{\rm sph} = 2$.
-The horizontal solid line is equivalent to a zero vertical offset.
-Among the bulges with $n_{\rm sph}<2$, 12 have a positive vertical offset and 11 have a negative vertical offset.
-Hence, bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
-from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
-\label{fig:offset}
-\end{center}
-\end{figure}
-
-\begin{table*}
-\centering
-\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$ diagram.}
-\begin{tabular}{llccccc}
-\tableline
-\tableline
-{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
-\tableline 
-\\
- & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
-All (66)               & BCES $(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
-                       & mFITEXY $(Y|X)$    & $8.17^{+0.06}_{-0.07}$ & $-0.43^{+0.03}_{-0.04}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
-                       & {\tt linmix\_err} $(Y|X)$     & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\ [0.5em]
-                       & BCES $(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
-                       & mFITEXY $(X|Y)$    & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.68$ \\
-                       & {\tt linmix\_err} $(X|Y)$     & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\ [0.5em]
-                       & BCES Bisector  & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
-                       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
-                       & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.03$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]
-
-$n>2$ (43)             & BCES $(Y|X)$      & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
-                       & mFITEXY $(Y|X)$    & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
-                       & {\tt linmix\_err} $(Y|X)$     & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\ [0.5em]
-                       & BCES $(X|Y)$      & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
-                       & mFITEXY $(X|Y)$    & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
-                       & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\ [0.5em]
-                       & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
-                       & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
-                       & {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]
-
-Core-S\'ersic (22) & BCES $(Y|X)$   & $9.06 \pm 0.09$ & $-0.32 \pm 0.11$  & $-25.73$ & $-$    & $0.42$ \\
-                   & mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.09}$ & $-0.26^{+0.08}_{-0.07}$ & $-25.73$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
-                   & {\tt linmix\_err} $(Y|X)$  & $9.04 \pm 0.10$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.40 \pm 0.08$ & $0.42$ \\ [0.5em]
-                   & BCES $(X|Y)$   & $9.06 \pm 0.12$ & $-0.65 \pm 0.12$  & $-25.73$ & $-$    & $0.61$ \\
-                   & mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $-0.72^{+0.17}_{-0.31}$ & $-25.73$ & $0.61^{+0.14}_{-0.09}$ & $0.68$ \\
-                   & {\tt linmix\_err} $(X|Y)$  & $9.03 \pm 0.17$ & $-0.69 \pm 0.27$ & $-25.73$ & $0.68 \pm 0.30$ & $0.64$ \\ [0.5em]
-                   & BCES Bisector  & $9.06 \pm 0.10$ & $-0.47 \pm 0.08$  & $-25.73$ & $-$    & $0.48$ \\
-                   & mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $-0.47^{+0.12}_{-0.17}$ & $-25.73$ & $-$    & $0.48$ \\
-                   & {\tt linmix\_err} Bisector & $9.04 \pm 0.14$ & $-0.44 \pm 0.12$ & $-25.73$ & $-$    & $0.46$ \\ [0.5em]
-
-S\'ersic (44) & BCES $(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
-              & mFITEXY $(Y|X)$   & $7.72^{+0.08}_{-0.09}$ & $-0.41^{+0.07}_{-0.08}$ & $-22.92$ & $0.54^{+0.08}_{-0.07}$ & $0.61$ \\
-              & {\tt linmix\_err} $(Y|X)$  & $7.73 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\ [0.5em]
-              & BCES $(X|Y)$   & $7.71 \pm 0.14$ & $-0.86 \pm 0.16$ & $-22.92$ & $-$    & $0.93$ \\
-              & mFITEXY $(X|Y)$   & $7.72^{+0.14}_{-0.13}$ & $-0.86^{+0.13}_{-0.19}$ & $-22.92$ & $0.77^{+0.13}_{-0.10}$ & $0.93$ \\
-              & {\tt linmix\_err} $(X|Y)$  & $7.73 \pm 0.14$ & $-0.86 \pm 0.17$ & $-22.92$ & $0.79 \pm  0.20$ & $0.93$ \\ [0.5em]
-              & BCES Bisector  & $7.71 \pm 0.10$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
-              & mFITEXY Bisector  & $7.72^{+0.11}_{-0.11}$ & $-0.61^{+0.10}_{-0.12}$ & $-22.92$ & $-$                    & $0.71$ \\
-              & {\tt linmix\_err} Bisector & $7.73 \pm 0.12$ & $-0.62 \pm 0.09$ & $-22.92$ & $-$    & $0.71$ \\ [0.5em]
-
-{\bf Early-type (E+S0)} (45) & BCES $(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
-                             & mFITEXY $(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40^{+0.06}_{-0.05}$ & $0.46$ \\
-                             & {\tt linmix\_err} $(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.41 \pm 0.06$ & $0.46$ \\ [0.5em]
-                             & BCES $(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
-                             & mFITEXY $(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $0.49^{+0.08}_{-0.06}$ & $0.57$\\
-                             & {\tt linmix\_err} $(X|Y)$  & $8.55 \pm 0.09$ & $-0.48 \pm 0.06$ & $-24.47$ & $0.51 \pm 0.10$ & $0.56$ \\ [0.5em]
-                             & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
-                             & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
-                             & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $-0.40 \pm 0.04$ & $-24.47$ & $-$    & $0.49$ \\ [0.5em]
-
-{\bf Late-type (Sp)} (17) & BCES $(Y|X)$    & $7.18 \pm 0.16$ & $-0.79 \pm 0.43$ & $-22.33$ & $-$    & $0.70$ \\
-                          & mFITEXY $(Y|X)$    & $7.20^{+0.15}_{-0.15}$ & $-0.53^{+0.22}_{-0.24}$ & $-22.33$ & $0.55^{+0.15}_{-0.10}$ & $0.63$ \\
-                          & {\tt linmix\_err} $(Y|X)$  & $7.24 \pm 0.19$ & $-0.46 \pm 0.32$ & $-22.33$ & $0.63 \pm 0.16$ & $0.62$ \\ [0.5em]
-                          & BCES $(X|Y)$    & $7.18 \pm 0.29$ & $-1.71 \pm 0.71$ & $-22.33$ & $-$    & $1.26$ \\
-                          & mFITEXY $(X|Y)$    & $7.38^{+0.54}_{-0.36}$ & $-2.02^{+0.71}_{-2.13}$ & $-22.33$ & $1.09^{+0.41}_{-0.24}$ & $1.50$ \\
-                          & {\tt linmix\_err} $(X|Y)$  & $7.34 \pm 0.43$ & $-1.93 \pm 1.30$ & $-22.33$ & $1.31 \pm 0.97$ & $1.43$ \\ [0.5em]
-                          & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.20}$ & $\boldsymbol{-1.15 \pm 0.27}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
-                          & mFITEXY Bisector   & $7.26^{+0.40}_{-0.28}$ & $-1.03^{+0.33}_{-0.52}$ & $-22.33$ & $-$    & $0.82$ \\
-                          & {\tt linmix\_err} Bisector & $7.27 \pm 0.33$ & $-0.96 \pm 0.37$ & $-22.33$ & $-$    & $0.78$ \\ [0.5em]
-
-\tableline 
-\tableline
-\end{tabular}
-\label{tab:lregsph} 
-\tablecomments{For each subsample, we indicate $\langle MAG_{\rm sph} \rangle$, its average value of spheroid magnitudes. 
-In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. 
-Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2). }
-\end{table*}
-
-\subsection{Black hole mass -- spheroid stellar mass}
-Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
-and its linear regression analysis in Table \ref{tab:lregmass}. 
-The bulges of the early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
-consistent with a dry-merging formation scenario\footnote{\bf In dry mergers, the black hole and the bulge grow at the same pace, 
-increasing their mass in lock step.},
-and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
-\cite{graham2012bent} reported that the $M_{\rm BH}/M_{\rm dyn,sph}$ ratio for core-S\'ersic galaxies was 0.36\% 
-($M_{\rm dyn,sph}$ is the spheroid dynamical mass), 
-and discussed the many implications of this.  
-Using a larger data sample, \cite{grahamscott2013} reported that the $M_{\rm BH}/M_{\rm *,sph}$ ratio was 0.49\% for core-S\'ersic galaxies.   
-Here we find a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.50 \pm 0.04\%$ for the 22 core-S\'ersic galaxies 
-and $0.68 \pm 0.04\%$ for the 45 early-type galaxies.  
-Among other things, this higher value (previously reported to be $0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}), 
-boosts estimates of the black hole mass function and mass density based on galaxy/spheroid luminosity functions. \\
-The bulges of the spiral galaxies trace a steeper \emph{late-type sequence}, 
-whose slope is less well constrained due to the smaller size of the subsample and, more importantly, 
-to the smaller range in $M_{\rm *,sph}$ that the subsample spans. 
-For the bulges of spiral galaxies, the BCES code returns a log-linear relation with a slope $= 3.00 \pm 1.30$, 
-while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) 
-slope $= 2.28^{+1.67}_{-1.01}$.
-More data would be welcome to better constrain the slope of this \emph{late-type sequence}, 
-although we note that direct measurements of black hole masses below $10^6\rm~M_\odot$ are extremely challenging to obtain 
-with the current technological resources. 
-In this regard, using a sample of $\sim$140 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
-bulges hosting Active Galactic Nuclei (AGNs) with virial
-black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ \citep{jiang2011a}, 
-\cite{grahamscott2015} showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges.
-The majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
-(NASA Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.} and
-we anticipate here that the correlation traced by our spiral galaxy bulges 
-may track the location of these lower mass AGN in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
-That is, the AGNs appear to be the low-mass continuation of our tentative \emph{late-type sequence} shown in Figure \ref{fig:mbhmasssph} 
-and this will be explored with more rigour in a forthcoming paper.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\columnwidth]{mbh_vs_mass_sph.pdf}
-\caption{Black hole mass plotted against spheroid stellar mass. 
-Symbols are coded according to the galaxy morphological type (see legend).
-The red dashed line indicates the BCES bisector linear regression for the bulges of the 45 early-type galaxies (E+S0), 
-with the red shaded area denoting its $1\sigma$ uncertainty. 
-The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
-a near-linear relation consistent with a dry-merging formation scenario.
-The steeper blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
-with the blue shaded area denoting its $1\sigma$ uncertainty. 
-The bulges of late-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
-indicating that gas-rich processes feed the black hole more efficiently (``quadratically'' or ``cubically'') than the host bulge grows in stellar mass. 
-We note that AGNs with $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ \citep{jiang2011a} appear to follow the blue line 
-(see Graham et al. 2015, \emph{in preparation}).}
-\label{fig:mbhmasssph}
-\end{center}
-\end{figure}
-
-\section{Conclusions}
-Using $3.6\rm~\mu m$ \emph{Spitzer} images, 
-we have performed accurate multicomponent decompositions (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, depleted core, etc.), 
-which were checked to be consistent with the two-dimensional galaxy kinematics, 
-for 66 nearby galaxies with a dynamical measurement of their black hole mass.
-We have derived galaxy luminosities, spheroid luminosities and spheroid stellar masses. 
-Our galaxy sample, besides being to date the largest sample with reliable bulge masses used to investigate black hole mass scaling relations, 
-contains 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7 \rm~M_{\odot}$. 
-This constitutes a significant improvement over past studies whose samples were biased towards high-mass, early-type galaxies. \\
-Using our state-of-the-art dataset, we have investigated substructure in the $M_{\rm BH} - L_{\rm gal}$, $M_{\rm BH} - L_{\rm sph}$ 
-and $M_{\rm BH} - M_{\rm *,sph}$ diagrams. 
-Our principal conclusions are: \\
-
-\begin{itemize}
-\item The logarithmic $M_{\rm BH} - M_{\rm *,sph}$ relation for the spheroidal components of early-type (elliptical + lenticular) galaxies 
-      has a slope of $1.04 \pm 0.10$ and intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
-      We call this tight correlation an \emph{early-type sequence}. 
-      The $M_{\rm BH} - M_{\rm *,sph}$ log-relation for the bulges of late-type (spiral) galaxies has a slope of $2-3$,
-      which is less well constrained due to
-      the smaller size of the subsample and, more importantly, the smaller range in spheroid stellar mass 
-      ($3 \times 10^9 \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 3 \times 10^{10}$) that the subsample spans. 
-      We refer to this correlation as a \emph{late-type sequence}. 
-      In (gas-poor) early-type galaxies, the black hole and the stellar content of the spheroidal component grow at the same pace, 
-      following a linear $M_{\rm BH} - M_{\rm *,sph}$ relation. 
-      In (gas-rich) spiral galaxies, the black hole grows faster than its host bulge, 
-      following a quadratic/cubic $M_{\rm BH} - M_{\rm *,sph}$ relation. 
-      Unsurprisingly, in a color-magnitude diagram\footnote{Total $B-V$ colors, 
-      corrected for inclination, Galactic extinction and K-correction, 
-      were taken from the HyperLEDA online database \citep{hyperleda}.}, 
-      our early- and late-type galaxies occupy the two distinct regions of the red sequence and the blue cloud, respectively. 
-      For analogy with this, we refer to our \emph{early-type sequence} as a \emph{red sequence} 
-      and to our \emph{late-type sequence} as a \emph{blue sequence}. 
-\item The median $M_{\rm BH}/M_{\rm *,sph}$ ratio for the early-type galaxies is $0.68 \pm 0.04\%$. 
-      This value is dramatically larger than what was previously reported ($0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}), 
-      but in close agreement with the value of $0.49\%$ reported by \cite{grahamscott2013} for core-S\'ersic spheroids. 
-\item The logarithmic $M_{\rm BH} - M_{\rm *,sph}$ relations for the core-S\'ersic and S\'ersic spheroids 
-      have slopes with over-lapping uncertainties ($1.19 \pm 0.23$ and $1.48 \pm 0.20$, respectively).  
-      The S\'ersic relation is less steep than, but also has over-lapping uncertainties with, 
-      the slope of $2.22 \pm 0.58$ reported by \cite{scott2013} for S\'ersic spheroids.  
-      The distinction between core-S\'ersic and S\'ersic spheroids found by \cite{scott2013} is thus less pronounced here. 
-\item In the $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) diagram, for early-type galaxies, 
-      we did not observe the change in slope required for consistency with the log-linear $M_{\rm BH} - \sigma$ and bent $L_{\rm sph} - \sigma$ correlations.
-      This issue of inconsistency remains therefore an open question. 
-      It might be that we are still not probing enough low-mass black holes ($M_{\rm BH} < 10^7\rm~M_\odot$) 
-      for the subsample of early-type galaxies, 
-      or that the transition from  $L_{\rm sph} \propto \sigma^2$ at low luminosities to $L_{\rm sph} \propto \sigma^{(5-6)}$ at high luminosities 
-      is less sharp than previously thought.
-      We intend to investigate this point in our future work. 
-\item Spheroids with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
-      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. 
-\item The $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ correlations have the same level of intrinsic scatter 
-      when considering early-type galaxies only. 
-      Once reasonable numbers of spiral galaxies are included, 
-      $M_{\rm BH}$ correlates better with $L_{\rm sph}$ than with $L_{\rm gal}$ {\bf (see also \citealt{erwingadotti2012,beifiori2012})}. 
-\end{itemize}
-
-Finally, we note that some of the literature-sourced black hole mass measurements used by \cite{kormendyho2013} are different from those used here.  
-While these differences are smaller than $18\%$ for $78\%$ of the galaxies, 
-in three cases (NGC 0821, NGC 4291, and NGC 3393) they are larger than a factor of $2.3$.  
-We repeated our entire analysis using only the 58 galaxies that are in common between our sample and the sample of \cite{kormendyho2013}, 
-assuming for these galaxies the black hole mass measurements published by \cite{kormendyho2013}. 
-In doing so, we found that none of our conclusions changed.
-
-\begin{table*}
-\centering
-\caption{Linear regression analysis of the $M_{\rm BH} - M_{\rm *,sph}$ diagram.}
-\begin{tabular}{llccccc}
-\tableline
-\tableline
-{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle M_{\rm *,sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
-\tableline 
-\\
-  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} / \langle M_{\rm *,sph} \rangle)]$} \\ [0.5em]
- Core-S\'ersic (22)     & BCES $(Y|X)$      & $9.06 \pm 0.09$ & $0.86 \pm 0.28$ & $10^{11.28}$ & $-$ & $0.42$ \\
- 			& mFITEXY $(Y|X)$   & $9.06^{+0.08}_{-0.08}$ & $0.68^{+0.21}_{-0.20}$ & $10^{11.28}$ & $0.36^{+0.09}_{-0.06}$ & $0.42$ \\
-  			& {\tt linmix\_err} $(Y|X)$     & $9.04 \pm 0.10$ & $0.64 \pm 0.25$ & $10^{11.28}$ & $0.40 \pm 0.09$ & $0.42$ \\ [0.5em]
-			& BCES $(X|Y)$      & $9.06 \pm 0.12$ & $1.70 \pm 0.32$ & $10^{11.28}$ & $-$ & $0.61$ \\
- 			& mFITEXY $(X|Y)$   & $9.03^{+0.15}_{-0.16}$ & $1.90^{+0.85}_{-0.46}$ & $10^{11.28}$ & $0.62^{+0.13}_{-0.10}$ & $0.68$ \\
- 			& {\tt linmix\_err} $(X|Y)$     & $9.03 \pm 0.17$ & $1.80 \pm 0.70$ & $10^{11.28}$ & $0.67 \pm 0.30$ & $0.65$ \\ [0.5em]
- 			& BCES Bisector     & $9.06 \pm 0.10$ & $1.19 \pm 0.23$ & $10^{11.28}$ & $-$ & $0.47$ \\
- 			& mFITEXY Bisector  & $9.05^{+0.12}_{-0.13}$ & $1.12^{+0.35}_{-0.27}$ & $10^{11.28}$ & $-$                    & $0.46$ \\
- 			& {\tt linmix\_err} Bisector	& $9.04 \pm 0.14$ & $1.06 \pm 0.26$ & $10^{11.28}$ & $-$	& $0.45$ \\ [0.5em]
-
- S\'ersic (44)		& BCES $(Y|X)$      & $7.71 \pm 0.09$ & $0.95 \pm 0.21$ & $10^{10.25}$ & $-$ & $0.64$ \\
- 			& mFITEXY $(Y|X)$   & $7.72^{+0.10}_{-0.09}$ & $0.96^{+0.21}_{-0.21}$ & $10^{10.25}$ & $0.58^{+0.09}_{-0.07}$ & $0.64$ \\
- 			& {\tt linmix\_err} $(Y|X)$     & $7.73 \pm 0.10$ & $0.98 \pm 0.24$ & $10^{10.25}$ & $0.59 \pm 0.08$ & $0.65$ \\ [0.5em]
- 			& BCES $(X|Y)$      & $7.71 \pm 0.16$ & $2.52 \pm 0.54$ & $10^{10.25}$ & $-$ & $1.11$ \\
- 			& mFITEXY $(X|Y)$   & $7.72^{+0.16}_{-0.16}$ & $2.49^{+0.69}_{-0.45}$ & $10^{10.25}$ & $0.93^{+0.15}_{-0.13}$ & $1.10$ \\
- 			& {\tt linmix\_err} $(X|Y)$     & $7.73 \pm 0.17$ & $2.48 \pm 0.59$ & $10^{10.25}$ & $0.95 \pm 0.27$ & $1.10$ \\ [0.5em]
- 			& BCES Bisector     & $7.71 \pm 0.11$ & $1.48 \pm 0.20$ & $10^{10.25}$ & $-$ & $0.74$ \\
- 			& mFITEXY Bisector  & $7.72^{+0.13}_{-0.13}$ & $1.49^{+0.33}_{-0.28}$ & $10^{10.25}$ & $-$    & $0.74$ \\
- 			& {\tt linmix\_err} Bisector	& $7.73 \pm 0.14$ & $1.49 \pm 0.24$ & $10^{10.25}$ & $-$	& $0.74$ \\ [0.5em]
-
-{\bf Early-type (E+S0)} (45)  & BCES $(Y|X)$       & $8.56 \pm 0.07$ & $0.85 \pm 0.12$ & $10^{10.81}$ & $-$ & $0.48$ \\
-                              & mFITEXY $(Y|X)$     & $8.56^{+0.06}_{-0.07}$ & $0.83^{+0.11}_{-0.11}$ & $10^{10.81}$ & $0.42^{+0.07}_{-0.05}$ & $0.48$ \\
-                              & {\tt linmix\_err} $(Y|X)$     & $8.55 \pm 0.07$ & $0.82 \pm 0.12$ & $10^{10.81}$ & $0.43 \pm 0.06$ & $0.48$ \\ [0.5em]
-                              & BCES $(X|Y)$       & $8.56 \pm 0.09$ & $1.27 \pm 0.13$ & $10^{10.81}$ & $-$ & $0.59$ \\
-                              & mFITEXY $(X|Y)$     & $8.54^{+0.08}_{-0.09}$ & $1.32^{+0.18}_{-0.15}$ & $10^{10.81}$ & $0.53^{+0.08}_{-0.07}$ & $0.61$ \\
-                              & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $1.29 \pm 0.17$ & $10^{10.81}$ & $0.54 \pm 0.11$ & $0.59$ \\ [0.5em]
-                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.04 \pm 0.10}$ & $\boldsymbol{10^{10.81}}$ & $-$ & $\boldsymbol{0.51}$ \\
-                              & mFITEXY Bisector    & $8.55^{+0.07}_{-0.08}$ & $1.05^{+0.14}_{-0.12}$ & $10^{10.81}$ & $-$                    & $0.51$ \\
-                              & {\tt linmix\_err} Bisector    & $8.55 \pm 0.08$ & $1.03 \pm 0.10$ & $10^{10.81}$ & $-$    & $0.51$ \\ [0.5em]
-
-{\bf Late-type (Sp)} (17)    & BCES $(Y|X)$    & $7.18 \pm 0.17$ & $1.95 \pm 1.52$ & $10^{10.05}$ & $-$ & $0.74$ \\ 
-                             & mFITEXY $(Y|X)$     & $7.20^{+0.15}_{-0.16}$ & $1.22^{+0.70}_{-0.62}$  & $10^{10.05}$ & $0.59^{+0.16}_{-0.11}$ & $0.66$ \\
-                             & {\tt linmix\_err} $(Y|X)$  & $7.23 \pm 0.19$ & $0.96 \pm 0.96$ & $10^{10.05}$ & $0.67 \pm 0.16$ & $0.65$ \\ [0.5em]
-                             & BCES $(X|Y)$    & $7.18 \pm 0.39$ & $5.89 \pm 3.40$ & $10^{10.05}$ & $-$ & $1.70$ \\
-                             & mFITEXY $(X|Y)$     & $7.44^{+1.45}_{-0.52}$ & $7.14^{+26.31}_{-3.01}$ & $10^{10.05}$ & $1.49^{+0.56}_{-0.36}$ & $2.08$ \\
-                             & {\tt linmix\_err} $(X|Y)$  & $7.42 \pm 0.64$ & $6.96 \pm 6.73$ & $10^{10.05}$ & $1.83 \pm 1.86$ & $2.03$ \\ [0.5em]
-                             & {\bf BCES Bisector}& $\boldsymbol{7.18 \pm 0.21}$ & $\boldsymbol{3.00 \pm 1.30}$ & $\boldsymbol{10^{10.05}}$ & $-$ & $\boldsymbol{0.94}$ \\
-                             & {\bf mFITEXY Bisector}    & $\boldsymbol{7.24^{+1.04}_{-0.39}}$ & $\boldsymbol{2.28^{+1.67}_{-1.01}}$  & $\boldsymbol{10^{10.05}}$ & $-$    & $\boldsymbol{0.79}$ \\
-                             & {\tt linmix\_err} Bisector & $7.26 \pm 0.47$ & $1.94 \pm 1.24$ & $10^{10.05}$ & $-$    & $0.74$ \\ [0.5em]
-
-\tableline 
-\tableline
-\end{tabular}
-\label{tab:lregmass} 
-\tablecomments{For each subsample, we indicate $\langle M_{\rm *,sph} \rangle$, its average value of spheroid stellar masses. 
-In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $\log(M_{\rm BH})$ direction. }
-\end{table*}
-
-\acknowledgments
-GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. 
-{\bf We thank the anonymous referee for their thorough review and highly appreciate the comments and suggestions, 
-which significantly contributed to improving the quality of the publication. } \\
-This research was supported by Australian Research Council funding through grants
-DP110103509 and FT110100263.
-This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
-on-board the Spitzer Space Telescope, 
-which is operated by the Jet Propulsion Laboratory, 
-California Institute of Technology under a contract with NASA.
-This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
-which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
-under contract with the National Aeronautics and Space Administration. 
-We acknowledge the usage of the HyperLeda database (\url{http://leda.univ-lyon1.fr}).
-The BCES routine \citep{akritasbershady1996} was run via the python module 
-written by Rodrigo Nemmen \citep{nemmen2012}, which is available at \url{https://github.com/rsnemmen/BCES}.
-
-\bibliography{SMBHbibliography}
-
-\clearpage
+The header of column 5 in Table 4 is incorrectly given as $\langle MAG_{\rm sph} \rangle$. 
+It should read $\langle M_{\rm *,sph} \rangle$.
 

### 2016-03-14 thesis/acknowledgement.tex
acknowl.

@@
 
-alister, duncan, c blake, greg
+First thanks go to my supervisor Alister, 
+for offering me a PhD project in the country I always dreamt to live in, 
+for guiding me during this long journey, 
+for his patience and support, 
+for all the lessons I've learnt, 
+and for being constantly available to all of his students, 
+no matters how many late nights he had to spend in the office correcting my writings. 
+Second thanks go to my co-supervisor Duncan for the constructing scientific conversations that we had, 
+for his useful comments and suggestions, 
+and for his genuine interest in making sure that at any stage everything was going well. 
+Very special thanks are reserved to Chris Blake, Duncan, Greg, and Karl, 
+for their invaluable, immediate, unconditionate support, when I most than ever needed it.
 
-karl,
-
-gonzalo, rob, piero, glenn, anna, angela,
-
-elisa, shaun, silvia, james
-
-gym friends, rock climbing friends
+%To my family and in particular to zia Anna and Suzy for being such enviable badasses 
+%and such great examples. 
+%
+%To my PhD brothers and sisters, Angela, Anna, Gonzalo, Pierluigi, and Rob, 
+%I'm glad I've been on this boat in your excellent company, guys. 
+%Many thanks also to Glenn and Jeff for your informal and very comfortable attitude, 
+%for always encouraging me to do my best and for all the good laughs we've had. 
+%
+%To my irreplaceable friends Elisa, Gonzalo, Greg $\heartsuit$ Anna, James, Shaun, Silvia, 
+%thank you very much for being real. 
+%
+%And last, to Garry, because you might have glimpsed a tinder that already was inside me, 
+%but you are doing a very good job at making it a blaze.

### 2016-03-14 thesis/conclusions.tex
acknowl.

@@
 and various properties of the host spheroid, 
-aiming at a more profound understanding of the co-evolution between SMBHs and galaxies. 
+aiming at a more profound understanding of the co-evolution between SMBHs and their host galaxies. 
 A summary of our principal findings and some additional considerations are presented here. 
@@
 given the level of detail to which our galaxy decompositions were carried out, 
-we do not consider possible for current automatic routines to reproduce our analysis. \\
+we do not consider possible for current automatic routines to reproduce our human-supervised analysis. \\
 In our 1D galaxy decomposition code, the minimisation routine is based on the Levenberg-Marquardt algorithm, 
@@
 for semi-analytical models and simulations of galaxy evolution that include black hole growth, 
-and it also affects calculations of gravitational waves background from SMBH binary coalescence 
-(but see \citealt{shankar2016}). \\
+and it also affects calculations of gravitational waves background from SMBH binary coalescence. 
+However, it is important to keep in mind the warnings of \citeauthor{merritt2013book} 
+(\citeyear{merritt2013book}; see also \citealt{ferraresemerritt2000,merrittferrarese2001ms,merrittferrarese2001sphinfl,
+valluri2004,ferrareseford2005}), 
+who cautioned that the majority of stellar-dynamics based black hole mass measurements 
+are likely to have been overestimated by a factor of $3$ to $4$ 
+due to an insufficient spatial resolution of the sphere-of-influence of black holes. 
+His concern seems to be confirmed by the very recent findings of \citet{shankar2016}, 
+who argued that the current sample of directly measured black hole masses 
+is highly biased by the fact that their detectability 
+is subject to the requirement of spatially resolve their gravitational sphere-of-influence. 
+This selection effect allows us to see only the upper envelope of the ``true'' black hole mass correlations, 
+artificially increasing the normalization of the $M_{\rm BH} - \sigma_*$ correlation by a factor of $\approx 3$ 
+and even more dramatically that of the $M_{\rm BH} - M_{\rm *,sph}$ correlation. 
+New black hole mass measurements obtained with the extraordinary spatial resolution of the next generation 
+30-meter class telescopes will help shed light on this point.  \\
 
-m-n? \\
+In Chapter \ref{ch:mn} \citep{paperIII}, 
+we analysed the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
+and found that in the former early- and late-type galaxies split into two separate correlations, 
+whereas in the latter all galaxies -- irrespective of their morphological type -- define a single correlation. 
+Our $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
+show consistent amount of intrinsic scatter, 
+in agreement with the results from \citet{grahamdriver2007}. 
+The present dataset allows one to explore also the relation of the black hole mass with 
+the spheroid central surface density, $\mu_{\rm 0, sph}$, 
+and the spheroid deprojected central stellar density, $\rho_{\rm *,0,sph}$. \\
 
@@
 
-%(but see Shankar et al.~\emph{submitted to MNRAS} TBD). \\
+\vspace{5cm}
+\begin{flushright}
+\emph{Keep looking up. }
+\end{flushright}

### 2016-03-15 thesis/conclusions.tex
poco

@@
 which was not found using the individual datasets of three of the four aforementioned studies. 
-From this we concluded that some of the galaxy decompositions were not accurate. 
+From this we concluded that some of their galaxy decompositions were not accurate. 
 Chapter \ref{ch:recov-mn} emphasises the importance of a correct, physically motivated selection of model components 
@@
 Our subsample of S\'ersic spheroids defines a less steep $M_{\rm BH} - L_{\rm sph}$ 
-sequence than previously reported by \citet{grahamscott2013}. 
-We did not observe any offset of spheroids with S\'ersic index $n_{\rm sph} < 2$ 
+sequence than previously reported \citep{grahamscott2013}. 
+Looking at the spheroids with S\'ersic index $n_{\rm sph} < 2$, 
+we did not observe any systematic offset 
 from the $M_{\rm BH} - L_{\rm sph}$ correlation traced by spheroids with $n_{\rm sph} > 2$, 
@@
 We identified two distinct trends in the $M_{\rm BH} - M_{\rm *,sph}$ diagram, 
-that is, a \emph{red sequence} of early-type galaxies (elliptical+lenticular) 
+that is, a \emph{red sequence} of early-type (elliptical+lenticular) galaxies 
 following $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$ 
-and a dramatically steeper \emph{blue sequence} of late-type galaxies (spiral) 
+and a dramatically steeper \emph{blue sequence} of late-type (spiral) galaxies 
 following $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$. 
@@
 $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ collected by \citet{grahamscott2015} 
-appear to be the low-mass continuation of the $M_{\rm BH} - M_{\rm *,sph}$ sequence traced by our spiral galaxies. 
+appears to be the low-mass continuation of the $M_{\rm BH} - M_{\rm *,sph}$ sequence traced by our spiral galaxies. 
 Finally, we note that our estimate of the normalization of the $M_{\rm BH} - M_{\rm *,sph}$ relation for early-type galaxies 
@@
 in agreement with the results from \citet{grahamdriver2007}. 
-The present dataset allows one to explore also the relation of the black hole mass with 
-the spheroid central surface density, $\mu_{\rm 0, sph}$, 
-and the spheroid deprojected central stellar density, $\rho_{\rm *,0,sph}$. \\
+The present dataset allows one to explore also the correlation of black hole mass with 
+spheroid central surface density, $\mu_{\rm 0, sph}$, 
+and spheroid deprojected central stellar density, $\rho_{\rm *,0,sph}$. \\
 
@@
 therefore these galaxies should be considered as legitimate members of the $M_{\rm BH} - \sigma$ correlation. 
-An alternative possibility for the CCGs is that their partially depleted core 
-has been replenished by stars, globular clusters and nuclear star clusters 
+An alternative possibility for the CCGs is that their partially depleted cores 
+have been replenished by stars, globular clusters and nuclear star clusters 
 acquired from minor dry mergers, 
-where the accreted satellite galaxies do not host a massive black hole. 
+where the accreted satellite galaxies did not host a massive black hole. 
 However, high-resolution cosmological simulations seem to favour an ``inside-out'' formation scenario 
@@
 i.e.~they experienced negligible evolution over the last $10 \rm~Gyr$. 
-If also their black holes has had little or no mass accretion since $z = 2$, 
+If also their black holes have had little or no mass accretion since $z = 2$, 
 assuming that the $M_{\rm BH} - M_{\rm *,sph}$ relation was already in place $10 \rm~Gyr$ ago, 
@@
 is roughly the same as that at $z=2$. 
-Therefore, finding a larger number of local galaxies with the same charachteristics of the aforementioned five 
+Therefore, finding a larger number of local galaxies with the same charachteristics as the aforementioned five 
 would be helpful to study the redshift evolution of the $M_{\rm BH} - M_{\rm *,sph}$ 
@@
 However, it should be noted that their criterion of high mass and compactness relies on the \emph{galaxy} properties 
-rather than on the \emph{spheroid} properties, 
-therefore a number of these candidates might not be real descendant of the $z=2$ population\footnote{Some 
+rather than the \emph{spheroid} properties, 
+therefore a number of these candidates might not be real descendants of the $z=2$ population\footnote{Some 
 candidates might be lenticular galaxies with compact \emph{galaxy} sizes and large disc-to-total ratios, 
 therefore their spheroids would be significantly less massive than the $z=2$ red nuggets. }. 
-The same holds for the simulated compact massive galaxies of \citet{wellons2016}. 
-It would be interesting to perform photometric decompositions for these 76 candidates 
-and select only those with compact massive \emph{spheroids}.
+The same concern holds for the simulated compact massive galaxies of \citet{wellons2016}. 
+It would be interesting to perform photometric decompositions 
+for the observed 76 compact massive galaxies of \citet{saulder2015} 
+and for those simulated by \citet{wellons2016}, 
+to select only those with compact massive \emph{spheroids}.
+
+\citet{kormendy2011} and \citet{kormendyho2013} argued that black holes correlate only 
+with the remnants of major mergers, i.e.~classical bulges and elliptical galaxies, 
+and that
 

### 2016-03-16 thesis/abstract.tex
abstract

\chapter*{Abstract}

Supermassive black holes in the local Universe obey a surprisingly large number of scaling laws 
that involve the black hole mass and various properties of the host spheroids. 
These ``black hole mass scaling relations'' reveal a strong symbiosis between galaxies and black holes, 
define important constraints about their co-evolution through the cosmic time, 
and set the boundary conditions (at $z=0$) for theoretical models and simulations of galaxy evolution.

A careful galaxy decomposition is required to accurately measure a galaxy's spheroid properties. 
Recent studies have performed structural decomposition 
for similar samples of galaxies with a direct measure of the black hole mass, 
but they have not converged to the same conclusions. 
This is because their best-fit model parameters for the same galaxy were often significantly different 
due to various systematic effects, 
and their models for the same galaxy were frequently not consistent with each other in terms of fitted components. 
Moreover, none of these studies attempted an individual galaxy-by-galaxy comparison of their models 
with the previous literature. 
We have now made this comparison, identified the optimal decomposition, 
and obtained improved black hole mass scaling relations.

Using \emph{Spitzer} observations at $3.6 ~\mu \rm m$, 
which is the best available wavelength band to trace the stellar mass, 
we performed state-of-the-art structural decompositions for $66$ galaxies 
with a direct measure of their black hole mass. 
Thanks to a meticulous inspection of each galaxy's substructure -- 
through photometric and isophotal analysis, unsharp masking, auxiliary information extracted from the literature, 
and, for the first time, kinematic maps, 
we are able to identify \emph{a priori} the physical galaxy components. 
Our multicomponent models account for spheroid, large-scale disc, 
embedded or nuclear discs, spiral arms, bars, rings, halo, extended or unresolved nuclear source and partially depleted core. 
The combination of photometric and kinematic information was crucial 
to confirm the presence of rotationally supported components in most early-type (elliptical+lenticular) galaxies, 
and to identify their radial extent (nuclear, intermediate-scale or large-scale discs). 
Upon performing galaxy decompositions with both one-dimensional (1D) and two-dimensional (2D) parametric techniques, 
we observed no systematic differences between the results from 1D and 2D methods, 
but we found more advantages in the former.

%Our black hole mass range spans 5 orders of magnitude and allows us to explore the less studied low-mass end of the correlations. 
%We use Spitzer/IRAC 3.6  mosaics because the 3.6  luminosity is the best tracer of the stellar mass.

We confirm that S\'ersic and core-S\'ersic galaxies follow different trends and therefore are associated to different evolutionary scenarios.

We present updates and modifications to several key black hole mass scaling relations, 
and discuss the important implications for galaxy evolution models.

Unlike previous studies that mainly investigated high-mass, early-type galaxies, 
our sample contains a large number of spiral galaxies with low black hole masses ($<10^7 M$), 
and allows us to better investigate the poorly studied low-mass end of the black hole scaling relations.
We present updates and modifications to several key black hole mass scaling relations, showing that early-type (elliptical+lenticular) 
and late-type (spiral) galaxies follow different trends and thus their black holes grow at a different pace, 
and we discuss the important implications for galaxy evolution models.

### 2016-03-16 thesis/conclusions.tex
abstract

@@
 to select only those with compact massive \emph{spheroids}. 
-
 \citet{kormendy2011} and \citet{kormendyho2013} argued that black holes correlate only 
 with the remnants of major mergers, i.e.~classical bulges and elliptical galaxies, 
-and that
+and that the growth of the most massive black holes happened by means of a co-evolution with their host galaxies 
+via a series of mergers and AGN feedback. 
+The universality of this picture is contradicted by galaxies like Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115. 
+These galaxies have classical bulges, 
+they host some of the most massive black holes known ($10^9 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 10^{10}$), 
+but are not the product of major mergers as the majority of today's massive elliptical galaxies. 
+In effect, these galaxies have conserved their $10 \rm~Gyr$ old compact massive spheroids 
+because they had little or no evolution since $z \approx 2$; 
+note that $z \approx 3$ is the epoch that corresponds to the highest cosmic merger rate 
+for galaxies more massive than $10^{10} \rm~M_\odot$ (e.g.~\citealt{conselice2008}).
 

### 2016-03-17 thesis/ellicular.tex
corrections to chapters

@@
-\chapter{Monster black holes in compact massive spheroids with intermediate scale discs}
+\chapter{Monster Black Holes in (Compact) Massive Spheroids with Intermediate-Scale Discs}
 \label{ch:ellic}
@@
 no mention of the mass-size relation was made in Chapter \ref{ch:intro} 
-because not immediately related to SMBHs. 
+because it is not immediately related to SMBHs. 
 Therefore, a more extensive introduction of this last point is given here. \\
 
-It has been claimed that high-redshift passive galaxies were significanly more compact 
+It has been claimed that a considerable number of high-redshift passive galaxies are significantly more compact 
 than their local counterparts. 
@@
 at $z=1.4-2.5$ with stellar masses $\gtrsim 10^{11} \rm~M_\odot$ 
-and effective radii significantly smaller than those of local couterparts. 
+and effective radii significantly smaller than those of local counterparts. 
 \citet{trujillo2006} analysed ten massive $\approx 5 \times 10^{11} \rm~M_\odot$ galaxies at $z=1.2-1.7$ 
@@
 those of local descendants, 
-and silimilar conclusions were reached by several other studies 
+and similar conclusions were reached by several other studies 
 (e.g.\citealt{toft2007,trujillo2007,zirm2007,buitrago2008,damjanov2009}). 
 While some studies have pointed out that ``progenitor bias''\footnote{``Progenitor bias'' refers to sample confusion 
-of the local descendants of high-redhift massive quiescent galaxies. 
+of the local descendants of high-redshift massive quiescent galaxies. 
 While some of the $z=0$ red-sequence galaxies might have had a passive evolution since $z \approx 2$, 
@@
 However, not enough satellites have been found around massive galaxies 
-to support the minor dry mergers scenario 
+to support the minor dry merger scenario 
 (e.g.~\citealt{khochfarburkert2006,maller2006,hopkins2009,naab2009,mclure2013}). 
 A fascinating solution to the problem was proposed by \citet{graham2013review}, 
-who suggested that the high-redshift compact massive spheroids have evolved into the bulges 
+who suggested that the high-redshift compact massive spheroids 
+(also dubbed ``red nuggets'', \citealt{damjanov2009}) have evolved into the bulges 
 of today's massive early-type disc galaxies (see also \citealt{dullograham2013cores} and \citealt{driver2013}). 
 This view was confirmed by \citet{gds2015}, 
-who used bulge/disc decomposition 
+who used published, reliable bulge/disc decompositions 
 to unveil a large number of previously unnoticed local stellar spheroidal systems 
@@
 and similar number density as the high-redshift compact massive spheroids. 
-\citet{gds2015} advocated the growth of two-dimensional stellar disks around the compact massive spheroids 
+\citet{gds2015} advocated the growth of two-dimensional stellar discs around the compact massive spheroids 
 to explain the evolution of these objects. \\
 
-The remainder of this chapter comprises the published version of the paper 
+Here we focus on five local early-type galaxies (Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115) 
+for which we performed accurate multicomponent decomposition 
+with the aid of photometric and kinematic information. 
+Our analysis shows that these galaxies all share the same morphological structure: 
+a stellar spheroidal component with the same properties (massive, compact, and old) as the high-redshift red nuggets 
+and an intermediate-scale stellar disc that remains embedded within the spheroid. 
+These five galaxies had their black hole masses estimated with a direct method.  
+Four of them had been previously modelled by other studies \citep{rusli2011,vandenbosch2012,walsh2015,yildirim2015}, 
+which failed to account for the correct radial extent of the stellar disc 
+and consequently underestimated the spheroid luminosity.
+This yielded unusually large $M_{\rm BH} / L_{\rm sph}$ ratios.  \\
+
+The remainder of this Chapter comprises the published version of the paper 
 ``Explaining the reportedly overmassive black holes in early-type galaxies with intermediate-scale discs'' 

### 2016-03-17 thesis/galaxyvivisection.tex
corrections to chapters

@@
 during which I was shown their 2D galaxy decomposition method using {\tt GALFIT3} \citep{peng2010}. 
-This helped set the basis for the development of my own galaxy decomposition strategy. \\
+This helped set the basis for the development of my own galaxy decomposition strategy, 
+which is detailed in this Chapter. \\
 
@@
 
-The remainder of this chapter comprises the published version of the paper 
+The remainder of this Chapter comprises the published version of the paper 
 ``Supermassive Black Holes and Their Host Spheroids. I. Disassembling Galaxies'' 

### 2016-03-17 thesis/introduction.tex
corrections to chapters

@@
 
-\section{Supermassive black holes} 
+\section{Supermassive Black Holes} 
 An astrophysical black hole is a region of the space-time whose escape velocity is greater than the speed of light.
@@
 
-\subsection{Measuring black hole masses}
+\subsection{Measuring Black Hole Masses}
 Techniques to measure the mass of SMBHs can be divided into two main categories: direct and indirect methods 
@@
 
-\subsection{Scaling relations}
+\subsection{Scaling Relations}
 Over the last three decades, observations have demonstrated that 
@@
 
-\subsection{Co-evolution and AGN feedback}
+\subsection{Co-evolution and AGN Feedback}
 The tightness (or small scatter) of the observed black hole mass correlations led to the idea
@@
 
-\subsection{The S\'ersic/core-S\'ersic paradigm}  
+\subsection{The S\'ersic/Core-S\'ersic Paradigm}  
 \label{sec:bent}
@@
 
-\subsection{S\'ersic and core-S\'ersic spheroids} 
+\subsection{S\'ersic and Core-S\'ersic Spheroids} 
 \label{sec:corser}
@@
 
-\subsection{Origin of SMBHs}
+\subsection{Origin of Supermassive Black Holes}
 As of today, the formation of SMBHs is still an unsolved puzzle. 
@@
 
-\subsection{Monster black holes}
+\subsection{Monster Black Holes}
 \label{sec:monsters}
@@
 
-\section{Galaxy decomposition}
+\section{Galaxy Decomposition}
 Galaxy decomposition is a parametric analysis that allows one to fit the surface brightness distribution
@@
 
-\subsection{Photometry and kinematics}
+\subsection{Photometry and Kinematics}
 \label{sec:photokin}
@@
 
-\subsection{A compendium of the previous literature }
+\subsection{A Compendium of the Previous Literature }
 Over the past nine years, five independent studies 
@@
 
-\section{Thesis outline}
+\section{Thesis Outline}
 The aim of this thesis is to refine and re-investigate several black hole mass scaling relations 

### 2016-03-17 thesis/mm.tex
conclusions ellicular
corrections to chapters

@@
 In Chapter \ref{ch:galviv}, reliable and accurate multicomponent decompositions were presented 
-for 66 galaxies out of the 75 belonging to the initial sample. 
-These 66 galaxies constitute our final sample, 
-which is currently the largest sample to date used to investigate correlations between 
+for 66 galaxies, our final sample, out of the 75 belonging to the initial sample. 
+These 66 galaxies currently constitute the largest sample to date 
+with reliable and homogeneous (i.e.~derived in a systematic and consistent manner) 
+structural decompositions 
+that can be used to investigate correlations between 
 directly measured black hole masses and host galaxy parameters. \\
@@
 
-\item Some studies have distinguished pseudobulges and classical bulges according to their S\'ersic index, 
+\item Some studies have distinguished pseudo-bulges and classical bulges according to their S\'ersic index, 
       and claimed that in the $M_{\rm BH} - L_{\rm sph}$ diagram 
-      pseudobulges are offset from the correlation defined by classical bulges. 
+      pseudo-bulges are offset from the correlation defined by classical bulges. 
       Here we test this result with our data.
@@
 In particular, more emphasis is typically given to the slope rather than the intercept of scaling relations, 
-because the slope is the parameter that theoretical models (currently) predict. 
+because the slope is the parameter that theoretical models (currently) 
+predict\footnote{However, more and more attention is being paid to the intercept of black hole mass scaling relations, 
+which plays a major role for the prediction of cosmic gravitational waves background from SMBH binary coalescence 
+(e.g.~\citealt{shannon2015,shankar2016}), 
+the derivation of the SMBH mass function and space density, 
+or the calibration of the reverberation mapping virial factor. }. 
 Several studies (e.g.~\citealt{tremaine2002,graham2007,tundo2007,graham2016review}) 
@@
 
-The remainder of this chapter comprises the published version of the paper 
+The remainder of this Chapter comprises the published version of the paper 
 ``Supermassive Black Holes and Their Host Spheroids. 
@@
 
-\includepdf[pages={1-12}]{ApJ2016.pdf}
+\includepdf[pages={1-12}]{ApJ2016a.pdf}

### 2016-03-17 thesis/recovery-mn.tex
corrections to chapters

@@
-\chapter{The recovery of the $M_{\rm BH} - n_{\rm sph}$ relation}
+\chapter{The Recovery of the $M_{\rm BH} - n_{\rm sph}$ Relation}
 \label{ch:recov-mn}
@@
 
-The remainder of this chapter comprises the published version of the paper 
+The remainder of this Chapter comprises the published version of the paper 
 ``The supermassive black hole mass -- S\'ersic index relations for bulges and elliptical galaxies''

### 2016-03-17 thesis/ubermassive-msigma.tex
corrections to chapters

@@
-\chapter{Monster black holes in Central Cluster Galaxies}
+\chapter{Monster Black Holes in Massive Galaxies}
 \label{ch:msigma}
@@
 as a natural consequence of the fact that these galaxies have experienced more dry mergers 
-than any other early-type galaxy. 
+than any other early-type galaxy (see also \citealt{kormendyho2013}). 
 Their semi-analytical models are based on the idea that parabolic dissipationless dry mergers 
@@
 \end{equation}
-where the nomenclature is self-esplicative. \\
+where the nomenclature is self-explicative. \\
 By imposing the conservation of total energy, we get 
@@
 
-The remainder of this chapter comprises the published version of the paper 
+The remainder of this Chapter comprises the published version of the paper 
 ``Overmassive black holes in the $M_{\rm BH} - \sigma$ diagram 

### 2016-03-21 thesis/abstract.tex
comments on chapters incorporated

@@
 define important constraints about their co-evolution through the cosmic time, 
-and set the boundary conditions (at $z=0$) for theoretical models and simulations of galaxy evolution.
+and set the boundary conditions (at $z=0$) for theoretical models and simulations of galaxy evolution. \\
 
-A careful galaxy decomposition is required to accurately measure a galaxy's spheroid properties. 
-Recent studies have performed structural decomposition 
-for similar samples of galaxies with a direct measure of the black hole mass, 
-but they have not converged to the same conclusions. 
-This is because their best-fit model parameters for the same galaxy were often significantly different 
-due to various systematic effects, 
-and their models for the same galaxy were frequently not consistent with each other in terms of fitted components. 
-Moreover, none of these studies attempted an individual galaxy-by-galaxy comparison of their models 
-with the previous literature. 
-We have now made this comparison, identified the optimal decomposition, 
-and obtained improved black hole mass scaling relations.
+%%A careful galaxy decomposition is required to accurately measure a galaxy's spheroid properties. 
+%%Recent studies have attempted structural decomposition 
+%%for similar samples of galaxies with a direct measure of the black hole mass, 
+%%but they have not converged to the same conclusions. 
+%%This is because their models for the same galaxy were often not consistent with each other in terms of fitted components, 
+%%or, even when they used the same model for the same galaxy, they obtained significantly different best-fit parameters 
+%%due to various systematic effects.
+%%Moreover, none of these studies attempted an individual galaxy-by-galaxy comparison of their models 
+%%with the previous literature. 
+%%We have now made this comparison, identified the optimal decomposition, 
+%%and obtained improved black hole mass scaling relations, 
+%%which are detailed in this thesis. \\
 
@@
 through photometric and isophotal analysis, unsharp masking, auxiliary information extracted from the literature, 
-and, for the first time, kinematic maps, 
-we are able to identify \emph{a priori} the physical galaxy components. 
-Our multicomponent models account for spheroid, large-scale disc, 
-embedded or nuclear discs, spiral arms, bars, rings, halo, extended or unresolved nuclear source and partially depleted core. 
+and, for the first time, kinematic maps -- 
+we were able to identify \emph{a priori} the physical galaxy components. 
+%Our multicomponent models account for spheroid, large-scale disc, 
+%embedded or nuclear discs, spiral arms, bars, rings, halo, extended or unresolved nuclear source and partially depleted core. 
 The combination of photometric and kinematic information was crucial 
@@
 but we found more advantages in the former. 
+Our 66 galaxies constitute the largest sample to date 
+for which these two conditions are satisfied: 
+(\emph{i}) the spheroid structural parameters have been measured accurately and homogeneously;  
+(\emph{ii}) and the black hole mass has been securely estimated with a direct method. 
+%Unlike previous studies that mainly investigated massive early-type galaxies, 
+%our sample contains a large number of spiral galaxies with low black hole masses ($<10^7 \rm~M_\odot$), 
+%and allowed us to better investigate the poorly studied low-mass end of some black hole mass correlations. 
+This thesis presents updates and modifications to several black hole mass scaling relations, 
+and discusses important implications for galaxy evolution models. \\
 
-%Our black hole mass range spans 5 orders of magnitude and allows us to explore the less studied low-mass end of the correlations. 
-%We use Spitzer/IRAC 3.6  mosaics because the 3.6  luminosity is the best tracer of the stellar mass.
+mm + mn \\
 
-We confirm that S\'ersic and core-S\'ersic galaxies follow different trends and therefore are associated to different evolutionary scenarios.
-
-We present updates and modifications to several key black hole mass scaling relations, 
-and discuss the important implications for galaxy evolution models.
-
-Unlike previous studies that mainly investigated high-mass, early-type galaxies, 
-our sample contains a large number of spiral galaxies with low black hole masses ($<10^7 M$), 
-and allows us to better investigate the poorly studied low-mass end of the black hole scaling relations.
-We present updates and modifications to several key black hole mass scaling relations, showing that early-type (elliptical+lenticular) 
-and late-type (spiral) galaxies follow different trends and thus their black holes grow at a different pace, 
-and we discuss the important implications for galaxy evolution models.
+ubermassive \\

### 2016-03-21 thesis/ellicular.tex
comments on chapters incorporated

@@
 Our analysis shows that these galaxies all share the same morphological structure: 
-a stellar spheroidal component with the same properties (massive, compact, and old) as the high-redshift red nuggets 
+a stellar spheroidal component with the same properties (massive, compact, and old) as the high-redshift red nuggets, 
 and an intermediate-scale stellar disc that remains embedded within the spheroid. 

### 2016-03-21 thesis/mn.tex
corrections to chapters
comments on chapters incorporated

@@
 black hole mass and galaxy or spheroid luminosity, 
-in this Chapter we will perform an analogous analysis 
+in this Chapter we perform an analogous analysis 
 to explore the relation between black hole mass and spheroid S\'ersic index ($M_{\rm BH} - n_{\rm sph}$). 
@@
 
-The remainder of this chapter comprises the peer-reviewed version of the paper 
+From a physical point of view, the $M_{\rm BH} - n_{\rm sph}$ correlation is interesting because 
+the S\'ersic index is a measure of the central radial concentration of stars, 
+which dictates the radial distribution of mass within a galaxy's spheroid 
+and therefore determines the dynamical response of stars 
+as measured through the observable $\sigma_*$ \citep{grahamdriver2007}. \\
+
+The remainder of this Chapter comprises the peer-reviewed version of the paper 
 ``Supermassive Black Holes and Their Host Spheroids. 

### 2016-03-22 thesis/abstract.tex
thesis completed

@@
 
-Supermassive black holes in the local Universe obey a surprisingly large number of scaling laws 
-that involve the black hole mass and various properties of the host spheroids. 
+Supermassive black holes in local galaxies obey a surprisingly large number of scaling laws 
+that involve the black hole mass and various properties of the host spheroid or galaxy. 
 These ``black hole mass scaling relations'' reveal a strong symbiosis between galaxies and black holes, 
 define important constraints about their co-evolution through the cosmic time, 
-and set the boundary conditions (at $z=0$) for theoretical models and simulations of galaxy evolution. \\
+and set the boundary conditions (at $z=0$) for theoretical models and simulations of galaxy evolution.
 
-%%A careful galaxy decomposition is required to accurately measure a galaxy's spheroid properties. 
-%%Recent studies have attempted structural decomposition 
-%%for similar samples of galaxies with a direct measure of the black hole mass, 
-%%but they have not converged to the same conclusions. 
-%%This is because their models for the same galaxy were often not consistent with each other in terms of fitted components, 
-%%or, even when they used the same model for the same galaxy, they obtained significantly different best-fit parameters 
-%%due to various systematic effects.
-%%Moreover, none of these studies attempted an individual galaxy-by-galaxy comparison of their models 
-%%with the previous literature. 
-%%We have now made this comparison, identified the optimal decomposition, 
-%%and obtained improved black hole mass scaling relations, 
-%%which are detailed in this thesis. \\
-
-Using \emph{Spitzer} observations at $3.6 ~\mu \rm m$, 
+Using \emph{Spitzer} observations at $3.6~\mu\rm m$, 
 which is the best available wavelength band to trace the stellar mass, 
 we performed state-of-the-art structural decompositions for $66$ galaxies 
-with a direct measure of their black hole mass. 
+with a direct measure of their black hole mass, $M_{\rm BH}$. 
 Thanks to a meticulous inspection of each galaxy's substructure -- 
-through photometric and isophotal analysis, unsharp masking, auxiliary information extracted from the literature, 
+by means of photometric and isophotal analysis, unsharp masking, auxiliary information extracted from the literature, 
 and, for the first time, kinematic maps -- 
 we were able to identify \emph{a priori} the physical galaxy components. 
-%Our multicomponent models account for spheroid, large-scale disc, 
-%embedded or nuclear discs, spiral arms, bars, rings, halo, extended or unresolved nuclear source and partially depleted core. 
 The combination of photometric and kinematic information was crucial 
@@
 Our 66 galaxies constitute the largest sample to date 
-for which these two conditions are satisfied: 
+for which the following two conditions are satisfied: 
 (\emph{i}) the spheroid structural parameters have been measured accurately and homogeneously;  
 (\emph{ii}) and the black hole mass has been securely estimated with a direct method. 
-%Unlike previous studies that mainly investigated massive early-type galaxies, 
-%our sample contains a large number of spiral galaxies with low black hole masses ($<10^7 \rm~M_\odot$), 
-%and allowed us to better investigate the poorly studied low-mass end of some black hole mass correlations. 
 This thesis presents updates and modifications to several black hole mass scaling relations, 
-and discusses important implications for galaxy evolution models. \\
+and discusses important implications for galaxy evolution models.
 
-mm + mn \\
-
-ubermassive \\
+For early-type (elliptical + lenticular) galaxies only, 
+the black hole mass correlates equally well with galaxy luminosity, $L_{\rm gal}$, 
+and spheroid luminosity, $L_{\rm sph}$, or spheroid stellar mass, $M_{\rm *,sph}$. 
+However, when all galaxies (early- and late-type) are considered together, 
+the $M_{\rm BH} - L_{\rm sph}$ relation has a lower level of intrinsic scatter than the $M_{\rm BH} - L_{\rm gal}$ relation. 
+In the $M_{\rm BH} - M_{\rm *,sph}$ diagram, early-type galaxies define a tight linear correlation (a \emph{red sequence}), 
+whereas late-type (spiral) galaxies follow a $2-3$ times steeper \emph{blue sequence}. 
+The spheroid S\'ersic index, $n_{\rm sph}$, scales with $M_{\rm BH}$ 
+in the same way for early- and late-type galaxies. 
+Black holes that appear to be ``overmassive'' compared to expectations from the stellar velocity dispersion, $\sigma_*$, 
+have been theoretically explained with their host galaxies having experienced more dry mergers than any other galaxy. 
+In spite of that, we present empirical evidence supporting a scenario 
+where the host galaxies of such overmassive black holes have undergone the lowest degree of dry merging. 
+Finally, we debunk claims of four overmassive black holes in the $M_{\rm BH} - M_{\rm *,sph}$ diagram 
+by demonstrating that the luminosity of their host spheroids had been considerably underestimated. 
+We show that these four spheroids are unevolved relics of $z=2$ quiescent compact massive spheroids, 
+and we confer about the significant consequences of this.

### 2016-03-22 thesis/conclusions.tex
corrections to chapters
thesis completed

@@
-\chapter{Final remarks and future perspectives}
+\chapter{Final Remarks and Future Perspectives}
 \label{ch:concl}
@@
 
-In Chapter \ref{ch:msigma}, we focused on the $M_{\rm BH} - \sigma$ diagram 
+In Chapter \ref{ch:msigma}, we focused on the $M_{\rm BH} - \sigma_*$ diagram 
 and in particular on the over-massive black holes that have been reported to exist 
@@
 Our analysis suggests that 
-the merger history of the CCGs hosting over-massive black holes in the $M_{\rm BH} - \sigma$ diagram 
+the merger history of the CCGs hosting over-massive black holes in the $M_{\rm BH} - \sigma_*$ diagram 
 is not exceptional, 
-therefore these galaxies should be considered as legitimate members of the $M_{\rm BH} - \sigma$ correlation. 
+therefore these galaxies should be considered as legitimate members of the $M_{\rm BH} - \sigma_*$ correlation. 
 An alternative possibility for the CCGs is that their partially depleted cores 

### 2016-03-22 thesis/declaration.tex
acknowl.
thesis completed

@@
 The work presented in this thesis has been carried out 
-in the Centre for Astrophysics \& Supercomputing 
+in the Centre for Astrophysics and Supercomputing 
 at Swinburne University of Technology between September 2012 and April 2016. 
-The content of the chapters listed below has appeared in refereed journals.
+The content of the chapters listed below has appeared or will appear in refereed journals.
 
@@
 
+\item Chapter \ref{ch:mn} has been accepted for publication in \emph{The Astrophysical Journal} as 
+``Supermassive black holes and their host spheroids 
+III. The $M_{\rm BH} - n_{\rm sph}$ correlation''
+by Giulia A.~D.~Savorgnan.
+
 \item Chapter \ref{ch:msigma} has been published as 

### 2016-03-22 thesis/ellicular.tex
thesis completed

@@
 (also dubbed ``red nuggets'', \citealt{damjanov2009}) have evolved into the bulges 
-of today's massive early-type disc galaxies (see also \citealt{dullograham2013cores} and \citealt{driver2013}). 
+of today's massive early-type disc galaxies (see also \citealt{dullograham2014cores} and \citealt{driver2013}). 
 This view was confirmed by \citet{gds2015}, 

### 2016-03-22 thesis/introduction.tex
thesis completed

@@
 The discovery of ultraluminous quasars at $z>6$ has accentuated the urge to create very massive black hole seeds in a relatively short time 
-(e.g.~\citealt{alexandernatarajan2014,madau2014,lupi2015}). 
+(e.g.~\citealt{alexandernatarajan2014,madau2014,lupi2016}). 
 To date, there have been nearly 50 claims of $z>6$ quasars hosting $\gtrsim 10^9~\rm M_\odot$ black holes 
@@
 than the extraordinary value previously reported. 
-However, \cite{yildirim2015} and \cite{scharwachter2015} confirmed \citeauthor{vandenbosch2012}'s measurement. \\
+However, \cite{yildirim2015} and \cite{scharwachter2016} confirmed \citeauthor{vandenbosch2012}'s measurement. \\
 

### 2016-03-22 thesis/publications.tex
thesis completed

\chapter*{List of publications}

In addition to my six lead-author papers that constitute the main body of this thesis, 
as a result of my PhD project, I participated in the following publications:

\begin{itemize}

\item Shankar, F., Bernardi, M., Sheth, R.~K., Ferrarese, L., Graham, A.~W.,
      {\bf Savorgnan, G.~A.~D.}, Allevato, V., Marconi, A., Laesker, R., Lapi, A. \\
      Selection bias in dynamically-measured super-massive black hole samples: 
      its consequences and the quest for the most fundamental relation \\
      Submitted to \emph{MNRAS}. \\

\item Graham, A.~W., Durr\'e, M., {\bf Savorgnan, G.~A.~D.}, Medling, A.~M., 
      Batcheldor, D., Scott, N., Watson, B., Marconi, A. \\
      A Normal Supermassive Black Hole in NGC 1277 \\
      \emph{ApJ}, 819, 43, 2016. \\

\item Graham, A.~W., Dullo, B., {\bf Savorgnan, G.~A.~D.} \\
      Hiding in Plain Sight: An Abundance of Compact Massive Spheroids in the Local Universe \\
      \emph{ApJ}, 804, 32. 2015. \\

\end{itemize}

### 2016-03-23 thesis/conclusions.tex
m

@@
 and various properties of the host spheroid, 
-aiming at a more profound understanding of the co-evolution between SMBHs and their host galaxies. 
+in the pursuit of a more profound understanding of the co-evolution between SMBHs and their host galaxies. 
 A summary of our principal findings and some additional considerations are presented here. 
@@
 and found that in the former early- and late-type galaxies split into two separate correlations, 
-whereas in the latter all galaxies -- irrespective of their morphological type -- define a single correlation. 
+whereas in the latter relation all galaxies -- irrespective of their morphological type -- define a single correlation. 
 Our $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
@@
 \cite{gds2015} showed that, while the majority of the high-redshift compact massive spheroids 
-have evolved into today's bulges of lenticular and early-type spiral galaxies, 
+have evolved into today's bulges of lenticular and early-type spiral galaxies (see also \citealt{graham2013review}), 
 i.e.~they have accreted a large-scale stellar disc, 
@@
 The universality of this picture is contradicted by galaxies like Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115. 
-These galaxies have classical bulges, 
-they host some of the most massive black holes known ($10^9 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 10^{10}$), 
-but are not the product of major mergers as the majority of today's massive elliptical galaxies. 
+These galaxies have classical bulges and  
+host some of the most massive black holes known ($10^9 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 10^{10}$), 
+but they are not the product of major mergers like the majority of today's massive elliptical galaxies. 
 In effect, these galaxies have conserved their $10 \rm~Gyr$ old compact massive spheroids 

### 2016-03-31 thesis/conclusions.tex
back from gramps

@@
 given the level of detail to which our galaxy decompositions were carried out, 
-we do not consider possible for current automatic routines to reproduce our human-supervised analysis. \\
+we do not consider it possible for current automatic routines to reproduce our human-supervised analysis. \\
 In our 1D galaxy decomposition code, the minimisation routine is based on the Levenberg-Marquardt algorithm, 
@@
 Our subsample of S\'ersic spheroids defines a less steep $M_{\rm BH} - L_{\rm sph}$ 
-sequence than previously reported \citep{grahamscott2013}. 
+sequence (with a log-slope of $1.53 \pm 0.20$) than previously reported ($2.73 \pm 0.55$, \citealt{grahamscott2013}). 
 Looking at the spheroids with S\'ersic index $n_{\rm sph} < 2$, 
@@
 in disagreement with the claims of \citet{sani2011}. 
+However, this might be due to our sample selection and this result might change once reasonable number of galaxies 
+with low-mass black holes ($M_{\rm BH} \lesssim 10^6 \rm~M_\odot$) will be added to the $M_{\rm BH} - L_{\rm sph}$ diagram 
+(see Ciambur et al.~\emph{in preparation}).
 We identified two distinct trends in the $M_{\rm BH} - M_{\rm *,sph}$ diagram, 

### 2016-04-01 thesis/acknowledgement.tex
end

--- 2016-03-10 thesis/acknowledgement.tex
@@
 
-alister, duncan, c blake, greg
+First thanks go to my supervisor Alister, 
+for offering me a PhD project in the country I always dreamt to live in, 
+for guiding me during this long journey, 
+for his patience and support, 
+for all the lessons I've learnt, 
+and for being constantly available to all of his students, 
+regardless of how many late nights he had to spend in the office correcting my writings. 
+Second thanks go to my co-supervisor Duncan for the constructive scientific conversations that we had, 
+for his useful comments and suggestions, 
+and for his genuine interest in making sure that at any stage everything was going well with me. 
+Very special thanks are reserved to Chris Blake, Duncan, Greg, and Karl, 
+for their invaluable, immediate, unconditionate support when I most than ever needed it.
 
-karl,
-
-gonzalo, rob, piero, glenn, anna, angela,
-
-elisa, shaun, silvia, james
-
-gym friends, rock climbing friends
+%To my family and in particular to zia Anna and Suzy for being such enviable badasses 
+%and such great examples. 
+%
+%To my PhD brothers and sisters, Angela, Anna, Gonzalo, Pierluigi, and Rob, 
+%I'm glad I've been on this boat in your excellent company, guys. 
+%Many thanks also to Glenn and Jeff for their informal and very comfortable attitude, 
+%for always encouraging me to do my best and for all the good laughs we've had. 
+%
+%To my irreplaceable friends Elisa, Gonzalo, Greg $\heartsuit$ Anna, James, Shaun, Silvia, 
+%thank you very much for being real. 
+%
+%And last, to Garry, because you might have glimpsed a tinder that already was inside me, 
+%but you are doing a very good job at making it a blaze.

### 2016-04-19 thesis/declaration.tex
end
copyright

@@
 
-\item Chapter \ref{ch:mn} has been accepted for publication in \emph{The Astrophysical Journal} as 
+\item Chapter \ref{ch:mn} has been published as 
 ``Supermassive black holes and their host spheroids 
 III. The $M_{\rm BH} - n_{\rm sph}$ correlation''
-by Giulia A.~D.~Savorgnan.
+in 2016, ApJ, 821, 88, by Giulia A.~D.~Savorgnan.
 
@@
 \end{itemize}
+
+I warrant that I have obtained, where necessary, permission from the copyright owners to use 
+any third part copyright material reproduced in the thesis, 
+or to use any of my own published work in which the copyright 
+is held by another party.

### 2016-04-27 thesis/declaration.tex
copyright no
dispatched

@@
 is held by another party. 
+AAS and Oxford University Press grant back to authors the non-exclusive right of republication, 
+subject only to giving appropriate credit to the journal in which the article was published. 
+This non-exclusive right of republication gives authors the right to approve or deny 
+reproduction of all or part of the article and to post the final published version online.  
+No written permission is required to have the papers reproduced in the thesis with the original journal 
+format\footnote{For more information, see 
+\url{http://iopscience.iop.org/page/copyright} and 
+\url{http://www.oxfordjournals.org/our_journals/mnras/rights_permissions_ras.html} .}.

### 2016-06-28 thesis/mn.tex
figure

@@
 
-The remainder of this Chapter comprises the peer-reviewed version of the paper 
+The remainder of this Chapter comprises the published version of the paper 
 ``Supermassive Black Holes and Their Host Spheroids. 
@@
 by G.~A.~D.~Savorgnan,  
-accepted for publication in the \emph{The Astrophysical Journal}.
+as it appears in Volume 821 of the \emph{The Astrophysical Journal}.
 
-\includepdf[pages={1-10}]{ApJ2016b.pdf}
+\includepdf[pages={1-8}]{ApJ2016b.pdf}

### 2016-06-28 thesis/publications.tex
figure

@@
       its consequences and the quest for the most fundamental relation \\
-      Submitted to \emph{MNRAS}. \\
+      Accepted for publication in \emph{MNRAS}. \\
 

### 2016-06-28 python_codes/decomposition/ProFitErole1.0.1/instruments/plotting.py

@@ -43,6 +43,9 @@ def doFitPanel(fitPanel, rrr, mu, good_rrr, good_mu, bad_rrr, bad_mu, maxsma_arc
 	fitPanel.xaxis.set_minor_locator(minorLocator)
 #  	majorLocator   = MultipleLocator(xaxisMajorLocator)
 #  	fitPanel.xaxis.set_major_locator(majorLocator)
+	ticks = np.arange(0, maxsma_arcsec, 0.5)
+	fitPanel.xaxis.set_ticks(ticks)
+	fitPanel.xaxis.set_major_formatter(ticker.FormatStrFormatter('%0.1f'))
 
 	majorLocator   = MultipleLocator(2)
 	minorLocator   = MultipleLocator(1)
@@ -53,6 +56,8 @@ def doFitPanel(fitPanel, rrr, mu, good_rrr, good_mu, bad_rrr, bad_mu, maxsma_arc
 	ticks = np.arange(int(start)-1, int(end), -2)
 	fitPanel.yaxis.set_ticks(ticks)
 	fitPanel.yaxis.set_major_formatter(ticker.FormatStrFormatter('%0.0f'))
+	
+	fitPanel.tick_params(axis='both', which='major', labelsize=15)
 	
 	#xxx = np.arange(min(rrr),max(rrr),0.1)
 	xxx = rrr
@@ -134,18 +139,21 @@ def doFitPanel(fitPanel, rrr, mu, good_rrr, good_mu, bad_rrr, bad_mu, maxsma_arc
 def doResPanel(resPanel, rrr, good_rrr, resid, good_resid, maxsma_arcsec, sampling, goodIndexes_integer, badIndexes_integer):
 	
 	resPanel.set_xlim([maxsma_arcsec*(-0.1),1.1*maxsma_arcsec])
-	resPanel.set_ylim([+0.199,-0.199])
+	resPanel.set_ylim([+0.25,-0.25])
 	
 	minorLocator   = MultipleLocator(xaxisMinorLocator)
 	resPanel.xaxis.set_minor_locator(minorLocator)
 #  	majorLocator   = MultipleLocator(xaxisMajorLocator)
 #  	resPanel.xaxis.set_major_locator(majorLocator)
+	ticks = np.arange(0, maxsma_arcsec, 0.5)
+	resPanel.xaxis.set_ticks(ticks)
+	resPanel.xaxis.set_major_formatter(ticker.FormatStrFormatter('%0.1f'))
 
 	majorLocator   = MultipleLocator(0.1)
[…]

### 2016-06-28 python_codes/decomposition/ProFitErole1.0.1/makeAllFigures.py

@@ -1,228 +1,0 @@
-#!/usr/bin/python
-
-import numpy as np
-from lmfit import minimize, Parameters, report_fit
-import inspect
-from scipy.ndimage.filters import gaussian_filter1d, correlate1d
-from scipy.special import gammainc, gamma
-import sys
-import pylab
-import matplotlib.pyplot as plt
-import shutil
-
-# local folders of project
-
-from reading.dataFileNames import readInitialSettings
-from reading.ellipseOutput import readEllipseOutput
-from reading.inputModel import readInputModel
-from reading.excludeData import readExcludedData
-from reading.bestFitModel import readBestFitModel
-
-from cls.cls import *
-from cls.settings import *
-from cls.psf import *
-
-from instruments.fitResult import printFitResult
-from instruments.model import buildModel
-from instruments.output import *
-
-from modelComponents.disc import buildDisc
-from modelComponents.ferrer import buildFerrer
-from modelComponents.gaussian import buildGaussian
-from modelComponents.psf import buildPsf
-from modelComponents.psfWing import buildPsfWing
-from modelComponents.sersic import buildSersic
-from modelComponents.truncDisc import buildTruncDisc
-from modelComponents.truncSersic import buildTruncSersic
-from modelComponents.gaussRing import buildGaussRing
-
-from instruments.residual import residual
-from instruments import b_n
-from instruments.plotting import *
-
-
-#################################################### 
-
-terminal = sys.stdout
-
-
-########## FIT AND PLOT ################
-
-def readFitAndPlot(excludedRangeList, galaxyName, axisFit, psfFunction, sampling, bestfitFig, equivalentAxisFit):
-
-    #build data arrays
-    
-    datatab = readEllipseOutput(ellipseOutput) 
-    
-    #exclude R=0 point
-    datatab = datatab[datatab['sma']>0]
-    #exclude data fainter than (3) sky RMS
-    datatab = datatab[datatab['intens']>skyRMS]
-    
-    row = datatab['row']
-    sma = datatab['sma']
-    intens = datatab['intens']
-    intens_err = datatab['intens_err']
-    #pix_var = datatab['pix_var']
-    #rms = datatab['rms']
[…]

### 2016-06-28 python_codes/decomposition/ProFitErole1.0.1/makeCompleteFigure.py

@@ -1,0 +1,228 @@
+#!/usr/bin/python
+
+import numpy as np
+from lmfit import minimize, Parameters, report_fit
+import inspect
+from scipy.ndimage.filters import gaussian_filter1d, correlate1d
+from scipy.special import gammainc, gamma
+import sys
+import pylab
+import matplotlib.pyplot as plt
+import shutil
+
+# local folders of project
+
+from reading.dataFileNames import readInitialSettings
+from reading.ellipseOutput import readEllipseOutput
+from reading.inputModel import readInputModel
+from reading.excludeData import readExcludedData
+from reading.bestFitModel import readBestFitModel
+
+from cls.cls import *
+from cls.settings import *
+from cls.psf import *
+
+from instruments.fitResult import printFitResult
+from instruments.model import buildModel
+from instruments.output import *
+
+from modelComponents.disc import buildDisc
+from modelComponents.ferrer import buildFerrer
+from modelComponents.gaussian import buildGaussian
+from modelComponents.psf import buildPsf
+from modelComponents.psfWing import buildPsfWing
+from modelComponents.sersic import buildSersic
+from modelComponents.truncDisc import buildTruncDisc
+from modelComponents.truncSersic import buildTruncSersic
+from modelComponents.gaussRing import buildGaussRing
+
+from instruments.residual import residual
+from instruments import b_n
+from instruments.plotting import *
+
+
+#################################################### 
+
+terminal = sys.stdout
+
+
+########## FIT AND PLOT ################
+
+def readFitAndPlot(excludedRangeList, galaxyName, axisFit, psfFunction, sampling, bestfitFig, equivalentAxisFit):
+
+    #build data arrays
+    
+    datatab = readEllipseOutput(ellipseOutput) 
+    
+    #exclude R=0 point
+    datatab = datatab[datatab['sma']>0]
+    #exclude data fainter than (3) sky RMS
+    datatab = datatab[datatab['intens']>skyRMS]
+    
+    row = datatab['row']
+    sma = datatab['sma']
+    intens = datatab['intens']
+    intens_err = datatab['intens_err']
+    #pix_var = datatab['pix_var']
+    #rms = datatab['rms']
[…]

### 2016-06-28 python_codes/decomposition/ProFitErole1.0.1/modelComponents/ferrer.py

@@ -1,6 +1,7 @@
 from convolution.psfConvolution import doPsfConvolution
 import numpy as np
 from scipy import special #.hyp2f1
+from scipy import integrate
 
 def buildFerrer(x, params, component, psfFunction, convolve, zeropoint):
 
@@ -22,6 +23,12 @@ def buildFerrer(x, params, component, psfFunction, convolve, zeropoint):
 
 def computeFerrerParameters(r_out, mu_0, alpha, beta):
 	
-	m_tot = mu_0 - 2.5 * np.log10(2 * np.pi * r_out**2 * (0.5 * special.hyp2f1(-alpha, 2/(2-beta), (-beta)/(2-beta), 1)))
+	#m_tot = mu_0 - 2.5 * np.log10(2 * np.pi * r_out**2 * (0.5 * special.hyp2f1(-alpha, 2/(2-beta), (-beta)/(2-beta), 1)))
+
+	x = np.linspace(0.0001, r_out, num=10000)
+	y = (10**(-mu_0/2.5)) * ( 1 - (x/r_out)**(2 - (beta)) )**(alpha)
+
+	y_int = np.trapz(y, x)
+	m_tot = -2.5 * np.log10(y_int)
 	
 	return m_tot
